### 2016-08-25 document/main.tex
Initial commit from existing repo

% === Revtex Declaration ===
\documentclass[aps, 10pt, english, twoside, pra, nofootinbib, longbibliography]{revtex4-1}

% === All of the Packages I use frequently ===
\usepackage{../packages/shared}

% === Drafting Declarations ===
\draftprofile[TC Fraser]{TC}{Red}
\draftprofile[Elie Wolfe]{E}{Green}

% === Numbering For amsthm theorem environments ===
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{\mathcal{I}}
\newcommand{\perm}{\Omega}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\circ}
% When I introduce a new term or definition
\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}

% === Mathematical operators that are denoted with words ===
\newcommand{\setoperator}[1]{%
\expandafter\DeclareDocumentCommand\csname#1\endcsname{O{} O{} m}{{\mathsf{#1}_{##1}^{##2}\!}\br{##3}}%
}

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group

\newcommand{\outc}[1]{o\!\bs{#1}} % Fritz's BBTII notation for observed outcomes
\DeclareDocumentCommand{\prob}{O{} O{}}{\ifthenelse{\equal{#1}{}}{P}{P_{#1}}\ifthenelse{\equal{#2}{}}{}{\!\br{#2}}} % probability distribution
\DeclareDocumentCommand{\probvec}{O{} O{}}{\ifthenelse{\equal{#1}{}}{\mathcal{P}}{\mathcal{P}_{#1}}\ifthenelse{\equal{#2}{}}{}{\!\br{#2}}} % probability distribution vector

% === To allow for labeling of rows and columns of a matrix ===
\usepackage{kbordermatrix}
\renewcommand{\kbldelim}{(} % Left delimiter
\renewcommand{\kbrdelim}{)} % Right delimiter

% === Causal structure formatting for tikz ===
\input{../figures/causal_structures/formatting}

\begin{document}
    \title{Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada \\ University of Waterloo, Waterloo, Ontario, Canada}
    % \author{Elie Wolfe}
    % \email{ewolfe@perimeter@institute.ca}
    % \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada}
    \date{\today}
    \begin{abstract}
        Causal inference aims to identify which observable distributions are compatible with a given causal structure. Compatibility inequalities for the triangle scenario have been obtained and demonstrated to be violated by quantum configurations. Obtaining these inequalities has lead to the development of new computational techniques suitable for large causal structures with numerous outcomes. Numerical optimizations against these inequalities have found new quantum configurations that are incompatible with the triangle scenario, potentially suggesting new quantum resources qualitatively different from those known previously. \todo[TC]{Write a better abstract.}
    \end{abstract}
    \maketitle
    \tableofcontents

    \section{Introduction}
    \todo[TC]{Discuss why the marginal problem is important.}
    \section{Definitions \& Notation}
    \comment[TC]{This entire section should be integrated into the body when logical to do so.}
    \begin{definition}
        Borrowing the notation from \cite{Fritz_2014}, each random variable $v$ has a set of all possible outcomes called the \term{outcome space} or \term{valuation space} and is denoted $O_v$. When referencing a \textit{specific} element of $O_v$ or \textit{valuation} of $v$, the notation $\outc{v}$ is used. This notation generalizes to set of random variables $V = \bc{v_1, \ldots, v_{\abs{V}}}$;
        a specific outcome of $\outc{V} \in O_V$ is used to reference a particular tuple or vector of outcomes,
        \[ \outc{V} \defined \br{\outc{v_1}, \outc{v_2}, \ldots, \outc{v_{\abs{V}}} } = \br{\outc{v}}_{v \in V} \eq \label{eq:outcomespace}\]
        It is important to note that the ordering of events in \cref{eq:outcomespace} is irrelevant. Similarly, the outcome space $O_V$ for a set of random variables $V$ is the \term{valuation product} `$\valprod$' of the individual outcome spaces,
        \[ O_V \defined O_{v_1} \valprod \cdots \valprod O_{v_{\abs{V}}} \]
        Where `$\valprod$' is defined such that for $A \cap B = \emptyset$,
        \[ \outc{A} \valprod \outc{B} \defined \br{\outc{a_1}, \ldots, \outc{a_{\abs{A}}}, \outc{b_1}, \ldots, \outc{b_{\abs{B}}}} = \br{\outc{v}}_{v \in A \cup B} \]
        Often `$\valprod$' will be omitted where there is little ambiguity. When referencing the probability that a set of variables $V$ has outcome $\outc{V}$ (say $v_1 = 0, v_2 = 3$), we intend for the following class of notations to be used interchangeably.
        \[ \prob[V][\outc{V}] = \prob[][\outc{V}] = \prob[][\outc{v_1}\outc{v_2}] = \prob[][v_1 = 0, v_2 = 3] = \prob[][v_2 = 3, v_1 = 0] = \prob[v_1, v_2][03] \]
    \end{definition}

    \begin{definition}
        \label{def:extendable}
        An outcome $\outc{V}$ is said to be \term{extendable} to an outcome $\outc{W}$ (where $V \subseteq W$) if there exists an outcome $\outc{W\setminus V}$ such that $\outc{W} = \outc{W\setminus V} \valprod \outc{V}$.
        \[ \Ext{\outc{V} \to \outc{W}} \iff \exists \outc{W\setminus V} \mid \outc{W} = \outc{W\setminus V} \valprod \outc{V} \]
        The idea being that a \textit{less specific} outcome $\outc{V}$ can be made \textit{more specific} by assigning outcomes to the remaining random variables in $W \setminus V$. If such an outcome $\outc{W\setminus V}$ exists, it is unique.
    \end{definition}

    \begin{definition}
        The set of all extendable outcomes of $\outc{V}$ in $O_{W}$ is called the \term{extendable set} and can be written as,
        \[ \Ext[W]{\outc{V}} \defined \outc{V} \valprod O_{W\setminus V} \defined \bc{\outc{W} \in O_{W} \mid \Ext{\outc{V} \to \outc{W}}} \]
        The extendable set of $\outc{V}$ in $W$ is the set of all outcomes of $O_W$ that \textit{agree} with $\outc{V}$ about valuations for variables in $V$. In this language, two outcomes $\outc{V}$ and $\outc{W}$ are \term{compatible} if they are both extendable to some outcome $\outc{V \cup W}$. Equivalently, $\outc{V}$ and $\outc{W}$ agree on their valuations of $V \cap W$.
        \[ \Com{\outc{V}, \outc{W}} \iff \exists \outc{V \cup W} \mid \Ext{\outc{V} \to \outc{V \cup W}}, \Ext{\outc{W} \to \outc{V \cup W}} \]
    \end{definition}

    \begin{example}
        Consider two sets of random variables $V = \bc{a, b}$ and $W = \bc{a, b, c}$. Clearly $V \subseteq W$; a prerequisite for extendability. Also take all individual outcome spaces to be finite and of order 3: $O_a = O_b = O_c = \bc{1,2,3}$. Then $\outc{V} = \outc{\bc{a,b}} = \br{a = 1, b = 2}$ is extendable to the outcome $\outc{W} = \br{a = 1, b = 2, c = 1}$, and the extendable set of $\outc{V}$ in $O_{W}$ is,
        \[ \Ext[a,b,c]{a = 1, b = 2} = \bc{\br{a = 1, b = 2, c = 1}, \br{a = 1, b = 2, c = 2}, \br{a = 1, b = 2, c = 3}} \]
    \end{example}

    % \begin{definition}
    %     Two outcomes $\outc{V_1}$ and $\outc{V_2}$ over two distinct sets of random variables $V_1$ and $V_2$ are called \term{accordant} or \textit{compatible} if they are mutually realizable. In terms of extendable sets, $\outc{V_1}$ and $\outc{V_2}$ are accordant if there exists an outcome $\outc{V_1 \cup V_2} \in O_{V_1 \cup V_2}$ such that,
    %     \[ \outc{V_1}, \outc{V_2} \subseteq \outc{V_1 \cup V_2}  \]
    %     Accordance between two outcomes is the \textit{opposite} of exclusive.
    % \end{definition}

    \begin{definition}
        \label{def:graph}
        A \term{graph} is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes can represent any object and the edges are pairs of nodes. For convenience of notation, one defines an index set over the nodes denoted $\ind_\nodes$.
        \[ \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{\bc{n_j, n_k} \mid j,k \in \ind_\nodes} \]
    \end{definition}

    \begin{definition}
        \label{def:directed_graph}
        A \term{directed graph} $\graph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes can represent any object and the edges are \textit{ordered} pairs of nodes. For convenience of notation, one defines an index set over the nodes denoted $\ind_\nodes$.
        \[ \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{n_j \to n_k \mid j,k \in \ind_\nodes} \]
    \end{definition}

    \begin{definition}
        \label{def:graph_terms}
        The following definitions are common language in directed graph theory. Let $n, m \in \nodes$ be example nodes of the graph $\graph$.
        \begin{itemize}
            \item The \term{parents of a node}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
            \item The \term{children of a node}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
            \item The \term{ancestry of a node}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$
        \end{itemize}
        All of these terms can be generalized to sets of nodes $N \subseteq \nodes$ through union over the elements,
        \begin{itemize}
            \item The \term{parents of a node set}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
            \item The \term{children of a node set}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
            \item The \term{ancestry of a node set}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
        \end{itemize}
        Moreover, an \term{induced subgraph} of $\graph$ due to a set of nodes $N \subseteq \nodes$ is the graph composed of $N$ and all edges $e \in \edges$ of the original graph that are contained in $N$.
        \[ \Sub[\graph]{N} \defined \br{N, \bc{e_i \mid i \in \ind_\edges, e_i \subseteq N}}\]
        An \term{ancestral subgraph} of $\graph$ due to $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
    \end{definition}

    \begin{definition}
        \label{def:dag}
        A \term{directed acyclic graph} or \term{DAG} $\graph$ is an directed graph \cref{def:directed_graph} with the additional property that no node $n$ is in its set of \term{ancestors}.
        \[ \forall n \in \nodes : n \notin \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}\]
        Notice the difference between using the natural numbers $\mathbb{N}$ to distinguish \textit{ancestors} from \textit{ancestry}.
    \end{definition}

    \begin{definition}
        \label{def:hypergraph}
        A \term{hypergraph} denoted $\hgraph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{hyperedges} respectively where the nodes can represent any object and the hyperedges are \textit{subsets} of nodes. For convenience of notation, one defines an index set over the nodes and hyperedges of a hypergraph $\hgraph$ denoted $\ind_\nodes$ and $\ind_\edges$ respectively.
        \[ \hgraph = \br{\nodes, \edges} \quad \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{e_i \mid i \in \ind_\edges, e_i \subseteq \nodes} \]
        Note that whenever the hyperedge or node index is arbitrary, it will be omitted. There is a dual correspondence between hyperedges $e \in \edges$ and nodes $n \in \nodes$ in a Hypergraph. A hyperedge $e$ is viewed as a set of nodes $\bc{n_i}$, and a node $n$ can be viewed as the set of hyperedges $\bc{e_i}$ that contain it.
    \end{definition}

    \begin{definition}
        \label{def:hgraph_trans}
        A \term{hypergraph transversal} (or edge hitting set) $\trans$ of a hypergraph $\hgraph$ is a set of nodes $\trans \subseteq \nodes$ that have non-empty intersections with every hyperedge in $\edges$.
        \[ \trans = \bc{n_i \in \nodes \mid i \in \ind_\trans } \quad \forall e \in \edges : \trans \cap e \neq \emptyset \]
    \end{definition}

    \begin{definition}
        A \term{necessary node} of a transversal $\trans$ is a node $n$ such that $\trans \setminus n$ is no longer a valid transversal. The set of all necessary nodes is denoted $\Nec{\trans}$,
        \[ \Nec{\trans} = \bc{n \in \trans \mid \exists e \in \edges : \br{\trans \setminus n} \cap e = \emptyset} \]
        An \term{unnecessary node} of a transversal $\trans$ is any node that is \textit{not} necessary. The set of all unnecessary nodes is denoted $\UnNec{\trans}$,
        \[ \UnNec{\trans} = \trans \setminus \Nec{\trans} \]
        A \term{minimal hypergraph transversal} $\trans$ is any valid transversal of $\hgraph$ where every node $n$ is \textit{necessary}.
        \[ \trans = \Nec{\trans} \]
    \end{definition}

    \begin{definition}
        A \term{weighted hypergraph} $\hgraph_\weights$ is a regular hypergraph satisfying \cref{def:hypergraph} equipped with a set of weights $\weights$ ascribed to each node such that a weighted hypergraph is written as a triplet $\br{\weights, \nodes, \edges}$.
        \[ \weights = \bc{w_i \mid i \in \ind_\nodes, w_i \in \R} \]
        One would say that a particular node $n_i$ carries weight $w_i$ for each $i \in \ind_\nodes$.
    \end{definition}

    \begin{definition}
        A \term{bounded transversal} of a weighted hypergraph $\hgraph_\weights$ is a transversal $\trans$ of the unweighted hypergraph $\hgraph$ and a real number $t$ (denoted $\trans_{\leq t}$) such that the sum of the node weights of the transversal is bounded by $t$.
        \[ \trans_{\leq t} = \bc{n_i \mid i \in \ind_\trans} \quad \text{s.t.} \sum_{j\in\ind_\trans} w_j \leq t \]
        One can definte analogous \term{(strictly) upper/lower bounded transversals} by considering modifications of the notation: $\trans_{< t}, \trans_{\geq t}, \trans_{> t}$.
    \end{definition}

    \begin{definition}
        A \term{causal structure} is simply a DAG with the extra classification of each node into one of two categories; the \term{latent nodes} and \term{observed nodes} denoted $\nodes_L$ and $\nodes_O$. The latent nodes correspond to random variables that are either hidden through some fundamental process or cannot/will not be measured. The observed nodes are random variables that are measurable. Every node is either latent or observed and no node is both:
        \[ \nodes_L \cap \nodes_O = \emptyset \qquad \nodes_L \cup \nodes_O = \nodes \]
    \end{definition}

    \begin{definition}
        The \term{product distribution} two distributions is denoted as usual with $\times$ and is defined as,
        \[ \br{\prob[v] \times \prob[w]}\br{\outc{v}, \outc{w}} \defined \prob[v][\outc{v}]\prob[w][\outc{w}] \]
        A product distribution of $k$ distributions is defined recursively,
        \[ \prod_{i=1}^{k} \prob[v_i] \defined \br{\prob[v_1] \times \cdots \times \prob[v_k]} \]
    \end{definition}

    \begin{definition}
        The \term{marginalization} of a distribution $\prob[v \cup w]$ to the distribution $\prob[v]$ is denoted $\sum_{w} \prob[v \cup w] = \prob[v]$ and is defined such that,
        \[ \forall \outc{v} \in O_v : \br{\sum_{w} \prob[v, w]}\br{\outc{v}} \defined \sum_{o\bs{w} \in O_w} \prob[v, w][\outc{v}, \outc{w}] \]
    \end{definition}

    \begin{definition}
        Following common notation used in \cite{Fritz_2011}, we use the notation $\bs{k} = \br{1, \ldots, k}$ to be a finite index set. Moreover, when referencing a finite set with $k$ elements, we can write,
        \[ A_{\bs{k}} \defined \bc{A_i}_{i \in \bs{k}} = \bc{A_1, \ldots, A_k} \]
    \end{definition}

    \todo[TC]{How many definitions do I need to write??}

    \section{Triangle Scenario}
    \todo[TC]{Discuss the Triangle Scenario, previous work done on it, etc.}

    Figure 8 of Appendix E \cite{Henson_2014}
    Figure 1 of \cite{Inflation}

    Focusing on the inflation depicted in \cref{fig:inflated_triangle_scenario}, we obtained the maximally pre-injectable sets through the procedure outlined in \cite{Inflation}.
    \begin{equation*}
        \eq \label{eq:pre-injectable_triangle_scenario}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
    As can be counted, there are $12$ maximally pre-injectable sets which will be indexed $1$ through $12$ in the order seen above ($\bc{V_1, \ldots, V_{12}}$)

    \begin{figure}
    \begin{center}
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../figures/causal_structures/triangle_scenario}}
            \caption{The casual structure of the Triangle Scenario. Three variables $A,B,C$ are observable and illustrated as triangles, while $X, Y, Z$ are latent variables illustrated as circles.}
            \label{fig:triangle_scenario}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \scalebox{0.8}{\input{../figures/causal_structures/inflated_triangle_scenario}}
            \caption{An inflated causal structure of the Triangle Scenario \cref{fig:triangle_scenario}.}
            \label{fig:inflated_triangle_scenario}
        \end{minipage}
    \end{center}
    \end{figure}

    \section{Compatibility, Contextuality and the Marginal Problem}
    \label{sec:comp_con_mp}
    In order to determine if a given marginal distribution $\prob[V]$ or set of marginal distributions $\prob[V_{\bs{k}}] \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ is compatible with a causal structure $\graph$, one should first formalize what is meant by \textit{compatible}.

    \begin{definition}
        A set of \term{causal parameters} for a particular causal structure $\graph$ is the specification of a conditional distribution for every node $n \in \nodes$ given it's parents in $\graph$.
        \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
    \end{definition}
    \begin{definition}
        \label{def:compatible}
        A marginal distribution $\prob[V]$ is \term{compatible} with a causal structure $\graph$ (where it is assumed that $V \subseteq \nodes_O$) if there exists a \textit{choice} of causal parameters $\bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes}$ such that $\prob[V]$ can be \textit{recovered} from the following series of operations:
        \begin{enumerate}
            \item First obtain a joint distribution over \textit{all} nodes of of the causal structure,
            \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] \]
            \item Then marginalize over the latent nodes of $\graph$,
            \[ \prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes] \]
            \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$,
            \[ \prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O] \]
        \end{enumerate}
        A set of marginal distributions $\prob[V_{\bs{k}}]$ is compatible with $\graph$ if each of the distributions can be made compatible by the \textit{same} choice of causal parameters.
        A distribution $\prob[V]$ or set of distributions $\prob[V_{\bs{k}}]$ is said to be \term{incompatible} with a causal structure if there \textit{does not exist} a set of causal parameters with the above mentioned property.

        \todo[TC]{Source this?}
    \end{definition}
    Operations 2 and 3 of \cref{def:compatible} are related to the \textit{marginal problem}.
    \begin{definition}
        \label{def:marginal_problem}
        \term{The Marginal Problem:} Given a set of distributions $\prob[V_{\bs{k}}] \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ where $V_i \subseteq \mathcal{V}$ for some set of random variables $\mathcal{V}$ and $k \geq 2$, does there exist a joint distribution $\prob[\mathcal{V}]$ such that each given distribution $\prob[V_i]$ can be obtained from marginalizing $\prob[\mathcal{V}]$?
        \[ \forall i \in \bs{k} : \prob[V_i] = \sum_{\mathcal{V} \setminus V_i} \prob[\mathcal{V}] \]
        Typically (although not strictly necessary), $\mathcal{V}$ is taken to mean the union of all $V_i$'s.
        \[ \mathcal{V} = V_1 \cup \cdots \cup V_k = \bigcup_{i\in\bs{k}} V_i \eq \label{eq:marginals_union} \]
    \end{definition}

    \todo[TC]{Mention polytope perspective and existing methods}
    \begin{definition}
        \label{def:marginal_model}
        A reoccurring motif of these discussions will be the set of distributions $\prob[V_{\bs{k}}] \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ mentioned in \cref{def:marginal_problem}. In agreement with \cite{Fritz_2011} we will call this set of distributions a \term{marginal model} and denote it $\prob_{V_{\bs{k}}}$ provided that they are \textit{compatible}:
        \[ \forall i \neq j \text{ if } V_i \cap V_j \neq \emptyset \text{ then } \sum_{V_i \setminus V_j} \prob[V_i] = \sum_{V_j \setminus V_i} \prob[V_j]  \]
        We call the set of subsets $V_{\bs{k}} \defined \bc{V_1, \ldots, V_k}$ the marginal contexts or the \term{maximal marginal scenario} $V_{\bs{k}}$\footnote{Rigorously speaking as defined by \cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where $V' \in V_{\bs{k}}$ whenever $V' \subseteq V_i$ for some $i$. ``Maximal'' refers to the restriction that $\forall i,j : V_i \not \subseteq V_j$.} and an individual $V_i$ a \term{marginal context}. The union of all contexts is denoted $\mathcal{V}$ and define it exactly as in \cref{eq:marginals_union}.

        Following definition 2.3 in \cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a solution to the marginal problem and \term{non-contextual} otherwise.

        In addition, we elect to define the \term{marginal outcomes} $O_{V_{\bs{k}}}$ to be the set of all outcomes belonging to outcomes of the marginal contexts.
        \[ O_{V_{\bs{k}}} \defined O_{V_1} \cup \cdots \cup O_{V_k} = \bigcup_{i \in \bs{k}} O_{V_i} \]
        % By an intended abuse of notation, we say that a particular outcome is an ``element'' of $O_{V_{\bs{k}}}$ if it is an element of $O_{V_i}$ for some $i \in \bs{k}$.
        % \[ \outc{V_i} \in O_{V_{\bs{k}}} \]
        Note that $O_{V_{\bs{k}}}$ is \textit{not} a valid outcome space, analogous to the fact that $P_{V_{\bs{k}}}$ is \textit{not} a probability distribution. Instead $O_{V_{\bs{k}}}$ is a collection of outcome spaces just as $P_{V_{\bs{k}}}$ is a collection of distributions.
    \end{definition}

    \begin{definition}
        A \term{causal compatibility inequality} $\mathcal{I}_{V_{\bs{k}}}$ for a marginal scenario $V_{\bs{k}}$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob_{V_{\bs{k}}}$. Whenever the marginal scenario $V_{\bs{k}}$ in question is evident by context, the subscript of $\mathcal{I}_{V_{\bs{k}}}$ will be dropped leaving just $\mathcal{I}$.
    \end{definition}
    \todo[TC]{Discuss Compatibility, connection to cooperative games/resources, bell incompatibility?}
    \todo[TC]{Connection between contextuality and Compatibility via the marginal problem for causal parameters}
    \todo[TC]{Discuss what is meant by a `complete' solution to the marginal problem}
    \todo[TC]{Maybe define the possibilistic marginal problem for later}
    \section{Summary of the Inflation Technique}
    \label{sec:summary_inflation}
    The causal inflation technique, first pioneered by Wolfe, Spekkens, and Fritz \cite{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of Ref. \cite{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a probability distribution is compatible or incompatible with a given causal structure. As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure. Copies of the original nodes are distinguished by an additional subscript called the \term{copy-index}. For example node $A$ of \cref{fig:triangle_scenario} has copies $A_1, A_2, A_3, A_4$ in the inflation of \cref{fig:inflated_triangle_scenario}. Following the notions of Ref. \cite{Inflation}, all such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'. A copy-index is effectively arbitrary, so $A'$ will refer to an arbitrary inflated copy of $A$.
    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if $X = Y$ upon removal of the copy-index. Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
    \begin{definition}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
    \end{definition}
    The motivation being that since the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$. To do this, first notice that every compatible joint distribution $\prob[\nodes]$ uniquely defines a set of causal parameters for $\graph$.
    \[ \forall n \in \nodes : \prob[n\mid \Pa[\graph]{n}] = \sum_{\nodes \setminus n} \prob[\nodes] \eq \label{eq:unique_causal_parameters}\]
    Now since \cref{eq:inflation_defn} enforces that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$, one can create a set of \term{inflated causal parameters} using \cref{eq:unique_causal_parameters},
    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \]
    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course not all compatible joint distributions on $\nodes'$ are constructed in this way; all that is demonstrated is that all joint distributions constructed in this way are compatible.}.
    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \]
    This is known as the \term{weak inflation lemma}; compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$. Before generalizing to the inflation lemma, a careful observation needs to be made. For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$ over $N$ induces a compatible marginal distribution $\prob[N']$ over $N'$. In fact since $N'$ contains no duplicate nodes up to copy index (simply because $N \sim N'$ and $N$ cannot contain duplicate nodes), $\prob[N] = \prob[N']$. We refer such sets $N'$ as the \term{injectable sets} of $\graph'$ and $N$ the \term{images of the injectable sets} of $\graph$.
    \begin{align*}
        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
    \end{align*}

    \begin{lemma}
        \label{lem:inflation}
        \term{The Inflation Lemma} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
        This is lemma 3 of \cite{Inflation}.
    \end{lemma}

    The inflation lemma is the most important result of the causal inflation technique \cite{Inflation}. The contrapositive version of \cref{lem:inflation} is a powerful tool for determining compatibility. Any compatibility constraint on marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ of the inflated causal structure $\graph'$ correspond to valid compatibility constraints on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure. Corollary 5 of \cite{Inflation} proves this explicitly for incompatibility inequalities $\mathcal{I}$; which the remainder of this work focuses on.  Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$). Therefore, in situations where latent nodes are present in $\graph$, one only needs to consider injectable sets that are composed of \textit{observable nodes}.

    In this work, we obtain inequalities that constrain the set of injectable marginal models $\bc{\prob[N'] \mid N' \in \ImInj[\graph]{\graph'}}$ for the inflated Triangle Scenario of \cref{fig:triangle_scenario} by considering the marginal problem (see \cref{sec:comp_con_mp}) for the set of \term{maximally pre-injectable sets}\footnote{The set of all pre-injectable sets forms a topological \textit{simplicial conplex}. `Maximal' refers to the pre-injectable sets that are no proper subset of another.}. As defined by \cite{Inflation}, a pre-injectable set $V$ is a subset of $\nodes'$ that can be written as the decomposed into the union of injectable sets $V = \bigcup_i N'_i$ where $\bc{N'_i \in \Inj[\graph]{\graph'}}$ that are mutually \term{ancestrally independent},
    \[ \forall i,j : N'_i \ancestralindep N'_j \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset  \]
    In doing so, any distribution over all nodes of a pre-injectable set $\prob[\cup_i N'_i]$ will factorize according to graphical $d$-separation conditions \cite{Pearl_2009},
    \[ \prob[V] = \prob[\cup_i N'_i] = \prod_{i}\prob[N'_i] \]
    This turns linear inequalities over the pre-injectable distributions into polynomial inequalities over the injectable distributions, allowing one to replace all such distributions with equivalent distributions over the original random variables of $\nodes$. $\PreInj[\graph]{\graph'}$ will denote the set of all pre-injectable sets.

    \section{The Fritz Distribution}
    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario. Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
    \begin{align*}
    \eq \label{eq:fritz_dist}
    \begin{split}
    \prob[F][111] = \prob[F][221] = \prob[F][412] = \prob[F][322] = \prob[F][233] = \prob[F][143] = \prob[F][344] = \prob[F][434] &= \f{1}{32}\br{2 + \sqrt{2}} \\
    \prob[F][121] = \prob[F][211] = \prob[F][422] = \prob[F][312] = \prob[F][243] = \prob[F][133] = \prob[F][334] = \prob[F][444] &= \f{1}{32}\br{2 - \sqrt{2}}
    \end{split}
    \end{align*}
    Here the notation $\prob[F][abc] = \prob[ABC][abc] = \prob[][A=a,B=b,C=c]$ is used. The Fritz distribution $\prob[F]$ can be realized with the following quantum configuration:
    \begin{equation}
    \begin{gathered}
    \label{eq:fritz_quantum_realization}
    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+} \\
    M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
    M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
    M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gathered}
    \end{equation}
    Where for convenience of notation $\psi_x$ is used to denote the superposition,
    \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.
    Fritz first proved it's incompatibility \cite{Fritz_2012} by showing $C$ acts a moderator to ensure measurement pseudo-settings for $A$ and $B$ are independent, satisfying non-broadcasting requirements for the standard Bell scenario. In fact, by coarse-graining outcomes for $A$ and $B$ and treating $C$ as a measurement-setting moderator, $P_F$ maximally violates the CHSH inequality. To illustrate this, begin with the CHSH inequality \cite{CHSH_Original},
    \[ \ba{AB|S_A=1, S_B=1} + \ba{AB|S_A=1, S_B=2} + \ba{AB|S_A=2, S_B=1} - \ba{AB|S_A=2, S_B=2} \leq 2 \eq \label{eq:CHSH}\]
    Where $\ba{AB|S_A=i, S_B=j}$ is the correlation between $A$ and $B$ given the measurement settings for $A$ ($B$) is $i$ ($j$) respectively. Next each of $C$'s outcomes become the conditioned settings in \cref{eq:CHSH},
    \[ \ba{AB|C=2} + \ba{AB|C=3} + \ba{AB|C=4} - \ba{AB|C=1} \leq 2 \eq \label{eq:chsh_c}\]
    Finally, specifying the two outcome coarse-graining as $\bc{1,2,3,4} \rightarrow \bc{\br{1,4}, \br{2,3}}$ gives a definition of correlation,
    \[ \ba{AB} \defined 2\bc{\prob[][11] + \prob[][14] + \prob[][41] + \prob[][44] + \prob[][22] + \prob[][23] + \prob[][32] + \prob[][33]} - 1 \]
    Which when applied to the Fritz distribution \cref{eq:fritz_dist} gives the following correlations:
    \begin{gather*}
    \ba{AB|C=2} = 2 \bc{\f{1}{32}\bs{2\br{2+\sqrt{2}}+2\br{2-\sqrt{2}}}} - 1 = \f{\sqrt{2}}{2} \\
    \ba{AB|C=3} = \ba{AB|C=4} = \f{\sqrt{2}}{2} \quad \ba{AB|C=1} = -\f{\sqrt{2}}{2}
    \end{gather*}
    Which when applied to \cref{eq:chsh_c} gives the familiar Tsirelson violation of $2\sqrt{2} \not\leq 2$ \cite{Cirelson_1980}.

    Before continuing it is worth noting that \cref{eq:fritz_dist} is non-unique. Any distribution that is equal to \cref{eq:fritz_dist} via a permutation of outcomes or exchange of parties is also referred to as a Fritz distribution. Moreover, the quantum realization of \cref{eq:fritz_quantum_realization} is non-unique. In fact, \cref{eq:fritz_quantum_realization} is not the realization that Fritz originally had in mind. Nonetheless \cref{eq:fritz_dist} is taken as \textit{the} Fritz distribution for concreteness throughout this paper.

    \todo[TC]{Summarize Problem 2.17 in fritz BBT, make it more formal}
    \section{Certificate Inequalities}
    \label{sec:certificate_inequalities}
    \subsection{Casting the Inflated Marginal Problem as a Linear Program}
    After obtaining the maximal pre-injectable sets associated with a particular inflation, one can write the marginal problem of \cref{def:marginal_problem} as a linear program. The key observation is that marginalization is a \textit{linear} operator that can be performed via a matrix multiplication. To do this, we will define the \textit{marginalization matrix}.
    \begin{definition}
        The \term{marginalization matrix} $M$ for a marginal scenario $V_{\bs{k}} = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} outcomes $\outc{\mathcal{V}} \in O_{\mathcal{V}}$ and the rows are indexed by \textit{marginal} outcomes corresponding to all outcomes $\outc{V_i} \in O_{V_{\bs{k}}}$. The entries of $M$ are populated whenever a row index is extendable to a column index.
        \[ M\bs{\outc{V_i}, \outc{\mathcal{V}}} = \begin{cases}
            1 & \Ext{\outc{V_i} \to \outc{\mathcal{V}}} \\
            0 & \text{otherwise}
        \end{cases} \]
        The marginalization matrix has $\abs{O_\mathcal{V}}$ columns and $\abs{O_{V_{\bs{k}}}} = \sum_{i=1}^{k} \abs{O_{V_i}}$ rows. The number of non-zero entries of $M$ is a simple expression,
        \[ \sum_{i=1}^{k} \abs{O_{V_i}}\abs{O_{\mathcal{V} \setminus V_i}} = \sum_{i=1}^{k} \abs{O_{\mathcal{V}}} = k\abs{O_{\mathcal{V}}} \]
        This is due to the fact that each elements of $\bc{V_1, \ldots, V_k}$ contributes a single non-zero entry to each column of $M$, resulting in $k\abs{O_\mathcal{V}}$ total non-zero entries.
    \end{definition}
    \todo[TC]{Computationally Efficient generation?}

    To illustrate this concretely, consider the following example:
    \begin{example}
        Suppose one has $4$ binary random variables $\mathcal{V} = \bc{a,b,c}$ in mind and $2$ subsets $V_{\bs{2}} = \bc{\bc{a,c}, \bc{b}}$. Then the marginalization matrix is:
        \[ M = \kbordermatrix{
            (a,b,c) = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
            (a=0, c=0) & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
            (a=0, c=1) & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 \\
            (a=1, c=0) & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 \\
            (a=1, c=1) & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 1 \\
            (b=0)      & 1 & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
            (b=1)      & 0 & 0 & 1 & 1 & 0 & 0 & 1 & 1
        } \]
    \end{example}

    In order to describe how marginalization can be written as matrix multiplication $M \cdot x = b$, we need to describe how to define two more quantities:

    \begin{definition}
        The \term{joint distribution vector} $\probvec[\mathcal{V}]$ for a probability distribution $\prob[\mathcal{V}]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\mathcal{V}]$ assigns to each outcome of $\outc{\mathcal{V}}$ of $O_\mathcal{V}$. $\probvec[\mathcal{V}]$ shares the same indices as the \textit{column} indices of $M$.
        \[ \probvec[\mathcal{V}]^\intercal = \bs{\prob[\mathcal{V}][\outc{\mathcal{V}}]}_{o\bs{\mathcal{V}} \in O_{\mathcal{V}}} \]
    \end{definition}
    \begin{definition}
        The \term{marginal distribution vector} $\probvec[V_{\bs{k}}]$ for a marginal model $\prob[V_{\bs{k}}] = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $O_{V_{\bs{k}}}$. $\probvec[V_{\bs{k}}]$ shares the same indices as the \textit{row} indices of $M$.
        \[ \probvec[V_{\bs{k}}]^\intercal = \bs{\prob[V_i][\outc{V_i}] }_{o\bs{V_i} \in O_{V_{\bs{k}}}} \]
    \end{definition}
    The marginal and joint distribution vectors are related via the marginalization matrix $M$. Given a joint distribution vector $\probvec[\mathcal{V}]$ one can obtain the marginal distribution vector $\probvec[V_{\bs{k}}]$ by multiplying $M$ by $\probvec[\mathcal{V}]$.
    \[ \probvec[V_{\bs{k}}] = M \cdot \probvec[\mathcal{V}] \eq \label{eq:marginal_problem_matrix} \]
    \todo[TC]{Discuss non-unique but consistent ordering of $M$, $\probvec[\mathcal{V}]$ and $\probvec[V_{\bs{k}}]$}

    The marginal problem can now be rephrased in the language of the marginalization matrix. Suppose one obtains a marginal distribution vector $\probvec[V_{\bs{k}}]$. The marginal problem becomes equivalent to the question: \textit{Does there exist a joint distribution vector $\probvec[\mathcal{V}]$ such that \cref{eq:marginal_problem_matrix} holds?}

    \begin{definition}
        \label{def:marginal_linear_program}
        \term{The Marginal Linear Program} is the following linear program:
        \begin{alignat*}{2}
            & \text{minimize:} \quad&& \emptyset \cdot x\\
            & \text{subject to:} && x \succeq 0 \\
            & && M \cdot x = \probvec[V_{\bs{k}}]
        \end{alignat*}
        If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries). The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:marginal_problem_matrix} and is a valid joint distribution vector. Therefore feasibility implies that $\prob[\mathcal{V}] = x$, solving the marginal problem with positive result. Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\prob[\mathcal{V}]$ over all random variables.
    \end{definition}
    \begin{definition}
        \label{def:dual_marginal_linear_program}
        \term{The Dual Marginal Linear Program} is the dual of \cref{def:marginal_linear_program} formulated via a procedure similar to \cite{Lahaie_2008}:
        \begin{alignat*}{2}
            & \text{minimize:} \quad&& y \cdot \probvec[V_{\bs{k}}]\\
            & \text{subject to:} && y \cdot M \succeq 0
        \end{alignat*}
        Where $y$ is a real valued vector with the same length as $\probvec[V_{\bs{k}}]$.
    \end{definition}
    \subsection{Infeasibility Certificates}
    \label{sec:infeasibility_certificates}
    The dual marginal linear program also provides an answer to the marginal problem. To prove this, first notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints are satisfied. Secondly if $y \cdot M \succeq 0$ and $x \succeq 0$, then the following must hold if the primal is feasible:
    \[ y \cdot \probvec[V_{\bs{k}}] =  y \cdot M \cdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
    Therefore the \textit{sign} of the dual value $d \defined \min \br{y \cdot \probvec[V_{\bs{k}}]}$ solves the marginal problem. If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore the marginal problem has negative result. Likewise if $d$ satisfies \cref{eq:dual_marginal_ineq}, then a joint distribution $\prob[\mathcal{V}]$ exists. Before continuing, an important observation needs to be made. If $d \geq 0$, then it is exactly $d = 0$, due to the existence of the trivial $y = \emptyset$. This observation is an instance of the \textit{Complementary Slackness Property} of \cite{Bradley_1977}. \comment[TC]{Is this really the CSP?} Moreover, if $d < 0$, then it is unbounded $d = -\inf$. This latter point becomes clear upon recognizing that for any $y$ such that $d < 0$, another $y'$ can be constructed by multiplying $y$ by a real constant $\al$ greater than one such that,
    \[ y' = \al y \mid \al > 1 \implies d' = \al d < d \]
    Since a more negative $d'$ can always be found, it must be that $d$ is unbounded. This is a demonstration of the fundamental \textit{Unboundedness Property} of \cite{Bradley_1977}; if the dual is unbounded, then the primal is infeasible.

    \comment[TC]{\href{http://web.stanford.edu/~ashishg/msande111/notes/chapter4.pdf}{Farkas's lemma} here?}

    \begin{definition} An \term{infeasibility certificate} is any vector $y$ that satisfies the constraints of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec[V_{\bs{k}}]$.
    \[ y \in \R^{\abs{O_{V_{\bs{k}}}}} : y \cdot M \succeq 0, \quad y \cdot \probvec[V_{\bs{k}}] < 0 \]
    Furthermore, any $y$ satisfying $y \cdot M \succeq 0$ induces a \term{certificate inequality} that constraints the space of marginal distribution vectors which takes the symbolic form of \cref{eq:dual_marginal_ineq},
    \[ y \cdot \probvec[V_{\bs{k}}] \geq 0 \]
    Where the entries of the certificate $y$ act as coefficients for the entries of $\probvec[V_{\bs{k}}]$.
    \end{definition}
    \todo[TC]{Discuss Infeasibility Certificates basis}

    \begin{example}
        The marginal problem for the inflated causal structure $\graph'$ depicted in \cref{fig:inflated_triangle_scenario} concerns itself with the pre-injectable marginal scenario $\PreInj[\graph]{\graph'} = V_{\bs{12}} = \bc{\prob[V_1], \ldots, \prob[V_{12}]}$. The marginalization matrix $M$ has $16,896$ rows and $16,777,216$ columns.
        \begin{align*}
            &\text{\# Rows} = \sum_{i=1}^{12} \abs{O_{V_i}} = \sum_{i=1}^{12} 4^{\abs{V_i}} = 4 \cdot 4^6 + 8 \cdot 4^3 = 16,896 \\
            &\text{\# Columns} = \abs{O_{\nodes'}} = 4^{\abs{\nodes'}} = 4^{12} = 16,777,216
        \end{align*}
        With $12 \cdot 4^{12} = 201,326,592$ non-zero entries.
    \end{example}

    \todo[TC]{Discuss the certificate inequalities we found.}

    \[ \mathcal{I}\tsb{Mosek-Cert}, \mathcal{I}\tsb{Cert} \]

    \section{Logical Implications of Non-Contextuality}

    Section \ref{sec:certificate_inequalities} discusses how one can obtain a valid compatibility inequality that witnesses incompatibility for a particular marginal model $\prob_{V_{\bs{k}}}$ by writing the marginal problem as a linear program.
    \todo[TC]{Motivate why certificates are not enough, want many solutions, want logical foundation}
    \subsection{Logical Implications \& Inequalities}
    \label{sec:implication_inequalities}
    Following the work conducted by Mansfield and Fritz \cite{Mansfield_2012}, we consider a possibilistic implications of the form,
    \[ a \implies c_1 \lor \cdots \lor c_m = \bigvee_{i\in \bs{m}} c_i \eq \label{eq:1n_pi}\]
    Where $a$ and each of the $c_i$'s are simply events or outcomes of a particular set of variables. The letter `$a$' is chosen for the event $a$ since it takes the place of the logical \term{antecedent} of \cref{eq:1n_pi}. Likewise, the letter `$c$' is chosen to represent logical \term{consequents}. We refer to the set of all $c_i$'s simply as $C = \bc{c_i \mid i \in \bs{m}}$. The implication \cref{eq:1n_pi} can be read as \textit{whenever $a$ occurs, at least one element of $c$ also occurs}.

    It is possible to turn possibilistic implications into probabilistic inequalities by recognizing that the logical implication of \cref{eq:1n_pi} induces the inequality,
    \[ \prob[][a] \leq \prob[][\bigvee_{i=1}^{m} c_i] \]
    Furthermore utilizing Boole's inequality,
    \[ \prob[][\bigvee_{i=1}^{m} c_i] \leq \sum_{i=1}^{m} \prob[][c_i] \eq \label{eq:booles} \]
    Gives,
    \[ \prob[][a] \leq \sum_{i=1}^{m} \prob[][c_i] \eq \label{eq:1n_ineq} \]
    Such that whenever the inequality \cref{eq:1n_ineq} is violated, the implication in \cref{eq:1n_pi} is violated as well. Note that the converse is \textit{not} true; if the inequality \cref{eq:1n_ineq} holds true, it is still possible for there to be a violation of \cref{eq:1n_pi}.

    \begin{remark}
        An important result of Boole's inequality is that \cref{eq:booles} becomes an exact \textit{equality} whenever elements of $C$ are pairwise disjoint. Therefore, finding a set $C$ of pairwise disjoint events satisfying \cref{eq:1n_pi} will give rise to tighter inequalities.
    \end{remark}

    \subsection{Implications in the Marginal Problem}
    \label{sec:implications_marginal_problem}
    The question then remains, \textit{how does non-contextuality give rise to implications of the form of \cref{eq:1n_pi}?} Begin by making the principle assumption that a joint distribution \textit{does} exist for a marginal model $\prob[V_{\bs{k}}]$. This assumption induces logical \textit{tautologies} that take the form of \cref{eq:1n_pi}, which we call \term{marginal implications}, using the following train of logic.
    \begin{enumerate}
        \item Suppose a particular marginal outcome $a \in O_{V_{\bs{k}}}$ happens to occur.
        \item Since a joint distribution exists, then $a$ refers to some \textit{incomplete} knowledge about a \textit{joint} event $j = \outc{\mathcal{V}} \in O_{\mathcal{V}}$ that actually occured. More precisely, this set of possible $j$'s is the extendable set of $a$ in $O_{\mathcal{V}}$.
        \[ j \in \Ext[\mathcal{V}]{a} \]
        \item Therefore whenever $a$ occurs, one of the elements $j$ of $\Ext[\mathcal{V}]{a}$ \textit{has} to occur.
        \[ a \implies \bigvee_{j \in \Ext[\mathcal{V}]{a}} j \eq \label{eq:A_impies_extendable}\]
        \item Now suppose we could obtain a set of marginal outcomes $C = \bc{c_1, \ldots, c_m}$ each different from $a$ such that for every $j$, $\Ext{c \to j}$ for at least one element $c \in C$. If such a $C$ can be found, then the possibility of at least one $j$ occurring implies the possibility of at least one $c$ occurring.
        \[ \bigvee_{j \in \Ext[\mathcal{V}]{a}} j \implies c_1 \vee \cdots \vee c_m = \bigvee_{i \in \bs{m}} c_i\eq \label{eq:extendable_implies_cover} \]

        \item Combing \cref{eq:A_impies_extendable} with \cref{eq:extendable_implies_cover}, one obtains \cref{eq:1n_pi}.
    \end{enumerate}

    \todo[TC]{Talk about why this is called hardy paradox}

    Finding all marginal implications for a chosen marginal outcome $a$ corresponds to finding a set of marginal outcomes $C = \bc{c_1, \ldots, c_m}$ whose extendable sets \textit{cover} $\Ext[\mathcal{V}]{a}$. Formally this corresponds to a \term{set covering} problem \todo[TC]{cite} which we elected to cast as the equivalent \term{hypergraph transversal problem}.

    \todo[TC]{Mention sufficient solution to the possibilistic marginal problem}
    \todo[TC]{Illustrate how it can distinguish more than possibilistic differences}

    Given an antecedent $a$, we can construct a hypergraph $\hgraph_{a}$ called the \term{marginal hypergraph} with nodes $\nodes_a$ and $\edges_a$. The nodes of this hypergraph are the subset of marginal outcomes $\nodes_a \subseteq O^{V_{\bs{k}}}$ \textit{compatible} with $a$.
    The edges are labeled by outcomes in $\Ext[\mathcal{V}]{a} \subseteq O_{\mathcal{V}}$, namely the set of $j$'s, and contain all nodes compatible with $j$.
    \begin{align*}
        \nodes_a &= \bc{n \in O^{V_{\bs{k}}} \mid \Com{n, a}} \eq \label{eq:hgraph_nodes} \\
        \edges_a &= \bc{\bc{n \in O^{V_{\bs{k}}} \mid \Com{n, j}} , j \in \Ext[\mathcal{V}]{a}} \eq \label{eq:hgraph_edges}
    \end{align*}
    \begin{remark}
        \label{remark:trivial_transversal}
        Note that every node is contained in some edge. To prove this, consider the definition of compatibility between outcomes. If every $n$ is compatible with $a$, then there exists some outcome $j \in \Ext[\mathcal{V}]{A}$ such that $\Ext{n \to j}$. Therefore since $\Ext{n \to j}$, $\Com{n, j}$; satisfying the central condition of \cref{eq:hgraph_edges}.
    \end{remark}

    \subsection{Higher Order Marginal Implications}

    \todo[TC]{Discuss $(m,n)-type$ implications and the non-triviality}
    \todo[TC]{Link to logical bell inequalities/completeness or not?}

    \subsection{Hypergraph Transversals}
    Section \ref{sec:implications_marginal_problem} demonstrates how finding possibilistic marginal implications can be casted as a hypergraph transversal problem. This section aims to summarize the general idea behind existing algorithms and also discusses some of the inequalities found using these algorithms. \todo[TC]{References here }

    \begin{definition}
        A \term{hypergraph transversal generation} is any algorithm that correctly generates the complete set of all minimal transversals of $\mathcal{H}$.
    \end{definition}

    \begin{definition}
        Any hypergraph with strictly non-empty edges $\forall e \neq \emptyset$ will always admit the \term{trivial transversal} $\trans^*$ where all nodes are considered as members $\trans^* = \nodes$. Any hypergraph with empty edges will be called a \term{degenerate hypergraph} as it admits no transversals\footnote{Most authors require that all hypergraphs be non-degenerate \cite{Kavvadias_2005}.}.
    \end{definition}
    Remark \ref{remark:trivial_transversal} guarantees that all marginal hypergraphs are non-degenerate. There are two distinct approaches to hypergraph transversal generation: \textit{top-down} and \textit{bottom-up}.
    \begin{definition}
        A \term{top-down} hypergraph transversal generation refers to any algorithm that begins with the trivial transversal $\trans^*$ and iteratively removes unnecessary nodes from $\trans^*$.
    \end{definition}

    \begin{definition}
        A \term{bottom-up} hypergraph transversal generation refers to any algorithm that begins with the empty set $\emptyset$ and iteratively adds nodes.
    \end{definition}

    One should select a top-down method if the typical size of minimal transversals $\abs{\trans}$ is comparable to the number of nodes $\abs{\nodes}$, otherwise a bottom-up method will perform better.
    For our purposes we implemented a deep-first transversal algorithm similar to
    Recalling \cref{remark:trivial_transversal}

    \subsection{Weighted Hypergraph Transversals}
    In \cref{sec:certificate_inequalities} is was demonstrated that the Fritz distribution is witness-able via a certificate inequality. It is also possible to witness
    \todo[TC]{Discuss the Inequalities Derived/ Trivial and non-trivial}

    \todo[TC]{Weighted transversals and Optimizations}
    \todo[TC]{Seeding inequalities (huge advantage here)}
    \section{Deriving Symmetric Inequalities}
    Symmetric compatibility inequalities are useful for a number of reasons. First, Bancal et. al. \cite{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:comp_con_mp}; the number of extremal points typically grows exponentially in $\mathcal{V}$, but only polynomial for the symmetric polytope. They also note a number of interesting inequalities (such as CHSH \cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that quantum-non-trivial inequalities can be recovered from facets of a symmetric polytope. Second, numerical optimizations against inequalities invariant under exchange of parties will lead to one of two interesting cases: either the extremal distribution is invariant under exchange of parties or it is not. The latter case generates a family of incompatible distributions obtained by exchanging parties of the found extremal distribution\footnote{If the extremal distribution is not invariant under exchange of parties, there is indication that the space of accessible distributions is non-convex.}. In this section we discuss how to achieve computational advantage and its application to the inequality techniques mentioned in \cref{sec:certificate_inequalities} and \cref{sec:implication_inequalities}.
    \subsection{Causal Symmetry}
    The aim of this section is to formalize what types of symmetries are present in a particular causal structure $\graph$. The group of these causal symmetries will define, for each compatibility inequality $\mathcal{I}_{V_{\bs{k}}}$, a family of inequalities that are also valid incompatibility inequalities.

    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\varphi$ from $N$ to $N$.
    \[ \Perm{N} = \bc{\varphi \mid \varphi : N \to N} \]
    The action of $\varphi \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\varphi$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
    \begin{align*}
    \varphi\br{\graph} &\defined \br{\varphi\br{\nodes}, \varphi\br{\edges}} \\
    \varphi\br{\nodes} &\defined \bc{\varphi\br{n} \mid n \in \nodes} = \nodes \\
    \varphi\br{\edges} &\defined \bc{\varphi\br{e} \mid e \in \edges}
    \end{align*}
    To motivate a more general treatment of such symmetries, consider the Triangle Scenario of \cref{fig:triangle_scenario}. Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\varphi \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\varphi\br{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes. By construction, any valid compatibility inequality $\mathcal{I}_{V_{\bs{k}}}$ for the marginal scenario $V_{\bs{k}} = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes. Therefore applying $\varphi$ to all distributions in $\mathcal{I}_{V_{\bs{k}}}$ yields $\varphi\br{\mathcal{I}_{V_{\bs{k}}}} \defined \varphi\br{\mathcal{I}}_{\varphi\br{V_{\bs{k}}}}$, another valid compatibility inequality for the permuted marginal scenario $\varphi\br{V_{\bs{k}}}$ defined as,
    \[ \varphi\br{V_{\bs{k}}} = \bc{\varphi\br{V_1}, \ldots, \varphi\br{V_k}} \]
    % \begin{example}
    %     \todo[TC]{Above trivial example.}
    %     Consider the marginal scenario $V_{\bs{4}} = \bc{\bc{A,B,C}, \bc{A}, \bc{B}, \bc{C}}$ and the compatibility inequality $\mathcal{I}_{\bc{ABC, A, B, C}}$ for the Triangle Scenario in \cref{fig:triangle_scenario} with the following form,
    %     \[ \prob[ABC][002]\prob[ABC][003] \leq \prob[A][0]\prob[C][3] \]
    %     Now consider $\varphi = \bc{A \to A, B \to C, C \to B}$. Since $\varphi\br{\graph} = \graph$, $\varphi\br{\mathcal{I}_{V_{\bs{k}}}}$ is also a valid compatibility inequality,
    % \end{example}
    More generically, any permutation $\varphi$ that preserves the graphical structure of $\graph$ can be applied to $\mathcal{I}_{V_{\bs{k}}}$ to generate new and valid compatibility inequalities. Specifically this alludes to the \term{graph automorphism group} $\Aut{\graph}$ of $\graph$.
    \[ \Aut{\graph} \defined \bc{\varphi \in \Perm{\nodes} \mid \varphi\br{\graph} = \graph} \]
    In general, $\Aut{\graph}$ could include elements $\varphi$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}. This behaviour is \textit{undesired} for causal inference where the latent nodes will never appear in a marginal scenario. Instead, the subgroup of $\Aut{\graph}$ that never maps observable nodes to latent nodes is the \term{set-wise stabilizer} of $\Aut{\graph}$ for $\nodes_O$ and will be expressed with a subscript.

    \begin{definition}
        The \term{causal symmetry group} for a causal structure $\graph$ is the graph automorphism subgroup that stabilizes the observable nodes.
        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\br{\graph} = \graph, \forall n \in \nodes_O :\varphi\br{n} \in \nodes_O} \]
        Given any compatibility inequality $\mathcal{I}_{V_{\bs{k}}}$, each element $\varphi$ of the causal symmetry group defines a new valid compatibility inequality $\varphi\br{\mathcal{I}_{V_{\bs{k}}}} = \varphi\br{\mathcal{I}}_{\varphi\br{V_{\bs{k}}}}$.
    \end{definition}

    The inflation technique discussed in \cref{sec:summary_inflation} allows one to derive compatibility inequalities for a causal structure $\graph$ by considering the marginal problem over the pre-injectable sets of $\graph'$ denoted $\PreInj[\graph]{\graph'} = \bc{V_1, \ldots, V_k}$. It is important to recall that due to \cref{lem:inflation}, inequalities $\mathcal{I}'$ for $\graph'$ are \textit{only} transferable to inequalities $\mathcal{I}$ for $\graph$ if $\mathcal{I}'$ is in terms of distributions over the pre-injectable sets $\mathcal{I}'_{\PreInj[\graph]{\graph'}}$. As a consequence of this observation, we need to consider a subgroup of the causal symmetry group that preserves the pre-injectable sets,
    \[ \varphi\br{\PreInj[\graph]{\graph'}} = \PreInj[\graph]{\graph'} \eq \label{eq:preserved_preinj} \]

    \begin{definition}
        The \term{restricted causal symmetry group} $\Phi$ for a causal structure $\graph$ and a marginal scenario $V_{\bs{k}}$ is the graph automorphism subgroup that stabilizes the marginal scenario $V_{\bs{k}}$.
        \[ \Phi \defined \Aut[V_{\bs{k}}]{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\br{\graph} = \graph, \forall V \in V_{\bs{k}} : \varphi\br{V} \in V_{\bs{k}}} \]
        Given any compatibility inequality $\mathcal{I}_{V_{\bs{k}}}$ each element $\varphi$ of the causal symmetry group defines a new valid compatibility inequality $\varphi\br{\mathcal{I}_{V_{\bs{k}}}} = \varphi\br{\mathcal{I}}_{V_{\bs{k}}}$ over the \textit{same} marginal context $V_{\bs{k}}$.
    \end{definition}

    The restricted causal symmetry group for the pre-injectable sets of an inflation $\graph'$ is the ideal symmetry group for use with the inflation technique. If one obtains a particular inequality $\mathcal{I}'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\Phi$, an entire family of valid compatibility inequalities are also obtained.
    \[ \bc{\varphi\br{\mathcal{I}'}_{\PreInj[\graph]{\graph'}} \mid \varphi \in \Phi} \text{ where } \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
    We have obtained $\Phi$ for the inflated triangle scenario \cref{fig:inflated_triangle_scenario}. $\Phi$ is an order $48$ group with the following $4$ generators:
    \begin{equation*}
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_1 \\
    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_2 \\
    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_3 \\
    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
    \end{aligned}
    \quad
    \begin{aligned}[c]
    &\hspace{1mm}\varphi_4 \\
    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
    \end{aligned}
    \end{equation*}
    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the inflated Triangle Scenario $\graph'$ of \cref{fig:inflated_triangle_scenario}. Moreover they stabilize the observable nodes, and the map pre-injectable sets of \cref{eq:pre-injectable_triangle_scenario} to the pre-injectable sets. Finally, in the Triangle Scenario we have that,
    \[ \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \sim \Aut[\nodes_O]{\graph} \]
    To see this, $\varphi_1$ and $\varphi_4$ become the identity element $\mathbb{I}$ in $\Aut[\nodes_O]{\graph}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
    \subsection{Symmetric Marginal Polytope}
    Up until this point, we have discussed how new inequalities can be created from known ones by exploiting causal symmetry. Although very useful, we divert our attention to finding \textit{symmetric} inequalities themselves.
    \[ \forall \varphi \in \Phi :  \varphi\br{\mathcal{I}_{V_{\bs{k}}}} = \mathcal{I}_{V_{\bs{k}}} \]
    In order to do this, we must first define how elements $\varphi \in \Phi$ act on marginal outcomes $O_{V_{\bs{k}}}$.
    \begin{example}
        Consider the outcome $\outc{ABC} = \br{A = 0, B = 1, C = 2} \in O_{ABC}$ where all variables have $4$ possible outcomes $\bc{0,1,2,3}$\footnote{Strictly speaking, the action of $\varphi$ is only well defined if each variable $v \in \mathcal{V}$ has the same outcome space $O_v$.} and the permutation $\varphi = \bc{A \to D, B \to C, C \to B, D \to A}$. We can act on $\outc{ABC}$ with $\varphi$ to obtain a different outcome which we denote $\varphi\br{\outc{ABC}}$,
        \[ \varphi\br{\outc{ABC}} \defined \br{\varphi\br{A} = 0, \varphi\br{B} = 1, \varphi\br{C} = 2} = \br{D = 0, C = 1, B = 2} = \outc{BCD} \]
        This notation can be misleading; when isolated $\outc{BCD}$ refers to an \textit{arbitrary} outcome of $O_{BCD}$, while in this context it is intended that $\outc{BCD}$ refers to the \textit{specific} outcome of $O_{BCD}$ that matches the numerical valuation of $\outc{ABC}$. Probabilistically, the action of $\varphi$ is defined as,
        \[ \varphi\br{\prob[ABC]\br{012}} \defined \prob[\varphi\br{ABC}]\br{012} = \prob[DCB][012] = \prob[BCD][210] \]
    \end{example}

    Through repeated action of $\varphi \in \Phi$ on marginal outcomes $m \in O_{V_{\bs{k}}}$ and joint outcomes $j \in O_{\mathcal{V}}$, one can define group orbits of $\Phi$ in $O_{V_{\bs{k}}}$ and $O_{\mathcal{V}}$.
    \begin{align*}
    \Orb[\Phi]{m} &\defined \bc{\varphi\br{m} \in O_{V_{\bs{k}}} \mid \varphi \in \Phi} \\
    \Orb[\Phi]{j} &\defined \bc{\varphi\br{j} \in O_{\mathcal{V}} \mid \varphi \in \Phi}
    \end{align*}

    \begin{definition}
        The \term{symmetric marginalization matrix} $M_{\Phi}$ for a marginal scenario $V_{\bs{k}}$ and a particular restricted causal symmetry $\Phi$ is a contracted version of the marginalization matrix $M$ for $V_{\bs{k}}$. Each row of $M_{\Phi}$ corresponds to a marginal orbit $\Orb[\Phi]{m}$. Analogously each column of $M_{\Phi}$ corresponds to a joint orbit $\Orb[\Phi]{j}$. The entries of $M_{\Phi}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
        \[ M_{\Phi}\bs{\Orb[\Phi]{m}, \Orb[\Phi]{j}} = \sum_{\substack{j' \in \Orb[\Phi]{j} \\ m' \in \Orb[\Phi]{m}}} M\bs{m',j'} \]
    \end{definition}

    \subsection{Symmetric Logical Implications}
    \subsection{Results}

    \todo[TC]{Identify the desired symmetry group}
    \todo[TC]{How we obtained the desired symmetry group}
    \todo[TC]{Group orbits to symmetric marginal description matrix}
    \todo[TC]{Infeasibility on symmetric marginal problem}
    \todo[TC]{Hardy Transversals can't work on the symmetric marginal problem}
    \todo[TC]{Symmetrizing non-symmetric inequalities through avoiding orbits}
    \todo[TC]{higher order transversals on mutually impossible events}
    \section{Non-linear Optimizations}
    \label{sec:optimizations}
    \todo[TC]{Mention outlook on te importance of classification and determining interesting inequalities \cite{Bancal_2010}}
    Compatibility inequalities for a given causal structure are fantastic for finding incompatible distributions. In the inflation technique, this is no exception. Parameterizing a space distributions using a set of real-valued parameters $\lambda$, enables us to perform numerical optimizations against these inequalities in hopes that a particular set of parameters $\lambda$ is able to generate an incompatible distribution $\prob$. To illustrate this generic procedure and it's reliability, we will first examine the popular CHSH inequality.
    \subsection{Numerical Violations of The CHSH Inequality}
    The CHSH inequality \cite{CHSH_Original} can we viewed as a causal compatibility inequality for the iconic Bell Scenario (Fig. 19 of \cite{Wood_2012}, Fig. 11 of \cite{Inflation}, Fig. 1 a) of \cite{Tavakoli_2015}, etc.) corresponding to Bell's notion of local causality \cite{Wood_2012}. It constrains the set of 2-outcome bipartite distributions over local binary measurement settings for each party $\prob[AB\mid S_A S_B] \defined \bc{\prob[AB\mid 0 0], \prob[AB\mid 01], \prob[AB\mid 10], \prob[AB\mid 11]}$. Numerical optimization \textit{should} obtain the algebraic violation associated with the PR-Box correlations \cite{PR_1995}. Maintaining full generality, we simply need to parameterize these $4$ distributions using \cref{eq:uniform_param}, each requiring $4$ real-valued parameters. We define the optimization target for the CHSH inequality to be the left-hand-side of \cref{eq:CHSH},
    \[ \mathcal{I}\tsb{CHSH} = \ba{AB|11} + \ba{AB|12} + \ba{AB|21} - \ba{AB|22} \]
    Figure \ref{fig:CHSH_convex} demonstrates this optimization for $5$ random seed parameters $\lambda^0$, each converging to the expected value of $4$. Analogously, \cite{Cirelson_1980}

    \begin{figure}
    \newlength\figureheight
    \newlength\figurewidth
    \setlength\figureheight{2.7in}
    \setlength\figurewidth{.48\textwidth}
    \begin{center}
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \includegraphics{../figures/CHSH_convex.pdf}
            \caption{Convex optimizations against $\mathcal{I}\tsb{CHSH}$ recover algebraic violation of $4$.}
            \label{fig:CHSH_convex}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \includegraphics{../figures/CHSH_quantum.pdf}
            \caption{Quantum optimizations against $\mathcal{I}\tsb{CHSH}$ recover maximum violation of $2\sqrt{2}$.}
            \label{fig:CHSH_quantum}
        \end{minipage}
    \end{center}
    \end{figure}

    \todo[TC]{Demonstrate Quantum, Convexity}
    \todo[TC]{Why Inequalities are great for optimizations}
    \todo[TC]{Non-linearity}
    \todo[TC]{Techniques Used}
    \todo[TC]{Finding maximum violation of CHSH easily}
    \todo[TC]{Unreliance when number of parameters increases}
    \todo[TC]{Issues with local minimum}
    \todo[TC]{Using initial conditions close to fritz, obtain greater violation}
    \todo[TC]{Greater violation shares possibilistic structure of fritz and violates CHSH under definition}
    \todo[TC]{Not realizable with maximally entangled qubit states}
    \todo[TC]{Not realizable with separable measurements}
    \todo[TC]{Many non-trivial inequalities to be tested}
    \todo[TC]{inequality -> dist -> inequality evolution}
    \section{Conclusions}
    \todo[TC]{Inflation technique allows one to witness fritz incompatibility}
    \todo[TC]{Linear optimization induces certificates which are incompatibility witnesses}
    \todo[TC]{There are quantum distributions in the Triangle Scenario that are incompatible and different from fritz in terms of entanglement but not possibilistic structure}
    \section{Open Questions \& Future Work}
    \todo[TC]{Lots of stuff}
    \appendix
    \section{Exemplary Inequalities}
    \section{Connections to Sheaf-Theoretic Treatment}
    \section{Higher Order Logical Implications as a Complete Solution to the Marginal Problem}
    \section{Computationally Efficient Parametrization of the Unitary Group}
    Spengler, Huber and Hiesmayr \cite{Spengler_2010_Unitary} suggest the parameterization of the unitary group $\mathcal{U}\br{d}$ using a $d\times d$-matrix of real-valued parameters $\lambda_{n, m}$,
    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
    Where $P_l$ are one-dimensional projective operators,
    \[ P_l = \ket{l}\bra{l} \eq \label{eq:projective_operator} \]
    and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices,
    \[ \sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m} \]
    Where $1 \leq m < n \leq d$. Spengler et. al. proved the validity of \cref{eq:spengler_unitary} in Ref. \cite{Spengler_2010_Unitary}.

    For the sake of reference, let us label the matrix exponential terms in \cref{eq:spengler_unitary} in a manner that corresponds to their affect on an orthonormal basis $\bc{\ket{1}, \ldots, \ket{d}}$.
    \begin{align}
    \begin{split}
        GP_l &= \exp\br{iP_l \lambda_{l,l}} \\
        RP_{n,m} &= \exp\br{i P_n \lambda_{n,m}} \\
        R_{m,n} &= \exp\br{i \si_{m,n} \lambda_{m,n}}
    \end{split} \eq \label{eq:exp_terms}
    \end{align}
    It is possible to remove the reliance on matrix exponential operations in \cref{eq:spengler_unitary} by utilizing the explicit form of the exponential terms in \cref{eq:exp_terms}. As a first step, recognize the defining property of the projective operators \cref{eq:projective_operator},
    \[ P_l^k = \br{\ket{l}\bra{l}}^k = \ket{l}\bra{l} = P_l \]
    This greatly simplifies the global phase terms $GP_l$,
    \[ GP_l = \exp\br{iP_l \lambda_{l,l}} = \sum_{k=0}^{\inf} \f{\br{iP_l \lambda_{l,l}}^k}{k!} = \mathbb{I} + \sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}P_l^k = \mathbb{I} + P_l \bs{\sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}} = \mathbb{I} + P_l \br{e^{i \lambda_{l,l}} - 1} \eq \label{eq:unitary_GP} \]
    Analogously for the relative phase terms $RP_{n,m}$,
    \[ RP_{n,m} = \cdots = \mathbb{I} + P_n \br{e^{i \lambda_{n,m}} - 1} \eq \label{eq:unitary_RP} \]
    Finally, the rotation terms $R_{m,n}$ can also be simplified by examining powers of $i \sigma_{n,m}$,
    \[ R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}} = \sum_{k=0}^{\inf} \f{\br{\ket{m}\bra{n} - \ket{n}\bra{m}}^k \lambda_{m,n}^k}{k!} \]
    One can verify that the following properties hold,
    \begin{align*}
        \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^0 &= \mathbb{I} \\
        \forall k \in \N, k \neq 0 : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k} &= \br{-1}^k\br{\ket{m}\bra{m} + \ket{n}\bra{n}} \\
        \forall k \in \N : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k+1} &= \br{-1}^k\br{\ket{m}\bra{n} - \ket{n}\bra{m}}
    \end{align*}
    Revealing the simplified form of $R_{m,n}$,
    \[ R_{m,n} = \mathbb{I} + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \sum_{j=1}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j}}{\br{2j}!} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sum_{j=0}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j+1}}{\br{2j+1}!} \]
    \[ R_{m,n} = \mathbb{I} + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \eq \label{eq:unitary_R} \]
    By combining the optimizations of \cref{eq:unitary_RP,eq:unitary_R,eq:unitary_GP} together we arrive at an equivalent form for \cref{eq:spengler_unitary} that is computational more efficient.
    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}}} \cdot \bs{\prod_{l=1}^{d} GP_l} \eq \label{eq:fast_spengler_unitary} \]
    In quantum mechanics, the global phase of a state $\ket{\psi} \in \Hilb^n$ is a \textit{redundant} parameter. Parameterizing unitaries using \cref{eq:fast_spengler_unitary} is especially attractive since the global phase terms $GP_l$ can be dropped, allowing one to parameterize all unitaries in $\mathcal{U}\br{d}$ up to this degeneracy \cite{Spengler_2010_Unitary}\footnote{In our implementation, we accomplish this by explicitly setting $\lambda_{l,l} = 0$ in \cref{eq:unitary_GP}}.
    \[ U_{/ GP_l} = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}}} \eq \label{eq:fast_spengler_unitary_gp} \]
    \todo[TC]{Explanation of Computational Complexity $\mathcal{O}\br{d^3}$ vs. $\mathcal{O}\br{1}$ using \cite{Moler_2003}}
    \todo[TC]{Pre-Caching for Fixed dimension $d$}
    \todo[TC]{Talk about inverse via haar measure}

    \section{Parametrization of Quantum States \& Measurements}
    Throughout \cref{sec:optimizations}, we utilize a variety of parameterizations of quantum states and measurements in order to generate quantum-accessible probability distributions. There are numerous techniques that can used when parameterizing quantum states and measurements \cite{Petz_2015, Hedemann_2013,Spengler_2010_Unitary,Fujii_2005,James_2001} with applications \todo[TC]{Finish this sentence}. For our purposes, we need to parameterize the space of quantum-accessible distributions $\prob[\mathcal{Q}]$ that are \textit{realized} on the Triangle Scenario. We have implemented $\prob[\mathcal{Q}]$ under the following description.
    \[ \prob[ABC]\br{abc} = \Tr\bs{\Omega^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \Omega M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \eq \label{eq:triangle_quantum_distributions} \]

    \subsection{Quantum States}
    The bipartite states $\br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ of \cref{eq:triangle_quantum_distributions} were taken to be two-qubit density matrices acting on $\Hilb^2 \otimes \Hilb^2$.\footnote{We also considered qutrit $\Hilb^3$ qutit $\Hilb^4$ states. However for $6$ $d$-dimensional $\Hilb^d$ states, the joint density matrix $\rho$ acts on $\br{\Hilb^d}^{\otimes 6}$ making it a $\br{d^6, d^6}$ matrix with $d^{12}$ entries. Computationally only $d = 2$ was feasible for our optimization tasks.} The space of all such states corresponds to the space of all $4\times 4$ positive semi-definite hermitian matrices with unitary trace. Throughout this section, we refer to these bipartite states simply as $\rho$ unless otherwise indicated. There are three distinct techniques that we have considered.

    Taking inspiration from \cite{James_2001}, we can parameterize all such density matrices $\rho$ using \term{Cholesky Parametrization} \cite{Grasmair_2014}. The Cholesky decomposition allows one to write any hermitian positive semi-definite matrix $\rho$ in terms of a lower (or upper) triangular matrix $T$ using $\rho = T^\dagger T$. Our Cholesky parameterization consists of assigning $16$ real-valued parameters $\lambda$ to the entires of $T$ and generating a unitary trace $\rho$ similar to eq. (4.4) of \cite{James_2001}.
    \[ \rho = \f{T^\dagger T}{\Tr\br{T^\dagger T}} \quad T = \pmtrx{\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}} \eq \label{eq:cholesky_param} \]
    Our deviation from exclusiving using \cref{eq:cholesky_param} is two-fold. First, \cref{eq:cholesky_param} is degenerate in that the normalization indicates only $16 - 1 = 15$ parameters are required for fully generic parameterization of all such states $\rho$. Removing this degeneracy is possible although difficult. Second, the parameters $\lambda_i$ carry no physical meaning associated with the state $\rho$, unlike our next parameterization.

    In Spengler, Huber and Hiesmayr's work \cite{Spengler_2010_Unitary}, they discuss how to parameterization density matrices $\rho$ acting on $\Hilb^d$ of rank $k$ through it's spectral decomposition,
    \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i}\bra{\psi_i} \quad p_i \geq 0, \sum_{i} p_i = 1, k \leq d \eq \label{eq:unitary_param_density} \]
    Where any orthonormal basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into a computational basis $\bc{\ket{i}}$ by a unitary $U \in \mathcal{U}\br{d}$ such that $\ket{\psi_i} = U\ket{i}$. We refer to \cref{eq:unitary_param_density} as the \term{Spengler Parametrization}. Without loss of generality we parameterize all full-rank ($k=d$) matrices by simultaneously parameterizing the $d=4$ eigenvalues $p_i$ of \cref{eq:unitary_param_density} using \cref{eq:convex_param} and the unitary group $\mathcal{U}\br{4}$ up to global phase equivalence using \cref{eq:fast_spengler_unitary_gp}. Parameterizing $\rho$ using the Spengler parameterization requires $3 + 12 = 15$ parameters; admitting no degeneracies.

    Finally in cases where we wish to restrict ourselves to \textit{pure} bipartite states $\rho = \ket{\psi}\bra{\psi}$, we have the luxury to use a \term{Schmidt Parametrization}. This is accomplished via a Schmidt decomposition $\ket{\psi_{AB}} = \sum_{i}\sigma_i \ket{i_A}\otimes\ket{i_B}$ where normalization demands that $\sum_{i} \sigma_i^2 = 1$, $\bc{\ket{i_A}}$ and $\bc{\ket{i_B}}$ are orthonormal bases for $\Hilb_A$ and $\Hilb_B$ respectively \cite{Neilsen_Chaung_2011}. Additionally for qubit sources we can \textit{choose} our orthonormal bases to be the computational basis $\bc{\ket{0}, \ket{1}}$ and write,
    \[ \ket{\psi} = \cos^2\br{\lambda_1} \ket{0} \otimes \ket{0} + \sin^2\br{\lambda_1} \ket{1} \otimes \ket{1} \]
    Where only $1$ real-valued parameter $\lambda = \bc{\lambda_1}$ is required to parameterize all pure states up to local unitaries. Pure states are also attractive due to their computational advantage in computing \cref{eq:triangle_quantum_distributions}. If each state $\rho$ is decomposable into $\ket{\psi}\bra{\psi}$, then \cref{eq:triangle_quantum_distributions} can be written as,
    \[ \prob[ABC]\br{abc} = \bramidket{\psi_{AB}\psi_{BC}\psi_{CA}}{\Omega M_{A,a}\otimes M_{B,b} \otimes M_{C,c} \Omega^\intercal}{\psi_{AB}\psi_{BC}\psi_{CA}} \eq \label{eq:pure_state_quantum_triangle} \]
    Avoiding the expensive matrix multiplications of \cref{eq:triangle_quantum_distributions}.
    \subsection{Measurements}
    With full generality, we consider a measurement $M$ to be a \term{projective-operator valued measure (POVM)} represented by a set of hermitian, positive semi-definite operators $\bc{M_i}_{i=1,\ldots,k}$\footnote{The $i$-th element of $M$ is referenced using a subscript $M_i$. The set of measurement elements for a particular party $X$ will be written $M_X$. When both party and element are to be referenced, we write $M_{X,i}$.} acting on $\Hilb^d$ summing to the identity,
    \[ \forall \ket{\phi} \in \Hilb^d : \bra{\phi} M_i \ket{\phi} \geq 0 \quad \sum_{i=1}^{k} M_i = \mathbb{I}_{\Hilb^d} \eq \label{eq:povm} \]
    When considering $k=2$ outcome measurements acting on $\Hilb^4$ we parameterize the first POVM element $M_1$ by using a Cholesky parameterization similar to \cref{eq:cholesky_param} without normalizing for trace. Afterwards, $M_2$ is fully determined by \cref{eq:povm}.
    \[ M_1 = T^\dagger T \quad M_2 = \mathbb{I} - T^\dagger T \eq \label{eq:2_povm}\]
    However, in order for $M_2$ to be positive semi-definite, the largest eigenvalue of $M_1$ has to be less than 1. To see this is a necessary and sufficient constraint, first expand out \cref{eq:2_povm},
    \[ \bramidket{\phi}{M_2}{\phi} = \bramidket{\phi}{\mathbb{I} - M_1}{\phi} = \abs{\phi}^2 - \bra{\phi}\br{\sum_{i=1}^{d}m^{\br{i}}_1 \ket{m^{\br{i}}_1}\bra{m^{\br{i}}_1}}\ket{\phi} \]
    Next write a generic $\ket{\phi} \in \Hilb^d$ in terms of a linear combination of the eigenvectors of $M_1$\footnote{The eigenvectors of $M_1$ form an orthonormal basis for $\Hilb^d$ because $M_1$ is Hermitian}.
    \[ \bramidket{\phi}{M_2}{\phi} = \sum_{j}\abs{\braket{\phi}{m^{\br{j}}_1}}^2 - \sum_{i} m^{\br{i}}_1 \abs{\braket{\phi}{m^{\br{i}}_1}}^2 = \sum_{i} \br{1 - m^{\br{i}}_1} \abs{\braket{\phi}{m^{\br{i}}_1}}^2 \eq \label{eq:eigen_less_one} \]
    Since $\ket{\phi}$ is arbitrary, for each $i$ set $\ket{\phi} = \ket{m^{\br{i}}_1}$ to see that each eigenvalue of $M_1$ needs to be less than $1$.
    \[ \bramidket{m^{\br{i}}_1}{M_2}{m^{\br{i}}_1} = \br{1 - m^{\br{i}}_1} \geq 0 \implies m^{\br{i}}_1 \leq 1 \eq \label{eq:2_povm_suff} \]
    By \cref{eq:eigen_less_one} is not difficult to see that \cref{eq:2_povm_suff} is a sufficient condition. During optimization, \cref{eq:2_povm_suff} can either be enforced passively as a constraint or directly by normalizing $M_1$ by its largest eigenvalue $\max\br{m_1^{\br{i}}}$ whenever necessary.

    When generalizing the above parameterization to more than $2$ outcomes, only necessary conditions were found. Generating $k$-outcome POVM measurements is doable using rejection sampling techniques such as those used in \cite{Petz_2012} however a valid parameterization with little to no degeneracy was not found. Upon making this observation, a necessary departure to \term{projective-valued measures (PVMs)} is warranted\footnote{Strictly speaking, when the number of outcomes ($k$) \textit{matches} the Hilbert space dimension ($d$), \cref{eq:povm} implies \cref{eq:pvm} by completeness. When considering $4$ outcome measurements on bipartite qubit states in $\Hilb^4$, PVMs are completely general. Moreover, Naimark's dilation theorem guarantees that PVMs acting on $\Hilb^q$ can \textit{emulate} the behaviour of any POVM acting on $\Hilb^d$ provided that $q$ is sufficiently larger than $d$ \cite{Naimark}.}. With loss of generality, consider the set of PVMs $M$ satisfying \cref{eq:povm} in addition to orthogonal and projective properties,
    \[ M_i M_j = \de_{ij} M_i \quad M_i = \ket{m_i}\bra{m_i} \eq \label{eq:pvm}\]
    Parameterizing $M$ for $k$-outcome measurements corresponds to parameterizing the set of all $k$-th order orthonormal sub-bases of $\Hilb^d$.
    First note that any such basis $\bc{\ket{\psi_1}, \ldots, \ket{\psi_k}}$ can be transformed into the computational basis $\bc{\ket{1}, \ldots, \ket{k}}$ by a unitary denoted $U \in \mathcal{U}\br{d}$,
    \[ U \ket{\psi_i} = \ket{i} \]
    With this observation we just need to parameterize the set of all unitaries $\mathcal{U}\br{d}$,
    \[ M = \bc{ U\ket{i}\bra{i}U^\dagger }_{i \in 1, \ldots, k} \]
    Specifically, the projective property each $M_i$ means that the global phase of $U$ is completely arbitrary; one only needs to consider parameterizing unitaries up to global phase \cref{eq:fast_spengler_unitary_gp}. This method was inspired by the \textit{measurement seeding} method of P{\'{a}}l and V{\'{e}}rtesi's \cite{Pal_2010} iterative optimization technique.

    Analogously to \cref{eq:pure_state_quantum_triangle}, projective measurements offer considerable computational advantage as \cref{eq:triangle_quantum_distributions} can be rewritten as,
    \[ \prob[ABC]\br{abc} = \bramidket{m_{A,a}m_{B,b}m_{C,c}}{\Omega^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \Omega}{m_{A,a}m_{B,b}m_{C,c}} \eq \label{eq:pure_meas_quantum_triangle} \]

    \subsection{Network Permutation Matrix}
    \begin{figure}
        \centering
        \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../figures/perm_mtrx.pdf}
        \caption{The network permutation matrix $\Omega$ for $\br{\Hilb^2}^{\otimes 6}$ realized on the triangle scenario. Black represents a value of $1$ and $0$ otherwise.}
        \label{fig:perm_mtrx}
    \end{figure}
    Finally, we introduce the \term{network permutation matrix} $\Omega$ for the Triangle Scenario of \cref{fig:triangle_scenario}. For bipartite qubit states, $\Omega$ becomes a $64\times64$ bit-wise matrix that acts on the measurements $M$ and is depicted in \cref{fig:perm_mtrx}. To illuminate its necessity, consider \cref{eq:triangle_quantum_distributions} without $\Omega$.
    \begin{align*}
    \prob[ABC]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA}} \br{M^a_{A}\otimes M^b_{B} \otimes M^c_{C}}}\\
    &= \Tr\bs{\br{\rho_{AB}M^a_{A}}\otimes\br{\rho_{BC}M^b_{B}}\otimes\br{\rho_{CA}M^c_{C}}}\\
    &= \Tr\br{\rho_{AB}M^a_{A}}\Tr{\br{\rho_{BC}M^b_{B}}}\Tr{\br{\rho_{CA}M^c_{C}}}\\
    &= \prob[A\mid \rho_{AB}]\br{a}\prob[B\mid \rho_{BC}]\br{b}\prob[C\mid \rho_{CA}]\br{c}
    \end{align*}
    On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$. This is analogously troubling for $B$ and $C$ as well. The network permutation matrix $\Omega$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$. To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
    \[ \Omega\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
    $\Omega$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''. It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
    \[ \Omega \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
    \subsection{Degeneracy}
    \todo[TC]{Discuss local unitary degeneracy}
    \section{Convex Parametrization of Finite Probability Distributions}
    As discussed in \cref{sec:optimizations}, there is a need to parameterize the family of all probability distributions $\prob[V]$ over a given set of variables $V = \br{v_1, \ldots, v_{\abs{V}}}$. If the cardinality of $O_{V}$ is finite, then this computationally feasible. The space of probability distributions over $n = \abs{O_{V}}$ distinct outcomes forms a $n-1$ dimensional convex polytope naturally embedded in $\R_{\geq 0}^n$ \cite{Brunner_2013} that is parameterizable by $n-1$ real value parameters; normalization $\sum_{o\bs{V} \in O_V} \prob[V][\outc{V}] = 1$ accounts for the `$-1$'. An example of a non-degenerate parameterization of $\prob[V]$ consists of $n-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{n-1}}, \lambda_i \in \bs{0, \pi/2}$ which generate the $n$ probability values $p_j$ using hyperspherical coordinates \cite{Hedemann_2013, Spengler_2010_Unitary},
    \begin{equation}
    \begin{gathered}
        \label{eq:convex_param}
        p_j = \cos^2 \lambda_j \prod_{i=1}^{j-1} \sin^2 \lambda_i \quad \forall j \in 1, \ldots, n - 1 \\
        p_n = \prod_{i=1}^{n-1} \sin^2 \lambda_i
    \end{gathered}
    \end{equation}
    Furthermore due to the periodicity of the parameter space $\lambda$, \cref{eq:convex_param} can be used for either constrained or unconstrained optimization problems. For continuity reasons, unconstrained optimizations are performed whenever possible.

    Although non-degenerate, this parameterization suffers from uniformity; a randomly sampled vector of parameters $\lambda$ \textit{does not} translate to a randomly sampled probability $\prob[V]$. An easy-to-implement, degenerate parameterization of $\prob[V]$ can be constructed by simply beginning with $n$ real parameters $\lambda = \br{\lambda_1, \ldots, \lambda_n}$, then making them positive and normalized by their sum\footnote{Strictly speaking, \cref{eq:uniform_param} \textit{also} suffers from non-uniformity; being biased toward uniform probability distributions $\prob[V]$. \todo[TC]{Discuss rejection sampling simplex algorithms}}.
    \[ p_j = \f{\abs{\lambda_j}}{\sum_{i=1}^{n} \abs{\lambda_i}} \quad \forall j \in 1, \ldots, n \eq \label{eq:uniform_param} \]
    For various convex optimization tasks sensitive to initial conditions outlined \cref{sec:optimizations}, the latter parameterization of \cref{eq:uniform_param} generally performed better than the former \cref{eq:convex_param}.

    \bibliography{references}
\end{document}

### 2016-09-01 document/main.tex
add kbordermatrix.sty to repository, not automatic in ShareLatex. (The license of kbordermatrix.sty - lack of licensing information, to be precise - allows it to be on CTAN, but not in free software distributions.)
notational revamp

@@
 \newcommand{\ancestralindep}{\perp}
-\newcommand{\valprod}{\circ}
+\newcommand{\valprod}{\times}
+\newcommand{\bigvalprod}{\prod}
+\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
+\newcommand{\ext}{\mathrel{\Yright}}
+\newcommand{\res}{\mathrel{\Yleft}}
+\newcommand{\gelem}{\varphi}
+\newcommand{\action}[1]{\gelem\bs{#1}}
+\newcommand{\mscenario}{\mathcal{M}}
+\newcommand{\jointvar}{\mathcal{J}}
 % When I introduce a new term or definition
@@
 \newcommand{\setoperator}[1]{%
-\expandafter\DeclareDocumentCommand\csname#1\endcsname{O{} O{} m}{{\mathsf{#1}_{##1}^{##2}\!}\br{##3}}%
+\expandafter\DeclareDocumentCommand\csname#1\endcsname{O{} O{} m}{{\mathsf{#1}_{##1}^{##2}}\br{##3}}%
 }
@@
 \setoperator{Perm} % Permutation group
-
-\newcommand{\outc}[1]{o\!\bs{#1}} % Fritz's BBTII notation for observed outcomes
-\DeclareDocumentCommand{\prob}{O{} O{}}{\ifthenelse{\equal{#1}{}}{P}{P_{#1}}\ifthenelse{\equal{#2}{}}{}{\!\br{#2}}} % probability distribution
-\DeclareDocumentCommand{\probvec}{O{} O{}}{\ifthenelse{\equal{#1}{}}{\mathcal{P}}{\mathcal{P}_{#1}}\ifthenelse{\equal{#2}{}}{}{\!\br{#2}}} % probability distribution vector
+\setoperator{Out} % Outcome space
+\setoperator{Dom} % Domian
+
+\newcommand{\outc}[1]{o\bs{#1}} % Fritz's BBTII notation for observed outcomes
+\DeclareDocumentCommand{\prob}{O{} O{}}{\ifthenelse{\equal{#1}{}}{P}{P_{#1}}\ifthenelse{\equal{#2}{}}{}{\br{#2}}} % probability distribution
+\DeclareDocumentCommand{\probvec}{O{} O{}}{\ifthenelse{\equal{#1}{}}{\mathcal{P}}{\mathcal{P}_{#1}}\ifthenelse{\equal{#2}{}}{}{\br{#2}}} % probability distribution vector
 
@@
     \begin{definition}
-        Borrowing the notation from \cite{Fritz_2014}, each random variable $v$ has a set of all possible outcomes called the \term{outcome space} or \term{valuation space} and is denoted $O_v$.
-When referencing a \textit{specific} element of $O_v$ or \textit{valuation} of $v$, the notation $\outc{v}$ is used.
-This notation generalizes to set of random variables $V = \bc{v_1, \ldots, v_{\abs{V}}}$;
-        a specific outcome of $\outc{V} \in O_V$ is used to reference a particular tuple or vector of outcomes,
-        \[ \outc{V} \defined \br{\outc{v_1}, \outc{v_2}, \ldots, \outc{v_{\abs{V}}} } = \br{\outc{v}}_{v \in V} \eq \label{eq:outcomespace}\]
-        It is important to note that the ordering of events in \cref{eq:outcomespace} is irrelevant.
-Similarly, the outcome space $O_V$ for a set of random variables $V$ is the \term{valuation product} `$\valprod$' of the individual outcome spaces,
-        \[ O_V \defined O_{v_1} \valprod \cdots \valprod O_{v_{\abs{V}}} \]
-        Where `$\valprod$' is defined such that for $A \cap B = \emptyset$,
-        \[ \outc{A} \valprod \outc{B} \defined \br{\outc{a_1}, \ldots, \outc{a_{\abs{A}}}, \outc{b_1}, \ldots, \outc{b_{\abs{B}}}} = \br{\outc{v}}_{v \in A \cup B} \]
-        Often `$\valprod$' will be omitted where there is little ambiguity.
-When referencing the probability that a set of variables $V$ has outcome $\outc{V}$ (say $v_1 = 0, v_2 = 3$), we intend for the following class of notations to be used interchangeably.
-        \[ \prob[V][\outc{V}] = \prob[][\outc{V}] = \prob[][\outc{v_1}\outc{v_2}] = \prob[][v_1 = 0, v_2 = 3] = \prob[][v_2 = 3, v_1 = 0] = \prob[v_1, v_2][03] \]
+        Following common notation used in \cite{Fritz_2011}, we use the notation $\bs{k} = \bc{1, \ldots, k}$ to be a finite index set.
+Moreover, when referencing a finite set with $k$ elements, we can write,
+        \[ A_{\bs{k}} \defined \bc{A_i}_{i \in \bs{k}} = \bc{A_1, \ldots, A_k} \]
+    \end{definition}
+    \begin{definition}
+        \label{def:outcome_space}
+        Each random variable $v$ has a set of possible outcomes which are labeled by \term{outcome labels} $O_v$.
+The set of all outcomes themselves is its \term{outcome space} and is represented by the set of all functions from $v$ to $O_v$\footnote{Using functional language for outcome events is necessary for a sheaf-theoretic treatment of contextuality \cite{Abramsky_2011}.},
+        \[ \Out{v} \defined \bc{f : \bc{v} \to O_v} \]
+        Each of these functions has a singular domain ($v$) and thus can be concisely written in a compact form $\bc{v \mapsto o}$ where $o \in O_v$ represents some generic outcome label.
+Each function $f$ should be interpreted as the \textit{event} that $v$ obtains the outcome $o$, as well as the function that takes $v$ to $o$ $\bc{v \mapsto f\br{v} = o}$.
+Evidently $\Out{v}$ is isomorphic to $O_v$, and in many cases the two can be considered equivalent; however we make this particular semantic distinction now in preparation of \cref{sec:symmetry}.
+    \end{definition}
+
+    \begin{definition}
+        This notation generalizes to more than one variable. Letting $V = \bc{v_1, v_2}$, we define $\Out{V}$ to be the set of all joint valuations of $v_1$ and $v_2$.
+        % Where the valuation product between outcome spaces is defined as follows,\footnote{At this level, a valuation product behaves analogously to a Cartesian product.
+However in \cref{def:extendable_set}, we define the a valuation product between outcomes and outcomes spaces.}
+        \[ \Out{V} = \Out{\bc{v_1, v_2}} \defined \bc{f : \bc{v_1, v_2} \to \bc{O_{v_1}, O_{v_2}} \mid f\br{v_i} \in O_{v_i}, i \in \bc{1,2}}  \]
+        As a natural generalization, when considering a larger set of random variables $V = \bc{v_i}_{i \in \bs{k}}$ we define the joint outcome space in an analogous way,
+        \[ \Out{V} \defined \bc{f: \bc{v_i}_{i \in \bs{k}} \to \bc{O_{v_i}}_{i \in \bs{k}} \mid \forall i \in \bs{k} : f\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
+        Each outcome $f$ can be compactly represented as a set of mappings over each element of $V$.
+        \[ f = \bc{v_1 \mapsto f\br{v_1}, \ldots, v_k \mapsto f\br{v_k}} = \bc{v_i\mapsto f\br{v_i}}_{i \in \bs{k}} \]
+        The domain of $f$ refers to the set of random variables it valuates and is denoted as $\Dom{f}$. If $f \in \Out{V}$, then $\Dom{f} = V$.
+        % Where the joint outcome labels are elements of a Cartesian product,
+        % \[ O_V \defined O_{v_1} \times \cdots \times O_{v_{\abs{V}}}  \]
+
+        % And a generic, unspecified joint outcome in $\Out{V}$ is written as $\outc{V}$ in a similar fashion to \cref{def:outcome_space} and is represented by a tuple of individual outcomes.
+        % \[ \outc{V} \defined \br{\outc{v_1}, \ldots, \outc{v_{k}}} = \br{\outc{v}}_{v \in V} \eq \label{eq:outcomespace}\]
+        % It is important to note that the ordering of events in \cref{eq:outcomespace} is irrelevant.
+         % The definition of a valuation product can also be extended to outcomes themselves.
+Let $A$ and $B$ be sets of random variables and let $\outc{A} \in \Out{A}$ and $\outc{B} \in \Out{B}$.
+If $$
+    \end{definition}
+
+    \begin{example}
+        Interpreting $f \in \Out{V}$ as an \textit{event} or \textit{outcome} on $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][f]$ to $f$.
+Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$.
+Furthermore let $f \in \Out{V}$ be the outcome $\br{v_1 \mapsto 2, v_2 \mapsto 1}$.
+The following class of notations will be considered interchangeable,
+        \[ \prob[V][f] = \prob[v_1, v_2][f] = \prob[][v_1 \mapsto f_1\br{v_1}, v_2 \mapsto f_2\br{v_2}] = \prob[][v_1 \mapsto 2, v_2 \mapsto 1] = \prob[v_1v_2][21] \]
+        Each of which should be read as ``the probability that $v_1$ gets outcome $2$ AND $v_2$ gets outcome $1$''.
+    \end{example}
+
+    \begin{remark}
+        \label{rem:domain_dist}
+        In each of the above notations, $\prob[V]$ always represents a probability distribution over the \textit{domain} of $f \in \Out{V}$.
+In cases where the subscript is omitted, it should be assumed to be over the domain of $f$.
+        \[ \prob[V][f] = \prob[\Dom{f}][f] = \prob[][f] \]
+    \end{remark}
+
+    \begin{definition}
+        \label{def:restriction}
+        Let $V = \bc{v_1, \ldots, v_k}$ be a set of random variables and $W \subseteq V$ be a subset of $V$.
+Moreover, let $f \in \Out{V}$ be a joint outcome over $V$; assigning a unique label to each variable in $V$.
+The \term{restriction of $f$ onto $W$} (denoted $f|_{W} \in \Out{W}$) is the outcome of $\Out{W}$ that \textit{agrees} with each of $f$'s assignments for variables in $W$.
+        \[ \forall v \in W : f\br{v} = f|_{W}\br{v} \]
+    \end{definition}
+
+    \begin{definition}
+        \label{def:outcome_compatible}
+        Consider two sets of random variables $V$ and $W$ and two specific outcomes $f_V \in \Out{V}$ and $f_W \in \Out{W}$.
+The outcomes $f_V$ and $f_W$ are said to be \term{compatible} if they agree on their valuations of $V \cap W$.
+Compatibility will be denoted with `$\com$'.
+        \[ f_V \com f_W \iff {f_V}|_{V\cap W} = {f_W}|_{V\cap W} \]
+        Compatibility is a reflexive and symmetric, but \textit{not} transitive.
+There are two cases when compatibility is transitive; whenever $V \cap W = \emptyset$ or $V = W$.
+Whenever $V \cap W = \emptyset$, $f_V$ and $f_W$ can be said to be \textit{trivially} compatible.
+Moreover if $V = W$, compatibility becomes ordinary equivalence,
+        \[ V = W \quad \textrm{and} \quad f_V \com f_W \iff f_V = f_W \]
     \end{definition}
@@
         \label{def:extendable}
-        An outcome $\outc{V}$ is said to be \term{extendable} to an outcome $\outc{W}$ (where $V \subseteq W$) if there exists an outcome $\outc{W\setminus V}$ such that $\outc{W} = \outc{W\setminus V} \valprod \outc{V}$.
-        \[ \Ext{\outc{V} \to \outc{W}} \iff \exists \outc{W\setminus V} \mid \outc{W} = \outc{W\setminus V} \valprod \outc{V} \]
-        The idea being that a \textit{less specific} outcome $\outc{V}$ can be made \textit{more specific} by assigning outcomes to the remaining random variables in $W \setminus V$.
-If such an outcome $\outc{W\setminus V}$ exists, it is unique.
-    \end{definition}
-
-    \begin{definition}
-        The set of all extendable outcomes of $\outc{V}$ in $O_{W}$ is called the \term{extendable set} and can be written as,
-        \[ \Ext[W]{\outc{V}} \defined \outc{V} \valprod O_{W\setminus V} \defined \bc{\outc{W} \in O_{W} \mid \Ext{\outc{V} \to \outc{W}}} \]
-        The extendable set of $\outc{V}$ in $W$ is the set of all outcomes of $O_W$ that \textit{agree} with $\outc{V}$ about valuations for variables in $V$.
-In this language, two outcomes $\outc{V}$ and $\outc{W}$ are \term{compatible} if they are both extendable to some outcome $\outc{V \cup W}$.
-Equivalently, $\outc{V}$ and $\outc{W}$ agree on their valuations of $V \cap W$.
-        \[ \Com{\outc{V}, \outc{W}} \iff \exists \outc{V \cup W} \mid \Ext{\outc{V} \to \outc{V \cup W}}, \Ext{\outc{W} \to \outc{V \cup W}} \]
+        Let $f_V \in \Out{V}$ and $f_W \in \Out{W}$ be outcomes of $V$ and $W$ respectively as in \cref{def:outcome_compatible}.
+If $f_V$ and $f_W$ are compatible, and $W \subseteq V$ then $f_W$ is said to be \term{extendable} to $f_V$ and is denoted `$\ext$'.
+        \[ f_W \ext f_V \iff f_W \com f_V \quad \textrm{and} \quad W \subseteq V \iff {f_W} = {f_V}|_{W} \]
+        The dual language is also appropriate: $f_W$ is a \term{restriction} of $f_V$ (denoted $f_V \res f_W$) if and only if $f_W$ is extendable to $f_V$.
+If $f_W \ext f_V$ then there exists a unique element $f_{V \setminus W} \in \Out{V \setminus W}$ such that $f_V$ can be reconstructed by gluing together $f_{V \setminus W}$ and $f_W$.
+        \[ \forall v \in V : f_V\br{v} = \begin{cases}
+            f_W\br{v} & v \in W \\
+            f_{V\setminus W}\br{v} & v \in V \setminus W
+        \end{cases}  \]
+    \end{definition}
+
+    \begin{remark}
+        The notation `$g \com h$' is used to indicate compatibility between $g \in \Out{V}$ and $h \in \Out{W}$ because of the following observation; $g$ and $h$ are compatible if and only if they are extendable to some outcome $f \in \Out{V \cup W}$.
+        \[ g \com h \iff \exists f \in \Out{V \cup W} \mid g \ext f \res h \]
+        In fact, such an $f$ is uniquely defined,
+        \[ \forall v \in V : f\br{v} = \begin{cases}
+            g\br{v} & v \in V \\
+            h\br{v} & v \in W
+        \end{cases} \]
+    \end{remark}
+
+    \begin{definition}
+        \label{def:extendable_set}
+        The set of all extendable outcomes of $f \in \Out{W}$ into $V$ is called the \term{extendable set of $f$ into $V$} and can be written as,
+        \[ \Ext[V]{f} \defined \bc{g \in \Out{V} \mid f \ext g} \subseteq \Out{V} \]
+        The extendable set of $f$ into $V$ is the subset of outcomes in $\Out{V}$ that \textit{agree} with $f$ about valuations for variables in $W$.
     \end{definition}
@@
     \begin{example}
-        Consider two sets of random variables $V = \bc{a, b}$ and $W = \bc{a, b, c}$.
-Clearly $V \subseteq W$; a prerequisite for extendability.
-Also take all individual outcome spaces to be finite and of order 3: $O_a = O_b = O_c = \bc{1,2,3}$.
-Then $\outc{V} = \outc{\bc{a,b}} = \br{a = 1, b = 2}$ is extendable to the outcome $\outc{W} = \br{a = 1, b = 2, c = 1}$, and the extendable set of $\outc{V}$ in $O_{W}$ is,
-        \[ \Ext[a,b,c]{a = 1, b = 2} = \bc{\br{a = 1, b = 2, c = 1}, \br{a = 1, b = 2, c = 2}, \br{a = 1, b = 2, c = 3}} \]
+        Let $W = \bc{a, b}$ and $V = \bc{a, b, c}$ be two sets of random variables.
+Clearly $W \subseteq V$; a prerequisite for extendability.
+Further impose that the outcome labels for each variable are the same: $O_a = O_b = O_c = \bc{0,1,2}$.
+As an example, let $f = \bc{a \mapsto f\br{a} = 1, b \mapsto f\br{b} = 2} \in \Out{W}$; $f$ is extendable to the outcome $g = \bc{a \mapsto g\br{a} = 1, b \mapsto g\br{b} = 2, c \mapsto g\br{c} = 1} \in \Out{V}$, and the extendable set of $f$ into $V$ is,
+        \[ \Ext[V]{f} = \Ext[a,b,c]{a \mapsto 1, b \mapsto 2} = \bc{\bc{a \mapsto 1, b \mapsto 2, c \mapsto 0}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 1}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 2}} \]
     \end{example}
@@
     \begin{definition}
-        The \term{product distribution} two distributions is denoted as usual with $\times$ and is defined as,
-        \[ \br{\prob[v] \times \prob[w]}\br{\outc{v}, \outc{w}} \defined \prob[v][\outc{v}]\prob[w][\outc{w}] \]
-        A product distribution of $k$ distributions is defined recursively,
-        \[ \prod_{i=1}^{k} \prob[v_i] \defined \br{\prob[v_1] \times \cdots \times \prob[v_k]} \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{marginalization} of a distribution $\prob[v \cup w]$ to the distribution $\prob[v]$ is denoted $\sum_{w} \prob[v \cup w] = \prob[v]$ and is defined such that,
-        \[ \forall \outc{v} \in O_v : \br{\sum_{w} \prob[v, w]}\br{\outc{v}} \defined \sum_{o\bs{w} \in O_w} \prob[v, w][\outc{v}, \outc{w}] \]
-    \end{definition}
-
-    \begin{definition}
-        Following common notation used in \cite{Fritz_2011}, we use the notation $\bs{k} = \br{1, \ldots, k}$ to be a finite index set.
-Moreover, when referencing a finite set with $k$ elements, we can write,
-        \[ A_{\bs{k}} \defined \bc{A_i}_{i \in \bs{k}} = \bc{A_1, \ldots, A_k} \]
+        The \term{product distribution} of two disjoint distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as usual with $\prob[V] \times \prob[W]$ and is defined as,
+        \[ \forall f \in \Out{V \cup W} : \br{\prob[V] \times \prob[W]}\br{f} \defined \prob[V][f|_{V}]\cdot\prob[W][f|_{W}] \]
+        A product distribution of $k$ mutually disjoint distributions is defined as,
+        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
+    \end{definition}
+
+    \begin{definition}
+        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
+        \[ \forall f \in \Out{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
     \end{definition}
@@
     \label{sec:comp_con_mp}
-    In order to determine if a given marginal distribution $\prob[V]$ or set of marginal distributions $\prob[V_{\bs{k}}] \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ is compatible with a causal structure $\graph$, one should first formalize what is meant by \textit{compatible}.
+    In order to determine if a given marginal distribution $\prob[V]$ or set of marginal distributions $\bc{\prob[V_i]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ is compatible with a causal structure $\graph$, one should first formalize what is meant by \textit{compatible}.
 
@@
         \end{enumerate}
-        A set of marginal distributions $\prob[V_{\bs{k}}]$ is compatible with $\graph$ if each of the distributions can be made compatible by the \textit{same} choice of causal parameters.
-        A distribution $\prob[V]$ or set of distributions $\prob[V_{\bs{k}}]$ is said to be \term{incompatible} with a causal structure if there \textit{does not exist} a set of causal parameters with the above mentioned property.
+        A set of marginal distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}}$ is compatible with $\graph$ if each distribution $\prob[V_{i}]$ can be made compatible by the \textit{same} choice of causal parameters.
+        A distribution $\prob[V]$ or set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}}$ is said to be \term{incompatible} with a causal structure if there \textit{does not exist} a set of causal parameters with the above mentioned property.
 
@@
         \label{def:marginal_problem}
-        \term{The Marginal Problem:} Given a set of distributions $\prob[V_{\bs{k}}] \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ where $V_i \subseteq \mathcal{V}$ for some set of random variables $\mathcal{V}$ and $k \geq 2$, does there exist a joint distribution $\prob[\mathcal{V}]$ such that each given distribution $\prob[V_i]$ can be obtained from marginalizing $\prob[\mathcal{V}]$?
-        \[ \forall i \in \bs{k} : \prob[V_i] = \sum_{\mathcal{V} \setminus V_i} \prob[\mathcal{V}] \]
-        Typically (although not strictly necessary), $\mathcal{V}$ is taken to mean the union of all $V_i$'s.
-        \[ \mathcal{V} = V_1 \cup \cdots \cup V_k = \bigcup_{i\in\bs{k}} V_i \eq \label{eq:marginals_union} \]
+        \term{The Marginal Problem:} Given a set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ where $V_i \subseteq \jointvar$ for some set of random variables $\jointvar$, does there exist a joint distribution $\prob[\jointvar]$ such that each given distribution $\prob[V_i]$ can be obtained from marginalizing $\prob[\jointvar]$?
+        \[ \forall i \in \bs{k} : \prob[V_i] = \sum_{\jointvar \setminus V_i} \prob[\jointvar] \]
+        Typically (although not strictly necessary\footnote{Appending any additional variables to $\jointvar$ will not affect the existence of a joint distribution.}), $\jointvar$ is taken to mean the union of all $V_i$'s.
+        \[ \jointvar = V_1 \cup \cdots \cup V_k = \bigcup_{i\in\bs{k}} V_i \eq \label{eq:marginals_union} \]
     \end{definition}
@@
         \label{def:marginal_model}
-        A reoccurring motif of these discussions will be the set of distributions $\prob[V_{\bs{k}}] \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ mentioned in \cref{def:marginal_problem}.
-In agreement with \cite{Fritz_2011} we will call this set of distributions a \term{marginal model} and denote it $\prob_{V_{\bs{k}}}$ provided that they are \textit{compatible}:
+        A reoccurring motif of these discussions will be the set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ mentioned in \cref{def:marginal_problem}.
+In agreement with \cite{Fritz_2011} we call the set of subsets $\mscenario \defined \bc{V_1, \ldots, V_k}$ the marginal contexts or the \term{maximal marginal scenario}\footnote{Rigorously speaking as defined by \cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that $V' \in \mscenario$ whenever $V' \subseteq V_i$ for some $i \in \bs{k}$.
+``Maximal'' refers to the restriction that $\forall i,j : V_i \not \subseteq V_j$.}.
+An individual $V_i \in \mscenario$ is a \term{marginal context}.
+The union of all contexts is denoted $\jointvar$ and is defined exactly as in \cref{eq:marginals_union}.
+        Moreover, we will call the set of distributions a \term{marginal model} and denote it $\prob^{\mscenario}$ provided that they are \textit{compatible} \todo[TC]{Mention quantum non-signalling and maybe $k \geq 3$}:
         \[ \forall i \neq j \text{ if } V_i \cap V_j \neq \emptyset \text{ then } \sum_{V_i \setminus V_j} \prob[V_i] = \sum_{V_j \setminus V_i} \prob[V_j]  \]
-        We call the set of subsets $V_{\bs{k}} \defined \bc{V_1, \ldots, V_k}$ the marginal contexts or the \term{maximal marginal scenario} $V_{\bs{k}}$\footnote{Rigorously speaking as defined by \cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where $V' \in V_{\bs{k}}$ whenever $V' \subseteq V_i$ for some $i$.
-``Maximal'' refers to the restriction that $\forall i,j : V_i \not \subseteq V_j$.} and an individual $V_i$ a \term{marginal context}.
-The union of all contexts is denoted $\mathcal{V}$ and define it exactly as in \cref{eq:marginals_union}.
-
-        Following definition 2.3 in \cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a solution to the marginal problem and \term{non-contextual} otherwise.
-
-        In addition, we elect to define the \term{marginal outcomes} $O_{V_{\bs{k}}}$ to be the set of all outcomes belonging to outcomes of the marginal contexts.
-        \[ O_{V_{\bs{k}}} \defined O_{V_1} \cup \cdots \cup O_{V_k} = \bigcup_{i \in \bs{k}} O_{V_i} \]
-        % By an intended abuse of notation, we say that a particular outcome is an ``element'' of $O_{V_{\bs{k}}}$ if it is an element of $O_{V_i}$ for some $i \in \bs{k}$.
-        % \[ \outc{V_i} \in O_{V_{\bs{k}}} \]
-        Note that $O_{V_{\bs{k}}}$ is \textit{not} a valid outcome space, analogous to the fact that $P_{V_{\bs{k}}}$ is \textit{not} a probability distribution.
-Instead $O_{V_{\bs{k}}}$ is a collection of outcome spaces just as $P_{V_{\bs{k}}}$ is a collection of distributions.
-    \end{definition}
-
-    \begin{definition}
-        A \term{causal compatibility inequality} $\mathcal{I}_{V_{\bs{k}}}$ for a marginal scenario $V_{\bs{k}}$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob_{V_{\bs{k}}}$.
-Whenever the marginal scenario $V_{\bs{k}}$ in question is evident by context, the subscript of $\mathcal{I}_{V_{\bs{k}}}$ will be dropped leaving just $\mathcal{I}$.
+        Following definition 2.3 in \cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a joint distribution $\prob[\jointvar]$ and \term{non-contextual} otherwise.
+
+        In addition, we elect to define the \term{marginal outcomes} $\Out{\mscenario}$ to be the set of all outcomes belonging to outcomes $\Out{V_i}$ of the marginal context\footnote{Here `$\coprod$' refers to the \textit{disjoint union} of outcome contexts; when $i \neq j$, $\Out{V_i} \cap \Out{V_j} = \emptyset$ since $V_i \neq V_j$.}.
+        \[ \Out{\mscenario} \defined \coprod_{i \in \bs{k}} \Out{V_i} \]
+        % By an intended abuse of notation, we say that a particular outcome is an ``element'' of $O_{\mscenario}$ if it is an element of $O_{V_i}$ for some $i \in \bs{k}$.
+        % \[ \outc{V_i} \in O_{\mscenario} \]
+        Each marginal outcome $m \in \Out{\mscenario}$ belongs to a unique marginal outcome space $\Out{V_i}$.
+To make reference to the marginal context $V_i$ associated with $m$, recall \cref{rem:domain_dist}: the context for $m$ is precisely the domain of $m$ ($V_i = \Dom{m}$).
+Note that $\Out{\mscenario}$ is a slight abuse of notation; $\Out{\mscenario}$ is \textit{not} a valid outcome space, analogous to the fact that $P^{\mscenario}$ is \textit{not} a probability distribution.
+Instead $\Out{\mscenario}$ is a \textit{flattened} collection of outcome spaces just as $P^{\mscenario}$ is a collection of distributions.
+The \term{joint outcomes} $\Out{\jointvar}$ are defined in the usual fashion of \cref{def:outcome_space}.
+    \end{definition}
+
+    \begin{definition}
+        A \term{causal compatibility inequality} $\mathcal{I}_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$.
+Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $\mathcal{I}_{\mscenario}$ will be dropped leaving just $\mathcal{I}$.
     \end{definition}
@@
     \label{sec:certificate_inequalities}
-    \subsection{Casting the Inflated Marginal Problem as a Linear Program}
+    \subsection{Casting the Marginal Problem as a Linear Program}
     After obtaining the maximal pre-injectable sets associated with a particular inflation, one can write the marginal problem of \cref{def:marginal_problem} as a linear program.
 The key observation is that marginalization is a \textit{linear} operator that can be performed via a matrix multiplication.
-To do this, we will define the \textit{marginalization matrix}.
-    \begin{definition}
-        The \term{marginalization matrix} $M$ for a marginal scenario $V_{\bs{k}} = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} outcomes $\outc{\mathcal{V}} \in O_{\mathcal{V}}$ and the rows are indexed by \textit{marginal} outcomes corresponding to all outcomes $\outc{V_i} \in O_{V_{\bs{k}}}$.
+To do this, we will define the \textit{incidence matrix}.
+    \begin{definition}
+        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} outcomes $j \in \Out{\jointvar}$ and the rows are indexed by \textit{marginal} outcomes $m \in \Out{\mscenario}$.
 The entries of $M$ are populated whenever a row index is extendable to a column index.
-        \[ M\bs{\outc{V_i}, \outc{\mathcal{V}}} = \begin{cases}
-            1 & \Ext{\outc{V_i} \to \outc{\mathcal{V}}} \\
+        \[ M\bs{m, j} = \begin{cases}
+            1 & m \ext j \\
             0 & \text{otherwise}
         \end{cases} \]
-        The marginalization matrix has $\abs{O_\mathcal{V}}$ columns and $\abs{O_{V_{\bs{k}}}} = \sum_{i=1}^{k} \abs{O_{V_i}}$ rows. The number of non-zero entries of $M$ is a simple expression,
-        \[ \sum_{i=1}^{k} \abs{O_{V_i}}\abs{O_{\mathcal{V} \setminus V_i}} = \sum_{i=1}^{k} \abs{O_{\mathcal{V}}} = k\abs{O_{\mathcal{V}}} \]
-        This is due to the fact that each elements of $\bc{V_1, \ldots, V_k}$ contributes a single non-zero entry to each column of $M$, resulting in $k\abs{O_\mathcal{V}}$ total non-zero entries.
+        The incidence matrix has $\abs{\Out{\jointvar}}$ columns and $\abs{\Out{\mscenario}} = \sum_{i\in \bs{k}} \abs{\Out{V_i}}$ rows. The number of non-zero entries of $M$ is a simple expression,
+        \[ \sum_{i\in\bs{k}} \abs{\Out{V_i}}\abs{\Out{\jointvar \setminus V_i}} = \sum_{i\in \bs{k}} \abs{\Out{\jointvar}} = k\abs{\Out{\jointvar}} \]
+        This is due to the fact that each marginal context contributes a single non-zero entry to each column of $M$, resulting in $k\abs{\Out{\jointvar}}$ total non-zero entries.
     \end{definition}
@@
     \begin{example}
-        Suppose one has $4$ binary random variables $\mathcal{V} = \bc{a,b,c}$ in mind and $2$ subsets $V_{\bs{2}} = \bc{\bc{a,c}, \bc{b}}$. Then the marginalization matrix is:
+        Suppose one has $4$ binary random variables $\jointvar = \bc{a,b,c}$ in mind and $2$ contexts $\mscenario = \bc{\bc{a,c}, \bc{b}}$. Then the incidence matrix is:
         \[ M = \kbordermatrix{
@@
     \begin{definition}
-        The \term{joint distribution vector} $\probvec[\mathcal{V}]$ for a probability distribution $\prob[\mathcal{V}]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\mathcal{V}]$ assigns to each outcome of $\outc{\mathcal{V}}$ of $O_\mathcal{V}$.
-$\probvec[\mathcal{V}]$ shares the same indices as the \textit{column} indices of $M$.
-        \[ \probvec[\mathcal{V}]^\intercal = \bs{\prob[\mathcal{V}][\outc{\mathcal{V}}]}_{o\bs{\mathcal{V}} \in O_{\mathcal{V}}} \]
-    \end{definition}
-    \begin{definition}
-        The \term{marginal distribution vector} $\probvec[V_{\bs{k}}]$ for a marginal model $\prob[V_{\bs{k}}] = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $O_{V_{\bs{k}}}$.
-$\probvec[V_{\bs{k}}]$ shares the same indices as the \textit{row} indices of $M$.
-        \[ \probvec[V_{\bs{k}}]^\intercal = \bs{\prob[V_i][\outc{V_i}] }_{o\bs{V_i} \in O_{V_{\bs{k}}}} \]
-    \end{definition}
-    The marginal and joint distribution vectors are related via the marginalization matrix $M$.
-Given a joint distribution vector $\probvec[\mathcal{V}]$ one can obtain the marginal distribution vector $\probvec[V_{\bs{k}}]$ by multiplying $M$ by $\probvec[\mathcal{V}]$.
-    \[ \probvec[V_{\bs{k}}] = M \cdot \probvec[\mathcal{V}] \eq \label{eq:marginal_problem_matrix} \]
-    \todo[TC]{Discuss non-unique but consistent ordering of $M$, $\probvec[\mathcal{V}]$ and $\probvec[V_{\bs{k}}]$}
-
-    The marginal problem can now be rephrased in the language of the marginalization matrix.
-Suppose one obtains a marginal distribution vector $\probvec[V_{\bs{k}}]$.
-The marginal problem becomes equivalent to the question: \textit{Does there exist a joint distribution vector $\probvec[\mathcal{V}]$ such that \cref{eq:marginal_problem_matrix} holds?}
+        The \term{joint distribution vector} $\probvec[\jointvar]$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint outcome of $j \in \Out{\jointvar}$.
+$\probvec[\jointvar]$ shares the same indices as the \textit{column} indices of $M$.
+        \[ \forall j \in \Out{\jointvar} : \probvec[\jointvar]^\intercal\bs{j} = \prob[\jointvar][j] \]
+    \end{definition}
+    \begin{definition}
+        The \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Out{\mscenario}$.
+$\probvec^{\mscenario}$ shares the same indices as the \textit{row} indices of $M$.
+        \[ \forall m \in \Out{\mscenario} : {\probvec^{\mscenario}}^\intercal\bs{m} = \prob[\Dom{m}][m] \]
+        Where $\Dom{m} \in \mscenario$ and $\prob[\Dom{m}] \in \prob^{\mscenario}$ as per \cref{rem:domain_dist}.
+    \end{definition}
+    The marginal and joint distribution vectors are related via the incidence matrix $M$.
+Given a joint distribution vector $\probvec[\jointvar]$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec[\jointvar]$.
+    \[ \probvec^{\mscenario} = M \cdot \probvec[\jointvar] \eq \label{eq:marginal_problem_matrix} \]
+    \todo[TC]{Discuss non-unique but consistent ordering of $M$, $\probvec[\jointvar]$ and $\probvec^{\mscenario}$}
+
+    The marginal problem can now be rephrased in the language of the incidence matrix.
+Suppose one obtains a marginal distribution vector $\probvec^{\mscenario}$.
+The marginal problem becomes equivalent to the question: \textit{Does there exist a joint distribution vector $\probvec[\jointvar]$ such that \cref{eq:marginal_problem_matrix} holds?}
 
@@
             & \text{subject to:} && x \succeq 0 \\
-            & && M \cdot x = \probvec[V_{\bs{k}}]
+            & && M \cdot x = \probvec^{\mscenario}
         \end{alignat*}
@@
 The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:marginal_problem_matrix} and is a valid joint distribution vector.
-Therefore feasibility implies that $\prob[\mathcal{V}] = x$, solving the marginal problem with positive result.
-Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\prob[\mathcal{V}]$ over all random variables.
+Therefore feasibility implies that $\prob[\jointvar] = x$, solving the marginal problem with positive result.
+Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\prob[\jointvar]$ over all random variables.
     \end{definition}
@@
         \begin{alignat*}{2}
-            & \text{minimize:} \quad&& y \cdot \probvec[V_{\bs{k}}]\\
+            & \text{minimize:} \quad&& y \cdot \probvec^{\mscenario}\\
             & \text{subject to:} && y \cdot M \succeq 0
         \end{alignat*}
-        Where $y$ is a real valued vector with the same length as $\probvec[V_{\bs{k}}]$.
+        Where $y$ is a real valued vector with the same length as $\probvec^{\mscenario}$.
     \end{definition}
@@
 Secondly if $y \cdot M \succeq 0$ and $x \succeq 0$, then the following must hold if the primal is feasible:
-    \[ y \cdot \probvec[V_{\bs{k}}] =  y \cdot M \cdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
-    Therefore the \textit{sign} of the dual value $d \defined \min \br{y \cdot \probvec[V_{\bs{k}}]}$ solves the marginal problem.
+    \[ y \cdot \probvec^{\mscenario} =  y \cdot M \cdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
+    Therefore the \textit{sign} of the dual value $d \defined \min \br{y \cdot \probvec^{\mscenario}}$ solves the marginal problem.
 If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore the marginal problem has negative result.
-Likewise if $d$ satisfies \cref{eq:dual_marginal_ineq}, then a joint distribution $\prob[\mathcal{V}]$ exists.
+Likewise if $d$ satisfies \cref{eq:dual_marginal_ineq}, then a joint distribution $\prob[\jointvar]$ exists.
 Before continuing, an important observation needs to be made.
@@
 
-    \begin{definition} An \term{infeasibility certificate} is any vector $y$ that satisfies the constraints of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec[V_{\bs{k}}]$.
-    \[ y \in \R^{\abs{O_{V_{\bs{k}}}}} : y \cdot M \succeq 0, \quad y \cdot \probvec[V_{\bs{k}}] < 0 \]
+    \begin{definition} An \term{infeasibility certificate} is any vector $y$ that satisfies the constraints of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
+    \[ y \in \R^{\abs{\Out{\mscenario}}} : y \cdot M \succeq 0, \quad y \cdot \probvec^{\mscenario} < 0 \]
     Furthermore, any $y$ satisfying $y \cdot M \succeq 0$ induces a \term{certificate inequality} that constraints the space of marginal distribution vectors which takes the symbolic form of \cref{eq:dual_marginal_ineq},
-    \[ y \cdot \probvec[V_{\bs{k}}] \geq 0 \]
-    Where the entries of the certificate $y$ act as coefficients for the entries of $\probvec[V_{\bs{k}}]$.
+    \[ y \cdot \probvec^{\mscenario} \geq 0 \]
+    Where the entries of the certificate $y$ act as coefficients for the entries of $\probvec^{\mscenario}$.
     \end{definition}
@@
     \begin{example}
-        The marginal problem for the inflated causal structure $\graph'$ depicted in \cref{fig:inflated_triangle_scenario} concerns itself with the pre-injectable marginal scenario $\PreInj[\graph]{\graph'} = V_{\bs{12}} = \bc{\prob[V_1], \ldots, \prob[V_{12}]}$.
-The marginalization matrix $M$ has $16,896$ rows and $16,777,216$ columns.
+        The marginal problem for the inflated causal structure $\graph'$ depicted in \cref{fig:inflated_triangle_scenario} concerns itself with the pre-injectable marginal scenario $\mscenario = \PreInj[\graph]{\graph'} = \bc{V_1, \ldots, V_{12}}$.
+The incidence matrix $M$ has $16,896$ rows and $16,777,216$ columns.
         \begin{align*}
-            &\text{\# Rows} = \sum_{i=1}^{12} \abs{O_{V_i}} = \sum_{i=1}^{12} 4^{\abs{V_i}} = 4 \cdot 4^6 + 8 \cdot 4^3 = 16,896 \\
+            &\text{\# Rows} = \abs{\Out{\mscenario}} = \sum_{i=1}^{12} \abs{\Out{V_i}} = \sum_{i=1}^{12} 4^{\abs{V_i}} = 4 \cdot 4^6 + 8 \cdot 4^3 = 16,896 \\
             &\text{\# Columns} = \abs{O_{\nodes'}} = 4^{\abs{\nodes'}} = 4^{12} = 16,777,216
@@
 
-    \section{Logical Implications of Non-Contextuality}
-
-    Section \ref{sec:certificate_inequalities} discusses how one can obtain a valid compatibility inequality that witnesses incompatibility for a particular marginal model $\prob_{V_{\bs{k}}}$ by writing the marginal problem as a linear program.
+    \section{Covering Inequalities}
+
+    Section \ref{sec:certificate_inequalities} discusses how one can obtain a valid compatibility inequality that witnesses incompatibility for a particular marginal model $\prob^{\mscenario}$ by writing the marginal problem as a linear program.
     \todo[TC]{Motivate why certificates are not enough, want many solutions, want logical foundation}
@@
     \label{sec:implications_marginal_problem}
-    The question then remains, \textit{how does non-contextuality give rise to implications of the form of \cref{eq:1n_pi}?} Begin by making the principle assumption that a joint distribution \textit{does} exist for a marginal model $\prob[V_{\bs{k}}]$.
+    The question then remains, \textit{how does non-contextuality give rise to implications of the form of \cref{eq:1n_pi}?} Begin by making the principle assumption that a joint distribution \textit{does} exist for a marginal model $\prob^{\mscenario}$.
 This assumption induces logical \textit{tautologies} that take the form of \cref{eq:1n_pi}, which we call \term{marginal implications}, using the following train of logic.
     \begin{enumerate}
-        \item Suppose a particular marginal outcome $a \in O_{V_{\bs{k}}}$ happens to occur.
-        \item Since a joint distribution exists, then $a$ refers to some \textit{incomplete} knowledge about a \textit{joint} event $j = \outc{\mathcal{V}} \in O_{\mathcal{V}}$ that actually occured.
-More precisely, this set of possible $j$'s is the extendable set of $a$ in $O_{\mathcal{V}}$.
-        \[ j \in \Ext[\mathcal{V}]{a} \]
-        \item Therefore whenever $a$ occurs, one of the elements $j$ of $\Ext[\mathcal{V}]{a}$ \textit{has} to occur.
-        \[ a \implies \bigvee_{j \in \Ext[\mathcal{V}]{a}} j \eq \label{eq:A_impies_extendable}\]
+        \item Suppose a particular marginal outcome $a \in O_{\mscenario}$ happens to occur.
+        \item Since a joint distribution exists, then $a$ refers to some \textit{incomplete} knowledge about a \textit{joint} event $j = \outc{\jointvar} \in O_{\jointvar}$ that actually occured.
+More precisely, this set of possible $j$'s is the extendable set of $a$ in $O_{\jointvar}$.
+        \[ j \in \Ext[\jointvar]{a} \]
+        \item Therefore whenever $a$ occurs, one of the elements $j$ of $\Ext[\jointvar]{a}$ \textit{has} to occur.
+        \[ a \implies \bigvee_{j \in \Ext[\jointvar]{a}} j \eq \label{eq:A_impies_extendable}\]
         \item Now suppose we could obtain a set of marginal outcomes $C = \bc{c_1, \ldots, c_m}$ each different from $a$ such that for every $j$, $\Ext{c \to j}$ for at least one element $c \in C$.
 If such a $C$ can be found, then the possibility of at least one $j$ occurring implies the possibility of at least one $c$ occurring.
-        \[ \bigvee_{j \in \Ext[\mathcal{V}]{a}} j \implies c_1 \vee \cdots \vee c_m = \bigvee_{i \in \bs{m}} c_i\eq \label{eq:extendable_implies_cover} \]
+        \[ \bigvee_{j \in \Ext[\jointvar]{a}} j \implies c_1 \vee \cdots \vee c_m = \bigvee_{i \in \bs{m}} c_i\eq \label{eq:extendable_implies_cover} \]
 
@@
 
-    Finding all marginal implications for a chosen marginal outcome $a$ corresponds to finding a set of marginal outcomes $C = \bc{c_1, \ldots, c_m}$ whose extendable sets \textit{cover} $\Ext[\mathcal{V}]{a}$.
+    Finding all marginal implications for a chosen marginal outcome $a$ corresponds to finding a set of marginal outcomes $C = \bc{c_1, \ldots, c_m}$ whose extendable sets \textit{cover} $\Ext[\jointvar]{a}$.
 Formally this corresponds to a \term{set covering} problem \todo[TC]{cite} which we elected to cast as the equivalent \term{hypergraph transversal problem}.
@@
     Given an antecedent $a$, we can construct a hypergraph $\hgraph_{a}$ called the \term{marginal hypergraph} with nodes $\nodes_a$ and $\edges_a$.
-The nodes of this hypergraph are the subset of marginal outcomes $\nodes_a \subseteq O^{V_{\bs{k}}}$ \textit{compatible} with $a$.
-    The edges are labeled by outcomes in $\Ext[\mathcal{V}]{a} \subseteq O_{\mathcal{V}}$, namely the set of $j$'s, and contain all nodes compatible with $j$.
+The nodes of this hypergraph are the subset of marginal outcomes $\nodes_a \subseteq O^{\mscenario}$ \textit{compatible} with $a$.
+    The edges are labeled by outcomes in $\Ext[\jointvar]{a} \subseteq O_{\jointvar}$, namely the set of $j$'s, and contain all nodes compatible with $j$.
     \begin{align*}
-        \nodes_a &= \bc{n \in O^{V_{\bs{k}}} \mid \Com{n, a}} \eq \label{eq:hgraph_nodes} \\
-        \edges_a &= \bc{\bc{n \in O^{V_{\bs{k}}} \mid \Com{n, j}} , j \in \Ext[\mathcal{V}]{a}} \eq \label{eq:hgraph_edges}
+        \nodes_a &= \bc{n \in O^{\mscenario} \mid \Com{n, a}} \eq \label{eq:hgraph_nodes} \\
+        \edges_a &= \bc{\bc{n \in O^{\mscenario} \mid \Com{n, j}} , j \in \Ext[\jointvar]{a}} \eq \label{eq:hgraph_edges}
     \end{align*}
@@
 To prove this, consider the definition of compatibility between outcomes.
-If every $n$ is compatible with $a$, then there exists some outcome $j \in \Ext[\mathcal{V}]{A}$ such that $\Ext{n \to j}$.
+If every $n$ is compatible with $a$, then there exists some outcome $j \in \Ext[\jointvar]{A}$ such that $\Ext{n \to j}$.
 Therefore since $\Ext{n \to j}$, $\Com{n, j}$; satisfying the central condition of \cref{eq:hgraph_edges}.
@@
     \section{Deriving Symmetric Inequalities}
+    \label{sec:symmetry}
     Symmetric compatibility inequalities are useful for a number of reasons.
@@
 al.
-\cite{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:comp_con_mp}; the number of extremal points typically grows exponentially in $\mathcal{V}$, but only polynomial for the symmetric polytope.
+\cite{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:comp_con_mp}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
 They also note a number of interesting inequalities (such as CHSH \cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that quantum-non-trivial inequalities can be recovered from facets of a symmetric polytope.
@@
     The aim of this section is to formalize what types of symmetries are present in a particular causal structure $\graph$.
-The group of these causal symmetries will define, for each compatibility inequality $\mathcal{I}_{V_{\bs{k}}}$, a family of inequalities that are also valid incompatibility inequalities.
-
-    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\varphi$ from $N$ to $N$.
-    \[ \Perm{N} = \bc{\varphi \mid \varphi : N \to N} \]
-    The action of $\varphi \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\varphi$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
+The group of these causal symmetries will define, for each compatibility inequality $\mathcal{I}_{\mscenario}$, a family of inequalities that are also valid incompatibility inequalities.
+
+    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\gelem$ from $N$ to $N$.
+    \[ \Perm{N} = \bc{\gelem \mid \gelem : N \to N} \]
+    The action of $\gelem \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\gelem$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
     \begin{align*}
-    \varphi\br{\graph} &\defined \br{\varphi\br{\nodes}, \varphi\br{\edges}} \\
-    \varphi\br{\nodes} &\defined \bc{\varphi\br{n} \mid n \in \nodes} = \nodes \\
-    \varphi\br{\edges} &\defined \bc{\varphi\br{e} \mid e \in \edges}
+    \action{\graph} &\defined \br{\action{\nodes}, \action{\edges}} \\
+    \action{\nodes} &\defined \bc{\action{n} \mid n \in \nodes} = \nodes \\
+    \action{\edges} &\defined \bc{\action{e} \mid e \in \edges}
     \end{align*}
     To motivate a more general treatment of such symmetries, consider the Triangle Scenario of \cref{fig:triangle_scenario}.
-Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\varphi \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\varphi\br{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes.
-By construction, any valid compatibility inequality $\mathcal{I}_{V_{\bs{k}}}$ for the marginal scenario $V_{\bs{k}} = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes.
-Therefore applying $\varphi$ to all distributions in $\mathcal{I}_{V_{\bs{k}}}$ yields $\varphi\br{\mathcal{I}_{V_{\bs{k}}}} \defined \varphi\br{\mathcal{I}}_{\varphi\br{V_{\bs{k}}}}$, another valid compatibility inequality for the permuted marginal scenario $\varphi\br{V_{\bs{k}}}$ defined as,
-    \[ \varphi\br{V_{\bs{k}}} = \bc{\varphi\br{V_1}, \ldots, \varphi\br{V_k}} \]
+Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\gelem \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\action{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes.
+By construction, any valid compatibility inequality $\mathcal{I}_{\mscenario}$ for the marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes.
+Therefore applying $\gelem$ to all distributions in $\mathcal{I}_{\mscenario}$ yields $\action{\mathcal{I}_{\mscenario}} \defined \action{\mathcal{I}}_{\action{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\action{\mscenario}$ defined as,
+    \[ \action{\mscenario} = \bc{\action{V_1}, \ldots, \action{V_k}} \]
     % \begin{example}
@@
     %     \[ \prob[ABC][002]\prob[ABC][003] \leq \prob[A][0]\prob[C][3] \]
-    %     Now consider $\varphi = \bc{A \to A, B \to C, C \to B}$. Since $\varphi\br{\graph} = \graph$, $\varphi\br{\mathcal{I}_{V_{\bs{k}}}}$ is also a valid compatibility inequality,
+    %     Now consider $\gelem = \bc{A \to A, B \to C, C \to B}$. Since $\action{\graph} = \graph$, $\action{\mathcal{I}_{\mscenario}}$ is also a valid compatibility inequality,
     % \end{example}
-    More generically, any permutation $\varphi$ that preserves the graphical structure of $\graph$ can be applied to $\mathcal{I}_{V_{\bs{k}}}$ to generate new and valid compatibility inequalities.
+    More generically, any permutation $\gelem$ that preserves the graphical structure of $\graph$ can be applied to $\mathcal{I}_{\mscenario}$ to generate new and valid compatibility inequalities.
 Specifically this alludes to the \term{graph automorphism group} $\Aut{\graph}$ of $\graph$.
-    \[ \Aut{\graph} \defined \bc{\varphi \in \Perm{\nodes} \mid \varphi\br{\graph} = \graph} \]
-    In general, $\Aut{\graph}$ could include elements $\varphi$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}.
+    \[ \Aut{\graph} \defined \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph} \]
+    In general, $\Aut{\graph}$ could include elements $\gelem$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}.
 This behaviour is \textit{undesired} for causal inference where the latent nodes will never appear in a marginal scenario.
@@
         The \term{causal symmetry group} for a causal structure $\graph$ is the graph automorphism subgroup that stabilizes the observable nodes.
-        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\br{\graph} = \graph, \forall n \in \nodes_O :\varphi\br{n} \in \nodes_O} \]
-        Given any compatibility inequality $\mathcal{I}_{V_{\bs{k}}}$, each element $\varphi$ of the causal symmetry group defines a new valid compatibility inequality $\varphi\br{\mathcal{I}_{V_{\bs{k}}}} = \varphi\br{\mathcal{I}}_{\varphi\br{V_{\bs{k}}}}$.
+        \[ \Aut[\nodes_O]{\graph} = \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph, \forall n \in \nodes_O :\action{n} \in \nodes_O} \]
+        Given any compatibility inequality $\mathcal{I}_{\mscenario}$, each element $\gelem$ of the causal symmetry group defines a new valid compatibility inequality $\action{\mathcal{I}_{\mscenario}} = \action{\mathcal{I}}_{\action{\mscenario}}$.
     \end{definition}
@@
 As a consequence of this observation, we need to consider a subgroup of the causal symmetry group that preserves the pre-injectable sets,
-    \[ \varphi\br{\PreInj[\graph]{\graph'}} = \PreInj[\graph]{\graph'} \eq \label{eq:preserved_preinj} \]
-
-    \begin{definition}
-        The \term{restricted causal symmetry group} $\Phi$ for a causal structure $\graph$ and a marginal scenario $V_{\bs{k}}$ is the graph automorphism subgroup that stabilizes the marginal scenario $V_{\bs{k}}$.
-        \[ \Phi \defined \Aut[V_{\bs{k}}]{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\br{\graph} = \graph, \forall V \in V_{\bs{k}} : \varphi\br{V} \in V_{\bs{k}}} \]
-        Given any compatibility inequality $\mathcal{I}_{V_{\bs{k}}}$ each element $\varphi$ of the causal symmetry group defines a new valid compatibility inequality $\varphi\br{\mathcal{I}_{V_{\bs{k}}}} = \varphi\br{\mathcal{I}}_{V_{\bs{k}}}$ over the \textit{same} marginal context $V_{\bs{k}}$.
+    \[ \action{\PreInj[\graph]{\graph'}} = \PreInj[\graph]{\graph'} \eq \label{eq:preserved_preinj} \]
+
+    \begin{definition}
+        The \term{restricted causal symmetry group} $\Phi$ for a causal structure $\graph$ and a marginal scenario $\mscenario$ is the graph automorphism subgroup that stabilizes the marginal scenario $\mscenario$.
+        \[ \Phi \defined \Aut[\mscenario]{\graph} = \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph, \forall V \in \mscenario : \action{V} \in \mscenario} \]
+        Given any compatibility inequality $\mathcal{I}_{\mscenario}$ each element $\gelem$ of the causal symmetry group defines a new valid compatibility inequality $\action{\mathcal{I}_{\mscenario}} = \action{\mathcal{I}}_{\mscenario}$ over the \textit{same} marginal context $\mscenario$.
     \end{definition}
@@
 If one obtains a particular inequality $\mathcal{I}'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\Phi$, an entire family of valid compatibility inequalities are also obtained.
-    \[ \bc{\varphi\br{\mathcal{I}'}_{\PreInj[\graph]{\graph'}} \mid \varphi \in \Phi} \text{ where } \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
+    \[ \bc{\action{\mathcal{I}'}_{\PreInj[\graph]{\graph'}} \mid \gelem \in \Phi} \text{ where } \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
     We have obtained $\Phi$ for the inflated triangle scenario \cref{fig:inflated_triangle_scenario}. $\Phi$ is an order $48$ group with the following $4$ generators:
@@
     \begin{aligned}[c]
-    &\hspace{1mm}\varphi_1 \\
+    &\hspace{1mm}\gelem_1 \\
     A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
@@
     \begin{aligned}[c]
-    &\hspace{1mm}\varphi_2 \\
+    &\hspace{1mm}\gelem_2 \\
     A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
@@
     \begin{aligned}[c]
-    &\hspace{1mm}\varphi_3 \\
+    &\hspace{1mm}\gelem_3 \\
     A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
@@
     \begin{aligned}[c]
-    &\hspace{1mm}\varphi_4 \\
+    &\hspace{1mm}\gelem_4 \\
     A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
@@
     %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
-    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the inflated Triangle Scenario $\graph'$ of \cref{fig:inflated_triangle_scenario}.
+    It is easy to verify that $\gelem_1, \gelem_2, \gelem_3, \gelem_4$ are all automorphisms of the inflated Triangle Scenario $\graph'$ of \cref{fig:inflated_triangle_scenario}.
 Moreover they stabilize the observable nodes, and the map pre-injectable sets of \cref{eq:pre-injectable_triangle_scenario} to the pre-injectable sets.
@@
     \[ \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \sim \Aut[\nodes_O]{\graph} \]
-    To see this, $\varphi_1$ and $\varphi_4$ become the identity element $\mathbb{I}$ in $\Aut[\nodes_O]{\graph}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
+    To see this, $\gelem_1$ and $\gelem_4$ become the identity element $\mathbb{I}$ in $\Aut[\nodes_O]{\graph}$ upon removal of the copy-index, leaving $\gelem_2$ to generate reflections and $\gelem_3$ to generate rotations.
     \subsection{Symmetric Marginal Polytope}
@@
 Although very useful, we divert our attention to finding \textit{symmetric} inequalities themselves.
-    \[ \forall \varphi \in \Phi :  \varphi\br{\mathcal{I}_{V_{\bs{k}}}} = \mathcal{I}_{V_{\bs{k}}} \]
-    In order to do this, we must first define how elements $\varphi \in \Phi$ act on marginal outcomes $O_{V_{\bs{k}}}$.
+    \[ \forall \gelem \in \Phi :  \action{\mathcal{I}_{\mscenario}} = \mathcal{I}_{\mscenario} \]
+    In order to do this, we must first define how elements $\gelem \in \Phi$ act on marginal outcomes $O_{\mscenario}$.
+    \begin{definition}
+        Let $\jointvar = \bc{v_1, \ldots, v_k}$ be a collection of random variables and let $\gelem \in \Perm{\jointvar}$.
+$\jointvar$ is said to be \term{label invariant with respect to $\gelem$} if the outcome labels for each variable $v \in \jointvar$ are unchanged under the action of $\gelem$.
+        \[ \forall v \in \jointvar : O_{v} = O_{\action{v}} \]
+        Label invariance is a prerequisite for any kind of symmetry amoung random variables.
+    \end{definition}
+    \begin{definition}
+        Let $\jointvar = \br{v_1, \ldots v_k}$ be a collection of random variables along with a specific outcome $m \in \Out{V}$ where $V \subseteq \jointvar$.
+The action of $\gelem \in \Perm{\jointvar}$ on $m$ is a new outcome $\action{m} \in \Out{\action{V}}$ over $\action{V} \subseteq \jointvar$ defined as follows,
+        \[ \forall v \in V : \br{\action{m}}\br{\action{v}} \defined m \br{v} \]
+        The idea being that $\gelem$ modifies $m$ in such a way that permutes its domain while leaving its range invariant.
+    \end{definition}
     \begin{example}
-        Consider the outcome $\outc{ABC} = \br{A = 0, B = 1, C = 2} \in O_{ABC}$ where all variables have $4$ possible outcomes $\bc{0,1,2,3}$\footnote{Strictly speaking, the action of $\varphi$ is only well defined if each variable $v \in \mathcal{V}$ has the same outcome space $O_v$.} and the permutation $\varphi = \bc{A \to D, B \to C, C \to B, D \to A}$.
-We can act on $\outc{ABC}$ with $\varphi$ to obtain a different outcome which we denote $\varphi\br{\outc{ABC}}$,
-        \[ \varphi\br{\outc{ABC}} \defined \br{\varphi\br{A} = 0, \varphi\br{B} = 1, \varphi\br{C} = 2} = \br{D = 0, C = 1, B = 2} = \outc{BCD} \]
-        This notation can be misleading; when isolated $\outc{BCD}$ refers to an \textit{arbitrary} outcome of $O_{BCD}$, while in this context it is intended that $\outc{BCD}$ refers to the \textit{specific} outcome of $O_{BCD}$ that matches the numerical valuation of $\outc{ABC}$.
-Probabilistically, the action of $\varphi$ is defined as,
-        \[ \varphi\br{\prob[ABC]\br{012}} \defined \prob[\varphi\br{ABC}]\br{012} = \prob[DCB][012] = \prob[BCD][210] \]
+        Consider the outcome $m = \bc{A \mapsto 0, B \mapsto 1, C \mapsto 2} \in \Out{\bc{A,B,C}}$ where all variables have $4$ possible outcomes $O_A = O_B = O_C = \bc{0,1,2,3}$ and the permutation $\gelem = \bc{A \to D, B \to C, C \to B, D \to A}$.
+        The \textit{action} of $\gelem$ on $m$ is as follows,
+        \begin{align*}
+            \action{m} &= \action{\bc{A \mapsto m\br{A}, B \mapsto m\br{B}, C \mapsto m\br{C}}} \\
+            &= \bc{\action{A} \mapsto m\br{A}, \action{B} \mapsto m\br{B}, \action{C} \mapsto m\br{C}} \\
+            &= \bc{D \mapsto m\br{A}, C \mapsto m\br{B}, B \mapsto m\br{C}} \\
+            &= \bc{D \mapsto 0, C \mapsto 1, B \mapsto 2} \\
+            &= \bc{B \mapsto 2, C \mapsto 1, D \mapsto 0}
+        \end{align*}
+        Evidently, $\action{m} \in \Out{\bc{B, C, D}}$.
     \end{example}
 
-    Through repeated action of $\varphi \in \Phi$ on marginal outcomes $m \in O_{V_{\bs{k}}}$ and joint outcomes $j \in O_{\mathcal{V}}$, one can define group orbits of $\Phi$ in $O_{V_{\bs{k}}}$ and $O_{\mathcal{V}}$.
+    Through repeated action of $\gelem \in \Phi$ on marginal outcomes $m \in \Out{\mscenario}$ and joint outcomes $j \in \Out{\jointvar}$, one can define group orbits of $\Phi$ in $\Out{\mscenario}$ and $\Out{\jointvar}$.
     \begin{align*}
-    \Orb[\Phi]{m} &\defined \bc{\varphi\br{m} \in O_{V_{\bs{k}}} \mid \varphi \in \Phi} \\
-    \Orb[\Phi]{j} &\defined \bc{\varphi\br{j} \in O_{\mathcal{V}} \mid \varphi \in \Phi}
+        \Orb[\Phi]{m} &\defined \bc{\action{m} \mid \gelem \in \Phi} \\
+        \Orb[\Phi]{j} &\defined \bc{\action{j} \mid \gelem \in \Phi}
     \end{align*}
@@
     \begin{definition}
-        The \term{symmetric marginalization matrix} $M_{\Phi}$ for a marginal scenario $V_{\bs{k}}$ and a particular restricted causal symmetry $\Phi$ is a contracted version of the marginalization matrix $M$ for $V_{\bs{k}}$.
+        The \term{symmetric incidence matrix} $M_{\Phi}$ for a marginal scenario $\mscenario$ and a particular restricted causal symmetry $\Phi$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
 Each row of $M_{\Phi}$ corresponds to a marginal orbit $\Orb[\Phi]{m}$.
@@
     \section{Connections to Sheaf-Theoretic Treatment}
-    \section{Higher Order Logical Implications as a Complete Solution to the Marginal Problem}
     \section{Computationally Efficient Parametrization of the Unitary Group}

### 2016-09-03 document/main.tex
Progress

@@
 
+\usepackage{silence}
+\WarningFilter{revtex4-1}{Repair the float}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 % === All of the Packages I use frequently ===
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
 
@@
 \newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
-\newcommand{\ext}{\mathrel{\Yright}}
-\newcommand{\res}{\mathrel{\Yleft}}
+\newcommand{\ext}{\mathrel{\Yleft}}
+\newcommand{\res}{\mathrel{\Yright}}
 \newcommand{\gelem}{\varphi}
@@
 \newcommand{\jointvar}{\mathcal{J}}
+\newcommand{\mext}[1]{E_{#1}}
+\newcommand{\mul}[1]{\Gamma_{#1}}
+\newcommand{\isext}[2]{\delta_{#1 \ext #2}}
+\newcommand{\ts}{\mathcal{T}}
 % When I introduce a new term or definition
@@
 \setoperator{PreInj} % Pre-injectable sets
+\setoperator{ImPreInj} % images of the Pre-injectable sets
 \setoperator{Aut} % graph automorphism
@@
     \begin{definition}
-        This notation generalizes to more than one variable. Letting $V = \bc{v_1, v_2}$, we define $\Out{V}$ to be the set of all joint valuations of $v_1$ and $v_2$.
+        % This notation generalizes to more than one variable. Letting $V = \bc{v_1, v_2}$, we define $\Out{V}$ to be the set of all joint valuations of $v_1$ and $v_2$.
         % Where the valuation product between outcome spaces is defined as follows,\footnote{At this level, a valuation product behaves analogously to a Cartesian product.
 However in \cref{def:extendable_set}, we define the a valuation product between outcomes and outcomes spaces.}
-        \[ \Out{V} = \Out{\bc{v_1, v_2}} \defined \bc{f : \bc{v_1, v_2} \to \bc{O_{v_1}, O_{v_2}} \mid f\br{v_i} \in O_{v_i}, i \in \bc{1,2}}  \]
+        % \[ \Out{V} = \Out{\bc{v_1, v_2}} \defined \bc{f : \bc{v_1, v_2} \to \bc{O_{v_1}, O_{v_2}} \mid f\br{v_i} \in O_{v_i}, i \in \bc{1,2}}  \]
         As a natural generalization, when considering a larger set of random variables $V = \bc{v_i}_{i \in \bs{k}}$ we define the joint outcome space in an analogous way,
@@
     \begin{remark}
-        The notation `$g \com h$' is used to indicate compatibility between $g \in \Out{V}$ and $h \in \Out{W}$ because of the following observation; $g$ and $h$ are compatible if and only if they are extendable to some outcome $f \in \Out{V \cup W}$.
-        \[ g \com h \iff \exists f \in \Out{V \cup W} \mid g \ext f \res h \]
+        The notation `$g \com h$' is used to indicate compatibility between $g \in \Out{V}$ and $h \in \Out{W}$ because of the following observation; $g$ and $h$ are compatible if and only if extensions of some outcome $f \in \Out{V \cap W}$.
+        \[ g \com h \iff \exists f \in \Out{V \cap W} \mid g \res f \ext h \]
         In fact, such an $f$ is uniquely defined,
-        \[ \forall v \in V : f\br{v} = \begin{cases}
-            g\br{v} & v \in V \\
-            h\br{v} & v \in W
-        \end{cases} \]
+        \[ \forall v \in V \cap W : f\br{v} = g\br{v} = g\br{v} \]
     \end{remark}
@@
 
+    \subsection{Preliminary Definitions}
+
+    Before discussing the present work, we
+
     \todo[TC]{How many definitions do I need to write??}
 
-    \section{Triangle Scenario}
-    \todo[TC]{Discuss the Triangle Scenario, previous work done on it, etc.}
-
-    Figure 8 of Appendix E \cite{Henson_2014}
-    Figure 1 of \cite{Inflation}
-
-    Focusing on the inflation depicted in \cref{fig:inflated_triangle_scenario}, we obtained the maximally pre-injectable sets through the procedure outlined in \cite{Inflation}.
+    \section{Compatibility, Contextuality and the Marginal Problem}
+    \label{sec:comp_con_mp}
+    In order to determine if a given marginal distribution $\prob[V]$ or set of marginal distributions $\bc{\prob[V_i]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ is compatible with a causal structure $\graph$, one should first formalize what is meant by \textit{compatible}.
+
+    \begin{definition}
+        A set of \term{causal parameters} for a particular causal structure $\graph$ is the specification of a conditional distribution for every node $n \in \nodes$ given it's parents in $\graph$.
+        \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
+    \end{definition}
+    \begin{definition}
+        \label{def:compatible}
+        A marginal distribution $\prob[V]$ is \term{compatible} with a causal structure $\graph$ (where it is assumed that $V \subseteq \nodes_O$) if there exists a \textit{choice} of causal parameters $\bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes}$ such that $\prob[V]$ can be \textit{recovered} from the following series of operations:
+        \begin{enumerate}
+            \item First obtain a joint distribution over \textit{all} nodes of of the causal structure,
+            \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] \]
+            \item Then marginalize over the latent nodes of $\graph$,
+            \[ \prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes] \]
+            \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$,
+            \[ \prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O] \]
+        \end{enumerate}
+        A set of marginal distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}}$ is compatible with $\graph$ if each distribution $\prob[V_{i}]$ can be made compatible by the \textit{same} choice of causal parameters.
+        A distribution $\prob[V]$ or set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}}$ is said to be \term{incompatible} with a causal structure if there \textit{does not exist} a set of causal parameters with the above mentioned property.
+
+        \todo[TC]{Source this?}
+    \end{definition}
+    Operations 2 and 3 of \cref{def:compatible} are related to the \textit{marginal problem}.
+    \begin{definition}
+        \label{def:marginal_problem}
+        \term{The Marginal Problem:} Given a set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ where $V_i \subseteq \jointvar$ for some set of random variables $\jointvar$, does there exist a joint distribution $\prob[\jointvar]$ such that each given distribution $\prob[V_i]$ can be obtained from marginalizing $\prob[\jointvar]$?
+        \[ \forall i \in \bs{k} : \prob[V_i] = \sum_{\jointvar \setminus V_i} \prob[\jointvar] \]
+        Typically (although not strictly necessary\footnote{Appending any additional variables to $\jointvar$ will not affect the existence of a joint distribution.}), $\jointvar$ is taken to mean the union of all $V_i$'s.
+        \[ \jointvar = V_1 \cup \cdots \cup V_k = \bigcup_{i\in\bs{k}} V_i \eq \label{eq:marginals_union} \]
+    \end{definition}
+
+    \todo[TC]{Mention polytope perspective and existing methods}
+    \begin{definition}
+        \label{def:marginal_model}
+        A reoccurring motif of these discussions will be the set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ mentioned in \cref{def:marginal_problem}.
+In agreement with \cite{Fritz_2011} we call the set of subsets $\mscenario \defined \bc{V_1, \ldots, V_k}$ the marginal contexts or the \term{maximal marginal scenario}\footnote{Rigorously speaking as defined by \cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that $V' \in \mscenario$ whenever $V' \subseteq V_i$ for some $i \in \bs{k}$.
+``Maximal'' refers to the restriction that $\forall i,j : V_i \not \subseteq V_j$.}.
+An individual $V_i \in \mscenario$ is a \term{marginal context}.
+The union of all contexts is denoted $\jointvar$ and is defined exactly as in \cref{eq:marginals_union}.
+        Moreover, we will call the set of distributions a \term{marginal model} and denote it $\prob^{\mscenario}$ provided that they are \textit{compatible} \todo[TC]{Mention quantum non-signalling and maybe $k \geq 3$}:
+        \[ \forall i \neq j \text{ if } V_i \cap V_j \neq \emptyset \text{ then } \sum_{V_i \setminus V_j} \prob[V_i] = \sum_{V_j \setminus V_i} \prob[V_j]  \]
+        Following definition 2.3 in \cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a joint distribution $\prob[\jointvar]$ and \term{non-contextual} otherwise.
+
+        In addition, we elect to define the \term{marginal outcomes} $\Out{\mscenario}$ to be the set of all outcomes belonging to outcomes $\Out{V_i}$ of the marginal context\footnote{Here `$\coprod$' refers to the \textit{disjoint union} of outcome contexts; when $i \neq j$, $\Out{V_i} \cap \Out{V_j} = \emptyset$ since $V_i \neq V_j$.}.
+        \[ \Out{\mscenario} \defined \coprod_{i \in \bs{k}} \Out{V_i} \]
+        % By an intended abuse of notation, we say that a particular outcome is an ``element'' of $O_{\mscenario}$ if it is an element of $O_{V_i}$ for some $i \in \bs{k}$.
+        % \[ \outc{V_i} \in O_{\mscenario} \]
+        Each marginal outcome $m \in \Out{\mscenario}$ belongs to a unique marginal outcome space $\Out{V_i}$.
+To make reference to the marginal context $V_i$ associated with $m$, recall \cref{rem:domain_dist}: the context for $m$ is precisely the domain of $m$ ($V_i = \Dom{m}$).
+Note that $\Out{\mscenario}$ is a slight abuse of notation; $\Out{\mscenario}$ is \textit{not} a valid outcome space, analogous to the fact that $P^{\mscenario}$ is \textit{not} a probability distribution.
+Instead $\Out{\mscenario}$ is a \textit{flattened} collection of outcome spaces just as $P^{\mscenario}$ is a collection of distributions.
+The \term{joint outcomes} $\Out{\jointvar}$ are defined in the usual fashion of \cref{def:outcome_space}.
+    \end{definition}
+
+    \begin{definition}
+        A \term{causal compatibility inequality} $\mathcal{I}_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$.
+Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $\mathcal{I}_{\mscenario}$ will be dropped leaving just $\mathcal{I}$.
+    \end{definition}
+
+    \todo[TC]{Discuss Compatibility, connection to cooperative games/resources, bell incompatibility?}
+    \todo[TC]{Connection between contextuality and Compatibility via the marginal problem for causal parameters}
+    \todo[TC]{Discuss what is meant by a `complete' solution to the marginal problem}
+    \todo[TC]{Maybe define the possibilistic marginal problem for later}
+
+    \section{The Triangle Scenario}
+    \label{sec:triangle_scenario}
+    \begin{figure}
+    \begin{center}
+        \begin{minipage}[b]{.48\textwidth}
+            \centering
+            \scalebox{1.0}{\input{../figures/causal_structures/triangle_scenario}}
+            \caption{The casual structure of the Triangle Scenario. Three variables $A,B,C$ are observable and illustrated as triangles, while $X, Y, Z$ are latent variables illustrated as circles.}
+            \label{fig:triangle_scenario}
+        \end{minipage}\hspace{0.04\textwidth}%
+        \begin{minipage}[b]{.48\textwidth}
+            \centering
+            \scalebox{0.8}{\input{../figures/causal_structures/inflated_triangle_scenario}}
+            \caption{An inflated causal structure of the Triangle Scenario \cref{fig:triangle_scenario}.}
+            \label{fig:inflated_triangle_scenario}
+        \end{minipage}
+    \end{center}
+    \end{figure}
+
+    The triangle scenario $\ts$ is a causal structure composed of $3$ parties $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
+It has that has been studied extensively in existing literature (see \cite[Fig.
+1]{Steudel_2010}, \cite[Fig.
+6]{Chaves_2014}, \cite[Fig.
+8]{Branciard_2012}, \cite[Fig.
+8, Appendix E]{Henson_2014}, \cite[Fig.
+3]{Fritz_2012}, \cite[Fig.
+1]{Inflation}, $\ldots$) and is reproduced here in \cref{fig:triangle_scenario} for convenience.
+At the time of publication for \cite{Branciard_2012} it was noted that characterizing locality in $\ts$ remained an open problem and that identifying locality constraints in this configuration seemed challenging.
+In \cite{Henson_2014}, $\ts$ was classified as an ``interesting'' causal structure.\footnote{Indicating that conditional independence relations are not a sufficient characterization of compatibility for $\ts$ \cite{Henson_2014}.
+Note that in $\ts$ there are \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Additionally $\ts$ is presented along with a family of entropic inequalities that constrain the set of compatible distributions \cite{Henson_2014}.
+Furthermore in \cite{Fritz_2012}, Fritz demonstrated that $\ts$ is the \textit{smallest} correlation scenario in which their exists quantum incompatible distributions by explicitly mentioning one (which we elect to call the \textit{Fritz distribution} in \cref{sec:fritz_dist}) and poses an important question asking if other incompatible quantum distributions exist.
+Finally in \cite{Inflation}, Wolfe et.
+al.
+make use of $\ts$ along with the Bell Scenario to demonstrate a novel technique for causal inference called the \textit{inflation technique} (summarized in \cref{sec:summary_inflation}).
+Wolfe et.
+al.
+validate the power and applicability of the inflation technique by proving incompatibility between $\ts$ and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints \cite{Inflation}.
+Moreover, a family of polynomial, $2$-outcome, compatibility inequalities are explicitly derived for an exemplary inflation of $\ts$ and $37$ non-trivial representatives are printed in \cite{Inflation}.
+
+    Identifying quantum-accessible distributions that are incompatible with the triangle scenario is of particular importance as it \todo[TC]{Discuss why we are doing this.}
+
+    As a preliminary search for quantum incompatibility in $\ts$, we performed numerical optimizations using bipartite qubit states and $2$-outcome POVM measurements (see \cref{sec:param_quantum_states} for details) against the $37$ compatibility inequalities printed in \cite{Inflation} as well as the entropic inequalities presented by \cite{Henson_2014}.
+Unfortunately, none of these inequalities could be violated.
+These early results suggest, although do not prove, that quantum non-locality is not present in $\ts$ for \textit{two-outcome} measurements.
+We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in $\ts$ for a larger number of outcomes.
+
+    Specifically, we make use of the inflation technique for an inflated triangle scenario $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} and cast the \textit{causal compatibility} problem as a \textit{marginal problem}.
+We develop a new technique which we call the \textit{extendable covering procedure (ECP)} to find a complete solution to the marginal problem that is suitable for large causal structures where the observable nodes are equipped with numerous outcomes.
+We use this technique to find numerous compatibility inequalities, some of which witness the incompatibility of the Fritz distribution.
+Before discussing the ECP, the Fritz distribution will be re-defined explicitly here, followed by a quick summary of the inflation technique of \cite{Inflation}.
+Following these summaries of existing work, we present the ECP and its connection to Hardy-type paradoxes \cite{Inflation,Liang_2011,Mansfield_2012}, certificate inequalities and logical Bell inequalities \cite{Abramsky_2011}.
+Moreover, the ECP can be adapted to derive symmetric inequalities or inequalities bounding any subspace of marginal models.
+To conclude, we subject our found inequalities to non-linear optimizations and discuss the implications of our results.
+
+    \section{The Fritz Distribution}
+    \label{sec:fritz_dist}
+    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario \cite{Fritz_2012}.
+Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
+    \begin{align*}
+    \eq \label{eq:fritz_dist}
+    \begin{split}
+    \prob[F][111] = \prob[F][221] = \prob[F][412] = \prob[F][322] = \prob[F][233] = \prob[F][143] = \prob[F][344] = \prob[F][434] &= \f{1}{32}\br{2 + \sqrt{2}} \\
+    \prob[F][121] = \prob[F][211] = \prob[F][422] = \prob[F][312] = \prob[F][243] = \prob[F][133] = \prob[F][334] = \prob[F][444] &= \f{1}{32}\br{2 - \sqrt{2}}
+    \end{split}
+    \end{align*}
+    Here the notation $\prob[F][abc] = \prob[ABC][abc] = \prob[][A=a,B=b,C=c]$ is used. The Fritz distribution $\prob[F]$ can be realized with the following quantum configuration:
+    \begin{equation}
+    \begin{gathered}
+    \label{eq:fritz_quantum_realization}
+    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+} \\
+    M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
+    M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
+    M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
+    \end{gathered}
+    \end{equation}
+    Where for convenience of notation $\psi_x$ is used to denote the superposition,
+    \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
+    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.
+
+    Fritz first proved it's incompatibility \cite{Fritz_2012} by showing $C$ acts a moderator to ensure measurement pseudo-settings for $A$ and $B$ are independent, satisfying non-broadcasting requirements for the standard Bell scenario.
+In fact, by coarse-graining outcomes for $A$ and $B$ and treating $C$ as a measurement-setting moderator, $P_F$ maximally violates the CHSH inequality.
+To illustrate this, begin with the CHSH inequality \cite{CHSH_Original},
+    \[ \ba{AB|S_A=1, S_B=1} + \ba{AB|S_A=1, S_B=2} + \ba{AB|S_A=2, S_B=1} - \ba{AB|S_A=2, S_B=2} \leq 2 \eq \label{eq:CHSH}\]
+    Where $\ba{AB|S_A=i, S_B=j}$ is the correlation between $A$ and $B$ given the measurement settings for $A$ ($B$) is $i$ ($j$) respectively.
+Next each of $C$'s outcomes become the conditioned settings in \cref{eq:CHSH},
+    \[ \ba{AB|C=2} + \ba{AB|C=3} + \ba{AB|C=4} - \ba{AB|C=1} \leq 2 \eq \label{eq:chsh_c}\]
+    Finally, specifying the two outcome coarse-graining as $\bc{1,2,3,4} \rightarrow \bc{\br{1,4}, \br{2,3}}$ gives a definition of correlation,
+    \[ \ba{AB} \defined 2\bc{\prob[][11] + \prob[][14] + \prob[][41] + \prob[][44] + \prob[][22] + \prob[][23] + \prob[][32] + \prob[][33]} - 1 \]
+    Which when applied to the Fritz distribution \cref{eq:fritz_dist} gives the following correlations:
+    \begin{gather*}
+    \ba{AB|C=2} = 2 \bc{\f{1}{32}\bs{2\br{2+\sqrt{2}}+2\br{2-\sqrt{2}}}} - 1 = \f{\sqrt{2}}{2} \\
+    \ba{AB|C=3} = \ba{AB|C=4} = \f{\sqrt{2}}{2} \quad \ba{AB|C=1} = -\f{\sqrt{2}}{2}
+    \end{gather*}
+    Which when applied to \cref{eq:chsh_c} gives the familiar Tsirelson violation of $2\sqrt{2} \not\leq 2$ \cite{Cirelson_1980}.
+
+    Before continuing it is worth noting that \cref{eq:fritz_dist} is non-unique.
+Any distribution that is equal to \cref{eq:fritz_dist} via a permutation of outcomes or exchange of parties is also referred to as a Fritz distribution.
+Moreover, the quantum realization of \cref{eq:fritz_quantum_realization} is non-unique.
+In fact, \cref{eq:fritz_quantum_realization} is not the realization that Fritz originally had in mind.
+Nonetheless \cref{eq:fritz_dist} is taken as \textit{the} Fritz distribution for concreteness throughout this paper.
+
+    In \cite{Fritz_2012}, Fritz posits the following question: \textit{Find an example of non-classical quantum correlations in $\ts$ together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}
+
+    \todo[TC]{Summarize Problem 2.17 in fritz BBT, make it more formal}
+
+    \section{Summary of the Inflation Technique}
+    \label{sec:summary_inflation}
+    The causal inflation technique, first pioneered by Wolfe, Spekkens, and Fritz \cite{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of Ref.
+\cite{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a probability distribution is compatible or incompatible with a given causal structure.
+As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
+Copies of the original nodes are distinguished by an additional subscript called the \term{copy-index}.
+For example node $A$ of \cref{fig:triangle_scenario} has copies $A_1, A_2, A_3, A_4$ in the inflation of \cref{fig:inflated_triangle_scenario}.
+Following the notions of Ref.
+\cite{Inflation}, all such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
+A copy-index is effectively arbitrary, so $A'$ will refer to an arbitrary inflated copy of $A$.
+    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
+    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if $X = Y$ upon removal of the copy-index.
+Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
+    \begin{definition}
+        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
+        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
+    \end{definition}
+    The motivation being that since the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
+To do this, first notice that every compatible joint distribution $\prob[\nodes]$ uniquely defines a set of causal parameters for $\graph$.
+    \[ \forall n \in \nodes : \prob[n\mid \Pa[\graph]{n}] = \sum_{\nodes \setminus n} \prob[\nodes] \eq \label{eq:unique_causal_parameters}\]
+    Now since \cref{eq:inflation_defn} enforces that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$, one can create a set of \term{inflated causal parameters} using \cref{eq:unique_causal_parameters},
+    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \]
+    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course not all compatible joint distributions on $\nodes'$ are constructed in this way; all that is demonstrated is that all joint distributions constructed in this way are compatible.}.
+    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \]
+    This is known as the \term{weak inflation lemma}; compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$.
+Before generalizing to the inflation lemma, a careful observation needs to be made.
+For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$ over $N$ induces a compatible marginal distribution $\prob[N']$ over $N'$.
+In fact since $N'$ contains no duplicate nodes up to copy index (simply because $N \sim N'$ and $N$ cannot contain duplicate nodes), $\prob[N] = \prob[N']$.
+We refer such sets $N'$ as the \term{injectable sets} of $\graph'$ and $N$ the \term{images of the injectable sets} of $\graph$.
+    \begin{align*}
+        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
+        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
+    \end{align*}
+
+    \begin{lemma}
+        \label{lem:inflation}
+        \term{The Inflation Lemma} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+        This is lemma 3 of \cite{Inflation}.
+    \end{lemma}
+
+    The inflation lemma is the most important result of the causal inflation technique \cite{Inflation}.
+The contrapositive version of \cref{lem:inflation} is a powerful tool for determining compatibility.
+Any compatibility constraint on marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ of the inflated causal structure $\graph'$ correspond to valid compatibility constraints on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure.
+Corollary 5 of \cite{Inflation} proves this explicitly for incompatibility inequalities $\mathcal{I}$; which the remainder of this work focuses on.
+Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
+Therefore, in situations where latent nodes are present in $\graph$, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
+
+    In this work, we obtain inequalities that constrain the set of injectable marginal models $\bc{\prob[N'] \mid N' \in \ImInj[\graph]{\graph'}}$ for the inflated Triangle Scenario of \cref{fig:triangle_scenario} by considering the marginal problem (see \cref{sec:comp_con_mp}) for the set of \term{maximally pre-injectable sets}\footnote{The set of all pre-injectable sets forms a topological \textit{simplicial conplex}.
+`Maximal' refers to the pre-injectable sets that are no proper subset of another.}.
+A pre-injectable set $V$ is a subset of $\nodes'$ that can be decomposed into the disjoint union of injectable sets $V = \coprod_i N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ that are mutually \term{ancestrally independent},
+    \[ \forall i,j : N'_i \ancestralindep N'_j \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset  \]
+    In doing so, any distribution over all nodes of a pre-injectable set $\prob[\cup_i N'_i]$ will factorize according to graphical $d$-separation conditions \cite{Pearl_2009},
+    \[ \prob[V] = \prob[\cup_i N'_i] = \prod_{i}\prob[N'_i] \]
+    This turns linear inequalities over the pre-injectable distributions into polynomial inequalities over the injectable distributions, allowing one to replace all such distributions with equivalent distributions over the original random variables of $\nodes$.
+$\PreInj[\graph]{\graph'}$ will denote the set of all pre-injectable sets.
+
+    Focusing on the inflation $\ts'$ depicted in \cref{fig:inflated_triangle_scenario}, we obtained the injectable sets $\Inj[\ts]{\ts'}$ along with the maximally pre-injectable sets through a simple graphical procedure outlined in \cite{Inflation}.
     \begin{equation*}
@@
     \end{equation*}
-    As can be counted, there are $12$ maximally pre-injectable sets which will be indexed $1$ through $12$ in the order seen above ($\bc{V_1, \ldots, V_{12}}$)
-
-    \begin{figure}
-    \begin{center}
-        \begin{minipage}[b]{.48\textwidth}
-            \centering
-            \scalebox{1.0}{\input{../figures/causal_structures/triangle_scenario}}
-            \caption{The casual structure of the Triangle Scenario. Three variables $A,B,C$ are observable and illustrated as triangles, while $X, Y, Z$ are latent variables illustrated as circles.}
-            \label{fig:triangle_scenario}
-        \end{minipage}\hspace{0.04\textwidth}%
-        \begin{minipage}[b]{.48\textwidth}
-            \centering
-            \scalebox{0.8}{\input{../figures/causal_structures/inflated_triangle_scenario}}
-            \caption{An inflated causal structure of the Triangle Scenario \cref{fig:triangle_scenario}.}
-            \label{fig:inflated_triangle_scenario}
-        \end{minipage}
-    \end{center}
-    \end{figure}
-
-    \section{Compatibility, Contextuality and the Marginal Problem}
-    \label{sec:comp_con_mp}
-    In order to determine if a given marginal distribution $\prob[V]$ or set of marginal distributions $\bc{\prob[V_i]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ is compatible with a causal structure $\graph$, one should first formalize what is meant by \textit{compatible}.
-
-    \begin{definition}
-        A set of \term{causal parameters} for a particular causal structure $\graph$ is the specification of a conditional distribution for every node $n \in \nodes$ given it's parents in $\graph$.
-        \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
-    \end{definition}
-    \begin{definition}
-        \label{def:compatible}
-        A marginal distribution $\prob[V]$ is \term{compatible} with a causal structure $\graph$ (where it is assumed that $V \subseteq \nodes_O$) if there exists a \textit{choice} of causal parameters $\bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes}$ such that $\prob[V]$ can be \textit{recovered} from the following series of operations:
-        \begin{enumerate}
-            \item First obtain a joint distribution over \textit{all} nodes of of the causal structure,
-            \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] \]
-            \item Then marginalize over the latent nodes of $\graph$,
-            \[ \prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes] \]
-            \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$,
-            \[ \prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O] \]
-        \end{enumerate}
-        A set of marginal distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}}$ is compatible with $\graph$ if each distribution $\prob[V_{i}]$ can be made compatible by the \textit{same} choice of causal parameters.
-        A distribution $\prob[V]$ or set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}}$ is said to be \term{incompatible} with a causal structure if there \textit{does not exist} a set of causal parameters with the above mentioned property.
-
-        \todo[TC]{Source this?}
-    \end{definition}
-    Operations 2 and 3 of \cref{def:compatible} are related to the \textit{marginal problem}.
-    \begin{definition}
-        \label{def:marginal_problem}
-        \term{The Marginal Problem:} Given a set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ where $V_i \subseteq \jointvar$ for some set of random variables $\jointvar$, does there exist a joint distribution $\prob[\jointvar]$ such that each given distribution $\prob[V_i]$ can be obtained from marginalizing $\prob[\jointvar]$?
-        \[ \forall i \in \bs{k} : \prob[V_i] = \sum_{\jointvar \setminus V_i} \prob[\jointvar] \]
-        Typically (although not strictly necessary\footnote{Appending any additional variables to $\jointvar$ will not affect the existence of a joint distribution.}), $\jointvar$ is taken to mean the union of all $V_i$'s.
-        \[ \jointvar = V_1 \cup \cdots \cup V_k = \bigcup_{i\in\bs{k}} V_i \eq \label{eq:marginals_union} \]
-    \end{definition}
-
-    \todo[TC]{Mention polytope perspective and existing methods}
-    \begin{definition}
-        \label{def:marginal_model}
-        A reoccurring motif of these discussions will be the set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ mentioned in \cref{def:marginal_problem}.
-In agreement with \cite{Fritz_2011} we call the set of subsets $\mscenario \defined \bc{V_1, \ldots, V_k}$ the marginal contexts or the \term{maximal marginal scenario}\footnote{Rigorously speaking as defined by \cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that $V' \in \mscenario$ whenever $V' \subseteq V_i$ for some $i \in \bs{k}$.
-``Maximal'' refers to the restriction that $\forall i,j : V_i \not \subseteq V_j$.}.
-An individual $V_i \in \mscenario$ is a \term{marginal context}.
-The union of all contexts is denoted $\jointvar$ and is defined exactly as in \cref{eq:marginals_union}.
-        Moreover, we will call the set of distributions a \term{marginal model} and denote it $\prob^{\mscenario}$ provided that they are \textit{compatible} \todo[TC]{Mention quantum non-signalling and maybe $k \geq 3$}:
-        \[ \forall i \neq j \text{ if } V_i \cap V_j \neq \emptyset \text{ then } \sum_{V_i \setminus V_j} \prob[V_i] = \sum_{V_j \setminus V_i} \prob[V_j]  \]
-        Following definition 2.3 in \cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a joint distribution $\prob[\jointvar]$ and \term{non-contextual} otherwise.
-
-        In addition, we elect to define the \term{marginal outcomes} $\Out{\mscenario}$ to be the set of all outcomes belonging to outcomes $\Out{V_i}$ of the marginal context\footnote{Here `$\coprod$' refers to the \textit{disjoint union} of outcome contexts; when $i \neq j$, $\Out{V_i} \cap \Out{V_j} = \emptyset$ since $V_i \neq V_j$.}.
-        \[ \Out{\mscenario} \defined \coprod_{i \in \bs{k}} \Out{V_i} \]
-        % By an intended abuse of notation, we say that a particular outcome is an ``element'' of $O_{\mscenario}$ if it is an element of $O_{V_i}$ for some $i \in \bs{k}$.
-        % \[ \outc{V_i} \in O_{\mscenario} \]
-        Each marginal outcome $m \in \Out{\mscenario}$ belongs to a unique marginal outcome space $\Out{V_i}$.
-To make reference to the marginal context $V_i$ associated with $m$, recall \cref{rem:domain_dist}: the context for $m$ is precisely the domain of $m$ ($V_i = \Dom{m}$).
-Note that $\Out{\mscenario}$ is a slight abuse of notation; $\Out{\mscenario}$ is \textit{not} a valid outcome space, analogous to the fact that $P^{\mscenario}$ is \textit{not} a probability distribution.
-Instead $\Out{\mscenario}$ is a \textit{flattened} collection of outcome spaces just as $P^{\mscenario}$ is a collection of distributions.
-The \term{joint outcomes} $\Out{\jointvar}$ are defined in the usual fashion of \cref{def:outcome_space}.
-    \end{definition}
-
-    \begin{definition}
-        A \term{causal compatibility inequality} $\mathcal{I}_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$.
-Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $\mathcal{I}_{\mscenario}$ will be dropped leaving just $\mathcal{I}$.
-    \end{definition}
-    \todo[TC]{Discuss Compatibility, connection to cooperative games/resources, bell incompatibility?}
-    \todo[TC]{Connection between contextuality and Compatibility via the marginal problem for causal parameters}
-    \todo[TC]{Discuss what is meant by a `complete' solution to the marginal problem}
-    \todo[TC]{Maybe define the possibilistic marginal problem for later}
-    \section{Summary of the Inflation Technique}
-    \label{sec:summary_inflation}
-    The causal inflation technique, first pioneered by Wolfe, Spekkens, and Fritz \cite{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of Ref.
-\cite{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a probability distribution is compatible or incompatible with a given causal structure.
-As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
-Copies of the original nodes are distinguished by an additional subscript called the \term{copy-index}.
-For example node $A$ of \cref{fig:triangle_scenario} has copies $A_1, A_2, A_3, A_4$ in the inflation of \cref{fig:inflated_triangle_scenario}.
-Following the notions of Ref.
-\cite{Inflation}, all such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
-A copy-index is effectively arbitrary, so $A'$ will refer to an arbitrary inflated copy of $A$.
-    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
-    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if $X = Y$ upon removal of the copy-index.
-Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
-    \begin{definition}
-        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
-        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
-    \end{definition}
-    The motivation being that since the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
-To do this, first notice that every compatible joint distribution $\prob[\nodes]$ uniquely defines a set of causal parameters for $\graph$.
-    \[ \forall n \in \nodes : \prob[n\mid \Pa[\graph]{n}] = \sum_{\nodes \setminus n} \prob[\nodes] \eq \label{eq:unique_causal_parameters}\]
-    Now since \cref{eq:inflation_defn} enforces that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$, one can create a set of \term{inflated causal parameters} using \cref{eq:unique_causal_parameters},
-    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \]
-    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course not all compatible joint distributions on $\nodes'$ are constructed in this way; all that is demonstrated is that all joint distributions constructed in this way are compatible.}.
-    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \]
-    This is known as the \term{weak inflation lemma}; compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$.
-Before generalizing to the inflation lemma, a careful observation needs to be made.
-For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$ over $N$ induces a compatible marginal distribution $\prob[N']$ over $N'$.
-In fact since $N'$ contains no duplicate nodes up to copy index (simply because $N \sim N'$ and $N$ cannot contain duplicate nodes), $\prob[N] = \prob[N']$.
-We refer such sets $N'$ as the \term{injectable sets} of $\graph'$ and $N$ the \term{images of the injectable sets} of $\graph$.
-    \begin{align*}
-        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
-        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
-    \end{align*}
-
-    \begin{lemma}
-        \label{lem:inflation}
-        \term{The Inflation Lemma} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-        This is lemma 3 of \cite{Inflation}.
-    \end{lemma}
-
-    The inflation lemma is the most important result of the causal inflation technique \cite{Inflation}.
-The contrapositive version of \cref{lem:inflation} is a powerful tool for determining compatibility.
-Any compatibility constraint on marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ of the inflated causal structure $\graph'$ correspond to valid compatibility constraints on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure.
-Corollary 5 of \cite{Inflation} proves this explicitly for incompatibility inequalities $\mathcal{I}$; which the remainder of this work focuses on.
-Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
-Therefore, in situations where latent nodes are present in $\graph$, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
-
-    In this work, we obtain inequalities that constrain the set of injectable marginal models $\bc{\prob[N'] \mid N' \in \ImInj[\graph]{\graph'}}$ for the inflated Triangle Scenario of \cref{fig:triangle_scenario} by considering the marginal problem (see \cref{sec:comp_con_mp}) for the set of \term{maximally pre-injectable sets}\footnote{The set of all pre-injectable sets forms a topological \textit{simplicial conplex}.
-`Maximal' refers to the pre-injectable sets that are no proper subset of another.}.
-As defined by \cite{Inflation}, a pre-injectable set $V$ is a subset of $\nodes'$ that can be written as the decomposed into the union of injectable sets $V = \bigcup_i N'_i$ where $\bc{N'_i \in \Inj[\graph]{\graph'}}$ that are mutually \term{ancestrally independent},
-    \[ \forall i,j : N'_i \ancestralindep N'_j \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset  \]
-    In doing so, any distribution over all nodes of a pre-injectable set $\prob[\cup_i N'_i]$ will factorize according to graphical $d$-separation conditions \cite{Pearl_2009},
-    \[ \prob[V] = \prob[\cup_i N'_i] = \prod_{i}\prob[N'_i] \]
-    This turns linear inequalities over the pre-injectable distributions into polynomial inequalities over the injectable distributions, allowing one to replace all such distributions with equivalent distributions over the original random variables of $\nodes$.
-$\PreInj[\graph]{\graph'}$ will denote the set of all pre-injectable sets.
-
-    \section{The Fritz Distribution}
-    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario.
-Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
-    \begin{align*}
-    \eq \label{eq:fritz_dist}
-    \begin{split}
-    \prob[F][111] = \prob[F][221] = \prob[F][412] = \prob[F][322] = \prob[F][233] = \prob[F][143] = \prob[F][344] = \prob[F][434] &= \f{1}{32}\br{2 + \sqrt{2}} \\
-    \prob[F][121] = \prob[F][211] = \prob[F][422] = \prob[F][312] = \prob[F][243] = \prob[F][133] = \prob[F][334] = \prob[F][444] &= \f{1}{32}\br{2 - \sqrt{2}}
-    \end{split}
-    \end{align*}
-    Here the notation $\prob[F][abc] = \prob[ABC][abc] = \prob[][A=a,B=b,C=c]$ is used. The Fritz distribution $\prob[F]$ can be realized with the following quantum configuration:
-    \begin{equation}
-    \begin{gathered}
-    \label{eq:fritz_quantum_realization}
-    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+} \\
-    M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
-    M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
-    M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
-    \end{gathered}
-    \end{equation}
-    Where for convenience of notation $\psi_x$ is used to denote the superposition,
-    \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
-    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.
-    Fritz first proved it's incompatibility \cite{Fritz_2012} by showing $C$ acts a moderator to ensure measurement pseudo-settings for $A$ and $B$ are independent, satisfying non-broadcasting requirements for the standard Bell scenario.
-In fact, by coarse-graining outcomes for $A$ and $B$ and treating $C$ as a measurement-setting moderator, $P_F$ maximally violates the CHSH inequality.
-To illustrate this, begin with the CHSH inequality \cite{CHSH_Original},
-    \[ \ba{AB|S_A=1, S_B=1} + \ba{AB|S_A=1, S_B=2} + \ba{AB|S_A=2, S_B=1} - \ba{AB|S_A=2, S_B=2} \leq 2 \eq \label{eq:CHSH}\]
-    Where $\ba{AB|S_A=i, S_B=j}$ is the correlation between $A$ and $B$ given the measurement settings for $A$ ($B$) is $i$ ($j$) respectively.
-Next each of $C$'s outcomes become the conditioned settings in \cref{eq:CHSH},
-    \[ \ba{AB|C=2} + \ba{AB|C=3} + \ba{AB|C=4} - \ba{AB|C=1} \leq 2 \eq \label{eq:chsh_c}\]
-    Finally, specifying the two outcome coarse-graining as $\bc{1,2,3,4} \rightarrow \bc{\br{1,4}, \br{2,3}}$ gives a definition of correlation,
-    \[ \ba{AB} \defined 2\bc{\prob[][11] + \prob[][14] + \prob[][41] + \prob[][44] + \prob[][22] + \prob[][23] + \prob[][32] + \prob[][33]} - 1 \]
-    Which when applied to the Fritz distribution \cref{eq:fritz_dist} gives the following correlations:
-    \begin{gather*}
-    \ba{AB|C=2} = 2 \bc{\f{1}{32}\bs{2\br{2+\sqrt{2}}+2\br{2-\sqrt{2}}}} - 1 = \f{\sqrt{2}}{2} \\
-    \ba{AB|C=3} = \ba{AB|C=4} = \f{\sqrt{2}}{2} \quad \ba{AB|C=1} = -\f{\sqrt{2}}{2}
-    \end{gather*}
-    Which when applied to \cref{eq:chsh_c} gives the familiar Tsirelson violation of $2\sqrt{2} \not\leq 2$ \cite{Cirelson_1980}.
-
-    Before continuing it is worth noting that \cref{eq:fritz_dist} is non-unique.
-Any distribution that is equal to \cref{eq:fritz_dist} via a permutation of outcomes or exchange of parties is also referred to as a Fritz distribution.
-Moreover, the quantum realization of \cref{eq:fritz_quantum_realization} is non-unique.
-In fact, \cref{eq:fritz_quantum_realization} is not the realization that Fritz originally had in mind.
-Nonetheless \cref{eq:fritz_dist} is taken as \textit{the} Fritz distribution for concreteness throughout this paper.
-
-    \todo[TC]{Summarize Problem 2.17 in fritz BBT, make it more formal}
+    As can be counted, there are $12$ maximally pre-injectable sets $\ts'$ which will be indexed $1$ through $12$ in the order seen above ($\bc{V_1, \ldots, V_{12}}$).
+The maximally pre-injectable sets $\bc{V_i}_{i \in \bs{12}}$ form a maximal marginal scenario $\mscenario$ over the observable nodes of $\ts'$ when equipped with outcome labels.
+Using \cref{lem:inflation} inequalities $\mathcal{I}_{\PreInj[\ts]{\ts'}}$ constraining the set of contextual marginal models $\prob^{\mscenario}$ can be deflated into polynomial inequalities over $\mathcal{I}_{\ImInj[\ts]{\ts'}}$ bounding compatible marginal models over the images of the injectable sets in $\ts$.
+    \[ \ImInj[\ts]{\ts'} = \bc{\bc{A, B, C}, \bc{A}, \bc{B}, \bc{C}} \]
+
     \section{Certificate Inequalities}
@@
 The entries of $M$ are populated whenever a row index is extendable to a column index.
-        \[ M\bs{m, j} = \begin{cases}
+        \[ M\bs{m, j} = \de_{m \ext j} \defined \begin{cases}
             1 & m \ext j \\
@@
         \end{cases} \]
-        The incidence matrix has $\abs{\Out{\jointvar}}$ columns and $\abs{\Out{\mscenario}} = \sum_{i\in \bs{k}} \abs{\Out{V_i}}$ rows. The number of non-zero entries of $M$ is a simple expression,
+        Where $\de_{m \ext j}$ is an \textit{extendability indicator}.
+The incidence matrix has $\abs{\Out{\jointvar}}$ columns and $\abs{\Out{\mscenario}} = \sum_{i\in \bs{k}} \abs{\Out{V_i}}$ rows.
+The number of non-zero entries of $M$ is a simple expression,
         \[ \sum_{i\in\bs{k}} \abs{\Out{V_i}}\abs{\Out{\jointvar \setminus V_i}} = \sum_{i\in \bs{k}} \abs{\Out{\jointvar}} = k\abs{\Out{\jointvar}} \]
@@
     \begin{example}
-        Suppose one has $4$ binary random variables $\jointvar = \bc{a,b,c}$ in mind and $2$ contexts $\mscenario = \bc{\bc{a,c}, \bc{b}}$. Then the incidence matrix is:
+        \label{ex:marginal_matrix}
+        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and consider the marginal scenario $\mscenario = \bc{\bc{a,c}, \bc{b}}$. The incidence matrix becomes:
         \[ M = \kbordermatrix{
-            (a,b,c) = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
-            (a=0, c=0) & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-            (a=0, c=1) & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 \\
-            (a=1, c=0) & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 \\
-            (a=1, c=1) & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 1 \\
-            (b=0)      & 1 & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
-            (b=1)      & 0 & 0 & 1 & 1 & 0 & 0 & 1 & 1
+            (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
+            (a\mapsto0, c\mapsto0) & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+            (a\mapsto0, c\mapsto1) & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 \\
+            (a\mapsto1, c\mapsto0) & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 \\
+            (a\mapsto1, c\mapsto1) & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 1 \\
+            (b\mapsto0)            & 1 & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
+            (b\mapsto1)            & 0 & 0 & 1 & 1 & 0 & 0 & 1 & 1
         } \]
@@
 
-    In order to describe how marginalization can be written as matrix multiplication $M \cdot x = b$, we need to describe how to define two more quantities:
+    \begin{example}
+        The marginal problem for the inflated causal structure $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} concerns itself with the pre-injectable marginal scenario $\mscenario = \PreInj[\ts]{\ts'} = \bc{V_1, \ldots, V_{12}}$.
+Equipping the observed nodes of $\ts'$ with $4$-element outcome labels, the incidence matrix $M$ has $16,896$ rows and $16,777,216$ columns.
+        \begin{align*}
+            &\text{\# Rows} = \abs{\Out{\mscenario}} = \sum_{i=1}^{12} \abs{\Out{V_i}} = \sum_{i=1}^{12} 4^{\abs{V_i}} = 4 \cdot 4^6 + 8 \cdot 4^3 = 16,896 \\
+            &\text{\# Columns} = \abs{\Out{\jointvar}} = 4^{\abs{\jointvar}} = 4^{12} = 16,777,216
+        \end{align*}
+        With $12 \cdot 4^{12} = 201,326,592$ non-zero entries. For obvious reasons, no attempt is made to reproduce it here.
+    \end{example}
+
+    In order to describe how marginalization can be written as matrix multiplication $M \cdot x = b$, two more quantities need to be described:
 
@@
     \[ \probvec^{\mscenario} = M \cdot \probvec[\jointvar] \eq \label{eq:marginal_problem_matrix} \]
-    \todo[TC]{Discuss non-unique but consistent ordering of $M$, $\probvec[\jointvar]$ and $\probvec^{\mscenario}$}
+
+    \begin{remark}
+        The particular ordering of the rows and columns of $M$ carries no importance, but it \textit{must} be consistent between $M$, $\probvec[\jointvar]$ and $\probvec^{\mscenario}$.
+Throughout this work, a \textit{canonical ordering} is used: the marginal contexts are written in the same order as listed in the marginal scenario $\mscenario$ and outcomes within a marginal context are enumerated in a \textit{raveling} order; exemplified in \cref{ex:marginal_matrix}.
+    \end{remark}
 
@@
 
-    \begin{definition} An \term{infeasibility certificate} is any vector $y$ that satisfies the constraints of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
+    \begin{definition} An \term{infeasibility certificate} \cite{Andersen_2001} is any vector $y$ that satisfies the constraints of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
     \[ y \in \R^{\abs{\Out{\mscenario}}} : y \cdot M \succeq 0, \quad y \cdot \probvec^{\mscenario} < 0 \]
@@
     \todo[TC]{Discuss Infeasibility Certificates basis}
-
-    \begin{example}
-        The marginal problem for the inflated causal structure $\graph'$ depicted in \cref{fig:inflated_triangle_scenario} concerns itself with the pre-injectable marginal scenario $\mscenario = \PreInj[\graph]{\graph'} = \bc{V_1, \ldots, V_{12}}$.
-The incidence matrix $M$ has $16,896$ rows and $16,777,216$ columns.
+    \todo[TC]{Discuss the certificate inequalities we found.}
+
+    \[ \mathcal{I}\tsb{Mosek-Cert}, \mathcal{I}\tsb{Cert} \]
+
+    \section{Covering Inequalities}
+
+    Section \ref{sec:certificate_inequalities} discusses how one can obtain a valid compatibility inequality that witnesses incompatibility for a particular marginal model $\prob^{\mscenario}$ by writing the marginal problem as a linear program.
+It was demonstrated that every incompatible distribution is witness-able by some certificate inequality.
+However, when a particular marginal model $\prob^{\mscenario}$ is not known, a linear optimization offers no utility.
+    \todo[TC]{Motivate why certificates are not enough, want many solutions, want logical foundation}
+    % Throughout this section, there will be a few omissions of notation to help clar
+
+    In this section, we will first summarize a method that can be used to obtain a complete solution to the \textit{possibilistic} marginal problem and indirectly offer a \textit{partial} solution to the \textit{probabilistic} marginal problem.
+Doing so corresponds to enumerating all
+    \subsection{Logical Covers}
+    In this section, we summarize the familiar notion of a logical cover
+    % \begin{lemma}
+    %     \label{lemma:logical_extenable_set}
+    %     Let $m \in \Out{\mscenario}$ be some marginal outcome of the marginal scenario $\mscenario$.
+If any marginal model $\prob^{\mscenario}$ is to be non-contextual, the following condition must hold.
+    %     \[ m \iff \bigvee_{j \in \Ext[\jointvar]{m}} j \]
+    %     The idea being that if a joint distribution exists, then the event $m$ represents partial knowledge of the entire system $\jointvar$; whenever $m$ occurs, exactly one of the extendable joint outcomes has to have occurred.
+    % \end{lemma}
+    Suppose one has a particular marginal outcome $a \in \Out{\mscenario}$ and a marginal model $\prob^{\mscenario}$ that assigns the probability $\prob[][a]$ to the outcome $a$.
+If the marginal model $\prob^{\mscenario}$ is to admit a joint distribution $\prob[\jointvar]$, then it must be that $\prob[][a]$ is equal to a marginalization over $a$'s extendable set into $\jointvar$.
+    \[ \prob[][a] = \sum_{j \in \Ext[\jointvar]{a}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_a}\]
+    This corresponds to row $a$ of the incidence matrix $M$.
+Next consider a subset of marginal outcomes $C \subseteq \Out{\mscenario}$.
+Summing over the associated probabilities $\bc{\prob[][c]}_{c \in C}$ and applying \cref{eq:marginal_extendable_sum_a} yields,
+    \[ \sum_{c \in C}\prob[][c] = \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_cs} \]
+    If for all joint distributions $\prob[\jointvar]$ it can be demonstrated that the following holds,
+    \[ \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\prob[\jointvar][j] \geq \sum_{j \in \Ext[\jointvar]{a}}\prob[\jointvar][j] \eq \label{eq:extendable_cover_first} \]
+    Then combining \cref{eq:marginal_extendable_sum_a,eq:marginal_extendable_sum_cs,eq:extendable_cover_first} yields a valid compatibility inequality for $\mscenario$.
+    \[ \prob[][a] \leq \sum_{c \in C}\prob[][c] \eq \label{eq:1ncover} \]
+    In order for \cref{eq:extendable_cover_first} to hold for \textit{all} joint distributions $\prob[\jointvar]$, it must hold on an algebraic level; each term on the right-hand side of \cref{eq:extendable_cover_first} also appears on the left-hand side of \cref{eq:extendable_cover_first}.\footnote{If there were a joint outcome $j^*$ present on the right-hand side of \cref{eq:extendable_cover_first} but not the left, then \cref{eq:extendable_cover_first} would be violated by the deterministic distribution $\prob[\jointvar][j^*] = 1$} Therefore, identifying all compatibility inequalities that can be written in the form of \cref{eq:1ncover} corresponds to identifying all sets $C \subseteq \Out{\mscenario}$ such that their joint distribution terms algebraically \textit{cover} the joint distribution terms for $a \in \Out{\mscenario}$.
+
+    The notion of forming a
+
+    \subsection{Extendable Covers}
+    We will now generalize the notion of a logical cover by considering more exotic antecedents corresponding to multiple marginal outcomes $A \subseteq \Out{\mscenario}$ along with weights $\mul{A}$ for each outcome.
+Afterwards we demonstrate that these generalized covers also admit non-trivial probabilistic compatibility inequalities.
+
+    \begin{definition}
+        A \term{multiplicity set} or \term{m-set} $\mul{S}$ for a marginal scenario $\mscenario$ is a function $\mul{S} : \Out{\mscenario} \to \Z_{\geq 0}$ that assigns to each marginal outcome $m \in \Out{\mscenario}$ a \textit{multiplicity} $\mul{S}\br{m} \in \Z_{\geq 0}$.
+The subscript $S$ is a subset of marginal outcome $S \subseteq \Out{\mscenario}$ indicating which marginal outcomes receive non-zero multiplicity.
+        \[ \forall s \in S : \mul{S}\br{s} \in \N  \quad \forall m \in \Out{\mscenario}\setminus S : \mul{S}\br{m} = 0 \]
+        We define the \term{extension of an m-set} $\mul{S}$ into $\jointvar$ to be the m-set $\mul{\mext{S}}$ which assigns multiplicities to \textit{joint} outcomes $j \in \Out{\jointvar}$.
+The extension of $S$ denoted $\mext{S}$ is the set of all joint outcomes that are extensions of marginal outcomes $s \in S$.
+        \[ \mext{S} = \bigcup_{s \in S} \Ext[\jointvar]{s} \]
+        While the multiplicity of each element $j \in \mext{S}$ corresponds to the sum over multiplicities $\mul{S}\br{s}$ where $j \in \Ext[\jointvar]{s}$.
+        \[ \forall j \in \mext{S} : \mul{\mext{S}}\br{j} = \sum_{s \in S} \mul{S}\br{s} \isext{s}{j} \eq \label{eq:joint_multiplicity}\]
+        With all other joint outcomes receiving a zero multiplicity $\forall j \not\in \mext{S} : \mul{\mext{S}}\br{j} = 0$.
+    \end{definition}
+    \begin{definition}
+        An m-set $\mul{C}$ is an \term{extendable cover} of an m-set $\mul{A}$ for a marginal scenario $\mscenario$ if and only if the following two conditions hold\footnote{In fact \cref{eq:multi_extenable_cover_def} implies \cref{eq:flat_extenable_cover_def} since $\forall j \not \in \mext{A} : \mul{\mext{A}}\br{j} = 0$.}:
+        \begin{gather*}
+            E_A \subseteq E_C \eq \label{eq:flat_extenable_cover_def}\\
+            \forall j \in E_A : \mul{\mext{A}}\br{j} \leq \mul{\mext{C}}\br{j} \eq \label{eq:multi_extenable_cover_def}
+        \end{gather*}
+    \end{definition}
+    Identifying extendable covers is of great importance because of the following theorem.
+    \begin{theorem}
+        If the m-set $\mul{C}$ is an extendable cover of the m-set $\mul{A}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $\mathcal{I}_{\mscenario}$ for the marginal scenario $\mscenario$.
+        \[ \sum_{a \in A}\mul{A}\br{a}\prob[][a] \leq \sum_{c \in C}\mul{C}\br{c}\prob[][c] \eq \label{eq:extendable_cover} \]
+    \end{theorem}
+    \begin{proof}
+        To prove that \cref{eq:extendable_cover} is a valid compatibility inequality $\mathcal{I}_{\mscenario}$ for all marginal models $\prob^\mscenario$, we will demonstrate that \cref{eq:extendable_cover} follows from the assumption that a joint distribution $\prob[\jointvar]$ exists.
+
+        For each m-set $\mul{S}$ write the weighted sum over the probabilities $\bc{\prob[][s]}_{s \in S}$ in terms of the joint distribution $\prob[\jointvar]$ using \cref{eq:joint_multiplicity}.
         \begin{align*}
-            &\text{\# Rows} = \abs{\Out{\mscenario}} = \sum_{i=1}^{12} \abs{\Out{V_i}} = \sum_{i=1}^{12} 4^{\abs{V_i}} = 4 \cdot 4^6 + 8 \cdot 4^3 = 16,896 \\
-            &\text{\# Columns} = \abs{O_{\nodes'}} = 4^{\abs{\nodes'}} = 4^{12} = 16,777,216
+        \eq \label{eq:derivation_cover}
+        \begin{split}
+        \sum_{s \in S} \mul{S}\br{s}\prob[][s] &= \sum_{s \in S} \mul{S} \br{s} \sum_{j \in \Ext[\jointvar]{s}} \prob[\jointvar][j] \\
+        &= \sum_{s \in S} \mul{S} \br{s} \sum_{j \in \Out{\jointvar}} \isext{s}{j} \prob[\jointvar][j] \\
+        &=  \sum_{j \in \Out{\jointvar}} \bs{\sum_{s \in S} \mul{S} \br{s} \isext{s}{j}} \prob[\jointvar][j] \\
+        &= \sum_{j \in E_{S}} \mul{\mext{S}}\br{j} \prob[\jointvar][j]
+        \end{split}
         \end{align*}
-        With $12 \cdot 4^{12} = 201,326,592$ non-zero entries.
-    \end{example}
-
-    \todo[TC]{Discuss the certificate inequalities we found.}
-
-    \[ \mathcal{I}\tsb{Mosek-Cert}, \mathcal{I}\tsb{Cert} \]
-
-    \section{Covering Inequalities}
-
-    Section \ref{sec:certificate_inequalities} discusses how one can obtain a valid compatibility inequality that witnesses incompatibility for a particular marginal model $\prob^{\mscenario}$ by writing the marginal problem as a linear program.
-    \todo[TC]{Motivate why certificates are not enough, want many solutions, want logical foundation}
+        First examine the substitution $S \to C$,
+        \[ \sum_{c \in C} \mul{C}\br{c}\prob[][c] = \sum_{j \in E_{C}} \mul{\mext{C}}\br{j} \prob[\jointvar][j] \]
+        By \cref{eq:flat_extenable_cover_def} $E_A \subseteq E_C$,
+        \[ \sum_{c \in C} \mul{C}\br{c}\prob[][c] = \sum_{j \in E_{A}} \mul{\mext{C}}\br{j} \prob[\jointvar][j] + \sum_{j \in E_{C} \setminus E_{A}} \mul{\mext{C}}\br{j} \prob[\jointvar][j] \]
+        Notice that the sum over $j \in E_{C} \setminus E_{A}$ is entirely positive since $\mul{\mext{C}}\br{j} \in \N$ and $\prob[\jointvar][j] \geq 0$.
+Moreover \cref{eq:multi_extenable_cover_def} gives $\mul{\mext{C}}\br{j} \geq \mul{\mext{A}}\br{j}$.
+Combining these observations along with \cref{eq:derivation_cover} for $S \to A$, one arrives at the inequality,
+        \[ \sum_{c \in C} \mul{C}\br{c}\prob[][c] \geq \sum_{j \in E_{A}} \mul{\mext{A}}\br{j} \prob[\jointvar][j] = \sum_{a \in A} \mul{A}\br{a}\prob[][a] \]
+        Which is equivalent to \cref{eq:extendable_cover}; every non-contextual marginal model $\prob^{\mscenario}$ must satisfy \cref{eq:extendable_cover}.
+    \end{proof}
+    % \begin{corollary}
+    %     If the m-set $\mul{C}$ is an extendable cover of the m-set $\br{A, \mulA}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $\mathcal{I}_{\mscenario}$ for the marginal scenario $\mscenario$.
+    %     \[ \sum_{a \in A}\prob[][a] \leq \sum_{c \in C}\prob[][c] \eq \label{eq:extendable_cover_flat} \]
+    % \end{corollary}
+    % \begin{proof}
+    %     This follows from the fact that if $\mul{C}$ is an extendable cover of $\br{A, \mulA}$, then $\br{C, \mathbf{1}_{C}}$ is an extendable cover of $\br{A, \mathbf{1}_{A}}$.
+Since $E_A \subseteq E_C$ is already trivially satisfied, all that remains is to demonstrate that \cref{eq:multi_extenable_cover_def} holds for unitary multiplicities $\mathbf{1}_A$ and $\mathbf{1}_C$.
+
+    %     First examine extension $\br{E_C, \mul{\mext{C}}}$ for the m-set $\mul{C}$ as defined by \cref{eq:joint_multiplicity},
+    %     \[ \forall j \in E_C : \mul{\mext{C}}\br{j} = \sum_{c \in C} \mulC\br{c} \isext{c}{j} \]
+
+    %     First apply \cref{lemma:logical_extenable_set} to an arbitrary set $S \in \bc{A, C}$,
+    %     \[ \bigvee_{s \in S} s \iff \bigvee_{s \in S} \bigvee_{j \in \Ext[\jointvar]{s}} j \iff \bigvee_{j \in E_S} j \eq \label{eq:logical_iff_ext}\]
+    %     Now since $E_A \subseteq E_C$ by \cref{eq:flat_extenable_cover_def} we have that,
+    %     \[ \bigvee_{j \in E_A} j \implies \bigvee_{j \in E_C} j \eq \label{eq:logical_cover}\]
+    %     Combining \cref{eq:logical_iff_ext,eq:logical_cover} one arrives at,
+    %     \[ \bigvee_{a \in A} a \implies \bigvee_{c \in C}c \]
+    % \end{proof}
+    % For a working example, let $\jointvar = \bc{a, b, c}$ be a set of binary random variables ($O = \bc{0,1}$) and $\mscenario = \bc{\bc{a,b},\bc{b,c},\bc{a,c}}$ be the marginal context.
+
+    \subsection{Complete Solution to The Marginal Problem}
+    \begin{theorem}
+        \label{thm:complete_solution_ext_cover}
+    \end{theorem}
+    \subsection{Extendable Cover Procedure}
+    The \term{extendable cover procedure} begins with an antecedent m-set $\mul{A}$ and iteratively produces consequent m-sets $\mul{C}$ that are extendable covers of $\mul{A}$.
+To facilitate this, we define a \term{partial consequent m-set} to be any marginal m-set $\mul{S}$ that \textit{has yet to} become an extendable cover of $\mul{A}$.
+Also define the null m-set $\mul{\emptyset}$ to be the m-set assigning zero multiplicity to each marginal outcome.
+
+    \begin{algorithm}[H]
+    \caption{The Extendable Cover Procedure (ECP)}
+    \label{alg:ecp}
+    \begin{algorithmic}
+      \State $\mul{S}^{0} = \mul{\emptyset}$
+    \end{algorithmic}
+    \end{algorithm}
+
+    % \begin{algorithm}
+    %   \caption{The Extendable Cover Procedure (ECP)
+    %     \label{alg:ecp}}
+    %   \begin{algorithmic}[1]
+    %     \Require{An antecedent m-set $\mul{A}$ and a partial consequent m-set $\mul{S}$.}
+    %     \Statex
+    %     \Function{ECP}{$\mul{A}, \mul{S}$}
+    %       % \Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
+    %       % \Let{$\delta$}{$0$}
+    %       % \For{$i \gets 1 \textrm{ to } n$}
+    %       %   \If{$z_i \neq 0$}
+    %       %     \Let{$\delta$}{$\delta + 1$}
+    %       %   \EndIf
+    %       % \EndFor
+    %       \State \Return{$\delta$}
+    %     \EndFunction
+    %   \end{algorithmic}
+    % \end{algorithm}
+
+    \todo[TC]{Trivial nodes}
+    \todo[TC]{Duplication under Deflation}
+    \todo[TC]{Memory}
+    \todo[TC]{Parallelization}
+    \todo[TC]{Simplicial Complex}
+    \subsubsection{Optimizations}
+
+    \subsubsection{Avoiding Trivial Inequalities}
+    A \term{trivial compatibility inequality} $\mathcal{I}_{\mscenario}$ is an inequality that is satisfied by all marginal models $\prob^{\mscenario}$, not just compatible ones.
+Trivial compatibility inequalities are of no importance Since the set of all extendable cover inequalities
+    \todo[TC]{}
+    \subsection{}
+    \subsection{Irreducible Covers}
+    \todo[TC]{Basis certificates}
+    \subsection{Limited Factorization}
+
     \subsection{Logical Implications \& Inequalities}
@@
     \section{Open Questions \& Future Work}
+    The marginal problem has be well studied in various contexts \cite[\ldots]{Vorobev_1962,Inflation,Fritz_2011}.
+Reference \cite{Fritz_2011} contains an excellent summary of its connection to other fields of research including knowledge integration, database theory and coalition games in game theory.
     \todo[TC]{Lots of stuff}
@@
     \section{Parametrization of Quantum States \& Measurements}
+    \label{sec:param_quantum_states}
     Throughout \cref{sec:optimizations}, we utilize a variety of parameterizations of quantum states and measurements in order to generate quantum-accessible probability distributions.

### 2016-09-07 document/main.tex
More work on the extension covering procedure, changed notation again

@@
 
-\usepackage{silence}
-\WarningFilter{revtex4-1}{Repair the float}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
+% \usepackage{silence}
+% \WarningFilter{revtex4-1}{Repair the float}
+% \usepackage{algorithm}
+% \usepackage[noend]{algpseudocode}
 % === All of the Packages I use frequently ===
@@
 \newcommand{\jointvar}{\mathcal{J}}
-\newcommand{\mext}[1]{E_{#1}}
-\newcommand{\mul}[1]{\Gamma_{#1}}
+\newcommand{\mset}[1]{\gamma^{#1}}
+\newcommand{\extmset}[1]{\Gamma^{#1}}
+\newcommand{\supp}[1]{\si\br{#1}}
+
+% \newcommand{\mext}[1]{E_{#1}}
+% \newcommand{\mul}[1]{\Gamma_{#1}}
 \newcommand{\isext}[2]{\delta_{#1 \ext #2}}
-\newcommand{\ts}{\mathcal{T}}
+\newcommand{\ts}{{\graph}}
 % When I introduce a new term or definition
@@
 \setoperator{Dom} % Domian
+% \setoperator{Dom} % Domian
+% \setoperator{Dom} % Domian
 
@@
 % === To allow for labeling of rows and columns of a matrix ===
-\usepackage{kbordermatrix}
+\usepackage{../packages/kbordermatrix}
 \renewcommand{\kbldelim}{(} % Left delimiter
@@
     \begin{abstract}
-        Causal inference aims to identify which observable distributions are compatible with a given causal structure.
-Compatibility inequalities for the triangle scenario have been obtained and demonstrated to be violated by quantum configurations.
-Obtaining these inequalities has lead to the development of new computational techniques suitable for large causal structures with numerous outcomes.
-Numerical optimizations against these inequalities have found new quantum configurations that are incompatible with the triangle scenario, potentially suggesting new quantum resources qualitatively different from those known previously.
-\todo[TC]{Write a better abstract.}
+        Quantum correlations are often incompatible with a classical assumption of causal structure.
+This nonclassicality is often known as quantum nonlocality, and it is witnessed through the violation of causal compatability inequalities, such as Bell inequalities.
+Such inequalities were recently derived for the Triangle scenario [arXiv:1609.00672], begging the question: can these inequalities be violated by quantum correlations?
+Here we answer this affirmatively, and discuss specific Triangle scenario inequalities and quantum configurations which manifest nonclassical correlations.
+We also report the development of novel computational techniques suitable for large causal structures with numerous outcomes.
+Numerical optimzations reveal quantum resources potentially qualitatively different from those known previously.
     \end{abstract}
@@
     \begin{definition}
-        \label{def:hypergraph}
-        A \term{hypergraph} denoted $\hgraph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{hyperedges} respectively where the nodes can represent any object and the hyperedges are \textit{subsets} of nodes.
-For convenience of notation, one defines an index set over the nodes and hyperedges of a hypergraph $\hgraph$ denoted $\ind_\nodes$ and $\ind_\edges$ respectively.
-        \[ \hgraph = \br{\nodes, \edges} \quad \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{e_i \mid i \in \ind_\edges, e_i \subseteq \nodes} \]
-        Note that whenever the hyperedge or node index is arbitrary, it will be omitted.
-There is a dual correspondence between hyperedges $e \in \edges$ and nodes $n \in \nodes$ in a Hypergraph.
-A hyperedge $e$ is viewed as a set of nodes $\bc{n_i}$, and a node $n$ can be viewed as the set of hyperedges $\bc{e_i}$ that contain it.
-    \end{definition}
-
-    \begin{definition}
-        \label{def:hgraph_trans}
-        A \term{hypergraph transversal} (or edge hitting set) $\trans$ of a hypergraph $\hgraph$ is a set of nodes $\trans \subseteq \nodes$ that have non-empty intersections with every hyperedge in $\edges$.
-        \[ \trans = \bc{n_i \in \nodes \mid i \in \ind_\trans } \quad \forall e \in \edges : \trans \cap e \neq \emptyset \]
-    \end{definition}
-
-    \begin{definition}
-        A \term{necessary node} of a transversal $\trans$ is a node $n$ such that $\trans \setminus n$ is no longer a valid transversal. The set of all necessary nodes is denoted $\Nec{\trans}$,
-        \[ \Nec{\trans} = \bc{n \in \trans \mid \exists e \in \edges : \br{\trans \setminus n} \cap e = \emptyset} \]
-        An \term{unnecessary node} of a transversal $\trans$ is any node that is \textit{not} necessary. The set of all unnecessary nodes is denoted $\UnNec{\trans}$,
-        \[ \UnNec{\trans} = \trans \setminus \Nec{\trans} \]
-        A \term{minimal hypergraph transversal} $\trans$ is any valid transversal of $\hgraph$ where every node $n$ is \textit{necessary}.
-        \[ \trans = \Nec{\trans} \]
-    \end{definition}
-
-    \begin{definition}
-        A \term{weighted hypergraph} $\hgraph_\weights$ is a regular hypergraph satisfying \cref{def:hypergraph} equipped with a set of weights $\weights$ ascribed to each node such that a weighted hypergraph is written as a triplet $\br{\weights, \nodes, \edges}$.
-        \[ \weights = \bc{w_i \mid i \in \ind_\nodes, w_i \in \R} \]
-        One would say that a particular node $n_i$ carries weight $w_i$ for each $i \in \ind_\nodes$.
-    \end{definition}
-
-    \begin{definition}
-        A \term{bounded transversal} of a weighted hypergraph $\hgraph_\weights$ is a transversal $\trans$ of the unweighted hypergraph $\hgraph$ and a real number $t$ (denoted $\trans_{\leq t}$) such that the sum of the node weights of the transversal is bounded by $t$.
-        \[ \trans_{\leq t} = \bc{n_i \mid i \in \ind_\trans} \quad \text{s.t.} \sum_{j\in\ind_\trans} w_j \leq t \]
-        One can definte analogous \term{(strictly) upper/lower bounded transversals} by considering modifications of the notation: $\trans_{< t}, \trans_{\geq t}, \trans_{> t}$.
-    \end{definition}
-
-    \begin{definition}
         A \term{causal structure} is simply a DAG with the extra classification of each node into one of two categories; the \term{latent nodes} and \term{observed nodes} denoted $\nodes_L$ and $\nodes_O$.
@@
     \end{definition}
-
-    \subsection{Preliminary Definitions}
-
-    Before discussing the present work, we
-
-    \todo[TC]{How many definitions do I need to write??}
+    \comment[TC]{How many definitions do I need to write??}
 
@@
     \begin{definition}
-        A \term{causal compatibility inequality} $\mathcal{I}_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$.
-Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $\mathcal{I}_{\mscenario}$ will be dropped leaving just $\mathcal{I}$.
+        A \term{causal compatibility inequality} $I_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$.
+Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $I_{\mscenario}$ will be dropped leaving just $I$.
     \end{definition}
@@
 
-    As a preliminary search for quantum incompatibility in $\ts$, we performed numerical optimizations using bipartite qubit states and $2$-outcome POVM measurements (see \cref{sec:param_quantum_states} for details) against the $37$ compatibility inequalities printed in \cite{Inflation} as well as the entropic inequalities presented by \cite{Henson_2014}.
+    As a preliminary search for quantum incompatibility in $\ts$, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements (see \cref{sec:param_quantum_states} for details) against the $37$ compatibility inequalities printed in \cite{Inflation} as well as the entropic inequalities presented by \cite{Henson_2014}.
 Unfortunately, none of these inequalities could be violated.
@@
     Specifically, we make use of the inflation technique for an inflated triangle scenario $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} and cast the \textit{causal compatibility} problem as a \textit{marginal problem}.
-We develop a new technique which we call the \textit{extendable covering procedure (ECP)} to find a complete solution to the marginal problem that is suitable for large causal structures where the observable nodes are equipped with numerous outcomes.
+We develop a new technique which we call the \textit{extension covering procedure (ECP)} to find a complete solution to the marginal problem that is suitable for large causal structures where the observable nodes are equipped with numerous outcomes.
 We use this technique to find numerous compatibility inequalities, some of which witness the incompatibility of the Fritz distribution.
@@
 Any compatibility constraint on marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ of the inflated causal structure $\graph'$ correspond to valid compatibility constraints on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure.
-Corollary 5 of \cite{Inflation} proves this explicitly for incompatibility inequalities $\mathcal{I}$; which the remainder of this work focuses on.
+Corollary 5 of \cite{Inflation} proves this explicitly for incompatibility inequalities $I$; which the remainder of this work focuses on.
 Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
@@
 The maximally pre-injectable sets $\bc{V_i}_{i \in \bs{12}}$ form a maximal marginal scenario $\mscenario$ over the observable nodes of $\ts'$ when equipped with outcome labels.
-Using \cref{lem:inflation} inequalities $\mathcal{I}_{\PreInj[\ts]{\ts'}}$ constraining the set of contextual marginal models $\prob^{\mscenario}$ can be deflated into polynomial inequalities over $\mathcal{I}_{\ImInj[\ts]{\ts'}}$ bounding compatible marginal models over the images of the injectable sets in $\ts$.
+Using \cref{lem:inflation} inequalities $I_{\PreInj[\ts]{\ts'}}$ constraining the set of contextual marginal models $\prob^{\mscenario}$ can be deflated into polynomial inequalities over $I_{\ImInj[\ts]{\ts'}}$ bounding compatible marginal models over the images of the injectable sets in $\ts$.
     \[ \ImInj[\ts]{\ts'} = \bc{\bc{A, B, C}, \bc{A}, \bc{B}, \bc{C}} \]
+    \comment[TC]{This is not all the images. I should clarify this.}
 
@@
 
-    \[ \mathcal{I}\tsb{Mosek-Cert}, \mathcal{I}\tsb{Cert} \]
+    \[ I\tsb{Mosek-Cert}, I\tsb{Cert} \]
 
@@
     \subsection{Logical Covers}
-    In this section, we summarize the familiar notion of a logical cover
-    % \begin{lemma}
-    %     \label{lemma:logical_extenable_set}
-    %     Let $m \in \Out{\mscenario}$ be some marginal outcome of the marginal scenario $\mscenario$.
+    In this section, we summarize the familiar notion of logical implications as witnesses for contextuality.
+Let $a \in \Out{\mscenario}$ be a marginal outcome and let $C = \bc{c_1, \ldots, c_{\abs{C}}} \subseteq \Out{\mscenario}$ be a subset of marginal outcomes.
+The subset $C$ is a \term{logical cover} of $a$ if the following possibilistic statement holds for \textit{all} marginal models $\prob^{\mscenario}$.
+    \[ a \implies c_1 \vee \ldots \vee c_{\abs{C}} = \bigvee_{c \in C} c \eq \label{eq:1a_implication} \]
+    The marginal outcome $a$ will be referred to as the \textit{antecedent} and $C$ as the \textit{consequent set}.
+A marginal model $\prob^{\mscenario}$ satisfies \cref{eq:1a_implication} if there always exists at least one $c \in C$ that is possible ($\prob[][c] > 0$) whenever $a$ is possible.
+A marginal model $\prob^{\mscenario}$ violates \cref{eq:1a_implication} whenever \textit{none} of the outcomes in $C$ are possible while $a$ is nonetheless still possible.
+Marginal models that violate logical statements such as \cref{eq:1a_implication} are known as \term{Hardy Paradoxes} \cite{Inflation,Mansfield_2012,Mancinska_2014}.
+The concept of witnessing quantum incompatibility on a logical level has been analyzed thoroughly for decades \cite{Greenberger_1990,Abramsky_2012}; being motivated by a false sense of robustness compared to probabilistic constraints.
+Logical covers such as \cref{eq:1a_implication} are in one-to-one correspondence with a subset of probabilistic inequalties.
+
+    \begin{lemma}
+        \label{lemma:logical_extenable_set}
+        Let $a \in \Out{\mscenario}$ be some marginal outcome of the marginal scenario $\mscenario$.
 If any marginal model $\prob^{\mscenario}$ is to be non-contextual, the following condition must hold.
-    %     \[ m \iff \bigvee_{j \in \Ext[\jointvar]{m}} j \]
-    %     The idea being that if a joint distribution exists, then the event $m$ represents partial knowledge of the entire system $\jointvar$; whenever $m$ occurs, exactly one of the extendable joint outcomes has to have occurred.
-    % \end{lemma}
-    Suppose one has a particular marginal outcome $a \in \Out{\mscenario}$ and a marginal model $\prob^{\mscenario}$ that assigns the probability $\prob[][a]$ to the outcome $a$.
-If the marginal model $\prob^{\mscenario}$ is to admit a joint distribution $\prob[\jointvar]$, then it must be that $\prob[][a]$ is equal to a marginalization over $a$'s extendable set into $\jointvar$.
-    \[ \prob[][a] = \sum_{j \in \Ext[\jointvar]{a}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_a}\]
-    This corresponds to row $a$ of the incidence matrix $M$.
-Next consider a subset of marginal outcomes $C \subseteq \Out{\mscenario}$.
-Summing over the associated probabilities $\bc{\prob[][c]}_{c \in C}$ and applying \cref{eq:marginal_extendable_sum_a} yields,
+        \[ a \iff \bigvee_{j \in \Ext[\jointvar]{a}} j \eq \label{eq:lemma_logical_extendable_set}\]
+    \end{lemma}
+    The idea being that if a joint distribution exists, then the event $a$ represents partial knowledge of the entire system $\jointvar$; whenever $a$ occurs, exactly one of the extendable joint outcomes has to have occurred.
+Likewise \cref{lemma:logical_extenable_set} applies to a collection of marginal outcomes $C \in \Out{\mscenario}$,
+    \[ \bigvee_{c \in C} c \iff \bigvee_{c \in C} \bigvee_{j \in \Ext[\jointvar]{c}} j \eq \label{eq:logical_extension_C}\]
+    If a subset $C$ can be constructed such that its extension \textit{covers} the extendable set of $a$,
+    \[ \Ext[\jointvar]{a} \subseteq \bigcup_{c \in C} \Ext[\jointvar]{c} \eq \label{eq:logical_containment} \]
+    Then the combination of \cref{eq:lemma_logical_extendable_set,eq:logical_extension_C,eq:logical_containment} yields \cref{eq:1a_implication}.
+Hence the motivation for calling \cref{eq:1a_implication} a logical cover.
+
+    The principle statement of \cref{lemma:logical_extenable_set} can be taken in a probabilistic form.
+If the marginal model $\prob^{\mscenario}$ is to admit a joint distribution $\prob[\jointvar]$, then it must be that the probability $\prob[][a]$ of any marginal outcome $a \in \Out{\mscenario}$ is equal to a marginalization over its extendable set into $\jointvar$.
+    \[ \prob[][a] = \sum_{j \in \Ext[\jointvar]{a}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_a} \]
+    A logical cover $C \subseteq \Out{\mscenario}$ of $a$ has probabilistic extension,
     \[ \sum_{c \in C}\prob[][c] = \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_cs} \]
-    If for all joint distributions $\prob[\jointvar]$ it can be demonstrated that the following holds,
-    \[ \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\prob[\jointvar][j] \geq \sum_{j \in \Ext[\jointvar]{a}}\prob[\jointvar][j] \eq \label{eq:extendable_cover_first} \]
-    Then combining \cref{eq:marginal_extendable_sum_a,eq:marginal_extendable_sum_cs,eq:extendable_cover_first} yields a valid compatibility inequality for $\mscenario$.
-    \[ \prob[][a] \leq \sum_{c \in C}\prob[][c] \eq \label{eq:1ncover} \]
-    In order for \cref{eq:extendable_cover_first} to hold for \textit{all} joint distributions $\prob[\jointvar]$, it must hold on an algebraic level; each term on the right-hand side of \cref{eq:extendable_cover_first} also appears on the left-hand side of \cref{eq:extendable_cover_first}.\footnote{If there were a joint outcome $j^*$ present on the right-hand side of \cref{eq:extendable_cover_first} but not the left, then \cref{eq:extendable_cover_first} would be violated by the deterministic distribution $\prob[\jointvar][j^*] = 1$} Therefore, identifying all compatibility inequalities that can be written in the form of \cref{eq:1ncover} corresponds to identifying all sets $C \subseteq \Out{\mscenario}$ such that their joint distribution terms algebraically \textit{cover} the joint distribution terms for $a \in \Out{\mscenario}$.
-
-    The notion of forming a
-
-    \subsection{Extendable Covers}
-    We will now generalize the notion of a logical cover by considering more exotic antecedents corresponding to multiple marginal outcomes $A \subseteq \Out{\mscenario}$ along with weights $\mul{A}$ for each outcome.
+    Since $C$ is a logical cover of $a$, the right-hand side of \cref{eq:marginal_extendable_sum_a} algebraically covers \cref{eq:marginal_extendable_sum_cs}\footnote{If there were a joint outcome $j^*$ present on the right-hand side of \cref{eq:marginal_extendable_sum_a} but not the right-hand side of \cref{eq:marginal_extendable_sum_cs}, then \cref{eq:1a_probabilistic} would be violated by the deterministic distribution $\prob[\jointvar][j^*] = 1$}.
+Therefore one recovers a probabilistic version of \cref{eq:1a_implication},
+    \[ \prob[][a] \leq \sum_{c \in C}\prob[][c] \eq \label{eq:1a_probabilistic} \]
+    \begin{remark}
+        It is also possible to recover \cref{eq:1a_probabilistic} from \cref{eq:1a_implication} directly, by putting \cref{eq:1a_implication} into disjunction normal form and assigning it a certain probability,
+        \[ \prob[][\neg a \vee \bigvee_{c \in C} c] = 1 \]
+        Then applying Boole's indentity and the negative rule $\prob[][\neg a] = 1 - \prob[][a]$ one recovers \cref{eq:1a_probabilistic}.
+    \end{remark}
+    \begin{remark}
+        The probabilistic logical cover \cref{eq:1a_probabilistic} is an \textit{upgraded} version of \cref{eq:1a_implication} in the following sense.
+        \begin{itemize}
+            \item Every non-contextual marginal model $\prob^{\mscenario}$ satisfies both \cref{eq:1a_probabilistic} and \cref{eq:1a_implication}.
+            \item Every contextual marginal model $\prob^{\mscenario}$ that violates \cref{eq:1a_implication} will also violate \cref{eq:1a_probabilistic}; but the converse is not necessarily true.
+        \end{itemize}
+    \end{remark}
+
+    Computationally enumerating all logical covers for a particular antecedent $a$ corresponds to a hypergraph transversal problem \cite{Inflation}, an idea we return to in the more general picture to follow.
+
+    \subsection{Extension Covers}
+    We will now generalize the notion of a logical cover by considering more exotic antecedents corresponding to multiple marginal outcomes along with weights $\mset{A}$ for each outcome.
 Afterwards we demonstrate that these generalized covers also admit non-trivial probabilistic compatibility inequalities.
@@
     \begin{definition}
-        A \term{multiplicity set} or \term{m-set} $\mul{S}$ for a marginal scenario $\mscenario$ is a function $\mul{S} : \Out{\mscenario} \to \Z_{\geq 0}$ that assigns to each marginal outcome $m \in \Out{\mscenario}$ a \textit{multiplicity} $\mul{S}\br{m} \in \Z_{\geq 0}$.
-The subscript $S$ is a subset of marginal outcome $S \subseteq \Out{\mscenario}$ indicating which marginal outcomes receive non-zero multiplicity.
-        \[ \forall s \in S : \mul{S}\br{s} \in \N  \quad \forall m \in \Out{\mscenario}\setminus S : \mul{S}\br{m} = 0 \]
-        We define the \term{extension of an m-set} $\mul{S}$ into $\jointvar$ to be the m-set $\mul{\mext{S}}$ which assigns multiplicities to \textit{joint} outcomes $j \in \Out{\jointvar}$.
-The extension of $S$ denoted $\mext{S}$ is the set of all joint outcomes that are extensions of marginal outcomes $s \in S$.
-        \[ \mext{S} = \bigcup_{s \in S} \Ext[\jointvar]{s} \]
-        While the multiplicity of each element $j \in \mext{S}$ corresponds to the sum over multiplicities $\mul{S}\br{s}$ where $j \in \Ext[\jointvar]{s}$.
-        \[ \forall j \in \mext{S} : \mul{\mext{S}}\br{j} = \sum_{s \in S} \mul{S}\br{s} \isext{s}{j} \eq \label{eq:joint_multiplicity}\]
-        With all other joint outcomes receiving a zero multiplicity $\forall j \not\in \mext{S} : \mul{\mext{S}}\br{j} = 0$.
-    \end{definition}
-    \begin{definition}
-        An m-set $\mul{C}$ is an \term{extendable cover} of an m-set $\mul{A}$ for a marginal scenario $\mscenario$ if and only if the following two conditions hold\footnote{In fact \cref{eq:multi_extenable_cover_def} implies \cref{eq:flat_extenable_cover_def} since $\forall j \not \in \mext{A} : \mul{\mext{A}}\br{j} = 0$.}:
+        We first define the marginal indicator vector $\de_{m}$ to be the unit vector indexed by marginal outcomes $\Out{\mscenario}$ that is $1$ whenever the index is $m$, and $0$ otherwise.
+        \[ \de_{m}\br{m} = 1 \quad \forall m' \neq m : \de_{m} \br{m'} = 0 \]
+        Analogously defined is the joint indicator vector $\de_{j}$.
+        \[ \de_{j}\br{j} = 1 \quad \forall j' \neq j : \de_{j} \br{j'} = 0 \]
+    \end{definition}
+
+    We first recall that every non-contextual marginal model $\prob^{\mscenario}$ can be written as the convex combination of columns of the incidence matrix $M$.
+    \[ \probvec^{\mscenario} = M \cdot \probvec[\jointvar] = \sum_{j \in \Out{\jointvar}} \de_{m \ext j} \prob[\jointvar][j] \]
+    Thus we define the set of all non-contextual marginal models as $\mathcal{NC}$,
+    \[ \mathcal{NC} \defined \bc{\probvec^{\mscenario} \mid \probvec^{\mscenario} = \sum_{j} \mu_{j} \de_{j \res \mscenario}, \mu_j \geq 0, \sum_{j} \mu_{j} = 1} \]
+
+    \begin{definition}
+        Let $\mscenario$ be a marginal scenario and let $m \in \Out{\mscenario}$ be a marginal outcome.
+The \term{extension of $m$ onto $\jointvar$} is the function $\de_{m \ext \jointvar} : \Out{\jointvar} \to \bc{0, 1}$ that indicates membership of $\Ext[\jointvar]{m}$.
+        \[ \de_{m \ext \jointvar}\br{j} \defined \begin{cases}
+            1 & j \ext m \\
+            0 & \textrm{otherwise}
+        \end{cases} \]
+        As a vector indexed by joint outcomes $j \in \Out{\jointvar}$, $\de_{m \ext \jointvar}$ is precisely the $m$-th row of the incidence matrix.
+    \end{definition}
+    \begin{definition}
+        Let $\mscenario$ be a marginal scenario and let $j \in \Out{\jointvar}$ be a joint outcome.
+The \term{restriction of $j$ onto $\mscenario$} is deterministic marginal model $\de_{j \res \mscenario} : \Out{\mscenario} \to \bc{0, 1}$.
+        \[ \de_{j \res \mscenario}\br{m} \defined \begin{cases}
+            1 & j \ext m  \\
+            0 & \textrm{otherwise}
+        \end{cases} \]
+        As a vector indexed by marginal outcomes $m \in \Out{\mscenario}$, $\de_{j \ext \mscenario}$ is precisely the $j$-th column of the incidence matrix.
+    \end{definition}
+
+    \begin{definition}
+        A \term{multiplicity set} or \term{m-set} $\mset{S}$ for a marginal scenario $\mscenario$ is a vector indexed by marginal outcomes $m \in \Out{\mscenario}$ whose entries are non-negative integers $\mset{S}_{m} \in \Z_{\geq 0}$.
+The \term{support} $\supp{\mset{S}}$ of an m-set is the set of marginal outcomes that are assigned strictly positive multiplicity.
+        \[ \supp{\mset{S}} \defined \bc{m \in \Out{\mscenario} \mid \mset{S}_m \in \N} \]
+    \end{definition}
+
+    \begin{definition}
+        The \term{extension of an m-set} $\mset{S}$ into $\jointvar$ denoted $\extmset{S}$ is a vector indexed by \textit{joint} outcomes $j \in \Out{\jointvar}$ and is defined as follows,
+        \[ \extmset{S}_{j} \defined \sum_{s \in \supp{\mset{S}}} \mset{S}_{s} \de_{s \ext j} \eq \label{eq:joint_multiplicity} \]
+        As an immediate consequence, the support of $\extmset{S}$ is immediately known,
+        \[ \supp{\extmset{S}} = \bigcup_{s \in \supp{\mset{S}}} \Ext[\jointvar]{s} \]
+    \end{definition}
+    \begin{definition}
+        An m-set $\mset{C}$ is an \term{extension cover} of an m-set $\mset{A}$ for a marginal scenario $\mscenario$ if and only if the following two conditions hold\footnote{In fact \cref{eq:multi_extenable_cover_def} implies \cref{eq:flat_extenable_cover_def} since $\forall j \not \in \supp{\extmset{A}} : \extmset{A}_j = 0$.}:
         \begin{gather*}
-            E_A \subseteq E_C \eq \label{eq:flat_extenable_cover_def}\\
-            \forall j \in E_A : \mul{\mext{A}}\br{j} \leq \mul{\mext{C}}\br{j} \eq \label{eq:multi_extenable_cover_def}
+            \supp{\extmset{A}} \subseteq \supp{\extmset{C}} \eq \label{eq:flat_extenable_cover_def}\\
+            \forall j \in \supp{\extmset{A}} : \extmset{A}_{j} \leq \extmset{C}_j \eq \label{eq:multi_extenable_cover_def}
         \end{gather*}
     \end{definition}
-    Identifying extendable covers is of great importance because of the following theorem.
+    Identifying extension covers is of great importance because of the following theorem.
     \begin{theorem}
-        If the m-set $\mul{C}$ is an extendable cover of the m-set $\mul{A}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $\mathcal{I}_{\mscenario}$ for the marginal scenario $\mscenario$.
-        \[ \sum_{a \in A}\mul{A}\br{a}\prob[][a] \leq \sum_{c \in C}\mul{C}\br{c}\prob[][c] \eq \label{eq:extendable_cover} \]
+        \label{thm:extendable_cover_ineq}
+        If the m-set $\mset{C}$ is an extension cover of the m-set $\mset{A}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
+        \[ \sum_{a \in \supp{\mset{A}}}\mset{A}_a\prob[][a] \leq \sum_{c \in \supp{\mset{C}}}\mset{C}_c\prob[][c] \eq \label{eq:extendable_cover} \]
     \end{theorem}
     \begin{proof}
-        To prove that \cref{eq:extendable_cover} is a valid compatibility inequality $\mathcal{I}_{\mscenario}$ for all marginal models $\prob^\mscenario$, we will demonstrate that \cref{eq:extendable_cover} follows from the assumption that a joint distribution $\prob[\jointvar]$ exists.
-
-        For each m-set $\mul{S}$ write the weighted sum over the probabilities $\bc{\prob[][s]}_{s \in S}$ in terms of the joint distribution $\prob[\jointvar]$ using \cref{eq:joint_multiplicity}.
+        To prove that \cref{eq:extendable_cover} is a valid compatibility inequality $I_{\mscenario}$ for all marginal models $\prob^\mscenario$, we will demonstrate that \cref{eq:extendable_cover} follows from the assumption that a joint distribution $\prob[\jointvar]$ exists.
+
+        For each m-set $\mset{S}$ write the weighted sum over the probabilities $\bc{\prob[][s]}_{s \in \supp{\mset{S}}}$ in terms of the joint distribution $\prob[\jointvar]$ using \cref{eq:joint_multiplicity}.
         \begin{align*}
@@
         \begin{split}
-        \sum_{s \in S} \mul{S}\br{s}\prob[][s] &= \sum_{s \in S} \mul{S} \br{s} \sum_{j \in \Ext[\jointvar]{s}} \prob[\jointvar][j] \\
-        &= \sum_{s \in S} \mul{S} \br{s} \sum_{j \in \Out{\jointvar}} \isext{s}{j} \prob[\jointvar][j] \\
-        &=  \sum_{j \in \Out{\jointvar}} \bs{\sum_{s \in S} \mul{S} \br{s} \isext{s}{j}} \prob[\jointvar][j] \\
-        &= \sum_{j \in E_{S}} \mul{\mext{S}}\br{j} \prob[\jointvar][j]
+        \sum_{s \in \supp{\mset{S}}} \mset{S}_s\prob[][s] &= \sum_{s \in \supp{\mset{S}}} \mset{S}_s  \sum_{j \in \Ext[\jointvar]{s}} \prob[\jointvar][j] \\
+        &= \sum_{s \in \supp{\mset{S}}} \mset{S}_s \sum_{j \in \Out{\jointvar}} \isext{s}{j} \prob[\jointvar][j] \\
+        &= \sum_{j \in \Out{\jointvar}} \bs{\sum_{s \in \supp{\mset{S}}} \mset{S}_s  \isext{s}{j}} \prob[\jointvar][j] \\
+        &= \sum_{j \in \supp{\extmset{S}}} \extmset{S}_j \prob[\jointvar][j]
         \end{split}
@@
         First examine the substitution $S \to C$,
-        \[ \sum_{c \in C} \mul{C}\br{c}\prob[][c] = \sum_{j \in E_{C}} \mul{\mext{C}}\br{j} \prob[\jointvar][j] \]
-        By \cref{eq:flat_extenable_cover_def} $E_A \subseteq E_C$,
-        \[ \sum_{c \in C} \mul{C}\br{c}\prob[][c] = \sum_{j \in E_{A}} \mul{\mext{C}}\br{j} \prob[\jointvar][j] + \sum_{j \in E_{C} \setminus E_{A}} \mul{\mext{C}}\br{j} \prob[\jointvar][j] \]
-        Notice that the sum over $j \in E_{C} \setminus E_{A}$ is entirely positive since $\mul{\mext{C}}\br{j} \in \N$ and $\prob[\jointvar][j] \geq 0$.
-Moreover \cref{eq:multi_extenable_cover_def} gives $\mul{\mext{C}}\br{j} \geq \mul{\mext{A}}\br{j}$.
+        \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] = \sum_{j \in \supp{\extmset{C}}} \extmset{C}_j \prob[\jointvar][j] \]
+        By \cref{eq:flat_extenable_cover_def} $\supp{\extmset{A}} \subseteq \supp{\extmset{C}}$,
+        \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] = \sum_{j \in \supp{\extmset{C}}} \extmset{C}_j \prob[\jointvar][j] + \sum_{j \in \supp{\extmset{C}} \setminus \supp{\extmset{A}}} \extmset{C}_j \prob[\jointvar][j] \]
+        Notice that the sum over $j \in \supp{\extmset{C}} \setminus \supp{\extmset{A}}$ is entirely positive since $\extmset{C}_j \in \N$ and $\prob[\jointvar][j] \geq 0$.
+Moreover \cref{eq:multi_extenable_cover_def} gives $\extmset{C}_j \geq \extmset{A}_j$.
 Combining these observations along with \cref{eq:derivation_cover} for $S \to A$, one arrives at the inequality,
-        \[ \sum_{c \in C} \mul{C}\br{c}\prob[][c] \geq \sum_{j \in E_{A}} \mul{\mext{A}}\br{j} \prob[\jointvar][j] = \sum_{a \in A} \mul{A}\br{a}\prob[][a] \]
+        \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] \geq \sum_{j \in \supp{\extmset{A}}} \extmset{A}_j \prob[\jointvar][j] = \sum_{a \in \supp{\mset{A}}} \mset{A}_a\prob[][a] \]
         Which is equivalent to \cref{eq:extendable_cover}; every non-contextual marginal model $\prob^{\mscenario}$ must satisfy \cref{eq:extendable_cover}.
     \end{proof}
+    \begin{corollary}
+        \label{cor:linear_integer}
+        Every linear, integer coefficient compatibility inequality that is homogeneous is an extension covering inequality.
+    \end{corollary}
+    \begin{proof}
+        A proof is easy to see by contradiction.
+Let $I_{\mscenario} = \bc{\gamma \cdot \probvec^{\mscenario} \geq 0}$ where $\gamma_m \in \Z | \forall m \in \Out{\mscenario}$ be a homogeneous, linear, integer coefficient, compatibility inequality such that it is \textit{not} an extension covering inequality.
+Next seperate $\gamma$ into its positive and negative components,
+        \[ \gamma_m^{+} = \begin{cases}
+            \gamma_m & \gamma_m > 0 \\
+            0 & \gamma_m \leq 0
+        \end{cases}
+        \qquad
+        \gamma_m^{-} = \begin{cases}
+            -\gamma_m & \gamma_m < 0 \\
+            0 & \gamma_m \geq 0
+        \end{cases} \]
+        Such that both $\gamma^{+}$ and $\gamma^{-}$ are valid m-sets.
+Therefore $I_{\mscenario} = \bc{\br{\gamma^{+} - \gamma^{-}} \cdot \probvec^{\mscenario} \geq 0}$.
+Since this inequality is \textit{not} an extension cover, it must be that there exists at least one joint outcome $j' \in \Out{\jointvar}$ such that $\Gamma^{-}_{j'} > \Gamma^{+}_{j'}$.
+Consequently by \cref{eq:derivation_cover}, the deterministic distribution $\probvec^{\mscenario} = \de_{j' \res \mscenario}$ \textit{violates} $I_{\mscenario}$.
+However since $\de_{j' \res \mscenario} \in \mathcal{NC}$ and violates $I_{\mscenario}$, $I_{\mscenario}$ can not be a compatibility inequality; disagreeing with the assumption that it was.
+    \end{proof}
     % \begin{corollary}
-    %     If the m-set $\mul{C}$ is an extendable cover of the m-set $\br{A, \mulA}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $\mathcal{I}_{\mscenario}$ for the marginal scenario $\mscenario$.
-    %     \[ \sum_{a \in A}\prob[][a] \leq \sum_{c \in C}\prob[][c] \eq \label{eq:extendable_cover_flat} \]
+    %     If the m-set $\mset{C}$ is an extension cover of the m-set $\br{A, \mulA}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
+    %     \[ \sum_{a \in \supp{\mset{A}}}\prob[][a] \leq \sum_{c \in \supp{\mset{C}}}\prob[][c] \eq \label{eq:extendable_cover_flat} \]
     % \end{corollary}
     % \begin{proof}
-    %     This follows from the fact that if $\mul{C}$ is an extendable cover of $\br{A, \mulA}$, then $\br{C, \mathbf{1}_{C}}$ is an extendable cover of $\br{A, \mathbf{1}_{A}}$.
+    %     This follows from the fact that if $\mset{C}$ is an extension cover of $\br{A, \mulA}$, then $\br{C, \mathbf{1}_{C}}$ is an extension cover of $\br{A, \mathbf{1}_{A}}$.
 Since $E_A \subseteq E_C$ is already trivially satisfied, all that remains is to demonstrate that \cref{eq:multi_extenable_cover_def} holds for unitary multiplicities $\mathbf{1}_A$ and $\mathbf{1}_C$.
 
-    %     First examine extension $\br{E_C, \mul{\mext{C}}}$ for the m-set $\mul{C}$ as defined by \cref{eq:joint_multiplicity},
-    %     \[ \forall j \in E_C : \mul{\mext{C}}\br{j} = \sum_{c \in C} \mulC\br{c} \isext{c}{j} \]
+    %     First examine extension $\br{E_C, \mul{\mext{C}}}$ for the m-set $\mset{C}$ as defined by \cref{eq:joint_multiplicity},
+    %     \[ \forall j \in E_C : \extmset{C}_j = \sum_{c \in \supp{\mset{C}}} \mulC\br{c} \isext{c}{j} \]
 
     %     First apply \cref{lemma:logical_extenable_set} to an arbitrary set $S \in \bc{A, C}$,
-    %     \[ \bigvee_{s \in S} s \iff \bigvee_{s \in S} \bigvee_{j \in \Ext[\jointvar]{s}} j \iff \bigvee_{j \in E_S} j \eq \label{eq:logical_iff_ext}\]
+    %     \[ \bigvee_{s \in \supp{\mset{S}}} s \iff \bigvee_{s \in \supp{\mset{S}}} \bigvee_{j \in \Ext[\jointvar]{s}} j \iff \bigvee_{j \in E_S} j \eq \label{eq:logical_iff_ext}\]
     %     Now since $E_A \subseteq E_C$ by \cref{eq:flat_extenable_cover_def} we have that,
@@
     %     Combining \cref{eq:logical_iff_ext,eq:logical_cover} one arrives at,
-    %     \[ \bigvee_{a \in A} a \implies \bigvee_{c \in C}c \]
+    %     \[ \bigvee_{a \in \supp{\mset{A}}} a \implies \bigvee_{c \in \supp{\mset{C}}}c \]
     % \end{proof}
@@
 
-    \subsection{Complete Solution to The Marginal Problem}
+    \subsection{Completeness of Extension Covers}
+    Corollary \ref{cor:linear_integer} alludes to completeness of extension covers.
+It vaguely suggests that every non-contextuality inequality needs to be an extension cover, otherwise there would exist a compatible and deterministic distribution that violates it.
+We will now demonstrate this completeness explicitly by first discussing what is required of a complete solution to the marginal problem.
+    \begin{definition}
+        A \term{complete solution to the marginal problem} is a finite set of $q$ vectors $\gamma_1, \ldots, \gamma_q$ together with $q$ real numbers $k \in \R$
+    \end{definition}
+    \begin{theorem}
+        \label{thm:complete_solution_log_cover}
+        The set of all logical covering inequalities forms a sufficient solution to the possibilistic marginal problem.
+    \end{theorem}
     \begin{theorem}
         \label{thm:complete_solution_ext_cover}
+        The set of all extension covering inequalities forms a sufficient solution to the probabilistic marginal problem.
     \end{theorem}
-    \subsection{Extendable Cover Procedure}
-    The \term{extendable cover procedure} begins with an antecedent m-set $\mul{A}$ and iteratively produces consequent m-sets $\mul{C}$ that are extendable covers of $\mul{A}$.
-To facilitate this, we define a \term{partial consequent m-set} to be any marginal m-set $\mul{S}$ that \textit{has yet to} become an extendable cover of $\mul{A}$.
-Also define the null m-set $\mul{\emptyset}$ to be the m-set assigning zero multiplicity to each marginal outcome.
-
-    \begin{algorithm}[H]
-    \caption{The Extendable Cover Procedure (ECP)}
-    \label{alg:ecp}
-    \begin{algorithmic}
-      \State $\mul{S}^{0} = \mul{\emptyset}$
-    \end{algorithmic}
-    \end{algorithm}
+    \begin{proof}
+    \end{proof}
+    \begin{definition}
+        An extension cover $\mset{C}$ of $\mset{A}$ is said to be \term{minimal} if there does not exist an extension cover $\mset{C'}$ different from $\mset{C}$ such that,
+        \[ \forall j \in \Out{\jointvar} : \mset{C'}_j \leq \mset{C}_j \]
+    \end{definition}
+
+    If a more minimal extension cover $\mset{C'}$ does exists, then the inequality it defines (as per \cref{thm:extendable_cover_ineq} directly implies the inequality defined by $\mset{C}$.
+
+    \begin{definition}
+        An extension cover $\mset{C}$ of $\mset{A}$ is said to be \term{reducible} if there exists a \textit{partition} of $\mset{C}$ and $\mset{A}$,
+        \[ \mset{C} = \mset{C_1} + \mset{C_2} \qquad \mset{A} = \mset{A_1} + \mset{A_2} \]
+        Such that $\mset{C_1}$ is an extension cover for $\mset{A_1}$ and $\mset{C_2}$ is an extension cover for $\mset{A_2}$.
+If $\br{\mset{C}, \mset{A}}$ does \textit{not} admit a partition, then it is said to be \term{irreducible}.
+    \end{definition}
+
+    \todo[TC]{Basis certificates}
+
+    \subsection{Extension Cover Procedure}
+    The \term{extension cover procedure} begins with an antecedent m-set $\mset{A}$ and iteratively produces consequent m-sets $\mset{C}$ that are extension covers of $\mset{A}$.
+To facilitate this, we define a \term{partial consequent m-set} to be any marginal m-set $\mset{*C}$ that \textit{has yet to} become an extension cover of $\mset{A}$.
+Also define the null m-set $\mset{\emptyset}$ to be the m-set assigning zero multiplicity to each marginal outcome.
+As a preliminary insight, it is realatively easy to construct a valid extension cover of $\mset{A}$ by first beginning with $\mset{*C} = \mset{\emptyset}$ and iteratively increasing entries in $\mset{*C}$ until \cref{eq:multi_extenable_cover_def} is satisfied.
+To ensure efficient construction, it is wise to first identity a particular joint outcome $j'$ that violates \cref{eq:multi_extenable_cover_def} $\extmset{*C}_{j'} < \extmset{A}_{j'}$, and then append to $\extmset{*C}$ a marginal outcome $m$ ($\extmset{*C} \mapsto \extmset{*C} + \de_{m}$) that is extendable to $j'$.
+Eventually, enough marginal outcomes will be added to the partial extension cover $\extmset{*C}$ for \cref{eq:multi_extenable_cover_def} to hold.
+
+    This procedure can be generalized to find \textit{all} minimal extension covers for a chosen antecdent m-set $\mset{A}$ and is best formalized as a \textit{weighted hypergraph transversal} problem.
+
+    \subsubsection{Hypergraphs}
+    \begin{definition}
+        \label{def:hypergraph}
+        A \term{hypergraph} denoted $\hgraph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{hyperedges} respectively where the nodes can represent any object and the hyperedges are \textit{subsets} of nodes.
+For convenience of notation, one defines an index set over the nodes and hyperedges of a hypergraph $\hgraph$ denoted $\ind_\nodes$ and $\ind_\edges$ respectively.
+        \[ \hgraph = \br{\nodes, \edges} \quad \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{e_i \mid i \in \ind_\edges, e_i \subseteq \nodes} \]
+        Note that whenever the hyperedge or node index is arbitrary, it will be omitted.
+There is a dual correspondence between hyperedges $e \in \edges$ and nodes $n \in \nodes$ in a Hypergraph.
+A hyperedge $e$ is viewed as a set of nodes $\bc{n_i}$, and a node $n$ can be viewed as the set of hyperedges $\bc{e_i}$ that contain it.
+    \end{definition}
+
+    \begin{definition}
+        \label{def:hgraph_trans}
+        A \term{hypergraph transversal} (or edge hitting set) $\trans$ of a hypergraph $\hgraph$ is a set of nodes $\trans \subseteq \nodes$ that have non-empty intersections with every hyperedge in $\edges$.
+        \[ \trans = \bc{n_i \in \nodes \mid i \in \ind_\trans } \quad \forall e \in \edges : \trans \cap e \neq \emptyset \]
+    \end{definition}
+
+    \begin{definition}
+        A \term{necessary node} of a transversal $\trans$ is a node $n$ such that $\trans \setminus n$ is no longer a valid transversal. The set of all necessary nodes is denoted $\Nec{\trans}$,
+        \[ \Nec{\trans} = \bc{n \in \trans \mid \exists e \in \edges : \br{\trans \setminus n} \cap e = \emptyset} \]
+        An \term{unnecessary node} of a transversal $\trans$ is any node that is \textit{not} necessary. The set of all unnecessary nodes is denoted $\UnNec{\trans}$,
+        \[ \UnNec{\trans} = \trans \setminus \Nec{\trans} \]
+        A \term{minimal hypergraph transversal} $\trans$ is any valid transversal of $\hgraph$ where every node $n$ is \textit{necessary}.
+        \[ \trans = \Nec{\trans} \]
+    \end{definition}
+
+    \begin{definition}
+        A \term{weighted hypergraph} $\hgraph_\weights$ is a regular hypergraph satisfying \cref{def:hypergraph} equipped with a set of weights $\weights$ ascribed to each node such that a weighted hypergraph is written as a triplet $\br{\weights, \nodes, \edges}$.
+        \[ \weights = \bc{w_i \mid i \in \ind_\nodes, w_i \in \R} \]
+        One would say that a particular node $n_i$ carries weight $w_i$ for each $i \in \ind_\nodes$.
+    \end{definition}
+
+    \begin{definition}
+        A \term{bounded transversal} of a weighted hypergraph $\hgraph_\weights$ is a transversal $\trans$ of the unweighted hypergraph $\hgraph$ and a real number $t$ (denoted $\trans_{\leq t}$) such that the sum of the node weights of the transversal is bounded by $t$.
+        \[ \trans_{\leq t} = \bc{n_i \mid i \in \ind_\trans} \quad \text{s.t.} \sum_{j\in\ind_\trans} w_j \leq t \]
+        One can definte analogous \term{(strictly) upper/lower bounded transversals} by considering modifications of the notation: $\trans_{< t}, \trans_{\geq t}, \trans_{> t}$.
+    \end{definition}
+
+    % \begin{algorithm}[H]
+    % \caption{The Extension Cover Procedure (ECP)}
+    % \label{alg:ecp}
+    % \begin{algorithmic}
+    %   \State $\mset{S}^{0} = \mul{\emptyset}$
+    % \end{algorithmic}
+    % \end{algorithm}
 
     % \begin{algorithm}
-    %   \caption{The Extendable Cover Procedure (ECP)
+    %   \caption{The Extension Cover Procedure (ECP)
     %     \label{alg:ecp}}
     %   \begin{algorithmic}[1]
-    %     \Require{An antecedent m-set $\mul{A}$ and a partial consequent m-set $\mul{S}$.}
+    %     \Require{An antecedent m-set $\mset{A}$ and a partial consequent m-set $\mset{S}$.}
     %     \Statex
-    %     \Function{ECP}{$\mul{A}, \mul{S}$}
+    %     \Function{ECP}{$\mset{A}, \mset{S}$}
     %       % \Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
@@
     \todo[TC]{Simplicial Complex}
-    \subsubsection{Optimizations}
+    \subsubsection{Advantages}
 
     \subsubsection{Avoiding Trivial Inequalities}
-    A \term{trivial compatibility inequality} $\mathcal{I}_{\mscenario}$ is an inequality that is satisfied by all marginal models $\prob^{\mscenario}$, not just compatible ones.
-Trivial compatibility inequalities are of no importance Since the set of all extendable cover inequalities
-    \todo[TC]{}
-    \subsection{}
-    \subsection{Irreducible Covers}
-    \todo[TC]{Basis certificates}
-    \subsection{Limited Factorization}
-
-    \subsection{Logical Implications \& Inequalities}
-    \label{sec:implication_inequalities}
-    Following the work conducted by Mansfield and Fritz \cite{Mansfield_2012}, we consider a possibilistic implications of the form,
-    \[ a \implies c_1 \lor \cdots \lor c_m = \bigvee_{i\in \bs{m}} c_i \eq \label{eq:1n_pi}\]
-    Where $a$ and each of the $c_i$'s are simply events or outcomes of a particular set of variables.
-The letter `$a$' is chosen for the event $a$ since it takes the place of the logical \term{antecedent} of \cref{eq:1n_pi}.
-Likewise, the letter `$c$' is chosen to represent logical \term{consequents}.
-We refer to the set of all $c_i$'s simply as $C = \bc{c_i \mid i \in \bs{m}}$.
-The implication \cref{eq:1n_pi} can be read as \textit{whenever $a$ occurs, at least one element of $c$ also occurs}.
-
-    It is possible to turn possibilistic implications into probabilistic inequalities by recognizing that the logical implication of \cref{eq:1n_pi} induces the inequality,
-    \[ \prob[][a] \leq \prob[][\bigvee_{i=1}^{m} c_i] \]
-    Furthermore utilizing Boole's inequality,
-    \[ \prob[][\bigvee_{i=1}^{m} c_i] \leq \sum_{i=1}^{m} \prob[][c_i] \eq \label{eq:booles} \]
-    Gives,
-    \[ \prob[][a] \leq \sum_{i=1}^{m} \prob[][c_i] \eq \label{eq:1n_ineq} \]
-    Such that whenever the inequality \cref{eq:1n_ineq} is violated, the implication in \cref{eq:1n_pi} is violated as well.
-Note that the converse is \textit{not} true; if the inequality \cref{eq:1n_ineq} holds true, it is still possible for there to be a violation of \cref{eq:1n_pi}.
-
-    \begin{remark}
-        An important result of Boole's inequality is that \cref{eq:booles} becomes an exact \textit{equality} whenever elements of $C$ are pairwise disjoint.
-Therefore, finding a set $C$ of pairwise disjoint events satisfying \cref{eq:1n_pi} will give rise to tighter inequalities.
-    \end{remark}
-
-    \subsection{Implications in the Marginal Problem}
-    \label{sec:implications_marginal_problem}
-    The question then remains, \textit{how does non-contextuality give rise to implications of the form of \cref{eq:1n_pi}?} Begin by making the principle assumption that a joint distribution \textit{does} exist for a marginal model $\prob^{\mscenario}$.
-This assumption induces logical \textit{tautologies} that take the form of \cref{eq:1n_pi}, which we call \term{marginal implications}, using the following train of logic.
-    \begin{enumerate}
-        \item Suppose a particular marginal outcome $a \in O_{\mscenario}$ happens to occur.
-        \item Since a joint distribution exists, then $a$ refers to some \textit{incomplete} knowledge about a \textit{joint} event $j = \outc{\jointvar} \in O_{\jointvar}$ that actually occured.
-More precisely, this set of possible $j$'s is the extendable set of $a$ in $O_{\jointvar}$.
-        \[ j \in \Ext[\jointvar]{a} \]
-        \item Therefore whenever $a$ occurs, one of the elements $j$ of $\Ext[\jointvar]{a}$ \textit{has} to occur.
-        \[ a \implies \bigvee_{j \in \Ext[\jointvar]{a}} j \eq \label{eq:A_impies_extendable}\]
-        \item Now suppose we could obtain a set of marginal outcomes $C = \bc{c_1, \ldots, c_m}$ each different from $a$ such that for every $j$, $\Ext{c \to j}$ for at least one element $c \in C$.
-If such a $C$ can be found, then the possibility of at least one $j$ occurring implies the possibility of at least one $c$ occurring.
-        \[ \bigvee_{j \in \Ext[\jointvar]{a}} j \implies c_1 \vee \cdots \vee c_m = \bigvee_{i \in \bs{m}} c_i\eq \label{eq:extendable_implies_cover} \]
-
-        \item Combing \cref{eq:A_impies_extendable} with \cref{eq:extendable_implies_cover}, one obtains \cref{eq:1n_pi}.
-    \end{enumerate}
-
-    \todo[TC]{Talk about why this is called hardy paradox}
-
-    Finding all marginal implications for a chosen marginal outcome $a$ corresponds to finding a set of marginal outcomes $C = \bc{c_1, \ldots, c_m}$ whose extendable sets \textit{cover} $\Ext[\jointvar]{a}$.
-Formally this corresponds to a \term{set covering} problem \todo[TC]{cite} which we elected to cast as the equivalent \term{hypergraph transversal problem}.
-
-    \todo[TC]{Mention sufficient solution to the possibilistic marginal problem}
-    \todo[TC]{Illustrate how it can distinguish more than possibilistic differences}
-
-    Given an antecedent $a$, we can construct a hypergraph $\hgraph_{a}$ called the \term{marginal hypergraph} with nodes $\nodes_a$ and $\edges_a$.
-The nodes of this hypergraph are the subset of marginal outcomes $\nodes_a \subseteq O^{\mscenario}$ \textit{compatible} with $a$.
-    The edges are labeled by outcomes in $\Ext[\jointvar]{a} \subseteq O_{\jointvar}$, namely the set of $j$'s, and contain all nodes compatible with $j$.
-    \begin{align*}
-        \nodes_a &= \bc{n \in O^{\mscenario} \mid \Com{n, a}} \eq \label{eq:hgraph_nodes} \\
-        \edges_a &= \bc{\bc{n \in O^{\mscenario} \mid \Com{n, j}} , j \in \Ext[\jointvar]{a}} \eq \label{eq:hgraph_edges}
-    \end{align*}
-    \begin{remark}
-        \label{remark:trivial_transversal}
-        Note that every node is contained in some edge.
-To prove this, consider the definition of compatibility between outcomes.
-If every $n$ is compatible with $a$, then there exists some outcome $j \in \Ext[\jointvar]{A}$ such that $\Ext{n \to j}$.
-Therefore since $\Ext{n \to j}$, $\Com{n, j}$; satisfying the central condition of \cref{eq:hgraph_edges}.
-    \end{remark}
-
-    \subsection{Higher Order Marginal Implications}
-
-    \todo[TC]{Discuss $(m,n)-type$ implications and the non-triviality}
-    \todo[TC]{Link to logical bell inequalities/completeness or not?}
-
-    \subsection{Hypergraph Transversals}
-    Section \ref{sec:implications_marginal_problem} demonstrates how finding possibilistic marginal implications can be casted as a hypergraph transversal problem.
-This section aims to summarize the general idea behind existing algorithms and also discusses some of the inequalities found using these algorithms.
-\todo[TC]{References here }
+    A \term{trivial compatibility inequality} $I_{\mscenario}$ is an inequality that is satisfied by all marginal models $\prob^{\mscenario}$, not just compatible ones.
+Trivial compatibility inequalities are of no importance Since the set of all extension cover inequalities
+    \todo[TC]{Targeted Seeds}
 
@@
     The aim of this section is to formalize what types of symmetries are present in a particular causal structure $\graph$.
-The group of these causal symmetries will define, for each compatibility inequality $\mathcal{I}_{\mscenario}$, a family of inequalities that are also valid incompatibility inequalities.
+The group of these causal symmetries will define, for each compatibility inequality $I_{\mscenario}$, a family of inequalities that are also valid incompatibility inequalities.
 
@@
 Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\gelem \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\action{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes.
-By construction, any valid compatibility inequality $\mathcal{I}_{\mscenario}$ for the marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes.
-Therefore applying $\gelem$ to all distributions in $\mathcal{I}_{\mscenario}$ yields $\action{\mathcal{I}_{\mscenario}} \defined \action{\mathcal{I}}_{\action{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\action{\mscenario}$ defined as,
+By construction, any valid compatibility inequality $I_{\mscenario}$ for the marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes.
+Therefore applying $\gelem$ to all distributions in $I_{\mscenario}$ yields $\action{I_{\mscenario}} \defined \action{I}_{\action{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\action{\mscenario}$ defined as,
     \[ \action{\mscenario} = \bc{\action{V_1}, \ldots, \action{V_k}} \]
@@
     %     \todo[TC]{Above trivial example.}
-    %     Consider the marginal scenario $V_{\bs{4}} = \bc{\bc{A,B,C}, \bc{A}, \bc{B}, \bc{C}}$ and the compatibility inequality $\mathcal{I}_{\bc{ABC, A, B, C}}$ for the Triangle Scenario in \cref{fig:triangle_scenario} with the following form,
+    %     Consider the marginal scenario $V_{\bs{4}} = \bc{\bc{A,B,C}, \bc{A}, \bc{B}, \bc{C}}$ and the compatibility inequality $I_{\bc{ABC, A, B, C}}$ for the Triangle Scenario in \cref{fig:triangle_scenario} with the following form,
     %     \[ \prob[ABC][002]\prob[ABC][003] \leq \prob[A][0]\prob[C][3] \]
-    %     Now consider $\gelem = \bc{A \to A, B \to C, C \to B}$. Since $\action{\graph} = \graph$, $\action{\mathcal{I}_{\mscenario}}$ is also a valid compatibility inequality,
+    %     Now consider $\gelem = \bc{A \to A, B \to C, C \to B}$. Since $\action{\graph} = \graph$, $\action{I_{\mscenario}}$ is also a valid compatibility inequality,
     % \end{example}
-    More generically, any permutation $\gelem$ that preserves the graphical structure of $\graph$ can be applied to $\mathcal{I}_{\mscenario}$ to generate new and valid compatibility inequalities.
+    More generically, any permutation $\gelem$ that preserves the graphical structure of $\graph$ can be applied to $I_{\mscenario}$ to generate new and valid compatibility inequalities.
 Specifically this alludes to the \term{graph automorphism group} $\Aut{\graph}$ of $\graph$.
@@
         \[ \Aut[\nodes_O]{\graph} = \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph, \forall n \in \nodes_O :\action{n} \in \nodes_O} \]
-        Given any compatibility inequality $\mathcal{I}_{\mscenario}$, each element $\gelem$ of the causal symmetry group defines a new valid compatibility inequality $\action{\mathcal{I}_{\mscenario}} = \action{\mathcal{I}}_{\action{\mscenario}}$.
+        Given any compatibility inequality $I_{\mscenario}$, each element $\gelem$ of the causal symmetry group defines a new valid compatibility inequality $\action{I_{\mscenario}} = \action{I}_{\action{\mscenario}}$.
     \end{definition}
@@
     The inflation technique discussed in \cref{sec:summary_inflation} allows one to derive compatibility inequalities for a causal structure $\graph$ by considering the marginal problem over the pre-injectable sets of $\graph'$ denoted $\PreInj[\graph]{\graph'} = \bc{V_1, \ldots, V_k}$.
-It is important to recall that due to \cref{lem:inflation}, inequalities $\mathcal{I}'$ for $\graph'$ are \textit{only} transferable to inequalities $\mathcal{I}$ for $\graph$ if $\mathcal{I}'$ is in terms of distributions over the pre-injectable sets $\mathcal{I}'_{\PreInj[\graph]{\graph'}}$.
+It is important to recall that due to \cref{lem:inflation}, inequalities $I'$ for $\graph'$ are \textit{only} transferable to inequalities $I$ for $\graph$ if $I'$ is in terms of distributions over the pre-injectable sets $I'_{\PreInj[\graph]{\graph'}}$.
 As a consequence of this observation, we need to consider a subgroup of the causal symmetry group that preserves the pre-injectable sets,
@@
         \[ \Phi \defined \Aut[\mscenario]{\graph} = \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph, \forall V \in \mscenario : \action{V} \in \mscenario} \]
-        Given any compatibility inequality $\mathcal{I}_{\mscenario}$ each element $\gelem$ of the causal symmetry group defines a new valid compatibility inequality $\action{\mathcal{I}_{\mscenario}} = \action{\mathcal{I}}_{\mscenario}$ over the \textit{same} marginal context $\mscenario$.
+        Given any compatibility inequality $I_{\mscenario}$ each element $\gelem$ of the causal symmetry group defines a new valid compatibility inequality $\action{I_{\mscenario}} = \action{I}_{\mscenario}$ over the \textit{same} marginal context $\mscenario$.
     \end{definition}
@@
     The restricted causal symmetry group for the pre-injectable sets of an inflation $\graph'$ is the ideal symmetry group for use with the inflation technique.
-If one obtains a particular inequality $\mathcal{I}'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\Phi$, an entire family of valid compatibility inequalities are also obtained.
-    \[ \bc{\action{\mathcal{I}'}_{\PreInj[\graph]{\graph'}} \mid \gelem \in \Phi} \text{ where } \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
+If one obtains a particular inequality $I'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\Phi$, an entire family of valid compatibility inequalities are also obtained.
+    \[ \bc{\action{I'}_{\PreInj[\graph]{\graph'}} \mid \gelem \in \Phi} \text{ where } \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
     We have obtained $\Phi$ for the inflated triangle scenario \cref{fig:inflated_triangle_scenario}. $\Phi$ is an order $48$ group with the following $4$ generators:
@@
 Although very useful, we divert our attention to finding \textit{symmetric} inequalities themselves.
-    \[ \forall \gelem \in \Phi :  \action{\mathcal{I}_{\mscenario}} = \mathcal{I}_{\mscenario} \]
+    \[ \forall \gelem \in \Phi :  \action{I_{\mscenario}} = I_{\mscenario} \]
     In order to do this, we must first define how elements $\gelem \in \Phi$ act on marginal outcomes $O_{\mscenario}$.
@@
 
-    \subsection{Symmetric Logical Implications}
     \subsection{Results}
 
-    \todo[TC]{Identify the desired symmetry group}
     \todo[TC]{How we obtained the desired symmetry group}
     \todo[TC]{Group orbits to symmetric marginal description matrix}
-    \todo[TC]{Infeasibility on symmetric marginal problem}
-    \todo[TC]{Hardy Transversals can't work on the symmetric marginal problem}
-    \todo[TC]{Symmetrizing non-symmetric inequalities through avoiding orbits}
-    \todo[TC]{higher order transversals on mutually impossible events}
+    \todo[TC]{representative antecedents completely solve the marginal problem}
+
     \section{Non-linear Optimizations}
@@
 We define the optimization target for the CHSH inequality to be the left-hand-side of \cref{eq:CHSH},
-    \[ \mathcal{I}\tsb{CHSH} = \ba{AB|11} + \ba{AB|12} + \ba{AB|21} - \ba{AB|22} \]
+    \[ I\tsb{CHSH} = \ba{AB|11} + \ba{AB|12} + \ba{AB|21} - \ba{AB|22} \]
     Figure \ref{fig:CHSH_convex} demonstrates this optimization for $5$ random seed parameters $\lambda^0$, each converging to the expected value of $4$. Analogously, \cite{Cirelson_1980}
@@
             \includegraphics{../figures/CHSH_convex.pdf}
-            \caption{Convex optimizations against $\mathcal{I}\tsb{CHSH}$ recover algebraic violation of $4$.}
+            \caption{Convex optimizations against $I\tsb{CHSH}$ recover algebraic violation of $4$.}
             \label{fig:CHSH_convex}
@@
             \includegraphics{../figures/CHSH_quantum.pdf}
-            \caption{Quantum optimizations against $\mathcal{I}\tsb{CHSH}$ recover maximum violation of $2\sqrt{2}$.}
+            \caption{Quantum optimizations against $I\tsb{CHSH}$ recover maximum violation of $2\sqrt{2}$.}
             \label{fig:CHSH_quantum}

### 2016-09-15 document/main.tex
working draft
symmetries

@@
 \newtheorem{remark}[theorem]{Remark}
+
+% === To allow for labeling of rows and columns of a matrix ===
+\usepackage{kbordermatrix}
+\renewcommand{\kbldelim}{(} % Left delimiter
+\renewcommand{\kbrdelim}{)} % Right delimiter
 
@@
 \newcommand{\ind}{\mathcal{I}}
-\newcommand{\perm}{\Omega}
+\newcommand{\netperm}{\Pi}
 \newcommand{\Hilb}{\mathcal{H}}
@@
 \newcommand{\res}{\mathrel{\Yright}}
-\newcommand{\gelem}{\varphi}
-\newcommand{\action}[1]{\gelem\bs{#1}}
+\newcommand{\gep}{\varphi}
+\newcommand{\gp}{\Phi}
+\newcommand{\geo}{\omega}
+\newcommand{\go}{\Omega}
 \newcommand{\mscenario}{\mathcal{M}}
@@
 
-% === To allow for labeling of rows and columns of a matrix ===
-\usepackage{../packages/kbordermatrix}
-\renewcommand{\kbldelim}{(} % Left delimiter
-\renewcommand{\kbrdelim}{)} % Right delimiter
-
 % === Causal structure formatting for tikz ===
@@
     \label{eq:fritz_quantum_realization}
-    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+} \\
+    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\gp^+}\bra{\gp^+} \\
     M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
@@
     \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
-    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.
+    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\gp^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.
 
@@
         \label{ex:marginal_matrix}
-        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and consider the marginal scenario $\mscenario = \bc{\bc{a,c}, \bc{b}}$. The incidence matrix becomes:
+        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and consider the marginal scenario $\mscenario = \bc{\bc{a,b}, \bc{b,c}, \bc{a,c}}$. The incidence matrix becomes:
+        \newcommand{\kone}{\mathbf{1}}
+        \newcommand{\kzer}{\textcolor{gray}{0}}
         \[ M = \kbordermatrix{
             (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
-            (a\mapsto0, c\mapsto0) & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-            (a\mapsto0, c\mapsto1) & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 \\
-            (a\mapsto1, c\mapsto0) & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 \\
-            (a\mapsto1, c\mapsto1) & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 1 \\
-            (b\mapsto0)            & 1 & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
-            (b\mapsto1)            & 0 & 0 & 1 & 1 & 0 & 0 & 1 & 1
+            (a\mapsto0, b\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
+            (a\mapsto0, b\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
+            (a\mapsto1, b\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
+            (a\mapsto1, b\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
+            (b\mapsto0, c\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
+            (b\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
+            (b\mapsto1, c\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
+            (b\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
+            (a\mapsto0, c\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
+            (a\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
+            (a\mapsto1, c\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
+            (a\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
         } \]
@@
     \end{definition}
-    Remark \ref{remark:trivial_transversal} guarantees that all marginal hypergraphs are non-degenerate.
-There are two distinct approaches to hypergraph transversal generation: \textit{top-down} and \textit{bottom-up}.
+    Remark ?? guarantees that all marginal hypergraphs are non-degenerate. There are two distinct approaches to hypergraph transversal generation: \textit{top-down} and \textit{bottom-up}.
     \begin{definition}
@@
     For our purposes we implemented a deep-first transversal algorithm similar to
-    Recalling \cref{remark:trivial_transversal}
+    Recalling
 
@@
     \todo[TC]{Seeding inequalities (huge advantage here)}
-    \section{Deriving Symmetric Inequalities}
+    \section{Marginal Symmetries}
     \label{sec:symmetry}
@@
 The latter case generates a family of incompatible distributions obtained by exchanging parties of the found extremal distribution\footnote{If the extremal distribution is not invariant under exchange of parties, there is indication that the space of accessible distributions is non-convex.}.
-In this section we discuss how to achieve computational advantage and its application to the inequality techniques mentioned in \cref{sec:certificate_inequalities} and \cref{sec:implication_inequalities}.
+In this section we discuss how to exploit symmetries in the extension covering procedure in order to reduce the computational search space.
+\\
+
+    To demonstrate what kinds of symmetries are valid, we present the following example:
+    \begin{example}
+        \label{ex:symmetries}
+        First consider the marginal scenario $\mscenario = \bc{\bc{a, b, c}, \bc{c, d}, \bc{a, d}}$ where each variable in $\jointvar = \bc{a,b,c,d}$ is binary.
+Moreover, let $I_{\mscenario}$ be the compatibility inequality,
+        \[ I_{\mscenario} = \bc{\prob[abc][010] \leq \prob[cd][00] + \prob[ad][01]}  \]
+        Intuitively, a compatibility is independent of outcome labels $O_a = O_b = O_c = O_d = \bc{0,1}$.
+Therefore new compatibility inequalities can be generated from $I_{\mscenario}$ by permuting its outcome labels.
+Let $\geo_v : O_v \to O_v : \bc{0,1} \mapsto \geo_v\bs{\bc{0,1}} = \bc{1,0}$ be a permutation of the outcome labels for variable $v$.
+Let $\geo = \geo_a \times \geo_c$ be the permutation of variables $a$ and $c$.
+The action of $\geo$ on outcome labels induces an action on the inequality $I_{\mscenario}$ itself,
+        \begin{align*}
+        \geo\bs{I_{\mscenario}} &= \bc{\prob[abc][\geo\bs{010}] \leq \prob[cd][\geo\bs{00}] + \prob[ad][\geo\bs{01}]} \\
+        &= \bc{\prob[abc][111] \leq \prob[cd][10] + \prob[ad][11]}
+        \end{align*}
+        The new inequality $\geo\bs{I_{\mscenario}}$ is also a valid compatibility inequality.
+By construction, any permutation $\geo$ over outcome labels leaves the marginal scenario invariant ($\geo\bs{\mscenario} = \mscenario$) and thus we may write $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$.
+\\
+
+        Alternatively, permutations of the variables themselves are also permitted.
+Let $\gep : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \gep\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ be a permutation of the variables $\jointvar$.
+Intuitively $\gep$ acts on $I_{\mscenario}$ in the following way,
+        \begin{align*}
+        \gep\bs{I_{\mscenario}} &= \bc{\prob[\gep\bs{abc}][010] \leq \prob[\gep\bs{cd}][00] + \prob[\gep\bs{ad}][01]} \\
+        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
+        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
+        \end{align*}
+        In general (as in this example), permutations over all variables can modify the marginal scenario $\gep\bs{\mscenario} \neq \mscenario$; in general we write $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
+    \end{example}
+
+    \subsection{Outcome Label Symmetry}
+    As demonstrated by \cref{ex:symmetries}, permutations on outcome labels can be applied to inequalities themselves to generate new inequalities.
+To formalize this notion, let $\Perm{S}$ denote the \term{permutation group} acting on the set $S$ consisting of all bijective maps $s : S \to S$.
+    \[ \Perm{S} = \bc{s : S \to S} \]
+    \begin{definition}
+        Then (outcome) \term{label permutation group} $\go$ for a set of random variables $\mathcal{V} = \bc{v_1, \ldots, v_n}$ is the direct product of permutations over the outcome labels for each variable $v_i \in \mathcal{V}$,
+        \[ \go \defined \Perm{O_{v_1}} \times \cdots \times \Perm{O_{v_n}} = \prod_{v \in \mathcal{V}} \Perm{O_{v}} \]
+        The action of $\geo \in \go$ on an outcome $f \in \Out{\mathcal{V}}$ (denoted $\geo\bs{f}$) is defined as,
+        \[ \forall v \in \mathcal{V} : \br{\geo\bs{f}}\br{v} \defined \geo\bs{f\br{v}} \eq \label{eq:acto}\]
+    \end{definition}
+    \begin{lemma}
+        \label{lem:extendable_invariance_acto}
+        If a marginal outcome $m \in \Out{V} \subset \Out{\mscenario}$ is extendable to the joint outcome $j \in \Out{J}$, then $\geo\bs{m}$ is extendable to $\geo\bs{j}$ for any label permutation $\geo \in \go$.
+        \[ m \ext j \iff \geo\bs{m} \ext \geo\bs{j} \eq \label{eq:extendable_invariance_acto}\]
+    \end{lemma}
+    \begin{proof}
+        The proof should be clear by the definition of extendability (\cref{def:extendable}).
+        \[ m \ext j \iff \forall v \in \Dom{m} : j\br{v} = m\br{v} \]
+        Since $\Dom{m} = \Dom{\geo\bs{m}}$ and by \cref{eq:acto},
+        \[ \forall v \in \Dom{\geo\bs{m}}: \br{\geo\bs{j}}\br{v} = \geo\bs{j\br{v}} = \geo\bs{m\br{v}} = \br{\geo\bs{m}}\br{v} \]
+        We have that $\geo\bs{m} \ext \geo\bs{j}$. The left implication of \cref{eq:extendable_invariance_acto} follows by considering $\geo^{-1} \in \go$.
+    \end{proof}
+    \begin{corollary}
+        \label{coll:incidence_invariance}
+        Let $M$ be the incidence matrix for a marginal scenario $\mscenario$ and $\geo \in \go$ be a label permutation of the joint random variables $\jointvar$.
+By \cref{lem:extendable_invariance_acto}, the action of $\geo$ on $M$ leaves $M$ invariant ($\geo\bs{M} = M$),
+        \[ \geo\bs{M}_{m,j} \defined M_{\geo\bs{m},\geo\bs{j}} = \de_{\geo\bs{m} \ext \geo\bs{j}} = \de_{m \ext j} = M_{m,j} \]
+    \end{corollary}
+    \begin{theorem}
+        For each compatibility inequality $I_{\mscenario}$ and label permutation $\geo \in \go$, the inequality defined by $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$ is also a valid compatibility inequality for the marginal scenario $\mscenario$.
+    \end{theorem}
+    \begin{proof}
+        First let $I_{\mscenario} = \bc{\ga \cdot \probvec^{\mscenario} \geq 0}$ for the marginal scenario $\mscenario$ and $\ga$ is the certificate associated with $I_{\mscenario}$.
+Furthermore let $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario} = \bc{\ga \cdot \geo\bs{\probvec}^{\mscenario} \geq 0}$ be the inequality obtained after permuting $\probvec^{\mscenario}$ defined as,
+        \[ \forall m \in \Out{\mscenario} : \geo\bs{\probvec}^{\mscenario}_m \defined \probvec^{\mscenario}_{\geo\bs{m}} \]
+        It should be clear to see that $\geo\bs{I_{\mscenario}}$ can be rewritten as,
+        \[ \ga \cdot \geo\bs{\probvec}^{\mscenario} = \sum_{m \in \supp{\ga}} \ga_{m} \probvec^{\mscenario}_{\geo\bs{m}} = \sum_{\geo^{-1}\bs{m} \in \supp{\geo^{-1}\bs{\ga}}} \ga_{\geo^{-1}\bs{m}} \probvec^{\mscenario}_{m} = \geo^{-1}\bs{\ga} \cdot \probvec^{\mscenario} \]
+        Therefore the permuted inequality is equivalent to,
+        \[ \geo\bs{I}_{\mscenario} = \bc{\geo^{-1}\bs{\ga} \cdot \probvec^{\mscenario} \geq 0} \]
+        All that remains to be proven is that $\geo^{-1}\bs{\ga}$ forms a valid certificate for the incidence matrix $M$. Since $\geo \in \go$, then by \cref{coll:incidence_invariance},
+        \[ \br{\geo^{-1}\bs{\ga} \cdot M}_j = \sum_{m \in \supp{\geo^{-1}\bs{\ga}}} \geo^{-1}\bs{\ga}_m \de_{m\ext j} = \sum_{m \in \supp{\ga}} \bs{\ga}_m \de_{\geo\bs{m}\ext j} = \sum_{m \in \supp{\ga}} \bs{\ga}_m \de_{m\ext \geo^{-1}\bs{j}} = \br{\ga \cdot M}_{\geo^{-1}\bs{j}} \]
+        But since $I_{\mscenario}$ is a valid compatibility inequality, $\ga \cdot M \succeq 0$ and thus $\geo^{-1}\bs{\ga} \cdot M \succeq 0$ making $\geo\bs{I}_{\mscenario}$ a valid compatibility inequality as well.
+    \end{proof}
+
     \subsection{Causal Symmetry}
@@
 
-    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\gelem$ from $N$ to $N$.
-    \[ \Perm{N} = \bc{\gelem \mid \gelem : N \to N} \]
-    The action of $\gelem \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\gelem$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
+    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\gep$ from $N$ to $N$.
+    \[ \Perm{N} = \bc{\gep \mid \gep : N \to N} \]
+    The action of $\gep \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\gep$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
     \begin{align*}
-    \action{\graph} &\defined \br{\action{\nodes}, \action{\edges}} \\
-    \action{\nodes} &\defined \bc{\action{n} \mid n \in \nodes} = \nodes \\
-    \action{\edges} &\defined \bc{\action{e} \mid e \in \edges}
+    \gep\bs{\graph} &\defined \br{\gep\bs{\nodes}, \gep\bs{\edges}} \\
+    \gep\bs{\nodes} &\defined \bc{\gep\bs{n} \mid n \in \nodes} = \nodes \\
+    \gep\bs{\edges} &\defined \bc{\gep\bs{e} \mid e \in \edges}
     \end{align*}
     To motivate a more general treatment of such symmetries, consider the Triangle Scenario of \cref{fig:triangle_scenario}.
-Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\gelem \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\action{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes.
+Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\gep \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\gep\bs{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes.
 By construction, any valid compatibility inequality $I_{\mscenario}$ for the marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes.
-Therefore applying $\gelem$ to all distributions in $I_{\mscenario}$ yields $\action{I_{\mscenario}} \defined \action{I}_{\action{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\action{\mscenario}$ defined as,
-    \[ \action{\mscenario} = \bc{\action{V_1}, \ldots, \action{V_k}} \]
+Therefore applying $\gep$ to all distributions in $I_{\mscenario}$ yields $\gep\bs{I_{\mscenario}} \defined \gep\bs{I}_{\gep\bs{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\gep\bs{\mscenario}$ defined as,
+    \[ \gep\bs{\mscenario} = \bc{\gep\bs{V_1}, \ldots, \gep\bs{V_k}} \]
     % \begin{example}
@@
     %     \[ \prob[ABC][002]\prob[ABC][003] \leq \prob[A][0]\prob[C][3] \]
-    %     Now consider $\gelem = \bc{A \to A, B \to C, C \to B}$. Since $\action{\graph} = \graph$, $\action{I_{\mscenario}}$ is also a valid compatibility inequality,
+    %     Now consider $\gep = \bc{A \to A, B \to C, C \to B}$. Since $\gep\bs{\graph} = \graph$, $\gep\bs{I_{\mscenario}}$ is also a valid compatibility inequality,
     % \end{example}
-    More generically, any permutation $\gelem$ that preserves the graphical structure of $\graph$ can be applied to $I_{\mscenario}$ to generate new and valid compatibility inequalities.
+    More generically, any permutation $\gep$ that preserves the graphical structure of $\graph$ can be applied to $I_{\mscenario}$ to generate new and valid compatibility inequalities.
 Specifically this alludes to the \term{graph automorphism group} $\Aut{\graph}$ of $\graph$.
-    \[ \Aut{\graph} \defined \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph} \]
-    In general, $\Aut{\graph}$ could include elements $\gelem$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}.
+    \[ \Aut{\graph} \defined \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph} \]
+    In general, $\Aut{\graph}$ could include elements $\gep$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}.
 This behaviour is \textit{undesired} for causal inference where the latent nodes will never appear in a marginal scenario.
@@
         The \term{causal symmetry group} for a causal structure $\graph$ is the graph automorphism subgroup that stabilizes the observable nodes.
-        \[ \Aut[\nodes_O]{\graph} = \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph, \forall n \in \nodes_O :\action{n} \in \nodes_O} \]
-        Given any compatibility inequality $I_{\mscenario}$, each element $\gelem$ of the causal symmetry group defines a new valid compatibility inequality $\action{I_{\mscenario}} = \action{I}_{\action{\mscenario}}$.
+        \[ \Aut[\nodes_O]{\graph} = \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph, \forall n \in \nodes_O :\gep\bs{n} \in \nodes_O} \]
+        Given any compatibility inequality $I_{\mscenario}$, each element $\gep$ of the causal symmetry group defines a new valid compatibility inequality $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
     \end{definition}
@@
 As a consequence of this observation, we need to consider a subgroup of the causal symmetry group that preserves the pre-injectable sets,
-    \[ \action{\PreInj[\graph]{\graph'}} = \PreInj[\graph]{\graph'} \eq \label{eq:preserved_preinj} \]
-
-    \begin{definition}
-        The \term{restricted causal symmetry group} $\Phi$ for a causal structure $\graph$ and a marginal scenario $\mscenario$ is the graph automorphism subgroup that stabilizes the marginal scenario $\mscenario$.
-        \[ \Phi \defined \Aut[\mscenario]{\graph} = \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph, \forall V \in \mscenario : \action{V} \in \mscenario} \]
-        Given any compatibility inequality $I_{\mscenario}$ each element $\gelem$ of the causal symmetry group defines a new valid compatibility inequality $\action{I_{\mscenario}} = \action{I}_{\mscenario}$ over the \textit{same} marginal context $\mscenario$.
+    \[ \gep\bs{\PreInj[\graph]{\graph'}} = \PreInj[\graph]{\graph'} \eq \label{eq:preserved_preinj} \]
+
+    \begin{definition}
+        The \term{restricted causal symmetry group} $\gp$ for a causal structure $\graph$ and a marginal scenario $\mscenario$ is the graph automorphism subgroup that stabilizes the marginal scenario $\mscenario$.
+        \[ \gp \defined \Aut[\mscenario]{\graph} = \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph, \forall V \in \mscenario : \gep\bs{V} \in \mscenario} \]
+        Given any compatibility inequality $I_{\mscenario}$ each element $\gep$ of the causal symmetry group defines a new valid compatibility inequality $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\mscenario}$ over the \textit{same} marginal context $\mscenario$.
     \end{definition}
@@
     The restricted causal symmetry group for the pre-injectable sets of an inflation $\graph'$ is the ideal symmetry group for use with the inflation technique.
-If one obtains a particular inequality $I'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\Phi$, an entire family of valid compatibility inequalities are also obtained.
-    \[ \bc{\action{I'}_{\PreInj[\graph]{\graph'}} \mid \gelem \in \Phi} \text{ where } \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
-    We have obtained $\Phi$ for the inflated triangle scenario \cref{fig:inflated_triangle_scenario}. $\Phi$ is an order $48$ group with the following $4$ generators:
+If one obtains a particular inequality $I'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\gp$, an entire family of valid compatibility inequalities are also obtained.
+    \[ \bc{\gep\bs{I'}_{\PreInj[\graph]{\graph'}} \mid \gep \in \gp} \text{ where } \gp = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
+    We have obtained $\gp$ for the inflated triangle scenario \cref{fig:inflated_triangle_scenario}. $\gp$ is an order $48$ group with the following $4$ generators:
     \begin{equation*}
     \begin{aligned}[c]
-    &\hspace{1mm}\gelem_1 \\
+    &\hspace{1mm}\gep_1 \\
     A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
@@
     \begin{aligned}[c]
-    &\hspace{1mm}\gelem_2 \\
+    &\hspace{1mm}\gep_2 \\
     A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
@@
     \begin{aligned}[c]
-    &\hspace{1mm}\gelem_3 \\
+    &\hspace{1mm}\gep_3 \\
     A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
@@
     \begin{aligned}[c]
-    &\hspace{1mm}\gelem_4 \\
+    &\hspace{1mm}\gep_4 \\
     A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
@@
     %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
-    It is easy to verify that $\gelem_1, \gelem_2, \gelem_3, \gelem_4$ are all automorphisms of the inflated Triangle Scenario $\graph'$ of \cref{fig:inflated_triangle_scenario}.
+    It is easy to verify that $\gep_1, \gep_2, \gep_3, \gep_4$ are all automorphisms of the inflated Triangle Scenario $\graph'$ of \cref{fig:inflated_triangle_scenario}.
 Moreover they stabilize the observable nodes, and the map pre-injectable sets of \cref{eq:pre-injectable_triangle_scenario} to the pre-injectable sets.
 Finally, in the Triangle Scenario we have that,
-    \[ \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \sim \Aut[\nodes_O]{\graph} \]
-    To see this, $\gelem_1$ and $\gelem_4$ become the identity element $\mathbb{I}$ in $\Aut[\nodes_O]{\graph}$ upon removal of the copy-index, leaving $\gelem_2$ to generate reflections and $\gelem_3$ to generate rotations.
+    \[ \gp = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \sim \Aut[\nodes_O]{\graph} \]
+    To see this, $\gep_1$ and $\gep_4$ become the identity element $\mathbb{I}$ in $\Aut[\nodes_O]{\graph}$ upon removal of the copy-index, leaving $\gep_2$ to generate reflections and $\gep_3$ to generate rotations.
     \subsection{Symmetric Marginal Polytope}
@@
 Although very useful, we divert our attention to finding \textit{symmetric} inequalities themselves.
-    \[ \forall \gelem \in \Phi :  \action{I_{\mscenario}} = I_{\mscenario} \]
-    In order to do this, we must first define how elements $\gelem \in \Phi$ act on marginal outcomes $O_{\mscenario}$.
-    \begin{definition}
-        Let $\jointvar = \bc{v_1, \ldots, v_k}$ be a collection of random variables and let $\gelem \in \Perm{\jointvar}$.
-$\jointvar$ is said to be \term{label invariant with respect to $\gelem$} if the outcome labels for each variable $v \in \jointvar$ are unchanged under the action of $\gelem$.
-        \[ \forall v \in \jointvar : O_{v} = O_{\action{v}} \]
+    \[ \forall \gep \in \gp :  \gep\bs{I_{\mscenario}} = I_{\mscenario} \]
+    In order to do this, we must first define how elements $\gep \in \gp$ act on marginal outcomes $O_{\mscenario}$.
+    \begin{definition}
+        Let $\jointvar = \bc{v_1, \ldots, v_k}$ be a collection of random variables and let $\gep \in \Perm{\jointvar}$.
+$\jointvar$ is said to be \term{label invariant with respect to $\gep$} if the outcome labels for each variable $v \in \jointvar$ are unchanged under the action of $\gep$.
+        \[ \forall v \in \jointvar : O_{v} = O_{\gep\bs{v}} \]
         Label invariance is a prerequisite for any kind of symmetry amoung random variables.
@@
         Let $\jointvar = \br{v_1, \ldots v_k}$ be a collection of random variables along with a specific outcome $m \in \Out{V}$ where $V \subseteq \jointvar$.
-The action of $\gelem \in \Perm{\jointvar}$ on $m$ is a new outcome $\action{m} \in \Out{\action{V}}$ over $\action{V} \subseteq \jointvar$ defined as follows,
-        \[ \forall v \in V : \br{\action{m}}\br{\action{v}} \defined m \br{v} \]
-        The idea being that $\gelem$ modifies $m$ in such a way that permutes its domain while leaving its range invariant.
+The action of $\gep \in \Perm{\jointvar}$ on $m$ is a new outcome $\gep\bs{m} \in \Out{\gep\bs{V}}$ over $\gep\bs{V} \subseteq \jointvar$ defined as follows,
+        \[ \forall v \in V : \br{\gep\bs{m}}\br{\gep\bs{v}} \defined m \br{v} \]
+        The idea being that $\gep$ modifies $m$ in such a way that permutes its domain while leaving its range invariant.
     \end{definition}
     \begin{example}
-        Consider the outcome $m = \bc{A \mapsto 0, B \mapsto 1, C \mapsto 2} \in \Out{\bc{A,B,C}}$ where all variables have $4$ possible outcomes $O_A = O_B = O_C = \bc{0,1,2,3}$ and the permutation $\gelem = \bc{A \to D, B \to C, C \to B, D \to A}$.
-        The \textit{action} of $\gelem$ on $m$ is as follows,
+        Consider the outcome $m = \bc{A \mapsto 0, B \mapsto 1, C \mapsto 2} \in \Out{\bc{A,B,C}}$ where all variables have $4$ possible outcomes $O_A = O_B = O_C = \bc{0,1,2,3}$ and the permutation $\gep = \bc{A \to D, B \to C, C \to B, D \to A}$.
+        The \textit{action} of $\gep$ on $m$ is as follows,
         \begin{align*}
-            \action{m} &= \action{\bc{A \mapsto m\br{A}, B \mapsto m\br{B}, C \mapsto m\br{C}}} \\
-            &= \bc{\action{A} \mapsto m\br{A}, \action{B} \mapsto m\br{B}, \action{C} \mapsto m\br{C}} \\
+            \gep\bs{m} &= \gep\bs{\bc{A \mapsto m\br{A}, B \mapsto m\br{B}, C \mapsto m\br{C}}} \\
+            &= \bc{\gep\bs{A} \mapsto m\br{A}, \gep\bs{B} \mapsto m\br{B}, \gep\bs{C} \mapsto m\br{C}} \\
             &= \bc{D \mapsto m\br{A}, C \mapsto m\br{B}, B \mapsto m\br{C}} \\
@@
         \end{align*}
-        Evidently, $\action{m} \in \Out{\bc{B, C, D}}$.
+        Evidently, $\gep\bs{m} \in \Out{\bc{B, C, D}}$.
     \end{example}
 
-    Through repeated action of $\gelem \in \Phi$ on marginal outcomes $m \in \Out{\mscenario}$ and joint outcomes $j \in \Out{\jointvar}$, one can define group orbits of $\Phi$ in $\Out{\mscenario}$ and $\Out{\jointvar}$.
+    Through repeated action of $\gep \in \gp$ on marginal outcomes $m \in \Out{\mscenario}$ and joint outcomes $j \in \Out{\jointvar}$, one can define group orbits of $\gp$ in $\Out{\mscenario}$ and $\Out{\jointvar}$.
     \begin{align*}
-        \Orb[\Phi]{m} &\defined \bc{\action{m} \mid \gelem \in \Phi} \\
-        \Orb[\Phi]{j} &\defined \bc{\action{j} \mid \gelem \in \Phi}
+        \Orb[\gp]{m} &\defined \bc{\gep\bs{m} \mid \gep \in \gp} \\
+        \Orb[\gp]{j} &\defined \bc{\gep\bs{j} \mid \gep \in \gp}
     \end{align*}
@@
     \begin{definition}
-        The \term{symmetric incidence matrix} $M_{\Phi}$ for a marginal scenario $\mscenario$ and a particular restricted causal symmetry $\Phi$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
-Each row of $M_{\Phi}$ corresponds to a marginal orbit $\Orb[\Phi]{m}$.
-Analogously each column of $M_{\Phi}$ corresponds to a joint orbit $\Orb[\Phi]{j}$.
-The entries of $M_{\Phi}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
-        \[ M_{\Phi}\bs{\Orb[\Phi]{m}, \Orb[\Phi]{j}} = \sum_{\substack{j' \in \Orb[\Phi]{j} \\ m' \in \Orb[\Phi]{m}}} M\bs{m',j'} \]
+        The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and a particular restricted causal symmetry $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
+Each row of $M_{\gp}$ corresponds to a marginal orbit $\Orb[\gp]{m}$.
+Analogously each column of $M_{\gp}$ corresponds to a joint orbit $\Orb[\gp]{j}$.
+The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
+        \[ M_{\gp}\bs{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M\bs{m',j'} \]
     \end{definition}
@@
 We have implemented $\prob[\mathcal{Q}]$ under the following description.
-    \[ \prob[ABC]\br{abc} = \Tr\bs{\Omega^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \Omega M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \eq \label{eq:triangle_quantum_distributions} \]
+    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \eq \label{eq:triangle_quantum_distributions} \]
 
@@
 If each state $\rho$ is decomposable into $\ket{\psi}\bra{\psi}$, then \cref{eq:triangle_quantum_distributions} can be written as,
-    \[ \prob[ABC]\br{abc} = \bramidket{\psi_{AB}\psi_{BC}\psi_{CA}}{\Omega M_{A,a}\otimes M_{B,b} \otimes M_{C,c} \Omega^\intercal}{\psi_{AB}\psi_{BC}\psi_{CA}} \eq \label{eq:pure_state_quantum_triangle} \]
+    \[ \prob[ABC]\br{abc} = \bramidket{\psi_{AB}\psi_{BC}\psi_{CA}}{\netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c} \netperm^\intercal}{\psi_{AB}\psi_{BC}\psi_{CA}} \eq \label{eq:pure_state_quantum_triangle} \]
     Avoiding the expensive matrix multiplications of \cref{eq:triangle_quantum_distributions}.
@@
     Analogously to \cref{eq:pure_state_quantum_triangle}, projective measurements offer considerable computational advantage as \cref{eq:triangle_quantum_distributions} can be rewritten as,
-    \[ \prob[ABC]\br{abc} = \bramidket{m_{A,a}m_{B,b}m_{C,c}}{\Omega^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \Omega}{m_{A,a}m_{B,b}m_{C,c}} \eq \label{eq:pure_meas_quantum_triangle} \]
+    \[ \prob[ABC]\br{abc} = \bramidket{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{A,a}m_{B,b}m_{C,c}} \eq \label{eq:pure_meas_quantum_triangle} \]
 
@@
         \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../figures/perm_mtrx.pdf}
-        \caption{The network permutation matrix $\Omega$ for $\br{\Hilb^2}^{\otimes 6}$ realized on the triangle scenario. Black represents a value of $1$ and $0$ otherwise.}
+        \caption{The network permutation matrix $\netperm$ for $\br{\Hilb^2}^{\otimes 6}$ realized on the triangle scenario. Black represents a value of $1$ and $0$ otherwise.}
         \label{fig:perm_mtrx}
     \end{figure}
-    Finally, we introduce the \term{network permutation matrix} $\Omega$ for the Triangle Scenario of \cref{fig:triangle_scenario}.
-For bipartite qubit states, $\Omega$ becomes a $64\times64$ bit-wise matrix that acts on the measurements $M$ and is depicted in \cref{fig:perm_mtrx}.
-To illuminate its necessity, consider \cref{eq:triangle_quantum_distributions} without $\Omega$.
+    Finally, we introduce the \term{network permutation matrix} $\netperm$ for the Triangle Scenario of \cref{fig:triangle_scenario}.
+For bipartite qubit states, $\netperm$ becomes a $64\times64$ bit-wise matrix that acts on the measurements $M$ and is depicted in \cref{fig:perm_mtrx}.
+To illuminate its necessity, consider \cref{eq:triangle_quantum_distributions} without $\netperm$.
     \begin{align*}
@@
 This is analogously troubling for $B$ and $C$ as well.
-The network permutation matrix $\Omega$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$.
+The network permutation matrix $\netperm$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$.
 To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
-    \[ \Omega\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
-    $\Omega$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''.
+    \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
+    $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''.
 It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
-    \[ \Omega \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
+    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
     \subsection{Degeneracy}

### 2016-10-20 document/main.tex
Some progress

@@
 \newcommand{\trans}{\mathcal{T}}
-\newcommand{\ind}{\mathcal{I}}
+\newcommand{\ind}{S}
+\newcommand{\inhibit}{\mathcal{I}}
 \newcommand{\netperm}{\Pi}
@@
 \newcommand{\jointvar}{\mathcal{J}}
-\newcommand{\mset}[1]{\gamma^{#1}}
-\newcommand{\extmset}[1]{\Gamma^{#1}}
+\newcommand{\mset}{\gamma}
+\newcommand{\extmset}{\Gamma}
 \newcommand{\supp}[1]{\si\br{#1}}
+\newcommand{\kone}{\mathbf{1}}
+\newcommand{\kzer}{\textcolor{gray}{0}}
 
@@
 \setoperator{Perm} % Permutation group
-\setoperator{Out} % Outcome space
-\setoperator{Dom} % Domian
+% \setoperator{Out} % Outcome space
+\newcommand{\Sect}[1]{\s{S}\br{#1}} % Outcome space
+\newcommand{\Dom}[1]{\s{D}\br{#1}} % Domian
 % \setoperator{Dom} % Domian
@@
     \section{Introduction}
-    \todo[TC]{Discuss why the marginal problem is important.}
-    \section{Definitions \& Notation}
-    \comment[TC]{This entire section should be integrated into the body when logical to do so.}
-    \begin{definition}
-        Following common notation used in \cite{Fritz_2011}, we use the notation $\bs{k} = \bc{1, \ldots, k}$ to be a finite index set.
-Moreover, when referencing a finite set with $k$ elements, we can write,
-        \[ A_{\bs{k}} \defined \bc{A_i}_{i \in \bs{k}} = \bc{A_1, \ldots, A_k} \]
-    \end{definition}
-    \begin{definition}
-        \label{def:outcome_space}
-        Each random variable $v$ has a set of possible outcomes which are labeled by \term{outcome labels} $O_v$.
-The set of all outcomes themselves is its \term{outcome space} and is represented by the set of all functions from $v$ to $O_v$\footnote{Using functional language for outcome events is necessary for a sheaf-theoretic treatment of contextuality \cite{Abramsky_2011}.},
-        \[ \Out{v} \defined \bc{f : \bc{v} \to O_v} \]
-        Each of these functions has a singular domain ($v$) and thus can be concisely written in a compact form $\bc{v \mapsto o}$ where $o \in O_v$ represents some generic outcome label.
-Each function $f$ should be interpreted as the \textit{event} that $v$ obtains the outcome $o$, as well as the function that takes $v$ to $o$ $\bc{v \mapsto f\br{v} = o}$.
-Evidently $\Out{v}$ is isomorphic to $O_v$, and in many cases the two can be considered equivalent; however we make this particular semantic distinction now in preparation of \cref{sec:symmetry}.
-    \end{definition}
-
-    \begin{definition}
-        % This notation generalizes to more than one variable. Letting $V = \bc{v_1, v_2}$, we define $\Out{V}$ to be the set of all joint valuations of $v_1$ and $v_2$.
-        % Where the valuation product between outcome spaces is defined as follows,\footnote{At this level, a valuation product behaves analogously to a Cartesian product.
-However in \cref{def:extendable_set}, we define the a valuation product between outcomes and outcomes spaces.}
-        % \[ \Out{V} = \Out{\bc{v_1, v_2}} \defined \bc{f : \bc{v_1, v_2} \to \bc{O_{v_1}, O_{v_2}} \mid f\br{v_i} \in O_{v_i}, i \in \bc{1,2}}  \]
-        As a natural generalization, when considering a larger set of random variables $V = \bc{v_i}_{i \in \bs{k}}$ we define the joint outcome space in an analogous way,
-        \[ \Out{V} \defined \bc{f: \bc{v_i}_{i \in \bs{k}} \to \bc{O_{v_i}}_{i \in \bs{k}} \mid \forall i \in \bs{k} : f\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
-        Each outcome $f$ can be compactly represented as a set of mappings over each element of $V$.
-        \[ f = \bc{v_1 \mapsto f\br{v_1}, \ldots, v_k \mapsto f\br{v_k}} = \bc{v_i\mapsto f\br{v_i}}_{i \in \bs{k}} \]
-        The domain of $f$ refers to the set of random variables it valuates and is denoted as $\Dom{f}$. If $f \in \Out{V}$, then $\Dom{f} = V$.
-        % Where the joint outcome labels are elements of a Cartesian product,
-        % \[ O_V \defined O_{v_1} \times \cdots \times O_{v_{\abs{V}}}  \]
-
-        % And a generic, unspecified joint outcome in $\Out{V}$ is written as $\outc{V}$ in a similar fashion to \cref{def:outcome_space} and is represented by a tuple of individual outcomes.
-        % \[ \outc{V} \defined \br{\outc{v_1}, \ldots, \outc{v_{k}}} = \br{\outc{v}}_{v \in V} \eq \label{eq:outcomespace}\]
-        % It is important to note that the ordering of events in \cref{eq:outcomespace} is irrelevant.
-         % The definition of a valuation product can also be extended to outcomes themselves.
-Let $A$ and $B$ be sets of random variables and let $\outc{A} \in \Out{A}$ and $\outc{B} \in \Out{B}$.
-If $$
-    \end{definition}
-
+    \todo[TC]{Mention Bell's work} \\
+
+    \todo[TC]{Violations of inequalities correspond to resources} \\
+
+    \todo[TC]{Finding inequalities is hard} \\
+
+    \todo[TC]{Causal inference is a great lens to answer these questions} \\
+
+    \todo[TC]{Demonstrated the usefulness of the inflation technique} \\
+
+    \todo[TC]{Definite Extension procedure} \\
+
+    \todo[TC]{Optimizations against inequalities} \\
+
+    \section{Compatibility, Contextuality and the Marginal Problem}
+    \label{sec:comp_con_mp}
+
+    \subsection{Preliminary Notions}
+    \label{eq:comp_con_mp_notions}
+    A reoccurring motif of these discussions will be a set of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_k]}$.
+In agreement with~\cite{Fritz_2011} we adopt the following definitions and notation.
+
+    \begin{definition}
+        \label{def:marginal_model}
+        A set of random variables $\jointvar = \bc{v_1, \ldots, v_n}$ is referred to as the \term{joint random variables} when denoted with a $\jointvar$.
+A subset of joint variables $V \subset \jointvar$ is called \term{marginal context}.
+A collection of marginal contexts is called the \term{marginal scenario}\footnote{Rigorously speaking as defined by~\cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that $V' \in \mscenario$ whenever $V' \subseteq V \in \mscenario$.
+Throughout this document, we only consider the \textit{maximal marginal scenario}; restricting our focus to the largest contexts in the marginal scenario $\forall i,j \in 1, \ldots, k: V_i \not \subseteq V_j$.} and is denoted $\mscenario$\footnote{It is also assumed that the marginal scenario covers the joint variables $\jointvar = \bigcup_{i = 1}^{k} V_i$.}.
+        \[ \mscenario \defined \bc{V_1, \ldots, V_k \mid V_i \subseteq \jointvar} \]
+        Additionally, the set of probability distributions $\bc{\prob[V_1], \ldots, \prob[V_k]}$ over the marginal scenario is called a \term{marginal model} is compactly denoted $\prob^{\mscenario}$.
+    \end{definition}
+    A specific marginal model $\prob^{\mscenario}$ for a marginal scenario $\mscenario$ abstractly represents a set of measurements or observations made on a physical system.
+Associated with the physical system are physical models or causal structures.
+
+    \begin{definition}
+        A \term{causal structure} is a directed acyclic graph (DAG) $\graph = \br{\nodes, \edges}$ with the extra distinction between two classes of nodes: the \term{latent nodes} $\nodes_L$ and \term{observed nodes} $\nodes_O$.
+    \end{definition}
+    The latent nodes of a causal structure correspond aim to represent completely general hidden variables that are hidden by some fundamental process or cannot be measured due to other limitations.
+The observed nodes represent random variables that are measurable and in practice will be observed as a collection of marginal contexts $\mscenario$.
+Any observation over this particular marginal scenario is expressible as a marginal model $\prob^{\mscenario}$.
+The field of causal inference aims to answer the looming question: \text{Is the observed marginal model compatible with the hypothesized causal structure?} \\
+
+    In order to determine if a given marginal model $\prob^{\mscenario}$ is compatible with a causal structure $\graph$, a formal notion of \textit{compatibility} is warranted; first for a single marginal distribution $\prob[V]$ and then for a complete marginal model $\prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]}$.
+
+    \begin{definition}
+        A set of \term{causal parameters} for a particular causal structure $\graph$ is the specification of a conditional distribution for every node $n \in \nodes$ given its parents in $\graph$.
+        \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \eq \label{eq:def:casual_param}\]
+    \end{definition}
+
+    \begin{definition}
+        \label{def:compatible}
+        A marginal distribution $\prob[V]$ is \term{compatible} with a causal structure $\graph$ if there exists a \textit{choice} of causal parameters such that $\prob[V]$ can be \textit{recovered} from the following series of operations:
+        \begin{enumerate}
+            \item Obtain a joint probability distribution over \textit{all} nodes of of the causal structure using the chosen casual parameters: $\prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}]$.
+            \item Marginalize over the latent nodes of $\graph$: $\prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes]$.
+            \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$: $\prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O]$
+        \end{enumerate}
+        If it is not possible for $\prob[V]$ to be recovered for \textit{any} choice of causal parameters, then $\prob[V]$ is \term{incompatible}.
+To generalize, a marginal model $\prob^{\mscenario}$ is compatible with $\graph$ if each distribution $\prob[V] \in \prob^{\mscenario}$ can be made compatible by the \textit{same} choice of causal parameters; otherwise it is incompatible.
+    \end{definition}
+
+    There are two reasons why a given marginal model $\prob^{\mscenario}$ would be deemed incompatible.
+One possibility is that the marginal model $\prob^{\mscenario}$ does not admit a joint distribution $\prob[\jointvar]$ such that it is impossible for requirement 3 of \cref{def:compatible} to hold\footnote{It is typical for $\nodes_O = \jointvar$.
+At the very least, it is demanded that $\jointvar \subseteq \nodes_O$.}.
+Alternatively, it could be possible that a joint distribution $\prob[\jointvar]$ exists but can not factor into causal parameters as per requirement 1 of \cref{def:compatible}.
+The former point-of-failure, namely the non-admission of a joint distribution, will be principle focus of this paper.
+Colloquially, the existence (or non-existence) of a joint distribution is referred to as \textit{the marginal problem}.
+
+    \begin{definition}
+        \label{def:marginal_problem}
+        \term{The Marginal Problem:} Given a marginal model $\prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]}$ marginal to the joint variables $\jointvar = \bigcup_{i} V_i$, does there exist a joint distribution $\prob[\jointvar]$ such that each given distribution $\prob[V_i]$ can be obtained by marginalizing $\prob[\jointvar]$?
+        \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \eq \label{eq:def:marginal_problem}\]
+        Following definition 2.3 in~\cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a joint distribution $\prob[\jointvar]$ and \term{non-contextual} otherwise.
+    \end{definition}
+
+    There are two perspectives that can be taken when trying to answer the marginal problem.
+The first comes as stated by \cref{def:marginal_problem}; when inured with a particular marginal model $\prob^{\mscenario}$, can you construct a joint distribution that satisfies \cref{def:marginal_problem}?
+Alternatively and more abstractly, when provided a marginal \textit{mscenario} $\mscenario$ what is the set of all marginal models that are (non-)contextual?
+To facilitate future discussions, let $\s{NC}$ denote the set of marginal models that are non-contextual (admitting a joint distribution) and let $\s{C}$ denote the set of contextual marginal models.
+It becomes desirable to identifying conditions that constrain either $\s{NC}$ or $\s{C}$.
+We will continue to refer to a \term{complete solution marginal problem} as a finite set of necessary and sufficient conditions able to discern if a given marginal model $\prob^{\mscenario}$ is in $\s{NC}$ or $\s{C}$.
+These constraints typically take the form of linear inequalities over probabilities $\prob^{\mscenario}$.
+
+    \begin{definition}
+        A \term{$\s{NC}$-inequality} $I_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every non-contextual marginal model $\prob^{\mscenario}$.
+    \end{definition}
+
+    In the \cref{sec:linear_program}, we will explore and briefly mention existing techniques for completely (or partially) solving the marginal problem.
+The basis of understanding being that \cref{eq:def:marginal_problem} is a \textit{linear} operation.
+In certain circumstances, \cref{eq:def:marginal_problem} can be represented as a matrix operation.
+
+    \todo[TC]{Maybe define the possibilistic marginal problem for later} \\
+
+    \subsection{Casting the Marginal Problem as a Linear Program}
+    \label{sec:linear_program}
+
+    Heretofore, our discussions of compatibility, contextuality and the marginal problem have be completely general, making no reference to the nature of the outcomes of the random variables $\jointvar$; whether they be discrete or continuous, finite or unbounded, or otherwise.
+\todo[TC]{It is entirely possible to obtain complete solutions to the marginal problem for continuous and unbounded measure spaces using entropic inequalities.
+[Elaborate and reference]} In this paper we restrict our attention to finite outcomes.
+In particular, we will focus on marginal scenarios that are finite but have a large number of outcomes.
+To assist with the subsequent analysis, we recall some familiar notions of probability theory together with new terminology and notation.
+\\
+
+    \subsubsection{Sections}
+    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$.
+We also define the set of all \term{sections over $v$} $\Sect{v}$\footnote{Technically $\Sect{v}$ can be called a \textit{sheaf} but we neglect to introduce that terminology here.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
+    \[ \Sect{v} \defined \bc{s : \bc{v} \to O_v} \label{eq:outcome_space} \]
+    Making the unfamiliar distinction between sections $s$ and outcomes in $O_v$ might seem pedantic.
+Evidently, $\Sect{v}$ and $O_v$ have a one-to-one correspondence.
+There is rarely any harm in referring synonymously to either as outcomes.
+Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
+    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetry}.
+As a natural generalization we define the tuple sections for collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
+    \[ \Sect{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
+    Each section $s$ can be compactly represented as a set of mappings over each element of $V$.
+    \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
+    The domain $\Dom{s}$ of an section $s$ is the set of random variables it valuates, i.e. if $s \in \Sect{V}$, then $\Dom{s} = V$.
     \begin{example}
-        Interpreting $f \in \Out{V}$ as an \textit{event} or \textit{outcome} on $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][f]$ to $f$.
+        Let $s \in \Sect{V}$ be a section over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$.
 Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$.
-Furthermore let $f \in \Out{V}$ be the outcome $\br{v_1 \mapsto 2, v_2 \mapsto 1}$.
-The following class of notations will be considered interchangeable,
-        \[ \prob[V][f] = \prob[v_1, v_2][f] = \prob[][v_1 \mapsto f_1\br{v_1}, v_2 \mapsto f_2\br{v_2}] = \prob[][v_1 \mapsto 2, v_2 \mapsto 1] = \prob[v_1v_2][21] \]
-        Each of which should be read as ``the probability that $v_1$ gets outcome $2$ AND $v_2$ gets outcome $1$''.
+Furthermore let $f \in \Sect{V}$ be the section $\br{v_1 \mapsto 2, v_2 \mapsto 1}$.
+Then the following notations are interchangeable,
+        \[ \prob[][s] = \prob[\Dom{s}][s] = \prob[V][s] = \prob[v_1, v_2][s] = \prob[][v_1 \mapsto s_1\br{v_1}, v_2 \mapsto s_2\br{v_2}] = \prob[][v_1 \mapsto 2, v_2 \mapsto 1] = \prob[v_1v_2][21] \]
+        Each of which should be read as ``the probability that $v_1$ got outcome $2$ and $v_2$ got outcome $1$''
     \end{example}
+    \begin{definition}
+    \label{def:section_restriction}
+    For every $W \subseteq V$ and $s \in \Sect{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Sect{W}$) is the section in $\Sect{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
+    \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
+    \end{definition}
+    \begin{definition}
+    \label{def:section_compatible}
+    The sections $s_{V} \in \Sect{V}$ and $s_{W} \in \Sect{W}$ are said to be \term{compatible} sections if they agree on their valuations of $V \cap W$.
+Compatibility will be denoted with the infix `$\com$'.
+    \[ s_{V} \com s_{W} \iff {s_{V}}|_{V\cap W} = {s_{W}}|_{V\cap W} \]
+    \end{definition}
+    \begin{definition}
+    \label{def:section_extendable}
+    It $s_V \in \Sect{V}$ and $s_W \in \Sect{W}$ compatible sections and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
+    \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
+    Extendability is dual to the notion of a \term{restriction} of $s_V$; $s_V$ can be restricted to $s_W$ ($s_V \res s_W$) if and only if $s_W$ is extendable to $s_V$.
+    \end{definition}
 
     \begin{remark}
-        \label{rem:domain_dist}
-        In each of the above notations, $\prob[V]$ always represents a probability distribution over the \textit{domain} of $f \in \Out{V}$.
-In cases where the subscript is omitted, it should be assumed to be over the domain of $f$.
-        \[ \prob[V][f] = \prob[\Dom{f}][f] = \prob[][f] \]
+        The notation `$s \com t$' is used to indicate compatibility between $s \in \Sect{V}$ and $t \in \Sect{W}$ because of the following observation: $s$ and $t$ are compatible if and only if they are extensions of some outcome $r \in \Sect{V \cap W}$.
+        \[ s \com t \iff \exists r \in \Sect{V \cap W} \mid s \res r \ext t \]
+        In fact $r$ is uniquely defined.
+        \[ \forall v \in V \cap W : r\br{v} = s\br{v} = t\br{v} \]
     \end{remark}
@@
     \begin{definition}
-        \label{def:restriction}
-        Let $V = \bc{v_1, \ldots, v_k}$ be a set of random variables and $W \subseteq V$ be a subset of $V$.
-Moreover, let $f \in \Out{V}$ be a joint outcome over $V$; assigning a unique label to each variable in $V$.
-The \term{restriction of $f$ onto $W$} (denoted $f|_{W} \in \Out{W}$) is the outcome of $\Out{W}$ that \textit{agrees} with each of $f$'s assignments for variables in $W$.
-        \[ \forall v \in W : f\br{v} = f|_{W}\br{v} \]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:outcome_compatible}
-        Consider two sets of random variables $V$ and $W$ and two specific outcomes $f_V \in \Out{V}$ and $f_W \in \Out{W}$.
-The outcomes $f_V$ and $f_W$ are said to be \term{compatible} if they agree on their valuations of $V \cap W$.
-Compatibility will be denoted with `$\com$'.
-        \[ f_V \com f_W \iff {f_V}|_{V\cap W} = {f_W}|_{V\cap W} \]
-        Compatibility is a reflexive and symmetric, but \textit{not} transitive.
-There are two cases when compatibility is transitive; whenever $V \cap W = \emptyset$ or $V = W$.
-Whenever $V \cap W = \emptyset$, $f_V$ and $f_W$ can be said to be \textit{trivially} compatible.
-Moreover if $V = W$, compatibility becomes ordinary equivalence,
-        \[ V = W \quad \textrm{and} \quad f_V \com f_W \iff f_V = f_W \]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:extendable}
-        Let $f_V \in \Out{V}$ and $f_W \in \Out{W}$ be outcomes of $V$ and $W$ respectively as in \cref{def:outcome_compatible}.
-If $f_V$ and $f_W$ are compatible, and $W \subseteq V$ then $f_W$ is said to be \term{extendable} to $f_V$ and is denoted `$\ext$'.
-        \[ f_W \ext f_V \iff f_W \com f_V \quad \textrm{and} \quad W \subseteq V \iff {f_W} = {f_V}|_{W} \]
-        The dual language is also appropriate: $f_W$ is a \term{restriction} of $f_V$ (denoted $f_V \res f_W$) if and only if $f_W$ is extendable to $f_V$.
-If $f_W \ext f_V$ then there exists a unique element $f_{V \setminus W} \in \Out{V \setminus W}$ such that $f_V$ can be reconstructed by gluing together $f_{V \setminus W}$ and $f_W$.
-        \[ \forall v \in V : f_V\br{v} = \begin{cases}
-            f_W\br{v} & v \in W \\
-            f_{V\setminus W}\br{v} & v \in V \setminus W
-        \end{cases}  \]
-    \end{definition}
-
-    \begin{remark}
-        The notation `$g \com h$' is used to indicate compatibility between $g \in \Out{V}$ and $h \in \Out{W}$ because of the following observation; $g$ and $h$ are compatible if and only if extensions of some outcome $f \in \Out{V \cap W}$.
-        \[ g \com h \iff \exists f \in \Out{V \cap W} \mid g \res f \ext h \]
-        In fact, such an $f$ is uniquely defined,
-        \[ \forall v \in V \cap W : f\br{v} = g\br{v} = g\br{v} \]
-    \end{remark}
-
-    \begin{definition}
         \label{def:extendable_set}
-        The set of all extendable outcomes of $f \in \Out{W}$ into $V$ is called the \term{extendable set of $f$ into $V$} and can be written as,
-        \[ \Ext[V]{f} \defined \bc{g \in \Out{V} \mid f \ext g} \subseteq \Out{V} \]
-        The extendable set of $f$ into $V$ is the subset of outcomes in $\Out{V}$ that \textit{agree} with $f$ about valuations for variables in $W$.
+        The set of all extendable sections of $s \in \Sect{W}$ into $V$ is called the \term{extendable set of $s$ into $V$}.
+        \[ \Ext[V]{s} \defined \bc{g \in \Sect{V} \mid s \ext g} \subseteq \Sect{V} \]
+        The extendable set of $s$ into $V$ is the subset of sections in $\Sect{V}$ that \textit{agrees} with $s$ about valuations for variables in $W$.
     \end{definition}
@@
 Further impose that the outcome labels for each variable are the same: $O_a = O_b = O_c = \bc{0,1,2}$.
-As an example, let $f = \bc{a \mapsto f\br{a} = 1, b \mapsto f\br{b} = 2} \in \Out{W}$; $f$ is extendable to the outcome $g = \bc{a \mapsto g\br{a} = 1, b \mapsto g\br{b} = 2, c \mapsto g\br{c} = 1} \in \Out{V}$, and the extendable set of $f$ into $V$ is,
-        \[ \Ext[V]{f} = \Ext[a,b,c]{a \mapsto 1, b \mapsto 2} = \bc{\bc{a \mapsto 1, b \mapsto 2, c \mapsto 0}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 1}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 2}} \]
+As an example, let $s = \bc{a \mapsto s\br{a} = 1, b \mapsto s\br{b} = 2} \in \Sect{W}$.
+The extendable set of $s$ into $V$ is,
+        \[ \Ext[V]{s} = \Ext[a,b,c]{a \mapsto 1, b \mapsto 2} = \bc{\bc{a \mapsto 1, b \mapsto 2, c \mapsto 0}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 1}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 2}} \]
     \end{example}
 
+    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint sections} $\Sect{\jointvar}$.
+Similarly we define the \term{context sections} $\bc{\Sect{V} \mid V \in \mscenario}$.
+Finally, we elect to define the disjoint union of all context sections are called the \term{marginal sections} and by an abuse of notation we will denote this disjoint union as $\Sect{\mscenario}$.
+    \[ \Sect{\mscenario} = \coprod_{V \in \mscenario} \Sect{V} \]
+    Each marginal section $m \in \Sect{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
+    \subsubsection{Linear Programs}
+    \label{sec:linear_programs}
+
+    We are now fully equipped to write the marginal problem as a matrix multiplication.
+    \begin{definition}
+        \label{def:incidence_matrix}
+        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} sections $j \in \Sect{\jointvar}$ and the rows are indexed by \textit{marginal} sections $m \in \Sect{\mscenario}$.
+The entries of $M$ are populated whenever a row index is extendable to a column index.
+        \[ M_{m,j} = \de_{m \ext j} \defined \begin{cases}
+            1 & m \ext j \\
+            0 & \text{otherwise}
+        \end{cases} \]
+        Where $\de_{m \ext j}$ is termed the \term{extendability indicator}.
+The incidence matrix has $\abs{\Sect{\jointvar}}$ columns, $\abs{\Sect{\mscenario}} = \sum_{i} \abs{\Sect{V_i}}$ rows and $k\abs{\Sect{\jointvar}}$ non-zero entries.
+    \end{definition}
+    To illustrate this concretely, consider the following example:
+    \begin{example}
+        \label{ex:incidence_matrix}
+        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{a,b}, \bc{b,c}, \bc{a,c}}$. The incidence matrix becomes:
+        \[ M = \kbordermatrix{
+            (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
+            (a\mapsto0, b\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
+            (a\mapsto0, b\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
+            (a\mapsto1, b\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
+            (a\mapsto1, b\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
+            (b\mapsto0, c\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
+            (b\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
+            (b\mapsto1, c\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
+            (b\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
+            (a\mapsto0, c\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
+            (a\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
+            (a\mapsto1, c\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
+            (a\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
+        } \eq \label{eq:example_incidence}\]
+    \end{example}
+
+    \begin{definition}
+        The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint section $j \in \Sect{\jointvar}$.
+$\probvec^{\jointvar}$ shares the same indices as the \textit{column} indices of $M$.
+        \[ \forall j \in \Sect{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
+    \end{definition}
+    \begin{definition}
+        The \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Sect{\mscenario}$.
+$\probvec^{\mscenario}$ shares the same indices as the \textit{row} indices of $M$.
+        \[ \forall m \in \Sect{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
+    \end{definition}
+    The marginal and joint distribution vectors are related via the incidence matrix $M$.
+Given a joint distribution vector $\probvec^{\jointvar}$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec^{\jointvar}$.
+    \[ \probvec^{\mscenario} = M \cdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
+    Henceforth we will use $\probvec^{\jointvar}$ ($\probvec^{\mscenario}$) and $\prob[\jointvar]$ ($\prob^{\jointvar}$) interchangeably.
+
+    \begin{remark}
+        The particular ordering of the rows and columns of $M$ carries no importance, but it \textit{must} be consistent between $M$, $\probvec^{\jointvar}$ and $\probvec^{\mscenario}$.
+    \end{remark}
+
+    The marginal problem can now be rephrased in the language of the incidence matrix.
+Suppose one obtains a marginal distribution vector $\probvec^{\mscenario}$.
+The marginal problem becomes equivalent to the question: \textit{Does there exist a joint distribution vector $\probvec^{\jointvar}$ such that \cref{eq:incidence_matrix_use} holds?}
+
+    % \begin{example}
+    %     The marginal problem for the inflated causal structure $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} concerns itself with the pre-injectable marginal scenario $\mscenario = \PreInj[\ts]{\ts'} = \bc{V_1, \ldots, V_{12}}$.
+Equipping the observed nodes of $\ts'$ with $4$-element outcome labels, the incidence matrix $M$ has $16,896$ rows and $16,777,216$ columns.
+    %     \begin{align*}
+    %         &\text{\# Rows} = \abs{\Sect{\mscenario}} = \sum_{i=1}^{12} \abs{\Sect{V_i}} = \sum_{i=1}^{12} 4^{\abs{V_i}} = 4 \cdot 4^6 + 8 \cdot 4^3 = 16,896 \\
+    %         &\text{\# Columns} = \abs{\Sect{\jointvar}} = 4^{\abs{\jointvar}} = 4^{12} = 16,777,216
+    %     \end{align*}
+    %     With $12 \cdot 4^{12} = 201,326,592$ non-zero entries. For obvious reasons, no attempt is made to reproduce it here.
+    % \end{example}
+    \begin{definition}
+        \label{def:marginal_linear_program}
+        \term{The Marginal Linear Program} is the following linear program:
+        \begin{alignat*}{2}
+            & \text{minimize:} \quad&& \emptyset \cdot x\\
+            & \text{subject to:} && x \succeq 0 \\
+            & && M \cdot x = \probvec^{\mscenario}
+        \end{alignat*}
+        If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries).
+The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:incidence_matrix_use} and is a valid joint distribution vector.
+Therefore feasibility implies that $\probvec^{\jointvar} = x$.
+Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\probvec^{\jointvar}$ over all random variables.
+    \end{definition}
+    \todo[TC]{Talk about about the linear solvers and how this is easy to implement.}
+    \begin{definition}
+        \label{def:dual_marginal_linear_program}
+        \term{The Dual Marginal Linear Program} is the dual of \cref{def:marginal_linear_program} formulated via a procedure similar to~\cite{Lahaie_2008}:
+        \begin{alignat*}{2}
+            & \text{minimize:} \quad&& y \cdot \probvec^{\mscenario}\\
+            & \text{subject to:} && y \cdot M \succeq 0
+        \end{alignat*}
+        Where $y$ is a real valued vector with the same length as $\probvec^{\mscenario}$.
+    \end{definition}
+
+    The dual marginal linear program not only answers the marginal problem for a specific marginal model $\probvec^{\mscenario}$ but as a by-product provides an inequality that witnesses its contextuality.
+First notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints become satisfied.
+Secondly if the dual constraint $y \cdot M \succeq 0$ holds and the primal is feasible, then the following must hold:
+    \[ y \cdot \probvec^{\mscenario} =  y \cdot M \cdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
+    Therefore the \textit{sign} of the dual value $d \defined \min \br{y \cdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality.
+If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore $\probvec^{\mscenario}$ is contextual.
+Likewise if $d \geq 0$ (satisfying \cref{eq:dual_marginal_ineq}), then $\probvec^{\mscenario}$ is non-contextual.
+\footnote{Actually, if $d \geq 0$ then it is exactly $d = 0$ due to the existence of the trivial $y = \emptyset$.
+This observation is an instance of the \textit{Complementary Slackness Property} of~\cite{Bradley_1977}.
+\comment[TC]{Is this really the CSP?} Moreover, if $d < 0$, then it is unbounded $d = -\inf$.
+This latter point becomes clear upon recognizing that for any $y$ with $d < 0$, another $y' = \al y$ can be constructed (with $\al > 1$) such that $d' = \al d < d$.
+Since a more negative $d'$ can always be found, it must be that $d$ is unbounded.
+This is a demonstration of the fundamental \textit{Unboundedness Property} of~\cite{Bradley_1977}; if the dual is unbounded, then the primal is infeasible.
+\comment[TC]{\href{http://web.stanford.edu/~ashishg/msande111/notes/chapter4.pdf}{Farkas's lemma} here?}}
+
+    \begin{definition} An \term{infeasibility certificate}~\cite{Andersen_2001} is any vector $y$ that satisfies the constraint of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
+    \[ y \in \R^{\abs{\Sect{\mscenario}}} : y \cdot M \succeq 0, \quad y \cdot \probvec^{\mscenario} < 0 \]
+    Furthermore, any $y$ satisfying $y \cdot M \succeq 0$ can be promoted to a \term{certificate inequality} that constraints the set of non-contextual marginal models $\s{NC}$,
+    \[ \forall \probvec^{\mscenario} \in \s{NC} : y \cdot \probvec^{\mscenario} \geq 0 \]
+    \end{definition}
+
+    \todo[TC]{Discuss Infeasibility Certificates basis} \\
+
+    \todo[TC]{Discuss the certificate inequalities we found.} \\
+
+    \todo[TC]{Discuss Compatibility, connection to cooperative games/resources, bell incompatibility?} \\
+
+    \subsubsection{Fourier Motzkin Elimination}
+    The complete space of marginal models over $\mscenario$ can be partitioned into two spaces; non-contextual marginal models in $\s{NC}$ and contextual ones in $\s{C}$.
+
+    \todo[TC]{Logical Bell inequalities paper: only need to consider rational inequalities, actually integer inequalities, actually homogeneous inequalities} \\
+    \todo[TC]{Discuss computational complexity} \\
+    \todo[TC]{Mention what a complete solution looks like after using Fourier Motzkin}
+    \subsubsection{Marginal Polytope}
+    \todo[TC]{Very briefly discuss polytope perspective and facet inequalities vs. non-facet inequalities}
+    \todo[TC]{Define facets as irreducible inequalities}
+
+    \todo[TC]{Maybe put the description of our task here. This will motivate the need for more scalable approaches.}
+
+    \section{Transversal Inequalities}
+
+    Section \ref{sec:linear_programs} discusses how one can obtain a $\s{NC}$-inequality that witnesses the contextuality of a particular marginal model $\probvec^{\mscenario}$ by writing the marginal problem as a linear program.
+Every $\probvec^{\mscenario} \in \s{NC}$ is witness-able by some certificate inequality.
+Albeit when a candidate marginal model $\probvec^{\mscenario}$ is not present, linear optimization offers no utility.
+\\
+
+    This Section aims to develop a procedure for finding \textit{all} certificate inequalities in a computationally efficient manner.
+Specifically by finding all certificate inequalities that are also facets of the marginal polytope.
+Before doing so, we will first summarize a method that can be used to obtain a complete solution to the \textit{possibilistic} marginal problem and indirectly offer a \textit{partial} solution to the \textit{probabilistic} marginal problem.
+
+    \subsection{Hardy Transversals}
+    \label{sec:logical_inequalities}
+    Let $a \in \Sect{\mscenario}$ be any marginal section and $C = \bc{c_1, \ldots, c_{n}} \subseteq \Sect{\mscenario}$ be a subset of the marginal sections.
+Recall that $a, c_1, \ldots, c_n$ are particular \textit{events} over marginal contexts $V \in \mscenario$.
+We say that the subset $C$ forms a \term{logical extension} of $a$ if the following logical implication holds for \textit{all} marginal models $\probvec^{\mscenario}$.
+    \[ a \implies c_1 \vee \ldots \vee c_n = \bigvee_{c \in C} c \eq \label{eq:1a_implication} \]
+    Which can be dictated: \textit{Whenever the event $a$ occurs, at least one the events in $C$ occurs.} In this paper, the marginal event $a$ will be referred to as the \textit{antecedent} and $C$ as the \textit{consequent set}.
+To clarify, a marginal model $\probvec^{\mscenario}$ satisfies \cref{eq:1a_implication} if there always exists at least one $c \in C$ that is possible ($\probvec^{\mscenario}_c > 0$) whenever $a$ is possible.
+A marginal model $\probvec^{\mscenario}$ violates \cref{eq:1a_implication} whenever \textit{none} of the sections in $C$ are possible while $a$ is nonetheless still possible.
+Marginal models that violate logical statements such as \cref{eq:1a_implication} are known as \term{Hardy Paradoxes}~\cite{Inflation,Mansfield_2012,Mancinska_2014}.
+The concept of witnessing quantum incompatibility on a logical level has been analyzed thoroughly for decades~\cite{Greenberger_1990,Abramsky_2012}; being motivated by a greater sense of robustness compared to probabilistic constraints.
+\\
+
+    All logical implications of the form \cref{eq:1a_implication} can be constructed by first selecting $a$ and then configuring $C$ persuant to \cref{eq:1a_implication}.
+    \begin{definition}
+        \label{def:extendable_set}
+        For each marginal section $m \in \Sect{\mscenario}$ the \term{extendable set of $m$ into $\jointvar$} is the set of all joint sections $j \in \Sect{\jointvar}$ that are extensions of $m$.
+        \[ \Ext[\jointvar]{m} = \bc{j \in \Sect{\jointvar} \mid m \ext j} \]
+    \end{definition}
+    Practically speaking, the extendable set of $m$ into $\jointvar$ is represented by the $m$-th row of the incidence matrix $M$.
+    \begin{lemma}
+        \label{lemma:logical_extenable_set}
+        Let $a \in \Sect{\mscenario}$ and $\probvec^{\mscenario} \in \s{NC}$ be non-contextual. Then,
+        \[ a \iff \bigvee_{j \in \Ext[\jointvar]{a}} j \eq \label{eq:lemma_logical_extendable_set}\]
+    \end{lemma}
+    The idea being if a joint distribution does exists, then the event $a$ represents partial knowledge of the entire system $\jointvar$; whenever $a$ occurs, exactly one joint section $j$ has occurred and $j$ must be compatible with $a$.
+Likewise \cref{lemma:logical_extenable_set} applies to the consequent set $C \in \Sect{\mscenario}$,
+    \[ \bigvee_{c \in C} c \iff \bigvee_{c \in C} \bigvee_{j \in \Ext[\jointvar]{c}} j \eq \label{eq:logical_extension_C}\]
+    If a subset $C$ can be found such that its extendable set \textit{covers} the extendable set of $a$,
+    \[ \Ext[\jointvar]{a} \subseteq \bigcup_{c \in C} \Ext[\jointvar]{c} \eq \label{eq:logical_containment} \]
+    Then the combination of \cref{eq:lemma_logical_extendable_set,eq:logical_extension_C,eq:logical_containment} yields \cref{eq:1a_implication}.\\
+
+    It is possible to show that for each logical constraint there exists a probabilistic constraint that is tighter.
+The principle statement of \cref{lemma:logical_extenable_set} can be taken in a probabilistic form.
+If the marginal model $\probvec^{\mscenario}$ is to admit a joint distribution $\probvec^{\jointvar}$, then it must be that the antecedent probability $a\in \Sect{\mscenario}$ ($\probvec^{\mscenario}_a = \prob[\Dom{a}][a]$) is equal to a marginalization over its extendable set into $\jointvar$.
+    \[ \probvec^{\mscenario}_a = \sum_{j \in \Ext[\jointvar]{a}}\probvec^{\jointvar}_j \eq \label{eq:marginal_extendable_sum_a} \]
+    This is nothing more than the the $a$-th row of \cref{eq:incidence_matrix_use}. Likewise for the consequent set,
+    \[ \sum_{c \in C}\probvec^{\mscenario}_c = \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\probvec^{\jointvar}_j \eq \label{eq:marginal_extendable_sum_cs} \]
+    Since $C$ is a logical extension of $a$, the right-hand side of \cref{eq:marginal_extendable_sum_a} \textit{algebraically} covers \cref{eq:marginal_extendable_sum_cs}\footnote{If there were a joint outcome $j^*$ present on the right-hand side of \cref{eq:marginal_extendable_sum_a} but not the right-hand side of \cref{eq:marginal_extendable_sum_cs}, then \cref{eq:1a_probabilistic} would be violated by the deterministic joint distribution where $\probvec^{\jointvar}_{j^*} = 1$}.
+Therefore one recovers the probabilistic version of \cref{eq:1a_implication},
+    \[ \probvec^{\mscenario}_a \leq \sum_{c \in C}\probvec^{\jointvar}_c \eq \label{eq:1a_probabilistic} \]
+    Because \cref{eq:1a_probabilistic}'s logical precedent, inequalities of the form of \cref{eq:1a_probabilistic} are called \term{Hardy inequalities}.
+    \todo[TC]{Discuss logical bell inequalities}
+    \begin{remark}
+        It is also possible to recover \cref{eq:1a_probabilistic} from \cref{eq:1a_implication} by more direct means by putting \cref{eq:1a_implication} into disjunction normal form and assigning it a certain probability,
+        \[ \prob[][\neg a \vee \bigvee_{c \in C} c] = 1 \]
+        Then applying Boole's indentity and the negative rule $\prob[][\neg a] = 1 - \prob[][a]$ one recovers \cref{eq:1a_probabilistic}.
+    \end{remark}
+    \begin{remark}
+        The probabilistic logical extension \cref{eq:1a_probabilistic} is an \textit{upgraded} version of \cref{eq:1a_implication} in the following sense.
+        \begin{itemize}
+            \item Every $\probvec^{\mscenario} \in \s{NC}$ satisfies both \cref{eq:1a_probabilistic} and \cref{eq:1a_implication}.
+            \item Every $\probvec^{\mscenario} \in \s{C}$ that violates \cref{eq:1a_implication} will also violate \cref{eq:1a_probabilistic}; but the converse is not necessarily true.
+        \end{itemize}
+    \end{remark}
+
+    Computationally enumerating all logical extensions $C \subseteq \Sect{\jointvar}$ for a particular antecedent $a \in \Sect{\mscenario}$ corresponds iteratively selecting marginal sections $c \neq a$ for membership in $C$ until \cref{eq:logical_containment} is satisfies.
+This process is more generally known as a set-covering problem, or a hypergraph transversal problem~\cite{Inflation}, an idea we return to in the more general picture to follow.
+
+    \subsection{Definite Extensions}
+    We will now generalize the notion of a Hardy transversal by considering multi-sets of antecedents corresponding to multiple marginal outcomes each accompanied by an assigned multiplicity.
+Afterwards we provide an algorithm to completely solve the marginal problem by transversing generalized hypergraphs.
+To our benefit, this technique for solving the marginal problem offers considerable advantages over existing methods when dealing with large marginal scenarios.
+\\
+
+    To facilitate the discussion, some definitions and notation are necessary.
+    \begin{definition}
+        A \term{multi-set} or \term{bag} $\mset{}$ for a marginal scenario $\mscenario$ is a vector indexed by marginal outcomes $m \in \Sect{\mscenario}$ whose entries are integers $\mset{}_{m} \in \Z$.
+The \term{support} $\supp{\mset{}}$ of an bag is the subset of marginal outcomes that are assigned non-zero multiplicity.
+        \[ \supp{\mset{}} \defined \bc{m \in \Sect{\mscenario} \mid \mset{}_m \neq 0} \]
+        The \term{order} $\abs{\mset{}}$ of a multi-set $\mset{}$ is entry-wise sum of $\mset{}$.
+        \[ \abs{\mset{}} = \sum_{m \in \Sect{\mscenario}} \mset{}_m = \sum_{m \in \supp{\mset{}}} \mset{}_m \]
+    \end{definition}
+
+    \begin{definition}
+        The \term{marginal indicator} vector $\de^{m}$ for a marginal outcome $m$ is the unit vector indexed by marginal outcomes $\Sect{\mscenario}$ whose only non-zero entry is the marginal outcome $m$.
+        \[ \forall m' \in \Sect{\mscenario} : \de^{m}_{m'} = \begin{cases}
+            1 & m' = m \\
+            0 & m' \neq m
+        \end{cases} \]
+        Analogously defined is the \term{joint indicator} vector $\de^{j}$.
+    \end{definition}
+
+    \begin{definition}
+        The \term{extension $\extmset{}$ of an multi-set $\mset{}$} for a marginal scenario $\mscenario$ is a vector indexed by \textit{joint} outcomes $j \in \Sect{\jointvar}$ and is constructed by merging the extendable sets of each marginal outcome $m \in \supp{\mset{}}$.
+        \[ \forall j \in \Sect{\jointvar} : \extmset{}_{j} \defined \sum_{m \in \supp{\mset{}}} \mset{}_{m} \de_{m \ext j}\]
+        Which is equivalent to a left-multiplication of $\ga$ into the incidence matrix $M$.
+        \[ \extmset{} \defined \mset{} \cdot M \]
+    \end{definition}
+
+    For every multi-set $\mset{}$ there corresponds a candidate inequality $I_{\mscenario} = \bc{\mset{} \cdot \probvec^{\mscenario} \geq 0}$ whose validity is completely characterized by the extension of $\mset{}$.
+    \begin{theorem}
+        \label{thm:deinite_extension_main_thm}
+        Let $\mset{}$ be a multi-set for the marginal scenario $\mscenario$.
+Then the inequality $I_{\mscenario} = \bc{\mset{} \cdot \probvec^{\mscenario} \geq 0}$ is a valid non-contextuality inequality if and only if $\extmset{}$ is positive semi-definite.
+        \[ \forall \probvec^{\mscenario} \in \s{NC} : \mset{} \cdot \probvec^{\mscenario} \geq 0 \iff \extmset{} \succeq 0 \qquad \forall j : \extmset{}_j \geq 0 \eq \label{eq:thm:semi_definite_extension}\]
+    \end{theorem}
+    \begin{proof}
+        The proof follows directly from \cref{eq:incidence_matrix_use}. Since $\probvec^{\mscenario} = M \cdot \probvec^{\jointvar}$,
+        \[ \mset{} \cdot \probvec^{\mscenario} = \mset{} \cdot M \cdot \probvec^{\jointvar} = \extmset{} \cdot \probvec^{\jointvar} \]
+        Thus $\extmset{} \succeq 0$ implies that $\extmset{} \cdot \probvec^{\jointvar} \geq 0$ which gives $\mset{} \cdot \probvec^{\mscenario} \geq 0$.
+The forward case of \cref{eq:thm:semi_definite_extension} can be proven by contradiction.
+Suppose that $\mset{} \cdot \probvec^{\mscenario} \geq 0$ for all marginal models but $\Ga \not \succeq 0$.
+There then must exist at least one joint outcome $\exists j^{*} : \Ga_{j^{*}} < 0$ such that the deterministic joint distribution $\probvec^{\jointvar} = \de^{j^{*}}$ induces contradiction,
+        \[ 0 > \extmset{}_{j^{*}} = \extmset{}\cdot \de^{j^{*}} = \mset{} \cdot M \cdot \de^{j^{*}}  \]
+        Because $M \cdot \de^{j^{*}}$ is a non-contextual marginal model but $\ga \cdot M \cdot \de^{j^{*}} \not \geq 0$.
+    \end{proof}
+    \begin{corollary}
+        Let $\mset{}$ be a multi-set for the marginal scenario $\mscenario$.
+Then the equality $I_{\mscenario} = \bc{\mset{} \cdot \probvec^{\mscenario} = 0}$ is satisfied by all non-contextual marginal models if and only if $\extmset{}$ is a null vector (i.e.
+$\forall j : \extmset{}_{j} = 0$).
+    \end{corollary}
+
+    \Cref{thm:deinite_extension_main_thm} demonstrates it is possible to generate non-contextuality inequalities by finding multi-sets $\mset{}$ such that $\Ga \succeq 0$.
+In light of this, we will formally define the subset of joint outcomes $j$ that are preventing a candidate multi-set $\mset$ from having positive semi-definite extensions.
+
+    \begin{definition}
+        The \term{inhibiting set} $\inhibit\br{\mset}$ for a multi-set $\mset$ is the subset of joint outcomes preventing $\extmset \succeq 0$ from holding true.
+        \[ \inhibit\br{\mset} = \bc{j \in \Sect{\jointvar} \mid \br{\mset \cdot M}_j = \extmset_j < 0} \]
+    \end{definition}
+
+    Clearly if the multi-set itself is positive semi-definite $\mset{} \succeq 0$ then $\extmset{} \succeq 0$ is maintained always.
+As such, it is desired to obtain multi-sets $\mset{}$ that have some positive and negative entires.
+Procedurally, definite extensions can be built by beginning with a seed multi-set $\mset{}^{} = \mset{}^{A}$ (to be called the antecedent set) composed entirely of non-positive entries and iteratively modifying $\mset{}^{(n)}$ by adding $1$ to specific marginal outcomes $m$ ($\mset{}^{(n+1)} = \mset{}^{(n)} + \de^{m}$) in such a way that progresses $\extmset{}^{(n)}$ toward becoming positive semi-definite (i.e.
+by decreasing the inhibiting set).
+Taking inspiration from logical, Hardy-type, transversal inequalities discussed in \cref{sec:logical_inequalities}, we can view this process as a weighted hypergraph transversal problem.
+
+    \subsection{Definite Extension Procedure}
+    Before discussing the definite extension procedure (DEP) directly, we will motivate its main algorithmic component (weighted hypergraphs transversals) with a short example.
+    \subsubsection{Example}
+    \begin{example}
+        \label{ex:hypergraph_example}
+        Recall the exemplary incidence matrix $M$ of \cref{eq:example_incidence}, \cref{ex:incidence_matrix}.
+Our aim is generate some valid non-contextuality inequalities for marginal models $\probvec^{\mscenario}$.
+To compactify notation, enumerate the marginal outcomes (rows of $M$) $1$ through $12$ $\br{m_1, \ldots, m_{12}}$ and the joint outcomes (columns of $M$) $1$ through $8$ $\br{j_1, \ldots, j_{8}}$ (see \cref{fig:compact_incidence}).
+        \begin{figure}
+        \begin{center}
+            \begin{minipage}[b]{.48\textwidth}
+                \centering
+                \[ M = \kbordermatrix{
+                    & j_1 & j_2 & j_3 & j_4 & j_5 & j_6 & j_7 & j_8 \\
+                    m_1 & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
+                    m_2 & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
+                    m_3 & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
+                    m_4 & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
+                    m_5 & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
+                    m_6 & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
+                    m_7 & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
+                    m_8 & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
+                    m_9 & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
+                    m_{10} & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
+                    m_{11} & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
+                    m_{12} & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
+                } \]
+                \caption{The incidence matrix for the binary marginal scenario $\mscenario = \bc{\bc{a,b},\bc{b,c}, \bc{a,c}}$ with marginal outcomes $m_1, \ldots, m_{12}$ and joint outcomes $j_1, \ldots, j_{12}$.}
+                \label{fig:compact_incidence}
+            \end{minipage}\hspace{0.04\textwidth}%
+            \begin{minipage}[b]{.48\textwidth}
+                \centering
+                \scalebox{1.0}{\input{../figures/hypergraphs/minimal_example}}
+                \caption{An edge-weighted hypergraph $\hgraph_{\weights}$ corresponding to the antecedent set $\mset^{A}$ with $\mset^{A}_{m_3} = -1$ and $\mset^{A}_{m_8} = -2$.}
+                \label{fig:hypergraph_example}
+            \end{minipage}
+        \end{center}
+        \end{figure}
+        Now suppose our antecedent set is $\mset^{A}$ and has two specified entries:
+        \[ \mset^{A}_{m_{3}} = -1 \quad \mset^{A}_{m_{8}} = -2 \]
+        Then the antecedent extension is given by $\extmset^{A}= \mset^{A} \cdot M$:
+        \[ \extmset^{A}_{j_{4}} = \extmset^{A}_{j_{8}} = -2 \quad \extmset^{A}_{j_{5}} = \extmset^{A}_{j_{6}} = -1 \]
+        The objective then becomes to \textit{hit} the joint outcomes of the inhibiting set $\bc{j_{4}, j_{5}, j_{6}, j_{8}}$ with marginal outcomes organized as a consequent multi-set $\mset^{C} \succeq 0$ such that,
+        \[ \extmset^{C} + \extmset^{A} \succeq 0 \]
+        Taking motivation from \cref{sec:logical_inequalities}, this procedure can be casted as a multi-node hitting problem, or an edge-weighted hypergraph problem.
+Construct a weighted hypergraph $\hgraph_{\weights}$ (see \cref{fig:hypergraph_example}) where the edges are labeled by joint outcomes $\edges = \bc{e_{j_{4}}, e_{j_{5}}, e_{j_{6}}, e_{j_{8}}}$.
+These edges are assigned weights $w_j$ precisely equal to the magnitude of $\extmset^{A}$.
+        \[ \forall j \in \bc{{j_{4}}, {j_{5}}, {j_{6}}, {j_{8}}} : w_{j} = - \extmset^{A}_j \]This weighting represents the joint outcomes that are preventing $\extmset$ from becoming positive semi-definite.
+The nodes represent all possible marginal outcomes that have the potential to contribute to $\mset^{C}$.
+        \[ \nodes = \bc{m_2, m_4, m_5, m_6, m_{10}, m_{11}, m_{12}} \]
+        A node $m$ is a member of edge $e_{j}$ if $m \ext j$.
+By inspection of \cref{fig:hypergraph_example} one can identify numerous multi-sets of $\ga^{C}$ of $\nodes$ that hit each edge $w_j$ times.
+As a singular example,
+        \[ \trans = \bc{m_{2}, m_{10}, m_{11}, m_{12}, m_{12}} = \kbordermatrix{
+            & m_2 & m_4 & m_5 & m_6 & m_{10} & m_{11} & m_{12} \\
+            &   1 &   0 &   0 &   0 &      1 &      1 &      2
+        } \]
+        satisfies this condition.
+We call such $\trans$ \textit{transversals} of $\hgraph_{\weights}$.
+This multi-sets enable one to construct the positive semi-definite extension $\extmset^{C} + \extmset^{A}$ where $\extmset^{C} = \trans \cdot M$.
+This corresponds to the inequality $- \ga^{A} \cdot \probvec^{\mscenario} \leq \ga^{C} \cdot \probvec^{\mscenario}$,
+        \begin{align*}
+        \probvec^{\mscenario}_{m_3} + 2 \probvec^{\mscenario}_{m_8} &\leq \probvec^{\mscenario}_{m_{2}} + \probvec^{\mscenario}_{m_{10}} + \probvec^{\mscenario}_{m_{11}} + 2 \probvec^{\mscenario}_{m_{12}} \\
+        \prob[][m_3] + 2 \prob[][m_8] &\leq \prob[][m_{2}] + \prob[][m_{10}] + \prob[][m_{11}] + 2 \prob[][m_{12}] \\
+        \prob[ab][10] + 2 \prob[bc][11] &\leq \prob[ab][01] + \prob[ac][01] + \prob[ac][10] + 2 \prob[ac][11]
+        \end{align*}
+    \end{example}
     % \begin{definition}
-    %     Two outcomes $\outc{V_1}$ and $\outc{V_2}$ over two distinct sets of random variables $V_1$ and $V_2$ are called \term{accordant} or \textit{compatible} if they are mutually realizable.
-In terms of extendable sets, $\outc{V_1}$ and $\outc{V_2}$ are accordant if there exists an outcome $\outc{V_1 \cup V_2} \in O_{V_1 \cup V_2}$ such that,
-    %     \[ \outc{V_1}, \outc{V_2} \subseteq \outc{V_1 \cup V_2}  \]
-    %     Accordance between two outcomes is the \textit{opposite} of exclusive.
+    %     For convenience, denote the $m$-th row of the incidence matrix $M$ as $\de^{m \ext \jointvar}$ and the $j$-th column of $M$ by $\de^{j \res \mscenario}$.
+    %     \[ \de^{m \ext \jointvar}_j = \de^{j \res \mscenario}_m  = \de^{\mscenario \ext \jointvar}_{m,j} \]
+    %     The following relationships hold for the indicator vectors.
+    %     \[ \de^{\mscenario \ext \jointvar} \cdot \de^{j} = \de^{j \res \mscenario} \qquad \de^{m} \cdot \de^{\mscenario \ext \jointvar} = \de^{m \ext \jointvar} \]
     % \end{definition}
-
-    \begin{definition}
-        \label{def:graph}
-        A \term{graph} is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes can represent any object and the edges are pairs of nodes.
-For convenience of notation, one defines an index set over the nodes denoted $\ind_\nodes$.
-        \[ \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{\bc{n_j, n_k} \mid j,k \in \ind_\nodes} \]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:directed_graph}
-        A \term{directed graph} $\graph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes can represent any object and the edges are \textit{ordered} pairs of nodes.
-For convenience of notation, one defines an index set over the nodes denoted $\ind_\nodes$.
-        \[ \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{n_j \to n_k \mid j,k \in \ind_\nodes} \]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:graph_terms}
-        The following definitions are common language in directed graph theory. Let $n, m \in \nodes$ be example nodes of the graph $\graph$.
-        \begin{itemize}
-            \item The \term{parents of a node}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
-            \item The \term{children of a node}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
-            \item The \term{ancestry of a node}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$
-        \end{itemize}
-        All of these terms can be generalized to sets of nodes $N \subseteq \nodes$ through union over the elements,
-        \begin{itemize}
-            \item The \term{parents of a node set}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
-            \item The \term{children of a node set}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
-            \item The \term{ancestry of a node set}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
-        \end{itemize}
-        Moreover, an \term{induced subgraph} of $\graph$ due to a set of nodes $N \subseteq \nodes$ is the graph composed of $N$ and all edges $e \in \edges$ of the original graph that are contained in $N$.
-        \[ \Sub[\graph]{N} \defined \br{N, \bc{e_i \mid i \in \ind_\edges, e_i \subseteq N}}\]
-        An \term{ancestral subgraph} of $\graph$ due to $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
-        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:dag}
-        A \term{directed acyclic graph} or \term{DAG} $\graph$ is an directed graph \cref{def:directed_graph} with the additional property that no node $n$ is in its set of \term{ancestors}.
-        \[ \forall n \in \nodes : n \notin \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}\]
-        Notice the difference between using the natural numbers $\mathbb{N}$ to distinguish \textit{ancestors} from \textit{ancestry}.
-    \end{definition}
-
-    \begin{definition}
-        A \term{causal structure} is simply a DAG with the extra classification of each node into one of two categories; the \term{latent nodes} and \term{observed nodes} denoted $\nodes_L$ and $\nodes_O$.
-The latent nodes correspond to random variables that are either hidden through some fundamental process or cannot/will not be measured.
-The observed nodes are random variables that are measurable.
-Every node is either latent or observed and no node is both:
-        \[ \nodes_L \cap \nodes_O = \emptyset \qquad \nodes_L \cup \nodes_O = \nodes \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{product distribution} of two disjoint distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as usual with $\prob[V] \times \prob[W]$ and is defined as,
-        \[ \forall f \in \Out{V \cup W} : \br{\prob[V] \times \prob[W]}\br{f} \defined \prob[V][f|_{V}]\cdot\prob[W][f|_{W}] \]
-        A product distribution of $k$ mutually disjoint distributions is defined as,
-        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
-        \[ \forall f \in \Out{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
-    \end{definition}
-    \comment[TC]{How many definitions do I need to write??}
-
-    \section{Compatibility, Contextuality and the Marginal Problem}
-    \label{sec:comp_con_mp}
-    In order to determine if a given marginal distribution $\prob[V]$ or set of marginal distributions $\bc{\prob[V_i]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ is compatible with a causal structure $\graph$, one should first formalize what is meant by \textit{compatible}.
-
-    \begin{definition}
-        A set of \term{causal parameters} for a particular causal structure $\graph$ is the specification of a conditional distribution for every node $n \in \nodes$ given it's parents in $\graph$.
-        \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
-    \end{definition}
-    \begin{definition}
-        \label{def:compatible}
-        A marginal distribution $\prob[V]$ is \term{compatible} with a causal structure $\graph$ (where it is assumed that $V \subseteq \nodes_O$) if there exists a \textit{choice} of causal parameters $\bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes}$ such that $\prob[V]$ can be \textit{recovered} from the following series of operations:
-        \begin{enumerate}
-            \item First obtain a joint distribution over \textit{all} nodes of of the causal structure,
-            \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] \]
-            \item Then marginalize over the latent nodes of $\graph$,
-            \[ \prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes] \]
-            \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$,
-            \[ \prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O] \]
-        \end{enumerate}
-        A set of marginal distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}}$ is compatible with $\graph$ if each distribution $\prob[V_{i}]$ can be made compatible by the \textit{same} choice of causal parameters.
-        A distribution $\prob[V]$ or set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}}$ is said to be \term{incompatible} with a causal structure if there \textit{does not exist} a set of causal parameters with the above mentioned property.
-
-        \todo[TC]{Source this?}
-    \end{definition}
-    Operations 2 and 3 of \cref{def:compatible} are related to the \textit{marginal problem}.
-    \begin{definition}
-        \label{def:marginal_problem}
-        \term{The Marginal Problem:} Given a set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ where $V_i \subseteq \jointvar$ for some set of random variables $\jointvar$, does there exist a joint distribution $\prob[\jointvar]$ such that each given distribution $\prob[V_i]$ can be obtained from marginalizing $\prob[\jointvar]$?
-        \[ \forall i \in \bs{k} : \prob[V_i] = \sum_{\jointvar \setminus V_i} \prob[\jointvar] \]
-        Typically (although not strictly necessary\footnote{Appending any additional variables to $\jointvar$ will not affect the existence of a joint distribution.}), $\jointvar$ is taken to mean the union of all $V_i$'s.
-        \[ \jointvar = V_1 \cup \cdots \cup V_k = \bigcup_{i\in\bs{k}} V_i \eq \label{eq:marginals_union} \]
-    \end{definition}
-
-    \todo[TC]{Mention polytope perspective and existing methods}
-    \begin{definition}
-        \label{def:marginal_model}
-        A reoccurring motif of these discussions will be the set of distributions $\bc{\prob[V_{i}]}_{i \in \bs{k}} \defined \bc{\prob[V_1], \ldots, \prob[V_k]}$ mentioned in \cref{def:marginal_problem}.
-In agreement with \cite{Fritz_2011} we call the set of subsets $\mscenario \defined \bc{V_1, \ldots, V_k}$ the marginal contexts or the \term{maximal marginal scenario}\footnote{Rigorously speaking as defined by \cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that $V' \in \mscenario$ whenever $V' \subseteq V_i$ for some $i \in \bs{k}$.
-``Maximal'' refers to the restriction that $\forall i,j : V_i \not \subseteq V_j$.}.
-An individual $V_i \in \mscenario$ is a \term{marginal context}.
-The union of all contexts is denoted $\jointvar$ and is defined exactly as in \cref{eq:marginals_union}.
-        Moreover, we will call the set of distributions a \term{marginal model} and denote it $\prob^{\mscenario}$ provided that they are \textit{compatible} \todo[TC]{Mention quantum non-signalling and maybe $k \geq 3$}:
-        \[ \forall i \neq j \text{ if } V_i \cap V_j \neq \emptyset \text{ then } \sum_{V_i \setminus V_j} \prob[V_i] = \sum_{V_j \setminus V_i} \prob[V_j]  \]
-        Following definition 2.3 in \cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a joint distribution $\prob[\jointvar]$ and \term{non-contextual} otherwise.
-
-        In addition, we elect to define the \term{marginal outcomes} $\Out{\mscenario}$ to be the set of all outcomes belonging to outcomes $\Out{V_i}$ of the marginal context\footnote{Here `$\coprod$' refers to the \textit{disjoint union} of outcome contexts; when $i \neq j$, $\Out{V_i} \cap \Out{V_j} = \emptyset$ since $V_i \neq V_j$.}.
-        \[ \Out{\mscenario} \defined \coprod_{i \in \bs{k}} \Out{V_i} \]
-        % By an intended abuse of notation, we say that a particular outcome is an ``element'' of $O_{\mscenario}$ if it is an element of $O_{V_i}$ for some $i \in \bs{k}$.
-        % \[ \outc{V_i} \in O_{\mscenario} \]
-        Each marginal outcome $m \in \Out{\mscenario}$ belongs to a unique marginal outcome space $\Out{V_i}$.
-To make reference to the marginal context $V_i$ associated with $m$, recall \cref{rem:domain_dist}: the context for $m$ is precisely the domain of $m$ ($V_i = \Dom{m}$).
-Note that $\Out{\mscenario}$ is a slight abuse of notation; $\Out{\mscenario}$ is \textit{not} a valid outcome space, analogous to the fact that $P^{\mscenario}$ is \textit{not} a probability distribution.
-Instead $\Out{\mscenario}$ is a \textit{flattened} collection of outcome spaces just as $P^{\mscenario}$ is a collection of distributions.
-The \term{joint outcomes} $\Out{\jointvar}$ are defined in the usual fashion of \cref{def:outcome_space}.
-    \end{definition}
-
-    \begin{definition}
-        A \term{causal compatibility inequality} $I_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every compatible marginal model $\prob^{\mscenario}$.
-Whenever the marginal scenario $\mscenario$ in question is evident by context, the subscript of $I_{\mscenario}$ will be dropped leaving just $I$.
-    \end{definition}
-
-    \todo[TC]{Discuss Compatibility, connection to cooperative games/resources, bell incompatibility?}
-    \todo[TC]{Connection between contextuality and Compatibility via the marginal problem for causal parameters}
-    \todo[TC]{Discuss what is meant by a `complete' solution to the marginal problem}
-    \todo[TC]{Maybe define the possibilistic marginal problem for later}
+    % We first recall that every non-contextual marginal model $\prob^{\mscenario}$ can be written as the convex combination of columns of the incidence matrix $M$.
+    % \[ \probvec^{\mscenario} = M \cdot \probvec^{\jointvar} = \sum_{j \in \Sect{\jointvar}} \de_{m \ext j} \prob[\jointvar][j] \]
+    % Thus we define the set of all non-contextual marginal models as $\mathcal{NC}$,
+    % \[ \mathcal{NC} \defined \bc{\probvec^{\mscenario} \mid \probvec^{\mscenario} = \sum_{j} \mu_{j} \de_{j \res \mscenario}, \mu_j \geq 0, \sum_{j} \mu_{j} = 1} \]
+
+    % \begin{definition}
+    %     Let $\mscenario$ be a marginal scenario and let $j \in \Sect{\jointvar}$ be a joint outcome.
+The \term{restriction of $j$ onto $\mscenario$} is deterministic marginal model $\de_{j \res \mscenario} : \Sect{\mscenario} \to \bc{0, 1}$.
+    %     \[ \de_{j \res \mscenario}\br{m} \defined \begin{cases}
+    %         1 & j \ext m  \\
+    %         0 & \textrm{otherwise}
+    %     \end{cases} \]
+    %     As a vector indexed by marginal outcomes $m \in \Sect{\mscenario}$, $\de_{j \ext \mscenario}$ is precisely the $j$-th column of the incidence matrix.
+    % \end{definition}
+
+    % \begin{definition}
+    %     The \term{extension of an m-set} $\mset{S}$ into $\jointvar$ denoted $\extmset{S}$ is a vector indexed by \textit{joint} outcomes $j \in \Sect{\jointvar}$ and is defined as follows,
+    %     \[ \extmset{S}_{j} \defined \sum_{s \in \supp{\mset{S}}} \mset{S}_{s} \de_{s \ext j} \eq \label{eq:joint_multiplicity} \]
+    %     As an immediate consequence, the support of $\extmset{S}$ is immediately known,
+    %     \[ \supp{\extmset{S}} = \bigcup_{s \in \supp{\mset{S}}} \Ext[\jointvar]{s} \]
+    % \end{definition}
+    % \begin{definition}
+    %     An m-set $\mset{C}$ is an \term{extension cover} of an m-set $\mset{A}$ for a marginal scenario $\mscenario$ if and only if the following two conditions hold\footnote{In fact \cref{eq:multi_extenable_cover_def} implies \cref{eq:flat_extenable_cover_def} since $\forall j \not \in \supp{\extmset{A}} : \extmset{A}_j = 0$.}:
+    %     \begin{gather*}
+    %         \supp{\extmset{A}} \subseteq \supp{\extmset{C}} \eq \label{eq:flat_extenable_cover_def}\\
+    %         \forall j \in \supp{\extmset{A}} : \extmset{A}_{j} \leq \extmset{C}_j \eq \label{eq:multi_extenable_cover_def}
+    %     \end{gather*}
+    % \end{definition}
+    % Identifying extension covers is of great importance because of the following theorem.
+    % \begin{theorem}
+    %     \label{thm:extendable_cover_ineq}
+    %     If the m-set $\mset{C}$ is an extension cover of the m-set $\mset{A}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
+    %     \[ \sum_{a \in \supp{\mset{A}}}\mset{A}_a\prob[][a] \leq \sum_{c \in \supp{\mset{C}}}\mset{C}_c\prob[][c] \eq \label{eq:extendable_cover} \]
+    % \end{theorem}
+    % \begin{proof}
+    %     To prove that \cref{eq:extendable_cover} is a valid compatibility inequality $I_{\mscenario}$ for all marginal models $\prob^\mscenario$, we will demonstrate that \cref{eq:extendable_cover} follows from the assumption that a joint distribution $\prob[\jointvar]$ exists.
+
+    %     For each m-set $\mset{S}$ write the weighted sum over the probabilities $\bc{\prob[][s]}_{s \in \supp{\mset{S}}}$ in terms of the joint distribution $\prob[\jointvar]$ using \cref{eq:joint_multiplicity}.
+    %     \begin{align*}
+    %     \eq \label{eq:derivation_cover}
+    %     \begin{split}
+    %     \sum_{s \in \supp{\mset{S}}} \mset{S}_s\prob[][s] &= \sum_{s \in \supp{\mset{S}}} \mset{S}_s  \sum_{j \in \Ext[\jointvar]{s}} \prob[\jointvar][j] \\
+    %     &= \sum_{s \in \supp{\mset{S}}} \mset{S}_s \sum_{j \in \Sect{\jointvar}} \isext{s}{j} \prob[\jointvar][j] \\
+    %     &= \sum_{j \in \Sect{\jointvar}} \bs{\sum_{s \in \supp{\mset{S}}} \mset{S}_s  \isext{s}{j}} \prob[\jointvar][j] \\
+    %     &= \sum_{j \in \supp{\extmset{S}}} \extmset{S}_j \prob[\jointvar][j]
+    %     \end{split}
+    %     \end{align*}
+    %     First examine the substitution $S \to C$,
+    %     \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] = \sum_{j \in \supp{\extmset{C}}} \extmset{C}_j \prob[\jointvar][j] \]
+    %     By \cref{eq:flat_extenable_cover_def} $\supp{\extmset{A}} \subseteq \supp{\extmset{C}}$,
+    %     \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] = \sum_{j \in \supp{\extmset{C}}} \extmset{C}_j \prob[\jointvar][j] + \sum_{j \in \supp{\extmset{C}} \setminus \supp{\extmset{A}}} \extmset{C}_j \prob[\jointvar][j] \]
+    %     Notice that the sum over $j \in \supp{\extmset{C}} \setminus \supp{\extmset{A}}$ is entirely positive since $\extmset{C}_j \in \N$ and $\prob[\jointvar][j] \geq 0$.
+Moreover \cref{eq:multi_extenable_cover_def} gives $\extmset{C}_j \geq \extmset{A}_j$.
+Combining these observations along with \cref{eq:derivation_cover} for $S \to A$, one arrives at the inequality,
+    %     \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] \geq \sum_{j \in \supp{\extmset{A}}} \extmset{A}_j \prob[\jointvar][j] = \sum_{a \in \supp{\mset{A}}} \mset{A}_a\prob[][a] \]
+    %     Which is equivalent to \cref{eq:extendable_cover}; every non-contextual marginal model $\prob^{\mscenario}$ must satisfy \cref{eq:extendable_cover}.
+    % \end{proof}
+    % \begin{corollary}
+    %     \label{cor:linear_integer}
+    %     Every linear, integer coefficient compatibility inequality that is homogeneous is an extension covering inequality.
+    % \end{corollary}
+    % \begin{proof}
+    %     A proof is easy to see by contradiction.
+Let $I_{\mscenario} = \bc{\gamma \cdot \probvec^{\mscenario} \geq 0}$ where $\gamma_m \in \Z | \forall m \in \Sect{\mscenario}$ be a homogeneous, linear, integer coefficient, compatibility inequality such that it is \textit{not} an extension covering inequality.
+Next seperate $\gamma$ into its positive and negative components,
+    %     \[ \gamma_m^{+} = \begin{cases}
+    %         \gamma_m & \gamma_m > 0 \\
+    %         0 & \gamma_m \leq 0
+    %     \end{cases}
+    %     \qquad
+    %     \gamma_m^{-} = \begin{cases}
+    %         -\gamma_m & \gamma_m < 0 \\
+    %         0 & \gamma_m \geq 0
+    %     \end{cases} \]
+    %     Such that both $\gamma^{+}$ and $\gamma^{-}$ are valid m-sets.
+Therefore $I_{\mscenario} = \bc{\br{\gamma^{+} - \gamma^{-}} \cdot \probvec^{\mscenario} \geq 0}$.
+Since this inequality is \textit{not} an extension cover, it must be that there exists at least one joint outcome $j' \in \Sect{\jointvar}$ such that $\Gamma^{-}_{j'} > \Gamma^{+}_{j'}$.
+Consequently by \cref{eq:derivation_cover}, the deterministic distribution $\probvec^{\mscenario} = \de_{j' \res \mscenario}$ \textit{violates} $I_{\mscenario}$.
+However since $\de_{j' \res \mscenario} \in \mathcal{NC}$ and violates $I_{\mscenario}$, $I_{\mscenario}$ can not be a compatibility inequality; disagreeing with the assumption that it was.
+    % \end{proof}
+    % \begin{corollary}
+    %     If the m-set $\mset{C}$ is an extension cover of the m-set $\br{A, \mulA}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
+    %     \[ \sum_{a \in \supp{\mset{A}}}\prob[][a] \leq \sum_{c \in \supp{\mset{C}}}\prob[][c] \eq \label{eq:extendable_cover_flat} \]
+    % \end{corollary}
+    % \begin{proof}
+    %     This follows from the fact that if $\mset{C}$ is an extension cover of $\br{A, \mulA}$, then $\br{C, \mathbf{1}_{C}}$ is an extension cover of $\br{A, \mathbf{1}_{A}}$.
+Since $E_A \subseteq E_C$ is already trivially satisfied, all that remains is to demonstrate that \cref{eq:multi_extenable_cover_def} holds for unitary multiplicities $\mathbf{1}_A$ and $\mathbf{1}_C$.
+
+    %     First examine extension $\br{E_C, \mul{\mext{C}}}$ for the m-set $\mset{C}$ as defined by \cref{eq:joint_multiplicity},
+    %     \[ \forall j \in E_C : \extmset{C}_j = \sum_{c \in \supp{\mset{C}}} \mulC\br{c} \isext{c}{j} \]
+
+    %     First apply \cref{lemma:logical_extenable_set} to an arbitrary set $S \in \bc{A, C}$,
+    %     \[ \bigvee_{s \in \supp{\mset{S}}} s \iff \bigvee_{s \in \supp{\mset{S}}} \bigvee_{j \in \Ext[\jointvar]{s}} j \iff \bigvee_{j \in E_S} j \eq \label{eq:logical_iff_ext}\]
+    %     Now since $E_A \subseteq E_C$ by \cref{eq:flat_extenable_cover_def} we have that,
+    %     \[ \bigvee_{j \in E_A} j \implies \bigvee_{j \in E_C} j \eq \label{eq:logical_cover}\]
+    %     Combining \cref{eq:logical_iff_ext,eq:logical_cover} one arrives at,
+    %     \[ \bigvee_{a \in \supp{\mset{A}}} a \implies \bigvee_{c \in \supp{\mset{C}}}c \]
+    % \end{proof}
+    % For a working example, let $\jointvar = \bc{a, b, c}$ be a set of binary random variables ($O = \bc{0,1}$) and $\mscenario = \bc{\bc{a,b},\bc{b,c},\bc{a,c}}$ be the marginal context.
+    \subsubsection{Weighted Hypergraphs}
+    A \term{hypergraph} $\hgraph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{hyperedges} respectively where the hyperedges are \textit{subsets} of nodes $\forall e \in \edges : e \subset \nodes$.
+A hypergraph deviates from a traditional graph in that the edges have the capacity to contain more or less than $2$ nodes.
+There is a dual correspondence between the hyperedges $e \in \edges$ and nodes $n \in \nodes$ of a hypergraph: just as a hyperedge $e$ is interpreted as a set of nodes, a node $n$ can be viewed as the set of hyperedges $\bc{e \mid n \in e}$ that contain it.
+A \term{hypergraph transversal} (or edge hitting set) $\trans$ of a hypergraph $\hgraph$ is a set of nodes $\trans \subseteq \nodes$ that have a non-empty intersection with every hyperedge in $\edges$.
+    \[ \trans \subseteq \nodes \mid \forall e \in \edges : \trans \cap e \neq \emptyset \eq \label{eq:flat_trans_def}\]
+    A transversal $\trans$ is said to be \term{minimal} if there are no redundant nodes $n$ in $\trans$, i.e.
+no node $n$ can be removed from $\trans$ such that $\trans \setminus n$ remains a transversal.
+The condition for minimality expressed,
+    \[ \forall n \in \trans : \exists e \in \edges \mid \br{\trans \setminus n} \cap e = \emptyset \eq \label{eq:flat_trans_minimal}\]
+
+    When defining a \textit{weighted} hypergraph, there can be some ambiguity as to whether or not the weights $\weights$ are associated with the hyperedges or nodes.
+Since the definite extension procedure concerns itself with weighted hyperedges, we refer to edge-weighted hypergraphs simply as weighted hypergraphs.
+    \begin{definition}
+        A \term{(edge-)weighted hypergraph} $\hgraph_\weights$ is a hypergraph $\hgraph = \br{\nodes, \edges}$ together with a set of real-valued weights $\weights = \bc{w_e \mid e \in \edges}$ assigned to each hyperedge $e$.
+    \end{definition}
+    In the case of the definite extension procedure, these weights will typically be positive integers $w_e \in \Z_{> 0}$.
+As such, we make this the default setting moving forward.
+Accompanying weighted hypergraphs are the notion of weighted transversals.
+    \begin{definition}
+        A \term{weighted transversal} $\trans$ of a weighted hypergraph $\hgraph_{\weights}$ is a \textit{multi-set} or \textit{vector} of nodes $\forall n \in \nodes : \trans_n \in \N$ such that the total multiplicity of nodes in each hyperedge $e$ surpasses (or matches) the assigned weight $w_e$.
+        \[ \forall e \in \edges : \sum_{n \in e} \trans_{n} \geq w_e \eq \label{eq:weighted_trans_def}\]
+    \end{definition}
+    \begin{definition}
+        A weighted transversal $\trans$ of a weighted hypergraph $\hgraph_{\weights}$ is a said to be \term{minimal} or have \term{minimal-multiplicities} if all its entries $\trans_n : n \in \nodes$ are minimal in the sense that there does not exist a node $n' \in \supp{\trans}$ such that $\trans - \de^{n'}$ is still a transversal.
+        \[ \forall n' \in \nodes : \exists e \in \edges, n' \in e : \sum_{n \in e} \trans_{n} - 1 < w_e  \eq \label{eq:weighted_trans_minimal}\]
+        Equivalently, $\trans$ is minimal if there does not exists another transversal $\trans'$ that precedes $\trans$.
+        \[ \not \exists \trans' \neq \trans : \forall j : \trans'_j \leq \trans_j \]
+    \end{definition}
+    Remark than in the situation where all assigned weights are singular $w_e = 1$, the weighted minimality condition \cref{eq:weighted_trans_minimal} reduces to the unweighted minimality condition \cref{eq:flat_trans_minimal}.
+The principle component of the definite extension procedure can be summarized as follows:
+
+    \subsubsection{Transversals of Antecedent Hypergraphs}
+    Given an antecedent multi-set $\mset^{A}$ where $\mset^{A} \preceq 0$, identify the \textit{inhibiting set} $\inhibit\br{\mset^{A}}$ responsible for preventing $\extmset^{A}$ from being classified as positive semi-definite.
+For an antecedent set $\mset^{A}$ where all entries are negative, there are a few equivalent ways of representing the inhibiting set,
+    \[ \inhibit\br{\mset^{A}} = \supp{\extmset^{A}} = \bc{j \mid \extmset^A_j < 0} = \bc{j \mid \exists m \in \supp{\mset^A} : m \ext j } \]
+    The last interpretation corresponding to the extendable set of $\supp{\mset^{A}}$.
+Using the inhibiting set $\inhibit\br{\mset^{A}}$, construct a weighted hypergraph $\hgraph_\weights\br{\mset^A}$ such that,
+    \begin{align*}
+    \edges\br{\mset^{A}} &= \bc{e_j \mid j \in \inhibit\br{\mset^{A}}} \\
+    e_j &= \bc{m \in \Sect{\mscenario} \mid m \ext j, m \not \in \supp{\ga^A}} \\
+    \weights\br{\mset^{A}} &= \bc{w_j = - \extmset^{A}_j \mid j \in \inhibit\br{\mset^{A}}} \\
+    \nodes\br{\mset^A} &= \bigcup_{j \in \inhibit\br{\mset^A}} e_j \\
+    &= \bc{m \in \Sect{\mscenario} \mid m \not \in \supp{\mset^A}, \exists m' \in \supp{\mset^A} : m \com m'}
+    \end{align*}
+    The hyperedges $e_j \in \edges\br{\mset^{A}}$ are indexed by the inhibiting set.
+Each hyperedge $e_j$ is the subset of marginal outcomes $e_j \subseteq \Sect{\mscenario}$ that are extendable to $j$ (yet not already included in $\ga^A$\footnote{At this point, it might be unclear why we disregard marginal outcomes in $\supp{\ga^A}$.
+Sufficient reasoning will become apparent when presented with a complete discussion of the definite extension procedure.}).
+The weights $\weights\br{\mset^A}$ equal the amount that $\extmset^{A}$ needs to recover by, and the nodes $\nodes\br{\mset^A}$ are simply the union of all edges.
+This weighted hypergraph is termed the \term{antecedent hypergraph}.
+    \begin{remark}
+        The structure of a hypergraph $\hgraph$ (disregarding weights) is best computationally implemented as a bitwise matrix $H$ where the rows of $H$ are in correspondence with the nodes $n \in \nodes$ of $\hgraph$.
+Likewise, the columns of $H$ are in correspondence with the edges $e \in \edges$ of $\hgraph$.
+The entires of $H$ can be populated according to edge inclusion.
+        \[ H_{n,e} = \begin{cases}
+            1 & n \in e \\
+            0 & n \not \in e
+        \end{cases} \]
+        Regarding the antecedent hypergraph $\hgraph\br{\mset^A}$, the matrix form $H\br{\mset^A}$ of $\hgraph\br{\mset^A}$ can be constructed by taking the incidence matrix $M$ and deleting rows not in $\nodes\br{\mset^A}$ and columns not in $\edges\br{\mset^A}$.
+As an example, consider \cref{ex:hypergraph_example} and the hypergraph of \cref{fig:hypergraph_example}.
+The corresponding matrix representation of the hypergraph of \cref{ex:hypergraph_example} is a sub-matrix of the the incidence matrix depicted in \cref{fig:compact_incidence}.
+        \[ H\br{\mset^A} = \kbordermatrix{
+            & j_4 & j_5 & j_6 & j_8 \\
+            m_2 & \kone & \kzer & \kzer & \kzer \\
+            m_4 & \kzer & \kzer & \kzer & \kone \\
+            m_5 & \kzer & \kone & \kzer & \kzer \\
+            m_6 & \kzer & \kzer & \kone & \kzer \\
+            m_{10} & \kone & \kzer & \kzer & \kzer \\
+            m_{11} & \kzer & \kone & \kzer & \kzer \\
+            m_{12} & \kzer & \kzer & \kone & \kone
+        } \]
+        Although it is possible to generate antecedent hypergraphs in this manner, we recommend against it.
+One of the advantages of the definite extension procedure (to be discussed in \cref{sec:advantages_dep}) is that typically the size of an antecedent hypergraph $H$ is \textit{far smaller} than the original incidence matrix $M$.
+For large enough marginal scenarios, $M$ becomes too resource intensive to hold in memory, while $H$ remains far more manageable.
+    \end{remark}
+
+    After generating an antecedent hypergraph $\hgraph\br{\mset^A}$, it is possible to find all valid, homogeneous, non-contextuality inequalities $I_\mscenario = \bc{ \mset \cdot \probvec^{\mscenario} \geq 0}$ by finding all transversals of $\hgraph\br{\mset^A}$.
+As mentioned previously for each transversal $\trans$, the marginal multi-set $\mset^C$ agreeing with $\trans$ can be constructed,
+    \[ \forall m \in \supp{\trans} : \mset^C_{m} = \trans_m \]
+    Such that $\ga^A + \ga^C$ has definite extension, which by \cref{thm:deinite_extension_main_thm} induces the valid inequality,
+    \[ I_\mscenario = \bc{\br{\mset^C + \mset^A} \cdot \probvec^{\mscenario} \geq 0} \eq \label{eq:transversal_inequality}\]
+    More importantly, one only needs to consider \textit{minimal transversals} of $\hgraph\br{\mset^A}$.
+If a transversal $\trans$ is non-minimal, then there exists another transversal $\trans'$ such that $\trans' \preceq \trans$.
+A minimal transversal $\trans'$ would be have correspondence with a tighter inequality $I_\mscenario' = \bc{\br{{\mset'}^C + \mset^A} \cdot \probvec^{\mscenario} \geq 0}$ that is capable of witnessing contextually in a strictly large subset of marginal models $\probvec^{\mscenario}$.
+\\
+
+    \begin{definition}
+
+    \end{definition}
+
+    Therefore, it is possible to generate a family of \textit{tight} inequalities for each antecedent choice
+
+    \subsubsection{Completeness}
+    \label{sec:completeness_dep}
+    \todo[TC]{FM section would demonstrate that linear, homogeneous, integer inequalities are sufficient} \\
+    \todo[TC]{Talk about how all facets with antecedent order $n$ would be found by DEP at level $n$} \\
+    \todo[TC]{Upper limit of DEP is set by lowest antecedent order of FM result} \\
+    \subsubsection{Advantages}
+    \label{sec:advantages_dep}
+    \todo[TC]{Horizontally scalable} \\
+    \todo[TC]{Low Memory Overhead} \\
+    \todo[TC]{Effectively depth-first FM} \\
+    \todo[TC]{Offers partially solution when complete solution intangible} \\
+    \todo[TC]{Weighted transversal algorithms are natural extensions of regular algorithms} \\
+    \todo[TC]{inequalities found at lower orders of DEP hierarchy are either facets or are positively separable into one or more facets} \\
+    \todo[TC]{Symmetries MASSIVELY reduce search space, memory for complete solution (to be discussed)} \\
+    \todo[TC]{Can be adapted to find correlation inequalities} \\
+    \todo[TC]{Can be implemented as a relaxation procedure (becomes regular HT problem)} \\
+    \todo[TC]{Can be adapted to target a specific distribution} \\
+    \todo[TC]{Seed distributions to avoid trivial inequalities} \\
+    \subsubsection{Disadvantages}
+    \label{sec:disadvantages_dep}
+    \todo[TC]{We don't yet know exactly how high the hierarchy goes} \\
+    \todo[TC]{If complete solution is ultimately desired, FM is in principle far more efficient because it does need to prune anything} \\
+    \subsubsection{Unanswered questions}
+    % \todo[TC]{How to avoid regenerating inequalities that are reducible to lower order}
+    % Corollary \ref{cor:linear_integer} alludes to completeness of extension covers.
+It vaguely suggests that every non-contextuality inequality needs to be an extension cover, otherwise there would exist a compatible and deterministic distribution that violates it.
+We will now demonstrate this completeness explicitly by first discussing what is required of a complete solution to the marginal problem.
+    % \begin{definition}
+    %     A \term{complete solution to the marginal problem} is a finite set of $q$ vectors $\gamma_1, \ldots, \gamma_q$ together with $q$ real numbers $k \in \R$
+    % \end{definition}
+    % \begin{theorem}
+    %     \label{thm:complete_solution_log_cover}
+    %     The set of all logical covering inequalities forms a sufficient solution to the possibilistic marginal problem.
+    % \end{theorem}
+    % \begin{theorem}
+    %     \label{thm:complete_solution_ext_cover}
+    %     The set of all extension covering inequalities forms a sufficient solution to the probabilistic marginal problem.
+    % \end{theorem}
+    % \begin{proof}
+    % \end{proof}
+    % \begin{definition}
+    %     An extension cover $\mset{C}$ of $\mset{A}$ is said to be \term{minimal} if there does not exist an extension cover $\mset{C'}$ different from $\mset{C}$ such that,
+    %     \[ \forall j \in \Sect{\jointvar} : \mset{C'}_j \leq \mset{C}_j \]
+    % \end{definition}
+
+    % If a more minimal extension cover $\mset{C'}$ does exists, then the inequality it defines (as per \cref{thm:extendable_cover_ineq} directly implies the inequality defined by $\mset{C}$.
+
+    % \begin{definition}
+    %     An extension cover $\mset{C}$ of $\mset{A}$ is said to be \term{reducible} if there exists a \textit{partition} of $\mset{C}$ and $\mset{A}$,
+    %     \[ \mset{C} = \mset{C_1} + \mset{C_2} \qquad \mset{A} = \mset{A_1} + \mset{A_2} \]
+    %     Such that $\mset{C_1}$ is an extension cover for $\mset{A_1}$ and $\mset{C_2}$ is an extension cover for $\mset{A_2}$.
+If $\br{\mset{C}, \mset{A}}$ does \textit{not} admit a partition, then it is said to be \term{irreducible}.
+    % \end{definition}
+
+    % \todo[TC]{Basis certificates}
+
+    % % \begin{algorithm}[H]
+    % % \caption{The Extension Cover Procedure (DEP)}
+    % % \label{alg:ecp}
+    % % \begin{algorithmic}
+    % %   \State $\mset{S}^{0} = \mul{\emptyset}$
+    % % \end{algorithmic}
+    % % \end{algorithm}
+
+    % % \begin{algorithm}
+    % %   \caption{The Extension Cover Procedure (DEP)
+    % %     \label{alg:ecp}}
+    % %   \begin{algorithmic}[1]
+    % %     \Require{An antecedent m-set $\mset{A}$ and a partial consequent m-set $\mset{S}$.}
+    % %     \Statex
+    % %     \Function{DEP}{$\mset{A}, \mset{S}$}
+    % %       % \Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
+    % %       % \Let{$\delta$}{$0$}
+    % %       % \For{$i \gets 1 \textrm{ to } n$}
+    % %       %   \If{$z_i \neq 0$}
+    % %       %     \Let{$\delta$}{$\delta + 1$}
+    % %       %   \EndIf
+    % %       % \EndFor
+    % %       \State \Return{$\delta$}
+    % %     \EndFunction
+    % %   \end{algorithmic}
+    % % \end{algorithm}
+
+    % \todo[TC]{Trivial nodes}
+    % \todo[TC]{Duplication under Deflation}
+    % \todo[TC]{Memory}
+    % \todo[TC]{Parallelization}
+    % \todo[TC]{Simplicial Complex}
+    % \subsubsection{Advantages}
+
+    % \subsubsection{Avoiding Trivial Inequalities}
+    % A \term{trivial compatibility inequality} $I_{\mscenario}$ is an inequality that is satisfied by all marginal models $\prob^{\mscenario}$, not just compatible ones.
+Trivial compatibility inequalities are of no importance Since the set of all extension cover inequalities
+    % \todo[TC]{Targeted Seeds}
+
+    % \begin{definition}
+    %     A \term{hypergraph transversal generation} is any algorithm that correctly generates the complete set of all minimal transversals of $\mathcal{H}$.
+    % \end{definition}
+
+    % \begin{definition}
+    %     Any hypergraph with strictly non-empty edges $\forall e \neq \emptyset$ will always admit the \term{trivial transversal} $\trans^*$ where all nodes are considered as members $\trans^* = \nodes$.
+Any hypergraph with empty edges will be called a \term{degenerate hypergraph} as it admits no transversals\footnote{Most authors require that all hypergraphs be non-degenerate~\cite{Kavvadias_2005}.}.
+    % \end{definition}
+    % Remark ?? guarantees that all marginal hypergraphs are non-degenerate. There are two distinct approaches to hypergraph transversal generation: \textit{top-down} and \textit{bottom-up}.
+    % \begin{definition}
+    %     A \term{top-down} hypergraph transversal generation refers to any algorithm that begins with the trivial transversal $\trans^*$ and iteratively removes unnecessary nodes from $\trans^*$.
+    % \end{definition}
+
+    % \begin{definition}
+    %     A \term{bottom-up} hypergraph transversal generation refers to any algorithm that begins with the empty set $\emptyset$ and iteratively adds nodes.
+    % \end{definition}
+
+    % One should select a top-down method if the typical size of minimal transversals $\abs{\trans}$ is comparable to the number of nodes $\abs{\nodes}$, otherwise a bottom-up method will perform better.
+    % For our purposes we implemented a deep-first transversal algorithm similar to
+    % Recalling
+
+    % \subsection{Weighted Hypergraph Transversals}
+    % In \cref{sec:certificate_inequalities} is was demonstrated that the Fritz distribution is witness-able via a certificate inequality. It is also possible to witness
+    % \todo[TC]{Discuss the Inequalities Derived/ Trivial and non-trivial}
+
+    % \todo[TC]{Weighted transversals and Optimizations}
+    % \todo[TC]{Seeding inequalities (huge advantage here)}
+    \section{Marginal Symmetries}
+    \label{sec:symmetry}
+    Exploiting symmetries of a marginal scenario are useful for a few distinct reasons.
+First, Bancal et.
+al.~\cite{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:comp_con_mp}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
+They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that quantum-non-trivial inequalities can be recovered from facets of a symmetric polytope.
+Numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
+The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.\\
+
+    In this section we discuss how to exploit symmetries in the definite extension procedure in order to reduce the size of the computational search space.
+In contrast to~\cite{Bancal_2010}, we gain advantage in a non-lossy way; symmetries drastically accelerate the rate in which the DEP finds facets of the unsymmetrical polytope.
+\\
+
+    To demonstrate what types of symmetries we have in mind, we present the following example:
+    \begin{example}
+        \label{ex:symmetries}
+        First consider the marginal scenario $\mscenario = \bc{\bc{a, b, c}, \bc{c, d}, \bc{a, d}}$ where each variable in $\jointvar = \bc{a,b,c,d}$ has binary outcomes: $O_a = O_b = O_c = O_d = \bc{0,1}$.
+Moreover, let $I_{\mscenario}$ be a $\s{NC}$-inequality,
+        \[ I_{\mscenario} = \bc{\prob[abc][010] \leq \prob[cd][00] + \prob[ad][01]}  \]
+        Intuitively, a the contextuality of $\probvec^{\mscenario}$ is independent of the how one labels outcomes.
+Therefore new $\s{NC}$-inequalities can be generated from $I_{\mscenario}$ by permuting its outcomes.
+Let $\geo_v : O_v \to O_v : \bc{0,1} \mapsto \geo_v\bs{\bc{0,1}} = \bc{1,0}$ be a permutation of the outcomes for variable $v$; i.e.
+$\geo_v$ ``flips'' the outcomes for $v$.
+Let $\geo = \geo_a \times \geo_c$ be the permutation of variables $a$ and $c$.
+The action of $\geo$ on outcome labels induces an action on the inequality $I_{\mscenario}$ itself,
+        \begin{align*}
+        \geo\bs{I_{\mscenario}} &= \bc{\prob[abc][\geo\bs{010}] \leq \prob[cd][\geo\bs{00}] + \prob[ad][\geo\bs{01}]} \\
+        &= \bc{\prob[abc][111] \leq \prob[cd][10] + \prob[ad][11]}
+        \end{align*}
+        The new inequality $\geo\bs{I_{\mscenario}}$ is also a valid $\s{NC}$-inequality.
+By design, any permutation $\geo$ over outcomes leaves the marginal scenario invariant ($\geo\bs{\mscenario} = \mscenario$) and thus we may write $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$.
+\\
+
+        Alternatively, permutations of the variables themselves are also permitted.
+Let $\gep : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \gep\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ be a permutation of the variables $\jointvar$.
+Intuitively $\gep$ acts on $I_{\mscenario}$ in the following way,
+        \begin{align*}
+        \gep\bs{I_{\mscenario}} &= \bc{\prob[\gep\bs{abc}][010] \leq \prob[\gep\bs{cd}][00] + \prob[\gep\bs{ad}][01]} \\
+        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
+        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
+        \end{align*}
+        In general (as in this example), permutations over all variables can modify the marginal scenario $\gep\bs{\mscenario} \neq \mscenario$; in general we write $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
+Although $\gep\bs{I_{\mscenario}}$ is in fact a valid $\s{NC}$-inequality, in constrains marginal models of a different marginal scenario $\gep\bs{\mscenario}$ and are in general of no interest.
+    \end{example}
+
+    \subsection{Outcome Symmetry}
+    \label{sec:outome_label_symmetry}
+    As demonstrated by \cref{ex:symmetries}, permutations of outcomes can be applied to inequalities themselves to generate new inequalities.
+To formalize this notion, let $\Perm{S}$ denote the \term{permutation group} acting on the set $S$ consisting of all bijective maps $s : S \to S$.
+    \[ \Perm{S} = \bc{s : S \to S} \eq \label{eq:permutation_group_def}\]
+    \begin{definition}
+        The \term{outcome symmetry group} $\go$ for the set of joint variables $\jointvar = \bc{v_1, \ldots, v_n}$ is the direct product of permutations over the outcome labels for each variable $v \in \jointvar$,
+        \[ \go \defined \Perm{O_{v_1}} \times \cdots \times \Perm{O_{v_n}} = \prod_{v \in \jointvar} \Perm{O_{v}} \]
+        The action of $\geo \in \go$ on any section $s \in \Sect{V}$ (denoted $\geo\bs{s}$) where $V \subseteq \jointvar$ is defined as,
+        \[ \forall v \in \Dom{s} : \br{\geo\bs{s}}\br{v} \defined \geo\bs{s\br{v}} \eq \label{eq:act_on_outcome_label}\]
+    \end{definition}
+    \begin{lemma}
+        \label{lem:extendable_invariance_acto}
+        If a marginal section $m \in \Sect{\mscenario}$ is extendable to the joint section $j \in \Sect{J}$, then for any outcome permutation $\geo \in \go$, $\geo\bs{m}$ is extendable to $\geo\bs{j}$.
+        \[ m \ext j \iff \geo\bs{m} \ext \geo\bs{j} \eq \label{eq:extendable_invariance_acto}\]
+    \end{lemma}
+    \begin{proof}
+        The proof should be clear by the definition of extendability (\cref{def:section_extendable}).
+        \[ m \ext j \iff \forall v \in \Dom{m} : j\br{v} = m\br{v} \]
+        Every label permutation $\geo \in \go$ leaves the outcome domain invariant $\Dom{m} = \Dom{\geo\bs{m}}$. Thus by \cref{eq:act_on_outcome_label},
+        \begin{align*}
+        \forall v \in \Dom{\geo\bs{m}}: \br{\geo\bs{j}}\br{v} = \geo\bs{j\br{v}} = \geo\bs{m\br{v}} = \br{\geo\bs{m}}\br{v}
+        \end{align*}
+        Therefore we have that $m \ext j \implies \geo\bs{m} \ext \geo\bs{j}$. The left implication of \cref{eq:extendable_invariance_acto} follows by considering $\geo^{-1} \in \go$.
+    \end{proof}
+    \begin{corollary}
+        \label{coll:incidence_invariance}
+        Let $M$ be the incidence matrix for a marginal scenario $\mscenario$ and $\geo \in \go$ be a label permutation of the joint random variables $\jointvar$.
+By \cref{lem:extendable_invariance_acto}, the action of $\geo$ on $M$ leaves $M$ invariant ($\geo\bs{M} = M$),
+        \[ \geo\bs{M}_{m,j} \defined M_{\geo\bs{m},\geo\bs{j}} = \de_{\geo\bs{m} \ext \geo\bs{j}} = \de_{m \ext j} = M_{m,j} \eq \label{eq:incidence_invariance}\]
+    \end{corollary}
+    \begin{theorem}
+        \label{thm:inequalities_outcome_label_generation}
+        For each $\s{NC}$-inequality $I_{\mscenario}$ and outcome permutation $\geo \in \go$, the inequality defined by $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$ is also a valid $\s{NC}$-inequality.
+    \end{theorem}
+    \begin{proof}
+        First let $I_{\mscenario} = \bc{\ga \cdot \probvec^{\mscenario} \geq 0}$ be a $\s{NC}$-inequality for the marginal scenario $\mscenario$ where $\ga$ is the multi-set associated with $I_{\mscenario}$.
+Furthermore let $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario} = \bc{\ga \cdot \geo\bs{\probvec}^{\mscenario} \geq 0}$ be the inequality obtained after permuting $\probvec^{\mscenario}$ defined as,
+        \[ \forall m \in \Sect{\mscenario} : \geo\bs{\probvec}^{\mscenario}_m \defined \probvec^{\mscenario}_{\geo\bs{m}} \]
+        It should be clear to see that $\ga \cdot \geo\bs{\probvec}^{\mscenario}$ can be rewritten as,
+        \[ \ga \cdot \geo\bs{\probvec}^{\mscenario} = \sum_{m \in \Sect{\mscenario}} \ga_{m} \probvec^{\mscenario}_{\geo\bs{m}} = \sum_{m' \in \Sect{\mscenario}} \ga_{\geo^{-1}\bs{m'}} \probvec^{\mscenario}_{m'} = \geo^{-1}\bs{\ga} \cdot \probvec^{\mscenario}\]
+        Therefore the permuted inequality is equivalent to,
+        \[ \geo\bs{I}_{\mscenario} = \bc{\geo^{-1}\bs{\ga} \cdot \probvec^{\mscenario} \geq 0} \]
+        All that remains to be proven is that $\geo^{-1}\bs{\ga}$ forms a valid certificate for the incidence matrix $M$. Since $\geo \in \go$, \cref{coll:incidence_invariance} gives,
+        \[ \br{\geo^{-1}\bs{\ga} \cdot M}_j = \sum_{m \in \Sect{\mscenario}} \geo^{-1}\bs{\ga}_m \de_{m\ext j} = \sum_{m \in \Sect{\mscenario}} \bs{\ga}_m \de_{\geo\bs{m}\ext j} = \sum_{m \in \Sect{\mscenario}} \bs{\ga}_m \de_{m\ext \geo^{-1}\bs{j}} = \br{\ga \cdot M}_{\geo^{-1}\bs{j}} \]
+        But since $I_{\mscenario}$ is a $\s{NC}$-inequality, $\ga \cdot M \succeq 0$ and thus $\geo^{-1}\bs{\ga} \cdot M \succeq 0$ making $\geo\bs{I}_{\mscenario}$ a $\s{NC}$-inequality as well.
+    \end{proof}
+
+    \subsection{Variable Symmetry}
+
+    In \cref{sec:outome_label_symmetry}, permutations of outcomes were introduced as symmetries of the incidence matrix $M$.
+However the proof of \cref{thm:inequalities_outcome_label_generation} indicates that any permutation leaving the incidence matrix intact can be used to generate new inequalities.
+\\
+
+    Following the observations of \cref{ex:symmetries}, it is always possible to permute the random variables in a marginal scenario to produce new and valid inequalities.
+A generic permutation group over a the complete set of variables $\jointvar$ is simply $\Perm{\jointvar}$.
+Unlike elements of $\Om$, permutations $\gep \in \Perm{\jointvar}$ have the undesired possibility of transforming $\mscenario$ into a different marginal scenario.
+    \[ \gep\bs{\mscenario} \defined \bc{\gep\bs{V_1}, \ldots, \gep\bs{V_k}} \neq \mscenario \]
+    This means that there could exist $V_i \in \mscenario$ such that $\gep\bs{V_i} \not \in \mscenario$.
+In particular, permutations $\gep$ retaining this property are unable to generate $\s{NC}$-inequalities over the same marginal scenario.
+
+    \begin{definition}
+        The \term{variable permutation group} $\gp$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario.
+        \[ \Phi \defined \bc{\gep \in \Perm{\jointvar} \mid \forall V \in \mscenario : \gep\bs{V} \in \mscenario} \]
+        The action of $\gep \in \gp$ on any outcome $f \in \Sect{V}$ (denoted $\geo\bs{f}$) is defined as,
+        \[ \forall v \in \Dom{\gep\bs{f}} : \br{\gep\bs{f}}\br{v} \defined f\br{\gep^{-1}\bs{v}} \eq \label{eq:act_on_variable}\]
+    \end{definition}
+
+    \subsection{Marginal Symmetries}
+
+    \begin{definition}
+        A \term{marginal symmetry} of $\mscenario$ is a symmetry of the incidence matrix $M$ corresponding to a tuple $\br{\pi_\mscenario, \pi_\jointvar}$ such that $\pi_X \in \Perm{\Sect{X}}$ for $X= \mscenario, \jointvar$ such that the following diagram holds for all $m \in \Sect{\mscenario}$ and $j \in \Sect{\jointvar}$.
+        \begin{center}
+            \begin{tikzpicture}
+                \newcommand{\symmetryspace}{1.5};
+                \draw (0, \symmetryspace) node[](m){$m$};
+                \draw (\symmetryspace, \symmetryspace) node[](j){$j$};
+                \draw (0, 0) node[](pm){$\pi_{\mscenario}\bs{m}$};
+                \draw (\symmetryspace, 0) node[](pj){$\pi_{\jointvar}\bs{j}$};
+
+                \draw[->] (m) -- node[left]{$\pi_\mscenario$}(pm);
+                \draw[->] (j) -- node[right]{$\pi_\jointvar$}(pj);
+                \draw[-<] (m) -- (j);
+                \draw[-<] (pm) -- (pj);
+            \end{tikzpicture}
+        \end{center}
+    \end{definition}
+
+    \subsection{Causal Symmetry}
+
+    The aim of this section is to formalize what types of symmetries are present in a particular causal structure $\graph$.
+The group of these causal symmetries will define, for each compatibility inequality $I_{\mscenario}$, a family of inequalities that are also valid incompatibility inequalities.
+
+    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\gep$ from $N$ to $N$.
+    \[ \Perm{N} = \bc{\gep \mid \gep : N \to N} \]
+    The action of $\gep \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\gep$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
+    \begin{align*}
+    \gep\bs{\graph} &\defined \br{\gep\bs{\nodes}, \gep\bs{\edges}} \\
+    \gep\bs{\nodes} &\defined \bc{\gep\bs{n} \mid n \in \nodes} = \nodes \\
+    \gep\bs{\edges} &\defined \bc{\gep\bs{e} \mid e \in \edges}
+    \end{align*}
+    To motivate a more general treatment of such symmetries, consider the Triangle Scenario of \cref{fig:triangle_scenario}.
+Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\gep \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\gep\bs{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes.
+By construction, any valid compatibility inequality $I_{\mscenario}$ for the marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes.
+Therefore applying $\gep$ to all distributions in $I_{\mscenario}$ yields $\gep\bs{I_{\mscenario}} \defined \gep\bs{I}_{\gep\bs{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\gep\bs{\mscenario}$ defined as,
+    \[ \gep\bs{\mscenario} = \bc{\gep\bs{V_1}, \ldots, \gep\bs{V_k}} \]
+    % \begin{example}
+    %     \todo[TC]{Above trivial example.}
+    %     Consider the marginal scenario $V_{\bs{4}} = \bc{\bc{A,B,C}, \bc{A}, \bc{B}, \bc{C}}$ and the compatibility inequality $I_{\bc{ABC, A, B, C}}$ for the Triangle Scenario in \cref{fig:triangle_scenario} with the following form,
+    %     \[ \prob[ABC][002]\prob[ABC][003] \leq \prob[A][0]\prob[C][3] \]
+    %     Now consider $\gep = \bc{A \to A, B \to C, C \to B}$. Since $\gep\bs{\graph} = \graph$, $\gep\bs{I_{\mscenario}}$ is also a valid compatibility inequality,
+    % \end{example}
+    More generically, any permutation $\gep$ that preserves the graphical structure of $\graph$ can be applied to $I_{\mscenario}$ to generate new and valid compatibility inequalities.
+Specifically this alludes to the \term{graph automorphism group} $\Aut{\graph}$ of $\graph$.
+    \[ \Aut{\graph} \defined \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph} \]
+    In general, $\Aut{\graph}$ could include elements $\gep$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}.
+This behaviour is \textit{undesired} for causal inference where the latent nodes will never appear in a marginal scenario.
+Instead, the subgroup of $\Aut{\graph}$ that never maps observable nodes to latent nodes is the \term{set-wise stabilizer} of $\Aut{\graph}$ for $\nodes_O$ and will be expressed with a subscript.
+
+    \begin{definition}
+        The \term{causal symmetry group} for a causal structure $\graph$ is the graph automorphism subgroup that stabilizes the observable nodes.
+        \[ \Aut[\nodes_O]{\graph} = \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph, \forall n \in \nodes_O :\gep\bs{n} \in \nodes_O} \]
+        Given any compatibility inequality $I_{\mscenario}$, each element $\gep$ of the causal symmetry group defines a new valid compatibility inequality $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
+    \end{definition}
+
+    The inflation technique discussed in \cref{sec:summary_inflation} allows one to derive compatibility inequalities for a causal structure $\graph$ by considering the marginal problem over the pre-injectable sets of $\graph'$ denoted $\PreInj[\graph]{\graph'} = \bc{V_1, \ldots, V_k}$.
+It is important to recall that due to \cref{lem:inflation}, inequalities $I'$ for $\graph'$ are \textit{only} transferable to inequalities $I$ for $\graph$ if $I'$ is in terms of distributions over the pre-injectable sets $I'_{\PreInj[\graph]{\graph'}}$.
+As a consequence of this observation, we need to consider a subgroup of the causal symmetry group that preserves the pre-injectable sets,
+    \[ \gep\bs{\PreInj[\graph]{\graph'}} = \PreInj[\graph]{\graph'} \eq \label{eq:preserved_preinj} \]
+
+    \begin{definition}
+        The \term{restricted causal symmetry group} $\gp$ for a causal structure $\graph$ and a marginal scenario $\mscenario$ is the graph automorphism subgroup that stabilizes the marginal scenario $\mscenario$.
+        \[ \gp \defined \Aut[\mscenario]{\graph} = \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph, \forall V \in \mscenario : \gep\bs{V} \in \mscenario} \]
+        Given any compatibility inequality $I_{\mscenario}$ each element $\gep$ of the causal symmetry group defines a new valid compatibility inequality $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\mscenario}$ over the \textit{same} marginal context $\mscenario$.
+    \end{definition}
+
+    The restricted causal symmetry group for the pre-injectable sets of an inflation $\graph'$ is the ideal symmetry group for use with the inflation technique.
+If one obtains a particular inequality $I'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\gp$, an entire family of valid compatibility inequalities are also obtained.
+    \[ \bc{\gep\bs{I'}_{\PreInj[\graph]{\graph'}} \mid \gep \in \gp} \text{ where } \gp = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
+    We have obtained $\gp$ for the inflated triangle scenario \cref{fig:inflated_triangle_scenario}. $\gp$ is an order $48$ group with the following $4$ generators:
+    \begin{equation*}
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_1 \\
+    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_2 \\
+    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_3 \\
+    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_4 \\
+    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
+    \end{aligned}
+    \end{equation*}
+    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
+    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
+    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
+    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
+    It is easy to verify that $\gep_1, \gep_2, \gep_3, \gep_4$ are all automorphisms of the inflated Triangle Scenario $\graph'$ of \cref{fig:inflated_triangle_scenario}.
+Moreover they stabilize the observable nodes, and the map pre-injectable sets of \cref{eq:pre-injectable_triangle_scenario} to the pre-injectable sets.
+Finally, in the Triangle Scenario we have that,
+    \[ \gp = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \sim \Aut[\nodes_O]{\graph} \]
+    To see this, $\gep_1$ and $\gep_4$ become the identity element $\mathbb{I}$ in $\Aut[\nodes_O]{\graph}$ upon removal of the copy-index, leaving $\gep_2$ to generate reflections and $\gep_3$ to generate rotations.
+    \subsection{Symmetric Marginal Polytope}
+    Up until this point, we have discussed how new inequalities can be created from known ones by exploiting causal symmetry.
+Although very useful, we divert our attention to finding \textit{symmetric} inequalities themselves.
+    \[ \forall \gep \in \gp :  \gep\bs{I_{\mscenario}} = I_{\mscenario} \]
+    In order to do this, we must first define how elements $\gep \in \gp$ act on marginal outcomes $O_{\mscenario}$.
+    \begin{definition}
+        Let $\jointvar = \bc{v_1, \ldots, v_k}$ be a collection of random variables and let $\gep \in \Perm{\jointvar}$.
+$\jointvar$ is said to be \term{label invariant with respect to $\gep$} if the outcome labels for each variable $v \in \jointvar$ are unchanged under the action of $\gep$.
+        \[ \forall v \in \jointvar : O_{v} = O_{\gep\bs{v}} \]
+        Label invariance is a prerequisite for any kind of symmetry amoung random variables.
+    \end{definition}
+    \begin{definition}
+        Let $\jointvar = \br{v_1, \ldots v_k}$ be a collection of random variables along with a specific outcome $m \in \Sect{V}$ where $V \subseteq \jointvar$.
+The action of $\gep \in \Perm{\jointvar}$ on $m$ is a new outcome $\gep\bs{m} \in \Sect{\gep\bs{V}}$ over $\gep\bs{V} \subseteq \jointvar$ defined as follows,
+        \[ \forall v \in V : \br{\gep\bs{m}}\br{\gep\bs{v}} \defined m \br{v} \]
+        The idea being that $\gep$ modifies $m$ in such a way that permutes its domain while leaving its range invariant.
+    \end{definition}
+    \begin{example}
+        Consider the outcome $m = \bc{A \mapsto 0, B \mapsto 1, C \mapsto 2} \in \Sect{\bc{A,B,C}}$ where all variables have $4$ possible outcomes $O_A = O_B = O_C = \bc{0,1,2,3}$ and the permutation $\gep = \bc{A \to D, B \to C, C \to B, D \to A}$.
+        The \textit{action} of $\gep$ on $m$ is as follows,
+        \begin{align*}
+            \gep\bs{m} &= \gep\bs{\bc{A \mapsto m\br{A}, B \mapsto m\br{B}, C \mapsto m\br{C}}} \\
+            &= \bc{\gep\bs{A} \mapsto m\br{A}, \gep\bs{B} \mapsto m\br{B}, \gep\bs{C} \mapsto m\br{C}} \\
+            &= \bc{D \mapsto m\br{A}, C \mapsto m\br{B}, B \mapsto m\br{C}} \\
+            &= \bc{D \mapsto 0, C \mapsto 1, B \mapsto 2} \\
+            &= \bc{B \mapsto 2, C \mapsto 1, D \mapsto 0}
+        \end{align*}
+        Evidently, $\gep\bs{m} \in \Sect{\bc{B, C, D}}$.
+    \end{example}
+
+    Through repeated action of $\gep \in \gp$ on marginal outcomes $m \in \Sect{\mscenario}$ and joint outcomes $j \in \Sect{\jointvar}$, one can define group orbits of $\gp$ in $\Sect{\mscenario}$ and $\Sect{\jointvar}$.
+    \begin{align*}
+        \Orb[\gp]{m} &\defined \bc{\gep\bs{m} \mid \gep \in \gp} \\
+        \Orb[\gp]{j} &\defined \bc{\gep\bs{j} \mid \gep \in \gp}
+    \end{align*}
+
+    \begin{definition}
+        The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and a particular restricted causal symmetry $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
+Each row of $M_{\gp}$ corresponds to a marginal orbit $\Orb[\gp]{m}$.
+Analogously each column of $M_{\gp}$ corresponds to a joint orbit $\Orb[\gp]{j}$.
+The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
+        \[ M_{\gp}\bs{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M\bs{m',j'} \]
+    \end{definition}
+
+    \subsection{Results}
+
+    \todo[TC]{How we obtained the desired symmetry group}
+    \todo[TC]{Group orbits to symmetric marginal description matrix}
+    \todo[TC]{representative antecedents completely solve the marginal problem}
 
@@
     The triangle scenario $\ts$ is a causal structure composed of $3$ parties $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
-It has that has been studied extensively in existing literature (see \cite[Fig.
-1]{Steudel_2010}, \cite[Fig.
-6]{Chaves_2014}, \cite[Fig.
-8]{Branciard_2012}, \cite[Fig.
-8, Appendix E]{Henson_2014}, \cite[Fig.
-3]{Fritz_2012}, \cite[Fig.
+It has that has been studied extensively in existing literature (see~\cite[Fig.
+1]{Steudel_2010},~\cite[Fig.
+6]{Chaves_2014},~\cite[Fig.
+8]{Branciard_2012},~\cite[Fig.
+8, Appendix E]{Henson_2014},~\cite[Fig.
+3]{Fritz_2012},~\cite[Fig.
 1]{Inflation}, $\ldots$) and is reproduced here in \cref{fig:triangle_scenario} for convenience.
-At the time of publication for \cite{Branciard_2012} it was noted that characterizing locality in $\ts$ remained an open problem and that identifying locality constraints in this configuration seemed challenging.
-In \cite{Henson_2014}, $\ts$ was classified as an ``interesting'' causal structure.\footnote{Indicating that conditional independence relations are not a sufficient characterization of compatibility for $\ts$ \cite{Henson_2014}.
-Note that in $\ts$ there are \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Additionally $\ts$ is presented along with a family of entropic inequalities that constrain the set of compatible distributions \cite{Henson_2014}.
-Furthermore in \cite{Fritz_2012}, Fritz demonstrated that $\ts$ is the \textit{smallest} correlation scenario in which their exists quantum incompatible distributions by explicitly mentioning one (which we elect to call the \textit{Fritz distribution} in \cref{sec:fritz_dist}) and poses an important question asking if other incompatible quantum distributions exist.
-Finally in \cite{Inflation}, Wolfe et.
+At the time of publication for~\cite{Branciard_2012} it was noted that characterizing locality in $\ts$ remained an open problem and that identifying locality constraints in this configuration seemed challenging.
+In~\cite{Henson_2014}, $\ts$ was classified as an ``interesting'' causal structure.\footnote{Indicating that conditional independence relations are not a sufficient characterization of compatibility for $\ts$~\cite{Henson_2014}.
+Note that in $\ts$ there are \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Additionally $\ts$ is presented along with a family of entropic inequalities that constrain the set of compatible distributions~\cite{Henson_2014}.
+Furthermore in~\cite{Fritz_2012}, Fritz demonstrated that $\ts$ is the \textit{smallest} correlation scenario in which their exists quantum incompatible distributions by explicitly mentioning one (which we elect to call the \textit{Fritz distribution} in \cref{sec:fritz_dist}) and poses an important question asking if other incompatible quantum distributions exist.
+Finally in~\cite{Inflation}, Wolfe et.
 al.
@@
 al.
-validate the power and applicability of the inflation technique by proving incompatibility between $\ts$ and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints \cite{Inflation}.
-Moreover, a family of polynomial, $2$-outcome, compatibility inequalities are explicitly derived for an exemplary inflation of $\ts$ and $37$ non-trivial representatives are printed in \cite{Inflation}.
+validate the power and applicability of the inflation technique by proving incompatibility between $\ts$ and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints~\cite{Inflation}.
+Moreover, a family of polynomial, $2$-outcome, compatibility inequalities are explicitly derived for an exemplary inflation of $\ts$ and $37$ non-trivial representatives are printed in~\cite{Inflation}.
 
@@
 
-    As a preliminary search for quantum incompatibility in $\ts$, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements (see \cref{sec:param_quantum_states} for details) against the $37$ compatibility inequalities printed in \cite{Inflation} as well as the entropic inequalities presented by \cite{Henson_2014}.
+    As a preliminary search for quantum incompatibility in $\ts$, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements (see \cref{sec:param_quantum_states} for details) against the $37$ compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by~\cite{Henson_2014}.
 Unfortunately, none of these inequalities could be violated.
@@
     Specifically, we make use of the inflation technique for an inflated triangle scenario $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} and cast the \textit{causal compatibility} problem as a \textit{marginal problem}.
-We develop a new technique which we call the \textit{extension covering procedure (ECP)} to find a complete solution to the marginal problem that is suitable for large causal structures where the observable nodes are equipped with numerous outcomes.
+We develop a new technique which we call the \textit{definite extension procedure (DEP)} to find a complete solution to the marginal problem that is suitable for large causal structures where the observable nodes are equipped with numerous outcomes.
 We use this technique to find numerous compatibility inequalities, some of which witness the incompatibility of the Fritz distribution.
-Before discussing the ECP, the Fritz distribution will be re-defined explicitly here, followed by a quick summary of the inflation technique of \cite{Inflation}.
-Following these summaries of existing work, we present the ECP and its connection to Hardy-type paradoxes \cite{Inflation,Liang_2011,Mansfield_2012}, certificate inequalities and logical Bell inequalities \cite{Abramsky_2011}.
-Moreover, the ECP can be adapted to derive symmetric inequalities or inequalities bounding any subspace of marginal models.
+Before discussing the DEP, the Fritz distribution will be re-defined explicitly here, followed by a quick summary of the inflation technique of~\cite{Inflation}.
+Following these summaries of existing work, we present the DEP and its connection to Hardy-type paradoxes~\cite{Inflation,Liang_2011,Mansfield_2012}, certificate inequalities and logical Bell inequalities~\cite{Abramsky_2011}.
+Moreover, the DEP can be adapted to derive symmetric inequalities or inequalities bounding any subspace of marginal models.
 To conclude, we subject our found inequalities to non-linear optimizations and discuss the implications of our results.
@@
     \label{sec:fritz_dist}
-    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario \cite{Fritz_2012}.
+    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario~\cite{Fritz_2012}.
 Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
@@
 
-    Fritz first proved it's incompatibility \cite{Fritz_2012} by showing $C$ acts a moderator to ensure measurement pseudo-settings for $A$ and $B$ are independent, satisfying non-broadcasting requirements for the standard Bell scenario.
+    Fritz first proved it's incompatibility~\cite{Fritz_2012} by showing $C$ acts a moderator to ensure measurement pseudo-settings for $A$ and $B$ are independent, satisfying non-broadcasting requirements for the standard Bell scenario.
 In fact, by coarse-graining outcomes for $A$ and $B$ and treating $C$ as a measurement-setting moderator, $P_F$ maximally violates the CHSH inequality.
-To illustrate this, begin with the CHSH inequality \cite{CHSH_Original},
+To illustrate this, begin with the CHSH inequality~\cite{CHSH_Original},
     \[ \ba{AB|S_A=1, S_B=1} + \ba{AB|S_A=1, S_B=2} + \ba{AB|S_A=2, S_B=1} - \ba{AB|S_A=2, S_B=2} \leq 2 \eq \label{eq:CHSH}\]
@@
     \end{gather*}
-    Which when applied to \cref{eq:chsh_c} gives the familiar Tsirelson violation of $2\sqrt{2} \not\leq 2$ \cite{Cirelson_1980}.
+    Which when applied to \cref{eq:chsh_c} gives the familiar Tsirelson violation of $2\sqrt{2} \not\leq 2$~\cite{Cirelson_1980}.
 
@@
 
-    In \cite{Fritz_2012}, Fritz posits the following question: \textit{Find an example of non-classical quantum correlations in $\ts$ together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}
+    In~\cite{Fritz_2012}, Fritz posits the following question: \textit{Find an example of non-classical quantum correlations in $\ts$ together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}
 
@@
     \label{sec:summary_inflation}
-    The causal inflation technique, first pioneered by Wolfe, Spekkens, and Fritz \cite{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of Ref.
-\cite{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a probability distribution is compatible or incompatible with a given causal structure.
+    The causal inflation technique, first pioneered by Wolfe, Spekkens, and Fritz~\cite{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of Ref.~\cite{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a probability distribution is compatible or incompatible with a given causal structure.
 As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
@@
 For example node $A$ of \cref{fig:triangle_scenario} has copies $A_1, A_2, A_3, A_4$ in the inflation of \cref{fig:inflated_triangle_scenario}.
-Following the notions of Ref.
-\cite{Inflation}, all such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
+Following the notions of Ref.~\cite{Inflation}, all such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
 A copy-index is effectively arbitrary, so $A'$ will refer to an arbitrary inflated copy of $A$.
@@
         \term{The Inflation Lemma} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-        This is lemma 3 of \cite{Inflation}.
+        This is lemma 3 of~\cite{Inflation}.
     \end{lemma}
 
-    The inflation lemma is the most important result of the causal inflation technique \cite{Inflation}.
+    The inflation lemma is the most important result of the causal inflation technique~\cite{Inflation}.
 The contrapositive version of \cref{lem:inflation} is a powerful tool for determining compatibility.
 Any compatibility constraint on marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ of the inflated causal structure $\graph'$ correspond to valid compatibility constraints on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure.
-Corollary 5 of \cite{Inflation} proves this explicitly for incompatibility inequalities $I$; which the remainder of this work focuses on.
+Corollary 5 of~\cite{Inflation} proves this explicitly for incompatibility inequalities $I$; which the remainder of this work focuses on.
 Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
@@
     \[ \forall i,j : N'_i \ancestralindep N'_j \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset  \]
-    In doing so, any distribution over all nodes of a pre-injectable set $\prob[\cup_i N'_i]$ will factorize according to graphical $d$-separation conditions \cite{Pearl_2009},
+    In doing so, any distribution over all nodes of a pre-injectable set $\prob[\cup_i N'_i]$ will factorize according to graphical $d$-separation conditions~\cite{Pearl_2009},
     \[ \prob[V] = \prob[\cup_i N'_i] = \prod_{i}\prob[N'_i] \]
@@
 
-    Focusing on the inflation $\ts'$ depicted in \cref{fig:inflated_triangle_scenario}, we obtained the injectable sets $\Inj[\ts]{\ts'}$ along with the maximally pre-injectable sets through a simple graphical procedure outlined in \cite{Inflation}.
+    Focusing on the inflation $\ts'$ depicted in \cref{fig:inflated_triangle_scenario}, we obtained the injectable sets $\Inj[\ts]{\ts'}$ along with the maximally pre-injectable sets through a simple graphical procedure outlined in~\cite{Inflation}.
     \begin{equation*}
@@
 
-    \section{Certificate Inequalities}
-    \label{sec:certificate_inequalities}
-    \subsection{Casting the Marginal Problem as a Linear Program}
-    After obtaining the maximal pre-injectable sets associated with a particular inflation, one can write the marginal problem of \cref{def:marginal_problem} as a linear program.
-The key observation is that marginalization is a \textit{linear} operator that can be performed via a matrix multiplication.
-To do this, we will define the \textit{incidence matrix}.
-    \begin{definition}
-        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} outcomes $j \in \Out{\jointvar}$ and the rows are indexed by \textit{marginal} outcomes $m \in \Out{\mscenario}$.
-The entries of $M$ are populated whenever a row index is extendable to a column index.
-        \[ M\bs{m, j} = \de_{m \ext j} \defined \begin{cases}
-            1 & m \ext j \\
-            0 & \text{otherwise}
-        \end{cases} \]
-        Where $\de_{m \ext j}$ is an \textit{extendability indicator}.
-The incidence matrix has $\abs{\Out{\jointvar}}$ columns and $\abs{\Out{\mscenario}} = \sum_{i\in \bs{k}} \abs{\Out{V_i}}$ rows.
-The number of non-zero entries of $M$ is a simple expression,
-        \[ \sum_{i\in\bs{k}} \abs{\Out{V_i}}\abs{\Out{\jointvar \setminus V_i}} = \sum_{i\in \bs{k}} \abs{\Out{\jointvar}} = k\abs{\Out{\jointvar}} \]
-        This is due to the fact that each marginal context contributes a single non-zero entry to each column of $M$, resulting in $k\abs{\Out{\jointvar}}$ total non-zero entries.
-    \end{definition}
-    \todo[TC]{Computationally Efficient generation?}
-
-    To illustrate this concretely, consider the following example:
-    \begin{example}
-        \label{ex:marginal_matrix}
-        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and consider the marginal scenario $\mscenario = \bc{\bc{a,b}, \bc{b,c}, \bc{a,c}}$. The incidence matrix becomes:
-        \newcommand{\kone}{\mathbf{1}}
-        \newcommand{\kzer}{\textcolor{gray}{0}}
-        \[ M = \kbordermatrix{
-            (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
-            (a\mapsto0, b\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto0, b\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto1, b\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
-            (a\mapsto1, b\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
-            (b\mapsto0, c\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
-            (b\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
-            (b\mapsto1, c\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
-            (b\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
-            (a\mapsto0, c\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto1, c\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
-            (a\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
-        } \]
-    \end{example}
-
-    \begin{example}
-        The marginal problem for the inflated causal structure $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} concerns itself with the pre-injectable marginal scenario $\mscenario = \PreInj[\ts]{\ts'} = \bc{V_1, \ldots, V_{12}}$.
-Equipping the observed nodes of $\ts'$ with $4$-element outcome labels, the incidence matrix $M$ has $16,896$ rows and $16,777,216$ columns.
-        \begin{align*}
-            &\text{\# Rows} = \abs{\Out{\mscenario}} = \sum_{i=1}^{12} \abs{\Out{V_i}} = \sum_{i=1}^{12} 4^{\abs{V_i}} = 4 \cdot 4^6 + 8 \cdot 4^3 = 16,896 \\
-            &\text{\# Columns} = \abs{\Out{\jointvar}} = 4^{\abs{\jointvar}} = 4^{12} = 16,777,216
-        \end{align*}
-        With $12 \cdot 4^{12} = 201,326,592$ non-zero entries. For obvious reasons, no attempt is made to reproduce it here.
-    \end{example}
-
-    In order to describe how marginalization can be written as matrix multiplication $M \cdot x = b$, two more quantities need to be described:
-
-    \begin{definition}
-        The \term{joint distribution vector} $\probvec[\jointvar]$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint outcome of $j \in \Out{\jointvar}$.
-$\probvec[\jointvar]$ shares the same indices as the \textit{column} indices of $M$.
-        \[ \forall j \in \Out{\jointvar} : \probvec[\jointvar]^\intercal\bs{j} = \prob[\jointvar][j] \]
-    \end{definition}
-    \begin{definition}
-        The \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Out{\mscenario}$.
-$\probvec^{\mscenario}$ shares the same indices as the \textit{row} indices of $M$.
-        \[ \forall m \in \Out{\mscenario} : {\probvec^{\mscenario}}^\intercal\bs{m} = \prob[\Dom{m}][m] \]
-        Where $\Dom{m} \in \mscenario$ and $\prob[\Dom{m}] \in \prob^{\mscenario}$ as per \cref{rem:domain_dist}.
-    \end{definition}
-    The marginal and joint distribution vectors are related via the incidence matrix $M$.
-Given a joint distribution vector $\probvec[\jointvar]$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec[\jointvar]$.
-    \[ \probvec^{\mscenario} = M \cdot \probvec[\jointvar] \eq \label{eq:marginal_problem_matrix} \]
-
-    \begin{remark}
-        The particular ordering of the rows and columns of $M$ carries no importance, but it \textit{must} be consistent between $M$, $\probvec[\jointvar]$ and $\probvec^{\mscenario}$.
-Throughout this work, a \textit{canonical ordering} is used: the marginal contexts are written in the same order as listed in the marginal scenario $\mscenario$ and outcomes within a marginal context are enumerated in a \textit{raveling} order; exemplified in \cref{ex:marginal_matrix}.
-    \end{remark}
-
-    The marginal problem can now be rephrased in the language of the incidence matrix.
-Suppose one obtains a marginal distribution vector $\probvec^{\mscenario}$.
-The marginal problem becomes equivalent to the question: \textit{Does there exist a joint distribution vector $\probvec[\jointvar]$ such that \cref{eq:marginal_problem_matrix} holds?}
-
-    \begin{definition}
-        \label{def:marginal_linear_program}
-        \term{The Marginal Linear Program} is the following linear program:
-        \begin{alignat*}{2}
-            & \text{minimize:} \quad&& \emptyset \cdot x\\
-            & \text{subject to:} && x \succeq 0 \\
-            & && M \cdot x = \probvec^{\mscenario}
-        \end{alignat*}
-        If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries).
-The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:marginal_problem_matrix} and is a valid joint distribution vector.
-Therefore feasibility implies that $\prob[\jointvar] = x$, solving the marginal problem with positive result.
-Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\prob[\jointvar]$ over all random variables.
-    \end{definition}
-    \begin{definition}
-        \label{def:dual_marginal_linear_program}
-        \term{The Dual Marginal Linear Program} is the dual of \cref{def:marginal_linear_program} formulated via a procedure similar to \cite{Lahaie_2008}:
-        \begin{alignat*}{2}
-            & \text{minimize:} \quad&& y \cdot \probvec^{\mscenario}\\
-            & \text{subject to:} && y \cdot M \succeq 0
-        \end{alignat*}
-        Where $y$ is a real valued vector with the same length as $\probvec^{\mscenario}$.
-    \end{definition}
-    \subsection{Infeasibility Certificates}
-    \label{sec:infeasibility_certificates}
-    The dual marginal linear program also provides an answer to the marginal problem.
-To prove this, first notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints are satisfied.
-Secondly if $y \cdot M \succeq 0$ and $x \succeq 0$, then the following must hold if the primal is feasible:
-    \[ y \cdot \probvec^{\mscenario} =  y \cdot M \cdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
-    Therefore the \textit{sign} of the dual value $d \defined \min \br{y \cdot \probvec^{\mscenario}}$ solves the marginal problem.
-If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore the marginal problem has negative result.
-Likewise if $d$ satisfies \cref{eq:dual_marginal_ineq}, then a joint distribution $\prob[\jointvar]$ exists.
-Before continuing, an important observation needs to be made.
-If $d \geq 0$, then it is exactly $d = 0$, due to the existence of the trivial $y = \emptyset$.
-This observation is an instance of the \textit{Complementary Slackness Property} of \cite{Bradley_1977}.
-\comment[TC]{Is this really the CSP?} Moreover, if $d < 0$, then it is unbounded $d = -\inf$.
-This latter point becomes clear upon recognizing that for any $y$ such that $d < 0$, another $y'$ can be constructed by multiplying $y$ by a real constant $\al$ greater than one such that,
-    \[ y' = \al y \mid \al > 1 \implies d' = \al d < d \]
-    Since a more negative $d'$ can always be found, it must be that $d$ is unbounded.
-This is a demonstration of the fundamental \textit{Unboundedness Property} of \cite{Bradley_1977}; if the dual is unbounded, then the primal is infeasible.
-
-    \comment[TC]{\href{http://web.stanford.edu/~ashishg/msande111/notes/chapter4.pdf}{Farkas's lemma} here?}
-
-    \begin{definition} An \term{infeasibility certificate} \cite{Andersen_2001} is any vector $y$ that satisfies the constraints of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
-    \[ y \in \R^{\abs{\Out{\mscenario}}} : y \cdot M \succeq 0, \quad y \cdot \probvec^{\mscenario} < 0 \]
-    Furthermore, any $y$ satisfying $y \cdot M \succeq 0$ induces a \term{certificate inequality} that constraints the space of marginal distribution vectors which takes the symbolic form of \cref{eq:dual_marginal_ineq},
-    \[ y \cdot \probvec^{\mscenario} \geq 0 \]
-    Where the entries of the certificate $y$ act as coefficients for the entries of $\probvec^{\mscenario}$.
-    \end{definition}
-    \todo[TC]{Discuss Infeasibility Certificates basis}
-    \todo[TC]{Discuss the certificate inequalities we found.}
-
-    \[ I\tsb{Mosek-Cert}, I\tsb{Cert} \]
-
-    \section{Covering Inequalities}
-
-    Section \ref{sec:certificate_inequalities} discusses how one can obtain a valid compatibility inequality that witnesses incompatibility for a particular marginal model $\prob^{\mscenario}$ by writing the marginal problem as a linear program.
-It was demonstrated that every incompatible distribution is witness-able by some certificate inequality.
-However, when a particular marginal model $\prob^{\mscenario}$ is not known, a linear optimization offers no utility.
-    \todo[TC]{Motivate why certificates are not enough, want many solutions, want logical foundation}
-    % Throughout this section, there will be a few omissions of notation to help clar
-
-    In this section, we will first summarize a method that can be used to obtain a complete solution to the \textit{possibilistic} marginal problem and indirectly offer a \textit{partial} solution to the \textit{probabilistic} marginal problem.
-Doing so corresponds to enumerating all
-    \subsection{Logical Covers}
-    In this section, we summarize the familiar notion of logical implications as witnesses for contextuality.
-Let $a \in \Out{\mscenario}$ be a marginal outcome and let $C = \bc{c_1, \ldots, c_{\abs{C}}} \subseteq \Out{\mscenario}$ be a subset of marginal outcomes.
-The subset $C$ is a \term{logical cover} of $a$ if the following possibilistic statement holds for \textit{all} marginal models $\prob^{\mscenario}$.
-    \[ a \implies c_1 \vee \ldots \vee c_{\abs{C}} = \bigvee_{c \in C} c \eq \label{eq:1a_implication} \]
-    The marginal outcome $a$ will be referred to as the \textit{antecedent} and $C$ as the \textit{consequent set}.
-A marginal model $\prob^{\mscenario}$ satisfies \cref{eq:1a_implication} if there always exists at least one $c \in C$ that is possible ($\prob[][c] > 0$) whenever $a$ is possible.
-A marginal model $\prob^{\mscenario}$ violates \cref{eq:1a_implication} whenever \textit{none} of the outcomes in $C$ are possible while $a$ is nonetheless still possible.
-Marginal models that violate logical statements such as \cref{eq:1a_implication} are known as \term{Hardy Paradoxes} \cite{Inflation,Mansfield_2012,Mancinska_2014}.
-The concept of witnessing quantum incompatibility on a logical level has been analyzed thoroughly for decades \cite{Greenberger_1990,Abramsky_2012}; being motivated by a false sense of robustness compared to probabilistic constraints.
-Logical covers such as \cref{eq:1a_implication} are in one-to-one correspondence with a subset of probabilistic inequalties.
-
-    \begin{lemma}
-        \label{lemma:logical_extenable_set}
-        Let $a \in \Out{\mscenario}$ be some marginal outcome of the marginal scenario $\mscenario$.
-If any marginal model $\prob^{\mscenario}$ is to be non-contextual, the following condition must hold.
-        \[ a \iff \bigvee_{j \in \Ext[\jointvar]{a}} j \eq \label{eq:lemma_logical_extendable_set}\]
-    \end{lemma}
-    The idea being that if a joint distribution exists, then the event $a$ represents partial knowledge of the entire system $\jointvar$; whenever $a$ occurs, exactly one of the extendable joint outcomes has to have occurred.
-Likewise \cref{lemma:logical_extenable_set} applies to a collection of marginal outcomes $C \in \Out{\mscenario}$,
-    \[ \bigvee_{c \in C} c \iff \bigvee_{c \in C} \bigvee_{j \in \Ext[\jointvar]{c}} j \eq \label{eq:logical_extension_C}\]
-    If a subset $C$ can be constructed such that its extension \textit{covers} the extendable set of $a$,
-    \[ \Ext[\jointvar]{a} \subseteq \bigcup_{c \in C} \Ext[\jointvar]{c} \eq \label{eq:logical_containment} \]
-    Then the combination of \cref{eq:lemma_logical_extendable_set,eq:logical_extension_C,eq:logical_containment} yields \cref{eq:1a_implication}.
-Hence the motivation for calling \cref{eq:1a_implication} a logical cover.
-
-    The principle statement of \cref{lemma:logical_extenable_set} can be taken in a probabilistic form.
-If the marginal model $\prob^{\mscenario}$ is to admit a joint distribution $\prob[\jointvar]$, then it must be that the probability $\prob[][a]$ of any marginal outcome $a \in \Out{\mscenario}$ is equal to a marginalization over its extendable set into $\jointvar$.
-    \[ \prob[][a] = \sum_{j \in \Ext[\jointvar]{a}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_a} \]
-    A logical cover $C \subseteq \Out{\mscenario}$ of $a$ has probabilistic extension,
-    \[ \sum_{c \in C}\prob[][c] = \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\prob[\jointvar][j] \eq \label{eq:marginal_extendable_sum_cs} \]
-    Since $C$ is a logical cover of $a$, the right-hand side of \cref{eq:marginal_extendable_sum_a} algebraically covers \cref{eq:marginal_extendable_sum_cs}\footnote{If there were a joint outcome $j^*$ present on the right-hand side of \cref{eq:marginal_extendable_sum_a} but not the right-hand side of \cref{eq:marginal_extendable_sum_cs}, then \cref{eq:1a_probabilistic} would be violated by the deterministic distribution $\prob[\jointvar][j^*] = 1$}.
-Therefore one recovers a probabilistic version of \cref{eq:1a_implication},
-    \[ \prob[][a] \leq \sum_{c \in C}\prob[][c] \eq \label{eq:1a_probabilistic} \]
-    \begin{remark}
-        It is also possible to recover \cref{eq:1a_probabilistic} from \cref{eq:1a_implication} directly, by putting \cref{eq:1a_implication} into disjunction normal form and assigning it a certain probability,
-        \[ \prob[][\neg a \vee \bigvee_{c \in C} c] = 1 \]
-        Then applying Boole's indentity and the negative rule $\prob[][\neg a] = 1 - \prob[][a]$ one recovers \cref{eq:1a_probabilistic}.
-    \end{remark}
-    \begin{remark}
-        The probabilistic logical cover \cref{eq:1a_probabilistic} is an \textit{upgraded} version of \cref{eq:1a_implication} in the following sense.
-        \begin{itemize}
-            \item Every non-contextual marginal model $\prob^{\mscenario}$ satisfies both \cref{eq:1a_probabilistic} and \cref{eq:1a_implication}.
-            \item Every contextual marginal model $\prob^{\mscenario}$ that violates \cref{eq:1a_implication} will also violate \cref{eq:1a_probabilistic}; but the converse is not necessarily true.
-        \end{itemize}
-    \end{remark}
-
-    Computationally enumerating all logical covers for a particular antecedent $a$ corresponds to a hypergraph transversal problem \cite{Inflation}, an idea we return to in the more general picture to follow.
-
-    \subsection{Extension Covers}
-    We will now generalize the notion of a logical cover by considering more exotic antecedents corresponding to multiple marginal outcomes along with weights $\mset{A}$ for each outcome.
-Afterwards we demonstrate that these generalized covers also admit non-trivial probabilistic compatibility inequalities.
-
-    \begin{definition}
-        We first define the marginal indicator vector $\de_{m}$ to be the unit vector indexed by marginal outcomes $\Out{\mscenario}$ that is $1$ whenever the index is $m$, and $0$ otherwise.
-        \[ \de_{m}\br{m} = 1 \quad \forall m' \neq m : \de_{m} \br{m'} = 0 \]
-        Analogously defined is the joint indicator vector $\de_{j}$.
-        \[ \de_{j}\br{j} = 1 \quad \forall j' \neq j : \de_{j} \br{j'} = 0 \]
-    \end{definition}
-
-    We first recall that every non-contextual marginal model $\prob^{\mscenario}$ can be written as the convex combination of columns of the incidence matrix $M$.
-    \[ \probvec^{\mscenario} = M \cdot \probvec[\jointvar] = \sum_{j \in \Out{\jointvar}} \de_{m \ext j} \prob[\jointvar][j] \]
-    Thus we define the set of all non-contextual marginal models as $\mathcal{NC}$,
-    \[ \mathcal{NC} \defined \bc{\probvec^{\mscenario} \mid \probvec^{\mscenario} = \sum_{j} \mu_{j} \de_{j \res \mscenario}, \mu_j \geq 0, \sum_{j} \mu_{j} = 1} \]
-
-    \begin{definition}
-        Let $\mscenario$ be a marginal scenario and let $m \in \Out{\mscenario}$ be a marginal outcome.
-The \term{extension of $m$ onto $\jointvar$} is the function $\de_{m \ext \jointvar} : \Out{\jointvar} \to \bc{0, 1}$ that indicates membership of $\Ext[\jointvar]{m}$.
-        \[ \de_{m \ext \jointvar}\br{j} \defined \begin{cases}
-            1 & j \ext m \\
-            0 & \textrm{otherwise}
-        \end{cases} \]
-        As a vector indexed by joint outcomes $j \in \Out{\jointvar}$, $\de_{m \ext \jointvar}$ is precisely the $m$-th row of the incidence matrix.
-    \end{definition}
-    \begin{definition}
-        Let $\mscenario$ be a marginal scenario and let $j \in \Out{\jointvar}$ be a joint outcome.
-The \term{restriction of $j$ onto $\mscenario$} is deterministic marginal model $\de_{j \res \mscenario} : \Out{\mscenario} \to \bc{0, 1}$.
-        \[ \de_{j \res \mscenario}\br{m} \defined \begin{cases}
-            1 & j \ext m  \\
-            0 & \textrm{otherwise}
-        \end{cases} \]
-        As a vector indexed by marginal outcomes $m \in \Out{\mscenario}$, $\de_{j \ext \mscenario}$ is precisely the $j$-th column of the incidence matrix.
-    \end{definition}
-
-    \begin{definition}
-        A \term{multiplicity set} or \term{m-set} $\mset{S}$ for a marginal scenario $\mscenario$ is a vector indexed by marginal outcomes $m \in \Out{\mscenario}$ whose entries are non-negative integers $\mset{S}_{m} \in \Z_{\geq 0}$.
-The \term{support} $\supp{\mset{S}}$ of an m-set is the set of marginal outcomes that are assigned strictly positive multiplicity.
-        \[ \supp{\mset{S}} \defined \bc{m \in \Out{\mscenario} \mid \mset{S}_m \in \N} \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{extension of an m-set} $\mset{S}$ into $\jointvar$ denoted $\extmset{S}$ is a vector indexed by \textit{joint} outcomes $j \in \Out{\jointvar}$ and is defined as follows,
-        \[ \extmset{S}_{j} \defined \sum_{s \in \supp{\mset{S}}} \mset{S}_{s} \de_{s \ext j} \eq \label{eq:joint_multiplicity} \]
-        As an immediate consequence, the support of $\extmset{S}$ is immediately known,
-        \[ \supp{\extmset{S}} = \bigcup_{s \in \supp{\mset{S}}} \Ext[\jointvar]{s} \]
-    \end{definition}
-    \begin{definition}
-        An m-set $\mset{C}$ is an \term{extension cover} of an m-set $\mset{A}$ for a marginal scenario $\mscenario$ if and only if the following two conditions hold\footnote{In fact \cref{eq:multi_extenable_cover_def} implies \cref{eq:flat_extenable_cover_def} since $\forall j \not \in \supp{\extmset{A}} : \extmset{A}_j = 0$.}:
-        \begin{gather*}
-            \supp{\extmset{A}} \subseteq \supp{\extmset{C}} \eq \label{eq:flat_extenable_cover_def}\\
-            \forall j \in \supp{\extmset{A}} : \extmset{A}_{j} \leq \extmset{C}_j \eq \label{eq:multi_extenable_cover_def}
-        \end{gather*}
-    \end{definition}
-    Identifying extension covers is of great importance because of the following theorem.
-    \begin{theorem}
-        \label{thm:extendable_cover_ineq}
-        If the m-set $\mset{C}$ is an extension cover of the m-set $\mset{A}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
-        \[ \sum_{a \in \supp{\mset{A}}}\mset{A}_a\prob[][a] \leq \sum_{c \in \supp{\mset{C}}}\mset{C}_c\prob[][c] \eq \label{eq:extendable_cover} \]
-    \end{theorem}
-    \begin{proof}
-        To prove that \cref{eq:extendable_cover} is a valid compatibility inequality $I_{\mscenario}$ for all marginal models $\prob^\mscenario$, we will demonstrate that \cref{eq:extendable_cover} follows from the assumption that a joint distribution $\prob[\jointvar]$ exists.
-
-        For each m-set $\mset{S}$ write the weighted sum over the probabilities $\bc{\prob[][s]}_{s \in \supp{\mset{S}}}$ in terms of the joint distribution $\prob[\jointvar]$ using \cref{eq:joint_multiplicity}.
-        \begin{align*}
-        \eq \label{eq:derivation_cover}
-        \begin{split}
-        \sum_{s \in \supp{\mset{S}}} \mset{S}_s\prob[][s] &= \sum_{s \in \supp{\mset{S}}} \mset{S}_s  \sum_{j \in \Ext[\jointvar]{s}} \prob[\jointvar][j] \\
-        &= \sum_{s \in \supp{\mset{S}}} \mset{S}_s \sum_{j \in \Out{\jointvar}} \isext{s}{j} \prob[\jointvar][j] \\
-        &= \sum_{j \in \Out{\jointvar}} \bs{\sum_{s \in \supp{\mset{S}}} \mset{S}_s  \isext{s}{j}} \prob[\jointvar][j] \\
-        &= \sum_{j \in \supp{\extmset{S}}} \extmset{S}_j \prob[\jointvar][j]
-        \end{split}
-        \end{align*}
-        First examine the substitution $S \to C$,
-        \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] = \sum_{j \in \supp{\extmset{C}}} \extmset{C}_j \prob[\jointvar][j] \]
-        By \cref{eq:flat_extenable_cover_def} $\supp{\extmset{A}} \subseteq \supp{\extmset{C}}$,
-        \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] = \sum_{j \in \supp{\extmset{C}}} \extmset{C}_j \prob[\jointvar][j] + \sum_{j \in \supp{\extmset{C}} \setminus \supp{\extmset{A}}} \extmset{C}_j \prob[\jointvar][j] \]
-        Notice that the sum over $j \in \supp{\extmset{C}} \setminus \supp{\extmset{A}}$ is entirely positive since $\extmset{C}_j \in \N$ and $\prob[\jointvar][j] \geq 0$.
-Moreover \cref{eq:multi_extenable_cover_def} gives $\extmset{C}_j \geq \extmset{A}_j$.
-Combining these observations along with \cref{eq:derivation_cover} for $S \to A$, one arrives at the inequality,
-        \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] \geq \sum_{j \in \supp{\extmset{A}}} \extmset{A}_j \prob[\jointvar][j] = \sum_{a \in \supp{\mset{A}}} \mset{A}_a\prob[][a] \]
-        Which is equivalent to \cref{eq:extendable_cover}; every non-contextual marginal model $\prob^{\mscenario}$ must satisfy \cref{eq:extendable_cover}.
-    \end{proof}
-    \begin{corollary}
-        \label{cor:linear_integer}
-        Every linear, integer coefficient compatibility inequality that is homogeneous is an extension covering inequality.
-    \end{corollary}
-    \begin{proof}
-        A proof is easy to see by contradiction.
-Let $I_{\mscenario} = \bc{\gamma \cdot \probvec^{\mscenario} \geq 0}$ where $\gamma_m \in \Z | \forall m \in \Out{\mscenario}$ be a homogeneous, linear, integer coefficient, compatibility inequality such that it is \textit{not} an extension covering inequality.
-Next seperate $\gamma$ into its positive and negative components,
-        \[ \gamma_m^{+} = \begin{cases}
-            \gamma_m & \gamma_m > 0 \\
-            0 & \gamma_m \leq 0
-        \end{cases}
-        \qquad
-        \gamma_m^{-} = \begin{cases}
-            -\gamma_m & \gamma_m < 0 \\
-            0 & \gamma_m \geq 0
-        \end{cases} \]
-        Such that both $\gamma^{+}$ and $\gamma^{-}$ are valid m-sets.
-Therefore $I_{\mscenario} = \bc{\br{\gamma^{+} - \gamma^{-}} \cdot \probvec^{\mscenario} \geq 0}$.
-Since this inequality is \textit{not} an extension cover, it must be that there exists at least one joint outcome $j' \in \Out{\jointvar}$ such that $\Gamma^{-}_{j'} > \Gamma^{+}_{j'}$.
-Consequently by \cref{eq:derivation_cover}, the deterministic distribution $\probvec^{\mscenario} = \de_{j' \res \mscenario}$ \textit{violates} $I_{\mscenario}$.
-However since $\de_{j' \res \mscenario} \in \mathcal{NC}$ and violates $I_{\mscenario}$, $I_{\mscenario}$ can not be a compatibility inequality; disagreeing with the assumption that it was.
-    \end{proof}
-    % \begin{corollary}
-    %     If the m-set $\mset{C}$ is an extension cover of the m-set $\br{A, \mulA}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
-    %     \[ \sum_{a \in \supp{\mset{A}}}\prob[][a] \leq \sum_{c \in \supp{\mset{C}}}\prob[][c] \eq \label{eq:extendable_cover_flat} \]
-    % \end{corollary}
-    % \begin{proof}
-    %     This follows from the fact that if $\mset{C}$ is an extension cover of $\br{A, \mulA}$, then $\br{C, \mathbf{1}_{C}}$ is an extension cover of $\br{A, \mathbf{1}_{A}}$.
-Since $E_A \subseteq E_C$ is already trivially satisfied, all that remains is to demonstrate that \cref{eq:multi_extenable_cover_def} holds for unitary multiplicities $\mathbf{1}_A$ and $\mathbf{1}_C$.
-
-    %     First examine extension $\br{E_C, \mul{\mext{C}}}$ for the m-set $\mset{C}$ as defined by \cref{eq:joint_multiplicity},
-    %     \[ \forall j \in E_C : \extmset{C}_j = \sum_{c \in \supp{\mset{C}}} \mulC\br{c} \isext{c}{j} \]
-
-    %     First apply \cref{lemma:logical_extenable_set} to an arbitrary set $S \in \bc{A, C}$,
-    %     \[ \bigvee_{s \in \supp{\mset{S}}} s \iff \bigvee_{s \in \supp{\mset{S}}} \bigvee_{j \in \Ext[\jointvar]{s}} j \iff \bigvee_{j \in E_S} j \eq \label{eq:logical_iff_ext}\]
-    %     Now since $E_A \subseteq E_C$ by \cref{eq:flat_extenable_cover_def} we have that,
-    %     \[ \bigvee_{j \in E_A} j \implies \bigvee_{j \in E_C} j \eq \label{eq:logical_cover}\]
-    %     Combining \cref{eq:logical_iff_ext,eq:logical_cover} one arrives at,
-    %     \[ \bigvee_{a \in \supp{\mset{A}}} a \implies \bigvee_{c \in \supp{\mset{C}}}c \]
-    % \end{proof}
-    % For a working example, let $\jointvar = \bc{a, b, c}$ be a set of binary random variables ($O = \bc{0,1}$) and $\mscenario = \bc{\bc{a,b},\bc{b,c},\bc{a,c}}$ be the marginal context.
-
-    \subsection{Completeness of Extension Covers}
-    Corollary \ref{cor:linear_integer} alludes to completeness of extension covers.
-It vaguely suggests that every non-contextuality inequality needs to be an extension cover, otherwise there would exist a compatible and deterministic distribution that violates it.
-We will now demonstrate this completeness explicitly by first discussing what is required of a complete solution to the marginal problem.
-    \begin{definition}
-        A \term{complete solution to the marginal problem} is a finite set of $q$ vectors $\gamma_1, \ldots, \gamma_q$ together with $q$ real numbers $k \in \R$
-    \end{definition}
-    \begin{theorem}
-        \label{thm:complete_solution_log_cover}
-        The set of all logical covering inequalities forms a sufficient solution to the possibilistic marginal problem.
-    \end{theorem}
-    \begin{theorem}
-        \label{thm:complete_solution_ext_cover}
-        The set of all extension covering inequalities forms a sufficient solution to the probabilistic marginal problem.
-    \end{theorem}
-    \begin{proof}
-    \end{proof}
-    \begin{definition}
-        An extension cover $\mset{C}$ of $\mset{A}$ is said to be \term{minimal} if there does not exist an extension cover $\mset{C'}$ different from $\mset{C}$ such that,
-        \[ \forall j \in \Out{\jointvar} : \mset{C'}_j \leq \mset{C}_j \]
-    \end{definition}
-
-    If a more minimal extension cover $\mset{C'}$ does exists, then the inequality it defines (as per \cref{thm:extendable_cover_ineq} directly implies the inequality defined by $\mset{C}$.
-
-    \begin{definition}
-        An extension cover $\mset{C}$ of $\mset{A}$ is said to be \term{reducible} if there exists a \textit{partition} of $\mset{C}$ and $\mset{A}$,
-        \[ \mset{C} = \mset{C_1} + \mset{C_2} \qquad \mset{A} = \mset{A_1} + \mset{A_2} \]
-        Such that $\mset{C_1}$ is an extension cover for $\mset{A_1}$ and $\mset{C_2}$ is an extension cover for $\mset{A_2}$.
-If $\br{\mset{C}, \mset{A}}$ does \textit{not} admit a partition, then it is said to be \term{irreducible}.
-    \end{definition}
-
-    \todo[TC]{Basis certificates}
-
-    \subsection{Extension Cover Procedure}
-    The \term{extension cover procedure} begins with an antecedent m-set $\mset{A}$ and iteratively produces consequent m-sets $\mset{C}$ that are extension covers of $\mset{A}$.
-To facilitate this, we define a \term{partial consequent m-set} to be any marginal m-set $\mset{*C}$ that \textit{has yet to} become an extension cover of $\mset{A}$.
-Also define the null m-set $\mset{\emptyset}$ to be the m-set assigning zero multiplicity to each marginal outcome.
-As a preliminary insight, it is realatively easy to construct a valid extension cover of $\mset{A}$ by first beginning with $\mset{*C} = \mset{\emptyset}$ and iteratively increasing entries in $\mset{*C}$ until \cref{eq:multi_extenable_cover_def} is satisfied.
-To ensure efficient construction, it is wise to first identity a particular joint outcome $j'$ that violates \cref{eq:multi_extenable_cover_def} $\extmset{*C}_{j'} < \extmset{A}_{j'}$, and then append to $\extmset{*C}$ a marginal outcome $m$ ($\extmset{*C} \mapsto \extmset{*C} + \de_{m}$) that is extendable to $j'$.
-Eventually, enough marginal outcomes will be added to the partial extension cover $\extmset{*C}$ for \cref{eq:multi_extenable_cover_def} to hold.
-
-    This procedure can be generalized to find \textit{all} minimal extension covers for a chosen antecdent m-set $\mset{A}$ and is best formalized as a \textit{weighted hypergraph transversal} problem.
-
-    \subsubsection{Hypergraphs}
-    \begin{definition}
-        \label{def:hypergraph}
-        A \term{hypergraph} denoted $\hgraph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{hyperedges} respectively where the nodes can represent any object and the hyperedges are \textit{subsets} of nodes.
-For convenience of notation, one defines an index set over the nodes and hyperedges of a hypergraph $\hgraph$ denoted $\ind_\nodes$ and $\ind_\edges$ respectively.
-        \[ \hgraph = \br{\nodes, \edges} \quad \nodes = \bc{n_i \mid i \in \ind_\nodes} \quad \edges = \bc{e_i \mid i \in \ind_\edges, e_i \subseteq \nodes} \]
-        Note that whenever the hyperedge or node index is arbitrary, it will be omitted.
-There is a dual correspondence between hyperedges $e \in \edges$ and nodes $n \in \nodes$ in a Hypergraph.
-A hyperedge $e$ is viewed as a set of nodes $\bc{n_i}$, and a node $n$ can be viewed as the set of hyperedges $\bc{e_i}$ that contain it.
-    \end{definition}
-
-    \begin{definition}
-        \label{def:hgraph_trans}
-        A \term{hypergraph transversal} (or edge hitting set) $\trans$ of a hypergraph $\hgraph$ is a set of nodes $\trans \subseteq \nodes$ that have non-empty intersections with every hyperedge in $\edges$.
-        \[ \trans = \bc{n_i \in \nodes \mid i \in \ind_\trans } \quad \forall e \in \edges : \trans \cap e \neq \emptyset \]
-    \end{definition}
-
-    \begin{definition}
-        A \term{necessary node} of a transversal $\trans$ is a node $n$ such that $\trans \setminus n$ is no longer a valid transversal. The set of all necessary nodes is denoted $\Nec{\trans}$,
-        \[ \Nec{\trans} = \bc{n \in \trans \mid \exists e \in \edges : \br{\trans \setminus n} \cap e = \emptyset} \]
-        An \term{unnecessary node} of a transversal $\trans$ is any node that is \textit{not} necessary. The set of all unnecessary nodes is denoted $\UnNec{\trans}$,
-        \[ \UnNec{\trans} = \trans \setminus \Nec{\trans} \]
-        A \term{minimal hypergraph transversal} $\trans$ is any valid transversal of $\hgraph$ where every node $n$ is \textit{necessary}.
-        \[ \trans = \Nec{\trans} \]
-    \end{definition}
-
-    \begin{definition}
-        A \term{weighted hypergraph} $\hgraph_\weights$ is a regular hypergraph satisfying \cref{def:hypergraph} equipped with a set of weights $\weights$ ascribed to each node such that a weighted hypergraph is written as a triplet $\br{\weights, \nodes, \edges}$.
-        \[ \weights = \bc{w_i \mid i \in \ind_\nodes, w_i \in \R} \]
-        One would say that a particular node $n_i$ carries weight $w_i$ for each $i \in \ind_\nodes$.
-    \end{definition}
-
-    \begin{definition}
-        A \term{bounded transversal} of a weighted hypergraph $\hgraph_\weights$ is a transversal $\trans$ of the unweighted hypergraph $\hgraph$ and a real number $t$ (denoted $\trans_{\leq t}$) such that the sum of the node weights of the transversal is bounded by $t$.
-        \[ \trans_{\leq t} = \bc{n_i \mid i \in \ind_\trans} \quad \text{s.t.} \sum_{j\in\ind_\trans} w_j \leq t \]
-        One can definte analogous \term{(strictly) upper/lower bounded transversals} by considering modifications of the notation: $\trans_{< t}, \trans_{\geq t}, \trans_{> t}$.
-    \end{definition}
-
-    % \begin{algorithm}[H]
-    % \caption{The Extension Cover Procedure (ECP)}
-    % \label{alg:ecp}
-    % \begin{algorithmic}
-    %   \State $\mset{S}^{0} = \mul{\emptyset}$
-    % \end{algorithmic}
-    % \end{algorithm}
-
-    % \begin{algorithm}
-    %   \caption{The Extension Cover Procedure (ECP)
-    %     \label{alg:ecp}}
-    %   \begin{algorithmic}[1]
-    %     \Require{An antecedent m-set $\mset{A}$ and a partial consequent m-set $\mset{S}$.}
-    %     \Statex
-    %     \Function{ECP}{$\mset{A}, \mset{S}$}
-    %       % \Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
-    %       % \Let{$\delta$}{$0$}
-    %       % \For{$i \gets 1 \textrm{ to } n$}
-    %       %   \If{$z_i \neq 0$}
-    %       %     \Let{$\delta$}{$\delta + 1$}
-    %       %   \EndIf
-    %       % \EndFor
-    %       \State \Return{$\delta$}
-    %     \EndFunction
-    %   \end{algorithmic}
-    % \end{algorithm}
-
-    \todo[TC]{Trivial nodes}
-    \todo[TC]{Duplication under Deflation}
-    \todo[TC]{Memory}
-    \todo[TC]{Parallelization}
-    \todo[TC]{Simplicial Complex}
-    \subsubsection{Advantages}
-
-    \subsubsection{Avoiding Trivial Inequalities}
-    A \term{trivial compatibility inequality} $I_{\mscenario}$ is an inequality that is satisfied by all marginal models $\prob^{\mscenario}$, not just compatible ones.
-Trivial compatibility inequalities are of no importance Since the set of all extension cover inequalities
-    \todo[TC]{Targeted Seeds}
-
-    \begin{definition}
-        A \term{hypergraph transversal generation} is any algorithm that correctly generates the complete set of all minimal transversals of $\mathcal{H}$.
-    \end{definition}
-
-    \begin{definition}
-        Any hypergraph with strictly non-empty edges $\forall e \neq \emptyset$ will always admit the \term{trivial transversal} $\trans^*$ where all nodes are considered as members $\trans^* = \nodes$.
-Any hypergraph with empty edges will be called a \term{degenerate hypergraph} as it admits no transversals\footnote{Most authors require that all hypergraphs be non-degenerate \cite{Kavvadias_2005}.}.
-    \end{definition}
-    Remark ?? guarantees that all marginal hypergraphs are non-degenerate. There are two distinct approaches to hypergraph transversal generation: \textit{top-down} and \textit{bottom-up}.
-    \begin{definition}
-        A \term{top-down} hypergraph transversal generation refers to any algorithm that begins with the trivial transversal $\trans^*$ and iteratively removes unnecessary nodes from $\trans^*$.
-    \end{definition}
-
-    \begin{definition}
-        A \term{bottom-up} hypergraph transversal generation refers to any algorithm that begins with the empty set $\emptyset$ and iteratively adds nodes.
-    \end{definition}
-
-    One should select a top-down method if the typical size of minimal transversals $\abs{\trans}$ is comparable to the number of nodes $\abs{\nodes}$, otherwise a bottom-up method will perform better.
-    For our purposes we implemented a deep-first transversal algorithm similar to
-    Recalling
-
-    \subsection{Weighted Hypergraph Transversals}
-    In \cref{sec:certificate_inequalities} is was demonstrated that the Fritz distribution is witness-able via a certificate inequality. It is also possible to witness
-    \todo[TC]{Discuss the Inequalities Derived/ Trivial and non-trivial}
-
-    \todo[TC]{Weighted transversals and Optimizations}
-    \todo[TC]{Seeding inequalities (huge advantage here)}
-    \section{Marginal Symmetries}
-    \label{sec:symmetry}
-    Symmetric compatibility inequalities are useful for a number of reasons.
-First, Bancal et.
-al.
-\cite{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:comp_con_mp}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
-They also note a number of interesting inequalities (such as CHSH \cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that quantum-non-trivial inequalities can be recovered from facets of a symmetric polytope.
-Second, numerical optimizations against inequalities invariant under exchange of parties will lead to one of two interesting cases: either the extremal distribution is invariant under exchange of parties or it is not.
-The latter case generates a family of incompatible distributions obtained by exchanging parties of the found extremal distribution\footnote{If the extremal distribution is not invariant under exchange of parties, there is indication that the space of accessible distributions is non-convex.}.
-In this section we discuss how to exploit symmetries in the extension covering procedure in order to reduce the computational search space.
-\\
-
-    To demonstrate what kinds of symmetries are valid, we present the following example:
-    \begin{example}
-        \label{ex:symmetries}
-        First consider the marginal scenario $\mscenario = \bc{\bc{a, b, c}, \bc{c, d}, \bc{a, d}}$ where each variable in $\jointvar = \bc{a,b,c,d}$ is binary.
-Moreover, let $I_{\mscenario}$ be the compatibility inequality,
-        \[ I_{\mscenario} = \bc{\prob[abc][010] \leq \prob[cd][00] + \prob[ad][01]}  \]
-        Intuitively, a compatibility is independent of outcome labels $O_a = O_b = O_c = O_d = \bc{0,1}$.
-Therefore new compatibility inequalities can be generated from $I_{\mscenario}$ by permuting its outcome labels.
-Let $\geo_v : O_v \to O_v : \bc{0,1} \mapsto \geo_v\bs{\bc{0,1}} = \bc{1,0}$ be a permutation of the outcome labels for variable $v$.
-Let $\geo = \geo_a \times \geo_c$ be the permutation of variables $a$ and $c$.
-The action of $\geo$ on outcome labels induces an action on the inequality $I_{\mscenario}$ itself,
-        \begin{align*}
-        \geo\bs{I_{\mscenario}} &= \bc{\prob[abc][\geo\bs{010}] \leq \prob[cd][\geo\bs{00}] + \prob[ad][\geo\bs{01}]} \\
-        &= \bc{\prob[abc][111] \leq \prob[cd][10] + \prob[ad][11]}
-        \end{align*}
-        The new inequality $\geo\bs{I_{\mscenario}}$ is also a valid compatibility inequality.
-By construction, any permutation $\geo$ over outcome labels leaves the marginal scenario invariant ($\geo\bs{\mscenario} = \mscenario$) and thus we may write $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$.
-\\
-
-        Alternatively, permutations of the variables themselves are also permitted.
-Let $\gep : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \gep\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ be a permutation of the variables $\jointvar$.
-Intuitively $\gep$ acts on $I_{\mscenario}$ in the following way,
-        \begin{align*}
-        \gep\bs{I_{\mscenario}} &= \bc{\prob[\gep\bs{abc}][010] \leq \prob[\gep\bs{cd}][00] + \prob[\gep\bs{ad}][01]} \\
-        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
-        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
-        \end{align*}
-        In general (as in this example), permutations over all variables can modify the marginal scenario $\gep\bs{\mscenario} \neq \mscenario$; in general we write $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
-    \end{example}
-
-    \subsection{Outcome Label Symmetry}
-    As demonstrated by \cref{ex:symmetries}, permutations on outcome labels can be applied to inequalities themselves to generate new inequalities.
-To formalize this notion, let $\Perm{S}$ denote the \term{permutation group} acting on the set $S$ consisting of all bijective maps $s : S \to S$.
-    \[ \Perm{S} = \bc{s : S \to S} \]
-    \begin{definition}
-        Then (outcome) \term{label permutation group} $\go$ for a set of random variables $\mathcal{V} = \bc{v_1, \ldots, v_n}$ is the direct product of permutations over the outcome labels for each variable $v_i \in \mathcal{V}$,
-        \[ \go \defined \Perm{O_{v_1}} \times \cdots \times \Perm{O_{v_n}} = \prod_{v \in \mathcal{V}} \Perm{O_{v}} \]
-        The action of $\geo \in \go$ on an outcome $f \in \Out{\mathcal{V}}$ (denoted $\geo\bs{f}$) is defined as,
-        \[ \forall v \in \mathcal{V} : \br{\geo\bs{f}}\br{v} \defined \geo\bs{f\br{v}} \eq \label{eq:acto}\]
-    \end{definition}
-    \begin{lemma}
-        \label{lem:extendable_invariance_acto}
-        If a marginal outcome $m \in \Out{V} \subset \Out{\mscenario}$ is extendable to the joint outcome $j \in \Out{J}$, then $\geo\bs{m}$ is extendable to $\geo\bs{j}$ for any label permutation $\geo \in \go$.
-        \[ m \ext j \iff \geo\bs{m} \ext \geo\bs{j} \eq \label{eq:extendable_invariance_acto}\]
-    \end{lemma}
-    \begin{proof}
-        The proof should be clear by the definition of extendability (\cref{def:extendable}).
-        \[ m \ext j \iff \forall v \in \Dom{m} : j\br{v} = m\br{v} \]
-        Since $\Dom{m} = \Dom{\geo\bs{m}}$ and by \cref{eq:acto},
-        \[ \forall v \in \Dom{\geo\bs{m}}: \br{\geo\bs{j}}\br{v} = \geo\bs{j\br{v}} = \geo\bs{m\br{v}} = \br{\geo\bs{m}}\br{v} \]
-        We have that $\geo\bs{m} \ext \geo\bs{j}$. The left implication of \cref{eq:extendable_invariance_acto} follows by considering $\geo^{-1} \in \go$.
-    \end{proof}
-    \begin{corollary}
-        \label{coll:incidence_invariance}
-        Let $M$ be the incidence matrix for a marginal scenario $\mscenario$ and $\geo \in \go$ be a label permutation of the joint random variables $\jointvar$.
-By \cref{lem:extendable_invariance_acto}, the action of $\geo$ on $M$ leaves $M$ invariant ($\geo\bs{M} = M$),
-        \[ \geo\bs{M}_{m,j} \defined M_{\geo\bs{m},\geo\bs{j}} = \de_{\geo\bs{m} \ext \geo\bs{j}} = \de_{m \ext j} = M_{m,j} \]
-    \end{corollary}
-    \begin{theorem}
-        For each compatibility inequality $I_{\mscenario}$ and label permutation $\geo \in \go$, the inequality defined by $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$ is also a valid compatibility inequality for the marginal scenario $\mscenario$.
-    \end{theorem}
-    \begin{proof}
-        First let $I_{\mscenario} = \bc{\ga \cdot \probvec^{\mscenario} \geq 0}$ for the marginal scenario $\mscenario$ and $\ga$ is the certificate associated with $I_{\mscenario}$.
-Furthermore let $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario} = \bc{\ga \cdot \geo\bs{\probvec}^{\mscenario} \geq 0}$ be the inequality obtained after permuting $\probvec^{\mscenario}$ defined as,
-        \[ \forall m \in \Out{\mscenario} : \geo\bs{\probvec}^{\mscenario}_m \defined \probvec^{\mscenario}_{\geo\bs{m}} \]
-        It should be clear to see that $\geo\bs{I_{\mscenario}}$ can be rewritten as,
-        \[ \ga \cdot \geo\bs{\probvec}^{\mscenario} = \sum_{m \in \supp{\ga}} \ga_{m} \probvec^{\mscenario}_{\geo\bs{m}} = \sum_{\geo^{-1}\bs{m} \in \supp{\geo^{-1}\bs{\ga}}} \ga_{\geo^{-1}\bs{m}} \probvec^{\mscenario}_{m} = \geo^{-1}\bs{\ga} \cdot \probvec^{\mscenario} \]
-        Therefore the permuted inequality is equivalent to,
-        \[ \geo\bs{I}_{\mscenario} = \bc{\geo^{-1}\bs{\ga} \cdot \probvec^{\mscenario} \geq 0} \]
-        All that remains to be proven is that $\geo^{-1}\bs{\ga}$ forms a valid certificate for the incidence matrix $M$. Since $\geo \in \go$, then by \cref{coll:incidence_invariance},
-        \[ \br{\geo^{-1}\bs{\ga} \cdot M}_j = \sum_{m \in \supp{\geo^{-1}\bs{\ga}}} \geo^{-1}\bs{\ga}_m \de_{m\ext j} = \sum_{m \in \supp{\ga}} \bs{\ga}_m \de_{\geo\bs{m}\ext j} = \sum_{m \in \supp{\ga}} \bs{\ga}_m \de_{m\ext \geo^{-1}\bs{j}} = \br{\ga \cdot M}_{\geo^{-1}\bs{j}} \]
-        But since $I_{\mscenario}$ is a valid compatibility inequality, $\ga \cdot M \succeq 0$ and thus $\geo^{-1}\bs{\ga} \cdot M \succeq 0$ making $\geo\bs{I}_{\mscenario}$ a valid compatibility inequality as well.
-    \end{proof}
-
-    \subsection{Causal Symmetry}
-    The aim of this section is to formalize what types of symmetries are present in a particular causal structure $\graph$.
-The group of these causal symmetries will define, for each compatibility inequality $I_{\mscenario}$, a family of inequalities that are also valid incompatibility inequalities.
-
-    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\gep$ from $N$ to $N$.
-    \[ \Perm{N} = \bc{\gep \mid \gep : N \to N} \]
-    The action of $\gep \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\gep$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
-    \begin{align*}
-    \gep\bs{\graph} &\defined \br{\gep\bs{\nodes}, \gep\bs{\edges}} \\
-    \gep\bs{\nodes} &\defined \bc{\gep\bs{n} \mid n \in \nodes} = \nodes \\
-    \gep\bs{\edges} &\defined \bc{\gep\bs{e} \mid e \in \edges}
-    \end{align*}
-    To motivate a more general treatment of such symmetries, consider the Triangle Scenario of \cref{fig:triangle_scenario}.
-Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\gep \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\gep\bs{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes.
-By construction, any valid compatibility inequality $I_{\mscenario}$ for the marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes.
-Therefore applying $\gep$ to all distributions in $I_{\mscenario}$ yields $\gep\bs{I_{\mscenario}} \defined \gep\bs{I}_{\gep\bs{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\gep\bs{\mscenario}$ defined as,
-    \[ \gep\bs{\mscenario} = \bc{\gep\bs{V_1}, \ldots, \gep\bs{V_k}} \]
-    % \begin{example}
-    %     \todo[TC]{Above trivial example.}
-    %     Consider the marginal scenario $V_{\bs{4}} = \bc{\bc{A,B,C}, \bc{A}, \bc{B}, \bc{C}}$ and the compatibility inequality $I_{\bc{ABC, A, B, C}}$ for the Triangle Scenario in \cref{fig:triangle_scenario} with the following form,
-    %     \[ \prob[ABC][002]\prob[ABC][003] \leq \prob[A][0]\prob[C][3] \]
-    %     Now consider $\gep = \bc{A \to A, B \to C, C \to B}$. Since $\gep\bs{\graph} = \graph$, $\gep\bs{I_{\mscenario}}$ is also a valid compatibility inequality,
-    % \end{example}
-    More generically, any permutation $\gep$ that preserves the graphical structure of $\graph$ can be applied to $I_{\mscenario}$ to generate new and valid compatibility inequalities.
-Specifically this alludes to the \term{graph automorphism group} $\Aut{\graph}$ of $\graph$.
-    \[ \Aut{\graph} \defined \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph} \]
-    In general, $\Aut{\graph}$ could include elements $\gep$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}.
-This behaviour is \textit{undesired} for causal inference where the latent nodes will never appear in a marginal scenario.
-Instead, the subgroup of $\Aut{\graph}$ that never maps observable nodes to latent nodes is the \term{set-wise stabilizer} of $\Aut{\graph}$ for $\nodes_O$ and will be expressed with a subscript.
-
-    \begin{definition}
-        The \term{causal symmetry group} for a causal structure $\graph$ is the graph automorphism subgroup that stabilizes the observable nodes.
-        \[ \Aut[\nodes_O]{\graph} = \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph, \forall n \in \nodes_O :\gep\bs{n} \in \nodes_O} \]
-        Given any compatibility inequality $I_{\mscenario}$, each element $\gep$ of the causal symmetry group defines a new valid compatibility inequality $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
-    \end{definition}
-
-    The inflation technique discussed in \cref{sec:summary_inflation} allows one to derive compatibility inequalities for a causal structure $\graph$ by considering the marginal problem over the pre-injectable sets of $\graph'$ denoted $\PreInj[\graph]{\graph'} = \bc{V_1, \ldots, V_k}$.
-It is important to recall that due to \cref{lem:inflation}, inequalities $I'$ for $\graph'$ are \textit{only} transferable to inequalities $I$ for $\graph$ if $I'$ is in terms of distributions over the pre-injectable sets $I'_{\PreInj[\graph]{\graph'}}$.
-As a consequence of this observation, we need to consider a subgroup of the causal symmetry group that preserves the pre-injectable sets,
-    \[ \gep\bs{\PreInj[\graph]{\graph'}} = \PreInj[\graph]{\graph'} \eq \label{eq:preserved_preinj} \]
-
-    \begin{definition}
-        The \term{restricted causal symmetry group} $\gp$ for a causal structure $\graph$ and a marginal scenario $\mscenario$ is the graph automorphism subgroup that stabilizes the marginal scenario $\mscenario$.
-        \[ \gp \defined \Aut[\mscenario]{\graph} = \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph, \forall V \in \mscenario : \gep\bs{V} \in \mscenario} \]
-        Given any compatibility inequality $I_{\mscenario}$ each element $\gep$ of the causal symmetry group defines a new valid compatibility inequality $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\mscenario}$ over the \textit{same} marginal context $\mscenario$.
-    \end{definition}
-
-    The restricted causal symmetry group for the pre-injectable sets of an inflation $\graph'$ is the ideal symmetry group for use with the inflation technique.
-If one obtains a particular inequality $I'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\gp$, an entire family of valid compatibility inequalities are also obtained.
-    \[ \bc{\gep\bs{I'}_{\PreInj[\graph]{\graph'}} \mid \gep \in \gp} \text{ where } \gp = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
-    We have obtained $\gp$ for the inflated triangle scenario \cref{fig:inflated_triangle_scenario}. $\gp$ is an order $48$ group with the following $4$ generators:
-    \begin{equation*}
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_1 \\
-    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_2 \\
-    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_3 \\
-    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_4 \\
-    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
-    \end{aligned}
-    \end{equation*}
-    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
-    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
-    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
-    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
-    It is easy to verify that $\gep_1, \gep_2, \gep_3, \gep_4$ are all automorphisms of the inflated Triangle Scenario $\graph'$ of \cref{fig:inflated_triangle_scenario}.
-Moreover they stabilize the observable nodes, and the map pre-injectable sets of \cref{eq:pre-injectable_triangle_scenario} to the pre-injectable sets.
-Finally, in the Triangle Scenario we have that,
-    \[ \gp = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \sim \Aut[\nodes_O]{\graph} \]
-    To see this, $\gep_1$ and $\gep_4$ become the identity element $\mathbb{I}$ in $\Aut[\nodes_O]{\graph}$ upon removal of the copy-index, leaving $\gep_2$ to generate reflections and $\gep_3$ to generate rotations.
-    \subsection{Symmetric Marginal Polytope}
-    Up until this point, we have discussed how new inequalities can be created from known ones by exploiting causal symmetry.
-Although very useful, we divert our attention to finding \textit{symmetric} inequalities themselves.
-    \[ \forall \gep \in \gp :  \gep\bs{I_{\mscenario}} = I_{\mscenario} \]
-    In order to do this, we must first define how elements $\gep \in \gp$ act on marginal outcomes $O_{\mscenario}$.
-    \begin{definition}
-        Let $\jointvar = \bc{v_1, \ldots, v_k}$ be a collection of random variables and let $\gep \in \Perm{\jointvar}$.
-$\jointvar$ is said to be \term{label invariant with respect to $\gep$} if the outcome labels for each variable $v \in \jointvar$ are unchanged under the action of $\gep$.
-        \[ \forall v \in \jointvar : O_{v} = O_{\gep\bs{v}} \]
-        Label invariance is a prerequisite for any kind of symmetry amoung random variables.
-    \end{definition}
-    \begin{definition}
-        Let $\jointvar = \br{v_1, \ldots v_k}$ be a collection of random variables along with a specific outcome $m \in \Out{V}$ where $V \subseteq \jointvar$.
-The action of $\gep \in \Perm{\jointvar}$ on $m$ is a new outcome $\gep\bs{m} \in \Out{\gep\bs{V}}$ over $\gep\bs{V} \subseteq \jointvar$ defined as follows,
-        \[ \forall v \in V : \br{\gep\bs{m}}\br{\gep\bs{v}} \defined m \br{v} \]
-        The idea being that $\gep$ modifies $m$ in such a way that permutes its domain while leaving its range invariant.
-    \end{definition}
-    \begin{example}
-        Consider the outcome $m = \bc{A \mapsto 0, B \mapsto 1, C \mapsto 2} \in \Out{\bc{A,B,C}}$ where all variables have $4$ possible outcomes $O_A = O_B = O_C = \bc{0,1,2,3}$ and the permutation $\gep = \bc{A \to D, B \to C, C \to B, D \to A}$.
-        The \textit{action} of $\gep$ on $m$ is as follows,
-        \begin{align*}
-            \gep\bs{m} &= \gep\bs{\bc{A \mapsto m\br{A}, B \mapsto m\br{B}, C \mapsto m\br{C}}} \\
-            &= \bc{\gep\bs{A} \mapsto m\br{A}, \gep\bs{B} \mapsto m\br{B}, \gep\bs{C} \mapsto m\br{C}} \\
-            &= \bc{D \mapsto m\br{A}, C \mapsto m\br{B}, B \mapsto m\br{C}} \\
-            &= \bc{D \mapsto 0, C \mapsto 1, B \mapsto 2} \\
-            &= \bc{B \mapsto 2, C \mapsto 1, D \mapsto 0}
-        \end{align*}
-        Evidently, $\gep\bs{m} \in \Out{\bc{B, C, D}}$.
-    \end{example}
-
-    Through repeated action of $\gep \in \gp$ on marginal outcomes $m \in \Out{\mscenario}$ and joint outcomes $j \in \Out{\jointvar}$, one can define group orbits of $\gp$ in $\Out{\mscenario}$ and $\Out{\jointvar}$.
-    \begin{align*}
-        \Orb[\gp]{m} &\defined \bc{\gep\bs{m} \mid \gep \in \gp} \\
-        \Orb[\gp]{j} &\defined \bc{\gep\bs{j} \mid \gep \in \gp}
-    \end{align*}
-
-    \begin{definition}
-        The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and a particular restricted causal symmetry $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
-Each row of $M_{\gp}$ corresponds to a marginal orbit $\Orb[\gp]{m}$.
-Analogously each column of $M_{\gp}$ corresponds to a joint orbit $\Orb[\gp]{j}$.
-The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
-        \[ M_{\gp}\bs{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M\bs{m',j'} \]
-    \end{definition}
-
-    \subsection{Results}
-
-    \todo[TC]{How we obtained the desired symmetry group}
-    \todo[TC]{Group orbits to symmetric marginal description matrix}
-    \todo[TC]{representative antecedents completely solve the marginal problem}
-
     \section{Non-linear Optimizations}
     \label{sec:optimizations}
-    \todo[TC]{Mention outlook on te importance of classification and determining interesting inequalities \cite{Bancal_2010}}
+    \todo[TC]{Mention outlook on te importance of classification and determining interesting inequalities~\cite{Bancal_2010}}
     Compatibility inequalities for a given causal structure are fantastic for finding incompatible distributions.
@@
     \subsection{Numerical Violations of The CHSH Inequality}
-    The CHSH inequality \cite{CHSH_Original} can we viewed as a causal compatibility inequality for the iconic Bell Scenario (Fig.
-19 of \cite{Wood_2012}, Fig.
-11 of \cite{Inflation}, Fig.
-1 a) of \cite{Tavakoli_2015}, etc.) corresponding to Bell's notion of local causality \cite{Wood_2012}.
+    The CHSH inequality~\cite{CHSH_Original} can we viewed as a causal compatibility inequality for the iconic Bell Scenario (Fig.
+19 of~\cite{Wood_2012}, Fig.
+11 of~\cite{Inflation}, Fig.
+1 a) of~\cite{Tavakoli_2015}, etc.) corresponding to Bell's notion of local causality~\cite{Wood_2012}.
 It constrains the set of 2-outcome bipartite distributions over local binary measurement settings for each party $\prob[AB\mid S_A S_B] \defined \bc{\prob[AB\mid 0 0], \prob[AB\mid 01], \prob[AB\mid 10], \prob[AB\mid 11]}$.
-Numerical optimization \textit{should} obtain the algebraic violation associated with the PR-Box correlations \cite{PR_1995}.
+Numerical optimization \textit{should} obtain the algebraic violation associated with the PR-Box correlations~\cite{PR_1995}.
 Maintaining full generality, we simply need to parameterize these $4$ distributions using \cref{eq:uniform_param}, each requiring $4$ real-valued parameters.
@@
     \[ I\tsb{CHSH} = \ba{AB|11} + \ba{AB|12} + \ba{AB|21} - \ba{AB|22} \]
-    Figure \ref{fig:CHSH_convex} demonstrates this optimization for $5$ random seed parameters $\lambda^0$, each converging to the expected value of $4$. Analogously, \cite{Cirelson_1980}
+    Figure \ref{fig:CHSH_convex} demonstrates this optimization for $5$ random seed parameters $\lambda^0$, each converging to the expected value of $4$. Analogously,~\cite{Cirelson_1980}
 
@@
     \section{Open Questions \& Future Work}
-    The marginal problem has be well studied in various contexts \cite[\ldots]{Vorobev_1962,Inflation,Fritz_2011}.
-Reference \cite{Fritz_2011} contains an excellent summary of its connection to other fields of research including knowledge integration, database theory and coalition games in game theory.
+    The marginal problem has be well studied in various contexts~\cite[\ldots]{Vorobev_1962,Inflation,Fritz_2011}.
+Reference~\cite{Fritz_2011} contains an excellent summary of its connection to other fields of research including knowledge integration, database theory and coalition games in game theory.
     \todo[TC]{Lots of stuff}
     \appendix
+    \section{Common Terminology \& Notation}
+
+    \subsection{Graph Theory}
+    \begin{definition}
+        \label{def:graph}
+        A \term{graph} is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes have the capacity to represent any object while the edges are defined as \textit{pairs} of nodes.
+Typical, although not necessary, the nodes (edges) are indexed by an index set $\ind_\nodes$ ($\ind_{\edges}$).
+        \begin{align*}
+            \nodes &= \bc{n_i \mid n_i \in \ind_{\nodes}} \\
+            \edges &= \bc{e_i = \bc{n_j, n_k} \mid i \in \ind_{\edges}, j,k \in \ind_{\nodes}}
+        \end{align*}
+    \end{definition}
+
+    \begin{definition}
+        \label{def:directed_graph}
+        A \term{directed graph} $\graph$ is a graph where each edge $e$ has an order or \term{direction}.
+        \begin{align*}
+            \nodes &= \bc{n_i \mid n_i \in \ind_{\nodes}} \\
+            \edges &= \bc{e_i = \br{n_j \to n_k} \mid i \in \ind_{\edges}, j,k \in \ind_{\nodes}}
+        \end{align*}
+    \end{definition}
+
+    \begin{definition}
+        \label{def:graph_terms}
+        The following definitions are common language in directed graph theory. Let $n, m \in \nodes$ be example nodes of the graph $\graph$.
+        \begin{itemize}
+            \item The \term{parents of a node}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
+            \item The \term{children of a node}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
+            \item The \term{ancestry of a node}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$
+        \end{itemize}
+        All of these terms can be generalized to sets of nodes $N \subseteq \nodes$ through union over the elements,
+        \begin{itemize}
+            \item The \term{parents of a node set}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
+            \item The \term{children of a node set}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
+            \item The \term{ancestry of a node set}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
+        \end{itemize}
+    \end{definition}
+
+    \begin{definition}
+        An \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$.
+        \[ \Sub[\graph]{N} \defined \br{N, \bc{e_i \mid i \in \ind_\edges, e_i \subseteq N}} \]
+        An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
+        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
+    \end{definition}
+
+    \begin{definition}
+        \label{def:dag}
+        A \term{directed acyclic graph} or \term{DAG} $\graph = \br{\nodes, \edges}$ is an directed graph (see \cref{def:directed_graph}) with the additional property that no node $n$ is in its set of \term{ancestors}.
+        \[ \forall n \in \nodes : n \notin \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}\]
+        It is critical to note the difference in language between \textit{ancestors} from \textit{ancestry}.
+The ancestry $\An[\graph]{n}$ of a node $n$ is defined in \cref{def:graph_terms} using \textit{whole} numbers $\mathbb{W}$.
+In contrast, the ancestors of a node are defined similarly with \textit{natural} numbers $\mathbb{N}$.
+    \end{definition}
+
+    \subsection{Probability Theory}
+
+    \begin{definition}
+        The \term{product distribution} of two disjoint probability distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as $\prob[V] \times \prob[W]$.
+        \[ \forall f \in \Sect{V \cup W} : \br{\prob[V] \times \prob[W]}\br{f} \defined \prob[V][f|_{V}]\cdot\prob[W][f|_{W}] \]
+        A product distribution of $k$ mutually disjoint distributions is defined as,
+        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
+    \end{definition}
+
+    \begin{definition}
+        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
+        \[ \forall f \in \Sect{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
+    \end{definition}
+
     \section{Exemplary Inequalities}
@@
     \section{Computationally Efficient Parametrization of the Unitary Group}
-    Spengler, Huber and Hiesmayr \cite{Spengler_2010_Unitary} suggest the parameterization of the unitary group $\mathcal{U}\br{d}$ using a $d\times d$-matrix of real-valued parameters $\lambda_{n, m}$,
+    Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} suggest the parameterization of the unitary group $\mathcal{U}\br{d}$ using a $d\times d$-matrix of real-valued parameters $\lambda_{n, m}$,
     \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
@@
     \[ \sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m} \]
-    Where $1 \leq m < n \leq d$. Spengler et. al. proved the validity of \cref{eq:spengler_unitary} in Ref. \cite{Spengler_2010_Unitary}.
+    Where $1 \leq m < n \leq d$. Spengler et. al. proved the validity of \cref{eq:spengler_unitary} in Ref.~\cite{Spengler_2010_Unitary}.
 
@@
     In quantum mechanics, the global phase of a state $\ket{\psi} \in \Hilb^n$ is a \textit{redundant} parameter.
-Parameterizing unitaries using \cref{eq:fast_spengler_unitary} is especially attractive since the global phase terms $GP_l$ can be dropped, allowing one to parameterize all unitaries in $\mathcal{U}\br{d}$ up to this degeneracy \cite{Spengler_2010_Unitary}\footnote{In our implementation, we accomplish this by explicitly setting $\lambda_{l,l} = 0$ in \cref{eq:unitary_GP}}.
+Parameterizing unitaries using \cref{eq:fast_spengler_unitary} is especially attractive since the global phase terms $GP_l$ can be dropped, allowing one to parameterize all unitaries in $\mathcal{U}\br{d}$ up to this degeneracy~\cite{Spengler_2010_Unitary}\footnote{In our implementation, we accomplish this by explicitly setting $\lambda_{l,l} = 0$ in \cref{eq:unitary_GP}}.
     \[ U_{/ GP_l} = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}}} \eq \label{eq:fast_spengler_unitary_gp} \]
-    \todo[TC]{Explanation of Computational Complexity $\mathcal{O}\br{d^3}$ vs. $\mathcal{O}\br{1}$ using \cite{Moler_2003}}
+    \todo[TC]{Explanation of Computational Complexity $\mathcal{O}\br{d^3}$ vs. $\mathcal{O}\br{1}$ using~\cite{Moler_2003}}
     \todo[TC]{Pre-Caching for Fixed dimension $d$}
@@
     Throughout \cref{sec:optimizations}, we utilize a variety of parameterizations of quantum states and measurements in order to generate quantum-accessible probability distributions.
-There are numerous techniques that can used when parameterizing quantum states and measurements \cite{Petz_2015, Hedemann_2013,Spengler_2010_Unitary,Fujii_2005,James_2001} with applications \todo[TC]{Finish this sentence}.
+There are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Spengler_2010_Unitary,Fujii_2005,James_2001} with applications \todo[TC]{Finish this sentence}.
 For our purposes, we need to parameterize the space of quantum-accessible distributions $\prob[\mathcal{Q}]$ that are \textit{realized} on the Triangle Scenario.
@@
 
-    Taking inspiration from \cite{James_2001}, we can parameterize all such density matrices $\rho$ using \term{Cholesky Parametrization} \cite{Grasmair_2014}.
+    Taking inspiration from~\cite{James_2001}, we can parameterize all such density matrices $\rho$ using \term{Cholesky Parametrization}~\cite{Grasmair_2014}.
 The Cholesky decomposition allows one to write any hermitian positive semi-definite matrix $\rho$ in terms of a lower (or upper) triangular matrix $T$ using $\rho = T^\dagger T$.
 Our Cholesky parameterization consists of assigning $16$ real-valued parameters $\lambda$ to the entires of $T$ and generating a unitary trace $\rho$ similar to eq.
-(4.4) of \cite{James_2001}.
+(4.4) of~\cite{James_2001}.
     \[ \rho = \f{T^\dagger T}{\Tr\br{T^\dagger T}} \quad T = \pmtrx{\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}} \eq \label{eq:cholesky_param} \]
@@
 
-    In Spengler, Huber and Hiesmayr's work \cite{Spengler_2010_Unitary}, they discuss how to parameterization density matrices $\rho$ acting on $\Hilb^d$ of rank $k$ through it's spectral decomposition,
+    In Spengler, Huber and Hiesmayr's work~\cite{Spengler_2010_Unitary}, they discuss how to parameterization density matrices $\rho$ acting on $\Hilb^d$ of rank $k$ through it's spectral decomposition,
     \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i}\bra{\psi_i} \quad p_i \geq 0, \sum_{i} p_i = 1, k \leq d \eq \label{eq:unitary_param_density} \]
@@
     Finally in cases where we wish to restrict ourselves to \textit{pure} bipartite states $\rho = \ket{\psi}\bra{\psi}$, we have the luxury to use a \term{Schmidt Parametrization}.
-This is accomplished via a Schmidt decomposition $\ket{\psi_{AB}} = \sum_{i}\sigma_i \ket{i_A}\otimes\ket{i_B}$ where normalization demands that $\sum_{i} \sigma_i^2 = 1$, $\bc{\ket{i_A}}$ and $\bc{\ket{i_B}}$ are orthonormal bases for $\Hilb_A$ and $\Hilb_B$ respectively \cite{Neilsen_Chaung_2011}.
+This is accomplished via a Schmidt decomposition $\ket{\psi_{AB}} = \sum_{i}\sigma_i \ket{i_A}\otimes\ket{i_B}$ where normalization demands that $\sum_{i} \sigma_i^2 = 1$, $\bc{\ket{i_A}}$ and $\bc{\ket{i_B}}$ are orthonormal bases for $\Hilb_A$ and $\Hilb_B$ respectively~\cite{Neilsen_Chaung_2011}.
 Additionally for qubit sources we can \textit{choose} our orthonormal bases to be the computational basis $\bc{\ket{0}, \ket{1}}$ and write,
@@
     When generalizing the above parameterization to more than $2$ outcomes, only necessary conditions were found.
-Generating $k$-outcome POVM measurements is doable using rejection sampling techniques such as those used in \cite{Petz_2012} however a valid parameterization with little to no degeneracy was not found.
+Generating $k$-outcome POVM measurements is doable using rejection sampling techniques such as those used in~\cite{Petz_2012} however a valid parameterization with little to no degeneracy was not found.
 Upon making this observation, a necessary departure to \term{projective-valued measures (PVMs)} is warranted\footnote{Strictly speaking, when the number of outcomes ($k$) \textit{matches} the Hilbert space dimension ($d$), \cref{eq:povm} implies \cref{eq:pvm} by completeness.
 When considering $4$ outcome measurements on bipartite qubit states in $\Hilb^4$, PVMs are completely general.
-Moreover, Naimark's dilation theorem guarantees that PVMs acting on $\Hilb^q$ can \textit{emulate} the behaviour of any POVM acting on $\Hilb^d$ provided that $q$ is sufficiently larger than $d$ \cite{Naimark}.}.
+Moreover, Naimark's dilation theorem guarantees that PVMs acting on $\Hilb^q$ can \textit{emulate} the behaviour of any POVM acting on $\Hilb^d$ provided that $q$ is sufficiently larger than $d$~\cite{Naimark}.}.
 With loss of generality, consider the set of PVMs $M$ satisfying \cref{eq:povm} in addition to orthogonal and projective properties,
@@
     Specifically, the projective property each $M_i$ means that the global phase of $U$ is completely arbitrary; one only needs to consider parameterizing unitaries up to global phase \cref{eq:fast_spengler_unitary_gp}.
-This method was inspired by the \textit{measurement seeding} method of P{\'{a}}l and V{\'{e}}rtesi's \cite{Pal_2010} iterative optimization technique.
+This method was inspired by the \textit{measurement seeding} method of P{\'{a}}l and V{\'{e}}rtesi's~\cite{Pal_2010} iterative optimization technique.
 
@@
 If the cardinality of $O_{V}$ is finite, then this computationally feasible.
-The space of probability distributions over $n = \abs{O_{V}}$ distinct outcomes forms a $n-1$ dimensional convex polytope naturally embedded in $\R_{\geq 0}^n$ \cite{Brunner_2013} that is parameterizable by $n-1$ real value parameters; normalization $\sum_{o\bs{V} \in O_V} \prob[V][\outc{V}] = 1$ accounts for the `$-1$'.
-An example of a non-degenerate parameterization of $\prob[V]$ consists of $n-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{n-1}}, \lambda_i \in \bs{0, \pi/2}$ which generate the $n$ probability values $p_j$ using hyperspherical coordinates \cite{Hedemann_2013, Spengler_2010_Unitary},
+The space of probability distributions over $n = \abs{O_{V}}$ distinct outcomes forms a $n-1$ dimensional convex polytope naturally embedded in $\R_{\geq 0}^n$~\cite{Brunner_2013} that is parameterizable by $n-1$ real value parameters; normalization $\sum_{o\bs{V} \in O_V} \prob[V][\outc{V}] = 1$ accounts for the `$-1$'.
+An example of a non-degenerate parameterization of $\prob[V]$ consists of $n-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{n-1}}, \lambda_i \in \bs{0, \pi/2}$ which generate the $n$ probability values $p_j$ using hyperspherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary},
     \begin{equation}

### 2016-10-31 document/main.tex
Use LOCAL version of kbordermatrix.sty, for ShareLatex compatibility.
Refined some notation for symmetries

@@
 % === To allow for labeling of rows and columns of a matrix ===
-\usepackage{kbordermatrix}
+%\usepackage{kbordermatrix}
+\usepackage{../packages/kbordermatrix}
 \renewcommand{\kbldelim}{(} % Left delimiter
@@
 \newcommand{\jointvar}{\mathcal{J}}
-\newcommand{\mset}{\gamma}
-\newcommand{\extmset}{\Gamma}
+% \newcommand{\mset}{\gamma}
+% \newcommand{\extmset}{\Gamma}
 \newcommand{\supp}[1]{\si\br{#1}}
@@
 \newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}
+\newcommand{\tcdot}{} % Tentative cdot, not sure if I want to keep dots
 
@@
 \setoperator{Perm} % Permutation group
+\newcommand{\PermM}[1]{\La_{#1}} % Permutation matrix
 % \setoperator{Out} % Outcome space
-\newcommand{\Sect}[1]{\s{S}\br{#1}} % Outcome space
+\newcommand{\Events}[1]{\s{E}\br{#1}} % Set of events
 \newcommand{\Dom}[1]{\s{D}\br{#1}} % Domian
@@
 
-    \subsubsection{Sections}
+    \subsubsection{Events}
     To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$.
-We also define the set of all \term{sections over $v$} $\Sect{v}$\footnote{Technically $\Sect{v}$ can be called a \textit{sheaf} but we neglect to introduce that terminology here.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
-    \[ \Sect{v} \defined \bc{s : \bc{v} \to O_v} \label{eq:outcome_space} \]
-    Making the unfamiliar distinction between sections $s$ and outcomes in $O_v$ might seem pedantic.
-Evidently, $\Sect{v}$ and $O_v$ have a one-to-one correspondence.
+We also define the set of all \term{events over $v$} $\Events{v}$\footnote{In the language of sheaf-theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
+    \[ \Events{v} \defined \bc{s : \bc{v} \to O_v} \label{eq:outcome_space} \]
+    Evidently, $\Events{v}$ and $O_v$ have a one-to-one correspondence and this distinction can be confounding.
 There is rarely any harm in referring synonymously to either as outcomes.
@@
     Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetry}.
-As a natural generalization we define the tuple sections for collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
-    \[ \Sect{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
-    Each section $s$ can be compactly represented as a set of mappings over each element of $V$.
+As a natural generalization we define the event over a collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
+    \[ \Events{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
+    Each event $s$ can be compactly represented as a set of mappings over each element of $V$.
     \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
-    The domain $\Dom{s}$ of an section $s$ is the set of random variables it valuates, i.e. if $s \in \Sect{V}$, then $\Dom{s} = V$.
+    The domain $\Dom{s}$ of an event $s$ is the set of random variables it valuates, i.e. if $s \in \Events{V}$, then $\Dom{s} = V$.
     \begin{example}
-        Let $s \in \Sect{V}$ be a section over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$.
+        Let $s \in \Events{V}$ be an event over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$.
 Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$.
-Furthermore let $f \in \Sect{V}$ be the section $\br{v_1 \mapsto 2, v_2 \mapsto 1}$.
+Furthermore let $f \in \Events{V}$ be the section $\br{v_1 \mapsto 2, v_2 \mapsto 1}$.
 Then the following notations are interchangeable,
@@
     \label{def:section_restriction}
-    For every $W \subseteq V$ and $s \in \Sect{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Sect{W}$) is the section in $\Sect{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
+    For every $W \subseteq V$ and $s \in \Events{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Events{W}$) is the event in $\Events{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
     \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
@@
     \label{def:section_compatible}
-    The sections $s_{V} \in \Sect{V}$ and $s_{W} \in \Sect{W}$ are said to be \term{compatible} sections if they agree on their valuations of $V \cap W$.
+    The events $s_{V} \in \Events{V}$ and $s_{W} \in \Events{W}$ are said to be \term{compatible} events if they agree on their valuations of $V \cap W$.
 Compatibility will be denoted with the infix `$\com$'.
@@
     \label{def:section_extendable}
-    It $s_V \in \Sect{V}$ and $s_W \in \Sect{W}$ compatible sections and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
+    It $s_V \in \Events{V}$ and $s_W \in \Events{W}$ compatible events and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
     \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
@@
     \begin{remark}
-        The notation `$s \com t$' is used to indicate compatibility between $s \in \Sect{V}$ and $t \in \Sect{W}$ because of the following observation: $s$ and $t$ are compatible if and only if they are extensions of some outcome $r \in \Sect{V \cap W}$.
-        \[ s \com t \iff \exists r \in \Sect{V \cap W} \mid s \res r \ext t \]
+        The notation `$s \com t$' is used to indicate compatibility between $s \in \Events{V}$ and $t \in \Events{W}$ because of the following observation: $s$ and $t$ are compatible if and only if they are extensions of some event $r \in \Events{V \cap W}$.
+        \[ s \com t \iff \exists r \in \Events{V \cap W} \mid s \res r \ext t \]
         In fact $r$ is uniquely defined.
@@
 
-    \begin{definition}
-        \label{def:extendable_set}
-        The set of all extendable sections of $s \in \Sect{W}$ into $V$ is called the \term{extendable set of $s$ into $V$}.
-        \[ \Ext[V]{s} \defined \bc{g \in \Sect{V} \mid s \ext g} \subseteq \Sect{V} \]
-        The extendable set of $s$ into $V$ is the subset of sections in $\Sect{V}$ that \textit{agrees} with $s$ about valuations for variables in $W$.
-    \end{definition}
-
-    \begin{example}
-        Let $W = \bc{a, b}$ and $V = \bc{a, b, c}$ be two sets of random variables.
-Clearly $W \subseteq V$; a prerequisite for extendability.
-Further impose that the outcome labels for each variable are the same: $O_a = O_b = O_c = \bc{0,1,2}$.
-As an example, let $s = \bc{a \mapsto s\br{a} = 1, b \mapsto s\br{b} = 2} \in \Sect{W}$.
-The extendable set of $s$ into $V$ is,
-        \[ \Ext[V]{s} = \Ext[a,b,c]{a \mapsto 1, b \mapsto 2} = \bc{\bc{a \mapsto 1, b \mapsto 2, c \mapsto 0}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 1}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 2}} \]
-    \end{example}
-
-    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint sections} $\Sect{\jointvar}$.
-Similarly we define the \term{context sections} $\bc{\Sect{V} \mid V \in \mscenario}$.
-Finally, we elect to define the disjoint union of all context sections are called the \term{marginal sections} and by an abuse of notation we will denote this disjoint union as $\Sect{\mscenario}$.
-    \[ \Sect{\mscenario} = \coprod_{V \in \mscenario} \Sect{V} \]
-    Each marginal section $m \in \Sect{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
+    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint events} $\Events{\jointvar}$.
+Similarly we define the \term{context events} $\bc{\Events{V} \mid V \in \mscenario}$.
+Finally, we elect to define the disjoint union of all context events are called the \term{marginal events} and by an abuse of notation we will denote this disjoint union as $\Events{\mscenario}$.
+    \[ \Events{\mscenario} = \coprod_{V \in \mscenario} \Events{V} \]
+    Each marginal section $m \in \Events{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
     \subsubsection{Linear Programs}
@@
         \label{def:incidence_matrix}
-        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} sections $j \in \Sect{\jointvar}$ and the rows are indexed by \textit{marginal} sections $m \in \Sect{\mscenario}$.
+        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} events $j \in \Events{\jointvar}$ and the rows are events by \textit{marginal} sections $m \in \Events{\mscenario}$.
 The entries of $M$ are populated whenever a row index is extendable to a column index.
@@
         Where $\de_{m \ext j}$ is termed the \term{extendability indicator}.
-The incidence matrix has $\abs{\Sect{\jointvar}}$ columns, $\abs{\Sect{\mscenario}} = \sum_{i} \abs{\Sect{V_i}}$ rows and $k\abs{\Sect{\jointvar}}$ non-zero entries.
+The incidence matrix has $\abs{\Events{\jointvar}}$ columns, $\abs{\Events{\mscenario}} = \sum_{i} \abs{\Events{V_i}}$ rows and $k\abs{\Events{\jointvar}}$ non-zero entries.
     \end{definition}
@@
     \begin{definition}
-        The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint section $j \in \Sect{\jointvar}$.
+        The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint event $j \in \Events{\jointvar}$.
 $\probvec^{\jointvar}$ shares the same indices as the \textit{column} indices of $M$.
-        \[ \forall j \in \Sect{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
-    \end{definition}
-    \begin{definition}
-        The \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Sect{\mscenario}$.
+        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
+    \end{definition}
+    \begin{definition}
+        Analogously, \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Events{\mscenario}$.
 $\probvec^{\mscenario}$ shares the same indices as the \textit{row} indices of $M$.
-        \[ \forall m \in \Sect{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
+        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
     \end{definition}
@@
 Given a joint distribution vector $\probvec^{\jointvar}$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec^{\jointvar}$.
-    \[ \probvec^{\mscenario} = M \cdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
-    Henceforth we will use $\probvec^{\jointvar}$ ($\probvec^{\mscenario}$) and $\prob[\jointvar]$ ($\prob^{\jointvar}$) interchangeably.
+    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
+    Henceforth we will use $\probvec^{\jointvar}$ ($\probvec^{\mscenario}$) and $\prob[\jointvar]$ ($\prob_{\mscenario}$) interchangeably.
 
@@
 
-    % \begin{example}
-    %     The marginal problem for the inflated causal structure $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} concerns itself with the pre-injectable marginal scenario $\mscenario = \PreInj[\ts]{\ts'} = \bc{V_1, \ldots, V_{12}}$.
-Equipping the observed nodes of $\ts'$ with $4$-element outcome labels, the incidence matrix $M$ has $16,896$ rows and $16,777,216$ columns.
-    %     \begin{align*}
-    %         &\text{\# Rows} = \abs{\Sect{\mscenario}} = \sum_{i=1}^{12} \abs{\Sect{V_i}} = \sum_{i=1}^{12} 4^{\abs{V_i}} = 4 \cdot 4^6 + 8 \cdot 4^3 = 16,896 \\
-    %         &\text{\# Columns} = \abs{\Sect{\jointvar}} = 4^{\abs{\jointvar}} = 4^{12} = 16,777,216
-    %     \end{align*}
-    %     With $12 \cdot 4^{12} = 201,326,592$ non-zero entries. For obvious reasons, no attempt is made to reproduce it here.
-    % \end{example}
     \begin{definition}
@@
         \begin{alignat*}{2}
-            & \text{minimize:} \quad&& \emptyset \cdot x\\
+            & \text{minimize:} \quad&& \emptyset \tcdot x\\
             & \text{subject to:} && x \succeq 0 \\
-            & && M \cdot x = \probvec^{\mscenario}
+            & && M \tcdot x = \probvec^{\mscenario}
         \end{alignat*}
@@
         \begin{alignat*}{2}
-            & \text{minimize:} \quad&& y \cdot \probvec^{\mscenario}\\
-            & \text{subject to:} && y \cdot M \succeq 0
+            & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
+            & \text{subject to:} && y \tcdot M \succeq 0
         \end{alignat*}
@@
     The dual marginal linear program not only answers the marginal problem for a specific marginal model $\probvec^{\mscenario}$ but as a by-product provides an inequality that witnesses its contextuality.
-First notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints become satisfied.
-Secondly if the dual constraint $y \cdot M \succeq 0$ holds and the primal is feasible, then the following must hold:
-    \[ y \cdot \probvec^{\mscenario} =  y \cdot M \cdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
-    Therefore the \textit{sign} of the dual value $d \defined \min \br{y \cdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality.
+If this is not obvious, first notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints become satisfied.
+Secondly if the dual constraint $y \tcdot M \succeq 0$ holds \textit{and} the primal is feasible, then the following must hold:
+    \[ y \tcdot \probvec^{\mscenario} =  y \tcdot M \tcdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
+    Therefore the \textit{sign} of the dual value $d \defined \min \br{y \tcdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality.
 If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore $\probvec^{\mscenario}$ is contextual.
@@
     \begin{definition} An \term{infeasibility certificate}~\cite{Andersen_2001} is any vector $y$ that satisfies the constraint of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
-    \[ y \in \R^{\abs{\Sect{\mscenario}}} : y \cdot M \succeq 0, \quad y \cdot \probvec^{\mscenario} < 0 \]
-    Furthermore, any $y$ satisfying $y \cdot M \succeq 0$ can be promoted to a \term{certificate inequality} that constraints the set of non-contextual marginal models $\s{NC}$,
-    \[ \forall \probvec^{\mscenario} \in \s{NC} : y \cdot \probvec^{\mscenario} \geq 0 \]
+    \[ y \in \R^{\abs{\Events{\mscenario}}} : y \tcdot M \succeq 0, \quad y \tcdot \probvec^{\mscenario} < 0 \]
+    Furthermore, for every $y$ satisfying $y \tcdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of non-contextual marginal models $\s{NC}$,
+    \[ \forall \probvec^{\mscenario} \in \s{NC} : y \tcdot \probvec^{\mscenario} \geq 0 \]
     \end{definition}
@@
 
-    \subsubsection{Fourier Motzkin Elimination}
-    The complete space of marginal models over $\mscenario$ can be partitioned into two spaces; non-contextual marginal models in $\s{NC}$ and contextual ones in $\s{C}$.
+    \subsubsection{Fourier Motzkin Elimination \& Polytope Projection}
+
+    The complete space of marginal models over $\mscenario$ can be partitioned into two spaces: contextual ($\s{C}$) and non-contextual marginal models ($\s{NC}$).
+The separation between these spaces is completely characterized by the system of inequalities associated with \cref{eq:incidence_matrix_use}.
+Explicitly,
+    \begin{equation} \label{eq:halfspace_rep_incidence}
+    \begin{alignedat}{2}
+        \forall m \in \Events{\mscenario} :&&\quad \probvec^{\mscenario}_m - {\sum}_{j} M_{m, j} \probvec^{\jointvar}_j &\geq 0 \\
+        \forall m \in \Events{\mscenario} :&&\quad -\probvec^{\mscenario}_m + {\sum}_{j} M_{m, j} \probvec^{\jointvar}_j &\geq 0 \\
+        \forall j \in \Events{\jointvar} :&&\quad \probvec^{\jointvar}_j &\geq 0
+    \end{alignedat}
+    \end{equation}
+    Geometrically \cref{eq:halfspace_rep_incidence} is a family of $2\abs{\Events{\mscenario}} + \abs{\Events{\jointvar}}$ half-planes bounding $\R^{\abs{\Events{\mscenario}}} \times \R^{\abs{\Events{\jointvar}}}$.
+However testing the contextuality of a marginal model $\probvec^{\mscenario}$ requires a collection of inequalities bounding just $\R^{\abs{\Events{\mscenario}}}$.
+Transforming \cref{eq:halfspace_rep_incidence} into the desired system of inequalities is the task of linear-quantifier elimination.
+A popular tool for linear quantifier elimination is Fourier-Motzkin elimination \cite{Dantzig_1973,Inflation,Abramsky_2012,jones_2004}.
+We will avoid expounding the Fourier-Motzkin procedure in this paper and instead reproduce a few of its notable features and consequences.
+
+    \begin{definition} \cite[Section 12.2]{Schrijver_1998}
+        The \term{Fourier-Motzkin elimination} procedure begins with a matrix $A$ and a vector $b$ defining a system of inequalities $S_1 = \bc{A\tcdot x \leq b}$ constraining a set of variables $x$ and symbolically eliminates a sub-set of theses variables $x \setminus y$.
+Upon completion, one obtains a new set of constraints $S_2 = \bc{A' y \leq b'}$ such that,
+        \[ \exists y : A' y \leq b' \iff \exists x : A x \leq b \]
+        Any solution $y$ of $S_2$ will permit at least one solution $x$ in $S_1$ (and vice versa).
+    \end{definition}
+
+    When applied to the marginal problem of \cref{eq:halfspace_rep_incidence}, the Fourier-Motzkin procedure eliminates all reference to the joint probabilities $\probvec^{\jointvar}_j$ and returns a system of inequalities over the marginal probabilities $\probvec^{\mscenario}_m$ representing a \textit{complete} solution to the marginal problem.
+Applying the Fourier-Motzkin procedure to completely solve the marginal problem is discussed in more detail in~\cite{Inflation} and~\cite{Fritz_2011}.
+\todo[TC]{Improve this discussion of FMP}.
+\\
+
+    \todo[TC]{Discuss why FM is slow?}\\
+
+    \begin{remark}
+        In theory, Fourier-Motzkin offers a complete solution to the marginal problem for all marginal scenarios; its limitations are purely computational.
+In addition, the entire procedure only utilizes field operations \cite{Abramsky_2012} meaning that since \cref{eq:halfspace_rep_incidence} is a rational system of inequalities, then a complete solution to the marginal problem only requires a finite set of linear, rational coefficient inequalities.
+    \end{remark}
+
+    \begin{theorem}
+        There exists a set of necessary and sufficient conditions
+
+    \end{theorem}
 
@@
     \subsubsection{Marginal Polytope}
+    \begin{definition}
+        Let $I_{1}$ and $I_{2}$ represent two
+    \end{definition}
+    \begin{definition}
+        Let $\s{I}$
+    \end{definition}
+
     \todo[TC]{Very briefly discuss polytope perspective and facet inequalities vs. non-facet inequalities}
@@
 
-    This Section aims to develop a procedure for finding \textit{all} certificate inequalities in a computationally efficient manner.
+    This section aims to develop a procedure for finding \textit{all} certificate inequalities in a computationally efficient manner.
 Specifically by finding all certificate inequalities that are also facets of the marginal polytope.
-Before doing so, we will first summarize a method that can be used to obtain a complete solution to the \textit{possibilistic} marginal problem and indirectly offer a \textit{partial} solution to the \textit{probabilistic} marginal problem.
+Before doing so, we will first summarize a method \todo[TC]{Method where this idea came from, original insight from Hardy?} that can be used to obtain a complete solution to the \textit{possibilistic} marginal problem~\cite{Mansfield_2012} and indirectly offer a \textit{partial} solution to the \textit{probabilistic} marginal problem.
 
@@
     \label{sec:logical_inequalities}
-    Let $a \in \Sect{\mscenario}$ be any marginal section and $C = \bc{c_1, \ldots, c_{n}} \subseteq \Sect{\mscenario}$ be a subset of the marginal sections.
-Recall that $a, c_1, \ldots, c_n$ are particular \textit{events} over marginal contexts $V \in \mscenario$.
+    Let $a \in \Events{\mscenario}$ be any marginal event and $C = \bc{c_1, \ldots, c_{n}} \subseteq \Events{\mscenario}$ be a subset of the marginal events.
 We say that the subset $C$ forms a \term{logical extension} of $a$ if the following logical implication holds for \textit{all} marginal models $\probvec^{\mscenario}$.
@@
 
-    All logical implications of the form \cref{eq:1a_implication} can be constructed by first selecting $a$ and then configuring $C$ persuant to \cref{eq:1a_implication}.
+    All logical implications of the form \cref{eq:1a_implication} can be constructed by first selecting $a$ and then manufacturing a consequent set $C$ persuant to \cref{eq:1a_implication}.
+
     \begin{definition}
         \label{def:extendable_set}
-        For each marginal section $m \in \Sect{\mscenario}$ the \term{extendable set of $m$ into $\jointvar$} is the set of all joint sections $j \in \Sect{\jointvar}$ that are extensions of $m$.
-        \[ \Ext[\jointvar]{m} = \bc{j \in \Sect{\jointvar} \mid m \ext j} \]
-    \end{definition}
+        For each marginal event $m \in \Events{\mscenario}$ the \term{extendable set of $m$ into $\jointvar$} is the set of all joint events $j \in \Events{\jointvar}$ that are extensions of $m$.
+        \[ \Ext[\jointvar]{m} = \bc{j \in \Events{\jointvar} \mid m \ext j} \]
+    \end{definition}
+
+    The extendable set of $m$ into $\jointvar$ is the subset of events in $\Events{\jointvar}$ that \textit{agree} with $m$ about valuations for variables in $\Dom{m}$.
 Practically speaking, the extendable set of $m$ into $\jointvar$ is represented by the $m$-th row of the incidence matrix $M$.
+
     \begin{lemma}
         \label{lemma:logical_extenable_set}
-        Let $a \in \Sect{\mscenario}$ and $\probvec^{\mscenario} \in \s{NC}$ be non-contextual. Then,
+        Let $a \in \Events{\mscenario}$ and $\probvec^{\mscenario} \in \s{NC}$ be non-contextual. Then,
         \[ a \iff \bigvee_{j \in \Ext[\jointvar]{a}} j \eq \label{eq:lemma_logical_extendable_set}\]
     \end{lemma}
-    The idea being if a joint distribution does exists, then the event $a$ represents partial knowledge of the entire system $\jointvar$; whenever $a$ occurs, exactly one joint section $j$ has occurred and $j$ must be compatible with $a$.
-Likewise \cref{lemma:logical_extenable_set} applies to the consequent set $C \in \Sect{\mscenario}$,
+    The idea being if a joint distribution does exists, then the event $a$ represents partial knowledge of the entire system $\jointvar$; whenever $a$ is measured, exactly one joint event $j$ has occurred in reality and $j$ must be compatible with $a$.
+Likewise \cref{lemma:logical_extenable_set} applies to the consequent set $C \in \Events{\mscenario}$,
     \[ \bigvee_{c \in C} c \iff \bigvee_{c \in C} \bigvee_{j \in \Ext[\jointvar]{c}} j \eq \label{eq:logical_extension_C}\]
@@
     \[ \Ext[\jointvar]{a} \subseteq \bigcup_{c \in C} \Ext[\jointvar]{c} \eq \label{eq:logical_containment} \]
-    Then the combination of \cref{eq:lemma_logical_extendable_set,eq:logical_extension_C,eq:logical_containment} yields \cref{eq:1a_implication}.\\
+    Then the combination of \cref{eq:lemma_logical_extendable_set,eq:logical_extension_C,eq:logical_containment} yields \cref{eq:1a_implication}.
+Computationally enumerating all logical extensions $C \subseteq \Events{\jointvar}$ for a particular antecedent $a \in \Events{\mscenario}$ corresponds iteratively selecting marginal sections $c \neq a$ for membership in $C$ until \cref{eq:logical_containment} is satisfies.
+This process is more generally known as a set-covering problem, or a hypergraph transversal problem~\cite{Inflation}, an idea we return to in the more general picture to follow in \cref{sec:dep}.
+\todo[TC]{Maybe use an example here to define a Hardy transversal.}\\
 
@@
 The principle statement of \cref{lemma:logical_extenable_set} can be taken in a probabilistic form.
-If the marginal model $\probvec^{\mscenario}$ is to admit a joint distribution $\probvec^{\jointvar}$, then it must be that the antecedent probability $a\in \Sect{\mscenario}$ ($\probvec^{\mscenario}_a = \prob[\Dom{a}][a]$) is equal to a marginalization over its extendable set into $\jointvar$.
+If the marginal model $\probvec^{\mscenario}$ is to admit a joint distribution $\probvec^{\jointvar}$, then it must be that the antecedent probability $\probvec^{\mscenario}_a$ is equal to a marginalization over its extendable set into $\jointvar$.
     \[ \probvec^{\mscenario}_a = \sum_{j \in \Ext[\jointvar]{a}}\probvec^{\jointvar}_j \eq \label{eq:marginal_extendable_sum_a} \]
@@
     \[ \sum_{c \in C}\probvec^{\mscenario}_c = \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\probvec^{\jointvar}_j \eq \label{eq:marginal_extendable_sum_cs} \]
-    Since $C$ is a logical extension of $a$, the right-hand side of \cref{eq:marginal_extendable_sum_a} \textit{algebraically} covers \cref{eq:marginal_extendable_sum_cs}\footnote{If there were a joint outcome $j^*$ present on the right-hand side of \cref{eq:marginal_extendable_sum_a} but not the right-hand side of \cref{eq:marginal_extendable_sum_cs}, then \cref{eq:1a_probabilistic} would be violated by the deterministic joint distribution where $\probvec^{\jointvar}_{j^*} = 1$}.
+    Since $C$ is a logical extension of $a$, the right-hand side of \cref{eq:marginal_extendable_sum_a} \textit{algebraically} covers \cref{eq:marginal_extendable_sum_cs}\footnote{If there were a joint event $j^*$ present on the right-hand side of \cref{eq:marginal_extendable_sum_a} but not the right-hand side of \cref{eq:marginal_extendable_sum_cs}, then \cref{eq:1a_probabilistic} would be violated by the deterministic joint distribution where $\probvec^{\jointvar}_{j^*} = 1$}.
 Therefore one recovers the probabilistic version of \cref{eq:1a_implication},
     \[ \probvec^{\mscenario}_a \leq \sum_{c \in C}\probvec^{\jointvar}_c \eq \label{eq:1a_probabilistic} \]
-    Because \cref{eq:1a_probabilistic}'s logical precedent, inequalities of the form of \cref{eq:1a_probabilistic} are called \term{Hardy inequalities}.
+    Due to the logical precedent, inequalities of the form of \cref{eq:1a_probabilistic} are called \term{Hardy inequalities}.
+Marginal models that are contextual on a logical level are \term{possibilistically contextual}.
+In~\cite{Abramsky_2011} it was demonstrated that all possibilistically contextual models have their contextuality witnessed by logical extensions.
+In this sense, logical implications of the form \cref{eq:1a_implication} completely solve the possibilistic marginal problem.
     \todo[TC]{Discuss logical bell inequalities}
-    \begin{remark}
-        It is also possible to recover \cref{eq:1a_probabilistic} from \cref{eq:1a_implication} by more direct means by putting \cref{eq:1a_implication} into disjunction normal form and assigning it a certain probability,
-        \[ \prob[][\neg a \vee \bigvee_{c \in C} c] = 1 \]
-        Then applying Boole's indentity and the negative rule $\prob[][\neg a] = 1 - \prob[][a]$ one recovers \cref{eq:1a_probabilistic}.
-    \end{remark}
     \begin{remark}
@@
 
-    Computationally enumerating all logical extensions $C \subseteq \Sect{\jointvar}$ for a particular antecedent $a \in \Sect{\mscenario}$ corresponds iteratively selecting marginal sections $c \neq a$ for membership in $C$ until \cref{eq:logical_containment} is satisfies.
-This process is more generally known as a set-covering problem, or a hypergraph transversal problem~\cite{Inflation}, an idea we return to in the more general picture to follow.
-
     \subsection{Definite Extensions}
-    We will now generalize the notion of a Hardy transversal by considering multi-sets of antecedents corresponding to multiple marginal outcomes each accompanied by an assigned multiplicity.
+    We will now generalize the notion of a Hardy transversal by considering multi-sets of antecedents corresponding to multiple marginal events each accompanied by an assigned multiplicity.
 Afterwards we provide an algorithm to completely solve the marginal problem by transversing generalized hypergraphs.
@@
     \begin{definition}
-        A \term{multi-set} or \term{bag} $\mset{}$ for a marginal scenario $\mscenario$ is a vector indexed by marginal outcomes $m \in \Sect{\mscenario}$ whose entries are integers $\mset{}_{m} \in \Z$.
-The \term{support} $\supp{\mset{}}$ of an bag is the subset of marginal outcomes that are assigned non-zero multiplicity.
-        \[ \supp{\mset{}} \defined \bc{m \in \Sect{\mscenario} \mid \mset{}_m \neq 0} \]
-        The \term{order} $\abs{\mset{}}$ of a multi-set $\mset{}$ is entry-wise sum of $\mset{}$.
-        \[ \abs{\mset{}} = \sum_{m \in \Sect{\mscenario}} \mset{}_m = \sum_{m \in \supp{\mset{}}} \mset{}_m \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{marginal indicator} vector $\de^{m}$ for a marginal outcome $m$ is the unit vector indexed by marginal outcomes $\Sect{\mscenario}$ whose only non-zero entry is the marginal outcome $m$.
-        \[ \forall m' \in \Sect{\mscenario} : \de^{m}_{m'} = \begin{cases}
+        A \term{multi-set} or \term{bag} $\ga$ for a marginal scenario $\mscenario$ is a vector indexed by marginal events $m \in \Events{\mscenario}$ whose entries are integers $\ga_{m} \in \Z$.
+The \term{support} $\supp{\ga}$ of an bag is the subset of marginal events that are assigned non-zero multiplicity.
+        \[ \supp{\ga} \defined \bc{m \in \Events{\mscenario} \mid \ga_m \neq 0} \]
+        The \term{order} $\abs{\ga}$ of a multi-set $\ga$ is entry-wise sum of $\ga$.
+        \[ \abs{\ga} = \sum_{m \in \Events{\mscenario}} \ga_m = \sum_{m \in \supp{\ga}} \ga_m \]
+    \end{definition}
+
+    \begin{definition}
+        The \term{marginal indicator} vector $\de^{m}$ for a marginal event $m$ is the unit vector indexed by marginal outcomes $\Events{\mscenario}$ whose only non-zero entry is the marginal event $m$.
+        \[ \forall m' \in \Events{\mscenario} : \de^{m}_{m'} = \begin{cases}
             1 & m' = m \\
@@
     \begin{definition}
-        The \term{extension $\extmset{}$ of an multi-set $\mset{}$} for a marginal scenario $\mscenario$ is a vector indexed by \textit{joint} outcomes $j \in \Sect{\jointvar}$ and is constructed by merging the extendable sets of each marginal outcome $m \in \supp{\mset{}}$.
-        \[ \forall j \in \Sect{\jointvar} : \extmset{}_{j} \defined \sum_{m \in \supp{\mset{}}} \mset{}_{m} \de_{m \ext j}\]
-        Which is equivalent to a left-multiplication of $\ga$ into the incidence matrix $M$.
-        \[ \extmset{} \defined \mset{} \cdot M \]
-    \end{definition}
-
-    For every multi-set $\mset{}$ there corresponds a candidate inequality $I_{\mscenario} = \bc{\mset{} \cdot \probvec^{\mscenario} \geq 0}$ whose validity is completely characterized by the extension of $\mset{}$.
+        The \term{extension $\Ga$ of an multi-set $\ga$} for a marginal scenario $\mscenario$ is a vector indexed by \textit{joint} events $j \in \Events{\jointvar}$ and can be constructed by left-multiplication of $\ga$ into the incidence matrix $M$.
+        \[ \Ga \defined \ga \tcdot M \]
+    \end{definition}
+
+    For every multi-set $\ga$ there corresponds a candidate inequality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ whose validity is completely characterized by $\Ga$.
     \begin{theorem}
-        \label{thm:deinite_extension_main_thm}
-        Let $\mset{}$ be a multi-set for the marginal scenario $\mscenario$.
-Then the inequality $I_{\mscenario} = \bc{\mset{} \cdot \probvec^{\mscenario} \geq 0}$ is a valid non-contextuality inequality if and only if $\extmset{}$ is positive semi-definite.
-        \[ \forall \probvec^{\mscenario} \in \s{NC} : \mset{} \cdot \probvec^{\mscenario} \geq 0 \iff \extmset{} \succeq 0 \qquad \forall j : \extmset{}_j \geq 0 \eq \label{eq:thm:semi_definite_extension}\]
+        \label{thm:definite_extension_main_thm}
+        Let $\ga$ be a multi-set for the marginal scenario $\mscenario$.
+Then the inequality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ is a valid non-contextuality inequality if and only if $\Ga$ is positive semi-definite.
+        \[ \forall \probvec^{\mscenario} \in \s{NC} : \ga \tcdot \probvec^{\mscenario} \geq 0 \iff \Ga \succeq 0  \eq \label{eq:thm:semi_definite_extension}\]
     \end{theorem}
     \begin{proof}
-        The proof follows directly from \cref{eq:incidence_matrix_use}. Since $\probvec^{\mscenario} = M \cdot \probvec^{\jointvar}$,
-        \[ \mset{} \cdot \probvec^{\mscenario} = \mset{} \cdot M \cdot \probvec^{\jointvar} = \extmset{} \cdot \probvec^{\jointvar} \]
-        Thus $\extmset{} \succeq 0$ implies that $\extmset{} \cdot \probvec^{\jointvar} \geq 0$ which gives $\mset{} \cdot \probvec^{\mscenario} \geq 0$.
+        The proof follows directly from \cref{eq:incidence_matrix_use}. Since $\probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}$,
+        \[ \ga \tcdot \probvec^{\mscenario} = \ga \tcdot M \tcdot \probvec^{\jointvar} = \Ga \tcdot \probvec^{\jointvar} \]
+        If $\Ga \succeq 0$, then $\Ga \tcdot \probvec^{\jointvar} \geq 0$ which gives $\ga \tcdot \probvec^{\mscenario} \geq 0$.
 The forward case of \cref{eq:thm:semi_definite_extension} can be proven by contradiction.
-Suppose that $\mset{} \cdot \probvec^{\mscenario} \geq 0$ for all marginal models but $\Ga \not \succeq 0$.
-There then must exist at least one joint outcome $\exists j^{*} : \Ga_{j^{*}} < 0$ such that the deterministic joint distribution $\probvec^{\jointvar} = \de^{j^{*}}$ induces contradiction,
-        \[ 0 > \extmset{}_{j^{*}} = \extmset{}\cdot \de^{j^{*}} = \mset{} \cdot M \cdot \de^{j^{*}}  \]
-        Because $M \cdot \de^{j^{*}}$ is a non-contextual marginal model but $\ga \cdot M \cdot \de^{j^{*}} \not \geq 0$.
+Suppose that $\ga \tcdot \probvec^{\mscenario} \geq 0$ for all marginal models but $\Ga \not \succeq 0$.
+Consequently there exists at least one joint outcome $j^{*}$ such that $\Ga_{j^{*}} < 0$.
+This negative entry can be exploited by a deterministic joint distribution $\probvec^{\jointvar} = \de^{j^{*}}$,
+        \[ 0 > \Ga_{j^{*}} = \Ga\tcdot \de^{j^{*}} = \ga \tcdot M \tcdot \de^{j^{*}}  \]
+        Which is a contradiction: $M \tcdot \de^{j^{*}}$ is a non-contextual marginal model but $\ga \tcdot M \tcdot \de^{j^{*}} \not \geq 0$.
     \end{proof}
+
+    Clearly if the multi-set itself is positive semi-definite $\ga \succeq 0$ then $\Ga \succeq 0$ is also.
+Corresponding inequalities are then \textit{trivial}: being satisfied by all $\probvec^{\mscenario} \in \s{NC}$.
+As such, it is desired to obtain definite extensions $\Ga$ from \textit{indefinite} multi-sets $\ga$.
+
     \begin{corollary}
-        Let $\mset{}$ be a multi-set for the marginal scenario $\mscenario$.
-Then the equality $I_{\mscenario} = \bc{\mset{} \cdot \probvec^{\mscenario} = 0}$ is satisfied by all non-contextual marginal models if and only if $\extmset{}$ is a null vector (i.e.
-$\forall j : \extmset{}_{j} = 0$).
+        Let $\ga$ be a multi-set for the marginal scenario $\mscenario$.
+Then the equality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} = 0}$ is satisfied by all non-contextual marginal models if and only if $\Ga$ is a null vector (i.e.
+$\forall j : \Ga_{j} = 0$).
     \end{corollary}
 
-    \Cref{thm:deinite_extension_main_thm} demonstrates it is possible to generate non-contextuality inequalities by finding multi-sets $\mset{}$ such that $\Ga \succeq 0$.
-In light of this, we will formally define the subset of joint outcomes $j$ that are preventing a candidate multi-set $\mset$ from having positive semi-definite extensions.
-
-    \begin{definition}
-        The \term{inhibiting set} $\inhibit\br{\mset}$ for a multi-set $\mset$ is the subset of joint outcomes preventing $\extmset \succeq 0$ from holding true.
-        \[ \inhibit\br{\mset} = \bc{j \in \Sect{\jointvar} \mid \br{\mset \cdot M}_j = \extmset_j < 0} \]
-    \end{definition}
-
-    Clearly if the multi-set itself is positive semi-definite $\mset{} \succeq 0$ then $\extmset{} \succeq 0$ is maintained always.
-As such, it is desired to obtain multi-sets $\mset{}$ that have some positive and negative entires.
-Procedurally, definite extensions can be built by beginning with a seed multi-set $\mset{}^{} = \mset{}^{A}$ (to be called the antecedent set) composed entirely of non-positive entries and iteratively modifying $\mset{}^{(n)}$ by adding $1$ to specific marginal outcomes $m$ ($\mset{}^{(n+1)} = \mset{}^{(n)} + \de^{m}$) in such a way that progresses $\extmset{}^{(n)}$ toward becoming positive semi-definite (i.e.
+    \Cref{thm:definite_extension_main_thm} demonstrates it is possible to generate non-contextuality inequalities by finding multi-sets $\ga$ such that $\Ga \succeq 0$.
+In light of this, we will formally define the subset of joint outcomes $j$ that are preventing a candidate multi-set $\ga$ from having positive semi-definite extensions.
+
+    \begin{definition}
+        The \term{inhibiting set} $\inhibit\br{\ga}$ for a multi-set $\ga$ is the subset of joint outcomes preventing $\Ga \succeq 0$ from holding true.
+        \[ \inhibit\br{\ga} = \bc{j \in \Events{\jointvar} \mid \br{\ga \tcdot M}_j = \Ga_j < 0} \]
+    \end{definition}
+
+    Procedurally, definite extensions can be built by beginning with a seed multi-set $\ga^{(0)} = \ga^{A}$ composed entirely of non-positive entries and iteratively appending marginal events $m$ ($\ga^{(n+1)} = \ga^{(n)} + \de^{m}$) in such a way that progresses $\Ga^{(n)}$ toward becoming positive semi-definite (i.e.
 by decreasing the inhibiting set).
@@
     \subsection{Definite Extension Procedure}
+    \label{sec:dep}
     Before discussing the definite extension procedure (DEP) directly, we will motivate its main algorithmic component (weighted hypergraphs transversals) with a short example.
@@
                 \scalebox{1.0}{\input{../figures/hypergraphs/minimal_example}}
-                \caption{An edge-weighted hypergraph $\hgraph_{\weights}$ corresponding to the antecedent set $\mset^{A}$ with $\mset^{A}_{m_3} = -1$ and $\mset^{A}_{m_8} = -2$.}
+                \caption{An edge-weighted hypergraph $\hgraph_{\weights}$ corresponding to the antecedent set $\ga^{A}$ with $\ga^{A}_{m_3} = -1$ and $\ga^{A}_{m_8} = -2$.}
                 \label{fig:hypergraph_example}
@@
         \end{figure}
-        Now suppose our antecedent set is $\mset^{A}$ and has two specified entries:
-        \[ \mset^{A}_{m_{3}} = -1 \quad \mset^{A}_{m_{8}} = -2 \]
-        Then the antecedent extension is given by $\extmset^{A}= \mset^{A} \cdot M$:
-        \[ \extmset^{A}_{j_{4}} = \extmset^{A}_{j_{8}} = -2 \quad \extmset^{A}_{j_{5}} = \extmset^{A}_{j_{6}} = -1 \]
-        The objective then becomes to \textit{hit} the joint outcomes of the inhibiting set $\bc{j_{4}, j_{5}, j_{6}, j_{8}}$ with marginal outcomes organized as a consequent multi-set $\mset^{C} \succeq 0$ such that,
-        \[ \extmset^{C} + \extmset^{A} \succeq 0 \]
+        Now suppose our antecedent set is $\ga^{A}$ and has two specified entries:
+        \[ \ga^{A}_{m_{3}} = -1 \quad \ga^{A}_{m_{8}} = -2 \]
+        Then the antecedent extension is given by $\Ga^{A}= \ga^{A} \tcdot M$:
+        \[ \Ga^{A}_{j_{4}} = \Ga^{A}_{j_{8}} = -2 \quad \Ga^{A}_{j_{5}} = \Ga^{A}_{j_{6}} = -1 \]
+        The objective then becomes to \textit{cover} the joint events of the inhibiting set $\bc{j_{4}, j_{5}, j_{6}, j_{8}}$ with marginal events organized as a consequent multi-set $\ga^{C} \succeq 0$ such that,
+        \[ \Ga^{C} + \Ga^{A} \succeq 0 \]
         Taking motivation from \cref{sec:logical_inequalities}, this procedure can be casted as a multi-node hitting problem, or an edge-weighted hypergraph problem.
 Construct a weighted hypergraph $\hgraph_{\weights}$ (see \cref{fig:hypergraph_example}) where the edges are labeled by joint outcomes $\edges = \bc{e_{j_{4}}, e_{j_{5}}, e_{j_{6}}, e_{j_{8}}}$.
-These edges are assigned weights $w_j$ precisely equal to the magnitude of $\extmset^{A}$.
-        \[ \forall j \in \bc{{j_{4}}, {j_{5}}, {j_{6}}, {j_{8}}} : w_{j} = - \extmset^{A}_j \]This weighting represents the joint outcomes that are preventing $\extmset$ from becoming positive semi-definite.
-The nodes represent all possible marginal outcomes that have the potential to contribute to $\mset^{C}$.
+These edges are assigned weights $w_j$ precisely equal to the magnitude of $\Ga^{A}$.
+        \[ \forall j \in \bc{{j_{4}}, {j_{5}}, {j_{6}}, {j_{8}}} : w_{j} = - \Ga^{A}_j \]
+        These weights characterize the joint events that are preventing $\Ga$ from becoming positive semi-definite.
+The nodes represent all possible marginal events that have the potential to contribute to $\ga^{C}$.
         \[ \nodes = \bc{m_2, m_4, m_5, m_6, m_{10}, m_{11}, m_{12}} \]
@@
 We call such $\trans$ \textit{transversals} of $\hgraph_{\weights}$.
-This multi-sets enable one to construct the positive semi-definite extension $\extmset^{C} + \extmset^{A}$ where $\extmset^{C} = \trans \cdot M$.
-This corresponds to the inequality $- \ga^{A} \cdot \probvec^{\mscenario} \leq \ga^{C} \cdot \probvec^{\mscenario}$,
+This multi-set enables one to construct the positive semi-definite extension $\Ga^{C} + \Ga^{A}$ where $\Ga^{C} = \trans \tcdot M$.
+This corresponds to the inequality $- \ga^{A} \tcdot \probvec^{\mscenario} \leq \ga^{C} \tcdot \probvec^{\mscenario}$,
         \begin{align*}
@@
     %     The following relationships hold for the indicator vectors.
-    %     \[ \de^{\mscenario \ext \jointvar} \cdot \de^{j} = \de^{j \res \mscenario} \qquad \de^{m} \cdot \de^{\mscenario \ext \jointvar} = \de^{m \ext \jointvar} \]
+    %     \[ \de^{\mscenario \ext \jointvar} \tcdot \de^{j} = \de^{j \res \mscenario} \qquad \de^{m} \tcdot \de^{\mscenario \ext \jointvar} = \de^{m \ext \jointvar} \]
     % \end{definition}
     % We first recall that every non-contextual marginal model $\prob^{\mscenario}$ can be written as the convex combination of columns of the incidence matrix $M$.
-    % \[ \probvec^{\mscenario} = M \cdot \probvec^{\jointvar} = \sum_{j \in \Sect{\jointvar}} \de_{m \ext j} \prob[\jointvar][j] \]
+    % \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} = \sum_{j \in \Events{\jointvar}} \de_{m \ext j} \prob[\jointvar][j] \]
     % Thus we define the set of all non-contextual marginal models as $\mathcal{NC}$,
@@
     % \begin{definition}
-    %     Let $\mscenario$ be a marginal scenario and let $j \in \Sect{\jointvar}$ be a joint outcome.
-The \term{restriction of $j$ onto $\mscenario$} is deterministic marginal model $\de_{j \res \mscenario} : \Sect{\mscenario} \to \bc{0, 1}$.
+    %     Let $\mscenario$ be a marginal scenario and let $j \in \Events{\jointvar}$ be a joint outcome.
+The \term{restriction of $j$ onto $\mscenario$} is deterministic marginal model $\de_{j \res \mscenario} : \Events{\mscenario} \to \bc{0, 1}$.
     %     \[ \de_{j \res \mscenario}\br{m} \defined \begin{cases}
@@
     %     \end{cases} \]
-    %     As a vector indexed by marginal outcomes $m \in \Sect{\mscenario}$, $\de_{j \ext \mscenario}$ is precisely the $j$-th column of the incidence matrix.
+    %     As a vector indexed by marginal outcomes $m \in \Events{\mscenario}$, $\de_{j \ext \mscenario}$ is precisely the $j$-th column of the incidence matrix.
     % \end{definition}
@@
     % \begin{definition}
-    %     The \term{extension of an m-set} $\mset{S}$ into $\jointvar$ denoted $\extmset{S}$ is a vector indexed by \textit{joint} outcomes $j \in \Sect{\jointvar}$ and is defined as follows,
-    %     \[ \extmset{S}_{j} \defined \sum_{s \in \supp{\mset{S}}} \mset{S}_{s} \de_{s \ext j} \eq \label{eq:joint_multiplicity} \]
-    %     As an immediate consequence, the support of $\extmset{S}$ is immediately known,
-    %     \[ \supp{\extmset{S}} = \bigcup_{s \in \supp{\mset{S}}} \Ext[\jointvar]{s} \]
+    %     The \term{extension of an m-set} $\ga{S}$ into $\jointvar$ denoted $\Ga{S}$ is a vector indexed by \textit{joint} outcomes $j \in \Events{\jointvar}$ and is defined as follows,
+    %     \[ \Ga{S}_{j} \defined \sum_{s \in \supp{\ga{S}}} \ga{S}_{s} \de_{s \ext j} \eq \label{eq:joint_multiplicity} \]
+    %     As an immediate consequence, the support of $\Ga{S}$ is immediately known,
+    %     \[ \supp{\Ga{S}} = \bigcup_{s \in \supp{\ga{S}}} \Ext[\jointvar]{s} \]
     % \end{definition}
     % \begin{definition}
-    %     An m-set $\mset{C}$ is an \term{extension cover} of an m-set $\mset{A}$ for a marginal scenario $\mscenario$ if and only if the following two conditions hold\footnote{In fact \cref{eq:multi_extenable_cover_def} implies \cref{eq:flat_extenable_cover_def} since $\forall j \not \in \supp{\extmset{A}} : \extmset{A}_j = 0$.}:
+    %     An m-set $\ga{C}$ is an \term{extension cover} of an m-set $\ga{A}$ for a marginal scenario $\mscenario$ if and only if the following two conditions hold\footnote{In fact \cref{eq:multi_extenable_cover_def} implies \cref{eq:flat_extenable_cover_def} since $\forall j \not \in \supp{\Ga{A}} : \Ga{A}_j = 0$.}:
     %     \begin{gather*}
-    %         \supp{\extmset{A}} \subseteq \supp{\extmset{C}} \eq \label{eq:flat_extenable_cover_def}\\
-    %         \forall j \in \supp{\extmset{A}} : \extmset{A}_{j} \leq \extmset{C}_j \eq \label{eq:multi_extenable_cover_def}
+    %         \supp{\Ga{A}} \subseteq \supp{\Ga{C}} \eq \label{eq:flat_extenable_cover_def}\\
+    %         \forall j \in \supp{\Ga{A}} : \Ga{A}_{j} \leq \Ga{C}_j \eq \label{eq:multi_extenable_cover_def}
     %     \end{gather*}
@@
     %     \label{thm:extendable_cover_ineq}
-    %     If the m-set $\mset{C}$ is an extension cover of the m-set $\mset{A}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
-    %     \[ \sum_{a \in \supp{\mset{A}}}\mset{A}_a\prob[][a] \leq \sum_{c \in \supp{\mset{C}}}\mset{C}_c\prob[][c] \eq \label{eq:extendable_cover} \]
+    %     If the m-set $\ga{C}$ is an extension cover of the m-set $\ga{A}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
+    %     \[ \sum_{a \in \supp{\ga{A}}}\ga{A}_a\prob[][a] \leq \sum_{c \in \supp{\ga{C}}}\ga{C}_c\prob[][c] \eq \label{eq:extendable_cover} \]
     % \end{theorem}
@@
 
-    %     For each m-set $\mset{S}$ write the weighted sum over the probabilities $\bc{\prob[][s]}_{s \in \supp{\mset{S}}}$ in terms of the joint distribution $\prob[\jointvar]$ using \cref{eq:joint_multiplicity}.
+    %     For each m-set $\ga{S}$ write the weighted sum over the probabilities $\bc{\prob[][s]}_{s \in \supp{\ga{S}}}$ in terms of the joint distribution $\prob[\jointvar]$ using \cref{eq:joint_multiplicity}.
     %     \begin{align*}
@@
     %     \begin{split}
-    %     \sum_{s \in \supp{\mset{S}}} \mset{S}_s\prob[][s] &= \sum_{s \in \supp{\mset{S}}} \mset{S}_s  \sum_{j \in \Ext[\jointvar]{s}} \prob[\jointvar][j] \\
-    %     &= \sum_{s \in \supp{\mset{S}}} \mset{S}_s \sum_{j \in \Sect{\jointvar}} \isext{s}{j} \prob[\jointvar][j] \\
-    %     &= \sum_{j \in \Sect{\jointvar}} \bs{\sum_{s \in \supp{\mset{S}}} \mset{S}_s  \isext{s}{j}} \prob[\jointvar][j] \\
-    %     &= \sum_{j \in \supp{\extmset{S}}} \extmset{S}_j \prob[\jointvar][j]
+    %     \sum_{s \in \supp{\ga{S}}} \ga{S}_s\prob[][s] &= \sum_{s \in \supp{\ga{S}}} \ga{S}_s  \sum_{j \in \Ext[\jointvar]{s}} \prob[\jointvar][j] \\
+    %     &= \sum_{s \in \supp{\ga{S}}} \ga{S}_s \sum_{j \in \Events{\jointvar}} \isext{s}{j} \prob[\jointvar][j] \\
+    %     &= \sum_{j \in \Events{\jointvar}} \bs{\sum_{s \in \supp{\ga{S}}} \ga{S}_s  \isext{s}{j}} \prob[\jointvar][j] \\
+    %     &= \sum_{j \in \supp{\Ga{S}}} \Ga{S}_j \prob[\jointvar][j]
     %     \end{split}
@@
     %     First examine the substitution $S \to C$,
-    %     \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] = \sum_{j \in \supp{\extmset{C}}} \extmset{C}_j \prob[\jointvar][j] \]
-    %     By \cref{eq:flat_extenable_cover_def} $\supp{\extmset{A}} \subseteq \supp{\extmset{C}}$,
-    %     \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] = \sum_{j \in \supp{\extmset{C}}} \extmset{C}_j \prob[\jointvar][j] + \sum_{j \in \supp{\extmset{C}} \setminus \supp{\extmset{A}}} \extmset{C}_j \prob[\jointvar][j] \]
-    %     Notice that the sum over $j \in \supp{\extmset{C}} \setminus \supp{\extmset{A}}$ is entirely positive since $\extmset{C}_j \in \N$ and $\prob[\jointvar][j] \geq 0$.
-Moreover \cref{eq:multi_extenable_cover_def} gives $\extmset{C}_j \geq \extmset{A}_j$.
+    %     \[ \sum_{c \in \supp{\ga{C}}} \ga{C}_c\prob[][c] = \sum_{j \in \supp{\Ga{C}}} \Ga{C}_j \prob[\jointvar][j] \]
+    %     By \cref{eq:flat_extenable_cover_def} $\supp{\Ga{A}} \subseteq \supp{\Ga{C}}$,
+    %     \[ \sum_{c \in \supp{\ga{C}}} \ga{C}_c\prob[][c] = \sum_{j \in \supp{\Ga{C}}} \Ga{C}_j \prob[\jointvar][j] + \sum_{j \in \supp{\Ga{C}} \setminus \supp{\Ga{A}}} \Ga{C}_j \prob[\jointvar][j] \]
+    %     Notice that the sum over $j \in \supp{\Ga{C}} \setminus \supp{\Ga{A}}$ is entirely positive since $\Ga{C}_j \in \N$ and $\prob[\jointvar][j] \geq 0$.
+Moreover \cref{eq:multi_extenable_cover_def} gives $\Ga{C}_j \geq \Ga{A}_j$.
 Combining these observations along with \cref{eq:derivation_cover} for $S \to A$, one arrives at the inequality,
-    %     \[ \sum_{c \in \supp{\mset{C}}} \mset{C}_c\prob[][c] \geq \sum_{j \in \supp{\extmset{A}}} \extmset{A}_j \prob[\jointvar][j] = \sum_{a \in \supp{\mset{A}}} \mset{A}_a\prob[][a] \]
+    %     \[ \sum_{c \in \supp{\ga{C}}} \ga{C}_c\prob[][c] \geq \sum_{j \in \supp{\Ga{A}}} \Ga{A}_j \prob[\jointvar][j] = \sum_{a \in \supp{\ga{A}}} \ga{A}_a\prob[][a] \]
     %     Which is equivalent to \cref{eq:extendable_cover}; every non-contextual marginal model $\prob^{\mscenario}$ must satisfy \cref{eq:extendable_cover}.
@@
     %     A proof is easy to see by contradiction.
-Let $I_{\mscenario} = \bc{\gamma \cdot \probvec^{\mscenario} \geq 0}$ where $\gamma_m \in \Z | \forall m \in \Sect{\mscenario}$ be a homogeneous, linear, integer coefficient, compatibility inequality such that it is \textit{not} an extension covering inequality.
+Let $I_{\mscenario} = \bc{\gamma \tcdot \probvec^{\mscenario} \geq 0}$ where $\gamma_m \in \Z | \forall m \in \Events{\mscenario}$ be a homogeneous, linear, integer coefficient, compatibility inequality such that it is \textit{not} an extension covering inequality.
 Next seperate $\gamma$ into its positive and negative components,
@@
     %     Such that both $\gamma^{+}$ and $\gamma^{-}$ are valid m-sets.
-Therefore $I_{\mscenario} = \bc{\br{\gamma^{+} - \gamma^{-}} \cdot \probvec^{\mscenario} \geq 0}$.
-Since this inequality is \textit{not} an extension cover, it must be that there exists at least one joint outcome $j' \in \Sect{\jointvar}$ such that $\Gamma^{-}_{j'} > \Gamma^{+}_{j'}$.
+Therefore $I_{\mscenario} = \bc{\br{\gamma^{+} - \gamma^{-}} \tcdot \probvec^{\mscenario} \geq 0}$.
+Since this inequality is \textit{not} an extension cover, it must be that there exists at least one joint outcome $j' \in \Events{\jointvar}$ such that $\Gamma^{-}_{j'} > \Gamma^{+}_{j'}$.
 Consequently by \cref{eq:derivation_cover}, the deterministic distribution $\probvec^{\mscenario} = \de_{j' \res \mscenario}$ \textit{violates} $I_{\mscenario}$.
@@
     % \begin{corollary}
-    %     If the m-set $\mset{C}$ is an extension cover of the m-set $\br{A, \mulA}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
-    %     \[ \sum_{a \in \supp{\mset{A}}}\prob[][a] \leq \sum_{c \in \supp{\mset{C}}}\prob[][c] \eq \label{eq:extendable_cover_flat} \]
+    %     If the m-set $\ga{C}$ is an extension cover of the m-set $\br{A, \mulA}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
+    %     \[ \sum_{a \in \supp{\ga{A}}}\prob[][a] \leq \sum_{c \in \supp{\ga{C}}}\prob[][c] \eq \label{eq:extendable_cover_flat} \]
     % \end{corollary}
     % \begin{proof}
-    %     This follows from the fact that if $\mset{C}$ is an extension cover of $\br{A, \mulA}$, then $\br{C, \mathbf{1}_{C}}$ is an extension cover of $\br{A, \mathbf{1}_{A}}$.
+    %     This follows from the fact that if $\ga{C}$ is an extension cover of $\br{A, \mulA}$, then $\br{C, \mathbf{1}_{C}}$ is an extension cover of $\br{A, \mathbf{1}_{A}}$.
 Since $E_A \subseteq E_C$ is already trivially satisfied, all that remains is to demonstrate that \cref{eq:multi_extenable_cover_def} holds for unitary multiplicities $\mathbf{1}_A$ and $\mathbf{1}_C$.
 
-    %     First examine extension $\br{E_C, \mul{\mext{C}}}$ for the m-set $\mset{C}$ as defined by \cref{eq:joint_multiplicity},
-    %     \[ \forall j \in E_C : \extmset{C}_j = \sum_{c \in \supp{\mset{C}}} \mulC\br{c} \isext{c}{j} \]
+    %     First examine extension $\br{E_C, \mul{\mext{C}}}$ for the m-set $\ga{C}$ as defined by \cref{eq:joint_multiplicity},
+    %     \[ \forall j \in E_C : \Ga{C}_j = \sum_{c \in \supp{\ga{C}}} \mulC\br{c} \isext{c}{j} \]
 
     %     First apply \cref{lemma:logical_extenable_set} to an arbitrary set $S \in \bc{A, C}$,
-    %     \[ \bigvee_{s \in \supp{\mset{S}}} s \iff \bigvee_{s \in \supp{\mset{S}}} \bigvee_{j \in \Ext[\jointvar]{s}} j \iff \bigvee_{j \in E_S} j \eq \label{eq:logical_iff_ext}\]
+    %     \[ \bigvee_{s \in \supp{\ga{S}}} s \iff \bigvee_{s \in \supp{\ga{S}}} \bigvee_{j \in \Ext[\jointvar]{s}} j \iff \bigvee_{j \in E_S} j \eq \label{eq:logical_iff_ext}\]
     %     Now since $E_A \subseteq E_C$ by \cref{eq:flat_extenable_cover_def} we have that,
@@
     %     Combining \cref{eq:logical_iff_ext,eq:logical_cover} one arrives at,
-    %     \[ \bigvee_{a \in \supp{\mset{A}}} a \implies \bigvee_{c \in \supp{\mset{C}}}c \]
+    %     \[ \bigvee_{a \in \supp{\ga{A}}} a \implies \bigvee_{c \in \supp{\ga{C}}}c \]
     % \end{proof}
@@
         \[ \forall n' \in \nodes : \exists e \in \edges, n' \in e : \sum_{n \in e} \trans_{n} - 1 < w_e  \eq \label{eq:weighted_trans_minimal}\]
-        Equivalently, $\trans$ is minimal if there does not exists another transversal $\trans'$ that precedes $\trans$.
-        \[ \not \exists \trans' \neq \trans : \forall j : \trans'_j \leq \trans_j \]
-    \end{definition}
-    Remark than in the situation where all assigned weights are singular $w_e = 1$, the weighted minimality condition \cref{eq:weighted_trans_minimal} reduces to the unweighted minimality condition \cref{eq:flat_trans_minimal}.
+        Equivalently, $\trans$ is minimal if there does not exists another transversal $\trans' \neq \trans$ such that $\forall j : \trans'_j \leq \trans_j$.
+    \end{definition}
+    Remark that if all assigned weights are singular $w_e = 1$, the weighted minimality condition \cref{eq:weighted_trans_minimal} reduces to the unweighted minimality condition \cref{eq:flat_trans_minimal}.
 The principle component of the definite extension procedure can be summarized as follows:
@@
     \subsubsection{Transversals of Antecedent Hypergraphs}
-    Given an antecedent multi-set $\mset^{A}$ where $\mset^{A} \preceq 0$, identify the \textit{inhibiting set} $\inhibit\br{\mset^{A}}$ responsible for preventing $\extmset^{A}$ from being classified as positive semi-definite.
-For an antecedent set $\mset^{A}$ where all entries are negative, there are a few equivalent ways of representing the inhibiting set,
-    \[ \inhibit\br{\mset^{A}} = \supp{\extmset^{A}} = \bc{j \mid \extmset^A_j < 0} = \bc{j \mid \exists m \in \supp{\mset^A} : m \ext j } \]
-    The last interpretation corresponding to the extendable set of $\supp{\mset^{A}}$.
-Using the inhibiting set $\inhibit\br{\mset^{A}}$, construct a weighted hypergraph $\hgraph_\weights\br{\mset^A}$ such that,
+    Given an antecedent multi-set $\ga^{A}$ where $\ga^{A} \preceq 0$, identify the \textit{inhibiting set} $\inhibit\br{\ga^{A}}$ responsible for preventing $\Ga^{A}$ from being classified as positive semi-definite.
+For an antecedent set $\ga^{A}$ where all entries are negative, there are a few equivalent ways of representing the inhibiting set,
+    \[ \inhibit\br{\ga^{A}} = \supp{\Ga^{A}} = \bc{j \mid \Ga^A_j < 0} = \bc{j \mid \exists m \in \supp{\ga^A} : m \ext j } \]
+    The last interpretation corresponding to the extendable set of $\supp{\ga^{A}}$.
+Using the inhibiting set $\inhibit\br{\ga^{A}}$, construct a weighted hypergraph $\hgraph_\weights\br{\ga^A}$ such that,
     \begin{align*}
-    \edges\br{\mset^{A}} &= \bc{e_j \mid j \in \inhibit\br{\mset^{A}}} \\
-    e_j &= \bc{m \in \Sect{\mscenario} \mid m \ext j, m \not \in \supp{\ga^A}} \\
-    \weights\br{\mset^{A}} &= \bc{w_j = - \extmset^{A}_j \mid j \in \inhibit\br{\mset^{A}}} \\
-    \nodes\br{\mset^A} &= \bigcup_{j \in \inhibit\br{\mset^A}} e_j \\
-    &= \bc{m \in \Sect{\mscenario} \mid m \not \in \supp{\mset^A}, \exists m' \in \supp{\mset^A} : m \com m'}
+    \edges\br{\ga^{A}} &= \bc{e_j \mid j \in \inhibit\br{\ga^{A}}} \\
+    e_j &= \bc{m \in \Events{\mscenario} \mid m \ext j, m \not \in \supp{\ga^A}} \\
+    \weights\br{\ga^{A}} &= \bc{w_j = - \Ga^{A}_j \mid j \in \inhibit\br{\ga^{A}}} \\
+    \nodes\br{\ga^A} &= \bigcup_{j \in \inhibit\br{\ga^A}} e_j \\
+    &= \bc{m \in \Events{\mscenario} \mid m \not \in \supp{\ga^A}, \exists m' \in \supp{\ga^A} : m \com m'}
     \end{align*}
-    The hyperedges $e_j \in \edges\br{\mset^{A}}$ are indexed by the inhibiting set.
-Each hyperedge $e_j$ is the subset of marginal outcomes $e_j \subseteq \Sect{\mscenario}$ that are extendable to $j$ (yet not already included in $\ga^A$\footnote{At this point, it might be unclear why we disregard marginal outcomes in $\supp{\ga^A}$.
+    The hyperedges $e_j \in \edges\br{\ga^{A}}$ are indexed by the inhibiting set.
+Each hyperedge $e_j$ is the subset of marginal events $e_j \subseteq \Events{\mscenario}$ that are extendable to $j$ (yet not already included in $\ga^A$\footnote{At this point, it might be unclear why we disregard marginal outcomes in $\supp{\ga^A}$.
 Sufficient reasoning will become apparent when presented with a complete discussion of the definite extension procedure.}).
-The weights $\weights\br{\mset^A}$ equal the amount that $\extmset^{A}$ needs to recover by, and the nodes $\nodes\br{\mset^A}$ are simply the union of all edges.
+The weights $\weights\br{\ga^A}$ equal the amount that $\Ga^{A}$ needs to recover by, and the nodes $\nodes\br{\ga^A}$ are simply the union of all edges.
 This weighted hypergraph is termed the \term{antecedent hypergraph}.
@@
         \end{cases} \]
-        Regarding the antecedent hypergraph $\hgraph\br{\mset^A}$, the matrix form $H\br{\mset^A}$ of $\hgraph\br{\mset^A}$ can be constructed by taking the incidence matrix $M$ and deleting rows not in $\nodes\br{\mset^A}$ and columns not in $\edges\br{\mset^A}$.
+        Regarding the antecedent hypergraph $\hgraph\br{\ga^A}$, the matrix form $H\br{\ga^A}$ of $\hgraph\br{\ga^A}$ can be constructed by taking the incidence matrix $M$ and deleting rows not in $\nodes\br{\ga^A}$ and columns not in $\edges\br{\ga^A}$.
 As an example, consider \cref{ex:hypergraph_example} and the hypergraph of \cref{fig:hypergraph_example}.
 The corresponding matrix representation of the hypergraph of \cref{ex:hypergraph_example} is a sub-matrix of the the incidence matrix depicted in \cref{fig:compact_incidence}.
-        \[ H\br{\mset^A} = \kbordermatrix{
+        \[ H\br{\ga^A} = \kbordermatrix{
             & j_4 & j_5 & j_6 & j_8 \\
@@
 
-    After generating an antecedent hypergraph $\hgraph\br{\mset^A}$, it is possible to find all valid, homogeneous, non-contextuality inequalities $I_\mscenario = \bc{ \mset \cdot \probvec^{\mscenario} \geq 0}$ by finding all transversals of $\hgraph\br{\mset^A}$.
-As mentioned previously for each transversal $\trans$, the marginal multi-set $\mset^C$ agreeing with $\trans$ can be constructed,
-    \[ \forall m \in \supp{\trans} : \mset^C_{m} = \trans_m \]
-    Such that $\ga^A + \ga^C$ has definite extension, which by \cref{thm:deinite_extension_main_thm} induces the valid inequality,
-    \[ I_\mscenario = \bc{\br{\mset^C + \mset^A} \cdot \probvec^{\mscenario} \geq 0} \eq \label{eq:transversal_inequality}\]
-    More importantly, one only needs to consider \textit{minimal transversals} of $\hgraph\br{\mset^A}$.
+    After generating an antecedent hypergraph $\hgraph\br{\ga^A}$, it is possible to find all valid, homogeneous, non-contextuality inequalities $I_\mscenario = \bc{ \ga \tcdot \probvec^{\mscenario} \geq 0}$ by finding all transversals of $\hgraph\br{\ga^A}$.
+As mentioned previously for each transversal $\trans$, the marginal multi-set $\ga^C$ agreeing with $\trans$ can be constructed,
+    \[ \forall m \in \supp{\trans} : \ga^C_{m} = \trans_m \]
+    Such that $\ga^A + \ga^C$ has definite extension, which by \cref{thm:definite_extension_main_thm} induces the valid inequality,
+    \[ I_\mscenario = \bc{\br{\ga^C + \ga^A} \tcdot \probvec^{\mscenario} \geq 0} \eq \label{eq:transversal_inequality}\]
+    More importantly, one only needs to consider \textit{minimal transversals} of $\hgraph\br{\ga^A}$.
 If a transversal $\trans$ is non-minimal, then there exists another transversal $\trans'$ such that $\trans' \preceq \trans$.
-A minimal transversal $\trans'$ would be have correspondence with a tighter inequality $I_\mscenario' = \bc{\br{{\mset'}^C + \mset^A} \cdot \probvec^{\mscenario} \geq 0}$ that is capable of witnessing contextually in a strictly large subset of marginal models $\probvec^{\mscenario}$.
+A minimal transversal $\trans'$ would have correspondence with a tighter inequality $I_\mscenario' = \bc{\br{{\ga'}^C + \ga^A} \tcdot \probvec^{\mscenario} \geq 0}$ that is capable of witnessing contextually in a strictly large subset of marginal models $\probvec^{\mscenario}$.
 \\
@@
     \begin{definition}
-
-    \end{definition}
+        Let $I_1$ and $I_2$ denote two different $\s{NC}$-inequalities.
+    \end{definition}
+
+    \begin{definition}
+        Let $\s{Y}$ denote the set of all multi-sets $\ga$ with positive semi-definite extensions,
+        \[ \s{Y} = \bc{\ga \mid \ga \tcdot M = \Ga \succeq 0} \]
+        A multi-set $\ga$ is said to be \term{reducible/redundant} if,
+        \[ \exists \ga^1, \ga^2 \in \s{Y} : \ga = \ga^1 + \ga^2, \ga \neq \ga^1 \neq \ga^2 \neq 0 \]
+    \end{definition}
+
+    \todo[TC]{Figure out language and how to delineate the idea of reducible and irreducible extensions}
 
@@
     \todo[TC]{Upper limit of DEP is set by lowest antecedent order of FM result} \\
+    \begin{theorem}
+        \label{thm:completeness}
+        \todo[TC]{main completeness theorem}
+    \end{theorem}
     \subsubsection{Advantages}
@@
     \todo[TC]{If complete solution is ultimately desired, FM is in principle far more efficient because it does need to prune anything} \\
+    \todo[TC]{Trivial equalities show that lower-order transversals are equivalent to higher order transversals (maybe not)} \\
     \subsubsection{Unanswered questions}
@@
     % \begin{definition}
-    %     An extension cover $\mset{C}$ of $\mset{A}$ is said to be \term{minimal} if there does not exist an extension cover $\mset{C'}$ different from $\mset{C}$ such that,
-    %     \[ \forall j \in \Sect{\jointvar} : \mset{C'}_j \leq \mset{C}_j \]
+    %     An extension cover $\ga{C}$ of $\ga{A}$ is said to be \term{minimal} if there does not exist an extension cover $\ga{C'}$ different from $\ga{C}$ such that,
+    %     \[ \forall j \in \Events{\jointvar} : \ga{C'}_j \leq \ga{C}_j \]
     % \end{definition}
 
-    % If a more minimal extension cover $\mset{C'}$ does exists, then the inequality it defines (as per \cref{thm:extendable_cover_ineq} directly implies the inequality defined by $\mset{C}$.
+    % If a more minimal extension cover $\ga{C'}$ does exists, then the inequality it defines (as per \cref{thm:extendable_cover_ineq} directly implies the inequality defined by $\ga{C}$.
 
     % \begin{definition}
-    %     An extension cover $\mset{C}$ of $\mset{A}$ is said to be \term{reducible} if there exists a \textit{partition} of $\mset{C}$ and $\mset{A}$,
-    %     \[ \mset{C} = \mset{C_1} + \mset{C_2} \qquad \mset{A} = \mset{A_1} + \mset{A_2} \]
-    %     Such that $\mset{C_1}$ is an extension cover for $\mset{A_1}$ and $\mset{C_2}$ is an extension cover for $\mset{A_2}$.
-If $\br{\mset{C}, \mset{A}}$ does \textit{not} admit a partition, then it is said to be \term{irreducible}.
+    %     An extension cover $\ga{C}$ of $\ga{A}$ is said to be \term{reducible} if there exists a \textit{partition} of $\ga{C}$ and $\ga{A}$,
+    %     \[ \ga{C} = \ga{C_1} + \ga{C_2} \qquad \ga{A} = \ga{A_1} + \ga{A_2} \]
+    %     Such that $\ga{C_1}$ is an extension cover for $\ga{A_1}$ and $\ga{C_2}$ is an extension cover for $\ga{A_2}$.
+If $\br{\ga{C}, \ga{A}}$ does \textit{not} admit a partition, then it is said to be \term{irreducible}.
     % \end{definition}
@@
     % % \begin{algorithmic}
-    % %   \State $\mset{S}^{0} = \mul{\emptyset}$
+    % %   \State $\ga{S}^{0} = \mul{\emptyset}$
     % % \end{algorithmic}
@@
     % %   \begin{algorithmic}[1]
-    % %     \Require{An antecedent m-set $\mset{A}$ and a partial consequent m-set $\mset{S}$.}
+    % %     \Require{An antecedent m-set $\ga{A}$ and a partial consequent m-set $\ga{S}$.}
     % %     \Statex
-    % %     \Function{DEP}{$\mset{A}, \mset{S}$}
+    % %     \Function{DEP}{$\ga{A}, \ga{S}$}
     % %       % \Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
@@
 
+    \subsection{Marginal Symmetries}
+    As demonstrated by \cref{ex:symmetries}, permutations can be applied to inequalities themselves to generate new inequalities.
+To formalize this notion, let $\Perm{S}$ denote the \term{permutation group} acting on the set $S$ consisting of all bijective maps $\pi : S \to S$.
+    \[ \Perm{S} = \bc{\pi : S \to S} \eq \label{eq:permutation_group_def}\]
+    Together with the $\abs{S}\times\abs{S}$ permutation matrix $\PermM{\pi}$ for each permutation $\pi$,
+    \[ \forall i,j \in S : \quad {\PermM{\pi}}_{;i,j} \defined \begin{cases}
+        1 & \pi\br{i} = j\\
+        0 & \pi\br{i} \neq j\\
+    \end{cases} \]
+
+    \begin{definition}
+        A \term{marginal symmetry} of $\mscenario$ is a symmetry of the incidence matrix $M$ corresponding to a pair of permutations $\br{\pi_\mscenario \in \Perm{\Events{\mscenario}}, \pi_\jointvar\in \Perm{\Events{\jointvar}}}$ such that $M$ is invariant under permutation.
+        \[ \PermM{\pi_\mscenario} \tcdot M \tcdot \PermM{\pi_\jointvar} = M \]
+    \end{definition}
+
+    Identifying the set of all marginal symmetries for a given marginal model is very important; it allows one to generate new inequalities from known ones.
+
+    \begin{theorem}
+        \label{thm:inequalities_generated_symmetries}
+        For each $\s{NC}$-inequality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ and marginal symmetry $\br{\pi_{\mscenario}, \pi_{\jointvar}}$, the inequality $\pi_{\mscenario}\bs{I_{\mscenario}}$ defined by,
+        \[ \pi_{\mscenario}\bs{I_{\mscenario}} \defined \bc{\pi^{-1}_{\mscenario}\bs{\ga} \tcdot \probvec^{\mscenario} \geq 0} \eq \label{eq:thm:inequalities_generated_symmetries}\]
+        is also a valid $\s{NC}$-inequality.
+    \end{theorem}
+    \begin{proof}
+        Since $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ is a $\s{NC}$-inequality, then by \cref{thm:definite_extension_main_thm}, $\ga \tcdot M = \Ga \succeq 0$.
+Also note that $\PermM{\pi_{\jointvar}}$ is invertible with $\PermM{\pi_{\jointvar}}^{-1} = \PermM{\pi^{-1}_{\jointvar}}$.
+Therefore,
+        \[ \Ga\tcdot\PermM{\pi_{\jointvar}}^{-1} = \ga \tcdot M \tcdot \PermM{\pi_{\jointvar}}^{-1} = \ga\tcdot \PermM{\pi_{\mscenario}}\tcdot M \]
+        But $\Ga \succeq 0 \implies \Ga\tcdot\PermM{\pi_{\jointvar}}^{-1} \succeq 0$. Thus,
+        \[ \ga\tcdot\PermM{\pi_{\mscenario}}\tcdot M \succeq 0 \eq \label{eq:thm:inequalities_generated_symmetries_step}\]
+        Interpreting $\ga\tcdot\PermM{\pi_{\mscenario}}$ as a multi-set for $\mscenario$,
+        \[ \forall m \in \Events{\mscenario} : \br{\ga\tcdot\PermM{\pi_{\mscenario}}}_m = \ga_{\pi^{-1}_{\mscenario}\bs{m}} \defined \pi^{-1}_{\mscenario}\bs{\ga}_m \]
+        Therefore \cref{eq:thm:inequalities_generated_symmetries_step} shows that $\pi^{-1}_{\mscenario}\bs{\ga}$ has a positive semi-definite extension and thus \cref{thm:definite_extension_main_thm} proves that \cref{eq:thm:inequalities_generated_symmetries} is also a valid $\s{NC}$-inequality.
+    \end{proof}
+    \begin{remark}
+        There are two equivalent interpretations for the permuted inequality $\pi_{\mscenario}\bs{I_{\mscenario}}$ of \cref{thm:inequalities_generated_symmetries}. Notice,
+        \[ \pi^{-1}_{\mscenario}\bs{\ga} \tcdot \probvec^{\mscenario} = \ga \tcdot \La_{\pi_{\mscenario}} \tcdot \probvec^{\mscenario} = \ga \tcdot \pi_{\mscenario}\bs{\probvec}^{\mscenario} \]
+        Which means one can either think of $\pi_{\mscenario}\bs{I_{\mscenario}}$ as being $I_{\mscenario}$ with the coefficients rearranged, or with the probabilistic assignments rearranged.
+    \end{remark}
+
+    \todo[TC]{Discuss the importance of symmetries to restrict branching in DEP}
+
+    Diagrammatically, for each marginal event $m \in \Events{\mscenario}$ and joint event $j \in \Events{\jointvar}$, the notion of extendability is preserved by $\br{\pi_\mscenario, \pi_\jointvar}$.
+    \begin{center}
+        \begin{tikzpicture}
+            \newcommand{\symmetryspace}{1.5};
+            \draw (0, \symmetryspace) node[](m){$m$};
+            \draw (\symmetryspace, \symmetryspace) node[](j){$j$};
+            \draw (0, 0) node[](pm){$\pi_{\mscenario}\bs{m}$};
+            \draw (\symmetryspace, 0) node[](pj){$\pi_{\jointvar}\bs{j}$};
+
+            \draw[->] (m) -- node[left]{$\pi_\mscenario$}(pm);
+            \draw[->] (j) -- node[right]{$\pi_\jointvar$}(pj);
+            \draw[-<] (m) -- (j);
+            \draw[-<] (pm) -- (pj);
+        \end{tikzpicture}
+    \end{center}
+    Fortunately, every incidence matrix $M$ has a useful \term{uniqueness property}: there are no duplicated columns or rows in $M$.
+This means that in every marginal symmetry $\br{\pi_\mscenario, \pi_\jointvar}$, $\pi_\jointvar$ is uniquely determined by $\pi_\mscenario$ and vice versa.
+Therefore we restrict our attention and discussions to row permutations $\pi_\mscenario$, with column permutations being in one-to-one correspondence.
+Henceforth we will denote to the most general marginal symmetry using $\pi$ and take it to mean a permutation over marginal events.
+\\
+
     \subsection{Outcome Symmetry}
     \label{sec:outome_label_symmetry}
-    As demonstrated by \cref{ex:symmetries}, permutations of outcomes can be applied to inequalities themselves to generate new inequalities.
-To formalize this notion, let $\Perm{S}$ denote the \term{permutation group} acting on the set $S$ consisting of all bijective maps $s : S \to S$.
-    \[ \Perm{S} = \bc{s : S \to S} \eq \label{eq:permutation_group_def}\]
-    \begin{definition}
-        The \term{outcome symmetry group} $\go$ for the set of joint variables $\jointvar = \bc{v_1, \ldots, v_n}$ is the direct product of permutations over the outcome labels for each variable $v \in \jointvar$,
+    \begin{definition}
+        The \term{outcome symmetry group} $\go$ for the set of joint variables $\jointvar = \bc{v_1, \ldots, v_n}$ is the direct product of permutations over the outcomes for each variable $v \in \jointvar$,
         \[ \go \defined \Perm{O_{v_1}} \times \cdots \times \Perm{O_{v_n}} = \prod_{v \in \jointvar} \Perm{O_{v}} \]
-        The action of $\geo \in \go$ on any section $s \in \Sect{V}$ (denoted $\geo\bs{s}$) where $V \subseteq \jointvar$ is defined as,
+        The action of $\geo \in \go$ on any event $s \in \Events{V}$ (denoted $\geo\bs{s}$) where $V \subseteq \jointvar$ is defined as,
         \[ \forall v \in \Dom{s} : \br{\geo\bs{s}}\br{v} \defined \geo\bs{s\br{v}} \eq \label{eq:act_on_outcome_label}\]
     \end{definition}
-    \begin{lemma}
-        \label{lem:extendable_invariance_acto}
-        If a marginal section $m \in \Sect{\mscenario}$ is extendable to the joint section $j \in \Sect{J}$, then for any outcome permutation $\geo \in \go$, $\geo\bs{m}$ is extendable to $\geo\bs{j}$.
+    \begin{theorem}
+        \label{thm:extendable_invariance_acto}
+        If a marginal event $m \in \Events{\mscenario}$ is extendable to the joint event $j \in \Events{J}$, then for any outcome permutation $\geo \in \go$, $\geo\bs{m}$ is extendable to $\geo\bs{j}$.
         \[ m \ext j \iff \geo\bs{m} \ext \geo\bs{j} \eq \label{eq:extendable_invariance_acto}\]
-    \end{lemma}
+    \end{theorem}
     \begin{proof}
@@
         \[ m \ext j \iff \forall v \in \Dom{m} : j\br{v} = m\br{v} \]
-        Every label permutation $\geo \in \go$ leaves the outcome domain invariant $\Dom{m} = \Dom{\geo\bs{m}}$. Thus by \cref{eq:act_on_outcome_label},
+        Every outcome permutation $\geo \in \go$ leaves the domain of the event invariant $\Dom{m} = \Dom{\geo\bs{m}}$. Thus by \cref{eq:act_on_outcome_label},
         \begin{align*}
@@
         \label{coll:incidence_invariance}
-        Let $M$ be the incidence matrix for a marginal scenario $\mscenario$ and $\geo \in \go$ be a label permutation of the joint random variables $\jointvar$.
-By \cref{lem:extendable_invariance_acto}, the action of $\geo$ on $M$ leaves $M$ invariant ($\geo\bs{M} = M$),
+        Let $M$ be the incidence matrix for a marginal scenario $\mscenario$ and $\geo \in \go$ be an outcome permutation of the joint random variables $\jointvar$.
+By \cref{thm:extendable_invariance_acto}, the action of $\geo$ on $M$ leaves $M$ invariant ($\geo\bs{M} = M$),
         \[ \geo\bs{M}_{m,j} \defined M_{\geo\bs{m},\geo\bs{j}} = \de_{\geo\bs{m} \ext \geo\bs{j}} = \de_{m \ext j} = M_{m,j} \eq \label{eq:incidence_invariance}\]
     \end{corollary}
-    \begin{theorem}
-        \label{thm:inequalities_outcome_label_generation}
-        For each $\s{NC}$-inequality $I_{\mscenario}$ and outcome permutation $\geo \in \go$, the inequality defined by $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$ is also a valid $\s{NC}$-inequality.
-    \end{theorem}
-    \begin{proof}
-        First let $I_{\mscenario} = \bc{\ga \cdot \probvec^{\mscenario} \geq 0}$ be a $\s{NC}$-inequality for the marginal scenario $\mscenario$ where $\ga$ is the multi-set associated with $I_{\mscenario}$.
-Furthermore let $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario} = \bc{\ga \cdot \geo\bs{\probvec}^{\mscenario} \geq 0}$ be the inequality obtained after permuting $\probvec^{\mscenario}$ defined as,
-        \[ \forall m \in \Sect{\mscenario} : \geo\bs{\probvec}^{\mscenario}_m \defined \probvec^{\mscenario}_{\geo\bs{m}} \]
-        It should be clear to see that $\ga \cdot \geo\bs{\probvec}^{\mscenario}$ can be rewritten as,
-        \[ \ga \cdot \geo\bs{\probvec}^{\mscenario} = \sum_{m \in \Sect{\mscenario}} \ga_{m} \probvec^{\mscenario}_{\geo\bs{m}} = \sum_{m' \in \Sect{\mscenario}} \ga_{\geo^{-1}\bs{m'}} \probvec^{\mscenario}_{m'} = \geo^{-1}\bs{\ga} \cdot \probvec^{\mscenario}\]
-        Therefore the permuted inequality is equivalent to,
-        \[ \geo\bs{I}_{\mscenario} = \bc{\geo^{-1}\bs{\ga} \cdot \probvec^{\mscenario} \geq 0} \]
-        All that remains to be proven is that $\geo^{-1}\bs{\ga}$ forms a valid certificate for the incidence matrix $M$. Since $\geo \in \go$, \cref{coll:incidence_invariance} gives,
-        \[ \br{\geo^{-1}\bs{\ga} \cdot M}_j = \sum_{m \in \Sect{\mscenario}} \geo^{-1}\bs{\ga}_m \de_{m\ext j} = \sum_{m \in \Sect{\mscenario}} \bs{\ga}_m \de_{\geo\bs{m}\ext j} = \sum_{m \in \Sect{\mscenario}} \bs{\ga}_m \de_{m\ext \geo^{-1}\bs{j}} = \br{\ga \cdot M}_{\geo^{-1}\bs{j}} \]
-        But since $I_{\mscenario}$ is a $\s{NC}$-inequality, $\ga \cdot M \succeq 0$ and thus $\geo^{-1}\bs{\ga} \cdot M \succeq 0$ making $\geo\bs{I}_{\mscenario}$ a $\s{NC}$-inequality as well.
-    \end{proof}
-
     \subsection{Variable Symmetry}
@@
         \[ \Phi \defined \bc{\gep \in \Perm{\jointvar} \mid \forall V \in \mscenario : \gep\bs{V} \in \mscenario} \]
-        The action of $\gep \in \gp$ on any outcome $f \in \Sect{V}$ (denoted $\geo\bs{f}$) is defined as,
+        The action of $\gep \in \gp$ on any outcome $f \in \Events{V}$ (denoted $\geo\bs{f}$) is defined as,
         \[ \forall v \in \Dom{\gep\bs{f}} : \br{\gep\bs{f}}\br{v} \defined f\br{\gep^{-1}\bs{v}} \eq \label{eq:act_on_variable}\]
-    \end{definition}
-
-    \subsection{Marginal Symmetries}
-
-    \begin{definition}
-        A \term{marginal symmetry} of $\mscenario$ is a symmetry of the incidence matrix $M$ corresponding to a tuple $\br{\pi_\mscenario, \pi_\jointvar}$ such that $\pi_X \in \Perm{\Sect{X}}$ for $X= \mscenario, \jointvar$ such that the following diagram holds for all $m \in \Sect{\mscenario}$ and $j \in \Sect{\jointvar}$.
-        \begin{center}
-            \begin{tikzpicture}
-                \newcommand{\symmetryspace}{1.5};
-                \draw (0, \symmetryspace) node[](m){$m$};
-                \draw (\symmetryspace, \symmetryspace) node[](j){$j$};
-                \draw (0, 0) node[](pm){$\pi_{\mscenario}\bs{m}$};
-                \draw (\symmetryspace, 0) node[](pj){$\pi_{\jointvar}\bs{j}$};
-
-                \draw[->] (m) -- node[left]{$\pi_\mscenario$}(pm);
-                \draw[->] (j) -- node[right]{$\pi_\jointvar$}(pj);
-                \draw[-<] (m) -- (j);
-                \draw[-<] (pm) -- (pj);
-            \end{tikzpicture}
-        \end{center}
     \end{definition}
@@
     \begin{definition}
-        Let $\jointvar = \br{v_1, \ldots v_k}$ be a collection of random variables along with a specific outcome $m \in \Sect{V}$ where $V \subseteq \jointvar$.
-The action of $\gep \in \Perm{\jointvar}$ on $m$ is a new outcome $\gep\bs{m} \in \Sect{\gep\bs{V}}$ over $\gep\bs{V} \subseteq \jointvar$ defined as follows,
+        Let $\jointvar = \br{v_1, \ldots v_k}$ be a collection of random variables along with a specific outcome $m \in \Events{V}$ where $V \subseteq \jointvar$.
+The action of $\gep \in \Perm{\jointvar}$ on $m$ is a new outcome $\gep\bs{m} \in \Events{\gep\bs{V}}$ over $\gep\bs{V} \subseteq \jointvar$ defined as follows,
         \[ \forall v \in V : \br{\gep\bs{m}}\br{\gep\bs{v}} \defined m \br{v} \]
@@
     \begin{example}
-        Consider the outcome $m = \bc{A \mapsto 0, B \mapsto 1, C \mapsto 2} \in \Sect{\bc{A,B,C}}$ where all variables have $4$ possible outcomes $O_A = O_B = O_C = \bc{0,1,2,3}$ and the permutation $\gep = \bc{A \to D, B \to C, C \to B, D \to A}$.
+        Consider the outcome $m = \bc{A \mapsto 0, B \mapsto 1, C \mapsto 2} \in \Events{\bc{A,B,C}}$ where all variables have $4$ possible outcomes $O_A = O_B = O_C = \bc{0,1,2,3}$ and the permutation $\gep = \bc{A \to D, B \to C, C \to B, D \to A}$.
         The \textit{action} of $\gep$ on $m$ is as follows,
@@
         \end{align*}
-        Evidently, $\gep\bs{m} \in \Sect{\bc{B, C, D}}$.
+        Evidently, $\gep\bs{m} \in \Events{\bc{B, C, D}}$.
     \end{example}
 
-    Through repeated action of $\gep \in \gp$ on marginal outcomes $m \in \Sect{\mscenario}$ and joint outcomes $j \in \Sect{\jointvar}$, one can define group orbits of $\gp$ in $\Sect{\mscenario}$ and $\Sect{\jointvar}$.
+    Through repeated action of $\gep \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define group orbits of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$.
     \begin{align*}
@@
         The \term{product distribution} of two disjoint probability distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as $\prob[V] \times \prob[W]$.
-        \[ \forall f \in \Sect{V \cup W} : \br{\prob[V] \times \prob[W]}\br{f} \defined \prob[V][f|_{V}]\cdot\prob[W][f|_{W}] \]
+        \[ \forall f \in \Events{V \cup W} : \br{\prob[V] \times \prob[W]}\br{f} \defined \prob[V][f|_{V}]\tcdot\prob[W][f|_{W}] \]
         A product distribution of $k$ mutually disjoint distributions is defined as,
@@
         The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
-        \[ \forall f \in \Sect{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
+        \[ \forall f \in \Events{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
     \end{definition}
@@
     Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} suggest the parameterization of the unitary group $\mathcal{U}\br{d}$ using a $d\times d$-matrix of real-valued parameters $\lambda_{n, m}$,
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
+    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \tcdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
     Where $P_l$ are one-dimensional projective operators,
@@
     By combining the optimizations of \cref{eq:unitary_RP,eq:unitary_R,eq:unitary_GP} together we arrive at an equivalent form for \cref{eq:spengler_unitary} that is computational more efficient.
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}}} \cdot \bs{\prod_{l=1}^{d} GP_l} \eq \label{eq:fast_spengler_unitary} \]
+    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}}} \tcdot \bs{\prod_{l=1}^{d} GP_l} \eq \label{eq:fast_spengler_unitary} \]
     In quantum mechanics, the global phase of a state $\ket{\psi} \in \Hilb^n$ is a \textit{redundant} parameter.

### 2016-11-10 documents/Archive/main.tex
Started work on slides for Brazil

--- 2016-10-31 document/main.tex
@@
 
-% \usepackage{silence}
-% \WarningFilter{revtex4-1}{Repair the float}
-% \usepackage{algorithm}
-% \usepackage[noend]{algpseudocode}
 % === All of the Packages I use frequently ===
-\usepackage{../packages/shared}
-
-% === Drafting Declarations ===
-\draftprofile[TC Fraser]{TC}{Red}
-\draftprofile[Elie Wolfe]{E}{Green}
-
-% === Numbering For amsthm theorem environments ===
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-
-\theoremstyle{remark}
-\newtheorem{remark}[theorem]{Remark}
-
-% === To allow for labeling of rows and columns of a matrix ===
-%\usepackage{kbordermatrix}
-\usepackage{../packages/kbordermatrix}
-\renewcommand{\kbldelim}{(} % Left delimiter
-\renewcommand{\kbrdelim}{)} % Right delimiter
-
-% === Commonly re-occurring symbols ===
-\newcommand{\hgraph}{\mathcal{H}}
-\newcommand{\graph}{\mathcal{G}}
-\newcommand{\nodes}{\mathcal{N}}
-\newcommand{\weights}{\mathcal{W}}
-\newcommand{\edges}{\mathcal{E}}
-\newcommand{\trans}{\mathcal{T}}
-\newcommand{\ind}{S}
-\newcommand{\inhibit}{\mathcal{I}}
-\newcommand{\netperm}{\Pi}
-\newcommand{\Hilb}{\mathcal{H}}
-\newcommand{\ancestralindep}{\perp}
-\newcommand{\valprod}{\times}
-\newcommand{\bigvalprod}{\prod}
-\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
-\newcommand{\ext}{\mathrel{\Yleft}}
-\newcommand{\res}{\mathrel{\Yright}}
-\newcommand{\gep}{\varphi}
-\newcommand{\gp}{\Phi}
-\newcommand{\geo}{\omega}
-\newcommand{\go}{\Omega}
-\newcommand{\mscenario}{\mathcal{M}}
-\newcommand{\jointvar}{\mathcal{J}}
-% \newcommand{\mset}{\gamma}
-% \newcommand{\extmset}{\Gamma}
-\newcommand{\supp}[1]{\si\br{#1}}
-\newcommand{\kone}{\mathbf{1}}
-\newcommand{\kzer}{\textcolor{gray}{0}}
-
-% \newcommand{\mext}[1]{E_{#1}}
-% \newcommand{\mul}[1]{\Gamma_{#1}}
-\newcommand{\isext}[2]{\delta_{#1 \ext #2}}
-\newcommand{\ts}{{\graph}}
-% When I introduce a new term or definition
-\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}
-\newcommand{\tcdot}{} % Tentative cdot, not sure if I want to keep dots
-
-% === Mathematical operators that are denoted with words ===
-\newcommand{\setoperator}[1]{%
-\expandafter\DeclareDocumentCommand\csname#1\endcsname{O{} O{} m}{{\mathsf{#1}_{##1}^{##2}}\br{##3}}%
-}
-
-\setoperator{Pa} % Parents of a node
-\setoperator{Ch} % Children of a node
-\setoperator{An} % Ancestry of a node
-\setoperator{Sub} % subgraph
-\setoperator{AnSub} % Ancestral subgraph
-\setoperator{Ext} % Extension of outcomes
-\setoperator{Com} % Compatible equivalence relation
-\setoperator{Nec} % Necessary nodes
-\setoperator{UnNec} % Unnecessary nodes
-\setoperator{Inj} % injectable sets
-\setoperator{ImInj} % images of the injectable sets
-\setoperator{PreInj} % Pre-injectable sets
-\setoperator{ImPreInj} % images of the Pre-injectable sets
-\setoperator{Aut} % graph automorphism
-\setoperator{Orb} % Group Orbits
-\setoperator{Perm} % Permutation group
-\newcommand{\PermM}[1]{\La_{#1}} % Permutation matrix
-% \setoperator{Out} % Outcome space
-\newcommand{\Events}[1]{\s{E}\br{#1}} % Set of events
-\newcommand{\Dom}[1]{\s{D}\br{#1}} % Domian
-% \setoperator{Dom} % Domian
-% \setoperator{Dom} % Domian
-
-\newcommand{\outc}[1]{o\bs{#1}} % Fritz's BBTII notation for observed outcomes
-\DeclareDocumentCommand{\prob}{O{} O{}}{\ifthenelse{\equal{#1}{}}{P}{P_{#1}}\ifthenelse{\equal{#2}{}}{}{\br{#2}}} % probability distribution
-\DeclareDocumentCommand{\probvec}{O{} O{}}{\ifthenelse{\equal{#1}{}}{\mathcal{P}}{\mathcal{P}_{#1}}\ifthenelse{\equal{#2}{}}{}{\br{#2}}} % probability distribution vector
+\usepackage{../../packages/document_config}
+\usepackage{../../packages/shared}
+\usepackage{../../packages/misc_commands}
 
 % === Causal structure formatting for tikz ===
-\input{../figures/causal_structures/formatting}
+\input{../../figures/causal_structures/formatting}
 
@@
                 \centering
-                \scalebox{1.0}{\input{../figures/hypergraphs/minimal_example}}
+                \scalebox{1.0}{\input{../../figures/hypergraphs/minimal_example}}
                 \caption{An edge-weighted hypergraph $\hgraph_{\weights}$ corresponding to the antecedent set $\ga^{A}$ with $\ga^{A}_{m_3} = -1$ and $\ga^{A}_{m_8} = -2$.}
@@
             \centering
-            \scalebox{1.0}{\input{../figures/causal_structures/triangle_scenario}}
+            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
             \caption{The casual structure of the Triangle Scenario. Three variables $A,B,C$ are observable and illustrated as triangles, while $X, Y, Z$ are latent variables illustrated as circles.}
@@
             \centering
-            \scalebox{0.8}{\input{../figures/causal_structures/inflated_triangle_scenario}}
+            \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
             \caption{An inflated causal structure of the Triangle Scenario \cref{fig:triangle_scenario}.}
@@
             \centering
-            \includegraphics{../figures/CHSH_convex.pdf}
+            \includegraphics{../../figures/CHSH_convex.pdf}
             \caption{Convex optimizations against $I\tsb{CHSH}$ recover algebraic violation of $4$.}
@@
             \centering
-            \includegraphics{../figures/CHSH_quantum.pdf}
+            \includegraphics{../../figures/CHSH_quantum.pdf}
             \caption{Quantum optimizations against $I\tsb{CHSH}$ recover maximum violation of $2\sqrt{2}$.}
@@
         \centering
-        \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../figures/perm_mtrx.pdf}
+        \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
         \caption{The network permutation matrix $\netperm$ for $\br{\Hilb^2}^{\otimes 6}$ realized on the triangle scenario. Black represents a value of $1$ and $0$ otherwise.}
@@
 
-    \bibliography{references}
+    \bibliography{../references}
 \end{document}

### 2016-11-10 documents/BrazilSlides/slides.tex
Started work on slides for Brazil

\documentclass[
    hyperref={colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
    xcolor={dvipsnames},
]{beamer}

\setbeameroption{show notes}
\usefonttheme[onlymath]{serif}

\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}

% === Causal structure formatting for tikz ===
\input{../../figures/causal_structures/formatting}

\renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}

\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
\author[Fraser]{T.~C.~Fraser\inst{1}}
\institute[PI]
{
    \inst{1}%
    Perimeter Institute for Theoretical Physics\\
    Ontario, Canada
}
\date[QN 2016]{Quantum Networks, 2016}

\begin{document}

\frame{\titlepage}

\begin{frame}[allowframebreaks]
    \frametitle{References}
    \todo[TC]{Figure out how to get references at the end}
    \setbeamertemplate{bibliography item}{\insertbiblabel}
    \bibliographystyle{abbrv}
    \bibliography{../references}{}
\end{frame}

\begin{frame}
    \frametitle{Table of Contents}
\tableofcontents

\end{frame}

\section{Tools}

\begin{frame}
    \frametitle{Introduction}
    \note[item]{\todo[TC]{}}
\end{frame}

\begin{frame}
    \frametitle{Notation}
    \begin{itemize}
        \item Complete set of random variables are the \term{joint random variables}
        \[ \jointvar = \bc{v_1, \cdots, v_n} \]
        \item A subset of $V \subset \jointvar$ is a \term{marginal context}
        \item \term{Marginal scenario} $\mscenario$
        \[ \mscenario = \bc{V_1, \ldots, V_k \mid V_i \subset \jointvar} \quad \jointvar = {\bigcup}_{i} V_i  \]
        \item Marginal scenario forms a \textit{simplicial complex}
        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
        \item Restrict focus to \textit{maximal} marginal scenario where only the largest contexts are present
        \[ \forall V_i, V_j \in \mscenario : V_i \not \subset V_j \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Notation Cont'd}
    \begin{itemize}
        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
    \end{itemize}
    \todo[TC]{Insert generic causal structure}
\end{frame}

\begin{frame}
    \frametitle{Graph Theory [Optional Slide]}
    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
    \begin{itemize}
        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
    \end{itemize}
    Notation extends to sets of nodes $N \subseteq \nodes$,
    \begin{itemize}
        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
    \end{itemize}
    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
\end{frame}

\begin{frame}
    \frametitle{Causal Compatibility}
    \textbf{Question:} Is a marginal model $\prob^{\mscenario}$ \term{compatible} with a causal structure $\graph$?\\
    \[ \mscenario = \bc{V_1, \ldots, V_k \mid V_i \subset \nodes_O} \]
    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
    \begin{enumerate}
        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
    \end{enumerate}

    A \term{casual compatibility inequality} is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
    \note<1>[item]{}
\end{frame}

\begin{frame}
    \frametitle{Triangle Scenario}
    \begin{columns}
        \column{0.4\linewidth}
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
        \column{0.6\linewidth}
            \begin{itemize}
                \item Three parties $\nodes_O = \bc{A, B, C}$
                \item Pair-wise sharing three latent variables $\nodes_L = \bc{X, Y, Z}$
                \item \todo[TC]{Inject info about existing work}
                \item There exists \textit{quantum-accessible} distributions $\prob[ABC]$ that are \textit{incompatible} with the triangle scenario
            \end{itemize}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution}
    The \term{Fritz Distribution $\prob[F]$}:
    \begin{itemize}
        \item three-party $\prob[F] = \prob[ABC]$
        \item each party has four outcomes
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Inflation Technique}
    \begin{itemize}
        \item Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
    \end{itemize}
    \begin{definition}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
        And '$\sim$' is a \term{copy-index} equivalence relation
        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
    \end{definition}

\end{frame}

\begin{frame}
    \frametitle{Inflations of the Triangle Scenario}
    \begin{center}
    \begin{tabular}{cc}
        %\hline
        \scalebox{0.5}{\input{../../figures/causal_structures/triangle_scenario}}
        &
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral}}
        \\
        %\hline
        The Triangle Scenario
        &
        Spiral Inflation \\
        %\hline
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
        &
        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
        \\
        %\hline
        Cut Inflation
        &
        Large Inflation \\
        %\hline
    \end{tabular}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma}
    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
    \begin{enumerate}
        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
        \item Construct \term{inflated causal parameters}
        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma Cont'd}
    \begin{itemize}
        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $N \sim N'$
        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
        \begin{align*}
            \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
            \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'} \\
        \end{align*}
        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $N \sim N'$
        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $N \sim N'$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma Cont'd}
    \begin{lemma}
        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
    \end{lemma}
    \begin{corollary}
        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
    \end{corollary}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma Cont'd}
    \begin{lemma}
        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
    \end{lemma}
    \begin{corollary}
        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
    \end{corollary}
\end{frame}

\begin{frame}
    \frametitle{Inflation Pipeline}
    \note[item]{Walk through how the inflation pipeline works}
\end{frame}

\begin{frame}
    \frametitle{Outcomes and Events}
    \begin{itemize}
        \item Set of \term{outcomes} $O_v$ for each variable $v$
        \item Set of \term{events} for a set of variables $V$
        \[ \Events{V} \defined \bc{s: V \to O_V \mid \forall v \in V, s\br{v} \in O_v} \]
    \end{itemize}
    \begin{definition}
        The set of events over the joint variables $\Events{\jointvar}$ are termed the \term{joint events}.
    \end{definition}
    \begin{definition}
        The set of events over the marginal contexts are the \term{marginal events}
        \[ \Events{\mscenario} \defined \coprod_{V \in \mscenario} \Events{V} \]
    \end{definition}
\end{frame}

\begin{frame}
    \frametitle{Incidence Matrix}
    \begin{itemize}
        \item Incidence matrix $M$ is a bit-wise matrix
        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
        \item Column-indexed by joint events $j \in \Events{\jointvar}$
        \[ M_{m,j} = \begin{cases}
            1 & m \text{ compatible with } j \\
            0 & \text{otherwise}
        \end{cases} \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Application to Large Inflation}
    \begin{columns}
        \column{0.6\linewidth}
            \begin{itemize}
                \item Tackling Large inflation
                \item 12 pre-injectable sets (to follow)
            \end{itemize}
        \column{0.4\linewidth}
            \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Large Inflation Pre-injectable Sets}
    \begin{equation*}
        \begin{gathered}
            \textbf{Maximal Pre-injectable Sets} \\
            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
            \bc{A_1, B_3, C_4} \\
            \bc{A_1, B_4, C_2} \\
            \bc{A_2, B_1, C_4} \\
            \bc{A_2, B_2, C_2} \\
            \bc{A_3, B_3, C_3} \\
            \bc{A_3, B_4, C_1} \\
            \bc{A_4, B_1, C_3} \\
            \bc{A_4, B_2, C_1}
        \end{gathered}
        \qquad
        \begin{gathered}
            \textbf{Ancestral Independences} \\
            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
        \end{gathered}
    \end{equation*}
\end{frame}

\begin{frame}
    \frametitle{Large Inflation Incidence}
    \begin{itemize}
        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
        \item Inequalities Violated by Fritz distribution are inherently $4$-outcome
        \item Incidence matrix $M$ is very large $\sim 2.25 \textsf{Gb}$
        \[ \# \text{Columns} = \prod_{v \in \jointvar} O_{v} = 4^{12} = 16,777,216 \]
        \[ \# \text{Rows} = \sum_{V \in \mscenario} \prod_{v \in V} O_{v} = 4\times 4^{6} + 8 \times 4^{3} = 16,896 \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Inequalities Found}
\end{frame}

\section{Symmetries}
\begin{frame}
    \frametitle{Causal Symmetry}
\end{frame}

\begin{frame}
    \frametitle{Symmetric Incidence}
\end{frame}

\begin{frame}
    \frametitle{Symmetric Inequalities}
\end{frame}

\section{Searching for New Distributions}
\begin{frame}
    \frametitle{Numerical Optimization}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing Quantum Distributions}
    For our purposes, we need to parameterize the space of quantum-accessible distributions that are \textit{realized} on the Triangle Scenario
    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing Unitary Group}
    \begin{itemize}
        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} demonstrate a parameterization of $\s{U}\br{d}$ where the parameters are organized in a $d \times d$-matrix of real values $\la_{n,m}$
        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n} RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}} \]
        \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
        \item Relative Phase Terms: $RP_{m,n} = \exp\br{i P_n \lambda_{n,m}}$
        \item Rotation Terms: $R_{n,m} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
        \item Projection Operators: $P_l = \ket{l}\bra{l}$
        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing Unitary Group Cont'd}
    \begin{itemize}
        \item Each parameter $\la_{n,m}$ has physical interpretation
        \item Degeneracies are easily eliminated such as global phase
        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = 1 \]
        \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
        \item Computationally efficient
        \begin{alignat*}{2}
            GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
            RP_{m,n} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
            R_{n,m} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
            & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\
        \end{alignat*}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing States}
    \begin{itemize}
        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite qubit state acting on $\Hilb^{d/2} \otimes \Hilb^{d/2}$
        \item $d \times d$ positive semi-definite (PSD) hermitian matrices with unitary trace
        \item \term{Cholesky Parametrization} allows one to write any hermitian PSD as $\rho = T^{\dagger} T$
        \item For $d = 4$:
        \[ T = \begin{bmatrix}\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}\end{bmatrix} \]
        \item $d^2$ real-valued parameters
        \item Normalized $\rho = {T^{\dagger}T}/{\Tr\br{T^{\dagger} T}}$ adds degeneracy
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing States Cont'd}
    \begin{itemize}
        \item \term{SHH parameterization} \cite{Spengler_2010_Unitary} exploits spectral decomposition; for rank $k \leq d$ density matrix
        \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i} \bra{\psi_i} \qquad p_i \geq 0, \sum_i p_i = 1 \]
        \item Orthonormal $k$-element sub-basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into computational basis $\bc{\ket{i}}$ by unitary $U \in \s{U}\br{d}$ such that $\ket{\psi_i} = U \ket{i}$
        \item Freedom to choice $k$
        \item Parameterize $\rho$ through $\bc{p_i}$ and $\ti{U}_{k}$
        \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
        \item $d^2 - \br{d-k}^2 - k + \br{k-1} = 2dk -k^2 -1$ real-valued parameters (no-degeneracy)
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing POVMs}
    \begin{itemize}
        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
        \item $n$-outcome measurement
        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
        \item Warrants consideration of \term{projective-valued measures (PVMs)} (for $n = d$ this is without loss of generality)
    \end{itemize}
    \note<1>[item]{Naimark's Dilation Theorem}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing PVMs}
    \begin{itemize}
        \item Each party $\br{A, B, C}$ is assigned $n$-outcome $\br{M_A, M_B, M_C}$ such that,
        \[ M_{\chi,i}M_{\chi,j} = \de_{ij} M_{\chi, i} \quad M_{\chi, i} = \ket{m_{\chi,i}}\bra{m_{\chi,i}} \]
        \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
        \item Use unitary transformation again
        \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $2dn -n^2 -1$ real-valued parameters\
        \item PVMs are computationally more efficient
    \end{itemize}
    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
\end{frame}

\begin{frame}
    \frametitle{Network Permutation Matrix}
    \begin{columns}
        \column{0.6\linewidth}
        \begin{itemize}
            \item States and measurements in the Triangle Scenario are not aligned
            \item Without $\netperm$, $\prob[ABC]$ would be separable
            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
            \item $\netperm$ is a $2^6 \times 2^6$ matrix
        \end{itemize}
        \column{0.4\linewidth}
            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
    \end{columns}
    \begin{itemize}
        \item Shifts one qubit to the left
        \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
    \end{itemize}

\end{frame}

\begin{frame}
    \frametitle{Maximally Violating Distributions}
\end{frame}

\begin{frame}
    \frametitle{Non-Trivial Inequalities For Large Inflation}
\end{frame}

\begin{frame}
    \frametitle{Conclusions}
\end{frame}

\begin{frame}
    \frametitle{Post-doc Opportunities At Perimeter}
\end{frame}

\end{document}

### 2016-11-10 documents/DefiniteExtensions/dep.tex
Started work on slides for Brazil

--- 2016-11-10 documents/Archive/main.tex
@@
 
-% === Causal structure formatting for tikz ===
-\input{../../figures/causal_structures/formatting}
-
 \begin{document}
-    \title{Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario}
+    \title{The Definite Extension Procedure for Large-Scale Marginal Satisfiability}
     \author{Thomas C. Fraser}
@@
     \begin{abstract}
-        Quantum correlations are often incompatible with a classical assumption of causal structure.
-This nonclassicality is often known as quantum nonlocality, and it is witnessed through the violation of causal compatability inequalities, such as Bell inequalities.
-Such inequalities were recently derived for the Triangle scenario [arXiv:1609.00672], begging the question: can these inequalities be violated by quantum correlations?
-Here we answer this affirmatively, and discuss specific Triangle scenario inequalities and quantum configurations which manifest nonclassical correlations.
-We also report the development of novel computational techniques suitable for large causal structures with numerous outcomes.
-Numerical optimzations reveal quantum resources potentially qualitatively different from those known previously.
+        \todo[TC]{Write an abstract}
     \end{abstract}
@@
 
-    \section{Introduction}
-    \todo[TC]{Mention Bell's work} \\
-
-    \todo[TC]{Violations of inequalities correspond to resources} \\
-
-    \todo[TC]{Finding inequalities is hard} \\
-
-    \todo[TC]{Causal inference is a great lens to answer these questions} \\
-
-    \todo[TC]{Demonstrated the usefulness of the inflation technique} \\
-
-    \todo[TC]{Definite Extension procedure} \\
-
-    \todo[TC]{Optimizations against inequalities} \\
-
-    \section{Compatibility, Contextuality and the Marginal Problem}
-    \label{sec:comp_con_mp}
-
-    \subsection{Preliminary Notions}
-    \label{eq:comp_con_mp_notions}
-    A reoccurring motif of these discussions will be a set of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_k]}$.
-In agreement with~\cite{Fritz_2011} we adopt the following definitions and notation.
-
-    \begin{definition}
-        \label{def:marginal_model}
-        A set of random variables $\jointvar = \bc{v_1, \ldots, v_n}$ is referred to as the \term{joint random variables} when denoted with a $\jointvar$.
-A subset of joint variables $V \subset \jointvar$ is called \term{marginal context}.
-A collection of marginal contexts is called the \term{marginal scenario}\footnote{Rigorously speaking as defined by~\cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that $V' \in \mscenario$ whenever $V' \subseteq V \in \mscenario$.
-Throughout this document, we only consider the \textit{maximal marginal scenario}; restricting our focus to the largest contexts in the marginal scenario $\forall i,j \in 1, \ldots, k: V_i \not \subseteq V_j$.} and is denoted $\mscenario$\footnote{It is also assumed that the marginal scenario covers the joint variables $\jointvar = \bigcup_{i = 1}^{k} V_i$.}.
-        \[ \mscenario \defined \bc{V_1, \ldots, V_k \mid V_i \subseteq \jointvar} \]
-        Additionally, the set of probability distributions $\bc{\prob[V_1], \ldots, \prob[V_k]}$ over the marginal scenario is called a \term{marginal model} is compactly denoted $\prob^{\mscenario}$.
-    \end{definition}
-    A specific marginal model $\prob^{\mscenario}$ for a marginal scenario $\mscenario$ abstractly represents a set of measurements or observations made on a physical system.
-Associated with the physical system are physical models or causal structures.
-
-    \begin{definition}
-        A \term{causal structure} is a directed acyclic graph (DAG) $\graph = \br{\nodes, \edges}$ with the extra distinction between two classes of nodes: the \term{latent nodes} $\nodes_L$ and \term{observed nodes} $\nodes_O$.
-    \end{definition}
-    The latent nodes of a causal structure correspond aim to represent completely general hidden variables that are hidden by some fundamental process or cannot be measured due to other limitations.
-The observed nodes represent random variables that are measurable and in practice will be observed as a collection of marginal contexts $\mscenario$.
-Any observation over this particular marginal scenario is expressible as a marginal model $\prob^{\mscenario}$.
-The field of causal inference aims to answer the looming question: \text{Is the observed marginal model compatible with the hypothesized causal structure?} \\
-
-    In order to determine if a given marginal model $\prob^{\mscenario}$ is compatible with a causal structure $\graph$, a formal notion of \textit{compatibility} is warranted; first for a single marginal distribution $\prob[V]$ and then for a complete marginal model $\prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]}$.
-
-    \begin{definition}
-        A set of \term{causal parameters} for a particular causal structure $\graph$ is the specification of a conditional distribution for every node $n \in \nodes$ given its parents in $\graph$.
-        \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \eq \label{eq:def:casual_param}\]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:compatible}
-        A marginal distribution $\prob[V]$ is \term{compatible} with a causal structure $\graph$ if there exists a \textit{choice} of causal parameters such that $\prob[V]$ can be \textit{recovered} from the following series of operations:
-        \begin{enumerate}
-            \item Obtain a joint probability distribution over \textit{all} nodes of of the causal structure using the chosen casual parameters: $\prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}]$.
-            \item Marginalize over the latent nodes of $\graph$: $\prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes]$.
-            \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$: $\prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O]$
-        \end{enumerate}
-        If it is not possible for $\prob[V]$ to be recovered for \textit{any} choice of causal parameters, then $\prob[V]$ is \term{incompatible}.
-To generalize, a marginal model $\prob^{\mscenario}$ is compatible with $\graph$ if each distribution $\prob[V] \in \prob^{\mscenario}$ can be made compatible by the \textit{same} choice of causal parameters; otherwise it is incompatible.
-    \end{definition}
-
-    There are two reasons why a given marginal model $\prob^{\mscenario}$ would be deemed incompatible.
-One possibility is that the marginal model $\prob^{\mscenario}$ does not admit a joint distribution $\prob[\jointvar]$ such that it is impossible for requirement 3 of \cref{def:compatible} to hold\footnote{It is typical for $\nodes_O = \jointvar$.
-At the very least, it is demanded that $\jointvar \subseteq \nodes_O$.}.
-Alternatively, it could be possible that a joint distribution $\prob[\jointvar]$ exists but can not factor into causal parameters as per requirement 1 of \cref{def:compatible}.
-The former point-of-failure, namely the non-admission of a joint distribution, will be principle focus of this paper.
-Colloquially, the existence (or non-existence) of a joint distribution is referred to as \textit{the marginal problem}.
-
-    \begin{definition}
-        \label{def:marginal_problem}
-        \term{The Marginal Problem:} Given a marginal model $\prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]}$ marginal to the joint variables $\jointvar = \bigcup_{i} V_i$, does there exist a joint distribution $\prob[\jointvar]$ such that each given distribution $\prob[V_i]$ can be obtained by marginalizing $\prob[\jointvar]$?
-        \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \eq \label{eq:def:marginal_problem}\]
-        Following definition 2.3 in~\cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a joint distribution $\prob[\jointvar]$ and \term{non-contextual} otherwise.
-    \end{definition}
-
-    There are two perspectives that can be taken when trying to answer the marginal problem.
-The first comes as stated by \cref{def:marginal_problem}; when inured with a particular marginal model $\prob^{\mscenario}$, can you construct a joint distribution that satisfies \cref{def:marginal_problem}?
-Alternatively and more abstractly, when provided a marginal \textit{mscenario} $\mscenario$ what is the set of all marginal models that are (non-)contextual?
-To facilitate future discussions, let $\s{NC}$ denote the set of marginal models that are non-contextual (admitting a joint distribution) and let $\s{C}$ denote the set of contextual marginal models.
-It becomes desirable to identifying conditions that constrain either $\s{NC}$ or $\s{C}$.
-We will continue to refer to a \term{complete solution marginal problem} as a finite set of necessary and sufficient conditions able to discern if a given marginal model $\prob^{\mscenario}$ is in $\s{NC}$ or $\s{C}$.
-These constraints typically take the form of linear inequalities over probabilities $\prob^{\mscenario}$.
-
-    \begin{definition}
-        A \term{$\s{NC}$-inequality} $I_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every non-contextual marginal model $\prob^{\mscenario}$.
-    \end{definition}
-
-    In the \cref{sec:linear_program}, we will explore and briefly mention existing techniques for completely (or partially) solving the marginal problem.
-The basis of understanding being that \cref{eq:def:marginal_problem} is a \textit{linear} operation.
-In certain circumstances, \cref{eq:def:marginal_problem} can be represented as a matrix operation.
-
-    \todo[TC]{Maybe define the possibilistic marginal problem for later} \\
-
-    \subsection{Casting the Marginal Problem as a Linear Program}
-    \label{sec:linear_program}
-
-    Heretofore, our discussions of compatibility, contextuality and the marginal problem have be completely general, making no reference to the nature of the outcomes of the random variables $\jointvar$; whether they be discrete or continuous, finite or unbounded, or otherwise.
-\todo[TC]{It is entirely possible to obtain complete solutions to the marginal problem for continuous and unbounded measure spaces using entropic inequalities.
-[Elaborate and reference]} In this paper we restrict our attention to finite outcomes.
-In particular, we will focus on marginal scenarios that are finite but have a large number of outcomes.
-To assist with the subsequent analysis, we recall some familiar notions of probability theory together with new terminology and notation.
-\\
-
-    \subsubsection{Events}
-    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$.
-We also define the set of all \term{events over $v$} $\Events{v}$\footnote{In the language of sheaf-theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
-    \[ \Events{v} \defined \bc{s : \bc{v} \to O_v} \label{eq:outcome_space} \]
-    Evidently, $\Events{v}$ and $O_v$ have a one-to-one correspondence and this distinction can be confounding.
-There is rarely any harm in referring synonymously to either as outcomes.
-Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
-    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetry}.
-As a natural generalization we define the event over a collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
-    \[ \Events{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
-    Each event $s$ can be compactly represented as a set of mappings over each element of $V$.
-    \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
-    The domain $\Dom{s}$ of an event $s$ is the set of random variables it valuates, i.e. if $s \in \Events{V}$, then $\Dom{s} = V$.
-    \begin{example}
-        Let $s \in \Events{V}$ be an event over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$.
-Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$.
-Furthermore let $f \in \Events{V}$ be the section $\br{v_1 \mapsto 2, v_2 \mapsto 1}$.
-Then the following notations are interchangeable,
-        \[ \prob[][s] = \prob[\Dom{s}][s] = \prob[V][s] = \prob[v_1, v_2][s] = \prob[][v_1 \mapsto s_1\br{v_1}, v_2 \mapsto s_2\br{v_2}] = \prob[][v_1 \mapsto 2, v_2 \mapsto 1] = \prob[v_1v_2][21] \]
-        Each of which should be read as ``the probability that $v_1$ got outcome $2$ and $v_2$ got outcome $1$''
-    \end{example}
-    \begin{definition}
-    \label{def:section_restriction}
-    For every $W \subseteq V$ and $s \in \Events{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Events{W}$) is the event in $\Events{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
-    \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
-    \end{definition}
-    \begin{definition}
-    \label{def:section_compatible}
-    The events $s_{V} \in \Events{V}$ and $s_{W} \in \Events{W}$ are said to be \term{compatible} events if they agree on their valuations of $V \cap W$.
-Compatibility will be denoted with the infix `$\com$'.
-    \[ s_{V} \com s_{W} \iff {s_{V}}|_{V\cap W} = {s_{W}}|_{V\cap W} \]
-    \end{definition}
-    \begin{definition}
-    \label{def:section_extendable}
-    It $s_V \in \Events{V}$ and $s_W \in \Events{W}$ compatible events and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
-    \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
-    Extendability is dual to the notion of a \term{restriction} of $s_V$; $s_V$ can be restricted to $s_W$ ($s_V \res s_W$) if and only if $s_W$ is extendable to $s_V$.
-    \end{definition}
-
-    \begin{remark}
-        The notation `$s \com t$' is used to indicate compatibility between $s \in \Events{V}$ and $t \in \Events{W}$ because of the following observation: $s$ and $t$ are compatible if and only if they are extensions of some event $r \in \Events{V \cap W}$.
-        \[ s \com t \iff \exists r \in \Events{V \cap W} \mid s \res r \ext t \]
-        In fact $r$ is uniquely defined.
-        \[ \forall v \in V \cap W : r\br{v} = s\br{v} = t\br{v} \]
-    \end{remark}
-
-    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint events} $\Events{\jointvar}$.
-Similarly we define the \term{context events} $\bc{\Events{V} \mid V \in \mscenario}$.
-Finally, we elect to define the disjoint union of all context events are called the \term{marginal events} and by an abuse of notation we will denote this disjoint union as $\Events{\mscenario}$.
-    \[ \Events{\mscenario} = \coprod_{V \in \mscenario} \Events{V} \]
-    Each marginal section $m \in \Events{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
-    \subsubsection{Linear Programs}
-    \label{sec:linear_programs}
-
-    We are now fully equipped to write the marginal problem as a matrix multiplication.
-    \begin{definition}
-        \label{def:incidence_matrix}
-        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} events $j \in \Events{\jointvar}$ and the rows are events by \textit{marginal} sections $m \in \Events{\mscenario}$.
-The entries of $M$ are populated whenever a row index is extendable to a column index.
-        \[ M_{m,j} = \de_{m \ext j} \defined \begin{cases}
-            1 & m \ext j \\
-            0 & \text{otherwise}
-        \end{cases} \]
-        Where $\de_{m \ext j}$ is termed the \term{extendability indicator}.
-The incidence matrix has $\abs{\Events{\jointvar}}$ columns, $\abs{\Events{\mscenario}} = \sum_{i} \abs{\Events{V_i}}$ rows and $k\abs{\Events{\jointvar}}$ non-zero entries.
-    \end{definition}
-    To illustrate this concretely, consider the following example:
-    \begin{example}
-        \label{ex:incidence_matrix}
-        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{a,b}, \bc{b,c}, \bc{a,c}}$. The incidence matrix becomes:
-        \[ M = \kbordermatrix{
-            (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
-            (a\mapsto0, b\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto0, b\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto1, b\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
-            (a\mapsto1, b\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
-            (b\mapsto0, c\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
-            (b\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
-            (b\mapsto1, c\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
-            (b\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
-            (a\mapsto0, c\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto1, c\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
-            (a\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
-        } \eq \label{eq:example_incidence}\]
-    \end{example}
-
-    \begin{definition}
-        The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint event $j \in \Events{\jointvar}$.
-$\probvec^{\jointvar}$ shares the same indices as the \textit{column} indices of $M$.
-        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
-    \end{definition}
-    \begin{definition}
-        Analogously, \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Events{\mscenario}$.
-$\probvec^{\mscenario}$ shares the same indices as the \textit{row} indices of $M$.
-        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
-    \end{definition}
-    The marginal and joint distribution vectors are related via the incidence matrix $M$.
-Given a joint distribution vector $\probvec^{\jointvar}$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec^{\jointvar}$.
-    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
-    Henceforth we will use $\probvec^{\jointvar}$ ($\probvec^{\mscenario}$) and $\prob[\jointvar]$ ($\prob_{\mscenario}$) interchangeably.
-
-    \begin{remark}
-        The particular ordering of the rows and columns of $M$ carries no importance, but it \textit{must} be consistent between $M$, $\probvec^{\jointvar}$ and $\probvec^{\mscenario}$.
-    \end{remark}
-
-    The marginal problem can now be rephrased in the language of the incidence matrix.
-Suppose one obtains a marginal distribution vector $\probvec^{\mscenario}$.
-The marginal problem becomes equivalent to the question: \textit{Does there exist a joint distribution vector $\probvec^{\jointvar}$ such that \cref{eq:incidence_matrix_use} holds?}
-
-    \begin{definition}
-        \label{def:marginal_linear_program}
-        \term{The Marginal Linear Program} is the following linear program:
-        \begin{alignat*}{2}
-            & \text{minimize:} \quad&& \emptyset \tcdot x\\
-            & \text{subject to:} && x \succeq 0 \\
-            & && M \tcdot x = \probvec^{\mscenario}
-        \end{alignat*}
-        If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries).
-The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:incidence_matrix_use} and is a valid joint distribution vector.
-Therefore feasibility implies that $\probvec^{\jointvar} = x$.
-Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\probvec^{\jointvar}$ over all random variables.
-    \end{definition}
-    \todo[TC]{Talk about about the linear solvers and how this is easy to implement.}
-    \begin{definition}
-        \label{def:dual_marginal_linear_program}
-        \term{The Dual Marginal Linear Program} is the dual of \cref{def:marginal_linear_program} formulated via a procedure similar to~\cite{Lahaie_2008}:
-        \begin{alignat*}{2}
-            & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
-            & \text{subject to:} && y \tcdot M \succeq 0
-        \end{alignat*}
-        Where $y$ is a real valued vector with the same length as $\probvec^{\mscenario}$.
-    \end{definition}
-
-    The dual marginal linear program not only answers the marginal problem for a specific marginal model $\probvec^{\mscenario}$ but as a by-product provides an inequality that witnesses its contextuality.
-If this is not obvious, first notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints become satisfied.
-Secondly if the dual constraint $y \tcdot M \succeq 0$ holds \textit{and} the primal is feasible, then the following must hold:
-    \[ y \tcdot \probvec^{\mscenario} =  y \tcdot M \tcdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
-    Therefore the \textit{sign} of the dual value $d \defined \min \br{y \tcdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality.
-If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore $\probvec^{\mscenario}$ is contextual.
-Likewise if $d \geq 0$ (satisfying \cref{eq:dual_marginal_ineq}), then $\probvec^{\mscenario}$ is non-contextual.
-\footnote{Actually, if $d \geq 0$ then it is exactly $d = 0$ due to the existence of the trivial $y = \emptyset$.
-This observation is an instance of the \textit{Complementary Slackness Property} of~\cite{Bradley_1977}.
-\comment[TC]{Is this really the CSP?} Moreover, if $d < 0$, then it is unbounded $d = -\inf$.
-This latter point becomes clear upon recognizing that for any $y$ with $d < 0$, another $y' = \al y$ can be constructed (with $\al > 1$) such that $d' = \al d < d$.
-Since a more negative $d'$ can always be found, it must be that $d$ is unbounded.
-This is a demonstration of the fundamental \textit{Unboundedness Property} of~\cite{Bradley_1977}; if the dual is unbounded, then the primal is infeasible.
-\comment[TC]{\href{http://web.stanford.edu/~ashishg/msande111/notes/chapter4.pdf}{Farkas's lemma} here?}}
-
-    \begin{definition} An \term{infeasibility certificate}~\cite{Andersen_2001} is any vector $y$ that satisfies the constraint of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
-    \[ y \in \R^{\abs{\Events{\mscenario}}} : y \tcdot M \succeq 0, \quad y \tcdot \probvec^{\mscenario} < 0 \]
-    Furthermore, for every $y$ satisfying $y \tcdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of non-contextual marginal models $\s{NC}$,
-    \[ \forall \probvec^{\mscenario} \in \s{NC} : y \tcdot \probvec^{\mscenario} \geq 0 \]
-    \end{definition}
-
-    \todo[TC]{Discuss Infeasibility Certificates basis} \\
-
-    \todo[TC]{Discuss the certificate inequalities we found.} \\
-
-    \todo[TC]{Discuss Compatibility, connection to cooperative games/resources, bell incompatibility?} \\
-
-    \subsubsection{Fourier Motzkin Elimination \& Polytope Projection}
-
-    The complete space of marginal models over $\mscenario$ can be partitioned into two spaces: contextual ($\s{C}$) and non-contextual marginal models ($\s{NC}$).
-The separation between these spaces is completely characterized by the system of inequalities associated with \cref{eq:incidence_matrix_use}.
-Explicitly,
-    \begin{equation} \label{eq:halfspace_rep_incidence}
-    \begin{alignedat}{2}
-        \forall m \in \Events{\mscenario} :&&\quad \probvec^{\mscenario}_m - {\sum}_{j} M_{m, j} \probvec^{\jointvar}_j &\geq 0 \\
-        \forall m \in \Events{\mscenario} :&&\quad -\probvec^{\mscenario}_m + {\sum}_{j} M_{m, j} \probvec^{\jointvar}_j &\geq 0 \\
-        \forall j \in \Events{\jointvar} :&&\quad \probvec^{\jointvar}_j &\geq 0
-    \end{alignedat}
-    \end{equation}
-    Geometrically \cref{eq:halfspace_rep_incidence} is a family of $2\abs{\Events{\mscenario}} + \abs{\Events{\jointvar}}$ half-planes bounding $\R^{\abs{\Events{\mscenario}}} \times \R^{\abs{\Events{\jointvar}}}$.
-However testing the contextuality of a marginal model $\probvec^{\mscenario}$ requires a collection of inequalities bounding just $\R^{\abs{\Events{\mscenario}}}$.
-Transforming \cref{eq:halfspace_rep_incidence} into the desired system of inequalities is the task of linear-quantifier elimination.
-A popular tool for linear quantifier elimination is Fourier-Motzkin elimination \cite{Dantzig_1973,Inflation,Abramsky_2012,jones_2004}.
-We will avoid expounding the Fourier-Motzkin procedure in this paper and instead reproduce a few of its notable features and consequences.
-
-    \begin{definition} \cite[Section 12.2]{Schrijver_1998}
-        The \term{Fourier-Motzkin elimination} procedure begins with a matrix $A$ and a vector $b$ defining a system of inequalities $S_1 = \bc{A\tcdot x \leq b}$ constraining a set of variables $x$ and symbolically eliminates a sub-set of theses variables $x \setminus y$.
-Upon completion, one obtains a new set of constraints $S_2 = \bc{A' y \leq b'}$ such that,
-        \[ \exists y : A' y \leq b' \iff \exists x : A x \leq b \]
-        Any solution $y$ of $S_2$ will permit at least one solution $x$ in $S_1$ (and vice versa).
-    \end{definition}
-
-    When applied to the marginal problem of \cref{eq:halfspace_rep_incidence}, the Fourier-Motzkin procedure eliminates all reference to the joint probabilities $\probvec^{\jointvar}_j$ and returns a system of inequalities over the marginal probabilities $\probvec^{\mscenario}_m$ representing a \textit{complete} solution to the marginal problem.
-Applying the Fourier-Motzkin procedure to completely solve the marginal problem is discussed in more detail in~\cite{Inflation} and~\cite{Fritz_2011}.
-\todo[TC]{Improve this discussion of FMP}.
-\\
-
-    \todo[TC]{Discuss why FM is slow?}\\
-
-    \begin{remark}
-        In theory, Fourier-Motzkin offers a complete solution to the marginal problem for all marginal scenarios; its limitations are purely computational.
-In addition, the entire procedure only utilizes field operations \cite{Abramsky_2012} meaning that since \cref{eq:halfspace_rep_incidence} is a rational system of inequalities, then a complete solution to the marginal problem only requires a finite set of linear, rational coefficient inequalities.
-    \end{remark}
-
-    \begin{theorem}
-        There exists a set of necessary and sufficient conditions
-
-    \end{theorem}
-
-    \todo[TC]{Logical Bell inequalities paper: only need to consider rational inequalities, actually integer inequalities, actually homogeneous inequalities} \\
-    \todo[TC]{Discuss computational complexity} \\
-    \todo[TC]{Mention what a complete solution looks like after using Fourier Motzkin}
-    \subsubsection{Marginal Polytope}
-    \begin{definition}
-        Let $I_{1}$ and $I_{2}$ represent two
-    \end{definition}
-    \begin{definition}
-        Let $\s{I}$
-    \end{definition}
-
-    \todo[TC]{Very briefly discuss polytope perspective and facet inequalities vs. non-facet inequalities}
-    \todo[TC]{Define facets as irreducible inequalities}
-
-    \todo[TC]{Maybe put the description of our task here. This will motivate the need for more scalable approaches.}
-
-    \section{Transversal Inequalities}
-
-    Section \ref{sec:linear_programs} discusses how one can obtain a $\s{NC}$-inequality that witnesses the contextuality of a particular marginal model $\probvec^{\mscenario}$ by writing the marginal problem as a linear program.
-Every $\probvec^{\mscenario} \in \s{NC}$ is witness-able by some certificate inequality.
-Albeit when a candidate marginal model $\probvec^{\mscenario}$ is not present, linear optimization offers no utility.
-\\
-
-    This section aims to develop a procedure for finding \textit{all} certificate inequalities in a computationally efficient manner.
-Specifically by finding all certificate inequalities that are also facets of the marginal polytope.
-Before doing so, we will first summarize a method \todo[TC]{Method where this idea came from, original insight from Hardy?} that can be used to obtain a complete solution to the \textit{possibilistic} marginal problem~\cite{Mansfield_2012} and indirectly offer a \textit{partial} solution to the \textit{probabilistic} marginal problem.
-
-    \subsection{Hardy Transversals}
-    \label{sec:logical_inequalities}
-    Let $a \in \Events{\mscenario}$ be any marginal event and $C = \bc{c_1, \ldots, c_{n}} \subseteq \Events{\mscenario}$ be a subset of the marginal events.
-We say that the subset $C$ forms a \term{logical extension} of $a$ if the following logical implication holds for \textit{all} marginal models $\probvec^{\mscenario}$.
-    \[ a \implies c_1 \vee \ldots \vee c_n = \bigvee_{c \in C} c \eq \label{eq:1a_implication} \]
-    Which can be dictated: \textit{Whenever the event $a$ occurs, at least one the events in $C$ occurs.} In this paper, the marginal event $a$ will be referred to as the \textit{antecedent} and $C$ as the \textit{consequent set}.
-To clarify, a marginal model $\probvec^{\mscenario}$ satisfies \cref{eq:1a_implication} if there always exists at least one $c \in C$ that is possible ($\probvec^{\mscenario}_c > 0$) whenever $a$ is possible.
-A marginal model $\probvec^{\mscenario}$ violates \cref{eq:1a_implication} whenever \textit{none} of the sections in $C$ are possible while $a$ is nonetheless still possible.
-Marginal models that violate logical statements such as \cref{eq:1a_implication} are known as \term{Hardy Paradoxes}~\cite{Inflation,Mansfield_2012,Mancinska_2014}.
-The concept of witnessing quantum incompatibility on a logical level has been analyzed thoroughly for decades~\cite{Greenberger_1990,Abramsky_2012}; being motivated by a greater sense of robustness compared to probabilistic constraints.
-\\
-
-    All logical implications of the form \cref{eq:1a_implication} can be constructed by first selecting $a$ and then manufacturing a consequent set $C$ persuant to \cref{eq:1a_implication}.
-
-    \begin{definition}
-        \label{def:extendable_set}
-        For each marginal event $m \in \Events{\mscenario}$ the \term{extendable set of $m$ into $\jointvar$} is the set of all joint events $j \in \Events{\jointvar}$ that are extensions of $m$.
-        \[ \Ext[\jointvar]{m} = \bc{j \in \Events{\jointvar} \mid m \ext j} \]
-    \end{definition}
-
-    The extendable set of $m$ into $\jointvar$ is the subset of events in $\Events{\jointvar}$ that \textit{agree} with $m$ about valuations for variables in $\Dom{m}$.
-Practically speaking, the extendable set of $m$ into $\jointvar$ is represented by the $m$-th row of the incidence matrix $M$.
-
-    \begin{lemma}
-        \label{lemma:logical_extenable_set}
-        Let $a \in \Events{\mscenario}$ and $\probvec^{\mscenario} \in \s{NC}$ be non-contextual. Then,
-        \[ a \iff \bigvee_{j \in \Ext[\jointvar]{a}} j \eq \label{eq:lemma_logical_extendable_set}\]
-    \end{lemma}
-    The idea being if a joint distribution does exists, then the event $a$ represents partial knowledge of the entire system $\jointvar$; whenever $a$ is measured, exactly one joint event $j$ has occurred in reality and $j$ must be compatible with $a$.
-Likewise \cref{lemma:logical_extenable_set} applies to the consequent set $C \in \Events{\mscenario}$,
-    \[ \bigvee_{c \in C} c \iff \bigvee_{c \in C} \bigvee_{j \in \Ext[\jointvar]{c}} j \eq \label{eq:logical_extension_C}\]
-    If a subset $C$ can be found such that its extendable set \textit{covers} the extendable set of $a$,
-    \[ \Ext[\jointvar]{a} \subseteq \bigcup_{c \in C} \Ext[\jointvar]{c} \eq \label{eq:logical_containment} \]
-    Then the combination of \cref{eq:lemma_logical_extendable_set,eq:logical_extension_C,eq:logical_containment} yields \cref{eq:1a_implication}.
-Computationally enumerating all logical extensions $C \subseteq \Events{\jointvar}$ for a particular antecedent $a \in \Events{\mscenario}$ corresponds iteratively selecting marginal sections $c \neq a$ for membership in $C$ until \cref{eq:logical_containment} is satisfies.
-This process is more generally known as a set-covering problem, or a hypergraph transversal problem~\cite{Inflation}, an idea we return to in the more general picture to follow in \cref{sec:dep}.
-\todo[TC]{Maybe use an example here to define a Hardy transversal.}\\
-
-    It is possible to show that for each logical constraint there exists a probabilistic constraint that is tighter.
-The principle statement of \cref{lemma:logical_extenable_set} can be taken in a probabilistic form.
-If the marginal model $\probvec^{\mscenario}$ is to admit a joint distribution $\probvec^{\jointvar}$, then it must be that the antecedent probability $\probvec^{\mscenario}_a$ is equal to a marginalization over its extendable set into $\jointvar$.
-    \[ \probvec^{\mscenario}_a = \sum_{j \in \Ext[\jointvar]{a}}\probvec^{\jointvar}_j \eq \label{eq:marginal_extendable_sum_a} \]
-    This is nothing more than the the $a$-th row of \cref{eq:incidence_matrix_use}. Likewise for the consequent set,
-    \[ \sum_{c \in C}\probvec^{\mscenario}_c = \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\probvec^{\jointvar}_j \eq \label{eq:marginal_extendable_sum_cs} \]
-    Since $C$ is a logical extension of $a$, the right-hand side of \cref{eq:marginal_extendable_sum_a} \textit{algebraically} covers \cref{eq:marginal_extendable_sum_cs}\footnote{If there were a joint event $j^*$ present on the right-hand side of \cref{eq:marginal_extendable_sum_a} but not the right-hand side of \cref{eq:marginal_extendable_sum_cs}, then \cref{eq:1a_probabilistic} would be violated by the deterministic joint distribution where $\probvec^{\jointvar}_{j^*} = 1$}.
-Therefore one recovers the probabilistic version of \cref{eq:1a_implication},
-    \[ \probvec^{\mscenario}_a \leq \sum_{c \in C}\probvec^{\jointvar}_c \eq \label{eq:1a_probabilistic} \]
-    Due to the logical precedent, inequalities of the form of \cref{eq:1a_probabilistic} are called \term{Hardy inequalities}.
-Marginal models that are contextual on a logical level are \term{possibilistically contextual}.
-In~\cite{Abramsky_2011} it was demonstrated that all possibilistically contextual models have their contextuality witnessed by logical extensions.
-In this sense, logical implications of the form \cref{eq:1a_implication} completely solve the possibilistic marginal problem.
-    \todo[TC]{Discuss logical bell inequalities}
-    \begin{remark}
-        The probabilistic logical extension \cref{eq:1a_probabilistic} is an \textit{upgraded} version of \cref{eq:1a_implication} in the following sense.
-        \begin{itemize}
-            \item Every $\probvec^{\mscenario} \in \s{NC}$ satisfies both \cref{eq:1a_probabilistic} and \cref{eq:1a_implication}.
-            \item Every $\probvec^{\mscenario} \in \s{C}$ that violates \cref{eq:1a_implication} will also violate \cref{eq:1a_probabilistic}; but the converse is not necessarily true.
-        \end{itemize}
-    \end{remark}
-
-    \subsection{Definite Extensions}
-    We will now generalize the notion of a Hardy transversal by considering multi-sets of antecedents corresponding to multiple marginal events each accompanied by an assigned multiplicity.
-Afterwards we provide an algorithm to completely solve the marginal problem by transversing generalized hypergraphs.
-To our benefit, this technique for solving the marginal problem offers considerable advantages over existing methods when dealing with large marginal scenarios.
-\\
-
-    To facilitate the discussion, some definitions and notation are necessary.
-    \begin{definition}
-        A \term{multi-set} or \term{bag} $\ga$ for a marginal scenario $\mscenario$ is a vector indexed by marginal events $m \in \Events{\mscenario}$ whose entries are integers $\ga_{m} \in \Z$.
-The \term{support} $\supp{\ga}$ of an bag is the subset of marginal events that are assigned non-zero multiplicity.
-        \[ \supp{\ga} \defined \bc{m \in \Events{\mscenario} \mid \ga_m \neq 0} \]
-        The \term{order} $\abs{\ga}$ of a multi-set $\ga$ is entry-wise sum of $\ga$.
-        \[ \abs{\ga} = \sum_{m \in \Events{\mscenario}} \ga_m = \sum_{m \in \supp{\ga}} \ga_m \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{marginal indicator} vector $\de^{m}$ for a marginal event $m$ is the unit vector indexed by marginal outcomes $\Events{\mscenario}$ whose only non-zero entry is the marginal event $m$.
-        \[ \forall m' \in \Events{\mscenario} : \de^{m}_{m'} = \begin{cases}
-            1 & m' = m \\
-            0 & m' \neq m
-        \end{cases} \]
-        Analogously defined is the \term{joint indicator} vector $\de^{j}$.
-    \end{definition}
-
-    \begin{definition}
-        The \term{extension $\Ga$ of an multi-set $\ga$} for a marginal scenario $\mscenario$ is a vector indexed by \textit{joint} events $j \in \Events{\jointvar}$ and can be constructed by left-multiplication of $\ga$ into the incidence matrix $M$.
-        \[ \Ga \defined \ga \tcdot M \]
-    \end{definition}
-
-    For every multi-set $\ga$ there corresponds a candidate inequality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ whose validity is completely characterized by $\Ga$.
-    \begin{theorem}
-        \label{thm:definite_extension_main_thm}
-        Let $\ga$ be a multi-set for the marginal scenario $\mscenario$.
-Then the inequality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ is a valid non-contextuality inequality if and only if $\Ga$ is positive semi-definite.
-        \[ \forall \probvec^{\mscenario} \in \s{NC} : \ga \tcdot \probvec^{\mscenario} \geq 0 \iff \Ga \succeq 0  \eq \label{eq:thm:semi_definite_extension}\]
-    \end{theorem}
-    \begin{proof}
-        The proof follows directly from \cref{eq:incidence_matrix_use}. Since $\probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}$,
-        \[ \ga \tcdot \probvec^{\mscenario} = \ga \tcdot M \tcdot \probvec^{\jointvar} = \Ga \tcdot \probvec^{\jointvar} \]
-        If $\Ga \succeq 0$, then $\Ga \tcdot \probvec^{\jointvar} \geq 0$ which gives $\ga \tcdot \probvec^{\mscenario} \geq 0$.
-The forward case of \cref{eq:thm:semi_definite_extension} can be proven by contradiction.
-Suppose that $\ga \tcdot \probvec^{\mscenario} \geq 0$ for all marginal models but $\Ga \not \succeq 0$.
-Consequently there exists at least one joint outcome $j^{*}$ such that $\Ga_{j^{*}} < 0$.
-This negative entry can be exploited by a deterministic joint distribution $\probvec^{\jointvar} = \de^{j^{*}}$,
-        \[ 0 > \Ga_{j^{*}} = \Ga\tcdot \de^{j^{*}} = \ga \tcdot M \tcdot \de^{j^{*}}  \]
-        Which is a contradiction: $M \tcdot \de^{j^{*}}$ is a non-contextual marginal model but $\ga \tcdot M \tcdot \de^{j^{*}} \not \geq 0$.
-    \end{proof}
-
-    Clearly if the multi-set itself is positive semi-definite $\ga \succeq 0$ then $\Ga \succeq 0$ is also.
-Corresponding inequalities are then \textit{trivial}: being satisfied by all $\probvec^{\mscenario} \in \s{NC}$.
-As such, it is desired to obtain definite extensions $\Ga$ from \textit{indefinite} multi-sets $\ga$.
-
-    \begin{corollary}
-        Let $\ga$ be a multi-set for the marginal scenario $\mscenario$.
-Then the equality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} = 0}$ is satisfied by all non-contextual marginal models if and only if $\Ga$ is a null vector (i.e.
-$\forall j : \Ga_{j} = 0$).
-    \end{corollary}
-
-    \Cref{thm:definite_extension_main_thm} demonstrates it is possible to generate non-contextuality inequalities by finding multi-sets $\ga$ such that $\Ga \succeq 0$.
-In light of this, we will formally define the subset of joint outcomes $j$ that are preventing a candidate multi-set $\ga$ from having positive semi-definite extensions.
-
-    \begin{definition}
-        The \term{inhibiting set} $\inhibit\br{\ga}$ for a multi-set $\ga$ is the subset of joint outcomes preventing $\Ga \succeq 0$ from holding true.
-        \[ \inhibit\br{\ga} = \bc{j \in \Events{\jointvar} \mid \br{\ga \tcdot M}_j = \Ga_j < 0} \]
-    \end{definition}
-
-    Procedurally, definite extensions can be built by beginning with a seed multi-set $\ga^{(0)} = \ga^{A}$ composed entirely of non-positive entries and iteratively appending marginal events $m$ ($\ga^{(n+1)} = \ga^{(n)} + \de^{m}$) in such a way that progresses $\Ga^{(n)}$ toward becoming positive semi-definite (i.e.
-by decreasing the inhibiting set).
-Taking inspiration from logical, Hardy-type, transversal inequalities discussed in \cref{sec:logical_inequalities}, we can view this process as a weighted hypergraph transversal problem.
-
-    \subsection{Definite Extension Procedure}
-    \label{sec:dep}
-    Before discussing the definite extension procedure (DEP) directly, we will motivate its main algorithmic component (weighted hypergraphs transversals) with a short example.
-    \subsubsection{Example}
-    \begin{example}
-        \label{ex:hypergraph_example}
-        Recall the exemplary incidence matrix $M$ of \cref{eq:example_incidence}, \cref{ex:incidence_matrix}.
-Our aim is generate some valid non-contextuality inequalities for marginal models $\probvec^{\mscenario}$.
-To compactify notation, enumerate the marginal outcomes (rows of $M$) $1$ through $12$ $\br{m_1, \ldots, m_{12}}$ and the joint outcomes (columns of $M$) $1$ through $8$ $\br{j_1, \ldots, j_{8}}$ (see \cref{fig:compact_incidence}).
-        \begin{figure}
-        \begin{center}
-            \begin{minipage}[b]{.48\textwidth}
-                \centering
-                \[ M = \kbordermatrix{
-                    & j_1 & j_2 & j_3 & j_4 & j_5 & j_6 & j_7 & j_8 \\
-                    m_1 & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
-                    m_2 & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
-                    m_3 & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
-                    m_4 & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
-                    m_5 & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
-                    m_6 & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
-                    m_7 & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
-                    m_8 & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
-                    m_9 & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
-                    m_{10} & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
-                    m_{11} & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
-                    m_{12} & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
-                } \]
-                \caption{The incidence matrix for the binary marginal scenario $\mscenario = \bc{\bc{a,b},\bc{b,c}, \bc{a,c}}$ with marginal outcomes $m_1, \ldots, m_{12}$ and joint outcomes $j_1, \ldots, j_{12}$.}
-                \label{fig:compact_incidence}
-            \end{minipage}\hspace{0.04\textwidth}%
-            \begin{minipage}[b]{.48\textwidth}
-                \centering
-                \scalebox{1.0}{\input{../../figures/hypergraphs/minimal_example}}
-                \caption{An edge-weighted hypergraph $\hgraph_{\weights}$ corresponding to the antecedent set $\ga^{A}$ with $\ga^{A}_{m_3} = -1$ and $\ga^{A}_{m_8} = -2$.}
-                \label{fig:hypergraph_example}
-            \end{minipage}
-        \end{center}
-        \end{figure}
-        Now suppose our antecedent set is $\ga^{A}$ and has two specified entries:
-        \[ \ga^{A}_{m_{3}} = -1 \quad \ga^{A}_{m_{8}} = -2 \]
-        Then the antecedent extension is given by $\Ga^{A}= \ga^{A} \tcdot M$:
-        \[ \Ga^{A}_{j_{4}} = \Ga^{A}_{j_{8}} = -2 \quad \Ga^{A}_{j_{5}} = \Ga^{A}_{j_{6}} = -1 \]
-        The objective then becomes to \textit{cover} the joint events of the inhibiting set $\bc{j_{4}, j_{5}, j_{6}, j_{8}}$ with marginal events organized as a consequent multi-set $\ga^{C} \succeq 0$ such that,
-        \[ \Ga^{C} + \Ga^{A} \succeq 0 \]
-        Taking motivation from \cref{sec:logical_inequalities}, this procedure can be casted as a multi-node hitting problem, or an edge-weighted hypergraph problem.
-Construct a weighted hypergraph $\hgraph_{\weights}$ (see \cref{fig:hypergraph_example}) where the edges are labeled by joint outcomes $\edges = \bc{e_{j_{4}}, e_{j_{5}}, e_{j_{6}}, e_{j_{8}}}$.
-These edges are assigned weights $w_j$ precisely equal to the magnitude of $\Ga^{A}$.
-        \[ \forall j \in \bc{{j_{4}}, {j_{5}}, {j_{6}}, {j_{8}}} : w_{j} = - \Ga^{A}_j \]
-        These weights characterize the joint events that are preventing $\Ga$ from becoming positive semi-definite.
-The nodes represent all possible marginal events that have the potential to contribute to $\ga^{C}$.
-        \[ \nodes = \bc{m_2, m_4, m_5, m_6, m_{10}, m_{11}, m_{12}} \]
-        A node $m$ is a member of edge $e_{j}$ if $m \ext j$.
-By inspection of \cref{fig:hypergraph_example} one can identify numerous multi-sets of $\ga^{C}$ of $\nodes$ that hit each edge $w_j$ times.
-As a singular example,
-        \[ \trans = \bc{m_{2}, m_{10}, m_{11}, m_{12}, m_{12}} = \kbordermatrix{
-            & m_2 & m_4 & m_5 & m_6 & m_{10} & m_{11} & m_{12} \\
-            &   1 &   0 &   0 &   0 &      1 &      1 &      2
-        } \]
-        satisfies this condition.
-We call such $\trans$ \textit{transversals} of $\hgraph_{\weights}$.
-This multi-set enables one to construct the positive semi-definite extension $\Ga^{C} + \Ga^{A}$ where $\Ga^{C} = \trans \tcdot M$.
-This corresponds to the inequality $- \ga^{A} \tcdot \probvec^{\mscenario} \leq \ga^{C} \tcdot \probvec^{\mscenario}$,
-        \begin{align*}
-        \probvec^{\mscenario}_{m_3} + 2 \probvec^{\mscenario}_{m_8} &\leq \probvec^{\mscenario}_{m_{2}} + \probvec^{\mscenario}_{m_{10}} + \probvec^{\mscenario}_{m_{11}} + 2 \probvec^{\mscenario}_{m_{12}} \\
-        \prob[][m_3] + 2 \prob[][m_8] &\leq \prob[][m_{2}] + \prob[][m_{10}] + \prob[][m_{11}] + 2 \prob[][m_{12}] \\
-        \prob[ab][10] + 2 \prob[bc][11] &\leq \prob[ab][01] + \prob[ac][01] + \prob[ac][10] + 2 \prob[ac][11]
-        \end{align*}
-    \end{example}
-    % \begin{definition}
-    %     For convenience, denote the $m$-th row of the incidence matrix $M$ as $\de^{m \ext \jointvar}$ and the $j$-th column of $M$ by $\de^{j \res \mscenario}$.
-    %     \[ \de^{m \ext \jointvar}_j = \de^{j \res \mscenario}_m  = \de^{\mscenario \ext \jointvar}_{m,j} \]
-    %     The following relationships hold for the indicator vectors.
-    %     \[ \de^{\mscenario \ext \jointvar} \tcdot \de^{j} = \de^{j \res \mscenario} \qquad \de^{m} \tcdot \de^{\mscenario \ext \jointvar} = \de^{m \ext \jointvar} \]
-    % \end{definition}
-    % We first recall that every non-contextual marginal model $\prob^{\mscenario}$ can be written as the convex combination of columns of the incidence matrix $M$.
-    % \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} = \sum_{j \in \Events{\jointvar}} \de_{m \ext j} \prob[\jointvar][j] \]
-    % Thus we define the set of all non-contextual marginal models as $\mathcal{NC}$,
-    % \[ \mathcal{NC} \defined \bc{\probvec^{\mscenario} \mid \probvec^{\mscenario} = \sum_{j} \mu_{j} \de_{j \res \mscenario}, \mu_j \geq 0, \sum_{j} \mu_{j} = 1} \]
-
-    % \begin{definition}
-    %     Let $\mscenario$ be a marginal scenario and let $j \in \Events{\jointvar}$ be a joint outcome.
-The \term{restriction of $j$ onto $\mscenario$} is deterministic marginal model $\de_{j \res \mscenario} : \Events{\mscenario} \to \bc{0, 1}$.
-    %     \[ \de_{j \res \mscenario}\br{m} \defined \begin{cases}
-    %         1 & j \ext m  \\
-    %         0 & \textrm{otherwise}
-    %     \end{cases} \]
-    %     As a vector indexed by marginal outcomes $m \in \Events{\mscenario}$, $\de_{j \ext \mscenario}$ is precisely the $j$-th column of the incidence matrix.
-    % \end{definition}
-
-    % \begin{definition}
-    %     The \term{extension of an m-set} $\ga{S}$ into $\jointvar$ denoted $\Ga{S}$ is a vector indexed by \textit{joint} outcomes $j \in \Events{\jointvar}$ and is defined as follows,
-    %     \[ \Ga{S}_{j} \defined \sum_{s \in \supp{\ga{S}}} \ga{S}_{s} \de_{s \ext j} \eq \label{eq:joint_multiplicity} \]
-    %     As an immediate consequence, the support of $\Ga{S}$ is immediately known,
-    %     \[ \supp{\Ga{S}} = \bigcup_{s \in \supp{\ga{S}}} \Ext[\jointvar]{s} \]
-    % \end{definition}
-    % \begin{definition}
-    %     An m-set $\ga{C}$ is an \term{extension cover} of an m-set $\ga{A}$ for a marginal scenario $\mscenario$ if and only if the following two conditions hold\footnote{In fact \cref{eq:multi_extenable_cover_def} implies \cref{eq:flat_extenable_cover_def} since $\forall j \not \in \supp{\Ga{A}} : \Ga{A}_j = 0$.}:
-    %     \begin{gather*}
-    %         \supp{\Ga{A}} \subseteq \supp{\Ga{C}} \eq \label{eq:flat_extenable_cover_def}\\
-    %         \forall j \in \supp{\Ga{A}} : \Ga{A}_{j} \leq \Ga{C}_j \eq \label{eq:multi_extenable_cover_def}
-    %     \end{gather*}
-    % \end{definition}
-    % Identifying extension covers is of great importance because of the following theorem.
-    % \begin{theorem}
-    %     \label{thm:extendable_cover_ineq}
-    %     If the m-set $\ga{C}$ is an extension cover of the m-set $\ga{A}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
-    %     \[ \sum_{a \in \supp{\ga{A}}}\ga{A}_a\prob[][a] \leq \sum_{c \in \supp{\ga{C}}}\ga{C}_c\prob[][c] \eq \label{eq:extendable_cover} \]
-    % \end{theorem}
-    % \begin{proof}
-    %     To prove that \cref{eq:extendable_cover} is a valid compatibility inequality $I_{\mscenario}$ for all marginal models $\prob^\mscenario$, we will demonstrate that \cref{eq:extendable_cover} follows from the assumption that a joint distribution $\prob[\jointvar]$ exists.
-
-    %     For each m-set $\ga{S}$ write the weighted sum over the probabilities $\bc{\prob[][s]}_{s \in \supp{\ga{S}}}$ in terms of the joint distribution $\prob[\jointvar]$ using \cref{eq:joint_multiplicity}.
-    %     \begin{align*}
-    %     \eq \label{eq:derivation_cover}
-    %     \begin{split}
-    %     \sum_{s \in \supp{\ga{S}}} \ga{S}_s\prob[][s] &= \sum_{s \in \supp{\ga{S}}} \ga{S}_s  \sum_{j \in \Ext[\jointvar]{s}} \prob[\jointvar][j] \\
-    %     &= \sum_{s \in \supp{\ga{S}}} \ga{S}_s \sum_{j \in \Events{\jointvar}} \isext{s}{j} \prob[\jointvar][j] \\
-    %     &= \sum_{j \in \Events{\jointvar}} \bs{\sum_{s \in \supp{\ga{S}}} \ga{S}_s  \isext{s}{j}} \prob[\jointvar][j] \\
-    %     &= \sum_{j \in \supp{\Ga{S}}} \Ga{S}_j \prob[\jointvar][j]
-    %     \end{split}
-    %     \end{align*}
-    %     First examine the substitution $S \to C$,
-    %     \[ \sum_{c \in \supp{\ga{C}}} \ga{C}_c\prob[][c] = \sum_{j \in \supp{\Ga{C}}} \Ga{C}_j \prob[\jointvar][j] \]
-    %     By \cref{eq:flat_extenable_cover_def} $\supp{\Ga{A}} \subseteq \supp{\Ga{C}}$,
-    %     \[ \sum_{c \in \supp{\ga{C}}} \ga{C}_c\prob[][c] = \sum_{j \in \supp{\Ga{C}}} \Ga{C}_j \prob[\jointvar][j] + \sum_{j \in \supp{\Ga{C}} \setminus \supp{\Ga{A}}} \Ga{C}_j \prob[\jointvar][j] \]
-    %     Notice that the sum over $j \in \supp{\Ga{C}} \setminus \supp{\Ga{A}}$ is entirely positive since $\Ga{C}_j \in \N$ and $\prob[\jointvar][j] \geq 0$.
-Moreover \cref{eq:multi_extenable_cover_def} gives $\Ga{C}_j \geq \Ga{A}_j$.
-Combining these observations along with \cref{eq:derivation_cover} for $S \to A$, one arrives at the inequality,
-    %     \[ \sum_{c \in \supp{\ga{C}}} \ga{C}_c\prob[][c] \geq \sum_{j \in \supp{\Ga{A}}} \Ga{A}_j \prob[\jointvar][j] = \sum_{a \in \supp{\ga{A}}} \ga{A}_a\prob[][a] \]
-    %     Which is equivalent to \cref{eq:extendable_cover}; every non-contextual marginal model $\prob^{\mscenario}$ must satisfy \cref{eq:extendable_cover}.
-    % \end{proof}
-    % \begin{corollary}
-    %     \label{cor:linear_integer}
-    %     Every linear, integer coefficient compatibility inequality that is homogeneous is an extension covering inequality.
-    % \end{corollary}
-    % \begin{proof}
-    %     A proof is easy to see by contradiction.
-Let $I_{\mscenario} = \bc{\gamma \tcdot \probvec^{\mscenario} \geq 0}$ where $\gamma_m \in \Z | \forall m \in \Events{\mscenario}$ be a homogeneous, linear, integer coefficient, compatibility inequality such that it is \textit{not} an extension covering inequality.
-Next seperate $\gamma$ into its positive and negative components,
-    %     \[ \gamma_m^{+} = \begin{cases}
-    %         \gamma_m & \gamma_m > 0 \\
-    %         0 & \gamma_m \leq 0
-    %     \end{cases}
-    %     \qquad
-    %     \gamma_m^{-} = \begin{cases}
-    %         -\gamma_m & \gamma_m < 0 \\
-    %         0 & \gamma_m \geq 0
-    %     \end{cases} \]
-    %     Such that both $\gamma^{+}$ and $\gamma^{-}$ are valid m-sets.
-Therefore $I_{\mscenario} = \bc{\br{\gamma^{+} - \gamma^{-}} \tcdot \probvec^{\mscenario} \geq 0}$.
-Since this inequality is \textit{not} an extension cover, it must be that there exists at least one joint outcome $j' \in \Events{\jointvar}$ such that $\Gamma^{-}_{j'} > \Gamma^{+}_{j'}$.
-Consequently by \cref{eq:derivation_cover}, the deterministic distribution $\probvec^{\mscenario} = \de_{j' \res \mscenario}$ \textit{violates} $I_{\mscenario}$.
-However since $\de_{j' \res \mscenario} \in \mathcal{NC}$ and violates $I_{\mscenario}$, $I_{\mscenario}$ can not be a compatibility inequality; disagreeing with the assumption that it was.
-    % \end{proof}
-    % \begin{corollary}
-    %     If the m-set $\ga{C}$ is an extension cover of the m-set $\br{A, \mulA}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
-    %     \[ \sum_{a \in \supp{\ga{A}}}\prob[][a] \leq \sum_{c \in \supp{\ga{C}}}\prob[][c] \eq \label{eq:extendable_cover_flat} \]
-    % \end{corollary}
-    % \begin{proof}
-    %     This follows from the fact that if $\ga{C}$ is an extension cover of $\br{A, \mulA}$, then $\br{C, \mathbf{1}_{C}}$ is an extension cover of $\br{A, \mathbf{1}_{A}}$.
-Since $E_A \subseteq E_C$ is already trivially satisfied, all that remains is to demonstrate that \cref{eq:multi_extenable_cover_def} holds for unitary multiplicities $\mathbf{1}_A$ and $\mathbf{1}_C$.
-
-    %     First examine extension $\br{E_C, \mul{\mext{C}}}$ for the m-set $\ga{C}$ as defined by \cref{eq:joint_multiplicity},
-    %     \[ \forall j \in E_C : \Ga{C}_j = \sum_{c \in \supp{\ga{C}}} \mulC\br{c} \isext{c}{j} \]
-
-    %     First apply \cref{lemma:logical_extenable_set} to an arbitrary set $S \in \bc{A, C}$,
-    %     \[ \bigvee_{s \in \supp{\ga{S}}} s \iff \bigvee_{s \in \supp{\ga{S}}} \bigvee_{j \in \Ext[\jointvar]{s}} j \iff \bigvee_{j \in E_S} j \eq \label{eq:logical_iff_ext}\]
-    %     Now since $E_A \subseteq E_C$ by \cref{eq:flat_extenable_cover_def} we have that,
-    %     \[ \bigvee_{j \in E_A} j \implies \bigvee_{j \in E_C} j \eq \label{eq:logical_cover}\]
-    %     Combining \cref{eq:logical_iff_ext,eq:logical_cover} one arrives at,
-    %     \[ \bigvee_{a \in \supp{\ga{A}}} a \implies \bigvee_{c \in \supp{\ga{C}}}c \]
-    % \end{proof}
-    % For a working example, let $\jointvar = \bc{a, b, c}$ be a set of binary random variables ($O = \bc{0,1}$) and $\mscenario = \bc{\bc{a,b},\bc{b,c},\bc{a,c}}$ be the marginal context.
-    \subsubsection{Weighted Hypergraphs}
-    A \term{hypergraph} $\hgraph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{hyperedges} respectively where the hyperedges are \textit{subsets} of nodes $\forall e \in \edges : e \subset \nodes$.
-A hypergraph deviates from a traditional graph in that the edges have the capacity to contain more or less than $2$ nodes.
-There is a dual correspondence between the hyperedges $e \in \edges$ and nodes $n \in \nodes$ of a hypergraph: just as a hyperedge $e$ is interpreted as a set of nodes, a node $n$ can be viewed as the set of hyperedges $\bc{e \mid n \in e}$ that contain it.
-A \term{hypergraph transversal} (or edge hitting set) $\trans$ of a hypergraph $\hgraph$ is a set of nodes $\trans \subseteq \nodes$ that have a non-empty intersection with every hyperedge in $\edges$.
-    \[ \trans \subseteq \nodes \mid \forall e \in \edges : \trans \cap e \neq \emptyset \eq \label{eq:flat_trans_def}\]
-    A transversal $\trans$ is said to be \term{minimal} if there are no redundant nodes $n$ in $\trans$, i.e.
-no node $n$ can be removed from $\trans$ such that $\trans \setminus n$ remains a transversal.
-The condition for minimality expressed,
-    \[ \forall n \in \trans : \exists e \in \edges \mid \br{\trans \setminus n} \cap e = \emptyset \eq \label{eq:flat_trans_minimal}\]
-
-    When defining a \textit{weighted} hypergraph, there can be some ambiguity as to whether or not the weights $\weights$ are associated with the hyperedges or nodes.
-Since the definite extension procedure concerns itself with weighted hyperedges, we refer to edge-weighted hypergraphs simply as weighted hypergraphs.
-    \begin{definition}
-        A \term{(edge-)weighted hypergraph} $\hgraph_\weights$ is a hypergraph $\hgraph = \br{\nodes, \edges}$ together with a set of real-valued weights $\weights = \bc{w_e \mid e \in \edges}$ assigned to each hyperedge $e$.
-    \end{definition}
-    In the case of the definite extension procedure, these weights will typically be positive integers $w_e \in \Z_{> 0}$.
-As such, we make this the default setting moving forward.
-Accompanying weighted hypergraphs are the notion of weighted transversals.
-    \begin{definition}
-        A \term{weighted transversal} $\trans$ of a weighted hypergraph $\hgraph_{\weights}$ is a \textit{multi-set} or \textit{vector} of nodes $\forall n \in \nodes : \trans_n \in \N$ such that the total multiplicity of nodes in each hyperedge $e$ surpasses (or matches) the assigned weight $w_e$.
-        \[ \forall e \in \edges : \sum_{n \in e} \trans_{n} \geq w_e \eq \label{eq:weighted_trans_def}\]
-    \end{definition}
-    \begin{definition}
-        A weighted transversal $\trans$ of a weighted hypergraph $\hgraph_{\weights}$ is a said to be \term{minimal} or have \term{minimal-multiplicities} if all its entries $\trans_n : n \in \nodes$ are minimal in the sense that there does not exist a node $n' \in \supp{\trans}$ such that $\trans - \de^{n'}$ is still a transversal.
-        \[ \forall n' \in \nodes : \exists e \in \edges, n' \in e : \sum_{n \in e} \trans_{n} - 1 < w_e  \eq \label{eq:weighted_trans_minimal}\]
-        Equivalently, $\trans$ is minimal if there does not exists another transversal $\trans' \neq \trans$ such that $\forall j : \trans'_j \leq \trans_j$.
-    \end{definition}
-    Remark that if all assigned weights are singular $w_e = 1$, the weighted minimality condition \cref{eq:weighted_trans_minimal} reduces to the unweighted minimality condition \cref{eq:flat_trans_minimal}.
-The principle component of the definite extension procedure can be summarized as follows:
-
-    \subsubsection{Transversals of Antecedent Hypergraphs}
-    Given an antecedent multi-set $\ga^{A}$ where $\ga^{A} \preceq 0$, identify the \textit{inhibiting set} $\inhibit\br{\ga^{A}}$ responsible for preventing $\Ga^{A}$ from being classified as positive semi-definite.
-For an antecedent set $\ga^{A}$ where all entries are negative, there are a few equivalent ways of representing the inhibiting set,
-    \[ \inhibit\br{\ga^{A}} = \supp{\Ga^{A}} = \bc{j \mid \Ga^A_j < 0} = \bc{j \mid \exists m \in \supp{\ga^A} : m \ext j } \]
-    The last interpretation corresponding to the extendable set of $\supp{\ga^{A}}$.
-Using the inhibiting set $\inhibit\br{\ga^{A}}$, construct a weighted hypergraph $\hgraph_\weights\br{\ga^A}$ such that,
-    \begin{align*}
-    \edges\br{\ga^{A}} &= \bc{e_j \mid j \in \inhibit\br{\ga^{A}}} \\
-    e_j &= \bc{m \in \Events{\mscenario} \mid m \ext j, m \not \in \supp{\ga^A}} \\
-    \weights\br{\ga^{A}} &= \bc{w_j = - \Ga^{A}_j \mid j \in \inhibit\br{\ga^{A}}} \\
-    \nodes\br{\ga^A} &= \bigcup_{j \in \inhibit\br{\ga^A}} e_j \\
-    &= \bc{m \in \Events{\mscenario} \mid m \not \in \supp{\ga^A}, \exists m' \in \supp{\ga^A} : m \com m'}
-    \end{align*}
-    The hyperedges $e_j \in \edges\br{\ga^{A}}$ are indexed by the inhibiting set.
-Each hyperedge $e_j$ is the subset of marginal events $e_j \subseteq \Events{\mscenario}$ that are extendable to $j$ (yet not already included in $\ga^A$\footnote{At this point, it might be unclear why we disregard marginal outcomes in $\supp{\ga^A}$.
-Sufficient reasoning will become apparent when presented with a complete discussion of the definite extension procedure.}).
-The weights $\weights\br{\ga^A}$ equal the amount that $\Ga^{A}$ needs to recover by, and the nodes $\nodes\br{\ga^A}$ are simply the union of all edges.
-This weighted hypergraph is termed the \term{antecedent hypergraph}.
-    \begin{remark}
-        The structure of a hypergraph $\hgraph$ (disregarding weights) is best computationally implemented as a bitwise matrix $H$ where the rows of $H$ are in correspondence with the nodes $n \in \nodes$ of $\hgraph$.
-Likewise, the columns of $H$ are in correspondence with the edges $e \in \edges$ of $\hgraph$.
-The entires of $H$ can be populated according to edge inclusion.
-        \[ H_{n,e} = \begin{cases}
-            1 & n \in e \\
-            0 & n \not \in e
-        \end{cases} \]
-        Regarding the antecedent hypergraph $\hgraph\br{\ga^A}$, the matrix form $H\br{\ga^A}$ of $\hgraph\br{\ga^A}$ can be constructed by taking the incidence matrix $M$ and deleting rows not in $\nodes\br{\ga^A}$ and columns not in $\edges\br{\ga^A}$.
-As an example, consider \cref{ex:hypergraph_example} and the hypergraph of \cref{fig:hypergraph_example}.
-The corresponding matrix representation of the hypergraph of \cref{ex:hypergraph_example} is a sub-matrix of the the incidence matrix depicted in \cref{fig:compact_incidence}.
-        \[ H\br{\ga^A} = \kbordermatrix{
-            & j_4 & j_5 & j_6 & j_8 \\
-            m_2 & \kone & \kzer & \kzer & \kzer \\
-            m_4 & \kzer & \kzer & \kzer & \kone \\
-            m_5 & \kzer & \kone & \kzer & \kzer \\
-            m_6 & \kzer & \kzer & \kone & \kzer \\
-            m_{10} & \kone & \kzer & \kzer & \kzer \\
-            m_{11} & \kzer & \kone & \kzer & \kzer \\
-            m_{12} & \kzer & \kzer & \kone & \kone
-        } \]
-        Although it is possible to generate antecedent hypergraphs in this manner, we recommend against it.
-One of the advantages of the definite extension procedure (to be discussed in \cref{sec:advantages_dep}) is that typically the size of an antecedent hypergraph $H$ is \textit{far smaller} than the original incidence matrix $M$.
-For large enough marginal scenarios, $M$ becomes too resource intensive to hold in memory, while $H$ remains far more manageable.
-    \end{remark}
-
-    After generating an antecedent hypergraph $\hgraph\br{\ga^A}$, it is possible to find all valid, homogeneous, non-contextuality inequalities $I_\mscenario = \bc{ \ga \tcdot \probvec^{\mscenario} \geq 0}$ by finding all transversals of $\hgraph\br{\ga^A}$.
-As mentioned previously for each transversal $\trans$, the marginal multi-set $\ga^C$ agreeing with $\trans$ can be constructed,
-    \[ \forall m \in \supp{\trans} : \ga^C_{m} = \trans_m \]
-    Such that $\ga^A + \ga^C$ has definite extension, which by \cref{thm:definite_extension_main_thm} induces the valid inequality,
-    \[ I_\mscenario = \bc{\br{\ga^C + \ga^A} \tcdot \probvec^{\mscenario} \geq 0} \eq \label{eq:transversal_inequality}\]
-    More importantly, one only needs to consider \textit{minimal transversals} of $\hgraph\br{\ga^A}$.
-If a transversal $\trans$ is non-minimal, then there exists another transversal $\trans'$ such that $\trans' \preceq \trans$.
-A minimal transversal $\trans'$ would have correspondence with a tighter inequality $I_\mscenario' = \bc{\br{{\ga'}^C + \ga^A} \tcdot \probvec^{\mscenario} \geq 0}$ that is capable of witnessing contextually in a strictly large subset of marginal models $\probvec^{\mscenario}$.
-\\
-
-    \begin{definition}
-        Let $I_1$ and $I_2$ denote two different $\s{NC}$-inequalities.
-    \end{definition}
-
-    \begin{definition}
-        Let $\s{Y}$ denote the set of all multi-sets $\ga$ with positive semi-definite extensions,
-        \[ \s{Y} = \bc{\ga \mid \ga \tcdot M = \Ga \succeq 0} \]
-        A multi-set $\ga$ is said to be \term{reducible/redundant} if,
-        \[ \exists \ga^1, \ga^2 \in \s{Y} : \ga = \ga^1 + \ga^2, \ga \neq \ga^1 \neq \ga^2 \neq 0 \]
-    \end{definition}
-
-    \todo[TC]{Figure out language and how to delineate the idea of reducible and irreducible extensions}
-
-    Therefore, it is possible to generate a family of \textit{tight} inequalities for each antecedent choice
-
-    \subsubsection{Completeness}
-    \label{sec:completeness_dep}
-    \todo[TC]{FM section would demonstrate that linear, homogeneous, integer inequalities are sufficient} \\
-    \todo[TC]{Talk about how all facets with antecedent order $n$ would be found by DEP at level $n$} \\
-    \todo[TC]{Upper limit of DEP is set by lowest antecedent order of FM result} \\
-    \begin{theorem}
-        \label{thm:completeness}
-        \todo[TC]{main completeness theorem}
-    \end{theorem}
-    \subsubsection{Advantages}
-    \label{sec:advantages_dep}
-    \todo[TC]{Horizontally scalable} \\
-    \todo[TC]{Low Memory Overhead} \\
-    \todo[TC]{Effectively depth-first FM} \\
-    \todo[TC]{Offers partially solution when complete solution intangible} \\
-    \todo[TC]{Weighted transversal algorithms are natural extensions of regular algorithms} \\
-    \todo[TC]{inequalities found at lower orders of DEP hierarchy are either facets or are positively separable into one or more facets} \\
-    \todo[TC]{Symmetries MASSIVELY reduce search space, memory for complete solution (to be discussed)} \\
-    \todo[TC]{Can be adapted to find correlation inequalities} \\
-    \todo[TC]{Can be implemented as a relaxation procedure (becomes regular HT problem)} \\
-    \todo[TC]{Can be adapted to target a specific distribution} \\
-    \todo[TC]{Seed distributions to avoid trivial inequalities} \\
-    \subsubsection{Disadvantages}
-    \label{sec:disadvantages_dep}
-    \todo[TC]{We don't yet know exactly how high the hierarchy goes} \\
-    \todo[TC]{If complete solution is ultimately desired, FM is in principle far more efficient because it does need to prune anything} \\
-    \todo[TC]{Trivial equalities show that lower-order transversals are equivalent to higher order transversals (maybe not)} \\
-    \subsubsection{Unanswered questions}
-    % \todo[TC]{How to avoid regenerating inequalities that are reducible to lower order}
-    % Corollary \ref{cor:linear_integer} alludes to completeness of extension covers.
-It vaguely suggests that every non-contextuality inequality needs to be an extension cover, otherwise there would exist a compatible and deterministic distribution that violates it.
-We will now demonstrate this completeness explicitly by first discussing what is required of a complete solution to the marginal problem.
-    % \begin{definition}
-    %     A \term{complete solution to the marginal problem} is a finite set of $q$ vectors $\gamma_1, \ldots, \gamma_q$ together with $q$ real numbers $k \in \R$
-    % \end{definition}
-    % \begin{theorem}
-    %     \label{thm:complete_solution_log_cover}
-    %     The set of all logical covering inequalities forms a sufficient solution to the possibilistic marginal problem.
-    % \end{theorem}
-    % \begin{theorem}
-    %     \label{thm:complete_solution_ext_cover}
-    %     The set of all extension covering inequalities forms a sufficient solution to the probabilistic marginal problem.
-    % \end{theorem}
-    % \begin{proof}
-    % \end{proof}
-    % \begin{definition}
-    %     An extension cover $\ga{C}$ of $\ga{A}$ is said to be \term{minimal} if there does not exist an extension cover $\ga{C'}$ different from $\ga{C}$ such that,
-    %     \[ \forall j \in \Events{\jointvar} : \ga{C'}_j \leq \ga{C}_j \]
-    % \end{definition}
-
-    % If a more minimal extension cover $\ga{C'}$ does exists, then the inequality it defines (as per \cref{thm:extendable_cover_ineq} directly implies the inequality defined by $\ga{C}$.
-
-    % \begin{definition}
-    %     An extension cover $\ga{C}$ of $\ga{A}$ is said to be \term{reducible} if there exists a \textit{partition} of $\ga{C}$ and $\ga{A}$,
-    %     \[ \ga{C} = \ga{C_1} + \ga{C_2} \qquad \ga{A} = \ga{A_1} + \ga{A_2} \]
-    %     Such that $\ga{C_1}$ is an extension cover for $\ga{A_1}$ and $\ga{C_2}$ is an extension cover for $\ga{A_2}$.
-If $\br{\ga{C}, \ga{A}}$ does \textit{not} admit a partition, then it is said to be \term{irreducible}.
-    % \end{definition}
-
-    % \todo[TC]{Basis certificates}
-
-    % % \begin{algorithm}[H]
-    % % \caption{The Extension Cover Procedure (DEP)}
-    % % \label{alg:ecp}
-    % % \begin{algorithmic}
-    % %   \State $\ga{S}^{0} = \mul{\emptyset}$
-    % % \end{algorithmic}
-    % % \end{algorithm}
-
-    % % \begin{algorithm}
-    % %   \caption{The Extension Cover Procedure (DEP)
-    % %     \label{alg:ecp}}
-    % %   \begin{algorithmic}[1]
-    % %     \Require{An antecedent m-set $\ga{A}$ and a partial consequent m-set $\ga{S}$.}
-    % %     \Statex
-    % %     \Function{DEP}{$\ga{A}, \ga{S}$}
-    % %       % \Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
-    % %       % \Let{$\delta$}{$0$}
-    % %       % \For{$i \gets 1 \textrm{ to } n$}
-    % %       %   \If{$z_i \neq 0$}
-    % %       %     \Let{$\delta$}{$\delta + 1$}
-    % %       %   \EndIf
-    % %       % \EndFor
-    % %       \State \Return{$\delta$}
-    % %     \EndFunction
-    % %   \end{algorithmic}
-    % % \end{algorithm}
-
-    % \todo[TC]{Trivial nodes}
-    % \todo[TC]{Duplication under Deflation}
-    % \todo[TC]{Memory}
-    % \todo[TC]{Parallelization}
-    % \todo[TC]{Simplicial Complex}
-    % \subsubsection{Advantages}
-
-    % \subsubsection{Avoiding Trivial Inequalities}
-    % A \term{trivial compatibility inequality} $I_{\mscenario}$ is an inequality that is satisfied by all marginal models $\prob^{\mscenario}$, not just compatible ones.
-Trivial compatibility inequalities are of no importance Since the set of all extension cover inequalities
-    % \todo[TC]{Targeted Seeds}
-
-    % \begin{definition}
-    %     A \term{hypergraph transversal generation} is any algorithm that correctly generates the complete set of all minimal transversals of $\mathcal{H}$.
-    % \end{definition}
-
-    % \begin{definition}
-    %     Any hypergraph with strictly non-empty edges $\forall e \neq \emptyset$ will always admit the \term{trivial transversal} $\trans^*$ where all nodes are considered as members $\trans^* = \nodes$.
-Any hypergraph with empty edges will be called a \term{degenerate hypergraph} as it admits no transversals\footnote{Most authors require that all hypergraphs be non-degenerate~\cite{Kavvadias_2005}.}.
-    % \end{definition}
-    % Remark ?? guarantees that all marginal hypergraphs are non-degenerate. There are two distinct approaches to hypergraph transversal generation: \textit{top-down} and \textit{bottom-up}.
-    % \begin{definition}
-    %     A \term{top-down} hypergraph transversal generation refers to any algorithm that begins with the trivial transversal $\trans^*$ and iteratively removes unnecessary nodes from $\trans^*$.
-    % \end{definition}
-
-    % \begin{definition}
-    %     A \term{bottom-up} hypergraph transversal generation refers to any algorithm that begins with the empty set $\emptyset$ and iteratively adds nodes.
-    % \end{definition}
-
-    % One should select a top-down method if the typical size of minimal transversals $\abs{\trans}$ is comparable to the number of nodes $\abs{\nodes}$, otherwise a bottom-up method will perform better.
-    % For our purposes we implemented a deep-first transversal algorithm similar to
-    % Recalling
-
-    % \subsection{Weighted Hypergraph Transversals}
-    % In \cref{sec:certificate_inequalities} is was demonstrated that the Fritz distribution is witness-able via a certificate inequality. It is also possible to witness
-    % \todo[TC]{Discuss the Inequalities Derived/ Trivial and non-trivial}
-
-    % \todo[TC]{Weighted transversals and Optimizations}
-    % \todo[TC]{Seeding inequalities (huge advantage here)}
-    \section{Marginal Symmetries}
-    \label{sec:symmetry}
-    Exploiting symmetries of a marginal scenario are useful for a few distinct reasons.
-First, Bancal et.
-al.~\cite{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:comp_con_mp}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
-They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that quantum-non-trivial inequalities can be recovered from facets of a symmetric polytope.
-Numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
-The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.\\
-
-    In this section we discuss how to exploit symmetries in the definite extension procedure in order to reduce the size of the computational search space.
-In contrast to~\cite{Bancal_2010}, we gain advantage in a non-lossy way; symmetries drastically accelerate the rate in which the DEP finds facets of the unsymmetrical polytope.
-\\
-
-    To demonstrate what types of symmetries we have in mind, we present the following example:
-    \begin{example}
-        \label{ex:symmetries}
-        First consider the marginal scenario $\mscenario = \bc{\bc{a, b, c}, \bc{c, d}, \bc{a, d}}$ where each variable in $\jointvar = \bc{a,b,c,d}$ has binary outcomes: $O_a = O_b = O_c = O_d = \bc{0,1}$.
-Moreover, let $I_{\mscenario}$ be a $\s{NC}$-inequality,
-        \[ I_{\mscenario} = \bc{\prob[abc][010] \leq \prob[cd][00] + \prob[ad][01]}  \]
-        Intuitively, a the contextuality of $\probvec^{\mscenario}$ is independent of the how one labels outcomes.
-Therefore new $\s{NC}$-inequalities can be generated from $I_{\mscenario}$ by permuting its outcomes.
-Let $\geo_v : O_v \to O_v : \bc{0,1} \mapsto \geo_v\bs{\bc{0,1}} = \bc{1,0}$ be a permutation of the outcomes for variable $v$; i.e.
-$\geo_v$ ``flips'' the outcomes for $v$.
-Let $\geo = \geo_a \times \geo_c$ be the permutation of variables $a$ and $c$.
-The action of $\geo$ on outcome labels induces an action on the inequality $I_{\mscenario}$ itself,
-        \begin{align*}
-        \geo\bs{I_{\mscenario}} &= \bc{\prob[abc][\geo\bs{010}] \leq \prob[cd][\geo\bs{00}] + \prob[ad][\geo\bs{01}]} \\
-        &= \bc{\prob[abc][111] \leq \prob[cd][10] + \prob[ad][11]}
-        \end{align*}
-        The new inequality $\geo\bs{I_{\mscenario}}$ is also a valid $\s{NC}$-inequality.
-By design, any permutation $\geo$ over outcomes leaves the marginal scenario invariant ($\geo\bs{\mscenario} = \mscenario$) and thus we may write $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$.
-\\
-
-        Alternatively, permutations of the variables themselves are also permitted.
-Let $\gep : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \gep\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ be a permutation of the variables $\jointvar$.
-Intuitively $\gep$ acts on $I_{\mscenario}$ in the following way,
-        \begin{align*}
-        \gep\bs{I_{\mscenario}} &= \bc{\prob[\gep\bs{abc}][010] \leq \prob[\gep\bs{cd}][00] + \prob[\gep\bs{ad}][01]} \\
-        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
-        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
-        \end{align*}
-        In general (as in this example), permutations over all variables can modify the marginal scenario $\gep\bs{\mscenario} \neq \mscenario$; in general we write $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
-Although $\gep\bs{I_{\mscenario}}$ is in fact a valid $\s{NC}$-inequality, in constrains marginal models of a different marginal scenario $\gep\bs{\mscenario}$ and are in general of no interest.
-    \end{example}
-
-    \subsection{Marginal Symmetries}
-    As demonstrated by \cref{ex:symmetries}, permutations can be applied to inequalities themselves to generate new inequalities.
-To formalize this notion, let $\Perm{S}$ denote the \term{permutation group} acting on the set $S$ consisting of all bijective maps $\pi : S \to S$.
-    \[ \Perm{S} = \bc{\pi : S \to S} \eq \label{eq:permutation_group_def}\]
-    Together with the $\abs{S}\times\abs{S}$ permutation matrix $\PermM{\pi}$ for each permutation $\pi$,
-    \[ \forall i,j \in S : \quad {\PermM{\pi}}_{;i,j} \defined \begin{cases}
-        1 & \pi\br{i} = j\\
-        0 & \pi\br{i} \neq j\\
-    \end{cases} \]
-
-    \begin{definition}
-        A \term{marginal symmetry} of $\mscenario$ is a symmetry of the incidence matrix $M$ corresponding to a pair of permutations $\br{\pi_\mscenario \in \Perm{\Events{\mscenario}}, \pi_\jointvar\in \Perm{\Events{\jointvar}}}$ such that $M$ is invariant under permutation.
-        \[ \PermM{\pi_\mscenario} \tcdot M \tcdot \PermM{\pi_\jointvar} = M \]
-    \end{definition}
-
-    Identifying the set of all marginal symmetries for a given marginal model is very important; it allows one to generate new inequalities from known ones.
-
-    \begin{theorem}
-        \label{thm:inequalities_generated_symmetries}
-        For each $\s{NC}$-inequality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ and marginal symmetry $\br{\pi_{\mscenario}, \pi_{\jointvar}}$, the inequality $\pi_{\mscenario}\bs{I_{\mscenario}}$ defined by,
-        \[ \pi_{\mscenario}\bs{I_{\mscenario}} \defined \bc{\pi^{-1}_{\mscenario}\bs{\ga} \tcdot \probvec^{\mscenario} \geq 0} \eq \label{eq:thm:inequalities_generated_symmetries}\]
-        is also a valid $\s{NC}$-inequality.
-    \end{theorem}
-    \begin{proof}
-        Since $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ is a $\s{NC}$-inequality, then by \cref{thm:definite_extension_main_thm}, $\ga \tcdot M = \Ga \succeq 0$.
-Also note that $\PermM{\pi_{\jointvar}}$ is invertible with $\PermM{\pi_{\jointvar}}^{-1} = \PermM{\pi^{-1}_{\jointvar}}$.
-Therefore,
-        \[ \Ga\tcdot\PermM{\pi_{\jointvar}}^{-1} = \ga \tcdot M \tcdot \PermM{\pi_{\jointvar}}^{-1} = \ga\tcdot \PermM{\pi_{\mscenario}}\tcdot M \]
-        But $\Ga \succeq 0 \implies \Ga\tcdot\PermM{\pi_{\jointvar}}^{-1} \succeq 0$. Thus,
-        \[ \ga\tcdot\PermM{\pi_{\mscenario}}\tcdot M \succeq 0 \eq \label{eq:thm:inequalities_generated_symmetries_step}\]
-        Interpreting $\ga\tcdot\PermM{\pi_{\mscenario}}$ as a multi-set for $\mscenario$,
-        \[ \forall m \in \Events{\mscenario} : \br{\ga\tcdot\PermM{\pi_{\mscenario}}}_m = \ga_{\pi^{-1}_{\mscenario}\bs{m}} \defined \pi^{-1}_{\mscenario}\bs{\ga}_m \]
-        Therefore \cref{eq:thm:inequalities_generated_symmetries_step} shows that $\pi^{-1}_{\mscenario}\bs{\ga}$ has a positive semi-definite extension and thus \cref{thm:definite_extension_main_thm} proves that \cref{eq:thm:inequalities_generated_symmetries} is also a valid $\s{NC}$-inequality.
-    \end{proof}
-    \begin{remark}
-        There are two equivalent interpretations for the permuted inequality $\pi_{\mscenario}\bs{I_{\mscenario}}$ of \cref{thm:inequalities_generated_symmetries}. Notice,
-        \[ \pi^{-1}_{\mscenario}\bs{\ga} \tcdot \probvec^{\mscenario} = \ga \tcdot \La_{\pi_{\mscenario}} \tcdot \probvec^{\mscenario} = \ga \tcdot \pi_{\mscenario}\bs{\probvec}^{\mscenario} \]
-        Which means one can either think of $\pi_{\mscenario}\bs{I_{\mscenario}}$ as being $I_{\mscenario}$ with the coefficients rearranged, or with the probabilistic assignments rearranged.
-    \end{remark}
-
-    \todo[TC]{Discuss the importance of symmetries to restrict branching in DEP}
-
-    Diagrammatically, for each marginal event $m \in \Events{\mscenario}$ and joint event $j \in \Events{\jointvar}$, the notion of extendability is preserved by $\br{\pi_\mscenario, \pi_\jointvar}$.
-    \begin{center}
-        \begin{tikzpicture}
-            \newcommand{\symmetryspace}{1.5};
-            \draw (0, \symmetryspace) node[](m){$m$};
-            \draw (\symmetryspace, \symmetryspace) node[](j){$j$};
-            \draw (0, 0) node[](pm){$\pi_{\mscenario}\bs{m}$};
-            \draw (\symmetryspace, 0) node[](pj){$\pi_{\jointvar}\bs{j}$};
-
-            \draw[->] (m) -- node[left]{$\pi_\mscenario$}(pm);
-            \draw[->] (j) -- node[right]{$\pi_\jointvar$}(pj);
-            \draw[-<] (m) -- (j);
-            \draw[-<] (pm) -- (pj);
-        \end{tikzpicture}
-    \end{center}
-    Fortunately, every incidence matrix $M$ has a useful \term{uniqueness property}: there are no duplicated columns or rows in $M$.
-This means that in every marginal symmetry $\br{\pi_\mscenario, \pi_\jointvar}$, $\pi_\jointvar$ is uniquely determined by $\pi_\mscenario$ and vice versa.
-Therefore we restrict our attention and discussions to row permutations $\pi_\mscenario$, with column permutations being in one-to-one correspondence.
-Henceforth we will denote to the most general marginal symmetry using $\pi$ and take it to mean a permutation over marginal events.
-\\
-
-    \subsection{Outcome Symmetry}
-    \label{sec:outome_label_symmetry}
-    \begin{definition}
-        The \term{outcome symmetry group} $\go$ for the set of joint variables $\jointvar = \bc{v_1, \ldots, v_n}$ is the direct product of permutations over the outcomes for each variable $v \in \jointvar$,
-        \[ \go \defined \Perm{O_{v_1}} \times \cdots \times \Perm{O_{v_n}} = \prod_{v \in \jointvar} \Perm{O_{v}} \]
-        The action of $\geo \in \go$ on any event $s \in \Events{V}$ (denoted $\geo\bs{s}$) where $V \subseteq \jointvar$ is defined as,
-        \[ \forall v \in \Dom{s} : \br{\geo\bs{s}}\br{v} \defined \geo\bs{s\br{v}} \eq \label{eq:act_on_outcome_label}\]
-    \end{definition}
-    \begin{theorem}
-        \label{thm:extendable_invariance_acto}
-        If a marginal event $m \in \Events{\mscenario}$ is extendable to the joint event $j \in \Events{J}$, then for any outcome permutation $\geo \in \go$, $\geo\bs{m}$ is extendable to $\geo\bs{j}$.
-        \[ m \ext j \iff \geo\bs{m} \ext \geo\bs{j} \eq \label{eq:extendable_invariance_acto}\]
-    \end{theorem}
-    \begin{proof}
-        The proof should be clear by the definition of extendability (\cref{def:section_extendable}).
-        \[ m \ext j \iff \forall v \in \Dom{m} : j\br{v} = m\br{v} \]
-        Every outcome permutation $\geo \in \go$ leaves the domain of the event invariant $\Dom{m} = \Dom{\geo\bs{m}}$. Thus by \cref{eq:act_on_outcome_label},
-        \begin{align*}
-        \forall v \in \Dom{\geo\bs{m}}: \br{\geo\bs{j}}\br{v} = \geo\bs{j\br{v}} = \geo\bs{m\br{v}} = \br{\geo\bs{m}}\br{v}
-        \end{align*}
-        Therefore we have that $m \ext j \implies \geo\bs{m} \ext \geo\bs{j}$. The left implication of \cref{eq:extendable_invariance_acto} follows by considering $\geo^{-1} \in \go$.
-    \end{proof}
-    \begin{corollary}
-        \label{coll:incidence_invariance}
-        Let $M$ be the incidence matrix for a marginal scenario $\mscenario$ and $\geo \in \go$ be an outcome permutation of the joint random variables $\jointvar$.
-By \cref{thm:extendable_invariance_acto}, the action of $\geo$ on $M$ leaves $M$ invariant ($\geo\bs{M} = M$),
-        \[ \geo\bs{M}_{m,j} \defined M_{\geo\bs{m},\geo\bs{j}} = \de_{\geo\bs{m} \ext \geo\bs{j}} = \de_{m \ext j} = M_{m,j} \eq \label{eq:incidence_invariance}\]
-    \end{corollary}
-    \subsection{Variable Symmetry}
-
-    In \cref{sec:outome_label_symmetry}, permutations of outcomes were introduced as symmetries of the incidence matrix $M$.
-However the proof of \cref{thm:inequalities_outcome_label_generation} indicates that any permutation leaving the incidence matrix intact can be used to generate new inequalities.
-\\
-
-    Following the observations of \cref{ex:symmetries}, it is always possible to permute the random variables in a marginal scenario to produce new and valid inequalities.
-A generic permutation group over a the complete set of variables $\jointvar$ is simply $\Perm{\jointvar}$.
-Unlike elements of $\Om$, permutations $\gep \in \Perm{\jointvar}$ have the undesired possibility of transforming $\mscenario$ into a different marginal scenario.
-    \[ \gep\bs{\mscenario} \defined \bc{\gep\bs{V_1}, \ldots, \gep\bs{V_k}} \neq \mscenario \]
-    This means that there could exist $V_i \in \mscenario$ such that $\gep\bs{V_i} \not \in \mscenario$.
-In particular, permutations $\gep$ retaining this property are unable to generate $\s{NC}$-inequalities over the same marginal scenario.
-
-    \begin{definition}
-        The \term{variable permutation group} $\gp$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario.
-        \[ \Phi \defined \bc{\gep \in \Perm{\jointvar} \mid \forall V \in \mscenario : \gep\bs{V} \in \mscenario} \]
-        The action of $\gep \in \gp$ on any outcome $f \in \Events{V}$ (denoted $\geo\bs{f}$) is defined as,
-        \[ \forall v \in \Dom{\gep\bs{f}} : \br{\gep\bs{f}}\br{v} \defined f\br{\gep^{-1}\bs{v}} \eq \label{eq:act_on_variable}\]
-    \end{definition}
-
-    \subsection{Causal Symmetry}
-
-    The aim of this section is to formalize what types of symmetries are present in a particular causal structure $\graph$.
-The group of these causal symmetries will define, for each compatibility inequality $I_{\mscenario}$, a family of inequalities that are also valid incompatibility inequalities.
-
-    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\gep$ from $N$ to $N$.
-    \[ \Perm{N} = \bc{\gep \mid \gep : N \to N} \]
-    The action of $\gep \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\gep$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
-    \begin{align*}
-    \gep\bs{\graph} &\defined \br{\gep\bs{\nodes}, \gep\bs{\edges}} \\
-    \gep\bs{\nodes} &\defined \bc{\gep\bs{n} \mid n \in \nodes} = \nodes \\
-    \gep\bs{\edges} &\defined \bc{\gep\bs{e} \mid e \in \edges}
-    \end{align*}
-    To motivate a more general treatment of such symmetries, consider the Triangle Scenario of \cref{fig:triangle_scenario}.
-Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\gep \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\gep\bs{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes.
-By construction, any valid compatibility inequality $I_{\mscenario}$ for the marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes.
-Therefore applying $\gep$ to all distributions in $I_{\mscenario}$ yields $\gep\bs{I_{\mscenario}} \defined \gep\bs{I}_{\gep\bs{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\gep\bs{\mscenario}$ defined as,
-    \[ \gep\bs{\mscenario} = \bc{\gep\bs{V_1}, \ldots, \gep\bs{V_k}} \]
-    % \begin{example}
-    %     \todo[TC]{Above trivial example.}
-    %     Consider the marginal scenario $V_{\bs{4}} = \bc{\bc{A,B,C}, \bc{A}, \bc{B}, \bc{C}}$ and the compatibility inequality $I_{\bc{ABC, A, B, C}}$ for the Triangle Scenario in \cref{fig:triangle_scenario} with the following form,
-    %     \[ \prob[ABC][002]\prob[ABC][003] \leq \prob[A][0]\prob[C][3] \]
-    %     Now consider $\gep = \bc{A \to A, B \to C, C \to B}$. Since $\gep\bs{\graph} = \graph$, $\gep\bs{I_{\mscenario}}$ is also a valid compatibility inequality,
-    % \end{example}
-    More generically, any permutation $\gep$ that preserves the graphical structure of $\graph$ can be applied to $I_{\mscenario}$ to generate new and valid compatibility inequalities.
-Specifically this alludes to the \term{graph automorphism group} $\Aut{\graph}$ of $\graph$.
-    \[ \Aut{\graph} \defined \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph} \]
-    In general, $\Aut{\graph}$ could include elements $\gep$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}.
-This behaviour is \textit{undesired} for causal inference where the latent nodes will never appear in a marginal scenario.
-Instead, the subgroup of $\Aut{\graph}$ that never maps observable nodes to latent nodes is the \term{set-wise stabilizer} of $\Aut{\graph}$ for $\nodes_O$ and will be expressed with a subscript.
-
-    \begin{definition}
-        The \term{causal symmetry group} for a causal structure $\graph$ is the graph automorphism subgroup that stabilizes the observable nodes.
-        \[ \Aut[\nodes_O]{\graph} = \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph, \forall n \in \nodes_O :\gep\bs{n} \in \nodes_O} \]
-        Given any compatibility inequality $I_{\mscenario}$, each element $\gep$ of the causal symmetry group defines a new valid compatibility inequality $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
-    \end{definition}
-
-    The inflation technique discussed in \cref{sec:summary_inflation} allows one to derive compatibility inequalities for a causal structure $\graph$ by considering the marginal problem over the pre-injectable sets of $\graph'$ denoted $\PreInj[\graph]{\graph'} = \bc{V_1, \ldots, V_k}$.
-It is important to recall that due to \cref{lem:inflation}, inequalities $I'$ for $\graph'$ are \textit{only} transferable to inequalities $I$ for $\graph$ if $I'$ is in terms of distributions over the pre-injectable sets $I'_{\PreInj[\graph]{\graph'}}$.
-As a consequence of this observation, we need to consider a subgroup of the causal symmetry group that preserves the pre-injectable sets,
-    \[ \gep\bs{\PreInj[\graph]{\graph'}} = \PreInj[\graph]{\graph'} \eq \label{eq:preserved_preinj} \]
-
-    \begin{definition}
-        The \term{restricted causal symmetry group} $\gp$ for a causal structure $\graph$ and a marginal scenario $\mscenario$ is the graph automorphism subgroup that stabilizes the marginal scenario $\mscenario$.
-        \[ \gp \defined \Aut[\mscenario]{\graph} = \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph, \forall V \in \mscenario : \gep\bs{V} \in \mscenario} \]
-        Given any compatibility inequality $I_{\mscenario}$ each element $\gep$ of the causal symmetry group defines a new valid compatibility inequality $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\mscenario}$ over the \textit{same} marginal context $\mscenario$.
-    \end{definition}
-
-    The restricted causal symmetry group for the pre-injectable sets of an inflation $\graph'$ is the ideal symmetry group for use with the inflation technique.
-If one obtains a particular inequality $I'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\gp$, an entire family of valid compatibility inequalities are also obtained.
-    \[ \bc{\gep\bs{I'}_{\PreInj[\graph]{\graph'}} \mid \gep \in \gp} \text{ where } \gp = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
-    We have obtained $\gp$ for the inflated triangle scenario \cref{fig:inflated_triangle_scenario}. $\gp$ is an order $48$ group with the following $4$ generators:
-    \begin{equation*}
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_1 \\
-    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_2 \\
-    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_3 \\
-    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_4 \\
-    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
-    \end{aligned}
-    \end{equation*}
-    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
-    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
-    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
-    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
-    It is easy to verify that $\gep_1, \gep_2, \gep_3, \gep_4$ are all automorphisms of the inflated Triangle Scenario $\graph'$ of \cref{fig:inflated_triangle_scenario}.
-Moreover they stabilize the observable nodes, and the map pre-injectable sets of \cref{eq:pre-injectable_triangle_scenario} to the pre-injectable sets.
-Finally, in the Triangle Scenario we have that,
-    \[ \gp = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \sim \Aut[\nodes_O]{\graph} \]
-    To see this, $\gep_1$ and $\gep_4$ become the identity element $\mathbb{I}$ in $\Aut[\nodes_O]{\graph}$ upon removal of the copy-index, leaving $\gep_2$ to generate reflections and $\gep_3$ to generate rotations.
-    \subsection{Symmetric Marginal Polytope}
-    Up until this point, we have discussed how new inequalities can be created from known ones by exploiting causal symmetry.
-Although very useful, we divert our attention to finding \textit{symmetric} inequalities themselves.
-    \[ \forall \gep \in \gp :  \gep\bs{I_{\mscenario}} = I_{\mscenario} \]
-    In order to do this, we must first define how elements $\gep \in \gp$ act on marginal outcomes $O_{\mscenario}$.
-    \begin{definition}
-        Let $\jointvar = \bc{v_1, \ldots, v_k}$ be a collection of random variables and let $\gep \in \Perm{\jointvar}$.
-$\jointvar$ is said to be \term{label invariant with respect to $\gep$} if the outcome labels for each variable $v \in \jointvar$ are unchanged under the action of $\gep$.
-        \[ \forall v \in \jointvar : O_{v} = O_{\gep\bs{v}} \]
-        Label invariance is a prerequisite for any kind of symmetry amoung random variables.
-    \end{definition}
-    \begin{definition}
-        Let $\jointvar = \br{v_1, \ldots v_k}$ be a collection of random variables along with a specific outcome $m \in \Events{V}$ where $V \subseteq \jointvar$.
-The action of $\gep \in \Perm{\jointvar}$ on $m$ is a new outcome $\gep\bs{m} \in \Events{\gep\bs{V}}$ over $\gep\bs{V} \subseteq \jointvar$ defined as follows,
-        \[ \forall v \in V : \br{\gep\bs{m}}\br{\gep\bs{v}} \defined m \br{v} \]
-        The idea being that $\gep$ modifies $m$ in such a way that permutes its domain while leaving its range invariant.
-    \end{definition}
-    \begin{example}
-        Consider the outcome $m = \bc{A \mapsto 0, B \mapsto 1, C \mapsto 2} \in \Events{\bc{A,B,C}}$ where all variables have $4$ possible outcomes $O_A = O_B = O_C = \bc{0,1,2,3}$ and the permutation $\gep = \bc{A \to D, B \to C, C \to B, D \to A}$.
-        The \textit{action} of $\gep$ on $m$ is as follows,
-        \begin{align*}
-            \gep\bs{m} &= \gep\bs{\bc{A \mapsto m\br{A}, B \mapsto m\br{B}, C \mapsto m\br{C}}} \\
-            &= \bc{\gep\bs{A} \mapsto m\br{A}, \gep\bs{B} \mapsto m\br{B}, \gep\bs{C} \mapsto m\br{C}} \\
-            &= \bc{D \mapsto m\br{A}, C \mapsto m\br{B}, B \mapsto m\br{C}} \\
-            &= \bc{D \mapsto 0, C \mapsto 1, B \mapsto 2} \\
-            &= \bc{B \mapsto 2, C \mapsto 1, D \mapsto 0}
-        \end{align*}
-        Evidently, $\gep\bs{m} \in \Events{\bc{B, C, D}}$.
-    \end{example}
-
-    Through repeated action of $\gep \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define group orbits of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$.
-    \begin{align*}
-        \Orb[\gp]{m} &\defined \bc{\gep\bs{m} \mid \gep \in \gp} \\
-        \Orb[\gp]{j} &\defined \bc{\gep\bs{j} \mid \gep \in \gp}
-    \end{align*}
-
-    \begin{definition}
-        The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and a particular restricted causal symmetry $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
-Each row of $M_{\gp}$ corresponds to a marginal orbit $\Orb[\gp]{m}$.
-Analogously each column of $M_{\gp}$ corresponds to a joint orbit $\Orb[\gp]{j}$.
-The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
-        \[ M_{\gp}\bs{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M\bs{m',j'} \]
-    \end{definition}
-
-    \subsection{Results}
-
-    \todo[TC]{How we obtained the desired symmetry group}
-    \todo[TC]{Group orbits to symmetric marginal description matrix}
-    \todo[TC]{representative antecedents completely solve the marginal problem}
-
-    \section{The Triangle Scenario}
-    \label{sec:triangle_scenario}
-    \begin{figure}
-    \begin{center}
-        \begin{minipage}[b]{.48\textwidth}
-            \centering
-            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
-            \caption{The casual structure of the Triangle Scenario. Three variables $A,B,C$ are observable and illustrated as triangles, while $X, Y, Z$ are latent variables illustrated as circles.}
-            \label{fig:triangle_scenario}
-        \end{minipage}\hspace{0.04\textwidth}%
-        \begin{minipage}[b]{.48\textwidth}
-            \centering
-            \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
-            \caption{An inflated causal structure of the Triangle Scenario \cref{fig:triangle_scenario}.}
-            \label{fig:inflated_triangle_scenario}
-        \end{minipage}
-    \end{center}
-    \end{figure}
-
-    The triangle scenario $\ts$ is a causal structure composed of $3$ parties $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
-It has that has been studied extensively in existing literature (see~\cite[Fig.
-1]{Steudel_2010},~\cite[Fig.
-6]{Chaves_2014},~\cite[Fig.
-8]{Branciard_2012},~\cite[Fig.
-8, Appendix E]{Henson_2014},~\cite[Fig.
-3]{Fritz_2012},~\cite[Fig.
-1]{Inflation}, $\ldots$) and is reproduced here in \cref{fig:triangle_scenario} for convenience.
-At the time of publication for~\cite{Branciard_2012} it was noted that characterizing locality in $\ts$ remained an open problem and that identifying locality constraints in this configuration seemed challenging.
-In~\cite{Henson_2014}, $\ts$ was classified as an ``interesting'' causal structure.\footnote{Indicating that conditional independence relations are not a sufficient characterization of compatibility for $\ts$~\cite{Henson_2014}.
-Note that in $\ts$ there are \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Additionally $\ts$ is presented along with a family of entropic inequalities that constrain the set of compatible distributions~\cite{Henson_2014}.
-Furthermore in~\cite{Fritz_2012}, Fritz demonstrated that $\ts$ is the \textit{smallest} correlation scenario in which their exists quantum incompatible distributions by explicitly mentioning one (which we elect to call the \textit{Fritz distribution} in \cref{sec:fritz_dist}) and poses an important question asking if other incompatible quantum distributions exist.
-Finally in~\cite{Inflation}, Wolfe et.
-al.
-make use of $\ts$ along with the Bell Scenario to demonstrate a novel technique for causal inference called the \textit{inflation technique} (summarized in \cref{sec:summary_inflation}).
-Wolfe et.
-al.
-validate the power and applicability of the inflation technique by proving incompatibility between $\ts$ and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints~\cite{Inflation}.
-Moreover, a family of polynomial, $2$-outcome, compatibility inequalities are explicitly derived for an exemplary inflation of $\ts$ and $37$ non-trivial representatives are printed in~\cite{Inflation}.
-
-    Identifying quantum-accessible distributions that are incompatible with the triangle scenario is of particular importance as it \todo[TC]{Discuss why we are doing this.}
-
-    As a preliminary search for quantum incompatibility in $\ts$, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements (see \cref{sec:param_quantum_states} for details) against the $37$ compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by~\cite{Henson_2014}.
-Unfortunately, none of these inequalities could be violated.
-These early results suggest, although do not prove, that quantum non-locality is not present in $\ts$ for \textit{two-outcome} measurements.
-We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in $\ts$ for a larger number of outcomes.
-
-    Specifically, we make use of the inflation technique for an inflated triangle scenario $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} and cast the \textit{causal compatibility} problem as a \textit{marginal problem}.
-We develop a new technique which we call the \textit{definite extension procedure (DEP)} to find a complete solution to the marginal problem that is suitable for large causal structures where the observable nodes are equipped with numerous outcomes.
-We use this technique to find numerous compatibility inequalities, some of which witness the incompatibility of the Fritz distribution.
-Before discussing the DEP, the Fritz distribution will be re-defined explicitly here, followed by a quick summary of the inflation technique of~\cite{Inflation}.
-Following these summaries of existing work, we present the DEP and its connection to Hardy-type paradoxes~\cite{Inflation,Liang_2011,Mansfield_2012}, certificate inequalities and logical Bell inequalities~\cite{Abramsky_2011}.
-Moreover, the DEP can be adapted to derive symmetric inequalities or inequalities bounding any subspace of marginal models.
-To conclude, we subject our found inequalities to non-linear optimizations and discuss the implications of our results.
-
-    \section{The Fritz Distribution}
-    \label{sec:fritz_dist}
-    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario~\cite{Fritz_2012}.
-Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
-    \begin{align*}
-    \eq \label{eq:fritz_dist}
-    \begin{split}
-    \prob[F][111] = \prob[F][221] = \prob[F][412] = \prob[F][322] = \prob[F][233] = \prob[F][143] = \prob[F][344] = \prob[F][434] &= \f{1}{32}\br{2 + \sqrt{2}} \\
-    \prob[F][121] = \prob[F][211] = \prob[F][422] = \prob[F][312] = \prob[F][243] = \prob[F][133] = \prob[F][334] = \prob[F][444] &= \f{1}{32}\br{2 - \sqrt{2}}
-    \end{split}
-    \end{align*}
-    Here the notation $\prob[F][abc] = \prob[ABC][abc] = \prob[][A=a,B=b,C=c]$ is used. The Fritz distribution $\prob[F]$ can be realized with the following quantum configuration:
-    \begin{equation}
-    \begin{gathered}
-    \label{eq:fritz_quantum_realization}
-    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\gp^+}\bra{\gp^+} \\
-    M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
-    M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
-    M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
-    \end{gathered}
-    \end{equation}
-    Where for convenience of notation $\psi_x$ is used to denote the superposition,
-    \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
-    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\gp^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.
-
-    Fritz first proved it's incompatibility~\cite{Fritz_2012} by showing $C$ acts a moderator to ensure measurement pseudo-settings for $A$ and $B$ are independent, satisfying non-broadcasting requirements for the standard Bell scenario.
-In fact, by coarse-graining outcomes for $A$ and $B$ and treating $C$ as a measurement-setting moderator, $P_F$ maximally violates the CHSH inequality.
-To illustrate this, begin with the CHSH inequality~\cite{CHSH_Original},
-    \[ \ba{AB|S_A=1, S_B=1} + \ba{AB|S_A=1, S_B=2} + \ba{AB|S_A=2, S_B=1} - \ba{AB|S_A=2, S_B=2} \leq 2 \eq \label{eq:CHSH}\]
-    Where $\ba{AB|S_A=i, S_B=j}$ is the correlation between $A$ and $B$ given the measurement settings for $A$ ($B$) is $i$ ($j$) respectively.
-Next each of $C$'s outcomes become the conditioned settings in \cref{eq:CHSH},
-    \[ \ba{AB|C=2} + \ba{AB|C=3} + \ba{AB|C=4} - \ba{AB|C=1} \leq 2 \eq \label{eq:chsh_c}\]
-    Finally, specifying the two outcome coarse-graining as $\bc{1,2,3,4} \rightarrow \bc{\br{1,4}, \br{2,3}}$ gives a definition of correlation,
-    \[ \ba{AB} \defined 2\bc{\prob[][11] + \prob[][14] + \prob[][41] + \prob[][44] + \prob[][22] + \prob[][23] + \prob[][32] + \prob[][33]} - 1 \]
-    Which when applied to the Fritz distribution \cref{eq:fritz_dist} gives the following correlations:
-    \begin{gather*}
-    \ba{AB|C=2} = 2 \bc{\f{1}{32}\bs{2\br{2+\sqrt{2}}+2\br{2-\sqrt{2}}}} - 1 = \f{\sqrt{2}}{2} \\
-    \ba{AB|C=3} = \ba{AB|C=4} = \f{\sqrt{2}}{2} \quad \ba{AB|C=1} = -\f{\sqrt{2}}{2}
-    \end{gather*}
-    Which when applied to \cref{eq:chsh_c} gives the familiar Tsirelson violation of $2\sqrt{2} \not\leq 2$~\cite{Cirelson_1980}.
-
-    Before continuing it is worth noting that \cref{eq:fritz_dist} is non-unique.
-Any distribution that is equal to \cref{eq:fritz_dist} via a permutation of outcomes or exchange of parties is also referred to as a Fritz distribution.
-Moreover, the quantum realization of \cref{eq:fritz_quantum_realization} is non-unique.
-In fact, \cref{eq:fritz_quantum_realization} is not the realization that Fritz originally had in mind.
-Nonetheless \cref{eq:fritz_dist} is taken as \textit{the} Fritz distribution for concreteness throughout this paper.
-
-    In~\cite{Fritz_2012}, Fritz posits the following question: \textit{Find an example of non-classical quantum correlations in $\ts$ together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}
-
-    \todo[TC]{Summarize Problem 2.17 in fritz BBT, make it more formal}
-
-    \section{Summary of the Inflation Technique}
-    \label{sec:summary_inflation}
-    The causal inflation technique, first pioneered by Wolfe, Spekkens, and Fritz~\cite{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of Ref.~\cite{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a probability distribution is compatible or incompatible with a given causal structure.
-As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
-Copies of the original nodes are distinguished by an additional subscript called the \term{copy-index}.
-For example node $A$ of \cref{fig:triangle_scenario} has copies $A_1, A_2, A_3, A_4$ in the inflation of \cref{fig:inflated_triangle_scenario}.
-Following the notions of Ref.~\cite{Inflation}, all such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
-A copy-index is effectively arbitrary, so $A'$ will refer to an arbitrary inflated copy of $A$.
-    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
-    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if $X = Y$ upon removal of the copy-index.
-Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
-    \begin{definition}
-        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
-        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
-    \end{definition}
-    The motivation being that since the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
-To do this, first notice that every compatible joint distribution $\prob[\nodes]$ uniquely defines a set of causal parameters for $\graph$.
-    \[ \forall n \in \nodes : \prob[n\mid \Pa[\graph]{n}] = \sum_{\nodes \setminus n} \prob[\nodes] \eq \label{eq:unique_causal_parameters}\]
-    Now since \cref{eq:inflation_defn} enforces that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$, one can create a set of \term{inflated causal parameters} using \cref{eq:unique_causal_parameters},
-    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \]
-    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course not all compatible joint distributions on $\nodes'$ are constructed in this way; all that is demonstrated is that all joint distributions constructed in this way are compatible.}.
-    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \]
-    This is known as the \term{weak inflation lemma}; compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$.
-Before generalizing to the inflation lemma, a careful observation needs to be made.
-For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$ over $N$ induces a compatible marginal distribution $\prob[N']$ over $N'$.
-In fact since $N'$ contains no duplicate nodes up to copy index (simply because $N \sim N'$ and $N$ cannot contain duplicate nodes), $\prob[N] = \prob[N']$.
-We refer such sets $N'$ as the \term{injectable sets} of $\graph'$ and $N$ the \term{images of the injectable sets} of $\graph$.
-    \begin{align*}
-        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
-        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
-    \end{align*}
-
-    \begin{lemma}
-        \label{lem:inflation}
-        \term{The Inflation Lemma} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-        This is lemma 3 of~\cite{Inflation}.
-    \end{lemma}
-
-    The inflation lemma is the most important result of the causal inflation technique~\cite{Inflation}.
-The contrapositive version of \cref{lem:inflation} is a powerful tool for determining compatibility.
-Any compatibility constraint on marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ of the inflated causal structure $\graph'$ correspond to valid compatibility constraints on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure.
-Corollary 5 of~\cite{Inflation} proves this explicitly for incompatibility inequalities $I$; which the remainder of this work focuses on.
-Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
-Therefore, in situations where latent nodes are present in $\graph$, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
-
-    In this work, we obtain inequalities that constrain the set of injectable marginal models $\bc{\prob[N'] \mid N' \in \ImInj[\graph]{\graph'}}$ for the inflated Triangle Scenario of \cref{fig:triangle_scenario} by considering the marginal problem (see \cref{sec:comp_con_mp}) for the set of \term{maximally pre-injectable sets}\footnote{The set of all pre-injectable sets forms a topological \textit{simplicial conplex}.
-`Maximal' refers to the pre-injectable sets that are no proper subset of another.}.
-A pre-injectable set $V$ is a subset of $\nodes'$ that can be decomposed into the disjoint union of injectable sets $V = \coprod_i N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ that are mutually \term{ancestrally independent},
-    \[ \forall i,j : N'_i \ancestralindep N'_j \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset  \]
-    In doing so, any distribution over all nodes of a pre-injectable set $\prob[\cup_i N'_i]$ will factorize according to graphical $d$-separation conditions~\cite{Pearl_2009},
-    \[ \prob[V] = \prob[\cup_i N'_i] = \prod_{i}\prob[N'_i] \]
-    This turns linear inequalities over the pre-injectable distributions into polynomial inequalities over the injectable distributions, allowing one to replace all such distributions with equivalent distributions over the original random variables of $\nodes$.
-$\PreInj[\graph]{\graph'}$ will denote the set of all pre-injectable sets.
-
-    Focusing on the inflation $\ts'$ depicted in \cref{fig:inflated_triangle_scenario}, we obtained the injectable sets $\Inj[\ts]{\ts'}$ along with the maximally pre-injectable sets through a simple graphical procedure outlined in~\cite{Inflation}.
-    \begin{equation*}
-        \eq \label{eq:pre-injectable_triangle_scenario}
-        \begin{gathered}
-            \textbf{Maximal Pre-injectable Sets} \\
-            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
-            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
-            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
-            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
-            \bc{A_1, B_3, C_4} \\
-            \bc{A_1, B_4, C_2} \\
-            \bc{A_2, B_1, C_4} \\
-            \bc{A_2, B_2, C_2} \\
-            \bc{A_3, B_3, C_3} \\
-            \bc{A_3, B_4, C_1} \\
-            \bc{A_4, B_1, C_3} \\
-            \bc{A_4, B_2, C_1}
-        \end{gathered}
-        \qquad
-        \begin{gathered}
-            \textbf{Ancestral Independences} \\
-            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
-            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
-            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
-            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
-            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
-            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
-            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
-            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
-            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
-            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
-            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
-            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
-        \end{gathered}
-    \end{equation*}
-    As can be counted, there are $12$ maximally pre-injectable sets $\ts'$ which will be indexed $1$ through $12$ in the order seen above ($\bc{V_1, \ldots, V_{12}}$).
-The maximally pre-injectable sets $\bc{V_i}_{i \in \bs{12}}$ form a maximal marginal scenario $\mscenario$ over the observable nodes of $\ts'$ when equipped with outcome labels.
-Using \cref{lem:inflation} inequalities $I_{\PreInj[\ts]{\ts'}}$ constraining the set of contextual marginal models $\prob^{\mscenario}$ can be deflated into polynomial inequalities over $I_{\ImInj[\ts]{\ts'}}$ bounding compatible marginal models over the images of the injectable sets in $\ts$.
-    \[ \ImInj[\ts]{\ts'} = \bc{\bc{A, B, C}, \bc{A}, \bc{B}, \bc{C}} \]
-    \comment[TC]{This is not all the images. I should clarify this.}
-
-    \section{Non-linear Optimizations}
-    \label{sec:optimizations}
-    \todo[TC]{Mention outlook on te importance of classification and determining interesting inequalities~\cite{Bancal_2010}}
-    Compatibility inequalities for a given causal structure are fantastic for finding incompatible distributions.
-In the inflation technique, this is no exception.
-Parameterizing a space distributions using a set of real-valued parameters $\lambda$, enables us to perform numerical optimizations against these inequalities in hopes that a particular set of parameters $\lambda$ is able to generate an incompatible distribution $\prob$.
-To illustrate this generic procedure and it's reliability, we will first examine the popular CHSH inequality.
-    \subsection{Numerical Violations of The CHSH Inequality}
-    The CHSH inequality~\cite{CHSH_Original} can we viewed as a causal compatibility inequality for the iconic Bell Scenario (Fig.
-19 of~\cite{Wood_2012}, Fig.
-11 of~\cite{Inflation}, Fig.
-1 a) of~\cite{Tavakoli_2015}, etc.) corresponding to Bell's notion of local causality~\cite{Wood_2012}.
-It constrains the set of 2-outcome bipartite distributions over local binary measurement settings for each party $\prob[AB\mid S_A S_B] \defined \bc{\prob[AB\mid 0 0], \prob[AB\mid 01], \prob[AB\mid 10], \prob[AB\mid 11]}$.
-Numerical optimization \textit{should} obtain the algebraic violation associated with the PR-Box correlations~\cite{PR_1995}.
-Maintaining full generality, we simply need to parameterize these $4$ distributions using \cref{eq:uniform_param}, each requiring $4$ real-valued parameters.
-We define the optimization target for the CHSH inequality to be the left-hand-side of \cref{eq:CHSH},
-    \[ I\tsb{CHSH} = \ba{AB|11} + \ba{AB|12} + \ba{AB|21} - \ba{AB|22} \]
-    Figure \ref{fig:CHSH_convex} demonstrates this optimization for $5$ random seed parameters $\lambda^0$, each converging to the expected value of $4$. Analogously,~\cite{Cirelson_1980}
-
-    \begin{figure}
-    \newlength\figureheight
-    \newlength\figurewidth
-    \setlength\figureheight{2.7in}
-    \setlength\figurewidth{.48\textwidth}
-    \begin{center}
-        \begin{minipage}[b]{.48\textwidth}
-            \centering
-            \includegraphics{../../figures/CHSH_convex.pdf}
-            \caption{Convex optimizations against $I\tsb{CHSH}$ recover algebraic violation of $4$.}
-            \label{fig:CHSH_convex}
-        \end{minipage}\hspace{0.04\textwidth}%
-        \begin{minipage}[b]{.48\textwidth}
-            \centering
-            \includegraphics{../../figures/CHSH_quantum.pdf}
-            \caption{Quantum optimizations against $I\tsb{CHSH}$ recover maximum violation of $2\sqrt{2}$.}
-            \label{fig:CHSH_quantum}
-        \end{minipage}
-    \end{center}
-    \end{figure}
-
-    \todo[TC]{Demonstrate Quantum, Convexity}
-    \todo[TC]{Why Inequalities are great for optimizations}
-    \todo[TC]{Non-linearity}
-    \todo[TC]{Techniques Used}
-    \todo[TC]{Finding maximum violation of CHSH easily}
-    \todo[TC]{Unreliance when number of parameters increases}
-    \todo[TC]{Issues with local minimum}
-    \todo[TC]{Using initial conditions close to fritz, obtain greater violation}
-    \todo[TC]{Greater violation shares possibilistic structure of fritz and violates CHSH under definition}
-    \todo[TC]{Not realizable with maximally entangled qubit states}
-    \todo[TC]{Not realizable with separable measurements}
-    \todo[TC]{Many non-trivial inequalities to be tested}
-    \todo[TC]{inequality -> dist -> inequality evolution}
-    \section{Conclusions}
-    \todo[TC]{Inflation technique allows one to witness fritz incompatibility}
-    \todo[TC]{Linear optimization induces certificates which are incompatibility witnesses}
-    \todo[TC]{There are quantum distributions in the Triangle Scenario that are incompatible and different from fritz in terms of entanglement but not possibilistic structure}
-    \section{Open Questions \& Future Work}
-    The marginal problem has be well studied in various contexts~\cite[\ldots]{Vorobev_1962,Inflation,Fritz_2011}.
-Reference~\cite{Fritz_2011} contains an excellent summary of its connection to other fields of research including knowledge integration, database theory and coalition games in game theory.
-    \todo[TC]{Lots of stuff}
-    \appendix
-    \section{Common Terminology \& Notation}
-
-    \subsection{Graph Theory}
-    \begin{definition}
-        \label{def:graph}
-        A \term{graph} is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes have the capacity to represent any object while the edges are defined as \textit{pairs} of nodes.
-Typical, although not necessary, the nodes (edges) are indexed by an index set $\ind_\nodes$ ($\ind_{\edges}$).
-        \begin{align*}
-            \nodes &= \bc{n_i \mid n_i \in \ind_{\nodes}} \\
-            \edges &= \bc{e_i = \bc{n_j, n_k} \mid i \in \ind_{\edges}, j,k \in \ind_{\nodes}}
-        \end{align*}
-    \end{definition}
-
-    \begin{definition}
-        \label{def:directed_graph}
-        A \term{directed graph} $\graph$ is a graph where each edge $e$ has an order or \term{direction}.
-        \begin{align*}
-            \nodes &= \bc{n_i \mid n_i \in \ind_{\nodes}} \\
-            \edges &= \bc{e_i = \br{n_j \to n_k} \mid i \in \ind_{\edges}, j,k \in \ind_{\nodes}}
-        \end{align*}
-    \end{definition}
-
-    \begin{definition}
-        \label{def:graph_terms}
-        The following definitions are common language in directed graph theory. Let $n, m \in \nodes$ be example nodes of the graph $\graph$.
-        \begin{itemize}
-            \item The \term{parents of a node}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
-            \item The \term{children of a node}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
-            \item The \term{ancestry of a node}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$
-        \end{itemize}
-        All of these terms can be generalized to sets of nodes $N \subseteq \nodes$ through union over the elements,
-        \begin{itemize}
-            \item The \term{parents of a node set}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
-            \item The \term{children of a node set}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
-            \item The \term{ancestry of a node set}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
-        \end{itemize}
-    \end{definition}
-
-    \begin{definition}
-        An \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$.
-        \[ \Sub[\graph]{N} \defined \br{N, \bc{e_i \mid i \in \ind_\edges, e_i \subseteq N}} \]
-        An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
-        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:dag}
-        A \term{directed acyclic graph} or \term{DAG} $\graph = \br{\nodes, \edges}$ is an directed graph (see \cref{def:directed_graph}) with the additional property that no node $n$ is in its set of \term{ancestors}.
-        \[ \forall n \in \nodes : n \notin \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}\]
-        It is critical to note the difference in language between \textit{ancestors} from \textit{ancestry}.
-The ancestry $\An[\graph]{n}$ of a node $n$ is defined in \cref{def:graph_terms} using \textit{whole} numbers $\mathbb{W}$.
-In contrast, the ancestors of a node are defined similarly with \textit{natural} numbers $\mathbb{N}$.
-    \end{definition}
-
-    \subsection{Probability Theory}
-
-    \begin{definition}
-        The \term{product distribution} of two disjoint probability distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as $\prob[V] \times \prob[W]$.
-        \[ \forall f \in \Events{V \cup W} : \br{\prob[V] \times \prob[W]}\br{f} \defined \prob[V][f|_{V}]\tcdot\prob[W][f|_{W}] \]
-        A product distribution of $k$ mutually disjoint distributions is defined as,
-        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
-        \[ \forall f \in \Events{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
-    \end{definition}
-
-    \section{Exemplary Inequalities}
-    \section{Connections to Sheaf-Theoretic Treatment}
-    \section{Computationally Efficient Parametrization of the Unitary Group}
-    Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} suggest the parameterization of the unitary group $\mathcal{U}\br{d}$ using a $d\times d$-matrix of real-valued parameters $\lambda_{n, m}$,
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \tcdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
-    Where $P_l$ are one-dimensional projective operators,
-    \[ P_l = \ket{l}\bra{l} \eq \label{eq:projective_operator} \]
-    and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices,
-    \[ \sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m} \]
-    Where $1 \leq m < n \leq d$. Spengler et. al. proved the validity of \cref{eq:spengler_unitary} in Ref.~\cite{Spengler_2010_Unitary}.
-
-    For the sake of reference, let us label the matrix exponential terms in \cref{eq:spengler_unitary} in a manner that corresponds to their affect on an orthonormal basis $\bc{\ket{1}, \ldots, \ket{d}}$.
-    \begin{align}
-    \begin{split}
-        GP_l &= \exp\br{iP_l \lambda_{l,l}} \\
-        RP_{n,m} &= \exp\br{i P_n \lambda_{n,m}} \\
-        R_{m,n} &= \exp\br{i \si_{m,n} \lambda_{m,n}}
-    \end{split} \eq \label{eq:exp_terms}
-    \end{align}
-    It is possible to remove the reliance on matrix exponential operations in \cref{eq:spengler_unitary} by utilizing the explicit form of the exponential terms in \cref{eq:exp_terms}.
-As a first step, recognize the defining property of the projective operators \cref{eq:projective_operator},
-    \[ P_l^k = \br{\ket{l}\bra{l}}^k = \ket{l}\bra{l} = P_l \]
-    This greatly simplifies the global phase terms $GP_l$,
-    \[ GP_l = \exp\br{iP_l \lambda_{l,l}} = \sum_{k=0}^{\inf} \f{\br{iP_l \lambda_{l,l}}^k}{k!} = \mathbb{I} + \sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}P_l^k = \mathbb{I} + P_l \bs{\sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}} = \mathbb{I} + P_l \br{e^{i \lambda_{l,l}} - 1} \eq \label{eq:unitary_GP} \]
-    Analogously for the relative phase terms $RP_{n,m}$,
-    \[ RP_{n,m} = \cdots = \mathbb{I} + P_n \br{e^{i \lambda_{n,m}} - 1} \eq \label{eq:unitary_RP} \]
-    Finally, the rotation terms $R_{m,n}$ can also be simplified by examining powers of $i \sigma_{n,m}$,
-    \[ R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}} = \sum_{k=0}^{\inf} \f{\br{\ket{m}\bra{n} - \ket{n}\bra{m}}^k \lambda_{m,n}^k}{k!} \]
-    One can verify that the following properties hold,
-    \begin{align*}
-        \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^0 &= \mathbb{I} \\
-        \forall k \in \N, k \neq 0 : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k} &= \br{-1}^k\br{\ket{m}\bra{m} + \ket{n}\bra{n}} \\
-        \forall k \in \N : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k+1} &= \br{-1}^k\br{\ket{m}\bra{n} - \ket{n}\bra{m}}
-    \end{align*}
-    Revealing the simplified form of $R_{m,n}$,
-    \[ R_{m,n} = \mathbb{I} + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \sum_{j=1}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j}}{\br{2j}!} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sum_{j=0}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j+1}}{\br{2j+1}!} \]
-    \[ R_{m,n} = \mathbb{I} + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \eq \label{eq:unitary_R} \]
-    By combining the optimizations of \cref{eq:unitary_RP,eq:unitary_R,eq:unitary_GP} together we arrive at an equivalent form for \cref{eq:spengler_unitary} that is computational more efficient.
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}}} \tcdot \bs{\prod_{l=1}^{d} GP_l} \eq \label{eq:fast_spengler_unitary} \]
-    In quantum mechanics, the global phase of a state $\ket{\psi} \in \Hilb^n$ is a \textit{redundant} parameter.
-Parameterizing unitaries using \cref{eq:fast_spengler_unitary} is especially attractive since the global phase terms $GP_l$ can be dropped, allowing one to parameterize all unitaries in $\mathcal{U}\br{d}$ up to this degeneracy~\cite{Spengler_2010_Unitary}\footnote{In our implementation, we accomplish this by explicitly setting $\lambda_{l,l} = 0$ in \cref{eq:unitary_GP}}.
-    \[ U_{/ GP_l} = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}}} \eq \label{eq:fast_spengler_unitary_gp} \]
-    \todo[TC]{Explanation of Computational Complexity $\mathcal{O}\br{d^3}$ vs. $\mathcal{O}\br{1}$ using~\cite{Moler_2003}}
-    \todo[TC]{Pre-Caching for Fixed dimension $d$}
-    \todo[TC]{Talk about inverse via haar measure}
-
-    \section{Parametrization of Quantum States \& Measurements}
-    \label{sec:param_quantum_states}
-    Throughout \cref{sec:optimizations}, we utilize a variety of parameterizations of quantum states and measurements in order to generate quantum-accessible probability distributions.
-There are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Spengler_2010_Unitary,Fujii_2005,James_2001} with applications \todo[TC]{Finish this sentence}.
-For our purposes, we need to parameterize the space of quantum-accessible distributions $\prob[\mathcal{Q}]$ that are \textit{realized} on the Triangle Scenario.
-We have implemented $\prob[\mathcal{Q}]$ under the following description.
-    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \eq \label{eq:triangle_quantum_distributions} \]
-
-    \subsection{Quantum States}
-    The bipartite states $\br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ of \cref{eq:triangle_quantum_distributions} were taken to be two-qubit density matrices acting on $\Hilb^2 \otimes \Hilb^2$.\footnote{We also considered qutrit $\Hilb^3$ qutit $\Hilb^4$ states.
-However for $6$ $d$-dimensional $\Hilb^d$ states, the joint density matrix $\rho$ acts on $\br{\Hilb^d}^{\otimes 6}$ making it a $\br{d^6, d^6}$ matrix with $d^{12}$ entries.
-Computationally only $d = 2$ was feasible for our optimization tasks.} The space of all such states corresponds to the space of all $4\times 4$ positive semi-definite hermitian matrices with unitary trace.
-Throughout this section, we refer to these bipartite states simply as $\rho$ unless otherwise indicated.
-There are three distinct techniques that we have considered.
-
-    Taking inspiration from~\cite{James_2001}, we can parameterize all such density matrices $\rho$ using \term{Cholesky Parametrization}~\cite{Grasmair_2014}.
-The Cholesky decomposition allows one to write any hermitian positive semi-definite matrix $\rho$ in terms of a lower (or upper) triangular matrix $T$ using $\rho = T^\dagger T$.
-Our Cholesky parameterization consists of assigning $16$ real-valued parameters $\lambda$ to the entires of $T$ and generating a unitary trace $\rho$ similar to eq.
-(4.4) of~\cite{James_2001}.
-    \[ \rho = \f{T^\dagger T}{\Tr\br{T^\dagger T}} \quad T = \pmtrx{\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}} \eq \label{eq:cholesky_param} \]
-    Our deviation from exclusiving using \cref{eq:cholesky_param} is two-fold.
-First, \cref{eq:cholesky_param} is degenerate in that the normalization indicates only $16 - 1 = 15$ parameters are required for fully generic parameterization of all such states $\rho$.
-Removing this degeneracy is possible although difficult.
-Second, the parameters $\lambda_i$ carry no physical meaning associated with the state $\rho$, unlike our next parameterization.
-
-    In Spengler, Huber and Hiesmayr's work~\cite{Spengler_2010_Unitary}, they discuss how to parameterization density matrices $\rho$ acting on $\Hilb^d$ of rank $k$ through it's spectral decomposition,
-    \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i}\bra{\psi_i} \quad p_i \geq 0, \sum_{i} p_i = 1, k \leq d \eq \label{eq:unitary_param_density} \]
-    Where any orthonormal basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into a computational basis $\bc{\ket{i}}$ by a unitary $U \in \mathcal{U}\br{d}$ such that $\ket{\psi_i} = U\ket{i}$.
-We refer to \cref{eq:unitary_param_density} as the \term{Spengler Parametrization}.
-Without loss of generality we parameterize all full-rank ($k=d$) matrices by simultaneously parameterizing the $d=4$ eigenvalues $p_i$ of \cref{eq:unitary_param_density} using \cref{eq:convex_param} and the unitary group $\mathcal{U}\br{4}$ up to global phase equivalence using \cref{eq:fast_spengler_unitary_gp}.
-Parameterizing $\rho$ using the Spengler parameterization requires $3 + 12 = 15$ parameters; admitting no degeneracies.
-
-    Finally in cases where we wish to restrict ourselves to \textit{pure} bipartite states $\rho = \ket{\psi}\bra{\psi}$, we have the luxury to use a \term{Schmidt Parametrization}.
-This is accomplished via a Schmidt decomposition $\ket{\psi_{AB}} = \sum_{i}\sigma_i \ket{i_A}\otimes\ket{i_B}$ where normalization demands that $\sum_{i} \sigma_i^2 = 1$, $\bc{\ket{i_A}}$ and $\bc{\ket{i_B}}$ are orthonormal bases for $\Hilb_A$ and $\Hilb_B$ respectively~\cite{Neilsen_Chaung_2011}.
-Additionally for qubit sources we can \textit{choose} our orthonormal bases to be the computational basis $\bc{\ket{0}, \ket{1}}$ and write,
-    \[ \ket{\psi} = \cos^2\br{\lambda_1} \ket{0} \otimes \ket{0} + \sin^2\br{\lambda_1} \ket{1} \otimes \ket{1} \]
-    Where only $1$ real-valued parameter $\lambda = \bc{\lambda_1}$ is required to parameterize all pure states up to local unitaries.
-Pure states are also attractive due to their computational advantage in computing \cref{eq:triangle_quantum_distributions}.
-If each state $\rho$ is decomposable into $\ket{\psi}\bra{\psi}$, then \cref{eq:triangle_quantum_distributions} can be written as,
-    \[ \prob[ABC]\br{abc} = \bramidket{\psi_{AB}\psi_{BC}\psi_{CA}}{\netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c} \netperm^\intercal}{\psi_{AB}\psi_{BC}\psi_{CA}} \eq \label{eq:pure_state_quantum_triangle} \]
-    Avoiding the expensive matrix multiplications of \cref{eq:triangle_quantum_distributions}.
-    \subsection{Measurements}
-    With full generality, we consider a measurement $M$ to be a \term{projective-operator valued measure (POVM)} represented by a set of hermitian, positive semi-definite operators $\bc{M_i}_{i=1,\ldots,k}$\footnote{The $i$-th element of $M$ is referenced using a subscript $M_i$.
-The set of measurement elements for a particular party $X$ will be written $M_X$.
-When both party and element are to be referenced, we write $M_{X,i}$.} acting on $\Hilb^d$ summing to the identity,
-    \[ \forall \ket{\phi} \in \Hilb^d : \bra{\phi} M_i \ket{\phi} \geq 0 \quad \sum_{i=1}^{k} M_i = \mathbb{I}_{\Hilb^d} \eq \label{eq:povm} \]
-    When considering $k=2$ outcome measurements acting on $\Hilb^4$ we parameterize the first POVM element $M_1$ by using a Cholesky parameterization similar to \cref{eq:cholesky_param} without normalizing for trace.
-Afterwards, $M_2$ is fully determined by \cref{eq:povm}.
-    \[ M_1 = T^\dagger T \quad M_2 = \mathbb{I} - T^\dagger T \eq \label{eq:2_povm}\]
-    However, in order for $M_2$ to be positive semi-definite, the largest eigenvalue of $M_1$ has to be less than 1.
-To see this is a necessary and sufficient constraint, first expand out \cref{eq:2_povm},
-    \[ \bramidket{\phi}{M_2}{\phi} = \bramidket{\phi}{\mathbb{I} - M_1}{\phi} = \abs{\phi}^2 - \bra{\phi}\br{\sum_{i=1}^{d}m^{\br{i}}_1 \ket{m^{\br{i}}_1}\bra{m^{\br{i}}_1}}\ket{\phi} \]
-    Next write a generic $\ket{\phi} \in \Hilb^d$ in terms of a linear combination of the eigenvectors of $M_1$\footnote{The eigenvectors of $M_1$ form an orthonormal basis for $\Hilb^d$ because $M_1$ is Hermitian}.
-    \[ \bramidket{\phi}{M_2}{\phi} = \sum_{j}\abs{\braket{\phi}{m^{\br{j}}_1}}^2 - \sum_{i} m^{\br{i}}_1 \abs{\braket{\phi}{m^{\br{i}}_1}}^2 = \sum_{i} \br{1 - m^{\br{i}}_1} \abs{\braket{\phi}{m^{\br{i}}_1}}^2 \eq \label{eq:eigen_less_one} \]
-    Since $\ket{\phi}$ is arbitrary, for each $i$ set $\ket{\phi} = \ket{m^{\br{i}}_1}$ to see that each eigenvalue of $M_1$ needs to be less than $1$.
-    \[ \bramidket{m^{\br{i}}_1}{M_2}{m^{\br{i}}_1} = \br{1 - m^{\br{i}}_1} \geq 0 \implies m^{\br{i}}_1 \leq 1 \eq \label{eq:2_povm_suff} \]
-    By \cref{eq:eigen_less_one} is not difficult to see that \cref{eq:2_povm_suff} is a sufficient condition.
-During optimization, \cref{eq:2_povm_suff} can either be enforced passively as a constraint or directly by normalizing $M_1$ by its largest eigenvalue $\max\br{m_1^{\br{i}}}$ whenever necessary.
-
-    When generalizing the above parameterization to more than $2$ outcomes, only necessary conditions were found.
-Generating $k$-outcome POVM measurements is doable using rejection sampling techniques such as those used in~\cite{Petz_2012} however a valid parameterization with little to no degeneracy was not found.
-Upon making this observation, a necessary departure to \term{projective-valued measures (PVMs)} is warranted\footnote{Strictly speaking, when the number of outcomes ($k$) \textit{matches} the Hilbert space dimension ($d$), \cref{eq:povm} implies \cref{eq:pvm} by completeness.
-When considering $4$ outcome measurements on bipartite qubit states in $\Hilb^4$, PVMs are completely general.
-Moreover, Naimark's dilation theorem guarantees that PVMs acting on $\Hilb^q$ can \textit{emulate} the behaviour of any POVM acting on $\Hilb^d$ provided that $q$ is sufficiently larger than $d$~\cite{Naimark}.}.
-With loss of generality, consider the set of PVMs $M$ satisfying \cref{eq:povm} in addition to orthogonal and projective properties,
-    \[ M_i M_j = \de_{ij} M_i \quad M_i = \ket{m_i}\bra{m_i} \eq \label{eq:pvm}\]
-    Parameterizing $M$ for $k$-outcome measurements corresponds to parameterizing the set of all $k$-th order orthonormal sub-bases of $\Hilb^d$.
-    First note that any such basis $\bc{\ket{\psi_1}, \ldots, \ket{\psi_k}}$ can be transformed into the computational basis $\bc{\ket{1}, \ldots, \ket{k}}$ by a unitary denoted $U \in \mathcal{U}\br{d}$,
-    \[ U \ket{\psi_i} = \ket{i} \]
-    With this observation we just need to parameterize the set of all unitaries $\mathcal{U}\br{d}$,
-    \[ M = \bc{ U\ket{i}\bra{i}U^\dagger }_{i \in 1, \ldots, k} \]
-    Specifically, the projective property each $M_i$ means that the global phase of $U$ is completely arbitrary; one only needs to consider parameterizing unitaries up to global phase \cref{eq:fast_spengler_unitary_gp}.
-This method was inspired by the \textit{measurement seeding} method of P{\'{a}}l and V{\'{e}}rtesi's~\cite{Pal_2010} iterative optimization technique.
-
-    Analogously to \cref{eq:pure_state_quantum_triangle}, projective measurements offer considerable computational advantage as \cref{eq:triangle_quantum_distributions} can be rewritten as,
-    \[ \prob[ABC]\br{abc} = \bramidket{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{A,a}m_{B,b}m_{C,c}} \eq \label{eq:pure_meas_quantum_triangle} \]
-
-    \subsection{Network Permutation Matrix}
-    \begin{figure}
-        \centering
-        \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
-        \caption{The network permutation matrix $\netperm$ for $\br{\Hilb^2}^{\otimes 6}$ realized on the triangle scenario. Black represents a value of $1$ and $0$ otherwise.}
-        \label{fig:perm_mtrx}
-    \end{figure}
-    Finally, we introduce the \term{network permutation matrix} $\netperm$ for the Triangle Scenario of \cref{fig:triangle_scenario}.
-For bipartite qubit states, $\netperm$ becomes a $64\times64$ bit-wise matrix that acts on the measurements $M$ and is depicted in \cref{fig:perm_mtrx}.
-To illuminate its necessity, consider \cref{eq:triangle_quantum_distributions} without $\netperm$.
-    \begin{align*}
-    \prob[ABC]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA}} \br{M^a_{A}\otimes M^b_{B} \otimes M^c_{C}}}\\
-    &= \Tr\bs{\br{\rho_{AB}M^a_{A}}\otimes\br{\rho_{BC}M^b_{B}}\otimes\br{\rho_{CA}M^c_{C}}}\\
-    &= \Tr\br{\rho_{AB}M^a_{A}}\Tr{\br{\rho_{BC}M^b_{B}}}\Tr{\br{\rho_{CA}M^c_{C}}}\\
-    &= \prob[A\mid \rho_{AB}]\br{a}\prob[B\mid \rho_{BC}]\br{b}\prob[C\mid \rho_{CA}]\br{c}
-    \end{align*}
-    On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$.
-This is analogously troubling for $B$ and $C$ as well.
-The network permutation matrix $\netperm$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$.
-To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
-    \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
-    $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''.
-It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
-    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
-    \subsection{Degeneracy}
-    \todo[TC]{Discuss local unitary degeneracy}
-    \section{Convex Parametrization of Finite Probability Distributions}
-    As discussed in \cref{sec:optimizations}, there is a need to parameterize the family of all probability distributions $\prob[V]$ over a given set of variables $V = \br{v_1, \ldots, v_{\abs{V}}}$.
-If the cardinality of $O_{V}$ is finite, then this computationally feasible.
-The space of probability distributions over $n = \abs{O_{V}}$ distinct outcomes forms a $n-1$ dimensional convex polytope naturally embedded in $\R_{\geq 0}^n$~\cite{Brunner_2013} that is parameterizable by $n-1$ real value parameters; normalization $\sum_{o\bs{V} \in O_V} \prob[V][\outc{V}] = 1$ accounts for the `$-1$'.
-An example of a non-degenerate parameterization of $\prob[V]$ consists of $n-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{n-1}}, \lambda_i \in \bs{0, \pi/2}$ which generate the $n$ probability values $p_j$ using hyperspherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary},
-    \begin{equation}
-    \begin{gathered}
-        \label{eq:convex_param}
-        p_j = \cos^2 \lambda_j \prod_{i=1}^{j-1} \sin^2 \lambda_i \quad \forall j \in 1, \ldots, n - 1 \\
-        p_n = \prod_{i=1}^{n-1} \sin^2 \lambda_i
-    \end{gathered}
-    \end{equation}
-    Furthermore due to the periodicity of the parameter space $\lambda$, \cref{eq:convex_param} can be used for either constrained or unconstrained optimization problems.
-For continuity reasons, unconstrained optimizations are performed whenever possible.
-
-    Although non-degenerate, this parameterization suffers from uniformity; a randomly sampled vector of parameters $\lambda$ \textit{does not} translate to a randomly sampled probability $\prob[V]$.
-An easy-to-implement, degenerate parameterization of $\prob[V]$ can be constructed by simply beginning with $n$ real parameters $\lambda = \br{\lambda_1, \ldots, \lambda_n}$, then making them positive and normalized by their sum\footnote{Strictly speaking, \cref{eq:uniform_param} \textit{also} suffers from non-uniformity; being biased toward uniform probability distributions $\prob[V]$.
-\todo[TC]{Discuss rejection sampling simplex algorithms}}.
-    \[ p_j = \f{\abs{\lambda_j}}{\sum_{i=1}^{n} \abs{\lambda_i}} \quad \forall j \in 1, \ldots, n \eq \label{eq:uniform_param} \]
-    For various convex optimization tasks sensitive to initial conditions outlined \cref{sec:optimizations}, the latter parameterization of \cref{eq:uniform_param} generally performed better than the former \cref{eq:convex_param}.
-
-    \bibliography{../references}
+    \todo[TC]{Flesh out document from archive}
 \end{document}

### 2016-11-10 documents/TriangleScenario/ts.tex
Started work on slides for Brazil

--- 2016-11-10 documents/Archive/main.tex
@@
 \begin{document}
-    \title{Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario}
+    \title{Causal Compatability Inequalities Admitting of Quantum Violations in the Triangle Scenario}
     \author{Thomas C. Fraser}
@@
 Here we answer this affirmatively, and discuss specific Triangle scenario inequalities and quantum configurations which manifest nonclassical correlations.
-We also report the development of novel computational techniques suitable for large causal structures with numerous outcomes.
 Numerical optimzations reveal quantum resources potentially qualitatively different from those known previously.
@@
 
-    \section{Introduction}
-    \todo[TC]{Mention Bell's work} \\
+    \todo[TC]{Flesh out document from archive}
 
-    \todo[TC]{Violations of inequalities correspond to resources} \\
-
-    \todo[TC]{Finding inequalities is hard} \\
-
-    \todo[TC]{Causal inference is a great lens to answer these questions} \\
-
-    \todo[TC]{Demonstrated the usefulness of the inflation technique} \\
-
-    \todo[TC]{Definite Extension procedure} \\
-
-    \todo[TC]{Optimizations against inequalities} \\
-
-    \section{Compatibility, Contextuality and the Marginal Problem}
-    \label{sec:comp_con_mp}
-
-    \subsection{Preliminary Notions}
-    \label{eq:comp_con_mp_notions}
-    A reoccurring motif of these discussions will be a set of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_k]}$.
-In agreement with~\cite{Fritz_2011} we adopt the following definitions and notation.
-
-    \begin{definition}
-        \label{def:marginal_model}
-        A set of random variables $\jointvar = \bc{v_1, \ldots, v_n}$ is referred to as the \term{joint random variables} when denoted with a $\jointvar$.
-A subset of joint variables $V \subset \jointvar$ is called \term{marginal context}.
-A collection of marginal contexts is called the \term{marginal scenario}\footnote{Rigorously speaking as defined by~\cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that $V' \in \mscenario$ whenever $V' \subseteq V \in \mscenario$.
-Throughout this document, we only consider the \textit{maximal marginal scenario}; restricting our focus to the largest contexts in the marginal scenario $\forall i,j \in 1, \ldots, k: V_i \not \subseteq V_j$.} and is denoted $\mscenario$\footnote{It is also assumed that the marginal scenario covers the joint variables $\jointvar = \bigcup_{i = 1}^{k} V_i$.}.
-        \[ \mscenario \defined \bc{V_1, \ldots, V_k \mid V_i \subseteq \jointvar} \]
-        Additionally, the set of probability distributions $\bc{\prob[V_1], \ldots, \prob[V_k]}$ over the marginal scenario is called a \term{marginal model} is compactly denoted $\prob^{\mscenario}$.
-    \end{definition}
-    A specific marginal model $\prob^{\mscenario}$ for a marginal scenario $\mscenario$ abstractly represents a set of measurements or observations made on a physical system.
-Associated with the physical system are physical models or causal structures.
-
-    \begin{definition}
-        A \term{causal structure} is a directed acyclic graph (DAG) $\graph = \br{\nodes, \edges}$ with the extra distinction between two classes of nodes: the \term{latent nodes} $\nodes_L$ and \term{observed nodes} $\nodes_O$.
-    \end{definition}
-    The latent nodes of a causal structure correspond aim to represent completely general hidden variables that are hidden by some fundamental process or cannot be measured due to other limitations.
-The observed nodes represent random variables that are measurable and in practice will be observed as a collection of marginal contexts $\mscenario$.
-Any observation over this particular marginal scenario is expressible as a marginal model $\prob^{\mscenario}$.
-The field of causal inference aims to answer the looming question: \text{Is the observed marginal model compatible with the hypothesized causal structure?} \\
-
-    In order to determine if a given marginal model $\prob^{\mscenario}$ is compatible with a causal structure $\graph$, a formal notion of \textit{compatibility} is warranted; first for a single marginal distribution $\prob[V]$ and then for a complete marginal model $\prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]}$.
-
-    \begin{definition}
-        A set of \term{causal parameters} for a particular causal structure $\graph$ is the specification of a conditional distribution for every node $n \in \nodes$ given its parents in $\graph$.
-        \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \eq \label{eq:def:casual_param}\]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:compatible}
-        A marginal distribution $\prob[V]$ is \term{compatible} with a causal structure $\graph$ if there exists a \textit{choice} of causal parameters such that $\prob[V]$ can be \textit{recovered} from the following series of operations:
-        \begin{enumerate}
-            \item Obtain a joint probability distribution over \textit{all} nodes of of the causal structure using the chosen casual parameters: $\prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}]$.
-            \item Marginalize over the latent nodes of $\graph$: $\prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes]$.
-            \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$: $\prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O]$
-        \end{enumerate}
-        If it is not possible for $\prob[V]$ to be recovered for \textit{any} choice of causal parameters, then $\prob[V]$ is \term{incompatible}.
-To generalize, a marginal model $\prob^{\mscenario}$ is compatible with $\graph$ if each distribution $\prob[V] \in \prob^{\mscenario}$ can be made compatible by the \textit{same} choice of causal parameters; otherwise it is incompatible.
-    \end{definition}
-
-    There are two reasons why a given marginal model $\prob^{\mscenario}$ would be deemed incompatible.
-One possibility is that the marginal model $\prob^{\mscenario}$ does not admit a joint distribution $\prob[\jointvar]$ such that it is impossible for requirement 3 of \cref{def:compatible} to hold\footnote{It is typical for $\nodes_O = \jointvar$.
-At the very least, it is demanded that $\jointvar \subseteq \nodes_O$.}.
-Alternatively, it could be possible that a joint distribution $\prob[\jointvar]$ exists but can not factor into causal parameters as per requirement 1 of \cref{def:compatible}.
-The former point-of-failure, namely the non-admission of a joint distribution, will be principle focus of this paper.
-Colloquially, the existence (or non-existence) of a joint distribution is referred to as \textit{the marginal problem}.
-
-    \begin{definition}
-        \label{def:marginal_problem}
-        \term{The Marginal Problem:} Given a marginal model $\prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]}$ marginal to the joint variables $\jointvar = \bigcup_{i} V_i$, does there exist a joint distribution $\prob[\jointvar]$ such that each given distribution $\prob[V_i]$ can be obtained by marginalizing $\prob[\jointvar]$?
-        \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \eq \label{eq:def:marginal_problem}\]
-        Following definition 2.3 in~\cite{Fritz_2011}, a marginal model is said to be \term{contextual} if it \textit{does not} admit a joint distribution $\prob[\jointvar]$ and \term{non-contextual} otherwise.
-    \end{definition}
-
-    There are two perspectives that can be taken when trying to answer the marginal problem.
-The first comes as stated by \cref{def:marginal_problem}; when inured with a particular marginal model $\prob^{\mscenario}$, can you construct a joint distribution that satisfies \cref{def:marginal_problem}?
-Alternatively and more abstractly, when provided a marginal \textit{mscenario} $\mscenario$ what is the set of all marginal models that are (non-)contextual?
-To facilitate future discussions, let $\s{NC}$ denote the set of marginal models that are non-contextual (admitting a joint distribution) and let $\s{C}$ denote the set of contextual marginal models.
-It becomes desirable to identifying conditions that constrain either $\s{NC}$ or $\s{C}$.
-We will continue to refer to a \term{complete solution marginal problem} as a finite set of necessary and sufficient conditions able to discern if a given marginal model $\prob^{\mscenario}$ is in $\s{NC}$ or $\s{C}$.
-These constraints typically take the form of linear inequalities over probabilities $\prob^{\mscenario}$.
-
-    \begin{definition}
-        A \term{$\s{NC}$-inequality} $I_{\mscenario}$ for a marginal scenario $\mscenario$ is a probabilistic inequality that is obeyed for every non-contextual marginal model $\prob^{\mscenario}$.
-    \end{definition}
-
-    In the \cref{sec:linear_program}, we will explore and briefly mention existing techniques for completely (or partially) solving the marginal problem.
-The basis of understanding being that \cref{eq:def:marginal_problem} is a \textit{linear} operation.
-In certain circumstances, \cref{eq:def:marginal_problem} can be represented as a matrix operation.
-
-    \todo[TC]{Maybe define the possibilistic marginal problem for later} \\
-
-    \subsection{Casting the Marginal Problem as a Linear Program}
-    \label{sec:linear_program}
-
-    Heretofore, our discussions of compatibility, contextuality and the marginal problem have be completely general, making no reference to the nature of the outcomes of the random variables $\jointvar$; whether they be discrete or continuous, finite or unbounded, or otherwise.
-\todo[TC]{It is entirely possible to obtain complete solutions to the marginal problem for continuous and unbounded measure spaces using entropic inequalities.
-[Elaborate and reference]} In this paper we restrict our attention to finite outcomes.
-In particular, we will focus on marginal scenarios that are finite but have a large number of outcomes.
-To assist with the subsequent analysis, we recall some familiar notions of probability theory together with new terminology and notation.
-\\
-
-    \subsubsection{Events}
-    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$.
-We also define the set of all \term{events over $v$} $\Events{v}$\footnote{In the language of sheaf-theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
-    \[ \Events{v} \defined \bc{s : \bc{v} \to O_v} \label{eq:outcome_space} \]
-    Evidently, $\Events{v}$ and $O_v$ have a one-to-one correspondence and this distinction can be confounding.
-There is rarely any harm in referring synonymously to either as outcomes.
-Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
-    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetry}.
-As a natural generalization we define the event over a collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
-    \[ \Events{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
-    Each event $s$ can be compactly represented as a set of mappings over each element of $V$.
-    \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
-    The domain $\Dom{s}$ of an event $s$ is the set of random variables it valuates, i.e. if $s \in \Events{V}$, then $\Dom{s} = V$.
-    \begin{example}
-        Let $s \in \Events{V}$ be an event over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$.
-Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$.
-Furthermore let $f \in \Events{V}$ be the section $\br{v_1 \mapsto 2, v_2 \mapsto 1}$.
-Then the following notations are interchangeable,
-        \[ \prob[][s] = \prob[\Dom{s}][s] = \prob[V][s] = \prob[v_1, v_2][s] = \prob[][v_1 \mapsto s_1\br{v_1}, v_2 \mapsto s_2\br{v_2}] = \prob[][v_1 \mapsto 2, v_2 \mapsto 1] = \prob[v_1v_2][21] \]
-        Each of which should be read as ``the probability that $v_1$ got outcome $2$ and $v_2$ got outcome $1$''
-    \end{example}
-    \begin{definition}
-    \label{def:section_restriction}
-    For every $W \subseteq V$ and $s \in \Events{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Events{W}$) is the event in $\Events{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
-    \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
-    \end{definition}
-    \begin{definition}
-    \label{def:section_compatible}
-    The events $s_{V} \in \Events{V}$ and $s_{W} \in \Events{W}$ are said to be \term{compatible} events if they agree on their valuations of $V \cap W$.
-Compatibility will be denoted with the infix `$\com$'.
-    \[ s_{V} \com s_{W} \iff {s_{V}}|_{V\cap W} = {s_{W}}|_{V\cap W} \]
-    \end{definition}
-    \begin{definition}
-    \label{def:section_extendable}
-    It $s_V \in \Events{V}$ and $s_W \in \Events{W}$ compatible events and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
-    \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
-    Extendability is dual to the notion of a \term{restriction} of $s_V$; $s_V$ can be restricted to $s_W$ ($s_V \res s_W$) if and only if $s_W$ is extendable to $s_V$.
-    \end{definition}
-
-    \begin{remark}
-        The notation `$s \com t$' is used to indicate compatibility between $s \in \Events{V}$ and $t \in \Events{W}$ because of the following observation: $s$ and $t$ are compatible if and only if they are extensions of some event $r \in \Events{V \cap W}$.
-        \[ s \com t \iff \exists r \in \Events{V \cap W} \mid s \res r \ext t \]
-        In fact $r$ is uniquely defined.
-        \[ \forall v \in V \cap W : r\br{v} = s\br{v} = t\br{v} \]
-    \end{remark}
-
-    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint events} $\Events{\jointvar}$.
-Similarly we define the \term{context events} $\bc{\Events{V} \mid V \in \mscenario}$.
-Finally, we elect to define the disjoint union of all context events are called the \term{marginal events} and by an abuse of notation we will denote this disjoint union as $\Events{\mscenario}$.
-    \[ \Events{\mscenario} = \coprod_{V \in \mscenario} \Events{V} \]
-    Each marginal section $m \in \Events{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
-    \subsubsection{Linear Programs}
-    \label{sec:linear_programs}
-
-    We are now fully equipped to write the marginal problem as a matrix multiplication.
-    \begin{definition}
-        \label{def:incidence_matrix}
-        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} events $j \in \Events{\jointvar}$ and the rows are events by \textit{marginal} sections $m \in \Events{\mscenario}$.
-The entries of $M$ are populated whenever a row index is extendable to a column index.
-        \[ M_{m,j} = \de_{m \ext j} \defined \begin{cases}
-            1 & m \ext j \\
-            0 & \text{otherwise}
-        \end{cases} \]
-        Where $\de_{m \ext j}$ is termed the \term{extendability indicator}.
-The incidence matrix has $\abs{\Events{\jointvar}}$ columns, $\abs{\Events{\mscenario}} = \sum_{i} \abs{\Events{V_i}}$ rows and $k\abs{\Events{\jointvar}}$ non-zero entries.
-    \end{definition}
-    To illustrate this concretely, consider the following example:
-    \begin{example}
-        \label{ex:incidence_matrix}
-        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{a,b}, \bc{b,c}, \bc{a,c}}$. The incidence matrix becomes:
-        \[ M = \kbordermatrix{
-            (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
-            (a\mapsto0, b\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto0, b\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto1, b\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
-            (a\mapsto1, b\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
-            (b\mapsto0, c\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
-            (b\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
-            (b\mapsto1, c\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
-            (b\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
-            (a\mapsto0, c\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
-            (a\mapsto1, c\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
-            (a\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
-        } \eq \label{eq:example_incidence}\]
-    \end{example}
-
-    \begin{definition}
-        The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint event $j \in \Events{\jointvar}$.
-$\probvec^{\jointvar}$ shares the same indices as the \textit{column} indices of $M$.
-        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
-    \end{definition}
-    \begin{definition}
-        Analogously, \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Events{\mscenario}$.
-$\probvec^{\mscenario}$ shares the same indices as the \textit{row} indices of $M$.
-        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
-    \end{definition}
-    The marginal and joint distribution vectors are related via the incidence matrix $M$.
-Given a joint distribution vector $\probvec^{\jointvar}$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec^{\jointvar}$.
-    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
-    Henceforth we will use $\probvec^{\jointvar}$ ($\probvec^{\mscenario}$) and $\prob[\jointvar]$ ($\prob_{\mscenario}$) interchangeably.
-
-    \begin{remark}
-        The particular ordering of the rows and columns of $M$ carries no importance, but it \textit{must} be consistent between $M$, $\probvec^{\jointvar}$ and $\probvec^{\mscenario}$.
-    \end{remark}
-
-    The marginal problem can now be rephrased in the language of the incidence matrix.
-Suppose one obtains a marginal distribution vector $\probvec^{\mscenario}$.
-The marginal problem becomes equivalent to the question: \textit{Does there exist a joint distribution vector $\probvec^{\jointvar}$ such that \cref{eq:incidence_matrix_use} holds?}
-
-    \begin{definition}
-        \label{def:marginal_linear_program}
-        \term{The Marginal Linear Program} is the following linear program:
-        \begin{alignat*}{2}
-            & \text{minimize:} \quad&& \emptyset \tcdot x\\
-            & \text{subject to:} && x \succeq 0 \\
-            & && M \tcdot x = \probvec^{\mscenario}
-        \end{alignat*}
-        If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries).
-The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:incidence_matrix_use} and is a valid joint distribution vector.
-Therefore feasibility implies that $\probvec^{\jointvar} = x$.
-Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\probvec^{\jointvar}$ over all random variables.
-    \end{definition}
-    \todo[TC]{Talk about about the linear solvers and how this is easy to implement.}
-    \begin{definition}
-        \label{def:dual_marginal_linear_program}
-        \term{The Dual Marginal Linear Program} is the dual of \cref{def:marginal_linear_program} formulated via a procedure similar to~\cite{Lahaie_2008}:
-        \begin{alignat*}{2}
-            & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
-            & \text{subject to:} && y \tcdot M \succeq 0
-        \end{alignat*}
-        Where $y$ is a real valued vector with the same length as $\probvec^{\mscenario}$.
-    \end{definition}
-
-    The dual marginal linear program not only answers the marginal problem for a specific marginal model $\probvec^{\mscenario}$ but as a by-product provides an inequality that witnesses its contextuality.
-If this is not obvious, first notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints become satisfied.
-Secondly if the dual constraint $y \tcdot M \succeq 0$ holds \textit{and} the primal is feasible, then the following must hold:
-    \[ y \tcdot \probvec^{\mscenario} =  y \tcdot M \tcdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
-    Therefore the \textit{sign} of the dual value $d \defined \min \br{y \tcdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality.
-If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore $\probvec^{\mscenario}$ is contextual.
-Likewise if $d \geq 0$ (satisfying \cref{eq:dual_marginal_ineq}), then $\probvec^{\mscenario}$ is non-contextual.
-\footnote{Actually, if $d \geq 0$ then it is exactly $d = 0$ due to the existence of the trivial $y = \emptyset$.
-This observation is an instance of the \textit{Complementary Slackness Property} of~\cite{Bradley_1977}.
-\comment[TC]{Is this really the CSP?} Moreover, if $d < 0$, then it is unbounded $d = -\inf$.
-This latter point becomes clear upon recognizing that for any $y$ with $d < 0$, another $y' = \al y$ can be constructed (with $\al > 1$) such that $d' = \al d < d$.
-Since a more negative $d'$ can always be found, it must be that $d$ is unbounded.
-This is a demonstration of the fundamental \textit{Unboundedness Property} of~\cite{Bradley_1977}; if the dual is unbounded, then the primal is infeasible.
-\comment[TC]{\href{http://web.stanford.edu/~ashishg/msande111/notes/chapter4.pdf}{Farkas's lemma} here?}}
-
-    \begin{definition} An \term{infeasibility certificate}~\cite{Andersen_2001} is any vector $y$ that satisfies the constraint of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
-    \[ y \in \R^{\abs{\Events{\mscenario}}} : y \tcdot M \succeq 0, \quad y \tcdot \probvec^{\mscenario} < 0 \]
-    Furthermore, for every $y$ satisfying $y \tcdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of non-contextual marginal models $\s{NC}$,
-    \[ \forall \probvec^{\mscenario} \in \s{NC} : y \tcdot \probvec^{\mscenario} \geq 0 \]
-    \end{definition}
-
-    \todo[TC]{Discuss Infeasibility Certificates basis} \\
-
-    \todo[TC]{Discuss the certificate inequalities we found.} \\
-
-    \todo[TC]{Discuss Compatibility, connection to cooperative games/resources, bell incompatibility?} \\
-
-    \subsubsection{Fourier Motzkin Elimination \& Polytope Projection}
-
-    The complete space of marginal models over $\mscenario$ can be partitioned into two spaces: contextual ($\s{C}$) and non-contextual marginal models ($\s{NC}$).
-The separation between these spaces is completely characterized by the system of inequalities associated with \cref{eq:incidence_matrix_use}.
-Explicitly,
-    \begin{equation} \label{eq:halfspace_rep_incidence}
-    \begin{alignedat}{2}
-        \forall m \in \Events{\mscenario} :&&\quad \probvec^{\mscenario}_m - {\sum}_{j} M_{m, j} \probvec^{\jointvar}_j &\geq 0 \\
-        \forall m \in \Events{\mscenario} :&&\quad -\probvec^{\mscenario}_m + {\sum}_{j} M_{m, j} \probvec^{\jointvar}_j &\geq 0 \\
-        \forall j \in \Events{\jointvar} :&&\quad \probvec^{\jointvar}_j &\geq 0
-    \end{alignedat}
-    \end{equation}
-    Geometrically \cref{eq:halfspace_rep_incidence} is a family of $2\abs{\Events{\mscenario}} + \abs{\Events{\jointvar}}$ half-planes bounding $\R^{\abs{\Events{\mscenario}}} \times \R^{\abs{\Events{\jointvar}}}$.
-However testing the contextuality of a marginal model $\probvec^{\mscenario}$ requires a collection of inequalities bounding just $\R^{\abs{\Events{\mscenario}}}$.
-Transforming \cref{eq:halfspace_rep_incidence} into the desired system of inequalities is the task of linear-quantifier elimination.
-A popular tool for linear quantifier elimination is Fourier-Motzkin elimination \cite{Dantzig_1973,Inflation,Abramsky_2012,jones_2004}.
-We will avoid expounding the Fourier-Motzkin procedure in this paper and instead reproduce a few of its notable features and consequences.
-
-    \begin{definition} \cite[Section 12.2]{Schrijver_1998}
-        The \term{Fourier-Motzkin elimination} procedure begins with a matrix $A$ and a vector $b$ defining a system of inequalities $S_1 = \bc{A\tcdot x \leq b}$ constraining a set of variables $x$ and symbolically eliminates a sub-set of theses variables $x \setminus y$.
-Upon completion, one obtains a new set of constraints $S_2 = \bc{A' y \leq b'}$ such that,
-        \[ \exists y : A' y \leq b' \iff \exists x : A x \leq b \]
-        Any solution $y$ of $S_2$ will permit at least one solution $x$ in $S_1$ (and vice versa).
-    \end{definition}
-
-    When applied to the marginal problem of \cref{eq:halfspace_rep_incidence}, the Fourier-Motzkin procedure eliminates all reference to the joint probabilities $\probvec^{\jointvar}_j$ and returns a system of inequalities over the marginal probabilities $\probvec^{\mscenario}_m$ representing a \textit{complete} solution to the marginal problem.
-Applying the Fourier-Motzkin procedure to completely solve the marginal problem is discussed in more detail in~\cite{Inflation} and~\cite{Fritz_2011}.
-\todo[TC]{Improve this discussion of FMP}.
-\\
-
-    \todo[TC]{Discuss why FM is slow?}\\
-
-    \begin{remark}
-        In theory, Fourier-Motzkin offers a complete solution to the marginal problem for all marginal scenarios; its limitations are purely computational.
-In addition, the entire procedure only utilizes field operations \cite{Abramsky_2012} meaning that since \cref{eq:halfspace_rep_incidence} is a rational system of inequalities, then a complete solution to the marginal problem only requires a finite set of linear, rational coefficient inequalities.
-    \end{remark}
-
-    \begin{theorem}
-        There exists a set of necessary and sufficient conditions
-
-    \end{theorem}
-
-    \todo[TC]{Logical Bell inequalities paper: only need to consider rational inequalities, actually integer inequalities, actually homogeneous inequalities} \\
-    \todo[TC]{Discuss computational complexity} \\
-    \todo[TC]{Mention what a complete solution looks like after using Fourier Motzkin}
-    \subsubsection{Marginal Polytope}
-    \begin{definition}
-        Let $I_{1}$ and $I_{2}$ represent two
-    \end{definition}
-    \begin{definition}
-        Let $\s{I}$
-    \end{definition}
-
-    \todo[TC]{Very briefly discuss polytope perspective and facet inequalities vs. non-facet inequalities}
-    \todo[TC]{Define facets as irreducible inequalities}
-
-    \todo[TC]{Maybe put the description of our task here. This will motivate the need for more scalable approaches.}
-
-    \section{Transversal Inequalities}
-
-    Section \ref{sec:linear_programs} discusses how one can obtain a $\s{NC}$-inequality that witnesses the contextuality of a particular marginal model $\probvec^{\mscenario}$ by writing the marginal problem as a linear program.
-Every $\probvec^{\mscenario} \in \s{NC}$ is witness-able by some certificate inequality.
-Albeit when a candidate marginal model $\probvec^{\mscenario}$ is not present, linear optimization offers no utility.
-\\
-
-    This section aims to develop a procedure for finding \textit{all} certificate inequalities in a computationally efficient manner.
-Specifically by finding all certificate inequalities that are also facets of the marginal polytope.
-Before doing so, we will first summarize a method \todo[TC]{Method where this idea came from, original insight from Hardy?} that can be used to obtain a complete solution to the \textit{possibilistic} marginal problem~\cite{Mansfield_2012} and indirectly offer a \textit{partial} solution to the \textit{probabilistic} marginal problem.
-
-    \subsection{Hardy Transversals}
-    \label{sec:logical_inequalities}
-    Let $a \in \Events{\mscenario}$ be any marginal event and $C = \bc{c_1, \ldots, c_{n}} \subseteq \Events{\mscenario}$ be a subset of the marginal events.
-We say that the subset $C$ forms a \term{logical extension} of $a$ if the following logical implication holds for \textit{all} marginal models $\probvec^{\mscenario}$.
-    \[ a \implies c_1 \vee \ldots \vee c_n = \bigvee_{c \in C} c \eq \label{eq:1a_implication} \]
-    Which can be dictated: \textit{Whenever the event $a$ occurs, at least one the events in $C$ occurs.} In this paper, the marginal event $a$ will be referred to as the \textit{antecedent} and $C$ as the \textit{consequent set}.
-To clarify, a marginal model $\probvec^{\mscenario}$ satisfies \cref{eq:1a_implication} if there always exists at least one $c \in C$ that is possible ($\probvec^{\mscenario}_c > 0$) whenever $a$ is possible.
-A marginal model $\probvec^{\mscenario}$ violates \cref{eq:1a_implication} whenever \textit{none} of the sections in $C$ are possible while $a$ is nonetheless still possible.
-Marginal models that violate logical statements such as \cref{eq:1a_implication} are known as \term{Hardy Paradoxes}~\cite{Inflation,Mansfield_2012,Mancinska_2014}.
-The concept of witnessing quantum incompatibility on a logical level has been analyzed thoroughly for decades~\cite{Greenberger_1990,Abramsky_2012}; being motivated by a greater sense of robustness compared to probabilistic constraints.
-\\
-
-    All logical implications of the form \cref{eq:1a_implication} can be constructed by first selecting $a$ and then manufacturing a consequent set $C$ persuant to \cref{eq:1a_implication}.
-
-    \begin{definition}
-        \label{def:extendable_set}
-        For each marginal event $m \in \Events{\mscenario}$ the \term{extendable set of $m$ into $\jointvar$} is the set of all joint events $j \in \Events{\jointvar}$ that are extensions of $m$.
-        \[ \Ext[\jointvar]{m} = \bc{j \in \Events{\jointvar} \mid m \ext j} \]
-    \end{definition}
-
-    The extendable set of $m$ into $\jointvar$ is the subset of events in $\Events{\jointvar}$ that \textit{agree} with $m$ about valuations for variables in $\Dom{m}$.
-Practically speaking, the extendable set of $m$ into $\jointvar$ is represented by the $m$-th row of the incidence matrix $M$.
-
-    \begin{lemma}
-        \label{lemma:logical_extenable_set}
-        Let $a \in \Events{\mscenario}$ and $\probvec^{\mscenario} \in \s{NC}$ be non-contextual. Then,
-        \[ a \iff \bigvee_{j \in \Ext[\jointvar]{a}} j \eq \label{eq:lemma_logical_extendable_set}\]
-    \end{lemma}
-    The idea being if a joint distribution does exists, then the event $a$ represents partial knowledge of the entire system $\jointvar$; whenever $a$ is measured, exactly one joint event $j$ has occurred in reality and $j$ must be compatible with $a$.
-Likewise \cref{lemma:logical_extenable_set} applies to the consequent set $C \in \Events{\mscenario}$,
-    \[ \bigvee_{c \in C} c \iff \bigvee_{c \in C} \bigvee_{j \in \Ext[\jointvar]{c}} j \eq \label{eq:logical_extension_C}\]
-    If a subset $C$ can be found such that its extendable set \textit{covers} the extendable set of $a$,
-    \[ \Ext[\jointvar]{a} \subseteq \bigcup_{c \in C} \Ext[\jointvar]{c} \eq \label{eq:logical_containment} \]
-    Then the combination of \cref{eq:lemma_logical_extendable_set,eq:logical_extension_C,eq:logical_containment} yields \cref{eq:1a_implication}.
-Computationally enumerating all logical extensions $C \subseteq \Events{\jointvar}$ for a particular antecedent $a \in \Events{\mscenario}$ corresponds iteratively selecting marginal sections $c \neq a$ for membership in $C$ until \cref{eq:logical_containment} is satisfies.
-This process is more generally known as a set-covering problem, or a hypergraph transversal problem~\cite{Inflation}, an idea we return to in the more general picture to follow in \cref{sec:dep}.
-\todo[TC]{Maybe use an example here to define a Hardy transversal.}\\
-
-    It is possible to show that for each logical constraint there exists a probabilistic constraint that is tighter.
-The principle statement of \cref{lemma:logical_extenable_set} can be taken in a probabilistic form.
-If the marginal model $\probvec^{\mscenario}$ is to admit a joint distribution $\probvec^{\jointvar}$, then it must be that the antecedent probability $\probvec^{\mscenario}_a$ is equal to a marginalization over its extendable set into $\jointvar$.
-    \[ \probvec^{\mscenario}_a = \sum_{j \in \Ext[\jointvar]{a}}\probvec^{\jointvar}_j \eq \label{eq:marginal_extendable_sum_a} \]
-    This is nothing more than the the $a$-th row of \cref{eq:incidence_matrix_use}. Likewise for the consequent set,
-    \[ \sum_{c \in C}\probvec^{\mscenario}_c = \sum_{c \in C}\sum_{j \in \Ext[\jointvar]{c}}\probvec^{\jointvar}_j \eq \label{eq:marginal_extendable_sum_cs} \]
-    Since $C$ is a logical extension of $a$, the right-hand side of \cref{eq:marginal_extendable_sum_a} \textit{algebraically} covers \cref{eq:marginal_extendable_sum_cs}\footnote{If there were a joint event $j^*$ present on the right-hand side of \cref{eq:marginal_extendable_sum_a} but not the right-hand side of \cref{eq:marginal_extendable_sum_cs}, then \cref{eq:1a_probabilistic} would be violated by the deterministic joint distribution where $\probvec^{\jointvar}_{j^*} = 1$}.
-Therefore one recovers the probabilistic version of \cref{eq:1a_implication},
-    \[ \probvec^{\mscenario}_a \leq \sum_{c \in C}\probvec^{\jointvar}_c \eq \label{eq:1a_probabilistic} \]
-    Due to the logical precedent, inequalities of the form of \cref{eq:1a_probabilistic} are called \term{Hardy inequalities}.
-Marginal models that are contextual on a logical level are \term{possibilistically contextual}.
-In~\cite{Abramsky_2011} it was demonstrated that all possibilistically contextual models have their contextuality witnessed by logical extensions.
-In this sense, logical implications of the form \cref{eq:1a_implication} completely solve the possibilistic marginal problem.
-    \todo[TC]{Discuss logical bell inequalities}
-    \begin{remark}
-        The probabilistic logical extension \cref{eq:1a_probabilistic} is an \textit{upgraded} version of \cref{eq:1a_implication} in the following sense.
-        \begin{itemize}
-            \item Every $\probvec^{\mscenario} \in \s{NC}$ satisfies both \cref{eq:1a_probabilistic} and \cref{eq:1a_implication}.
-            \item Every $\probvec^{\mscenario} \in \s{C}$ that violates \cref{eq:1a_implication} will also violate \cref{eq:1a_probabilistic}; but the converse is not necessarily true.
-        \end{itemize}
-    \end{remark}
-
-    \subsection{Definite Extensions}
-    We will now generalize the notion of a Hardy transversal by considering multi-sets of antecedents corresponding to multiple marginal events each accompanied by an assigned multiplicity.
-Afterwards we provide an algorithm to completely solve the marginal problem by transversing generalized hypergraphs.
-To our benefit, this technique for solving the marginal problem offers considerable advantages over existing methods when dealing with large marginal scenarios.
-\\
-
-    To facilitate the discussion, some definitions and notation are necessary.
-    \begin{definition}
-        A \term{multi-set} or \term{bag} $\ga$ for a marginal scenario $\mscenario$ is a vector indexed by marginal events $m \in \Events{\mscenario}$ whose entries are integers $\ga_{m} \in \Z$.
-The \term{support} $\supp{\ga}$ of an bag is the subset of marginal events that are assigned non-zero multiplicity.
-        \[ \supp{\ga} \defined \bc{m \in \Events{\mscenario} \mid \ga_m \neq 0} \]
-        The \term{order} $\abs{\ga}$ of a multi-set $\ga$ is entry-wise sum of $\ga$.
-        \[ \abs{\ga} = \sum_{m \in \Events{\mscenario}} \ga_m = \sum_{m \in \supp{\ga}} \ga_m \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{marginal indicator} vector $\de^{m}$ for a marginal event $m$ is the unit vector indexed by marginal outcomes $\Events{\mscenario}$ whose only non-zero entry is the marginal event $m$.
-        \[ \forall m' \in \Events{\mscenario} : \de^{m}_{m'} = \begin{cases}
-            1 & m' = m \\
-            0 & m' \neq m
-        \end{cases} \]
-        Analogously defined is the \term{joint indicator} vector $\de^{j}$.
-    \end{definition}
-
-    \begin{definition}
-        The \term{extension $\Ga$ of an multi-set $\ga$} for a marginal scenario $\mscenario$ is a vector indexed by \textit{joint} events $j \in \Events{\jointvar}$ and can be constructed by left-multiplication of $\ga$ into the incidence matrix $M$.
-        \[ \Ga \defined \ga \tcdot M \]
-    \end{definition}
-
-    For every multi-set $\ga$ there corresponds a candidate inequality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ whose validity is completely characterized by $\Ga$.
-    \begin{theorem}
-        \label{thm:definite_extension_main_thm}
-        Let $\ga$ be a multi-set for the marginal scenario $\mscenario$.
-Then the inequality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ is a valid non-contextuality inequality if and only if $\Ga$ is positive semi-definite.
-        \[ \forall \probvec^{\mscenario} \in \s{NC} : \ga \tcdot \probvec^{\mscenario} \geq 0 \iff \Ga \succeq 0  \eq \label{eq:thm:semi_definite_extension}\]
-    \end{theorem}
-    \begin{proof}
-        The proof follows directly from \cref{eq:incidence_matrix_use}. Since $\probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}$,
-        \[ \ga \tcdot \probvec^{\mscenario} = \ga \tcdot M \tcdot \probvec^{\jointvar} = \Ga \tcdot \probvec^{\jointvar} \]
-        If $\Ga \succeq 0$, then $\Ga \tcdot \probvec^{\jointvar} \geq 0$ which gives $\ga \tcdot \probvec^{\mscenario} \geq 0$.
-The forward case of \cref{eq:thm:semi_definite_extension} can be proven by contradiction.
-Suppose that $\ga \tcdot \probvec^{\mscenario} \geq 0$ for all marginal models but $\Ga \not \succeq 0$.
-Consequently there exists at least one joint outcome $j^{*}$ such that $\Ga_{j^{*}} < 0$.
-This negative entry can be exploited by a deterministic joint distribution $\probvec^{\jointvar} = \de^{j^{*}}$,
-        \[ 0 > \Ga_{j^{*}} = \Ga\tcdot \de^{j^{*}} = \ga \tcdot M \tcdot \de^{j^{*}}  \]
-        Which is a contradiction: $M \tcdot \de^{j^{*}}$ is a non-contextual marginal model but $\ga \tcdot M \tcdot \de^{j^{*}} \not \geq 0$.
-    \end{proof}
-
-    Clearly if the multi-set itself is positive semi-definite $\ga \succeq 0$ then $\Ga \succeq 0$ is also.
-Corresponding inequalities are then \textit{trivial}: being satisfied by all $\probvec^{\mscenario} \in \s{NC}$.
-As such, it is desired to obtain definite extensions $\Ga$ from \textit{indefinite} multi-sets $\ga$.
-
-    \begin{corollary}
-        Let $\ga$ be a multi-set for the marginal scenario $\mscenario$.
-Then the equality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} = 0}$ is satisfied by all non-contextual marginal models if and only if $\Ga$ is a null vector (i.e.
-$\forall j : \Ga_{j} = 0$).
-    \end{corollary}
-
-    \Cref{thm:definite_extension_main_thm} demonstrates it is possible to generate non-contextuality inequalities by finding multi-sets $\ga$ such that $\Ga \succeq 0$.
-In light of this, we will formally define the subset of joint outcomes $j$ that are preventing a candidate multi-set $\ga$ from having positive semi-definite extensions.
-
-    \begin{definition}
-        The \term{inhibiting set} $\inhibit\br{\ga}$ for a multi-set $\ga$ is the subset of joint outcomes preventing $\Ga \succeq 0$ from holding true.
-        \[ \inhibit\br{\ga} = \bc{j \in \Events{\jointvar} \mid \br{\ga \tcdot M}_j = \Ga_j < 0} \]
-    \end{definition}
-
-    Procedurally, definite extensions can be built by beginning with a seed multi-set $\ga^{(0)} = \ga^{A}$ composed entirely of non-positive entries and iteratively appending marginal events $m$ ($\ga^{(n+1)} = \ga^{(n)} + \de^{m}$) in such a way that progresses $\Ga^{(n)}$ toward becoming positive semi-definite (i.e.
-by decreasing the inhibiting set).
-Taking inspiration from logical, Hardy-type, transversal inequalities discussed in \cref{sec:logical_inequalities}, we can view this process as a weighted hypergraph transversal problem.
-
-    \subsection{Definite Extension Procedure}
-    \label{sec:dep}
-    Before discussing the definite extension procedure (DEP) directly, we will motivate its main algorithmic component (weighted hypergraphs transversals) with a short example.
-    \subsubsection{Example}
-    \begin{example}
-        \label{ex:hypergraph_example}
-        Recall the exemplary incidence matrix $M$ of \cref{eq:example_incidence}, \cref{ex:incidence_matrix}.
-Our aim is generate some valid non-contextuality inequalities for marginal models $\probvec^{\mscenario}$.
-To compactify notation, enumerate the marginal outcomes (rows of $M$) $1$ through $12$ $\br{m_1, \ldots, m_{12}}$ and the joint outcomes (columns of $M$) $1$ through $8$ $\br{j_1, \ldots, j_{8}}$ (see \cref{fig:compact_incidence}).
-        \begin{figure}
-        \begin{center}
-            \begin{minipage}[b]{.48\textwidth}
-                \centering
-                \[ M = \kbordermatrix{
-                    & j_1 & j_2 & j_3 & j_4 & j_5 & j_6 & j_7 & j_8 \\
-                    m_1 & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
-                    m_2 & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
-                    m_3 & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
-                    m_4 & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
-                    m_5 & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
-                    m_6 & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
-                    m_7 & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
-                    m_8 & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
-                    m_9 & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
-                    m_{10} & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
-                    m_{11} & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
-                    m_{12} & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
-                } \]
-                \caption{The incidence matrix for the binary marginal scenario $\mscenario = \bc{\bc{a,b},\bc{b,c}, \bc{a,c}}$ with marginal outcomes $m_1, \ldots, m_{12}$ and joint outcomes $j_1, \ldots, j_{12}$.}
-                \label{fig:compact_incidence}
-            \end{minipage}\hspace{0.04\textwidth}%
-            \begin{minipage}[b]{.48\textwidth}
-                \centering
-                \scalebox{1.0}{\input{../../figures/hypergraphs/minimal_example}}
-                \caption{An edge-weighted hypergraph $\hgraph_{\weights}$ corresponding to the antecedent set $\ga^{A}$ with $\ga^{A}_{m_3} = -1$ and $\ga^{A}_{m_8} = -2$.}
-                \label{fig:hypergraph_example}
-            \end{minipage}
-        \end{center}
-        \end{figure}
-        Now suppose our antecedent set is $\ga^{A}$ and has two specified entries:
-        \[ \ga^{A}_{m_{3}} = -1 \quad \ga^{A}_{m_{8}} = -2 \]
-        Then the antecedent extension is given by $\Ga^{A}= \ga^{A} \tcdot M$:
-        \[ \Ga^{A}_{j_{4}} = \Ga^{A}_{j_{8}} = -2 \quad \Ga^{A}_{j_{5}} = \Ga^{A}_{j_{6}} = -1 \]
-        The objective then becomes to \textit{cover} the joint events of the inhibiting set $\bc{j_{4}, j_{5}, j_{6}, j_{8}}$ with marginal events organized as a consequent multi-set $\ga^{C} \succeq 0$ such that,
-        \[ \Ga^{C} + \Ga^{A} \succeq 0 \]
-        Taking motivation from \cref{sec:logical_inequalities}, this procedure can be casted as a multi-node hitting problem, or an edge-weighted hypergraph problem.
-Construct a weighted hypergraph $\hgraph_{\weights}$ (see \cref{fig:hypergraph_example}) where the edges are labeled by joint outcomes $\edges = \bc{e_{j_{4}}, e_{j_{5}}, e_{j_{6}}, e_{j_{8}}}$.
-These edges are assigned weights $w_j$ precisely equal to the magnitude of $\Ga^{A}$.
-        \[ \forall j \in \bc{{j_{4}}, {j_{5}}, {j_{6}}, {j_{8}}} : w_{j} = - \Ga^{A}_j \]
-        These weights characterize the joint events that are preventing $\Ga$ from becoming positive semi-definite.
-The nodes represent all possible marginal events that have the potential to contribute to $\ga^{C}$.
-        \[ \nodes = \bc{m_2, m_4, m_5, m_6, m_{10}, m_{11}, m_{12}} \]
-        A node $m$ is a member of edge $e_{j}$ if $m \ext j$.
-By inspection of \cref{fig:hypergraph_example} one can identify numerous multi-sets of $\ga^{C}$ of $\nodes$ that hit each edge $w_j$ times.
-As a singular example,
-        \[ \trans = \bc{m_{2}, m_{10}, m_{11}, m_{12}, m_{12}} = \kbordermatrix{
-            & m_2 & m_4 & m_5 & m_6 & m_{10} & m_{11} & m_{12} \\
-            &   1 &   0 &   0 &   0 &      1 &      1 &      2
-        } \]
-        satisfies this condition.
-We call such $\trans$ \textit{transversals} of $\hgraph_{\weights}$.
-This multi-set enables one to construct the positive semi-definite extension $\Ga^{C} + \Ga^{A}$ where $\Ga^{C} = \trans \tcdot M$.
-This corresponds to the inequality $- \ga^{A} \tcdot \probvec^{\mscenario} \leq \ga^{C} \tcdot \probvec^{\mscenario}$,
-        \begin{align*}
-        \probvec^{\mscenario}_{m_3} + 2 \probvec^{\mscenario}_{m_8} &\leq \probvec^{\mscenario}_{m_{2}} + \probvec^{\mscenario}_{m_{10}} + \probvec^{\mscenario}_{m_{11}} + 2 \probvec^{\mscenario}_{m_{12}} \\
-        \prob[][m_3] + 2 \prob[][m_8] &\leq \prob[][m_{2}] + \prob[][m_{10}] + \prob[][m_{11}] + 2 \prob[][m_{12}] \\
-        \prob[ab][10] + 2 \prob[bc][11] &\leq \prob[ab][01] + \prob[ac][01] + \prob[ac][10] + 2 \prob[ac][11]
-        \end{align*}
-    \end{example}
-    % \begin{definition}
-    %     For convenience, denote the $m$-th row of the incidence matrix $M$ as $\de^{m \ext \jointvar}$ and the $j$-th column of $M$ by $\de^{j \res \mscenario}$.
-    %     \[ \de^{m \ext \jointvar}_j = \de^{j \res \mscenario}_m  = \de^{\mscenario \ext \jointvar}_{m,j} \]
-    %     The following relationships hold for the indicator vectors.
-    %     \[ \de^{\mscenario \ext \jointvar} \tcdot \de^{j} = \de^{j \res \mscenario} \qquad \de^{m} \tcdot \de^{\mscenario \ext \jointvar} = \de^{m \ext \jointvar} \]
-    % \end{definition}
-    % We first recall that every non-contextual marginal model $\prob^{\mscenario}$ can be written as the convex combination of columns of the incidence matrix $M$.
-    % \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} = \sum_{j \in \Events{\jointvar}} \de_{m \ext j} \prob[\jointvar][j] \]
-    % Thus we define the set of all non-contextual marginal models as $\mathcal{NC}$,
-    % \[ \mathcal{NC} \defined \bc{\probvec^{\mscenario} \mid \probvec^{\mscenario} = \sum_{j} \mu_{j} \de_{j \res \mscenario}, \mu_j \geq 0, \sum_{j} \mu_{j} = 1} \]
-
-    % \begin{definition}
-    %     Let $\mscenario$ be a marginal scenario and let $j \in \Events{\jointvar}$ be a joint outcome.
-The \term{restriction of $j$ onto $\mscenario$} is deterministic marginal model $\de_{j \res \mscenario} : \Events{\mscenario} \to \bc{0, 1}$.
-    %     \[ \de_{j \res \mscenario}\br{m} \defined \begin{cases}
-    %         1 & j \ext m  \\
-    %         0 & \textrm{otherwise}
-    %     \end{cases} \]
-    %     As a vector indexed by marginal outcomes $m \in \Events{\mscenario}$, $\de_{j \ext \mscenario}$ is precisely the $j$-th column of the incidence matrix.
-    % \end{definition}
-
-    % \begin{definition}
-    %     The \term{extension of an m-set} $\ga{S}$ into $\jointvar$ denoted $\Ga{S}$ is a vector indexed by \textit{joint} outcomes $j \in \Events{\jointvar}$ and is defined as follows,
-    %     \[ \Ga{S}_{j} \defined \sum_{s \in \supp{\ga{S}}} \ga{S}_{s} \de_{s \ext j} \eq \label{eq:joint_multiplicity} \]
-    %     As an immediate consequence, the support of $\Ga{S}$ is immediately known,
-    %     \[ \supp{\Ga{S}} = \bigcup_{s \in \supp{\ga{S}}} \Ext[\jointvar]{s} \]
-    % \end{definition}
-    % \begin{definition}
-    %     An m-set $\ga{C}$ is an \term{extension cover} of an m-set $\ga{A}$ for a marginal scenario $\mscenario$ if and only if the following two conditions hold\footnote{In fact \cref{eq:multi_extenable_cover_def} implies \cref{eq:flat_extenable_cover_def} since $\forall j \not \in \supp{\Ga{A}} : \Ga{A}_j = 0$.}:
-    %     \begin{gather*}
-    %         \supp{\Ga{A}} \subseteq \supp{\Ga{C}} \eq \label{eq:flat_extenable_cover_def}\\
-    %         \forall j \in \supp{\Ga{A}} : \Ga{A}_{j} \leq \Ga{C}_j \eq \label{eq:multi_extenable_cover_def}
-    %     \end{gather*}
-    % \end{definition}
-    % Identifying extension covers is of great importance because of the following theorem.
-    % \begin{theorem}
-    %     \label{thm:extendable_cover_ineq}
-    %     If the m-set $\ga{C}$ is an extension cover of the m-set $\ga{A}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
-    %     \[ \sum_{a \in \supp{\ga{A}}}\ga{A}_a\prob[][a] \leq \sum_{c \in \supp{\ga{C}}}\ga{C}_c\prob[][c] \eq \label{eq:extendable_cover} \]
-    % \end{theorem}
-    % \begin{proof}
-    %     To prove that \cref{eq:extendable_cover} is a valid compatibility inequality $I_{\mscenario}$ for all marginal models $\prob^\mscenario$, we will demonstrate that \cref{eq:extendable_cover} follows from the assumption that a joint distribution $\prob[\jointvar]$ exists.
-
-    %     For each m-set $\ga{S}$ write the weighted sum over the probabilities $\bc{\prob[][s]}_{s \in \supp{\ga{S}}}$ in terms of the joint distribution $\prob[\jointvar]$ using \cref{eq:joint_multiplicity}.
-    %     \begin{align*}
-    %     \eq \label{eq:derivation_cover}
-    %     \begin{split}
-    %     \sum_{s \in \supp{\ga{S}}} \ga{S}_s\prob[][s] &= \sum_{s \in \supp{\ga{S}}} \ga{S}_s  \sum_{j \in \Ext[\jointvar]{s}} \prob[\jointvar][j] \\
-    %     &= \sum_{s \in \supp{\ga{S}}} \ga{S}_s \sum_{j \in \Events{\jointvar}} \isext{s}{j} \prob[\jointvar][j] \\
-    %     &= \sum_{j \in \Events{\jointvar}} \bs{\sum_{s \in \supp{\ga{S}}} \ga{S}_s  \isext{s}{j}} \prob[\jointvar][j] \\
-    %     &= \sum_{j \in \supp{\Ga{S}}} \Ga{S}_j \prob[\jointvar][j]
-    %     \end{split}
-    %     \end{align*}
-    %     First examine the substitution $S \to C$,
-    %     \[ \sum_{c \in \supp{\ga{C}}} \ga{C}_c\prob[][c] = \sum_{j \in \supp{\Ga{C}}} \Ga{C}_j \prob[\jointvar][j] \]
-    %     By \cref{eq:flat_extenable_cover_def} $\supp{\Ga{A}} \subseteq \supp{\Ga{C}}$,
-    %     \[ \sum_{c \in \supp{\ga{C}}} \ga{C}_c\prob[][c] = \sum_{j \in \supp{\Ga{C}}} \Ga{C}_j \prob[\jointvar][j] + \sum_{j \in \supp{\Ga{C}} \setminus \supp{\Ga{A}}} \Ga{C}_j \prob[\jointvar][j] \]
-    %     Notice that the sum over $j \in \supp{\Ga{C}} \setminus \supp{\Ga{A}}$ is entirely positive since $\Ga{C}_j \in \N$ and $\prob[\jointvar][j] \geq 0$.
-Moreover \cref{eq:multi_extenable_cover_def} gives $\Ga{C}_j \geq \Ga{A}_j$.
-Combining these observations along with \cref{eq:derivation_cover} for $S \to A$, one arrives at the inequality,
-    %     \[ \sum_{c \in \supp{\ga{C}}} \ga{C}_c\prob[][c] \geq \sum_{j \in \supp{\Ga{A}}} \Ga{A}_j \prob[\jointvar][j] = \sum_{a \in \supp{\ga{A}}} \ga{A}_a\prob[][a] \]
-    %     Which is equivalent to \cref{eq:extendable_cover}; every non-contextual marginal model $\prob^{\mscenario}$ must satisfy \cref{eq:extendable_cover}.
-    % \end{proof}
-    % \begin{corollary}
-    %     \label{cor:linear_integer}
-    %     Every linear, integer coefficient compatibility inequality that is homogeneous is an extension covering inequality.
-    % \end{corollary}
-    % \begin{proof}
-    %     A proof is easy to see by contradiction.
-Let $I_{\mscenario} = \bc{\gamma \tcdot \probvec^{\mscenario} \geq 0}$ where $\gamma_m \in \Z | \forall m \in \Events{\mscenario}$ be a homogeneous, linear, integer coefficient, compatibility inequality such that it is \textit{not} an extension covering inequality.
-Next seperate $\gamma$ into its positive and negative components,
-    %     \[ \gamma_m^{+} = \begin{cases}
-    %         \gamma_m & \gamma_m > 0 \\
-    %         0 & \gamma_m \leq 0
-    %     \end{cases}
-    %     \qquad
-    %     \gamma_m^{-} = \begin{cases}
-    %         -\gamma_m & \gamma_m < 0 \\
-    %         0 & \gamma_m \geq 0
-    %     \end{cases} \]
-    %     Such that both $\gamma^{+}$ and $\gamma^{-}$ are valid m-sets.
-Therefore $I_{\mscenario} = \bc{\br{\gamma^{+} - \gamma^{-}} \tcdot \probvec^{\mscenario} \geq 0}$.
-Since this inequality is \textit{not} an extension cover, it must be that there exists at least one joint outcome $j' \in \Events{\jointvar}$ such that $\Gamma^{-}_{j'} > \Gamma^{+}_{j'}$.
-Consequently by \cref{eq:derivation_cover}, the deterministic distribution $\probvec^{\mscenario} = \de_{j' \res \mscenario}$ \textit{violates} $I_{\mscenario}$.
-However since $\de_{j' \res \mscenario} \in \mathcal{NC}$ and violates $I_{\mscenario}$, $I_{\mscenario}$ can not be a compatibility inequality; disagreeing with the assumption that it was.
-    % \end{proof}
-    % \begin{corollary}
-    %     If the m-set $\ga{C}$ is an extension cover of the m-set $\br{A, \mulA}$ for a marginal scenario $\mscenario$, then the following is a valid compatibility $I_{\mscenario}$ for the marginal scenario $\mscenario$.
-    %     \[ \sum_{a \in \supp{\ga{A}}}\prob[][a] \leq \sum_{c \in \supp{\ga{C}}}\prob[][c] \eq \label{eq:extendable_cover_flat} \]
-    % \end{corollary}
-    % \begin{proof}
-    %     This follows from the fact that if $\ga{C}$ is an extension cover of $\br{A, \mulA}$, then $\br{C, \mathbf{1}_{C}}$ is an extension cover of $\br{A, \mathbf{1}_{A}}$.
-Since $E_A \subseteq E_C$ is already trivially satisfied, all that remains is to demonstrate that \cref{eq:multi_extenable_cover_def} holds for unitary multiplicities $\mathbf{1}_A$ and $\mathbf{1}_C$.
-
-    %     First examine extension $\br{E_C, \mul{\mext{C}}}$ for the m-set $\ga{C}$ as defined by \cref{eq:joint_multiplicity},
-    %     \[ \forall j \in E_C : \Ga{C}_j = \sum_{c \in \supp{\ga{C}}} \mulC\br{c} \isext{c}{j} \]
-
-    %     First apply \cref{lemma:logical_extenable_set} to an arbitrary set $S \in \bc{A, C}$,
-    %     \[ \bigvee_{s \in \supp{\ga{S}}} s \iff \bigvee_{s \in \supp{\ga{S}}} \bigvee_{j \in \Ext[\jointvar]{s}} j \iff \bigvee_{j \in E_S} j \eq \label{eq:logical_iff_ext}\]
-    %     Now since $E_A \subseteq E_C$ by \cref{eq:flat_extenable_cover_def} we have that,
-    %     \[ \bigvee_{j \in E_A} j \implies \bigvee_{j \in E_C} j \eq \label{eq:logical_cover}\]
-    %     Combining \cref{eq:logical_iff_ext,eq:logical_cover} one arrives at,
-    %     \[ \bigvee_{a \in \supp{\ga{A}}} a \implies \bigvee_{c \in \supp{\ga{C}}}c \]
-    % \end{proof}
-    % For a working example, let $\jointvar = \bc{a, b, c}$ be a set of binary random variables ($O = \bc{0,1}$) and $\mscenario = \bc{\bc{a,b},\bc{b,c},\bc{a,c}}$ be the marginal context.
-    \subsubsection{Weighted Hypergraphs}
-    A \term{hypergraph} $\hgraph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{hyperedges} respectively where the hyperedges are \textit{subsets} of nodes $\forall e \in \edges : e \subset \nodes$.
-A hypergraph deviates from a traditional graph in that the edges have the capacity to contain more or less than $2$ nodes.
-There is a dual correspondence between the hyperedges $e \in \edges$ and nodes $n \in \nodes$ of a hypergraph: just as a hyperedge $e$ is interpreted as a set of nodes, a node $n$ can be viewed as the set of hyperedges $\bc{e \mid n \in e}$ that contain it.
-A \term{hypergraph transversal} (or edge hitting set) $\trans$ of a hypergraph $\hgraph$ is a set of nodes $\trans \subseteq \nodes$ that have a non-empty intersection with every hyperedge in $\edges$.
-    \[ \trans \subseteq \nodes \mid \forall e \in \edges : \trans \cap e \neq \emptyset \eq \label{eq:flat_trans_def}\]
-    A transversal $\trans$ is said to be \term{minimal} if there are no redundant nodes $n$ in $\trans$, i.e.
-no node $n$ can be removed from $\trans$ such that $\trans \setminus n$ remains a transversal.
-The condition for minimality expressed,
-    \[ \forall n \in \trans : \exists e \in \edges \mid \br{\trans \setminus n} \cap e = \emptyset \eq \label{eq:flat_trans_minimal}\]
-
-    When defining a \textit{weighted} hypergraph, there can be some ambiguity as to whether or not the weights $\weights$ are associated with the hyperedges or nodes.
-Since the definite extension procedure concerns itself with weighted hyperedges, we refer to edge-weighted hypergraphs simply as weighted hypergraphs.
-    \begin{definition}
-        A \term{(edge-)weighted hypergraph} $\hgraph_\weights$ is a hypergraph $\hgraph = \br{\nodes, \edges}$ together with a set of real-valued weights $\weights = \bc{w_e \mid e \in \edges}$ assigned to each hyperedge $e$.
-    \end{definition}
-    In the case of the definite extension procedure, these weights will typically be positive integers $w_e \in \Z_{> 0}$.
-As such, we make this the default setting moving forward.
-Accompanying weighted hypergraphs are the notion of weighted transversals.
-    \begin{definition}
-        A \term{weighted transversal} $\trans$ of a weighted hypergraph $\hgraph_{\weights}$ is a \textit{multi-set} or \textit{vector} of nodes $\forall n \in \nodes : \trans_n \in \N$ such that the total multiplicity of nodes in each hyperedge $e$ surpasses (or matches) the assigned weight $w_e$.
-        \[ \forall e \in \edges : \sum_{n \in e} \trans_{n} \geq w_e \eq \label{eq:weighted_trans_def}\]
-    \end{definition}
-    \begin{definition}
-        A weighted transversal $\trans$ of a weighted hypergraph $\hgraph_{\weights}$ is a said to be \term{minimal} or have \term{minimal-multiplicities} if all its entries $\trans_n : n \in \nodes$ are minimal in the sense that there does not exist a node $n' \in \supp{\trans}$ such that $\trans - \de^{n'}$ is still a transversal.
-        \[ \forall n' \in \nodes : \exists e \in \edges, n' \in e : \sum_{n \in e} \trans_{n} - 1 < w_e  \eq \label{eq:weighted_trans_minimal}\]
-        Equivalently, $\trans$ is minimal if there does not exists another transversal $\trans' \neq \trans$ such that $\forall j : \trans'_j \leq \trans_j$.
-    \end{definition}
-    Remark that if all assigned weights are singular $w_e = 1$, the weighted minimality condition \cref{eq:weighted_trans_minimal} reduces to the unweighted minimality condition \cref{eq:flat_trans_minimal}.
-The principle component of the definite extension procedure can be summarized as follows:
-
-    \subsubsection{Transversals of Antecedent Hypergraphs}
-    Given an antecedent multi-set $\ga^{A}$ where $\ga^{A} \preceq 0$, identify the \textit{inhibiting set} $\inhibit\br{\ga^{A}}$ responsible for preventing $\Ga^{A}$ from being classified as positive semi-definite.
-For an antecedent set $\ga^{A}$ where all entries are negative, there are a few equivalent ways of representing the inhibiting set,
-    \[ \inhibit\br{\ga^{A}} = \supp{\Ga^{A}} = \bc{j \mid \Ga^A_j < 0} = \bc{j \mid \exists m \in \supp{\ga^A} : m \ext j } \]
-    The last interpretation corresponding to the extendable set of $\supp{\ga^{A}}$.
-Using the inhibiting set $\inhibit\br{\ga^{A}}$, construct a weighted hypergraph $\hgraph_\weights\br{\ga^A}$ such that,
-    \begin{align*}
-    \edges\br{\ga^{A}} &= \bc{e_j \mid j \in \inhibit\br{\ga^{A}}} \\
-    e_j &= \bc{m \in \Events{\mscenario} \mid m \ext j, m \not \in \supp{\ga^A}} \\
-    \weights\br{\ga^{A}} &= \bc{w_j = - \Ga^{A}_j \mid j \in \inhibit\br{\ga^{A}}} \\
-    \nodes\br{\ga^A} &= \bigcup_{j \in \inhibit\br{\ga^A}} e_j \\
-    &= \bc{m \in \Events{\mscenario} \mid m \not \in \supp{\ga^A}, \exists m' \in \supp{\ga^A} : m \com m'}
-    \end{align*}
-    The hyperedges $e_j \in \edges\br{\ga^{A}}$ are indexed by the inhibiting set.
-Each hyperedge $e_j$ is the subset of marginal events $e_j \subseteq \Events{\mscenario}$ that are extendable to $j$ (yet not already included in $\ga^A$\footnote{At this point, it might be unclear why we disregard marginal outcomes in $\supp{\ga^A}$.
-Sufficient reasoning will become apparent when presented with a complete discussion of the definite extension procedure.}).
-The weights $\weights\br{\ga^A}$ equal the amount that $\Ga^{A}$ needs to recover by, and the nodes $\nodes\br{\ga^A}$ are simply the union of all edges.
-This weighted hypergraph is termed the \term{antecedent hypergraph}.
-    \begin{remark}
-        The structure of a hypergraph $\hgraph$ (disregarding weights) is best computationally implemented as a bitwise matrix $H$ where the rows of $H$ are in correspondence with the nodes $n \in \nodes$ of $\hgraph$.
-Likewise, the columns of $H$ are in correspondence with the edges $e \in \edges$ of $\hgraph$.
-The entires of $H$ can be populated according to edge inclusion.
-        \[ H_{n,e} = \begin{cases}
-            1 & n \in e \\
-            0 & n \not \in e
-        \end{cases} \]
-        Regarding the antecedent hypergraph $\hgraph\br{\ga^A}$, the matrix form $H\br{\ga^A}$ of $\hgraph\br{\ga^A}$ can be constructed by taking the incidence matrix $M$ and deleting rows not in $\nodes\br{\ga^A}$ and columns not in $\edges\br{\ga^A}$.
-As an example, consider \cref{ex:hypergraph_example} and the hypergraph of \cref{fig:hypergraph_example}.
-The corresponding matrix representation of the hypergraph of \cref{ex:hypergraph_example} is a sub-matrix of the the incidence matrix depicted in \cref{fig:compact_incidence}.
-        \[ H\br{\ga^A} = \kbordermatrix{
-            & j_4 & j_5 & j_6 & j_8 \\
-            m_2 & \kone & \kzer & \kzer & \kzer \\
-            m_4 & \kzer & \kzer & \kzer & \kone \\
-            m_5 & \kzer & \kone & \kzer & \kzer \\
-            m_6 & \kzer & \kzer & \kone & \kzer \\
-            m_{10} & \kone & \kzer & \kzer & \kzer \\
-            m_{11} & \kzer & \kone & \kzer & \kzer \\
-            m_{12} & \kzer & \kzer & \kone & \kone
-        } \]
-        Although it is possible to generate antecedent hypergraphs in this manner, we recommend against it.
-One of the advantages of the definite extension procedure (to be discussed in \cref{sec:advantages_dep}) is that typically the size of an antecedent hypergraph $H$ is \textit{far smaller} than the original incidence matrix $M$.
-For large enough marginal scenarios, $M$ becomes too resource intensive to hold in memory, while $H$ remains far more manageable.
-    \end{remark}
-
-    After generating an antecedent hypergraph $\hgraph\br{\ga^A}$, it is possible to find all valid, homogeneous, non-contextuality inequalities $I_\mscenario = \bc{ \ga \tcdot \probvec^{\mscenario} \geq 0}$ by finding all transversals of $\hgraph\br{\ga^A}$.
-As mentioned previously for each transversal $\trans$, the marginal multi-set $\ga^C$ agreeing with $\trans$ can be constructed,
-    \[ \forall m \in \supp{\trans} : \ga^C_{m} = \trans_m \]
-    Such that $\ga^A + \ga^C$ has definite extension, which by \cref{thm:definite_extension_main_thm} induces the valid inequality,
-    \[ I_\mscenario = \bc{\br{\ga^C + \ga^A} \tcdot \probvec^{\mscenario} \geq 0} \eq \label{eq:transversal_inequality}\]
-    More importantly, one only needs to consider \textit{minimal transversals} of $\hgraph\br{\ga^A}$.
-If a transversal $\trans$ is non-minimal, then there exists another transversal $\trans'$ such that $\trans' \preceq \trans$.
-A minimal transversal $\trans'$ would have correspondence with a tighter inequality $I_\mscenario' = \bc{\br{{\ga'}^C + \ga^A} \tcdot \probvec^{\mscenario} \geq 0}$ that is capable of witnessing contextually in a strictly large subset of marginal models $\probvec^{\mscenario}$.
-\\
-
-    \begin{definition}
-        Let $I_1$ and $I_2$ denote two different $\s{NC}$-inequalities.
-    \end{definition}
-
-    \begin{definition}
-        Let $\s{Y}$ denote the set of all multi-sets $\ga$ with positive semi-definite extensions,
-        \[ \s{Y} = \bc{\ga \mid \ga \tcdot M = \Ga \succeq 0} \]
-        A multi-set $\ga$ is said to be \term{reducible/redundant} if,
-        \[ \exists \ga^1, \ga^2 \in \s{Y} : \ga = \ga^1 + \ga^2, \ga \neq \ga^1 \neq \ga^2 \neq 0 \]
-    \end{definition}
-
-    \todo[TC]{Figure out language and how to delineate the idea of reducible and irreducible extensions}
-
-    Therefore, it is possible to generate a family of \textit{tight} inequalities for each antecedent choice
-
-    \subsubsection{Completeness}
-    \label{sec:completeness_dep}
-    \todo[TC]{FM section would demonstrate that linear, homogeneous, integer inequalities are sufficient} \\
-    \todo[TC]{Talk about how all facets with antecedent order $n$ would be found by DEP at level $n$} \\
-    \todo[TC]{Upper limit of DEP is set by lowest antecedent order of FM result} \\
-    \begin{theorem}
-        \label{thm:completeness}
-        \todo[TC]{main completeness theorem}
-    \end{theorem}
-    \subsubsection{Advantages}
-    \label{sec:advantages_dep}
-    \todo[TC]{Horizontally scalable} \\
-    \todo[TC]{Low Memory Overhead} \\
-    \todo[TC]{Effectively depth-first FM} \\
-    \todo[TC]{Offers partially solution when complete solution intangible} \\
-    \todo[TC]{Weighted transversal algorithms are natural extensions of regular algorithms} \\
-    \todo[TC]{inequalities found at lower orders of DEP hierarchy are either facets or are positively separable into one or more facets} \\
-    \todo[TC]{Symmetries MASSIVELY reduce search space, memory for complete solution (to be discussed)} \\
-    \todo[TC]{Can be adapted to find correlation inequalities} \\
-    \todo[TC]{Can be implemented as a relaxation procedure (becomes regular HT problem)} \\
-    \todo[TC]{Can be adapted to target a specific distribution} \\
-    \todo[TC]{Seed distributions to avoid trivial inequalities} \\
-    \subsubsection{Disadvantages}
-    \label{sec:disadvantages_dep}
-    \todo[TC]{We don't yet know exactly how high the hierarchy goes} \\
-    \todo[TC]{If complete solution is ultimately desired, FM is in principle far more efficient because it does need to prune anything} \\
-    \todo[TC]{Trivial equalities show that lower-order transversals are equivalent to higher order transversals (maybe not)} \\
-    \subsubsection{Unanswered questions}
-    % \todo[TC]{How to avoid regenerating inequalities that are reducible to lower order}
-    % Corollary \ref{cor:linear_integer} alludes to completeness of extension covers.
-It vaguely suggests that every non-contextuality inequality needs to be an extension cover, otherwise there would exist a compatible and deterministic distribution that violates it.
-We will now demonstrate this completeness explicitly by first discussing what is required of a complete solution to the marginal problem.
-    % \begin{definition}
-    %     A \term{complete solution to the marginal problem} is a finite set of $q$ vectors $\gamma_1, \ldots, \gamma_q$ together with $q$ real numbers $k \in \R$
-    % \end{definition}
-    % \begin{theorem}
-    %     \label{thm:complete_solution_log_cover}
-    %     The set of all logical covering inequalities forms a sufficient solution to the possibilistic marginal problem.
-    % \end{theorem}
-    % \begin{theorem}
-    %     \label{thm:complete_solution_ext_cover}
-    %     The set of all extension covering inequalities forms a sufficient solution to the probabilistic marginal problem.
-    % \end{theorem}
-    % \begin{proof}
-    % \end{proof}
-    % \begin{definition}
-    %     An extension cover $\ga{C}$ of $\ga{A}$ is said to be \term{minimal} if there does not exist an extension cover $\ga{C'}$ different from $\ga{C}$ such that,
-    %     \[ \forall j \in \Events{\jointvar} : \ga{C'}_j \leq \ga{C}_j \]
-    % \end{definition}
-
-    % If a more minimal extension cover $\ga{C'}$ does exists, then the inequality it defines (as per \cref{thm:extendable_cover_ineq} directly implies the inequality defined by $\ga{C}$.
-
-    % \begin{definition}
-    %     An extension cover $\ga{C}$ of $\ga{A}$ is said to be \term{reducible} if there exists a \textit{partition} of $\ga{C}$ and $\ga{A}$,
-    %     \[ \ga{C} = \ga{C_1} + \ga{C_2} \qquad \ga{A} = \ga{A_1} + \ga{A_2} \]
-    %     Such that $\ga{C_1}$ is an extension cover for $\ga{A_1}$ and $\ga{C_2}$ is an extension cover for $\ga{A_2}$.
-If $\br{\ga{C}, \ga{A}}$ does \textit{not} admit a partition, then it is said to be \term{irreducible}.
-    % \end{definition}
-
-    % \todo[TC]{Basis certificates}
-
-    % % \begin{algorithm}[H]
-    % % \caption{The Extension Cover Procedure (DEP)}
-    % % \label{alg:ecp}
-    % % \begin{algorithmic}
-    % %   \State $\ga{S}^{0} = \mul{\emptyset}$
-    % % \end{algorithmic}
-    % % \end{algorithm}
-
-    % % \begin{algorithm}
-    % %   \caption{The Extension Cover Procedure (DEP)
-    % %     \label{alg:ecp}}
-    % %   \begin{algorithmic}[1]
-    % %     \Require{An antecedent m-set $\ga{A}$ and a partial consequent m-set $\ga{S}$.}
-    % %     \Statex
-    % %     \Function{DEP}{$\ga{A}, \ga{S}$}
-    % %       % \Let{$z$}{$x \oplus y$} \Comment{$\oplus$: bitwise exclusive-or}
-    % %       % \Let{$\delta$}{$0$}
-    % %       % \For{$i \gets 1 \textrm{ to } n$}
-    % %       %   \If{$z_i \neq 0$}
-    % %       %     \Let{$\delta$}{$\delta + 1$}
-    % %       %   \EndIf
-    % %       % \EndFor
-    % %       \State \Return{$\delta$}
-    % %     \EndFunction
-    % %   \end{algorithmic}
-    % % \end{algorithm}
-
-    % \todo[TC]{Trivial nodes}
-    % \todo[TC]{Duplication under Deflation}
-    % \todo[TC]{Memory}
-    % \todo[TC]{Parallelization}
-    % \todo[TC]{Simplicial Complex}
-    % \subsubsection{Advantages}
-
-    % \subsubsection{Avoiding Trivial Inequalities}
-    % A \term{trivial compatibility inequality} $I_{\mscenario}$ is an inequality that is satisfied by all marginal models $\prob^{\mscenario}$, not just compatible ones.
-Trivial compatibility inequalities are of no importance Since the set of all extension cover inequalities
-    % \todo[TC]{Targeted Seeds}
-
-    % \begin{definition}
-    %     A \term{hypergraph transversal generation} is any algorithm that correctly generates the complete set of all minimal transversals of $\mathcal{H}$.
-    % \end{definition}
-
-    % \begin{definition}
-    %     Any hypergraph with strictly non-empty edges $\forall e \neq \emptyset$ will always admit the \term{trivial transversal} $\trans^*$ where all nodes are considered as members $\trans^* = \nodes$.
-Any hypergraph with empty edges will be called a \term{degenerate hypergraph} as it admits no transversals\footnote{Most authors require that all hypergraphs be non-degenerate~\cite{Kavvadias_2005}.}.
-    % \end{definition}
-    % Remark ?? guarantees that all marginal hypergraphs are non-degenerate. There are two distinct approaches to hypergraph transversal generation: \textit{top-down} and \textit{bottom-up}.
-    % \begin{definition}
-    %     A \term{top-down} hypergraph transversal generation refers to any algorithm that begins with the trivial transversal $\trans^*$ and iteratively removes unnecessary nodes from $\trans^*$.
-    % \end{definition}
-
-    % \begin{definition}
-    %     A \term{bottom-up} hypergraph transversal generation refers to any algorithm that begins with the empty set $\emptyset$ and iteratively adds nodes.
-    % \end{definition}
-
-    % One should select a top-down method if the typical size of minimal transversals $\abs{\trans}$ is comparable to the number of nodes $\abs{\nodes}$, otherwise a bottom-up method will perform better.
-    % For our purposes we implemented a deep-first transversal algorithm similar to
-    % Recalling
-
-    % \subsection{Weighted Hypergraph Transversals}
-    % In \cref{sec:certificate_inequalities} is was demonstrated that the Fritz distribution is witness-able via a certificate inequality. It is also possible to witness
-    % \todo[TC]{Discuss the Inequalities Derived/ Trivial and non-trivial}
-
-    % \todo[TC]{Weighted transversals and Optimizations}
-    % \todo[TC]{Seeding inequalities (huge advantage here)}
-    \section{Marginal Symmetries}
-    \label{sec:symmetry}
-    Exploiting symmetries of a marginal scenario are useful for a few distinct reasons.
-First, Bancal et.
-al.~\cite{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:comp_con_mp}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
-They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that quantum-non-trivial inequalities can be recovered from facets of a symmetric polytope.
-Numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
-The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.\\
-
-    In this section we discuss how to exploit symmetries in the definite extension procedure in order to reduce the size of the computational search space.
-In contrast to~\cite{Bancal_2010}, we gain advantage in a non-lossy way; symmetries drastically accelerate the rate in which the DEP finds facets of the unsymmetrical polytope.
-\\
-
-    To demonstrate what types of symmetries we have in mind, we present the following example:
-    \begin{example}
-        \label{ex:symmetries}
-        First consider the marginal scenario $\mscenario = \bc{\bc{a, b, c}, \bc{c, d}, \bc{a, d}}$ where each variable in $\jointvar = \bc{a,b,c,d}$ has binary outcomes: $O_a = O_b = O_c = O_d = \bc{0,1}$.
-Moreover, let $I_{\mscenario}$ be a $\s{NC}$-inequality,
-        \[ I_{\mscenario} = \bc{\prob[abc][010] \leq \prob[cd][00] + \prob[ad][01]}  \]
-        Intuitively, a the contextuality of $\probvec^{\mscenario}$ is independent of the how one labels outcomes.
-Therefore new $\s{NC}$-inequalities can be generated from $I_{\mscenario}$ by permuting its outcomes.
-Let $\geo_v : O_v \to O_v : \bc{0,1} \mapsto \geo_v\bs{\bc{0,1}} = \bc{1,0}$ be a permutation of the outcomes for variable $v$; i.e.
-$\geo_v$ ``flips'' the outcomes for $v$.
-Let $\geo = \geo_a \times \geo_c$ be the permutation of variables $a$ and $c$.
-The action of $\geo$ on outcome labels induces an action on the inequality $I_{\mscenario}$ itself,
-        \begin{align*}
-        \geo\bs{I_{\mscenario}} &= \bc{\prob[abc][\geo\bs{010}] \leq \prob[cd][\geo\bs{00}] + \prob[ad][\geo\bs{01}]} \\
-        &= \bc{\prob[abc][111] \leq \prob[cd][10] + \prob[ad][11]}
-        \end{align*}
-        The new inequality $\geo\bs{I_{\mscenario}}$ is also a valid $\s{NC}$-inequality.
-By design, any permutation $\geo$ over outcomes leaves the marginal scenario invariant ($\geo\bs{\mscenario} = \mscenario$) and thus we may write $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$.
-\\
-
-        Alternatively, permutations of the variables themselves are also permitted.
-Let $\gep : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \gep\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ be a permutation of the variables $\jointvar$.
-Intuitively $\gep$ acts on $I_{\mscenario}$ in the following way,
-        \begin{align*}
-        \gep\bs{I_{\mscenario}} &= \bc{\prob[\gep\bs{abc}][010] \leq \prob[\gep\bs{cd}][00] + \prob[\gep\bs{ad}][01]} \\
-        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
-        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
-        \end{align*}
-        In general (as in this example), permutations over all variables can modify the marginal scenario $\gep\bs{\mscenario} \neq \mscenario$; in general we write $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
-Although $\gep\bs{I_{\mscenario}}$ is in fact a valid $\s{NC}$-inequality, in constrains marginal models of a different marginal scenario $\gep\bs{\mscenario}$ and are in general of no interest.
-    \end{example}
-
-    \subsection{Marginal Symmetries}
-    As demonstrated by \cref{ex:symmetries}, permutations can be applied to inequalities themselves to generate new inequalities.
-To formalize this notion, let $\Perm{S}$ denote the \term{permutation group} acting on the set $S$ consisting of all bijective maps $\pi : S \to S$.
-    \[ \Perm{S} = \bc{\pi : S \to S} \eq \label{eq:permutation_group_def}\]
-    Together with the $\abs{S}\times\abs{S}$ permutation matrix $\PermM{\pi}$ for each permutation $\pi$,
-    \[ \forall i,j \in S : \quad {\PermM{\pi}}_{;i,j} \defined \begin{cases}
-        1 & \pi\br{i} = j\\
-        0 & \pi\br{i} \neq j\\
-    \end{cases} \]
-
-    \begin{definition}
-        A \term{marginal symmetry} of $\mscenario$ is a symmetry of the incidence matrix $M$ corresponding to a pair of permutations $\br{\pi_\mscenario \in \Perm{\Events{\mscenario}}, \pi_\jointvar\in \Perm{\Events{\jointvar}}}$ such that $M$ is invariant under permutation.
-        \[ \PermM{\pi_\mscenario} \tcdot M \tcdot \PermM{\pi_\jointvar} = M \]
-    \end{definition}
-
-    Identifying the set of all marginal symmetries for a given marginal model is very important; it allows one to generate new inequalities from known ones.
-
-    \begin{theorem}
-        \label{thm:inequalities_generated_symmetries}
-        For each $\s{NC}$-inequality $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ and marginal symmetry $\br{\pi_{\mscenario}, \pi_{\jointvar}}$, the inequality $\pi_{\mscenario}\bs{I_{\mscenario}}$ defined by,
-        \[ \pi_{\mscenario}\bs{I_{\mscenario}} \defined \bc{\pi^{-1}_{\mscenario}\bs{\ga} \tcdot \probvec^{\mscenario} \geq 0} \eq \label{eq:thm:inequalities_generated_symmetries}\]
-        is also a valid $\s{NC}$-inequality.
-    \end{theorem}
-    \begin{proof}
-        Since $I_{\mscenario} = \bc{\ga \tcdot \probvec^{\mscenario} \geq 0}$ is a $\s{NC}$-inequality, then by \cref{thm:definite_extension_main_thm}, $\ga \tcdot M = \Ga \succeq 0$.
-Also note that $\PermM{\pi_{\jointvar}}$ is invertible with $\PermM{\pi_{\jointvar}}^{-1} = \PermM{\pi^{-1}_{\jointvar}}$.
-Therefore,
-        \[ \Ga\tcdot\PermM{\pi_{\jointvar}}^{-1} = \ga \tcdot M \tcdot \PermM{\pi_{\jointvar}}^{-1} = \ga\tcdot \PermM{\pi_{\mscenario}}\tcdot M \]
-        But $\Ga \succeq 0 \implies \Ga\tcdot\PermM{\pi_{\jointvar}}^{-1} \succeq 0$. Thus,
-        \[ \ga\tcdot\PermM{\pi_{\mscenario}}\tcdot M \succeq 0 \eq \label{eq:thm:inequalities_generated_symmetries_step}\]
-        Interpreting $\ga\tcdot\PermM{\pi_{\mscenario}}$ as a multi-set for $\mscenario$,
-        \[ \forall m \in \Events{\mscenario} : \br{\ga\tcdot\PermM{\pi_{\mscenario}}}_m = \ga_{\pi^{-1}_{\mscenario}\bs{m}} \defined \pi^{-1}_{\mscenario}\bs{\ga}_m \]
-        Therefore \cref{eq:thm:inequalities_generated_symmetries_step} shows that $\pi^{-1}_{\mscenario}\bs{\ga}$ has a positive semi-definite extension and thus \cref{thm:definite_extension_main_thm} proves that \cref{eq:thm:inequalities_generated_symmetries} is also a valid $\s{NC}$-inequality.
-    \end{proof}
-    \begin{remark}
-        There are two equivalent interpretations for the permuted inequality $\pi_{\mscenario}\bs{I_{\mscenario}}$ of \cref{thm:inequalities_generated_symmetries}. Notice,
-        \[ \pi^{-1}_{\mscenario}\bs{\ga} \tcdot \probvec^{\mscenario} = \ga \tcdot \La_{\pi_{\mscenario}} \tcdot \probvec^{\mscenario} = \ga \tcdot \pi_{\mscenario}\bs{\probvec}^{\mscenario} \]
-        Which means one can either think of $\pi_{\mscenario}\bs{I_{\mscenario}}$ as being $I_{\mscenario}$ with the coefficients rearranged, or with the probabilistic assignments rearranged.
-    \end{remark}
-
-    \todo[TC]{Discuss the importance of symmetries to restrict branching in DEP}
-
-    Diagrammatically, for each marginal event $m \in \Events{\mscenario}$ and joint event $j \in \Events{\jointvar}$, the notion of extendability is preserved by $\br{\pi_\mscenario, \pi_\jointvar}$.
-    \begin{center}
-        \begin{tikzpicture}
-            \newcommand{\symmetryspace}{1.5};
-            \draw (0, \symmetryspace) node[](m){$m$};
-            \draw (\symmetryspace, \symmetryspace) node[](j){$j$};
-            \draw (0, 0) node[](pm){$\pi_{\mscenario}\bs{m}$};
-            \draw (\symmetryspace, 0) node[](pj){$\pi_{\jointvar}\bs{j}$};
-
-            \draw[->] (m) -- node[left]{$\pi_\mscenario$}(pm);
-            \draw[->] (j) -- node[right]{$\pi_\jointvar$}(pj);
-            \draw[-<] (m) -- (j);
-            \draw[-<] (pm) -- (pj);
-        \end{tikzpicture}
-    \end{center}
-    Fortunately, every incidence matrix $M$ has a useful \term{uniqueness property}: there are no duplicated columns or rows in $M$.
-This means that in every marginal symmetry $\br{\pi_\mscenario, \pi_\jointvar}$, $\pi_\jointvar$ is uniquely determined by $\pi_\mscenario$ and vice versa.
-Therefore we restrict our attention and discussions to row permutations $\pi_\mscenario$, with column permutations being in one-to-one correspondence.
-Henceforth we will denote to the most general marginal symmetry using $\pi$ and take it to mean a permutation over marginal events.
-\\
-
-    \subsection{Outcome Symmetry}
-    \label{sec:outome_label_symmetry}
-    \begin{definition}
-        The \term{outcome symmetry group} $\go$ for the set of joint variables $\jointvar = \bc{v_1, \ldots, v_n}$ is the direct product of permutations over the outcomes for each variable $v \in \jointvar$,
-        \[ \go \defined \Perm{O_{v_1}} \times \cdots \times \Perm{O_{v_n}} = \prod_{v \in \jointvar} \Perm{O_{v}} \]
-        The action of $\geo \in \go$ on any event $s \in \Events{V}$ (denoted $\geo\bs{s}$) where $V \subseteq \jointvar$ is defined as,
-        \[ \forall v \in \Dom{s} : \br{\geo\bs{s}}\br{v} \defined \geo\bs{s\br{v}} \eq \label{eq:act_on_outcome_label}\]
-    \end{definition}
-    \begin{theorem}
-        \label{thm:extendable_invariance_acto}
-        If a marginal event $m \in \Events{\mscenario}$ is extendable to the joint event $j \in \Events{J}$, then for any outcome permutation $\geo \in \go$, $\geo\bs{m}$ is extendable to $\geo\bs{j}$.
-        \[ m \ext j \iff \geo\bs{m} \ext \geo\bs{j} \eq \label{eq:extendable_invariance_acto}\]
-    \end{theorem}
-    \begin{proof}
-        The proof should be clear by the definition of extendability (\cref{def:section_extendable}).
-        \[ m \ext j \iff \forall v \in \Dom{m} : j\br{v} = m\br{v} \]
-        Every outcome permutation $\geo \in \go$ leaves the domain of the event invariant $\Dom{m} = \Dom{\geo\bs{m}}$. Thus by \cref{eq:act_on_outcome_label},
-        \begin{align*}
-        \forall v \in \Dom{\geo\bs{m}}: \br{\geo\bs{j}}\br{v} = \geo\bs{j\br{v}} = \geo\bs{m\br{v}} = \br{\geo\bs{m}}\br{v}
-        \end{align*}
-        Therefore we have that $m \ext j \implies \geo\bs{m} \ext \geo\bs{j}$. The left implication of \cref{eq:extendable_invariance_acto} follows by considering $\geo^{-1} \in \go$.
-    \end{proof}
-    \begin{corollary}
-        \label{coll:incidence_invariance}
-        Let $M$ be the incidence matrix for a marginal scenario $\mscenario$ and $\geo \in \go$ be an outcome permutation of the joint random variables $\jointvar$.
-By \cref{thm:extendable_invariance_acto}, the action of $\geo$ on $M$ leaves $M$ invariant ($\geo\bs{M} = M$),
-        \[ \geo\bs{M}_{m,j} \defined M_{\geo\bs{m},\geo\bs{j}} = \de_{\geo\bs{m} \ext \geo\bs{j}} = \de_{m \ext j} = M_{m,j} \eq \label{eq:incidence_invariance}\]
-    \end{corollary}
-    \subsection{Variable Symmetry}
-
-    In \cref{sec:outome_label_symmetry}, permutations of outcomes were introduced as symmetries of the incidence matrix $M$.
-However the proof of \cref{thm:inequalities_outcome_label_generation} indicates that any permutation leaving the incidence matrix intact can be used to generate new inequalities.
-\\
-
-    Following the observations of \cref{ex:symmetries}, it is always possible to permute the random variables in a marginal scenario to produce new and valid inequalities.
-A generic permutation group over a the complete set of variables $\jointvar$ is simply $\Perm{\jointvar}$.
-Unlike elements of $\Om$, permutations $\gep \in \Perm{\jointvar}$ have the undesired possibility of transforming $\mscenario$ into a different marginal scenario.
-    \[ \gep\bs{\mscenario} \defined \bc{\gep\bs{V_1}, \ldots, \gep\bs{V_k}} \neq \mscenario \]
-    This means that there could exist $V_i \in \mscenario$ such that $\gep\bs{V_i} \not \in \mscenario$.
-In particular, permutations $\gep$ retaining this property are unable to generate $\s{NC}$-inequalities over the same marginal scenario.
-
-    \begin{definition}
-        The \term{variable permutation group} $\gp$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario.
-        \[ \Phi \defined \bc{\gep \in \Perm{\jointvar} \mid \forall V \in \mscenario : \gep\bs{V} \in \mscenario} \]
-        The action of $\gep \in \gp$ on any outcome $f \in \Events{V}$ (denoted $\geo\bs{f}$) is defined as,
-        \[ \forall v \in \Dom{\gep\bs{f}} : \br{\gep\bs{f}}\br{v} \defined f\br{\gep^{-1}\bs{v}} \eq \label{eq:act_on_variable}\]
-    \end{definition}
-
-    \subsection{Causal Symmetry}
-
-    The aim of this section is to formalize what types of symmetries are present in a particular causal structure $\graph$.
-The group of these causal symmetries will define, for each compatibility inequality $I_{\mscenario}$, a family of inequalities that are also valid incompatibility inequalities.
-
-    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\gep$ from $N$ to $N$.
-    \[ \Perm{N} = \bc{\gep \mid \gep : N \to N} \]
-    The action of $\gep \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\gep$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
-    \begin{align*}
-    \gep\bs{\graph} &\defined \br{\gep\bs{\nodes}, \gep\bs{\edges}} \\
-    \gep\bs{\nodes} &\defined \bc{\gep\bs{n} \mid n \in \nodes} = \nodes \\
-    \gep\bs{\edges} &\defined \bc{\gep\bs{e} \mid e \in \edges}
-    \end{align*}
-    To motivate a more general treatment of such symmetries, consider the Triangle Scenario of \cref{fig:triangle_scenario}.
-Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\gep \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\gep\bs{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes.
-By construction, any valid compatibility inequality $I_{\mscenario}$ for the marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes.
-Therefore applying $\gep$ to all distributions in $I_{\mscenario}$ yields $\gep\bs{I_{\mscenario}} \defined \gep\bs{I}_{\gep\bs{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\gep\bs{\mscenario}$ defined as,
-    \[ \gep\bs{\mscenario} = \bc{\gep\bs{V_1}, \ldots, \gep\bs{V_k}} \]
-    % \begin{example}
-    %     \todo[TC]{Above trivial example.}
-    %     Consider the marginal scenario $V_{\bs{4}} = \bc{\bc{A,B,C}, \bc{A}, \bc{B}, \bc{C}}$ and the compatibility inequality $I_{\bc{ABC, A, B, C}}$ for the Triangle Scenario in \cref{fig:triangle_scenario} with the following form,
-    %     \[ \prob[ABC][002]\prob[ABC][003] \leq \prob[A][0]\prob[C][3] \]
-    %     Now consider $\gep = \bc{A \to A, B \to C, C \to B}$. Since $\gep\bs{\graph} = \graph$, $\gep\bs{I_{\mscenario}}$ is also a valid compatibility inequality,
-    % \end{example}
-    More generically, any permutation $\gep$ that preserves the graphical structure of $\graph$ can be applied to $I_{\mscenario}$ to generate new and valid compatibility inequalities.
-Specifically this alludes to the \term{graph automorphism group} $\Aut{\graph}$ of $\graph$.
-    \[ \Aut{\graph} \defined \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph} \]
-    In general, $\Aut{\graph}$ could include elements $\gep$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}.
-This behaviour is \textit{undesired} for causal inference where the latent nodes will never appear in a marginal scenario.
-Instead, the subgroup of $\Aut{\graph}$ that never maps observable nodes to latent nodes is the \term{set-wise stabilizer} of $\Aut{\graph}$ for $\nodes_O$ and will be expressed with a subscript.
-
-    \begin{definition}
-        The \term{causal symmetry group} for a causal structure $\graph$ is the graph automorphism subgroup that stabilizes the observable nodes.
-        \[ \Aut[\nodes_O]{\graph} = \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph, \forall n \in \nodes_O :\gep\bs{n} \in \nodes_O} \]
-        Given any compatibility inequality $I_{\mscenario}$, each element $\gep$ of the causal symmetry group defines a new valid compatibility inequality $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
-    \end{definition}
-
-    The inflation technique discussed in \cref{sec:summary_inflation} allows one to derive compatibility inequalities for a causal structure $\graph$ by considering the marginal problem over the pre-injectable sets of $\graph'$ denoted $\PreInj[\graph]{\graph'} = \bc{V_1, \ldots, V_k}$.
-It is important to recall that due to \cref{lem:inflation}, inequalities $I'$ for $\graph'$ are \textit{only} transferable to inequalities $I$ for $\graph$ if $I'$ is in terms of distributions over the pre-injectable sets $I'_{\PreInj[\graph]{\graph'}}$.
-As a consequence of this observation, we need to consider a subgroup of the causal symmetry group that preserves the pre-injectable sets,
-    \[ \gep\bs{\PreInj[\graph]{\graph'}} = \PreInj[\graph]{\graph'} \eq \label{eq:preserved_preinj} \]
-
-    \begin{definition}
-        The \term{restricted causal symmetry group} $\gp$ for a causal structure $\graph$ and a marginal scenario $\mscenario$ is the graph automorphism subgroup that stabilizes the marginal scenario $\mscenario$.
-        \[ \gp \defined \Aut[\mscenario]{\graph} = \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph, \forall V \in \mscenario : \gep\bs{V} \in \mscenario} \]
-        Given any compatibility inequality $I_{\mscenario}$ each element $\gep$ of the causal symmetry group defines a new valid compatibility inequality $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\mscenario}$ over the \textit{same} marginal context $\mscenario$.
-    \end{definition}
-
-    The restricted causal symmetry group for the pre-injectable sets of an inflation $\graph'$ is the ideal symmetry group for use with the inflation technique.
-If one obtains a particular inequality $I'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\gp$, an entire family of valid compatibility inequalities are also obtained.
-    \[ \bc{\gep\bs{I'}_{\PreInj[\graph]{\graph'}} \mid \gep \in \gp} \text{ where } \gp = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
-    We have obtained $\gp$ for the inflated triangle scenario \cref{fig:inflated_triangle_scenario}. $\gp$ is an order $48$ group with the following $4$ generators:
-    \begin{equation*}
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_1 \\
-    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_2 \\
-    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_3 \\
-    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_4 \\
-    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
-    \end{aligned}
-    \end{equation*}
-    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
-    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
-    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
-    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
-    It is easy to verify that $\gep_1, \gep_2, \gep_3, \gep_4$ are all automorphisms of the inflated Triangle Scenario $\graph'$ of \cref{fig:inflated_triangle_scenario}.
-Moreover they stabilize the observable nodes, and the map pre-injectable sets of \cref{eq:pre-injectable_triangle_scenario} to the pre-injectable sets.
-Finally, in the Triangle Scenario we have that,
-    \[ \gp = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \sim \Aut[\nodes_O]{\graph} \]
-    To see this, $\gep_1$ and $\gep_4$ become the identity element $\mathbb{I}$ in $\Aut[\nodes_O]{\graph}$ upon removal of the copy-index, leaving $\gep_2$ to generate reflections and $\gep_3$ to generate rotations.
-    \subsection{Symmetric Marginal Polytope}
-    Up until this point, we have discussed how new inequalities can be created from known ones by exploiting causal symmetry.
-Although very useful, we divert our attention to finding \textit{symmetric} inequalities themselves.
-    \[ \forall \gep \in \gp :  \gep\bs{I_{\mscenario}} = I_{\mscenario} \]
-    In order to do this, we must first define how elements $\gep \in \gp$ act on marginal outcomes $O_{\mscenario}$.
-    \begin{definition}
-        Let $\jointvar = \bc{v_1, \ldots, v_k}$ be a collection of random variables and let $\gep \in \Perm{\jointvar}$.
-$\jointvar$ is said to be \term{label invariant with respect to $\gep$} if the outcome labels for each variable $v \in \jointvar$ are unchanged under the action of $\gep$.
-        \[ \forall v \in \jointvar : O_{v} = O_{\gep\bs{v}} \]
-        Label invariance is a prerequisite for any kind of symmetry amoung random variables.
-    \end{definition}
-    \begin{definition}
-        Let $\jointvar = \br{v_1, \ldots v_k}$ be a collection of random variables along with a specific outcome $m \in \Events{V}$ where $V \subseteq \jointvar$.
-The action of $\gep \in \Perm{\jointvar}$ on $m$ is a new outcome $\gep\bs{m} \in \Events{\gep\bs{V}}$ over $\gep\bs{V} \subseteq \jointvar$ defined as follows,
-        \[ \forall v \in V : \br{\gep\bs{m}}\br{\gep\bs{v}} \defined m \br{v} \]
-        The idea being that $\gep$ modifies $m$ in such a way that permutes its domain while leaving its range invariant.
-    \end{definition}
-    \begin{example}
-        Consider the outcome $m = \bc{A \mapsto 0, B \mapsto 1, C \mapsto 2} \in \Events{\bc{A,B,C}}$ where all variables have $4$ possible outcomes $O_A = O_B = O_C = \bc{0,1,2,3}$ and the permutation $\gep = \bc{A \to D, B \to C, C \to B, D \to A}$.
-        The \textit{action} of $\gep$ on $m$ is as follows,
-        \begin{align*}
-            \gep\bs{m} &= \gep\bs{\bc{A \mapsto m\br{A}, B \mapsto m\br{B}, C \mapsto m\br{C}}} \\
-            &= \bc{\gep\bs{A} \mapsto m\br{A}, \gep\bs{B} \mapsto m\br{B}, \gep\bs{C} \mapsto m\br{C}} \\
-            &= \bc{D \mapsto m\br{A}, C \mapsto m\br{B}, B \mapsto m\br{C}} \\
-            &= \bc{D \mapsto 0, C \mapsto 1, B \mapsto 2} \\
-            &= \bc{B \mapsto 2, C \mapsto 1, D \mapsto 0}
-        \end{align*}
-        Evidently, $\gep\bs{m} \in \Events{\bc{B, C, D}}$.
-    \end{example}
-
-    Through repeated action of $\gep \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define group orbits of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$.
-    \begin{align*}
-        \Orb[\gp]{m} &\defined \bc{\gep\bs{m} \mid \gep \in \gp} \\
-        \Orb[\gp]{j} &\defined \bc{\gep\bs{j} \mid \gep \in \gp}
-    \end{align*}
-
-    \begin{definition}
-        The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and a particular restricted causal symmetry $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
-Each row of $M_{\gp}$ corresponds to a marginal orbit $\Orb[\gp]{m}$.
-Analogously each column of $M_{\gp}$ corresponds to a joint orbit $\Orb[\gp]{j}$.
-The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
-        \[ M_{\gp}\bs{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M\bs{m',j'} \]
-    \end{definition}
-
-    \subsection{Results}
-
-    \todo[TC]{How we obtained the desired symmetry group}
-    \todo[TC]{Group orbits to symmetric marginal description matrix}
-    \todo[TC]{representative antecedents completely solve the marginal problem}
-
-    \section{The Triangle Scenario}
-    \label{sec:triangle_scenario}
-    \begin{figure}
-    \begin{center}
-        \begin{minipage}[b]{.48\textwidth}
-            \centering
-            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
-            \caption{The casual structure of the Triangle Scenario. Three variables $A,B,C$ are observable and illustrated as triangles, while $X, Y, Z$ are latent variables illustrated as circles.}
-            \label{fig:triangle_scenario}
-        \end{minipage}\hspace{0.04\textwidth}%
-        \begin{minipage}[b]{.48\textwidth}
-            \centering
-            \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
-            \caption{An inflated causal structure of the Triangle Scenario \cref{fig:triangle_scenario}.}
-            \label{fig:inflated_triangle_scenario}
-        \end{minipage}
-    \end{center}
-    \end{figure}
-
-    The triangle scenario $\ts$ is a causal structure composed of $3$ parties $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
-It has that has been studied extensively in existing literature (see~\cite[Fig.
-1]{Steudel_2010},~\cite[Fig.
-6]{Chaves_2014},~\cite[Fig.
-8]{Branciard_2012},~\cite[Fig.
-8, Appendix E]{Henson_2014},~\cite[Fig.
-3]{Fritz_2012},~\cite[Fig.
-1]{Inflation}, $\ldots$) and is reproduced here in \cref{fig:triangle_scenario} for convenience.
-At the time of publication for~\cite{Branciard_2012} it was noted that characterizing locality in $\ts$ remained an open problem and that identifying locality constraints in this configuration seemed challenging.
-In~\cite{Henson_2014}, $\ts$ was classified as an ``interesting'' causal structure.\footnote{Indicating that conditional independence relations are not a sufficient characterization of compatibility for $\ts$~\cite{Henson_2014}.
-Note that in $\ts$ there are \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Additionally $\ts$ is presented along with a family of entropic inequalities that constrain the set of compatible distributions~\cite{Henson_2014}.
-Furthermore in~\cite{Fritz_2012}, Fritz demonstrated that $\ts$ is the \textit{smallest} correlation scenario in which their exists quantum incompatible distributions by explicitly mentioning one (which we elect to call the \textit{Fritz distribution} in \cref{sec:fritz_dist}) and poses an important question asking if other incompatible quantum distributions exist.
-Finally in~\cite{Inflation}, Wolfe et.
-al.
-make use of $\ts$ along with the Bell Scenario to demonstrate a novel technique for causal inference called the \textit{inflation technique} (summarized in \cref{sec:summary_inflation}).
-Wolfe et.
-al.
-validate the power and applicability of the inflation technique by proving incompatibility between $\ts$ and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints~\cite{Inflation}.
-Moreover, a family of polynomial, $2$-outcome, compatibility inequalities are explicitly derived for an exemplary inflation of $\ts$ and $37$ non-trivial representatives are printed in~\cite{Inflation}.
-
-    Identifying quantum-accessible distributions that are incompatible with the triangle scenario is of particular importance as it \todo[TC]{Discuss why we are doing this.}
-
-    As a preliminary search for quantum incompatibility in $\ts$, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements (see \cref{sec:param_quantum_states} for details) against the $37$ compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by~\cite{Henson_2014}.
-Unfortunately, none of these inequalities could be violated.
-These early results suggest, although do not prove, that quantum non-locality is not present in $\ts$ for \textit{two-outcome} measurements.
-We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in $\ts$ for a larger number of outcomes.
-
-    Specifically, we make use of the inflation technique for an inflated triangle scenario $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} and cast the \textit{causal compatibility} problem as a \textit{marginal problem}.
-We develop a new technique which we call the \textit{definite extension procedure (DEP)} to find a complete solution to the marginal problem that is suitable for large causal structures where the observable nodes are equipped with numerous outcomes.
-We use this technique to find numerous compatibility inequalities, some of which witness the incompatibility of the Fritz distribution.
-Before discussing the DEP, the Fritz distribution will be re-defined explicitly here, followed by a quick summary of the inflation technique of~\cite{Inflation}.
-Following these summaries of existing work, we present the DEP and its connection to Hardy-type paradoxes~\cite{Inflation,Liang_2011,Mansfield_2012}, certificate inequalities and logical Bell inequalities~\cite{Abramsky_2011}.
-Moreover, the DEP can be adapted to derive symmetric inequalities or inequalities bounding any subspace of marginal models.
-To conclude, we subject our found inequalities to non-linear optimizations and discuss the implications of our results.
-
-    \section{The Fritz Distribution}
-    \label{sec:fritz_dist}
-    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario~\cite{Fritz_2012}.
-Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
-    \begin{align*}
-    \eq \label{eq:fritz_dist}
-    \begin{split}
-    \prob[F][111] = \prob[F][221] = \prob[F][412] = \prob[F][322] = \prob[F][233] = \prob[F][143] = \prob[F][344] = \prob[F][434] &= \f{1}{32}\br{2 + \sqrt{2}} \\
-    \prob[F][121] = \prob[F][211] = \prob[F][422] = \prob[F][312] = \prob[F][243] = \prob[F][133] = \prob[F][334] = \prob[F][444] &= \f{1}{32}\br{2 - \sqrt{2}}
-    \end{split}
-    \end{align*}
-    Here the notation $\prob[F][abc] = \prob[ABC][abc] = \prob[][A=a,B=b,C=c]$ is used. The Fritz distribution $\prob[F]$ can be realized with the following quantum configuration:
-    \begin{equation}
-    \begin{gathered}
-    \label{eq:fritz_quantum_realization}
-    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\gp^+}\bra{\gp^+} \\
-    M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
-    M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
-    M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
-    \end{gathered}
-    \end{equation}
-    Where for convenience of notation $\psi_x$ is used to denote the superposition,
-    \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
-    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\gp^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.
-
-    Fritz first proved it's incompatibility~\cite{Fritz_2012} by showing $C$ acts a moderator to ensure measurement pseudo-settings for $A$ and $B$ are independent, satisfying non-broadcasting requirements for the standard Bell scenario.
-In fact, by coarse-graining outcomes for $A$ and $B$ and treating $C$ as a measurement-setting moderator, $P_F$ maximally violates the CHSH inequality.
-To illustrate this, begin with the CHSH inequality~\cite{CHSH_Original},
-    \[ \ba{AB|S_A=1, S_B=1} + \ba{AB|S_A=1, S_B=2} + \ba{AB|S_A=2, S_B=1} - \ba{AB|S_A=2, S_B=2} \leq 2 \eq \label{eq:CHSH}\]
-    Where $\ba{AB|S_A=i, S_B=j}$ is the correlation between $A$ and $B$ given the measurement settings for $A$ ($B$) is $i$ ($j$) respectively.
-Next each of $C$'s outcomes become the conditioned settings in \cref{eq:CHSH},
-    \[ \ba{AB|C=2} + \ba{AB|C=3} + \ba{AB|C=4} - \ba{AB|C=1} \leq 2 \eq \label{eq:chsh_c}\]
-    Finally, specifying the two outcome coarse-graining as $\bc{1,2,3,4} \rightarrow \bc{\br{1,4}, \br{2,3}}$ gives a definition of correlation,
-    \[ \ba{AB} \defined 2\bc{\prob[][11] + \prob[][14] + \prob[][41] + \prob[][44] + \prob[][22] + \prob[][23] + \prob[][32] + \prob[][33]} - 1 \]
-    Which when applied to the Fritz distribution \cref{eq:fritz_dist} gives the following correlations:
-    \begin{gather*}
-    \ba{AB|C=2} = 2 \bc{\f{1}{32}\bs{2\br{2+\sqrt{2}}+2\br{2-\sqrt{2}}}} - 1 = \f{\sqrt{2}}{2} \\
-    \ba{AB|C=3} = \ba{AB|C=4} = \f{\sqrt{2}}{2} \quad \ba{AB|C=1} = -\f{\sqrt{2}}{2}
-    \end{gather*}
-    Which when applied to \cref{eq:chsh_c} gives the familiar Tsirelson violation of $2\sqrt{2} \not\leq 2$~\cite{Cirelson_1980}.
-
-    Before continuing it is worth noting that \cref{eq:fritz_dist} is non-unique.
-Any distribution that is equal to \cref{eq:fritz_dist} via a permutation of outcomes or exchange of parties is also referred to as a Fritz distribution.
-Moreover, the quantum realization of \cref{eq:fritz_quantum_realization} is non-unique.
-In fact, \cref{eq:fritz_quantum_realization} is not the realization that Fritz originally had in mind.
-Nonetheless \cref{eq:fritz_dist} is taken as \textit{the} Fritz distribution for concreteness throughout this paper.
-
-    In~\cite{Fritz_2012}, Fritz posits the following question: \textit{Find an example of non-classical quantum correlations in $\ts$ together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}
-
-    \todo[TC]{Summarize Problem 2.17 in fritz BBT, make it more formal}
-
-    \section{Summary of the Inflation Technique}
-    \label{sec:summary_inflation}
-    The causal inflation technique, first pioneered by Wolfe, Spekkens, and Fritz~\cite{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of Ref.~\cite{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a probability distribution is compatible or incompatible with a given causal structure.
-As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
-Copies of the original nodes are distinguished by an additional subscript called the \term{copy-index}.
-For example node $A$ of \cref{fig:triangle_scenario} has copies $A_1, A_2, A_3, A_4$ in the inflation of \cref{fig:inflated_triangle_scenario}.
-Following the notions of Ref.~\cite{Inflation}, all such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
-A copy-index is effectively arbitrary, so $A'$ will refer to an arbitrary inflated copy of $A$.
-    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
-    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if $X = Y$ upon removal of the copy-index.
-Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
-    \begin{definition}
-        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
-        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
-    \end{definition}
-    The motivation being that since the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
-To do this, first notice that every compatible joint distribution $\prob[\nodes]$ uniquely defines a set of causal parameters for $\graph$.
-    \[ \forall n \in \nodes : \prob[n\mid \Pa[\graph]{n}] = \sum_{\nodes \setminus n} \prob[\nodes] \eq \label{eq:unique_causal_parameters}\]
-    Now since \cref{eq:inflation_defn} enforces that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$, one can create a set of \term{inflated causal parameters} using \cref{eq:unique_causal_parameters},
-    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \]
-    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course not all compatible joint distributions on $\nodes'$ are constructed in this way; all that is demonstrated is that all joint distributions constructed in this way are compatible.}.
-    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \]
-    This is known as the \term{weak inflation lemma}; compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$.
-Before generalizing to the inflation lemma, a careful observation needs to be made.
-For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$ over $N$ induces a compatible marginal distribution $\prob[N']$ over $N'$.
-In fact since $N'$ contains no duplicate nodes up to copy index (simply because $N \sim N'$ and $N$ cannot contain duplicate nodes), $\prob[N] = \prob[N']$.
-We refer such sets $N'$ as the \term{injectable sets} of $\graph'$ and $N$ the \term{images of the injectable sets} of $\graph$.
-    \begin{align*}
-        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
-        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
-    \end{align*}
-
-    \begin{lemma}
-        \label{lem:inflation}
-        \term{The Inflation Lemma} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-        This is lemma 3 of~\cite{Inflation}.
-    \end{lemma}
-
-    The inflation lemma is the most important result of the causal inflation technique~\cite{Inflation}.
-The contrapositive version of \cref{lem:inflation} is a powerful tool for determining compatibility.
-Any compatibility constraint on marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ of the inflated causal structure $\graph'$ correspond to valid compatibility constraints on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure.
-Corollary 5 of~\cite{Inflation} proves this explicitly for incompatibility inequalities $I$; which the remainder of this work focuses on.
-Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
-Therefore, in situations where latent nodes are present in $\graph$, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
-
-    In this work, we obtain inequalities that constrain the set of injectable marginal models $\bc{\prob[N'] \mid N' \in \ImInj[\graph]{\graph'}}$ for the inflated Triangle Scenario of \cref{fig:triangle_scenario} by considering the marginal problem (see \cref{sec:comp_con_mp}) for the set of \term{maximally pre-injectable sets}\footnote{The set of all pre-injectable sets forms a topological \textit{simplicial conplex}.
-`Maximal' refers to the pre-injectable sets that are no proper subset of another.}.
-A pre-injectable set $V$ is a subset of $\nodes'$ that can be decomposed into the disjoint union of injectable sets $V = \coprod_i N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ that are mutually \term{ancestrally independent},
-    \[ \forall i,j : N'_i \ancestralindep N'_j \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset  \]
-    In doing so, any distribution over all nodes of a pre-injectable set $\prob[\cup_i N'_i]$ will factorize according to graphical $d$-separation conditions~\cite{Pearl_2009},
-    \[ \prob[V] = \prob[\cup_i N'_i] = \prod_{i}\prob[N'_i] \]
-    This turns linear inequalities over the pre-injectable distributions into polynomial inequalities over the injectable distributions, allowing one to replace all such distributions with equivalent distributions over the original random variables of $\nodes$.
-$\PreInj[\graph]{\graph'}$ will denote the set of all pre-injectable sets.
-
-    Focusing on the inflation $\ts'$ depicted in \cref{fig:inflated_triangle_scenario}, we obtained the injectable sets $\Inj[\ts]{\ts'}$ along with the maximally pre-injectable sets through a simple graphical procedure outlined in~\cite{Inflation}.
-    \begin{equation*}
-        \eq \label{eq:pre-injectable_triangle_scenario}
-        \begin{gathered}
-            \textbf{Maximal Pre-injectable Sets} \\
-            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
-            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
-            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
-            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
-            \bc{A_1, B_3, C_4} \\
-            \bc{A_1, B_4, C_2} \\
-            \bc{A_2, B_1, C_4} \\
-            \bc{A_2, B_2, C_2} \\
-            \bc{A_3, B_3, C_3} \\
-            \bc{A_3, B_4, C_1} \\
-            \bc{A_4, B_1, C_3} \\
-            \bc{A_4, B_2, C_1}
-        \end{gathered}
-        \qquad
-        \begin{gathered}
-            \textbf{Ancestral Independences} \\
-            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
-            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
-            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
-            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
-            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
-            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
-            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
-            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
-            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
-            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
-            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
-            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
-        \end{gathered}
-    \end{equation*}
-    As can be counted, there are $12$ maximally pre-injectable sets $\ts'$ which will be indexed $1$ through $12$ in the order seen above ($\bc{V_1, \ldots, V_{12}}$).
-The maximally pre-injectable sets $\bc{V_i}_{i \in \bs{12}}$ form a maximal marginal scenario $\mscenario$ over the observable nodes of $\ts'$ when equipped with outcome labels.
-Using \cref{lem:inflation} inequalities $I_{\PreInj[\ts]{\ts'}}$ constraining the set of contextual marginal models $\prob^{\mscenario}$ can be deflated into polynomial inequalities over $I_{\ImInj[\ts]{\ts'}}$ bounding compatible marginal models over the images of the injectable sets in $\ts$.
-    \[ \ImInj[\ts]{\ts'} = \bc{\bc{A, B, C}, \bc{A}, \bc{B}, \bc{C}} \]
-    \comment[TC]{This is not all the images. I should clarify this.}
-
-    \section{Non-linear Optimizations}
-    \label{sec:optimizations}
-    \todo[TC]{Mention outlook on te importance of classification and determining interesting inequalities~\cite{Bancal_2010}}
-    Compatibility inequalities for a given causal structure are fantastic for finding incompatible distributions.
-In the inflation technique, this is no exception.
-Parameterizing a space distributions using a set of real-valued parameters $\lambda$, enables us to perform numerical optimizations against these inequalities in hopes that a particular set of parameters $\lambda$ is able to generate an incompatible distribution $\prob$.
-To illustrate this generic procedure and it's reliability, we will first examine the popular CHSH inequality.
-    \subsection{Numerical Violations of The CHSH Inequality}
-    The CHSH inequality~\cite{CHSH_Original} can we viewed as a causal compatibility inequality for the iconic Bell Scenario (Fig.
-19 of~\cite{Wood_2012}, Fig.
-11 of~\cite{Inflation}, Fig.
-1 a) of~\cite{Tavakoli_2015}, etc.) corresponding to Bell's notion of local causality~\cite{Wood_2012}.
-It constrains the set of 2-outcome bipartite distributions over local binary measurement settings for each party $\prob[AB\mid S_A S_B] \defined \bc{\prob[AB\mid 0 0], \prob[AB\mid 01], \prob[AB\mid 10], \prob[AB\mid 11]}$.
-Numerical optimization \textit{should} obtain the algebraic violation associated with the PR-Box correlations~\cite{PR_1995}.
-Maintaining full generality, we simply need to parameterize these $4$ distributions using \cref{eq:uniform_param}, each requiring $4$ real-valued parameters.
-We define the optimization target for the CHSH inequality to be the left-hand-side of \cref{eq:CHSH},
-    \[ I\tsb{CHSH} = \ba{AB|11} + \ba{AB|12} + \ba{AB|21} - \ba{AB|22} \]
-    Figure \ref{fig:CHSH_convex} demonstrates this optimization for $5$ random seed parameters $\lambda^0$, each converging to the expected value of $4$. Analogously,~\cite{Cirelson_1980}
-
-    \begin{figure}
-    \newlength\figureheight
-    \newlength\figurewidth
-    \setlength\figureheight{2.7in}
-    \setlength\figurewidth{.48\textwidth}
-    \begin{center}
-        \begin{minipage}[b]{.48\textwidth}
-            \centering
-            \includegraphics{../../figures/CHSH_convex.pdf}
-            \caption{Convex optimizations against $I\tsb{CHSH}$ recover algebraic violation of $4$.}
-            \label{fig:CHSH_convex}
-        \end{minipage}\hspace{0.04\textwidth}%
-        \begin{minipage}[b]{.48\textwidth}
-            \centering
-            \includegraphics{../../figures/CHSH_quantum.pdf}
-            \caption{Quantum optimizations against $I\tsb{CHSH}$ recover maximum violation of $2\sqrt{2}$.}
-            \label{fig:CHSH_quantum}
-        \end{minipage}
-    \end{center}
-    \end{figure}
-
-    \todo[TC]{Demonstrate Quantum, Convexity}
-    \todo[TC]{Why Inequalities are great for optimizations}
-    \todo[TC]{Non-linearity}
-    \todo[TC]{Techniques Used}
-    \todo[TC]{Finding maximum violation of CHSH easily}
-    \todo[TC]{Unreliance when number of parameters increases}
-    \todo[TC]{Issues with local minimum}
-    \todo[TC]{Using initial conditions close to fritz, obtain greater violation}
-    \todo[TC]{Greater violation shares possibilistic structure of fritz and violates CHSH under definition}
-    \todo[TC]{Not realizable with maximally entangled qubit states}
-    \todo[TC]{Not realizable with separable measurements}
-    \todo[TC]{Many non-trivial inequalities to be tested}
-    \todo[TC]{inequality -> dist -> inequality evolution}
-    \section{Conclusions}
-    \todo[TC]{Inflation technique allows one to witness fritz incompatibility}
-    \todo[TC]{Linear optimization induces certificates which are incompatibility witnesses}
-    \todo[TC]{There are quantum distributions in the Triangle Scenario that are incompatible and different from fritz in terms of entanglement but not possibilistic structure}
-    \section{Open Questions \& Future Work}
-    The marginal problem has be well studied in various contexts~\cite[\ldots]{Vorobev_1962,Inflation,Fritz_2011}.
-Reference~\cite{Fritz_2011} contains an excellent summary of its connection to other fields of research including knowledge integration, database theory and coalition games in game theory.
-    \todo[TC]{Lots of stuff}
-    \appendix
-    \section{Common Terminology \& Notation}
-
-    \subsection{Graph Theory}
-    \begin{definition}
-        \label{def:graph}
-        A \term{graph} is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes have the capacity to represent any object while the edges are defined as \textit{pairs} of nodes.
-Typical, although not necessary, the nodes (edges) are indexed by an index set $\ind_\nodes$ ($\ind_{\edges}$).
-        \begin{align*}
-            \nodes &= \bc{n_i \mid n_i \in \ind_{\nodes}} \\
-            \edges &= \bc{e_i = \bc{n_j, n_k} \mid i \in \ind_{\edges}, j,k \in \ind_{\nodes}}
-        \end{align*}
-    \end{definition}
-
-    \begin{definition}
-        \label{def:directed_graph}
-        A \term{directed graph} $\graph$ is a graph where each edge $e$ has an order or \term{direction}.
-        \begin{align*}
-            \nodes &= \bc{n_i \mid n_i \in \ind_{\nodes}} \\
-            \edges &= \bc{e_i = \br{n_j \to n_k} \mid i \in \ind_{\edges}, j,k \in \ind_{\nodes}}
-        \end{align*}
-    \end{definition}
-
-    \begin{definition}
-        \label{def:graph_terms}
-        The following definitions are common language in directed graph theory. Let $n, m \in \nodes$ be example nodes of the graph $\graph$.
-        \begin{itemize}
-            \item The \term{parents of a node}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
-            \item The \term{children of a node}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
-            \item The \term{ancestry of a node}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$
-        \end{itemize}
-        All of these terms can be generalized to sets of nodes $N \subseteq \nodes$ through union over the elements,
-        \begin{itemize}
-            \item The \term{parents of a node set}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
-            \item The \term{children of a node set}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
-            \item The \term{ancestry of a node set}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
-        \end{itemize}
-    \end{definition}
-
-    \begin{definition}
-        An \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$.
-        \[ \Sub[\graph]{N} \defined \br{N, \bc{e_i \mid i \in \ind_\edges, e_i \subseteq N}} \]
-        An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
-        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:dag}
-        A \term{directed acyclic graph} or \term{DAG} $\graph = \br{\nodes, \edges}$ is an directed graph (see \cref{def:directed_graph}) with the additional property that no node $n$ is in its set of \term{ancestors}.
-        \[ \forall n \in \nodes : n \notin \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}\]
-        It is critical to note the difference in language between \textit{ancestors} from \textit{ancestry}.
-The ancestry $\An[\graph]{n}$ of a node $n$ is defined in \cref{def:graph_terms} using \textit{whole} numbers $\mathbb{W}$.
-In contrast, the ancestors of a node are defined similarly with \textit{natural} numbers $\mathbb{N}$.
-    \end{definition}
-
-    \subsection{Probability Theory}
-
-    \begin{definition}
-        The \term{product distribution} of two disjoint probability distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as $\prob[V] \times \prob[W]$.
-        \[ \forall f \in \Events{V \cup W} : \br{\prob[V] \times \prob[W]}\br{f} \defined \prob[V][f|_{V}]\tcdot\prob[W][f|_{W}] \]
-        A product distribution of $k$ mutually disjoint distributions is defined as,
-        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
-        \[ \forall f \in \Events{W} : \br{\sum_{V \setminus W} \prob[V]}\br{f} \defined \sum_{g \in \Ext[V]{f}} \prob[V][g] \]
-    \end{definition}
-
-    \section{Exemplary Inequalities}
-    \section{Connections to Sheaf-Theoretic Treatment}
-    \section{Computationally Efficient Parametrization of the Unitary Group}
-    Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} suggest the parameterization of the unitary group $\mathcal{U}\br{d}$ using a $d\times d$-matrix of real-valued parameters $\lambda_{n, m}$,
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \tcdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
-    Where $P_l$ are one-dimensional projective operators,
-    \[ P_l = \ket{l}\bra{l} \eq \label{eq:projective_operator} \]
-    and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices,
-    \[ \sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m} \]
-    Where $1 \leq m < n \leq d$. Spengler et. al. proved the validity of \cref{eq:spengler_unitary} in Ref.~\cite{Spengler_2010_Unitary}.
-
-    For the sake of reference, let us label the matrix exponential terms in \cref{eq:spengler_unitary} in a manner that corresponds to their affect on an orthonormal basis $\bc{\ket{1}, \ldots, \ket{d}}$.
-    \begin{align}
-    \begin{split}
-        GP_l &= \exp\br{iP_l \lambda_{l,l}} \\
-        RP_{n,m} &= \exp\br{i P_n \lambda_{n,m}} \\
-        R_{m,n} &= \exp\br{i \si_{m,n} \lambda_{m,n}}
-    \end{split} \eq \label{eq:exp_terms}
-    \end{align}
-    It is possible to remove the reliance on matrix exponential operations in \cref{eq:spengler_unitary} by utilizing the explicit form of the exponential terms in \cref{eq:exp_terms}.
-As a first step, recognize the defining property of the projective operators \cref{eq:projective_operator},
-    \[ P_l^k = \br{\ket{l}\bra{l}}^k = \ket{l}\bra{l} = P_l \]
-    This greatly simplifies the global phase terms $GP_l$,
-    \[ GP_l = \exp\br{iP_l \lambda_{l,l}} = \sum_{k=0}^{\inf} \f{\br{iP_l \lambda_{l,l}}^k}{k!} = \mathbb{I} + \sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}P_l^k = \mathbb{I} + P_l \bs{\sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}} = \mathbb{I} + P_l \br{e^{i \lambda_{l,l}} - 1} \eq \label{eq:unitary_GP} \]
-    Analogously for the relative phase terms $RP_{n,m}$,
-    \[ RP_{n,m} = \cdots = \mathbb{I} + P_n \br{e^{i \lambda_{n,m}} - 1} \eq \label{eq:unitary_RP} \]
-    Finally, the rotation terms $R_{m,n}$ can also be simplified by examining powers of $i \sigma_{n,m}$,
-    \[ R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}} = \sum_{k=0}^{\inf} \f{\br{\ket{m}\bra{n} - \ket{n}\bra{m}}^k \lambda_{m,n}^k}{k!} \]
-    One can verify that the following properties hold,
-    \begin{align*}
-        \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^0 &= \mathbb{I} \\
-        \forall k \in \N, k \neq 0 : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k} &= \br{-1}^k\br{\ket{m}\bra{m} + \ket{n}\bra{n}} \\
-        \forall k \in \N : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k+1} &= \br{-1}^k\br{\ket{m}\bra{n} - \ket{n}\bra{m}}
-    \end{align*}
-    Revealing the simplified form of $R_{m,n}$,
-    \[ R_{m,n} = \mathbb{I} + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \sum_{j=1}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j}}{\br{2j}!} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sum_{j=0}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j+1}}{\br{2j+1}!} \]
-    \[ R_{m,n} = \mathbb{I} + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \eq \label{eq:unitary_R} \]
-    By combining the optimizations of \cref{eq:unitary_RP,eq:unitary_R,eq:unitary_GP} together we arrive at an equivalent form for \cref{eq:spengler_unitary} that is computational more efficient.
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}}} \tcdot \bs{\prod_{l=1}^{d} GP_l} \eq \label{eq:fast_spengler_unitary} \]
-    In quantum mechanics, the global phase of a state $\ket{\psi} \in \Hilb^n$ is a \textit{redundant} parameter.
-Parameterizing unitaries using \cref{eq:fast_spengler_unitary} is especially attractive since the global phase terms $GP_l$ can be dropped, allowing one to parameterize all unitaries in $\mathcal{U}\br{d}$ up to this degeneracy~\cite{Spengler_2010_Unitary}\footnote{In our implementation, we accomplish this by explicitly setting $\lambda_{l,l} = 0$ in \cref{eq:unitary_GP}}.
-    \[ U_{/ GP_l} = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}}} \eq \label{eq:fast_spengler_unitary_gp} \]
-    \todo[TC]{Explanation of Computational Complexity $\mathcal{O}\br{d^3}$ vs. $\mathcal{O}\br{1}$ using~\cite{Moler_2003}}
-    \todo[TC]{Pre-Caching for Fixed dimension $d$}
-    \todo[TC]{Talk about inverse via haar measure}
-
-    \section{Parametrization of Quantum States \& Measurements}
-    \label{sec:param_quantum_states}
-    Throughout \cref{sec:optimizations}, we utilize a variety of parameterizations of quantum states and measurements in order to generate quantum-accessible probability distributions.
-There are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Spengler_2010_Unitary,Fujii_2005,James_2001} with applications \todo[TC]{Finish this sentence}.
-For our purposes, we need to parameterize the space of quantum-accessible distributions $\prob[\mathcal{Q}]$ that are \textit{realized} on the Triangle Scenario.
-We have implemented $\prob[\mathcal{Q}]$ under the following description.
-    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \eq \label{eq:triangle_quantum_distributions} \]
-
-    \subsection{Quantum States}
-    The bipartite states $\br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ of \cref{eq:triangle_quantum_distributions} were taken to be two-qubit density matrices acting on $\Hilb^2 \otimes \Hilb^2$.\footnote{We also considered qutrit $\Hilb^3$ qutit $\Hilb^4$ states.
-However for $6$ $d$-dimensional $\Hilb^d$ states, the joint density matrix $\rho$ acts on $\br{\Hilb^d}^{\otimes 6}$ making it a $\br{d^6, d^6}$ matrix with $d^{12}$ entries.
-Computationally only $d = 2$ was feasible for our optimization tasks.} The space of all such states corresponds to the space of all $4\times 4$ positive semi-definite hermitian matrices with unitary trace.
-Throughout this section, we refer to these bipartite states simply as $\rho$ unless otherwise indicated.
-There are three distinct techniques that we have considered.
-
-    Taking inspiration from~\cite{James_2001}, we can parameterize all such density matrices $\rho$ using \term{Cholesky Parametrization}~\cite{Grasmair_2014}.
-The Cholesky decomposition allows one to write any hermitian positive semi-definite matrix $\rho$ in terms of a lower (or upper) triangular matrix $T$ using $\rho = T^\dagger T$.
-Our Cholesky parameterization consists of assigning $16$ real-valued parameters $\lambda$ to the entires of $T$ and generating a unitary trace $\rho$ similar to eq.
-(4.4) of~\cite{James_2001}.
-    \[ \rho = \f{T^\dagger T}{\Tr\br{T^\dagger T}} \quad T = \pmtrx{\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}} \eq \label{eq:cholesky_param} \]
-    Our deviation from exclusiving using \cref{eq:cholesky_param} is two-fold.
-First, \cref{eq:cholesky_param} is degenerate in that the normalization indicates only $16 - 1 = 15$ parameters are required for fully generic parameterization of all such states $\rho$.
-Removing this degeneracy is possible although difficult.
-Second, the parameters $\lambda_i$ carry no physical meaning associated with the state $\rho$, unlike our next parameterization.
-
-    In Spengler, Huber and Hiesmayr's work~\cite{Spengler_2010_Unitary}, they discuss how to parameterization density matrices $\rho$ acting on $\Hilb^d$ of rank $k$ through it's spectral decomposition,
-    \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i}\bra{\psi_i} \quad p_i \geq 0, \sum_{i} p_i = 1, k \leq d \eq \label{eq:unitary_param_density} \]
-    Where any orthonormal basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into a computational basis $\bc{\ket{i}}$ by a unitary $U \in \mathcal{U}\br{d}$ such that $\ket{\psi_i} = U\ket{i}$.
-We refer to \cref{eq:unitary_param_density} as the \term{Spengler Parametrization}.
-Without loss of generality we parameterize all full-rank ($k=d$) matrices by simultaneously parameterizing the $d=4$ eigenvalues $p_i$ of \cref{eq:unitary_param_density} using \cref{eq:convex_param} and the unitary group $\mathcal{U}\br{4}$ up to global phase equivalence using \cref{eq:fast_spengler_unitary_gp}.
-Parameterizing $\rho$ using the Spengler parameterization requires $3 + 12 = 15$ parameters; admitting no degeneracies.
-
-    Finally in cases where we wish to restrict ourselves to \textit{pure} bipartite states $\rho = \ket{\psi}\bra{\psi}$, we have the luxury to use a \term{Schmidt Parametrization}.
-This is accomplished via a Schmidt decomposition $\ket{\psi_{AB}} = \sum_{i}\sigma_i \ket{i_A}\otimes\ket{i_B}$ where normalization demands that $\sum_{i} \sigma_i^2 = 1$, $\bc{\ket{i_A}}$ and $\bc{\ket{i_B}}$ are orthonormal bases for $\Hilb_A$ and $\Hilb_B$ respectively~\cite{Neilsen_Chaung_2011}.
-Additionally for qubit sources we can \textit{choose} our orthonormal bases to be the computational basis $\bc{\ket{0}, \ket{1}}$ and write,
-    \[ \ket{\psi} = \cos^2\br{\lambda_1} \ket{0} \otimes \ket{0} + \sin^2\br{\lambda_1} \ket{1} \otimes \ket{1} \]
-    Where only $1$ real-valued parameter $\lambda = \bc{\lambda_1}$ is required to parameterize all pure states up to local unitaries.
-Pure states are also attractive due to their computational advantage in computing \cref{eq:triangle_quantum_distributions}.
-If each state $\rho$ is decomposable into $\ket{\psi}\bra{\psi}$, then \cref{eq:triangle_quantum_distributions} can be written as,
-    \[ \prob[ABC]\br{abc} = \bramidket{\psi_{AB}\psi_{BC}\psi_{CA}}{\netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c} \netperm^\intercal}{\psi_{AB}\psi_{BC}\psi_{CA}} \eq \label{eq:pure_state_quantum_triangle} \]
-    Avoiding the expensive matrix multiplications of \cref{eq:triangle_quantum_distributions}.
-    \subsection{Measurements}
-    With full generality, we consider a measurement $M$ to be a \term{projective-operator valued measure (POVM)} represented by a set of hermitian, positive semi-definite operators $\bc{M_i}_{i=1,\ldots,k}$\footnote{The $i$-th element of $M$ is referenced using a subscript $M_i$.
-The set of measurement elements for a particular party $X$ will be written $M_X$.
-When both party and element are to be referenced, we write $M_{X,i}$.} acting on $\Hilb^d$ summing to the identity,
-    \[ \forall \ket{\phi} \in \Hilb^d : \bra{\phi} M_i \ket{\phi} \geq 0 \quad \sum_{i=1}^{k} M_i = \mathbb{I}_{\Hilb^d} \eq \label{eq:povm} \]
-    When considering $k=2$ outcome measurements acting on $\Hilb^4$ we parameterize the first POVM element $M_1$ by using a Cholesky parameterization similar to \cref{eq:cholesky_param} without normalizing for trace.
-Afterwards, $M_2$ is fully determined by \cref{eq:povm}.
-    \[ M_1 = T^\dagger T \quad M_2 = \mathbb{I} - T^\dagger T \eq \label{eq:2_povm}\]
-    However, in order for $M_2$ to be positive semi-definite, the largest eigenvalue of $M_1$ has to be less than 1.
-To see this is a necessary and sufficient constraint, first expand out \cref{eq:2_povm},
-    \[ \bramidket{\phi}{M_2}{\phi} = \bramidket{\phi}{\mathbb{I} - M_1}{\phi} = \abs{\phi}^2 - \bra{\phi}\br{\sum_{i=1}^{d}m^{\br{i}}_1 \ket{m^{\br{i}}_1}\bra{m^{\br{i}}_1}}\ket{\phi} \]
-    Next write a generic $\ket{\phi} \in \Hilb^d$ in terms of a linear combination of the eigenvectors of $M_1$\footnote{The eigenvectors of $M_1$ form an orthonormal basis for $\Hilb^d$ because $M_1$ is Hermitian}.
-    \[ \bramidket{\phi}{M_2}{\phi} = \sum_{j}\abs{\braket{\phi}{m^{\br{j}}_1}}^2 - \sum_{i} m^{\br{i}}_1 \abs{\braket{\phi}{m^{\br{i}}_1}}^2 = \sum_{i} \br{1 - m^{\br{i}}_1} \abs{\braket{\phi}{m^{\br{i}}_1}}^2 \eq \label{eq:eigen_less_one} \]
-    Since $\ket{\phi}$ is arbitrary, for each $i$ set $\ket{\phi} = \ket{m^{\br{i}}_1}$ to see that each eigenvalue of $M_1$ needs to be less than $1$.
-    \[ \bramidket{m^{\br{i}}_1}{M_2}{m^{\br{i}}_1} = \br{1 - m^{\br{i}}_1} \geq 0 \implies m^{\br{i}}_1 \leq 1 \eq \label{eq:2_povm_suff} \]
-    By \cref{eq:eigen_less_one} is not difficult to see that \cref{eq:2_povm_suff} is a sufficient condition.
-During optimization, \cref{eq:2_povm_suff} can either be enforced passively as a constraint or directly by normalizing $M_1$ by its largest eigenvalue $\max\br{m_1^{\br{i}}}$ whenever necessary.
-
-    When generalizing the above parameterization to more than $2$ outcomes, only necessary conditions were found.
-Generating $k$-outcome POVM measurements is doable using rejection sampling techniques such as those used in~\cite{Petz_2012} however a valid parameterization with little to no degeneracy was not found.
-Upon making this observation, a necessary departure to \term{projective-valued measures (PVMs)} is warranted\footnote{Strictly speaking, when the number of outcomes ($k$) \textit{matches} the Hilbert space dimension ($d$), \cref{eq:povm} implies \cref{eq:pvm} by completeness.
-When considering $4$ outcome measurements on bipartite qubit states in $\Hilb^4$, PVMs are completely general.
-Moreover, Naimark's dilation theorem guarantees that PVMs acting on $\Hilb^q$ can \textit{emulate} the behaviour of any POVM acting on $\Hilb^d$ provided that $q$ is sufficiently larger than $d$~\cite{Naimark}.}.
-With loss of generality, consider the set of PVMs $M$ satisfying \cref{eq:povm} in addition to orthogonal and projective properties,
-    \[ M_i M_j = \de_{ij} M_i \quad M_i = \ket{m_i}\bra{m_i} \eq \label{eq:pvm}\]
-    Parameterizing $M$ for $k$-outcome measurements corresponds to parameterizing the set of all $k$-th order orthonormal sub-bases of $\Hilb^d$.
-    First note that any such basis $\bc{\ket{\psi_1}, \ldots, \ket{\psi_k}}$ can be transformed into the computational basis $\bc{\ket{1}, \ldots, \ket{k}}$ by a unitary denoted $U \in \mathcal{U}\br{d}$,
-    \[ U \ket{\psi_i} = \ket{i} \]
-    With this observation we just need to parameterize the set of all unitaries $\mathcal{U}\br{d}$,
-    \[ M = \bc{ U\ket{i}\bra{i}U^\dagger }_{i \in 1, \ldots, k} \]
-    Specifically, the projective property each $M_i$ means that the global phase of $U$ is completely arbitrary; one only needs to consider parameterizing unitaries up to global phase \cref{eq:fast_spengler_unitary_gp}.
-This method was inspired by the \textit{measurement seeding} method of P{\'{a}}l and V{\'{e}}rtesi's~\cite{Pal_2010} iterative optimization technique.
-
-    Analogously to \cref{eq:pure_state_quantum_triangle}, projective measurements offer considerable computational advantage as \cref{eq:triangle_quantum_distributions} can be rewritten as,
-    \[ \prob[ABC]\br{abc} = \bramidket{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{A,a}m_{B,b}m_{C,c}} \eq \label{eq:pure_meas_quantum_triangle} \]
-
-    \subsection{Network Permutation Matrix}
-    \begin{figure}
-        \centering
-        \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
-        \caption{The network permutation matrix $\netperm$ for $\br{\Hilb^2}^{\otimes 6}$ realized on the triangle scenario. Black represents a value of $1$ and $0$ otherwise.}
-        \label{fig:perm_mtrx}
-    \end{figure}
-    Finally, we introduce the \term{network permutation matrix} $\netperm$ for the Triangle Scenario of \cref{fig:triangle_scenario}.
-For bipartite qubit states, $\netperm$ becomes a $64\times64$ bit-wise matrix that acts on the measurements $M$ and is depicted in \cref{fig:perm_mtrx}.
-To illuminate its necessity, consider \cref{eq:triangle_quantum_distributions} without $\netperm$.
-    \begin{align*}
-    \prob[ABC]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA}} \br{M^a_{A}\otimes M^b_{B} \otimes M^c_{C}}}\\
-    &= \Tr\bs{\br{\rho_{AB}M^a_{A}}\otimes\br{\rho_{BC}M^b_{B}}\otimes\br{\rho_{CA}M^c_{C}}}\\
-    &= \Tr\br{\rho_{AB}M^a_{A}}\Tr{\br{\rho_{BC}M^b_{B}}}\Tr{\br{\rho_{CA}M^c_{C}}}\\
-    &= \prob[A\mid \rho_{AB}]\br{a}\prob[B\mid \rho_{BC}]\br{b}\prob[C\mid \rho_{CA}]\br{c}
-    \end{align*}
-    On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$.
-This is analogously troubling for $B$ and $C$ as well.
-The network permutation matrix $\netperm$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$.
-To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
-    \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
-    $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''.
-It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
-    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
-    \subsection{Degeneracy}
-    \todo[TC]{Discuss local unitary degeneracy}
-    \section{Convex Parametrization of Finite Probability Distributions}
-    As discussed in \cref{sec:optimizations}, there is a need to parameterize the family of all probability distributions $\prob[V]$ over a given set of variables $V = \br{v_1, \ldots, v_{\abs{V}}}$.
-If the cardinality of $O_{V}$ is finite, then this computationally feasible.
-The space of probability distributions over $n = \abs{O_{V}}$ distinct outcomes forms a $n-1$ dimensional convex polytope naturally embedded in $\R_{\geq 0}^n$~\cite{Brunner_2013} that is parameterizable by $n-1$ real value parameters; normalization $\sum_{o\bs{V} \in O_V} \prob[V][\outc{V}] = 1$ accounts for the `$-1$'.
-An example of a non-degenerate parameterization of $\prob[V]$ consists of $n-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{n-1}}, \lambda_i \in \bs{0, \pi/2}$ which generate the $n$ probability values $p_j$ using hyperspherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary},
-    \begin{equation}
-    \begin{gathered}
-        \label{eq:convex_param}
-        p_j = \cos^2 \lambda_j \prod_{i=1}^{j-1} \sin^2 \lambda_i \quad \forall j \in 1, \ldots, n - 1 \\
-        p_n = \prod_{i=1}^{n-1} \sin^2 \lambda_i
-    \end{gathered}
-    \end{equation}
-    Furthermore due to the periodicity of the parameter space $\lambda$, \cref{eq:convex_param} can be used for either constrained or unconstrained optimization problems.
-For continuity reasons, unconstrained optimizations are performed whenever possible.
-
-    Although non-degenerate, this parameterization suffers from uniformity; a randomly sampled vector of parameters $\lambda$ \textit{does not} translate to a randomly sampled probability $\prob[V]$.
-An easy-to-implement, degenerate parameterization of $\prob[V]$ can be constructed by simply beginning with $n$ real parameters $\lambda = \br{\lambda_1, \ldots, \lambda_n}$, then making them positive and normalized by their sum\footnote{Strictly speaking, \cref{eq:uniform_param} \textit{also} suffers from non-uniformity; being biased toward uniform probability distributions $\prob[V]$.
-\todo[TC]{Discuss rejection sampling simplex algorithms}}.
-    \[ p_j = \f{\abs{\lambda_j}}{\sum_{i=1}^{n} \abs{\lambda_i}} \quad \forall j \in 1, \ldots, n \eq \label{eq:uniform_param} \]
-    For various convex optimization tasks sensitive to initial conditions outlined \cref{sec:optimizations}, the latter parameterization of \cref{eq:uniform_param} generally performed better than the former \cref{eq:convex_param}.
-
-    \bibliography{../references}
 \end{document}

### 2016-11-11 documents/BrazilSlides/slides.tex
Made some progress on the intro and dug up old inequalities

@@
 \documentclass[
-    hyperref={colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
+    % hyperref={bookmarks=false,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
     xcolor={dvipsnames},
@@
 
-\setbeameroption{show notes}
-\usefonttheme[onlymath]{serif}
-
+% \usepackage{pgfpages} % For viewing slides on the right
+\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
+\setbeameroption{show notes} % Shows notes on the right of the main slides
+% \setbeameroption{show notes on second screen}
+\usefonttheme[onlymath]{serif} % For serif font in math mode
+\usepackage[round]{natbib} % Needed for Author name citations
 \usepackage{../../packages/shared}
 \usepackage{../../packages/misc_commands}
-
-% === Causal structure formatting for tikz ===
-\input{../../figures/causal_structures/formatting}
-
+\input{../../figures/causal_structures/formatting} % Causal structure formatting for tikz
 \renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}
@@
 \title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
-\author[Fraser]{T.~C.~Fraser\inst{1}}
+\author[Fraser]{T.C.~Fraser\inst{1}}
 \institute[PI]
@@
     \setbeamertemplate{bibliography item}{\insertbiblabel}
-    \bibliographystyle{abbrv}
+    \bibliographystyle{plainnat}
     \bibliography{../references}{}
@@
     \frametitle{Introduction}
-    \note[item]{\todo[TC]{}}
+    \note[item]{Thank International Institute for Physics (IIP) for support}
+    \note[item]{Thank Perimeter Institute for Theoretical Physics (PI) for support}
+\end{frame}
+\begin{frame}
+    \frametitle{Objective}
+    \begin{itemize}
+        \item Derive causal compatibility/locality inequalities that distinguish quantum distributions from classical ones
+        \item Specifically for the Triangle Scenario (TS)
+    \end{itemize}
+    \begin{center}
+        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
+    \end{center}
+    \note[item]{Research project's goal was to derive new causal compatibility inequalities that distinguish quantum correlations from classical correlations}
+    \note[item]{More specifically, the ambition of the project is to obtain such inequalities that constraint compatibility with The Triangle Scenario}
+    \note[item]{Triangle Scenario has be studied extensively before}
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Notation}
+    \frametitle{Objective Cont'd}
     \begin{itemize}
-        \item Complete set of random variables are the \term{joint random variables}
-        \[ \jointvar = \bc{v_1, \cdots, v_n} \]
-        \item A subset of $V \subset \jointvar$ is a \term{marginal context}
-        \item \term{Marginal scenario} $\mscenario$
-        \[ \mscenario = \bc{V_1, \ldots, V_k \mid V_i \subset \jointvar} \quad \jointvar = {\bigcup}_{i} V_i  \]
-        \item Marginal scenario forms a \textit{simplicial complex}
-        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        \item Restrict focus to \textit{maximal} marginal scenario where only the largest contexts are present
-        \[ \forall V_i, V_j \in \mscenario : V_i \not \subset V_j \]
+        \item In~\citet{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}
+        \item In~\citet{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)
+        \item In~\citet{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility
+        \item Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective
     \end{itemize}
+    \note[item]{At the time of publishing~\citet{Branciard_2012}, problem seems hard.}
+    \note[item]{Important because its smallest correlation scenario with quantum non-locality.}
+    \note[item]{Compatibility can not be determined from conditional independence relations (there are none)}
+    \note[item]{It would be interesting to find quantum non-locality in the triangle scenario that does not rely on Bell's theorem.}
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Notation Cont'd}
+    \frametitle{This Talk}
+    \begin{itemize}
+        \item Report the discovery of such inequalities
+        \item Explain how these inequalities were obtained
+        \item Discuss quantum distributions that violate compatibility inequalities
+        \item Attempts at finding new quantum distributions different than those proposed by~\cite{Fritz_2012}
+        \item Briefly discuss symmetric inequalities
+    \end{itemize}
+    \note[item]{The purpose of this talk is to present these new-found inequalities and explain how they were obtained}
+    \note[item]{Additionally I will talk about my attempts at using these inequalities to find new incompatible quantum distributions}
+    \note[item]{In doing so, will discuss how we obtained symmetric compatibility inequalities that have violations in the Triangle Scenario}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Example Inequality}
+    \begin{itemize}
+        \item Quick example/preview:
+    \end{itemize}
+    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
+    \begin{itemize}
+        \item $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
+        \item Four outcomes for each $A, B, C$
+        \item Polynomial in $\prob[ABC]$, marginals $\prob[AB]$, $\prob[BC]$, $\prob[AC]$, $\prob[A]$, $\prob[B]$, $\prob[C]$
+    \end{itemize}
+    \note[item]{As a quick example or preview of what is to come, here is a an example inequality admits quantum violations in the triangle scenario}
+    \note[item]{Some features of note: inequality is polynomial in $\prob[ABC]$ and its marginals}
+\end{frame}
+
+% \begin{frame}
+%     \frametitle{Notation}
+%     \begin{itemize}
+%         \item A subset of $V \subset \jointvar$ is a \term{marginal context}
+%         \item Restrict focus to \textit{maximal} marginal scenario where only the largest contexts are present
+%         \[ \forall V_i, V_j \in \mscenario : V_i \not \subset V_j \]
+%     \end{itemize}
+% \end{frame}
+
+\begin{frame}
+    \frametitle{Notation}
+    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
     \begin{itemize}
@@
         \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
+        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
+        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
+        % \item Marginal scenario forms a \textit{simplicial complex}
+        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
+        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
         \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
@@
     \end{itemize}
-    \todo[TC]{Insert generic causal structure}
+    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
+    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
+    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
+    \note[item]{Marginal scenario refers to the those sets of random variables}
+    \note[item]{The complete set of random variables are the joint random variables}
 \end{frame}
@@
     \frametitle{Causal Compatibility}
-    \textbf{Question:} Is a marginal model $\prob^{\mscenario}$ \term{compatible} with a causal structure $\graph$?\\
-    \[ \mscenario = \bc{V_1, \ldots, V_k \mid V_i \subset \nodes_O} \]
+    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
     \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
@@
     \end{enumerate}
-
-    A \term{casual compatibility inequality} is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
-    \note<1>[item]{}
+    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Triangle Scenario}
-    \begin{columns}
-        \column{0.4\linewidth}
-            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
-        \column{0.6\linewidth}
+    \frametitle{Deriving Inequalities}
+    Two necessary components to compatibility:
+    \begin{enumerate}
+        \item[1.] \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
         \begin{itemize}
-                \item Three parties $\nodes_O = \bc{A, B, C}$
-                \item Pair-wise sharing three latent variables $\nodes_L = \bc{X, Y, Z}$
-                \item \todo[TC]{Inject info about existing work}
-                \item There exists \textit{quantum-accessible} distributions $\prob[ABC]$ that are \textit{incompatible} with the triangle scenario
+            \item Is the marginal model contextual or non-contextual?
+            \item 3 distinct ways to tackle this problem
+            \begin{enumerate}
+                \item[1.] Convex hull, Polytope projection, Fourier-Motzkin
+                \item[2.] Possibilistic Hardy Inequalities (Hypergraph transversals)
+                \item[3.] Linear Program Feasibility/Infeasibility
+            \end{enumerate}
         \end{itemize}
-    \end{columns}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Distribution}
-    The \term{Fritz Distribution $\prob[F]$}:
+    \end{enumerate}
+    \begin{enumerate}
+        \item[2.] \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
         \begin{itemize}
-        \item three-party $\prob[F] = \prob[ABC]$
-        \item each party has four outcomes
+            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
+            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
         \end{itemize}
+    \end{enumerate}
 \end{frame}
@@
     \frametitle{Inflation Technique}
-    \begin{itemize}
-        \item Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
-    \end{itemize}
+    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
     \begin{definition}
@@
     \end{definition}
-
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Inflation Lemma Cont'd}
-    \begin{lemma}
-        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-    \end{lemma}
-    \begin{corollary}
-        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
-    \end{corollary}
+    \frametitle{Triangle Scenario}
+    \begin{columns}
+        \column{0.4\linewidth}
+            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
+        \column{0.6\linewidth}
+            \begin{itemize}
+                \item Three parties $\nodes_O = \bc{A, B, C}$
+                \item Pair-wise sharing three latent variables $\nodes_L = \bc{X, Y, Z}$
+                \item \todo[TC]{Inject info about existing work}
+                \item There exists \textit{quantum-accessible} distributions $\prob[ABC]$ that are \textit{incompatible} with the triangle scenario
+            \end{itemize}
+    \end{columns}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Distribution}
+    The \term{Fritz Distribution $\prob[F]$}:
+    \begin{itemize}
+        \item three-party $\prob[F] = \prob[ABC]$
+        \item each party has four outcomes
+    \end{itemize}
 \end{frame}
@@
     \frametitle{Causal Symmetry}
+    \begin{itemize}
+        \item Desirable to find compatibility inequality $I$ such that
+        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
+        \item Compatibility is independent of variable labels
+        \[ \forall \varphi \in \Perm{\nodes} : I \stackrel{\text{com}}{\rightarrow} \graph \implies \varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \varphi\bs{\graph}  \]
+        \item If $\varphi\bs{\graph} = \graph$ then $\varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \graph$
+    \end{itemize}
+    \begin{definition}
+        The \term{causal symmetry group} of causal structure $\graph$:
+        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
+        Strictly speaking, one needs to preserve observable nodes:
+        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
+    \end{definition}
+    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
+    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e.
+inequality) that is symmetric under exchange of parties}
+    \note<1>[item]{Surprisingly, it is possible to do so!}
+    \note<1>[item]{Here is how.}
+    \note<1>[item]{First, we will formally define the symmetry group in question}
+    \note<1>[item]{Causal symmetry group is the }
 \end{frame}

### 2016-11-11 documents/BrazilSlides/slides.tex
Marginal Problem foramlism

@@
 \renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}
+\renewcommand{\tcdot}{\cdot} % Tentative cdot, not sure if I want to keep dots
 
@@
 \begin{frame}
+    \frametitle{$d$-Separation Polynomial}
+
+\end{frame}
+
+\begin{frame}
     \frametitle{Triangle Scenario}
@@
 \begin{frame}
+    \frametitle{Distribution Vectors}
+    \begin{itemize}
+        \item \term{Joint Distribution Vector $\probvec^{\jointvar}$}
+        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
+        \item \term{Marginal Distribution Vector $\probvec^{\mscenario}$}
+        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
     \frametitle{Incidence Matrix}
     \begin{itemize}
-        \item Incidence matrix $M$ is a bit-wise matrix
+        \item Marginal Problem as linear program
+        \begin{align*}
+            \probvec^{\mscenario}_m &= {\sum}_{j} M_{m,j} \probvec^{\jointvar}_j \\
+            \probvec^{\mscenario} &= M \tcdot \probvec^{\jointvar}
+        \end{align*}
+        \item \term{Incidence matrix} $M$ is a bit-wise matrix
         \item Row-indexed by marginal events $m \in \Events{\mscenario}$
@@
         \[ M_{m,j} = \begin{cases}
-            1 & m \text{ compatible with } j \\
+            1 & m = j|_{\Dom{m}} \\
             0 & \text{otherwise}
         \end{cases} \]
+        \begin{gather*}
+        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
+        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
+        \end{gather*}
+
     \end{itemize}
+\end{frame}
+
+\begin{frame}[shrink=10]
+    \frametitle{Example}
+    Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{A,B,C}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{A,B}, \bc{B,C}, \bc{A,C}}$. The incidence matrix becomes:
+    \[ M = \kbordermatrix{
+        (A,B,C) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
+        (A=0, B=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
+        (A=0, B=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
+        (A=1, B=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
+        (A=1, B=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
+        (B=0, C=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
+        (B=0, C=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
+        (B=1, C=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
+        (B=1, C=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
+        (A=0, C=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
+        (A=0, C=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
+        (A=1, C=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
+        (A=1, C=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
+    } \]
 \end{frame}
@@
             \begin{itemize}
-                \item Tackling Large inflation
-                \item 12 pre-injectable sets (to follow)
+                \item Find compatibility inequalities for TS by finding non-contextuality inequalities for Large Inflation
+                \item Marginal Scenario is the set of maximal pre-injectable sets
+                \item 12 maximal pre-injectable sets (to follow)
             \end{itemize}
@@
         \item Incidence matrix $M$ is very large $\sim 2.25 \textsf{Gb}$
-        \[ \# \text{Columns} = \prod_{v \in \jointvar} O_{v} = 4^{12} = 16,777,216 \]
-        \[ \# \text{Rows} = \sum_{V \in \mscenario} \prod_{v \in V} O_{v} = 4\times 4^{6} + 8 \times 4^{3} = 16,896 \]
+        \[ \# \text{Columns} = 4^{12} = 16,777,216 \]
+        \[ \# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896 \]
     \end{itemize}
@@
         \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
-        \item Relative Phase Terms: $RP_{m,n} = \exp\br{i P_n \lambda_{n,m}}$
-        \item Rotation Terms: $R_{n,m} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
+        \item Relative Phase Terms: $RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$
+        \item Rotation Terms: $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
         \item Projection Operators: $P_l = \ket{l}\bra{l}$
@@
             GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
-            RP_{m,n} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
-            R_{n,m} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
+            RP_{n,m} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
+            R_{m,n} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
             & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\

### 2016-11-13 documents/Archive/main.tex
More progress, slides to present found inequalities

@@
     \begin{split}
-    \prob[F][111] = \prob[F][221] = \prob[F][412] = \prob[F][322] = \prob[F][233] = \prob[F][143] = \prob[F][344] = \prob[F][434] &= \f{1}{32}\br{2 + \sqrt{2}} \\
-    \prob[F][121] = \prob[F][211] = \prob[F][422] = \prob[F][312] = \prob[F][243] = \prob[F][133] = \prob[F][334] = \prob[F][444] &= \f{1}{32}\br{2 - \sqrt{2}}
+    \prob[F][000] = \prob[F][110] = \prob[F][301] = \prob[F][211] = \prob[F][122] = \prob[F][032] = \prob[F][233] = \prob[F][323] &= \f{1}{32}\br{2 + \sqrt{2}} \\
+    \prob[F][010] = \prob[F][100] = \prob[F][311] = \prob[F][201] = \prob[F][132] = \prob[F][022] = \prob[F][223] = \prob[F][333] &= \f{1}{32}\br{2 - \sqrt{2}}
     \end{split}
@@
 Next each of $C$'s outcomes become the conditioned settings in \cref{eq:CHSH},
-    \[ \ba{AB|C=2} + \ba{AB|C=3} + \ba{AB|C=4} - \ba{AB|C=1} \leq 2 \eq \label{eq:chsh_c}\]
+    \[ \ba{AB|C=1} + \ba{AB|C=2} + \ba{AB|C=3} - \ba{AB|C=0} \leq 2 \eq \label{eq:chsh_c}\]
     Finally, specifying the two outcome coarse-graining as $\bc{1,2,3,4} \rightarrow \bc{\br{1,4}, \br{2,3}}$ gives a definition of correlation,
-    \[ \ba{AB} \defined 2\bc{\prob[][11] + \prob[][14] + \prob[][41] + \prob[][44] + \prob[][22] + \prob[][23] + \prob[][32] + \prob[][33]} - 1 \]
+    \[ \ba{AB} \defined 2\bc{\prob[][00] + \prob[][03] + \prob[][30] + \prob[][33] + \prob[][11] + \prob[][12] + \prob[][21] + \prob[][22]} - 1 \]
     Which when applied to the Fritz distribution \cref{eq:fritz_dist} gives the following correlations:
     \begin{gather*}
-    \ba{AB|C=2} = 2 \bc{\f{1}{32}\bs{2\br{2+\sqrt{2}}+2\br{2-\sqrt{2}}}} - 1 = \f{\sqrt{2}}{2} \\
-    \ba{AB|C=3} = \ba{AB|C=4} = \f{\sqrt{2}}{2} \quad \ba{AB|C=1} = -\f{\sqrt{2}}{2}
+    \ba{AB|C=1} = 2 \bc{\f{1}{32}\bs{2\br{2+\sqrt{2}}+2\br{2-\sqrt{2}}}} - 1 = \f{\sqrt{2}}{2} \\
+    \ba{AB|C=2} = \ba{AB|C=4} = \f{\sqrt{2}}{2} \quad \ba{AB|C=1} = -\f{\sqrt{2}}{2}
     \end{gather*}

### 2016-11-13 documents/BrazilSlides/slides.tex
More progress, slides to present found inequalities

@@
 \documentclass[
-    % hyperref={bookmarks=false,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
+    hyperref={bookmarks=false,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
     xcolor={dvipsnames},
 ]{beamer}
+
+\usetheme[height=8mm]{Rochester}
+\usecolortheme{default}
 
@@
 }
-\date[QN 2016]{Quantum Networks, 2016}
+\date[QN 2016]{Quantum Networks IIP, Nov. 2016}
 
@@
     \begin{enumerate}
-        \item[1.] \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
+        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
         \begin{itemize}
@@
             \begin{enumerate}
-                \item[1.] Convex hull, Polytope projection, Fourier-Motzkin
-                \item[2.] Possibilistic Hardy Inequalities (Hypergraph transversals)
-                \item[3.] Linear Program Feasibility/Infeasibility
+                \item Convex hull, Polytope projection, Fourier-Motzkin
+                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
+                \item Linear Program Feasibility/Infeasibility
             \end{enumerate}
         \end{itemize}
-    \end{enumerate}
-    \begin{enumerate}
-        \item[2.] \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
+        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
         \begin{itemize}
@@
 \begin{frame}
-    \frametitle{Inflations of the Triangle Scenario}
+    \frametitle{Some Inflations of the Triangle Scenario}
     \begin{center}
@@
     \frametitle{$d$-Separation Polynomial}
-
-\end{frame}
-
-\begin{frame}
-    \frametitle{Triangle Scenario}
-    \begin{columns}
-        \column{0.4\linewidth}
-            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
-        \column{0.6\linewidth}
     \begin{itemize}
-                \item Three parties $\nodes_O = \bc{A, B, C}$
-                \item Pair-wise sharing three latent variables $\nodes_L = \bc{X, Y, Z}$
-                \item \todo[TC]{Inject info about existing work}
-                \item There exists \textit{quantum-accessible} distributions $\prob[ABC]$ that are \textit{incompatible} with the triangle scenario
+        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
+        \item \textbf{Linear inequality} for $\graph'$
     \end{itemize}
-    \end{columns}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Distribution}
-    The \term{Fritz Distribution $\prob[F]$}:
+    \begin{center}
+        \begin{tikzpicture}[scale=0.8]
+            \pgfmathsetmacro{\hs}{1.8};
+            \pgfmathsetmacro{\vs}{1};
+            \pgfmathsetmacro{\cross}{0.3};
+            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
+            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
+            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
+            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
+            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
+            \draw (0, 0) node[](b){??};
+            \draw[thick, ] (a) -- (ab);
+            \draw[thick, ] (c) -- (cd);
+            \draw[thick, ] (a) -- (ac);
+            \draw[thick, ->] (ac) -- (c);
+            \draw[thick, ->] (ab) -- (b);
+            \draw[thick, ->] (cd) -- (d);
+            \draw[very thick, red]
+            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
+            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
+            ;
+        \end{tikzpicture}
+    \end{center}
     \begin{itemize}
-        \item three-party $\prob[F] = \prob[ABC]$
-        \item each party has four outcomes
+        \item \textbf{Polynomial inequality} for $\graph$!
     \end{itemize}
@@
 \begin{frame}
-    \frametitle{Inflation Pipeline}
-    \note[item]{Walk through how the inflation pipeline works}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Outcomes and Events}
+    \frametitle{Pre-injectable Sets}
     \begin{itemize}
-        \item Set of \term{outcomes} $O_v$ for each variable $v$
-        \item Set of \term{events} for a set of variables $V$
-        \[ \Events{V} \defined \bc{s: V \to O_V \mid \forall v \in V, s\br{v} \in O_v} \]
-    \end{itemize}
-    \begin{definition}
-        The set of events over the joint variables $\Events{\jointvar}$ are termed the \term{joint events}.
-    \end{definition}
-    \begin{definition}
-        The set of events over the marginal contexts are the \term{marginal events}
-        \[ \Events{\mscenario} \defined \coprod_{V \in \mscenario} \Events{V} \]
-    \end{definition}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Distribution Vectors}
-    \begin{itemize}
-        \item \term{Joint Distribution Vector $\probvec^{\jointvar}$}
-        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
-        \item \term{Marginal Distribution Vector $\probvec^{\mscenario}$}
-        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
+        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
+        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
+        \item A \term{pre-injectable set} $N'$:
+        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
+        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
+        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
     \end{itemize}
@@
 \begin{frame}
-    \frametitle{Incidence Matrix}
+    \frametitle{Pre-injectable Sets of Large Inflation}
+    \begin{center}
+        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
+    \end{center}
     \begin{itemize}
-        \item Marginal Problem as linear program
-        \begin{align*}
-            \probvec^{\mscenario}_m &= {\sum}_{j} M_{m,j} \probvec^{\jointvar}_j \\
-            \probvec^{\mscenario} &= M \tcdot \probvec^{\jointvar}
-        \end{align*}
-        \item \term{Incidence matrix} $M$ is a bit-wise matrix
-        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
-        \item Column-indexed by joint events $j \in \Events{\jointvar}$
-        \[ M_{m,j} = \begin{cases}
-            1 & m = j|_{\Dom{m}} \\
-            0 & \text{otherwise}
-        \end{cases} \]
-        \begin{gather*}
-        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
-        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
-        \end{gather*}
-
+        \item Has $12$ maximal pre-injectable sets (to follow)
     \end{itemize}
-\end{frame}
-
-\begin{frame}[shrink=10]
-    \frametitle{Example}
-    Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{A,B,C}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{A,B}, \bc{B,C}, \bc{A,C}}$. The incidence matrix becomes:
-    \[ M = \kbordermatrix{
-        (A,B,C) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
-        (A=0, B=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
-        (A=0, B=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
-        (A=1, B=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
-        (A=1, B=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
-        (B=0, C=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
-        (B=0, C=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
-        (B=1, C=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
-        (B=1, C=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
-        (A=0, C=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
-        (A=0, C=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
-        (A=1, C=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
-        (A=1, C=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
-    } \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Application to Large Inflation}
-    \begin{columns}
-        \column{0.6\linewidth}
-            \begin{itemize}
-                \item Find compatibility inequalities for TS by finding non-contextuality inequalities for Large Inflation
-                \item Marginal Scenario is the set of maximal pre-injectable sets
-                \item 12 maximal pre-injectable sets (to follow)
-            \end{itemize}
-        \column{0.4\linewidth}
-            \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
-    \end{columns}
 \end{frame}
@@
 \begin{frame}
+    \frametitle{Deriving Inequalities}
+    \begin{itemize}
+        \item Inflation facilitates turning linear, inflated inequalities into polynomial deflated ones
+        \item \textbf{Question:} How to derive compatibility inequalities for $\graph'$?
+        \item \textbf{Answer:} Use your favorite technique for deriving compatibility inequalities:
+        \begin{itemize}
+            \item Entropic inequalities
+            \item Finite outcome inequalities
+        \end{itemize}
+        \item Here we solve the marginal problem for $\mscenario = \PreInj[\graph]{\graph'}$
+        \item First some notation and formalism
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Outcomes and Events}
+    \begin{definition}
+        Each variable $v$ has finite set of \term{outcomes} $O_v$. \\
+        Each set of variables $V$ has finite set of \term{events} $\Events{V}$:
+        \[ \Events{V} \defined \bc{s: V \to O_V \mid \forall v \in V, s\br{v} \in O_v} \]
+    \end{definition}
+    \begin{definition}
+        The set of events over the joint variables $\Events{\jointvar}$ are termed the \term{joint events}.
+    \end{definition}
+    \begin{definition}
+        The set of events over the marginal contexts are the \term{marginal events}
+        \[ \Events{\mscenario} \defined \coprod_{V \in \mscenario} \Events{V} \]
+    \end{definition}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Distribution Vectors}
+    \begin{definition}
+        The \term{joint distribution vector} $\probvec^{\jointvar}$
+        \[ \probvec^{\jointvar}_j = \prob[\jointvar][j] \quad \forall j \in \Events{\jointvar}\]
+    \end{definition}
+    \begin{definition}
+        The \term{marginal distribution vector} $\probvec^{\mscenario}$
+        \[ \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \quad \forall m \in \Events{\mscenario}, \Dom{m} \in \mscenario\]
+    \end{definition}
+    Can now write complete marginal problem as matrix multiplication:
+    \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \iff \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Incidence Matrix}
+    \begin{itemize}
+        \item \term{Incidence matrix} $M$ is a bit-wise matrix
+        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
+        \item Column-indexed by joint events $j \in \Events{\jointvar}$
+        \[ M_{m,j} = \begin{cases}
+            1 & m = j|_{\Dom{m}} \\
+            0 & \text{otherwise}
+        \end{cases} \]
+        \begin{gather*}
+        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
+        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
+        \end{gather*}
+
+    \end{itemize}
+\end{frame}
+
+\begin{frame}[shrink=10]
+    \frametitle{Example}
+    Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{A,B,C}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{A,B}, \bc{B,C}, \bc{A,C}}$. The incidence matrix becomes:
+    \[ M = \kbordermatrix{
+        (A,B,C) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
+        (A=0, B=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
+        (A=0, B=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
+        (A=1, B=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
+        (A=1, B=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
+        (B=0, C=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
+        (B=0, C=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
+        (B=1, C=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
+        (B=1, C=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
+        (A=0, C=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
+        (A=0, C=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
+        (A=1, C=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
+        (A=1, C=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
+    } \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Marginal Linear Program}
+    \begin{itemize}
+        \item Obtain inequalities from incidence matrix $M$ and known incompatible distribution $\probvec^{\mscenario}$
+    \end{itemize}
+    \begin{columns}[T]
+        \column{0.4\linewidth}%
+            \term{Marginal LP}:%
+            \begin{alignat*}{2}
+                & \text{minimize:} \quad&& \emptyset \tcdot x\\
+                & \text{subject to:} && x \succeq 0 \\
+                & && M \tcdot x = \probvec^{\mscenario} \\
+            \end{alignat*}%
+        \column{0.4\linewidth}%
+            \term{Dual Marginal LP}:%
+            \begin{alignat*}{2}
+                & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
+                & \text{subject to:} && y \tcdot M \succeq 0 \\
+            \end{alignat*}%
+    \end{columns}
+    \begin{itemize}
+        \item $y$ is an \term{infeasibility certificate}:
+        \[ y \tcdot M \tcdot x = y \tcdot \probvec^{\mscenario} \geq 0  \]
+        \item \term{Infeasibility inequality}: $y \tcdot \probvec^{\mscenario} \geq 0$
+        \item Most linear programing toolkits return certificates (\href[pdfnewwindow]{http://docs.mosek.com/8.0/pythonapi/optimizer-task-gety.html}{\textit{Mosek}}, \href[pdfnewwindow]{https://www.gurobi.com/documentation/6.5/refman/farkasdual.html}{\textit{Gurobi}}, \href[pdfnewwindow]{http://www-01.ibm.com/support/docview.wss?uid=swg21400058}{\textit{CPLEX}}, \href[pdfnewwindow]{http://cvxr.com/cvx/doc/basics.html\#dual-variables}{\textit{cvxr}}/\href[pdfnewwindow]{http://cvxopt.org/userguide/coneprog.html\#linear-cone-programs}{\textit{cvxopt}}.)
+    \end{itemize}
+    \note[item]{It is possible to derive non-contextuality inequalities from $M$ and a known incompatible distribution $\probvec^{\mscenario}$}
+    \note[item]{Note the null objective; the minimization objective is trivially always zero}
+    \note[item]{The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.}
+    \note[item]{If \textit{feasible}, then there exists a vector $x$ that is a valid joint distribution vector $\probvec^{\jointvar}$.}
+    \note[item]{Feasibility implies that $\probvec^{\jointvar} = x$.}
+    \note[item]{Infeasibility implies contextuality}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Known Incompatible Distribution in The Triangle Scenario}
+    \cite{Fritz_2012} provides quantum-accessible distribution incompatible with TS
+    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
+    \begin{center}
+        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Distribution}
+    The \term{Fritz Distribution $\prob[F]$}:
+    \begin{itemize}
+        \item three-party $\prob[F] = \prob[ABC]$
+        \item each party has $4$ outcomes
+    \end{itemize}
+    \begin{gather*}
+    \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
+    \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
+    \end{gather*}
+    \begin{itemize}
+        \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
+        \item Correlation coarse graining $\bc{0,1,2,3} \to \bc{\br{0,3}, \br{1,2}}$
+    \end{itemize}
+    \[ \ba{AB | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{AB | C = 3} = - \f{1}{\sqrt{2}} \]
+    \begin{itemize}
+        \item Gives CHSH violation
+    \end{itemize}
+    \[ \ba{AB|C=0} + \ba{AB|C=1} + \ba{AB|C=2} - \ba{AB|C=3} = 2\sqrt{2} \not \leq 2 \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Quantum Implementation of Fritz Distribution}
+    \begin{gather*}
+        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\gp^+}\bra{\gp^+} \\
+        M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
+        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
+        M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
+    \end{gather*}
+    \begin{itemize}
+        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
+        \item Maximally entangled Bell states:
+    \end{itemize}
+    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\gp^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Notes of Fritz Distribution}
+    \begin{itemize}
+        \item Proof contingent on perfect correlation between $C$ and pseudo-settings
+        \item Proof not robust to noise
+    \end{itemize}
+    \begin{problem}[2.17 in \cite{Fritz_2012}]
+        Find an example of non-classical quantum correlations in TS together with a proof of its non-classicality which does not hinge on Bell’s Theorem.
+    \end{problem}
+    \begin{itemize}
+        \item ``...would be helpful to have inequalities...''
+        \item Possible to find inequalities violated by $\prob[F]$ using the Large inflation of the TS
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
     \frametitle{Large Inflation Incidence}
@@
         \item Incidence matrix $M$ is very large $\sim 2.25 \textsf{Gb}$
-        \[ \# \text{Columns} = 4^{12} = 16,777,216 \]
-        \[ \# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896 \]
+        \begin{itemize}
+            \item $\# \text{Columns} = 4^{12} = 16,777,216$
+            \item $\# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896$
+            \item $\# \text{Non-zero Entries} = 201,326,592$
+        \end{itemize}
     \end{itemize}
@@
 \begin{frame}
-    \frametitle{Inequalities Found}
+    \frametitle{Triangle Scenario Inequality}
+
 \end{frame}
@@
     \note<1>[item]{First, we will formally define the symmetry group in question}
-    \note<1>[item]{Causal symmetry group is the }
+    \note<1>[item]{Causal symmetry group is the group of automorphisms on causal structure}
 \end{frame}
@@
 
-\begin{frame}
-    \frametitle{Symmetric Inequalities}
+\begin{frame}[shrink=60]
+    \frametitle{Party Symmetric Inequality}
+    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
 \end{frame}
@@
         \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
+        \item Parameters $\la_{n,m} \in \bs{0, 2\pi}$
     \end{itemize}
@@
             \item $\netperm$ is a $2^6 \times 2^6$ matrix
+            \item Shifts one qubit to the left
         \end{itemize}
@@
     \end{columns}
-    \begin{itemize}
-        \item Shifts one qubit to the left
     \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
-    \end{itemize}
 
@@
 \begin{frame}
-    \frametitle{Non-Trivial Inequalities For Large Inflation}
-\end{frame}
-
-\begin{frame}
     \frametitle{Conclusions}
+    \begin{itemize}
+        \item New causal compatibility inequalities have been found for the TS
+        \item Inflation technique capable of producing inequalities with quantum/classical witnesses
+        \item Proof of non-classicality is robust to noise
+        \item Fritz witnessable by party symmetric inequalities
+        \item Maximally violating distributions are different than Fritz but also similar
+        \item Further research is necessary
+    \end{itemize}
 \end{frame}

### 2016-11-14 documents/BrazilSlides/slides.tex
Added some plots that depict the typical behaviour of super-Fritz violations.

@@
 \title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
-\author[Fraser]{T.C.~Fraser\inst{1}}
-\institute[PI]
+\author[Fraser]{T.C.~Fraser\inst{1,2}}
+\institute
 {
@@
     Perimeter Institute for Theoretical Physics\\
-    Ontario, Canada
+    Ontario, Canada \\
+    \inst{2}%
+    University of Waterloo\\
+    Ontario, Canada \\
 }
-\date[QN 2016]{Quantum Networks IIP, Nov. 2016}
+\date[QN 2016]{Quantum Networks Workshop, IIP, Nov. 2016}
 
@@
 
-\begin{frame}
-    \frametitle{Table of Contents}
-\tableofcontents
+% \begin{frame}
+%     \frametitle{Table of Contents}
+% \tableofcontents
 
-\end{frame}
-
-\section{Tools}
+% \end{frame}
 
@@
 \begin{frame}
-    \frametitle{Graph Theory [Optional Slide]}
+    \frametitle{Graph Theory [Optional]}
     Let $n, m \in \nodes$ be nodes of the graph $\graph$.
@@
     \frametitle{Quantum Implementation of Fritz Distribution}
+    \begin{itemize}
+        \item States:
+    \end{itemize}
     \begin{gather*}
-        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\gp^+}\bra{\gp^+} \\
+        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
+    \end{gather*}
+    \begin{itemize}
+        \item Maximally entangled Bell states:
+    \end{itemize}
+    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
+    \begin{itemize}
+        \item Measurements:
+    \end{itemize}
+    \begin{gather*}
         M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
@@
         \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
-        \item Maximally entangled Bell states:
     \end{itemize}
-    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\gp^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
 \end{frame}
@@
         \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
-        \item Inequalities Violated by Fritz distribution are inherently $4$-outcome
-        \item Incidence matrix $M$ is very large $\sim 2.25 \textsf{Gb}$
+        \item Inequalities violated by Fritz distribution are inherently $4$-outcome
+        \item Incidence matrix $M$ is \textbf{very large} $\sim 2.25 \textsf{Gb}$
         \begin{itemize}
@@
 
-\section{Symmetries}
 \begin{frame}
@@
         \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
-        \item Compatibility is independent of variable labels
-        \[ \forall \varphi \in \Perm{\nodes} : I \stackrel{\text{com}}{\rightarrow} \graph \implies \varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \varphi\bs{\graph}  \]
-        \item If $\varphi\bs{\graph} = \graph$ then $\varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \graph$
+        \item Compatibility is independent of variable labels $I, \graph \to \varphi\bs{I}, \varphi\bs{\graph}$
+        \item Need $\varphi\bs{\graph} = \graph$ to find new $\varphi\bs{I}$
     \end{itemize}
@@
 \begin{frame}
+    \frametitle{Causal Symmetry and Inflation}
+    \begin{itemize}
+        \item Causal symmetry group for $\graph'$ is no good!
+        \item Not possible to deflate inequality if it's not in terms of injectable sets
+        \begin{definition}
+            The \term{restricted causal symmetry group} $\Phi$ of $\graph'$:
+            \[ \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
+        \end{definition}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Restricted Causal Symmetry of Large Inflation}
+    \begin{itemize}
+        \item $\Phi$ for the large inflation is an order $48$ group with $4$ generators
+    \end{itemize}
+    \begin{equation*}
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_1 \\
+    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_2 \\
+    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_3 \\
+    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_4 \\
+    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
+    \end{aligned}
+    \end{equation*}
+\end{frame}
+
+\begin{frame}
     \frametitle{Symmetric Incidence}
+    \begin{itemize}
+        \item Group orbits through repeated action of $\varphi \in \Phi$ on $m \in \Events{\mscenario}$ and $j \in \Events{\jointvar}$
+    \end{itemize}
+    \begin{align*}
+        \Phi\bs{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \Phi} \\
+        \Phi\bs{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \Phi}
+    \end{align*}
+    \begin{itemize}
+        \item Construct \term{symmetric incidence matrix} $\Phi\bs{M}$
+    \end{itemize}
+    \[ \Phi\bs{M}_{\Phi\bs{m}, \Phi\bs{j}} = \sum_{m' \in \Phi\bs{m}}\sum_{j' \in \Phi\bs{j}} M_{m',j'} \]
+    \[ \Phi\bs{M} = \La_{\Phi\bs{\Events{\mscenario}}}\tcdot M \tcdot \La_{\Phi\bs{\Events{\jointvar}}} \]
+    \begin{itemize}
+        \item $\Phi\bs{M}$ not a bit-wise matrix like $M$
+        \item For large inflation $M$ is $16,896 \times 16,777,216$
+        \item For large inflation $\Phi\bs{M}$ is $450 \times 358,120$ % 3566922 entries
+    \end{itemize}
 \end{frame}
@@
     \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
-\end{frame}
-
-\section{Searching for New Distributions}
-\begin{frame}
-    \frametitle{Numerical Optimization}
 \end{frame}
@@
     \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Numerical Optimization}
+    \begin{itemize}
+        \item Attempt to find new non-classical distributions
+        \item Objective function $f\br{\la} \in \R$
+        \begin{enumerate}
+            \item Real-valued parameters $\la = \br{\la_0, \ldots, \la_n}$
+            \item Quantum states/measurements $\rho_{AB}, \rho_{BC}, \rho_{CA}, M_{A}, M_{B}, M_{C}$
+            \item Distribution $\prob[ABC]$
+            \item Plug into inequality $I$ in homogeneous form $I\br{\prob[ABC]} \geq 0$
+            \item Output is objective value $I\br{\prob[ABC]}$
+        \end{enumerate}
+        \item Numerical minimization of $f\br{\la}$
+        \[ f(\la_{(k+1)}) = \la_{(k)} - \ga_{(k)} \del f(\la_{(k)})  \]
+        \item Non-convex, non-linear, smooth/continuous
+        \item Gradient Descent, BFGS Method, Nelder-Mead simplex method
+        \item Stochastic methods: simulated annealing, basin-hopping
+    \end{itemize}
 \end{frame}
@@
         \item Degeneracies are easily eliminated such as global phase
-        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = 1 \]
+        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = \ident \]
         \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
@@
         \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
-        \item $d^2 - \br{d-k}^2 - k + \br{k-1} = 2dk -k^2 -1$ real-valued parameters (no-degeneracy)
+        \item real-value parameters $d^2 - \br{d-k}^2 - k$ for $\ti{U}_{k}$, $k-1$ for $\bc{p_i}$ (no degeneracy)
     \end{itemize}
@@
         \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
-        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $2dn -n^2 -1$ real-valued parameters\
+        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $n(2d - n - 1)$ real-valued parameters\
         \item PVMs are computationally more efficient
@@
     \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Results}
+    \begin{itemize}
+        \item Full rank $\rho, M$ gives $81$ free parameters
+        \[ \abs{\la} = 3 \cdot (12 + 3) + 3 \cdot 12 = 81 \]
+        \item Parameterization of quantum distributions still degenerate
+        \item Noisy seed (Gaussian noise):
+        \[ \la_{(0)} = \la_{(F)} + \de \la \qquad \de \la_{i} \sim \s{N}\br{\mu = 0, \si^2 = (2\pi10^{\chi})^2} \]
+        \item Uniform seed:
+        \[ \la_{(0), i} \sim \s{U}\br{[0, 2\pi]} \]
+    \end{itemize}
 
@@
 \begin{frame}
+    \frametitle{Fritz Local Minima}
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Local Minima Zoomed}
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Max Entangled vs. Max Violating (???) [Optional]}
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_random_seed.pdf}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Max Entangled vs. Max Violating (???) [Optional]}
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_random_seed_Zoomed.pdf}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
+\end{frame}
+
+\begin{frame}
     \frametitle{Maximally Violating Distributions}
+    \begin{itemize}
+        \item Able to out-perform violation provided by Fritz distribution
+        \item Maximally-violating states are not maximally-entangled; similar to detection loop-hole example of \cite{Methot_2006}
+        \item Violation very sensitive to the initial parameters $\la_{(0)}$
+        \item Both symmetric and asymmetric inequalities exhibit same qualitative features
+    \end{itemize}
 \end{frame}
@@
         \item Proof of non-classicality is robust to noise
-        \item Fritz witnessable by party symmetric inequalities
+        \item Fritz witness-able by party symmetric inequalities
         \item Maximally violating distributions are different than Fritz but also similar

### 2016-11-14 documents/BrazilSlides/slides.tex
Updates from ShareLaTeX

--- 2016-11-11 documents/BrazilSlides/slides.tex
@@
 \documentclass[
-    % hyperref={bookmarks=false,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
+    hyperref={colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
     xcolor={dvipsnames},
@@
 
-% \usepackage{pgfpages} % For viewing slides on the right
-\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
-\setbeameroption{show notes} % Shows notes on the right of the main slides
-% \setbeameroption{show notes on second screen}
-\usefonttheme[onlymath]{serif} % For serif font in math mode
-\usepackage[round]{natbib} % Needed for Author name citations
+\setbeameroption{show notes}
+\usefonttheme[onlymath]{serif}
+
 \usepackage{../../packages/shared}
 \usepackage{../../packages/misc_commands}
-\input{../../figures/causal_structures/formatting} % Causal structure formatting for tikz
+
+% === Causal structure formatting for tikz ===
+\input{../../figures/causal_structures/formatting}
+
 \renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}
-\renewcommand{\tcdot}{\cdot} % Tentative cdot, not sure if I want to keep dots
 
 \title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
-\author[Fraser]{T.C.~Fraser\inst{1}}
+\author[Fraser]{T.~C.~Fraser\inst{1}}
 \institute[PI]
@@
     \setbeamertemplate{bibliography item}{\insertbiblabel}
-    \bibliographystyle{plainnat}
+    \bibliographystyle{abbrv}
     \bibliography{../references}{}
@@
     \frametitle{Introduction}
-    \note[item]{Thank International Institute for Physics (IIP) for support}
-    \note[item]{Thank Perimeter Institute for Theoretical Physics (PI) for support}
-\end{frame}
-\begin{frame}
-    \frametitle{Objective}
-    \begin{itemize}
-        \item Derive causal compatibility/locality inequalities that distinguish quantum distributions from classical ones
-        \item Specifically for the Triangle Scenario (TS)
-    \end{itemize}
-    \begin{center}
-        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
-    \end{center}
-    \note[item]{Research project's goal was to derive new causal compatibility inequalities that distinguish quantum correlations from classical correlations}
-    \note[item]{More specifically, the ambition of the project is to obtain such inequalities that constraint compatibility with The Triangle Scenario}
-    \note[item]{Triangle Scenario has be studied extensively before}
+    \note[item]{\todo[TC]{}}
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Objective Cont'd}
+    \frametitle{Notation}
     \begin{itemize}
-        \item In~\citet{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}
-        \item In~\citet{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)
-        \item In~\citet{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility
-        \item Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective
+        \item Complete set of random variables are the \term{joint random variables}
+        \[ \jointvar = \bc{v_1, \cdots, v_n} \]
+        \item A subset of $V \subset \jointvar$ is a \term{marginal context}
+        \item \term{Marginal scenario} $\mscenario$
+        \[ \mscenario = \bc{V_1, \ldots, V_k \mid V_i \subset \jointvar} \quad \jointvar = {\bigcup}_{i} V_i  \]
+        \item Marginal scenario forms a \textit{simplicial complex}
+        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
+        \item Restrict focus to \textit{maximal} marginal scenario where only the largest contexts are present
+        \[ \forall V_i, V_j \in \mscenario : V_i \not \subset V_j \]
     \end{itemize}
-    \note[item]{At the time of publishing~\citet{Branciard_2012}, problem seems hard.}
-    \note[item]{Important because its smallest correlation scenario with quantum non-locality.}
-    \note[item]{Compatibility can not be determined from conditional independence relations (there are none)}
-    \note[item]{It would be interesting to find quantum non-locality in the triangle scenario that does not rely on Bell's theorem.}
 \end{frame}
@@
 \begin{frame}
-    \frametitle{This Talk}
-    \begin{itemize}
-        \item Report the discovery of such inequalities
-        \item Explain how these inequalities were obtained
-        \item Discuss quantum distributions that violate compatibility inequalities
-        \item Attempts at finding new quantum distributions different than those proposed by~\cite{Fritz_2012}
-        \item Briefly discuss symmetric inequalities
-    \end{itemize}
-    \note[item]{The purpose of this talk is to present these new-found inequalities and explain how they were obtained}
-    \note[item]{Additionally I will talk about my attempts at using these inequalities to find new incompatible quantum distributions}
-    \note[item]{In doing so, will discuss how we obtained symmetric compatibility inequalities that have violations in the Triangle Scenario}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Example Inequality}
-    \begin{itemize}
-        \item Quick example/preview:
-    \end{itemize}
-    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
-    \begin{itemize}
-        \item $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
-        \item Four outcomes for each $A, B, C$
-        \item Polynomial in $\prob[ABC]$, marginals $\prob[AB]$, $\prob[BC]$, $\prob[AC]$, $\prob[A]$, $\prob[B]$, $\prob[C]$
-    \end{itemize}
-    \note[item]{As a quick example or preview of what is to come, here is a an example inequality admits quantum violations in the triangle scenario}
-    \note[item]{Some features of note: inequality is polynomial in $\prob[ABC]$ and its marginals}
-\end{frame}
-
-% \begin{frame}
-%     \frametitle{Notation}
-%     \begin{itemize}
-%         \item A subset of $V \subset \jointvar$ is a \term{marginal context}
-%         \item Restrict focus to \textit{maximal} marginal scenario where only the largest contexts are present
-%         \[ \forall V_i, V_j \in \mscenario : V_i \not \subset V_j \]
-%     \end{itemize}
-% \end{frame}
-
-\begin{frame}
-    \frametitle{Notation}
-    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
+    \frametitle{Notation Cont'd}
     \begin{itemize}
@@
         \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
-        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
-        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        % \item Marginal scenario forms a \textit{simplicial complex}
-        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
         \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
@@
     \end{itemize}
-    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
-    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
-    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
-    \note[item]{Marginal scenario refers to the those sets of random variables}
-    \note[item]{The complete set of random variables are the joint random variables}
+    \todo[TC]{Insert generic causal structure}
 \end{frame}
@@
     \frametitle{Causal Compatibility}
-    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
+    \textbf{Question:} Is a marginal model $\prob^{\mscenario}$ \term{compatible} with a causal structure $\graph$?\\
+    \[ \mscenario = \bc{V_1, \ldots, V_k \mid V_i \subset \nodes_O} \]
     \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
@@
     \end{enumerate}
-    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
+
+    A \term{casual compatibility inequality} is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
+    \note<1>[item]{}
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Deriving Inequalities}
-    Two necessary components to compatibility:
-    \begin{enumerate}
-        \item[1.] \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
+    \frametitle{Triangle Scenario}
+    \begin{columns}
+        \column{0.4\linewidth}
+            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
+        \column{0.6\linewidth}
             \begin{itemize}
-            \item Is the marginal model contextual or non-contextual?
-            \item 3 distinct ways to tackle this problem
-            \begin{enumerate}
-                \item[1.] Convex hull, Polytope projection, Fourier-Motzkin
-                \item[2.] Possibilistic Hardy Inequalities (Hypergraph transversals)
-                \item[3.] Linear Program Feasibility/Infeasibility
-            \end{enumerate}
+                \item Three parties $\nodes_O = \bc{A, B, C}$
+                \item Pair-wise sharing three latent variables $\nodes_L = \bc{X, Y, Z}$
+                \item \todo[TC]{Inject info about existing work}
+                \item There exists \textit{quantum-accessible} distributions $\prob[ABC]$ that are \textit{incompatible} with the triangle scenario
             \end{itemize}
-    \end{enumerate}
-    \begin{enumerate}
-        \item[2.] \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
+    \end{columns}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Distribution}
+    The \term{Fritz Distribution $\prob[F]$}:
     \begin{itemize}
-            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
-            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
+        \item three-party $\prob[F] = \prob[ABC]$
+        \item each party has four outcomes
     \end{itemize}
-    \end{enumerate}
 \end{frame}
@@
     \frametitle{Inflation Technique}
-    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
+    \begin{itemize}
+        \item Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
+    \end{itemize}
     \begin{definition}
@@
     \end{definition}
+
 \end{frame}
@@
 \begin{frame}
-    \frametitle{$d$-Separation Polynomial}
-
-\end{frame}
-
-\begin{frame}
-    \frametitle{Triangle Scenario}
-    \begin{columns}
-        \column{0.4\linewidth}
-            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
-        \column{0.6\linewidth}
-            \begin{itemize}
-                \item Three parties $\nodes_O = \bc{A, B, C}$
-                \item Pair-wise sharing three latent variables $\nodes_L = \bc{X, Y, Z}$
-                \item \todo[TC]{Inject info about existing work}
-                \item There exists \textit{quantum-accessible} distributions $\prob[ABC]$ that are \textit{incompatible} with the triangle scenario
-            \end{itemize}
-    \end{columns}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Distribution}
-    The \term{Fritz Distribution $\prob[F]$}:
-    \begin{itemize}
-        \item three-party $\prob[F] = \prob[ABC]$
-        \item each party has four outcomes
-    \end{itemize}
+    \frametitle{Inflation Lemma Cont'd}
+    \begin{lemma}
+        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+    \end{lemma}
+    \begin{corollary}
+        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
+    \end{corollary}
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Distribution Vectors}
-    \begin{itemize}
-        \item \term{Joint Distribution Vector $\probvec^{\jointvar}$}
-        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
-        \item \term{Marginal Distribution Vector $\probvec^{\mscenario}$}
-        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
     \frametitle{Incidence Matrix}
     \begin{itemize}
-        \item Marginal Problem as linear program
-        \begin{align*}
-            \probvec^{\mscenario}_m &= {\sum}_{j} M_{m,j} \probvec^{\jointvar}_j \\
-            \probvec^{\mscenario} &= M \tcdot \probvec^{\jointvar}
-        \end{align*}
-        \item \term{Incidence matrix} $M$ is a bit-wise matrix
+        \item Incidence matrix $M$ is a bit-wise matrix
         \item Row-indexed by marginal events $m \in \Events{\mscenario}$
@@
         \[ M_{m,j} = \begin{cases}
-            1 & m = j|_{\Dom{m}} \\
+            1 & m \text{ compatible with } j \\
             0 & \text{otherwise}
         \end{cases} \]
-        \begin{gather*}
-        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
-        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
-        \end{gather*}
-
     \end{itemize}
-\end{frame}
-
-\begin{frame}[shrink=10]
-    \frametitle{Example}
-    Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{A,B,C}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{A,B}, \bc{B,C}, \bc{A,C}}$. The incidence matrix becomes:
-    \[ M = \kbordermatrix{
-        (A,B,C) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
-        (A=0, B=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
-        (A=0, B=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
-        (A=1, B=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
-        (A=1, B=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
-        (B=0, C=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
-        (B=0, C=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
-        (B=1, C=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
-        (B=1, C=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
-        (A=0, C=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
-        (A=0, C=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
-        (A=1, C=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
-        (A=1, C=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
-    } \]
 \end{frame}
@@
             \begin{itemize}
-                \item Find compatibility inequalities for TS by finding non-contextuality inequalities for Large Inflation
-                \item Marginal Scenario is the set of maximal pre-injectable sets
-                \item 12 maximal pre-injectable sets (to follow)
+                \item Tackling Large inflation
+                \item 12 pre-injectable sets (to follow)
             \end{itemize}
@@
         \item Incidence matrix $M$ is very large $\sim 2.25 \textsf{Gb}$
-        \[ \# \text{Columns} = 4^{12} = 16,777,216 \]
-        \[ \# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896 \]
+        \[ \# \text{Columns} = \prod_{v \in \jointvar} O_{v} = 4^{12} = 16,777,216 \]
+        \[ \# \text{Rows} = \sum_{V \in \mscenario} \prod_{v \in V} O_{v} = 4\times 4^{6} + 8 \times 4^{3} = 16,896 \]
     \end{itemize}
@@
     \frametitle{Causal Symmetry}
-    \begin{itemize}
-        \item Desirable to find compatibility inequality $I$ such that
-        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
-        \item Compatibility is independent of variable labels
-        \[ \forall \varphi \in \Perm{\nodes} : I \stackrel{\text{com}}{\rightarrow} \graph \implies \varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \varphi\bs{\graph}  \]
-        \item If $\varphi\bs{\graph} = \graph$ then $\varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \graph$
-    \end{itemize}
-    \begin{definition}
-        The \term{causal symmetry group} of causal structure $\graph$:
-        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
-        Strictly speaking, one needs to preserve observable nodes:
-        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
-    \end{definition}
-    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
-    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e.
-inequality) that is symmetric under exchange of parties}
-    \note<1>[item]{Surprisingly, it is possible to do so!}
-    \note<1>[item]{Here is how.}
-    \note<1>[item]{First, we will formally define the symmetry group in question}
-    \note<1>[item]{Causal symmetry group is the }
 \end{frame}
@@
         \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
-        \item Relative Phase Terms: $RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$
-        \item Rotation Terms: $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
+        \item Relative Phase Terms: $RP_{m,n} = \exp\br{i P_n \lambda_{n,m}}$
+        \item Rotation Terms: $R_{n,m} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
         \item Projection Operators: $P_l = \ket{l}\bra{l}$
@@
             GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
-            RP_{n,m} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
-            R_{m,n} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
+            RP_{m,n} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
+            R_{n,m} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
             & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\

### 2016-11-14 documents/DefiniteExtensions/dep.tex
Updates from ShareLaTeX
Major sync issues with Github, tried to pull from repository without committing. May cause errors. Sorry!

@@
 
-    \todo[TC]{Flesh out document from archive}
+    \section{Introduction}
+        \begin{itemize}
+            \item \todo[TC]{Marginal problem}
+            \item \todo[TC]{Use cases for the marginal problem}
+            \item \todo[TC]{Motivate issue of computational complexity}
+            \item \todo[TC]{Will be presenting technique capable of fully solving marginal problem}
+            \item \todo[TC]{Early termination offers partial solution}
+        \end{itemize}
+
+    \section{Marginal Problem}
+        \begin{itemize}
+            \item \todo[TC]{Set up notation and definitions}
+        \end{itemize}
+
+    \section{Existing Methods}
+        \begin{itemize}
+            \item \todo[TC]{Geometric interpretation of marginal Polytope}
+            \item \todo[TC]{Fourier Motzkin, Convex Hull}
+            \item \todo[TC]{ESP, Symmetric, etc...}
+            \item \todo[TC]{Existing methods do not exploit features of interest}
+            \item \todo[TC]{Logical Contextuality \& Hardy Transversals}
+        \end{itemize}
+
+    \section{Definite Extension Procedure}
+        \begin{itemize}
+            \item \todo[TC]{Prove features of complete solution}
+            \item \todo[TC]{Homogeneous, linear, integral}
+            \item \todo[TC]{Multi-set representation of inequality (certificates)}
+        \end{itemize}
+    \subsection{Hypergraph Transversals}
+        \begin{itemize}
+            \item \todo[TC]{Generalizing Logical Contextuality inequalities to more exotic antecedents}
+            \item \todo[TC]{Algorithms}
+        \end{itemize}
+
+    \subsection{Irreducibility \& Facets}
+        \begin{itemize}
+            \item \todo[TC]{Define facets and their properties}
+            \item \todo[TC]{Algorithms}
+            \item \todo[TC]{Visualization}
+        \end{itemize}
+
+    \subsection{Accelerations \& Symmetries}
+        \todo[TC]{**Need to prove/disprove complete symmetry group**}
+        \begin{itemize}
+            \item \todo[TC]{Complete Characterization of Marginal Symmetries}
+            \item \todo[TC]{Outcome Symmetries}
+            \item \todo[TC]{Variable Symmetries}
+            \item \todo[TC]{Search space and Output massively reduced}
+        \end{itemize}
+
+    \subsection{Hierarchy vs. Relaxation}
+        \todo[TC]{**Need to determine upper limit**}
+        \begin{itemize}
+            \item \todo[TC]{Implementation as Hierarchy or Relaxation}
+        \end{itemize}
+
+    \subsection{Convex Hull Problem}
+        \begin{itemize}
+            \item \todo[TC]{Possible to use this on generic convex hull}
+        \end{itemize}
+
+    \subsection{Targeted Definite Extension Procedure}
+        \begin{itemize}
+            \item \todo[TC]{With known incompatible distributions can target output}
+            \item \todo[TC]{Seeds inequalities}
+        \end{itemize}
+
+    \section{Demonstrations}
+
+    \subsection{Generic Problem}
+    \subsection{Quantum Non-locality}
+    \subsection{Something Else}
+
+    \section{Conclusions}
+        \begin{itemize}
+            \item \todo[TC]{In situations where Fourier Motzkin is intractable/will never finish, other methods need to be used}
+            \item \todo[TC]{If number of facets is massive, partial solution with flexibility is desired}
+            \item \todo[TC]{Symmetries drastically reduce the output space and search space}
+            \item \todo[TC]{DEP offers a canonical presentation of output space}
+        \end{itemize}
+
+    \section*{Acknowledgments}
+    \begin{itemize}
+        \item \todo[TC]{Elie}
+        \item \todo[TC]{Perimeter}
+        \item \todo[TC]{University of Waterloo}
+        \item \todo[TC]{Possible due to Mike Lazaridis Scholarship}
+    \end{itemize}
+
 \end{document}

### 2016-11-14 figures/inequalities/nosymwitness_ineq_print.tex
Major sync issues with Github, tried to pull from repository without committing. May cause errors. Sorry!

\begin{align*}
	P_{ABC}(110)P_{ABC}(223) + P_{ABC}(110)P_{ABC}(233) + P_{ABC}(110)P_{ABC}(323) + P_{ABC}(110)P_{ABC}(333)
\end{align*}
\[\leq\]
\begin{align*}
	2P_{ABC}(020)P_{ABC}(213) + 2P_{ABC}(023)P_{ABC}(210) + 2P_{ABC}(023)P_{ABC}(310) + 2P_{ABC}(030)P_{ABC}(213) + 2P_{ABC}(033)P_{ABC}(210)+ \\
	2P_{ABC}(033)P_{ABC}(310) + 2P_{ABC}(120)P_{ABC}(213) + 2P_{ABC}(123)P_{ABC}(210) + 2P_{ABC}(123)P_{ABC}(310) + 2P_{ABC}(130)P_{ABC}(213)+ \\
	2P_{ABC}(132)P_{ABC}(311) + 2P_{ABC}(133)P_{ABC}(210) + 2P_{ABC}(133)P_{ABC}(310) + P_{ABC}(000)P_{ABC}(003) + P_{ABC}(000)P_{ABC}(013)+ \\
	P_{ABC}(000)P_{ABC}(023) + P_{ABC}(000)P_{ABC}(033) + P_{ABC}(000)P_{ABC}(103) + P_{ABC}(000)P_{ABC}(113) + P_{ABC}(000)P_{ABC}(123)+ \\
	P_{ABC}(000)P_{ABC}(133) + P_{ABC}(000)P_{ABC}(203) + P_{ABC}(000)P_{ABC}(213) + P_{ABC}(000)P_{ABC}(223) + P_{ABC}(003)P_{ABC}(010)+ \\
	P_{ABC}(003)P_{ABC}(020) + P_{ABC}(003)P_{ABC}(030) + P_{ABC}(003)P_{ABC}(100) + P_{ABC}(003)P_{ABC}(110) + P_{ABC}(003)P_{ABC}(120)+ \\
	P_{ABC}(003)P_{ABC}(130) + P_{ABC}(003)P_{ABC}(200) + P_{ABC}(003)P_{ABC}(210) + P_{ABC}(003)P_{ABC}(220) + P_{ABC}(003)P_{ABC}(230)+ \\
	P_{ABC}(003)P_{ABC}(300) + P_{ABC}(003)P_{ABC}(310) + P_{ABC}(003)P_{ABC}(320) + P_{ABC}(003)P_{ABC}(330) + P_{ABC}(010)P_{ABC}(013)+ \\
	P_{ABC}(010)P_{ABC}(023) + P_{ABC}(010)P_{ABC}(033) + P_{ABC}(010)P_{ABC}(103) + P_{ABC}(010)P_{ABC}(113) + P_{ABC}(010)P_{ABC}(123)+ \\
	P_{ABC}(010)P_{ABC}(133) + P_{ABC}(010)P_{ABC}(203) + P_{ABC}(010)P_{ABC}(213) + P_{ABC}(010)P_{ABC}(223) + P_{ABC}(013)P_{ABC}(020)+ \\
	P_{ABC}(013)P_{ABC}(030) + P_{ABC}(013)P_{ABC}(100) + P_{ABC}(013)P_{ABC}(110) + P_{ABC}(013)P_{ABC}(120) + P_{ABC}(013)P_{ABC}(130)+ \\
	P_{ABC}(013)P_{ABC}(200) + P_{ABC}(013)P_{ABC}(210) + P_{ABC}(013)P_{ABC}(220) + P_{ABC}(013)P_{ABC}(230) + P_{ABC}(013)P_{ABC}(300)+ \\
	P_{ABC}(013)P_{ABC}(310) + P_{ABC}(013)P_{ABC}(320) + P_{ABC}(013)P_{ABC}(330) + P_{ABC}(020)P_{ABC}(023) + P_{ABC}(020)P_{ABC}(033)+ \\
	P_{ABC}(020)P_{ABC}(103) + P_{ABC}(020)P_{ABC}(113) + P_{ABC}(020)P_{ABC}(123) + P_{ABC}(020)P_{ABC}(133) + P_{ABC}(020)P_{ABC}(203)+ \\
	P_{ABC}(020)P_{ABC}(210) + P_{ABC}(020)P_{ABC}(211) + P_{ABC}(020)P_{ABC}(212) + P_{ABC}(020)P_{ABC}(223) + P_{ABC}(020)P_{ABC}(233)+ \\
	P_{ABC}(020)P_{ABC}(310) + P_{ABC}(020)P_{ABC}(311) + P_{ABC}(020)P_{ABC}(312) + P_{ABC}(020)P_{ABC}(313) + P_{ABC}(021)P_{ABC}(210)+ \\
	P_{ABC}(021)P_{ABC}(211) + P_{ABC}(021)P_{ABC}(212) + P_{ABC}(021)P_{ABC}(213) + P_{ABC}(021)P_{ABC}(310) + P_{ABC}(021)P_{ABC}(311)+ \\
	P_{ABC}(021)P_{ABC}(312) + P_{ABC}(021)P_{ABC}(313) + P_{ABC}(022)P_{ABC}(210) + P_{ABC}(022)P_{ABC}(212) + P_{ABC}(022)P_{ABC}(213)+ \\
	P_{ABC}(022)P_{ABC}(310) + P_{ABC}(022)P_{ABC}(311) + P_{ABC}(022)P_{ABC}(312) + P_{ABC}(022)P_{ABC}(313) + P_{ABC}(023)P_{ABC}(030)+ \\
	P_{ABC}(023)P_{ABC}(100) + P_{ABC}(023)P_{ABC}(110) + P_{ABC}(023)P_{ABC}(120) + P_{ABC}(023)P_{ABC}(130) + P_{ABC}(023)P_{ABC}(200)+ \\
	P_{ABC}(023)P_{ABC}(211) + P_{ABC}(023)P_{ABC}(212) + P_{ABC}(023)P_{ABC}(213) + P_{ABC}(023)P_{ABC}(220) + P_{ABC}(023)P_{ABC}(230)+ \\
	P_{ABC}(023)P_{ABC}(300) + P_{ABC}(023)P_{ABC}(311) + P_{ABC}(023)P_{ABC}(312) + P_{ABC}(023)P_{ABC}(313) + P_{ABC}(023)P_{ABC}(320)+ \\
	P_{ABC}(023)P_{ABC}(330) + P_{ABC}(030)P_{ABC}(033) + P_{ABC}(030)P_{ABC}(103) + P_{ABC}(030)P_{ABC}(113) + P_{ABC}(030)P_{ABC}(123)+ \\
	P_{ABC}(030)P_{ABC}(133) + P_{ABC}(030)P_{ABC}(203) + P_{ABC}(030)P_{ABC}(210) + P_{ABC}(030)P_{ABC}(211) + P_{ABC}(030)P_{ABC}(212)+ \\
	P_{ABC}(030)P_{ABC}(223) + P_{ABC}(030)P_{ABC}(233) + P_{ABC}(030)P_{ABC}(310) + P_{ABC}(030)P_{ABC}(311) + P_{ABC}(030)P_{ABC}(312)+ \\
	P_{ABC}(030)P_{ABC}(313) + P_{ABC}(031)P_{ABC}(210) + P_{ABC}(031)P_{ABC}(211) + P_{ABC}(031)P_{ABC}(212) + P_{ABC}(031)P_{ABC}(213)+ \\
	P_{ABC}(031)P_{ABC}(310) + P_{ABC}(031)P_{ABC}(311) + P_{ABC}(031)P_{ABC}(312) + P_{ABC}(031)P_{ABC}(313) + P_{ABC}(032)P_{ABC}(210)+ \\
	P_{ABC}(032)P_{ABC}(212) + P_{ABC}(032)P_{ABC}(213) + P_{ABC}(032)P_{ABC}(310) + P_{ABC}(032)P_{ABC}(311) + P_{ABC}(032)P_{ABC}(312)+ \\
	P_{ABC}(032)P_{ABC}(313) + P_{ABC}(033)P_{ABC}(100) + P_{ABC}(033)P_{ABC}(110) + P_{ABC}(033)P_{ABC}(120) + P_{ABC}(033)P_{ABC}(130)+ \\
	P_{ABC}(033)P_{ABC}(200) + P_{ABC}(033)P_{ABC}(211) + P_{ABC}(033)P_{ABC}(212) + P_{ABC}(033)P_{ABC}(213) + P_{ABC}(033)P_{ABC}(220)+ \\
	P_{ABC}(033)P_{ABC}(230) + P_{ABC}(033)P_{ABC}(300) + P_{ABC}(033)P_{ABC}(311) + P_{ABC}(033)P_{ABC}(312) + P_{ABC}(033)P_{ABC}(313)+ \\
	P_{ABC}(033)P_{ABC}(320) + P_{ABC}(033)P_{ABC}(330) + P_{ABC}(100)P_{ABC}(103) + P_{ABC}(100)P_{ABC}(113) + P_{ABC}(100)P_{ABC}(123)+ \\
	P_{ABC}(100)P_{ABC}(133) + P_{ABC}(100)P_{ABC}(203) + P_{ABC}(100)P_{ABC}(213) + P_{ABC}(100)P_{ABC}(223) + P_{ABC}(103)P_{ABC}(110)+ \\
	P_{ABC}(103)P_{ABC}(120) + P_{ABC}(103)P_{ABC}(130) + P_{ABC}(103)P_{ABC}(200) + P_{ABC}(103)P_{ABC}(210) + P_{ABC}(103)P_{ABC}(220)+ \\
	P_{ABC}(103)P_{ABC}(230) + P_{ABC}(103)P_{ABC}(300) + P_{ABC}(103)P_{ABC}(310) + P_{ABC}(103)P_{ABC}(320) + P_{ABC}(103)P_{ABC}(330)+ \\
	P_{ABC}(110)P_{ABC}(113) + P_{ABC}(110)P_{ABC}(123) + P_{ABC}(110)P_{ABC}(133) + P_{ABC}(110)P_{ABC}(203) + P_{ABC}(110)P_{ABC}(213)+ \\
	P_{ABC}(110)P_{ABC}(223) + P_{ABC}(113)P_{ABC}(120) + P_{ABC}(113)P_{ABC}(130) + P_{ABC}(113)P_{ABC}(200) + P_{ABC}(113)P_{ABC}(210)+ \\
	P_{ABC}(113)P_{ABC}(220) + P_{ABC}(113)P_{ABC}(230) + P_{ABC}(113)P_{ABC}(300) + P_{ABC}(113)P_{ABC}(310) + P_{ABC}(113)P_{ABC}(320)+ \\
	P_{ABC}(113)P_{ABC}(330) + P_{ABC}(120)P_{ABC}(123) + P_{ABC}(120)P_{ABC}(133) + P_{ABC}(120)P_{ABC}(203) + P_{ABC}(120)P_{ABC}(210)+ \\
	P_{ABC}(120)P_{ABC}(211) + P_{ABC}(120)P_{ABC}(212) + P_{ABC}(120)P_{ABC}(223) + P_{ABC}(120)P_{ABC}(233) + P_{ABC}(120)P_{ABC}(310)+ \\
	P_{ABC}(120)P_{ABC}(311) + P_{ABC}(120)P_{ABC}(312) + P_{ABC}(120)P_{ABC}(313) + P_{ABC}(121)P_{ABC}(210) + P_{ABC}(121)P_{ABC}(211)+ \\
	P_{ABC}(121)P_{ABC}(212) + P_{ABC}(121)P_{ABC}(213) + P_{ABC}(121)P_{ABC}(310) + P_{ABC}(121)P_{ABC}(311) + P_{ABC}(121)P_{ABC}(312)+ \\
	P_{ABC}(121)P_{ABC}(313) + P_{ABC}(122)P_{ABC}(210) + P_{ABC}(122)P_{ABC}(212) + P_{ABC}(122)P_{ABC}(213) + P_{ABC}(122)P_{ABC}(310)+ \\
	P_{ABC}(122)P_{ABC}(311) + P_{ABC}(122)P_{ABC}(312) + P_{ABC}(122)P_{ABC}(313) + P_{ABC}(123)P_{ABC}(130) + P_{ABC}(123)P_{ABC}(200)+ \\
	P_{ABC}(123)P_{ABC}(211) + P_{ABC}(123)P_{ABC}(212) + P_{ABC}(123)P_{ABC}(213) + P_{ABC}(123)P_{ABC}(220) + P_{ABC}(123)P_{ABC}(230)+ \\
	P_{ABC}(123)P_{ABC}(300) + P_{ABC}(123)P_{ABC}(311) + P_{ABC}(123)P_{ABC}(312) + P_{ABC}(123)P_{ABC}(313) + P_{ABC}(123)P_{ABC}(320)+ \\
	P_{ABC}(123)P_{ABC}(330) + P_{ABC}(130)P_{ABC}(133) + P_{ABC}(130)P_{ABC}(203) + P_{ABC}(130)P_{ABC}(210) + P_{ABC}(130)P_{ABC}(211)+ \\
	P_{ABC}(130)P_{ABC}(212) + P_{ABC}(130)P_{ABC}(223) + P_{ABC}(130)P_{ABC}(233) + P_{ABC}(130)P_{ABC}(310) + P_{ABC}(130)P_{ABC}(311)+ \\
	P_{ABC}(130)P_{ABC}(312) + P_{ABC}(130)P_{ABC}(313) + P_{ABC}(131)P_{ABC}(210) + P_{ABC}(131)P_{ABC}(211) + P_{ABC}(131)P_{ABC}(212)+ \\
	P_{ABC}(131)P_{ABC}(213) + P_{ABC}(131)P_{ABC}(310) + P_{ABC}(131)P_{ABC}(311) + P_{ABC}(131)P_{ABC}(312) + P_{ABC}(131)P_{ABC}(313)+ \\
	P_{ABC}(132)P_{ABC}(201) + P_{ABC}(132)P_{ABC}(210) + P_{ABC}(132)P_{ABC}(211) + P_{ABC}(132)P_{ABC}(212) + P_{ABC}(132)P_{ABC}(213)+ \\
	P_{ABC}(132)P_{ABC}(301) + P_{ABC}(132)P_{ABC}(310) + P_{ABC}(132)P_{ABC}(312) + P_{ABC}(132)P_{ABC}(313) + P_{ABC}(133)P_{ABC}(200)+ \\
	P_{ABC}(133)P_{ABC}(211) + P_{ABC}(133)P_{ABC}(212) + P_{ABC}(133)P_{ABC}(213) + P_{ABC}(133)P_{ABC}(220) + P_{ABC}(133)P_{ABC}(230)+ \\
	P_{ABC}(133)P_{ABC}(300) + P_{ABC}(133)P_{ABC}(311) + P_{ABC}(133)P_{ABC}(312) + P_{ABC}(133)P_{ABC}(313) + P_{ABC}(133)P_{ABC}(320)+ \\
	P_{ABC}(133)P_{ABC}(330) + P_{ABC}(200)P_{ABC}(203) + P_{ABC}(200)P_{ABC}(213) + P_{ABC}(200)P_{ABC}(223) + P_{ABC}(200)P_{ABC}(233)+ \\
	P_{ABC}(200)P_{ABC}(303) + P_{ABC}(200)P_{ABC}(313) + P_{ABC}(200)P_{ABC}(323) + P_{ABC}(200)P_{ABC}(333) + P_{ABC}(203)P_{ABC}(210)+ \\
	P_{ABC}(203)P_{ABC}(220) + P_{ABC}(203)P_{ABC}(230) + P_{ABC}(203)P_{ABC}(300) + P_{ABC}(203)P_{ABC}(310) + P_{ABC}(203)P_{ABC}(320)+ \\
	P_{ABC}(203)P_{ABC}(330) + P_{ABC}(210)P_{ABC}(213) + P_{ABC}(210)P_{ABC}(223) + P_{ABC}(210)P_{ABC}(233) + P_{ABC}(210)P_{ABC}(303)+ \\
	P_{ABC}(210)P_{ABC}(313) + P_{ABC}(210)P_{ABC}(323) + P_{ABC}(210)P_{ABC}(333) + P_{ABC}(213)P_{ABC}(220) + P_{ABC}(213)P_{ABC}(230)+ \\
	P_{ABC}(213)P_{ABC}(300) + P_{ABC}(213)P_{ABC}(310) + P_{ABC}(213)P_{ABC}(320) + P_{ABC}(213)P_{ABC}(330) + P_{ABC}(220)P_{ABC}(223)+ \\
	P_{ABC}(220)P_{ABC}(233) + P_{ABC}(220)P_{ABC}(303) + P_{ABC}(220)P_{ABC}(313) + P_{ABC}(220)P_{ABC}(323) + P_{ABC}(220)P_{ABC}(333)+ \\
	P_{ABC}(223)P_{ABC}(230) + P_{ABC}(223)P_{ABC}(300) + P_{ABC}(223)P_{ABC}(310) + P_{ABC}(223)P_{ABC}(320) + P_{ABC}(223)P_{ABC}(330)+ \\
	P_{ABC}(230)P_{ABC}(233) + P_{ABC}(230)P_{ABC}(303) + P_{ABC}(230)P_{ABC}(313) + P_{ABC}(230)P_{ABC}(323) + P_{ABC}(230)P_{ABC}(333)+ \\
	P_{ABC}(233)P_{ABC}(300) + P_{ABC}(233)P_{ABC}(310) + P_{ABC}(233)P_{ABC}(320) + P_{ABC}(233)P_{ABC}(330) + P_{ABC}(300)P_{ABC}(303)+ \\
	P_{ABC}(300)P_{ABC}(313) + P_{ABC}(300)P_{ABC}(323) + P_{ABC}(300)P_{ABC}(333) + P_{ABC}(303)P_{ABC}(310) + P_{ABC}(303)P_{ABC}(320)+ \\
	P_{ABC}(303)P_{ABC}(330) + P_{ABC}(310)P_{ABC}(313) + P_{ABC}(310)P_{ABC}(323) + P_{ABC}(310)P_{ABC}(333) + P_{ABC}(313)P_{ABC}(320)+ \\
	P_{ABC}(313)P_{ABC}(330) + P_{ABC}(320)P_{ABC}(323) + P_{ABC}(320)P_{ABC}(333) + P_{ABC}(323)P_{ABC}(330) + P_{ABC}(330)P_{ABC}(333)
\end{align*}

### 2016-11-14 documents/TriangleScenario/ts.tex
Updates from ShareLaTeX

@@
 
-    \todo[TC]{Flesh out document from archive}
+    \section{Introduction}
+    \begin{itemize}
+        \item \todo[TC]{Overview of importance of inequalities}
+        \item \todo[TC]{Triangle Scenario and existing work}
+        \item \todo[TC]{Objective of research project}
+        \item \todo[TC]{Structure of this paper}
+    \end{itemize}
+
+    \section{Causal Compatibility}
+    \begin{itemize}
+        \item \todo[TC]{Define marginal scenario}
+        \item \todo[TC]{Define marginal model}
+        \item \todo[TC]{Define causal structure}
+        \item \todo[TC]{Define compatibility}
+    \end{itemize}
+
+    \section{Triangle Scenario}
+    \begin{itemize}
+        \item \todo[TC]{Discuss some of its appearances in other work}
+        \item \todo[TC]{Figure}
+    \end{itemize}
+    \subsection{Fritz Distribution}
+    \begin{itemize}
+        \item \todo[TC]{Reproduce Fritz Distribution}
+        \item \todo[TC]{Recall its proof of incompatibility}
+        \item \todo[TC]{Requires perfect correlations}
+        \item \todo[TC]{Not robust to noise}
+        \item \todo[TC]{Fritz Problem 2.17}
+    \end{itemize}
+    \section{Inflation Technique}
+    \begin{itemize}
+        \item \todo[TC]{Summarize inflation technique}
+        \item \todo[TC]{Inflations of Triangle Scenario}
+        \item \todo[TC]{Demonstrate that one can derive causal incompatibility inequalities from inflation}
+        \item \todo[TC]{Pre-injectable sets for Large inflation}
+    \end{itemize}
+
+    \section{Deriving Inequalities}
+    \begin{itemize}
+        \item \todo[TC]{Marginal problem}
+        \item \todo[TC]{Popular methods: Fourier Motzkin (Convex hull, Polytope projection), Hardy implication inequalities, linear program/certificate}
+        \item \todo[TC]{Overview incidence for Large Inflation}
+        \item \todo[TC]{Rule out expensive methods like FM}
+        \item \todo[TC]{Present some of the inequalities found}
+    \end{itemize}
+
+    \subsection{Symmetric Inequalities}
+    \begin{itemize}
+        \item \todo[TC]{Discuss symmetries and why they are useful}
+        \item \todo[TC]{Symmetrizing Incidence Matrix}
+        \item \todo[TC]{Large inflation incidence contracted drastically}
+        \item \todo[TC]{Present some of the inequalities found}
+    \end{itemize}
+
+    \section{Violations}
+    \begin{itemize}
+        \item \todo[TC]{Fritz Distribution violates found inequalities}
+    \end{itemize}
+    \subsection{Numerical Optimizations}
+    \begin{itemize}
+        \item \todo[TC]{Generic idea}
+        \item \todo[TC]{Optimization techniques used}
+    \end{itemize}
+    \subsection{Parameterizing Quantum Distributions}
+    \begin{itemize}
+        \item \todo[TC]{Unitaries}
+        \item \todo[TC]{States}
+        \item \todo[TC]{Measurements}
+        \item \todo[TC]{Aligning States / Permutation}
+    \end{itemize}
+    \subsection{Results}
+    \begin{itemize}
+        \item \todo[TC]{Plots of various optimizations}
+        \item \todo[TC]{Features of maximally violating distributions}
+    \end{itemize}
+
+    \section{Conclusions}
+    \begin{itemize}
+        \item \todo[TC]{Inflation technique capable of finding inequalities witnessing quantum/classic difference in TS}
+        \item \todo[TC]{Causal incompatibility inequalities found violated by known distributions}
+        \item \todo[TC]{Maximal distributions are different than Fritz but still rely on Bell's theorem}
+        \item \todo[TC]{Refinement on Fritz's question}
+    \end{itemize}
+
+    \section*{Acknowledgments}
+    \begin{itemize}
+        \item \todo[TC]{Elie}
+        \item \todo[TC]{Perimeter}
+        \item \todo[TC]{University of Waterloo}
+        \item \todo[TC]{Possible due to Mike Lazaridis Scholarship}
+    \end{itemize}
 

### 2016-11-14 documents/BrazilSlides/slides.tex
Updates from ShareLaTeX
Fixed ShareLatex's overwrite?

--- 2016-11-14 documents/BrazilSlides/slides.tex
@@
 \documentclass[
-    hyperref={bookmarks=false,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
+    hyperref={bookmarks=false},% ,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue
     xcolor={dvipsnames},
@@
 
-\usetheme[height=8mm]{Rochester}
-\usecolortheme{default}
+\usetheme[height=8mm]{Rochester} % Main Theme
+\usecolortheme{default} % Color Theme
 
@@
 \usefonttheme[onlymath]{serif} % For serif font in math mode
-\usepackage[round]{natbib} % Needed for Author name citations
+% \usepackage[round]{natbib} % Needed for Author name citations
+\usepackage[backend=biber]{biblatex} %
 \usepackage{../../packages/shared}
@@
 \renewcommand{\tcdot}{\cdot} % Tentative cdot, not sure if I want to keep dots
+\setbeamertemplate{bibliography item}{\insertbiblabel}
+\addbibresource{../references.bib}
 
@@
 \frame{\titlepage}
-
-\begin{frame}[allowframebreaks]
-    \frametitle{References}
-    \todo[TC]{Figure out how to get references at the end}
-    \setbeamertemplate{bibliography item}{\insertbiblabel}
-    \bibliographystyle{plainnat}
-    \bibliography{../references}{}
-\end{frame}
 
@@
     \begin{itemize}
-        \item In~\citet{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}
-        \item In~\citet{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)
-        \item In~\citet{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility
+        \item In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}
+        \item In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)
+        \item In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility
         \item Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective
     \end{itemize}
-    \note[item]{At the time of publishing~\citet{Branciard_2012}, problem seems hard.}
+    \note[item]{At the time of publishing~\cite{Branciard_2012}, problem seems hard.}
     \note[item]{Important because its smallest correlation scenario with quantum non-locality.}
@@
 
+\begin{frame}[allowframebreaks]
+    \frametitle{References}
+    \todo[TC]{Figure out how to get references at the end}
+    \printbibliography
+\end{frame}
+
 \end{document}

### 2016-11-17 documents/BrazilSlides/slides.tex
Testing Binary files again
Changed authoryear citations again
Added slide numbers.
Started work on reducing verbiage and increasing figure count.

@@
 \usefonttheme[onlymath]{serif} % For serif font in math mode
-% \usepackage[round]{natbib} % Needed for Author name citations
-\usepackage[backend=biber]{biblatex} %
+\usepackage[backend=biber, citestyle=authoryear]{biblatex} %
+
+\usepackage{silence}
+\WarningFilter{biblatex}{Patching footnotes failed}
+\renewcommand\mkbibacro[1]{{\footnotesize\MakeUppercase{#1}}} % http://tex.stackexchange.com/questions/203111/small-caps-font-warning-in-beamer-using-biblatex
+
 \usepackage{../../packages/shared}
@@
     \note[item]{Triangle Scenario has be studied extensively before}
+    \note[item]{In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}}
+    \note[item]{In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)}
+    \note[item]{In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility}
+    \note[item]{Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective}
 \end{frame}
@@
     \frametitle{Objective Cont'd}
-    \begin{itemize}
-        \item In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}
-        \item In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)
-        \item In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility
-        \item Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective
-    \end{itemize}
     \note[item]{At the time of publishing~\cite{Branciard_2012}, problem seems hard.}
@@
     \frametitle{References}
-    \todo[TC]{Figure out how to get references at the end}
     \printbibliography

### 2016-11-17 documents/BrazilSlides/slides.tex
new noise figures, new code to plot distributions, references, other stuff to come in the morning

@@
 \documentclass[
-    hyperref={bookmarks=false},% ,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue
+    hyperref={bookmarks=false},% ,, linkcolor=blue, urlcolor=blue,, colorlinks=true, citecolor=MidnightBlue
     xcolor={dvipsnames},
@@
 \usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
-\setbeameroption{show notes} % Shows notes on the right of the main slides
+\AtBeginNote{\scriptsize} % Make notes small
+\setbeameroption{show notes} % Shows notes
+% \setbeameroption{show only notes} % Shows only notes
 % \setbeameroption{show notes on second screen}
 \usefonttheme[onlymath]{serif} % For serif font in math mode
-\usepackage[backend=biber, citestyle=authoryear]{biblatex} %
+\usepackage[backend=biber, style=authoryear, doi=false,isbn=false,url=false, citestyle=authoryear-comp]{biblatex} %
+
+\setbeamertemplate{navigation symbols}{
+\insertslidenavigationsymbol%
+\insertframenavigationsymbol%
+\insertsubsectionnavigationsymbol%
+\insertsectionnavigationsymbol%
+\insertdocnavigationsymbol%
+\insertbackfindforwardnavigationsymbol%
+\hspace{1em}%
+\usebeamerfont{footline} \insertframenumber/\inserttotalframenumber%
+}
 
@@
 \addbibresource{../references.bib}
+\AtBeginBibliography{\small}
 
@@
 
-\frame{\titlepage}
-
-% \begin{frame}
-%     \frametitle{Table of Contents}
-% \tableofcontents
-
-% \end{frame}
-
 \begin{frame}
-    \frametitle{Introduction}
+    \titlepage
     \note[item]{Thank International Institute for Physics (IIP) for support}
@@
 \end{frame}
+
 \begin{frame}
-    \frametitle{Objective}
-    \begin{itemize}
-        \item Derive causal compatibility/locality inequalities that distinguish quantum distributions from classical ones
-        \item Specifically for the Triangle Scenario (TS)
-    \end{itemize}
+    \frametitle{The Triangle Scenario (TS)}
     \begin{center}
-        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
+        \scalebox{1.5}{\input{../../figures/causal_structures/triangle_scenario}}
     \end{center}
     \note[item]{Research project's goal was to derive new causal compatibility inequalities that distinguish quantum correlations from classical correlations}
-    \note[item]{More specifically, the ambition of the project is to obtain such inequalities that constraint compatibility with The Triangle Scenario}
     \note[item]{Triangle Scenario has be studied extensively before}
@@
     \note[item]{In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)}
-    \note[item]{In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility}
+    \note[item]{In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility (there are none)}
     \note[item]{Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective}
@@
 \begin{frame}
-    \frametitle{Objective Cont'd}
-    \note[item]{At the time of publishing~\cite{Branciard_2012}, problem seems hard.}
-    \note[item]{Important because its smallest correlation scenario with quantum non-locality.}
-    \note[item]{Compatibility can not be determined from conditional independence relations (there are none)}
-    \note[item]{It would be interesting to find quantum non-locality in the triangle scenario that does not rely on Bell's theorem.}
-\end{frame}
-
-\begin{frame}
     \frametitle{This Talk}
-    \begin{itemize}
+    \begin{enumerate}
         \item Report the discovery of such inequalities
         \item Explain how these inequalities were obtained
-        \item Discuss quantum distributions that violate compatibility inequalities
-        \item Attempts at finding new quantum distributions different than those proposed by~\cite{Fritz_2012}
-        \item Briefly discuss symmetric inequalities
-    \end{itemize}
+        \item Symmetric inequalities
+        \item Greater violations
+        \item Different kinds of non-locality?
+    \end{enumerate}
     \note[item]{The purpose of this talk is to present these new-found inequalities and explain how they were obtained}
-    \note[item]{Additionally I will talk about my attempts at using these inequalities to find new incompatible quantum distributions}
-    \note[item]{In doing so, will discuss how we obtained symmetric compatibility inequalities that have violations in the Triangle Scenario}
+    \note[item]{Talk about how symmetries play two roles in the search for quantum non-locality}
+    \note[item]{Demonstrate how these inequalities are robust to noise}
+    \note[item]{Finding maximally violating distributions}
 \end{frame}
@@
 
+\newcommand{\probplotvalue}[1]{%
+    \definecolor{probvalcolor}{RGB}{#1}%
+    \definecolor{outlinecolor}{RGB}{127, 127, 127}%
+    \begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]%
+        \pgfmathsetmacro{\size}{0.2};%
+        \draw[outlinecolor, fill=probvalcolor] (-\size,-\size) -- (-\size, +\size) -- (+\size, +\size) -- (+\size, -\size) -- cycle;%
+    \end{tikzpicture}%
+}%
+
 \begin{frame}
     \frametitle{Fritz Distribution}
-    The \term{Fritz Distribution $\prob[F]$}:
-    \begin{itemize}
-        \item three-party $\prob[F] = \prob[ABC]$
-        \item each party has $4$ outcomes
-    \end{itemize}
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot.pdf}
+    \end{center}
+    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Distribution Course Graining CHSH [Optional]}
     \begin{gather*}
@@
 \begin{frame}
-    \frametitle{Quantum Implementation of Fritz Distribution}
+    \frametitle{Quantum Implementation of Fritz Distribution [Optional]}
     \begin{itemize}
@@
     \end{itemize}
+\end{frame}
 
+\begin{frame}
+    \frametitle{Uniform Noise}
+    \[ \s{U}_{\varepsilon}\br{P} = \br{1 + \varepsilon} P + \varepsilon \s{U} \]
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/distributions/uniform_dist_plot.pdf}
+    \end{center}
+    \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
+    % \begin{center}
+    %     \begin{tikzpicture}
+    %         \pgfmathsetmacro{\ts}{0.5}; % term spacing
+    %         \draw[] (0*\ts,0) node[]{$P_\varepsilon$};
+    %         \draw[] (1*\ts,0) node[]{$=$};
+    %         \draw[] (2*\ts,0) node[]{$(1-\varepsilon)P_{F}$};
+    %         \draw[] (3*\ts,0) node[]{$+$};
+    %         \draw[] (4*\ts,0) node[]{$\delta$};
+    %     \end{tikzpicture}
+    % \end{center}
 \end{frame}

### 2016-11-19 documents/BrazilSlides/slides.tex
Added some slides to the beginning, will finish slides while traveling

@@
     \begin{enumerate}
-        \item Report the discovery of such inequalities
-        \item Explain how these inequalities were obtained
-        \item Symmetric inequalities
-        \item Greater violations
-        \item Different kinds of non-locality?
+        \item Inflation technique provides polynomial inequalities
+        \item Inequalities witnessing non-local quantum correlations in the Triangle Scenario
+        \item Discuss search for new non-local quantum correlations
     \end{enumerate}
-    \note[item]{The purpose of this talk is to present these new-found inequalities and explain how they were obtained}
-    \note[item]{Talk about how symmetries play two roles in the search for quantum non-locality}
-    \note[item]{Demonstrate how these inequalities are robust to noise}
-    \note[item]{Finding maximally violating distributions}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Example Inequality}
-    \begin{itemize}
-        \item Quick example/preview:
-    \end{itemize}
-    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
-    \begin{itemize}
-        \item $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
-        \item Four outcomes for each $A, B, C$
-        \item Polynomial in $\prob[ABC]$, marginals $\prob[AB]$, $\prob[BC]$, $\prob[AC]$, $\prob[A]$, $\prob[B]$, $\prob[C]$
-    \end{itemize}
-    \note[item]{As a quick example or preview of what is to come, here is a an example inequality admits quantum violations in the triangle scenario}
-    \note[item]{Some features of note: inequality is polynomial in $\prob[ABC]$ and its marginals}
-\end{frame}
-
-% \begin{frame}
-%     \frametitle{Notation}
-%     \begin{itemize}
-%         \item A subset of $V \subset \jointvar$ is a \term{marginal context}
-%         \item Restrict focus to \textit{maximal} marginal scenario where only the largest contexts are present
-%         \[ \forall V_i, V_j \in \mscenario : V_i \not \subset V_j \]
-%     \end{itemize}
-% \end{frame}
-
-\begin{frame}
-    \frametitle{Notation}
-    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
-    \begin{itemize}
-        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
-        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
-        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
-        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        % \item Marginal scenario forms a \textit{simplicial complex}
-        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
-        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
-        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
-    \end{itemize}
-    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
-    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
-    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
-    \note[item]{Marginal scenario refers to the those sets of random variables}
-    \note[item]{The complete set of random variables are the joint random variables}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Graph Theory [Optional]}
-    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
-    \begin{itemize}
-        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
-        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
-        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
-        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
-    \end{itemize}
-    Notation extends to sets of nodes $N \subseteq \nodes$,
-    \begin{itemize}
-        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
-        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
-        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
-    \end{itemize}
-    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
-    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
+    \note[item]{This talk is going to have three components}
+    \note[item]{Demonstrating how something called the inflation technique allows one derive polynomial compatibility constraints for and causal structure}
+    \note[item]{Using the inflation technique to find inequalities that demonstrate non-local quantum distributions on the Triangle scenario}
 \end{frame}
@@
     \frametitle{Causal Compatibility}
-    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
-    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
-    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
-    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
-    \begin{enumerate}
-        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
-        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
-    \end{enumerate}
-    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
+    \vfill
+    \begin{center}
+        Triangle Scenario
+    \end{center}
+    \[ \prob[ABC] = \int_{XYZ}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
+    \vfill
+    \begin{center}
+        \noindent\rule{8cm}{0.4pt}
+    \end{center}
+    \vfill
+    \begin{center}
+        General Setting
+    \end{center}
+    \[ \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \qquad \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
+    \vfill
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Deriving Inequalities}
-    Two necessary components to compatibility:
-    \begin{enumerate}
-        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
-        \begin{itemize}
-            \item Is the marginal model contextual or non-contextual?
-            \item 3 distinct ways to tackle this problem
-            \begin{enumerate}
-                \item Convex hull, Polytope projection, Fourier-Motzkin
-                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
-                \item Linear Program Feasibility/Infeasibility
-            \end{enumerate}
-        \end{itemize}
-        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
-        \begin{itemize}
-            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
-            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
-        \end{itemize}
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Technique}
-    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
-    \begin{definition}
-        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
-        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
-        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
-        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
-        And '$\sim$' is a \term{copy-index} equivalence relation
-        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
-    \end{definition}
+    \frametitle{Demonstrating Inflation Technique}
+    \vfill
+    \begin{center}
+    \begin{columns}
+        \column{0.5\linewidth}%
+        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_1}}
+        \column{0.5\linewidth}%
+        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_1}}
+    \end{columns}
+    \end{center}
+    \only<1>{\[\forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n}\]}%
+    \only<2>{\[\AnSub[\graph]{A} \sim \AnSub[\graph']{A_1}\]}%
+    \only<3>{\[\AnSub[\graph]{C} \sim \AnSub[\graph']{C_2}\]}%
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Inflation Lemma}
-    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
-    \begin{enumerate}
-        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
-        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
-        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
-        \item Construct \term{inflated causal parameters}
-        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
-        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
-        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
-    \end{enumerate}
+    \frametitle{Injectable Sets}
+    \begin{center}
+    \begin{columns}
+        \column{0.5\linewidth}%
+        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_2}}
+        \column{0.5\linewidth}%
+        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_2}}
+    \end{columns}
+    \end{center}
+    \only<1>{\[\AnSub[\graph]{A,C} \sim \AnSub[\graph']{A_2,C_1}\]}%
+    \only<2>{\[?? \not \sim \AnSub[\graph']{B_1,B_2}\]}%
+    \only<3>{\[?? \not \sim \AnSub[\graph']{B_2,C_2}\]}%
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Inflation Lemma Cont'd}
-    \begin{itemize}
-        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $N \sim N'$
-        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
+    \frametitle{Injectable Sets Defined}
+    The \term{injectable sets in $\graph'$}:
     \begin{align*}
-            \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
-            \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'} \\
+        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
     \end{align*}
-        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $N \sim N'$
-        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $N \sim N'$
-    \end{itemize}
+    The \term{images of the injectable sets in $\graph$}:
+    \begin{align*}
+        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
+    \end{align*}
 \end{frame}
@@
 \begin{frame}
-    \frametitle{Inflation Lemma Cont'd}
-    \begin{lemma}
-        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-    \end{lemma}
-    \begin{corollary}
-        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
-    \end{corollary}
+    \frametitle{Perfect Correlation Is Incompatible}
+
 \end{frame}
@@
 \begin{frame}
-    \frametitle{$d$-Separation Polynomial}
+    \frametitle{Example Inequality}
     \begin{itemize}
-        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
-        \item \textbf{Linear inequality} for $\graph'$
+        \item Quick example/preview:
     \end{itemize}
-    \begin{center}
-        \begin{tikzpicture}[scale=0.8]
-            \pgfmathsetmacro{\hs}{1.8};
-            \pgfmathsetmacro{\vs}{1};
-            \pgfmathsetmacro{\cross}{0.3};
-            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
-            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
-            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
-            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
-            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
-            \draw (0, 0) node[](b){??};
-            \draw[thick, ] (a) -- (ab);
-            \draw[thick, ] (c) -- (cd);
-            \draw[thick, ] (a) -- (ac);
-            \draw[thick, ->] (ac) -- (c);
-            \draw[thick, ->] (ab) -- (b);
-            \draw[thick, ->] (cd) -- (d);
-            \draw[very thick, red]
-            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
-            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
-            ;
-        \end{tikzpicture}
-    \end{center}
+    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
     \begin{itemize}
-        \item \textbf{Polynomial inequality} for $\graph$!
+        \item $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
+        \item Four outcomes for each $A, B, C$
+        \item Polynomial in $\prob[ABC]$, marginals $\prob[AB]$, $\prob[BC]$, $\prob[AC]$, $\prob[A]$, $\prob[B]$, $\prob[C]$
     \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Pre-injectable Sets}
-    \begin{itemize}
-        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
-        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
-        \item A \term{pre-injectable set} $N'$:
-        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
-        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
-        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
-    \end{itemize}
+    \note[item]{As a quick example or preview of what is to come, here is a an example inequality admits quantum violations in the triangle scenario}
+    \note[item]{Some features of note: inequality is polynomial in $\prob[ABC]$ and its marginals}
 \end{frame}
@@
     \begin{center}
-        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot.pdf}
+        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_bits_brazil.pdf}
     \end{center}
@@
 \begin{frame}
-    \frametitle{Fritz Distribution Course Graining CHSH [Optional]}
-    \begin{gather*}
-    \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
-    \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
-    \end{gather*}
+    \frametitle{Fritz Distribution Violating CHSH}
+    % \begin{gather*}
+    % \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
+    % \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
+    % \end{gather*}
     \begin{itemize}
         \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
-        \item Correlation coarse graining $\bc{0,1,2,3} \to \bc{\br{0,3}, \br{1,2}}$
+        \item Correlation between right bits
     \end{itemize}
-    \[ \ba{AB | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{AB | C = 3} = - \f{1}{\sqrt{2}} \]
+    \[ \ba{A_rB_r} = \prob[A_rB_r][00] + \prob[A_rB_r][11] - \prob[A_rB_r][01] - \prob[A_rB_r][10] \]
+    \[ \ba{A_rB_r | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{A_rB_r | C = 3} = - \f{1}{\sqrt{2}} \]
     \begin{itemize}
@@
     \end{itemize}
-    \[ \ba{AB|C=0} + \ba{AB|C=1} + \ba{AB|C=2} - \ba{AB|C=3} = 2\sqrt{2} \not \leq 2 \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Quantum Implementation of Fritz Distribution [Optional]}
-    \begin{itemize}
-        \item States:
-    \end{itemize}
-    \begin{gather*}
-        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
-    \end{gather*}
-    \begin{itemize}
-        \item Maximally entangled Bell states:
-    \end{itemize}
-    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
-    \begin{itemize}
-        \item Measurements:
-    \end{itemize}
-    \begin{gather*}
-        M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
-        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
-        M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
-    \end{gather*}
-    \begin{itemize}
-        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
-    \end{itemize}
+    \begin{align*}
+    &\ba{A_rB_r|C=0} + \ba{A_rB_r|C=1} + \ba{A_rB_r|C=2} - \ba{A_rB_r|C=3} \\
+    &\quad = 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} \\
+    &\quad = 2\sqrt{2} \not \leq 2
+    \end{align*}
 \end{frame}
@@
 
+\begin{frame}
+    \frametitle{Notation [Optional]}
+    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
+    \begin{itemize}
+        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
+        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
+        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
+        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
+        % \item Marginal scenario forms a \textit{simplicial complex}
+        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
+        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
+        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
+        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
+    \end{itemize}
+    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
+    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
+    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
+    \note[item]{Marginal scenario refers to the those sets of random variables}
+    \note[item]{The complete set of random variables are the joint random variables}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Graph Theory [Optional]}
+    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
+    \begin{itemize}
+        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
+        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
+        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
+        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
+    \end{itemize}
+    Notation extends to sets of nodes $N \subseteq \nodes$,
+    \begin{itemize}
+        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
+        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
+        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
+    \end{itemize}
+    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
+    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Causal Compatibility [Optional]}
+    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
+    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
+    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
+    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
+    \begin{enumerate}
+        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
+        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
+    \end{enumerate}
+    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
+\end{frame}
+
+\begin{frame}
+    \frametitle{Deriving Inequalities [Optional]}
+    Two necessary components to compatibility:
+    \begin{enumerate}
+        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
+        \begin{itemize}
+            \item Is the marginal model contextual or non-contextual?
+            \item 3 distinct ways to tackle this problem
+            \begin{enumerate}
+                \item Convex hull, Polytope projection, Fourier-Motzkin
+                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
+                \item Linear Program Feasibility/Infeasibility
+            \end{enumerate}
+        \end{itemize}
+        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
+        \begin{itemize}
+            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
+            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
+        \end{itemize}
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Technique [Optional]}
+    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
+    \begin{definition}
+        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
+        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
+        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
+        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
+        And '$\sim$' is a \term{copy-index} equivalence relation
+        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
+    \end{definition}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Lemma [Optional]}
+    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
+    \begin{enumerate}
+        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
+        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
+        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
+        \item Construct \term{inflated causal parameters}
+        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
+        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
+        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Lemma Cont'd [Optional]}
+    \begin{itemize}
+        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
+        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
+    \end{itemize}
+    \begin{align*}
+        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}} \\
+        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
+    \end{align*}
+    \begin{itemize}
+        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
+        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Lemma Cont'd [Optional]}
+    \begin{lemma}
+        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+    \end{lemma}
+    \begin{corollary}
+        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
+    \end{corollary}
+\end{frame}
+
+\begin{frame}
+    \frametitle{$d$-Separation Polynomial [Optional]}
+    \begin{itemize}
+        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
+        \item \textbf{Linear inequality} for $\graph'$
+    \end{itemize}
+    \begin{center}
+        \begin{tikzpicture}[scale=0.8]
+            \pgfmathsetmacro{\hs}{1.8};
+            \pgfmathsetmacro{\vs}{1};
+            \pgfmathsetmacro{\cross}{0.3};
+            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
+            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
+            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
+            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
+            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
+            \draw (0, 0) node[](b){??};
+            \draw[thick, ] (a) -- (ab);
+            \draw[thick, ] (c) -- (cd);
+            \draw[thick, ] (a) -- (ac);
+            \draw[thick, ->] (ac) -- (c);
+            \draw[thick, ->] (ab) -- (b);
+            \draw[thick, ->] (cd) -- (d);
+            \draw[very thick, red]
+            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
+            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
+            ;
+        \end{tikzpicture}
+    \end{center}
+    \begin{itemize}
+        \item \textbf{Polynomial inequality} for $\graph$!
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Pre-injectable Sets [Optional]}
+    \begin{itemize}
+        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
+        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
+        \item A \term{pre-injectable set} $N'$:
+        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
+        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
+        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Quantum Implementation of Fritz Distribution [Optional]}
+    \begin{itemize}
+        \item States:
+    \end{itemize}
+    \begin{gather*}
+        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
+    \end{gather*}
+    \begin{itemize}
+        \item Maximally entangled Bell states:
+    \end{itemize}
+    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
+    \begin{itemize}
+        \item Measurements:
+    \end{itemize}
+    \begin{gather*}
+        M_{A} = \bc{\ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}} \\
+        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
+        M_{C} = \bc{\ket{01}\bra{01}, \ket{11}\bra{11}, \ket{00}\bra{00}, \ket{10}\bra{10}}
+    \end{gather*}
+    \begin{itemize}
+        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
+    \end{itemize}
+\end{frame}
+
 \end{document}

### 2016-11-19 figures/causal_structures/inflated_triangle_scenario_spiral_anim_1.tex
Added some slides to the beginning, will finish slides while traveling

\newcommand{\ift}{2.3}
\begin{tikzpicture}[scale=2]
    \begin{scope}[every node/.style=observed, onslide=<2->{fade}]
        \node[onslide=<3>{unfade}] (C2) at ({-2 + 2*1/\ift}, {2*1/(\ift*sqrt(3))}) {$C_2$};
        \node (C1) at ({-2 + 3*1/\ift}, {3*1/(\ift*sqrt(3))}) {$C_1$};
        \node (B2) at ({2 - 2*1/\ift}, {2*1/(\ift*sqrt(3))}) {$B_2$};
        \node (B1) at ({2 - 3*1/\ift}, {3*1/(\ift*sqrt(3))}) {$B_1$};
        \node (A2) at (0, {2*sqrt(3) - 2*2/sqrt(3)*(1/\ift)}) {$A_2$};
        \node[onslide=<2>{unfade}] (A1) at (0, {2*sqrt(3) - 3*2/sqrt(3)*(1/\ift)}) {$A_1$};
    \end{scope}
    \begin{scope}[every node/.style=latent, onslide=<2->{fade}]
        \node[onslide=<3>{unfade}] (X2) at (-1, {sqrt(3)}) {$X_2$};
        \node[onslide=<2>{unfade}] (X1) at ({-1 + 1/\ift}, {sqrt(3) - 1/(\ift*sqrt(3))}) {$X_1$};
        \node (Y2) at (1, {sqrt(3)}) {$Y_2$};
        \node[onslide=<2>{unfade}] (Y1) at ({1 - 1/\ift}, {sqrt(3) - 1/(\ift*sqrt(3))}) {$Y_1$};
        \node[onslide=<3>{unfade}] (Z1) at (0, 0.5) {$Z_1$};
        \node (Z2) at (0, 0) {$Z_2$};
    \end{scope}
    \begin{scope}[every path/.style={draw=cause, thick}, onslide=<2->{fade}]
        \path[postaction={on each segment={mid arrow}}]
        (Y1) -- (B1) (Y1) -- (B2) (Z1) -- (B1) (Z2) -- (B2)
        ;
        \path[postaction={on each segment={mid arrow}}]
        (X1) -- (A2) (X1) -- (C1) (Z1) -- (C1) (Y2) -- (A2)
        ;
        \path[postaction={on each segment={mid arrow}}, onslide=<3>{unfade}]
        (X2) -- (C2) (Z1) -- (C2)
        ;
        \path[postaction={on each segment={mid arrow}}, onslide=<2>{unfade}]
        (Y1) -- (A1) (X1) -- (A1)
        ;
    \end{scope}
\end{tikzpicture}

### 2016-11-19 figures/causal_structures/inflated_triangle_scenario_spiral_anim_2.tex
Added some slides to the beginning, will finish slides while traveling

\newcommand{\ift}{2.3}
\begin{tikzpicture}[scale=2]
    \begin{scope}[every node/.style=observed, onslide=<1->{fade}]
        \node[onslide=<3>{unfade}] (C2) at ({-2 + 2*1/\ift}, {2*1/(\ift*sqrt(3))}) {$C_2$};
        \node[onslide=<1>{unfade}] (C1) at ({-2 + 3*1/\ift}, {3*1/(\ift*sqrt(3))}) {$C_1$};
        \node[onslide=<2>{unfade},onslide=<3>{unfade}] (B2) at ({2 - 2*1/\ift}, {2*1/(\ift*sqrt(3))}) {$B_2$};
        \node[onslide=<2>{unfade}] (B1) at ({2 - 3*1/\ift}, {3*1/(\ift*sqrt(3))}) {$B_1$};
        \node[onslide=<1>{unfade}] (A2) at (0, {2*sqrt(3) - 2*2/sqrt(3)*(1/\ift)}) {$A_2$};
        \node[] (A1) at (0, {2*sqrt(3) - 3*2/sqrt(3)*(1/\ift)}) {$A_1$};
    \end{scope}
    \begin{scope}[every node/.style=latent, onslide=<1->{fade}]
        \node[onslide=<3>{unfade}] (X2) at (-1, {sqrt(3)}) {$X_2$};
        \node[onslide=<1>{unfade}] (X1) at ({-1 + 1/\ift}, {sqrt(3) - 1/(\ift*sqrt(3))}) {$X_1$};
        \node[onslide=<1>{unfade}] (Y2) at (1, {sqrt(3)}) {$Y_2$};
        \node[onslide=<2>{unfade}, onslide=<3>{unfade}] (Y1) at ({1 - 1/\ift}, {sqrt(3) - 1/(\ift*sqrt(3))}) {$Y_1$};
        \node[onslide=<1>{unfade}, onslide=<2>{unfade}, onslide=<3>{unfade}] (Z1) at (0, 0.5) {$Z_1$};
        \node[onslide=<2>{unfade}, onslide=<3>{unfade}] (Z2) at (0, 0) {$Z_2$};
    \end{scope}
    \begin{scope}[every path/.style={draw=cause, thick}, onslide=<1->{fade}]
        \path[postaction={on each segment={mid arrow}}, onslide=<2>{unfade}, onslide=<3>{unfade}]
        (Y1) -- (B2) (Z2) -- (B2)
        ;
        \path[postaction={on each segment={mid arrow}}, onslide=<2>{unfade}]
        (Y1) -- (B1) (Z1) -- (B1)
        ;
        \path[postaction={on each segment={mid arrow}}, onslide=<1>{unfade}]
        (X1) -- (A2) (X1) -- (C1) (Z1) -- (C1) (Y2) -- (A2)
        ;
        \path[postaction={on each segment={mid arrow}}, onslide=<3>{unfade}]
        (X2) -- (C2) (Z1) -- (C2)
        ;
        \path[postaction={on each segment={mid arrow}}, ]
        (Y1) -- (A1) (X1) -- (A1)
        ;
    \end{scope}
\end{tikzpicture}

### 2016-11-19 figures/causal_structures/triangle_scenario_anim_1.tex
Added some slides to the beginning, will finish slides while traveling

\begin{tikzpicture}[scale=1]
    \begin{scope}[every node/.style=observed, onslide=<2->{fade}]
        \node[onslide=<3>{unfade}] (C) at (-2, 0) {$C$};
        \node (B) at (2, 0) {$B$};
        \node[onslide=<2>{unfade}] (A) at (0, {2*sqrt(3)}) {$A$};
    \end{scope}
    \begin{scope}[every node/.style=latent, onslide=<2->{fade}]
        \node[onslide=<2-3>{unfade}] (X) at (-1, {sqrt(3)}) {$X$};
        \node[onslide=<2>{unfade}] (Y) at (1, {sqrt(3)}) {$Y$};
        \node[onslide=<3>{unfade}] (Z) at (0, 0) {$Z$};
    \end{scope}
    \begin{scope}[every path/.style={draw=cause, thick}, onslide=<2->{fade}]
        \path[postaction={on each segment={mid arrow}}]
        (Y) -- (B)
        (Z) -- (B)
        ;
        \path[postaction={on each segment={mid arrow}}, onslide=<3>{unfade}]
        (X) -- (C)
        (Z) -- (C)
        ;
        \path[postaction={on each segment={mid arrow}}, onslide=<2>{unfade}]
        (X) -- (A)
        (Y) -- (A)
        ;
    \end{scope}
\end{tikzpicture}

### 2016-11-19 figures/causal_structures/triangle_scenario_anim_2.tex
Added some slides to the beginning, will finish slides while traveling

\begin{tikzpicture}[scale=1]
    \draw[red,scale=2, transform shape, onslide=<1>{opacity=0}, onslide=<2>{unfade}] (0,{0.7}) node{\textbf{\Huge ?}};
    \begin{scope}[every node/.style=observed, onslide=<1->{fade}]
        \node[onslide=<1>{unfade}] (C) at (-2, 0) {$C$};
        \node (B) at (2, 0) {$B$};
        \node[onslide=<1>{unfade}] (A) at (0, {2*sqrt(3)}) {$A$};
    \end{scope}
    \begin{scope}[every node/.style=latent, onslide=<1->{fade}]
        \node[onslide=<1>{unfade}] (X) at (-1, {sqrt(3)}) {$X$};
        \node[onslide=<1>{unfade}] (Y) at (1, {sqrt(3)}) {$Y$};
        \node[onslide=<1>{unfade}] (Z) at (0, 0) {$Z$};
    \end{scope}
    \begin{scope}[every path/.style={draw=cause, thick}, onslide=<1->{fade}]
        \path[postaction={on each segment={mid arrow}}]
        (Y) -- (B)
        (Z) -- (B)
        ;
        \path[postaction={on each segment={mid arrow}}, onslide=<1>{unfade}]
        (X) -- (C)
        (Z) -- (C)
        ;
        \path[postaction={on each segment={mid arrow}}, onslide=<1>{unfade}]
        (X) -- (A)
        (Y) -- (A)
        ;
    \end{scope}
\end{tikzpicture}

### 2016-11-21 documents/BrazilSlides/slides.tex
Started work on perfect correlations witnessing
Some more progress on the perfect correlation example
Added more the slides, much closer to how we discussed

@@
 \usecolortheme{default} % Color Theme
+\usepackage{lmodern} % Optional to remove font size warnings
 
@@
 \AtBeginNote{\scriptsize} % Make notes small
-\setbeameroption{show notes} % Shows notes
+% \setbeameroption{show notes} % Shows notes
 % \setbeameroption{show only notes} % Shows only notes
@@
 
+\AtBeginSection[]{
+  \begin{frame}
+  \vfill
+  \centering
+  \begin{beamercolorbox}[sep=16pt,center]{title}
+    \usebeamerfont{title}\insertsectionhead\par%
+  \end{beamercolorbox}
+  \vfill
+  \end{frame}
+}
+
 \usepackage{silence}
@@
 \AtBeginBibliography{\small}
+
+\newcommand{\probplotvalue}[1]{%
+    \definecolor{probvalcolor}{RGB}{#1}%
+    \definecolor{outlinecolor}{RGB}{127, 127, 127}%
+    \begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]%
+        \pgfmathsetmacro{\size}{0.2};%
+        \draw[outlinecolor, fill=probvalcolor] (-\size,-\size) -- (-\size, +\size) -- (+\size, +\size) -- (+\size, -\size) -- cycle;%
+    \end{tikzpicture}%
+}%
 
@@
     \end{center}
-    \[ \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \qquad \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
-    \vfill
-\end{frame}
-
+    \begin{align*}
+    \mscenario &= \bc{V_1, \ldots, V_n} \\
+    \prob^{\mscenario} &= \bc{\prob[V_1], \ldots, \prob[V_n]}
+    \end{align*}
+    \[ \forall V \in \mscenario: \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \]
+    \[ \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
+    \vfill
+\end{frame}
+
+\section{Part 1: Inflation Technique}
 \begin{frame}
@@
 \begin{frame}
-    \frametitle{Injectable Sets}
+    \frametitle{What are Injectable Sets?}
     \begin{center}
@@
     \frametitle{Injectable Sets Defined}
+    \vfill
     The \term{injectable sets in $\graph'$}:
@@
     \end{align*}
+    \vfill
+    \begin{center}
+        \textbf{What makes injectable sets useful?}
+    \end{center}
+    \vfill
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Lemma}
+    \begin{lemma}[Inflation Lemma]
+    Given $\graph$ and inflation $\graph$':
+    \begin{center}
+        \begin{tikzpicture}
+            \pgfmathsetmacro{\vs}{2.2};
+            \pgfmathsetmacro{\hs}{5.2};
+            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
+            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
+            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
+            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
+            \draw[very thick, ->] (pn) -- (cp);
+            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
+            \draw[very thick, ->] (cp_) -- (pn_);
+        \end{tikzpicture}
+    \end{center}
+    \end{lemma}
 \end{frame}
@@
     \frametitle{Perfect Correlation Is Incompatible}
-
-\end{frame}
-
-\begin{frame}
-    \frametitle{Example Inequality}
-    \begin{itemize}
-        \item Quick example/preview:
-    \end{itemize}
-    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
-    \begin{itemize}
-        \item $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
-        \item Four outcomes for each $A, B, C$
-        \item Polynomial in $\prob[ABC]$, marginals $\prob[AB]$, $\prob[BC]$, $\prob[AC]$, $\prob[A]$, $\prob[B]$, $\prob[C]$
-    \end{itemize}
-    \note[item]{As a quick example or preview of what is to come, here is a an example inequality admits quantum violations in the triangle scenario}
-    \note[item]{Some features of note: inequality is polynomial in $\prob[ABC]$ and its marginals}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Pre-injectable Sets of Large Inflation}
+    \begin{columns}
+        \column{0.5\linewidth}
+        \begin{center}
+            \includegraphics[width=\linewidth]{../../figures/distributions/perfect_correlation_2_outcomes.pdf}
+        \end{center}
+        \column{0.5\linewidth}
+        \begin{align*}
+        \probplotvalue{0, 0, 0} &= \f12 \\
+        \prob[ABC][abc] &= \f{\bs{000} + \bs{111}}{2} \\
+        \prob[ABC][abc] &= \begin{cases}
+            \f12 & a = b = c \\
+            0 & \text{ otherwise }
+        \end{cases}
+        \end{align*}
+    \end{columns}
+    \begin{center}
+        Compatibility Inequality
+    \end{center}
+    \[ \prob[A][0]\prob[B][1] \leq \prob[BC][10] + \prob[AC][01] \]
+    \begin{center}
+        Witnesses Perfect Correlation
+    \end{center}
+    \[ \br{\f{1}{2}}^{2} \not\leq 0 + 0 \]
+\end{frame}
+\makeatletter
+\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
+  \hskip -\arraycolsep
+  \let\@ifnextchar\new@ifnextchar
+  \array{#1}}
+\makeatother
+\begin{frame}
+    \frametitle{Deriving Compatibility Inequalities}
+    \begin{center}
+        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
+    \end{center}
+    \[ \mscenario = \bc{\bc{A_1, B_1}, \bc{B_1, C_1}, \bc{A_1, C_1}} \]
+    \[ \prob^{\mscenario} = \bc{\prob[A_1B_1], \prob[B_1C_1], \prob[A_1C_1]} \]
+    \[ \text{Compatibility requires:} \qquad \exists \prob[\jointvar] = \prob[A_1B_1C_1] \]
+    \[ \prob[A_1B_1] = {\sum}_{C_1} \prob[\jointvar] \qquad \prob[B_1C_1] = {\sum}_{A_1} \prob[\jointvar] \qquad \prob[A_1C_1] = {\sum}_{B_1} \prob[\jointvar]\]
+\end{frame}
+
+\begin{frame}[shrink=13]
+    \frametitle{Deriving Compatibility Inequalities Cont'd}
+    \[ \underbrace{\prob[A_1B_1] = {\sum}_{C_1} \prob[\jointvar] \qquad \prob[B_1C_1] = {\sum}_{A_1} \prob[\jointvar] \qquad \prob[A_1C_1] = {\sum}_{B_1} \prob[\jointvar]} \]
+    \[ \underbrace{\forall V \in \mscenario: \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] }\]
+    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}  \]
+    \[ \probvec^{\mscenario} =
+        \begin{pmatrix}
+            \prob[A_1B_1][00] \\
+            \prob[A_1B_1][01] \\
+            \prob[A_1B_1][10] \\
+            \prob[A_1B_1][11] \\
+            \hline
+            \prob[B_1C_1][00] \\
+            \prob[B_1C_1][01] \\
+            \prob[B_1C_1][10] \\
+            \prob[B_1C_1][11] \\
+            \hline
+            \prob[A_1C_1][00] \\
+            \prob[A_1C_1][01] \\
+            \prob[A_1C_1][10] \\
+            \prob[A_1C_1][11] \\
+        \end{pmatrix}
+        \qquad
+        \probvec^{\jointvar} =
+        \begin{pmatrix}
+            \prob[A_1B_1C_1][000] \\
+            \prob[A_1B_1C_1][001] \\
+            \prob[A_1B_1C_1][010] \\
+            \prob[A_1B_1C_1][011] \\
+            \prob[A_1B_1C_1][100] \\
+            \prob[A_1B_1C_1][101] \\
+            \prob[A_1B_1C_1][110] \\
+            \prob[A_1B_1C_1][111] \\
+        \end{pmatrix}
+    \]
+\end{frame}
+
+\begin{frame}[shrink=15]
+    \frametitle{Incidence Example}
+    \[ M = \kbordermatrix{
+        (A_1,B_1,C_1) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
+        (A_1=0, B_1=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
+        (A_1=0, B_1=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
+        (A_1=1, B_1=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
+        (A_1=1, B_1=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
+        (B_1=0, C_1=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
+        (B_1=0, C_1=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
+        (B_1=1, C_1=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
+        (B_1=1, C_1=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
+        (A_1=0, C_1=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
+        (A_1=0, C_1=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
+        (A_1=1, C_1=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
+        (A_1=1, C_1=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
+    } \]
+    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}  \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Marginal Linear Program}
+    \begin{columns}[T]
+        \column{0.4\linewidth}%
+            \term{Marginal LP}:%
+            \begin{alignat*}{2}
+                & \text{minimize:} \quad&& \emptyset \tcdot x\\
+                & \text{subject to:} && \probvec^{\jointvar} \succeq 0 \\
+                & && M \tcdot \probvec^{\jointvar} = \probvec^{\mscenario} \\
+            \end{alignat*}%
+        \column{0.4\linewidth}%
+            \term{Dual Marginal LP}:%
+            \begin{alignat*}{2}
+                & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
+                & \text{subject to:} && y \tcdot M \succeq 0 \\
+            \end{alignat*}%
+    \end{columns}
+    \begin{itemize}
+        \item If $\probvec^{\jointvar}$ exists, then:
+        \[ y \tcdot M \tcdot \probvec^{\jointvar} = y \tcdot \probvec^{\mscenario} \geq 0  \]
+        \item If not, then $y$ is an \term{infeasibility certificate} which generates \term{infeasibility inequality}:
+        \[ y \tcdot \probvec^{\mscenario} \geq 0 \]
+        \item Most linear programing toolkits return certificates (\href[pdfnewwindow]{http://docs.mosek.com/8.0/pythonapi/optimizer-task-gety.html}{\textit{Mosek}}, \href[pdfnewwindow]{https://www.gurobi.com/documentation/6.5/refman/farkasdual.html}{\textit{Gurobi}}, \href[pdfnewwindow]{http://www-01.ibm.com/support/docview.wss?uid=swg21400058}{\textit{CPLEX}}, \href[pdfnewwindow]{http://cvxr.com/cvx/doc/basics.html\#dual-variables}{\textit{cvxr}}/\href[pdfnewwindow]{http://cvxopt.org/userguide/coneprog.html\#linear-cone-programs}{\textit{cvxopt}}.)
+    \end{itemize}
+    \note[item]{It is possible to derive non-contextuality inequalities from $M$ and a known incompatible distribution $\probvec^{\mscenario}$}
+    \note[item]{Note the null objective; the minimization objective is trivially always zero}
+    \note[item]{The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.}
+    \note[item]{If \textit{feasible}, then there exists a vector $x$ that is a valid joint distribution vector $\probvec^{\jointvar}$.}
+    \note[item]{Feasibility implies that $\probvec^{\jointvar} = x$.}
+    \note[item]{Infeasibility implies contextuality}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Deflating Inequalities}
+    \begin{columns}
+        \column{0.5\linewidth}
+            \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut_anim_1}}
+        \column{0.5\linewidth}
+            \vfill
+            \begin{center}
+            \[ \Inj[\graph]{\graph'} = \begin{Bmatrix}
+                \bc{A_1,C_1}\\ \bc{B_1,C_1}\\ \bc{A_1}\\ \bc{B_1}\\ \bc{C_1}
+            \end{Bmatrix} \]
+            \[ \bc{A_1, B_1} \not \in \Inj[\graph]{\graph'} \]
+            \end{center}
+            \vfill
+    \end{columns}
+    \[ \prob[A_1B_1][01] \leq \prob[B_1C_1][10] + \prob[A_1C_1][01] \]
+    \only<1>{\begin{center}\textbf{Can not deflate inequality!}\end{center}}
+    \only<2>{\begin{center}\textbf{However!}\end{center}}
+    \only<2>{\[ \AnSub[\graph']{A_1} \cap \AnSub[\graph']{B_1} = \emptyset \iff A_1 \ancestralindep B_1 \]}
+    \onslide<3->{\[ \prob[A_1][0]\prob[B_1][1] \leq \prob[B_1C_1][10] + \prob[A_1C_1][01] \]}
+    \onslide<4->{\[ \prob[A][0]\prob[B][1] \leq \prob[BC][10] + \prob[AC][01] \]}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Gives Polynomial Inequalities}
+    \begin{itemize}
+        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
+        \item \textbf{Linear inequality} for $\graph'$
+    \end{itemize}
+    \begin{center}
+        \begin{tikzpicture}[scale=0.8]
+            \pgfmathsetmacro{\hs}{1.8};
+            \pgfmathsetmacro{\vs}{1};
+            \pgfmathsetmacro{\cross}{0.3};
+            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
+            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
+            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
+            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
+            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
+            \draw (0, 0) node[](b){??};
+            \draw[thick, ] (a) -- (ab);
+            \draw[thick, ] (c) -- (cd);
+            \draw[thick, ] (a) -- (ac);
+            \draw[thick, ->] (ac) -- (c);
+            \draw[thick, ->] (ab) -- (b);
+            \draw[thick, ->] (cd) -- (d);
+            \draw[very thick, red]
+            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
+            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
+            ;
+        \end{tikzpicture}
+    \end{center}
+    \begin{itemize}
+        \item \textbf{Polynomial inequality} for $\graph$!
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Pre-injectable Sets}
+    A \term{pre-injectable set} $N'$ is:
+    \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
+    \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
+    Only need to consider \term{maximal pre-injectable sets} denoted $\PreInj[\graph]{\graph'}$
+\end{frame}
+
+\section{Quantum Non-locality From Inflation}
+
+\begin{frame}
+    \frametitle{Quantum Correlation}
+    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
+    \begin{center}
+        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Distribution}
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_bits_brazil.pdf}
+    \end{center}
+    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Quantum Implementation of Fritz Distribution}
+    \begin{itemize}
+        \item States:
+    \end{itemize}
+    \begin{gather*}
+        \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \quad \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2}
+    \end{gather*}
+    \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
+    \begin{itemize}
+        \item Measurements:
+    \end{itemize}
+    \begin{gather*}
+        M_{A} = \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
+        M_{B} = \bc{\ket{0\psi_{6}}\bra{0\psi_{6}}, \ket{0\psi_{2}}\bra{0\psi_{2}}, \ket{1\psi_{0}}\bra{1\psi_{0}}, \ket{1\psi_{4}}\bra{1\psi_{4}}} \\
+        M_{C} = \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
+    \end{gather*}
+    \begin{itemize}
+        \item Shorthand: $\ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}}$
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Distribution Violating CHSH}
+    % \begin{gather*}
+    % \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
+    % \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
+    % \end{gather*}
+    \begin{itemize}
+        \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
+        \item Correlation between right bits
+    \end{itemize}
+    \[ \ba{A_rB_r} = \prob[A_rB_r][00] + \prob[A_rB_r][11] - \prob[A_rB_r][01] - \prob[A_rB_r][10] \]
+    \[ \ba{A_rB_r | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{A_rB_r | C = 3} = - \f{1}{\sqrt{2}} \]
+    \begin{itemize}
+        \item Gives CHSH violation
+    \end{itemize}
+    \begin{align*}
+    &\ba{A_rB_r|C=0} + \ba{A_rB_r|C=1} + \ba{A_rB_r|C=2} - \ba{A_rB_r|C=3} \\
+    &\quad = 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} \\
+    &\quad = 2\sqrt{2} \not \leq 2
+    \end{align*}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Notes on Fritz Distribution}
+    \begin{itemize}
+        \item Incompatibility proof contingent on perfect correlation between $C$ and pseudo-settings
+        \item Proof not robust to noise
+    \end{itemize}
+    \begin{problem}[2.17 in \cite{Fritz_2012}]
+        Find an example of non-classical quantum correlations in TS together with a proof of its non-classicality which does not hinge on Bell’s Theorem.
+    \end{problem}
+    \begin{itemize}
+        \item ``...would be helpful to have inequalities...''
+        % \item Possible to find inequalities violated by $\prob[F]$ using the Large inflation of the TS
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Large Inflation}
     \begin{center}
@@
     \end{center}
-    \begin{itemize}
-        \item Has $12$ maximal pre-injectable sets (to follow)
-    \end{itemize}
 \end{frame}
@@
 
-\begin{frame}
-    \frametitle{Deriving Inequalities}
-    \begin{itemize}
-        \item Inflation facilitates turning linear, inflated inequalities into polynomial deflated ones
-        \item \textbf{Question:} How to derive compatibility inequalities for $\graph'$?
-        \item \textbf{Answer:} Use your favorite technique for deriving compatibility inequalities:
-        \begin{itemize}
-            \item Entropic inequalities
-            \item Finite outcome inequalities
-        \end{itemize}
-        \item Here we solve the marginal problem for $\mscenario = \PreInj[\graph]{\graph'}$
-        \item First some notation and formalism
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Outcomes and Events}
+% \begin{frame}
+%     \frametitle{Deriving Inequalities}
+%     \begin{itemize}
+%         \item Inflation facilitates turning linear, inflated inequalities into polynomial deflated ones
+%         \item \textbf{Question:} How to derive compatibility inequalities for $\graph'$?
+%         \item \textbf{Answer:} Use your favorite technique for deriving compatibility inequalities:
+%         \begin{itemize}
+%             \item Entropic inequalities
+%             \item Finite outcome inequalities
+%         \end{itemize}
+%         \item Here we solve the marginal problem for $\mscenario = \PreInj[\graph]{\graph'}$
+%         \item First some notation and formalism
+%     \end{itemize}
+% \end{frame}
+
+\begin{frame}
+    \frametitle{Large Inflation Incidence}
+    \begin{itemize}
+        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
+        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
+        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
+        \item Inequalities violated by Fritz distribution are inherently $4$-outcome
+        \item Incidence matrix $M$ is \textbf{very large} $\sim 2.25 \textsf{Gb}$
+        \begin{itemize}
+            \item $\# \text{Columns} = 4^{12} = 16,777,216$
+            \item $\# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896$
+            \item $\# \text{Non-zero Entries} = 201,326,592$
+        \end{itemize}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Certificate for Fritz Distribution}
+    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
+    \vfill
+    \textbf{Note:} $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
+\end{frame}
+
+\begin{frame}[shrink=60]
+    \frametitle{Party Symmetric Inequality}
+    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
+\end{frame}
+
+\section{Maximal Violations \& Noise}
+
+\begin{frame}
+    \frametitle{Numerical Optimization}
+    Minimize objective function $f\br{\la} \in \R$:
+    \begin{enumerate}
+        \item Real-valued parameters $\la = \br{\la_0, \ldots, \la_n}$
+        \item Quantum states/measurements $\rho_{AB}, \rho_{BC}, \rho_{CA}, M_{A}, M_{B}, M_{C}$
+    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
+        \item Distribution $\prob[ABC]$
+        \item Plug into inequality $I$ in homogeneous form $I\br{\prob[ABC]} \geq 0$
+        \item Output is objective value $I\br{\prob[ABC]}$
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Numerical Optimization Methods}
+    \begin{itemize}
+        \item Numerical minimization of $f\br{\la}$
+        \[ f(\la_{(k+1)}) = \la_{(k)} - \ga_{(k)} \del f(\la_{(k)})  \]
+        \item Non-convex, non-linear, smooth/continuous
+        \item Gradient Descent, BFGS Method, Nelder-Mead simplex method
+        \item Stochastic methods: simulated annealing, basin-hopping
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Parameterizing Unitary Group}
+    \begin{itemize}
+        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} demonstrate a parameterization of $\s{U}\br{d}$ where the parameters are organized in a $d \times d$-matrix of real values $\la_{n,m}$
+        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n} RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}} \]
+        \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
+        \item Relative Phase Terms: $RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$
+        \item Rotation Terms: $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
+        \item Projection Operators: $P_l = \ket{l}\bra{l}$
+        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
+        \item Parameters $\la_{n,m} \in \bs{0, 2\pi}$
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Parameterizing Unitary Group Cont'd}
+    \begin{itemize}
+        \item Each parameter $\la_{n,m}$ has physical interpretation
+        \item Degeneracies are easily eliminated such as global phase
+        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = \ident \]
+        \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
+        \item Computationally efficient
+        \begin{alignat*}{2}
+            GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
+            RP_{n,m} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
+            R_{m,n} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
+            & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\
+        \end{alignat*}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Parameterizing States}
+    \begin{itemize}
+        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite qubit state acting on $\Hilb^{d/2} \otimes \Hilb^{d/2}$
+        \item $d \times d$ positive semi-definite (PSD) hermitian matrices with unitary trace
+        \item \term{Cholesky Parametrization} allows one to write any hermitian PSD as $\rho = T^{\dagger} T$
+        \item For $d = 4$:
+        \[ T = \begin{bmatrix}\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}\end{bmatrix} \]
+        \item $d^2$ real-valued parameters
+        \item Normalized $\rho = {T^{\dagger}T}/{\Tr\br{T^{\dagger} T}}$ adds degeneracy
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Parameterizing States Cont'd}
+    \begin{itemize}
+        \item \term{SHH parameterization} \cite{Spengler_2010_Unitary} exploits spectral decomposition; for rank $k \leq d$ density matrix
+        \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i} \bra{\psi_i} \qquad p_i \geq 0, \sum_i p_i = 1 \]
+        \item Orthonormal $k$-element sub-basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into computational basis $\bc{\ket{i}}$ by unitary $U \in \s{U}\br{d}$ such that $\ket{\psi_i} = U \ket{i}$
+        \item Freedom to choice $k$
+        \item Parameterize $\rho$ through $\bc{p_i}$ and $\ti{U}_{k}$
+        \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
+        \item real-value parameters $d^2 - \br{d-k}^2 - k$ for $\ti{U}_{k}$, $k-1$ for $\bc{p_i}$ (no degeneracy)
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Parameterizing POVMs}
+    \begin{itemize}
+        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
+        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
+        \item $n$-outcome measurement
+        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
+        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
+        \item Warrants consideration of \term{projective-valued measures (PVMs)}
+    \end{itemize}
+    \note<1>[item]{Naimark's Dilation Theorem}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Parameterizing PVMs}
+    \begin{itemize}
+        \item Each party $\br{A, B, C}$ is assigned $n$-outcome $\br{M_A, M_B, M_C}$ such that,
+        \[ M_{\chi,i}M_{\chi,j} = \de_{ij} M_{\chi, i} \quad M_{\chi, i} = \ket{m_{\chi,i}}\bra{m_{\chi,i}} \]
+        \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
+        \item Use unitary transformation again
+        \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
+        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $n(2d - n - 1)$ real-valued parameters\
+        \item PVMs are computationally more efficient
+    \end{itemize}
+    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Uniform Noise}
+    \[ \s{U}_{\varepsilon}\br{P} = \br{1 + \varepsilon} P + \varepsilon \s{U} \]
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/distributions/uniform_dist_plot.pdf}
+    \end{center}
+    \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
+    % \begin{center}
+    %     \begin{tikzpicture}
+    %         \pgfmathsetmacro{\ts}{0.5}; % term spacing
+    %         \draw[] (0*\ts,0) node[]{$P_\varepsilon$};
+    %         \draw[] (1*\ts,0) node[]{$=$};
+    %         \draw[] (2*\ts,0) node[]{$(1-\varepsilon)P_{F}$};
+    %         \draw[] (3*\ts,0) node[]{$+$};
+    %         \draw[] (4*\ts,0) node[]{$\delta$};
+    %     \end{tikzpicture}
+    % \end{center}
+\end{frame}
+\begin{frame}
+    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Maximally Violating Distributions}
+    \begin{itemize}
+        \item Able to out-perform violation provided by Fritz distribution
+        \item Maximally-violating states are not maximally-entangled; similar to detection loop-hole example of \cite{Methot_2006}
+        \item Violation very sensitive to the initial parameters $\la_{(0)}$
+        \item Both symmetric and asymmetric inequalities exhibit same qualitative features
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Conclusions}
+    \begin{itemize}
+        \item New causal compatibility inequalities have been found for the TS
+        \item Inflation technique capable of producing inequalities with quantum/classical witnesses
+        \item Proof of non-classicality is robust to noise
+        \item Fritz witness-able by party symmetric inequalities
+        \item Maximally violating distributions are different than Fritz but also similar
+        \item Further research is necessary
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Postdoc Opportunities At The Perimeter Institute}
+    \begin{center}
+    \textbf{Two Postdoctoral Fellowships in Quantum Foundations at the Perimeter Institute} \\
+    Project: \textit{Quantum Causal Structures} \\
+    \vfill
+    \begin{itemize}
+        \item How to define quantum causal models
+        \item Quantum causal inference
+        \item How to provide causal explanations of Bell inequality violations
+        \item Exploring the possibilities for indefinite causal structure
+    \end{itemize}
+    \vfill
+    {\scriptsize Application \& Info:}\\
+
+    The Perimeter Website $\to$ Research $\to$ Careers $\to$ Positions $\to$ Quantum Causal Structures Postdoctoral Fellowship
+    \textcolor{blue}{\url{https://www.perimeterinstitute.ca/2016/17-quantum-causal-structures-postdoctoral-fellowship}}
+    \vfill
+
+    {\scriptsize Funded by the John Templeton Foundation}
+    \end{center}
+
+\end{frame}
+
+\begin{frame}[allowframebreaks]
+    \frametitle{References}
+    \printbibliography
+\end{frame}
+
+\section{Optional Slides}
+
+\begin{frame}
+    \frametitle{Notation [Optional]}
+    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
+    \begin{itemize}
+        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
+        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
+        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
+        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
+        % \item Marginal scenario forms a \textit{simplicial complex}
+        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
+        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
+        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
+        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
+    \end{itemize}
+    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
+    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
+    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
+    \note[item]{Marginal scenario refers to the those sets of random variables}
+    \note[item]{The complete set of random variables are the joint random variables}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Graph Theory [Optional]}
+    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
+    \begin{itemize}
+        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
+        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
+        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
+        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
+    \end{itemize}
+    Notation extends to sets of nodes $N \subseteq \nodes$,
+    \begin{itemize}
+        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
+        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
+        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
+    \end{itemize}
+    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
+    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Causal Compatibility [Optional]}
+    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
+    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
+    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
+    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
+    \begin{enumerate}
+        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
+        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
+    \end{enumerate}
+    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
+\end{frame}
+
+\begin{frame}
+    \frametitle{Deriving Inequalities [Optional]}
+    Two necessary components to compatibility:
+    \begin{enumerate}
+        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
+        \begin{itemize}
+            \item Is the marginal model contextual or non-contextual?
+            \item 3 distinct ways to tackle this problem
+            \begin{enumerate}
+                \item Convex hull, Polytope projection, Fourier-Motzkin
+                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
+                \item Linear Program Feasibility/Infeasibility
+            \end{enumerate}
+        \end{itemize}
+        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
+        \begin{itemize}
+            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
+            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
+        \end{itemize}
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Technique [Optional]}
+    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
+    \begin{definition}
+        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
+        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
+        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
+        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
+        And '$\sim$' is a \term{copy-index} equivalence relation
+        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
+    \end{definition}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Lemma [Optional]}
+    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
+    \begin{enumerate}
+        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
+        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
+        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
+        \item Construct \term{inflated causal parameters}
+        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
+        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
+        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Lemma Cont'd [Optional]}
+    \begin{itemize}
+        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
+        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
+    \end{itemize}
+    \begin{align*}
+        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}} \\
+        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
+    \end{align*}
+    \begin{itemize}
+        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
+        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Lemma Cont'd [Optional]}
+    \begin{lemma}
+        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+    \end{lemma}
+    \begin{corollary}
+        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
+    \end{corollary}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Pre-injectable Sets [Optional]}
+    \begin{itemize}
+        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
+        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
+        \item A \term{pre-injectable set} $N'$:
+        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
+        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
+        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Quantum Implementation of Fritz Distribution [Optional]}
+    \begin{itemize}
+        \item States:
+    \end{itemize}
+    \begin{gather*}
+        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
+    \end{gather*}
+    \begin{itemize}
+        \item Maximally entangled Bell states:
+    \end{itemize}
+    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
+    \begin{itemize}
+        \item Measurements:
+    \end{itemize}
+    \begin{gather*}
+        M_{A} = \bc{\ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}} \\
+        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
+        M_{C} = \bc{\ket{01}\bra{01}, \ket{11}\bra{11}, \ket{00}\bra{00}, \ket{10}\bra{10}}
+    \end{gather*}
+    \begin{itemize}
+        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Network Permutation Matrix [Optional]}
+    \begin{columns}
+        \column{0.6\linewidth}
+        \begin{itemize}
+            \item States and measurements in the Triangle Scenario are not aligned
+            \item Without $\netperm$, $\prob[ABC]$ would be separable
+            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
+            \item $\netperm$ is a $2^6 \times 2^6$ matrix
+            \item Shifts one qubit to the left
+        \end{itemize}
+        \column{0.4\linewidth}
+            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
+    \end{columns}
+    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Outcomes and Events [Optional]}
     \begin{definition}
@@
 \begin{frame}
-    \frametitle{Distribution Vectors}
+    \frametitle{Distribution Vectors [Optional]}
     \begin{definition}
@@
 \begin{frame}
-    \frametitle{Incidence Matrix}
+    \frametitle{Incidence Matrix [Optional]}
     \begin{itemize}
@@
 
-\begin{frame}[shrink=10]
-    \frametitle{Example}
-    Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{A,B,C}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{A,B}, \bc{B,C}, \bc{A,C}}$. The incidence matrix becomes:
-    \[ M = \kbordermatrix{
-        (A,B,C) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
-        (A=0, B=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
-        (A=0, B=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
-        (A=1, B=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
-        (A=1, B=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
-        (B=0, C=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
-        (B=0, C=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
-        (B=1, C=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
-        (B=1, C=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
-        (A=0, C=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
-        (A=0, C=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
-        (A=1, C=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
-        (A=1, C=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
-    } \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Marginal Linear Program}
-    \begin{itemize}
-        \item Obtain inequalities from incidence matrix $M$ and known incompatible distribution $\probvec^{\mscenario}$
-    \end{itemize}
-    \begin{columns}[T]
-        \column{0.4\linewidth}%
-            \term{Marginal LP}:%
-            \begin{alignat*}{2}
-                & \text{minimize:} \quad&& \emptyset \tcdot x\\
-                & \text{subject to:} && x \succeq 0 \\
-                & && M \tcdot x = \probvec^{\mscenario} \\
-            \end{alignat*}%
-        \column{0.4\linewidth}%
-            \term{Dual Marginal LP}:%
-            \begin{alignat*}{2}
-                & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
-                & \text{subject to:} && y \tcdot M \succeq 0 \\
-            \end{alignat*}%
-    \end{columns}
-    \begin{itemize}
-        \item $y$ is an \term{infeasibility certificate}:
-        \[ y \tcdot M \tcdot x = y \tcdot \probvec^{\mscenario} \geq 0  \]
-        \item \term{Infeasibility inequality}: $y \tcdot \probvec^{\mscenario} \geq 0$
-        \item Most linear programing toolkits return certificates (\href[pdfnewwindow]{http://docs.mosek.com/8.0/pythonapi/optimizer-task-gety.html}{\textit{Mosek}}, \href[pdfnewwindow]{https://www.gurobi.com/documentation/6.5/refman/farkasdual.html}{\textit{Gurobi}}, \href[pdfnewwindow]{http://www-01.ibm.com/support/docview.wss?uid=swg21400058}{\textit{CPLEX}}, \href[pdfnewwindow]{http://cvxr.com/cvx/doc/basics.html\#dual-variables}{\textit{cvxr}}/\href[pdfnewwindow]{http://cvxopt.org/userguide/coneprog.html\#linear-cone-programs}{\textit{cvxopt}}.)
-    \end{itemize}
-    \note[item]{It is possible to derive non-contextuality inequalities from $M$ and a known incompatible distribution $\probvec^{\mscenario}$}
-    \note[item]{Note the null objective; the minimization objective is trivially always zero}
-    \note[item]{The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.}
-    \note[item]{If \textit{feasible}, then there exists a vector $x$ that is a valid joint distribution vector $\probvec^{\jointvar}$.}
-    \note[item]{Feasibility implies that $\probvec^{\jointvar} = x$.}
-    \note[item]{Infeasibility implies contextuality}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Known Incompatible Distribution in The Triangle Scenario}
-    \cite{Fritz_2012} provides quantum-accessible distribution incompatible with TS
-    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
-    \begin{center}
-        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
-    \end{center}
-\end{frame}
-
-\newcommand{\probplotvalue}[1]{%
-    \definecolor{probvalcolor}{RGB}{#1}%
-    \definecolor{outlinecolor}{RGB}{127, 127, 127}%
-    \begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]%
-        \pgfmathsetmacro{\size}{0.2};%
-        \draw[outlinecolor, fill=probvalcolor] (-\size,-\size) -- (-\size, +\size) -- (+\size, +\size) -- (+\size, -\size) -- cycle;%
-    \end{tikzpicture}%
-}%
-
-\begin{frame}
-    \frametitle{Fritz Distribution}
-    \begin{center}
-        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_bits_brazil.pdf}
-    \end{center}
-    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Distribution Violating CHSH}
-    % \begin{gather*}
-    % \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
-    % \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
-    % \end{gather*}
-    \begin{itemize}
-        \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
-        \item Correlation between right bits
-    \end{itemize}
-    \[ \ba{A_rB_r} = \prob[A_rB_r][00] + \prob[A_rB_r][11] - \prob[A_rB_r][01] - \prob[A_rB_r][10] \]
-    \[ \ba{A_rB_r | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{A_rB_r | C = 3} = - \f{1}{\sqrt{2}} \]
-    \begin{itemize}
-        \item Gives CHSH violation
-    \end{itemize}
-    \begin{align*}
-    &\ba{A_rB_r|C=0} + \ba{A_rB_r|C=1} + \ba{A_rB_r|C=2} - \ba{A_rB_r|C=3} \\
-    &\quad = 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} \\
-    &\quad = 2\sqrt{2} \not \leq 2
-    \end{align*}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Notes of Fritz Distribution}
-    \begin{itemize}
-        \item Proof contingent on perfect correlation between $C$ and pseudo-settings
-        \item Proof not robust to noise
-    \end{itemize}
-    \begin{problem}[2.17 in \cite{Fritz_2012}]
-        Find an example of non-classical quantum correlations in TS together with a proof of its non-classicality which does not hinge on Bell’s Theorem.
-    \end{problem}
-    \begin{itemize}
-        \item ``...would be helpful to have inequalities...''
-        \item Possible to find inequalities violated by $\prob[F]$ using the Large inflation of the TS
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Large Inflation Incidence}
-    \begin{itemize}
-        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
-        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
-        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
-        \item Inequalities violated by Fritz distribution are inherently $4$-outcome
-        \item Incidence matrix $M$ is \textbf{very large} $\sim 2.25 \textsf{Gb}$
-        \begin{itemize}
-            \item $\# \text{Columns} = 4^{12} = 16,777,216$
-            \item $\# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896$
-            \item $\# \text{Non-zero Entries} = 201,326,592$
-        \end{itemize}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Triangle Scenario Inequality}
-
-\end{frame}
-
-\begin{frame}
-    \frametitle{Causal Symmetry}
+\begin{frame}
+    \frametitle{Causal Symmetry [Optional]}
     \begin{itemize}
@@
 \begin{frame}
-    \frametitle{Causal Symmetry and Inflation}
+    \frametitle{Causal Symmetry and Inflation [Optional]}
     \begin{itemize}
@@
 \begin{frame}
-    \frametitle{Restricted Causal Symmetry of Large Inflation}
+    \frametitle{Restricted Causal Symmetry of Large Inflation [Optional]}
     \begin{itemize}
@@
 \begin{frame}
-    \frametitle{Symmetric Incidence}
+    \frametitle{Symmetric Incidence [Optional]}
     \begin{itemize}
@@
 
-\begin{frame}[shrink=60]
-    \frametitle{Party Symmetric Inequality}
-    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing Quantum Distributions}
-    For our purposes, we need to parameterize the space of quantum-accessible distributions that are \textit{realized} on the Triangle Scenario
-    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
-    \begin{center}
-        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
-    \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Numerical Optimization}
-    \begin{itemize}
-        \item Attempt to find new non-classical distributions
-        \item Objective function $f\br{\la} \in \R$
-        \begin{enumerate}
-            \item Real-valued parameters $\la = \br{\la_0, \ldots, \la_n}$
-            \item Quantum states/measurements $\rho_{AB}, \rho_{BC}, \rho_{CA}, M_{A}, M_{B}, M_{C}$
-            \item Distribution $\prob[ABC]$
-            \item Plug into inequality $I$ in homogeneous form $I\br{\prob[ABC]} \geq 0$
-            \item Output is objective value $I\br{\prob[ABC]}$
-        \end{enumerate}
-        \item Numerical minimization of $f\br{\la}$
-        \[ f(\la_{(k+1)}) = \la_{(k)} - \ga_{(k)} \del f(\la_{(k)})  \]
-        \item Non-convex, non-linear, smooth/continuous
-        \item Gradient Descent, BFGS Method, Nelder-Mead simplex method
-        \item Stochastic methods: simulated annealing, basin-hopping
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing Unitary Group}
-    \begin{itemize}
-        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} demonstrate a parameterization of $\s{U}\br{d}$ where the parameters are organized in a $d \times d$-matrix of real values $\la_{n,m}$
-        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n} RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}} \]
-        \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
-        \item Relative Phase Terms: $RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$
-        \item Rotation Terms: $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
-        \item Projection Operators: $P_l = \ket{l}\bra{l}$
-        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
-        \item Parameters $\la_{n,m} \in \bs{0, 2\pi}$
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing Unitary Group Cont'd}
-    \begin{itemize}
-        \item Each parameter $\la_{n,m}$ has physical interpretation
-        \item Degeneracies are easily eliminated such as global phase
-        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = \ident \]
-        \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
-        \item Computationally efficient
-        \begin{alignat*}{2}
-            GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
-            RP_{n,m} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
-            R_{m,n} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
-            & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\
-        \end{alignat*}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing States}
-    \begin{itemize}
-        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite qubit state acting on $\Hilb^{d/2} \otimes \Hilb^{d/2}$
-        \item $d \times d$ positive semi-definite (PSD) hermitian matrices with unitary trace
-        \item \term{Cholesky Parametrization} allows one to write any hermitian PSD as $\rho = T^{\dagger} T$
-        \item For $d = 4$:
-        \[ T = \begin{bmatrix}\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}\end{bmatrix} \]
-        \item $d^2$ real-valued parameters
-        \item Normalized $\rho = {T^{\dagger}T}/{\Tr\br{T^{\dagger} T}}$ adds degeneracy
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing States Cont'd}
-    \begin{itemize}
-        \item \term{SHH parameterization} \cite{Spengler_2010_Unitary} exploits spectral decomposition; for rank $k \leq d$ density matrix
-        \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i} \bra{\psi_i} \qquad p_i \geq 0, \sum_i p_i = 1 \]
-        \item Orthonormal $k$-element sub-basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into computational basis $\bc{\ket{i}}$ by unitary $U \in \s{U}\br{d}$ such that $\ket{\psi_i} = U \ket{i}$
-        \item Freedom to choice $k$
-        \item Parameterize $\rho$ through $\bc{p_i}$ and $\ti{U}_{k}$
-        \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
-        \item real-value parameters $d^2 - \br{d-k}^2 - k$ for $\ti{U}_{k}$, $k-1$ for $\bc{p_i}$ (no degeneracy)
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing POVMs}
-    \begin{itemize}
-        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
-        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
-        \item $n$-outcome measurement
-        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
-        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
-        \item Warrants consideration of \term{projective-valued measures (PVMs)} (for $n = d$ this is without loss of generality)
-    \end{itemize}
-    \note<1>[item]{Naimark's Dilation Theorem}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing PVMs}
-    \begin{itemize}
-        \item Each party $\br{A, B, C}$ is assigned $n$-outcome $\br{M_A, M_B, M_C}$ such that,
-        \[ M_{\chi,i}M_{\chi,j} = \de_{ij} M_{\chi, i} \quad M_{\chi, i} = \ket{m_{\chi,i}}\bra{m_{\chi,i}} \]
-        \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
-        \item Use unitary transformation again
-        \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
-        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $n(2d - n - 1)$ real-valued parameters\
-        \item PVMs are computationally more efficient
-    \end{itemize}
-    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Network Permutation Matrix}
-    \begin{columns}
-        \column{0.6\linewidth}
-        \begin{itemize}
-            \item States and measurements in the Triangle Scenario are not aligned
-            \item Without $\netperm$, $\prob[ABC]$ would be separable
-            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
-            \item $\netperm$ is a $2^6 \times 2^6$ matrix
-            \item Shifts one qubit to the left
-        \end{itemize}
-        \column{0.4\linewidth}
-            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
-    \end{columns}
-    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Results}
-    \begin{itemize}
-        \item Full rank $\rho, M$ gives $81$ free parameters
-        \[ \abs{\la} = 3 \cdot (12 + 3) + 3 \cdot 12 = 81 \]
-        \item Parameterization of quantum distributions still degenerate
+\section{Local Minima Concerns}
+
+\begin{frame}
+    \frametitle{Results [Optional]}
+    \begin{itemize}
+        \item Finding global minimum is tricky
+        \item Difficult to converge to violation
         \item Noisy seed (Gaussian noise):
@@
 \begin{frame}
-    \frametitle{Uniform Noise}
-    \[ \s{U}_{\varepsilon}\br{P} = \br{1 + \varepsilon} P + \varepsilon \s{U} \]
-    \begin{center}
-        \includegraphics[width=\linewidth]{../../figures/distributions/uniform_dist_plot.pdf}
-    \end{center}
-    \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
-    % \begin{center}
-    %     \begin{tikzpicture}
-    %         \pgfmathsetmacro{\ts}{0.5}; % term spacing
-    %         \draw[] (0*\ts,0) node[]{$P_\varepsilon$};
-    %         \draw[] (1*\ts,0) node[]{$=$};
-    %         \draw[] (2*\ts,0) node[]{$(1-\varepsilon)P_{F}$};
-    %         \draw[] (3*\ts,0) node[]{$+$};
-    %         \draw[] (4*\ts,0) node[]{$\delta$};
-    %     \end{tikzpicture}
-    % \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Local Minima}
+    \frametitle{Fritz Local Minima [Optional]}
     \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}
@@
 \begin{frame}
-    \frametitle{Fritz Local Minima Zoomed}
+    \frametitle{Fritz Local Minima Zoomed [Optional]}
     \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}
@@
 
-\begin{frame}
-    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Maximally Violating Distributions}
-    \begin{itemize}
-        \item Able to out-perform violation provided by Fritz distribution
-        \item Maximally-violating states are not maximally-entangled; similar to detection loop-hole example of \cite{Methot_2006}
-        \item Violation very sensitive to the initial parameters $\la_{(0)}$
-        \item Both symmetric and asymmetric inequalities exhibit same qualitative features
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Conclusions}
-    \begin{itemize}
-        \item New causal compatibility inequalities have been found for the TS
-        \item Inflation technique capable of producing inequalities with quantum/classical witnesses
-        \item Proof of non-classicality is robust to noise
-        \item Fritz witness-able by party symmetric inequalities
-        \item Maximally violating distributions are different than Fritz but also similar
-        \item Further research is necessary
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Post-doc Opportunities At Perimeter}
-\end{frame}
-
-\begin{frame}[allowframebreaks]
-    \frametitle{References}
-    \printbibliography
-\end{frame}
-
-\begin{frame}
-    \frametitle{Notation [Optional]}
-    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
-    \begin{itemize}
-        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
-        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
-        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
-        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        % \item Marginal scenario forms a \textit{simplicial complex}
-        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
-        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
-        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
-    \end{itemize}
-    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
-    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
-    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
-    \note[item]{Marginal scenario refers to the those sets of random variables}
-    \note[item]{The complete set of random variables are the joint random variables}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Graph Theory [Optional]}
-    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
-    \begin{itemize}
-        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
-        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
-        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
-        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
-    \end{itemize}
-    Notation extends to sets of nodes $N \subseteq \nodes$,
-    \begin{itemize}
-        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
-        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
-        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
-    \end{itemize}
-    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
-    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Causal Compatibility [Optional]}
-    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
-    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
-    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
-    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
-    \begin{enumerate}
-        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
-        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
-    \end{enumerate}
-    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
-\end{frame}
-
-\begin{frame}
-    \frametitle{Deriving Inequalities [Optional]}
-    Two necessary components to compatibility:
-    \begin{enumerate}
-        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
-        \begin{itemize}
-            \item Is the marginal model contextual or non-contextual?
-            \item 3 distinct ways to tackle this problem
-            \begin{enumerate}
-                \item Convex hull, Polytope projection, Fourier-Motzkin
-                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
-                \item Linear Program Feasibility/Infeasibility
-            \end{enumerate}
-        \end{itemize}
-        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
-        \begin{itemize}
-            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
-            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
-        \end{itemize}
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Technique [Optional]}
-    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
-    \begin{definition}
-        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
-        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
-        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
-        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
-        And '$\sim$' is a \term{copy-index} equivalence relation
-        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
-    \end{definition}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Lemma [Optional]}
-    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
-    \begin{enumerate}
-        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
-        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
-        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
-        \item Construct \term{inflated causal parameters}
-        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
-        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
-        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Lemma Cont'd [Optional]}
-    \begin{itemize}
-        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
-        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
-    \end{itemize}
-    \begin{align*}
-        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}} \\
-        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
-    \end{align*}
-    \begin{itemize}
-        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
-        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Lemma Cont'd [Optional]}
-    \begin{lemma}
-        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-    \end{lemma}
-    \begin{corollary}
-        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
-    \end{corollary}
-\end{frame}
-
-\begin{frame}
-    \frametitle{$d$-Separation Polynomial [Optional]}
-    \begin{itemize}
-        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
-        \item \textbf{Linear inequality} for $\graph'$
-    \end{itemize}
-    \begin{center}
-        \begin{tikzpicture}[scale=0.8]
-            \pgfmathsetmacro{\hs}{1.8};
-            \pgfmathsetmacro{\vs}{1};
-            \pgfmathsetmacro{\cross}{0.3};
-            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
-            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
-            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
-            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
-            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
-            \draw (0, 0) node[](b){??};
-            \draw[thick, ] (a) -- (ab);
-            \draw[thick, ] (c) -- (cd);
-            \draw[thick, ] (a) -- (ac);
-            \draw[thick, ->] (ac) -- (c);
-            \draw[thick, ->] (ab) -- (b);
-            \draw[thick, ->] (cd) -- (d);
-            \draw[very thick, red]
-            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
-            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
-            ;
-        \end{tikzpicture}
-    \end{center}
-    \begin{itemize}
-        \item \textbf{Polynomial inequality} for $\graph$!
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Pre-injectable Sets [Optional]}
-    \begin{itemize}
-        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
-        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
-        \item A \term{pre-injectable set} $N'$:
-        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
-        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
-        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Quantum Implementation of Fritz Distribution [Optional]}
-    \begin{itemize}
-        \item States:
-    \end{itemize}
-    \begin{gather*}
-        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
-    \end{gather*}
-    \begin{itemize}
-        \item Maximally entangled Bell states:
-    \end{itemize}
-    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
-    \begin{itemize}
-        \item Measurements:
-    \end{itemize}
-    \begin{gather*}
-        M_{A} = \bc{\ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}} \\
-        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
-        M_{C} = \bc{\ket{01}\bra{01}, \ket{11}\bra{11}, \ket{00}\bra{00}, \ket{10}\bra{10}}
-    \end{gather*}
-    \begin{itemize}
-        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
-    \end{itemize}
-\end{frame}
-
 \end{document}

### 2016-11-21 figures/causal_structures/inflated_triangle_scenario_cut_anim_1.tex
Added more the slides, much closer to how we discussed

\newcommand{\ift}{2.3}
\begin{tikzpicture}[scale=2]
    \begin{scope}[every node/.style=observed, onslide=<2->{fade}]
        \node (C1) at ({-2 + 3*1/\ift}, {3*1/(\ift*sqrt(3))}) {$C_1$};
        \node[onslide=<2->{unfade}] (B1) at ({2 - 3*1/\ift}, {3*1/(\ift*sqrt(3))}) {$B_1$};
        \node[onslide=<2->{unfade}] (A1) at (0, {2*sqrt(3) - 2*2/sqrt(3)*(1/\ift)}) {$A_1$};
    \end{scope}
    \begin{scope}[every node/.style=latent, onslide=<2->{fade}]
        \node[onslide=<2->{unfade}] (X1) at ({-1 + 1/\ift}, {sqrt(3) - 1/(\ift*sqrt(3))}) {$X_1$};
        \node[onslide=<2->{unfade}] (Y2) at (1, {sqrt(3)}) {$Y_2$};
        \node[onslide=<2->{unfade}] (Y1) at ({1 - 1/\ift}, {sqrt(3) - 1/(\ift*sqrt(3))}) {$Y_1$};
        \node[onslide=<2->{unfade}] (Z1) at (0, 0.5) {$Z_1$};
    \end{scope}
    \begin{scope}[every path/.style={draw=cause, thick}, onslide=<2->{fade}]
        \path[postaction={on each segment={mid arrow}}]
        (X1) -- (C1)
        (Z1) -- (C1)
        ;
        \path[postaction={on each segment={mid arrow}}, onslide=<2->{unfade}]
        (X1) -- (A1)
        (Y2) -- (A1)
        (Y1) -- (B1)
        (Z1) -- (B1)
        ;
    \end{scope}
\end{tikzpicture}

### 2016-11-21 documents/BrazilSlides/slides.tex
More progress, added noise plots normalized

@@
 \end{frame}
-
+\begin{frame}
+    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Maximally Violating Distributions}
+    \begin{itemize}
+        \item Able to out-perform violation provided by Fritz distribution
+        \item Maximally-violating states are not maximally-entangled; similar to detection loop-hole example of \cite{Methot_2006}
+        \item Both symmetric and asymmetric inequalities exhibit same qualitative features
+        % \item Violation very sensitive to the initial parameters $\la_{(0)}$
+    \end{itemize}
+\end{frame}
 \begin{frame}
     \frametitle{Uniform Noise}
-    \[ \s{U}_{\varepsilon}\br{P} = \br{1 + \varepsilon} P + \varepsilon \s{U} \]
+    \[ \s{U}_{\varepsilon}\br{P} = \br{1 - \varepsilon} P + \varepsilon \s{U} \]
     \begin{center}
@@
 \end{frame}
-\begin{frame}
-    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Maximally Violating Distributions}
-    \begin{itemize}
-        \item Able to out-perform violation provided by Fritz distribution
-        \item Maximally-violating states are not maximally-entangled; similar to detection loop-hole example of \cite{Methot_2006}
-        \item Violation very sensitive to the initial parameters $\la_{(0)}$
-        \item Both symmetric and asymmetric inequalities exhibit same qualitative features
-    \end{itemize}
+
+\begin{frame}
+    \frametitle{Robust to Noise}
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/noise/four_rep_inequalities_uniform_noise.pdf}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Robust to Noise Zoomed}
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/noise/four_rep_inequalities_uniform_noise_zoomed.pdf}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Noisy Non-locality}
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
+    \end{center}
+    \[ \probplotvalue{255, 255, 255} = 0.00133 \]
 \end{frame}
@@
     \frametitle{Conclusions}
-    \begin{itemize}
-        \item New causal compatibility inequalities have been found for the TS
-        \item Inflation technique capable of producing inequalities with quantum/classical witnesses
-        \item Proof of non-classicality is robust to noise
-        \item Fritz witness-able by party symmetric inequalities
-        \item Maximally violating distributions are different than Fritz but also similar
-        \item Further research is necessary
-    \end{itemize}
+    \begin{enumerate}
+        \item Inflation technique capable of producing polynomial inequalities with quantum/classical witnesses
+        \item Fritz witness-able by party-symmetric inequalities
+        \item Maximally violating distributions require non-maximally entangled states
+    \end{enumerate}
 \end{frame}
@@
         \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Quantum Implementation of Fritz Distribution [Optional]}
-    \begin{itemize}
-        \item States:
-    \end{itemize}
-    \begin{gather*}
-        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
-    \end{gather*}
-    \begin{itemize}
-        \item Maximally entangled Bell states:
-    \end{itemize}
-    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
-    \begin{itemize}
-        \item Measurements:
-    \end{itemize}
-    \begin{gather*}
-        M_{A} = \bc{\ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}} \\
-        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
-        M_{C} = \bc{\ket{01}\bra{01}, \ket{11}\bra{11}, \ket{00}\bra{00}, \ket{10}\bra{10}}
-    \end{gather*}
-    \begin{itemize}
-        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
     \end{itemize}

### 2016-11-21 documents/BrazilSlides/slides.tex
Added inequalities for talk

@@
 
+\begin{frame}[shrink=64]
+    \frametitle{Certificate for Fritz Distribution (Full)}
+    \begin{center}
+        \input{../../figures/inequalities/nosymwitness_ineq_print}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Party Symmetric Inequality}
+    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print_pretty}
+    \vfill
+    \textbf{Note:} $\bs{\prob[][113]\prob[][330]}_3$ shorthand sum over permutations:
+    \[ \prob[][113]\prob[][330] + \prob[][131]\prob[][303] + \prob[][311]\prob[][033] \]
+\end{frame}
+
 \begin{frame}[shrink=60]
-    \frametitle{Party Symmetric Inequality}
+    \frametitle{Party Symmetric Inequality (Full)}
     \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
@@
     \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Maximal Violation}
+    \includegraphics[width=\linewidth]{../../figures/distributions/plotted_dist_I_2_max_violation.pdf}
+    \[ \text{Relative Violation:} \qquad V_F = \f{\min_P\bc{I\br{P}}}{I\br{P_F}} \]
 \end{frame}
@@
 
+\begin{frame}
+    \frametitle{Symmetrized Fritz [Optional]}
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/distributions/symmetrized_fritz.pdf}
+    \end{center}
+    \begin{itemize}
+        \item More non-local yet not quantum-accessible
+        \item Quantum-accessible distributions form non-context set
+    \end{itemize}
+\end{frame}
+
 \section{Local Minima Concerns}

### 2016-11-25 documents/BrazilSlides/slides.tex
Changed Section Headers
Slight improvements to the slides

@@
 
-\section{Quantum Non-locality From Inflation}
+\section{Part 2: Quantum Non-locality From Inflation}
 
@@
 \begin{frame}
+    \frametitle{Triangle Scenario As Bell Scenario}
+    \begin{center}
+        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational_fritz_bell}}
+    \end{center}
+\end{frame}
+
+\begin{frame}
     \frametitle{Fritz Distribution}
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_brazil.pdf}
+    \end{center}
+    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Distribution Bit-Measurements}
     \begin{center}
@@
         M_{A} = \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
-        M_{B} = \bc{\ket{0\psi_{6}}\bra{0\psi_{6}}, \ket{0\psi_{2}}\bra{0\psi_{2}}, \ket{1\psi_{0}}\bra{1\psi_{0}}, \ket{1\psi_{4}}\bra{1\psi_{4}}} \\
+        M_{B} = \bc{\ket{\psi_{6}0}\bra{\psi_{6}0}, \ket{\psi_{2}0}\bra{\psi_{2}0}, \ket{\psi_{0}1}\bra{\psi_{0}1}, \ket{\psi_{4}1}\bra{\psi_{4}1}} \\
         M_{C} = \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
@@
     \begin{center}
-        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
+        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
     \end{center}
@@
 \begin{frame}
+    \frametitle{Symmetric Inequalities}
+    \begin{itemize}
+        \item Certificate inequalities are curated/constructed to witness violation of particular distribution
+        \item Above inequality not the best candidate to search for non-locality different than Fritz distribution
+        \item Perhaps one could obtain inequality that does not assign special preference to $C$
+        \item Desirable to find compatibility inequality $I$ such that
+        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
     \frametitle{Party Symmetric Inequality}
@@
 
-\section{Maximal Violations \& Noise}
+\section{Part 3: Maximal Violations \& Noise}
 
@@
 \begin{frame}
+    \frametitle{Quantum Model On Triangle Scenario}
+    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
+    \begin{center}
+        \scalebox{0.6}{\input{../../figures/causal_structures/triangle_scenario_operational}}
+    \end{center}
+    \begin{itemize}
+        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite \textbf{qubit} state acting on $\Hilb^{2} \otimes \Hilb^{2}$
+        \item Each party $\br{A, B, C}$ is assigned $4$-outcome PVM set $\br{M_A, M_B, M_C}$
+        \item Parameterized using unitary transformations $U \in \s{U}\br{4}$
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
     \frametitle{Parameterizing Unitary Group}
     \begin{itemize}
-        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} demonstrate a parameterization of $\s{U}\br{d}$ where the parameters are organized in a $d \times d$-matrix of real values $\la_{n,m}$
-        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n} RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}} \]
-        \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
-        \item Relative Phase Terms: $RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$
-        \item Rotation Terms: $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
+        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} parameterization of $\s{U}\br{d}$
+        \[ \la = \begin{pmatrix}
+            \textcolor{Blue}{\la_{1,1}} & \textcolor{OliveGreen}{\cdots} & \textcolor{OliveGreen}{\la_{1, d}} \\
+            \textcolor{Maroon}{\vdots} & \textcolor{Blue}{\ddots} & \textcolor{OliveGreen}{\vdots} \\
+            \textcolor{Maroon}{\la_{d,1}} & \textcolor{Maroon}{\cdots} & \textcolor{Blue}{\la_{d, d}} \\
+        \end{pmatrix} \]
+        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \textcolor{OliveGreen}{R_{m,n}} \textcolor{Maroon}{RP_{n,m}}}} \tcdot \bs{\prod_{l=1}^{d} \textcolor{Blue}{GP_{l}}} \]
+        \item Global Phase Terms: \textcolor{Blue}{$GP_{l} = \exp\br{iP_l \lambda_{l,l}}$}
+        \item Relative Phase Terms: \textcolor{Maroon}{$RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$}
+        \item Rotation Terms: \textcolor{OliveGreen}{$R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$}
         \item Projection Operators: $P_l = \ket{l}\bra{l}$
@@
         \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
-        \item Computationally efficient
+        % \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
+        \[ \ti{U} = \prod_{m=1}^{d} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
+        \item Computationally efficient (no matrix exponentials)
         \begin{alignat*}{2}
@@
 \begin{frame}
+    \frametitle{Parameterizing PVMs}
+    \begin{itemize}
+        \item Each part is assigned $d$ element \term{projective-valued measures (PVMs)} acting on $\s{H}^d$,
+        \[ M = \bc{M_1, \ldots, M_d} \qquad \sum_{i=1}^{d} M_{i} = \ident \]
+        \[ \forall i: \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_i \ket{\psi} \geq 0 \quad M_i = M_i^{\dagger} \]
+        \[ M_{i}M_{j} = \de_{ij} M_{i} \quad M_{i} = \ket{m_{i}}\bra{m_{i}} \]
+        % \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
+        \item Unitary transform maps $M$ to computational basis
+        \[ \bc{\ket{m_{1}}, \ldots, \ket{m_{d}}} = \bc{U \ket{1}, \ldots, U \ket{d}} \]
+        \item Global phase irrelevant: $\ti{U}$ requires $d(d - 1)$ real-valued parameters
+        \item PVMs are computationally more efficient than POVMs
+    \end{itemize}
+    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
+\end{frame}
+
+\begin{frame}
     \frametitle{Parameterizing States}
     \begin{itemize}
-        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite qubit state acting on $\Hilb^{d/2} \otimes \Hilb^{d/2}$
-        \item $d \times d$ positive semi-definite (PSD) hermitian matrices with unitary trace
-        \item \term{Cholesky Parametrization} allows one to write any hermitian PSD as $\rho = T^{\dagger} T$
-        \item For $d = 4$:
-        \[ T = \begin{bmatrix}\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}\end{bmatrix} \]
-        \item $d^2$ real-valued parameters
-        \item Normalized $\rho = {T^{\dagger}T}/{\Tr\br{T^{\dagger} T}}$ adds degeneracy
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing States Cont'd}
-    \begin{itemize}
-        \item \term{SHH parameterization} \cite{Spengler_2010_Unitary} exploits spectral decomposition; for rank $k \leq d$ density matrix
-        \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i} \bra{\psi_i} \qquad p_i \geq 0, \sum_i p_i = 1 \]
-        \item Orthonormal $k$-element sub-basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into computational basis $\bc{\ket{i}}$ by unitary $U \in \s{U}\br{d}$ such that $\ket{\psi_i} = U \ket{i}$
-        \item Freedom to choice $k$
-        \item Parameterize $\rho$ through $\bc{p_i}$ and $\ti{U}_{k}$
-        \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
-        \item real-value parameters $d^2 - \br{d-k}^2 - k$ for $\ti{U}_{k}$, $k-1$ for $\bc{p_i}$ (no degeneracy)
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing POVMs}
-    \begin{itemize}
-        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
-        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
-        \item $n$-outcome measurement
-        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
-        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
-        \item Warrants consideration of \term{projective-valued measures (PVMs)}
-    \end{itemize}
-    \note<1>[item]{Naimark's Dilation Theorem}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing PVMs}
-    \begin{itemize}
-        \item Each party $\br{A, B, C}$ is assigned $n$-outcome $\br{M_A, M_B, M_C}$ such that,
-        \[ M_{\chi,i}M_{\chi,j} = \de_{ij} M_{\chi, i} \quad M_{\chi, i} = \ket{m_{\chi,i}}\bra{m_{\chi,i}} \]
-        \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
-        \item Use unitary transformation again
-        \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
-        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $n(2d - n - 1)$ real-valued parameters\
-        \item PVMs are computationally more efficient
-    \end{itemize}
-    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
-\end{frame}
-\begin{frame}
-    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
+        \item Exploit spectral decomposition
+        \[ \rho = \sum_{i=1}^{d} p_i \ket{\psi_i} \bra{\psi_i} \qquad p_i \geq 0, \sum_i p_i = 1 \]
+        \item Unitary transform maps $\bc{\ket{\psi_i}}$ to computational basis
+        \[ \bc{\ket{\psi_{1}}, \ldots, \ket{\psi_{d}}} = \bc{U \ket{1}, \ldots, U \ket{d}} \]
+        \item Global phase irrelevant again $\ti{U}$ requires $d\br{d - 1}$ real-valued parameters
+        \item Eigenvalues $\bc{p_i}$ parameterized using hyper-spherical coordinates: $d - 1$ real-valued parameters
+    \end{itemize}
 \end{frame}
@@
     \[ \text{Relative Violation:} \qquad V_F = \f{\min_P\bc{I\br{P}}}{I\br{P_F}} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
 \end{frame}
@@
     \end{center}
-    \[ \probplotvalue{255, 255, 255} = 0.00133 \]
+    \[ \probplotvalue{255, 255, 243} = 0.00133 \]
 \end{frame}
@@
     \begin{enumerate}
-        \item Inflation technique capable of producing polynomial inequalities with quantum/classical witnesses
-        \item Fritz witness-able by party-symmetric inequalities
-        \item Maximally violating distributions require non-maximally entangled states
+        \item \textbf{Inflation technique} capable of producing polynomial inequalities with quantum/classical witnesses
+        \item Fritz witness-able by \textbf{party-symmetric inequalities}
+        \item Maximally violating distributions require \textbf{non-maximally entangled states}
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Unanswered Questions}
+    \begin{enumerate}
+        \item Do these new non-local distributions suggest \textbf{new quantum resources} in the triangle scenario?
+        \item Can any non-local quantum correlations in the triangle scenario \textbf{satisfy CHSH inequalities} (under Fritz type coarse graining)?
+        \item Which inequalities are \textbf{most robust} to noise? Facets?
     \end{enumerate}
@@
 
-\section{Optional Slides}
+\section{Appendix A: Optional Slides}
 
@@
 
-\section{Local Minima Concerns}
+\begin{frame}
+    \frametitle{Parameterizing POVMs [Optional]}
+    \begin{itemize}
+        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
+        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
+        \item $n$-outcome measurement
+        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
+        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
+        \item Warrants consideration of \term{projective-valued measures (PVMs)}
+    \end{itemize}
+    \note<1>[item]{Naimark's Dilation Theorem}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Cholesky Parameterization of States [Optional]}
+    \begin{itemize}
+        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite qubit state acting on $\Hilb^{d/2} \otimes \Hilb^{d/2}$
+        \item $d \times d$ positive semi-definite (PSD) hermitian matrices with unitary trace
+        \item \term{Cholesky Parametrization} allows one to write any hermitian PSD as $\rho = T^{\dagger} T$
+        \item For $d = 4$:
+        \[ T = \begin{bmatrix}\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}\end{bmatrix} \]
+        \item $d^2$ real-valued parameters
+        \item Normalized $\rho = {T^{\dagger}T}/{\Tr\br{T^{\dagger} T}}$ adds degeneracy
+    \end{itemize}
+\end{frame}
+
+\section{Appendix B: Local Minima Concerns}
 

### 2016-11-25 documents/BrazilSlides/speaking_notes.tex
Some speaking notes for the talk

\documentclass{article}
\usepackage{xcolor}

\usepackage[backend=biber, style=authoryear, doi=false,isbn=false,url=false, citestyle=authoryear-comp]{biblatex} %
\addbibresource{../references.bib}

\newcommand{\newslide}{\textcolor{red}{[New~Slide]}}
\newcommand{\elaborate}{\textcolor{gray}{[Elaborate]}}

\begin{document}
    Hello everyone, I'd like to begin by thanking the International Institute of Physics and the organizers of this workshop for inviting me to present.
    I regret not being able to attend in person and am sincerely gracious for being permitted to deliver my presentation via Skype.
    Moreover, I'd like to thank the Perimeter Institute in Canada for directly funding this research. \\

    Given that it is likely very few of you know who I am, I believe a short introduction is warranted. My name is TC Fraser and I am currently completing my undergraduate degree at the University of Waterloo in Canada. This research project was the result of me being awarded the Mike Lazaridis Scholarship for Theoretical Physics which enabled me to conduct research at the Perimeter Institute in Canada over the last several months. I am currently supervised by Elie Wolfe, and nearly all of the following results were made possible by his guidance and mentor-ship. \\

    The objective of my research was to study and characterize quantum non-locality in a very particular causal structure know as the triangle scenario. \newslide The triangle scenario consists of three observers (A,B,C) arranged in a triangular manner each pair-wise sharing local latent/hidden variables. Throughout this talk I will be representing observable nodes as blue triangles and latent nodes as orange circles. \\

    More specifically, the primal objective of this research was to derive causal compatibility inequalities for the triangle scenario that are violated by quantum correlations; something that nobody has obtained previous. The purpose of doing so is to search for novel non-local resources that are potentially different than those known previously. \\

    The triangle scenario has been studied previously:
    In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}.
    {In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)}; an example I will elucidate later in this talk.
    {In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility (there are none)}.
    {Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving such inequalities.}

    \begin{center}
        \textbf{Part 1: Inflation Technique}
    \end{center}
    \newslide

    To that end, in this talk I will be summarizing a new tool that can be used to solve numerous causal inference and causal compatibility problems called the Inflation Technique developed by ~\cite{Inflation}. The Inflation Technique provides an avenue for constructing polynomial inequalities that constraint the set of compatible distributions. \\

    In order to demonstrate the typical procedures that comprise the inflation technique, I will work through a very simple example of non-local correlations on the triangle scenario. Doing so will motivate how I constructed compatibility inequalities that can be violated by quantum correlations. \\

    To conclude, I will discuss how these inequalities can be used to help search for novel incompatible quantum distributions using numerical optimization techniques. \\

    \newslide

    Before continuing, it is beneficial to define precisely what is meant by causal compatibility in the triangle scenario. A probability distribution over $A,B,C$ is compatible with the triangle scenario if it can be written as the product over the causal parameters of the triangle. That is to say, a joint distribution factorizes into distributions over each node given its parents in the triangle scenario. Effectively, compatibility corresponds to the probabilistic independence relations generated by the graphical structure of the triangle scenario. \\

    The more general setting for causal compatibility has two necessary components: the existence of a joint distribution over all nodes in the causal structure and that the joint distribution factors into causal parameters. \elaborate\\

    \newslide

    I will now introduce you to the core concepts and features that go into the Inflation Technique. It is important to remember that the inflation technique is a tool to solve numerous causal inference problems and can be applied to effectively any causal structure. Nonetheless I will be focusing on its application to the triangle scenario specifically. \\

    \newslide

    The inflation technique concerns itself with the following idea. Given a causal structure (such as the triangle scenario depicted of the left), one can construct an inflated causal structure such as the one depicted on the right. A inflation resembles the original causal structure in two ways:
    \begin{enumerate}
        \item The nodes in the inflated causal structure share the same labels as those in the original causal structure up to a numerical subscript called the copy-index. The copy-index simply is used to distinguish different copies of nodes from the original causal structure.
        \item The local ancestral features of the inflated causal structure are identical to those of the original causal structure.
    \end{enumerate}
    \elaborate\\

    \newslide\\
    To illustrate this concretely, examine node $A_1$ of the inflated causal structure.\\
    \elaborate\\
    \newslide\\
    \elaborate\\
    \newslide\\
    As you might imagine, inflations are not unique. Depicted here are a few inflations of the triangle scenario that have been of use when it comes to examining non-locality in the the triangle scenario. It is useful and quite amusing to invent names for the various inflations.
    \elaborate\\
    \newslide\\
    Now that we have an idea of inflations are, I want to introduce a very important type of a set of node.
    \elaborate
    \newslide\\
    Injectable sets are very useful because of the following inflation lemma that connects compatibility on the original causal structure to compatibility on the inflated causal structure.\\

    If one manages to obtain a compatible marginal model defined over the images of the injectable sets, then by definition that means there exists a set of causal parameters. From this, we can construct a set of inflated causal parameters defined over the nodes of the inflated causal structure by copying the conditional distributions whenever necessary. As a result, we can construct all sorts of compatible distributions on the inflated causal structure. \\

    By itself, the inflation lemma isn't very useful, but as a corollary, we can apply this process in reverse to inequalities on the inflated causal.
    \elaborate
    \newslide\\
    To demonstrate this procedure concretely, I will prove that perfect correlations are not compatible with the triangle scenario. It is important to remember that there are certainly more intuitive and immediate ways of demonstrating that perfect correlations are non-local, I only present the argument in this way to illustrate exactly how the more general procedure can be implemented to find compatibility inequalities that are violated by quantum distributions.
    \elaborate
    \elaborate
    \elaborate

    \begin{center}
        \textbf{Part 2: Quantum Non-locality From Inflation}
    \end{center}

    At this stage, it is my hope that you have a rough idea about how to generate polynomial compatibility inequalities using the inflation technique. Moreover it should be clear that if you have non-local distributions that are know to be non-local by other means, then one can manufacture an inequality that witnesses it's non-locality. \\

    With this guiding principle in mind, I can find inequalities that are violated by quantum distributions if I know of some non-local quantum distributions ahead of time. \\

    \elaborate

    \begin{center}
        \textbf{Part 2.5: Fritz Distribution}
    \end{center}

    I mentioned early that Tobias Fritz discovered quantum non-locality in the triangle scenario and proved its non-locality without explicitly using inequalities. The brilliant insight he made was to recognize that the famous Bell scenario can be effectively embedded into the triangle scenario in the following way. \\

    \newslide

    By simply rearranging/relabeling the nodes of the triangle scenario, one can recover something that looks remarkably similar to a Bell scenario between $A$ and $B$ where each party has a measurement setting $S_A$ and $S_B$ that determines the measurement to be made on their shared resource $\lambda$. \\

    The key difference between the Bell scenario and this embedding is that the measurement pusedo-settings are latent nodes. Therefore in order to directly mimic the Bell scenario, $C$ needs to taken on the role of announcing the measurement settings for $A$ and $B$. After doing so, any non-locality in the Bell scenario can be embedded into non-locality in of the triangle scenario. \\

    If $A,B,C$ are given $4$-outcome measurements, we can achieve Bell non-locality explicitly.

    \newslide
    \elaborate

    \printbibliography

\end{document}

### 2016-11-25 documents/BrazilSlides/slides.tex
Some speaking notes for the talk
added one final slide

@@
     \begin{lemma}[Inflation Lemma]
-    Given $\graph$ and inflation $\graph$':
+    Given $\graph = \br{\nodes, \edges}$ and inflation $\graph' = \br{\nodes', \edges'}$:
     \begin{center}
@@
     \begin{itemize}
-        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} parameterization of $\s{U}\br{d}$
+        \item \cite{Spengler_2010_Unitary} parameterization of $\s{U}\br{d}$
         \[ \la = \begin{pmatrix}
@@
     \frametitle{Maximal Violation}
+    \includegraphics[width=\linewidth]{../../figures/distributions/plotted_dist_I_0_max_violation.pdf}
+    \[ \text{Relative Violation:} \qquad V_F = \f{\min_P\bc{I\br{P}}}{I\br{P_F}} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Maximal Violation Symmetric}
     \includegraphics[width=\linewidth]{../../figures/distributions/plotted_dist_I_2_max_violation.pdf}

### 2016-12-07 documents/TriangleScenario/ts.tex
Updates from ShareLaTeX
Added description of Fritz and parametrization to the quantum paper

@@
 % === Revtex Declaration ===
-\documentclass[aps, 10pt, english, twoside, pra, nofootinbib, longbibliography]{revtex4-1}
+\documentclass[aps, 10pt, english, twoside, pra, nofootinbib, tightenlines, longbibliography]{revtex4-1}
 
@@
 \begin{document}
-    \title{Causal Compatability Inequalities Admitting of Quantum Violations in the Triangle Scenario}
+    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
     \author{Thomas C. Fraser}
@@
         Quantum correlations are often incompatible with a classical assumption of causal structure.
-This nonclassicality is often known as quantum nonlocality, and it is witnessed through the violation of causal compatability inequalities, such as Bell inequalities.
+This nonclassicality is often known as quantum nonlocality, and it is witnessed through the violation of causal compatibility inequalities, such as Bell inequalities.
 Such inequalities were recently derived for the Triangle scenario [arXiv:1609.00672], begging the question: can these inequalities be violated by quantum correlations?
@@
     \subsection{Fritz Distribution}
-    \begin{itemize}
-        \item \todo[TC]{Reproduce Fritz Distribution}
-        \item \todo[TC]{Recall its proof of incompatibility}
-        \item \todo[TC]{Requires perfect correlations}
-        \item \todo[TC]{Not robust to noise}
-        \item \todo[TC]{Fritz Problem 2.17}
-    \end{itemize}
+    \label{sec:fritz_distribution}
+    \begin{figure}
+    \begin{center}
+        % \fbox{%
+        \begin{minipage}[t]{.48\textwidth}
+            \centering
+            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational_fritz_bell}}
+            \caption{The triangle scenario re-imagined to mimic the Bell scenario. The measurement settings $S_{\p{A}},S_{\p{B}}$ are latent nodes unlike the Bell scenario (\cref{fig:bell_scenario}).}
+            \label{fig:triangle_scenario_with_fritz_bell_embedded}
+        \end{minipage}%
+        % }%
+        \hspace{0.04\textwidth}%
+        % \fbox{%
+        \begin{minipage}[t]{.48\textwidth}
+            \centering
+            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
+            \caption{The Bell scenario consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively.}
+            \label{fig:bell_scenario}
+        \end{minipage}%
+        % }%
+    \end{center}
+    \end{figure}
+    As was originally noticed by Fritz~\cite{Fritz_2012}, it is possible to construct quantum distributions incompatible with the triangle scenario by utilizing quantum distributions incompatible with the familiar Bell scenario.
+To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_scenario_with_fritz_bell_embedded} and contrast it with the Bell scenario of \cref{fig:bell_scenario}.
+The crucial distinction to be made is that the respective measurement settings $S_{\p{A}}, S_{\p{B}}$ in the Bell scenario become latent nodes in the triangle scenario.
+In order to embed Bell scenario incompatibility into the triangle scenario, the latent nodes $S_{\p{A}}, S_{\p{B}}$ need to be observable and independent of the shared latent node $\la$.
+This can be accomplished by having $C$ measure the measurement settings $S_{\p{A}}, S_{\p{B}}$ and announce them as an outcome.
+Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell scenario is also incompatible with the triangle scenario provided that $C$ is perfectly correlated with $S_{\p{A}}, S_{\p{B}}$.
+Understandably there are numerous ways that this can be accomplished, albeit we will focus on elucidating an exemplary case.
+
+    The \term{Fritz distribution}, denoted $\prob[\fritz]$, is a quantum-accessible distribution known to be incompatible with the triangle scenario~\cite{Fritz_2012}.
+Explicitly, the Fritz distribution can be written as follows:
+    \begin{align*}
+    \eq \label{eq:fritz_dist}
+    \begin{split}
+        \prob[\fritz][000] = \prob[\fritz][110] = \prob[\fritz][021] = \prob[\fritz][131] = \prob[\fritz][202] = \prob[\fritz][312] = \prob[\fritz][233] = \prob[\fritz][323] &= \f{1}{32}\br{2 + \sqrt{2}} \\
+        \prob[\fritz][010] = \prob[\fritz][100] = \prob[\fritz][031] = \prob[\fritz][121] = \prob[\fritz][212] = \prob[\fritz][302] = \prob[\fritz][223] = \prob[\fritz][333] &= \f{1}{32}\br{2 - \sqrt{2}}
+    \end{split}
+    \end{align*}
+    Here the notation $\prob[\fritz][abc] = \prob[\p{ABC}][abc] = \prob[][\p A=a,\p B=b,\p C=c]$ is used as shorthand.
+The Fritz distribution is best visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}.
+From this diagram, it can be seen that each of $\p{C}$'s outcomes restricts the possible outcomes for $\p A,\p B$ into a $2 \times 2$ block.
+If one writes the outcome labels $\bc{0,1,2,3}$ in binary $\bc{00,01,10,11}$, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by the outcome of $\p C$.
+Pursuant to the embedding of~\cref{fig:triangle_scenario_with_fritz_bell_embedded} the left-hand bits emulate the measurement settings $S_{\p A}$ and $S_{\p B}$ and the right-hand bits emulate a two-outcome measurement performed by $A, B$ as they would in~\cref{fig:bell_scenario}.
+Specifically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6]{../../figures/distributions/fritz_dist_plot_bits_no_title.pdf}
+            \caption{The Fritz distribution visualized using a $4 \times 4 \times 4$ grid.
+The $4$ outcomes of $A,B,C$ are written in binary as a doublet of bits to illustrate that certain bits act as measurement pseudo-settings.}
+            \label{fig:fritz_distribution_visualized}
+    \end{center}
+    \end{figure}
+    Consequently, it is possible to define the correlation between right-bits of $A$ and $B$,
+    \[ \ba{\p A_r \p B_r} = \prob[\p A_r \p B_r][00] + \prob[\p A_r \p B_r][11] - \prob[\p A_r \p B_r][01] - \prob[\p A_r \p B_r][10] \]
+    And also define a CHSH inequality~\cite{CHSH_Original} for the right-bits of $A$ and $B$,
+    \[ \ba{\p A_r \p B_r|\p C = 00} + \ba{\p A_r \p B_r|\p C = 01} + \ba{\p A_r \p B_r|\p C = 10} - \ba{\p A_r \p B_r|\p C = 11} \leq 2 \eq \label{eq:CHSH} \]
+    Substitution of \cref{eq:fritz_dist} into \cref{eq:CHSH} yields maximal violation~\cite{Cirelson_1980},
+    \[ 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} = 2\sqrt{2} \not \leq 2 \]
+    The Fritz distribution $\prob[\fritz]$ can be realized as a set of quantum states and measurements.
+The shared resource between $A$ and $B$ (graphically denoted $\la$) is the maximally entangled Bell state:
+    \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \qquad \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \]
+    While the states shared with $C$ are the following mixed states:
+    \[ \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2} \]
+    The measurements employed by $A,B$ and $C$ are separable, projective measurements,
+    \begin{align*}
+        M_{A} &= \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
+        M_{B} &= \bc{\ket{\psi_{6}0}\bra{\psi_{6}0}, \ket{\psi_{2}0}\bra{\psi_{2}0}, \ket{\psi_{0}1}\bra{\psi_{0}1}, \ket{\psi_{4}1}\bra{\psi_{4}1}} \\
+        M_{C} &= \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
+    \end{align*}
+    Where $\ket{\psi_n}$ is shorthand for,
+    \[ \ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}} \]
+
+    Before continuing it is worth noting that \cref{eq:fritz_dist} is non-unique.
+Any distribution that is equal to \cref{eq:fritz_dist} via a permutation of outcomes or exchange of parties is should also be referred to as a Fritz distribution.
+Moreover, the quantum realization presented here is not unique either.
+Nonetheless for concreteness, \cref{eq:fritz_dist} is taken as \textit{the} Fritz distribution throughout this paper.
+
+    Additionally, it is important to understand the domain in which Fritz's proof of incompatibility is valid.
+Specifically, \cref{eq:CHSH} can only be applied to the triangle scenario where there exists perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$.
+The details of this restriction are discussed and proven in Fritz's original work~\cite{Fritz_2012}.
+As such, the incompatibility proof employed by Fritz is not applicable to any distribution that significantly deviates from the Fritz distribution presented above.
+For example, if one affinely combines \cref{eq:fritz_dist} with uniform noise, at what point does the resultant distribution become compatibility?
+This problem is discussed more in \cref{sec:noise}.
+
+    Upon reflection, the Fritz distribution can rightly be considered slightly manufactured.
+The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions under a triangle scenario embedding offers no additional perspective onto the types of resources made accessible by quantum mechanics.
+Therefore, it is desirable to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell scenario.
+In~\cite{Fritz_2012}, Fritz presented the following problem: \textit{Find an example of non-classical quantum correlations in the triangle scenario together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.} The problem is understandably stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures.
+To refine the discussions, consider the following refinements of the problem:
+    \begin{enumerate}
+        \item Find proofs of causal incompatibility of quantum distributions on the triangle scenario that are not reliant on perfect correlations.
+        \item Find incompatible quantum distributions on the triangle scenario that are \textit{more incompatible} that all Fritz-type embeddings.
+    \end{enumerate}
+    \todo[TC]{Discuss the accomplishments of this paper towards answering these problems. }
+
     \section{Inflation Technique}
@@
     \end{itemize}
+    \begin{figure}
+    \begin{center}
+            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
+            \caption{The triangle scenario as modeled by quantum states and measurements.}
+            \label{fig:triangle_scenario_quantum_model}
+    \end{center}
+    \end{figure}
     \subsection{Parameterizing Quantum Distributions}
-    \begin{itemize}
-        \item \todo[TC]{Unitaries}
-        \item \todo[TC]{States}
-        \item \todo[TC]{Measurements}
-        \item \todo[TC]{Aligning States / Permutation}
-    \end{itemize}
+    \label{sec:param_quantum_dist}
+    In search of new, incompatible, quantum distributions that can be realized on the triangle scenario, numerical optimizations over the the space of quantum-accessible probability distributions are performed.
+To do so, we are interested in a parameterization all distributions that can be expressed as follows:
+    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
+    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately\footnote{$\netperm$ is discussed more thoroughly in \cref{sec:perm_matrix}.}.
+
+    In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
+The states $\rho$ are taken to be bipartite \textit{qubit} states acting on $\s{H}^{2} \otimes \s{H}^{2}$.
+This is motivated by \cref{sec:fritz_distribution} in which the Fritz distribution only requires qubit states.
+In generality, one could consider $n$-dimensional states acting on $\s{H}^{n} \otimes \s{H}^{n}$.
+However, in such cases the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ then acts on $\br{\Hilb^{n}}^{\otimes 6}$ requiring a $n^6 \times n^6$ matrix with $n^{12}$ entries.
+Therefore, $n = 2$ is far more computationally feasible than $n > 2$.
+Additionally, restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
+First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the triangle scenario.
+Second, generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, however a valid, unbiased parameterization was not found for $k > 2$.
+Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as follows:
+    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]
+
+    In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
+Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, a single technique is presented that was found to be most computationally suitable for our purposes.
+    \subsubsection{Unitary Group}
+    \label{sec:unitary_group}
+    To facilitate the parameterization of quantum states states and PVMs, a parameterization of the unitary group of dimension $d$ (denoted $\s{U}\br{d}$) by Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} is introduced.
+Discussions of its application to states and measurements are deferred to \cref{sec:states} and \cref{sec:measurements} respectively.
+
+    In Ref.~\cite{Spengler_2010_Unitary}, Spengler \textit{et. al.} proved that all unitaries $U \in \s{U}\br{d}$ can be parameterized without degeneracy as follows:
+    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \tcdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
+    Where $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ form a $d \times d$ matrix of real-valued parameters with periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
+    \[ \la = \begin{pmatrix}
+        \la_{1,1} & \cdots & \la_{1, d} \\
+        \vdots & \ddots & \vdots \\
+        \la_{d,1} & \cdots & \la_{d, d} \\
+    \end{pmatrix} \]
+    And where $P_l$ are one-dimensional projective operators,
+    \[ P_l = \ket{l}\bra{l} \qquad 1 \leq l \leq d \eq \label{eq:projective_operator} \]
+    and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices,
+    \[ \sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m} \qquad 1 \leq m < n \leq d\]
+    The SSH parameterization (\cref{eq:spengler_unitary}) is unique in that each of the real-valued parameters $\la_{n,m}$ has physical significance.
+For the sake of reference, let us label the matrix exponential terms in \cref{eq:spengler_unitary} in a manner that corresponds to their affect on an orthonormal basis $\bc{\ket{1}, \ldots, \ket{d}}$.
+    \begin{align*}
+    \begin{split}
+        GP_l &= \exp\br{iP_l \lambda_{l,l}} \\
+        RP_{n,m} &= \exp\br{i P_n \lambda_{n,m}} \\
+        R_{m,n} &= \exp\br{i \si_{m,n} \lambda_{m,n}}
+    \end{split} \eq \label{eq:exp_terms}
+    \end{align*}
+    For example, $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$.
+Analogously, $RP_{n,m}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $GP_l$ fixes the global phase of $\ket{l}$.
+Possessing a parameterization that maintains this physical interpretation is useful as it allows one to readily eliminate any degeneracies.
+For the purposes of quantum distributions such as \cref{eq:quantum_model_triangle}, it should be clear that any contributions to global phase are irrelevant.
+The SSH parameterization becomes especially attractive because it readily permits one to drop the global phase terms by setting $\la_{l,l} = 0$ for all $l = 1, \ldots, d$.
+It is convenient to denote the set of all unitaries up to global phase considerations as $\ti {\s{U}}\br{d}$ and express $\ti {U} \in \ti {\s{U}}\br{d}$ using $d\br{d-1}$ real-valued parameters:
+    \[ \ti U = \prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}} \eq \label{eq:spengler_unitary_gp} \]
+    Another attractive feature of the SSH parameterization not mentioned in~\cite{Spengler_2010_Unitary} is that \cref{eq:spengler_unitary}, and thus \cref{eq:spengler_unitary_gp}, can be implemented in a computationally efficient manner.
+This is discussed in \cref{sec:comp_spengler}.
+    \subsubsection{Measurements}
+    \label{sec:measurements}
+    For each measurement set $M$ in \cref{eq:quantum_model_triangle}, we consider a $d$-element projective-valued measure (PVM) $M = \bc{M_1, \ldots, M_d}$ satisfying a number of familiar constraints:
+    \begin{gather*}
+    \forall \ket{\phi} \in \Hilb^d: \bra{\phi} M_i \ket{\phi} \geq 0 \qquad \sum_{i=1}^{d} M_i = \ident_{d} \\
+    M_i = \ket{m_i}\bra{m_i} \qquad M_i M_j = \de_{ij} M_i
+    \end{gather*}
+    Therefore, parameterizing $M$ corresponds to parameterizing the set of all orthonormal basis $\bc{\ket{\psi_1}, \ldots, \ket{\psi_d}}$ of $\Hilb^d$.
+    First note that any such basis can be transformed into the computational basis $\bc{\ket{1}, \ldots, \ket{d}}$ by a unitary denoted $U^{-1} \in \mathcal{U}\br{d}$.
+    \[ \forall i : U^{-1} \ket{\psi_i} = \ket{i} \eq \label{eq:unitary_transform}\]
+    With this observation, all that is required is to parameterize the set of all unitaries $U \in \mathcal{U}\br{d}$.
+Specifically, the projective property each $M_i \in M$ means that the global phase of $U$ is completely arbitrary; one only needs to consider parameterizing unitaries up to global phase using \cref{eq:spengler_unitary_gp}.
+    \[ M = \bc{\ti U \ket{i} \bra{i} \ti U^{\dagger} \mid i \in \bc{1, \ldots, d}} \]
+    For the purposes discussed in \cref{sec:param_quantum_dist}, only $d = 4$ outcome measurements are utilized and therefore requiring $4\br{4 - 1} = 12$ real-valued parameters.
+This method was inspired by the measurement seeding method of P{\'{a}}l and V{\'{e}}rtesi's~\cite{Pal_2010} iterative optimization technique.
+    \subsubsection{States}
+    \label{sec:states}
+
+    Each state $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ of \cref{eq:quantum_model_triangle} is modeled as a two-qubit density matrices acting on $\Hilb^2 \otimes \Hilb^2$.
+The space of all such states corresponds to the space of all $4\times 4$ positive semi-definite hermitian matrices with unitary trace.
+    \[ \forall \ket{\phi} \in \Hilb^d: \bra{\phi} \rho \ket{\phi} \geq 0 \qquad \rho^{\dagger} = \rho \qquad \Tr\br{\rho} = 1 \eq \label{eq:density_matrix}\]
+    Although is common to parameterize all such matrices using a Cholesky decomposition~\cite{Grasmair_2014}, we make use of the non-degenerate SHH parameterization~\cite{Spengler_2010_Unitary} and the spectral decomposition of $\rho$.
+Retaining full generality, consider full-rank density matrices:
+    \[ \rho = \sum_{i=1}^{d} p_i \ket{\psi_i}\bra{\psi_i} \qquad \sum_{i=1}^{d} p_i = 1, p_i \geq 0 \eq \label{eq:param_density} \]
+    Where $\bc{p_i}$ are the eigenvalues of $\rho$ and $\bc{\ket{\psi_i}}$ are its eigenstates.
+It is here that one recognizes the reapplication of \cref{eq:unitary_transform}: any orthonormal basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into a computational basis $\bc{\ket{i}}$ by a unitary transformation $U \in \mathcal{U}\br{d}$ such that $\ket{\psi_i} = U\ket{i}$.
+Analogous to the projective measurements considered in \cref{sec:measurements}, the global phase contributions are redundant.
+    \[ \rho = \sum_{i=1}^{d} p_i \ti U\ket{i}\bra{i} \ti U^{\dagger} \]
+    Parameterizing the eigenvalues requires $d - 1$ real-valued parameters due to the trace constraint of \cref{eq:density_matrix}.
+The eigenvalues are parameterized without degeneracy using a tuple of $d-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{d-1}}, \lambda_i \in \bs{0, 2 \pi}$ using hyperspherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}:
+    \begin{align*}
+    \eq \label{eq:convex_param}
+    \begin{split}
+        p_n &= \prod_{i=1}^{n-1} \sin^2 \lambda_i \\
+        p_j &= \cos^2 \lambda_j \prod_{i=1}^{j-1} \sin^2 \lambda_i \quad \forall j \in 1, \ldots, n - 1
+    \end{split}
+    \end{align*}
+    Therefore it is possible to parametrize all $d$-dimensional density matrices satisfying \cref{eq:density_matrix} using $d\br{d - 1} + d - 1 = d^2 -1$ parameters.
+    \subsubsection{Permutation Matrix}
+    \label{sec:perm_matrix}
+    \begin{figure}
+        \centering
+        \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
+        \caption{The triangle scenario permutation matrix $\netperm$ for $\br{\Hilb^2}^{\otimes 6}$. Black represents a value of $1$ and white represents $0$.}
+        \label{fig:perm_mtrx}
+    \end{figure}
+    Finally, we introduce the a permutation matrix $\netperm$ for the triangle scenario.
+For bipartite qubit states, $\netperm$ is the $64\times64$ bit-wise matrix depicted in \cref{fig:perm_mtrx}.
+Upon examination of \cref{eq:quantum_model_triangle_pvms}, we consider $\netperm$ to be acting on the joint global state $\rho_{\p{AB}} \otimes \rho_{\p{BC}} \otimes \rho_{\p{CA}}$.
+To illuminate its necessity, consider \cref{eq:quantum_model_triangle} in the absence of $\netperm$.
+    \begin{align*}
+    \prob[\p{ABC}]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{\p{AB}} \otimes \rho_{\p{BC}} \otimes \rho_{\p{CA}}} \br{M^a_{\p{A}}\otimes M^b_{\p{B}} \otimes M^c_{\p{C}}}}\\
+    &= \Tr\bs{\br{\rho_{\p{AB}}M^a_{\p{A}}}\otimes\br{\rho_{\p{BC}}M^b_{\p{B}}}\otimes\br{\rho_{\p{CA}}M^c_{\p{C}}}}\\
+    &= \Tr\br{\rho_{\p{AB}}M^a_{\p{A}}}\Tr\br{\rho_{\p{BC}}M^b_{\p{B}}}\Tr\br{\rho_{\p{CA}}M^c_{\p{C}}}\\
+    &= \prob[\p{A}\mid \rho_{\p{AB}}]\br{a}\prob[\p{B}\mid \rho_{\p{BC}}]\br{b}\prob[\p{C}\mid \rho_{\p{CA}}]\br{c}
+    \end{align*}
+    On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$.
+This is analogously troubling for $B$ and $C$ as well.
+To resolve this issue, the permutation matrix $\netperm$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$.
+To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
+    \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
+    $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''.
+It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
+    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
     \subsection{Results}
@@
         \item \todo[TC]{Features of maximally violating distributions}
+    \end{itemize}
+
+    \section{Noise}
+    \label{sec:noise}
+    \begin{itemize}
+        \item \todo[TC]{Recall why noise is important (experimental and foundational)}
+        \item \todo[TC]{Describe our noise model}
+        \item \todo[TC]{Plots}
+        \item \todo[TC]{Define and discuss the crossing point}
+        \item \todo[TC]{Discussion as to what noise measures}
     \end{itemize}
@@
     \end{itemize}
+    \appendix
+    \section{Computationally Efficient Parameterization of the Unitary Group}
+    \label{sec:comp_spengler}
 
+    If \cref{sec:unitary_group}, the SSH parameterization was introduced as a non-degenerate parameterization of the unitary group $\s{U}\br{d}$.
+As presented, the SSH parameterization suffers due to the presence of computationally expensive matrix exponential terms~\cite{Moler_2003}.
+Although not explicitly mentioned in~\cite{Spengler_2010_Unitary}, it is possible to remove the reliance on matrix exponential operations in \cref{eq:spengler_unitary} by utilizing the explicit form of the exponential terms in \cref{eq:exp_terms}.
+As a first step, recognize the defining property of the projective operators \cref{eq:projective_operator},
+    \[ P_l^k = \br{\ket{l}\bra{l}}^k = \ket{l}\bra{l} = P_l \]
+    This greatly simplifies the global phase terms $GP_l$,
+    \[ GP_l = \exp\br{iP_l \lambda_{l,l}} = \sum_{k=0}^{\inf} \f{\br{iP_l \lambda_{l,l}}^k}{k!} = \ident + \sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}P_l^k = \ident + P_l \bs{\sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}} = \ident + P_l \br{e^{i \lambda_{l,l}} - 1} \eq \label{eq:unitary_GP} \]
+    Analogously for the relative phase terms $RP_{n,m}$,
+    \[ RP_{n,m} = \cdots = \ident + P_n \br{e^{i \lambda_{n,m}} - 1} \eq \label{eq:unitary_RP} \]
+    Finally, the rotation terms $R_{m,n}$ can also be simplified by examining powers of $i \sigma_{n,m}$,
+    \[ R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}} = \sum_{k=0}^{\inf} \f{\br{\ket{m}\bra{n} - \ket{n}\bra{m}}^k \lambda_{m,n}^k}{k!} \]
+    One can verify that the following properties hold,
+    \begin{align*}
+        \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^0 &= \ident \\
+        \forall k \in \N, k \neq 0 : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k} &= \br{-1}^k\br{\ket{m}\bra{m} + \ket{n}\bra{n}} \\
+        \forall k \in \N : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k+1} &= \br{-1}^k\br{\ket{m}\bra{n} - \ket{n}\bra{m}}
+    \end{align*}
+    Revealing the simplified form of $R_{m,n}$,
+    \[ R_{m,n} = \ident + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \sum_{j=1}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j}}{\br{2j}!} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sum_{j=0}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j+1}}{\br{2j+1}!} \]
+    \[ R_{m,n} = \ident + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \eq \label{eq:unitary_R} \]
+    By combining the optimizations of \cref{eq:unitary_GP,eq:unitary_RP,eq:unitary_R} together we arrive at an equivalent form for \cref{eq:spengler_unitary} that is computational more efficient.
+    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n}RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}}  \eq \label{eq:spengler_unitary_fast} \]
+
+    \bibliography{../references}
 \end{document}

### 2017-01-04 documents/437Slides/slides.tex
slides for 437 talk

--- 2016-11-25 documents/BrazilSlides/slides.tex
@@
 }
-\date[QN 2016]{Quantum Networks Workshop, IIP, Nov. 2016}
+\date[Phys 437 2017]{Phys 437 Oral Report, Jan. 2017}
 
@@
     \titlepage
-    \note[item]{Thank International Institute for Physics (IIP) for support}
-    \note[item]{Thank Perimeter Institute for Theoretical Physics (PI) for support}
-\end{frame}
-
-\begin{frame}
-    \frametitle{The Triangle Scenario (TS)}
-    \begin{center}
-        \scalebox{1.5}{\input{../../figures/causal_structures/triangle_scenario}}
-    \end{center}
-    \note[item]{Research project's goal was to derive new causal compatibility inequalities that distinguish quantum correlations from classical correlations}
-    \note[item]{Triangle Scenario has be studied extensively before}
-    \note[item]{In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}}
-    \note[item]{In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)}
-    \note[item]{In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility (there are none)}
-    \note[item]{Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective}
 \end{frame}
@@
     \begin{enumerate}
-        \item Inflation technique provides polynomial inequalities
-        \item Inequalities witnessing non-local quantum correlations in the Triangle Scenario
-        \item Discuss search for new non-local quantum correlations
+        \item Motive why quantum-classical difference is worth studying
+        \item Explain why the triangle scenario is interesting
+        \item Briefly discuss how we obtained new measures of non-classicality
+        \item Discuss search for new non-classical quantum correlations
     \end{enumerate}
-    \note[item]{This talk is going to have three components}
-    \note[item]{Demonstrating how something called the inflation technique allows one derive polynomial compatibility constraints for and causal structure}
-    \note[item]{Using the inflation technique to find inequalities that demonstrate non-local quantum distributions on the Triangle scenario}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Quantum/Classical Discrepancies}
+    \textbf{Quantum Mechanics can do stuff that Classical Mechanics can't!}
+    \begin{itemize}
+        \item Quantum Information/Communication
+        \begin{itemize}
+            \item Quantum Key Distribution (QKD)
+        \end{itemize}
+    \end{itemize}
+    \begin{itemize}
+        \item Quantum Algorithms/Computation
+        \begin{itemize}
+            \item Shor's Algorithm, Quantum Simulated Annealing, String Matching, \ldots
+            \item Polynomial or even exponential advantage
+            \item \url{http://math.nist.gov/quantum/zoo/}
+        \end{itemize}
+    \end{itemize}
+    \begin{itemize}
+        \item Quantum Foundations
+        \begin{itemize}
+            \item Derivation of Bell inequalities
+            \item Abandoning local hidden variable theories (LHVs)
+        \end{itemize}
+    \end{itemize}
+    \textbf{Important to determine \textit{precisely} where quantum/classical differ, but how?}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Notation \& Jargon}
+    \begin{center}
+        Which observations are \textit{compatible} with a given classical model?
+    \end{center}
+    \begin{columns}
+        \column{0.45\textwidth}
+        \begin{center}
+            \textbf{Causal Structure $\graph$}\\
+            {\footnotesize (classical model)} \\
+            \[ \graph = \br{\nodes, \edges} \]
+            \vspace{-0.3in}
+            \begin{align*}
+                \edges &: \text{\term{causal influence}} \\
+                \nodes &: \text{\term{random variables}} \\
+                \nodes_{O} &: \text{\term{observable variables}} \\
+                \nodes_{L} &: \text{\term{latent variables}}
+            \end{align*}
+            \[ \nodes = \nodes_{O} \cup \nodes_{L} \]
+        \end{center}
+        \column{0.45\textwidth}
+        \begin{center}
+            \textbf{Marginal Model $\prob^{\mscenario}$} \\
+            {\footnotesize (observations)}
+            \[ \mscenario : \text{\term{marginal scenario}} \]
+            \[ \mscenario = \bc{V \mid V \subseteq \nodes_{O}} \]
+            \[ \prob^{\mscenario} = \bc{\prob[V] \mid V \in \mscenario} \]
+        \end{center}
+    \end{columns}
+\end{frame}
+
+\begin{frame}
+    \frametitle{The Triangle Scenario}
+    \begin{center}
+        \scalebox{1.5}{\input{../../figures/causal_structures/triangle_scenario}}
+    \end{center}
 \end{frame}
@@
     \frametitle{Causal Compatibility}
+    \textbf{Question:} Is $\prob^{\mscenario}$ \term{compatible} with $\graph$?\\
+    \textbf{Answer:} If $\prob^{\mscenario}$ is to be compatible with $\graph$ then:
+    \begin{enumerate}
+        \item $\prob^{\mscenario}$ must admit a \term{joint distribution} $\prob[\nodes]$:
+        \[ \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \]
+        \item $\prob[\nodes]$ must obey \term{Markov conditions}:
+        \[ \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
+    \end{enumerate}
+    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
+\end{frame}
+
+\begin{frame}
+    \frametitle{Classical (Compatible) Distributions for Triangle Scenario}
+    \[ \prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
+    \begin{center}
+        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Quantum Distributions for Triangle Scenario}
+    \[ \prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}} \]
+    \begin{center}
+        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Why Triangle Scenario?}
+    \begin{itemize}
+        \item Triangle scenario (TS) has be studied extensively before
+        \item In~\cite{Branciard_2012} it was noted that characterizing quantum non-classicality in TS remained an \textbf{open problem} and that identifying compatibility inequalities \textbf{seemed challenging}
+        \item In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which quantum non-classicality is manifest (proof without inequalities)
+        \item In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility (there are none)
+        \item Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have been unable to find inequalities with quantum violations
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Deriving Inequalities}
+    \begin{itemize}
+        \item Two necessary components to compatibility: joint distribution, Markov separability
+        \item It is possible to cast Markov separability problem into a joint distribution problem (at least partially)!
+        \item \term{Inflation Technique}\cref{Inflation} developed by E. Wolfe, R. Spekkens, T. Fritz provides tools for solving compatibility problem
+        \item \term{Definite Extension Procedure} developed by myself, E. Wolfe and others allows one to derive inequalities for \textbf{very large} causal structures
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Causal Compatibility Inequalities}
+    \begin{gather*}
+    P_{ABC}(000)P_{C}(3) \\
+    \leq \\
+    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \\
+    P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \\
+    P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \\
+    P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \\
+    P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \\
+    P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \\
+    P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \\
+    P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \\
+    P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \\
+    P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \\
+    P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) \\
+    \end{gather*}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Causal Compatibility Inequalities (Simplified)}
+    \begin{gather*}
+        P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + \\
+        P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
+        \leq \\
+        P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + \\
+        P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + P_{AB}(20) + P_{AB}(30) + P_{C}(3)P_{C}(0)
+    \end{gather*}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Certificate for Fritz Distribution}
+    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
     \vfill
-    \begin{center}
-        Triangle Scenario
-    \end{center}
-    \[ \prob[ABC] = \int_{XYZ}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
+    \textbf{Note:} $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
+\end{frame}
+
+\begin{frame}[shrink=64]
+    \frametitle{Certificate for Fritz Distribution (Full)}
+    \begin{center}
+        \input{../../figures/inequalities/nosymwitness_ineq_print}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Party Symmetric Inequality}
+    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print_pretty}
     \vfill
-    \begin{center}
-        \noindent\rule{8cm}{0.4pt}
-    \end{center}
-    \vfill
-    \begin{center}
-        General Setting
-    \end{center}
+    \textbf{Note:} $\bs{\prob[][113]\prob[][330]}_3$ shorthand sum over permutations:
+    \[ \prob[][113]\prob[][330] + \prob[][131]\prob[][303] + \prob[][311]\prob[][033] \]
+\end{frame}
+
+\begin{frame}[shrink=60]
+    \frametitle{Party Symmetric Inequality (Full)}
+    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Distribution}
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_brazil.pdf}
+    \end{center}
+    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Maximal Violation}
+    \includegraphics[width=\linewidth]{../../figures/distributions/plotted_dist_I_0_max_violation.pdf}
+    \[ \text{Relative Violation:} \qquad V_F = \f{\min_P\bc{I\br{P}}}{I\br{P_F}} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Maximal Violation Symmetric}
+    \includegraphics[width=\linewidth]{../../figures/distributions/plotted_dist_I_2_max_violation.pdf}
+    \[ \text{Relative Violation:} \qquad V_F = \f{\min_P\bc{I\br{P}}}{I\br{P_F}} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Uniform Noise}
+    \[ \s{U}_{\varepsilon}\br{P} = \br{1 - \varepsilon} P + \varepsilon \s{U} \]
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/distributions/uniform_dist_plot.pdf}
+    \end{center}
+    \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
+    % \begin{center}
+    %     \begin{tikzpicture}
+    %         \pgfmathsetmacro{\ts}{0.5}; % term spacing
+    %         \draw[] (0*\ts,0) node[]{$P_\varepsilon$};
+    %         \draw[] (1*\ts,0) node[]{$=$};
+    %         \draw[] (2*\ts,0) node[]{$(1-\varepsilon)P_{F}$};
+    %         \draw[] (3*\ts,0) node[]{$+$};
+    %         \draw[] (4*\ts,0) node[]{$\delta$};
+    %     \end{tikzpicture}
+    % \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Robust to Noise Zoomed}
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/noise/four_rep_inequalities_uniform_noise_zoomed.pdf}
+    \end{center}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Conclusions}
+    \begin{itemize}
+        \item Quantum/Classical difference can be observed in the triangle scenario
+        \item Successful demonstration of the inflation technique
+        \item Developed new algorithmic tools to find such inequalities
+        \item New measures of non-classicality which lead to new quantum mechanical resources
+    \end{itemize}
+\end{frame}
+
+\begin{frame}[allowframebreaks]
+    \frametitle{References}
+    \printbibliography
+\end{frame}
+
+\section{Appendix A: Optional Slides}
+
+\begin{frame}
+    \frametitle{Notation}
+    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
+    \begin{itemize}
+        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
+        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
+        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
+        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
+        % \item Marginal scenario forms a \textit{simplicial complex}
+        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
+        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
+        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
+        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
+    \end{itemize}
+    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
+    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
+    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
+    \note[item]{Marginal scenario refers to the those sets of random variables}
+    \note[item]{The complete set of random variables are the joint random variables}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Graph Theory}
+    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
+    \begin{itemize}
+        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
+        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
+        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
+        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
+    \end{itemize}
+    Notation extends to sets of nodes $N \subseteq \nodes$,
+    \begin{itemize}
+        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
+        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
+        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
+    \end{itemize}
+    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
+    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Causal Compatibility}
+    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
+    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
+    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
+    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
+    \begin{enumerate}
+        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
+        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
+    \end{enumerate}
+    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
+\end{frame}
+
+\begin{frame}
+    \frametitle{Deriving Inequalities}
+    Two necessary components to compatibility:
+    \begin{enumerate}
+        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
+        \begin{itemize}
+            \item Is the marginal model contextual or non-contextual?
+            \item 3 distinct ways to tackle this problem
+            \begin{enumerate}
+                \item Convex hull, Polytope projection, Fourier-Motzkin
+                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
+                \item Linear Program Feasibility/Infeasibility
+            \end{enumerate}
+        \end{itemize}
+        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
+        \begin{itemize}
+            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
+            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
+        \end{itemize}
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Technique}
+    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
+    \begin{definition}
+        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
+        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
+        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
+        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
+        And '$\sim$' is a \term{copy-index} equivalence relation
+        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
+    \end{definition}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Lemma}
+    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
+    \begin{enumerate}
+        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
+        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
+        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
+        \item Construct \term{inflated causal parameters}
+        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
+        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
+        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Lemma Cont'd}
+    \begin{itemize}
+        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
+        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
+    \end{itemize}
     \begin{align*}
-    \mscenario &= \bc{V_1, \ldots, V_n} \\
-    \prob^{\mscenario} &= \bc{\prob[V_1], \ldots, \prob[V_n]}
+        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}} \\
+        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
     \end{align*}
-    \[ \forall V \in \mscenario: \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \]
-    \[ \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
-    \vfill
-\end{frame}
-
-\section{Part 1: Inflation Technique}
+    \begin{itemize}
+        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
+        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inflation Lemma Cont'd}
+    \begin{lemma}
+        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+    \end{lemma}
+    \begin{corollary}
+        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
+    \end{corollary}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Pre-injectable Sets}
+    \begin{itemize}
+        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
+        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
+        \item A \term{pre-injectable set} $N'$:
+        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
+        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
+        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Network Permutation Matrix}
+    \begin{columns}
+        \column{0.6\linewidth}
+        \begin{itemize}
+            \item States and measurements in the Triangle Scenario are not aligned
+            \item Without $\netperm$, $\prob[ABC]$ would be separable
+            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
+            \item $\netperm$ is a $2^6 \times 2^6$ matrix
+            \item Shifts one qubit to the left
+        \end{itemize}
+        \column{0.4\linewidth}
+            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
+    \end{columns}
+    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Outcomes and Events}
+    \begin{definition}
+        Each variable $v$ has finite set of \term{outcomes} $O_v$. \\
+        Each set of variables $V$ has finite set of \term{events} $\Events{V}$:
+        \[ \Events{V} \defined \bc{s: V \to O_V \mid \forall v \in V, s\br{v} \in O_v} \]
+    \end{definition}
+    \begin{definition}
+        The set of events over the joint variables $\Events{\jointvar}$ are termed the \term{joint events}.
+    \end{definition}
+    \begin{definition}
+        The set of events over the marginal contexts are the \term{marginal events}
+        \[ \Events{\mscenario} \defined \coprod_{V \in \mscenario} \Events{V} \]
+    \end{definition}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Distribution Vectors}
+    \begin{definition}
+        The \term{joint distribution vector} $\probvec^{\jointvar}$
+        \[ \probvec^{\jointvar}_j = \prob[\jointvar][j] \quad \forall j \in \Events{\jointvar}\]
+    \end{definition}
+    \begin{definition}
+        The \term{marginal distribution vector} $\probvec^{\mscenario}$
+        \[ \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \quad \forall m \in \Events{\mscenario}, \Dom{m} \in \mscenario\]
+    \end{definition}
+    Can now write complete marginal problem as matrix multiplication:
+    \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \iff \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \]
+\end{frame}
+
+\begin{frame}
+    \frametitle{Incidence Matrix}
+    \begin{itemize}
+        \item \term{Incidence matrix} $M$ is a bit-wise matrix
+        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
+        \item Column-indexed by joint events $j \in \Events{\jointvar}$
+        \[ M_{m,j} = \begin{cases}
+            1 & m = j|_{\Dom{m}} \\
+            0 & \text{otherwise}
+        \end{cases} \]
+        \begin{gather*}
+        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
+        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
+        \end{gather*}
+
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Causal Symmetry}
+    \begin{itemize}
+        \item Desirable to find compatibility inequality $I$ such that
+        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
+        \item Compatibility is independent of variable labels $I, \graph \to \varphi\bs{I}, \varphi\bs{\graph}$
+        \item Need $\varphi\bs{\graph} = \graph$ to find new $\varphi\bs{I}$
+    \end{itemize}
+    \begin{definition}
+        The \term{causal symmetry group} of causal structure $\graph$:
+        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
+        Strictly speaking, one needs to preserve observable nodes:
+        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
+    \end{definition}
+    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
+    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e.
+inequality) that is symmetric under exchange of parties}
+    \note<1>[item]{Surprisingly, it is possible to do so!}
+    \note<1>[item]{Here is how.}
+    \note<1>[item]{First, we will formally define the symmetry group in question}
+    \note<1>[item]{Causal symmetry group is the group of automorphisms on causal structure}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Causal Symmetry and Inflation}
+    \begin{itemize}
+        \item Causal symmetry group for $\graph'$ is no good!
+        \item Not possible to deflate inequality if it's not in terms of injectable sets
+        \begin{definition}
+            The \term{restricted causal symmetry group} $\Phi$ of $\graph'$:
+            \[ \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
+        \end{definition}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Restricted Causal Symmetry of Large Inflation}
+    \begin{itemize}
+        \item $\Phi$ for the large inflation is an order $48$ group with $4$ generators
+    \end{itemize}
+    \begin{equation*}
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_1 \\
+    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_2 \\
+    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_3 \\
+    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\gep_4 \\
+    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
+    \end{aligned}
+    \end{equation*}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Symmetric Incidence}
+    \begin{itemize}
+        \item Group orbits through repeated action of $\varphi \in \Phi$ on $m \in \Events{\mscenario}$ and $j \in \Events{\jointvar}$
+    \end{itemize}
+    \begin{align*}
+        \Phi\bs{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \Phi} \\
+        \Phi\bs{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \Phi}
+    \end{align*}
+    \begin{itemize}
+        \item Construct \term{symmetric incidence matrix} $\Phi\bs{M}$
+    \end{itemize}
+    \[ \Phi\bs{M}_{\Phi\bs{m}, \Phi\bs{j}} = \sum_{m' \in \Phi\bs{m}}\sum_{j' \in \Phi\bs{j}} M_{m',j'} \]
+    \[ \Phi\bs{M} = \La_{\Phi\bs{\Events{\mscenario}}}\tcdot M \tcdot \La_{\Phi\bs{\Events{\jointvar}}} \]
+    \begin{itemize}
+        \item $\Phi\bs{M}$ not a bit-wise matrix like $M$
+        \item For large inflation $M$ is $16,896 \times 16,777,216$
+        \item For large inflation $\Phi\bs{M}$ is $450 \times 358,120$ % 3566922 entries
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Symmetric Inequalities}
+    \begin{itemize}
+        \item Certificate inequalities are curated/constructed to witness violation of particular distribution
+        \item Above inequality not the best candidate to search for non-locality different than Fritz distribution
+        \item Perhaps one could obtain inequality that does not assign special preference to $C$
+        \item Desirable to find compatibility inequality $I$ such that
+        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Symmetrized Fritz}
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/distributions/symmetrized_fritz.pdf}
+    \end{center}
+    \begin{itemize}
+        \item More non-local yet not quantum-accessible
+        \item Quantum-accessible distributions form non-context set
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Parameterizing POVMs}
+    \begin{itemize}
+        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
+        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
+        \item $n$-outcome measurement
+        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
+        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
+        \item Warrants consideration of \term{projective-valued measures (PVMs)}
+    \end{itemize}
+    \note<1>[item]{Naimark's Dilation Theorem}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Cholesky Parameterization of States}
+    \begin{itemize}
+        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite qubit state acting on $\Hilb^{d/2} \otimes \Hilb^{d/2}$
+        \item $d \times d$ positive semi-definite (PSD) hermitian matrices with unitary trace
+        \item \term{Cholesky Parametrization} allows one to write any hermitian PSD as $\rho = T^{\dagger} T$
+        \item For $d = 4$:
+        \[ T = \begin{bmatrix}\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}\end{bmatrix} \]
+        \item $d^2$ real-valued parameters
+        \item Normalized $\rho = {T^{\dagger}T}/{\Tr\br{T^{\dagger} T}}$ adds degeneracy
+    \end{itemize}
+\end{frame}
+
+\section{Appendix B: Local Minima Concerns}
+
+\begin{frame}
+    \frametitle{Results}
+    \begin{itemize}
+        \item Finding global minimum is tricky
+        \item Difficult to converge to violation
+        \item Noisy seed (Gaussian noise):
+        \[ \la_{(0)} = \la_{(F)} + \de \la \qquad \de \la_{i} \sim \s{N}\br{\mu = 0, \si^2 = (2\pi10^{\chi})^2} \]
+        \item Uniform seed:
+        \[ \la_{(0), i} \sim \s{U}\br{[0, 2\pi]} \]
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Local Minima}
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fritz Local Minima Zoomed}
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Max Entangled vs. Max Violating (???)}
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_random_seed.pdf}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Max Entangled vs. Max Violating (???)}
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_random_seed_Zoomed.pdf}
+\end{frame}
+
+\section{Section C: Inflation Technique}
 \begin{frame}
@@
         %\hline
-        \scalebox{0.5}{\input{../../figures/causal_structures/triangle_scenario}}
+        \scalebox{0.4}{\input{../../figures/causal_structures/inflated_triangle_scenario_wagon_wheel}}
         &
@@
         %\hline
-        The Triangle Scenario
+        Wagon Wheel Inflation
         &
@@
         &
-        Large Inflation \\
+        Web Inflation \\
         %\hline
@@
 
-\section{Part 2: Quantum Non-locality From Inflation}
-
-\begin{frame}
-    \frametitle{Quantum Correlation}
-    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
-    \begin{center}
-        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
-    \end{center}
-\end{frame}
+\section{Appendix D: Quantum Non-classicality From Inflation}
 
@@
 
-\begin{frame}
-    \frametitle{Certificate for Fritz Distribution}
-    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
-    \vfill
-    \textbf{Note:} $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
-\end{frame}
-
-\begin{frame}[shrink=64]
-    \frametitle{Certificate for Fritz Distribution (Full)}
-    \begin{center}
-        \input{../../figures/inequalities/nosymwitness_ineq_print}
-    \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Symmetric Inequalities}
-    \begin{itemize}
-        \item Certificate inequalities are curated/constructed to witness violation of particular distribution
-        \item Above inequality not the best candidate to search for non-locality different than Fritz distribution
-        \item Perhaps one could obtain inequality that does not assign special preference to $C$
-        \item Desirable to find compatibility inequality $I$ such that
-        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Party Symmetric Inequality}
-    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print_pretty}
-    \vfill
-    \textbf{Note:} $\bs{\prob[][113]\prob[][330]}_3$ shorthand sum over permutations:
-    \[ \prob[][113]\prob[][330] + \prob[][131]\prob[][303] + \prob[][311]\prob[][033] \]
-\end{frame}
-
-\begin{frame}[shrink=60]
-    \frametitle{Party Symmetric Inequality (Full)}
-    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
-\end{frame}
-
-\section{Part 3: Maximal Violations \& Noise}
+\section{Appendix F: Maximal Violations \& Noise}
 
@@
 
-\begin{frame}
-    \frametitle{Postdoc Opportunities At The Perimeter Institute}
-    \begin{center}
-    \textbf{Two Postdoctoral Fellowships in Quantum Foundations at the Perimeter Institute} \\
-    Project: \textit{Quantum Causal Structures} \\
-    \vfill
-    \begin{itemize}
-        \item How to define quantum causal models
-        \item Quantum causal inference
-        \item How to provide causal explanations of Bell inequality violations
-        \item Exploring the possibilities for indefinite causal structure
-    \end{itemize}
-    \vfill
-    {\scriptsize Application \& Info:}\\
-
-    The Perimeter Website $\to$ Research $\to$ Careers $\to$ Positions $\to$ Quantum Causal Structures Postdoctoral Fellowship
-    \textcolor{blue}{\url{https://www.perimeterinstitute.ca/2016/17-quantum-causal-structures-postdoctoral-fellowship}}
-    \vfill
-
-    {\scriptsize Funded by the John Templeton Foundation}
-    \end{center}
-
-\end{frame}
-
-\begin{frame}[allowframebreaks]
-    \frametitle{References}
-    \printbibliography
-\end{frame}
-
-\section{Appendix A: Optional Slides}
-
-\begin{frame}
-    \frametitle{Notation [Optional]}
-    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
-    \begin{itemize}
-        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
-        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
-        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
-        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        % \item Marginal scenario forms a \textit{simplicial complex}
-        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
-        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
-        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
-    \end{itemize}
-    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
-    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
-    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
-    \note[item]{Marginal scenario refers to the those sets of random variables}
-    \note[item]{The complete set of random variables are the joint random variables}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Graph Theory [Optional]}
-    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
-    \begin{itemize}
-        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
-        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
-        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
-        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
-    \end{itemize}
-    Notation extends to sets of nodes $N \subseteq \nodes$,
-    \begin{itemize}
-        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
-        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
-        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
-    \end{itemize}
-    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
-    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Causal Compatibility [Optional]}
-    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
-    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
-    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
-    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
-    \begin{enumerate}
-        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
-        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
-    \end{enumerate}
-    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
-\end{frame}
-
-\begin{frame}
-    \frametitle{Deriving Inequalities [Optional]}
-    Two necessary components to compatibility:
-    \begin{enumerate}
-        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
-        \begin{itemize}
-            \item Is the marginal model contextual or non-contextual?
-            \item 3 distinct ways to tackle this problem
-            \begin{enumerate}
-                \item Convex hull, Polytope projection, Fourier-Motzkin
-                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
-                \item Linear Program Feasibility/Infeasibility
-            \end{enumerate}
-        \end{itemize}
-        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
-        \begin{itemize}
-            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
-            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
-        \end{itemize}
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Technique [Optional]}
-    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
-    \begin{definition}
-        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
-        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
-        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
-        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
-        And '$\sim$' is a \term{copy-index} equivalence relation
-        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
-    \end{definition}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Lemma [Optional]}
-    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
-    \begin{enumerate}
-        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
-        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
-        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
-        \item Construct \term{inflated causal parameters}
-        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
-        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
-        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Lemma Cont'd [Optional]}
-    \begin{itemize}
-        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
-        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
-    \end{itemize}
-    \begin{align*}
-        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}} \\
-        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
-    \end{align*}
-    \begin{itemize}
-        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
-        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Lemma Cont'd [Optional]}
-    \begin{lemma}
-        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-    \end{lemma}
-    \begin{corollary}
-        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
-    \end{corollary}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Pre-injectable Sets [Optional]}
-    \begin{itemize}
-        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
-        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
-        \item A \term{pre-injectable set} $N'$:
-        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
-        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
-        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Network Permutation Matrix [Optional]}
-    \begin{columns}
-        \column{0.6\linewidth}
-        \begin{itemize}
-            \item States and measurements in the Triangle Scenario are not aligned
-            \item Without $\netperm$, $\prob[ABC]$ would be separable
-            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
-            \item $\netperm$ is a $2^6 \times 2^6$ matrix
-            \item Shifts one qubit to the left
-        \end{itemize}
-        \column{0.4\linewidth}
-            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
-    \end{columns}
-    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Outcomes and Events [Optional]}
-    \begin{definition}
-        Each variable $v$ has finite set of \term{outcomes} $O_v$. \\
-        Each set of variables $V$ has finite set of \term{events} $\Events{V}$:
-        \[ \Events{V} \defined \bc{s: V \to O_V \mid \forall v \in V, s\br{v} \in O_v} \]
-    \end{definition}
-    \begin{definition}
-        The set of events over the joint variables $\Events{\jointvar}$ are termed the \term{joint events}.
-    \end{definition}
-    \begin{definition}
-        The set of events over the marginal contexts are the \term{marginal events}
-        \[ \Events{\mscenario} \defined \coprod_{V \in \mscenario} \Events{V} \]
-    \end{definition}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Distribution Vectors [Optional]}
-    \begin{definition}
-        The \term{joint distribution vector} $\probvec^{\jointvar}$
-        \[ \probvec^{\jointvar}_j = \prob[\jointvar][j] \quad \forall j \in \Events{\jointvar}\]
-    \end{definition}
-    \begin{definition}
-        The \term{marginal distribution vector} $\probvec^{\mscenario}$
-        \[ \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \quad \forall m \in \Events{\mscenario}, \Dom{m} \in \mscenario\]
-    \end{definition}
-    Can now write complete marginal problem as matrix multiplication:
-    \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \iff \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Incidence Matrix [Optional]}
-    \begin{itemize}
-        \item \term{Incidence matrix} $M$ is a bit-wise matrix
-        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
-        \item Column-indexed by joint events $j \in \Events{\jointvar}$
-        \[ M_{m,j} = \begin{cases}
-            1 & m = j|_{\Dom{m}} \\
-            0 & \text{otherwise}
-        \end{cases} \]
-        \begin{gather*}
-        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
-        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
-        \end{gather*}
-
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Causal Symmetry [Optional]}
-    \begin{itemize}
-        \item Desirable to find compatibility inequality $I$ such that
-        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
-        \item Compatibility is independent of variable labels $I, \graph \to \varphi\bs{I}, \varphi\bs{\graph}$
-        \item Need $\varphi\bs{\graph} = \graph$ to find new $\varphi\bs{I}$
-    \end{itemize}
-    \begin{definition}
-        The \term{causal symmetry group} of causal structure $\graph$:
-        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
-        Strictly speaking, one needs to preserve observable nodes:
-        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
-    \end{definition}
-    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
-    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e.
-inequality) that is symmetric under exchange of parties}
-    \note<1>[item]{Surprisingly, it is possible to do so!}
-    \note<1>[item]{Here is how.}
-    \note<1>[item]{First, we will formally define the symmetry group in question}
-    \note<1>[item]{Causal symmetry group is the group of automorphisms on causal structure}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Causal Symmetry and Inflation [Optional]}
-    \begin{itemize}
-        \item Causal symmetry group for $\graph'$ is no good!
-        \item Not possible to deflate inequality if it's not in terms of injectable sets
-        \begin{definition}
-            The \term{restricted causal symmetry group} $\Phi$ of $\graph'$:
-            \[ \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
-        \end{definition}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Restricted Causal Symmetry of Large Inflation [Optional]}
-    \begin{itemize}
-        \item $\Phi$ for the large inflation is an order $48$ group with $4$ generators
-    \end{itemize}
-    \begin{equation*}
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_1 \\
-    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_2 \\
-    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_3 \\
-    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_4 \\
-    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
-    \end{aligned}
-    \end{equation*}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Symmetric Incidence [Optional]}
-    \begin{itemize}
-        \item Group orbits through repeated action of $\varphi \in \Phi$ on $m \in \Events{\mscenario}$ and $j \in \Events{\jointvar}$
-    \end{itemize}
-    \begin{align*}
-        \Phi\bs{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \Phi} \\
-        \Phi\bs{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \Phi}
-    \end{align*}
-    \begin{itemize}
-        \item Construct \term{symmetric incidence matrix} $\Phi\bs{M}$
-    \end{itemize}
-    \[ \Phi\bs{M}_{\Phi\bs{m}, \Phi\bs{j}} = \sum_{m' \in \Phi\bs{m}}\sum_{j' \in \Phi\bs{j}} M_{m',j'} \]
-    \[ \Phi\bs{M} = \La_{\Phi\bs{\Events{\mscenario}}}\tcdot M \tcdot \La_{\Phi\bs{\Events{\jointvar}}} \]
-    \begin{itemize}
-        \item $\Phi\bs{M}$ not a bit-wise matrix like $M$
-        \item For large inflation $M$ is $16,896 \times 16,777,216$
-        \item For large inflation $\Phi\bs{M}$ is $450 \times 358,120$ % 3566922 entries
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Symmetrized Fritz [Optional]}
-    \begin{center}
-        \includegraphics[width=\linewidth]{../../figures/distributions/symmetrized_fritz.pdf}
-    \end{center}
-    \begin{itemize}
-        \item More non-local yet not quantum-accessible
-        \item Quantum-accessible distributions form non-context set
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing POVMs [Optional]}
-    \begin{itemize}
-        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
-        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
-        \item $n$-outcome measurement
-        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
-        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
-        \item Warrants consideration of \term{projective-valued measures (PVMs)}
-    \end{itemize}
-    \note<1>[item]{Naimark's Dilation Theorem}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Cholesky Parameterization of States [Optional]}
-    \begin{itemize}
-        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite qubit state acting on $\Hilb^{d/2} \otimes \Hilb^{d/2}$
-        \item $d \times d$ positive semi-definite (PSD) hermitian matrices with unitary trace
-        \item \term{Cholesky Parametrization} allows one to write any hermitian PSD as $\rho = T^{\dagger} T$
-        \item For $d = 4$:
-        \[ T = \begin{bmatrix}\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}\end{bmatrix} \]
-        \item $d^2$ real-valued parameters
-        \item Normalized $\rho = {T^{\dagger}T}/{\Tr\br{T^{\dagger} T}}$ adds degeneracy
-    \end{itemize}
-\end{frame}
-
-\section{Appendix B: Local Minima Concerns}
-
-\begin{frame}
-    \frametitle{Results [Optional]}
-    \begin{itemize}
-        \item Finding global minimum is tricky
-        \item Difficult to converge to violation
-        \item Noisy seed (Gaussian noise):
-        \[ \la_{(0)} = \la_{(F)} + \de \la \qquad \de \la_{i} \sim \s{N}\br{\mu = 0, \si^2 = (2\pi10^{\chi})^2} \]
-        \item Uniform seed:
-        \[ \la_{(0), i} \sim \s{U}\br{[0, 2\pi]} \]
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Local Minima [Optional]}
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Local Minima Zoomed [Optional]}
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Max Entangled vs. Max Violating (???) [Optional]}
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_random_seed.pdf}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Max Entangled vs. Max Violating (???) [Optional]}
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_random_seed_Zoomed.pdf}
-\end{frame}
-
+% \begin{frame}
+%     \frametitle{Postdoc Opportunities At The Perimeter Institute}
+%     \begin{center}
+%     \textbf{Two Postdoctoral Fellowships in Quantum Foundations at the Perimeter Institute} \\
+%     Project: \textit{Quantum Causal Structures} \\
+%     \vfill
+%     \begin{itemize}
+%         \item How to define quantum causal models
+%         \item Quantum causal inference
+%         \item How to provide causal explanations of Bell inequality violations
+%         \item Exploring the possibilities for indefinite causal structure
+%     \end{itemize}
+%     \vfill
+%     {\scriptsize Application \& Info:}\\
+
+%     The Perimeter Website $\to$ Research $\to$ Careers $\to$ Positions $\to$ Quantum Causal Structures Postdoctoral Fellowship
+%     \textcolor{blue}{\url{https://www.perimeterinstitute.ca/2016/17-quantum-causal-structures-postdoctoral-fellowship}}
+%     \vfill
+
+%     {\scriptsize Funded by the John Templeton Foundation}
+%     \end{center}
+
+% \end{frame}
 \end{document}

### 2017-01-04 documents/Notes/WagonWheel.tex
slides for 437 talk

\documentclass[12pt]{article}

\usepackage[dvipsnames]{xcolor}
\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}
\input{../../figures/causal_structures/formatting} % Causal structure formatting for tikz

\begin{document}

    \textbf{Rosset Variation:}\\

    Considering the \term{WagonWheel} inflation depicted below,

    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_wagon_wheel}}
    \end{center}

    And the usual \term{Fritz distribution},

    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plotted.pdf}
    \end{center}

    The maximal pre-injectable sets are,

    \begin{align*}
        \bc{\bc{A_2, B_1, C_3}, \bc{C_1}} \\
        \bc{\bc{A_1, B_1, C_4}, \bc{C_2}} \\
        \bc{\bc{A_1, B_2, C_1}, \bc{C_3}} \\
        \bc{\bc{A_2, B_2, C_2}, \bc{C_4}} \\
    \end{align*}

    And they define an incidence matrix that is $1024 \times 65,536$. Using the \term{Definite Extension Procedure} to first order (i.e. single antecedent) I can derive the following representative inequality:

    \begin{gather*}
    P_{ABC}(000)P_{C}(3) \\
    \leq \\
    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \\
    P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \\
    P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \\
    P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \\
    P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \\
    P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \\
    P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \\
    P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \\
    P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \\
    P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \\
    P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) \\
    \end{gather*}

    That witnesses the Fritz distribution with violation,
    \[ -0.0129428304698 \]
    \textit{Quite interestingly}, all my numerical attempts to violate further are fruitless (only improving on the violation in the $6$-th decimal place $-0.0129437678359$). Therefore, it seems that the Fritz distribution is a local minima of this inequality! This inequality also suffers from the global minima issues; any significant deviation from parameters that generate the Fritz distribution results in a null result (the optimization tends toward inequality saturation).\\

    Regarding noise, it seems that this inequality is \textit{less robust} to noise than some of the ones generated via the web inflation (crossing the saturation point around $\ep \approx 0.07$ instead of $\ep \approx 0.08$),

    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/noise/wagon_wheel_12.pdf}
    \end{center}

    More importantly, you asked about the \term{Rosset Variation} to the Fritz distribution where $C$ announces $A\tsb{in} \cdot B\tsb{in}$ instead of the usual $\bc{A\tsb{in},B\tsb{in}}$

    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/rosset_variation_plotted.pdf}
    \end{center}

    \textit{Very interestingly}, it turns out that this distribution \textbf{can not} be witnessed by first order inequalities! This is so surprising to me that I in doubt; Did you manage to witness this as a first order inequality? If so, then there is something broken in my code.\\

    If I am correct, this suggests something very interesting. Additionally, I am interested in checking this Rosset Variation against the large/web inflation in order to see if first order inequalities can be found there. I have been reluctant to do this myself as my laptop does not possess the computing requirements and my desktop machine at home can be unreliable. Let me know if this is worth pursuing. Additionally, I will be implementing the definition extension procedure in full over the next few weeks so it will be interesting to see at what order the Rosset Variation can be witnessed. \\

    \textbf{Compactifying Inequalities:}\\

    In addition, I attempted to find a way to compactify the notation/terms present in some of the inequalities we have found thus far. I attempted to write some code to this but made insignificant progress. The process is still very manual and the compactified inequalities are still hard to interpret. For example, the inequality presented above can be written as:

    \begin{gather*}
        P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + \\
        P_{ABC}(202) + P_{ABC}(302) + \\
        P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
        \leq \\ P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + \\
        P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + P_{AB}(20) + P_{AB}(30) + \\
        P_{C}(3)P_{C}(0)
    \end{gather*}

    Of course, this inequality is the result of a \textit{canonical minimalization}. Without minimalizing the inequalities (i.e. keeping all of the zero-weighted terms pursuant to the Fritz distribution) one obtains,

    \begin{gather*}
        P_{ABC}(000)P_{C}(3) + P_{ABC}(003)P_{C}(0) + P_{ABC}(103)P_{C}(0) + \\
        P_{ABC}(000) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(100) \\
        \leq \\
        P_{B}(0) + \\
        P_{AC}(03)P_{C}(0) + P_{AC}(13)P_{C}(0) + \\
        P_{AC}(02) + P_{AC}(03) + \\
        P_{BC}(03)P_{C}(0) + \\
        P_{ABC}(011) + P_{ABC}(020) + P_{ABC}(030) + P_{ABC}(001) + \\
        P_{ABC}(031)P_{C}(2) + P_{ABC}(223)P_{C}(0) + P_{ABC}(302)P_{C}(1) + \\
        P_{ABC}(213)P_{C}(0) + P_{ABC}(313)P_{C}(0)
    \end{gather*}

\end{document}

### 2017-01-04 documents/437Slides/slides.tex
Yevick suggestions

@@
 
-\begin{frame}
-    \frametitle{This Talk}
-    \begin{enumerate}
-        \item Motive why quantum-classical difference is worth studying
-        \item Explain why the triangle scenario is interesting
-        \item Briefly discuss how we obtained new measures of non-classicality
-        \item Discuss search for new non-classical quantum correlations
-    \end{enumerate}
-\end{frame}
+% \begin{frame}
+%     \frametitle{This Talk}
+%     \begin{enumerate}
+%         \item Motive why quantum-classical difference is worth studying
+%         \item Explain why the triangle scenario is interesting
+%         \item Briefly discuss how we obtained new measures of non-classicality
+%         \item Discuss search for new non-classical quantum correlations
+%     \end{enumerate}
+% \end{frame}
 
@@
     \begin{center}
-        Which observations are \textit{compatible} with a given classical model?
+        Given a set of observations, are they \textit{compatible} with a given classical model?
     \end{center}
@@
             \textbf{Marginal Model $\prob^{\mscenario}$} \\
-            {\footnotesize (observations)}
+            {\footnotesize (set of observations)}
             \[ \mscenario : \text{\term{marginal scenario}} \]
@@
 \begin{frame}
-    \frametitle{The Triangle Scenario}
-    \begin{center}
-        \scalebox{1.5}{\input{../../figures/causal_structures/triangle_scenario}}
-    \end{center}
-\end{frame}
-
-\begin{frame}
     \frametitle{Causal Compatibility}
+    \textbf{Question:} Can your model $\graph$ explain the observation $\prob^{\mscenario}$?\\
     \textbf{Question:} Is $\prob^{\mscenario}$ \term{compatible} with $\graph$?\\
+    \vspace{0.3in}
     \textbf{Answer:} If $\prob^{\mscenario}$ is to be compatible with $\graph$ then:
@@
         \[ \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \]
-        \item $\prob[\nodes]$ must obey \term{Markov conditions}:
+        \item $\prob[\nodes]$ must obey \term{Markov conditions} (independence given parents):
         \[ \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
     \end{enumerate}
-    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
+\end{frame}
+
+\begin{frame}
+    \frametitle{Inequalities}
+    \textbf{Task:} Determine if $\prob^{\mscenario}$ is \term{compatible} or \term{incompatible} with $\graph$\\
+    \vspace{0.3in}
+    \textbf{Tool:} A \term{casual compatibility inequality} $I$ is an inequality satisfied by all compatible $\prob^{\mscenario}$
+    \vspace{0.3in}
+    \begin{itemize}
+        \item Inequalities $I$ are \textbf{extremely useful}:
+        \item If $\prob^{\mscenario}$ satisfies \textit{all} such constraints $I$, then it is \textit{compatible} with $\graph$
+        \item If $\prob^{\mscenario}$ violates \textit{any} constraint $I$, then it is \textit{incompatible} with $\graph$
+        \item Inequalities act as \textit{measures} of non-classicality
+        \item $I$ identifies \textit{fundamentally} new resources or quantum advantages!
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Case Study: The Triangle Scenario}
+    \begin{center}
+        \scalebox{1.5}{\input{../../figures/causal_structures/triangle_scenario}}
+    \end{center}
 \end{frame}
@@
     \begin{itemize}
-        \item Triangle scenario (TS) has be studied extensively before
+        \item The TS could be home to \textbf{brand new} entanglement resources which could lead to new technologies and fundamental physics, albeit very difficult to find
         \item In~\cite{Branciard_2012} it was noted that characterizing quantum non-classicality in TS remained an \textbf{open problem} and that identifying compatibility inequalities \textbf{seemed challenging}

### 2017-01-04 documents/437Slides/slides.tex
Updates from ShareLaTeX

--- 2017-01-04 documents/437Slides/slides.tex
@@
         \item It is possible to cast Markov separability problem into a joint distribution problem (at least partially)!
-        \item \term{Inflation Technique}\cref{Inflation} developed by E. Wolfe, R. Spekkens, T. Fritz provides tools for solving compatibility problem
+        \item \term{Inflation Technique}~\cite{Inflation} provides tools for solving compatibility problem
         \item \term{Definite Extension Procedure} developed by myself, E. Wolfe and others allows one to derive inequalities for \textbf{very large} causal structures

### 2017-01-17 documents/TriangleScenario/ts.tex
finished 437 report

@@
 \usepackage{../../packages/misc_commands}
+\usepackage{subcaption}
+\usepackage{enumitem}
+
+\renewcommand{\Events}[1]{\mathcal{S}\br{#1}}
+\renewcommand{\tcdot}{\cdot}
 
@@
         Quantum correlations are often incompatible with a classical assumption of causal structure.
-This nonclassicality is often known as quantum nonlocality, and it is witnessed through the violation of causal compatibility inequalities, such as Bell inequalities.
-Such inequalities were recently derived for the Triangle scenario [arXiv:1609.00672], begging the question: can these inequalities be violated by quantum correlations?
-Here we answer this affirmatively, and discuss specific Triangle scenario inequalities and quantum configurations which manifest nonclassical correlations.
-Numerical optimzations reveal quantum resources potentially qualitatively different from those known previously.
+This non-classicality is often known as quantum non-locality, and it is witnessed through the violation of causal compatibility inequalities, such as Bell inequalities.
+Such inequalities were recently derived for the triangle scenario [arXiv:1609.00672], begging the question: can these inequalities be violated by quantum correlations?
+Here we answer this affirmatively, and discuss specific triangle scenario inequalities and quantum configurations which manifest non-classical correlations.
+Numerical optimizations reveal quantum resources potentially qualitatively different from those known previously.
     \end{abstract}
@@
     \tableofcontents
+    \clearpage
 
     \section{Introduction}
-    \begin{itemize}
-        \item \todo[TC]{Overview of importance of inequalities}
-        \item \todo[TC]{Triangle Scenario and existing work}
-        \item \todo[TC]{Objective of research project}
-        \item \todo[TC]{Structure of this paper}
-    \end{itemize}
+    \label{sec:introduction}
+    In recent decades, the technical utility of quantum mechanics has become abundantly clear; quantum computational algorithms such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016} maintain advantage over their classical counterparts.
+Additionally, classical communications technologies stand to benefit from the nature of quantum mechanics --- a popular example being Quantum Key Distribution~\cite{Bennett_2014}.
+Any time classical resources are unable to emulate quantum mechanics, there represents an opportunity to exploit the non-classical features of quantum mechanics in order to solve a variety of computational and communicational problems~\cite{Neilsen_Chaung_2011}.
+Albeit, not all tasks stand to benefit from quantum resources~\cite{Almeida_2010}.
+Presently, discovering situations or tasks where quantum mechanics offers an advantage, and proving that advantage is genuine, is a primal objective of theoretical quantum information theory.
+\\
+
+    From a foundational prospective, the majority of attempts to characterize precisely where quantum mechanics and classical mechanics differ have involved Bell inequalities~\cite{Bell_1964}.
+Originally, Bell inequalities were derived in response to the famous EPR paradox~\cite{EPR_Orig} to rule out hidden variable theories for quantum mechanics.
+Studying and discovering Bell-type inequalities is useful because a complete set of Bell inequalities provides a systematic way of classifying the \textit{classicality} of a given observation.
+These inequalities are best understood from the perspective of \term{causal inference} --- a problem which aims to determine which observations can or can not be explained by a hypothesized causal structure.
+The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}.
+Inequalities such as Bell inequalities constrain the space of observations that are compatible with a hypothesized causal structure.
+In the case of the original Bell inequalities, the classical causal model in question is known as the Bell scenario~\cite{Wood_2012} and is depicted in \cref{fig:bell_scenario}.
+The Bell scenario involves two parties ($A, B$) who each make measurements decided by random settings ($S_A, S_B$) on a shared hidden resource $\la$.
+Quantum non-classicality in the Bell scenario and related structures have been studied thoroughly since Bell's original work~\cite{Brunner_2013}.
+However, novel scenarios such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014} are arguably less understood compared to the Bell scenario.
+Here we investigate one particular causal scenario: the triangle scenario (\cref{fig:triangle_scenario}).
+\\
+
+    The triangle scenario (\cref{fig:triangle_scenario}) is a causal structure composed of $3$ parties labeled $A, B, C$ arranged in a triangular configuration while pair-wise sharing hidden/latent variables $X, Y, Z$.
+It has been studied extensively in literature before (see~\cite[Fig.
+1]{Steudel_2010},~\cite[Fig.
+6]{Chaves_2014},~\cite[Fig.
+8]{Branciard_2012},~\cite[Fig.
+8, Appendix E]{Henson_2014},~\cite[Fig.
+3]{Fritz_2012},~\cite[Fig.
+1]{Inflation}, $\ldots$).
+A healthy portion of which the existing literature will be discussed in \cref{sec:triangle_scenario}.
+For instance \citet{Branciard_2012} noted that characterizing locality in the triangle scenario remained an \textit{open problem} and that identifying causal compatibility inequalities for this configuration \textit{seemed challenging}.
+The subject of this document is to expound on the developments made towards understanding quantum non-classicality in the triangle scenario.
+\\
+
+    As a preliminary summary, causal compatibility inequalities were derived for the triangle scenario that are able to be violated by specific quantum-accessible distributions.
+This was accomplished by combining two previous works.
+The first, an insight made by \citet{Fritz_2012} regarding the ability to re-interpret the Bell scenario as a portion of the triangle scenario.
+The second, a new framework for solving causal inference problems developed by Wolfe \emph{et al.}~\cite{Inflation} called \term{The Inflation Technique}.
+Ultimately, this work serves as a strong indication that the Inflation Technique offers new insights into specifically quantum non-classicality.
+Moreover, these new inequalities offer an avenue for finding and identifying new forms of non-classicality unknown previously.
+This report discusses attempts to find such resources with partial success and outlines refinements that can be made for future exploration.\\
+
+    The following paper is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used.
+\Cref{sec:triangle_scenario} discusses the triangle scenario and its existing research in detail; identifying its stark differences from the Bell scenario and motivates why the triangle scenario was chosen as a case study.
+\Cref{sec:fritz_distribution} defines and discusses a singular quantum correlation first discovered by \citet{Fritz_2012} which we term the \term{Fritz distribution}.
+The Fritz distribution was proven to be non-classical without the use of inequalities --- this report derives inequalities that do.
+\Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the context of this work.
+Although the summary presented here is sufficient, the original work~\cite{Inflation} offers a more concrete and pedagogical introduction.
+\Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the triangle scenario that are violated by quantum-accessible distributions.
+A sample of these inequalities are presented at the end of \cref{sec:deriving_inequalities} as well as \cref{sec:web_inequality,sec:symmetic_web_inequality}.
+Finally, \cref{sec:violations_noise} mentions a method for parameterizing the space of quantum-accessible distributions which is used to numerically optimize against our derived inequalities in search of stronger types of non-classicality.
+Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.
 
     \section{Causal Compatibility}
-    \begin{itemize}
-        \item \todo[TC]{Define marginal scenario}
-        \item \todo[TC]{Define marginal model}
-        \item \todo[TC]{Define causal structure}
-        \item \todo[TC]{Define compatibility}
-    \end{itemize}
+    \label{sec:causal_compatibility}
+    The task of causal inference aims to determine whether or not a given family of observed probability distributions can be explained by a proposed causal mechanism~\cite{Pearl_2009}.
+If a set of observed distributions can be explained by the hypothesized causal mechanism, then the observations are said to be \textit{compatible} with the causal mechanism.
+In order to define compatibility rigorously, we first need to formally define what is meant by ``set of observations''.
+
+    \subsection{Marginal Models}
+    Given a set of observable variables $\jointvar = \bc{v_1, \ldots, v_k}$ where each $v \in \jointvar$ is a statistical random variable, one can conceivably make a measurement over of these variables and obtain a joint probability distribution $\prob[\jointvar] = \prob[v_1,\ldots,v_n]$.
+More generally however, and depending on the context, it is possible to make a measurement on a portion of the system $V \subset \jointvar$ in order to obtain a marginal distribution $\prob[V]$.
+With complete generality however, one could in principle make a measurement on a collection of portions of the system $\mscenario = \bc{V_1, \ldots, V_m \mid \forall i : V_i \subseteq \jointvar}$ obtaining a collection of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_m] \mid \forall i: V_i \in \mscenario}$.
+\\
+
+    The set $\mscenario = \bc{V \mid V \subseteq \jointvar}$ of subsets of $\jointvar$ is referred to as the \term{marginal scenario} and each element $V \in \mscenario$ is termed a \term{(marginal) context} of $\mscenario$.
+The complete set of marginal distributions is referred to as the \term{marginal model} and is denoted with an superscript $\prob^{\mscenario}$:
+    \[ \prob^{\mscenario} = \bc{\prob[V] \mid V \in \mscenario} \]
+    A marginal model acts as the most general description of a family of observations that can be made over $\jointvar$.
+Strictly speaking, as defined by~\cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that all subsets of contexts are also contexts.
+    \[ \forall V \in \mscenario, V' \subset V : V' \in \mscenario \]
+    Throughout this document, we only consider (without loss of generality) the \textit{maximal} marginal scenario; restricting our focus to the largest contexts in the marginal scenario.
+Additionally, all marginal scenarios are taken to be \text{complete} in the sense that the marginal scenario covers the complete set of observable variables $\jointvar$.
+    \[ \jointvar = \bigcup_{V \in \mscenario} V \]
+
+    \subsection{Causal Structure}
+    A \term{causal structure} abstractly represents the hypothesized causal mechanism.
+Mathematically, a causal structure is a directed acyclic graph $\graph = \br{\nodes, \edges}$ of nodes $\nodes$ and edges $\edges$ as defined in \cref{sec:graph_theory}.
+The nodes of a causal structure are random variables and are classified into two disjoint classes: the \term{latent nodes} $\nodes_L$ representing the set of nodes that are unobservable and the \term{observed nodes} $\nodes_O$.
+The latent nodes of a causal structure represent completely hidden variables that are hidden by some fundamental process or cannot be measured due to other limitations.
+The observed nodes represent random variables that are measurable and in practice will be observed by the marginal model $\prob^\mscenario$.
+The edges $\edges$ of a causal structure represent casual influence between variables within the causal structure.
+\\
+
+    A number of causal structures are depicted throughout this document (see \cref{fig:bell_scenario,fig:triangle_scenario} as well as \cref{fig:inflations}).
+As an example, the triangle scenario has $3$ observable nodes and $3$ latent nodes,
+    \[ \nodes_{O} = \bc{A, B, C} \qquad \nodes_{L} = \bc{X, Y, Z} \]
+    along with $6$ edges indicating that the latent nodes $\bc{X, Y, Z}$ cause and influence the observed nodes $\bc{A, B, C}$.
+    \[ \edges = \bc{\bc{X \to A}, \bc{Y \to A}, \bc{Y \to B}, \bc{Z \to B}, \bc{Z \to C}, \bc{X \to C}} \]
+
+    \subsection{Compatibility}
+    \label{sec:compatibility}
+
+    Now that the notions of a causal structure $\graph$ and a marginal model $\prob^{\mscenario}$ are defined, it is now possible to precisely define the notion of compatibility between the two.
+Intuitively, the causal connections within $\graph$ should restrict and limit the set of possible observations that can be made on $\graph$.
+Namely, if each variable $n \in \nodes$ is caused by its parents $\Pa[\graph]{n}$, then $n$ should be independent of all other variables that are not its descendants.
+This is known as the \term{local Markov property}:
+    \[ n \indep \nodes \setminus \De[\graph]{n} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
+    Where $\indep$ denotes statistical independence.
+With this as motivation, we define a set of \term{causal parameters} for a causal structure $\graph$ to be a specification of a conditional distribution for every variable $n \in \nodes$ given its parents:
+    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \eq \label{eq:causal_parameters} \]
+    It is important to note that a set of causal parameters is not unique; the numerical nature of set of causal parameters is a \text{choice}.
+Altogether, a marginal model $\prob^{\mscenario}$ is \term{compatible} with a causal structure $\graph$ if there exists a choice of causal parameters such that each context $\prob[V] \in \prob^{\mscenario}$ can be \textit{recovered} from the following series of operations:
+    \begin{enumerate}
+        \item Obtain a joint probability distribution over \textit{all} variables of the causal structure using the chosen casual parameters:\footnote{Here $\prod$ denotes the product distribution $\prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}]$.}
+        \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] \eq \label{eq:local_markov_property_operation}\]
+        This step ensures that the local Markov property (\cref{eq:causal_parameters}) holds for all variables $n \in \nodes$.
+        \item Marginalize over the latent variables of $\graph$ to obtain a joint distribution over the observed variables $\nodes_O$:
+        \[ \prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes] \eq \label{eq:observable_marginalization} \]
+        \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$:
+        \[ \prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O] \eq \label{eq:context_marginalization} \]
+    \end{enumerate}
+    It is important to note that compatibility between $\prob^{\mscenario}$ and $\graph$ requires that it is possible to recover \textit{each} context $\prob[V] \in \prob^{\mscenario}$ from the \textit{same} set of causal parameters.
+If it is not possible for $\prob^{\mscenario}$ to be recovered for \textit{any} choice of causal parameters, then $\prob^{\mscenario}$ is \term{incompatible}.
+
+    \subsection{Inequalities}
+    As defined in \cref{sec:compatibility}, determining compatibility is equivalent to determining if a set of causal parameters exists with the above-mentioned properties.
+In practice however, checking causal parameters systemically is intractable, especially when the cardinality (number of outcomes) of the latent variables is unspecified.
+Instead, \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of simply Bell inequalities for two reasons.
+First, ``Bell inequalities'' usually are associated specifically with the Bell scenario/Bell causal structure.
+Second, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob^{\mscenario}$ instead of \textit{linear}.} are probabilistic inequalities defined over the marginal contexts $\prob[V] \in \prob^{\mscenario}$ within the marginal model.
+If a marginal model $\prob^{\mscenario}$ happens to \textit{violate} any causal compatibility inequality, then that marginal model is definitely \textit{incompatible}.
+In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.\\
+
+    Unfortunately, a singular inequality can not prove that a given marginal model is \textit{compatible}, only \textit{incompatible}.
+Instead, a \textit{complete characterization} of compatibility would consist of a complete set of all valid causal compatibility inequalities; satisfaction of a complete set of inequalities does prove compatibility.
+Currently however, it is unknown how to obtain a complete characterization for any given causal structure, including the triangle scenario.
+\\
+
+    From the perspective of identifying quantum non-classicality, the causal structure $\graph$ acts as the classical hypothesis for a particular marginal model $\prob^{\mscenario}$.
+Therefore, non-classicality becomes synonymous with incompatibility: if a marginal model $\prob^{\mscenario}$ is incompatible, then it is non-classical.
+Henceforth, we will use these two terms interchangeably.
+From a resource standpoint, if the non-classicality of $\prob^{\mscenario}$ can be witnessed by an inequality $I$, but $\prob^{\mscenario}$ can be implemented using quantum states and measurements, then the causal compatibility inequality $I$ represents a concrete task where quantum resources out-perform classical resources.
 
     \section{Triangle Scenario}
-    \begin{itemize}
-        \item \todo[TC]{Discuss some of its appearances in other work}
-        \item \todo[TC]{Figure}
-    \end{itemize}
-    \subsection{Fritz Distribution}
+    \label{sec:triangle_scenario}
+
+    \begin{figure}
+    \begin{center}
+        \begin{minipage}[t]{.48\textwidth}
+            \centering
+            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
+            \caption{The Bell scenario consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively.
+The shared hidden variable is labeled $\la$.}
+            \label{fig:bell_scenario}
+        \end{minipage}\hspace{0.04\textwidth}%
+        \begin{minipage}[t]{.48\textwidth}
+            \centering
+            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
+            \caption{The casual structure of the triangle scenario. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
+            \label{fig:triangle_scenario}
+        \end{minipage}
+    \end{center}
+    \end{figure}
+    Discovering quantum non-classicality in any causal structure is desirable, so why, in particular, is it important to do so in the triangle scenario?
+As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{triangle scenario} (\cref{fig:triangle_scenario}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
+\\
+
+    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the triangle scenario if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that the joint distribution $\prob[\nodes] = \prob[ABCXYZ]$ is a product over the causal parameters,
+    \[ \prob[ABCXYZ] = \prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
+    And also, the given distribution $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$:
+    \[ \prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \eq \label{eq:triangle_compatibility} \]
+
+    For certain causal structures, the conditional independence relations provided by $d$-separation relations are a sufficient characterization of compatibility.
+Recently, \citet{Henson_2014}, classified the triangle scenario as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the triangle scenario possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover, \citet{Inflation} concretely demonstrate that the space classical distributions on the triangle scenario is non-convex, unlike the Bell scenario.
+It can be argued that convexity of the Bell scenario distributions is partially responsible for the wealth of knowledge that is known about the Bell scenario.
+It is also reasonable to speculate that quantum non-classicality in the triangle can be translated directly into a computational advantage for certain computational circuits~\cite{Terhal_2002}.
+Characterizing quantum non-classicality for interesting causal structures remains an unsolved problem, and the triangle scenario is a small, non-trivial case study.
+\\
+
+    Additionally, \citet{Fritz_2012} demonstrated that the triangle scenario is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell scenario in that measure setting variables are non-existence in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we have elected to call the Fritz distribution (see \cref{sec:fritz_distribution}).
+Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classical in the triangle scenario.
+\\
+
+    Finally \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}), a novel tool for solving causal inference problems.
+Using the inflation technique, they were able to prove incompatibility between the triangle scenario and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints.
+Therefore as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the triangle scenario that all others.
+\\
+
+    It is worth noting that a number of causal compatibility inequalities for the triangle scenario have been derived in previous works.
+For example, \citet{Steudel_2010} derived an inequality for a series of causal structures with $n \in \N$ variables where at most $c \in \N$ share a common ancestor.
+The triangle scenario is a special case with $c = 2$, $n = 3$.
+Moreover, \citet{Henson_2014} derive a family of entropic inequalities constraining the set of compatible correlations.
+Most impressively, \citet{Inflation} derive a family of polynomial, $2$-outcome, causal compatibility inequalities; $37$ non-trivial representatives are printed in~\cite{Inflation}.
+\\
+
+    As a preliminary search for quantum incompatibility in the triangle scenario, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}.
+Unfortunately, none of these inequalities could be violated.
+These early results suggest, although do not prove, that quantum non-classical does not exist in the triangle scenario for \textit{two-outcome} measurements.
+We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in triangle scenario for a degree of outcomes.
+\\
+
+    In conclusion, the triangle scenario is a causal structure whose non-classicality remains an open problem.
+The triangle scenario is a desirable case study because there is a quantum distribution that is known to be incompatible, but no previously known inequalities were able to witness its incompatibility.
+This failure represents a gap in our understanding of quantum non-classicality, where recent developments (namely the Inflation Technique) have made partial progress.
+This document expands on our understanding of non-classicality in the triangle scenario and also our understanding on how to find inequalities using the Inflation Technique for interesting causal structures in general.
+
+    \section{Fritz Distribution}
     \label{sec:fritz_distribution}
@@
     \begin{center}
-        % \fbox{%
-        \begin{minipage}[t]{.48\textwidth}
-            \centering
         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational_fritz_bell}}
@@
         \label{fig:triangle_scenario_with_fritz_bell_embedded}
-        \end{minipage}%
-        % }%
-        \hspace{0.04\textwidth}%
-        % \fbox{%
-        \begin{minipage}[t]{.48\textwidth}
-            \centering
-            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
-            \caption{The Bell scenario consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively.}
-            \label{fig:bell_scenario}
-        \end{minipage}%
-        % }%
     \end{center}
     \end{figure}
-    As was originally noticed by Fritz~\cite{Fritz_2012}, it is possible to construct quantum distributions incompatible with the triangle scenario by utilizing quantum distributions incompatible with the familiar Bell scenario.
+
+    As was originally noticed by \citet{Fritz_2012}, it is possible to construct quantum distributions incompatible with the triangle scenario by utilizing quantum distributions incompatible with the familiar Bell scenario.
 To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_scenario_with_fritz_bell_embedded} and contrast it with the Bell scenario of \cref{fig:bell_scenario}.
-The crucial distinction to be made is that the respective measurement settings $S_{\p{A}}, S_{\p{B}}$ in the Bell scenario become latent nodes in the triangle scenario.
-In order to embed Bell scenario incompatibility into the triangle scenario, the latent nodes $S_{\p{A}}, S_{\p{B}}$ need to be observable and independent of the shared latent node $\la$.
-This can be accomplished by having $C$ measure the measurement settings $S_{\p{A}}, S_{\p{B}}$ and announce them as an outcome.
-Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell scenario is also incompatible with the triangle scenario provided that $C$ is perfectly correlated with $S_{\p{A}}, S_{\p{B}}$.
-Understandably there are numerous ways that this can be accomplished, albeit we will focus on elucidating an exemplary case.
+Evidently, under the correct relabeling, large portions of the Triangle Scenario resemble the Bell Scenario.
+The crucial distinction is that the measurement settings $S_{\p{A}}, S_{\p{B}}$ are \textit{observable variables} in the Bell scenario but become \textit{latent variables} in the triangle scenario.
+In order to embed distributions that are incompatible with the Bell scenario into the triangle scenario, the latent nodes $S_{\p{A}}, S_{\p{B}}$ need to be observable and independent of the shared latent node $\la$.
+This can be accomplished by having $C$ ``measure'' the measurement settings $S_{\p{A}}, S_{\p{B}}$ and announce them as an outcome.
+Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell scenario is also incompatible with the triangle scenario provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$.
+Understandably there are numerous ways that this can be accomplished, albeit we will focus on elucidating an exemplary method.
+\\
 
     The \term{Fritz distribution}, denoted $\prob[\fritz]$, is a quantum-accessible distribution known to be incompatible with the triangle scenario~\cite{Fritz_2012}.
-Explicitly, the Fritz distribution can be written as follows:
+In the Fritz distribution, each of the variables $A,B,C$ have $4$ possible outcomes.
+Explicitly, $\prob[\fritz]$ can be written as:
     \begin{align*}
@@
     \begin{center}
-            \includegraphics[scale=0.6]{../../figures/distributions/fritz_dist_plot_bits_no_title.pdf}
+            \includegraphics[scale=0.6]{../../figures/distributions/fritz_dist_plotted_bits.pdf}
+            \vspace{-0.2in}
+            \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
             \caption{The Fritz distribution visualized using a $4 \times 4 \times 4$ grid.
@@
     \end{figure}
-    Consequently, it is possible to define the correlation between right-bits of $A$ and $B$,
+    Consequently, it is possible to define the correlation between the right-hand bits of $A$ and $B$ as the probability that $A_r$ and $B_r$ are equal less the probability that they differ:
     \[ \ba{\p A_r \p B_r} = \prob[\p A_r \p B_r][00] + \prob[\p A_r \p B_r][11] - \prob[\p A_r \p B_r][01] - \prob[\p A_r \p B_r][10] \]
-    And also define a CHSH inequality~\cite{CHSH_Original} for the right-bits of $A$ and $B$,
+    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell scenario defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the triangle scenario using the following mapping:
+    \[ \p{A}, \p{B}, S_{\p{A}}, S_{\p{B}} \mapsto \p{A_r}, \p{B_r}, \p A_l, \p B_l \]
+    As an example, the famous CHSH inequality~\cite{CHSH_Original},
+    \[ \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 0} + \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 1} + \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 0} - \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 1} \leq 2 \]
+    Can be written for the right-bits of $A$ and $B$,
     \[ \ba{\p A_r \p B_r|\p C = 00} + \ba{\p A_r \p B_r|\p C = 01} + \ba{\p A_r \p B_r|\p C = 10} - \ba{\p A_r \p B_r|\p C = 11} \leq 2 \eq \label{eq:CHSH} \]
-    Substitution of \cref{eq:fritz_dist} into \cref{eq:CHSH} yields maximal violation~\cite{Cirelson_1980},
+    Therefore, every compatible distribution $\prob[ABC]$ where $C$ is perfectly correlated $A_l,B_l$ must satisfy \cref{eq:CHSH}.
+Substituting the Fritz distribution (\cref{eq:fritz_dist}) into \cref{eq:CHSH} yields maximal violation~\cite{Cirelson_1980},
     \[ 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} = 2\sqrt{2} \not \leq 2 \]
-    The Fritz distribution $\prob[\fritz]$ can be realized as a set of quantum states and measurements.
-The shared resource between $A$ and $B$ (graphically denoted $\la$) is the maximally entangled Bell state:
+    Therefore, the Fritz distribution is incompatible with the triangle scenario as promised. \\
+
+    The Fritz distribution $\prob[\fritz]$ is of special interest because it can be realized as a set of quantum states and measurements on the quantum causal model depicted in \cref{fig:triangle_scenario_quantum_model}.
+The shared resource between $A$ and $B$ (graphically denoted $\la$ in \cref{fig:triangle_scenario_with_fritz_bell_embedded}) is the maximally entangled Bell state:
     \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \qquad \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \]
@@
     \[ \ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}} \]
+    Using the above states and measurements, the Fritz distribution $\prob[\fritz]$ can be recovered using the following:
+    \[ \prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}} \]
+    Where $\netperm$ is a $64 \times 64$ permutation matrix to be elaborated in \cref{sec:perm_matrix}. \\
 
@@
 Nonetheless for concreteness, \cref{eq:fritz_dist} is taken as \textit{the} Fritz distribution throughout this paper.
+Moreover, the quantum implementation of the Fritz distribution presented above is non-unique also.
+For example, it is possible to implement the Fritz distribution using maximally entangled Bell states for each shared resource $\rho_{AB}, \rho_{BC}, \rho_{CA}$ provided there is an appropriate adjustment to the measurements $M_A, M_B, M_C$.
+Ultimately however, only $\rho_{AB}$ is required to be entangled in order to reproduce the Fritz; after-all, $C$ is simply classically announcing $A_r$ and $B_r$ as he receives them.
+\\
 
@@
 As such, the incompatibility proof employed by Fritz is not applicable to any distribution that significantly deviates from the Fritz distribution presented above.
-For example, if one affinely combines \cref{eq:fritz_dist} with uniform noise, at what point does the resultant distribution become compatibility?
+For example, if one combines \cref{eq:fritz_dist} with more and more uniform noise, at what point does the resultant distribution transition from incompatibility to compatibility?
 This problem is discussed more in \cref{sec:noise}.
+\\
 
@@
 Therefore, it is desirable to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell scenario.
-In~\cite{Fritz_2012}, Fritz presented the following problem: \textit{Find an example of non-classical quantum correlations in the triangle scenario together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.} The problem is understandably stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures.
-To refine the discussions, consider the following refinements of the problem:
-    \begin{enumerate}
-        \item Find proofs of causal incompatibility of quantum distributions on the triangle scenario that are not reliant on perfect correlations.
-        \item Find incompatible quantum distributions on the triangle scenario that are \textit{more incompatible} that all Fritz-type embeddings.
+\citet{Fritz_2012} presented the following problem: \textit{Find an example of non-classical quantum correlations in the triangle scenario together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.} The problem is understandably stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures.
+In order to remove some of the ambiguity, consider the following refinements of the problem:
+    \begin{enumerate}[label=\textbf{R.\arabic*}]
+        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the triangle scenario that are \textit{not} reliant on perfect correlations.
+        \item \label{r:2} Find incompatible quantum distributions on the triangle scenario that satisfy all Bell scenario inequalities under Fritz-type embeddings.
+        \item \label{r:3} Find incompatible quantum distributions that require entanglement in more than one shared state.
     \end{enumerate}
-    \todo[TC]{Discuss the accomplishments of this paper towards answering these problems. }
+    The remainder of this document focuses on a positive solution to \ref{r:1} but leaves \ref{r:2} and \ref{r:3} partially unanswered.
 
     \section{Inflation Technique}
-    \begin{itemize}
-        \item \todo[TC]{Summarize inflation technique}
-        \item \todo[TC]{Inflations of Triangle Scenario}
-        \item \todo[TC]{Demonstrate that one can derive causal incompatibility inequalities from inflation}
-        \item \todo[TC]{Pre-injectable sets for Large inflation}
-    \end{itemize}
+    \label{sec:inflation_technique}
+    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a marginal model $\prob^{\mscenario}$ is compatible or incompatible with a given causal structure $\graph$.
+As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
+As a example, inflations of the triangle scenario are depicted in \cref{fig:inflations}.
+Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}.
+For example node $A$ of \cref{fig:triangle_scenario} has copies $A_1, A_2, A_3, A_4$ in the \textit{Web inflation} of \cref{fig:the_web_inflation}.
+All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
+A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
+    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
+    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index.
+Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
+    \begin{definition}
+        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
+        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
+        Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is equivalent to its counterpart in $\graph$ up to copy-index.
+    \end{definition}
+    The motivation behind this definition is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
+\\
+
+    To do this, first notice that every compatible joint distribution $\prob[\nodes]$ uniquely defines a set of causal parameters for $\graph$.
+It is possible to obtain these causal parameters by computing the single-variable marginal distributions of $\prob[\nodes]$,
+    \[ \forall n \in \nodes : \prob[n\mid \Pa[\graph]{n}] = \sum_{\nodes \setminus n} \prob[\nodes] \eq \label{eq:unique_causal_parameters}\]
+    Now it is possible to make use of the inflation criteria (\cref{eq:inflation_defn}) which at least enforces that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$.
+From this, one can create a set of \term{inflated causal parameters} using \cref{eq:unique_causal_parameters},
+    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \eq \label{eq:inflated_causal_parameters} \]
+    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course, there exists compatible joint distributions on $\nodes'$ that can not be constructed in this manner.
+The claim is that all joint distributions that are constructed in this way are compatible.}.
+    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \eq \label{eq:unique_causal_parameters_inflated}\]
+    Together, \cref{eq:unique_causal_parameters,eq:inflated_causal_parameters,eq:unique_causal_parameters_inflated} form the \term{weak inflation lemma}: compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$.
+Before generalizing to the inflation lemma, a careful observation needs to be made.
+For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$, where $N \subset \nodes$, induces a compatible marginal distribution $\prob[N']$ over $N'$.
+In fact, $N'$ must contain no duplicate nodes up to copy index and thus $\prob[N] = \prob[N']$.
+These subsets of nodes are so essential to the Inflation Technique they are assigned a special name: sets $N' \subseteq \nodes'$ as called the \term{injectable sets} of $\graph'$ and $N \subset \nodes$ the \term{images of the injectable sets} of $\graph$.
+    \begin{align*}
+        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
+        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
+    \end{align*}
+    Injectable sets are incredibly useful for causal compatibility because they allow one to extend the weak inflation lemma to \textit{the} inflation lemma:
+    \begin{lemma}
+        \label[lemma]{lem:inflation}
+        \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+    \end{lemma}
+    Diagrammatically, \cref{lem:inflation} can be visualized as follows:
+
+    \begin{center}
+        \begin{tikzpicture}
+            \pgfmathsetmacro{\vs}{2.2};
+            \pgfmathsetmacro{\hs}{5.2};
+            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
+            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
+            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
+            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
+            \draw[very thick, ->] (pn) -- (cp);
+            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
+            \draw[very thick, ->] (cp_) -- (pn_);
+        \end{tikzpicture}
+    \end{center}
+
+    The inflation lemma is the most important result of the causal inflation technique.
+The contrapositive version of \cref{lem:inflation} is a powerful tool for deriving causal compatibility constraints.
+Any causal compatibility constraint, such as a causal compatibility inequality, that constrains injectable marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ can be \textit{deflated} into a valid compatibility constraint on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure by dropping all references to the copy-indices.
+Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
+Therefore, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
+\\
+
+    Heretofore, the Inflation Technique as stated by \cref{lem:inflation} does not facilitate the derivation of any non-trivial inequalities.
+The Inflation lemma simply casts causal inference problems on $\graph$ to causal inference problems on $\graph'$.
+Fortunately, an inflated causal structure $\graph'$ possesses its own conditional independence relations which can be exploited to turn linear inequalities on $\graph'$ into polynomial inequalities on $\graph$.
+\\
+
+    Suppose that one were to obtain an inequality on $\graph'$ that contained probabilistic terms such as $\prob[N']$ where $N' \not \in \Inj[\graph]{\graph'}$.
+At this point, the Inflation lemma is not applicable because it requires probabilistic constraints to consist entirely of distributions $\prob[N']$ where $N'$ is injectable.
+If for example, $N' \not \in \Inj[\graph]{\graph'}$ could be partitioned into two injectable subsets $N_1' \in \Inj[\graph]{\graph'}$ and $N_2' \in \Inj[\graph]{\graph'}$ that where \term{ancestrally independent} in $\graph'$,
+    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
+    Then the compatible marginal context $\prob[N']$ must be probabilistically separable $\prob[N'] = \prob[N_1']\prob[N_2']$ due to \cref{eq:local_markov_property}.
+Since $N_1'$ and $N_2'$ are both injectable, the inflation lemma now applies and the original inequality can be deflated.
+
+    \begin{center}
+        \begin{tikzpicture}[scale=0.8]
+            \pgfmathsetmacro{\hs}{1.4};
+            \pgfmathsetmacro{\vs}{0.6};
+            \pgfmathsetmacro{\cross}{0.2};
+            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
+            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
+            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
+            \draw (2*\hs, 4*\vs + 0.7*\vs) node[]{$N_1' \cup N_2' = N$};
+            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
+            \draw (0, 0) node[](b){??};
+            \draw[thick, ] (a) -- (ab);
+            \draw[thick, ] (c) -- (cd);
+            \draw[thick, ] (a) -- (ac);
+            \draw[thick, ->] (ac) -- (c);
+            \draw[thick, ->] (ab) -- (b);
+            \draw[thick, ->] (cd) -- (d);
+            \draw[very thick, red]
+            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
+            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
+            ;
+        \end{tikzpicture}
+    \end{center}
+
+    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that can are called the \term{pre-injectable sets}.
+A set $N' \subseteq \nodes'$ is a pre-injectable set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.\\
+
+    A pre-injectable set $N'$ is of primal importance to the inflation technique because any distribution over $N'$ will factorize according to graphical $d$-separation conditions~\cite{Pearl_2009},
+    \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
+    Application of the inflation lemma to linear inequalities constraining pre-injectable distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
+Throughout the body of this work, we let $\PreInj[\graph]{\graph'}$ denote the set of all pre-injectable sets.
+Naturally, the pre-injectable sets will define a marginal scenario $\mscenario$ that in \cref{sec:deriving_inequalities} will be used to derive compatibility inequalities\footnote{Analogously for a marginal scenario $\mscenario$, the pre-injectable sets $\PreInj[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
+Therefore, in practice, it is completely sufficient to focus on the maximal pre-injectable sets}.
+
+    \begin{center}
+    \begin{figure}
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
+    \caption{The Cut inflation}\label{fig:cut_inflation}
+    \end{subfigure}
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral}}
+    \caption{The Spiral inflation}\label{fig:spiral_inflation}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_wagon_wheel}}
+    \caption{The Wagon-Wheel inflation}\label{fig:wagon_wheel_inflation}
+    \end{subfigure}
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
+    \caption{The Web Inflation}\label{fig:the_web_inflation}
+    \end{subfigure}
+    \caption{Some inflations of the triangle scenario.}
+    \label{fig:inflations}
+    \end{figure}
+    \end{center}
 
     \section{Deriving Inequalities}
-    \begin{itemize}
-        \item \todo[TC]{Marginal problem}
-        \item \todo[TC]{Popular methods: Fourier Motzkin (Convex hull, Polytope projection), Hardy implication inequalities, linear program/certificate}
-        \item \todo[TC]{Overview incidence for Large Inflation}
-        \item \todo[TC]{Rule out expensive methods like FM}
-        \item \todo[TC]{Present some of the inequalities found}
-    \end{itemize}
+    \label{sec:deriving_inequalities}
+
+    In \cref{sec:causal_compatibility}, we defined the notion of a causal compatibility inequality without providing a means for deriving/computing them.
+This section aims to delineate algorithms and methods that can be used to derive causal compatibility inequalities for generic causal inference problems.
+Recalling the definition of causal compatibility presented in \cref{sec:compatibility}, a marginal model $\prob^{\mscenario}$ is compatible with a causal structure $\graph = \br{\nodes, \edges}$ if it can be recovered from a series of operations.
+First choose a set of causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ and then construct a joint distribution $\prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}]$ over all nodes $\nodes$ (this step is \cref{eq:local_markov_property_operation}).
+Afterwards, each marginal distribution $\prob[V] \in \mscenario$ should be recoverable from a marginalization over $\prob[\nodes]$ (this step is the combination of \cref{eq:observable_marginalization,eq:context_marginalization}).
+Intuitively, these two requirements for a compatible marginal model $\prob^{\mscenario}$ provide two necessary components of compatibility:
+    \begin{enumerate}
+        \item The marginal model $\prob^{\mscenario}$ must admit a joint distribution $\prob[\nodes]$ (\cref{eq:observable_marginalization,eq:context_marginalization}).
+        \item The joint distribution $\prob[\nodes]$ must satisfy the Markov separability criteria (\cref{eq:local_markov_property_operation}).
+    \end{enumerate}
+    In practice, this is the natural order in which to classify the compatibility of a marginal model $\prob^{\mscenario}$.
+First check if the marginal model admits a joint distribution and if and only if it does, determine whether or not the local Markov property can be satisfied for some choice of causal parameters.
+Intuitively, there are two reasons why a given marginal model $\prob^{\mscenario}$ would be deemed incompatible.
+One possibility is that the marginal model $\prob^{\mscenario}$ does not admit a joint distribution $\prob[\nodes]$.
+Alternatively, it could be possible that a joint distribution $\prob[\nodes]$ exists but can not factor into causal parameters as per \cref{eq:local_markov_property_operation}.\\
+
+    Colloquially, the first necessary condition, namely the existence (or non-existence) of a joint distribution, is referred to as \term{the marginal problem}.
+The marginal problem asks: given a marginal model $\prob^{\mscenario} = \bc{\prob[V] \mid V \in \mscenario}$ marginal to the joint variables $\jointvar = \bigcup_{V \in \mscenario} V$, does there exist a joint distribution $\prob[\jointvar]$ such that each context $\prob[V]$ can be obtained by marginalizing $\prob[\jointvar]$?
+    \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \eq \label{eq:def:marginal_problem}\]
+    Note that we have changed notation from the nodes of a causal structure $\nodes$ to a joint set of variables $\jointvar$.
+This is done simply because the marginal problem is well-defined independent of a given causal structure.
+In fact, if a marginal model $\prob^{\mscenario}$ does not admit a joint distribution, then it cannot be compatible with \textit{any} causal structure whatsoever.
+A marginal model is said to be \textit{contextual} if it \textit{does not} admit a joint distribution and \textit{non-contextual} otherwise.
+The marginal problem has applications to numerous areas of mathematics including game theory~\cite{Vorobev_1962}, database theory, knowledge integration of expert system, and of course, quantum information theory~\cite{Fritz_2011}.
+\\
+
+    The marginal problem is distinct from the second necessary condition, which we term the \term{Markov separability problem} in numerous ways.
+First of all, the marginal problem as applied to causal inference tasks is only concerned with the observable variables $\nodes_{O}$ of $\graph$.
+This differs from the Markov separability problem which depends directly on the entire graphical structure of $\graph$ and thus must include the latent variables $\nodes_{L}$.
+The purpose of latent variables is to have unspecified behavior which makes checking the local Markov property exceedingly difficult in comparison to the marginal problem.
+Secondly, \cref{eq:def:marginal_problem} is inherently a linear system of constraints which be solved rather efficiently using linear programs (to be discussed in \cref{sec:marginal_linear}).
+The local Markov property concerns itself with probabilistic independence constraints which are polynomial.
+Fortunately, the Inflation Technique (summarized in \cref{sec:inflation_technique}) is able to cast (at least partially) the Markov separability problem as a marginal problem over an inflated causal structure.
+As such the Inflation Technique in many ways can be considered a relaxation technique which turns polynomial constraints into linear constraints.
+\\
+
+    In consideration of these observations, we will now endeavor to discuss how causal compatibility inequalities can be derived by casting the marginal problem as a linear program.
+After doing, it becomes possible to discuss existing methods for deriving constraints on the set of contextual marginal models.
+
+    \subsection{The Marginal Problem as a Linear Program}
+    \label{sec:marginal_linear}
+
+    Heretofore, our discussions of compatibility and the marginal problem have been general in the sense of making no reference to the nature the random variables $v \in \jointvar$.
+In particular, whether the outcomes of $v$ are discrete or continuous, finite or unbounded, or otherwise.
+In the case of infinite outcomes, the marginal problem can be used to derive entropic inequalities defined over the mutual information between variables $v \in \jointvar$~\cite{Fritz_2011}.
+Entropic inequalities however have been shown to be less constraining than inequalities defined over variables with finite cardinality~\cite{Inflation}.
+Throughout this document, we restrict our attention to finite outcomes.
+To assist with the subsequent analysis, we recall some familiar notions of probability theory.
+
+    \subsubsection{Events \& Outcomes}
+    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$.
+We also define the set of all \term{events over $v$} $\Events{v}$\footnote{In the language of sheaf-theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
+    \[ \Events{v} \defined \bc{s : \bc{v} \to O_v} \]
+    Evidently, $\Events{v}$ and $O_v$ have a one-to-one correspondence and this distinction can be confounding.
+There is rarely any harm in referring synonymously to either as outcomes.
+Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
+    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetric_inequalities}.
+As a natural generalization we define the event over a collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
+    \[ \Events{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
+    Each event $s$ can be compactly represented as a set of mappings over each element of $V$.
+    \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
+    The domain $\Dom{s}$ of an event $s$ is the set of random variables it valuates, i.e.
+if $s \in \Events{V}$, then $\Dom{s} = V$.
+Under this framework, a probability distribution $\prob[V]$ can be considered as a map from $\Events{V}$ to the unit interval $\bs{0,1}$.
+    \begin{example}
+        Let $s \in \Events{V}$ be an event over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$.
+Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$.
+Furthermore let $f \in \Events{V}$ be the event $\br{v_1 \mapsto 2, v_2 \mapsto 1}$.
+The following notations are interchangeable,
+        \[ \prob[][s] = \prob[\Dom{s}][s] = \prob[V][s] = \prob[v_1, v_2][s] = \prob[][v_1 \mapsto s_1\br{v_1}, v_2 \mapsto s_2\br{v_2}] = \prob[][v_1 = 2, v_2 = 1] = \prob[v_1v_2][21] \]
+        Each of which should be read as ``the probability that $v_1$ got outcome $2$ and $v_2$ got outcome $1$''
+    \end{example}
+    The marginal problem inherently depends on the concept of probabilistic marginalization.
+This concept can be understood at the level of events; one event $s \in \Events{V}$ can be ``marginalized'' or restricted to a smaller event $s' \in \Events{W}$ whenever $W \subseteq V$.
+    \begin{definition}
+    \label{def:section_restriction}
+    For every $W \subseteq V$ and $s \in \Events{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Events{W}$) is the event in $\Events{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
+    \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
+    \end{definition}
+    % \begin{definition}
+    % \label{def:section_compatible}
+    % The events $s_{V} \in \Events{V}$ and $s_{W} \in \Events{W}$ are said to be \term{compatible} events if they agree on their valuations of $V \cap W$.
+Compatibility will be denoted with the infix `$\com$'.
+    % \[ s_{V} \com s_{W} \iff {s_{V}}|_{V\cap W} = {s_{W}}|_{V\cap W} \]
+    % \end{definition}
+    % \begin{definition}
+    % \label{def:section_extendable}
+    % It $s_V \in \Events{V}$ and $s_W \in \Events{W}$ compatible events and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
+    % \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
+    % Extendability is dual to the notion of a \term{restriction} of $s_V$; $s_V$ can be restricted to $s_W$ ($s_V \res s_W$) if and only if $s_W$ is extendable to $s_V$.
+    % \end{definition}
+
+    % \begin{remark}
+    %     The notation `$s \com t$' is used to indicate compatibility between $s \in \Events{V}$ and $t \in \Events{W}$ because of the following observation: $s$ and $t$ are compatible if and only if they are extensions of some event $r \in \Events{V \cap W}$.
+    %     \[ s \com t \iff \exists r \in \Events{V \cap W} \mid s \res r \ext t \]
+    %     In fact $r$ is uniquely defined.
+    %     \[ \forall v \in V \cap W : r\br{v} = s\br{v} = t\br{v} \]
+    % \end{remark}
+
+    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint events} $\Events{\jointvar}$ which represent all possible global events over the entire set of joint variables.
+Similarly, we define the \term{context events} for a particular context $V \in \mscenario$ as $\Events{V}$.
+Finally, we elect to define the \term{marginal events} as the disjoint union of all context events and by an abuse of notation we will denote this disjoint union as $\Events{\mscenario}$.
+    \[ \Events{\mscenario} = \coprod_{V \in \mscenario} \Events{V} \]
+    Each marginal section $m \in \Events{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
+By construction each marginal event $m \in \Events{\mscenario}$ is a restriction of some joint event $j \in \Events{\jointvar}$.
+    \subsubsection{Linear Programs}
+    \label{sec:linear_programs}
+    The marginalization operation (\cref{eq:def:marginal_problem}) of the marginal problem is a linear operator.
+This linear operator maps a joint probability distribution $\prob[\jointvar] : \Events{\jointvar} \to \bs{0,1}$ into a marginal model $\prob^{\mscenario} = \bc{\prob[V] : \Events{V} \to \bs{0,1} \mid V \in \mscenario}$.
+Since $\Events{\mscenario}$ and $\Events{\jointvar}$ are finite, the marginal problem can be casted as a $\abs{\Events{\mscenario}} \times \abs{\Events{\jointvar}}$ matrix.
+
+    \begin{definition}
+        \label{def:incidence_matrix}
+        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} events $j \in \Events{\jointvar}$ and the rows are events by \textit{marginal} events $m \in \Events{\mscenario}$.
+The entries of $M$ are populated whenever a marginal event $m$ is a restriction of the joint event $j$.
+        \[ M_{m,j} \defined \begin{cases}
+            1 & m = j|_{\s{D}\br{m}} \\
+            0 & \text{otherwise}
+        \end{cases} \]
+        The incidence matrix has $\abs{\Events{\jointvar}}$ columns, $\abs{\Events{\mscenario}} = \sum_{i} \abs{\Events{V_i}}$ rows and $k\abs{\Events{\jointvar}}$ non-zero entries.
+    \end{definition}
+    To illustrate this concretely, consider the following example:
+    \begin{example}
+        \label{ex:incidence_matrix}
+        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{A,B,C}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{A,B}, \bc{B,C}, \bc{A,C}}$. The incidence matrix becomes:
+        \[ M = \kbordermatrix{
+            (A,B,C) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
+            (A\mapsto0, B\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
+            (A\mapsto0, B\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
+            (A\mapsto1, B\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
+            (A\mapsto1, B\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
+            (B\mapsto0, C\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
+            (B\mapsto0, C\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
+            (B\mapsto1, C\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
+            (B\mapsto1, C\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
+            (A\mapsto0, C\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
+            (A\mapsto0, C\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
+            (A\mapsto1, C\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
+            (A\mapsto1, C\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
+        } \eq \label{eq:example_incidence}\]
+    \end{example}
+    The incidence matrix needs to act (to the right) on a vector representing the joint probability $\prob[\jointvar]$ distribution and output a vector representing the marginal model $\prob^{\mscenario}$.
+    \begin{definition}
+        The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint event $j \in \Events{\jointvar}$.
+$\probvec^{\jointvar}$ shares the same indices as the \textit{column} indices of $M$.
+        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
+    \end{definition}
+    \begin{definition}
+        Analogously, \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Events{\mscenario}$.
+$\probvec^{\mscenario}$ shares the same indices as the \textit{row} indices of $M$.
+        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
+    \end{definition}
+    By design, the marginal and joint distribution vectors are related via the incidence matrix $M$.
+Given a joint distribution vector $\probvec^{\jointvar}$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec^{\jointvar}$.
+    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
+    Because the marginal distribution vector $\probvec^{\mscenario}$ is simply another representation of the marginal model $\prob^{\mscenario}$, we will henceforth use the language interchangeably.
+This is likewise done so for the joint distribution (vector) $\prob[\jointvar]$ ($\probvec^{\jointvar}$).
+As a quick remark, the particular ordering of the rows and columns of $M$ carries \textit{no importance}, but it \textit{must} be consistent between $M$, $\probvec^{\jointvar}$ and $\probvec^{\mscenario}$.
+The marginal problem can now be rephrased in the language of the incidence matrix.
+Suppose one obtains a marginal distribution vector $\probvec^{\mscenario}$; the marginal problem becomes equivalent to the question:
+    \textit{Does there exist a joint distribution vector $\probvec^{\jointvar}$ such that \cref{eq:incidence_matrix_use} holds?} \\
+
+    The marginal problem can sometimes take on a more general variant that does not begin with a specific marginal model~\cite{Abramsky_2012,Mansfield_2012,Fritz_2011}: \textit{Given a marginal scenario $\mscenario$, what is the set of all non-contextual marginal models?} \citet{Pitowsky_1991} demonstrates that the set of non-contextual marginal models forms a \textit{convex} polytope called the \term{marginal polytope}.
+The extremal rays of a marginal polytope directly correspond to the columns of $M$ which correspond to each of the $\abs{\Events{\jointvar}}$ \textit{deterministic} joint distributions $\probvec^{\jointvar}$.
+Since all joint distributions $\probvec^{\jointvar}$ are probability distributions, their entries must sum to unity.
+    \[ \sum_{j \in \Events{\jointvar}} \probvec^{\jointvar}_j = 1 \]
+    This normalization defines the convexity of the polytope; all non-contextual marginal models are convex mixtures of the deterministic marginal models pursuant to \cref{eq:incidence_matrix_use}.
+The marginal polytope is a beneficial tool for understanding contextuality.
+First, the \textit{facets} of a marginal polytope correspond to a finite set of linear inequalities that are complete in the sense that all contextual distributions violate at least one facet inequality~\cite{Brunner_2013}.
+From the perspective of a marginal polytope, convex hull algorithms can be used to compute a representation of the complete set of linear inequalities and completely solve the marginal problem.
+Alternatively, one can completely characterize the separation between the space of contextual and non-contextual distributions by the system of inequalities associated with \cref{eq:incidence_matrix_use}.
+Explicitly,
+    \begin{equation} \label{eq:halfspace_rep_incidence}
+    \begin{alignedat}{2}
+        \forall m \in \Events{\mscenario} :&&\quad \probvec^{\mscenario}_m - {\sum}_{j} M_{m, j} \probvec^{\jointvar}_j &\geq 0 \\
+        \forall m \in \Events{\mscenario} :&&\quad -\probvec^{\mscenario}_m + {\sum}_{j} M_{m, j} \probvec^{\jointvar}_j &\geq 0 \\
+        \forall j \in \Events{\jointvar} :&&\quad \probvec^{\jointvar}_j &\geq 0
+    \end{alignedat}
+    \end{equation}
+    Geometrically \cref{eq:halfspace_rep_incidence} is a family of $2\abs{\Events{\mscenario}} + \abs{\Events{\jointvar}}$ half-planes bounding $\R^{\abs{\Events{\mscenario}}} \times \R^{\abs{\Events{\jointvar}}}$.
+However testing the contextuality of a marginal model $\probvec^{\mscenario}$ requires a collection of inequalities bounding just $\R^{\abs{\Events{\mscenario}}}$.
+Transforming \cref{eq:halfspace_rep_incidence} into the desired system of inequalities is the task of linear-quantifier elimination.
+A popular tool for linear quantifier elimination is \term{Fourier-Motzkin elimination} \cite{Dantzig_1973,Inflation,Abramsky_2012,jones_2004}.
+Applying the Fourier-Motzkin procedure to completely solve the marginal problem is discussed in more detail in \citet{Fritz_2011}.
+An excellent survey of existing techniques for solving the marginal problem including Equality Set Projection~\cite{jones_2004} and Hardy-type hypergraph transversals can be found in \citet{Inflation}.
+In conclusion, there are a number of computational tools available to solve the marginal problem completely whenever no marginal model is provided.
+\\
+
+    Each of the above mentioned techniques suffers from computational complexity limitations.
+For example, the Fourier-Motzkin procedure is act worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}.
+For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable.
+This will become apparent in \cref{sec:found_inequalities} when the inflation technique is applied to the triangle scenario, producing marginal models that are very large.
+Moreover, algorithms to partially solve the marginal problem such as Hardy-type hypergraph transversals were used to determine hundreds of thousands of causal compatibility inequalities for the triangle scenario; none of which were able to be violated quantumly using numerical optimizations.
+Therefore, simpler approaches to the marginal problem needed to be considered.
+\\
+
+    Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining where or not a particular marginal model admitted a joint distribution or not.
+This question is naturally framed as the following linear problem:
+
+    \begin{definition}
+        \label{def:marginal_linear_program}
+        \term{The Marginal Linear Program} is the following linear program:
+        \begin{alignat*}{2}
+            & \text{minimize:} \quad&& \emptyset \tcdot x\\
+            & \text{subject to:} && x \succeq 0 \\
+            & && M \tcdot x = \probvec^{\mscenario}
+        \end{alignat*}
+        If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries).
+The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:incidence_matrix_use} and is a valid joint distribution vector.
+Therefore feasibility implies that $\probvec^{\jointvar}$ exists and is precisely $x$.
+Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\probvec^{\jointvar}$.
+    \end{definition}
+
+    To every linear program, there exists a dual linear program that characterizes the feasibility of the original~\cite{Schrijver_1998}.
+Constructing the dual linear program is straightforward~\cite{Lahaie_2008}.
+
+    \begin{definition}
+        \label{def:dual_marginal_linear_program}
+        \term{The Dual Marginal Linear Program}:
+        \begin{alignat*}{2}
+            & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
+            & \text{subject to:} && y \tcdot M \succeq 0
+        \end{alignat*}
+        Where $y$ is a real valued vector with the same length as $\probvec^{\mscenario}$.
+    \end{definition}
+
+    The dual marginal linear program not only answers the marginal problem for a specific marginal model $\probvec^{\mscenario}$ but as a by-product provides an inequality that witnesses its contextuality.
+If this is not obvious, first notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints become satisfied.
+Secondly if the dual constraint $y \tcdot M \succeq 0$ holds \textit{and} the primal is feasible, then the following must hold:
+    \[ y \tcdot \probvec^{\mscenario} =  y \tcdot M \tcdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
+    Therefore the \textit{sign} of the dual objective $d \defined \min \br{y \tcdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality.
+If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore $\probvec^{\mscenario}$ is contextual.
+Likewise if $d \geq 0$ (satisfying \cref{eq:dual_marginal_ineq}), then $\probvec^{\mscenario}$ is non-contextual.\footnote{Actually, if $d \geq 0$ then it is exactly $d = 0$ due to the existence of the trivial $y = \emptyset$.
+This observation is an instance of the \textit{Complementary Slackness Property} of~\cite{Bradley_1977}.
+Moreover, if $d < 0$, then it is unbounded $d = -\inf$.
+This latter point becomes clear upon recognizing that for any $y$ with $d < 0$, another $y' = \al y$ can be constructed (with $\al > 1$) such that $d' = \al d < d$.
+Since a more negative $d'$ can always be found, it must be that $d$ is unbounded.
+This is a demonstration of the fundamental \textit{Unboundedness Property} of~\cite{Bradley_1977}; if the dual is unbounded, then the primal is infeasible.} This is manifestation of Farkas's lemma~\cite{Schrijver_1998}.
+\\
+
+    An \term{infeasibility certificate}~\cite{Andersen_2001} is any vector $y$ that satisfies the constraint of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
+    \[ y \in \R^{\abs{\Events{\mscenario}}} : y \tcdot M \succeq 0, \quad y \tcdot \probvec^{\mscenario} < 0 \]
+    Most linear program software packages such as Mosek~\cite{Mosek_2016}, Gurobi~\cite{Gurobi_2016}, CPLEX~\cite{Cplex_2016} and CVX/CVX OPT~\cite{CVX_2016,CVX_Opt_2016} are capable of producing infeasibility certificates.
+    Furthermore, for every $y$ satisfying $y \tcdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of non-contextual marginal models.
+If $y$ is an infeasibility certificate, then all non-contextual marginal models $\probvec^{\mscenario}$ must satisfy \cref{eq:dual_marginal_ineq} making $y \cdot \probvec^{\mscenario} \geq 0$ a valid causal compatibility inequality.
+
+    \subsection{Triangle Scenario Inequalities}
+    \label{sec:found_inequalities}
+
+    Equipped with the Fritz distribution (\cref{sec:fritz_distribution}) and the inflation technique (\cref{sec:inflation_technique}), it is now possible to derive causal compatibility inequalities for the triangle that are violated by the Fritz distribution; the procedure for doing so is as follows.
+First select an inflation $\graph'$ of the triangle scenario $\graph$ and identify the maximal pre-injectable sets $\PreInj[\graph]{\graph'}$.
+These sets define the marginal scenario to be used in the Inflation Technique.
+Next, inflate the Fritz distribution into the pre-injectable sets as described by the Inflation lemma (\cref{lem:inflation}).
+Finally, obtain infeasibility certificates using some linear programing software and obtain a valid causal compatibility inequality that witnesses the Fritz distribution's incompatibility.
+\\
+
+    As a first demonstration, we make use of the Wagon-Wheel inflation (\cref{fig:wagon_wheel_inflation}) to find these inequalities.
+The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
+By inspection\footnote{Computing the injectable and pre-injectable sets computationally is possible and a technique is discussed in~\citet{Inflation}.}, the maximal pre-injectable sets of the Wagon-Wheel inflation are as follows:
+    \begin{equation*}
+        \eq \label{eq:pre_injectable_triangle_scenario_wagon_wheel}
+        \begin{gathered}
+            \textbf{Maximal Pre-injectable Sets} \\
+            \bc{A_2, B_1, C_3, C_1} \\
+            \bc{A_1, B_1, C_4, C_2} \\
+            \bc{A_1, B_2, C_1, C_3} \\
+            \bc{A_2, B_2, C_2, C_4} \\
+        \end{gathered}
+        \qquad
+        \begin{gathered}
+            \textbf{Ancestral Independences} \\
+            \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
+            \bc{A_1, B_1, C_4} \ancestralindep \bc{C_2} \\
+            \bc{A_1, B_2, C_1} \ancestralindep \bc{C_3} \\
+            \bc{A_2, B_2, C_2} \ancestralindep \bc{C_4} \\
+        \end{gathered}
+    \end{equation*}
+
+    These maximal pre-injectable sets define a marginal scenario where $\graph'$ is the Wagon-Wheel inflation of the triangle scenario $\graph$.
+    \[ \mscenario = \PreInj[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
+    The complete set of variables $\jointvar$ is simply the set of observable nodes in the Wagon-Wheel inflation,
+    \[ \jointvar = \nodes'_O = \bc{A_1, A_2, B_1, B_2, C_1, C_2, C_3, C_4} \]
+    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
+This marginal scenario $\mscenario$ then defines an incidence matrix capable of accommodating the Fritz distribution.
+    Analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \abs{\Events{V}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{\Events{v}} = 4^{\abs{\jointvar}} = 4^8 = 65,536$ columns.
+Understandably, this matrix is not reproduced here.
+The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.\\
+
+    The marginal distribution vector $\probvec^{\mscenario}$ is indexed by $1024$ marginal outcomes $m \in \Events{\mscenario}$ of the following \textit{symbolic} form,
+    \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
+    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_scenario_wagon_wheel},
+    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
+    And finally, each probability distribution in \cref{eq:marginal_vector_wagon_wheel_factors} is deflated by dropping copy-indices.
+    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[ABC]\br{000}\prob[C]\br{0}, \ldots, \prob[ABC]\br{323}\prob[C]\br{2}, \ldots, \prob[ABC]\br{333}\prob[C]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors_dropped}\]
+    This step is permitted because all of the remaining distributions in \cref{eq:marginal_vector_wagon_wheel_factors} are defined over the injectable sets of the Wagon-Wheel inflation.
+Numerically however, each of the elements of $\probvec^{\mscenario}$ are replaced with numerical values corresponding to the Fritz distribution upon deflation.
+Pursuant to \cref{eq:fritz_dist}, $\prob[ABC]\br{323}\prob[C]\br{2}$, for example, is assigned the following numerical value.
+    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267  \]
+    The same is applied to all other entries of $\probvec^{\mscenario}$.
+Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained.
+Below is an example of an infeasibility inequality obtained over the entries of \cref{eq:marginal_vector_wagon_wheel_factors_dropped}.
+    \begin{equation*}
+    \begin{gathered}
+    \eq\label{eq:ww_ineq}
+    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \\
+    P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \\
+    P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \\
+    P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \\
+    P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \\
+    P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \\
+    P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \\
+    P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \\
+    P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \\
+    P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \\
+    P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) - P_{ABC}(000)P_{C}(3) \geq 0
+    \end{gathered}
+    \end{equation*}
+    By construction, every marginal model $\probvec^{\mscenario} = \bc{\prob[ABC], \prob[AB], \prob[BC], \prob[AC], \prob[A], \prob[B], \prob[C]}$ compatible with the triangle scenario must satisfy \cref{eq:ww_ineq}.
+The Fritz distribution however violates \cref{eq:ww_ineq}.\\
+
+    Notice the final term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $-1$.
+For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$.
+
+    It is possible to simplify this inequality by marginalizing over sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) = P_{ABC}(300)$.
+Upon doing so, one obtains the following,
+    \begin{gather*}
+        P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \leq \\ P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + \\
+        + P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + P_{AB}(20) + P_{AB}(30) + P_{C}(3)P_{C}(0)
+    \end{gather*}
+
+    There are a couple of important concepts to understand.
+First, the Fritz distribution is known to be incompatible with the Triangle scenario due to the perfect correlation between $C$ and the measurement pseudo-settings.
+The inequality contained in \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the triangle scenario.
+For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$.
+Moreover, although the existence of an inequality capable of witnessing Fritz distribution is guaranteed, there was no guarantee that the marginal model associated with the Wagon-Wheel inflation (\cref{eq:wagon_wheel_marginal_model}) would be capable of producing such an inequality.
+In fact, smaller inflations of the triangle scenario such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
+\\
+
+    Larger inflations such as the Web inflation (\cref{fig:the_web_inflation}) were also used to generate causal compatibility inequalities that are violated by the Fritz distribution.
+The set of maximal pre-injectable sets for the Web inflation is considerably larger than \cref{eq:pre_injectable_triangle_scenario_wagon_wheel}.
+    \begin{equation*}
+        \eq \label{eq:pre_injectable_triangle_scenario_web}
+        \begin{gathered}
+            \textbf{Maximal Pre-injectable Sets} \\
+            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
+            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
+            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
+            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
+            \bc{A_1, B_3, C_4} \\
+            \bc{A_1, B_4, C_2} \\
+            \bc{A_2, B_1, C_4} \\
+            \bc{A_2, B_2, C_2} \\
+            \bc{A_3, B_3, C_3} \\
+            \bc{A_3, B_4, C_1} \\
+            \bc{A_4, B_1, C_3} \\
+            \bc{A_4, B_2, C_1}
+        \end{gathered}
+        \qquad
+        \begin{gathered}
+            \textbf{Ancestral Independences} \\
+            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
+            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
+            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
+            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
+            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
+            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
+            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
+            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
+            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
+            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
+            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
+            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
+        \end{gathered}
+    \end{equation*}
+    Again, analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ and $201,326,592$ non-zero entires.
+Using this incidence matrix, a number of incompatibility certificates were derived.
+For inspection, one is reproduced in \cref{sec:web_inequality}.
+\\
+
+    In summary, these causal compatibility inequalities represent a completion of objective \cref{r:1} from \cref{sec:fritz_distribution}.
+These inequalities are derived without making use of Bell's theorem and instead use the Inflation Technique which is completely independent of Bell's theorems.
+Additionally, the derivation of causal compatibility inequalities allows one prove incompatibility even when perfect correlations are absent.
+Moreover, they allow one to probe the amount of noise the Fritz distribution can sustain before becoming compatible (see \cref{sec:violations_noise}).
+Unfortunately, infeasibility certificates are found by linear programing software to certify the infeasibility of a \textit{particular distribution}.
+This means that inequalities like \cref{eq:ww_ineq}, the one presented in \cref{sec:web_inequality}, and others are specifically manufactured in order witness a particular type of quantum non-classicality.
+In an effort to derive inequalities that could lead to potentially new forms of non-classicality, we searched for inequalities that did not admit biased towards the Fritz distribution.
 
     \subsection{Symmetric Inequalities}
-    \begin{itemize}
-        \item \todo[TC]{Discuss symmetries and why they are useful}
-        \item \todo[TC]{Symmetrizing Incidence Matrix}
-        \item \todo[TC]{Large inflation incidence contracted drastically}
-        \item \todo[TC]{Present some of the inequalities found}
-    \end{itemize}
+    \label{sec:symmetric_inequalities}
 
-    \section{Violations}
-    \begin{itemize}
-        \item \todo[TC]{Fritz Distribution violates found inequalities}
-    \end{itemize}
+    Quite surprisingly, it is possible to derive causal compatibility inequalities for the triangle scenario that are symmetric under the exchange of parties.
+This is done by grouping marginal events $m \in \Events{\mscenario}$ into orbits under the action of party exchange.
+Even more interestingly, these inequalities are violated by the Fritz distribution.
+This comes as a surprise because the Fritz distribution is \text{not} invariant under the exchange of parties; in fact the Fritz distribution is noticeably biased toward $C$.
+\\
+
+    In general, exploiting symmetries of the marginal scenario is useful for a few distinct reasons.
+First, \citet{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:deriving_inequalities}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
+They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that non-trivial inequalities can be recovered from facets of a symmetric polytope.
+Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
+The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.\\
+
+    To demonstrate what types of symmetries we have in mind, we present the following example:
+    \begin{example}
+        \label[example]{ex:symmetries}
+        First consider the marginal scenario $\mscenario = \bc{\bc{A, B, C}, \bc{C, D}, \bc{A, D}}$ where each variable in $\jointvar = \bc{A,B,C,D}$ has binary outcomes: $O_A = O_B = O_C = O_D = \bc{0,1}$.
+Moreover, let $I_{\mscenario}$ be the following compatibility inequality over $\mscenario$ for some causal structure $\graph$,
+        \[ I_{\mscenario} = \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}  \]
+        Intuitively, the compatibility of $\probvec^{\mscenario}$ is \textit{independent} of the how one labels outcomes.
+Suppose $\varphi : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ is a permutation of the variables $\jointvar$.
+Intuitively $\varphi$ acts on $I_{\mscenario}$ in the following way,
+        \begin{align*}
+        \varphi\bs{I_{\mscenario}} &= \bc{\prob[\varphi\bs{abc}][010] \leq \prob[\varphi\bs{cd}][00] + \prob[\varphi\bs{ad}][01]} \\
+        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
+        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
+        \end{align*}
+        In general (as in this example), permutations over all variables can modify the marginal scenario $\varphi\bs{\mscenario} \neq \mscenario$; in general we write $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
+Although $\varphi\bs{I_{\mscenario}}$ is still a valid causal compatibility inequality, in constrains marginal models of a different marginal scenario $\varphi\bs{\mscenario}$ and are in general of no interest.
+    \end{example}
+
+    Following the observations of \cref{ex:symmetries}, it is always possible to permute the random variables in a marginal scenario to produce new and valid inequalities.
+The symmetry group over a the complete set of variables $\jointvar$ is simply the \text{permutation group}\footnote{The permutation group over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} $\Perm{\jointvar}$.
+As was noted in \cref{ex:symmetries}, some permutations $\varphi \in \Perm{\jointvar}$ have the undesired possibility of transforming $\mscenario$ into a different marginal scenario.
+    \[ \varphi\bs{\mscenario} \defined \bc{\varphi\bs{V_1}, \ldots, \varphi\bs{V_k}} \neq \mscenario \]
+    This means that there could exist $V \in \mscenario$ such that $\varphi\bs{V} \not \in \mscenario$.
+Permutations $\varphi$ retaining this property are unable to generate compatibility inequalities over the same marginal scenario.
+Therefore, the desired set of symmetries is a subgroup that takes $\mscenario$ to $\mscenario$.
+
+    \begin{definition}
+        The \term{variable permutation group} $\gp$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario.
+        \[ \Phi\br{\mscenario} \defined \bc{\varphi \in \Perm{\jointvar} \mid \forall V \in \mscenario : \varphi\bs{V} \in \mscenario} \]
+    \end{definition}
+
+    Obtaining the variable permutation group $\gp\br{\mscenario}$ is a simple application of a group stabilizer algorithm.
+After obtaining $\gp\br{\mscenario}$, one can take known compatibility inequalities $I_{\mscenario}$ can create a whole family of inequalities $\bc{\varphi\bs{I_{\mscenario}} \mid \varphi \in \gp\br{\mscenario}}$ that are valid for the same marginal scenario $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}} = \varphi\bs{I}_{\mscenario}$.
+\\
+
+    Although very useful for reducing computational complexity~\cite{Bancal_2010}, we divert our attention to finding \textit{symmetric} inequalities themselves.
+    \[ \forall \varphi \in \gp\br{\mscenario} :  \varphi\bs{I_{\mscenario}} = I_{\mscenario} \]
+    In order to do this, we must first define how elements $\varphi \in \gp$ act on marginal events.
+The action of $\varphi \in \gp$ on any outcome $f \in \Events{V}$ (denoted $\geo\bs{f}$) is defined as,
+    \[ \forall v \in \Dom{\varphi\bs{f}} : \br{\varphi\bs{f}}\br{v} \defined f\br{\varphi^{-1}\bs{v}} \eq \label{eq:act_on_variable}\]
+    \Cref{eq:act_on_variable} is nothing more than a mathematical definition for the intuitive action used in \cref{ex:symmetries}.
+    Through repeated action of $\varphi \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define \term{group orbits} of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$.
+    \begin{align*}
+        \Orb[\gp]{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \gp} \\
+        \Orb[\gp]{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \gp}
+    \end{align*}
+    Using these group orbits, it is possible to contract the incidence matrix $M$ of a marginal scenario into a symmetrized version.
+
+    \begin{definition}
+        The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and the variable permutation group $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
+Each row of $M_{\gp}$ corresponds to a marginal orbit $\Orb[\gp]{m}$.
+Analogously each column of $M_{\gp}$ corresponds to a joint orbit $\Orb[\gp]{j}$.
+The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
+        \[ \br{M_{\gp}}_{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M_{m',j'} \]
+    \end{definition}
+    It is possible to analogously define a \term{symmetric joint distribution vector} $\probvec^{\jointvar}_{\Phi}$ indexed by $\Orb[\gp]{j}$,
+    \[ \br{\probvec^{\jointvar}_{\Phi}}_{\Orb[\gp]{j}} = \sum_{j' \in \Orb[\gp]{j}} \probvec^{\jointvar}_{j} \]
+    And a \term{symmetric marginal distribution vector} $\probvec^{\mscenario}_{\Phi}$ indexed by $\Orb[\gp]{m}$,
+    \[ \br{\probvec^{\mscenario}_{\Phi}}_{\Orb[\gp]{m}} = \sum_{m' \in \Orb[\gp]{m}} \probvec^{\mscenario}_{m} \]
+    Which altogether define a new, \term{symmetric marginal problem},
+    \[ \probvec^{\mscenario}_{\Phi} = M_{\gp} \cdot \probvec^{\jointvar}_{\Phi} \]
+    The symmetric marginal problem can be solved using the same computational methods discussed in \cref{sec:deriving_inequalities} and will produce symmetric inequalities. \\
+
+    In the context of the Inflation technique, a variable symmetry $\Phi\br{\mscenario'}$ over an inflated marginal scenario $\mscenario'$ does not always correspond to a variable symmetry under deflation $\Phi\br{\mscenario}$.
+In order to derive deflated inequalities that are symmetric under an exchange of parties, it is required that $\Phi\br{\mscenario'} \sim \Phi\br{\mscenario}$ are equivalent up to copy-index.
+\\
+
+    For the Triangle scenario, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
+For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\PreInj[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
+    \begin{equation*}
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_1 \\
+    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_2 \\
+    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_3 \\
+    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_4 \\
+    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
+    \end{aligned}
+    \end{equation*}
+    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
+    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
+    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
+    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
+    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
+Moreover they stabilize the pre-injectable sets of \cref{eq:pre_injectable_triangle_scenario_web}.
+Importantly,
+    \[ \gp\br{\PreInj[\graph]{\graph'}} \sim \Perm{A,B,C} \]
+    To see this, $\varphi_1$ and $\varphi_4$ become the identity element $\ident$ in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
+\\
+
+    The symmetric incidence matrix $M_{\Phi}$ for the Web inflation is considerably smaller than $M$.
+The number of rows of $M_{\Phi}$ is a number of distinct orbits $\Orb[\Phi]{m}$ in $\Events{\mscenario}$.
+Likewise the number of columns is the number of distinct orbits $\Orb[\Phi]{j}$ in $\Events{\jointvar}$.
+For the Web inflation in particular, $M_{\Phi}$ is $450 \times 358,120$.
+Using the symmetric incidence matrix and linear programing methods, an infeasibility certificate was found that is capable of witnessing the Fritz distribution.
+This inequality is reproduced in \cref{sec:symmetic_web_inequality}.
+
+    \section{Violations \& Noise}
+    \label{sec:violations_noise}
+    Causal compatibility inequalities for the triangle scenario (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality.
+In this section, we illuminate two tasks that can be performed in order to further understand the nature of quantum non-classical by using inequalities.
+
+    \subsection{Noise}
+    \label{sec:noise}
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
+            \vspace{-0.2in}
+            \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
+            \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
+            \label{fig:uniform_distribution}
+    \end{center}
+    \end{figure}
+    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the triangle scenario by embedding Bell non-classicality.
+As was mentioned in \cref{sec:fritz_distribution}, this embedding required a very idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$.
+From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}.
+It is possible to minimize noise by developing more accurate measurement channels but perfect correlations are too idealistic.
+Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.
+\\
+
+    In the triangle scenario, we define a completely noisy observation as the uniform probability distribution $\s{U} = \s{U}_{ABC}$ (see \cref{fig:uniform_distribution})
+    \[ \s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}  \]
+    Since the uniform distribution $\s{U}$ is trivially compatible with the triangle scenario, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible.
+We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
+    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
+    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution as $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$.
+For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.
+As a standard, let $I\br{\prob} < 0$ represent violations while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturations of the inequality).
+\\
+
+    To analyze noise, $4$ inequalities where chosen.
+First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}.
+The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{sec:web_inequality} while $I_3$ is the symmetric inequality in \cref{sec:symmetic_web_inequality}.
+Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{sec:web_inequality}.
+
+    \begin{center}
+    \begin{figure}
+    \begin{subfigure}[b]{.48\linewidth}
+    \includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}
+    \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
+    \end{subfigure}
+    \begin{subfigure}[b]{.48\linewidth}
+    \includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}
+    \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
+    \end{subfigure}
+    \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
+    \end{figure}
+    \end{center}
+
+    The results of our experiments are plotted in \cref{fig:master_noise}.
+\Cref{fig:noise} illustrates that each curve $I\br{\s{N}_{\vep}\br{\prob[\fritz]}}$ as a function of $\vep$ is monotonically increasing as expected; the more noise added to the probability distribution, the more classical it becomes.
+\Cref{fig:noise_zoomed} is the same plot as \cref{fig:noise} zoomed onto the interval $\vep \in \bs{0, 0.12}$.
+These tests suggest that inequality $I_1$ (\cref{sec:web_inequality}), when compared against all others is most robust to noise.
+\\
+
+    Overall, this noise model demonstrates that the Fritz distribution remains incompatible with the triangle scenario up to at least a noise parameter of $\vep \simeq 0.085$.
+The associated distribution $\s N_{0.085}\br{\prob[\fritz]}$ is plotted in \cref{fig:noisy_fritz}.
+There remains the possibility that another inequality will be able to withstand a larger degree of noise that $I_1$.
+Given that $I_0, I_1, I_2, I_3$ are far from a representative inequalities and are likely not facets of any inflated marginal polytope, it is save to say that this is possible.
+
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
+            \vspace{-0.2in}
+            \[ \probplotvalue{255, 255, 243} = 0.00133 \]
+            \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
+            \label{fig:noisy_fritz}
+    \end{center}
+    \end{figure}
+
     \subsection{Numerical Optimizations}
-    \begin{itemize}
-        \item \todo[TC]{Generic idea}
-        \item \todo[TC]{Optimization techniques used}
-    \end{itemize}
+    \label{sec:optimizations}
+    Causal compatibility inequalities act as a \textit{measure} of non-classicality.
+If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$\footnote{Remember that larger violations are more negative when the inequalities are written in the proposed canonical form.} Nonetheless, this statement comes from several caveats.
+First, it is possible (and frequently the case) for ${I\br{\prob[1]}} < I\br{\prob[2]}$ to hold for one inequality $I$ but have ${\ti I\br{\prob[2]}} < \ti I\br{\prob[1]}$ hold for another inequality $\ti I$.
+In this case, all one can claim is that $\prob[1]$ is more incompatible than $\prob[2]$ with respective to $I$ but the contrary is true with respect to $\ti I$.
+Second, not all inequalities $I$ are \textit{good} measures of non-classicality.
+In the case of the Bell scenario, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality.
+This is because the facets form a necessary and sufficient set with all other inequalities following from positive mixtures of the facets.
+However, good measures of incompatibility are less understood in the triangle scenario where the space of classical correlations is non-convex.
+At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility (especially because they are curated toward the Fritz distribution).
+Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the triangle scenario.\\
+
+    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the triangle scenario in \cref{fig:triangle_scenario_quantum_model}.
+Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:quantum_model_triangle} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$.
+The objective value is simply the degree of violation $f = I\br{\prob[ABC]}$ and used to make adjustments to $\la$ in order to achieve largest and larger violations.
+\\
+
+    Finding larger violations to compatibility inequalities is nothing more that a numerical optimization (specifically minimization) of $f\br{\la}$.
+Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
+Specifically, the BFGS method~\cite[p.
+142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.
+238]{Nocedal_2000} were used along with a hybrid method called Basin Hopping~\cite{Wales_1997}.
+
+    \subsection{Parameterizing Quantum Distributions}
+    \label{sec:param_quantum_dist}
     \begin{figure}
@@
     \end{figure}
-    \subsection{Parameterizing Quantum Distributions}
-    \label{sec:param_quantum_dist}
     In search of new, incompatible, quantum distributions that can be realized on the triangle scenario, numerical optimizations over the the space of quantum-accessible probability distributions are performed.
@@
     Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately\footnote{$\netperm$ is discussed more thoroughly in \cref{sec:perm_matrix}.}.
+\\
 
@@
 
-    In Ref.~\cite{Spengler_2010_Unitary}, Spengler \textit{et. al.} proved that all unitaries $U \in \s{U}\br{d}$ can be parameterized without degeneracy as follows:
+    In Ref.~\cite{Spengler_2010_Unitary}, Spengler \textit{et al.} proved that all unitaries $U \in \s{U}\br{d}$ can be parameterized without degeneracy as follows:
     \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \tcdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
@@
     For the purposes discussed in \cref{sec:param_quantum_dist}, only $d = 4$ outcome measurements are utilized and therefore requiring $4\br{4 - 1} = 12$ real-valued parameters.
-This method was inspired by the measurement seeding method of P{\'{a}}l and V{\'{e}}rtesi's~\cite{Pal_2010} iterative optimization technique.
+This method was inspired by the measurement seeding method for iterative optimization used by \citet{Pal_2010} .
     \subsubsection{States}
@@
     Parameterizing the eigenvalues requires $d - 1$ real-valued parameters due to the trace constraint of \cref{eq:density_matrix}.
-The eigenvalues are parameterized without degeneracy using a tuple of $d-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{d-1}}, \lambda_i \in \bs{0, 2 \pi}$ using hyperspherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}:
+The eigenvalues are parameterized without degeneracy using a tuple of $d-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{d-1}}, \lambda_i \in \bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}:
     \begin{align*}
@@
     \end{align*}
-    Therefore it is possible to parametrize all $d$-dimensional density matrices satisfying \cref{eq:density_matrix} using $d\br{d - 1} + d - 1 = d^2 -1$ parameters.
+
+    Furthermore due to the periodicity of the parameter space $\bc{\lambda}$, \cref{eq:convex_param} can be used for either constrained or unconstrained optimization problems.
+For continuity reasons, unconstrained optimizations are performed whenever possible.
+In conclusion, it is possible to parametrize all $d$-dimensional density matrices satisfying \cref{eq:density_matrix} using $d\br{d - 1} + d - 1 = d^2 -1$ real-valued parameters.
+\\
+
+    Although non-degenerate, \cref{eq:convex_param} suffers from a lack of uniformity; a randomly sampled vector of parameters $\bc{\lambda}$ \textit{does not} translate to a randomly sampled set of eigenvalues $\bc{p_i}$.
+Another, albeit degenerate, parameterization of $\bc{p_i}$ involves beginning with $d$ real parameters $\lambda = \br{\lambda_1, \ldots, \lambda_d}$, then forcing normalization by dividing each parameter $\la_i$ by the their sum.\footnote{Strictly speaking, \cref{eq:uniform_param} \textit{also} suffers from non-uniformity; being biased toward eigenvalues that have similar values to each other.}.
+    \[ p_j = \f{\abs{\lambda_j}}{\sum_{i=1}^{n} \abs{\lambda_i}} \quad \forall j \in 1, \ldots, n \eq \label{eq:uniform_param} \]
+    For various optimization tasks sensitive to initial conditions outlined \cref{sec:optimizations}, the latter parameterization of \cref{eq:uniform_param} generally performed better than the former \cref{eq:convex_param}.
     \subsubsection{Permutation Matrix}
@@
         \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
-        \caption{The triangle scenario permutation matrix $\netperm$ for $\br{\Hilb^2}^{\otimes 6}$. Black represents a value of $1$ and white represents $0$.}
+        \caption{The permutation matrix $\netperm$ acting on $\br{\Hilb^2}^{\otimes 6}$ for the triangle scenario. Black entries represents a value of $1$ and white represents $0$.}
         \label{fig:perm_mtrx}
@@
     \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
-    \subsection{Results}
-    \begin{itemize}
-        \item \todo[TC]{Plots of various optimizations}
-        \item \todo[TC]{Features of maximally violating distributions}
-    \end{itemize}
+    \subsection{Numerical Optimization Results}
+    \label{sec:results}
 
-    \section{Noise}
-    \label{sec:noise}
-    \begin{itemize}
-        \item \todo[TC]{Recall why noise is important (experimental and foundational)}
-        \item \todo[TC]{Describe our noise model}
-        \item \todo[TC]{Plots}
-        \item \todo[TC]{Define and discuss the crossing point}
-        \item \todo[TC]{Discussion as to what noise measures}
-    \end{itemize}
+    \Cref{sec:param_quantum_dist} expounded on how we elected to parameterized the space of quantum distributions that can be realized on the quantum triangle scenario (\cref{fig:triangle_scenario_quantum_model}).
+Specifically, we make use of fully generic $4\times 4$ density matrices (bipartite qubit) for each shared resource and $4$-element projective measurements.
+For each inequality $I$, we define the relative violation $V_F$ to be maximum violation relative to the violation achieved by the Fritz distribution.
+    \[ V_F = \f{\min_{P}\bc{I\br{P}}}{I\br{P_F}} \]
+
+    The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{sec:web_inequality}.
+At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
+Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution.
+In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure} or set of possible events.
+What does this reveal about $I_1$ and non-classicality in the triangle scenario?
+This result is not entirely unexpected.
+As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to show incompatibility of the triangle scenario.
+Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for a specific forms of non-classicality that resemble the Fritz distribution very closely.
+\\
+
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
+            \caption{Probability distribution that maximizes violation of $I_1$ from \cref{sec:web_inequality} ($V_F \simeq 1.501$).}
+            \label{fig:maximum_violation_I_1}
+    \end{center}
+    \end{figure}
+
+    An alternative explanation has to do with the sensitively of the initial condition $\la_{\br{0}} = \br{\la_{\br{0}, 0}, \ldots, \la_{\br{0}, n}}$ in our optimization.
+In \cref{sec:param_quantum_dist}, it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
+Somewhat surprisingly, when using a uniform seed for $\la_0$, all optimization methods consistently converged to inequality saturation instead of inequality violation which of course is achievable by the Fritz distribution.
+Instead, only initial seeds close enough to the \textit{Fritz parameters} $\la_{\br{\fritz}}$ (the parameters that induce the Fritz distribution using the quantum implementation in \cref{sec:fritz_distribution}) where able to achieve violation.
+To illustrate this graphically, we let the initial seed be a small Gaussian perturbation $\de \la$ away from $\la_{\br{\fritz}}$ in parameter space.
+    \[ \la_{\br{0}} = \la_{\br{\fritz}} + \de \la  \]
+    The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation.
+For $I_1$, deviations of $\chi \gtrsim 1.3$ inhibited convergence to violation.
+This is depicted in \cref{fig:initial_conditions}.
+Therefore, it is unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
+Most likely, this phenomena is due to a combination of both effects.
+    \begin{center}
+    \begin{figure}
+    \begin{subfigure}[t]{.48\linewidth}
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}
+    \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
+    \end{subfigure}
+    \begin{subfigure}[t]{.48\linewidth}
+    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}
+    \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
+    \end{subfigure}
+    \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
+    \end{figure}
+    \end{center}
+    The second inequality in consideration is $I_3$; the \textit{symmetric} Web inflation inequality presented in \cref{sec:symmetic_web_inequality}.
+This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
+Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution.
+However, this result is far more surprising.
+Since the inequality is symmetric with respect to the exchange of parties $\varphi \in \Perm{A, B, C}$, one would naively expect that the maximum violating distribution is be symmetric as well.
+If it were not, one could construct a distribution that violates $I_3$ more by symmetrizing $\prob[\fritz]$ by summing over all possible permutations and normalizing.
+The symmetrized Fritz distribution is plotted in \cref{fig:symmetrized_fritz}.
+This distribution is also non-classical with relative violation $V_F = 3$.
+As it turns out, the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}\footnote{At least numerical optimizations suggest this is the case.} Therefore we conclude that the space of quantum accessible correlations on the triangle scenario is non-convex; a reiteration of a result found in~\citet{Inflation}.
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
+            \caption{Probability distribution that maximizes violation of $I_3$ from \cref{sec:symmetic_web_inequality} ($V_F \simeq 2.61$).}
+            \label{fig:maximum_violation_I_3}
+    \end{center}
+    \end{figure}
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
+            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
+            \label{fig:symmetrized_fritz}
+    \end{center}
+    \end{figure}
+
+    Finally for both $I_0$ and $I_2$, the maximum relative violation happens to be $V_F = 1$ (up to numerical precision).
+This means that the Fritz distribution either represents a local minimum of the parameter space or is in fact \textit{the} maximally violating distribution.
+Without further investigations, it is unclear if this behavior is related to the universality of the Fritz distribution or if its an artifact of the methods used to derive $I_0$ and $I_2$.
 
     \section{Conclusions}
-    \begin{itemize}
-        \item \todo[TC]{Inflation technique capable of finding inequalities witnessing quantum/classic difference in TS}
-        \item \todo[TC]{Causal incompatibility inequalities found violated by known distributions}
-        \item \todo[TC]{Maximal distributions are different than Fritz but still rely on Bell's theorem}
-        \item \todo[TC]{Refinement on Fritz's question}
-    \end{itemize}
+
+    In \cref{sec:triangle_scenario}, we elucidated that non-classicality in the triangle scenario has been an unsolved problem for nearly a decade.
+Initially,~\citet{Branciard_2012} identified the triangle scenario as a challenging causal structure for studying non-classicality.
+Afterwards,~\citet{Henson_2014} were able to to classify the triangle scenario as \textit{interesting} which partially explains why it remains an enigma.
+Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the triangle scenario.
+Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality.
+In \cref{sec:fritz_distribution} the Fritz distribution was introduced in detail and refinements where made to a problem originally proposed by~\citet{Fritz_2012}.
+For this research project, we made heavy use of the Inflation Technique of \cref{sec:inflation_technique} and the Fritz distribution in order to derive the first causal compatibility inequalities capable of having quantum violations.
+Finally, we used those inequalities in an attempt to discover new forms of non-classicality in the triangle scenario with partial success.\\
+
+    Ultimately, this work accomplishes two important tasks.
+First and foremost, the derivation of \cref{eq:ww_ineq} demonstrates the utility of the Inflation technique specifically for quantum causal inference problems.
+The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the triangle scenario -- a task that no other existing techniques succeeded at.
+Therefore, this work acts as a strong indication that the Inflation technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
+\\
+
+    Penultimately, the results presented here solve~\cite[Problem 2.17]{Fritz_2012} insofar as to refine the original problem into three related questions problems: \ref{r:1}, \ref{r:2} and \ref{r:3}.
+The methods and techniques demonstrated here provide a means of solving \ref{r:1} and gives an opportunity to begin tackling \ref{r:2} and \ref{r:3} in the form of numerical optimizations.
+Computational and comprehensive limitations have stunted progress towards solving \ref{r:2} and \ref{r:3}, so it still remains unclear if \ref{r:2} and \ref{r:3} have affirmative solutions in the first place.
 
     \section*{Acknowledgments}
+    T.C.
+Fraser would like to thank E.
+Wolfe for his excellent guidance and mentor-ship throughout the duration of this research project.
+Moreover, T.C.
+Fraser would like to thank the Perimeter Institute for financing this research and providing access to much needed computational resources.
+    \clearpage
+    \bibliography{../references}
+
+    \clearpage
+    \appendix
+
+    \section{Common Terminology \& Notation}
+
+    \subsection{Graph Theory}
+    \label{sec:graph_theory}
+    \begin{definition}
+        \label{def:graph}
+        A \term{graph} $\graph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes have the capacity to represent any object while the edges are defined as \textit{pairs} of nodes $\edges \subseteq \nodes \times \nodes$.
+A \term{directed graph} $\graph$ is a graph where each edge $e \in \edges$ is assigned an order or \term{direction} $e = \bc{n \to n'}$.
+    \end{definition}
+
+    \begin{definition}
+        \label{def:graph_terms}
+        The following definitions are common language in directed graph theory. Let $n, m \in \nodes$ be example nodes of the graph $\graph$.
         \begin{itemize}
-        \item \todo[TC]{Elie}
-        \item \todo[TC]{Perimeter}
-        \item \todo[TC]{University of Waterloo}
-        \item \todo[TC]{Possible due to Mike Lazaridis Scholarship}
+            \item The \term{parents of a node}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
+            \item The \term{children of a node}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
+            \item The \term{ancestry of a node}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$
+            \item The \term{descendants of a node}:  $\De[\graph]{n} \defined \bigcup_{i\in\mathbb{N}} \Ch[\graph][i]{n}$ where $\Ch[\graph][i]{n} \defined \Ch[\graph]{\Ch[\graph][i-1]{n}}$ and $\Ch[\graph][1]{n} = \Ch[\graph]{n}$
         \end{itemize}
-    \appendix
+        All of these terms can be generalized to sets of nodes $N \subseteq \nodes$ through union over the elements,
+        \begin{itemize}
+            \item The \term{parents of a node set}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
+            \item The \term{children of a node set}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
+            \item The \term{ancestry of a node set}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
+        \end{itemize}
+    \end{definition}
+
+    \begin{definition}
+        An \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$.
+        \[ \Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to n'} \mid n, n' \in N, e \in \edges}} \]
+        An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
+        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
+    \end{definition}
+
+    \begin{definition}
+        \label{def:dag}
+        A \term{directed acyclic graph} or \term{DAG} $\graph = \br{\nodes, \edges}$ is an directed graph with the additional property that no node $n$ is in its set of \term{ancestors}.
+        \[ \forall n \in \nodes : n \notin \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}\]
+        It is critical to note the difference in language between \textit{ancestors} from \textit{ancestry}.
+The ancestry $\An[\graph]{n}$ of a node $n$ is defined using \textit{whole} numbers $\mathbb{W}$.
+In contrast, the ancestors of a node are defined similarly with \textit{natural} numbers $\mathbb{N}$.
+    \end{definition}
+
+    \subsection{Probability Theory}
+    \label{sec:probability_theory}
+
+    \begin{definition}
+        The \term{product distribution} of two disjoint probability distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as $\prob[V] \times \prob[W]$.
+        \[ \forall s \in \Events{V \cup W} : \br{\prob[V] \times \prob[W]}\br{s} \defined \prob[V][s|_{V}]\tcdot\prob[W][s|_{W}] \]
+        A product distribution of $k$ mutually disjoint distributions is defined as,
+        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
+    \end{definition}
+
+    \begin{definition}
+        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
+        \[ \forall s \in \Events{W} : \br{\sum_{V \setminus W} \prob[V]}\br{s} \defined \sum_{j \in \Ext[V]{s}} \prob[V][j] \]
+        Where $\Ext[V]{s}$ denotes the set of all events $j \in \Events{V}$ that can be restricted to $s$,
+        \[ \Ext[V]{s} = \bc{j \in \Events{V} \mid s = j|_{\s{D}\br{s}}} \]
+    \end{definition}
+
     \section{Computationally Efficient Parameterization of the Unitary Group}
@@
 
-    \bibliography{../references}
+    \clearpage
+    \section{Large Triangle Scenario Inequalities}
+    \subsection{Web Inflation Inequality}
+    \label{sec:web_inequality}
+    The following is a causal compatibility inequality for the triangle scenario that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
+    \end{center}
+    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
+    \clearpage
+    \subsection{Symmetric Web Inflation Inequality}
+    \label{sec:symmetic_web_inequality}
+    The following is a symmetric causal compatibility inequality for the triangle scenario that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
+    \begin{center}
+        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
+    \end{center}
+    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for the sum over permutations:
+    \[ \bs{P(113)P(330)}_3 = P(113)P(330) + P(131)P(303) + P(311)P(033) \]
+
 \end{document}

### 2017-01-27 documents/TriangleScenario/ts.tex
small typo
Added journals to references

@@
 \usepackage{../../packages/misc_commands}
-\usepackage{subcaption}
-\usepackage{enumitem}
-
-\renewcommand{\Events}[1]{\mathcal{S}\br{#1}}
-\renewcommand{\tcdot}{\cdot}
+
+\renewcommand{\Events}[1]{\mathcal{S}\br{#1}} % This notation is conflicting
 
@@
 Given a joint distribution vector $\probvec^{\jointvar}$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec^{\jointvar}$.
-    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
+    \[ \probvec^{\mscenario} = M \cdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
     Because the marginal distribution vector $\probvec^{\mscenario}$ is simply another representation of the marginal model $\prob^{\mscenario}$, we will henceforth use the language interchangeably.
@@
     Each of the above mentioned techniques suffers from computational complexity limitations.
-For example, the Fourier-Motzkin procedure is act worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}.
+For example, the Fourier-Motzkin procedure is in the worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}.
 For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable.
@@
         \begin{alignat*}{2}
-            & \text{minimize:} \quad&& \emptyset \tcdot x\\
+            & \text{minimize:} \quad&& \emptyset \cdot x\\
             & \text{subject to:} && x \succeq 0 \\
-            & && M \tcdot x = \probvec^{\mscenario}
+            & && M \cdot x = \probvec^{\mscenario}
         \end{alignat*}
@@
         \begin{alignat*}{2}
-            & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
-            & \text{subject to:} && y \tcdot M \succeq 0
+            & \text{minimize:} \quad&& y \cdot \probvec^{\mscenario}\\
+            & \text{subject to:} && y \cdot M \succeq 0
         \end{alignat*}
@@
 If this is not obvious, first notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints become satisfied.
-Secondly if the dual constraint $y \tcdot M \succeq 0$ holds \textit{and} the primal is feasible, then the following must hold:
-    \[ y \tcdot \probvec^{\mscenario} =  y \tcdot M \tcdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
-    Therefore the \textit{sign} of the dual objective $d \defined \min \br{y \tcdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality.
+Secondly if the dual constraint $y \cdot M \succeq 0$ holds \textit{and} the primal is feasible, then the following must hold:
+    \[ y \cdot \probvec^{\mscenario} =  y \cdot M \cdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
+    Therefore the \textit{sign} of the dual objective $d \defined \min \br{y \cdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality.
 If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore $\probvec^{\mscenario}$ is contextual.
@@
     An \term{infeasibility certificate}~\cite{Andersen_2001} is any vector $y$ that satisfies the constraint of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
-    \[ y \in \R^{\abs{\Events{\mscenario}}} : y \tcdot M \succeq 0, \quad y \tcdot \probvec^{\mscenario} < 0 \]
+    \[ y \in \R^{\abs{\Events{\mscenario}}} : y \cdot M \succeq 0, \quad y \cdot \probvec^{\mscenario} < 0 \]
     Most linear program software packages such as Mosek~\cite{Mosek_2016}, Gurobi~\cite{Gurobi_2016}, CPLEX~\cite{Cplex_2016} and CVX/CVX OPT~\cite{CVX_2016,CVX_Opt_2016} are capable of producing infeasibility certificates.
-    Furthermore, for every $y$ satisfying $y \tcdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of non-contextual marginal models.
+    Furthermore, for every $y$ satisfying $y \cdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of non-contextual marginal models.
 If $y$ is an infeasibility certificate, then all non-contextual marginal models $\probvec^{\mscenario}$ must satisfy \cref{eq:dual_marginal_ineq} making $y \cdot \probvec^{\mscenario} \geq 0$ a valid causal compatibility inequality.
@@
     In Ref.~\cite{Spengler_2010_Unitary}, Spengler \textit{et al.} proved that all unitaries $U \in \s{U}\br{d}$ can be parameterized without degeneracy as follows:
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \tcdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
+    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
     Where $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ form a $d \times d$ matrix of real-valued parameters with periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
@@
         The \term{product distribution} of two disjoint probability distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as $\prob[V] \times \prob[W]$.
-        \[ \forall s \in \Events{V \cup W} : \br{\prob[V] \times \prob[W]}\br{s} \defined \prob[V][s|_{V}]\tcdot\prob[W][s|_{W}] \]
+        \[ \forall s \in \Events{V \cup W} : \br{\prob[V] \times \prob[W]}\br{s} \defined \prob[V][s|_{V}]\cdot\prob[W][s|_{W}] \]
         A product distribution of $k$ mutually disjoint distributions is defined as,
@@
     By combining the optimizations of \cref{eq:unitary_GP,eq:unitary_RP,eq:unitary_R} together we arrive at an equivalent form for \cref{eq:spengler_unitary} that is computational more efficient.
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n}RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}}  \eq \label{eq:spengler_unitary_fast} \]
+    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n}RP_{n,m}}} \cdot \bs{\prod_{l=1}^{d} GP_{l}}  \eq \label{eq:spengler_unitary_fast} \]
 
@@
     \begin{center}
+        % TODO [TC] replace this inequality with correct one
         \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
@@
     \begin{center}
+        % TODO [TC] replace this inequality with correct one
         \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}

### 2017-01-27 documents/TriangleScenarioArchive/ts.tex
getting the documents to work on sharelatex

--- 2017-01-27 documents/TriangleScenario/ts.tex
@@
 \renewcommand{\Events}[1]{\mathcal{S}\br{#1}} % This notation is conflicting
+\setlength{\parskip}{1em}
 
@@
 Presently, discovering situations or tasks where quantum mechanics offers an advantage, and proving that advantage is genuine, is a primal objective of theoretical quantum information theory.
-\\
 
@@
 Here we investigate one particular causal scenario: the triangle scenario (\cref{fig:triangle_scenario}).
-\\
 
@@
 The subject of this document is to expound on the developments made towards understanding quantum non-classicality in the triangle scenario.
-\\
 
@@
 Moreover, these new inequalities offer an avenue for finding and identifying new forms of non-classicality unknown previously.
-This report discusses attempts to find such resources with partial success and outlines refinements that can be made for future exploration.\\
+This report discusses attempts to find such resources with partial success and outlines refinements that can be made for future exploration.
 
@@
 With complete generality however, one could in principle make a measurement on a collection of portions of the system $\mscenario = \bc{V_1, \ldots, V_m \mid \forall i : V_i \subseteq \jointvar}$ obtaining a collection of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_m] \mid \forall i: V_i \in \mscenario}$.
-\\
 
@@
 The edges $\edges$ of a causal structure represent casual influence between variables within the causal structure.
-\\
 
@@
 If a marginal model $\prob^{\mscenario}$ happens to \textit{violate} any causal compatibility inequality, then that marginal model is definitely \textit{incompatible}.
-In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.\\
+In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.
 
@@
 Currently however, it is unknown how to obtain a complete characterization for any given causal structure, including the triangle scenario.
-\\
 
@@
 As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{triangle scenario} (\cref{fig:triangle_scenario}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
-\\
 
@@
 Characterizing quantum non-classicality for interesting causal structures remains an unsolved problem, and the triangle scenario is a small, non-trivial case study.
-\\
 
@@
 Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classical in the triangle scenario.
-\\
 
@@
 Therefore as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the triangle scenario that all others.
-\\
 
@@
 Most impressively, \citet{Inflation} derive a family of polynomial, $2$-outcome, causal compatibility inequalities; $37$ non-trivial representatives are printed in~\cite{Inflation}.
-\\
 
@@
 We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in triangle scenario for a degree of outcomes.
-\\
 
@@
 Understandably there are numerous ways that this can be accomplished, albeit we will focus on elucidating an exemplary method.
-\\
 
@@
     \[ 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} = 2\sqrt{2} \not \leq 2 \]
-    Therefore, the Fritz distribution is incompatible with the triangle scenario as promised. \\
+    Therefore, the Fritz distribution is incompatible with the triangle scenario as promised.
 
@@
     \[ \prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}} \]
-    Where $\netperm$ is a $64 \times 64$ permutation matrix to be elaborated in \cref{sec:perm_matrix}. \\
+    Where $\netperm$ is a $64 \times 64$ permutation matrix to be elaborated in \cref{sec:perm_matrix}.
 
@@
 Ultimately however, only $\rho_{AB}$ is required to be entangled in order to reproduce the Fritz; after-all, $C$ is simply classically announcing $A_r$ and $B_r$ as he receives them.
-\\
 
@@
 This problem is discussed more in \cref{sec:noise}.
-\\
 
@@
     The motivation behind this definition is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
-\\
 
@@
 Therefore, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
-\\
 
@@
 Fortunately, an inflated causal structure $\graph'$ possesses its own conditional independence relations which can be exploited to turn linear inequalities on $\graph'$ into polynomial inequalities on $\graph$.
-\\
 
@@
     Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that can are called the \term{pre-injectable sets}.
-A set $N' \subseteq \nodes'$ is a pre-injectable set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.\\
+A set $N' \subseteq \nodes'$ is a pre-injectable set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
 
@@
 One possibility is that the marginal model $\prob^{\mscenario}$ does not admit a joint distribution $\prob[\nodes]$.
-Alternatively, it could be possible that a joint distribution $\prob[\nodes]$ exists but can not factor into causal parameters as per \cref{eq:local_markov_property_operation}.\\
+Alternatively, it could be possible that a joint distribution $\prob[\nodes]$ exists but can not factor into causal parameters as per \cref{eq:local_markov_property_operation}.
 
@@
 The marginal problem has applications to numerous areas of mathematics including game theory~\cite{Vorobev_1962}, database theory, knowledge integration of expert system, and of course, quantum information theory~\cite{Fritz_2011}.
-\\
 
@@
 As such the Inflation Technique in many ways can be considered a relaxation technique which turns polynomial constraints into linear constraints.
-\\
 
@@
 Suppose one obtains a marginal distribution vector $\probvec^{\mscenario}$; the marginal problem becomes equivalent to the question:
-    \textit{Does there exist a joint distribution vector $\probvec^{\jointvar}$ such that \cref{eq:incidence_matrix_use} holds?} \\
+    \textit{Does there exist a joint distribution vector $\probvec^{\jointvar}$ such that \cref{eq:incidence_matrix_use} holds?}
 
@@
 In conclusion, there are a number of computational tools available to solve the marginal problem completely whenever no marginal model is provided.
-\\
 
@@
 Therefore, simpler approaches to the marginal problem needed to be considered.
-\\
 
@@
 This is a demonstration of the fundamental \textit{Unboundedness Property} of~\cite{Bradley_1977}; if the dual is unbounded, then the primal is infeasible.} This is manifestation of Farkas's lemma~\cite{Schrijver_1998}.
-\\
 
@@
 Finally, obtain infeasibility certificates using some linear programing software and obtain a valid causal compatibility inequality that witnesses the Fritz distribution's incompatibility.
-\\
 
@@
 Understandably, this matrix is not reproduced here.
-The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.\\
+The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
 
@@
     By construction, every marginal model $\probvec^{\mscenario} = \bc{\prob[ABC], \prob[AB], \prob[BC], \prob[AC], \prob[A], \prob[B], \prob[C]}$ compatible with the triangle scenario must satisfy \cref{eq:ww_ineq}.
-The Fritz distribution however violates \cref{eq:ww_ineq}.\\
+The Fritz distribution however violates \cref{eq:ww_ineq}.
 
@@
 In fact, smaller inflations of the triangle scenario such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
-\\
 
@@
 For inspection, one is reproduced in \cref{sec:web_inequality}.
-\\
 
@@
 This comes as a surprise because the Fritz distribution is \text{not} invariant under the exchange of parties; in fact the Fritz distribution is noticeably biased toward $C$.
-\\
 
@@
 Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
-The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.\\
+The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.
 
@@
 After obtaining $\gp\br{\mscenario}$, one can take known compatibility inequalities $I_{\mscenario}$ can create a whole family of inequalities $\bc{\varphi\bs{I_{\mscenario}} \mid \varphi \in \gp\br{\mscenario}}$ that are valid for the same marginal scenario $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}} = \varphi\bs{I}_{\mscenario}$.
-\\
 
@@
     \[ \probvec^{\mscenario}_{\Phi} = M_{\gp} \cdot \probvec^{\jointvar}_{\Phi} \]
-    The symmetric marginal problem can be solved using the same computational methods discussed in \cref{sec:deriving_inequalities} and will produce symmetric inequalities. \\
+    The symmetric marginal problem can be solved using the same computational methods discussed in \cref{sec:deriving_inequalities} and will produce symmetric inequalities.
 
@@
 In order to derive deflated inequalities that are symmetric under an exchange of parties, it is required that $\Phi\br{\mscenario'} \sim \Phi\br{\mscenario}$ are equivalent up to copy-index.
-\\
 
@@
     To see this, $\varphi_1$ and $\varphi_4$ become the identity element $\ident$ in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
-\\
 
@@
 Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.
-\\
 
@@
 As a standard, let $I\br{\prob} < 0$ represent violations while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturations of the inequality).
-\\
 
@@
 These tests suggest that inequality $I_1$ (\cref{sec:web_inequality}), when compared against all others is most robust to noise.
-\\
 
@@
 At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility (especially because they are curated toward the Fritz distribution).
-Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the triangle scenario.\\
+Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the triangle scenario.
 
@@
 The objective value is simply the degree of violation $f = I\br{\prob[ABC]}$ and used to make adjustments to $\la$ in order to achieve largest and larger violations.
-\\
 
@@
     Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately\footnote{$\netperm$ is discussed more thoroughly in \cref{sec:perm_matrix}.}.
-\\
 
@@
 In conclusion, it is possible to parametrize all $d$-dimensional density matrices satisfying \cref{eq:density_matrix} using $d\br{d - 1} + d - 1 = d^2 -1$ real-valued parameters.
-\\
 
@@
 Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for a specific forms of non-classicality that resemble the Fritz distribution very closely.
-\\
 
@@
 For this research project, we made heavy use of the Inflation Technique of \cref{sec:inflation_technique} and the Fritz distribution in order to derive the first causal compatibility inequalities capable of having quantum violations.
-Finally, we used those inequalities in an attempt to discover new forms of non-classicality in the triangle scenario with partial success.\\
+Finally, we used those inequalities in an attempt to discover new forms of non-classicality in the triangle scenario with partial success.
 
@@
 Therefore, this work acts as a strong indication that the Inflation technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
-\\
 
@@
     \clearpage
-    \bibliography{../references}
+    \bibliography{references}
 

### 2017-02-21 documents/TriangleScenarioArXiv/ts.tex
minor edits, spelling/phrasing etc

--- 2017-01-27 documents/TriangleScenarioArchive/ts.tex
@@
+\PassOptionsToPackage{justification=justified}{caption}
 % === Revtex Declaration ===
@@
 \renewcommand{\Events}[1]{\mathcal{S}\br{#1}} % This notation is conflicting
-\setlength{\parskip}{1em}
 
@@
     \begin{abstract}
-        Quantum correlations are often incompatible with a classical assumption of causal structure.
-This non-classicality is often known as quantum non-locality, and it is witnessed through the violation of causal compatibility inequalities, such as Bell inequalities.
-Such inequalities were recently derived for the triangle scenario [arXiv:1609.00672], begging the question: can these inequalities be violated by quantum correlations?
-Here we answer this affirmatively, and discuss specific triangle scenario inequalities and quantum configurations which manifest non-classical correlations.
-Numerical optimizations reveal quantum resources potentially qualitatively different from those known previously.
+        It has long been recognized that certain quantum correlations are often incompatible with particular assumption about classical causal structure.
+Such correlations are sometimes termed nonlocal, although it would be more accurate to say simply noncassical, as the presence of correlations certifies the genuinely nonclassical nature of a causal setup in a device-independent fashion.
+Whenever a  quantum correlation violates a causal compatibility inequality (e.g.
+a Bell inequality) then the correlation is witnessed as nonclassical.
+Any constraint which is satisfied by all correlations which \emph{are} classically compatible with a given causal scenario defined a causal compatibility criterion.
+Such criteria were recently were recently derived for the triangle scenario [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?
+Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical triangle triangle scenario is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary.
+Our main contribution inn this work, however, is the derivation of new causal compatibility inequalities for the triangle scenario which \emph{do} admit quantum violation.
+We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
     \end{abstract}
@@
     \tableofcontents
+    \setlength{\parskip}{1em}
     \clearpage
@@
     \label{sec:introduction}
-    In recent decades, the technical utility of quantum mechanics has become abundantly clear; quantum computational algorithms such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016} maintain advantage over their classical counterparts.
-Additionally, classical communications technologies stand to benefit from the nature of quantum mechanics --- a popular example being Quantum Key Distribution~\cite{Bennett_2014}.
-Any time classical resources are unable to emulate quantum mechanics, there represents an opportunity to exploit the non-classical features of quantum mechanics in order to solve a variety of computational and communicational problems~\cite{Neilsen_Chaung_2011}.
-Albeit, not all tasks stand to benefit from quantum resources~\cite{Almeida_2010}.
-Presently, discovering situations or tasks where quantum mechanics offers an advantage, and proving that advantage is genuine, is a primal objective of theoretical quantum information theory.
-
-    From a foundational prospective, the majority of attempts to characterize precisely where quantum mechanics and classical mechanics differ have involved Bell inequalities~\cite{Bell_1964}.
-Originally, Bell inequalities were derived in response to the famous EPR paradox~\cite{EPR_Orig} to rule out hidden variable theories for quantum mechanics.
-Studying and discovering Bell-type inequalities is useful because a complete set of Bell inequalities provides a systematic way of classifying the \textit{classicality} of a given observation.
-These inequalities are best understood from the perspective of \term{causal inference} --- a problem which aims to determine which observations can or can not be explained by a hypothesized causal structure.
+    In recent decades, the technical utility of quantum mechanics has become abundantly clear.
+In the realm of computation, quantum algorithms -- such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016} -- scale exponentially better than their classical counterparts.
+In the realm of secure communication, quantum protocols --- a popular example being Quantum Key Distribution~\cite{Bennett_2014} -- are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill.
+History, every opportunity of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the nonclassical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}.
+Motivated by past successes, a primal objective of modern quantum information theory is the discovery of new situations wherein quantum mechanics offers an advantage, and certification that the quantum advantage is genuine.
+
+    From a foundational prospective, the most robust demonstrations of quantum phenemena with no classical emulation have involved Bell inequalities~\cite{Bell_1964}.
+Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}.
+The enumeration of Bell inequalities has since become a widespread systematic way of demonstration the \textit{nonclassicality} of a given observation.
+More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}.
+Causal inference is concerned with classifying observations into those which can and cannot be explained by a hypothesized causal structure.
 The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}.
-Inequalities such as Bell inequalities constrain the space of observations that are compatible with a hypothesized causal structure.
-In the case of the original Bell inequalities, the classical causal model in question is known as the Bell scenario~\cite{Wood_2012} and is depicted in \cref{fig:bell_scenario}.
-The Bell scenario involves two parties ($A, B$) who each make measurements decided by random settings ($S_A, S_B$) on a shared hidden resource $\la$.
-Quantum non-classicality in the Bell scenario and related structures have been studied thoroughly since Bell's original work~\cite{Brunner_2013}.
-However, novel scenarios such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014} are arguably less understood compared to the Bell scenario.
+Causal compatability inequalities, such as Bell of Instrumental inequalities, charechterize the space of observations that are compatible with a hypothesized causal structure, albeit the charechterization offered by practically deriveable inequalities often only an approximation.
+To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell scenario, as depicted in \cref{fig:bell_scenario}.
+The fundamental Bell scenario involves noncommunicating parties making measurements on some hidden shared resource $\la$, where the measuremement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$.
+Quantum nonclassicality in the Bell scenario has been thoroughly studied since Bell's original work~\cite{Brunner_2013}.
+More complex scenarios, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood.
 Here we investigate one particular causal scenario: the triangle scenario (\cref{fig:triangle_scenario}).
@@
     The triangle scenario (\cref{fig:triangle_scenario}) is a causal structure composed of $3$ parties labeled $A, B, C$ arranged in a triangular configuration while pair-wise sharing hidden/latent variables $X, Y, Z$.
-It has been studied extensively in literature before (see~\cite[Fig.
+It has been extensively studied previously (see~\cite[Fig.
 1]{Steudel_2010},~\cite[Fig.
@@
 8]{Branciard_2012},~\cite[Fig.
-8, Appendix E]{Henson_2014},~\cite[Fig.
+8, App.
+E]{Henson_2014},~\cite[Fig.
 3]{Fritz_2012},~\cite[Fig.
 1]{Inflation}, $\ldots$).
-A healthy portion of which the existing literature will be discussed in \cref{sec:triangle_scenario}.
-For instance \citet{Branciard_2012} noted that characterizing locality in the triangle scenario remained an \textit{open problem} and that identifying causal compatibility inequalities for this configuration \textit{seemed challenging}.
-The subject of this document is to expound on the developments made towards understanding quantum non-classicality in the triangle scenario.
-
-    As a preliminary summary, causal compatibility inequalities were derived for the triangle scenario that are able to be violated by specific quantum-accessible distributions.
-This was accomplished by combining two previous works.
+An overview of some milestone results is provided in \cref{sec:triangle_scenario}.
+Identifying causal compatibility inequalities for this configuration has been seen as particularly challenging~\citet{Branciard_2012}.
+Further identifying causal compatibility inequalities of such high resolution that such inequalities can be violated by quantum-accessible distributions has remained out-of-reach for the triangle scenario.
+
+    This work is the first, therefore, to find causal compatibility inequalities for the triangle scenario that are able to be violated by quantum-accessible distributions.
+This accomplishment was made possible through the combination of two previous developments.
 The first, an insight made by \citet{Fritz_2012} regarding the ability to re-interpret the Bell scenario as a portion of the triangle scenario.
 The second, a new framework for solving causal inference problems developed by Wolfe \emph{et al.}~\cite{Inflation} called \term{The Inflation Technique}.
-Ultimately, this work serves as a strong indication that the Inflation Technique offers new insights into specifically quantum non-classicality.
-Moreover, these new inequalities offer an avenue for finding and identifying new forms of non-classicality unknown previously.
-This report discusses attempts to find such resources with partial success and outlines refinements that can be made for future exploration.
-
-    The following paper is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used.
-\Cref{sec:triangle_scenario} discusses the triangle scenario and its existing research in detail; identifying its stark differences from the Bell scenario and motivates why the triangle scenario was chosen as a case study.
-\Cref{sec:fritz_distribution} defines and discusses a singular quantum correlation first discovered by \citet{Fritz_2012} which we term the \term{Fritz distribution}.
-The Fritz distribution was proven to be non-classical without the use of inequalities --- this report derives inequalities that do.
-\Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the context of this work.
-Although the summary presented here is sufficient, the original work~\cite{Inflation} offers a more concrete and pedagogical introduction.
+Ultimately, this work serves as a validation that the Inflation Technique is sensitive enough to offer new insights into quantum nonclassicality.
+Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of nonclassicality.
+The authors attempts to find such novel resources were met with only partial success, suggesting clear refinements for future exploration.
+
+    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used.
+\Cref{sec:triangle_scenario} discusses the triangle scenario and provides an overview of existing research; identifying its stark differences from the Bell scenario and motivating why the triangle scenario was chosen as a case study.
+\Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first concieved of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}.
+The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities.
+\Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work.
+Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}.
 \Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the triangle scenario that are violated by quantum-accessible distributions.
-A sample of these inequalities are presented at the end of \cref{sec:deriving_inequalities} as well as \cref{sec:web_inequality,sec:symmetic_web_inequality}.
-Finally, \cref{sec:violations_noise} mentions a method for parameterizing the space of quantum-accessible distributions which is used to numerically optimize against our derived inequalities in search of stronger types of non-classicality.
+A sample of these inequalities are presented at the end of \cref{sec:deriving_inequalities} as well as in \cref{sec:web_inequality,sec:symmetic_web_inequality}.
+Finally, \cref{sec:violations_noise} introduces the method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality.
 Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.
@@
     \label{sec:causal_compatibility}
-    The task of causal inference aims to determine whether or not a given family of observed probability distributions can be explained by a proposed causal mechanism~\cite{Pearl_2009}.
+    The task of causal inference aims to determine the set of potentially observable probability distribution compatible with some hypothesis about causal relationships.
+whether or not a given family of observed probability distributions can be explained by a proposed causal mechanism~\cite{Pearl_2009}.
 If a set of observed distributions can be explained by the hypothesized causal mechanism, then the observations are said to be \textit{compatible} with the causal mechanism.
@@
     Given a set of observable variables $\jointvar = \bc{v_1, \ldots, v_k}$ where each $v \in \jointvar$ is a statistical random variable, one can conceivably make a measurement over of these variables and obtain a joint probability distribution $\prob[\jointvar] = \prob[v_1,\ldots,v_n]$.
-More generally however, and depending on the context, it is possible to make a measurement on a portion of the system $V \subset \jointvar$ in order to obtain a marginal distribution $\prob[V]$.
-With complete generality however, one could in principle make a measurement on a collection of portions of the system $\mscenario = \bc{V_1, \ldots, V_m \mid \forall i : V_i \subseteq \jointvar}$ obtaining a collection of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_m] \mid \forall i: V_i \in \mscenario}$.
+More generally however, and depending on the context, it is possible to make a measurement on a set of the system $V \subset \jointvar$ in order to obtain a marginal distribution $\prob[V]$.
+With complete generality however, one could in principle be limited so as to only be able to record observations on portions of the system $\mscenario = \bc{V_1, \ldots, V_m \mid \forall i : V_i \subseteq \jointvar}$ obtaining a collection of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_m] \mid \forall i: V_i \in \mscenario}$.
 
@@
     \[ \forall V \in \mscenario, V' \subset V : V' \in \mscenario \]
-    Throughout this document, we only consider (without loss of generality) the \textit{maximal} marginal scenario; restricting our focus to the largest contexts in the marginal scenario.
+    Throughout this document, we exclusively consider (without loss of generality) the \textit{maximal} marginal scenario; restricting our focus to the largest contexts in the marginal scenario.
 Additionally, all marginal scenarios are taken to be \text{complete} in the sense that the marginal scenario covers the complete set of observable variables $\jointvar$.
@@
     \subsection{Causal Structure}
-    A \term{causal structure} abstractly represents the hypothesized causal mechanism.
-Mathematically, a causal structure is a directed acyclic graph $\graph = \br{\nodes, \edges}$ of nodes $\nodes$ and edges $\edges$ as defined in \cref{sec:graph_theory}.
+    A hypothesis of causal mechanism is formally referred to as  a \term{causal structure}.
+Mathematically, a causal structure can be represented as a directed acyclic graph $\graph = \br{\nodes, \edges}$ of nodes $\nodes$ and edges $\edges$ as defined in \cref{sec:graph_theory}.
 The nodes of a causal structure are random variables and are classified into two disjoint classes: the \term{latent nodes} $\nodes_L$ representing the set of nodes that are unobservable and the \term{observed nodes} $\nodes_O$.
@@
     Now that the notions of a causal structure $\graph$ and a marginal model $\prob^{\mscenario}$ are defined, it is now possible to precisely define the notion of compatibility between the two.
-Intuitively, the causal connections within $\graph$ should restrict and limit the set of possible observations that can be made on $\graph$.
-Namely, if each variable $n \in \nodes$ is caused by its parents $\Pa[\graph]{n}$, then $n$ should be independent of all other variables that are not its descendants.
+Intuitively, the absence of certain causal connections within $\graph$ should restrict and limit the set of possible observations that can be made on $\graph$; equivalently, the causal connections within $\graph$ should explain $\prob^{\mscenario}$.
+If each variable $n \in \nodes$ is caused by its parents $\Pa[\graph]{n}$, then $n$ should be independent of all other variables that are not its descendants.
 This is known as the \term{local Markov property}:
@@
 Instead, \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of simply Bell inequalities for two reasons.
-First, ``Bell inequalities'' usually are associated specifically with the Bell scenario/Bell causal structure.
-Second, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob^{\mscenario}$ instead of \textit{linear}.} are probabilistic inequalities defined over the marginal contexts $\prob[V] \in \prob^{\mscenario}$ within the marginal model.
+Firstly, ``Bell inequalities'' usually are associated specifically with the Bell scenario/Bell causal structure.
+Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob^{\mscenario}$ instead of \textit{linear}.} are probabilistic inequalities defined over the marginal contexts $\prob[V] \in \prob^{\mscenario}$ within the marginal model.
 If a marginal model $\prob^{\mscenario}$ happens to \textit{violate} any causal compatibility inequality, then that marginal model is definitely \textit{incompatible}.
@@
 
-    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the triangle scenario if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that the joint distribution $\prob[\nodes] = \prob[ABCXYZ]$ is a product over the causal parameters,
-    \[ \prob[ABCXYZ] = \prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
-    And also, the given distribution $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$:
+    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the triangle scenario if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that
+    %the joint distribution $\prob[\nodes] = \prob[ABCXYZ]$ is a product over the causal parameters,
+    %\[ \prob[ABCXYZ] = \prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
+    %And also, the given distribution 
+    $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$:
     \[ \prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \eq \label{eq:triangle_compatibility} \]
@@
     For certain causal structures, the conditional independence relations provided by $d$-separation relations are a sufficient characterization of compatibility.
-Recently, \citet{Henson_2014}, classified the triangle scenario as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the triangle scenario possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover, \citet{Inflation} concretely demonstrate that the space classical distributions on the triangle scenario is non-convex, unlike the Bell scenario.
+Recently, \citet{Henson_2014}, classified the triangle scenario as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the triangle scenario possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover, \citet{Inflation} concretely demonstrate that the space of classical distributions on the triangle scenario is non-convex, unlike the Bell scenario.
 It can be argued that convexity of the Bell scenario distributions is partially responsible for the wealth of knowledge that is known about the Bell scenario.
@@
 
-    Additionally, \citet{Fritz_2012} demonstrated that the triangle scenario is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell scenario in that measure setting variables are non-existence in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we have elected to call the Fritz distribution (see \cref{sec:fritz_distribution}).
+    Additionally, \citet{Fritz_2012} demonstrated that the triangle scenario is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell scenario in that measure setting variables are non-existent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we have elected to call the Fritz distribution (see \cref{sec:fritz_distribution}).
 Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classical in the triangle scenario.
+     \comment[E]{Revisions processed up to here thusfar.}
 

### 2017-03-08 documents/TriangleScenarioArXiv/ts.tex
scenario -> structure, capitalized 'Triangle' in 'triangle scenario

@@
 \begin{document}
-    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
+    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
     \author{Thomas C. Fraser}
@@
 Any constraint which is satisfied by all correlations which \emph{are} classically compatible with a given causal scenario defined a causal compatibility criterion.
-Such criteria were recently were recently derived for the triangle scenario [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?
-Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical triangle triangle scenario is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary.
-Our main contribution inn this work, however, is the derivation of new causal compatibility inequalities for the triangle scenario which \emph{do} admit quantum violation.
+Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?
+Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical triangle Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary.
+Our main contribution inn this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \emph{do} admit quantum violation.
 We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
@@
 Causal compatability inequalities, such as Bell of Instrumental inequalities, charechterize the space of observations that are compatible with a hypothesized causal structure, albeit the charechterization offered by practically deriveable inequalities often only an approximation.
-To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell scenario, as depicted in \cref{fig:bell_scenario}.
-The fundamental Bell scenario involves noncommunicating parties making measurements on some hidden shared resource $\la$, where the measuremement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$.
-Quantum nonclassicality in the Bell scenario has been thoroughly studied since Bell's original work~\cite{Brunner_2013}.
+To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_scenario}.
+The fundamental Bell structure involves noncommunicating parties making measurements on some hidden shared resource $\la$, where the measuremement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$.
+Quantum nonclassicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}.
 More complex scenarios, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood.
-Here we investigate one particular causal scenario: the triangle scenario (\cref{fig:triangle_scenario}).
-
-    The triangle scenario (\cref{fig:triangle_scenario}) is a causal structure composed of $3$ parties labeled $A, B, C$ arranged in a triangular configuration while pair-wise sharing hidden/latent variables $X, Y, Z$.
+Here we investigate one particular causal scenario: the Triangle structure (\cref{fig:triangle_structure}).
+
+    The Triangle structure (\cref{fig:triangle_structure}) is a causal structure composed of $3$ parties labeled $A, B, C$ arranged in a triangular configuration while pair-wise sharing hidden/latent variables $X, Y, Z$.
 It has been extensively studied previously (see~\cite[Fig.
@@
 1]{Inflation}, $\ldots$).
-An overview of some milestone results is provided in \cref{sec:triangle_scenario}.
+An overview of some milestone results is provided in \cref{sec:triangle_structure}.
 Identifying causal compatibility inequalities for this configuration has been seen as particularly challenging~\citet{Branciard_2012}.
-Further identifying causal compatibility inequalities of such high resolution that such inequalities can be violated by quantum-accessible distributions has remained out-of-reach for the triangle scenario.
-
-    This work is the first, therefore, to find causal compatibility inequalities for the triangle scenario that are able to be violated by quantum-accessible distributions.
+Further identifying causal compatibility inequalities of such high resolution that such inequalities can be violated by quantum-accessible distributions has remained out-of-reach for the Triangle structure.
+
+    This work is the first, therefore, to find causal compatibility inequalities for the Triangle structure that are able to be violated by quantum-accessible distributions.
 This accomplishment was made possible through the combination of two previous developments.
-The first, an insight made by \citet{Fritz_2012} regarding the ability to re-interpret the Bell scenario as a portion of the triangle scenario.
+The first, an insight made by \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure.
 The second, a new framework for solving causal inference problems developed by Wolfe \emph{et al.}~\cite{Inflation} called \term{The Inflation Technique}.
@@
     The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used.
-\Cref{sec:triangle_scenario} discusses the triangle scenario and provides an overview of existing research; identifying its stark differences from the Bell scenario and motivating why the triangle scenario was chosen as a case study.
+\Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure was chosen as a case study.
 \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first concieved of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}.
@@
 Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}.
-\Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the triangle scenario that are violated by quantum-accessible distributions.
+\Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions.
 A sample of these inequalities are presented at the end of \cref{sec:deriving_inequalities} as well as in \cref{sec:web_inequality,sec:symmetic_web_inequality}.
@@
 
-    A number of causal structures are depicted throughout this document (see \cref{fig:bell_scenario,fig:triangle_scenario} as well as \cref{fig:inflations}).
-As an example, the triangle scenario has $3$ observable nodes and $3$ latent nodes,
+    A number of causal structures are depicted throughout this document (see \cref{fig:bell_scenario,fig:triangle_structure} as well as \cref{fig:inflations}).
+As an example, the Triangle structure has $3$ observable nodes and $3$ latent nodes,
     \[ \nodes_{O} = \bc{A, B, C} \qquad \nodes_{L} = \bc{X, Y, Z} \]
@@
 Instead, \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of simply Bell inequalities for two reasons.
-Firstly, ``Bell inequalities'' usually are associated specifically with the Bell scenario/Bell causal structure.
+Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure/Bell causal structure.
 Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob^{\mscenario}$ instead of \textit{linear}.} are probabilistic inequalities defined over the marginal contexts $\prob[V] \in \prob^{\mscenario}$ within the marginal model.
@@
 Instead, a \textit{complete characterization} of compatibility would consist of a complete set of all valid causal compatibility inequalities; satisfaction of a complete set of inequalities does prove compatibility.
-Currently however, it is unknown how to obtain a complete characterization for any given causal structure, including the triangle scenario.
+Currently however, it is unknown how to obtain a complete characterization for any given causal structure, including the Triangle structure.
 
@@
 
-    \section{Triangle Scenario}
-    \label{sec:triangle_scenario}
+    \section{Triangle Structure}
+    \label{sec:triangle_structure}
 
@@
             \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
-            \caption{The Bell scenario consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively.
+            \caption{The Bell structure consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively.
 The shared hidden variable is labeled $\la$.}
@@
             \centering
-            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
-            \caption{The casual structure of the triangle scenario. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
-            \label{fig:triangle_scenario}
+            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
+            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
+            \label{fig:triangle_structure}
         \end{minipage}
@@
     \end{figure}
-    Discovering quantum non-classicality in any causal structure is desirable, so why, in particular, is it important to do so in the triangle scenario?
-As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{triangle scenario} (\cref{fig:triangle_scenario}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
-
-    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the triangle scenario if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that
+    Discovering quantum non-classicality in any causal structure is desirable, so why, in particular, is it important to do so in the Triangle structure?
+As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
+
+    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that
     %the joint distribution $\prob[\nodes] = \prob[ABCXYZ]$ is a product over the causal parameters,
@@
     For certain causal structures, the conditional independence relations provided by $d$-separation relations are a sufficient characterization of compatibility.
-Recently, \citet{Henson_2014}, classified the triangle scenario as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the triangle scenario possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover, \citet{Inflation} concretely demonstrate that the space of classical distributions on the triangle scenario is non-convex, unlike the Bell scenario.
-It can be argued that convexity of the Bell scenario distributions is partially responsible for the wealth of knowledge that is known about the Bell scenario.
+Recently, \citet{Henson_2014}, classified the Triangle structure as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the Triangle structure possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover, \citet{Inflation} concretely demonstrate that the space of classical distributions on the Triangle structure is non-convex, unlike the Bell structure.
+It can be argued that convexity of the Bell structure distributions is partially responsible for the wealth of knowledge that is known about the Bell structure.
 It is also reasonable to speculate that quantum non-classicality in the triangle can be translated directly into a computational advantage for certain computational circuits~\cite{Terhal_2002}.
-Characterizing quantum non-classicality for interesting causal structures remains an unsolved problem, and the triangle scenario is a small, non-trivial case study.
-
-    Additionally, \citet{Fritz_2012} demonstrated that the triangle scenario is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell scenario in that measure setting variables are non-existent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we have elected to call the Fritz distribution (see \cref{sec:fritz_distribution}).
-Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classical in the triangle scenario.
+Characterizing quantum non-classicality for interesting causal structures remains an unsolved problem, and the Triangle structure is a small, non-trivial case study.
+
+    Additionally, \citet{Fritz_2012} demonstrated that the Triangle structure is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell structure in that measure setting variables are non-existent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we have elected to call the Fritz distribution (see \cref{sec:fritz_distribution}).
+Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classical in the Triangle structure.
     \comment[E]{Revisions processed up to here thusfar.}
@@
     Finally \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}), a novel tool for solving causal inference problems.
-Using the inflation technique, they were able to prove incompatibility between the triangle scenario and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints.
-Therefore as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the triangle scenario that all others.
-
-    It is worth noting that a number of causal compatibility inequalities for the triangle scenario have been derived in previous works.
+Using the inflation technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints.
+Therefore as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure that all others.
+
+    It is worth noting that a number of causal compatibility inequalities for the Triangle structure have been derived in previous works.
 For example, \citet{Steudel_2010} derived an inequality for a series of causal structures with $n \in \N$ variables where at most $c \in \N$ share a common ancestor.
-The triangle scenario is a special case with $c = 2$, $n = 3$.
+The Triangle structure is a special case with $c = 2$, $n = 3$.
 Moreover, \citet{Henson_2014} derive a family of entropic inequalities constraining the set of compatible correlations.
@@
 
-    As a preliminary search for quantum incompatibility in the triangle scenario, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}.
+    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}.
 Unfortunately, none of these inequalities could be violated.
-These early results suggest, although do not prove, that quantum non-classical does not exist in the triangle scenario for \textit{two-outcome} measurements.
-We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in triangle scenario for a degree of outcomes.
-
-    In conclusion, the triangle scenario is a causal structure whose non-classicality remains an open problem.
-The triangle scenario is a desirable case study because there is a quantum distribution that is known to be incompatible, but no previously known inequalities were able to witness its incompatibility.
+These early results suggest, although do not prove, that quantum non-classical does not exist in the Triangle structure for \textit{two-outcome} measurements.
+We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in Triangle structure for a degree of outcomes.
+
+    In conclusion, the Triangle structure is a causal structure whose non-classicality remains an open problem.
+The Triangle structure is a desirable case study because there is a quantum distribution that is known to be incompatible, but no previously known inequalities were able to witness its incompatibility.
 This failure represents a gap in our understanding of quantum non-classicality, where recent developments (namely the Inflation Technique) have made partial progress.
-This document expands on our understanding of non-classicality in the triangle scenario and also our understanding on how to find inequalities using the Inflation Technique for interesting causal structures in general.
+This document expands on our understanding of non-classicality in the Triangle structure and also our understanding on how to find inequalities using the Inflation Technique for interesting causal structures in general.
 
@@
     \begin{center}
-        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational_fritz_bell}}
-        \caption{The triangle scenario re-imagined to mimic the Bell scenario. The measurement settings $S_{\p{A}},S_{\p{B}}$ are latent nodes unlike the Bell scenario (\cref{fig:bell_scenario}).}
-        \label{fig:triangle_scenario_with_fritz_bell_embedded}
+        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational_fritz_bell}}
+        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{\p{A}},S_{\p{B}}$ are latent nodes unlike the Bell structure (\cref{fig:bell_scenario}).}
+        \label{fig:triangle_structure_with_fritz_bell_embedded}
     \end{center}
@@
 
-    As was originally noticed by \citet{Fritz_2012}, it is possible to construct quantum distributions incompatible with the triangle scenario by utilizing quantum distributions incompatible with the familiar Bell scenario.
-To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_scenario_with_fritz_bell_embedded} and contrast it with the Bell scenario of \cref{fig:bell_scenario}.
-Evidently, under the correct relabeling, large portions of the Triangle Scenario resemble the Bell Scenario.
-The crucial distinction is that the measurement settings $S_{\p{A}}, S_{\p{B}}$ are \textit{observable variables} in the Bell scenario but become \textit{latent variables} in the triangle scenario.
-In order to embed distributions that are incompatible with the Bell scenario into the triangle scenario, the latent nodes $S_{\p{A}}, S_{\p{B}}$ need to be observable and independent of the shared latent node $\la$.
+    As was originally noticed by \citet{Fritz_2012}, it is possible to construct quantum distributions incompatible with the Triangle structure by utilizing quantum distributions incompatible with the familiar Bell structure.
+To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} and contrast it with the Bell structure of \cref{fig:bell_scenario}.
+Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure.
+The crucial distinction is that the measurement settings $S_{\p{A}}, S_{\p{B}}$ are \textit{observable variables} in the Bell structure but become \textit{latent variables} in the Triangle structure.
+In order to embed distributions that are incompatible with the Bell structure into the Triangle structure, the latent nodes $S_{\p{A}}, S_{\p{B}}$ need to be observable and independent of the shared latent node $\la$.
 This can be accomplished by having $C$ ``measure'' the measurement settings $S_{\p{A}}, S_{\p{B}}$ and announce them as an outcome.
-Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell scenario is also incompatible with the triangle scenario provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$.
+Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$.
 Understandably there are numerous ways that this can be accomplished, albeit we will focus on elucidating an exemplary method.
 
-    The \term{Fritz distribution}, denoted $\prob[\fritz]$, is a quantum-accessible distribution known to be incompatible with the triangle scenario~\cite{Fritz_2012}.
+    The \term{Fritz distribution}, denoted $\prob[\fritz]$, is a quantum-accessible distribution known to be incompatible with the Triangle structure~\cite{Fritz_2012}.
 In the Fritz distribution, each of the variables $A,B,C$ have $4$ possible outcomes.
@@
 If one writes the outcome labels $\bc{0,1,2,3}$ in binary $\bc{00,01,10,11}$, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by the outcome of $\p C$.
-Pursuant to the embedding of~\cref{fig:triangle_scenario_with_fritz_bell_embedded} the left-hand bits emulate the measurement settings $S_{\p A}$ and $S_{\p B}$ and the right-hand bits emulate a two-outcome measurement performed by $A, B$ as they would in~\cref{fig:bell_scenario}.
+Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits emulate the measurement settings $S_{\p A}$ and $S_{\p B}$ and the right-hand bits emulate a two-outcome measurement performed by $A, B$ as they would in~\cref{fig:bell_scenario}.
 Specifically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.
@@
     \[ \ba{\p A_r \p B_r} = \prob[\p A_r \p B_r][00] + \prob[\p A_r \p B_r][11] - \prob[\p A_r \p B_r][01] - \prob[\p A_r \p B_r][10] \]
-    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell scenario defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the triangle scenario using the following mapping:
+    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the Triangle structure using the following mapping:
     \[ \p{A}, \p{B}, S_{\p{A}}, S_{\p{B}} \mapsto \p{A_r}, \p{B_r}, \p A_l, \p B_l \]
@@
     \[ 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} = 2\sqrt{2} \not \leq 2 \]
-    Therefore, the Fritz distribution is incompatible with the triangle scenario as promised.
-
-    The Fritz distribution $\prob[\fritz]$ is of special interest because it can be realized as a set of quantum states and measurements on the quantum causal model depicted in \cref{fig:triangle_scenario_quantum_model}.
-The shared resource between $A$ and $B$ (graphically denoted $\la$ in \cref{fig:triangle_scenario_with_fritz_bell_embedded}) is the maximally entangled Bell state:
+    Therefore, the Fritz distribution is incompatible with the Triangle structure as promised.
+
+    The Fritz distribution $\prob[\fritz]$ is of special interest because it can be realized as a set of quantum states and measurements on the quantum causal model depicted in \cref{fig:triangle_structure_quantum_model}.
+The shared resource between $A$ and $B$ (graphically denoted $\la$ in \cref{fig:triangle_structure_with_fritz_bell_embedded}) is the maximally entangled Bell state:
     \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \qquad \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \]
@@
     Additionally, it is important to understand the domain in which Fritz's proof of incompatibility is valid.
-Specifically, \cref{eq:CHSH} can only be applied to the triangle scenario where there exists perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$.
+Specifically, \cref{eq:CHSH} can only be applied to the Triangle structure where there exists perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$.
 The details of this restriction are discussed and proven in Fritz's original work~\cite{Fritz_2012}.
@@
     Upon reflection, the Fritz distribution can rightly be considered slightly manufactured.
-The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions under a triangle scenario embedding offers no additional perspective onto the types of resources made accessible by quantum mechanics.
-Therefore, it is desirable to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell scenario.
-\citet{Fritz_2012} presented the following problem: \textit{Find an example of non-classical quantum correlations in the triangle scenario together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.} The problem is understandably stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures.
+The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions under a Triangle structure embedding offers no additional perspective onto the types of resources made accessible by quantum mechanics.
+Therefore, it is desirable to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure.
+\citet{Fritz_2012} presented the following problem: \textit{Find an example of non-classical quantum correlations in the Triangle structure together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.} The problem is understandably stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures.
 In order to remove some of the ambiguity, consider the following refinements of the problem:
     \begin{enumerate}[label=\textbf{R.\arabic*}]
-        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the triangle scenario that are \textit{not} reliant on perfect correlations.
-        \item \label{r:2} Find incompatible quantum distributions on the triangle scenario that satisfy all Bell scenario inequalities under Fritz-type embeddings.
+        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
+        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
         \item \label{r:3} Find incompatible quantum distributions that require entanglement in more than one shared state.
@@
 As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
-As a example, inflations of the triangle scenario are depicted in \cref{fig:inflations}.
+As a example, inflations of the Triangle structure are depicted in \cref{fig:inflations}.
 Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}.
-For example node $A$ of \cref{fig:triangle_scenario} has copies $A_1, A_2, A_3, A_4$ in the \textit{Web inflation} of \cref{fig:the_web_inflation}.
+For example node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the \textit{Web inflation} of \cref{fig:the_web_inflation}.
 All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
@@
     \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
     \caption{The Cut inflation}\label{fig:cut_inflation}
@@
     \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral}}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
     \caption{The Spiral inflation}\label{fig:spiral_inflation}
@@
     \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_wagon_wheel}}
+    \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
     \caption{The Wagon-Wheel inflation}\label{fig:wagon_wheel_inflation}
@@
     \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure}}
     \caption{The Web Inflation}\label{fig:the_web_inflation}
     \end{subfigure}
-    \caption{Some inflations of the triangle scenario.}
+    \caption{Some inflations of the Triangle structure.}
     \label{fig:inflations}
@@
 For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable.
-This will become apparent in \cref{sec:found_inequalities} when the inflation technique is applied to the triangle scenario, producing marginal models that are very large.
-Moreover, algorithms to partially solve the marginal problem such as Hardy-type hypergraph transversals were used to determine hundreds of thousands of causal compatibility inequalities for the triangle scenario; none of which were able to be violated quantumly using numerical optimizations.
+This will become apparent in \cref{sec:found_inequalities} when the inflation technique is applied to the Triangle structure, producing marginal models that are very large.
+Moreover, algorithms to partially solve the marginal problem such as Hardy-type hypergraph transversals were used to determine hundreds of thousands of causal compatibility inequalities for the Triangle structure; none of which were able to be violated quantumly using numerical optimizations.
 Therefore, simpler approaches to the marginal problem needed to be considered.
@@
 
-    \subsection{Triangle Scenario Inequalities}
+    \subsection{Triangle Structure Inequalities}
     \label{sec:found_inequalities}
@@
     Equipped with the Fritz distribution (\cref{sec:fritz_distribution}) and the inflation technique (\cref{sec:inflation_technique}), it is now possible to derive causal compatibility inequalities for the triangle that are violated by the Fritz distribution; the procedure for doing so is as follows.
-First select an inflation $\graph'$ of the triangle scenario $\graph$ and identify the maximal pre-injectable sets $\PreInj[\graph]{\graph'}$.
+First select an inflation $\graph'$ of the Triangle structure $\graph$ and identify the maximal pre-injectable sets $\PreInj[\graph]{\graph'}$.
 These sets define the marginal scenario to be used in the Inflation Technique.
@@
     \begin{equation*}
-        \eq \label{eq:pre_injectable_triangle_scenario_wagon_wheel}
+        \eq \label{eq:pre_injectable_triangle_structure_wagon_wheel}
         \begin{gathered}
@@
 
-    These maximal pre-injectable sets define a marginal scenario where $\graph'$ is the Wagon-Wheel inflation of the triangle scenario $\graph$.
+    These maximal pre-injectable sets define a marginal scenario where $\graph'$ is the Wagon-Wheel inflation of the Triangle structure $\graph$.
     \[ \mscenario = \PreInj[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
@@
     \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
-    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_scenario_wagon_wheel},
+    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
     \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
@@
     \end{equation*}
-    By construction, every marginal model $\probvec^{\mscenario} = \bc{\prob[ABC], \prob[AB], \prob[BC], \prob[AC], \prob[A], \prob[B], \prob[C]}$ compatible with the triangle scenario must satisfy \cref{eq:ww_ineq}.
+    By construction, every marginal model $\probvec^{\mscenario} = \bc{\prob[ABC], \prob[AB], \prob[BC], \prob[AC], \prob[A], \prob[B], \prob[C]}$ compatible with the Triangle structure must satisfy \cref{eq:ww_ineq}.
 The Fritz distribution however violates \cref{eq:ww_ineq}.
@@
     There are a couple of important concepts to understand.
-First, the Fritz distribution is known to be incompatible with the Triangle scenario due to the perfect correlation between $C$ and the measurement pseudo-settings.
-The inequality contained in \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the triangle scenario.
+First, the Fritz distribution is known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings.
+The inequality contained in \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure.
 For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$.
 Moreover, although the existence of an inequality capable of witnessing Fritz distribution is guaranteed, there was no guarantee that the marginal model associated with the Wagon-Wheel inflation (\cref{eq:wagon_wheel_marginal_model}) would be capable of producing such an inequality.
-In fact, smaller inflations of the triangle scenario such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
+In fact, smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
 
     Larger inflations such as the Web inflation (\cref{fig:the_web_inflation}) were also used to generate causal compatibility inequalities that are violated by the Fritz distribution.
-The set of maximal pre-injectable sets for the Web inflation is considerably larger than \cref{eq:pre_injectable_triangle_scenario_wagon_wheel}.
+The set of maximal pre-injectable sets for the Web inflation is considerably larger than \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
     \begin{equation*}
-        \eq \label{eq:pre_injectable_triangle_scenario_web}
+        \eq \label{eq:pre_injectable_triangle_structure_web}
         \begin{gathered}
@@
 
-    Quite surprisingly, it is possible to derive causal compatibility inequalities for the triangle scenario that are symmetric under the exchange of parties.
+    Quite surprisingly, it is possible to derive causal compatibility inequalities for the Triangle structure that are symmetric under the exchange of parties.
 This is done by grouping marginal events $m \in \Events{\mscenario}$ into orbits under the action of party exchange.
@@
 
-    For the Triangle scenario, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
+    For the Triangle structure, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
 For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\PreInj[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
@@
     It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
-Moreover they stabilize the pre-injectable sets of \cref{eq:pre_injectable_triangle_scenario_web}.
+Moreover they stabilize the pre-injectable sets of \cref{eq:pre_injectable_triangle_structure_web}.
 Importantly,
@@
     \label{sec:violations_noise}
-    Causal compatibility inequalities for the triangle scenario (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality.
+    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality.
 In this section, we illuminate two tasks that can be performed in order to further understand the nature of quantum non-classical by using inequalities.
@@
     \end{figure}
-    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the triangle scenario by embedding Bell non-classicality.
+    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality.
 As was mentioned in \cref{sec:fritz_distribution}, this embedding required a very idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$.
@@
 
-    In the triangle scenario, we define a completely noisy observation as the uniform probability distribution $\s{U} = \s{U}_{ABC}$ (see \cref{fig:uniform_distribution})
+    In the Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U} = \s{U}_{ABC}$ (see \cref{fig:uniform_distribution})
     \[ \s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}  \]
-    Since the uniform distribution $\s{U}$ is trivially compatible with the triangle scenario, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible.
+    Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible.
 We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
@@
 
-    Overall, this noise model demonstrates that the Fritz distribution remains incompatible with the triangle scenario up to at least a noise parameter of $\vep \simeq 0.085$.
+    Overall, this noise model demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
 The associated distribution $\s N_{0.085}\br{\prob[\fritz]}$ is plotted in \cref{fig:noisy_fritz}.
@@
 Second, not all inequalities $I$ are \textit{good} measures of non-classicality.
-In the case of the Bell scenario, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality.
+In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality.
 This is because the facets form a necessary and sufficient set with all other inequalities following from positive mixtures of the facets.
-However, good measures of incompatibility are less understood in the triangle scenario where the space of classical correlations is non-convex.
+However, good measures of incompatibility are less understood in the Triangle structure where the space of classical correlations is non-convex.
 At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility (especially because they are curated toward the Fritz distribution).
-Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the triangle scenario.
-
-    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the triangle scenario in \cref{fig:triangle_scenario_quantum_model}.
+Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure.
+
+    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}.
 Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:quantum_model_triangle} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$.
@@
     \begin{center}
-            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
-            \caption{The triangle scenario as modeled by quantum states and measurements.}
-            \label{fig:triangle_scenario_quantum_model}
+            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
+            \caption{The Triangle structure as modeled by quantum states and measurements.}
+            \label{fig:triangle_structure_quantum_model}
     \end{center}
     \end{figure}
-    In search of new, incompatible, quantum distributions that can be realized on the triangle scenario, numerical optimizations over the the space of quantum-accessible probability distributions are performed.
+    In search of new, incompatible, quantum distributions that can be realized on the Triangle structure, numerical optimizations over the the space of quantum-accessible probability distributions are performed.
 To do so, we are interested in a parameterization all distributions that can be expressed as follows:
@@
 Additionally, restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
-First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the triangle scenario.
+First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure.
 Second, generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, however a valid, unbiased parameterization was not found for $k > 2$.
@@
         \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
-        \caption{The permutation matrix $\netperm$ acting on $\br{\Hilb^2}^{\otimes 6}$ for the triangle scenario. Black entries represents a value of $1$ and white represents $0$.}
+        \caption{The permutation matrix $\netperm$ acting on $\br{\Hilb^2}^{\otimes 6}$ for the Triangle structure. Black entries represents a value of $1$ and white represents $0$.}
         \label{fig:perm_mtrx}
     \end{figure}
-    Finally, we introduce the a permutation matrix $\netperm$ for the triangle scenario.
+    Finally, we introduce the a permutation matrix $\netperm$ for the Triangle structure.
 For bipartite qubit states, $\netperm$ is the $64\times64$ bit-wise matrix depicted in \cref{fig:perm_mtrx}.
@@
 
-    \Cref{sec:param_quantum_dist} expounded on how we elected to parameterized the space of quantum distributions that can be realized on the quantum triangle scenario (\cref{fig:triangle_scenario_quantum_model}).
+    \Cref{sec:param_quantum_dist} expounded on how we elected to parameterized the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}).
 Specifically, we make use of fully generic $4\times 4$ density matrices (bipartite qubit) for each shared resource and $4$-element projective measurements.
@@
 In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure} or set of possible events.
-What does this reveal about $I_1$ and non-classicality in the triangle scenario?
+What does this reveal about $I_1$ and non-classicality in the Triangle structure?
 This result is not entirely unexpected.
-As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to show incompatibility of the triangle scenario.
+As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to show incompatibility of the Triangle structure.
 Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for a specific forms of non-classicality that resemble the Fritz distribution very closely.
@@
 This distribution is also non-classical with relative violation $V_F = 3$.
-As it turns out, the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}\footnote{At least numerical optimizations suggest this is the case.} Therefore we conclude that the space of quantum accessible correlations on the triangle scenario is non-convex; a reiteration of a result found in~\citet{Inflation}.
+As it turns out, the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}\footnote{At least numerical optimizations suggest this is the case.} Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result found in~\citet{Inflation}.
     \begin{figure}
@@
 
-    In \cref{sec:triangle_scenario}, we elucidated that non-classicality in the triangle scenario has been an unsolved problem for nearly a decade.
-Initially,~\citet{Branciard_2012} identified the triangle scenario as a challenging causal structure for studying non-classicality.
-Afterwards,~\citet{Henson_2014} were able to to classify the triangle scenario as \textit{interesting} which partially explains why it remains an enigma.
-Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the triangle scenario.
+    In \cref{sec:triangle_structure}, we elucidated that non-classicality in the Triangle structure has been an unsolved problem for nearly a decade.
+Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality.
+Afterwards,~\citet{Henson_2014} were able to to classify the Triangle structure as \textit{interesting} which partially explains why it remains an enigma.
+Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the Triangle structure.
 Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality.
@@
 For this research project, we made heavy use of the Inflation Technique of \cref{sec:inflation_technique} and the Fritz distribution in order to derive the first causal compatibility inequalities capable of having quantum violations.
-Finally, we used those inequalities in an attempt to discover new forms of non-classicality in the triangle scenario with partial success.
+Finally, we used those inequalities in an attempt to discover new forms of non-classicality in the Triangle structure with partial success.
 
@@
 First and foremost, the derivation of \cref{eq:ww_ineq} demonstrates the utility of the Inflation technique specifically for quantum causal inference problems.
-The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the triangle scenario -- a task that no other existing techniques succeeded at.
+The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure -- a task that no other existing techniques succeeded at.
 Therefore, this work acts as a strong indication that the Inflation technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
@@
     \clearpage
-    \section{Large Triangle Scenario Inequalities}
+    \section{Large Triangle Structure Inequalities}
     \subsection{Web Inflation Inequality}
     \label{sec:web_inequality}
-    The following is a causal compatibility inequality for the triangle scenario that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
+    The following is a causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
     \begin{center}
@@
     \label{sec:symmetic_web_inequality}
-    The following is a symmetric causal compatibility inequality for the triangle scenario that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
+    The following is a symmetric causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
     \begin{center}

### 2017-03-08 documents/TriangleScenarioArXiv/ts.tex
changed inequalities in the appendixes to reflect their true form
fixed whitespace around a particular figure

@@
 
-    \begin{center}
     \begin{figure}
     \begin{subfigure}[b]{.48\linewidth}
-    \includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}
+    {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}}
     \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
@@
     \begin{subfigure}[b]{.48\linewidth}
-    \includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}
+    {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}}
     \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
@@
     \end{figure}
-    \end{center}
 
@@
 142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.
-238]{Nocedal_2000} were used along with a hybrid method called Basin Hopping~\cite{Wales_1997}.
+238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
 
@@
     \begin{center}
-        % TODO [TC] replace this inequality with correct one
+        \vspace{-0.2in}
         \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
@@
     \begin{center}
-        % TODO [TC] replace this inequality with correct one
+        \vspace{-0.2in}
         \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}

### 2017-03-08 documents/TriangleScenarioArXiv/ts.tex
refined the Fritz refinements

@@
-\PassOptionsToPackage{justification=justified}{caption}
 % === Revtex Declaration ===
@@
 \Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions.
-A sample of these inequalities are presented at the end of \cref{sec:deriving_inequalities} as well as in \cref{sec:web_inequality,sec:symmetic_web_inequality}.
+A sample of these inequalities are presented at the end of \cref{sec:found_inequalities} (specifically \cref{eq:ww_ineq}) as well as in \cref{sec:web_inequality,sec:symmetic_web_inequality}.
 Finally, \cref{sec:violations_noise} introduces the method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality.
@@
     \section{Causal Compatibility}
+    \todo[TC]{Talk to Elie about the varying notions of compatibility}
     \label{sec:causal_compatibility}
@@
 From a resource standpoint, if the non-classicality of $\prob^{\mscenario}$ can be witnessed by an inequality $I$, but $\prob^{\mscenario}$ can be implemented using quantum states and measurements, then the causal compatibility inequality $I$ represents a concrete task where quantum resources out-perform classical resources.
+
+    \section{Bell Structure}
+    \label{sec:bell_structure}
+    \todo[TC]{Review of Bell structure, Tsirelson-box, CHSH inequality}
 
@@
     Upon reflection, the Fritz distribution can rightly be considered slightly manufactured.
-The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions under a Triangle structure embedding offers no additional perspective onto the types of resources made accessible by quantum mechanics.
+The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of entanglement resources made accessible by quantum mechanics.
 Therefore, it is desirable to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure.
-\citet{Fritz_2012} presented the following problem: \textit{Find an example of non-classical quantum correlations in the Triangle structure together with a proof of its non-classicality which does not hinge on Bell’s Theorem.}\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.} The problem is understandably stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures.
-In order to remove some of the ambiguity, consider the following refinements of the problem:
+Pursuant to this, \citet{Fritz_2012} presented the following problem~\cite[Problem 2.17]{Fritz_2012}:%TODO figure out best way to link to this problem
+
+    \term{Fritz's Problem}: Find an example of non-classical quantum correlations in the Triangle structure together with a proof of its non-classicality which does not hinge on Bell’s theorem.\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.}
+
+    Understandably, Fritz's Problem is stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures.
+The remainder of this paper focuses on our advancement toward solving Fritz's Problem.
+\Cref{sec:conclusions} proposes three refinements of Fritz's Problem which are to be labeled \ref{r:1},\ref{r:2} and \ref{r:3} respectively.
+Specifically, \ref{r:1} embodies the degree in which the results of \cref{sec:found_inequalities} solve Fritz's problem while \ref{r:2} and \ref{r:3} characterize interpretations of Fritz's Problem that remain partially solved.
+
+    \section{Triangle Structure Inequalities}
+    \label{sec:found_inequalities}
+
+    Equipped with the Fritz distribution (\cref{sec:fritz_distribution}) and the inflation technique (\cref{sec:inflation_technique}), it is now possible to derive causal compatibility inequalities for the triangle that are violated by the Fritz distribution; the procedure for doing so is as follows.
+First select an inflation $\graph'$ of the Triangle structure $\graph$ and identify the maximal pre-injectable sets $\PreInj[\graph]{\graph'}$.
+These sets define the marginal scenario to be used in the Inflation Technique.
+Next, inflate the Fritz distribution into the pre-injectable sets as described by the Inflation lemma (\cref{lem:inflation}).
+Finally, obtain infeasibility certificates using some linear programing software and obtain a valid causal compatibility inequality that witnesses the Fritz distribution's incompatibility.
+
+    As a first demonstration, we make use of the Wagon-Wheel inflation (\cref{fig:wagon_wheel_inflation}) to find these inequalities.
+The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
+By inspection\footnote{Computing the injectable and pre-injectable sets computationally is possible and a technique is discussed in~\citet{Inflation}.}, the maximal pre-injectable sets of the Wagon-Wheel inflation are as follows:
+    \begin{equation*}
+        \eq \label{eq:pre_injectable_triangle_structure_wagon_wheel}
+        \begin{gathered}
+            \textbf{Maximal Pre-injectable Sets} \\
+            \bc{A_2, B_1, C_3, C_1} \\
+            \bc{A_1, B_1, C_4, C_2} \\
+            \bc{A_1, B_2, C_1, C_3} \\
+            \bc{A_2, B_2, C_2, C_4} \\
+        \end{gathered}
+        \qquad
+        \begin{gathered}
+            \textbf{Ancestral Independences} \\
+            \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
+            \bc{A_1, B_1, C_4} \ancestralindep \bc{C_2} \\
+            \bc{A_1, B_2, C_1} \ancestralindep \bc{C_3} \\
+            \bc{A_2, B_2, C_2} \ancestralindep \bc{C_4} \\
+        \end{gathered}
+    \end{equation*}
+
+    These maximal pre-injectable sets define a marginal scenario where $\graph'$ is the Wagon-Wheel inflation of the Triangle structure $\graph$.
+    \[ \mscenario = \PreInj[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
+    The complete set of variables $\jointvar$ is simply the set of observable nodes in the Wagon-Wheel inflation,
+    \[ \jointvar = \nodes'_O = \bc{A_1, A_2, B_1, B_2, C_1, C_2, C_3, C_4} \]
+    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
+This marginal scenario $\mscenario$ then defines an incidence matrix capable of accommodating the Fritz distribution.
+    Analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \abs{\Events{V}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{\Events{v}} = 4^{\abs{\jointvar}} = 4^8 = 65,536$ columns.
+Understandably, this matrix is not reproduced here.
+The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
+
+    The marginal distribution vector $\probvec^{\mscenario}$ is indexed by $1024$ marginal outcomes $m \in \Events{\mscenario}$ of the following \textit{symbolic} form,
+    \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
+    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
+    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
+    And finally, each probability distribution in \cref{eq:marginal_vector_wagon_wheel_factors} is deflated by dropping copy-indices.
+    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[ABC]\br{000}\prob[C]\br{0}, \ldots, \prob[ABC]\br{323}\prob[C]\br{2}, \ldots, \prob[ABC]\br{333}\prob[C]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors_dropped}\]
+    This step is permitted because all of the remaining distributions in \cref{eq:marginal_vector_wagon_wheel_factors} are defined over the injectable sets of the Wagon-Wheel inflation.
+Numerically however, each of the elements of $\probvec^{\mscenario}$ are replaced with numerical values corresponding to the Fritz distribution upon deflation.
+Pursuant to \cref{eq:fritz_dist}, $\prob[ABC]\br{323}\prob[C]\br{2}$, for example, is assigned the following numerical value.
+    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267  \]
+    The same is applied to all other entries of $\probvec^{\mscenario}$.
+Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained.
+Below is an example of an infeasibility inequality obtained over the entries of \cref{eq:marginal_vector_wagon_wheel_factors_dropped}.
+    \begin{equation*}
+    \begin{gathered}
+    \eq\label{eq:ww_ineq}
+    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \\
+    P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \\
+    P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \\
+    P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \\
+    P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \\
+    P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \\
+    P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \\
+    P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \\
+    P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \\
+    P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \\
+    P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) - P_{ABC}(000)P_{C}(3) \geq 0
+    \end{gathered}
+    \end{equation*}
+    By construction, every marginal model $\probvec^{\mscenario} = \bc{\prob[ABC], \prob[AB], \prob[BC], \prob[AC], \prob[A], \prob[B], \prob[C]}$ compatible with the Triangle structure must satisfy \cref{eq:ww_ineq}.
+The Fritz distribution however violates \cref{eq:ww_ineq}.
+
+    Notice the final term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $-1$.
+For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$.
+
+    It is possible to simplify this inequality by marginalizing over sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) = P_{ABC}(300)$.
+Upon doing so, one obtains the following,
+    \begin{gather*}
+        P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \leq \\ P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + \\
+        + P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + P_{AB}(20) + P_{AB}(30) + P_{C}(3)P_{C}(0)
+    \end{gather*}
+
+    There are a couple of important concepts to understand.
+First, the Fritz distribution is known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings.
+The inequality contained in \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure.
+For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$.
+Moreover, although the existence of an inequality capable of witnessing Fritz distribution is guaranteed, there was no guarantee that the marginal model associated with the Wagon-Wheel inflation (\cref{eq:wagon_wheel_marginal_model}) would be capable of producing such an inequality.
+In fact, smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
+
+    Larger inflations such as the Web inflation (\cref{fig:the_web_inflation}) were also used to generate causal compatibility inequalities that are violated by the Fritz distribution.
+The set of maximal pre-injectable sets for the Web inflation is considerably larger than \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
+    \begin{equation*}
+        \eq \label{eq:pre_injectable_triangle_structure_web}
+        \begin{gathered}
+            \textbf{Maximal Pre-injectable Sets} \\
+            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
+            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
+            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
+            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
+            \bc{A_1, B_3, C_4} \\
+            \bc{A_1, B_4, C_2} \\
+            \bc{A_2, B_1, C_4} \\
+            \bc{A_2, B_2, C_2} \\
+            \bc{A_3, B_3, C_3} \\
+            \bc{A_3, B_4, C_1} \\
+            \bc{A_4, B_1, C_3} \\
+            \bc{A_4, B_2, C_1}
+        \end{gathered}
+        \qquad
+        \begin{gathered}
+            \textbf{Ancestral Independences} \\
+            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
+            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
+            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
+            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
+            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
+            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
+            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
+            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
+            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
+            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
+            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
+            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
+        \end{gathered}
+    \end{equation*}
+    Again, analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ and $201,326,592$ non-zero entires.
+Using this incidence matrix, a number of incompatibility certificates were derived.
+For inspection, one is reproduced in \cref{sec:web_inequality}.
+
+    In summary, these causal compatibility inequalities represent a completion of objective \cref{r:1} from \cref{sec:fritz_distribution}.
+These inequalities are derived without making use of Bell's theorem and instead use the Inflation Technique which is completely independent of Bell's theorems.
+Additionally, the derivation of causal compatibility inequalities allows one prove incompatibility even when perfect correlations are absent.
+Moreover, they allow one to probe the amount of noise the Fritz distribution can sustain before becoming compatible (see \cref{sec:violations_noise}).
+Unfortunately, infeasibility certificates are found by linear programing software to certify the infeasibility of a \textit{particular distribution}.
+This means that inequalities like \cref{eq:ww_ineq}, the one presented in \cref{sec:web_inequality}, and others are specifically manufactured in order witness a particular type of quantum non-classicality.
+In an effort to derive inequalities that could lead to potentially new forms of non-classicality, we searched for inequalities that did not admit biased towards the Fritz distribution.
+
+    \section{Symmetric Inequalities}
+    \label{sec:symmetric_inequalities}
+
+    Quite surprisingly, it is possible to derive causal compatibility inequalities for the Triangle structure that are symmetric under the exchange of parties.
+This is done by grouping marginal events $m \in \Events{\mscenario}$ into orbits under the action of party exchange.
+Even more interestingly, these inequalities are violated by the Fritz distribution.
+This comes as a surprise because the Fritz distribution is \text{not} invariant under the exchange of parties; in fact the Fritz distribution is noticeably biased toward $C$.
+
+    In general, exploiting symmetries of the marginal scenario is useful for a few distinct reasons.
+First, \citet{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:deriving_inequalities}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
+They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that non-trivial inequalities can be recovered from facets of a symmetric polytope.
+Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
+The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.
+
+    To demonstrate what types of symmetries we have in mind, we present the following example:
+    \begin{example}
+        \label[example]{ex:symmetries}
+        First consider the marginal scenario $\mscenario = \bc{\bc{A, B, C}, \bc{C, D}, \bc{A, D}}$ where each variable in $\jointvar = \bc{A,B,C,D}$ has binary outcomes: $O_A = O_B = O_C = O_D = \bc{0,1}$.
+Moreover, let $I_{\mscenario}$ be the following compatibility inequality over $\mscenario$ for some causal structure $\graph$,
+        \[ I_{\mscenario} = \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}  \]
+        Intuitively, the compatibility of $\probvec^{\mscenario}$ is \textit{independent} of the how one labels outcomes.
+Suppose $\varphi : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ is a permutation of the variables $\jointvar$.
+Intuitively $\varphi$ acts on $I_{\mscenario}$ in the following way,
+        \begin{align*}
+        \varphi\bs{I_{\mscenario}} &= \bc{\prob[\varphi\bs{abc}][010] \leq \prob[\varphi\bs{cd}][00] + \prob[\varphi\bs{ad}][01]} \\
+        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
+        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
+        \end{align*}
+        In general (as in this example), permutations over all variables can modify the marginal scenario $\varphi\bs{\mscenario} \neq \mscenario$; in general we write $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
+Although $\varphi\bs{I_{\mscenario}}$ is still a valid causal compatibility inequality, in constrains marginal models of a different marginal scenario $\varphi\bs{\mscenario}$ and are in general of no interest.
+    \end{example}
+
+    Following the observations of \cref{ex:symmetries}, it is always possible to permute the random variables in a marginal scenario to produce new and valid inequalities.
+The symmetry group over a the complete set of variables $\jointvar$ is simply the \text{permutation group}\footnote{The permutation group over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} $\Perm{\jointvar}$.
+As was noted in \cref{ex:symmetries}, some permutations $\varphi \in \Perm{\jointvar}$ have the undesired possibility of transforming $\mscenario$ into a different marginal scenario.
+    \[ \varphi\bs{\mscenario} \defined \bc{\varphi\bs{V_1}, \ldots, \varphi\bs{V_k}} \neq \mscenario \]
+    This means that there could exist $V \in \mscenario$ such that $\varphi\bs{V} \not \in \mscenario$.
+Permutations $\varphi$ retaining this property are unable to generate compatibility inequalities over the same marginal scenario.
+Therefore, the desired set of symmetries is a subgroup that takes $\mscenario$ to $\mscenario$.
+
+    \begin{definition}
+        The \term{variable permutation group} $\gp$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario.
+        \[ \Phi\br{\mscenario} \defined \bc{\varphi \in \Perm{\jointvar} \mid \forall V \in \mscenario : \varphi\bs{V} \in \mscenario} \]
+    \end{definition}
+
+    Obtaining the variable permutation group $\gp\br{\mscenario}$ is a simple application of a group stabilizer algorithm.
+After obtaining $\gp\br{\mscenario}$, one can take known compatibility inequalities $I_{\mscenario}$ can create a whole family of inequalities $\bc{\varphi\bs{I_{\mscenario}} \mid \varphi \in \gp\br{\mscenario}}$ that are valid for the same marginal scenario $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}} = \varphi\bs{I}_{\mscenario}$.
+
+    Although very useful for reducing computational complexity~\cite{Bancal_2010}, we divert our attention to finding \textit{symmetric} inequalities themselves.
+    \[ \forall \varphi \in \gp\br{\mscenario} :  \varphi\bs{I_{\mscenario}} = I_{\mscenario} \]
+    In order to do this, we must first define how elements $\varphi \in \gp$ act on marginal events.
+The action of $\varphi \in \gp$ on any outcome $f \in \Events{V}$ (denoted $\geo\bs{f}$) is defined as,
+    \[ \forall v \in \Dom{\varphi\bs{f}} : \br{\varphi\bs{f}}\br{v} \defined f\br{\varphi^{-1}\bs{v}} \eq \label{eq:act_on_variable}\]
+    \Cref{eq:act_on_variable} is nothing more than a mathematical definition for the intuitive action used in \cref{ex:symmetries}.
+    Through repeated action of $\varphi \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define \term{group orbits} of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$.
+    \begin{align*}
+        \Orb[\gp]{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \gp} \\
+        \Orb[\gp]{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \gp}
+    \end{align*}
+    Using these group orbits, it is possible to contract the incidence matrix $M$ of a marginal scenario into a symmetrized version.
+
+    \begin{definition}
+        The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and the variable permutation group $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
+Each row of $M_{\gp}$ corresponds to a marginal orbit $\Orb[\gp]{m}$.
+Analogously each column of $M_{\gp}$ corresponds to a joint orbit $\Orb[\gp]{j}$.
+The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
+        \[ \br{M_{\gp}}_{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M_{m',j'} \]
+    \end{definition}
+    It is possible to analogously define a \term{symmetric joint distribution vector} $\probvec^{\jointvar}_{\Phi}$ indexed by $\Orb[\gp]{j}$,
+    \[ \br{\probvec^{\jointvar}_{\Phi}}_{\Orb[\gp]{j}} = \sum_{j' \in \Orb[\gp]{j}} \probvec^{\jointvar}_{j} \]
+    And a \term{symmetric marginal distribution vector} $\probvec^{\mscenario}_{\Phi}$ indexed by $\Orb[\gp]{m}$,
+    \[ \br{\probvec^{\mscenario}_{\Phi}}_{\Orb[\gp]{m}} = \sum_{m' \in \Orb[\gp]{m}} \probvec^{\mscenario}_{m} \]
+    Which altogether define a new, \term{symmetric marginal problem},
+    \[ \probvec^{\mscenario}_{\Phi} = M_{\gp} \cdot \probvec^{\jointvar}_{\Phi} \]
+    The symmetric marginal problem can be solved using the same computational methods discussed in \cref{sec:deriving_inequalities} and will produce symmetric inequalities.
+
+    In the context of the Inflation technique, a variable symmetry $\Phi\br{\mscenario'}$ over an inflated marginal scenario $\mscenario'$ does not always correspond to a variable symmetry under deflation $\Phi\br{\mscenario}$.
+In order to derive deflated inequalities that are symmetric under an exchange of parties, it is required that $\Phi\br{\mscenario'} \sim \Phi\br{\mscenario}$ are equivalent up to copy-index.
+
+    For the Triangle structure in particular, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
+For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\PreInj[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
+    \begin{equation*}
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_1 \\
+    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_2 \\
+    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_3 \\
+    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_4 \\
+    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
+    \end{aligned}
+    \end{equation*}
+    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
+    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
+    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
+    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
+    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
+Moreover they stabilize the pre-injectable sets of \cref{eq:pre_injectable_triangle_structure_web}.
+Importantly,
+    \[ \gp\br{\PreInj[\graph]{\graph'}} \sim \Perm{A,B,C} \]
+    To see this, $\varphi_1$ and $\varphi_4$ become the identity element $\ident$ in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
+
+    The symmetric incidence matrix $M_{\Phi}$ for the Web inflation is considerably smaller than $M$.
+The number of rows of $M_{\Phi}$ is a number of distinct orbits $\Orb[\Phi]{m}$ in $\Events{\mscenario}$.
+Likewise the number of columns is the number of distinct orbits $\Orb[\Phi]{j}$ in $\Events{\jointvar}$.
+For the Web inflation in particular, $M_{\Phi}$ is $450 \times 358,120$.
+Using the symmetric incidence matrix and linear programing methods, an infeasibility certificate was found that is capable of witnessing the Fritz distribution.
+This inequality is reproduced in \cref{sec:symmetic_web_inequality}.
+
+    \section{Violations \& Noise}
+    \label{sec:violations_noise}
+    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality.
+In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities.
+
+    \subsection{Noise}
+    \label{sec:noise}
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
+            \vspace{-0.2in}
+            \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
+            \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
+            \label{fig:uniform_distribution}
+    \end{center}
+    \end{figure}
+    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality.
+As was mentioned in \cref{sec:fritz_distribution}, this embedding required a very idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$.
+From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}.
+It is possible to minimize noise by developing more accurate measurement channels but perfect correlations are too idealistic.
+Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.
+
+    In the Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U} = \s{U}_{ABC}$ (see \cref{fig:uniform_distribution})
+    \[ \s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}  \]
+    Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible.
+We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
+    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
+    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution as $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$.
+For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.
+As a standard, let $I\br{\prob} < 0$ represent violations while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturations of the inequality).
+
+    To analyze noise, $4$ inequalities where chosen.
+First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}.
+The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{sec:web_inequality} while $I_3$ is the symmetric inequality in \cref{sec:symmetic_web_inequality}.
+Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{sec:web_inequality}.
+
+    \begin{figure}
+    \begin{subfigure}[b]{.48\linewidth}
+    {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}}
+    \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
+    \end{subfigure}
+    \begin{subfigure}[b]{.48\linewidth}
+    {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}}
+    \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
+    \end{subfigure}
+    \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
+    \end{figure}
+
+    The results of our experiments are plotted in \cref{fig:master_noise}.
+\Cref{fig:noise} illustrates that each curve $I\br{\s{N}_{\vep}\br{\prob[\fritz]}}$ as a function of $\vep$ is monotonically increasing as expected; the more noise added to the probability distribution, the more classical it becomes.
+\Cref{fig:noise_zoomed} is the same plot as \cref{fig:noise} zoomed onto the interval $\vep \in \bs{0, 0.12}$.
+These tests suggest that inequality $I_1$ (\cref{sec:web_inequality}), when compared against all others is most robust to noise.
+
+    Overall, this noise model demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
+The associated distribution $\s N_{0.085}\br{\prob[\fritz]}$ is plotted in \cref{fig:noisy_fritz}.
+There remains the possibility that another inequality will be able to withstand a larger degree of noise that $I_1$.
+Given that $I_0, I_1, I_2, I_3$ are far from a representative inequalities and are likely not facets of any inflated marginal polytope, it is save to say that this is possible.
+
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
+            \vspace{-0.2in}
+            \[ \probplotvalue{255, 255, 243} = 0.00133 \]
+            \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
+            \label{fig:noisy_fritz}
+    \end{center}
+    \end{figure}
+
+    \subsection{Numerical Optimizations}
+    \label{sec:optimizations}
+    Causal compatibility inequalities act as a \textit{measure} of non-classicality.
+If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$\footnote{Remember that larger violations are more negative when the inequalities are written in the proposed canonical form.} Nonetheless, this statement comes from several caveats.
+First, it is possible (and frequently the case) for ${I\br{\prob[1]}} < I\br{\prob[2]}$ to hold for one inequality $I$ but have ${\ti I\br{\prob[2]}} < \ti I\br{\prob[1]}$ hold for another inequality $\ti I$.
+In this case, all one can claim is that $\prob[1]$ is more incompatible than $\prob[2]$ with respective to $I$ but the contrary is true with respect to $\ti I$.
+Second, not all inequalities $I$ are \textit{good} measures of non-classicality.
+In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality.
+This is because the facets form a necessary and sufficient set with all other inequalities following from positive mixtures of the facets.
+However, good measures of incompatibility are less understood in the Triangle structure where the space of classical correlations is non-convex.
+At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility (especially because they are curated toward the Fritz distribution).
+Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure.
+
+    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}.
+Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:quantum_model_triangle} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$.
+The objective value is simply the degree of violation $f = I\br{\prob[ABC]}$ and used to make adjustments to $\la$ in order to achieve largest and larger violations.
+
+    Finding larger violations to compatibility inequalities is nothing more that a numerical optimization (specifically minimization) of $f\br{\la}$.
+Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
+Specifically, the BFGS method~\cite[p.
+142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.
+238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
+
+    \subsection{Parameterizing Quantum Distributions}
+    \label{sec:param_quantum_dist}
+    \begin{figure}
+    \begin{center}
+            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
+            \caption{The Triangle structure as modeled by quantum states and measurements.}
+            \label{fig:triangle_structure_quantum_model}
+    \end{center}
+    \end{figure}
+    In search of new, incompatible, quantum distributions that can be realized on the Triangle structure, numerical optimizations over the the space of quantum-accessible probability distributions are performed.
+To do so, we are interested in a parameterization all distributions that can be expressed as follows:
+    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
+    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately\footnote{$\netperm$ is discussed more thoroughly in \cref{sec:perm_matrix}.}.
+
+    In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
+The states $\rho$ are taken to be bipartite \textit{qubit} states acting on $\s{H}^{2} \otimes \s{H}^{2}$.
+This is motivated by \cref{sec:fritz_distribution} in which the Fritz distribution only requires qubit states.
+In generality, one could consider $n$-dimensional states acting on $\s{H}^{n} \otimes \s{H}^{n}$.
+However, in such cases the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ then acts on $\br{\Hilb^{n}}^{\otimes 6}$ requiring a $n^6 \times n^6$ matrix with $n^{12}$ entries.
+Therefore, $n = 2$ is far more computationally feasible than $n > 2$.
+Additionally, restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
+First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure.
+Second, generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, however a valid, unbiased parameterization was not found for $k > 2$.
+Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as follows:
+    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]
+
+    In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
+Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, a single technique is presented that was found to be most computationally suitable for our purposes.
+    \subsection{Numerical Optimization Results}
+    \label{sec:results}
+
+    \Cref{sec:param_quantum_dist} expounded on how we elected to parameterized the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}).
+Specifically, we make use of fully generic $4\times 4$ density matrices (bipartite qubit) for each shared resource and $4$-element projective measurements.
+For each inequality $I$, we define the relative violation $V_F$ to be maximum violation relative to the violation achieved by the Fritz distribution.
+    \[ V_F = \f{\min_{P}\bc{I\br{P}}}{I\br{P_F}} \]
+
+    The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{sec:web_inequality}.
+At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
+Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution.
+In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure} or set of possible events.
+What does this reveal about $I_1$ and non-classicality in the Triangle structure?
+This result is not entirely unexpected.
+As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to show incompatibility of the Triangle structure.
+Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for a specific forms of non-classicality that resemble the Fritz distribution very closely.
+
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
+            \caption{Probability distribution that maximizes violation of $I_1$ from \cref{sec:web_inequality} ($V_F \simeq 1.501$).}
+            \label{fig:maximum_violation_I_1}
+    \end{center}
+    \end{figure}
+
+    An alternative explanation has to do with the sensitively of the initial condition $\la_{\br{0}} = \br{\la_{\br{0}, 0}, \ldots, \la_{\br{0}, n}}$ in our optimization.
+In \cref{sec:param_quantum_dist}, it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
+Somewhat surprisingly, when using a uniform seed for $\la_0$, all optimization methods consistently converged to inequality saturation instead of inequality violation which of course is achievable by the Fritz distribution.
+Instead, only initial seeds close enough to the \textit{Fritz parameters} $\la_{\br{\fritz}}$ (the parameters that induce the Fritz distribution using the quantum implementation in \cref{sec:fritz_distribution}) where able to achieve violation.
+To illustrate this graphically, we let the initial seed be a small Gaussian perturbation $\de \la$ away from $\la_{\br{\fritz}}$ in parameter space.
+    \[ \la_{\br{0}} = \la_{\br{\fritz}} + \de \la  \]
+    The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation.
+For $I_1$, deviations of $\chi \gtrsim 1.3$ inhibited convergence to violation.
+This is depicted in \cref{fig:initial_conditions}.
+Therefore, it is unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
+Most likely, this phenomena is due to a combination of both effects.
+
+    \begin{figure}
+    \begin{subfigure}[t]{.48\linewidth}
+    {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
+    \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
+    \end{subfigure}
+    \begin{subfigure}[t]{.48\linewidth}
+    {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
+    \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
+    \end{subfigure}
+    \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
+    \end{figure}
+
+    The second inequality in consideration is $I_3$; the \textit{symmetric} Web inflation inequality presented in \cref{sec:symmetic_web_inequality}.
+This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
+Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution.
+However, this result is far more surprising.
+Since the inequality is symmetric with respect to the exchange of parties $\varphi \in \Perm{A, B, C}$, one would naively expect that the maximum violating distribution is be symmetric as well.
+If it were not, one could construct a distribution that violates $I_3$ more by symmetrizing $\prob[\fritz]$ by summing over all possible permutations and normalizing.
+The symmetrized Fritz distribution is plotted in \cref{fig:symmetrized_fritz}.
+This distribution is also non-classical with relative violation $V_F = 3$.
+As it turns out, the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}\footnote{At least numerical optimizations suggest this is the case.} Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result found in~\citet{Inflation}.
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
+            \caption{Probability distribution that maximizes violation of $I_3$ from \cref{sec:symmetic_web_inequality} ($V_F \simeq 2.61$).}
+            \label{fig:maximum_violation_I_3}
+    \end{center}
+    \end{figure}
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
+            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
+            \label{fig:symmetrized_fritz}
+    \end{center}
+    \end{figure}
+
+    Finally for both $I_0$ and $I_2$, the maximum relative violation happens to be $V_F = 1$ (up to numerical precision).
+This means that the Fritz distribution either represents a local minimum of the parameter space or is in fact \textit{the} maximally violating distribution.
+Without further investigations, it is unclear if this behavior is related to the universality of the Fritz distribution or if its an artifact of the methods used to derive $I_0$ and $I_2$.
+
+    \section{Conclusions}
+    \label{sec:conclusions}
+    In \cref{sec:triangle_structure}, we elucidated that compatibility in the Triangle structure has been an unsolved problem for nearly a decade.
+Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality.
+Afterwards,~\citet{Henson_2014} were able to to classify the Triangle structure as \textit{interesting} which partially explains why it remains an enigma.
+Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the Triangle structure.
+Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality.
+In \cref{sec:fritz_distribution} the Fritz distribution was described in detail along with Fritz's Problem~\cite[Problem 2.17]{Fritz_2012}.
+
+    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum accessible distributions.
+This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) when applied to the Fritz distribution.
+In the context of Fritz's Problem, our result corresponds to a resolution to the following refinement of Fritz's original Problem.
     \begin{enumerate}[label=\textbf{R.\arabic*}]
+        \setcounter{enumi}{0}
         \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
-        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
-        \item \label{r:3} Find incompatible quantum distributions that require entanglement in more than one shared state.
     \end{enumerate}
-    The remainder of this document focuses on a positive solution to \ref{r:1} but leaves \ref{r:2} and \ref{r:3} partially unanswered.
-
-    \section{Inflation Technique}
+
+    Ultimately, this work accomplishes two important tasks.
+First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation technique specifically for quantum causal inference problems.
+The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure -- a task that no other existing techniques have succeeded at.
+In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure.
+Consequently, this work strongly indicates that the Inflation technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
+Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations.
+In conclusion \ref{r:1} has been positively solved through the derivation of inequalities such as \cref{eq:ww_ineq} and those found in \cref{sec:web_inequalities}.
+
+    In consideration of out resolution to \ref{r:1}, we additionally propose two more refinements to Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
+    \begin{enumerate}[label=\textbf{R.\arabic*}]
+        \setcounter{enumi}{1}
+        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
+        \item \label{r:3} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
+    \end{enumerate}
+
+    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}.
+When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state.
+In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states.
+As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.}.
+The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
+Finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure.
+Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}).
+Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations.
+Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure.
+Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility.
+In summary, it remains unclear whether or not \ref{r:1} or \ref{r:2} is a harder problem or if either is even feasible.
+
+    \section*{Acknowledgments}
+    T.C.
+Fraser would like to thank E.
+Wolfe for his excellent guidance and mentor-ship throughout the duration of this research project.
+Moreover, T.C.
+Fraser would like to thank the Perimeter Institute for financing this research and providing access to much needed computational resources.
+    \clearpage
+    \bibliography{references}
+
+    \clearpage
+    \appendix
+
+    \section{Summary of Inflation Technique}
     \label{sec:inflation_technique}
-    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a marginal model $\prob^{\mscenario}$ is compatible or incompatible with a given causal structure $\graph$.
-As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
-As a example, inflations of the Triangle structure are depicted in \cref{fig:inflations}.
-Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}.
-For example node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the \textit{Web inflation} of \cref{fig:the_web_inflation}.
-All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
-A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
-    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
-    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index.
-Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
-    \begin{definition}
-        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
-        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
-        Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is equivalent to its counterpart in $\graph$ up to copy-index.
-    \end{definition}
-    The motivation behind this definition is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
-
-    To do this, first notice that every compatible joint distribution $\prob[\nodes]$ uniquely defines a set of causal parameters for $\graph$.
-It is possible to obtain these causal parameters by computing the single-variable marginal distributions of $\prob[\nodes]$,
-    \[ \forall n \in \nodes : \prob[n\mid \Pa[\graph]{n}] = \sum_{\nodes \setminus n} \prob[\nodes] \eq \label{eq:unique_causal_parameters}\]
-    Now it is possible to make use of the inflation criteria (\cref{eq:inflation_defn}) which at least enforces that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$.
-From this, one can create a set of \term{inflated causal parameters} using \cref{eq:unique_causal_parameters},
-    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \eq \label{eq:inflated_causal_parameters} \]
-    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course, there exists compatible joint distributions on $\nodes'$ that can not be constructed in this manner.
-The claim is that all joint distributions that are constructed in this way are compatible.}.
-    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \eq \label{eq:unique_causal_parameters_inflated}\]
-    Together, \cref{eq:unique_causal_parameters,eq:inflated_causal_parameters,eq:unique_causal_parameters_inflated} form the \term{weak inflation lemma}: compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$.
-Before generalizing to the inflation lemma, a careful observation needs to be made.
-For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$, where $N \subset \nodes$, induces a compatible marginal distribution $\prob[N']$ over $N'$.
-In fact, $N'$ must contain no duplicate nodes up to copy index and thus $\prob[N] = \prob[N']$.
-These subsets of nodes are so essential to the Inflation Technique they are assigned a special name: sets $N' \subseteq \nodes'$ as called the \term{injectable sets} of $\graph'$ and $N \subset \nodes$ the \term{images of the injectable sets} of $\graph$.
-    \begin{align*}
-        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
-        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
-    \end{align*}
-    Injectable sets are incredibly useful for causal compatibility because they allow one to extend the weak inflation lemma to \textit{the} inflation lemma:
-    \begin{lemma}
-        \label[lemma]{lem:inflation}
-        \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-    \end{lemma}
-    Diagrammatically, \cref{lem:inflation} can be visualized as follows:
-
-    \begin{center}
-        \begin{tikzpicture}
-            \pgfmathsetmacro{\vs}{2.2};
-            \pgfmathsetmacro{\hs}{5.2};
-            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
-            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
-            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
-            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
-            \draw[very thick, ->] (pn) -- (cp);
-            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
-            \draw[very thick, ->] (cp_) -- (pn_);
-        \end{tikzpicture}
-    \end{center}
-
-    The inflation lemma is the most important result of the causal inflation technique.
-The contrapositive version of \cref{lem:inflation} is a powerful tool for deriving causal compatibility constraints.
-Any causal compatibility constraint, such as a causal compatibility inequality, that constrains injectable marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ can be \textit{deflated} into a valid compatibility constraint on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure by dropping all references to the copy-indices.
-Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
-Therefore, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
-
-    Heretofore, the Inflation Technique as stated by \cref{lem:inflation} does not facilitate the derivation of any non-trivial inequalities.
-The Inflation lemma simply casts causal inference problems on $\graph$ to causal inference problems on $\graph'$.
-Fortunately, an inflated causal structure $\graph'$ possesses its own conditional independence relations which can be exploited to turn linear inequalities on $\graph'$ into polynomial inequalities on $\graph$.
-
-    Suppose that one were to obtain an inequality on $\graph'$ that contained probabilistic terms such as $\prob[N']$ where $N' \not \in \Inj[\graph]{\graph'}$.
-At this point, the Inflation lemma is not applicable because it requires probabilistic constraints to consist entirely of distributions $\prob[N']$ where $N'$ is injectable.
-If for example, $N' \not \in \Inj[\graph]{\graph'}$ could be partitioned into two injectable subsets $N_1' \in \Inj[\graph]{\graph'}$ and $N_2' \in \Inj[\graph]{\graph'}$ that where \term{ancestrally independent} in $\graph'$,
-    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
-    Then the compatible marginal context $\prob[N']$ must be probabilistically separable $\prob[N'] = \prob[N_1']\prob[N_2']$ due to \cref{eq:local_markov_property}.
-Since $N_1'$ and $N_2'$ are both injectable, the inflation lemma now applies and the original inequality can be deflated.
-
-    \begin{center}
-        \begin{tikzpicture}[scale=0.8]
-            \pgfmathsetmacro{\hs}{1.4};
-            \pgfmathsetmacro{\vs}{0.6};
-            \pgfmathsetmacro{\cross}{0.2};
-            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
-            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
-            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
-            \draw (2*\hs, 4*\vs + 0.7*\vs) node[]{$N_1' \cup N_2' = N$};
-            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
-            \draw (0, 0) node[](b){??};
-            \draw[thick, ] (a) -- (ab);
-            \draw[thick, ] (c) -- (cd);
-            \draw[thick, ] (a) -- (ac);
-            \draw[thick, ->] (ac) -- (c);
-            \draw[thick, ->] (ab) -- (b);
-            \draw[thick, ->] (cd) -- (d);
-            \draw[very thick, red]
-            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
-            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
-            ;
-        \end{tikzpicture}
-    \end{center}
-
-    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that can are called the \term{pre-injectable sets}.
-A set $N' \subseteq \nodes'$ is a pre-injectable set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
-
-    A pre-injectable set $N'$ is of primal importance to the inflation technique because any distribution over $N'$ will factorize according to graphical $d$-separation conditions~\cite{Pearl_2009},
-    \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
-    Application of the inflation lemma to linear inequalities constraining pre-injectable distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
-Throughout the body of this work, we let $\PreInj[\graph]{\graph'}$ denote the set of all pre-injectable sets.
-Naturally, the pre-injectable sets will define a marginal scenario $\mscenario$ that in \cref{sec:deriving_inequalities} will be used to derive compatibility inequalities\footnote{Analogously for a marginal scenario $\mscenario$, the pre-injectable sets $\PreInj[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
-Therefore, in practice, it is completely sufficient to focus on the maximal pre-injectable sets}.
-
-    \begin{center}
-    \begin{figure}
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
-    \caption{The Cut inflation}\label{fig:cut_inflation}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
-    \caption{The Spiral inflation}\label{fig:spiral_inflation}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
-    \caption{The Wagon-Wheel inflation}\label{fig:wagon_wheel_inflation}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure}}
-    \caption{The Web Inflation}\label{fig:the_web_inflation}
-    \end{subfigure}
-    \caption{Some inflations of the Triangle structure.}
-    \label{fig:inflations}
-    \end{figure}
-    \end{center}
-
-    \section{Deriving Inequalities}
+
+    \subsection{Satisfaction of d-Separation Relations}
+    \todo[TC]{Absorb the relevant components of the next section into this one}
+
+    \subsection{Marginal Satisfiability and Inequalities}
     \label{sec:deriving_inequalities}
@@
 
-    \subsection{The Marginal Problem as a Linear Program}
-    \label{sec:marginal_linear}
+    \subsubsection{The Marginal Problem as a Linear Program}
+    \label{sec:marginal_linear}\label{sec:linear_programs}
 
@@
 
-    \subsubsection{Events \& Outcomes}
+    % \subsubsection{Events \& Outcomes}
     To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$.
@@
 By construction each marginal event $m \in \Events{\mscenario}$ is a restriction of some joint event $j \in \Events{\jointvar}$.
-    \subsubsection{Linear Programs}
-    \label{sec:linear_programs}
+    % \subsubsection{Linear Programs}
+    % \label{sec:linear_programs}
     The marginalization operation (\cref{eq:def:marginal_problem}) of the marginal problem is a linear operator.
@@
 
-    \subsection{Triangle Structure Inequalities}
-    \label{sec:found_inequalities}
-
-    Equipped with the Fritz distribution (\cref{sec:fritz_distribution}) and the inflation technique (\cref{sec:inflation_technique}), it is now possible to derive causal compatibility inequalities for the triangle that are violated by the Fritz distribution; the procedure for doing so is as follows.
-First select an inflation $\graph'$ of the Triangle structure $\graph$ and identify the maximal pre-injectable sets $\PreInj[\graph]{\graph'}$.
-These sets define the marginal scenario to be used in the Inflation Technique.
-Next, inflate the Fritz distribution into the pre-injectable sets as described by the Inflation lemma (\cref{lem:inflation}).
-Finally, obtain infeasibility certificates using some linear programing software and obtain a valid causal compatibility inequality that witnesses the Fritz distribution's incompatibility.
-
-    As a first demonstration, we make use of the Wagon-Wheel inflation (\cref{fig:wagon_wheel_inflation}) to find these inequalities.
-The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
-By inspection\footnote{Computing the injectable and pre-injectable sets computationally is possible and a technique is discussed in~\citet{Inflation}.}, the maximal pre-injectable sets of the Wagon-Wheel inflation are as follows:
-    \begin{equation*}
-        \eq \label{eq:pre_injectable_triangle_structure_wagon_wheel}
-        \begin{gathered}
-            \textbf{Maximal Pre-injectable Sets} \\
-            \bc{A_2, B_1, C_3, C_1} \\
-            \bc{A_1, B_1, C_4, C_2} \\
-            \bc{A_1, B_2, C_1, C_3} \\
-            \bc{A_2, B_2, C_2, C_4} \\
-        \end{gathered}
-        \qquad
-        \begin{gathered}
-            \textbf{Ancestral Independences} \\
-            \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
-            \bc{A_1, B_1, C_4} \ancestralindep \bc{C_2} \\
-            \bc{A_1, B_2, C_1} \ancestralindep \bc{C_3} \\
-            \bc{A_2, B_2, C_2} \ancestralindep \bc{C_4} \\
-        \end{gathered}
-    \end{equation*}
-
-    These maximal pre-injectable sets define a marginal scenario where $\graph'$ is the Wagon-Wheel inflation of the Triangle structure $\graph$.
-    \[ \mscenario = \PreInj[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
-    The complete set of variables $\jointvar$ is simply the set of observable nodes in the Wagon-Wheel inflation,
-    \[ \jointvar = \nodes'_O = \bc{A_1, A_2, B_1, B_2, C_1, C_2, C_3, C_4} \]
-    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
-This marginal scenario $\mscenario$ then defines an incidence matrix capable of accommodating the Fritz distribution.
-    Analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \abs{\Events{V}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{\Events{v}} = 4^{\abs{\jointvar}} = 4^8 = 65,536$ columns.
-Understandably, this matrix is not reproduced here.
-The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
-
-    The marginal distribution vector $\probvec^{\mscenario}$ is indexed by $1024$ marginal outcomes $m \in \Events{\mscenario}$ of the following \textit{symbolic} form,
-    \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
-    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
-    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
-    And finally, each probability distribution in \cref{eq:marginal_vector_wagon_wheel_factors} is deflated by dropping copy-indices.
-    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[ABC]\br{000}\prob[C]\br{0}, \ldots, \prob[ABC]\br{323}\prob[C]\br{2}, \ldots, \prob[ABC]\br{333}\prob[C]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors_dropped}\]
-    This step is permitted because all of the remaining distributions in \cref{eq:marginal_vector_wagon_wheel_factors} are defined over the injectable sets of the Wagon-Wheel inflation.
-Numerically however, each of the elements of $\probvec^{\mscenario}$ are replaced with numerical values corresponding to the Fritz distribution upon deflation.
-Pursuant to \cref{eq:fritz_dist}, $\prob[ABC]\br{323}\prob[C]\br{2}$, for example, is assigned the following numerical value.
-    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267  \]
-    The same is applied to all other entries of $\probvec^{\mscenario}$.
-Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained.
-Below is an example of an infeasibility inequality obtained over the entries of \cref{eq:marginal_vector_wagon_wheel_factors_dropped}.
-    \begin{equation*}
-    \begin{gathered}
-    \eq\label{eq:ww_ineq}
-    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \\
-    P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \\
-    P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \\
-    P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \\
-    P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \\
-    P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \\
-    P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \\
-    P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \\
-    P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \\
-    P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \\
-    P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) - P_{ABC}(000)P_{C}(3) \geq 0
-    \end{gathered}
-    \end{equation*}
-    By construction, every marginal model $\probvec^{\mscenario} = \bc{\prob[ABC], \prob[AB], \prob[BC], \prob[AC], \prob[A], \prob[B], \prob[C]}$ compatible with the Triangle structure must satisfy \cref{eq:ww_ineq}.
-The Fritz distribution however violates \cref{eq:ww_ineq}.
-
-    Notice the final term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $-1$.
-For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$.
-
-    It is possible to simplify this inequality by marginalizing over sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) = P_{ABC}(300)$.
-Upon doing so, one obtains the following,
-    \begin{gather*}
-        P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \leq \\ P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + \\
-        + P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + P_{AB}(20) + P_{AB}(30) + P_{C}(3)P_{C}(0)
-    \end{gather*}
-
-    There are a couple of important concepts to understand.
-First, the Fritz distribution is known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings.
-The inequality contained in \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure.
-For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$.
-Moreover, although the existence of an inequality capable of witnessing Fritz distribution is guaranteed, there was no guarantee that the marginal model associated with the Wagon-Wheel inflation (\cref{eq:wagon_wheel_marginal_model}) would be capable of producing such an inequality.
-In fact, smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
-
-    Larger inflations such as the Web inflation (\cref{fig:the_web_inflation}) were also used to generate causal compatibility inequalities that are violated by the Fritz distribution.
-The set of maximal pre-injectable sets for the Web inflation is considerably larger than \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
-    \begin{equation*}
-        \eq \label{eq:pre_injectable_triangle_structure_web}
-        \begin{gathered}
-            \textbf{Maximal Pre-injectable Sets} \\
-            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
-            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
-            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
-            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
-            \bc{A_1, B_3, C_4} \\
-            \bc{A_1, B_4, C_2} \\
-            \bc{A_2, B_1, C_4} \\
-            \bc{A_2, B_2, C_2} \\
-            \bc{A_3, B_3, C_3} \\
-            \bc{A_3, B_4, C_1} \\
-            \bc{A_4, B_1, C_3} \\
-            \bc{A_4, B_2, C_1}
-        \end{gathered}
-        \qquad
-        \begin{gathered}
-            \textbf{Ancestral Independences} \\
-            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
-            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
-            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
-            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
-            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
-            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
-            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
-            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
-            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
-            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
-            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
-            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
-        \end{gathered}
-    \end{equation*}
-    Again, analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ and $201,326,592$ non-zero entires.
-Using this incidence matrix, a number of incompatibility certificates were derived.
-For inspection, one is reproduced in \cref{sec:web_inequality}.
-
-    In summary, these causal compatibility inequalities represent a completion of objective \cref{r:1} from \cref{sec:fritz_distribution}.
-These inequalities are derived without making use of Bell's theorem and instead use the Inflation Technique which is completely independent of Bell's theorems.
-Additionally, the derivation of causal compatibility inequalities allows one prove incompatibility even when perfect correlations are absent.
-Moreover, they allow one to probe the amount of noise the Fritz distribution can sustain before becoming compatible (see \cref{sec:violations_noise}).
-Unfortunately, infeasibility certificates are found by linear programing software to certify the infeasibility of a \textit{particular distribution}.
-This means that inequalities like \cref{eq:ww_ineq}, the one presented in \cref{sec:web_inequality}, and others are specifically manufactured in order witness a particular type of quantum non-classicality.
-In an effort to derive inequalities that could lead to potentially new forms of non-classicality, we searched for inequalities that did not admit biased towards the Fritz distribution.
-
-    \subsection{Symmetric Inequalities}
-    \label{sec:symmetric_inequalities}
-
-    Quite surprisingly, it is possible to derive causal compatibility inequalities for the Triangle structure that are symmetric under the exchange of parties.
-This is done by grouping marginal events $m \in \Events{\mscenario}$ into orbits under the action of party exchange.
-Even more interestingly, these inequalities are violated by the Fritz distribution.
-This comes as a surprise because the Fritz distribution is \text{not} invariant under the exchange of parties; in fact the Fritz distribution is noticeably biased toward $C$.
-
-    In general, exploiting symmetries of the marginal scenario is useful for a few distinct reasons.
-First, \citet{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:deriving_inequalities}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
-They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that non-trivial inequalities can be recovered from facets of a symmetric polytope.
-Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
-The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.
-
-    To demonstrate what types of symmetries we have in mind, we present the following example:
-    \begin{example}
-        \label[example]{ex:symmetries}
-        First consider the marginal scenario $\mscenario = \bc{\bc{A, B, C}, \bc{C, D}, \bc{A, D}}$ where each variable in $\jointvar = \bc{A,B,C,D}$ has binary outcomes: $O_A = O_B = O_C = O_D = \bc{0,1}$.
-Moreover, let $I_{\mscenario}$ be the following compatibility inequality over $\mscenario$ for some causal structure $\graph$,
-        \[ I_{\mscenario} = \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}  \]
-        Intuitively, the compatibility of $\probvec^{\mscenario}$ is \textit{independent} of the how one labels outcomes.
-Suppose $\varphi : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ is a permutation of the variables $\jointvar$.
-Intuitively $\varphi$ acts on $I_{\mscenario}$ in the following way,
+    \subsection{Causal Inflations}
+    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a marginal model $\prob^{\mscenario}$ is compatible or incompatible with a given causal structure $\graph$.
+As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
+As a example, inflations of the Triangle structure are depicted in \cref{fig:inflations}.
+Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}.
+For example node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the \textit{Web inflation} of \cref{fig:the_web_inflation}.
+All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
+A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
+    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
+    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index.
+Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
+    \begin{definition}
+        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
+        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
+        Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is equivalent to its counterpart in $\graph$ up to copy-index.
+    \end{definition}
+    The motivation behind this definition is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
+
+    To do this, first notice that every compatible joint distribution $\prob[\nodes]$ uniquely defines a set of causal parameters for $\graph$.
+It is possible to obtain these causal parameters by computing the single-variable marginal distributions of $\prob[\nodes]$,
+    \[ \forall n \in \nodes : \prob[n\mid \Pa[\graph]{n}] = \sum_{\nodes \setminus n} \prob[\nodes] \eq \label{eq:unique_causal_parameters}\]
+    Now it is possible to make use of the inflation criteria (\cref{eq:inflation_defn}) which at least enforces that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$.
+From this, one can create a set of \term{inflated causal parameters} using \cref{eq:unique_causal_parameters},
+    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \eq \label{eq:inflated_causal_parameters} \]
+    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course, there exists compatible joint distributions on $\nodes'$ that can not be constructed in this manner.
+The claim is that all joint distributions that are constructed in this way are compatible.}.
+    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \eq \label{eq:unique_causal_parameters_inflated}\]
+    Together, \cref{eq:unique_causal_parameters,eq:inflated_causal_parameters,eq:unique_causal_parameters_inflated} form the \term{weak inflation lemma}: compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$.
+Before generalizing to the inflation lemma, a careful observation needs to be made.
+For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$, where $N \subset \nodes$, induces a compatible marginal distribution $\prob[N']$ over $N'$.
+In fact, $N'$ must contain no duplicate nodes up to copy index and thus $\prob[N] = \prob[N']$.
+These subsets of nodes are so essential to the Inflation Technique they are assigned a special name: sets $N' \subseteq \nodes'$ as called the \term{injectable sets} of $\graph'$ and $N \subset \nodes$ the \term{images of the injectable sets} of $\graph$.
     \begin{align*}
-        \varphi\bs{I_{\mscenario}} &= \bc{\prob[\varphi\bs{abc}][010] \leq \prob[\varphi\bs{cd}][00] + \prob[\varphi\bs{ad}][01]} \\
-        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
-        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
+        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
+        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
     \end{align*}
-        In general (as in this example), permutations over all variables can modify the marginal scenario $\varphi\bs{\mscenario} \neq \mscenario$; in general we write $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
-Although $\varphi\bs{I_{\mscenario}}$ is still a valid causal compatibility inequality, in constrains marginal models of a different marginal scenario $\varphi\bs{\mscenario}$ and are in general of no interest.
-    \end{example}
-
-    Following the observations of \cref{ex:symmetries}, it is always possible to permute the random variables in a marginal scenario to produce new and valid inequalities.
-The symmetry group over a the complete set of variables $\jointvar$ is simply the \text{permutation group}\footnote{The permutation group over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} $\Perm{\jointvar}$.
-As was noted in \cref{ex:symmetries}, some permutations $\varphi \in \Perm{\jointvar}$ have the undesired possibility of transforming $\mscenario$ into a different marginal scenario.
-    \[ \varphi\bs{\mscenario} \defined \bc{\varphi\bs{V_1}, \ldots, \varphi\bs{V_k}} \neq \mscenario \]
-    This means that there could exist $V \in \mscenario$ such that $\varphi\bs{V} \not \in \mscenario$.
-Permutations $\varphi$ retaining this property are unable to generate compatibility inequalities over the same marginal scenario.
-Therefore, the desired set of symmetries is a subgroup that takes $\mscenario$ to $\mscenario$.
-
-    \begin{definition}
-        The \term{variable permutation group} $\gp$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario.
-        \[ \Phi\br{\mscenario} \defined \bc{\varphi \in \Perm{\jointvar} \mid \forall V \in \mscenario : \varphi\bs{V} \in \mscenario} \]
-    \end{definition}
-
-    Obtaining the variable permutation group $\gp\br{\mscenario}$ is a simple application of a group stabilizer algorithm.
-After obtaining $\gp\br{\mscenario}$, one can take known compatibility inequalities $I_{\mscenario}$ can create a whole family of inequalities $\bc{\varphi\bs{I_{\mscenario}} \mid \varphi \in \gp\br{\mscenario}}$ that are valid for the same marginal scenario $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}} = \varphi\bs{I}_{\mscenario}$.
-
-    Although very useful for reducing computational complexity~\cite{Bancal_2010}, we divert our attention to finding \textit{symmetric} inequalities themselves.
-    \[ \forall \varphi \in \gp\br{\mscenario} :  \varphi\bs{I_{\mscenario}} = I_{\mscenario} \]
-    In order to do this, we must first define how elements $\varphi \in \gp$ act on marginal events.
-The action of $\varphi \in \gp$ on any outcome $f \in \Events{V}$ (denoted $\geo\bs{f}$) is defined as,
-    \[ \forall v \in \Dom{\varphi\bs{f}} : \br{\varphi\bs{f}}\br{v} \defined f\br{\varphi^{-1}\bs{v}} \eq \label{eq:act_on_variable}\]
-    \Cref{eq:act_on_variable} is nothing more than a mathematical definition for the intuitive action used in \cref{ex:symmetries}.
-    Through repeated action of $\varphi \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define \term{group orbits} of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$.
-    \begin{align*}
-        \Orb[\gp]{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \gp} \\
-        \Orb[\gp]{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \gp}
-    \end{align*}
-    Using these group orbits, it is possible to contract the incidence matrix $M$ of a marginal scenario into a symmetrized version.
-
-    \begin{definition}
-        The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and the variable permutation group $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
-Each row of $M_{\gp}$ corresponds to a marginal orbit $\Orb[\gp]{m}$.
-Analogously each column of $M_{\gp}$ corresponds to a joint orbit $\Orb[\gp]{j}$.
-The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
-        \[ \br{M_{\gp}}_{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M_{m',j'} \]
-    \end{definition}
-    It is possible to analogously define a \term{symmetric joint distribution vector} $\probvec^{\jointvar}_{\Phi}$ indexed by $\Orb[\gp]{j}$,
-    \[ \br{\probvec^{\jointvar}_{\Phi}}_{\Orb[\gp]{j}} = \sum_{j' \in \Orb[\gp]{j}} \probvec^{\jointvar}_{j} \]
-    And a \term{symmetric marginal distribution vector} $\probvec^{\mscenario}_{\Phi}$ indexed by $\Orb[\gp]{m}$,
-    \[ \br{\probvec^{\mscenario}_{\Phi}}_{\Orb[\gp]{m}} = \sum_{m' \in \Orb[\gp]{m}} \probvec^{\mscenario}_{m} \]
-    Which altogether define a new, \term{symmetric marginal problem},
-    \[ \probvec^{\mscenario}_{\Phi} = M_{\gp} \cdot \probvec^{\jointvar}_{\Phi} \]
-    The symmetric marginal problem can be solved using the same computational methods discussed in \cref{sec:deriving_inequalities} and will produce symmetric inequalities.
-
-    In the context of the Inflation technique, a variable symmetry $\Phi\br{\mscenario'}$ over an inflated marginal scenario $\mscenario'$ does not always correspond to a variable symmetry under deflation $\Phi\br{\mscenario}$.
-In order to derive deflated inequalities that are symmetric under an exchange of parties, it is required that $\Phi\br{\mscenario'} \sim \Phi\br{\mscenario}$ are equivalent up to copy-index.
-
-    For the Triangle structure, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
-For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\PreInj[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
-    \begin{equation*}
-    \begin{aligned}[c]
-    &\hspace{1mm}\varphi_1 \\
-    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\varphi_2 \\
-    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\varphi_3 \\
-    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\varphi_4 \\
-    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
-    \end{aligned}
-    \end{equation*}
-    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
-    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
-    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
-    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
-    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
-Moreover they stabilize the pre-injectable sets of \cref{eq:pre_injectable_triangle_structure_web}.
-Importantly,
-    \[ \gp\br{\PreInj[\graph]{\graph'}} \sim \Perm{A,B,C} \]
-    To see this, $\varphi_1$ and $\varphi_4$ become the identity element $\ident$ in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
-
-    The symmetric incidence matrix $M_{\Phi}$ for the Web inflation is considerably smaller than $M$.
-The number of rows of $M_{\Phi}$ is a number of distinct orbits $\Orb[\Phi]{m}$ in $\Events{\mscenario}$.
-Likewise the number of columns is the number of distinct orbits $\Orb[\Phi]{j}$ in $\Events{\jointvar}$.
-For the Web inflation in particular, $M_{\Phi}$ is $450 \times 358,120$.
-Using the symmetric incidence matrix and linear programing methods, an infeasibility certificate was found that is capable of witnessing the Fritz distribution.
-This inequality is reproduced in \cref{sec:symmetic_web_inequality}.
-
-    \section{Violations \& Noise}
-    \label{sec:violations_noise}
-    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality.
-In this section, we illuminate two tasks that can be performed in order to further understand the nature of quantum non-classical by using inequalities.
-
-    \subsection{Noise}
-    \label{sec:noise}
+    Injectable sets are incredibly useful for causal compatibility because they allow one to extend the weak inflation lemma to \textit{the} inflation lemma:
+    \begin{lemma}
+        \label[lemma]{lem:inflation}
+        \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+    \end{lemma}
+    Diagrammatically, \cref{lem:inflation} can be visualized as follows:
+
+    \begin{center}
+        \begin{tikzpicture}
+            \pgfmathsetmacro{\vs}{2.2};
+            \pgfmathsetmacro{\hs}{5.2};
+            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
+            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
+            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
+            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
+            \draw[very thick, ->] (pn) -- (cp);
+            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
+            \draw[very thick, ->] (cp_) -- (pn_);
+        \end{tikzpicture}
+    \end{center}
+
+    The inflation lemma is the most important result of the causal inflation technique.
+The contrapositive version of \cref{lem:inflation} is a powerful tool for deriving causal compatibility constraints.
+Any causal compatibility constraint, such as a causal compatibility inequality, that constrains injectable marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ can be \textit{deflated} into a valid compatibility constraint on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure by dropping all references to the copy-indices.
+Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
+Therefore, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
+
+    Heretofore, the Inflation Technique as stated by \cref{lem:inflation} does not facilitate the derivation of any non-trivial inequalities.
+The Inflation lemma simply casts causal inference problems on $\graph$ to causal inference problems on $\graph'$.
+Fortunately, an inflated causal structure $\graph'$ possesses its own conditional independence relations which can be exploited to turn linear inequalities on $\graph'$ into polynomial inequalities on $\graph$.
+
+    Suppose that one were to obtain an inequality on $\graph'$ that contained probabilistic terms such as $\prob[N']$ where $N' \not \in \Inj[\graph]{\graph'}$.
+At this point, the Inflation lemma is not applicable because it requires probabilistic constraints to consist entirely of distributions $\prob[N']$ where $N'$ is injectable.
+If for example, $N' \not \in \Inj[\graph]{\graph'}$ could be partitioned into two injectable subsets $N_1' \in \Inj[\graph]{\graph'}$ and $N_2' \in \Inj[\graph]{\graph'}$ that where \term{ancestrally independent} in $\graph'$,
+    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
+    Then the compatible marginal context $\prob[N']$ must be probabilistically separable $\prob[N'] = \prob[N_1']\prob[N_2']$ due to \cref{eq:local_markov_property}.
+Since $N_1'$ and $N_2'$ are both injectable, the inflation lemma now applies and the original inequality can be deflated.
+
+    \begin{center}
+        \begin{tikzpicture}[scale=0.8]
+            \pgfmathsetmacro{\hs}{1.4};
+            \pgfmathsetmacro{\vs}{0.6};
+            \pgfmathsetmacro{\cross}{0.2};
+            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
+            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
+            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
+            \draw (2*\hs, 4*\vs + 0.7*\vs) node[]{$N_1' \cup N_2' = N$};
+            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
+            \draw (0, 0) node[](b){??};
+            \draw[thick, ] (a) -- (ab);
+            \draw[thick, ] (c) -- (cd);
+            \draw[thick, ] (a) -- (ac);
+            \draw[thick, ->] (ac) -- (c);
+            \draw[thick, ->] (ab) -- (b);
+            \draw[thick, ->] (cd) -- (d);
+            \draw[very thick, red]
+            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
+            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
+            ;
+        \end{tikzpicture}
+    \end{center}
+
+    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that can are called the \term{pre-injectable sets}.
+A set $N' \subseteq \nodes'$ is a pre-injectable set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
+
+    A pre-injectable set $N'$ is of primal importance to the inflation technique because any distribution over $N'$ will factorize according to graphical $d$-separation conditions~\cite{Pearl_2009},
+    \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
+    Application of the inflation lemma to linear inequalities constraining pre-injectable distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
+Throughout the body of this work, we let $\PreInj[\graph]{\graph'}$ denote the set of all pre-injectable sets.
+Naturally, the pre-injectable sets will define a marginal scenario $\mscenario$ that are used to derive compatibility inequalities in \cref{sec:deriving_inequalities}\footnote{Analogously for a marginal scenario $\mscenario$, the pre-injectable sets $\PreInj[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
+Therefore, in practice, it is completely sufficient to focus on the maximal pre-injectable sets}.
+
+    \begin{center}
     \begin{figure}
-    \begin{center}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
-            \vspace{-0.2in}
-            \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
-            \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
-            \label{fig:uniform_distribution}
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
+    \caption{The Cut inflation}\label{fig:cut_inflation}
+    \end{subfigure}
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
+    \caption{The Spiral inflation}\label{fig:spiral_inflation}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
+    \caption{The Wagon-Wheel inflation}\label{fig:wagon_wheel_inflation}
+    \end{subfigure}
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure}}
+    \caption{The Web Inflation}\label{fig:the_web_inflation}
+    \end{subfigure}
+    \caption{Some inflations of the Triangle structure.}
+    \label{fig:inflations}
+    \end{figure}
     \end{center}
-    \end{figure}
-    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality.
-As was mentioned in \cref{sec:fritz_distribution}, this embedding required a very idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$.
-From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}.
-It is possible to minimize noise by developing more accurate measurement channels but perfect correlations are too idealistic.
-Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.
-
-    In the Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U} = \s{U}_{ABC}$ (see \cref{fig:uniform_distribution})
-    \[ \s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}  \]
-    Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible.
-We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
-    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
-    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution as $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$.
-For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.
-As a standard, let $I\br{\prob} < 0$ represent violations while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturations of the inequality).
-
-    To analyze noise, $4$ inequalities where chosen.
-First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}.
-The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{sec:web_inequality} while $I_3$ is the symmetric inequality in \cref{sec:symmetic_web_inequality}.
-Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{sec:web_inequality}.
-
-    \begin{figure}
-    \begin{subfigure}[b]{.48\linewidth}
-    {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}}
-    \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
-    \end{subfigure}
-    \begin{subfigure}[b]{.48\linewidth}
-    {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}}
-    \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
-    \end{subfigure}
-    \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
-    \end{figure}
-
-    The results of our experiments are plotted in \cref{fig:master_noise}.
-\Cref{fig:noise} illustrates that each curve $I\br{\s{N}_{\vep}\br{\prob[\fritz]}}$ as a function of $\vep$ is monotonically increasing as expected; the more noise added to the probability distribution, the more classical it becomes.
-\Cref{fig:noise_zoomed} is the same plot as \cref{fig:noise} zoomed onto the interval $\vep \in \bs{0, 0.12}$.
-These tests suggest that inequality $I_1$ (\cref{sec:web_inequality}), when compared against all others is most robust to noise.
-
-    Overall, this noise model demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
-The associated distribution $\s N_{0.085}\br{\prob[\fritz]}$ is plotted in \cref{fig:noisy_fritz}.
-There remains the possibility that another inequality will be able to withstand a larger degree of noise that $I_1$.
-Given that $I_0, I_1, I_2, I_3$ are far from a representative inequalities and are likely not facets of any inflated marginal polytope, it is save to say that this is possible.
-
-    \begin{figure}
-    \begin{center}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
-            \vspace{-0.2in}
-            \[ \probplotvalue{255, 255, 243} = 0.00133 \]
-            \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
-            \label{fig:noisy_fritz}
-    \end{center}
-    \end{figure}
-
-    \subsection{Numerical Optimizations}
-    \label{sec:optimizations}
-    Causal compatibility inequalities act as a \textit{measure} of non-classicality.
-If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$\footnote{Remember that larger violations are more negative when the inequalities are written in the proposed canonical form.} Nonetheless, this statement comes from several caveats.
-First, it is possible (and frequently the case) for ${I\br{\prob[1]}} < I\br{\prob[2]}$ to hold for one inequality $I$ but have ${\ti I\br{\prob[2]}} < \ti I\br{\prob[1]}$ hold for another inequality $\ti I$.
-In this case, all one can claim is that $\prob[1]$ is more incompatible than $\prob[2]$ with respective to $I$ but the contrary is true with respect to $\ti I$.
-Second, not all inequalities $I$ are \textit{good} measures of non-classicality.
-In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality.
-This is because the facets form a necessary and sufficient set with all other inequalities following from positive mixtures of the facets.
-However, good measures of incompatibility are less understood in the Triangle structure where the space of classical correlations is non-convex.
-At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility (especially because they are curated toward the Fritz distribution).
-Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure.
-
-    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}.
-Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:quantum_model_triangle} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$.
-The objective value is simply the degree of violation $f = I\br{\prob[ABC]}$ and used to make adjustments to $\la$ in order to achieve largest and larger violations.
-
-    Finding larger violations to compatibility inequalities is nothing more that a numerical optimization (specifically minimization) of $f\br{\la}$.
-Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
-Specifically, the BFGS method~\cite[p.
-142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.
-238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
-
-    \subsection{Parameterizing Quantum Distributions}
-    \label{sec:param_quantum_dist}
-    \begin{figure}
-    \begin{center}
-            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
-            \caption{The Triangle structure as modeled by quantum states and measurements.}
-            \label{fig:triangle_structure_quantum_model}
-    \end{center}
-    \end{figure}
-    In search of new, incompatible, quantum distributions that can be realized on the Triangle structure, numerical optimizations over the the space of quantum-accessible probability distributions are performed.
-To do so, we are interested in a parameterization all distributions that can be expressed as follows:
-    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
-    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately\footnote{$\netperm$ is discussed more thoroughly in \cref{sec:perm_matrix}.}.
-
-    In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
-The states $\rho$ are taken to be bipartite \textit{qubit} states acting on $\s{H}^{2} \otimes \s{H}^{2}$.
-This is motivated by \cref{sec:fritz_distribution} in which the Fritz distribution only requires qubit states.
-In generality, one could consider $n$-dimensional states acting on $\s{H}^{n} \otimes \s{H}^{n}$.
-However, in such cases the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ then acts on $\br{\Hilb^{n}}^{\otimes 6}$ requiring a $n^6 \times n^6$ matrix with $n^{12}$ entries.
-Therefore, $n = 2$ is far more computationally feasible than $n > 2$.
-Additionally, restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
-First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure.
-Second, generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, however a valid, unbiased parameterization was not found for $k > 2$.
-Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as follows:
-    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]
-
-    In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
-Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, a single technique is presented that was found to be most computationally suitable for our purposes.
-    \subsubsection{Unitary Group}
+
+    \clearpage
+    \section{Quantum Parameterization of Triangle Structure}
+
+    \subsection{Unitary Group}
     \label{sec:unitary_group}
@@
 This is discussed in \cref{sec:comp_spengler}.
-    \subsubsection{Measurements}
+    \subsection{Measurements}
     \label{sec:measurements}
@@
 This method was inspired by the measurement seeding method for iterative optimization used by \citet{Pal_2010} .
-    \subsubsection{States}
+    \subsection{States}
     \label{sec:states}
@@
     For various optimization tasks sensitive to initial conditions outlined \cref{sec:optimizations}, the latter parameterization of \cref{eq:uniform_param} generally performed better than the former \cref{eq:convex_param}.
-    \subsubsection{Permutation Matrix}
+    \subsection{Permutation Matrix}
     \label{sec:perm_matrix}
@@
     \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
-    \subsection{Numerical Optimization Results}
-    \label{sec:results}
-
-    \Cref{sec:param_quantum_dist} expounded on how we elected to parameterized the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}).
-Specifically, we make use of fully generic $4\times 4$ density matrices (bipartite qubit) for each shared resource and $4$-element projective measurements.
-For each inequality $I$, we define the relative violation $V_F$ to be maximum violation relative to the violation achieved by the Fritz distribution.
-    \[ V_F = \f{\min_{P}\bc{I\br{P}}}{I\br{P_F}} \]
-
-    The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{sec:web_inequality}.
-At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
-Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution.
-In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure} or set of possible events.
-What does this reveal about $I_1$ and non-classicality in the Triangle structure?
-This result is not entirely unexpected.
-As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to show incompatibility of the Triangle structure.
-Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for a specific forms of non-classicality that resemble the Fritz distribution very closely.
-
-    \begin{figure}
-    \begin{center}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
-            \caption{Probability distribution that maximizes violation of $I_1$ from \cref{sec:web_inequality} ($V_F \simeq 1.501$).}
-            \label{fig:maximum_violation_I_1}
-    \end{center}
-    \end{figure}
-
-    An alternative explanation has to do with the sensitively of the initial condition $\la_{\br{0}} = \br{\la_{\br{0}, 0}, \ldots, \la_{\br{0}, n}}$ in our optimization.
-In \cref{sec:param_quantum_dist}, it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
-Somewhat surprisingly, when using a uniform seed for $\la_0$, all optimization methods consistently converged to inequality saturation instead of inequality violation which of course is achievable by the Fritz distribution.
-Instead, only initial seeds close enough to the \textit{Fritz parameters} $\la_{\br{\fritz}}$ (the parameters that induce the Fritz distribution using the quantum implementation in \cref{sec:fritz_distribution}) where able to achieve violation.
-To illustrate this graphically, we let the initial seed be a small Gaussian perturbation $\de \la$ away from $\la_{\br{\fritz}}$ in parameter space.
-    \[ \la_{\br{0}} = \la_{\br{\fritz}} + \de \la  \]
-    The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation.
-For $I_1$, deviations of $\chi \gtrsim 1.3$ inhibited convergence to violation.
-This is depicted in \cref{fig:initial_conditions}.
-Therefore, it is unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
-Most likely, this phenomena is due to a combination of both effects.
-    \begin{center}
-    \begin{figure}
-    \begin{subfigure}[t]{.48\linewidth}
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}
-    \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
-    \end{subfigure}
-    \begin{subfigure}[t]{.48\linewidth}
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}
-    \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
-    \end{subfigure}
-    \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
-    \end{figure}
-    \end{center}
-    The second inequality in consideration is $I_3$; the \textit{symmetric} Web inflation inequality presented in \cref{sec:symmetic_web_inequality}.
-This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
-Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution.
-However, this result is far more surprising.
-Since the inequality is symmetric with respect to the exchange of parties $\varphi \in \Perm{A, B, C}$, one would naively expect that the maximum violating distribution is be symmetric as well.
-If it were not, one could construct a distribution that violates $I_3$ more by symmetrizing $\prob[\fritz]$ by summing over all possible permutations and normalizing.
-The symmetrized Fritz distribution is plotted in \cref{fig:symmetrized_fritz}.
-This distribution is also non-classical with relative violation $V_F = 3$.
-As it turns out, the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}\footnote{At least numerical optimizations suggest this is the case.} Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result found in~\citet{Inflation}.
-    \begin{figure}
-    \begin{center}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
-            \caption{Probability distribution that maximizes violation of $I_3$ from \cref{sec:symmetic_web_inequality} ($V_F \simeq 2.61$).}
-            \label{fig:maximum_violation_I_3}
-    \end{center}
-    \end{figure}
-    \begin{figure}
-    \begin{center}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
-            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
-            \label{fig:symmetrized_fritz}
-    \end{center}
-    \end{figure}
-
-    Finally for both $I_0$ and $I_2$, the maximum relative violation happens to be $V_F = 1$ (up to numerical precision).
-This means that the Fritz distribution either represents a local minimum of the parameter space or is in fact \textit{the} maximally violating distribution.
-Without further investigations, it is unclear if this behavior is related to the universality of the Fritz distribution or if its an artifact of the methods used to derive $I_0$ and $I_2$.
-
-    \section{Conclusions}
-
-    In \cref{sec:triangle_structure}, we elucidated that non-classicality in the Triangle structure has been an unsolved problem for nearly a decade.
-Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality.
-Afterwards,~\citet{Henson_2014} were able to to classify the Triangle structure as \textit{interesting} which partially explains why it remains an enigma.
-Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the Triangle structure.
-Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality.
-In \cref{sec:fritz_distribution} the Fritz distribution was introduced in detail and refinements where made to a problem originally proposed by~\citet{Fritz_2012}.
-For this research project, we made heavy use of the Inflation Technique of \cref{sec:inflation_technique} and the Fritz distribution in order to derive the first causal compatibility inequalities capable of having quantum violations.
-Finally, we used those inequalities in an attempt to discover new forms of non-classicality in the Triangle structure with partial success.
-
-    Ultimately, this work accomplishes two important tasks.
-First and foremost, the derivation of \cref{eq:ww_ineq} demonstrates the utility of the Inflation technique specifically for quantum causal inference problems.
-The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure -- a task that no other existing techniques succeeded at.
-Therefore, this work acts as a strong indication that the Inflation technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
-
-    Penultimately, the results presented here solve~\cite[Problem 2.17]{Fritz_2012} insofar as to refine the original problem into three related questions problems: \ref{r:1}, \ref{r:2} and \ref{r:3}.
-The methods and techniques demonstrated here provide a means of solving \ref{r:1} and gives an opportunity to begin tackling \ref{r:2} and \ref{r:3} in the form of numerical optimizations.
-Computational and comprehensive limitations have stunted progress towards solving \ref{r:2} and \ref{r:3}, so it still remains unclear if \ref{r:2} and \ref{r:3} have affirmative solutions in the first place.
-
-    \section*{Acknowledgments}
-    T.C.
-Fraser would like to thank E.
-Wolfe for his excellent guidance and mentor-ship throughout the duration of this research project.
-Moreover, T.C.
-Fraser would like to thank the Perimeter Institute for financing this research and providing access to much needed computational resources.
-    \clearpage
-    \bibliography{references}
-
-    \clearpage
-    \appendix
-
-    \section{Common Terminology \& Notation}
-
-    \subsection{Graph Theory}
-    \label{sec:graph_theory}
-    \begin{definition}
-        \label{def:graph}
-        A \term{graph} $\graph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes have the capacity to represent any object while the edges are defined as \textit{pairs} of nodes $\edges \subseteq \nodes \times \nodes$.
-A \term{directed graph} $\graph$ is a graph where each edge $e \in \edges$ is assigned an order or \term{direction} $e = \bc{n \to n'}$.
-    \end{definition}
-
-    \begin{definition}
-        \label{def:graph_terms}
-        The following definitions are common language in directed graph theory. Let $n, m \in \nodes$ be example nodes of the graph $\graph$.
-        \begin{itemize}
-            \item The \term{parents of a node}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
-            \item The \term{children of a node}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
-            \item The \term{ancestry of a node}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$
-            \item The \term{descendants of a node}:  $\De[\graph]{n} \defined \bigcup_{i\in\mathbb{N}} \Ch[\graph][i]{n}$ where $\Ch[\graph][i]{n} \defined \Ch[\graph]{\Ch[\graph][i-1]{n}}$ and $\Ch[\graph][1]{n} = \Ch[\graph]{n}$
-        \end{itemize}
-        All of these terms can be generalized to sets of nodes $N \subseteq \nodes$ through union over the elements,
-        \begin{itemize}
-            \item The \term{parents of a node set}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
-            \item The \term{children of a node set}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
-            \item The \term{ancestry of a node set}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
-        \end{itemize}
-    \end{definition}
-
-    \begin{definition}
-        An \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$.
-        \[ \Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to n'} \mid n, n' \in N, e \in \edges}} \]
-        An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
-        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:dag}
-        A \term{directed acyclic graph} or \term{DAG} $\graph = \br{\nodes, \edges}$ is an directed graph with the additional property that no node $n$ is in its set of \term{ancestors}.
-        \[ \forall n \in \nodes : n \notin \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}\]
-        It is critical to note the difference in language between \textit{ancestors} from \textit{ancestry}.
-The ancestry $\An[\graph]{n}$ of a node $n$ is defined using \textit{whole} numbers $\mathbb{W}$.
-In contrast, the ancestors of a node are defined similarly with \textit{natural} numbers $\mathbb{N}$.
-    \end{definition}
-
-    \subsection{Probability Theory}
-    \label{sec:probability_theory}
-
-    \begin{definition}
-        The \term{product distribution} of two disjoint probability distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as $\prob[V] \times \prob[W]$.
-        \[ \forall s \in \Events{V \cup W} : \br{\prob[V] \times \prob[W]}\br{s} \defined \prob[V][s|_{V}]\cdot\prob[W][s|_{W}] \]
-        A product distribution of $k$ mutually disjoint distributions is defined as,
-        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
-        \[ \forall s \in \Events{W} : \br{\sum_{V \setminus W} \prob[V]}\br{s} \defined \sum_{j \in \Ext[V]{s}} \prob[V][j] \]
-        Where $\Ext[V]{s}$ denotes the set of all events $j \in \Events{V}$ that can be restricted to $s$,
-        \[ \Ext[V]{s} = \bc{j \in \Events{V} \mid s = j|_{\s{D}\br{s}}} \]
-    \end{definition}
-
-    \section{Computationally Efficient Parameterization of the Unitary Group}
+    \subsection{Computationally Efficient Parameterization of the Unitary Group}
     \label{sec:comp_spengler}
@@
 
+    \section{Common Terminology \& Notation}
+    \comment[TC]{keep, remove, or distribute into body where relevant?}
+    \subsection{Graph Theory}
+    \label{sec:graph_theory}
+    \begin{definition}
+        \label{def:graph}
+        A \term{graph} $\graph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes have the capacity to represent any object while the edges are defined as \textit{pairs} of nodes $\edges \subseteq \nodes \times \nodes$.
+A \term{directed graph} $\graph$ is a graph where each edge $e \in \edges$ is assigned an order or \term{direction} $e = \bc{n \to n'}$.
+    \end{definition}
+
+    \begin{definition}
+        \label{def:graph_terms}
+        The following definitions are common language in directed graph theory. Let $n, m \in \nodes$ be example nodes of the graph $\graph$.
+        \begin{itemize}
+            \item The \term{parents of a node}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
+            \item The \term{children of a node}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
+            \item The \term{ancestry of a node}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$
+            \item The \term{descendants of a node}:  $\De[\graph]{n} \defined \bigcup_{i\in\mathbb{N}} \Ch[\graph][i]{n}$ where $\Ch[\graph][i]{n} \defined \Ch[\graph]{\Ch[\graph][i-1]{n}}$ and $\Ch[\graph][1]{n} = \Ch[\graph]{n}$
+        \end{itemize}
+        All of these terms can be generalized to sets of nodes $N \subseteq \nodes$ through union over the elements,
+        \begin{itemize}
+            \item The \term{parents of a node set}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
+            \item The \term{children of a node set}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
+            \item The \term{ancestry of a node set}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
+        \end{itemize}
+    \end{definition}
+
+    \begin{definition}
+        An \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$.
+        \[ \Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to n'} \mid n, n' \in N, e \in \edges}} \]
+        An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
+        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
+    \end{definition}
+
+    \begin{definition}
+        \label{def:dag}
+        A \term{directed acyclic graph} or \term{DAG} $\graph = \br{\nodes, \edges}$ is an directed graph with the additional property that no node $n$ is in its set of \term{ancestors}.
+        \[ \forall n \in \nodes : n \notin \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}\]
+        It is critical to note the difference in language between \textit{ancestors} from \textit{ancestry}.
+The ancestry $\An[\graph]{n}$ of a node $n$ is defined using \textit{whole} numbers $\mathbb{W}$.
+In contrast, the ancestors of a node are defined similarly with \textit{natural} numbers $\mathbb{N}$.
+    \end{definition}
+
+    \subsection{Probability Theory}
+    \label{sec:probability_theory}
+
+    \begin{definition}
+        The \term{product distribution} of two disjoint probability distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as $\prob[V] \times \prob[W]$.
+        \[ \forall s \in \Events{V \cup W} : \br{\prob[V] \times \prob[W]}\br{s} \defined \prob[V][s|_{V}]\cdot\prob[W][s|_{W}] \]
+        A product distribution of $k$ mutually disjoint distributions is defined as,
+        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
+    \end{definition}
+
+    \begin{definition}
+        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
+        \[ \forall s \in \Events{W} : \br{\sum_{V \setminus W} \prob[V]}\br{s} \defined \sum_{j \in \Ext[V]{s}} \prob[V][j] \]
+        Where $\Ext[V]{s}$ denotes the set of all events $j \in \Events{V}$ that can be restricted to $s$,
+        \[ \Ext[V]{s} = \bc{j \in \Events{V} \mid s = j|_{\s{D}\br{s}}} \]
+    \end{definition}
+
     \clearpage
     \section{Large Triangle Structure Inequalities}
+    \label{sec:web_inequalities}
     \subsection{Web Inflation Inequality}

### 2017-03-08 documents/TriangleScenarioArXiv/ts.tex
final last minute edits

@@
 
-    \section{Violations \& Noise}
+    \section{Noisy Distributions \& Numerical Optimizations}
     \label{sec:violations_noise}
@@
 
-    \subsection{Parameterizing Quantum Distributions}
-    \label{sec:param_quantum_dist}
+    % \subsection{Parameterizing Quantum Distributions}
     \begin{figure}
@@
     In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
-Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, a single technique is presented that was found to be most computationally suitable for our purposes.
-    \subsection{Numerical Optimization Results}
+Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, although a single technique is presented in \cref{sec:unitary_group} that was found to be most computationally suitable for our purposes.
+\Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}.
+Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.
+
+    % \subsection{Numerical Optimization Results}
     \label{sec:results}
 
-    \Cref{sec:param_quantum_dist} expounded on how we elected to parameterized the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}).
-Specifically, we make use of fully generic $4\times 4$ density matrices (bipartite qubit) for each shared resource and $4$-element projective measurements.
     For each inequality $I$, we define the relative violation $V_F$ to be maximum violation relative to the violation achieved by the Fritz distribution.
@@
 Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility.
-In summary, it remains unclear whether or not \ref{r:1} or \ref{r:2} is a harder problem or if either is even feasible.
+In summary, it remains unclear whether or not \ref{r:2} or \ref{r:3} is a harder problem or if either is even feasible.
 
@@
     \section{Quantum Parameterization of Triangle Structure}
-
+    \label{sec:param_quantum_dist}
     \subsection{Unitary Group}

### 2017-03-08 documents/TriangleScenarioArXiv/ts.tex
fixed typos in the abstract

@@
         It has long been recognized that certain quantum correlations are often incompatible with particular assumption about classical causal structure.
-Such correlations are sometimes termed nonlocal, although it would be more accurate to say simply noncassical, as the presence of correlations certifies the genuinely nonclassical nature of a causal setup in a device-independent fashion.
+Such correlations are sometimes termed nonlocal, although they are more accurately termed non-classical, as the presence of correlations certifies the genuinely non-classical nature of a causal setup in a device-independent fashion.
 Whenever a quantum correlation violates a causal compatibility inequality (e.g.
-a Bell inequality) then the correlation is witnessed as nonclassical.
-Any constraint which is satisfied by all correlations which \emph{are} classically compatible with a given causal scenario defined a causal compatibility criterion.
+a Bell inequality) then the correlation is witnessed as non-classical.
+Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal scenario defined a causal compatibility criterion.
 Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?
-Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical triangle Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary.
-Our main contribution inn this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \emph{do} admit quantum violation.
+Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary.
+Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation.
 We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
@@
 These early results suggest, although do not prove, that quantum non-classical does not exist in the Triangle structure for \textit{two-outcome} measurements.
-We make \textit{no claim} that this is a universal truth and simply take it as motivation to explore incompatibility in Triangle structure for a degree of outcomes.
+It is therefore conjectured that all quantum non-classical distributions in the Triangle structure utilize more than $2$ outcomes in at least one party.
+Moreover we take these observations as motivation to explore incompatibility in Triangle structure for a larger cardinalities.
 
@@
 
-    \subsection{Noise}
+    \subsection{Noisy Distributions}
     \label{sec:noise}

### 2017-03-08 documents/TriangleScenarioArXiv/ts.tex
typo in abstract

@@
 a Bell inequality) then the correlation is witnessed as non-classical.
-Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal scenario defined a causal compatibility criterion.
+Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal scenario defines a causal compatibility criterion.
 Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?

### 2017-04-05 documents/TriangleScenarioArXiv/ts.tex
Updates from ShareLaTeX

@@
     \email{tcfraser@tcfraser.com}
-    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada \\ University of Waterloo, Waterloo, Ontario, Canada}
-    % \author{Elie Wolfe}
-    % \email{ewolfe@perimeter@institute.ca}
-    % \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada}
+    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
+    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
+    \author{Elie Wolfe}
+%    \email{ewolfe@perimeterinstitute.ca}
+    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
     \date{\today}
@@
 
-    \section*{Acknowledgments}
-    T.C.
+%    \section*{Acknowledgments}
+%    T.C.
 Fraser would like to thank E.
@@
 Fraser would like to thank the Perimeter Institute for financing this research and providing access to much needed computational resources.
+
+\begin{acknowledgments}
+This research was supported in part by Perimeter Institute for Theoretical Physics.
+Research at Perimeter Institute is supported by the Government of Canada through the Department of Innovation, Science and Economic Development Canada and by the Province of Ontario through the Ministry of Research, Innovation and Science.
+\end{acknowledgments}
+
     \clearpage
+    \setlength{\bibsep}{3pt plus 3pt minus 2pt}
+    \bibliographystyle{apsrev4-1}
+    \nocite{apsrev41Control}
     \bibliography{references}

### 2017-04-05 documents/TriangleScenarioArXiv/ts.tex
typos in abstract/authors multiple lines

@@
 % === Revtex Declaration ===
-\documentclass[aps, 10pt, english, twoside, pra, nofootinbib, tightenlines, longbibliography]{revtex4-1}
+\documentclass[aps, 10pt, english, twoside, pra, nofootinbib, tightenlines, longbibliography, superscriptaddress]{revtex4-1}
 
@@
     \author{Elie Wolfe}
+    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
     % \email{ewolfe@perimeterinstitute.ca}
-    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
     \date{\today}
@@
 In the realm of secure communication, quantum protocols --- a popular example being Quantum Key Distribution~\cite{Bennett_2014} -- are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill.
-History, every opportunity of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the nonclassical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}.
+History, every opportunity of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the non-classical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}.
 Motivated by past successes, a primal objective of modern quantum information theory is the discovery of new situations wherein quantum mechanics offers an advantage, and certification that the quantum advantage is genuine.
 
-    From a foundational prospective, the most robust demonstrations of quantum phenemena with no classical emulation have involved Bell inequalities~\cite{Bell_1964}.
+    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964}.
 Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}.
-The enumeration of Bell inequalities has since become a widespread systematic way of demonstration the \textit{nonclassicality} of a given observation.
+The enumeration of Bell inequalities has since become a widespread systematic way of demonstration the \textit{non-classicality} of a given observation.
 More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}.
@@
 The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}.
-Causal compatability inequalities, such as Bell of Instrumental inequalities, charechterize the space of observations that are compatible with a hypothesized causal structure, albeit the charechterization offered by practically deriveable inequalities often only an approximation.
+Causal compatibility inequalities, such as Bell of Instrumental inequalities, characterizer the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities often only an approximation.
 To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_scenario}.
-The fundamental Bell structure involves noncommunicating parties making measurements on some hidden shared resource $\la$, where the measuremement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$.
-Quantum nonclassicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}.
+The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$.
+Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}.
 More complex scenarios, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood.
@@
 The second, a new framework for solving causal inference problems developed by Wolfe \emph{et al.}~\cite{Inflation} called \term{The Inflation Technique}.
-Ultimately, this work serves as a validation that the Inflation Technique is sensitive enough to offer new insights into quantum nonclassicality.
-Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of nonclassicality.
+Ultimately, this work serves as a validation that the Inflation Technique is sensitive enough to offer new insights into quantum non-classicality.
+Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of non-classicality.
 The authors attempts to find such novel resources were met with only partial success, suggesting clear refinements for future exploration.
@@
 \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure was chosen as a case study.
-\Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first concieved of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}.
+\Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}.
 The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities.

### 2017-04-05 documents/TriangleScenarioArXiv/ts.tex
Moved references to end of document

@@
         It has long been recognized that certain quantum correlations are often incompatible with particular assumption about classical causal structure.
-Such correlations are sometimes termed nonlocal, although they are more accurately termed non-classical, as the presence of correlations certifies the genuinely non-classical nature of a causal setup in a device-independent fashion.
+Such correlations are sometimes termed non-local, although they are more accurately termed non-classical, as the presence of correlations certifies the genuinely non-classical nature of a causal setup in a device-independent fashion.
 Whenever a quantum correlation violates a causal compatibility inequality (e.g.
 a Bell inequality) then the correlation is witnessed as non-classical.
-Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal scenario defines a causal compatibility criterion.
+Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion.
 Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?
@@
 More complex scenarios, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood.
-Here we investigate one particular causal scenario: the Triangle structure (\cref{fig:triangle_structure}).
+Here we investigate one particular causal structure: the Triangle structure (\cref{fig:triangle_structure}).
 
@@
 
-%    \section*{Acknowledgments}
-%    T.C.
-Fraser would like to thank E.
-Wolfe for his excellent guidance and mentor-ship throughout the duration of this research project.
-Moreover, T.C.
-Fraser would like to thank the Perimeter Institute for financing this research and providing access to much needed computational resources.
-
     \begin{acknowledgments}
@@
     \end{acknowledgments}
-
-    \clearpage
-    \setlength{\bibsep}{3pt plus 3pt minus 2pt}
-    \bibliographystyle{apsrev4-1}
-    \nocite{apsrev41Control}
-    \bibliography{references}
 
@@
 
+    \clearpage
+    \setlength{\bibsep}{3pt plus 3pt minus 2pt}
+    \bibliographystyle{apsrev4-1}
+    \nocite{apsrev41Control}
+    \bibliography{references}
+
 \end{document}

### 2017-04-06 documents/TriangleScenarioArXiv/ts.tex
compatibility section no-longer references marginal models

@@
     \tableofcontents
-    \setlength{\parskip}{1em}
+    % \setlength{\parskip}{1em}
     \clearpage
@@
     In recent decades, the technical utility of quantum mechanics has become abundantly clear.
-In the realm of computation, quantum algorithms -- such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016} -- scale exponentially better than their classical counterparts.
-In the realm of secure communication, quantum protocols --- a popular example being Quantum Key Distribution~\cite{Bennett_2014} -- are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill.
-History, every opportunity of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the non-classical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}.
+In the realm of computation, quantum algorithms --- such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016} --- scale exponentially better than their classical counterparts.
+In the realm of secure communication, quantum protocols --- a popular example being Quantum Key Distribution~\cite{Bennett_2014} --- are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill.
+Throughout history, every aspect of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the non-classical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}.
 Motivated by past successes, a primal objective of modern quantum information theory is the discovery of new situations wherein quantum mechanics offers an advantage, and certification that the quantum advantage is genuine.
@@
 The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}.
-Causal compatibility inequalities, such as Bell of Instrumental inequalities, characterizer the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities often only an approximation.
+Causal compatibility inequalities, such as Bell and Instrumental inequalities, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation.
 To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_scenario}.
@@
 Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}.
-More complex scenarios, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood.
+More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood.
 Here we investigate one particular causal structure: the Triangle structure (\cref{fig:triangle_structure}).
@@
 An overview of some milestone results is provided in \cref{sec:triangle_structure}.
-Identifying causal compatibility inequalities for this configuration has been seen as particularly challenging~\citet{Branciard_2012}.
+Identifying causal compatibility inequalities for this configuration has been seen as particularly challenging~\cite{Branciard_2012}.
 Further identifying causal compatibility inequalities of such high resolution that such inequalities can be violated by quantum-accessible distributions has remained out-of-reach for the Triangle structure.
@@
     The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used.
+\Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities.
 \Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure was chosen as a case study.
@@
 The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities.
+A sample of these inequalities are presented in \cref{sec:found_inequalities} (specifically \cref{eq:ww_ineq} as well as in \cref{sec:web_inequality,sec:symmetic_web_inequality}\todo[TC]{Reorganize the location of the inequalities}).
 \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work.
@@
 \Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions.
-A sample of these inequalities are presented at the end of \cref{sec:found_inequalities} (specifically \cref{eq:ww_ineq}) as well as in \cref{sec:web_inequality,sec:symmetic_web_inequality}.
 Finally, \cref{sec:violations_noise} introduces the method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality.
 Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.
+\Cref{sec:conclusions} concludes with proposed avenues for further research.
 
     \section{Causal Compatibility}
-    \todo[TC]{Talk to Elie about the varying notions of compatibility}
     \label{sec:causal_compatibility}
-    The task of causal inference aims to determine the set of potentially observable probability distribution compatible with some hypothesis about causal relationships.
-whether or not a given family of observed probability distributions can be explained by a proposed causal mechanism~\cite{Pearl_2009}.
-If a set of observed distributions can be explained by the hypothesized causal mechanism, then the observations are said to be \textit{compatible} with the causal mechanism.
-In order to define compatibility rigorously, we first need to formally define what is meant by ``set of observations''.
-
-    \subsection{Marginal Models}
-    Given a set of observable variables $\jointvar = \bc{v_1, \ldots, v_k}$ where each $v \in \jointvar$ is a statistical random variable, one can conceivably make a measurement over of these variables and obtain a joint probability distribution $\prob[\jointvar] = \prob[v_1,\ldots,v_n]$.
-More generally however, and depending on the context, it is possible to make a measurement on a set of the system $V \subset \jointvar$ in order to obtain a marginal distribution $\prob[V]$.
-With complete generality however, one could in principle be limited so as to only be able to record observations on portions of the system $\mscenario = \bc{V_1, \ldots, V_m \mid \forall i : V_i \subseteq \jointvar}$ obtaining a collection of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_m] \mid \forall i: V_i \in \mscenario}$.
-
-    The set $\mscenario = \bc{V \mid V \subseteq \jointvar}$ of subsets of $\jointvar$ is referred to as the \term{marginal scenario} and each element $V \in \mscenario$ is termed a \term{(marginal) context} of $\mscenario$.
-The complete set of marginal distributions is referred to as the \term{marginal model} and is denoted with an superscript $\prob^{\mscenario}$:
-    \[ \prob^{\mscenario} = \bc{\prob[V] \mid V \in \mscenario} \]
-    A marginal model acts as the most general description of a family of observations that can be made over $\jointvar$.
-Strictly speaking, as defined by~\cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that all subsets of contexts are also contexts.
-    \[ \forall V \in \mscenario, V' \subset V : V' \in \mscenario \]
-    Throughout this document, we exclusively consider (without loss of generality) the \textit{maximal} marginal scenario; restricting our focus to the largest contexts in the marginal scenario.
-Additionally, all marginal scenarios are taken to be \text{complete} in the sense that the marginal scenario covers the complete set of observable variables $\jointvar$.
-    \[ \jointvar = \bigcup_{V \in \mscenario} V \]
-
-    \subsection{Causal Structure}
-    A hypothesis of causal mechanism is formally referred to as  a \term{causal structure}.
-Mathematically, a causal structure can be represented as a directed acyclic graph $\graph = \br{\nodes, \edges}$ of nodes $\nodes$ and edges $\edges$ as defined in \cref{sec:graph_theory}.
-The nodes of a causal structure are random variables and are classified into two disjoint classes: the \term{latent nodes} $\nodes_L$ representing the set of nodes that are unobservable and the \term{observed nodes} $\nodes_O$.
-The latent nodes of a causal structure represent completely hidden variables that are hidden by some fundamental process or cannot be measured due to other limitations.
-The observed nodes represent random variables that are measurable and in practice will be observed by the marginal model $\prob^\mscenario$.
-The edges $\edges$ of a causal structure represent casual influence between variables within the causal structure.
-
-    A number of causal structures are depicted throughout this document (see \cref{fig:bell_scenario,fig:triangle_structure} as well as \cref{fig:inflations}).
+    The task of causal inference is to determine the set of potentially observable probability distributions compatible with some hypothesis about causal relationships~\cite{Pearl_2009}.
+If an observed distribution can be explained by the hypothesized causal mechanism, then the distribution is said to be \textit{compatible} with said causal mechanism.
+In order to define compatibility rigorously, we first need to formally define the notion of a causal hypothesis.
+
+    A hypothesis of causal mechanism is formally referred to as a \term{causal structure} and can be represented as a \term{directed acyclic graph}.
+A directed graph $\graph$ is an ordered tuple $\br{\nodes, \edges}$ of respectively \textit{nodes} and \textit{edges} where each edge $e \in \edges$ connects a \textit{pair} of nodes $n, m \in \nodes$ with a directed arrow $e = \bc{n \to m}$.
+A directed graph is \textit{acyclic} if there are no paths following the directions of the edges starting from and returning to the same node.
+The nodes $\nodes$ of a causal structure represent random variables while the edges $\edges$ represent a casual influence from one variable to another pursuant to the prescribed direction.
+
+    Henceforth, we will utilize a number of familiar notions from graph theory and denote them accordingly.
+The \term{parents of a node} $n \in \nodes$ are all nodes which point directly into $n$, i.e.
+$\Pa[\graph]{n} \defined \bc{m \mid m \to n}$.
+Similarly defined are the \term{children of a node} $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$.
+Recursively defined are the \term{ancestors of a node} $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$ and the \term{descendants of a node} $\De[\graph]{n} \defined \bigcup_{i\in\mathbb{N}} \Ch[\graph][i]{n}$ where $\Ch[\graph][i]{n} \defined \Ch[\graph]{\Ch[\graph][i-1]{n}}$ and $\Ch[\graph][0]{n} = n$.
+Finally, we extend this notation to a subset of nodes $N \subseteq \nodes$ by performing a union over elements.
+As an example, the parents of the nodes $N \subseteq \nodes$ are denoted $\Pa[\graph]{N} = \bigcup_{n \in N} \Pa[\graph]{n}$.
+
+    % A number of causal structures are depicted throughout this document (see \cref{fig:bell_scenario,fig:triangle_structure,fig:inflations}).
 As an example, the Triangle structure has $3$ observable nodes and $3$ latent nodes,
-    \[ \nodes_{O} = \bc{A, B, C} \qquad \nodes_{L} = \bc{X, Y, Z} \]
-    along with $6$ edges indicating that the latent nodes $\bc{X, Y, Z}$ cause and influence the observed nodes $\bc{A, B, C}$.
-    \[ \edges = \bc{\bc{X \to A}, \bc{Y \to A}, \bc{Y \to B}, \bc{Z \to B}, \bc{Z \to C}, \bc{X \to C}} \]
-
-    \subsection{Compatibility}
-    \label{sec:compatibility}
-
-    Now that the notions of a causal structure $\graph$ and a marginal model $\prob^{\mscenario}$ are defined, it is now possible to precisely define the notion of compatibility between the two.
-Intuitively, the absence of certain causal connections within $\graph$ should restrict and limit the set of possible observations that can be made on $\graph$; equivalently, the causal connections within $\graph$ should explain $\prob^{\mscenario}$.
-If each variable $n \in \nodes$ is caused by its parents $\Pa[\graph]{n}$, then $n$ should be independent of all other variables that are not its descendants.
-This is known as the \term{local Markov property}:
-    \[ n \indep \nodes \setminus \De[\graph]{n} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
-    Where $\indep$ denotes statistical independence.
-With this as motivation, we define a set of \term{causal parameters} for a causal structure $\graph$ to be a specification of a conditional distribution for every variable $n \in \nodes$ given its parents:
-    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \eq \label{eq:causal_parameters} \]
-    It is important to note that a set of causal parameters is not unique; the numerical nature of set of causal parameters is a \text{choice}.
-Altogether, a marginal model $\prob^{\mscenario}$ is \term{compatible} with a causal structure $\graph$ if there exists a choice of causal parameters such that each context $\prob[V] \in \prob^{\mscenario}$ can be \textit{recovered} from the following series of operations:
-    \begin{enumerate}
-        \item Obtain a joint probability distribution over \textit{all} variables of the causal structure using the chosen casual parameters:\footnote{Here $\prod$ denotes the product distribution $\prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}]$.}
-        \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] \eq \label{eq:local_markov_property_operation}\]
-        This step ensures that the local Markov property (\cref{eq:causal_parameters}) holds for all variables $n \in \nodes$.
-        \item Marginalize over the latent variables of $\graph$ to obtain a joint distribution over the observed variables $\nodes_O$:
-        \[ \prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes] \eq \label{eq:observable_marginalization} \]
-        \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$:
-        \[ \prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O] \eq \label{eq:context_marginalization} \]
-    \end{enumerate}
-    It is important to note that compatibility between $\prob^{\mscenario}$ and $\graph$ requires that it is possible to recover \textit{each} context $\prob[V] \in \prob^{\mscenario}$ from the \textit{same} set of causal parameters.
-If it is not possible for $\prob^{\mscenario}$ to be recovered for \textit{any} choice of causal parameters, then $\prob^{\mscenario}$ is \term{incompatible}.
-
-    \subsection{Inequalities}
-    As defined in \cref{sec:compatibility}, determining compatibility is equivalent to determining if a set of causal parameters exists with the above-mentioned properties.
+    % \[ \nodes_{O} = \bc{A, B, C} \qquad \nodes_{L} = \bc{X, Y, Z} \]
+    % along with $6$ edges indicating that the latent nodes $\bc{X, Y, Z}$ cause and influence the observed nodes $\bc{A, B, C}$.
+    % \[ \edges = \bc{\bc{X \to A}, \bc{Y \to A}, \bc{Y \to B}, \bc{Z \to B}, \bc{Z \to C}, \bc{X \to C}} \]
+
+    Now that the notion of a causal structure $\graph$ is defined along with some standard graph-theoretic notation, it is now possible to precisely define the notion of compatibility between $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$.
+Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$.
+Specifically, the causal structure $\graph$ hypothesizes that each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$, then $n$ should be independent of all other variables, except its own descendants when conditioned over $\Pa[\graph]{n}$.
+This is known as the \term{local Markov property}:\footnote{Here $A \indep B \mid C$ denotes statistical independence between $A$ and $B$ conditional on $C$ where $A,B,C \subseteq \nodes$, i.e.
+for a given probability distribution $\prob[\nodes]$, $\prob[AB \mid C] = \prob[A \mid C]\prob[B \mid C]$.}
+    \[ n \indep \br{\nodes \setminus \De[\graph]{n}} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
+    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:local_markov_property}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}.
+Alternatively yet equivalently, the notion of compatibility can be interpreted as follows: a distribution $\prob[\nodes]$ is compatible with $\graph$ if $\prob[\nodes]$ can be consistently factorized into conditional probability distributions for each variable $n \in \nodes$ conditioned on its parents $\Pa[\graph]{n}$:
+    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:local_markov_property_operation}\]
+    The conditional distributions in \cref{eq:local_markov_property_operation} (i.e.
+$\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}.
+If a distribution $\prob[\nodes]$ violates \cref{eq:local_markov_property} or equivalently cannot be factorized according to \cref{eq:local_markov_property_operation}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$.
+When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is trivially easy to verify whether or not $\prob[\nodes]$ is compatibility with $\graph$; \cref{sec:satisfaction_of_d_sep_relations} describes in detail how this is accomplished.
+
+    A challenge is present when one is supplied with a partial observation, i.e.
+a joint distribution $\prob[\nodes_{O}]$ where $\nodes_{O} \subset \nodes$ is some subset of variables referred to as the \term{observable nodes} $\nodes_O$.
+In such cases, \cref{eq:local_markov_property_operation} can not be verified by direction calculation because it is certainly possible that the parents of some observable node are themselves unobservable $\Pa[\graph]{\nodes_{O}} \not \subseteq \nodes_{O}$.
+In such cases, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \prod_{n \in \nodes_{O}} \prob[n \mid \Pa[\graph]{n}]$.
+The unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$ representing hidden random variables that are hidden either by some fundamental process or cannot be measured due to other limitations.
+    \todo[TC]{Explain why this is difficult more.}
+    \todo[TC]{Figure out if I should include d-sep here}
+    \todo[TC]{Explain what this work and inflation accomplishes regarding this}
+
     In practice however, checking causal parameters systemically is intractable, especially when the cardinality (number of outcomes) of the latent variables is unspecified.
 Instead, \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of simply Bell inequalities for two reasons.
-Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure/Bell causal structure.
-Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob^{\mscenario}$ instead of \textit{linear}.} are probabilistic inequalities defined over the marginal contexts $\prob[V] \in \prob^{\mscenario}$ within the marginal model.
-If a marginal model $\prob^{\mscenario}$ happens to \textit{violate} any causal compatibility inequality, then that marginal model is definitely \textit{incompatible}.
+Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure.
+Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.} are probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its induced marginals which constraint the set of compatible probability distributions.
+If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}.
 In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.
 
-    Unfortunately, a singular inequality can not prove that a given marginal model is \textit{compatible}, only \textit{incompatible}.
+    Unfortunately, a singular inequality cannot prove that a given distribution is \textit{compatible}, only \textit{incompatible}.
 Instead, a \textit{complete characterization} of compatibility would consist of a complete set of all valid causal compatibility inequalities; satisfaction of a complete set of inequalities does prove compatibility.
@@
 
-    From the perspective of identifying quantum non-classicality, the causal structure $\graph$ acts as the classical hypothesis for a particular marginal model $\prob^{\mscenario}$.
-Therefore, non-classicality becomes synonymous with incompatibility: if a marginal model $\prob^{\mscenario}$ is incompatible, then it is non-classical.
+    From the perspective of identifying quantum non-classicality, a causal structure $\graph$ adopts the role of a classical hypothesis.
+Therefore, non-classicality becomes synonymous with incompatibility: if a distribution $\prob[\nodes_{O}]$ is incompatible, then it is non-classical.
 Henceforth, we will use these two terms interchangeably.
-From a resource standpoint, if the non-classicality of $\prob^{\mscenario}$ can be witnessed by an inequality $I$, but $\prob^{\mscenario}$ can be implemented using quantum states and measurements, then the causal compatibility inequality $I$ represents a concrete task where quantum resources out-perform classical resources.
+From a resource standpoint, if the non-classicality of $\prob[\nodes_{O}]$ can be witnessed by an inequality $I$, but $\prob[\nodes_{O}]$ can be implemented using quantum states and measurements, then the causal compatibility inequality $I$ represents a physical task where quantum resources out-perform classical resources.
 
@@
 
-    \section{Symmetric Inequalities}
-    \label{sec:symmetric_inequalities}
-
-    Quite surprisingly, it is possible to derive causal compatibility inequalities for the Triangle structure that are symmetric under the exchange of parties.
-This is done by grouping marginal events $m \in \Events{\mscenario}$ into orbits under the action of party exchange.
-Even more interestingly, these inequalities are violated by the Fritz distribution.
-This comes as a surprise because the Fritz distribution is \text{not} invariant under the exchange of parties; in fact the Fritz distribution is noticeably biased toward $C$.
-
-    In general, exploiting symmetries of the marginal scenario is useful for a few distinct reasons.
-First, \citet{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:deriving_inequalities}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
-They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that non-trivial inequalities can be recovered from facets of a symmetric polytope.
-Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
-The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.
-
-    To demonstrate what types of symmetries we have in mind, we present the following example:
-    \begin{example}
-        \label[example]{ex:symmetries}
-        First consider the marginal scenario $\mscenario = \bc{\bc{A, B, C}, \bc{C, D}, \bc{A, D}}$ where each variable in $\jointvar = \bc{A,B,C,D}$ has binary outcomes: $O_A = O_B = O_C = O_D = \bc{0,1}$.
-Moreover, let $I_{\mscenario}$ be the following compatibility inequality over $\mscenario$ for some causal structure $\graph$,
-        \[ I_{\mscenario} = \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}  \]
-        Intuitively, the compatibility of $\probvec^{\mscenario}$ is \textit{independent} of the how one labels outcomes.
-Suppose $\varphi : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ is a permutation of the variables $\jointvar$.
-Intuitively $\varphi$ acts on $I_{\mscenario}$ in the following way,
-        \begin{align*}
-        \varphi\bs{I_{\mscenario}} &= \bc{\prob[\varphi\bs{abc}][010] \leq \prob[\varphi\bs{cd}][00] + \prob[\varphi\bs{ad}][01]} \\
-        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
-        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
-        \end{align*}
-        In general (as in this example), permutations over all variables can modify the marginal scenario $\varphi\bs{\mscenario} \neq \mscenario$; in general we write $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
-Although $\varphi\bs{I_{\mscenario}}$ is still a valid causal compatibility inequality, in constrains marginal models of a different marginal scenario $\varphi\bs{\mscenario}$ and are in general of no interest.
-    \end{example}
-
-    Following the observations of \cref{ex:symmetries}, it is always possible to permute the random variables in a marginal scenario to produce new and valid inequalities.
-The symmetry group over a the complete set of variables $\jointvar$ is simply the \text{permutation group}\footnote{The permutation group over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} $\Perm{\jointvar}$.
-As was noted in \cref{ex:symmetries}, some permutations $\varphi \in \Perm{\jointvar}$ have the undesired possibility of transforming $\mscenario$ into a different marginal scenario.
-    \[ \varphi\bs{\mscenario} \defined \bc{\varphi\bs{V_1}, \ldots, \varphi\bs{V_k}} \neq \mscenario \]
-    This means that there could exist $V \in \mscenario$ such that $\varphi\bs{V} \not \in \mscenario$.
-Permutations $\varphi$ retaining this property are unable to generate compatibility inequalities over the same marginal scenario.
-Therefore, the desired set of symmetries is a subgroup that takes $\mscenario$ to $\mscenario$.
-
-    \begin{definition}
-        The \term{variable permutation group} $\gp$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario.
-        \[ \Phi\br{\mscenario} \defined \bc{\varphi \in \Perm{\jointvar} \mid \forall V \in \mscenario : \varphi\bs{V} \in \mscenario} \]
-    \end{definition}
-
-    Obtaining the variable permutation group $\gp\br{\mscenario}$ is a simple application of a group stabilizer algorithm.
-After obtaining $\gp\br{\mscenario}$, one can take known compatibility inequalities $I_{\mscenario}$ can create a whole family of inequalities $\bc{\varphi\bs{I_{\mscenario}} \mid \varphi \in \gp\br{\mscenario}}$ that are valid for the same marginal scenario $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}} = \varphi\bs{I}_{\mscenario}$.
-
-    Although very useful for reducing computational complexity~\cite{Bancal_2010}, we divert our attention to finding \textit{symmetric} inequalities themselves.
-    \[ \forall \varphi \in \gp\br{\mscenario} :  \varphi\bs{I_{\mscenario}} = I_{\mscenario} \]
-    In order to do this, we must first define how elements $\varphi \in \gp$ act on marginal events.
-The action of $\varphi \in \gp$ on any outcome $f \in \Events{V}$ (denoted $\geo\bs{f}$) is defined as,
-    \[ \forall v \in \Dom{\varphi\bs{f}} : \br{\varphi\bs{f}}\br{v} \defined f\br{\varphi^{-1}\bs{v}} \eq \label{eq:act_on_variable}\]
-    \Cref{eq:act_on_variable} is nothing more than a mathematical definition for the intuitive action used in \cref{ex:symmetries}.
-    Through repeated action of $\varphi \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define \term{group orbits} of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$.
-    \begin{align*}
-        \Orb[\gp]{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \gp} \\
-        \Orb[\gp]{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \gp}
-    \end{align*}
-    Using these group orbits, it is possible to contract the incidence matrix $M$ of a marginal scenario into a symmetrized version.
-
-    \begin{definition}
-        The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and the variable permutation group $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
-Each row of $M_{\gp}$ corresponds to a marginal orbit $\Orb[\gp]{m}$.
-Analogously each column of $M_{\gp}$ corresponds to a joint orbit $\Orb[\gp]{j}$.
-The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
-        \[ \br{M_{\gp}}_{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M_{m',j'} \]
-    \end{definition}
-    It is possible to analogously define a \term{symmetric joint distribution vector} $\probvec^{\jointvar}_{\Phi}$ indexed by $\Orb[\gp]{j}$,
-    \[ \br{\probvec^{\jointvar}_{\Phi}}_{\Orb[\gp]{j}} = \sum_{j' \in \Orb[\gp]{j}} \probvec^{\jointvar}_{j} \]
-    And a \term{symmetric marginal distribution vector} $\probvec^{\mscenario}_{\Phi}$ indexed by $\Orb[\gp]{m}$,
-    \[ \br{\probvec^{\mscenario}_{\Phi}}_{\Orb[\gp]{m}} = \sum_{m' \in \Orb[\gp]{m}} \probvec^{\mscenario}_{m} \]
-    Which altogether define a new, \term{symmetric marginal problem},
-    \[ \probvec^{\mscenario}_{\Phi} = M_{\gp} \cdot \probvec^{\jointvar}_{\Phi} \]
-    The symmetric marginal problem can be solved using the same computational methods discussed in \cref{sec:deriving_inequalities} and will produce symmetric inequalities.
-
-    In the context of the Inflation technique, a variable symmetry $\Phi\br{\mscenario'}$ over an inflated marginal scenario $\mscenario'$ does not always correspond to a variable symmetry under deflation $\Phi\br{\mscenario}$.
-In order to derive deflated inequalities that are symmetric under an exchange of parties, it is required that $\Phi\br{\mscenario'} \sim \Phi\br{\mscenario}$ are equivalent up to copy-index.
-
-    For the Triangle structure in particular, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
-For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\PreInj[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
-    \begin{equation*}
-    \begin{aligned}[c]
-    &\hspace{1mm}\varphi_1 \\
-    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\varphi_2 \\
-    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\varphi_3 \\
-    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\varphi_4 \\
-    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
-    \end{aligned}
-    \end{equation*}
-    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
-    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
-    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
-    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
-    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
-Moreover they stabilize the pre-injectable sets of \cref{eq:pre_injectable_triangle_structure_web}.
-Importantly,
-    \[ \gp\br{\PreInj[\graph]{\graph'}} \sim \Perm{A,B,C} \]
-    To see this, $\varphi_1$ and $\varphi_4$ become the identity element $\ident$ in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
-
-    The symmetric incidence matrix $M_{\Phi}$ for the Web inflation is considerably smaller than $M$.
-The number of rows of $M_{\Phi}$ is a number of distinct orbits $\Orb[\Phi]{m}$ in $\Events{\mscenario}$.
-Likewise the number of columns is the number of distinct orbits $\Orb[\Phi]{j}$ in $\Events{\jointvar}$.
-For the Web inflation in particular, $M_{\Phi}$ is $450 \times 358,120$.
-Using the symmetric incidence matrix and linear programing methods, an infeasibility certificate was found that is capable of witnessing the Fritz distribution.
-This inequality is reproduced in \cref{sec:symmetic_web_inequality}.
-
     \section{Noisy Distributions \& Numerical Optimizations}
@@
     \subsection{Satisfaction of d-Separation Relations}
+    \label{sec:satisfaction_of_d_sep_relations}
     \todo[TC]{Absorb the relevant components of the next section into this one}
+    \todo[TC]{Given a distribution and a causal structure, does the distribution satisfy the conditional d-Separation relations?}
 
     \subsection{Marginal Satisfiability and Inequalities}
-    \label{sec:deriving_inequalities}
-
+    \label{sec:marginal_satisfiability}
+    \label{sec:marginal_linear}\label{sec:linear_programs}
+
+    Given a set of observable variables $\jointvar = \bc{v_1, \ldots, v_k}$ where each $v \in \jointvar$ is a statistical random variable, one can conceivably make a measurement over of these variables and obtain a joint probability distribution $\prob[\jointvar] = \prob[v_1,\ldots,v_n]$.
+More generally however, and depending on the context, it is possible to make a measurement on a set of the system $V \subset \jointvar$ in order to obtain a marginal distribution $\prob[V]$.
+With complete generality however, one could in principle be limited so as to only be able to record observations on portions of the system $\mscenario = \bc{V_1, \ldots, V_m \mid \forall i : V_i \subseteq \jointvar}$ obtaining a collection of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_m] \mid \forall i: V_i \in \mscenario}$.
+
+    The set $\mscenario = \bc{V \mid V \subseteq \jointvar}$ of subsets of $\jointvar$ is referred to as the \term{marginal scenario} and each element $V \in \mscenario$ is termed a \term{(marginal) context} of $\mscenario$.
+The complete set of marginal distributions is referred to as the \term{marginal model} and is denoted with an superscript $\prob^{\mscenario}$:
+    \[ \prob^{\mscenario} = \bc{\prob[V] \mid V \in \mscenario} \]
+    A marginal model acts as the most general description of a family of observations that can be made over $\jointvar$.
+Strictly speaking, as defined by~\cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that all subsets of contexts are also contexts.
+    \[ \forall V \in \mscenario, V' \subset V : V' \in \mscenario \]
+    Throughout this document, we exclusively consider (without loss of generality) the \textit{maximal} marginal scenario; restricting our focus to the largest contexts in the marginal scenario.
+Additionally, all marginal scenarios are taken to be \text{complete} in the sense that the marginal scenario covers the complete set of observable variables $\jointvar$.
+    \[ \jointvar = \bigcup_{V \in \mscenario} V \]
+
+    % For a causal structure $\graph$, a chosen specification of a conditional distributions for each variable  is referred to as a set of \term{causal parameters for $\graph$}:
+    % \[  \eq \label{eq:causal_parameters} \]
+    It is important to note that a set of causal parameters is not unique; the numerical nature of set of causal parameters is a \text{choice}.
+Altogether, a marginal model $\prob^{\mscenario}$ is \term{compatible} with a causal structure $\graph$ if there exists a choice of causal parameters such that each context $\prob[V] \in \prob^{\mscenario}$ can be \textit{recovered} from the following series of operations:
+    \begin{enumerate}
+        \item Obtain a joint probability distribution over \textit{all} variables of the causal structure using the chosen casual parameters:\footnote{Here $\prod$ denotes the product distribution $\prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = $.}
+        \item Marginalize over the latent variables of $\graph$ to obtain a joint distribution over the observed variables $\nodes_O$:
+        \[ \prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes] \eq \label{eq:observable_marginalization} \]
+        \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$:
+        \[ \prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O] \eq \label{eq:context_marginalization} \]
+    \end{enumerate}
+    It is important to note that compatibility between $\prob^{\mscenario}$ and $\graph$ requires that it is possible to recover \textit{each} context $\prob[V] \in \prob^{\mscenario}$ from the \textit{same} set of causal parameters.
+If it is not possible for $\prob^{\mscenario}$ to be recovered for \textit{any} choice of causal parameters, then $\prob^{\mscenario}$ is \term{incompatible}.
     In \cref{sec:causal_compatibility}, we defined the notion of a causal compatibility inequality without providing a means for deriving/computing them.
 This section aims to delineate algorithms and methods that can be used to derive causal compatibility inequalities for generic causal inference problems.
-Recalling the definition of causal compatibility presented in \cref{sec:compatibility}, a marginal model $\prob^{\mscenario}$ is compatible with a causal structure $\graph = \br{\nodes, \edges}$ if it can be recovered from a series of operations.
+Recalling the definition of causal compatibility presented in \cref{sec:causal_compatibility}, a marginal model $\prob^{\mscenario}$ is compatible with a causal structure $\graph = \br{\nodes, \edges}$ if it can be recovered from a series of operations.
 First choose a set of causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ and then construct a joint distribution $\prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}]$ over all nodes $\nodes$ (this step is \cref{eq:local_markov_property_operation}).
@@
 After doing, it becomes possible to discuss existing methods for deriving constraints on the set of contextual marginal models.
-
-    \subsubsection{The Marginal Problem as a Linear Program}
-    \label{sec:marginal_linear}\label{sec:linear_programs}
 
@@
 
-    \subsection{Causal Inflations}
+    \subsection{Inflation Technique}
+    \label{sec:deriving_inequalities}
+    \label{sec:inflation_technique_main_summary}
     The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a marginal model $\prob^{\mscenario}$ is compatible or incompatible with a given causal structure $\graph$.
@@
     We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index.
-Equipped with the common graph-theoretic terminology and notation of \cref{def:graph_terms}, an inflation can be formally defined as follows:
+Equipped with the common graph-theoretic terminology and notation presented in \cref{sec:causal_compatibility}, an inflation can be formally defined as follows:
+
+    \todo[TC]{Incorporate these definitions into the discussion}
+    \begin{definition}
+        An \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$.
+        An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
+        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
+    \end{definition}
+
     \begin{definition}
@@
 
+    \subsection{Exemplary Inflations of The Triangle Structure}
+    \label{sec:exemplary_inflations_of_the_triangle structure}
+
     \begin{center}
@@
     \end{center}
+
+    \subsection{Deriving Symmetric Causal Compatibility Inequalities}
+    \label{sec:symmetric_inequalities}
+
+    Quite surprisingly, it is possible to derive causal compatibility inequalities for the Triangle structure that are symmetric under the exchange of parties.
+This is done by grouping marginal events $m \in \Events{\mscenario}$ into orbits under the action of party exchange.
+Even more interestingly, these inequalities are violated by the Fritz distribution.
+This comes as a surprise because the Fritz distribution is \text{not} invariant under the exchange of parties; in fact the Fritz distribution is noticeably biased toward $C$.
+
+    In general, exploiting symmetries of the marginal scenario is useful for a few distinct reasons.
+First, \citet{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:deriving_inequalities}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
+They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that non-trivial inequalities can be recovered from facets of a symmetric polytope.
+Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
+The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.
+
+    To demonstrate what types of symmetries we have in mind, we present the following example:
+    \begin{example}
+        \label[example]{ex:symmetries}
+        First consider the marginal scenario $\mscenario = \bc{\bc{A, B, C}, \bc{C, D}, \bc{A, D}}$ where each variable in $\jointvar = \bc{A,B,C,D}$ has binary outcomes: $O_A = O_B = O_C = O_D = \bc{0,1}$.
+Moreover, let $I_{\mscenario}$ be the following compatibility inequality over $\mscenario$ for some causal structure $\graph$,
+        \[ I_{\mscenario} = \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}  \]
+        Intuitively, the compatibility of $\probvec^{\mscenario}$ is \textit{independent} of the how one labels outcomes.
+Suppose $\varphi : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ is a permutation of the variables $\jointvar$.
+Intuitively $\varphi$ acts on $I_{\mscenario}$ in the following way,
+        \begin{align*}
+        \varphi\bs{I_{\mscenario}} &= \bc{\prob[\varphi\bs{abc}][010] \leq \prob[\varphi\bs{cd}][00] + \prob[\varphi\bs{ad}][01]} \\
+        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
+        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
+        \end{align*}
+        In general (as in this example), permutations over all variables can modify the marginal scenario $\varphi\bs{\mscenario} \neq \mscenario$; in general we write $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
+Although $\varphi\bs{I_{\mscenario}}$ is still a valid causal compatibility inequality, in constrains marginal models of a different marginal scenario $\varphi\bs{\mscenario}$ and are in general of no interest.
+    \end{example}
+
+    Following the observations of \cref{ex:symmetries}, it is always possible to permute the random variables in a marginal scenario to produce new and valid inequalities.
+The symmetry group over a the complete set of variables $\jointvar$ is simply the \text{permutation group}\footnote{The permutation group over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} $\Perm{\jointvar}$.
+As was noted in \cref{ex:symmetries}, some permutations $\varphi \in \Perm{\jointvar}$ have the undesired possibility of transforming $\mscenario$ into a different marginal scenario.
+    \[ \varphi\bs{\mscenario} \defined \bc{\varphi\bs{V_1}, \ldots, \varphi\bs{V_k}} \neq \mscenario \]
+    This means that there could exist $V \in \mscenario$ such that $\varphi\bs{V} \not \in \mscenario$.
+Permutations $\varphi$ retaining this property are unable to generate compatibility inequalities over the same marginal scenario.
+Therefore, the desired set of symmetries is a subgroup that takes $\mscenario$ to $\mscenario$.
+
+    \begin{definition}
+        The \term{variable permutation group} $\gp$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario.
+        \[ \Phi\br{\mscenario} \defined \bc{\varphi \in \Perm{\jointvar} \mid \forall V \in \mscenario : \varphi\bs{V} \in \mscenario} \]
+    \end{definition}
+
+    Obtaining the variable permutation group $\gp\br{\mscenario}$ is a simple application of a group stabilizer algorithm.
+After obtaining $\gp\br{\mscenario}$, one can take known compatibility inequalities $I_{\mscenario}$ can create a whole family of inequalities $\bc{\varphi\bs{I_{\mscenario}} \mid \varphi \in \gp\br{\mscenario}}$ that are valid for the same marginal scenario $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}} = \varphi\bs{I}_{\mscenario}$.
+
+    Although very useful for reducing computational complexity~\cite{Bancal_2010}, we divert our attention to finding \textit{symmetric} inequalities themselves.
+    \[ \forall \varphi \in \gp\br{\mscenario} :  \varphi\bs{I_{\mscenario}} = I_{\mscenario} \]
+    In order to do this, we must first define how elements $\varphi \in \gp$ act on marginal events.
+The action of $\varphi \in \gp$ on any outcome $f \in \Events{V}$ (denoted $\geo\bs{f}$) is defined as,
+    \[ \forall v \in \Dom{\varphi\bs{f}} : \br{\varphi\bs{f}}\br{v} \defined f\br{\varphi^{-1}\bs{v}} \eq \label{eq:act_on_variable}\]
+    \Cref{eq:act_on_variable} is nothing more than a mathematical definition for the intuitive action used in \cref{ex:symmetries}.
+    Through repeated action of $\varphi \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define \term{group orbits} of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$.
+    \begin{align*}
+        \Orb[\gp]{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \gp} \\
+        \Orb[\gp]{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \gp}
+    \end{align*}
+    Using these group orbits, it is possible to contract the incidence matrix $M$ of a marginal scenario into a symmetrized version.
+
+    \begin{definition}
+        The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and the variable permutation group $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
+Each row of $M_{\gp}$ corresponds to a marginal orbit $\Orb[\gp]{m}$.
+Analogously each column of $M_{\gp}$ corresponds to a joint orbit $\Orb[\gp]{j}$.
+The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
+        \[ \br{M_{\gp}}_{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M_{m',j'} \]
+    \end{definition}
+    It is possible to analogously define a \term{symmetric joint distribution vector} $\probvec^{\jointvar}_{\Phi}$ indexed by $\Orb[\gp]{j}$,
+    \[ \br{\probvec^{\jointvar}_{\Phi}}_{\Orb[\gp]{j}} = \sum_{j' \in \Orb[\gp]{j}} \probvec^{\jointvar}_{j} \]
+    And a \term{symmetric marginal distribution vector} $\probvec^{\mscenario}_{\Phi}$ indexed by $\Orb[\gp]{m}$,
+    \[ \br{\probvec^{\mscenario}_{\Phi}}_{\Orb[\gp]{m}} = \sum_{m' \in \Orb[\gp]{m}} \probvec^{\mscenario}_{m} \]
+    Which altogether define a new, \term{symmetric marginal problem},
+    \[ \probvec^{\mscenario}_{\Phi} = M_{\gp} \cdot \probvec^{\jointvar}_{\Phi} \]
+    The symmetric marginal problem can be solved using the same computational methods discussed in \cref{sec:deriving_inequalities} and will produce symmetric inequalities.
+
+    In the context of the Inflation technique, a variable symmetry $\Phi\br{\mscenario'}$ over an inflated marginal scenario $\mscenario'$ does not always correspond to a variable symmetry under deflation $\Phi\br{\mscenario}$.
+In order to derive deflated inequalities that are symmetric under an exchange of parties, it is required that $\Phi\br{\mscenario'} \sim \Phi\br{\mscenario}$ are equivalent up to copy-index.
+
+    For the Triangle structure in particular, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
+For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\PreInj[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
+    \begin{equation*}
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_1 \\
+    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_2 \\
+    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_3 \\
+    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
+    \end{aligned}
+    \quad
+    \begin{aligned}[c]
+    &\hspace{1mm}\varphi_4 \\
+    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
+    \end{aligned}
+    \end{equation*}
+    % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
+    %  (0, 2, 1, 3, 8, 10, 9, 11, 4, 6, 5, 7),
+    %  (8, 9, 10, 11, 0, 1, 2, 3, 4, 5, 6, 7),
+    %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
+    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
+Moreover they stabilize the pre-injectable sets of \cref{eq:pre_injectable_triangle_structure_web}.
+Importantly,
+    \[ \gp\br{\PreInj[\graph]{\graph'}} \sim \Perm{A,B,C} \]
+    To see this, $\varphi_1$ and $\varphi_4$ become the identity element $\ident$ in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
+
+    The symmetric incidence matrix $M_{\Phi}$ for the Web inflation is considerably smaller than $M$.
+The number of rows of $M_{\Phi}$ is a number of distinct orbits $\Orb[\Phi]{m}$ in $\Events{\mscenario}$.
+Likewise the number of columns is the number of distinct orbits $\Orb[\Phi]{j}$ in $\Events{\jointvar}$.
+For the Web inflation in particular, $M_{\Phi}$ is $450 \times 358,120$.
+Using the symmetric incidence matrix and linear programing methods, an infeasibility certificate was found that is capable of witnessing the Fritz distribution.
+This inequality is reproduced in \cref{sec:symmetic_web_inequality}.
 
@@
     \comment[TC]{keep, remove, or distribute into body where relevant?}
-    \subsection{Graph Theory}
-    \label{sec:graph_theory}
-    \begin{definition}
-        \label{def:graph}
-        A \term{graph} $\graph$ is an ordered tuple $\br{\nodes, \edges}$ of \textit{nodes} and \textit{edges} respectively where the nodes have the capacity to represent any object while the edges are defined as \textit{pairs} of nodes $\edges \subseteq \nodes \times \nodes$.
-A \term{directed graph} $\graph$ is a graph where each edge $e \in \edges$ is assigned an order or \term{direction} $e = \bc{n \to n'}$.
-    \end{definition}
-
-    \begin{definition}
-        \label{def:graph_terms}
-        The following definitions are common language in directed graph theory. Let $n, m \in \nodes$ be example nodes of the graph $\graph$.
-        \begin{itemize}
-            \item The \term{parents of a node}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
-            \item The \term{children of a node}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
-            \item The \term{ancestry of a node}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$ where $\Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}}$ and $\Pa[\graph][0]{n} = n$
-            \item The \term{descendants of a node}:  $\De[\graph]{n} \defined \bigcup_{i\in\mathbb{N}} \Ch[\graph][i]{n}$ where $\Ch[\graph][i]{n} \defined \Ch[\graph]{\Ch[\graph][i-1]{n}}$ and $\Ch[\graph][1]{n} = \Ch[\graph]{n}$
-        \end{itemize}
-        All of these terms can be generalized to sets of nodes $N \subseteq \nodes$ through union over the elements,
-        \begin{itemize}
-            \item The \term{parents of a node set}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
-            \item The \term{children of a node set}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
-            \item The \term{ancestry of a node set}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
-        \end{itemize}
-    \end{definition}
-
-    \begin{definition}
-        An \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$.
-        \[ \Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to n'} \mid n, n' \in N, e \in \edges}} \]
-        An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
-        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
-    \end{definition}
-
-    \begin{definition}
-        \label{def:dag}
-        A \term{directed acyclic graph} or \term{DAG} $\graph = \br{\nodes, \edges}$ is an directed graph with the additional property that no node $n$ is in its set of \term{ancestors}.
-        \[ \forall n \in \nodes : n \notin \bigcup_{i\in\mathbb{N}} \Pa[\graph][i]{n}\]
-        It is critical to note the difference in language between \textit{ancestors} from \textit{ancestry}.
-The ancestry $\An[\graph]{n}$ of a node $n$ is defined using \textit{whole} numbers $\mathbb{W}$.
-In contrast, the ancestors of a node are defined similarly with \textit{natural} numbers $\mathbb{N}$.
-    \end{definition}
 

### 2017-04-06 documents/TriangleScenarioArXiv/ts.tex
noise plots have been removed

@@
 
-    In the Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U} = \s{U}_{ABC}$ (see \cref{fig:uniform_distribution})
-    \[ \s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}  \]
+    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$ (see \cref{fig:uniform_distribution}).
 Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible.
@@
     \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
-    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution as $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$.
+    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$.
 For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.
-As a standard, let $I\br{\prob} < 0$ represent violations while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturations of the inequality).
-
+In order to compare different inequalities simultaneously, let $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
 To analyze noise, $4$ inequalities where chosen.
@@
 Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{sec:web_inequality}.
-
-    \begin{figure}
-    \begin{subfigure}[b]{.48\linewidth}
-    {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}}
-    \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
-    \end{subfigure}
-    \begin{subfigure}[b]{.48\linewidth}
-    {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}}
-    \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
-    \end{subfigure}
-    \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
-    \end{figure}
-
-    The results of our experiments are plotted in \cref{fig:master_noise}.
+Our tests suggest that inequality $I_1$ (\cref{sec:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
+The associated distribution $\s N_{0.085}\br{\prob[\fritz]}$ is plotted in \cref{fig:noisy_fritz}.
+Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I_1$.
+
+    % Given that $I_0, I_1, I_2, I_3$ are far from a representative inequalities and are likely not facets of any inflated marginal polytope, it is save to say that this is possible.
+
+    % \begin{figure}
+    % \begin{subfigure}[b]{.48\linewidth}
+    % {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}}
+    % \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{.48\linewidth}
+    % {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}}
+    % \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
+    % \end{subfigure}
+    % \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
+    % \end{figure}
+
+    % The results of our experiments are plotted in \cref{fig:master_noise}.
 \Cref{fig:noise} illustrates that each curve $I\br{\s{N}_{\vep}\br{\prob[\fritz]}}$ as a function of $\vep$ is monotonically increasing as expected; the more noise added to the probability distribution, the more classical it becomes.
 \Cref{fig:noise_zoomed} is the same plot as \cref{fig:noise} zoomed onto the interval $\vep \in \bs{0, 0.12}$.
-These tests suggest that inequality $I_1$ (\cref{sec:web_inequality}), when compared against all others is most robust to noise.
-
-    Overall, this noise model demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
-The associated distribution $\s N_{0.085}\br{\prob[\fritz]}$ is plotted in \cref{fig:noisy_fritz}.
-There remains the possibility that another inequality will be able to withstand a larger degree of noise that $I_1$.
-Given that $I_0, I_1, I_2, I_3$ are far from a representative inequalities and are likely not facets of any inflated marginal polytope, it is save to say that this is possible.
 

### 2017-04-06 documents/TriangleScenarioArXiv/ts.tex
removed the appendix for parameterizations, now included in the main body and much shorter

@@
     % \setlength{\parskip}{1em}
-    \clearpage
 
@@
 
-    \term{Fritz's Problem}: Find an example of non-classical quantum correlations in the Triangle structure together with a proof of its non-classicality which does not hinge on Bell’s theorem.\footnote{In the way Fritz defines, \textit{non-classical} correlations are the class of \textit{incompatible} correlations.}
+    \term{Fritz's Problem}: Find an example of non-classical quantum correlations in the Triangle structure together with a proof of its non-classicality which does not hinge on Bell’s theorem.
 
@@
 
-    \section{Noisy Distributions \& Numerical Optimizations}
+    \section{Numerical Optimizations \& Noisy Distributions}
     \label{sec:violations_noise}
@@
 In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities.
+In order to compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ so $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
+For the subsequent analysis, $4$ inequalities where chosen.
+First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}.
+The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{sec:web_inequality} while $I_3$ is the symmetric inequality in \cref{sec:symmetic_web_inequality}.
+Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{sec:web_inequality}.
 
@@
 For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.
-In order to compare different inequalities simultaneously, let $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
-To analyze noise, $4$ inequalities where chosen.
-First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}.
-The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{sec:web_inequality} while $I_3$ is the symmetric inequality in \cref{sec:symmetic_web_inequality}.
-Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{sec:web_inequality}.
 Our tests suggest that inequality $I_1$ (\cref{sec:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
-The associated distribution $\s N_{0.085}\br{\prob[\fritz]}$ is plotted in \cref{fig:noisy_fritz}.
+The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}.
 Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I_1$.
@@
     Causal compatibility inequalities act as a \textit{measure} of non-classicality.
-If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$\footnote{Remember that larger violations are more negative when the inequalities are written in the proposed canonical form.} Nonetheless, this statement comes from several caveats.
+If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$.
+However, this statement is accompanied by a few caveats.
 First, it is possible (and frequently the case) for ${I\br{\prob[1]}} < I\br{\prob[2]}$ to hold for one inequality $I$ but have ${\ti I\br{\prob[2]}} < \ti I\br{\prob[1]}$ hold for another inequality $\ti I$.
@@
 Second, not all inequalities $I$ are \textit{good} measures of non-classicality.
-In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality.
-This is because the facets form a necessary and sufficient set with all other inequalities following from positive mixtures of the facets.
+In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality because the facets form a necessary and sufficient of constraints with all other inequalities following from positive mixtures.
 However, good measures of incompatibility are less understood in the Triangle structure where the space of classical correlations is non-convex.
-At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility (especially because they are curated toward the Fritz distribution).
+At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility simply because they have be curated toward the Fritz distribution.
 Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure.
 
-    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}.
+    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be expressed as follows:
+    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
+    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately.
+In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
+In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
+Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states.
+Qubit states are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix.
+Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
+First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure.
+Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$.
+Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
+    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]
+
+    Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, a single technique by \citet{Spengler_2010_Unitary} was found to be most computationally suitable for our purposes.
+\Citet{Spengler_2010_Unitary} demonstrated that all $d\times d$ unitary matrices $U$ can be parameterized without degeneracy as follows:
+    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
+    Where the real valued parameters $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ have periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
+Moreover, $P_l$ are one-dimensional projective operators $P_l = \ket{l}\bra{l}$ and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices $\sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m}$ where $1 \leq m < n \leq d$.
+This parameterization has the useful feature that each of the real-valued parameters $\la_{n,m}$ a direct and intuitive physical affect on each element of a computational basis $\bc{\ket{1}, \ldots, \ket{d}}$.
+Explicitly, $\exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$.
+Analogously, $\exp\br{i P_n \lambda_{n,m}}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $\exp\br{iP_l \lambda_{l,l}}$ fixes the global phase of $\ket{l}$.
+Finally, although not explicitly mentioned in~\cite{Spengler_2010_Unitary}, it is possible to remove the reliance on the computationally expensive matrix exponential operations in \cref{eq:spengler_unitary}~\cite{Moler_2003}.
+
+    By parameterizing unitary matrices, it becomes possible to parameterize $d$-dimensional density matrices and $d$-element PVMs by recognizing that any orthonormal basis $\bc{\ket{\psi_j}}$ (where $1 \leq j \leq d$) can be transformed into the computational basis $\bc{\ket{j}}$ by a unitary transformation $U$, i.e.
+$U \ket{\psi_j} = \ket{j}$.
+First consider a $d$-element PVM $M = \bc{\ket{m_j}\bra{m_j} \mid 1 \leq j \leq d}$.
+Since $\bc{\ket{m_j}}$ forms an orthonormal basis, one can parameterize $M$ by writing $M = \bc{U^{\dagger}\ket{j}\bra{j}U \mid 1 \leq j \leq d}$ and parameterizing $U$ using \cref{eq:spengler_unitary}.
+This method was inspired by the measurement seeding method for iterative optimization used by \citet{Pal_2010}.
+Analogously, this argument can be extended to full-rank $d$-dimensional density matrices $\rho$ by performing a spectral decomposition $\rho = \sum_{j=1}^{d} p_j \ket{p_j} \bra{p_j}$ into eigenvalues $\bc{p_j}$ and eigenstates $\bc{\ket{p_j}}$.
+Since $\Tr\bc{\rho} = \sum_{j = 1}^{d} p_j = 1$ the eigenvalues of $\rho$ are parameterized without degeneracy using a tuple of $d-1$ real-valued parameters with periodicity $\bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}.
+Additionally, since $\rho$ is Hermitian, the eigenstates $\bc{\ket{p_j}}$ form an orthonormal basis and therefore the eigenstates are analogously parameterized using \cref{eq:spengler_unitary}: $\rho = \sum_{j=1}^{d} p_j U^{\dagger} \ket{j} \bra{j} U$.
+For our purposes, we have set $d = 4$ and fixed $\la_{l, l} = 0$ for $1 \leq l \leq d$ in \cref{eq:spengler_unitary} because the global phase contributions are irrelevant in \cref{eq:quantum_model_triangle_pvms}.
+    \[  \]
+    % \Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}.
+Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.
+
+    % the a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}.
 Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:quantum_model_triangle} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$.
@@
 
-    Finding larger violations to compatibility inequalities is nothing more that a numerical optimization (specifically minimization) of $f\br{\la}$.
     Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
@@
     \end{figure}
-    In search of new, incompatible, quantum distributions that can be realized on the Triangle structure, numerical optimizations over the the space of quantum-accessible probability distributions are performed.
-To do so, we are interested in a parameterization all distributions that can be expressed as follows:
-    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
-    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately\footnote{$\netperm$ is discussed more thoroughly in \cref{sec:perm_matrix}.}.
-
-    In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
-The states $\rho$ are taken to be bipartite \textit{qubit} states acting on $\s{H}^{2} \otimes \s{H}^{2}$.
-This is motivated by \cref{sec:fritz_distribution} in which the Fritz distribution only requires qubit states.
-In generality, one could consider $n$-dimensional states acting on $\s{H}^{n} \otimes \s{H}^{n}$.
-However, in such cases the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ then acts on $\br{\Hilb^{n}}^{\otimes 6}$ requiring a $n^6 \times n^6$ matrix with $n^{12}$ entries.
-Therefore, $n = 2$ is far more computationally feasible than $n > 2$.
-Additionally, restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
-First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure.
-Second, generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, however a valid, unbiased parameterization was not found for $k > 2$.
-Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as follows:
-    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]
-
-    In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
-Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, although a single technique is presented in \cref{sec:unitary_group} that was found to be most computationally suitable for our purposes.
-\Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}.
-Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.
 
@@
 
-    \clearpage
     \appendix
@@
 
-    \clearpage
-    \section{Quantum Parameterization of Triangle Structure}
-    \label{sec:param_quantum_dist}
-    \subsection{Unitary Group}
-    \label{sec:unitary_group}
-    To facilitate the parameterization of quantum states states and PVMs, a parameterization of the unitary group of dimension $d$ (denoted $\s{U}\br{d}$) by Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} is introduced.
+    % \section{Quantum Parameterization of Triangle Structure}
+    % \label{sec:param_quantum_dist}
+    % \subsection{Unitary Group}
+    % \label{sec:unitary_group}
+    % To facilitate the parameterization of quantum states states and PVMs, a parameterization of the unitary group of dimension $d$ (denoted $\s{U}\br{d}$) by Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} is introduced.
 Discussions of its application to states and measurements are deferred to \cref{sec:states} and \cref{sec:measurements} respectively.
 
-    In Ref.~\cite{Spengler_2010_Unitary}, Spengler \textit{et al.} proved that all unitaries $U \in \s{U}\br{d}$ can be parameterized without degeneracy as follows:
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
-    Where $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ form a $d \times d$ matrix of real-valued parameters with periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
-    \[ \la = \begin{pmatrix}
-        \la_{1,1} & \cdots & \la_{1, d} \\
-        \vdots & \ddots & \vdots \\
-        \la_{d,1} & \cdots & \la_{d, d} \\
-    \end{pmatrix} \]
-    And where $P_l$ are one-dimensional projective operators,
-    \[ P_l = \ket{l}\bra{l} \qquad 1 \leq l \leq d \eq \label{eq:projective_operator} \]
-    and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices,
-    \[ \sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m} \qquad 1 \leq m < n \leq d\]
-    The SSH parameterization (\cref{eq:spengler_unitary}) is unique in that each of the real-valued parameters $\la_{n,m}$ has physical significance.
+    % In Ref.~\cite{Spengler_2010_Unitary}, Spengler \textit{et al.} proved that all unitaries $U \in \s{U}\br{d}$ can be parameterized without degeneracy as follows:
+    % \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary_old} \]
+    % Where $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ form a $d \times d$ matrix of real-valued parameters with periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
+    % \[ \la = \begin{pmatrix}
+    %     \la_{1,1} & \cdots & \la_{1, d} \\
+    %     \vdots & \ddots & \vdots \\
+    %     \la_{d,1} & \cdots & \la_{d, d} \\
+    % \end{pmatrix} \]
+    % And where $P_l$ are one-dimensional projective operators,
+    % \[ P_l = \ket{l}\bra{l} \qquad 1 \leq l \leq d \eq \label{eq:projective_operator} \]
+    % and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices,
+    % \[ \sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m} \qquad 1 \leq m < n \leq d\]
+    % The SSH parameterization (\cref{eq:spengler_unitary}) is unique in that each of the real-valued parameters $\la_{n,m}$ has physical significance.
 For the sake of reference, let us label the matrix exponential terms in \cref{eq:spengler_unitary} in a manner that corresponds to their affect on an orthonormal basis $\bc{\ket{1}, \ldots, \ket{d}}$.
-    \begin{align*}
-    \begin{split}
-        GP_l &= \exp\br{iP_l \lambda_{l,l}} \\
-        RP_{n,m} &= \exp\br{i P_n \lambda_{n,m}} \\
-        R_{m,n} &= \exp\br{i \si_{m,n} \lambda_{m,n}}
-    \end{split} \eq \label{eq:exp_terms}
-    \end{align*}
-    For example, $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$.
+    % \begin{align*}
+    % \begin{split}
+    %     GP_l &= \exp\br{iP_l \lambda_{l,l}} \\
+    %     RP_{n,m} &= \exp\br{i P_n \lambda_{n,m}} \\
+    %     R_{m,n} &= \exp\br{i \si_{m,n} \lambda_{m,n}}
+    % \end{split} \eq \label{eq:exp_terms}
+    % \end{align*}
+    % For example, $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$.
 Analogously, $RP_{n,m}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $GP_l$ fixes the global phase of $\ket{l}$.
@@
 It is convenient to denote the set of all unitaries up to global phase considerations as $\ti {\s{U}}\br{d}$ and express $\ti {U} \in \ti {\s{U}}\br{d}$ using $d\br{d-1}$ real-valued parameters:
-    \[ \ti U = \prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}} \eq \label{eq:spengler_unitary_gp} \]
-    Another attractive feature of the SSH parameterization not mentioned in~\cite{Spengler_2010_Unitary} is that \cref{eq:spengler_unitary}, and thus \cref{eq:spengler_unitary_gp}, can be implemented in a computationally efficient manner.
+    % \[ \ti U = \prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}} \eq \label{eq:spengler_unitary_gp} \]
+    % Another attractive feature of the SSH parameterization not mentioned in~\cite{Spengler_2010_Unitary} is that \cref{eq:spengler_unitary}, and thus \cref{eq:spengler_unitary_gp}, can be implemented in a computationally efficient manner.
 This is discussed in \cref{sec:comp_spengler}.
-    \subsection{Measurements}
-    \label{sec:measurements}
-    For each measurement set $M$ in \cref{eq:quantum_model_triangle}, we consider a $d$-element projective-valued measure (PVM) $M = \bc{M_1, \ldots, M_d}$ satisfying a number of familiar constraints:
-    \begin{gather*}
-    \forall \ket{\phi} \in \Hilb^d: \bra{\phi} M_i \ket{\phi} \geq 0 \qquad \sum_{i=1}^{d} M_i = \ident_{d} \\
-    M_i = \ket{m_i}\bra{m_i} \qquad M_i M_j = \de_{ij} M_i
-    \end{gather*}
-    Therefore, parameterizing $M$ corresponds to parameterizing the set of all orthonormal basis $\bc{\ket{\psi_1}, \ldots, \ket{\psi_d}}$ of $\Hilb^d$.
-    First note that any such basis can be transformed into the computational basis $\bc{\ket{1}, \ldots, \ket{d}}$ by a unitary denoted $U^{-1} \in \mathcal{U}\br{d}$.
-    \[ \forall i : U^{-1} \ket{\psi_i} = \ket{i} \eq \label{eq:unitary_transform}\]
-    With this observation, all that is required is to parameterize the set of all unitaries $U \in \mathcal{U}\br{d}$.
+    % \subsection{Measurements}
+    % \label{sec:measurements}
+    % For each measurement set $M$ in \cref{eq:quantum_model_triangle}, we consider a $d$-element projective-valued measure (PVM) $M = \bc{M_1, \ldots, M_d}$ satisfying a number of familiar constraints:
+    % \begin{gather*}
+    % \forall \ket{\phi} \in \Hilb^d: \bra{\phi} M_i \ket{\phi} \geq 0 \qquad \sum_{i=1}^{d} M_i = \ident_{d} \\
+    % M_i = \ket{m_i}\bra{m_i} \qquad M_i M_j = \de_{ij} M_i
+    % \end{gather*}
+    % Therefore, parameterizing $M$ corresponds to parameterizing the set of all orthonormal basis $\bc{\ket{\psi_1}, \ldots, \ket{\psi_d}}$ of $\Hilb^d$.
+    % First note that any such basis can be transformed into the computational basis $\bc{\ket{1}, \ldots, \ket{d}}$ by a unitary denoted $U^{-1} \in \mathcal{U}\br{d}$.
+    % \[ \forall i : U^{-1} \ket{\psi_i} = \ket{i} \eq \label{eq:unitary_transform}\]
+    % With this observation, all that is required is to parameterize the set of all unitaries $U \in \mathcal{U}\br{d}$.
 Specifically, the projective property each $M_i \in M$ means that the global phase of $U$ is completely arbitrary; one only needs to consider parameterizing unitaries up to global phase using \cref{eq:spengler_unitary_gp}.
-    \[ M = \bc{\ti U \ket{i} \bra{i} \ti U^{\dagger} \mid i \in \bc{1, \ldots, d}} \]
-    For the purposes discussed in \cref{sec:param_quantum_dist}, only $d = 4$ outcome measurements are utilized and therefore requiring $4\br{4 - 1} = 12$ real-valued parameters.
+    % \[ M = \bc{\ti U \ket{i} \bra{i} \ti U^{\dagger} \mid i \in \bc{1, \ldots, d}} \]
+    % For the purposes discussed in \cref{sec:param_quantum_dist}, only $d = 4$ outcome measurements are utilized and therefore requiring $4\br{4 - 1} = 12$ real-valued parameters.
 This method was inspired by the measurement seeding method for iterative optimization used by \citet{Pal_2010} .
-    \subsection{States}
-    \label{sec:states}
-
-    Each state $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ of \cref{eq:quantum_model_triangle} is modeled as a two-qubit density matrices acting on $\Hilb^2 \otimes \Hilb^2$.
+    % \subsection{States}
+    % \label{sec:states}
+
+    % Each state $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ of \cref{eq:quantum_model_triangle} is modeled as a two-qubit density matrices acting on $\Hilb^2 \otimes \Hilb^2$.
 The space of all such states corresponds to the space of all $4\times 4$ positive semi-definite hermitian matrices with unitary trace.
-    \[ \forall \ket{\phi} \in \Hilb^d: \bra{\phi} \rho \ket{\phi} \geq 0 \qquad \rho^{\dagger} = \rho \qquad \Tr\br{\rho} = 1 \eq \label{eq:density_matrix}\]
-    Although is common to parameterize all such matrices using a Cholesky decomposition~\cite{Grasmair_2014}, we make use of the non-degenerate SHH parameterization~\cite{Spengler_2010_Unitary} and the spectral decomposition of $\rho$.
+    % \[ \forall \ket{\phi} \in \Hilb^d: \bra{\phi} \rho \ket{\phi} \geq 0 \qquad \rho^{\dagger} = \rho \qquad \Tr\br{\rho} = 1 \eq \label{eq:density_matrix}\]
+    % Although is common to parameterize all such matrices using a Cholesky decomposition~\cite{Grasmair_2014}, we make use of the non-degenerate SHH parameterization~\cite{Spengler_2010_Unitary} and the spectral decomposition of $\rho$.
 Retaining full generality, consider full-rank density matrices:
-    \[ \rho = \sum_{i=1}^{d} p_i \ket{\psi_i}\bra{\psi_i} \qquad \sum_{i=1}^{d} p_i = 1, p_i \geq 0 \eq \label{eq:param_density} \]
-    Where $\bc{p_i}$ are the eigenvalues of $\rho$ and $\bc{\ket{\psi_i}}$ are its eigenstates.
+    % \[ \rho = \sum_{i=1}^{d} p_i \ket{\psi_i}\bra{\psi_i} \qquad \sum_{i=1}^{d} p_i = 1, p_i \geq 0 \eq \label{eq:param_density} \]
+    % Where $\bc{p_i}$ are the eigenvalues of $\rho$ and $\bc{\ket{\psi_i}}$ are its eigenstates.
 It is here that one recognizes the reapplication of \cref{eq:unitary_transform}: any orthonormal basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into a computational basis $\bc{\ket{i}}$ by a unitary transformation $U \in \mathcal{U}\br{d}$ such that $\ket{\psi_i} = U\ket{i}$.
 Analogous to the projective measurements considered in \cref{sec:measurements}, the global phase contributions are redundant.
-    \[ \rho = \sum_{i=1}^{d} p_i \ti U\ket{i}\bra{i} \ti U^{\dagger} \]
-    Parameterizing the eigenvalues requires $d - 1$ real-valued parameters due to the trace constraint of \cref{eq:density_matrix}.
+    % \[ \rho = \sum_{i=1}^{d} p_i \ti U\ket{i}\bra{i} \ti U^{\dagger} \]
+    % Parameterizing the eigenvalues requires $d - 1$ real-valued parameters due to the trace constraint of \cref{eq:density_matrix}.
 The eigenvalues are parameterized without degeneracy using a tuple of $d-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{d-1}}, \lambda_i \in \bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}:
-    \begin{align*}
-    \eq \label{eq:convex_param}
-    \begin{split}
-        p_n &= \prod_{i=1}^{n-1} \sin^2 \lambda_i \\
-        p_j &= \cos^2 \lambda_j \prod_{i=1}^{j-1} \sin^2 \lambda_i \quad \forall j \in 1, \ldots, n - 1
-    \end{split}
-    \end{align*}
-
-    Furthermore due to the periodicity of the parameter space $\bc{\lambda}$, \cref{eq:convex_param} can be used for either constrained or unconstrained optimization problems.
+    % \begin{align*}
+    % \eq \label{eq:convex_param}
+    % \begin{split}
+    %     p_n &= \prod_{i=1}^{n-1} \sin^2 \lambda_i \\
+    %     p_j &= \cos^2 \lambda_j \prod_{i=1}^{j-1} \sin^2 \lambda_i \quad \forall j \in 1, \ldots, n - 1
+    % \end{split}
+    % \end{align*}
+
+    % Furthermore due to the periodicity of the parameter space $\bc{\lambda}$, \cref{eq:convex_param} can be used for either constrained or unconstrained optimization problems.
 For continuity reasons, unconstrained optimizations are performed whenever possible.
@@
 
-    Although non-degenerate, \cref{eq:convex_param} suffers from a lack of uniformity; a randomly sampled vector of parameters $\bc{\lambda}$ \textit{does not} translate to a randomly sampled set of eigenvalues $\bc{p_i}$.
+    % Although non-degenerate, \cref{eq:convex_param} suffers from a lack of uniformity; a randomly sampled vector of parameters $\bc{\lambda}$ \textit{does not} translate to a randomly sampled set of eigenvalues $\bc{p_i}$.
 Another, albeit degenerate, parameterization of $\bc{p_i}$ involves beginning with $d$ real parameters $\lambda = \br{\lambda_1, \ldots, \lambda_d}$, then forcing normalization by dividing each parameter $\la_i$ by the their sum.\footnote{Strictly speaking, \cref{eq:uniform_param} \textit{also} suffers from non-uniformity; being biased toward eigenvalues that have similar values to each other.}.
-    \[ p_j = \f{\abs{\lambda_j}}{\sum_{i=1}^{n} \abs{\lambda_i}} \quad \forall j \in 1, \ldots, n \eq \label{eq:uniform_param} \]
-    For various optimization tasks sensitive to initial conditions outlined \cref{sec:optimizations}, the latter parameterization of \cref{eq:uniform_param} generally performed better than the former \cref{eq:convex_param}.
-    \subsection{Permutation Matrix}
-    \label{sec:perm_matrix}
-    \begin{figure}
-        \centering
-        \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
-        \caption{The permutation matrix $\netperm$ acting on $\br{\Hilb^2}^{\otimes 6}$ for the Triangle structure. Black entries represents a value of $1$ and white represents $0$.}
-        \label{fig:perm_mtrx}
-    \end{figure}
-    Finally, we introduce the a permutation matrix $\netperm$ for the Triangle structure.
+    % \[ p_j = \f{\abs{\lambda_j}}{\sum_{i=1}^{n} \abs{\lambda_i}} \quad \forall j \in 1, \ldots, n \eq \label{eq:uniform_param} \]
+    % For various optimization tasks sensitive to initial conditions outlined \cref{sec:optimizations}, the latter parameterization of \cref{eq:uniform_param} generally performed better than the former \cref{eq:convex_param}.
+    % % \subsection{Permutation Matrix}
+    % % \label{sec:perm_matrix}
+    % % \begin{figure}
+    % %     \centering
+    % %     \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
+    % %     \caption{The permutation matrix $\netperm$ acting on $\br{\Hilb^2}^{\otimes 6}$ for the Triangle structure. Black entries represents a value of $1$ and white represents $0$.}
+    % %     \label{fig:perm_mtrx}
+    % % \end{figure}
+    % % Finally, we introduce the a permutation matrix $\netperm$ for the Triangle structure.
 For bipartite qubit states, $\netperm$ is the $64\times64$ bit-wise matrix depicted in \cref{fig:perm_mtrx}.
@@
 To illuminate its necessity, consider \cref{eq:quantum_model_triangle} in the absence of $\netperm$.
-    \begin{align*}
-    \prob[\p{ABC}]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{\p{AB}} \otimes \rho_{\p{BC}} \otimes \rho_{\p{CA}}} \br{M^a_{\p{A}}\otimes M^b_{\p{B}} \otimes M^c_{\p{C}}}}\\
-    &= \Tr\bs{\br{\rho_{\p{AB}}M^a_{\p{A}}}\otimes\br{\rho_{\p{BC}}M^b_{\p{B}}}\otimes\br{\rho_{\p{CA}}M^c_{\p{C}}}}\\
-    &= \Tr\br{\rho_{\p{AB}}M^a_{\p{A}}}\Tr\br{\rho_{\p{BC}}M^b_{\p{B}}}\Tr\br{\rho_{\p{CA}}M^c_{\p{C}}}\\
-    &= \prob[\p{A}\mid \rho_{\p{AB}}]\br{a}\prob[\p{B}\mid \rho_{\p{BC}}]\br{b}\prob[\p{C}\mid \rho_{\p{CA}}]\br{c}
-    \end{align*}
-    On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$.
+    % % \begin{align*}
+    % % \prob[\p{ABC}]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{\p{AB}} \otimes \rho_{\p{BC}} \otimes \rho_{\p{CA}}} \br{M^a_{\p{A}}\otimes M^b_{\p{B}} \otimes M^c_{\p{C}}}}\\
+    % % &= \Tr\bs{\br{\rho_{\p{AB}}M^a_{\p{A}}}\otimes\br{\rho_{\p{BC}}M^b_{\p{B}}}\otimes\br{\rho_{\p{CA}}M^c_{\p{C}}}}\\
+    % % &= \Tr\br{\rho_{\p{AB}}M^a_{\p{A}}}\Tr\br{\rho_{\p{BC}}M^b_{\p{B}}}\Tr\br{\rho_{\p{CA}}M^c_{\p{C}}}\\
+    % % &= \prob[\p{A}\mid \rho_{\p{AB}}]\br{a}\prob[\p{B}\mid \rho_{\p{BC}}]\br{b}\prob[\p{C}\mid \rho_{\p{CA}}]\br{c}
+    % % \end{align*}
+    % % On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$.
 This is analogously troubling for $B$ and $C$ as well.
@@
 To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
-    \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
-    $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''.
+    % % \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
+    % % $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''.
 It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
-    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
-    \subsection{Computationally Efficient Parameterization of the Unitary Group}
-    \label{sec:comp_spengler}
-
-    If \cref{sec:unitary_group}, the SSH parameterization was introduced as a non-degenerate parameterization of the unitary group $\s{U}\br{d}$.
+    % % \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
+    % \subsection{Computationally Efficient Parameterization of the Unitary Group}
+    % \label{sec:comp_spengler}
+
+    % If \cref{sec:unitary_group}, the SSH parameterization was introduced as a non-degenerate parameterization of the unitary group $\s{U}\br{d}$.
 As presented, the SSH parameterization suffers due to the presence of computationally expensive matrix exponential terms~\cite{Moler_2003}.
@@
 As a first step, recognize the defining property of the projective operators \cref{eq:projective_operator},
-    \[ P_l^k = \br{\ket{l}\bra{l}}^k = \ket{l}\bra{l} = P_l \]
-    This greatly simplifies the global phase terms $GP_l$,
-    \[ GP_l = \exp\br{iP_l \lambda_{l,l}} = \sum_{k=0}^{\inf} \f{\br{iP_l \lambda_{l,l}}^k}{k!} = \ident + \sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}P_l^k = \ident + P_l \bs{\sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}} = \ident + P_l \br{e^{i \lambda_{l,l}} - 1} \eq \label{eq:unitary_GP} \]
-    Analogously for the relative phase terms $RP_{n,m}$,
-    \[ RP_{n,m} = \cdots = \ident + P_n \br{e^{i \lambda_{n,m}} - 1} \eq \label{eq:unitary_RP} \]
-    Finally, the rotation terms $R_{m,n}$ can also be simplified by examining powers of $i \sigma_{n,m}$,
-    \[ R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}} = \sum_{k=0}^{\inf} \f{\br{\ket{m}\bra{n} - \ket{n}\bra{m}}^k \lambda_{m,n}^k}{k!} \]
-    One can verify that the following properties hold,
-    \begin{align*}
-        \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^0 &= \ident \\
-        \forall k \in \N, k \neq 0 : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k} &= \br{-1}^k\br{\ket{m}\bra{m} + \ket{n}\bra{n}} \\
-        \forall k \in \N : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k+1} &= \br{-1}^k\br{\ket{m}\bra{n} - \ket{n}\bra{m}}
-    \end{align*}
-    Revealing the simplified form of $R_{m,n}$,
-    \[ R_{m,n} = \ident + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \sum_{j=1}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j}}{\br{2j}!} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sum_{j=0}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j+1}}{\br{2j+1}!} \]
-    \[ R_{m,n} = \ident + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \eq \label{eq:unitary_R} \]
-    By combining the optimizations of \cref{eq:unitary_GP,eq:unitary_RP,eq:unitary_R} together we arrive at an equivalent form for \cref{eq:spengler_unitary} that is computational more efficient.
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n}RP_{n,m}}} \cdot \bs{\prod_{l=1}^{d} GP_{l}}  \eq \label{eq:spengler_unitary_fast} \]
-
-    \section{Common Terminology \& Notation}
-    \comment[TC]{keep, remove, or distribute into body where relevant?}
-
-    \subsection{Probability Theory}
-    \label{sec:probability_theory}
-
-    \begin{definition}
-        The \term{product distribution} of two disjoint probability distributions $\prob[V]$ and $\prob[W]$ (where $V \cap W = \emptyset$) is denoted as $\prob[V] \times \prob[W]$.
-        \[ \forall s \in \Events{V \cup W} : \br{\prob[V] \times \prob[W]}\br{s} \defined \prob[V][s|_{V}]\cdot\prob[W][s|_{W}] \]
-        A product distribution of $k$ mutually disjoint distributions is defined as,
-        \[ \prod_{i\in\bs{k}} \prob[V_i] \defined \br{\prob[V_1] \times \cdots \times \prob[V_k]} \]
-    \end{definition}
-
-    \begin{definition}
-        The \term{marginalization} of a distribution $\prob[V]$ to a distribution over $W \subseteq V$ is denoted $\sum_{V \setminus W} \prob[V]$ and is defined such that,
-        \[ \forall s \in \Events{W} : \br{\sum_{V \setminus W} \prob[V]}\br{s} \defined \sum_{j \in \Ext[V]{s}} \prob[V][j] \]
-        Where $\Ext[V]{s}$ denotes the set of all events $j \in \Events{V}$ that can be restricted to $s$,
-        \[ \Ext[V]{s} = \bc{j \in \Events{V} \mid s = j|_{\s{D}\br{s}}} \]
-    \end{definition}
-
-    \clearpage
+    % \[ P_l^k = \br{\ket{l}\bra{l}}^k = \ket{l}\bra{l} = P_l \]
+    % This greatly simplifies the global phase terms $GP_l$,
+    % \[ GP_l = \exp\br{iP_l \lambda_{l,l}} = \sum_{k=0}^{\inf} \f{\br{iP_l \lambda_{l,l}}^k}{k!} = \ident + \sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}P_l^k = \ident + P_l \bs{\sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}} = \ident + P_l \br{e^{i \lambda_{l,l}} - 1} \eq \label{eq:unitary_GP} \]
+    % Analogously for the relative phase terms $RP_{n,m}$,
+    % \[ RP_{n,m} = \cdots = \ident + P_n \br{e^{i \lambda_{n,m}} - 1} \eq \label{eq:unitary_RP} \]
+    % Finally, the rotation terms $R_{m,n}$ can also be simplified by examining powers of $i \sigma_{n,m}$,
+    % \[ R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}} = \sum_{k=0}^{\inf} \f{\br{\ket{m}\bra{n} - \ket{n}\bra{m}}^k \lambda_{m,n}^k}{k!} \]
+    % One can verify that the following properties hold,
+    % \begin{align*}
+    %     \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^0 &= \ident \\
+    %     \forall k \in \N, k \neq 0 : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k} &= \br{-1}^k\br{\ket{m}\bra{m} + \ket{n}\bra{n}} \\
+    %     \forall k \in \N : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k+1} &= \br{-1}^k\br{\ket{m}\bra{n} - \ket{n}\bra{m}}
+    % \end{align*}
+    % Revealing the simplified form of $R_{m,n}$,
+    % \[ R_{m,n} = \ident + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \sum_{j=1}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j}}{\br{2j}!} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sum_{j=0}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j+1}}{\br{2j+1}!} \]
+    % \[ R_{m,n} = \ident + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \eq \label{eq:unitary_R} \]
+    % By combining the optimizations of \cref{eq:unitary_GP,eq:unitary_RP,eq:unitary_R} together we arrive at an equivalent form for \cref{eq:spengler_unitary} that is computational more efficient.
+    % \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n}RP_{n,m}}} \cdot \bs{\prod_{l=1}^{d} GP_{l}}  \eq \label{eq:spengler_unitary_fast} \]
+
     \section{Large Triangle Structure Inequalities}
@@
     Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
-    \clearpage
     \subsection{Symmetric Web Inflation Inequality}
@@
 
-    \clearpage
     \setlength{\bibsep}{3pt plus 3pt minus 2pt}

### 2017-04-06 documents/TriangleScenarioArXiv/ts.tex
moved large web inequalities into the main body, only one appendix now

@@
 In an effort to derive inequalities that could lead to potentially new forms of non-classicality, we searched for inequalities that did not admit biased towards the Fritz distribution.
+
+    The following is a causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was derived using the Web inflation of \cref{fig:the_web_inflation}.
+    \begin{equation}
+        \label{sec:web_inequality}
+        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
+    \end{equation}
+    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
+    The following is a symmetric causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was derived using the Web inflation of \cref{fig:the_web_inflation}.
+    \begin{equation}
+        \label{sec:symmetic_web_inequality}
+        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
+    \end{equation}
+    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for the sum over permutations:
+    \[ \bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033) \]
 
@@
 
-    \section{Large Triangle Structure Inequalities}
-    \label{sec:web_inequalities}
-    \subsection{Web Inflation Inequality}
-    \label{sec:web_inequality}
-    The following is a causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
-    \begin{center}
-        \vspace{-0.2in}
-        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
-    \end{center}
-    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
-    \subsection{Symmetric Web Inflation Inequality}
-    \label{sec:symmetic_web_inequality}
-    The following is a symmetric causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
-    \begin{center}
-        \vspace{-0.2in}
-        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
-    \end{center}
-    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for the sum over permutations:
-    \[ \bs{P(113)P(330)}_3 = P(113)P(330) + P(131)P(303) + P(311)P(033) \]
-
     \setlength{\bibsep}{3pt plus 3pt minus 2pt}

### 2017-04-06 documents/TriangleScenarioArXiv/ts.tex
removed the quantum causal model and changed the labels on the large inequalities from sec: to eq:

@@
 The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities.
-A sample of these inequalities are presented in \cref{sec:found_inequalities} (specifically \cref{eq:ww_ineq} as well as in \cref{sec:web_inequality,sec:symmetic_web_inequality}\todo[TC]{Reorganize the location of the inequalities}).
+A sample of these inequalities are presented in \cref{sec:found_inequalities} (specifically \cref{eq:ww_ineq} as well as in \cref{eq:web_inequality,eq:symmetic_web_inequality}\todo[TC]{Reorganize the location of the inequalities}).
 \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work.
@@
 
-    The Fritz distribution $\prob[\fritz]$ is of special interest because it can be realized as a set of quantum states and measurements on the quantum causal model depicted in \cref{fig:triangle_structure_quantum_model}.
+    The Fritz distribution $\prob[\fritz]$ is of special interest because it can be realized as a set of quantum states and measurements.
 The shared resource between $A$ and $B$ (graphically denoted $\la$ in \cref{fig:triangle_structure_with_fritz_bell_embedded}) is the maximally entangled Bell state:
@@
 Using this incidence matrix, a number of incompatibility certificates were derived.
-For inspection, one is reproduced in \cref{sec:web_inequality}.
+For inspection, one is reproduced in \cref{eq:web_inequality}.
 
@@
 Unfortunately, infeasibility certificates are found by linear programing software to certify the infeasibility of a \textit{particular distribution}.
-This means that inequalities like \cref{eq:ww_ineq}, the one presented in \cref{sec:web_inequality}, and others are specifically manufactured in order witness a particular type of quantum non-classicality.
+This means that inequalities like \cref{eq:ww_ineq}, the one presented in \cref{eq:web_inequality}, and others are specifically manufactured in order witness a particular type of quantum non-classicality.
 In an effort to derive inequalities that could lead to potentially new forms of non-classicality, we searched for inequalities that did not admit biased towards the Fritz distribution.
@@
     \begin{equation}
-        \label{sec:web_inequality}
+        \label{eq:web_inequality}
         \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
@@
     \begin{equation}
-        \label{sec:symmetic_web_inequality}
+        \label{eq:symmetic_web_inequality}
         \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
@@
 First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}.
-The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{sec:web_inequality} while $I_3$ is the symmetric inequality in \cref{sec:symmetic_web_inequality}.
-Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{sec:web_inequality}.
+The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{eq:web_inequality} while $I_3$ is the symmetric inequality in \cref{eq:symmetic_web_inequality}.
+Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{eq:web_inequality}.
 
@@
 For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.
-Our tests suggest that inequality $I_1$ (\cref{sec:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
+Our tests suggest that inequality $I_1$ (\cref{eq:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
 The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}.
@@
 
-    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be expressed as follows:
+    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle Structure \cref{fig:triangle_structure} and thus expressed as follows:
     \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
@@
 Additionally, since $\rho$ is Hermitian, the eigenstates $\bc{\ket{p_j}}$ form an orthonormal basis and therefore the eigenstates are analogously parameterized using \cref{eq:spengler_unitary}: $\rho = \sum_{j=1}^{d} p_j U^{\dagger} \ket{j} \bra{j} U$.
-For our purposes, we have set $d = 4$ and fixed $\la_{l, l} = 0$ for $1 \leq l \leq d$ in \cref{eq:spengler_unitary} because the global phase contributions are irrelevant in \cref{eq:quantum_model_triangle_pvms}.
-    \[  \]
+For our purposes, we have set $d = 4$ and fixed $\la_{l, l} = 0$ for $1 \leq l \leq d$ in \cref{eq:spengler_unitary} because the global phase contributions are irrelevant for \cref{eq:quantum_model_triangle_pvms}.
+
     % \Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}.
@@
 
-    Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
-Specifically, the BFGS method~\cite[p.
-142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.
-238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
-
     % \subsection{Parameterizing Quantum Distributions}
-    \begin{figure}
-    \begin{center}
-            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
-            \caption{The Triangle structure as modeled by quantum states and measurements.}
-            \label{fig:triangle_structure_quantum_model}
-    \end{center}
-    \end{figure}
+    % \begin{figure}
+    % \begin{center}
+    %         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
+    %         \caption{The Triangle structure as modeled by quantum states and measurements.}
+    %         \label{fig:triangle_structure_quantum_model}
+    % \end{center}
+    % \end{figure}
 
     % \subsection{Numerical Optimization Results}
-    \label{sec:results}
-
-    For each inequality $I$, we define the relative violation $V_F$ to be maximum violation relative to the violation achieved by the Fritz distribution.
-    \[ V_F = \f{\min_{P}\bc{I\br{P}}}{I\br{P_F}} \]
-
-    The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{sec:web_inequality}.
+
+    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
+$V_F \defined \min_{P}\bc{I\br{P}}/I\br{P_F}$.
+The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{eq:web_inequality}.
 At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
@@
             \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
-            \caption{Probability distribution that maximizes violation of $I_1$ from \cref{sec:web_inequality} ($V_F \simeq 1.501$).}
+            \caption{Probability distribution that maximizes violation of $I_1$ from \cref{eq:web_inequality} ($V_F \simeq 1.501$).}
             \label{fig:maximum_violation_I_1}
@@
     \end{figure}
+
+    Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
+Specifically, the BFGS method~\cite[p.
+142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.
+238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
 
@@
 
-    The second inequality in consideration is $I_3$; the \textit{symmetric} Web inflation inequality presented in \cref{sec:symmetic_web_inequality}.
+    The second inequality in consideration is $I_3$; the \textit{symmetric} Web inflation inequality presented in \cref{eq:symmetic_web_inequality}.
 This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
@@
             \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
-            \caption{Probability distribution that maximizes violation of $I_3$ from \cref{sec:symmetic_web_inequality} ($V_F \simeq 2.61$).}
+            \caption{Probability distribution that maximizes violation of $I_3$ from \cref{eq:symmetic_web_inequality} ($V_F \simeq 2.61$).}
             \label{fig:maximum_violation_I_3}
@@
 Using the symmetric incidence matrix and linear programing methods, an infeasibility certificate was found that is capable of witnessing the Fritz distribution.
-This inequality is reproduced in \cref{sec:symmetic_web_inequality}.
+This inequality is reproduced in \cref{eq:symmetic_web_inequality}.
 

### 2017-04-06 documents/TriangleScenarioArXiv/ts.tex
First pass through at completing the numerical optimizations result section

@@
     \label{sec:noise}
-    \begin{figure}
-    \begin{center}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
-            \vspace{-0.2in}
-            \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
-            \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
-            \label{fig:uniform_distribution}
-    \end{center}
-    \end{figure}
+    % \begin{figure}
+    % \begin{center}
+    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
+    %         \vspace{-0.2in}
+    %         \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
+    %         \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
+    %         \label{fig:uniform_distribution}
+    % \end{center}
+    % \end{figure}
     In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality.
@@
 
-    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$ (see \cref{fig:uniform_distribution}).
+    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$.
 Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible.
@@
 Analogously, this argument can be extended to full-rank $d$-dimensional density matrices $\rho$ by performing a spectral decomposition $\rho = \sum_{j=1}^{d} p_j \ket{p_j} \bra{p_j}$ into eigenvalues $\bc{p_j}$ and eigenstates $\bc{\ket{p_j}}$.
-Since $\Tr\bc{\rho} = \sum_{j = 1}^{d} p_j = 1$ the eigenvalues of $\rho$ are parameterized without degeneracy using a tuple of $d-1$ real-valued parameters with periodicity $\bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}.
+Since $\Tr\br{\rho} = \sum_{j = 1}^{d} p_j = 1$ the eigenvalues of $\rho$ are parameterized without degeneracy using a tuple of $d-1$ real-valued parameters with periodicity $\bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}.
 Additionally, since $\rho$ is Hermitian, the eigenstates $\bc{\ket{p_j}}$ form an orthonormal basis and therefore the eigenstates are analogously parameterized using \cref{eq:spengler_unitary}: $\rho = \sum_{j=1}^{d} p_j U^{\dagger} \ket{j} \bra{j} U$.
@@
 
-    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
-$V_F \defined \min_{P}\bc{I\br{P}}/I\br{P_F}$.
-The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{eq:web_inequality}.
-At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
-Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution.
-In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure} or set of possible events.
-What does this reveal about $I_1$ and non-classicality in the Triangle structure?
-This result is not entirely unexpected.
-As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to show incompatibility of the Triangle structure.
-Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for a specific forms of non-classicality that resemble the Fritz distribution very closely.
-
     \begin{figure}
@@
 
+    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
+$V_F \defined \min_{P}\bc{I\br{P}}/I\br{P_F}$.
+The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{eq:web_inequality}.
+At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
+Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution.
+In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure}, i.e.
+the same set of possible events.
+This result is not entirely unexpected.
+As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure.
+Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.
+
+    An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization.
+Above it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
+Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to inequality \textit{saturation} instead of inequality \textit{violation} which is achievable by the Fritz distribution $\prob[\fritz]$.
+Instead, it was observed that only parameters close enough to the \textit{Fritz parameters} (the parameters that induce the Fritz distribution using the quantum implementation in \cref{sec:fritz_distribution}) were able to any violation.
 Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
@@
 238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
-
-    An alternative explanation has to do with the sensitively of the initial condition $\la_{\br{0}} = \br{\la_{\br{0}, 0}, \ldots, \la_{\br{0}, n}}$ in our optimization.
-In \cref{sec:param_quantum_dist}, it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
-Somewhat surprisingly, when using a uniform seed for $\la_0$, all optimization methods consistently converged to inequality saturation instead of inequality violation which of course is achievable by the Fritz distribution.
-Instead, only initial seeds close enough to the \textit{Fritz parameters} $\la_{\br{\fritz}}$ (the parameters that induce the Fritz distribution using the quantum implementation in \cref{sec:fritz_distribution}) where able to achieve violation.
-To illustrate this graphically, we let the initial seed be a small Gaussian perturbation $\de \la$ away from $\la_{\br{\fritz}}$ in parameter space.
-    \[ \la_{\br{0}} = \la_{\br{\fritz}} + \de \la  \]
-    The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation.
+Despite our varied efforts, it remains unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
+More likely, this phenomena is due to a combination of both effects.
+
+    % The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation.
 For $I_1$, deviations of $\chi \gtrsim 1.3$ inhibited convergence to violation.
 This is depicted in \cref{fig:initial_conditions}.
-Therefore, it is unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
-Most likely, this phenomena is due to a combination of both effects.
-
-    \begin{figure}
-    \begin{subfigure}[t]{.48\linewidth}
-    {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
-    \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
-    \end{subfigure}
-    \begin{subfigure}[t]{.48\linewidth}
-    {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
-    \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
-    \end{subfigure}
-    \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
-    \end{figure}
-
-    The second inequality in consideration is $I_3$; the \textit{symmetric} Web inflation inequality presented in \cref{eq:symmetic_web_inequality}.
+
+    % \begin{figure}
+    % \begin{subfigure}[t]{.48\linewidth}
+    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
+    % \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
+    % \end{subfigure}
+    % \begin{subfigure}[t]{.48\linewidth}
+    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
+    % \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
+    % \end{subfigure}
+    % \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
+    % \end{figure}
+
+    The second inequality in consideration is the \textit{symmetric} inequality $I_3$ ($\cref{eq:symmetic_web_inequality}$).
 This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
@@
 However, this result is far more surprising.
-Since the inequality is symmetric with respect to the exchange of parties $\varphi \in \Perm{A, B, C}$, one would naively expect that the maximum violating distribution is be symmetric as well.
+Since the inequality is symmetric with respect to the permutation of parties, one would naively expect that the maximum violating distribution be symmetric as well.
 If it were not, one could construct a distribution that violates $I_3$ more by symmetrizing $\prob[\fritz]$ by summing over all possible permutations and normalizing.
@@
 This distribution is also non-classical with relative violation $V_F = 3$.
-As it turns out, the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}\footnote{At least numerical optimizations suggest this is the case.} Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result found in~\citet{Inflation}.
+As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}.
+Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.
     \begin{figure}
@@
 This means that the Fritz distribution either represents a local minimum of the parameter space or is in fact \textit{the} maximally violating distribution.
-Without further investigations, it is unclear if this behavior is related to the universality of the Fritz distribution or if its an artifact of the methods used to derive $I_0$ and $I_2$.
+Without further investigations, it remains unclear if this behavior is related to the universality of the Fritz distribution or if its an artifact of the methods used to derive $I_0$ and $I_2$.
+
+    \subsection{Rosset Variation}
+    \label{sec:rosset_variation}
+    \todo[TC]{This might take a page}
 

### 2017-04-06 documents/TriangleScenarioArXiv/ts.tex
reduced the length of the section on the fritz distribution

@@
 
+    \[ \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 0} + \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 1} + \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 0} - \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 1} \leq 2 \eq \label{eq:CHSH_ineq_orig} \]
+
     \section{Triangle Structure}
@@
 This can be accomplished by having $C$ ``measure'' the measurement settings $S_{\p{A}}, S_{\p{B}}$ and announce them as an outcome.
-Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$.
+Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$~\cite{Fritz_2012}.
 Understandably there are numerous ways that this can be accomplished, albeit we will focus on elucidating an exemplary method.
 
-    The \term{Fritz distribution}, denoted $\prob[\fritz]$, is a quantum-accessible distribution known to be incompatible with the Triangle structure~\cite{Fritz_2012}.
+    The \term{Fritz distribution}, denoted $\prob[\fritz]$, is a quantum-accessible distribution incompatible with the Triangle structure~\cite{Fritz_2012}.
 In the Fritz distribution, each of the variables $A,B,C$ have $4$ possible outcomes.
@@
     Here the notation $\prob[\fritz][abc] = \prob[\p{ABC}][abc] = \prob[][\p A=a,\p B=b,\p C=c]$ is used as shorthand.
+The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:quantum_model_triangle}~\cite{Fritz_2012}.
 The Fritz distribution is best visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}.
@@
     \end{figure}
-    Consequently, it is possible to define the correlation between the right-hand bits of $A$ and $B$ as the probability that $A_r$ and $B_r$ are equal less the probability that they differ:
+    Consequently, it is possible to define the correlation $\ba{\p A_r \p B_r}$ between the right-hand bits of $\p A$ and $\p B$:
     \[ \ba{\p A_r \p B_r} = \prob[\p A_r \p B_r][00] + \prob[\p A_r \p B_r][11] - \prob[\p A_r \p B_r][01] - \prob[\p A_r \p B_r][10] \]
-    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the Triangle structure using the following mapping:
-    \[ \p{A}, \p{B}, S_{\p{A}}, S_{\p{B}} \mapsto \p{A_r}, \p{B_r}, \p A_l, \p B_l \]
-    As an example, the famous CHSH inequality~\cite{CHSH_Original},
-    \[ \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 0} + \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 1} + \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 0} - \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 1} \leq 2 \]
-    Can be written for the right-bits of $A$ and $B$,
-    \[ \ba{\p A_r \p B_r|\p C = 00} + \ba{\p A_r \p B_r|\p C = 01} + \ba{\p A_r \p B_r|\p C = 10} - \ba{\p A_r \p B_r|\p C = 11} \leq 2 \eq \label{eq:CHSH} \]
-    Therefore, every compatible distribution $\prob[ABC]$ where $C$ is perfectly correlated $A_l,B_l$ must satisfy \cref{eq:CHSH}.
-Substituting the Fritz distribution (\cref{eq:fritz_dist}) into \cref{eq:CHSH} yields maximal violation~\cite{Cirelson_1980},
-    \[ 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} = 2\sqrt{2} \not \leq 2 \]
-    Therefore, the Fritz distribution is incompatible with the Triangle structure as promised.
-
-    The Fritz distribution $\prob[\fritz]$ is of special interest because it can be realized as a set of quantum states and measurements.
-The shared resource between $A$ and $B$ (graphically denoted $\la$ in \cref{fig:triangle_structure_with_fritz_bell_embedded}) is the maximally entangled Bell state:
-    \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \qquad \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \]
-    While the states shared with $C$ are the following mixed states:
-    \[ \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2} \]
-    The measurements employed by $A,B$ and $C$ are separable, projective measurements,
-    \begin{align*}
-        M_{A} &= \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
-        M_{B} &= \bc{\ket{\psi_{6}0}\bra{\psi_{6}0}, \ket{\psi_{2}0}\bra{\psi_{2}0}, \ket{\psi_{0}1}\bra{\psi_{0}1}, \ket{\psi_{4}1}\bra{\psi_{4}1}} \\
-        M_{C} &= \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
-    \end{align*}
-    Where $\ket{\psi_n}$ is shorthand for,
-    \[ \ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}} \]
-    Using the above states and measurements, the Fritz distribution $\prob[\fritz]$ can be recovered using the following:
-    \[ \prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}} \]
-    Where $\netperm$ is a $64 \times 64$ permutation matrix to be elaborated in \cref{sec:perm_matrix}.
-
+    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the Triangle structure by performing a simple relabeling: $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}} \mapsto \p{A}_r, \p{B}_r, \p A_l, \p B_l$.
+As an example, the famous CHSH inequality~\cite{CHSH_Original} (\cref{eq:CHSH_ineq_orig}) constrains the correlation between the right-bits of $A$ and $B$,
+    \[ \ba{\p A_r \p B_r|\p C = 00} + \ba{\p A_r \p B_r|\p C = 01} + \ba{\p A_r \p B_r|\p C = 10} - \ba{\p A_r \p B_r|\p C = 11} \leq 2 \eq \label{eq:CHSH_intriangle} \]
+    Every compatible distribution $\prob[ABC]$ for which $C$ is perfectly correlated $A_l,B_l$ must satisfy \cref{eq:CHSH_intriangle}.
+Substituting the \cref{eq:fritz_dist} into \cref{eq:CHSH_intriangle} yields the maximal violation~\cite{Cirelson_1980}: $3 \br{1/\sqrt{2}} - \br{-1/\sqrt{2}} = 2\sqrt{2} \not \leq 2$.
+Therefore, we conclude the Fritz distribution is incompatible with the Triangle structure.
 Before continuing it is worth noting that \cref{eq:fritz_dist} is non-unique.
-Any distribution that is equal to \cref{eq:fritz_dist} via a permutation of outcomes or exchange of parties is should also be referred to as a Fritz distribution.
-Moreover, the quantum realization presented here is not unique either.
-Nonetheless for concreteness, \cref{eq:fritz_dist} is taken as \textit{the} Fritz distribution throughout this paper.
-Moreover, the quantum implementation of the Fritz distribution presented above is non-unique also.
-For example, it is possible to implement the Fritz distribution using maximally entangled Bell states for each shared resource $\rho_{AB}, \rho_{BC}, \rho_{CA}$ provided there is an appropriate adjustment to the measurements $M_A, M_B, M_C$.
+Nonetheless for concreteness, \cref{eq:fritz_dist} is taken as \textit{the} Fritz distribution throughout this manuscript.
+
+    % The shared resource between $A$ and $B$ (graphically denoted $\la$ in \cref{fig:triangle_structure_with_fritz_bell_embedded}) is the maximally entangled Bell state:
+    % \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \qquad \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \]
+    % While the states shared with $C$ are the following mixed states:
+    % \[ \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2} \]
+    % The measurements employed by $A,B$ and $C$ are separable, projective measurements,
+    % \begin{align*}
+    %     M_{A} &= \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
+    %     M_{B} &= \bc{\ket{\psi_{6}0}\bra{\psi_{6}0}, \ket{\psi_{2}0}\bra{\psi_{2}0}, \ket{\psi_{0}1}\bra{\psi_{0}1}, \ket{\psi_{4}1}\bra{\psi_{4}1}} \\
+    %     M_{C} &= \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
+    % \end{align*}
+    % Where $\ket{\psi_n}$ is shorthand for,
+    % \[ \ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}} \]
+    % Using the above states and measurements, the Fritz distribution $\prob[\fritz]$ can be recovered using the following:
+    % \[ \prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}} \]
+    % Where $\netperm$ is a $64 \times 64$ permutation matrix to be elaborated in \cref{sec:perm_matrix}.
+    % Moreover, the quantum implementation of the Fritz distribution presented above is non-unique also.
+For example, it is possible to implement the Fritz distribution using maximally entangled Bell states for each shared resource  provided there is an appropriate adjustment to the measurements .
 Ultimately however, only $\rho_{AB}$ is required to be entangled in order to reproduce the Fritz; after-all, $C$ is simply classically announcing $A_r$ and $B_r$ as he receives them.
 
-    Additionally, it is important to understand the domain in which Fritz's proof of incompatibility is valid.
-Specifically, \cref{eq:CHSH} can only be applied to the Triangle structure where there exists perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$.
-The details of this restriction are discussed and proven in Fritz's original work~\cite{Fritz_2012}.
-As such, the incompatibility proof employed by Fritz is not applicable to any distribution that significantly deviates from the Fritz distribution presented above.
+    It is important to understand the domain in which Fritz's proof of incompatibility is valid; the details of which can found in the original work~\cite{Fritz_2012}.
+Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequalty for the Triangle structure if there exists perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$.
+As a result, the incompatibility proof employed by Fritz is not applicable to any distribution that significantly deviates from the Fritz distribution presented above.
 For example, if one combines \cref{eq:fritz_dist} with more and more uniform noise, at what point does the resultant distribution transition from incompatibility to compatibility?
-This problem is discussed more in \cref{sec:noise}.
-
-    Upon reflection, the Fritz distribution can rightly be considered slightly manufactured.
+This question is partially answered in \cref{sec:noise}.
+
+    Upon reflection, the Fritz distribution can be considered \textit{manufactured}.
 The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of entanglement resources made accessible by quantum mechanics.
@@
     \end{figure}
-
-    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
-$V_F \defined \min_{P}\bc{I\br{P}}/I\br{P_F}$.
-The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{eq:web_inequality}.
-At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
-Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution.
-In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure}, i.e.
-the same set of possible events.
-This result is not entirely unexpected.
-As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure.
-Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.
-
-    An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization.
-Above it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
-Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to inequality \textit{saturation} instead of inequality \textit{violation} which is achievable by the Fritz distribution $\prob[\fritz]$.
-Instead, it was observed that only parameters close enough to the \textit{Fritz parameters} (the parameters that induce the Fritz distribution using the quantum implementation in \cref{sec:fritz_distribution}) were able to any violation.
-Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
-Specifically, the BFGS method~\cite[p.
-142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.
-238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
-Despite our varied efforts, it remains unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
-More likely, this phenomena is due to a combination of both effects.
-
-    % The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation.
-For $I_1$, deviations of $\chi \gtrsim 1.3$ inhibited convergence to violation.
-This is depicted in \cref{fig:initial_conditions}.
-
-    % \begin{figure}
-    % \begin{subfigure}[t]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
-    % \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
-    % \end{subfigure}
-    % \begin{subfigure}[t]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
-    % \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
-    % \end{subfigure}
-    % \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
-    % \end{figure}
-
-    The second inequality in consideration is the \textit{symmetric} inequality $I_3$ ($\cref{eq:symmetic_web_inequality}$).
-This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
-Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution.
-However, this result is far more surprising.
-Since the inequality is symmetric with respect to the permutation of parties, one would naively expect that the maximum violating distribution be symmetric as well.
-If it were not, one could construct a distribution that violates $I_3$ more by symmetrizing $\prob[\fritz]$ by summing over all possible permutations and normalizing.
-The symmetrized Fritz distribution is plotted in \cref{fig:symmetrized_fritz}.
-This distribution is also non-classical with relative violation $V_F = 3$.
-As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}.
-Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.
     \begin{figure}
@@
     \end{figure}
+
+    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
+$V_F \defined \min_{P}\bc{I\br{P}}/I\br{P_F}$.
+The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{eq:web_inequality}.
+At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
+Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution.
+In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure}, i.e.
+the same set of possible events.
+This result is not entirely unexpected.
+As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure.
+Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.
+
+    An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization.
+Above it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
+Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to inequality \textit{saturation} instead of inequality \textit{violation} which is achievable by the Fritz distribution $\prob[\fritz]$.
+Instead, it was observed that only parameters close enough to the \textit{Fritz parameters} (i.e.
+any non-unique set of parameters that induce the Fritz distribution) were able to achieve violation.
+Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
+Specifically, the BFGS method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
+Despite our varied efforts, it remains unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
+More likely, this phenomena is due to a combination of both effects.
+
+    It is also worth reporting that the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:quantum_model_triangle} are restricted to maximally entangled states.
+This result resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} which demonstrates that entanglement and non-classicality are different resources.
+
+    % The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation.
+For $I_1$, deviations of $\chi \gtrsim 1.3$ inhibited convergence to violation.
+This is depicted in \cref{fig:initial_conditions}.
+
+    % \begin{figure}
+    % \begin{subfigure}[t]{.48\linewidth}
+    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
+    % \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
+    % \end{subfigure}
+    % \begin{subfigure}[t]{.48\linewidth}
+    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
+    % \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
+    % \end{subfigure}
+    % \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
+    % \end{figure}
+
+    The second inequality in consideration is the \textit{symmetric} inequality $I_3$ (\cref{eq:symmetic_web_inequality}).
+This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
+Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution.
+However, this result is far more surprising.
+Since the inequality is symmetric with respect to the permutation of parties, one would naively expect that the maximum violating distribution be symmetric as well.
+If it were not, one could construct a distribution that violates $I_3$ more by symmetrizing $\prob[\fritz]$ by summing over all possible permutations and normalizing.
+The symmetrized Fritz distribution is plotted in \cref{fig:symmetrized_fritz}.
+This distribution is also non-classical with relative violation $V_F = 3$.
+As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}.
+Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.
 

### 2017-04-07 documents/TriangleScenarioArXiv/ts.tex
fixed dozens of typos and shortened several sections, namely the appendix on symmetries

@@
 \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities.
-\Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure was chosen as a case study.
+\Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure is worth studying.
 \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}.
 The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities.
-A sample of these inequalities are presented in \cref{sec:found_inequalities} (specifically \cref{eq:ww_ineq} as well as in \cref{eq:web_inequality,eq:symmetic_web_inequality}\todo[TC]{Reorganize the location of the inequalities}).
+A sample of these inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetic_web_inequality}.
+Finally, \cref{sec:violations_noise} introduces a method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality.
+Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.
+\Cref{sec:conclusions} concludes with proposed avenues for further research.
+
     \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work.
 Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}.
-\Cref{sec:deriving_inequalities} demonstrates how the inflation technique can be used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions.
-Finally, \cref{sec:violations_noise} introduces the method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality.
-Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.
-\Cref{sec:conclusions} concludes with proposed avenues for further research.
+\Cref{sec:deriving_inequalities} demonstrates how the Inflation Technique was used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions.
 
@@
 Alternatively yet equivalently, the notion of compatibility can be interpreted as follows: a distribution $\prob[\nodes]$ is compatible with $\graph$ if $\prob[\nodes]$ can be consistently factorized into conditional probability distributions for each variable $n \in \nodes$ conditioned on its parents $\Pa[\graph]{n}$:
-    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:local_markov_property_operation}\]
-    The conditional distributions in \cref{eq:local_markov_property_operation} (i.e.
+    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:compatibility_as_factorization}\]
+    The conditional distributions in \cref{eq:compatibility_as_factorization} (i.e.
 $\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}.
-If a distribution $\prob[\nodes]$ violates \cref{eq:local_markov_property} or equivalently cannot be factorized according to \cref{eq:local_markov_property_operation}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$.
+If a distribution $\prob[\nodes]$ violates \cref{eq:local_markov_property} or equivalently cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$.
 When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is trivially easy to verify whether or not $\prob[\nodes]$ is compatibility with $\graph$; \cref{sec:satisfaction_of_d_sep_relations} describes in detail how this is accomplished.
@@
 a joint distribution $\prob[\nodes_{O}]$ where $\nodes_{O} \subset \nodes$ is some subset of variables referred to as the \term{observable nodes} $\nodes_O$.
-In such cases, \cref{eq:local_markov_property_operation} can not be verified by direction calculation because it is certainly possible that the parents of some observable node are themselves unobservable $\Pa[\graph]{\nodes_{O}} \not \subseteq \nodes_{O}$.
+In such cases, \cref{eq:compatibility_as_factorization} can not be verified by direction calculation because it is certainly possible that the parents of some observable node are themselves unobservable $\Pa[\graph]{\nodes_{O}} \not \subseteq \nodes_{O}$.
 In such cases, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \prod_{n \in \nodes_{O}} \prob[n \mid \Pa[\graph]{n}]$.
@@
     \[ \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 0} + \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 1} + \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 0} - \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 1} \leq 2 \eq \label{eq:CHSH_ineq_orig} \]
-
-    \section{Triangle Structure}
-    \label{sec:triangle_structure}
 
@@
     \end{figure}
+    \section{Triangle Structure}
+    \label{sec:triangle_structure}
+
     Discovering quantum non-classicality in any causal structure is desirable, so why, in particular, is it important to do so in the Triangle structure?
 As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
-
 Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that
@@
 It can be argued that convexity of the Bell structure distributions is partially responsible for the wealth of knowledge that is known about the Bell structure.
-It is also reasonable to speculate that quantum non-classicality in the triangle can be translated directly into a computational advantage for certain computational circuits~\cite{Terhal_2002}.
+It is also reasonable to speculate that quantum non-classicality in the Triangle structure can be translated directly into a computational advantage for certain computational circuits~\cite{Terhal_2002}.
 Characterizing quantum non-classicality for interesting causal structures remains an unsolved problem, and the Triangle structure is a small, non-trivial case study.
 
-    Additionally, \citet{Fritz_2012} demonstrated that the Triangle structure is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell structure in that measure setting variables are non-existent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we have elected to call the Fritz distribution (see \cref{sec:fritz_distribution}).
+    Additionally, \citet{Fritz_2012} demonstrated that the Triangle structure is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell structure in that measurement setting variables are absent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we discuss in detail in \cref{sec:fritz_distribution}.
 Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classical in the Triangle structure.
-    \comment[E]{Revisions processed up to here thusfar.}
-
-    Finally \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}), a novel tool for solving causal inference problems.
-Using the inflation technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints.
-Therefore as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure that all others.
+    % \comment[E]{Revisions processed up to here thusfar.}
+
+    Finally, \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}) --- a novel tool for solving causal inference problems.
+Using the Inflation Technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints.
+Consequently, as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure than all others.
 
@@
 Moreover, \citet{Henson_2014} derive a family of entropic inequalities constraining the set of compatible correlations.
-Most impressively, \citet{Inflation} derive a family of polynomial, $2$-outcome, causal compatibility inequalities; $37$ non-trivial representatives are printed in~\cite{Inflation}.
+Most recently, \citet{Inflation} derive a family of polynomial, $2$-outcome, causal compatibility inequalities; $37$ non-trivial representatives are printed in~\cite{Inflation}.
 
@@
 These early results suggest, although do not prove, that quantum non-classical does not exist in the Triangle structure for \textit{two-outcome} measurements.
-It is therefore conjectured that all quantum non-classical distributions in the Triangle structure utilize more than $2$ outcomes in at least one party.
+Therefore, it is conjectured that all quantum non-classical distributions in the Triangle structure must utilize more than $2$ outcomes in at least one variable.
 Moreover we take these observations as motivation to explore incompatibility in Triangle structure for a larger cardinalities.
@@
     \end{align*}
-    Here the notation $\prob[\fritz][abc] = \prob[\p{ABC}][abc] = \prob[][\p A=a,\p B=b,\p C=c]$ is used as shorthand.
+    Here the notation $\prob[\fritz][abc] = \prob[\p{ABC}][abc] = \prob[][\p A\mapsto a,\p B\mapsto b,\p C\mapsto c]$ is used as shorthand.
 The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:quantum_model_triangle}~\cite{Fritz_2012}.
@@
 
-    % The shared resource between $A$ and $B$ (graphically denoted $\la$ in \cref{fig:triangle_structure_with_fritz_bell_embedded}) is the maximally entangled Bell state:
-    % \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \qquad \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \]
-    % While the states shared with $C$ are the following mixed states:
-    % \[ \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2} \]
-    % The measurements employed by $A,B$ and $C$ are separable, projective measurements,
-    % \begin{align*}
-    %     M_{A} &= \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
-    %     M_{B} &= \bc{\ket{\psi_{6}0}\bra{\psi_{6}0}, \ket{\psi_{2}0}\bra{\psi_{2}0}, \ket{\psi_{0}1}\bra{\psi_{0}1}, \ket{\psi_{4}1}\bra{\psi_{4}1}} \\
-    %     M_{C} &= \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
-    % \end{align*}
-    % Where $\ket{\psi_n}$ is shorthand for,
-    % \[ \ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}} \]
-    % Using the above states and measurements, the Fritz distribution $\prob[\fritz]$ can be recovered using the following:
-    % \[ \prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}} \]
-    % Where $\netperm$ is a $64 \times 64$ permutation matrix to be elaborated in \cref{sec:perm_matrix}.
-    % Moreover, the quantum implementation of the Fritz distribution presented above is non-unique also.
-For example, it is possible to implement the Fritz distribution using maximally entangled Bell states for each shared resource  provided there is an appropriate adjustment to the measurements .
-Ultimately however, only $\rho_{AB}$ is required to be entangled in order to reproduce the Fritz; after-all, $C$ is simply classically announcing $A_r$ and $B_r$ as he receives them.
-
     It is important to understand the domain in which Fritz's proof of incompatibility is valid; the details of which can found in the original work~\cite{Fritz_2012}.
-Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequalty for the Triangle structure if there exists perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$.
+Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequality for the Triangle structure if there exists perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$.
 As a result, the incompatibility proof employed by Fritz is not applicable to any distribution that significantly deviates from the Fritz distribution presented above.
@@
 
-    Equipped with the Fritz distribution (\cref{sec:fritz_distribution}) and the inflation technique (\cref{sec:inflation_technique}), it is now possible to derive causal compatibility inequalities for the triangle that are violated by the Fritz distribution; the procedure for doing so is as follows.
-First select an inflation $\graph'$ of the Triangle structure $\graph$ and identify the maximal pre-injectable sets $\PreInj[\graph]{\graph'}$.
-These sets define the marginal scenario to be used in the Inflation Technique.
-Next, inflate the Fritz distribution into the pre-injectable sets as described by the Inflation lemma (\cref{lem:inflation}).
-Finally, obtain infeasibility certificates using some linear programing software and obtain a valid causal compatibility inequality that witnesses the Fritz distribution's incompatibility.
-
-    As a first demonstration, we make use of the Wagon-Wheel inflation (\cref{fig:wagon_wheel_inflation}) to find these inequalities.
-The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
-By inspection\footnote{Computing the injectable and pre-injectable sets computationally is possible and a technique is discussed in~\citet{Inflation}.}, the maximal pre-injectable sets of the Wagon-Wheel inflation are as follows:
-    \begin{equation*}
-        \eq \label{eq:pre_injectable_triangle_structure_wagon_wheel}
-        \begin{gathered}
-            \textbf{Maximal Pre-injectable Sets} \\
-            \bc{A_2, B_1, C_3, C_1} \\
-            \bc{A_1, B_1, C_4, C_2} \\
-            \bc{A_1, B_2, C_1, C_3} \\
-            \bc{A_2, B_2, C_2, C_4} \\
-        \end{gathered}
-        \qquad
-        \begin{gathered}
-            \textbf{Ancestral Independences} \\
-            \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
-            \bc{A_1, B_1, C_4} \ancestralindep \bc{C_2} \\
-            \bc{A_1, B_2, C_1} \ancestralindep \bc{C_3} \\
-            \bc{A_2, B_2, C_2} \ancestralindep \bc{C_4} \\
-        \end{gathered}
-    \end{equation*}
-
-    These maximal pre-injectable sets define a marginal scenario where $\graph'$ is the Wagon-Wheel inflation of the Triangle structure $\graph$.
-    \[ \mscenario = \PreInj[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
-    The complete set of variables $\jointvar$ is simply the set of observable nodes in the Wagon-Wheel inflation,
-    \[ \jointvar = \nodes'_O = \bc{A_1, A_2, B_1, B_2, C_1, C_2, C_3, C_4} \]
-    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
-This marginal scenario $\mscenario$ then defines an incidence matrix capable of accommodating the Fritz distribution.
-    Analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \abs{\Events{V}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{\Events{v}} = 4^{\abs{\jointvar}} = 4^8 = 65,536$ columns.
-Understandably, this matrix is not reproduced here.
-The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
-
-    The marginal distribution vector $\probvec^{\mscenario}$ is indexed by $1024$ marginal outcomes $m \in \Events{\mscenario}$ of the following \textit{symbolic} form,
-    \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
-    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
-    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
-    And finally, each probability distribution in \cref{eq:marginal_vector_wagon_wheel_factors} is deflated by dropping copy-indices.
-    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[ABC]\br{000}\prob[C]\br{0}, \ldots, \prob[ABC]\br{323}\prob[C]\br{2}, \ldots, \prob[ABC]\br{333}\prob[C]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors_dropped}\]
-    This step is permitted because all of the remaining distributions in \cref{eq:marginal_vector_wagon_wheel_factors} are defined over the injectable sets of the Wagon-Wheel inflation.
-Numerically however, each of the elements of $\probvec^{\mscenario}$ are replaced with numerical values corresponding to the Fritz distribution upon deflation.
-Pursuant to \cref{eq:fritz_dist}, $\prob[ABC]\br{323}\prob[C]\br{2}$, for example, is assigned the following numerical value.
-    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267  \]
-    The same is applied to all other entries of $\probvec^{\mscenario}$.
-Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained.
-Below is an example of an infeasibility inequality obtained over the entries of \cref{eq:marginal_vector_wagon_wheel_factors_dropped}.
+    \Cref{sec:causal_compatibility} defined causal compatibility inequalities while \cref{sec:fritz_distribution} recalled and discussed the Fritz distribution together with a brief summary of its incompatibility with the Triangle Structure.
+Heretofore, there were no known causal compatibility inequalities for the Triangle Structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}.
+By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle Structure that are violated by the Fritz distribution.
+A representative sample of these inequalities are presented here.
+The methods used to derive these inequalities are largely based on the Inflation Technique~\cite{Inflation}.
+A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:inflation_technique} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.
+
+    The first causal compatibility inequality is reported below:
     \begin{equation*}
@@
     \eq\label{eq:ww_ineq}
-    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \\
-    P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \\
-    P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \\
-    P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \\
-    P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \\
-    P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \\
-    P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \\
-    P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \\
-    P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \\
-    P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \\
-    P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) - P_{ABC}(000)P_{C}(3) \geq 0
+    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \cdots \\
+    \cdots + P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \cdots \\
+    \cdots + P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \cdots \\
+    \cdots + P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \cdots \\
+    \cdots + P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \cdots \\
+    \cdots + P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \cdots \\
+    \cdots + P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \cdots \\
+    \cdots + P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \cdots \\
+    \cdots + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \cdots \\
+    \cdots + P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \cdots \\
+    \cdots + P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) - P_{ABC}(000)P_{C}(3) \geq 0
     \end{gathered}
     \end{equation*}
-    By construction, every marginal model $\probvec^{\mscenario} = \bc{\prob[ABC], \prob[AB], \prob[BC], \prob[AC], \prob[A], \prob[B], \prob[C]}$ compatible with the Triangle structure must satisfy \cref{eq:ww_ineq}.
-The Fritz distribution however violates \cref{eq:ww_ineq}.
-
+    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle Structure (i.e.
+factorizes according to \cref{eq:compatibility_as_factorization}) must satisfy \cref{eq:ww_ineq}.
+As a demonstration, the Fritz distribution violates \cref{eq:ww_ineq}.
 Notice the final term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $-1$.
-For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$.
-
-    It is possible to simplify this inequality by marginalizing over sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) = P_{ABC}(300)$.
+For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$.
+Consequently we conclude that the Fritz distribution is incompatible with the Triangle Structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.
+
+    It is possible to simplify \cref{eq:ww_ineq} identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$.
 Upon doing so, one obtains the following,
     \begin{gather*}
-        P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \leq \\ P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + \\
-        + P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + P_{AB}(20) + P_{AB}(30) + P_{C}(3)P_{C}(0)
+        P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + \cdots \\
+        \cdots + P_{AB}(20) + P_{AB}(30) + P_{C}(3)P_{C}(0) - P_{ABC}(000)P_{C}(3) - P_{ABC}(021)P_{C}(2) + \cdots \\
+        \cdots - P_{ABC}(202) - P_{ABC}(302) - P_{ABC}(233)P_{C}(0) - P_{AC}(33)P_{C}(0) \geq 0
     \end{gather*}
 
-    There are a couple of important concepts to understand.
-First, the Fritz distribution is known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings.
-The inequality contained in \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure.
+    In order to understand the importance of \cref{eq:ww_ineq}, there are a couple of important concepts to understand.
+First, the Fritz distribution was originally known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings $A_l, B_l$.
+The inequality of \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure.
 For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$.
-Moreover, although the existence of an inequality capable of witnessing Fritz distribution is guaranteed, there was no guarantee that the marginal model associated with the Wagon-Wheel inflation (\cref{eq:wagon_wheel_marginal_model}) would be capable of producing such an inequality.
-In fact, smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
-
-    Larger inflations such as the Web inflation (\cref{fig:the_web_inflation}) were also used to generate causal compatibility inequalities that are violated by the Fritz distribution.
-The set of maximal pre-injectable sets for the Web inflation is considerably larger than \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
+Furthermore, the existence of an inequality capable of witnessing Fritz distribution \textit{is guaranteed}, albeit there was \textit{no guarantee} that the Inflation Technique would be capable of producing such an inequality.
+In fact, \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
+This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as \cref{eq:ww_ineq} strong enough to witness incompatible quantum distributions for the Triangle Structure.
+More universally, this result shows that the Inflation Technique is a promising tool for understanding quantum non-classical in more general causal structures.
+
+    In addition to \cref{eq:ww_ineq}, numerous independent inequalities were derived for the Triangle Structure that are violated by the Fritz distribution.
+The majority of these inequalities share most or all of the qualitative features of \cref{eq:ww_ineq}, and hence those inequalities are omitted from this manuscript.
+Instead, we present \cref{eq:web_inequality}, another causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was produced using the \cref{fig:the_web_inflation} --- a considerably larger inflation than the Wagon-Wheel inflation.
+Note that in \cref{eq:web_inequality} $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
+
+    \begin{equation}
+        \label{eq:web_inequality}
+        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
+    \end{equation}
+
+    The inequalities presented above (\cref{eq:ww_ineq,eq:web_inequality}) were curated to demonstrate the incompatibility of the Fritz distribution in particular.
+To reiterate, the Fritz distribution is incompatible with the Triangle Structure because it assigns a unique role to one of the variables, specifically $C$.
+The asymmetry within the Fritz distribution is reflected in the asymmetry of \cref{eq:ww_ineq,eq:web_inequality}.
+In order to discover new forms of non-classicality in the Triangle Structure, it is desirable to obtain measures of non-classicality (i.e.
+inequalities) that do not admit this bias.
+In an effort to find a causal compatibility inequality qualitatively distinct from \cref{eq:ww_ineq,eq:web_inequality}, we developed a technique to derive inequalities with certain symmetry properties such as \cref{eq:symmetic_web_inequality} which is symmetric with respect to any permutation of the variables $A, B, C$.
+These techniques are explained in \cref{sec:symmetric_inequalities}.
+Surprisingly, \cref{eq:symmetic_web_inequality} is also violated by the Fritz distribution.
+    \begin{equation}
+        \label{eq:symmetic_web_inequality}
+        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
+    \end{equation}
+    Note that $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for a sum the over permutations of $A,B,C$, i.e.
+$\bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033)$.
+
+    Most importantly, these causal compatibility inequalities are a positive resolution of Fritz's problem from \cref{sec:fritz_distribution}.
+These inequalities are derived without making use of Bell's theorem and instead uses the Inflation Technique to approach non-classicality from a causal inference perspective.
+Additionally, the derivation of causal compatibility inequalities allows one prove incompatibility even when perfect correlations are absent.
+
+    \section{Numerical Optimizations \& Noisy Distributions}
+    \label{sec:violations_noise}
+    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality.
+In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities.
+In order to compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ so $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
+For the subsequent analysis, $4$ inequalities where chosen.
+First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}.
+The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{eq:web_inequality} while $I_3$ is the symmetric inequality in \cref{eq:symmetic_web_inequality}.
+Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{eq:web_inequality}.
+
+    \subsection{Noisy Distributions}
+    \label{sec:noise}
+    % \begin{figure}
+    % \begin{center}
+    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
+    %         \vspace{-0.2in}
+    %         \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
+    %         \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
+    %         \label{fig:uniform_distribution}
+    % \end{center}
+    % \end{figure}
+    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality.
+As was mentioned in \cref{sec:fritz_distribution}, this embedding required a very idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$.
+From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}.
+It is possible to minimize noise by developing more accurate measurement channels but perfect correlations are too idealistic.
+Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.
+
+    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$.
+Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible.
+We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
+    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
+    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$.
+For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.
+Our tests suggest that inequality $I_1$ (\cref{eq:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
+The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}.
+Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I_1$.
+
+    % Given that $I_0, I_1, I_2, I_3$ are far from a representative inequalities and are likely not facets of any inflated marginal polytope, it is save to say that this is possible.
+
+    % \begin{figure}
+    % \begin{subfigure}[b]{.48\linewidth}
+    % {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}}
+    % \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{.48\linewidth}
+    % {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}}
+    % \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
+    % \end{subfigure}
+    % \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
+    % \end{figure}
+
+    % The results of our experiments are plotted in \cref{fig:master_noise}.
+\Cref{fig:noise} illustrates that each curve $I\br{\s{N}_{\vep}\br{\prob[\fritz]}}$ as a function of $\vep$ is monotonically increasing as expected; the more noise added to the probability distribution, the more classical it becomes.
+\Cref{fig:noise_zoomed} is the same plot as \cref{fig:noise} zoomed onto the interval $\vep \in \bs{0, 0.12}$.
+
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
+            \vspace{-0.2in}
+            \[ \probplotvalue{255, 255, 243} = 0.00133 \]
+            \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
+            \label{fig:noisy_fritz}
+    \end{center}
+    \end{figure}
+
+    \subsection{Numerical Optimizations}
+    \label{sec:optimizations}
+    \todo[TC]{Determine if I should remove this paragraph or shorten it}
+    Causal compatibility inequalities act as a \textit{measure} of non-classicality.
+If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$.
+However, this statement is accompanied by a few caveats.
+First, it is possible (and frequently the case) for ${I\br{\prob[1]}} < I\br{\prob[2]}$ to hold for one inequality $I$ but have ${\ti I\br{\prob[2]}} < \ti I\br{\prob[1]}$ hold for another inequality $\ti I$.
+In this case, all one can claim is that $\prob[1]$ is more incompatible than $\prob[2]$ with respective to $I$ but the contrary is true with respect to $\ti I$.
+Second, not all inequalities $I$ are \textit{good} measures of non-classicality.
+In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality because the facets form a necessary and sufficient of constraints with all other inequalities following from positive mixtures.
+However, good measures of incompatibility are less understood in the Triangle structure where the space of classical correlations is non-convex.
+At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility simply because they have be curated toward the Fritz distribution.
+Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure.
+
+    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle Structure \cref{fig:triangle_structure} and thus expressed as follows:
+    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
+    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately.
+In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
+In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
+Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states.
+Qubit states are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix.
+Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
+First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure.
+Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$.
+Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
+    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]
+
+    Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, a single technique by \citet{Spengler_2010_Unitary} was found to be most computationally suitable for our purposes.
+\Citet{Spengler_2010_Unitary} demonstrated that all $d\times d$ unitary matrices $U$ can be parameterized without degeneracy as follows:
+    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
+    Where the real valued parameters $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ have periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
+Moreover, $P_l$ are one-dimensional projective operators $P_l = \ket{l}\bra{l}$ and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices $\sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m}$ where $1 \leq m < n \leq d$.
+This parameterization has the useful feature that each of the real-valued parameters $\la_{n,m}$ a direct and intuitive physical affect on each element of a computational basis $\bc{\ket{1}, \ldots, \ket{d}}$.
+Explicitly, $\exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$.
+Analogously, $\exp\br{i P_n \lambda_{n,m}}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $\exp\br{iP_l \lambda_{l,l}}$ fixes the global phase of $\ket{l}$.
+Finally, although not explicitly mentioned in~\cite{Spengler_2010_Unitary}, it is possible to remove the reliance on the computationally expensive matrix exponential operations in \cref{eq:spengler_unitary}~\cite{Moler_2003}.
+
+    By parameterizing unitary matrices, it becomes possible to parameterize $d$-dimensional density matrices and $d$-element PVMs by recognizing that any orthonormal basis $\bc{\ket{\psi_j}}$ (where $1 \leq j \leq d$) can be transformed into the computational basis $\bc{\ket{j}}$ by a unitary transformation $U$, i.e.
+$U \ket{\psi_j} = \ket{j}$.
+First consider a $d$-element PVM $M = \bc{\ket{m_j}\bra{m_j} \mid 1 \leq j \leq d}$.
+Since $\bc{\ket{m_j}}$ forms an orthonormal basis, one can parameterize $M$ by writing $M = \bc{U^{\dagger}\ket{j}\bra{j}U \mid 1 \leq j \leq d}$ and parameterizing $U$ using \cref{eq:spengler_unitary}.
+This method was inspired by the measurement seeding method for iterative optimization used by \citet{Pal_2010}.
+Analogously, this argument can be extended to full-rank $d$-dimensional density matrices $\rho$ by performing a spectral decomposition $\rho = \sum_{j=1}^{d} p_j \ket{p_j} \bra{p_j}$ into eigenvalues $\bc{p_j}$ and eigenstates $\bc{\ket{p_j}}$.
+Since $\Tr\br{\rho} = \sum_{j = 1}^{d} p_j = 1$ the eigenvalues of $\rho$ are parameterized without degeneracy using a tuple of $d-1$ real-valued parameters with periodicity $\bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}.
+Additionally, since $\rho$ is Hermitian, the eigenstates $\bc{\ket{p_j}}$ form an orthonormal basis and therefore the eigenstates are analogously parameterized using \cref{eq:spengler_unitary}: $\rho = \sum_{j=1}^{d} p_j U^{\dagger} \ket{j} \bra{j} U$.
+For our purposes, we have set $d = 4$ and fixed $\la_{l, l} = 0$ for $1 \leq l \leq d$ in \cref{eq:spengler_unitary} because the global phase contributions are irrelevant for \cref{eq:quantum_model_triangle_pvms}.
+
+    % \Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}.
+Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.
+
+    % the a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}.
+Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:quantum_model_triangle} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$.
+The objective value is simply the degree of violation $f = I\br{\prob[ABC]}$ and used to make adjustments to $\la$ in order to achieve largest and larger violations.
+
+    % \subsection{Parameterizing Quantum Distributions}
+    % \begin{figure}
+    % \begin{center}
+    %         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
+    %         \caption{The Triangle structure as modeled by quantum states and measurements.}
+    %         \label{fig:triangle_structure_quantum_model}
+    % \end{center}
+    % \end{figure}
+
+    % \subsection{Numerical Optimization Results}
+
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
+            \caption{Probability distribution that maximizes violation of $I_1$ from \cref{eq:web_inequality} ($V_F \simeq 1.501$).}
+            \label{fig:maximum_violation_I_1}
+    \end{center}
+    \end{figure}
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
+            \caption{Probability distribution that maximizes violation of $I_3$ from \cref{eq:symmetic_web_inequality} ($V_F \simeq 2.61$).}
+            \label{fig:maximum_violation_I_3}
+    \end{center}
+    \end{figure}
+    \begin{figure}
+    \begin{center}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
+            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
+            \label{fig:symmetrized_fritz}
+    \end{center}
+    \end{figure}
+
+    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
+$V_F \defined \min_{P}\bc{I\br{P}}/I\br{P_F}$.
+The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{eq:web_inequality}.
+At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
+Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution.
+In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure}, i.e.
+the same set of possible events.
+This result is not entirely unexpected.
+As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure.
+Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.
+
+    An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization.
+Above it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
+Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to inequality \textit{saturation} instead of inequality \textit{violation} which is achievable by the Fritz distribution $\prob[\fritz]$.
+Instead, it was observed that only parameters close enough to the \textit{Fritz parameters} (i.e.
+any non-unique set of parameters that induce the Fritz distribution) were able to achieve violation.
+Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
+Specifically, the BFGS method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
+Despite our varied efforts, it remains unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
+More likely, this phenomena is due to a combination of both effects.
+
+    It is also worth reporting that the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:quantum_model_triangle} are restricted to maximally entangled states.
+This result resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} which demonstrates that entanglement and non-classicality are different resources.
+
+    % The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation.
+For $I_1$, deviations of $\chi \gtrsim 1.3$ inhibited convergence to violation.
+This is depicted in \cref{fig:initial_conditions}.
+
+    % \begin{figure}
+    % \begin{subfigure}[t]{.48\linewidth}
+    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
+    % \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
+    % \end{subfigure}
+    % \begin{subfigure}[t]{.48\linewidth}
+    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
+    % \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
+    % \end{subfigure}
+    % \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
+    % \end{figure}
+
+    The second inequality in consideration is the \textit{symmetric} inequality $I_3$ (\cref{eq:symmetic_web_inequality}).
+This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
+Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution.
+However, this result is far more surprising.
+Since the inequality is symmetric with respect to the permutation of parties, one would naively expect that the maximum violating distribution be symmetric as well.
+If it were not, one could construct a distribution that violates $I_3$ more by symmetrizing $\prob[\fritz]$ by summing over all possible permutations and normalizing.
+The symmetrized Fritz distribution is plotted in \cref{fig:symmetrized_fritz}.
+This distribution is also non-classical with relative violation $V_F = 3$.
+As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}.
+Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.
+
+    Finally for both $I_0$ and $I_2$, the maximum relative violation happens to be $V_F = 1$ (up to numerical precision).
+This means that the Fritz distribution either represents a local minimum of the parameter space or is in fact \textit{the} maximally violating distribution.
+Without further investigations, it remains unclear if this behavior is related to the universality of the Fritz distribution or if its an artifact of the methods used to derive $I_0$ and $I_2$.
+
+    \subsection{Rosset Variation}
+    \label{sec:rosset_variation}
+    \todo[TC]{This might take a page}
+
+    \section{Conclusions}
+    \label{sec:conclusions}
+    In \cref{sec:triangle_structure}, we elucidated that compatibility in the Triangle structure has been an unsolved problem for nearly a decade.
+Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality.
+Afterwards,~\citet{Henson_2014} were able to to classify the Triangle structure as \textit{interesting} which partially explains why it remains an enigma.
+Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the Triangle structure.
+Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality.
+In \cref{sec:fritz_distribution} the Fritz distribution was described in detail along with Fritz's Problem~\cite[Problem 2.17]{Fritz_2012}.
+
+    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum accessible distributions.
+This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) when applied to the Fritz distribution.
+In the context of Fritz's Problem, our result corresponds to a resolution to the following refinement of Fritz's original Problem.
+    \begin{enumerate}[label=\textbf{R.\arabic*}]
+        \setcounter{enumi}{0}
+        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
+    \end{enumerate}
+
+    Ultimately, this work accomplishes two important tasks.
+First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation technique specifically for quantum causal inference problems.
+The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure --- a task that no other existing techniques have succeeded at.
+In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure.
+Consequently, this work strongly indicates that the Inflation technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
+Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations.
+In conclusion \ref{r:1} has been positively solved through the derivation of the inequalities found in \cref{sec:found_inequalities}.
+
+    In consideration of out resolution to \ref{r:1}, we additionally propose two more refinements to Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
+    \begin{enumerate}[label=\textbf{R.\arabic*}]
+        \setcounter{enumi}{1}
+        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
+        \item \label{r:3} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
+    \end{enumerate}
+
+    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}.
+When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state.
+In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states.
+As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.}.
+The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
+Finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure.
+Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}).
+Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations.
+Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure.
+Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility.
+In summary, it remains unclear whether or not \ref{r:2} or \ref{r:3} is a harder problem or if either is even feasible.
+
+    \begin{acknowledgments}
+    This research was supported in part by Perimeter Institute for Theoretical Physics.
+Research at Perimeter Institute is supported by the Government of Canada through the Department of Innovation, Science and Economic Development Canada and by the Province of Ontario through the Ministry of Research, Innovation and Science.
+    \end{acknowledgments}
+
+    \appendix
+
+    \section{Summary of Inflation Technique}
+    \label{sec:inflation_technique}
+
+    \subsection{Satisfaction of d-Separation Relations}
+    \label{sec:satisfaction_of_d_sep_relations}
+    \todo[TC]{Absorb the relevant components of the next section into this one}
+    \todo[TC]{Given a distribution and a causal structure, does the distribution satisfy the conditional d-Separation relations?}
+
+    \subsection{Marginal Satisfiability and Inequalities}
+    \label{sec:marginal_satisfiability}
+    \label{sec:marginal_linear}\label{sec:linear_programs}
+
+    This section aims to explain how to solve the following decision problem: given a collection of probability distributions $\bc{\prob[V_1], \ldots, \prob[V_m]}$ where each set of variables $V_{i} \subseteq \jointvar$ is a subset of some complete set of variables $\jointvar$, does there exist a joint distribution $\prob[\jointvar]$ such that each $\prob[V_i]$ can be obtained by marginalizing $\prob[\jointvar]$ over the variables not in $V_i$, i.e.
+$\prob[V_i] = \sum_{\jointvar \setminus V_i} \prob[\jointvar]$?
+Colloquially, this problem is referred to as \term{the marginal problem}~\cite{Fritz_2011}.
+Additionally, this section aims to accomplish something further.
+If such as joint distribution $\prob[\jointvar]$ exists, how does one find it?
+Moreover, if a joint distribution does not exist, find an inequality that $\bc{\prob[V_1], \ldots, \prob[V_m]}$ fails which proves such a joint distribution does not exist.
+This is accomplished by illustrating how the marginal problem can be expressed as a linear program in which the solution to the marginal problem is encoded in the feasibility or infeasibility of said linear program.
+This section is presented prior to \cref{sec:inflation_technique_main_summary} as the marginal problem becomes an integral component of the Inflation Technique in subsequently deriving the inequalities presented in \cref{sec:found_inequalities}.
+Moreover, the Marginal problem is presented here logically independent from the remainder of the manuscript both for procedural clarity and because the marginal problem has applications to numerous areas of mathematics including game theory~\cite{Vorobev_1962}, database theory, knowledge integration of expert system, and of course, quantum information theory~\cite{Fritz_2011}.
+
+    To begin, several pieces of nomenclature will be introduced to facilitate discussions.
+First, the set $\mscenario = \bc{V \mid V \subseteq \jointvar}$ of subsets of $\jointvar$ is referred to as the \term{marginal scenario} and each element $V \in \mscenario$ is termed a \term{(marginal) context} of $\mscenario$.
+The complete set of marginal distributions is referred to as the \term{marginal model} and is denoted with an superscript $\prob^{\mscenario} \defined \bc{\prob[V] \mid V \in \mscenario}$.
+A marginal model acts as the most general description of a family of observations that can be made over $\jointvar$.
+Strictly speaking, as defined by~\cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that all subsets of contexts are also contexts: $\forall V \in \mscenario, V' \subset V : V' \in \mscenario$.
+Throughout this section, we exclusively consider (without loss of generality) the \textit{maximal} marginal scenario; restricting our focus to the largest contexts in the marginal scenario.
+Additionally, all marginal scenarios are taken to be \text{complete} in the sense that the marginal scenario covers the complete set of observable variables, i.e $\jointvar = \bigcup_{V \in \mscenario} V$.
+Finally, we henceforth assume that each variable $v \in \s J$ has a finite cardinality.
+
+    The marginal problem asks: given a marginal model $\prob^{\mscenario} = \bc{\prob[V] \mid V \in \mscenario}$ marginal to the joint variables $\jointvar$, does there exist a joint distribution $\prob[\jointvar]$ such that each context $\prob[V]$ can be obtained by marginalizing $\prob[\jointvar]$?
+    \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \eq \label{eq:def:marginal_problem}\]
+    A marginal model $\prob^{\mscenario}$ is said to be \textit{contextual} if it \textit{does not} admit a joint distribution and \textit{non-contextual} otherwise.
+Notice that \cref{eq:def:marginal_problem} is inherently a linear system of constraints which be solved rather efficiently using linear programs.
+In consideration of this, we will now endeavor to discuss how to cast the \cref{eq:def:marginal_problem} as a matrix multiplication equation so that it becomes possible to discuss existing methods for deriving constraints on the set of contextual marginal models.
+
+    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$.
+We also define the set of all \term{events over $v$}, denoted $\Events{v}$,\footnote{In the language of sheaf-theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
+Evidently, $\Events{v}$ and $O_v$ have a one-to-one correspondence and this distinction can be confounding.
+There is rarely any harm in referring synonymously to either as outcomes.
+Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
+    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetric_inequalities}.
+As a natural generalization we define the events over a set of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
+    \[ \Events{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
+    Each event $s$ can be compactly represented as a set of mappings over each element of $V$, i.e.
+$s = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k}$.
+The domain $\Dom{s}$ of an event $s$ is the set of random variables it valuates, i.e.
+if $s \in \Events{V}$, then $\Dom{s} = V$.
+Under this framework, a probability distribution $\prob[V]$ can be considered as a map from $\Events{V}$ to the unit interval $\bs{0,1}$.
+    The marginal problem inherently depends on the concept of probabilistic marginalization.
+This concept can be understood at the level of events; one event $s \in \Events{V}$ can be ``marginalized'' or restricted to a smaller event $s' \in \Events{W}$ whenever $W \subseteq V$.
+For every $W \subseteq V$ and $s \in \Events{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Events{W}$) is the event in $\Events{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$: $\forall v \in W : s|_{W}\br{v} = s\br{v}$.
+
+    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint events} $\Events{\jointvar}$ which represent all possible global events over the entire set of joint variables.
+Similarly, we define the \term{context events} for a particular context $V \in \mscenario$ as $\Events{V}$.
+Finally, we elect to define the \term{marginal events} as the disjoint union over all context events and by an abuse of notation we will denote this union as $\Events{\mscenario} = \coprod_{V \in \mscenario} \Events{V}$.
+Each marginal section $m \in \Events{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
+By construction each marginal event $m \in \Events{\mscenario}$ is a restriction of some joint event $j \in \Events{\jointvar}$.
+    % \subsubsection{Linear Programs}
+    % \label{sec:linear_programs}
+
+    The marginalization operation (\cref{eq:def:marginal_problem}) of the marginal problem is a linear operator.
+This linear operator maps a joint probability distribution $\prob[\jointvar] : \Events{\jointvar} \to \bs{0,1}$ into a marginal model $\prob^{\mscenario} = \bc{\prob[V] : \Events{V} \to \bs{0,1} \mid V \in \mscenario}$.
+Since $\Events{\mscenario}$ and $\Events{\jointvar}$ are finite, the marginal problem can be represented as a $\abs{\Events{\mscenario}} \times \abs{\Events{\jointvar}}$ matrix.
+
+    \begin{definition}
+        \label{def:incidence_matrix}
+        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} events $j \in \Events{\jointvar}$ and the rows are events by \textit{marginal} events $m \in \Events{\mscenario}$.
+The entries of $M$ are populated whenever a marginal event $m$ is a restriction of the joint event $j$.
+        \[ M_{m,j} \defined \begin{cases}
+            1 & m = j|_{\s{D}\br{m}} \\
+            0 & \text{otherwise}
+        \end{cases} \]
+        The incidence matrix has $\abs{\Events{\jointvar}}$ columns, $\abs{\Events{\mscenario}} = \sum_{i} \abs{\Events{V_i}}$ rows and $k\abs{\Events{\jointvar}}$ non-zero entries.
+    \end{definition}
+    To illustrate this concretely, consider the following example.
+Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{A,B,C}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{A,B}, \bc{B,C}, \bc{A,C}}$.
+The incidence matrix for $\mscenario$ is:
+    \[ M = \kbordermatrix{
+        (A,B,C) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
+        (A\mapsto0, B\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
+        (A\mapsto0, B\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
+        (A\mapsto1, B\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
+        (A\mapsto1, B\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
+        (B\mapsto0, C\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
+        (B\mapsto0, C\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
+        (B\mapsto1, C\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
+        (B\mapsto1, C\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
+        (A\mapsto0, C\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
+        (A\mapsto0, C\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
+        (A\mapsto1, C\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
+        (A\mapsto1, C\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
+    } \eq \label{eq:example_incidence}\]
+    The incidence matrix needs to act (to the right) on a vector representing the joint probability $\prob[\jointvar]$ distribution and outputs a vector representing the marginal model $\prob^{\mscenario}$.
+The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector indexed by joint events $j \in \Events{\jointvar}$ whose entries are populated by the probabilities that $\prob[\jointvar]$ assigns to each joint event: $\probvec^{\jointvar}_j = \prob[\jointvar][j]$.
+Analogously, \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Events{\mscenario}$: $\probvec^{\mscenario}_m = \prob[\Dom{m}][m]$.
+
+    By design, the marginal and joint distribution vectors are related via the incidence matrix $M$.
+Given a joint distribution vector $\probvec^{\jointvar}$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec^{\jointvar}$.
+    \[ \probvec^{\mscenario} = M \cdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
+    As a quick remark, the particular ordering of the rows and columns of $M$ carries \textit{no importance}, but it \textit{must} be consistent between $M$, $\probvec^{\jointvar}$ and $\probvec^{\mscenario}$.
+The marginal problem can now be rephrased in the language of the incidence matrix.
+Suppose one obtains a marginal distribution vector $\probvec^{\mscenario}$; the marginal problem becomes equivalent to the question: does there exist a joint distribution vector $\probvec^{\jointvar}$ such that \cref{eq:incidence_matrix_use} holds?
+This question is naturally framed as the \term{marginal linear program}:
+    \begin{alignat*}{2}
+        & \text{minimize:} \quad&& \emptyset \cdot x\\
+        & \text{subject to:} && x \succeq 0 \\
+        & && M \cdot x = \probvec^{\mscenario}
+    \end{alignat*}
+    If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries).
+The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:incidence_matrix_use} and is a valid joint distribution vector.
+Therefore, feasibility of the marginal linear program not only implies that $\probvec^{\jointvar}$ exists but returns $\probvec^{\jointvar}$.
+Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\probvec^{\jointvar}$.
+To every linear program, there exists a dual linear program that characterizes the feasibility of the original~\cite{Schrijver_1998}.
+Constructing the dual linear program is straightforward~\cite{Lahaie_2008}.
+    \begin{alignat*}{2}
+        & \text{minimize:} \quad&& y \cdot \probvec^{\mscenario}\\
+        & \text{subject to:} && y \cdot M \succeq 0
+    \end{alignat*}
+
+    The dual marginal linear program not only answers the marginal problem for a specific marginal model $\probvec^{\mscenario}$ but as a by-product provides an inequality that witnesses its contextuality.
+If this is not obvious, first notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints become satisfied.
+Secondly if the dual constraint $y \cdot M \succeq 0$ holds \textit{and} the primal is feasible, then $y \cdot \probvec^{\mscenario} =  y \cdot M \cdot x \geq 0$.
+Therefore the \textit{sign} of the dual objective $d \defined \min \br{y \cdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality; if $d < 0$ then $y \cdot \probvec^{\mscenario} \geq 0$ is violated and therefore $\probvec^{\mscenario}$ is contextual.
+Likewise if $d \geq 0$ (satisfying $y \cdot \probvec^{\mscenario}$), then $\probvec^{\mscenario}$ is non-contextual.\footnote{Actually, if $d \geq 0$ then it is exactly $d = 0$ due to the existence of the trivial $y = \emptyset$.
+This observation is an instance of the \textit{Complementary Slackness Property} of~\cite{Bradley_1977}.
+Moreover, if $d < 0$, then it is unbounded $d = -\inf$.
+This latter point becomes clear upon recognizing that for any $y$ with $d < 0$, another $y' = \al y$ can be constructed (with $\al > 1$) such that $d' = \al d < d$.
+Since a more negative $d'$ can always be found, it must be that $d$ is unbounded.
+This is a demonstration of the fundamental \textit{Unboundedness Property} of~\cite{Bradley_1977}; if the dual is unbounded, then the primal is infeasible.} This is manifestation of Farkas's lemma~\cite{Schrijver_1998}.
+An \term{infeasibility certificate}~\cite{Andersen_2001} is any vector $y$ that satisfies the $y \cdot M \succeq 0$.
+Most linear program software packages such as Mosek~\cite{Mosek_2016}, Gurobi~\cite{Gurobi_2016}, CPLEX~\cite{Cplex_2016} and CVX/CVX OPT~\cite{CVX_2016,CVX_Opt_2016} are capable of producing infeasibility certificates.
+Furthermore, for every $y$ satisfying $y \cdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of non-contextual marginal models.
+If $y$ is an infeasibility certificate, then $y \cdot \probvec^{\mscenario} \geq 0$ is satisfied by all contextual marginal models.
+
+    The marginal problem can sometimes take on a more general variant that does not begin with a specific marginal model~\cite{Abramsky_2012,Mansfield_2012,Fritz_2011}: \textit{Given a marginal scenario $\mscenario$, what is the set of all non-contextual marginal models?} \citet{Pitowsky_1991} demonstrates that the set of non-contextual marginal models forms a \textit{convex} polytope called the \term{marginal polytope}.
+The extremal rays of a marginal polytope directly correspond to the columns of $M$ which further correspond to \textit{deterministic} joint distributions $\probvec^{\jointvar}$.
+Since all joint distributions $\probvec^{\jointvar}$ are probability distributions, their entries must sum to unity $\sum_{j \in \Events{\jointvar}} \probvec^{\jointvar}_j = 1$.
+This normalization defines the convexity of the polytope; all non-contextual marginal models are convex mixtures of the deterministic marginal models pursuant to \cref{eq:incidence_matrix_use}.
+The marginal polytope is a beneficial tool for understanding contextuality.
+First, the \textit{facets} of a marginal polytope correspond to a finite set of linear inequalities that are complete in the sense that all contextual distributions violate at least one facet inequality~\cite{Brunner_2013}.
+From the perspective of a marginal polytope, convex hull algorithms or linear quantifier elimination can be used to compute a representation of the complete set of linear inequalities and completely solve the marginal problem.
+A popular tool for linear quantifier elimination is \term{Fourier-Motzkin elimination} \cite{Dantzig_1973,Inflation,Abramsky_2012,jones_2004}.
+Applying the Fourier-Motzkin procedure to completely solve the marginal problem is discussed in more detail in \citet{Fritz_2011}.
+An excellent survey of existing techniques for solving the marginal problem including Equality Set Projection~\cite{jones_2004} and Hardy-type hypergraph transversals can be found in \citet{Inflation}.
+In conclusion, there are a number of computational tools available to solve the marginal problem completely whenever no marginal model is provided.
+
+    Each of the above mentioned techniques suffers from computational complexity limitations.
+For example, the Fourier-Motzkin procedure is in the worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}.
+For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable.
+This will become apparent in \cref{sec:exemplary_inflations_of_the_triangle structure} when the Inflation Technique is applied to the Triangle structure, producing marginal models that are very large.
+Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
+    \subsection{Inflation Technique}
+    \label{sec:deriving_inequalities}
+    \label{sec:inflation_technique_main_summary}
+    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$.
+As a preliminary summary, the Inflation Technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
+As a example, four inflations of the Triangle structure are depicted in \cref{fig:inflations}.
+Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}.
+For example, node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the inflated causal structure in \cref{fig:the_web_inflation}.
+All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
+A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
+    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
+    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index.
+In addition to the common graph-theoretic terminology and notation presented in \cref{sec:causal_compatibility}, we define two more concepts necessary to formally define an inflation of $\graph$.
+First, an \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$: $\Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to m} \mid n, m \in N}}$.
+An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$: $\AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}}$.
+
+    \begin{definition}
+        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
+        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
+    \end{definition}
+    Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is equivalent to its counterpart in $\graph$ up to copy-index.
+The motivation behind this definition is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible distribution $\prob[N]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
+To do this, first notice that for every distribution $\prob[N]$ compatible with $\graph$, there must exist a set of causal parameters $\{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes\}$ for $\graph$ such that $\prob[N] = \prod_{n \in N} \prob[n\mid \Pa[\graph]{n}]$.
+Since the inflation criteria (\cref{eq:inflation_defn}) requires that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$ one can create a set of \term{inflated causal parameters} by matching causal parameters according to respective copy-indices.
+    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \eq \label{eq:inflated_causal_parameters} \]
+    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course, there exists compatible joint distributions on $\nodes'$ that can not be constructed in this manner.
+The claim is that all joint distributions that are constructed in this way are compatible.}.
+    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \eq \label{eq:unique_causal_parameters_inflated}\]
+    % \cref{eq:unique_causal_parameters,eq:inflated_causal_parameters,eq:unique_causal_parameters_inflated}
+    Together, ??
+form the \term{weak inflation lemma}: compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$.
+Before generalizing to the inflation lemma, a careful observation needs to be made.
+For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$, where $N \subset \nodes$, induces a compatible marginal distribution $\prob[N']$ over $N'$.
+In fact, $N'$ must contain no duplicate nodes up to copy index and thus $\prob[N] = \prob[N']$.
+These subsets of nodes are so essential to the Inflation Technique they are assigned a special name: sets $N' \subseteq \nodes'$ as called the \term{injectable sets} of $\graph'$ and $N \subset \nodes$ the \term{images of the injectable sets} of $\graph$.
+    \begin{align*}
+        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
+        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
+    \end{align*}
+    Injectable sets are incredibly useful for causal compatibility because they allow one to extend the weak inflation lemma to \textit{the} inflation lemma:
+    \todo[TC]{How do I claim the inflation lemma without defining compatibility over a marginal model (instead of a distribution)}
+    \begin{lemma}
+        \label[lemma]{lem:inflation}
+        \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+    \end{lemma}
+    Diagrammatically, \cref{lem:inflation} can be visualized as follows:
+
+    \begin{center}
+        \begin{tikzpicture}
+            \pgfmathsetmacro{\vs}{2.2};
+            \pgfmathsetmacro{\hs}{5.2};
+            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
+            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
+            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
+            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
+            \draw[very thick, ->] (pn) -- (cp);
+            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
+            \draw[very thick, ->] (cp_) -- (pn_);
+        \end{tikzpicture}
+    \end{center}
+
+    The inflation lemma is the most important result of the causal Inflation Technique.
+The contrapositive version of \cref{lem:inflation} is a powerful tool for deriving causal compatibility constraints.
+Any causal compatibility constraint, such as a causal compatibility inequality, that constrains injectable marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ can be \textit{deflated} into a valid compatibility constraint on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure by dropping all references to the copy-indices.
+Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
+Therefore, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
+
+    Heretofore, the Inflation Technique as stated by \cref{lem:inflation} does not facilitate the derivation of any non-trivial inequalities.
+The Inflation lemma simply casts causal inference problems on $\graph$ to causal inference problems on $\graph'$.
+Fortunately, an inflated causal structure $\graph'$ possesses its own conditional independence relations which can be exploited to turn linear inequalities on $\graph'$ into polynomial inequalities on $\graph$.
+
+    Suppose that one were to obtain an inequality on $\graph'$ that contained probabilistic terms such as $\prob[N']$ where $N' \not \in \Inj[\graph]{\graph'}$.
+At this point, the Inflation lemma is not applicable because it requires probabilistic constraints to consist entirely of distributions $\prob[N']$ where $N'$ is injectable.
+If for example, $N' \not \in \Inj[\graph]{\graph'}$ could be partitioned into two injectable subsets $N_1' \in \Inj[\graph]{\graph'}$ and $N_2' \in \Inj[\graph]{\graph'}$ that where \term{ancestrally independent} in $\graph'$,
+    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
+    Then the compatible marginal context $\prob[N']$ must be probabilistically separable $\prob[N'] = \prob[N_1']\prob[N_2']$ due to \cref{eq:local_markov_property}.
+Since $N_1'$ and $N_2'$ are both injectable, the inflation lemma now applies and the original inequality can be deflated.
+
+    \begin{center}
+        \begin{tikzpicture}[scale=0.8]
+            \pgfmathsetmacro{\hs}{1.4};
+            \pgfmathsetmacro{\vs}{0.6};
+            \pgfmathsetmacro{\cross}{0.2};
+            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
+            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
+            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
+            \draw (2*\hs, 4*\vs + 0.7*\vs) node[]{$N_1' \cup N_2' = N$};
+            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
+            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
+            \draw (0, 0) node[](b){??};
+            \draw[thick, ] (a) -- (ab);
+            \draw[thick, ] (c) -- (cd);
+            \draw[thick, ] (a) -- (ac);
+            \draw[thick, ->] (ac) -- (c);
+            \draw[thick, ->] (ab) -- (b);
+            \draw[thick, ->] (cd) -- (d);
+            \draw[very thick, red]
+            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
+            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
+            ;
+        \end{tikzpicture}
+    \end{center}
+
+    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that can are called the \term{pre-injectable sets}.
+A set $N' \subseteq \nodes'$ is a pre-injectable set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
+
+    A pre-injectable set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to graphical $d$-separation conditions~\cite{Pearl_2009},
+    \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
+    Application of the inflation lemma to linear inequalities constraining pre-injectable distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
+Throughout the body of this work, we let $\PreInj[\graph]{\graph'}$ denote the set of all pre-injectable sets.
+Naturally, the pre-injectable sets will define a marginal scenario $\mscenario$ that are used to derive compatibility inequalities in \cref{sec:deriving_inequalities}\footnote{Analogously for a marginal scenario $\mscenario$, the pre-injectable sets $\PreInj[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
+Therefore, in practice, it is completely sufficient to focus on the maximal pre-injectable sets}.
+
+    \subsection{Exemplary Inflations of The Triangle Structure}
+    \label{sec:exemplary_inflations_of_the_triangle structure}
+
     \begin{equation*}
@@
 
-    In summary, these causal compatibility inequalities represent a completion of objective \cref{r:1} from \cref{sec:fritz_distribution}.
-These inequalities are derived without making use of Bell's theorem and instead use the Inflation Technique which is completely independent of Bell's theorems.
-Additionally, the derivation of causal compatibility inequalities allows one prove incompatibility even when perfect correlations are absent.
-Moreover, they allow one to probe the amount of noise the Fritz distribution can sustain before becoming compatible (see \cref{sec:violations_noise}).
-Unfortunately, infeasibility certificates are found by linear programing software to certify the infeasibility of a \textit{particular distribution}.
-This means that inequalities like \cref{eq:ww_ineq}, the one presented in \cref{eq:web_inequality}, and others are specifically manufactured in order witness a particular type of quantum non-classicality.
-In an effort to derive inequalities that could lead to potentially new forms of non-classicality, we searched for inequalities that did not admit biased towards the Fritz distribution.
-
-    The following is a causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was derived using the Web inflation of \cref{fig:the_web_inflation}.
-    \begin{equation}
-        \label{eq:web_inequality}
-        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
-    \end{equation}
-    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
-    The following is a symmetric causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was derived using the Web inflation of \cref{fig:the_web_inflation}.
-    \begin{equation}
-        \label{eq:symmetic_web_inequality}
-        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
-    \end{equation}
-    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for the sum over permutations:
-    \[ \bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033) \]
-
-    \section{Numerical Optimizations \& Noisy Distributions}
-    \label{sec:violations_noise}
-    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality.
-In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities.
-In order to compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ so $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
-For the subsequent analysis, $4$ inequalities where chosen.
-First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}.
-The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{eq:web_inequality} while $I_3$ is the symmetric inequality in \cref{eq:symmetic_web_inequality}.
-Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{eq:web_inequality}.
-
-    \subsection{Noisy Distributions}
-    \label{sec:noise}
-    % \begin{figure}
-    % \begin{center}
-    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
-    %         \vspace{-0.2in}
-    %         \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
-    %         \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
-    %         \label{fig:uniform_distribution}
-    % \end{center}
-    % \end{figure}
-    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality.
-As was mentioned in \cref{sec:fritz_distribution}, this embedding required a very idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$.
-From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}.
-It is possible to minimize noise by developing more accurate measurement channels but perfect correlations are too idealistic.
-Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.
-
-    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$.
-Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible.
-We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
-    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
-    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$.
-For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.
-Our tests suggest that inequality $I_1$ (\cref{eq:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
-The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}.
-Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I_1$.
-
-    % Given that $I_0, I_1, I_2, I_3$ are far from a representative inequalities and are likely not facets of any inflated marginal polytope, it is save to say that this is possible.
-
-    % \begin{figure}
-    % \begin{subfigure}[b]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}}
-    % \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}}
-    % \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
-    % \end{subfigure}
-    % \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
-    % \end{figure}
-
-    % The results of our experiments are plotted in \cref{fig:master_noise}.
-\Cref{fig:noise} illustrates that each curve $I\br{\s{N}_{\vep}\br{\prob[\fritz]}}$ as a function of $\vep$ is monotonically increasing as expected; the more noise added to the probability distribution, the more classical it becomes.
-\Cref{fig:noise_zoomed} is the same plot as \cref{fig:noise} zoomed onto the interval $\vep \in \bs{0, 0.12}$.
-
-    \begin{figure}
-    \begin{center}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
-            \vspace{-0.2in}
-            \[ \probplotvalue{255, 255, 243} = 0.00133 \]
-            \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
-            \label{fig:noisy_fritz}
-    \end{center}
-    \end{figure}
-
-    \subsection{Numerical Optimizations}
-    \label{sec:optimizations}
-    Causal compatibility inequalities act as a \textit{measure} of non-classicality.
-If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$.
-However, this statement is accompanied by a few caveats.
-First, it is possible (and frequently the case) for ${I\br{\prob[1]}} < I\br{\prob[2]}$ to hold for one inequality $I$ but have ${\ti I\br{\prob[2]}} < \ti I\br{\prob[1]}$ hold for another inequality $\ti I$.
-In this case, all one can claim is that $\prob[1]$ is more incompatible than $\prob[2]$ with respective to $I$ but the contrary is true with respect to $\ti I$.
-Second, not all inequalities $I$ are \textit{good} measures of non-classicality.
-In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality because the facets form a necessary and sufficient of constraints with all other inequalities following from positive mixtures.
-However, good measures of incompatibility are less understood in the Triangle structure where the space of classical correlations is non-convex.
-At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility simply because they have be curated toward the Fritz distribution.
-Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure.
-
-    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle Structure \cref{fig:triangle_structure} and thus expressed as follows:
-    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
-    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately.
-In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
-In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
-Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states.
-Qubit states are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix.
-Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
-First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure.
-Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$.
-Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
-    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]
-
-    Although there are numerous techniques that can used when parameterizing quantum states and measurements~\cite{Petz_2015, Hedemann_2013,Fujii_2005,James_2001,Grasmair_2014,Neilsen_Chaung_2011}, a single technique by \citet{Spengler_2010_Unitary} was found to be most computationally suitable for our purposes.
-\Citet{Spengler_2010_Unitary} demonstrated that all $d\times d$ unitary matrices $U$ can be parameterized without degeneracy as follows:
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
-    Where the real valued parameters $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ have periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
-Moreover, $P_l$ are one-dimensional projective operators $P_l = \ket{l}\bra{l}$ and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices $\sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m}$ where $1 \leq m < n \leq d$.
-This parameterization has the useful feature that each of the real-valued parameters $\la_{n,m}$ a direct and intuitive physical affect on each element of a computational basis $\bc{\ket{1}, \ldots, \ket{d}}$.
-Explicitly, $\exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$.
-Analogously, $\exp\br{i P_n \lambda_{n,m}}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $\exp\br{iP_l \lambda_{l,l}}$ fixes the global phase of $\ket{l}$.
-Finally, although not explicitly mentioned in~\cite{Spengler_2010_Unitary}, it is possible to remove the reliance on the computationally expensive matrix exponential operations in \cref{eq:spengler_unitary}~\cite{Moler_2003}.
-
-    By parameterizing unitary matrices, it becomes possible to parameterize $d$-dimensional density matrices and $d$-element PVMs by recognizing that any orthonormal basis $\bc{\ket{\psi_j}}$ (where $1 \leq j \leq d$) can be transformed into the computational basis $\bc{\ket{j}}$ by a unitary transformation $U$, i.e.
-$U \ket{\psi_j} = \ket{j}$.
-First consider a $d$-element PVM $M = \bc{\ket{m_j}\bra{m_j} \mid 1 \leq j \leq d}$.
-Since $\bc{\ket{m_j}}$ forms an orthonormal basis, one can parameterize $M$ by writing $M = \bc{U^{\dagger}\ket{j}\bra{j}U \mid 1 \leq j \leq d}$ and parameterizing $U$ using \cref{eq:spengler_unitary}.
-This method was inspired by the measurement seeding method for iterative optimization used by \citet{Pal_2010}.
-Analogously, this argument can be extended to full-rank $d$-dimensional density matrices $\rho$ by performing a spectral decomposition $\rho = \sum_{j=1}^{d} p_j \ket{p_j} \bra{p_j}$ into eigenvalues $\bc{p_j}$ and eigenstates $\bc{\ket{p_j}}$.
-Since $\Tr\br{\rho} = \sum_{j = 1}^{d} p_j = 1$ the eigenvalues of $\rho$ are parameterized without degeneracy using a tuple of $d-1$ real-valued parameters with periodicity $\bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}.
-Additionally, since $\rho$ is Hermitian, the eigenstates $\bc{\ket{p_j}}$ form an orthonormal basis and therefore the eigenstates are analogously parameterized using \cref{eq:spengler_unitary}: $\rho = \sum_{j=1}^{d} p_j U^{\dagger} \ket{j} \bra{j} U$.
-For our purposes, we have set $d = 4$ and fixed $\la_{l, l} = 0$ for $1 \leq l \leq d$ in \cref{eq:spengler_unitary} because the global phase contributions are irrelevant for \cref{eq:quantum_model_triangle_pvms}.
-
-    % \Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}.
-Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.
-
-    % the a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}.
-Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:quantum_model_triangle} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$.
-The objective value is simply the degree of violation $f = I\br{\prob[ABC]}$ and used to make adjustments to $\la$ in order to achieve largest and larger violations.
-
-    % \subsection{Parameterizing Quantum Distributions}
-    % \begin{figure}
-    % \begin{center}
-    %         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
-    %         \caption{The Triangle structure as modeled by quantum states and measurements.}
-    %         \label{fig:triangle_structure_quantum_model}
-    % \end{center}
-    % \end{figure}
-
-    % \subsection{Numerical Optimization Results}
-
-    \begin{figure}
-    \begin{center}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
-            \caption{Probability distribution that maximizes violation of $I_1$ from \cref{eq:web_inequality} ($V_F \simeq 1.501$).}
-            \label{fig:maximum_violation_I_1}
-    \end{center}
-    \end{figure}
-    \begin{figure}
-    \begin{center}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
-            \caption{Probability distribution that maximizes violation of $I_3$ from \cref{eq:symmetic_web_inequality} ($V_F \simeq 2.61$).}
-            \label{fig:maximum_violation_I_3}
-    \end{center}
-    \end{figure}
-    \begin{figure}
-    \begin{center}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
-            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
-            \label{fig:symmetrized_fritz}
-    \end{center}
-    \end{figure}
-
-    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
-$V_F \defined \min_{P}\bc{I\br{P}}/I\br{P_F}$.
-The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{eq:web_inequality}.
-At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
-Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution.
-In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure}, i.e.
-the same set of possible events.
-This result is not entirely unexpected.
-As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure.
-Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.
-
-    An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization.
-Above it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
-Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to inequality \textit{saturation} instead of inequality \textit{violation} which is achievable by the Fritz distribution $\prob[\fritz]$.
-Instead, it was observed that only parameters close enough to the \textit{Fritz parameters} (i.e.
-any non-unique set of parameters that induce the Fritz distribution) were able to achieve violation.
-Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
-Specifically, the BFGS method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
-Despite our varied efforts, it remains unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
-More likely, this phenomena is due to a combination of both effects.
-
-    It is also worth reporting that the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:quantum_model_triangle} are restricted to maximally entangled states.
-This result resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} which demonstrates that entanglement and non-classicality are different resources.
-
-    % The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation.
-For $I_1$, deviations of $\chi \gtrsim 1.3$ inhibited convergence to violation.
-This is depicted in \cref{fig:initial_conditions}.
-
-    % \begin{figure}
-    % \begin{subfigure}[t]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
-    % \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
-    % \end{subfigure}
-    % \begin{subfigure}[t]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
-    % \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
-    % \end{subfigure}
-    % \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
-    % \end{figure}
-
-    The second inequality in consideration is the \textit{symmetric} inequality $I_3$ (\cref{eq:symmetic_web_inequality}).
-This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
-Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution.
-However, this result is far more surprising.
-Since the inequality is symmetric with respect to the permutation of parties, one would naively expect that the maximum violating distribution be symmetric as well.
-If it were not, one could construct a distribution that violates $I_3$ more by symmetrizing $\prob[\fritz]$ by summing over all possible permutations and normalizing.
-The symmetrized Fritz distribution is plotted in \cref{fig:symmetrized_fritz}.
-This distribution is also non-classical with relative violation $V_F = 3$.
-As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}.
-Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.
-
-    Finally for both $I_0$ and $I_2$, the maximum relative violation happens to be $V_F = 1$ (up to numerical precision).
-This means that the Fritz distribution either represents a local minimum of the parameter space or is in fact \textit{the} maximally violating distribution.
-Without further investigations, it remains unclear if this behavior is related to the universality of the Fritz distribution or if its an artifact of the methods used to derive $I_0$ and $I_2$.
-
-    \subsection{Rosset Variation}
-    \label{sec:rosset_variation}
-    \todo[TC]{This might take a page}
-
-    \section{Conclusions}
-    \label{sec:conclusions}
-    In \cref{sec:triangle_structure}, we elucidated that compatibility in the Triangle structure has been an unsolved problem for nearly a decade.
-Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality.
-Afterwards,~\citet{Henson_2014} were able to to classify the Triangle structure as \textit{interesting} which partially explains why it remains an enigma.
-Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the Triangle structure.
-Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality.
-In \cref{sec:fritz_distribution} the Fritz distribution was described in detail along with Fritz's Problem~\cite[Problem 2.17]{Fritz_2012}.
-
-    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum accessible distributions.
-This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) when applied to the Fritz distribution.
-In the context of Fritz's Problem, our result corresponds to a resolution to the following refinement of Fritz's original Problem.
-    \begin{enumerate}[label=\textbf{R.\arabic*}]
-        \setcounter{enumi}{0}
-        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
-    \end{enumerate}
-
-    Ultimately, this work accomplishes two important tasks.
-First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation technique specifically for quantum causal inference problems.
-The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure -- a task that no other existing techniques have succeeded at.
-In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure.
-Consequently, this work strongly indicates that the Inflation technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
-Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations.
-In conclusion \ref{r:1} has been positively solved through the derivation of inequalities such as \cref{eq:ww_ineq} and those found in \cref{sec:web_inequalities}.
-
-    In consideration of out resolution to \ref{r:1}, we additionally propose two more refinements to Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
-    \begin{enumerate}[label=\textbf{R.\arabic*}]
-        \setcounter{enumi}{1}
-        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
-        \item \label{r:3} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
-    \end{enumerate}
-
-    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}.
-When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state.
-In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states.
-As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.}.
-The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
-Finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure.
-Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}).
-Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations.
-Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure.
-Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility.
-In summary, it remains unclear whether or not \ref{r:2} or \ref{r:3} is a harder problem or if either is even feasible.
-
-    \begin{acknowledgments}
-    This research was supported in part by Perimeter Institute for Theoretical Physics.
-Research at Perimeter Institute is supported by the Government of Canada through the Department of Innovation, Science and Economic Development Canada and by the Province of Ontario through the Ministry of Research, Innovation and Science.
-    \end{acknowledgments}
-
-    \appendix
-
-    \section{Summary of Inflation Technique}
-    \label{sec:inflation_technique}
-
-    \subsection{Satisfaction of d-Separation Relations}
-    \label{sec:satisfaction_of_d_sep_relations}
-    \todo[TC]{Absorb the relevant components of the next section into this one}
-    \todo[TC]{Given a distribution and a causal structure, does the distribution satisfy the conditional d-Separation relations?}
-
-    \subsection{Marginal Satisfiability and Inequalities}
-    \label{sec:marginal_satisfiability}
-    \label{sec:marginal_linear}\label{sec:linear_programs}
-
-    Given a set of observable variables $\jointvar = \bc{v_1, \ldots, v_k}$ where each $v \in \jointvar$ is a statistical random variable, one can conceivably make a measurement over of these variables and obtain a joint probability distribution $\prob[\jointvar] = \prob[v_1,\ldots,v_n]$.
-More generally however, and depending on the context, it is possible to make a measurement on a set of the system $V \subset \jointvar$ in order to obtain a marginal distribution $\prob[V]$.
-With complete generality however, one could in principle be limited so as to only be able to record observations on portions of the system $\mscenario = \bc{V_1, \ldots, V_m \mid \forall i : V_i \subseteq \jointvar}$ obtaining a collection of marginal probability distributions $\bc{\prob[V_1], \ldots, \prob[V_m] \mid \forall i: V_i \in \mscenario}$.
-
-    The set $\mscenario = \bc{V \mid V \subseteq \jointvar}$ of subsets of $\jointvar$ is referred to as the \term{marginal scenario} and each element $V \in \mscenario$ is termed a \term{(marginal) context} of $\mscenario$.
-The complete set of marginal distributions is referred to as the \term{marginal model} and is denoted with an superscript $\prob^{\mscenario}$:
-    \[ \prob^{\mscenario} = \bc{\prob[V] \mid V \in \mscenario} \]
-    A marginal model acts as the most general description of a family of observations that can be made over $\jointvar$.
-Strictly speaking, as defined by~\cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that all subsets of contexts are also contexts.
-    \[ \forall V \in \mscenario, V' \subset V : V' \in \mscenario \]
-    Throughout this document, we exclusively consider (without loss of generality) the \textit{maximal} marginal scenario; restricting our focus to the largest contexts in the marginal scenario.
-Additionally, all marginal scenarios are taken to be \text{complete} in the sense that the marginal scenario covers the complete set of observable variables $\jointvar$.
-    \[ \jointvar = \bigcup_{V \in \mscenario} V \]
-
-    % For a causal structure $\graph$, a chosen specification of a conditional distributions for each variable  is referred to as a set of \term{causal parameters for $\graph$}:
-    % \[  \eq \label{eq:causal_parameters} \]
-    It is important to note that a set of causal parameters is not unique; the numerical nature of set of causal parameters is a \text{choice}.
-Altogether, a marginal model $\prob^{\mscenario}$ is \term{compatible} with a causal structure $\graph$ if there exists a choice of causal parameters such that each context $\prob[V] \in \prob^{\mscenario}$ can be \textit{recovered} from the following series of operations:
-    \begin{enumerate}
-        \item Obtain a joint probability distribution over \textit{all} variables of the causal structure using the chosen casual parameters:\footnote{Here $\prod$ denotes the product distribution $\prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = $.}
-        \item Marginalize over the latent variables of $\graph$ to obtain a joint distribution over the observed variables $\nodes_O$:
-        \[ \prob[\nodes_O] = \sum_{\nodes_L} \prob[\nodes] \eq \label{eq:observable_marginalization} \]
-        \item Finally marginalize over the observed nodes not in $V$ to obtain $\prob[V]$:
-        \[ \prob[V] = \sum_{\nodes_O \setminus V} \prob[\nodes_O] \eq \label{eq:context_marginalization} \]
-    \end{enumerate}
-    It is important to note that compatibility between $\prob^{\mscenario}$ and $\graph$ requires that it is possible to recover \textit{each} context $\prob[V] \in \prob^{\mscenario}$ from the \textit{same} set of causal parameters.
-If it is not possible for $\prob^{\mscenario}$ to be recovered for \textit{any} choice of causal parameters, then $\prob^{\mscenario}$ is \term{incompatible}.
-    In \cref{sec:causal_compatibility}, we defined the notion of a causal compatibility inequality without providing a means for deriving/computing them.
-This section aims to delineate algorithms and methods that can be used to derive causal compatibility inequalities for generic causal inference problems.
-Recalling the definition of causal compatibility presented in \cref{sec:causal_compatibility}, a marginal model $\prob^{\mscenario}$ is compatible with a causal structure $\graph = \br{\nodes, \edges}$ if it can be recovered from a series of operations.
-First choose a set of causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ and then construct a joint distribution $\prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}]$ over all nodes $\nodes$ (this step is \cref{eq:local_markov_property_operation}).
-Afterwards, each marginal distribution $\prob[V] \in \mscenario$ should be recoverable from a marginalization over $\prob[\nodes]$ (this step is the combination of \cref{eq:observable_marginalization,eq:context_marginalization}).
-Intuitively, these two requirements for a compatible marginal model $\prob^{\mscenario}$ provide two necessary components of compatibility:
-    \begin{enumerate}
-        \item The marginal model $\prob^{\mscenario}$ must admit a joint distribution $\prob[\nodes]$ (\cref{eq:observable_marginalization,eq:context_marginalization}).
-        \item The joint distribution $\prob[\nodes]$ must satisfy the Markov separability criteria (\cref{eq:local_markov_property_operation}).
-    \end{enumerate}
-    In practice, this is the natural order in which to classify the compatibility of a marginal model $\prob^{\mscenario}$.
-First check if the marginal model admits a joint distribution and if and only if it does, determine whether or not the local Markov property can be satisfied for some choice of causal parameters.
-Intuitively, there are two reasons why a given marginal model $\prob^{\mscenario}$ would be deemed incompatible.
-One possibility is that the marginal model $\prob^{\mscenario}$ does not admit a joint distribution $\prob[\nodes]$.
-Alternatively, it could be possible that a joint distribution $\prob[\nodes]$ exists but can not factor into causal parameters as per \cref{eq:local_markov_property_operation}.
-
-    Colloquially, the first necessary condition, namely the existence (or non-existence) of a joint distribution, is referred to as \term{the marginal problem}.
-The marginal problem asks: given a marginal model $\prob^{\mscenario} = \bc{\prob[V] \mid V \in \mscenario}$ marginal to the joint variables $\jointvar = \bigcup_{V \in \mscenario} V$, does there exist a joint distribution $\prob[\jointvar]$ such that each context $\prob[V]$ can be obtained by marginalizing $\prob[\jointvar]$?
-    \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \eq \label{eq:def:marginal_problem}\]
-    Note that we have changed notation from the nodes of a causal structure $\nodes$ to a joint set of variables $\jointvar$.
-This is done simply because the marginal problem is well-defined independent of a given causal structure.
-In fact, if a marginal model $\prob^{\mscenario}$ does not admit a joint distribution, then it cannot be compatible with \textit{any} causal structure whatsoever.
-A marginal model is said to be \textit{contextual} if it \textit{does not} admit a joint distribution and \textit{non-contextual} otherwise.
-The marginal problem has applications to numerous areas of mathematics including game theory~\cite{Vorobev_1962}, database theory, knowledge integration of expert system, and of course, quantum information theory~\cite{Fritz_2011}.
-
-    The marginal problem is distinct from the second necessary condition, which we term the \term{Markov separability problem} in numerous ways.
-First of all, the marginal problem as applied to causal inference tasks is only concerned with the observable variables $\nodes_{O}$ of $\graph$.
-This differs from the Markov separability problem which depends directly on the entire graphical structure of $\graph$ and thus must include the latent variables $\nodes_{L}$.
-The purpose of latent variables is to have unspecified behavior which makes checking the local Markov property exceedingly difficult in comparison to the marginal problem.
-Secondly, \cref{eq:def:marginal_problem} is inherently a linear system of constraints which be solved rather efficiently using linear programs (to be discussed in \cref{sec:marginal_linear}).
-The local Markov property concerns itself with probabilistic independence constraints which are polynomial.
-Fortunately, the Inflation Technique (summarized in \cref{sec:inflation_technique}) is able to cast (at least partially) the Markov separability problem as a marginal problem over an inflated causal structure.
-As such the Inflation Technique in many ways can be considered a relaxation technique which turns polynomial constraints into linear constraints.
-
-    In consideration of these observations, we will now endeavor to discuss how causal compatibility inequalities can be derived by casting the marginal problem as a linear program.
-After doing, it becomes possible to discuss existing methods for deriving constraints on the set of contextual marginal models.
-
-    Heretofore, our discussions of compatibility and the marginal problem have been general in the sense of making no reference to the nature the random variables $v \in \jointvar$.
-In particular, whether the outcomes of $v$ are discrete or continuous, finite or unbounded, or otherwise.
-In the case of infinite outcomes, the marginal problem can be used to derive entropic inequalities defined over the mutual information between variables $v \in \jointvar$~\cite{Fritz_2011}.
-Entropic inequalities however have been shown to be less constraining than inequalities defined over variables with finite cardinality~\cite{Inflation}.
-Throughout this document, we restrict our attention to finite outcomes.
-To assist with the subsequent analysis, we recall some familiar notions of probability theory.
-
-    % \subsubsection{Events \& Outcomes}
-    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$.
-We also define the set of all \term{events over $v$} $\Events{v}$\footnote{In the language of sheaf-theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
-    \[ \Events{v} \defined \bc{s : \bc{v} \to O_v} \]
-    Evidently, $\Events{v}$ and $O_v$ have a one-to-one correspondence and this distinction can be confounding.
-There is rarely any harm in referring synonymously to either as outcomes.
-Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
-    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetric_inequalities}.
-As a natural generalization we define the event over a collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
-    \[ \Events{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
-    Each event $s$ can be compactly represented as a set of mappings over each element of $V$.
-    \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
-    The domain $\Dom{s}$ of an event $s$ is the set of random variables it valuates, i.e.
-if $s \in \Events{V}$, then $\Dom{s} = V$.
-Under this framework, a probability distribution $\prob[V]$ can be considered as a map from $\Events{V}$ to the unit interval $\bs{0,1}$.
-    \begin{example}
-        Let $s \in \Events{V}$ be an event over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$.
-Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$.
-Furthermore let $f \in \Events{V}$ be the event $\br{v_1 \mapsto 2, v_2 \mapsto 1}$.
-The following notations are interchangeable,
-        \[ \prob[][s] = \prob[\Dom{s}][s] = \prob[V][s] = \prob[v_1, v_2][s] = \prob[][v_1 \mapsto s_1\br{v_1}, v_2 \mapsto s_2\br{v_2}] = \prob[][v_1 = 2, v_2 = 1] = \prob[v_1v_2][21] \]
-        Each of which should be read as ``the probability that $v_1$ got outcome $2$ and $v_2$ got outcome $1$''
-    \end{example}
-    The marginal problem inherently depends on the concept of probabilistic marginalization.
-This concept can be understood at the level of events; one event $s \in \Events{V}$ can be ``marginalized'' or restricted to a smaller event $s' \in \Events{W}$ whenever $W \subseteq V$.
-    \begin{definition}
-    \label{def:section_restriction}
-    For every $W \subseteq V$ and $s \in \Events{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Events{W}$) is the event in $\Events{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
-    \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
-    \end{definition}
-    % \begin{definition}
-    % \label{def:section_compatible}
-    % The events $s_{V} \in \Events{V}$ and $s_{W} \in \Events{W}$ are said to be \term{compatible} events if they agree on their valuations of $V \cap W$.
-Compatibility will be denoted with the infix `$\com$'.
-    % \[ s_{V} \com s_{W} \iff {s_{V}}|_{V\cap W} = {s_{W}}|_{V\cap W} \]
-    % \end{definition}
-    % \begin{definition}
-    % \label{def:section_extendable}
-    % It $s_V \in \Events{V}$ and $s_W \in \Events{W}$ compatible events and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
-    % \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
-    % Extendability is dual to the notion of a \term{restriction} of $s_V$; $s_V$ can be restricted to $s_W$ ($s_V \res s_W$) if and only if $s_W$ is extendable to $s_V$.
-    % \end{definition}
-
-    % \begin{remark}
-    %     The notation `$s \com t$' is used to indicate compatibility between $s \in \Events{V}$ and $t \in \Events{W}$ because of the following observation: $s$ and $t$ are compatible if and only if they are extensions of some event $r \in \Events{V \cap W}$.
-    %     \[ s \com t \iff \exists r \in \Events{V \cap W} \mid s \res r \ext t \]
-    %     In fact $r$ is uniquely defined.
-    %     \[ \forall v \in V \cap W : r\br{v} = s\br{v} = t\br{v} \]
-    % \end{remark}
-
-    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint events} $\Events{\jointvar}$ which represent all possible global events over the entire set of joint variables.
-Similarly, we define the \term{context events} for a particular context $V \in \mscenario$ as $\Events{V}$.
-Finally, we elect to define the \term{marginal events} as the disjoint union of all context events and by an abuse of notation we will denote this disjoint union as $\Events{\mscenario}$.
-    \[ \Events{\mscenario} = \coprod_{V \in \mscenario} \Events{V} \]
-    Each marginal section $m \in \Events{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
-By construction each marginal event $m \in \Events{\mscenario}$ is a restriction of some joint event $j \in \Events{\jointvar}$.
-    % \subsubsection{Linear Programs}
-    % \label{sec:linear_programs}
-    The marginalization operation (\cref{eq:def:marginal_problem}) of the marginal problem is a linear operator.
-This linear operator maps a joint probability distribution $\prob[\jointvar] : \Events{\jointvar} \to \bs{0,1}$ into a marginal model $\prob^{\mscenario} = \bc{\prob[V] : \Events{V} \to \bs{0,1} \mid V \in \mscenario}$.
-Since $\Events{\mscenario}$ and $\Events{\jointvar}$ are finite, the marginal problem can be casted as a $\abs{\Events{\mscenario}} \times \abs{\Events{\jointvar}}$ matrix.
-
-    \begin{definition}
-        \label{def:incidence_matrix}
-        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} events $j \in \Events{\jointvar}$ and the rows are events by \textit{marginal} events $m \in \Events{\mscenario}$.
-The entries of $M$ are populated whenever a marginal event $m$ is a restriction of the joint event $j$.
-        \[ M_{m,j} \defined \begin{cases}
-            1 & m = j|_{\s{D}\br{m}} \\
-            0 & \text{otherwise}
-        \end{cases} \]
-        The incidence matrix has $\abs{\Events{\jointvar}}$ columns, $\abs{\Events{\mscenario}} = \sum_{i} \abs{\Events{V_i}}$ rows and $k\abs{\Events{\jointvar}}$ non-zero entries.
-    \end{definition}
-    To illustrate this concretely, consider the following example:
-    \begin{example}
-        \label{ex:incidence_matrix}
-        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{A,B,C}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{A,B}, \bc{B,C}, \bc{A,C}}$. The incidence matrix becomes:
-        \[ M = \kbordermatrix{
-            (A,B,C) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
-            (A\mapsto0, B\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
-            (A\mapsto0, B\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
-            (A\mapsto1, B\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
-            (A\mapsto1, B\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
-            (B\mapsto0, C\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
-            (B\mapsto0, C\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
-            (B\mapsto1, C\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
-            (B\mapsto1, C\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
-            (A\mapsto0, C\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
-            (A\mapsto0, C\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
-            (A\mapsto1, C\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
-            (A\mapsto1, C\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
-        } \eq \label{eq:example_incidence}\]
-    \end{example}
-    The incidence matrix needs to act (to the right) on a vector representing the joint probability $\prob[\jointvar]$ distribution and output a vector representing the marginal model $\prob^{\mscenario}$.
-    \begin{definition}
-        The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint event $j \in \Events{\jointvar}$.
-$\probvec^{\jointvar}$ shares the same indices as the \textit{column} indices of $M$.
-        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
-    \end{definition}
-    \begin{definition}
-        Analogously, \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Events{\mscenario}$.
-$\probvec^{\mscenario}$ shares the same indices as the \textit{row} indices of $M$.
-        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
-    \end{definition}
-    By design, the marginal and joint distribution vectors are related via the incidence matrix $M$.
-Given a joint distribution vector $\probvec^{\jointvar}$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec^{\jointvar}$.
-    \[ \probvec^{\mscenario} = M \cdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
-    Because the marginal distribution vector $\probvec^{\mscenario}$ is simply another representation of the marginal model $\prob^{\mscenario}$, we will henceforth use the language interchangeably.
-This is likewise done so for the joint distribution (vector) $\prob[\jointvar]$ ($\probvec^{\jointvar}$).
-As a quick remark, the particular ordering of the rows and columns of $M$ carries \textit{no importance}, but it \textit{must} be consistent between $M$, $\probvec^{\jointvar}$ and $\probvec^{\mscenario}$.
-The marginal problem can now be rephrased in the language of the incidence matrix.
-Suppose one obtains a marginal distribution vector $\probvec^{\mscenario}$; the marginal problem becomes equivalent to the question:
-    \textit{Does there exist a joint distribution vector $\probvec^{\jointvar}$ such that \cref{eq:incidence_matrix_use} holds?}
-
-    The marginal problem can sometimes take on a more general variant that does not begin with a specific marginal model~\cite{Abramsky_2012,Mansfield_2012,Fritz_2011}: \textit{Given a marginal scenario $\mscenario$, what is the set of all non-contextual marginal models?} \citet{Pitowsky_1991} demonstrates that the set of non-contextual marginal models forms a \textit{convex} polytope called the \term{marginal polytope}.
-The extremal rays of a marginal polytope directly correspond to the columns of $M$ which correspond to each of the $\abs{\Events{\jointvar}}$ \textit{deterministic} joint distributions $\probvec^{\jointvar}$.
-Since all joint distributions $\probvec^{\jointvar}$ are probability distributions, their entries must sum to unity.
-    \[ \sum_{j \in \Events{\jointvar}} \probvec^{\jointvar}_j = 1 \]
-    This normalization defines the convexity of the polytope; all non-contextual marginal models are convex mixtures of the deterministic marginal models pursuant to \cref{eq:incidence_matrix_use}.
-The marginal polytope is a beneficial tool for understanding contextuality.
-First, the \textit{facets} of a marginal polytope correspond to a finite set of linear inequalities that are complete in the sense that all contextual distributions violate at least one facet inequality~\cite{Brunner_2013}.
-From the perspective of a marginal polytope, convex hull algorithms can be used to compute a representation of the complete set of linear inequalities and completely solve the marginal problem.
-Alternatively, one can completely characterize the separation between the space of contextual and non-contextual distributions by the system of inequalities associated with \cref{eq:incidence_matrix_use}.
-Explicitly,
-    \begin{equation} \label{eq:halfspace_rep_incidence}
-    \begin{alignedat}{2}
-        \forall m \in \Events{\mscenario} :&&\quad \probvec^{\mscenario}_m - {\sum}_{j} M_{m, j} \probvec^{\jointvar}_j &\geq 0 \\
-        \forall m \in \Events{\mscenario} :&&\quad -\probvec^{\mscenario}_m + {\sum}_{j} M_{m, j} \probvec^{\jointvar}_j &\geq 0 \\
-        \forall j \in \Events{\jointvar} :&&\quad \probvec^{\jointvar}_j &\geq 0
-    \end{alignedat}
-    \end{equation}
-    Geometrically \cref{eq:halfspace_rep_incidence} is a family of $2\abs{\Events{\mscenario}} + \abs{\Events{\jointvar}}$ half-planes bounding $\R^{\abs{\Events{\mscenario}}} \times \R^{\abs{\Events{\jointvar}}}$.
-However testing the contextuality of a marginal model $\probvec^{\mscenario}$ requires a collection of inequalities bounding just $\R^{\abs{\Events{\mscenario}}}$.
-Transforming \cref{eq:halfspace_rep_incidence} into the desired system of inequalities is the task of linear-quantifier elimination.
-A popular tool for linear quantifier elimination is \term{Fourier-Motzkin elimination} \cite{Dantzig_1973,Inflation,Abramsky_2012,jones_2004}.
-Applying the Fourier-Motzkin procedure to completely solve the marginal problem is discussed in more detail in \citet{Fritz_2011}.
-An excellent survey of existing techniques for solving the marginal problem including Equality Set Projection~\cite{jones_2004} and Hardy-type hypergraph transversals can be found in \citet{Inflation}.
-In conclusion, there are a number of computational tools available to solve the marginal problem completely whenever no marginal model is provided.
-
-    Each of the above mentioned techniques suffers from computational complexity limitations.
-For example, the Fourier-Motzkin procedure is in the worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}.
-For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable.
-This will become apparent in \cref{sec:found_inequalities} when the inflation technique is applied to the Triangle structure, producing marginal models that are very large.
-Moreover, algorithms to partially solve the marginal problem such as Hardy-type hypergraph transversals were used to determine hundreds of thousands of causal compatibility inequalities for the Triangle structure; none of which were able to be violated quantumly using numerical optimizations.
-Therefore, simpler approaches to the marginal problem needed to be considered.
-
-    Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining where or not a particular marginal model admitted a joint distribution or not.
-This question is naturally framed as the following linear problem:
-
-    \begin{definition}
-        \label{def:marginal_linear_program}
-        \term{The Marginal Linear Program} is the following linear program:
-        \begin{alignat*}{2}
-            & \text{minimize:} \quad&& \emptyset \cdot x\\
-            & \text{subject to:} && x \succeq 0 \\
-            & && M \cdot x = \probvec^{\mscenario}
-        \end{alignat*}
-        If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries).
-The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:incidence_matrix_use} and is a valid joint distribution vector.
-Therefore feasibility implies that $\probvec^{\jointvar}$ exists and is precisely $x$.
-Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\probvec^{\jointvar}$.
-    \end{definition}
-
-    To every linear program, there exists a dual linear program that characterizes the feasibility of the original~\cite{Schrijver_1998}.
-Constructing the dual linear program is straightforward~\cite{Lahaie_2008}.
-
-    \begin{definition}
-        \label{def:dual_marginal_linear_program}
-        \term{The Dual Marginal Linear Program}:
-        \begin{alignat*}{2}
-            & \text{minimize:} \quad&& y \cdot \probvec^{\mscenario}\\
-            & \text{subject to:} && y \cdot M \succeq 0
-        \end{alignat*}
-        Where $y$ is a real valued vector with the same length as $\probvec^{\mscenario}$.
-    \end{definition}
-
-    The dual marginal linear program not only answers the marginal problem for a specific marginal model $\probvec^{\mscenario}$ but as a by-product provides an inequality that witnesses its contextuality.
-If this is not obvious, first notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints become satisfied.
-Secondly if the dual constraint $y \cdot M \succeq 0$ holds \textit{and} the primal is feasible, then the following must hold:
-    \[ y \cdot \probvec^{\mscenario} =  y \cdot M \cdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
-    Therefore the \textit{sign} of the dual objective $d \defined \min \br{y \cdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality.
-If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore $\probvec^{\mscenario}$ is contextual.
-Likewise if $d \geq 0$ (satisfying \cref{eq:dual_marginal_ineq}), then $\probvec^{\mscenario}$ is non-contextual.\footnote{Actually, if $d \geq 0$ then it is exactly $d = 0$ due to the existence of the trivial $y = \emptyset$.
-This observation is an instance of the \textit{Complementary Slackness Property} of~\cite{Bradley_1977}.
-Moreover, if $d < 0$, then it is unbounded $d = -\inf$.
-This latter point becomes clear upon recognizing that for any $y$ with $d < 0$, another $y' = \al y$ can be constructed (with $\al > 1$) such that $d' = \al d < d$.
-Since a more negative $d'$ can always be found, it must be that $d$ is unbounded.
-This is a demonstration of the fundamental \textit{Unboundedness Property} of~\cite{Bradley_1977}; if the dual is unbounded, then the primal is infeasible.} This is manifestation of Farkas's lemma~\cite{Schrijver_1998}.
-
-    An \term{infeasibility certificate}~\cite{Andersen_2001} is any vector $y$ that satisfies the constraint of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
-    \[ y \in \R^{\abs{\Events{\mscenario}}} : y \cdot M \succeq 0, \quad y \cdot \probvec^{\mscenario} < 0 \]
-    Most linear program software packages such as Mosek~\cite{Mosek_2016}, Gurobi~\cite{Gurobi_2016}, CPLEX~\cite{Cplex_2016} and CVX/CVX OPT~\cite{CVX_2016,CVX_Opt_2016} are capable of producing infeasibility certificates.
-    Furthermore, for every $y$ satisfying $y \cdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of non-contextual marginal models.
-If $y$ is an infeasibility certificate, then all non-contextual marginal models $\probvec^{\mscenario}$ must satisfy \cref{eq:dual_marginal_ineq} making $y \cdot \probvec^{\mscenario} \geq 0$ a valid causal compatibility inequality.
-
-    \subsection{Inflation Technique}
-    \label{sec:deriving_inequalities}
-    \label{sec:inflation_technique_main_summary}
-    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a marginal model $\prob^{\mscenario}$ is compatible or incompatible with a given causal structure $\graph$.
-As a preliminary summary, the inflation technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
-As a example, inflations of the Triangle structure are depicted in \cref{fig:inflations}.
-Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}.
-For example node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the \textit{Web inflation} of \cref{fig:the_web_inflation}.
-All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
-A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
-    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
-    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index.
-Equipped with the common graph-theoretic terminology and notation presented in \cref{sec:causal_compatibility}, an inflation can be formally defined as follows:
-
-    \todo[TC]{Incorporate these definitions into the discussion}
-    \begin{definition}
-        An \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$.
-        An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$.
-        \[ \AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}} \]
-    \end{definition}
-
-    \begin{definition}
-        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
-        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
-        Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is equivalent to its counterpart in $\graph$ up to copy-index.
-    \end{definition}
-    The motivation behind this definition is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible joint distribution $\prob[\nodes]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
-
-    To do this, first notice that every compatible joint distribution $\prob[\nodes]$ uniquely defines a set of causal parameters for $\graph$.
-It is possible to obtain these causal parameters by computing the single-variable marginal distributions of $\prob[\nodes]$,
-    \[ \forall n \in \nodes : \prob[n\mid \Pa[\graph]{n}] = \sum_{\nodes \setminus n} \prob[\nodes] \eq \label{eq:unique_causal_parameters}\]
-    Now it is possible to make use of the inflation criteria (\cref{eq:inflation_defn}) which at least enforces that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$.
-From this, one can create a set of \term{inflated causal parameters} using \cref{eq:unique_causal_parameters},
-    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \eq \label{eq:inflated_causal_parameters} \]
-    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course, there exists compatible joint distributions on $\nodes'$ that can not be constructed in this manner.
-The claim is that all joint distributions that are constructed in this way are compatible.}.
-    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \eq \label{eq:unique_causal_parameters_inflated}\]
-    Together, \cref{eq:unique_causal_parameters,eq:inflated_causal_parameters,eq:unique_causal_parameters_inflated} form the \term{weak inflation lemma}: compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$.
-Before generalizing to the inflation lemma, a careful observation needs to be made.
-For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$, where $N \subset \nodes$, induces a compatible marginal distribution $\prob[N']$ over $N'$.
-In fact, $N'$ must contain no duplicate nodes up to copy index and thus $\prob[N] = \prob[N']$.
-These subsets of nodes are so essential to the Inflation Technique they are assigned a special name: sets $N' \subseteq \nodes'$ as called the \term{injectable sets} of $\graph'$ and $N \subset \nodes$ the \term{images of the injectable sets} of $\graph$.
-    \begin{align*}
-        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
-        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
-    \end{align*}
-    Injectable sets are incredibly useful for causal compatibility because they allow one to extend the weak inflation lemma to \textit{the} inflation lemma:
-    \begin{lemma}
-        \label[lemma]{lem:inflation}
-        \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-    \end{lemma}
-    Diagrammatically, \cref{lem:inflation} can be visualized as follows:
-
-    \begin{center}
-        \begin{tikzpicture}
-            \pgfmathsetmacro{\vs}{2.2};
-            \pgfmathsetmacro{\hs}{5.2};
-            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
-            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
-            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
-            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
-            \draw[very thick, ->] (pn) -- (cp);
-            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
-            \draw[very thick, ->] (cp_) -- (pn_);
-        \end{tikzpicture}
-    \end{center}
-
-    The inflation lemma is the most important result of the causal inflation technique.
-The contrapositive version of \cref{lem:inflation} is a powerful tool for deriving causal compatibility constraints.
-Any causal compatibility constraint, such as a causal compatibility inequality, that constrains injectable marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ can be \textit{deflated} into a valid compatibility constraint on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure by dropping all references to the copy-indices.
-Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
-Therefore, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
-
-    Heretofore, the Inflation Technique as stated by \cref{lem:inflation} does not facilitate the derivation of any non-trivial inequalities.
-The Inflation lemma simply casts causal inference problems on $\graph$ to causal inference problems on $\graph'$.
-Fortunately, an inflated causal structure $\graph'$ possesses its own conditional independence relations which can be exploited to turn linear inequalities on $\graph'$ into polynomial inequalities on $\graph$.
-
-    Suppose that one were to obtain an inequality on $\graph'$ that contained probabilistic terms such as $\prob[N']$ where $N' \not \in \Inj[\graph]{\graph'}$.
-At this point, the Inflation lemma is not applicable because it requires probabilistic constraints to consist entirely of distributions $\prob[N']$ where $N'$ is injectable.
-If for example, $N' \not \in \Inj[\graph]{\graph'}$ could be partitioned into two injectable subsets $N_1' \in \Inj[\graph]{\graph'}$ and $N_2' \in \Inj[\graph]{\graph'}$ that where \term{ancestrally independent} in $\graph'$,
-    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
-    Then the compatible marginal context $\prob[N']$ must be probabilistically separable $\prob[N'] = \prob[N_1']\prob[N_2']$ due to \cref{eq:local_markov_property}.
-Since $N_1'$ and $N_2'$ are both injectable, the inflation lemma now applies and the original inequality can be deflated.
-
-    \begin{center}
-        \begin{tikzpicture}[scale=0.8]
-            \pgfmathsetmacro{\hs}{1.4};
-            \pgfmathsetmacro{\vs}{0.6};
-            \pgfmathsetmacro{\cross}{0.2};
-            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
-            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
-            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
-            \draw (2*\hs, 4*\vs + 0.7*\vs) node[]{$N_1' \cup N_2' = N$};
-            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
-            \draw (0, 0) node[](b){??};
-            \draw[thick, ] (a) -- (ab);
-            \draw[thick, ] (c) -- (cd);
-            \draw[thick, ] (a) -- (ac);
-            \draw[thick, ->] (ac) -- (c);
-            \draw[thick, ->] (ab) -- (b);
-            \draw[thick, ->] (cd) -- (d);
-            \draw[very thick, red]
-            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
-            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
-            ;
-        \end{tikzpicture}
-    \end{center}
-
-    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that can are called the \term{pre-injectable sets}.
-A set $N' \subseteq \nodes'$ is a pre-injectable set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
-
-    A pre-injectable set $N'$ is of primal importance to the inflation technique because any distribution over $N'$ will factorize according to graphical $d$-separation conditions~\cite{Pearl_2009},
-    \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
-    Application of the inflation lemma to linear inequalities constraining pre-injectable distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
-Throughout the body of this work, we let $\PreInj[\graph]{\graph'}$ denote the set of all pre-injectable sets.
-Naturally, the pre-injectable sets will define a marginal scenario $\mscenario$ that are used to derive compatibility inequalities in \cref{sec:deriving_inequalities}\footnote{Analogously for a marginal scenario $\mscenario$, the pre-injectable sets $\PreInj[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
-Therefore, in practice, it is completely sufficient to focus on the maximal pre-injectable sets}.
-
-    \subsection{Exemplary Inflations of The Triangle Structure}
-    \label{sec:exemplary_inflations_of_the_triangle structure}
-
+     First select an inflation $\graph'$ of the Triangle structure $\graph$ and identify the maximal pre-injectable sets $\PreInj[\graph]{\graph'}$.
+These sets define the marginal scenario to be used in the Inflation Technique.
+Next, inflate the Fritz distribution into the pre-injectable sets as described by the Inflation lemma (\cref{lem:inflation}).
+Finally, obtain infeasibility certificates using some linear programing software and obtain a valid causal compatibility inequality that witnesses the Fritz distribution's incompatibility.
+
+    As a first demonstration, we make use of the Wagon-Wheel inflation (\cref{fig:wagon_wheel_inflation}) to find these inequalities.
+The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
+By inspection\footnote{Computing the injectable and pre-injectable sets computationally is possible and a technique is discussed in~\citet{Inflation}.}, the maximal pre-injectable sets of the Wagon-Wheel inflation are as follows:
+    \begin{equation*}
+        \eq \label{eq:pre_injectable_triangle_structure_wagon_wheel}
+        \begin{gathered}
+            \textbf{Maximal Pre-injectable Sets} \\
+            \bc{A_2, B_1, C_3, C_1} \\
+            \bc{A_1, B_1, C_4, C_2} \\
+            \bc{A_1, B_2, C_1, C_3} \\
+            \bc{A_2, B_2, C_2, C_4} \\
+        \end{gathered}
+        \qquad
+        \begin{gathered}
+            \textbf{Ancestral Independences} \\
+            \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
+            \bc{A_1, B_1, C_4} \ancestralindep \bc{C_2} \\
+            \bc{A_1, B_2, C_1} \ancestralindep \bc{C_3} \\
+            \bc{A_2, B_2, C_2} \ancestralindep \bc{C_4} \\
+        \end{gathered}
+    \end{equation*}
+
+    These maximal pre-injectable sets define a marginal scenario where $\graph'$ is the Wagon-Wheel inflation of the Triangle structure $\graph$.
+    \[ \mscenario = \PreInj[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
+    The complete set of variables $\jointvar$ is simply the set of observable nodes in the Wagon-Wheel inflation,
+    \[ \jointvar = \nodes'_O = \bc{A_1, A_2, B_1, B_2, C_1, C_2, C_3, C_4} \]
+    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
+This marginal scenario $\mscenario$ then defines an incidence matrix capable of accommodating the Fritz distribution.
+    Analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \abs{\Events{V}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{\Events{v}} = 4^{\abs{\jointvar}} = 4^8 = 65,536$ columns.
+Understandably, this matrix is not reproduced here.
+The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
+
+    The marginal distribution vector $\probvec^{\mscenario}$ is indexed by $1024$ marginal outcomes $m \in \Events{\mscenario}$ of the following \textit{symbolic} form,
+    \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
+    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
+    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
+    And finally, each probability distribution in \cref{eq:marginal_vector_wagon_wheel_factors} is deflated by dropping copy-indices.
+    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[ABC]\br{000}\prob[C]\br{0}, \ldots, \prob[ABC]\br{323}\prob[C]\br{2}, \ldots, \prob[ABC]\br{333}\prob[C]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors_dropped}\]
+    This step is permitted because all of the remaining distributions in \cref{eq:marginal_vector_wagon_wheel_factors} are defined over the injectable sets of the Wagon-Wheel inflation.
+Numerically however, each of the elements of $\probvec^{\mscenario}$ are replaced with numerical values corresponding to the Fritz distribution upon deflation.
+Pursuant to \cref{eq:fritz_dist}, $\prob[ABC]\br{323}\prob[C]\br{2}$, for example, is assigned the following numerical value.
+    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267  \]
+    The same is applied to all other entries of $\probvec^{\mscenario}$.
+Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained.
+Below is an example of an infeasibility inequality obtained over the entries of \cref{eq:marginal_vector_wagon_wheel_factors_dropped}.
     \begin{center}
@@
 
-    Quite surprisingly, it is possible to derive causal compatibility inequalities for the Triangle structure that are symmetric under the exchange of parties.
-This is done by grouping marginal events $m \in \Events{\mscenario}$ into orbits under the action of party exchange.
-Even more interestingly, these inequalities are violated by the Fritz distribution.
-This comes as a surprise because the Fritz distribution is \text{not} invariant under the exchange of parties; in fact the Fritz distribution is noticeably biased toward $C$.
-
-    In general, exploiting symmetries of the marginal scenario is useful for a few distinct reasons.
-First, \citet{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:deriving_inequalities}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
+    \Cref{sec:inflation_technique_main_summary} detailed how to obtain causal compatibility inequalities for any causal structure by constructing a marginal problem (see \cref{sec:marginal_satisfiability}) and supplying an incompatible distribution to generate an infeasibility certificate.
+In \cref{sec:found_inequalities}, a causal compatibility inequality symmetric under permutations of the variables $A,B,C$ was presented (see \cref{eq:symmetic_web_inequality}).
+This section aims to describe a general technique that can be used to derive inequalities exhibiting this symmetry.
+In brief, this is accomplished by grouping marginal events $m \in \Events{\mscenario}$ of a marginal scenario $\mscenario$ into orbits under the action of variable permutations.
+
+    Exploiting symmetries of the marginal scenario is useful for a few distinct reasons.
+First, \citet{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:marginal_satisfiability}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
 They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that non-trivial inequalities can be recovered from facets of a symmetric polytope.
 Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
-The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to not be symmetric, there is indication that the space of accessible distributions is non-convex.}.
-
-    To demonstrate what types of symmetries we have in mind, we present the following example:
-    \begin{example}
-        \label[example]{ex:symmetries}
-        First consider the marginal scenario $\mscenario = \bc{\bc{A, B, C}, \bc{C, D}, \bc{A, D}}$ where each variable in $\jointvar = \bc{A,B,C,D}$ has binary outcomes: $O_A = O_B = O_C = O_D = \bc{0,1}$.
-Moreover, let $I_{\mscenario}$ be the following compatibility inequality over $\mscenario$ for some causal structure $\graph$,
-        \[ I_{\mscenario} = \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}  \]
-        Intuitively, the compatibility of $\probvec^{\mscenario}$ is \textit{independent} of the how one labels outcomes.
-Suppose $\varphi : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ is a permutation of the variables $\jointvar$.
+The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to be asymmetric, then one can conclude the space of accessible distributions is non-convex.}.
+
+    To clarify which symmetries we have in mind, first consider the marginal scenario $\mscenario = \bc{\bc{A, B, C}, \bc{C, D}, \bc{A, D}}$ where each variable in $\jointvar = \bc{A,B,C,D}$ has binary outcomes $\bc{0,1}$.
+Moreover, let $I_{\mscenario} \defined \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}$ be some inequality constraining the set of non-contextual marginal models $\prob^{\mscenario}$.
+Intuitively, the contextuality of a distribution $\prob[ABCD]$ should be \textit{independent} of the how one labels the variables in $\jointvar$.
+Suppose $\varphi \in \Perm{\jointvar}$\footnote{The permutation group $\Perm{S}$ over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} is a permutation of the variables $\jointvar$ such that $\varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$.
 Intuitively $\varphi$ acts on $I_{\mscenario}$ in the following way,
     \begin{align*}
+    \eq \label{eq:symmetry_example}
+    \begin{split}
         \varphi\bs{I_{\mscenario}} &= \bc{\prob[\varphi\bs{abc}][010] \leq \prob[\varphi\bs{cd}][00] + \prob[\varphi\bs{ad}][01]} \\
@@
         &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
+    \end{split}
     \end{align*}
-        In general (as in this example), permutations over all variables can modify the marginal scenario $\varphi\bs{\mscenario} \neq \mscenario$; in general we write $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
-Although $\varphi\bs{I_{\mscenario}}$ is still a valid causal compatibility inequality, in constrains marginal models of a different marginal scenario $\varphi\bs{\mscenario}$ and are in general of no interest.
-    \end{example}
-
-    Following the observations of \cref{ex:symmetries}, it is always possible to permute the random variables in a marginal scenario to produce new and valid inequalities.
-The symmetry group over a the complete set of variables $\jointvar$ is simply the \text{permutation group}\footnote{The permutation group over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} $\Perm{\jointvar}$.
-As was noted in \cref{ex:symmetries}, some permutations $\varphi \in \Perm{\jointvar}$ have the undesired possibility of transforming $\mscenario$ into a different marginal scenario.
-    \[ \varphi\bs{\mscenario} \defined \bc{\varphi\bs{V_1}, \ldots, \varphi\bs{V_k}} \neq \mscenario \]
-    This means that there could exist $V \in \mscenario$ such that $\varphi\bs{V} \not \in \mscenario$.
-Permutations $\varphi$ retaining this property are unable to generate compatibility inequalities over the same marginal scenario.
-Therefore, the desired set of symmetries is a subgroup that takes $\mscenario$ to $\mscenario$.
-
-    \begin{definition}
-        The \term{variable permutation group} $\gp$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario.
-        \[ \Phi\br{\mscenario} \defined \bc{\varphi \in \Perm{\jointvar} \mid \forall V \in \mscenario : \varphi\bs{V} \in \mscenario} \]
-    \end{definition}
-
+    Following this example, it is always possible to permute the random variables in marginal scenario to produce new and valid inequalities.
+In general, permutations over $\jointvar$ can modify the marginal scenario $\varphi\bs{\mscenario} \defined \bc{\varphi\bs{V_1}, \ldots, \varphi\bs{V_k}} \neq \mscenario$; this was the case for the above example.
+Therefore $\varphi$ has capacity to modify both the terms of the inequality as well as the set of marginal models it constrains $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
+Permutations $\varphi$ that modify the marginal scenario have no application within the framework of the Inflation Technique because \cref{lem:inflation} requires inflated inequality to constrain injectable sets.
+Therefore, the desired set of symmetries for our purposes is a subgroup of $\Perm{\jointvar}$ that takes $\mscenario$ to $\mscenario$.
+
+    The \term{variable permutation group} $\gp\br{\mscenario}$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario, $\Phi\br{\mscenario} \defined \bc{\varphi \in \Perm{\jointvar} \mid \forall V \in \mscenario : \varphi\bs{V} \in \mscenario}$.
     Obtaining the variable permutation group $\gp\br{\mscenario}$ is a simple application of a group stabilizer algorithm.
@@
 
-    Although very useful for reducing computational complexity~\cite{Bancal_2010}, we divert our attention to finding \textit{symmetric} inequalities themselves.
-    \[ \forall \varphi \in \gp\br{\mscenario} :  \varphi\bs{I_{\mscenario}} = I_{\mscenario} \]
-    In order to do this, we must first define how elements $\varphi \in \gp$ act on marginal events.
-The action of $\varphi \in \gp$ on any outcome $f \in \Events{V}$ (denoted $\geo\bs{f}$) is defined as,
-    \[ \forall v \in \Dom{\varphi\bs{f}} : \br{\varphi\bs{f}}\br{v} \defined f\br{\varphi^{-1}\bs{v}} \eq \label{eq:act_on_variable}\]
-    \Cref{eq:act_on_variable} is nothing more than a mathematical definition for the intuitive action used in \cref{ex:symmetries}.
-    Through repeated action of $\varphi \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define \term{group orbits} of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$.
-    \begin{align*}
-        \Orb[\gp]{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \gp} \\
-        \Orb[\gp]{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \gp}
-    \end{align*}
+    Although very useful for reducing computational complexity~\cite{Bancal_2010}, we divert our attention to finding \textit{symmetric} inequalities, i.e.
+those where $\forall \varphi \in \gp\br{\mscenario} :  \varphi\bs{I_{\mscenario}} = I_{\mscenario}$.
+Through repeated action of $\varphi \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define \term{group orbits} of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$; respectively $\Orb[\gp]{m} \defined \bc{\varphi\bs{m} \mid \varphi \in \gp}$, $\Orb[\gp]{j} \defined \bc{\varphi\bs{j} \mid \varphi \in \gp}$.
+The action of $\varphi \in \gp$ on any outcome $f \in \Events{V}$ (denoted $\geo\bs{f}$) is defined as $\br{\varphi\bs{f}}\br{v} \defined f\br{\varphi^{-1}\bs{v}}$ pursuant to intuitive action used in \cref{eq:symmetry_example}.
 Using these group orbits, it is possible to contract the incidence matrix $M$ of a marginal scenario into a symmetrized version.
-
-    \begin{definition}
 The \term{symmetric incidence matrix} $M_{\gp}$ for a marginal scenario $\mscenario$ and the variable permutation group $\gp$ is a contracted version of the incidence matrix $M$ for $\mscenario$.
@@
     \[ \br{M_{\gp}}_{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M_{m',j'} \]
-    \end{definition}
-    It is possible to analogously define a \term{symmetric joint distribution vector} $\probvec^{\jointvar}_{\Phi}$ indexed by $\Orb[\gp]{j}$,
-    \[ \br{\probvec^{\jointvar}_{\Phi}}_{\Orb[\gp]{j}} = \sum_{j' \in \Orb[\gp]{j}} \probvec^{\jointvar}_{j} \]
-    And a \term{symmetric marginal distribution vector} $\probvec^{\mscenario}_{\Phi}$ indexed by $\Orb[\gp]{m}$,
-    \[ \br{\probvec^{\mscenario}_{\Phi}}_{\Orb[\gp]{m}} = \sum_{m' \in \Orb[\gp]{m}} \probvec^{\mscenario}_{m} \]
-    Which altogether define a new, \term{symmetric marginal problem},
-    \[ \probvec^{\mscenario}_{\Phi} = M_{\gp} \cdot \probvec^{\jointvar}_{\Phi} \]
-    The symmetric marginal problem can be solved using the same computational methods discussed in \cref{sec:deriving_inequalities} and will produce symmetric inequalities.
+    It is possible to analogously define a \term{symmetric joint distribution vector} $\probvec^{\jointvar}_{\Phi}$ indexed by $\Orb[\gp]{j}$, $\br{\probvec^{\jointvar}_{\Phi}}_{\Orb[\gp]{j}} = \sum_{j' \in \Orb[\gp]{j}} \probvec^{\jointvar}_{j'}$ and a \term{symmetric marginal distribution vector} $\probvec^{\mscenario}_{\Phi}$ indexed by $\Orb[\gp]{m}$, $\br{\probvec^{\mscenario}_{\Phi}}_{\Orb[\gp]{m}} = \sum_{m' \in \Orb[\gp]{m}} \probvec^{\mscenario}_{m'}$.
+Together, $M_{\gp}, \probvec^{\jointvar}_{\Phi}$ and $\probvec^{\mscenario}_{\Phi}$ define a new, \term{symmetric marginal problem}: $\probvec^{\mscenario}_{\Phi} = M_{\gp} \cdot \probvec^{\jointvar}_{\Phi}$.
+The symmetric marginal problem can be solved using the same computational methods discussed in \cref{sec:marginal_satisfiability} and will produce symmetric inequalities.
 
@@
     \[ \gp\br{\PreInj[\graph]{\graph'}} \sim \Perm{A,B,C} \]
-    To see this, $\varphi_1$ and $\varphi_4$ become the identity element $\ident$ in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
+    To see this, $\varphi_1$ and $\varphi_4$ become the identity element in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
 
@@
 Using the symmetric incidence matrix and linear programing methods, an infeasibility certificate was found that is capable of witnessing the Fritz distribution.
-This inequality is reproduced in \cref{eq:symmetic_web_inequality}.
+The corresponding deflated inequality is presented in \cref{sec:found_inequalities} as \cref{eq:symmetic_web_inequality}.
 

### 2017-04-07 documents/TriangleScenarioArXiv/ts.tex
cleaned up appendix on inflation diagram details

@@
 
+    To reiterate, the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary} and more details can be found in \cref{sec:exemplary_inflations_of_the_triangle structure}.
+
     It is possible to simplify \cref{eq:ww_ineq} identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$.
@@
 
+    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle Structure by constructing inflations of the Triangle Structure satisfying \cref{eq:inflation_defn}.
+Explicitly, for a given inflation $\graph'$ of the Triangle Structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal pre-injectable sets of $\graph'$, i.e.
+$\mscenario = \PreInj[\graph]{\graph'}$.
+This section acts as a reference for the particular inflations of the Triangle scenario that are mentioned throughout this manuscript.
+Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their pre-injectable sets.
+An efficient algorithm for computing the injectable and pre-injectable sets of an inflation can be found in~\cite{Inflation}.
+    \begin{center}
+    \begin{figure}
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
+    \caption{The Cut inflation.}\label{fig:cut_inflation}
+    \end{subfigure}
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
+    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
+    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
+    \end{subfigure}
+    \begin{subfigure}[b]{.45\linewidth}
+    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure}}
+    \caption{The Web Inflation.}\label{fig:the_web_inflation}
+    \end{subfigure}
+    \caption{Some inflations of the Triangle structure.}
+    \label{fig:inflations}
+    \end{figure}
+    \end{center}
+
+    The first inequality presented in \cref{sec:found_inequalities} was \cref{eq:ww_ineq}.
+\cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation in \cref{fig:wagon_wheel_inflation}.
+The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
+The maximal pre-injectable sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
+These maximal pre-injectable sets define the following marginal scenario where the joint variables $\jointvar$ are simply the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
+    \[ \mscenario = \PreInj[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
+    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
+This marginal scenario $\mscenario$ then defines an incidence matrix $M$ capable of accommodating the Fritz distribution that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = 4^8 = 65,536$ columns.
+Understandably, this matrix is not reproduced here.
+The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
+
+    \begin{equation*}
+        \eq \label{eq:pre_injectable_triangle_structure_wagon_wheel}
+        \begin{gathered}
+            \textbf{Maximal Pre-injectable Sets} \\
+            \bc{A_2, B_1, C_3, C_1} \\
+            \bc{A_1, B_1, C_4, C_2} \\
+            \bc{A_1, B_2, C_1, C_3} \\
+            \bc{A_2, B_2, C_2, C_4} \\
+        \end{gathered}
+        \qquad
+        \begin{gathered}
+            \textbf{Ancestral Independences} \\
+            \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
+            \bc{A_1, B_1, C_4} \ancestralindep \bc{C_2} \\
+            \bc{A_1, B_2, C_1} \ancestralindep \bc{C_3} \\
+            \bc{A_2, B_2, C_2} \ancestralindep \bc{C_4} \\
+        \end{gathered}
+    \end{equation*}
+    To construct the marginal distribution vector $\probvec^{\mscenario}$ for the Fritz distribution, one begins with $\probvec^{\mscenario}$ defined in a \textit{symbolic} form,
+    \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
+    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
+    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
+    And penultimately, each probability distribution in \cref{eq:marginal_vector_wagon_wheel_factors} is deflated by dropping copy-indices.
+    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[ABC]\br{000}\prob[C]\br{0}, \ldots, \prob[ABC]\br{323}\prob[C]\br{2}, \ldots, \prob[ABC]\br{333}\prob[C]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors_dropped}\]
+    This step is permitted because all of the remaining distributions in \cref{eq:marginal_vector_wagon_wheel_factors} are defined over the injectable sets of the Wagon-Wheel inflation.
+Finally, each of the elements of $\probvec^{\mscenario}$ are replaced with numerical values pursuant to the Fritz distribution.
+For example, $\prob[ABC]\br{323}\prob[C]\br{2}$ is assigned the following numerical value:
+    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267  \]
+    The same is applied to all other entries of $\probvec^{\mscenario}$.
+Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained, corresponding precisely to \cref{eq:ww_ineq} using \cref{eq:marginal_vector_wagon_wheel_factors_dropped}.
+
+    The remaining inequalities in \cref{sec:found_inequalities} were derived using the Web inflation of \cref{fig:the_web_inflation}.
+The maximal pre-injectable sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_web}.
     \begin{equation*}
@@
     \end{equation*}
-    Again, analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ and $201,326,592$ non-zero entires.
-Using this incidence matrix, a number of incompatibility certificates were derived.
-For inspection, one is reproduced in \cref{eq:web_inequality}.
-
-     First select an inflation $\graph'$ of the Triangle structure $\graph$ and identify the maximal pre-injectable sets $\PreInj[\graph]{\graph'}$.
-These sets define the marginal scenario to be used in the Inflation Technique.
-Next, inflate the Fritz distribution into the pre-injectable sets as described by the Inflation lemma (\cref{lem:inflation}).
-Finally, obtain infeasibility certificates using some linear programing software and obtain a valid causal compatibility inequality that witnesses the Fritz distribution's incompatibility.
-
-    As a first demonstration, we make use of the Wagon-Wheel inflation (\cref{fig:wagon_wheel_inflation}) to find these inequalities.
-The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
-By inspection\footnote{Computing the injectable and pre-injectable sets computationally is possible and a technique is discussed in~\citet{Inflation}.}, the maximal pre-injectable sets of the Wagon-Wheel inflation are as follows:
-    \begin{equation*}
-        \eq \label{eq:pre_injectable_triangle_structure_wagon_wheel}
-        \begin{gathered}
-            \textbf{Maximal Pre-injectable Sets} \\
-            \bc{A_2, B_1, C_3, C_1} \\
-            \bc{A_1, B_1, C_4, C_2} \\
-            \bc{A_1, B_2, C_1, C_3} \\
-            \bc{A_2, B_2, C_2, C_4} \\
-        \end{gathered}
-        \qquad
-        \begin{gathered}
-            \textbf{Ancestral Independences} \\
-            \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
-            \bc{A_1, B_1, C_4} \ancestralindep \bc{C_2} \\
-            \bc{A_1, B_2, C_1} \ancestralindep \bc{C_3} \\
-            \bc{A_2, B_2, C_2} \ancestralindep \bc{C_4} \\
-        \end{gathered}
-    \end{equation*}
-
-    These maximal pre-injectable sets define a marginal scenario where $\graph'$ is the Wagon-Wheel inflation of the Triangle structure $\graph$.
-    \[ \mscenario = \PreInj[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
-    The complete set of variables $\jointvar$ is simply the set of observable nodes in the Wagon-Wheel inflation,
-    \[ \jointvar = \nodes'_O = \bc{A_1, A_2, B_1, B_2, C_1, C_2, C_3, C_4} \]
-    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
-This marginal scenario $\mscenario$ then defines an incidence matrix capable of accommodating the Fritz distribution.
-    Analogously to \cref{ex:incidence_matrix}, this marginal scenario defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \abs{\Events{V}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{\Events{v}} = 4^{\abs{\jointvar}} = 4^8 = 65,536$ columns.
-Understandably, this matrix is not reproduced here.
-The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
-
-    The marginal distribution vector $\probvec^{\mscenario}$ is indexed by $1024$ marginal outcomes $m \in \Events{\mscenario}$ of the following \textit{symbolic} form,
-    \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
-    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
-    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
-    And finally, each probability distribution in \cref{eq:marginal_vector_wagon_wheel_factors} is deflated by dropping copy-indices.
-    \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[ABC]\br{000}\prob[C]\br{0}, \ldots, \prob[ABC]\br{323}\prob[C]\br{2}, \ldots, \prob[ABC]\br{333}\prob[C]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors_dropped}\]
-    This step is permitted because all of the remaining distributions in \cref{eq:marginal_vector_wagon_wheel_factors} are defined over the injectable sets of the Wagon-Wheel inflation.
-Numerically however, each of the elements of $\probvec^{\mscenario}$ are replaced with numerical values corresponding to the Fritz distribution upon deflation.
-Pursuant to \cref{eq:fritz_dist}, $\prob[ABC]\br{323}\prob[C]\br{2}$, for example, is assigned the following numerical value.
-    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267  \]
-    The same is applied to all other entries of $\probvec^{\mscenario}$.
-Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained.
-Below is an example of an infeasibility inequality obtained over the entries of \cref{eq:marginal_vector_wagon_wheel_factors_dropped}.
-    \begin{center}
-    \begin{figure}
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
-    \caption{The Cut inflation}\label{fig:cut_inflation}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
-    \caption{The Spiral inflation}\label{fig:spiral_inflation}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
-    \caption{The Wagon-Wheel inflation}\label{fig:wagon_wheel_inflation}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure}}
-    \caption{The Web Inflation}\label{fig:the_web_inflation}
-    \end{subfigure}
-    \caption{Some inflations of the Triangle structure.}
-    \label{fig:inflations}
-    \end{figure}
-    \end{center}
+    Analogously to the Wagon-Wheel inflation, these pre-injectable sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ and $201,326,592$ non-zero entires.
 

### 2017-05-30 documents/TriangleScenarioArXiv/ts.tex
Attempting sharelatex fix
Added Miguel insight for the second refinement to Fritz's Problem

@@
 Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the Triangle structure.
+In \cref{sec:fritz_distribution} the Fritz distribution was described in detail along with Fritz's Problem~\cite[Problem 2.17]{Fritz_2012}.
 Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality.
-In \cref{sec:fritz_distribution} the Fritz distribution was described in detail along with Fritz's Problem~\cite[Problem 2.17]{Fritz_2012}.
 
@@
 
-    In consideration of out resolution to \ref{r:1}, we additionally propose two more refinements to Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
+    In consideration of our resolution to \ref{r:1}, we additionally propose two more refinements to Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
     \begin{enumerate}[label=\textbf{R.\arabic*}]
@@
 The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
-Finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure.
+At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure.
+Unfortunately, this is simply not the case.
+By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled.
+This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle Structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings.
+Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible.\footnote{This insight was originally made by Miguel Navascués in private communications.} Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle Structure which have the fewest number of outcomes.
+
     Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}).
@@
 Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility.
-In summary, it remains unclear whether or not \ref{r:2} or \ref{r:3} is a harder problem or if either is even feasible.
+Ultimately, it remains unclear whether or not a positive resolution to \ref{r:3} is even feasible.
 
@@
     \bibliographystyle{apsrev4-1}
-    \nocite{apsrev41Control}
+    % \nocite{apsrev41Control}
     \bibliography{references}

### 2017-05-30 documents/TriangleScenarioArXiv/ts.tex
Inflation technique -> Inflation Technique

@@
     Ultimately, this work accomplishes two important tasks.
-First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation technique specifically for quantum causal inference problems.
+First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation Technique specifically for quantum causal inference problems.
 The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure --- a task that no other existing techniques have succeeded at.
-In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure.
-Consequently, this work strongly indicates that the Inflation technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
+In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation Technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure.
+Consequently, this work strongly indicates that the Inflation Technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
 Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations.
@@
 
-    In the context of the Inflation technique, a variable symmetry $\Phi\br{\mscenario'}$ over an inflated marginal scenario $\mscenario'$ does not always correspond to a variable symmetry under deflation $\Phi\br{\mscenario}$.
+    In the context of the Inflation Technique, a variable symmetry $\Phi\br{\mscenario'}$ over an inflated marginal scenario $\mscenario'$ does not always correspond to a variable symmetry under deflation $\Phi\br{\mscenario}$.
 In order to derive deflated inequalities that are symmetric under an exchange of parties, it is required that $\Phi\br{\mscenario'} \sim \Phi\br{\mscenario}$ are equivalent up to copy-index.

### 2017-05-31 documents/TriangleScenarioArXiv/ts.tex
improved discussion of measures of non-classicality

@@
 \begin{document}
-    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
+    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure}
     \author{Thomas C. Fraser}
@@
     \begin{abstract}
-        It has long been recognized that certain quantum correlations are often incompatible with particular assumption about classical causal structure.
-Such correlations are sometimes termed non-local, although they are more accurately termed non-classical, as the presence of correlations certifies the genuinely non-classical nature of a causal setup in a device-independent fashion.
-Whenever a quantum correlation violates a causal compatibility inequality (e.g.
-a Bell inequality) then the correlation is witnessed as non-classical.
+        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure.
+Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion.
+In the context of two parties sharing a common resource, these non-classical correlations are also known as non-local correlations.
 Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion.
@@
     \end{figure}
-    \section{Triangle Structure}
+    \section{Triangle structure}
     \label{sec:triangle_structure}
@@
 
-    \section{Triangle Structure Inequalities}
+    \section{Triangle structure Inequalities}
     \label{sec:found_inequalities}
 
-    \Cref{sec:causal_compatibility} defined causal compatibility inequalities while \cref{sec:fritz_distribution} recalled and discussed the Fritz distribution together with a brief summary of its incompatibility with the Triangle Structure.
-Heretofore, there were no known causal compatibility inequalities for the Triangle Structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}.
-By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle Structure that are violated by the Fritz distribution.
+    \Cref{sec:causal_compatibility} defined causal compatibility inequalities while \cref{sec:fritz_distribution} recalled and discussed the Fritz distribution together with a brief summary of its incompatibility with the Triangle structure.
+Heretofore, there were no known causal compatibility inequalities for the Triangle structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}.
+By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle structure that are violated by the Fritz distribution.
 A representative sample of these inequalities are presented here.
@@
     \end{equation*}
-    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle Structure (i.e.
+    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure (i.e.
 factorizes according to \cref{eq:compatibility_as_factorization}) must satisfy \cref{eq:ww_ineq}.
@@
 For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$.
-Consequently we conclude that the Fritz distribution is incompatible with the Triangle Structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.
+Consequently we conclude that the Fritz distribution is incompatible with the Triangle structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.
 
@@
 In fact, \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
-This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as \cref{eq:ww_ineq} strong enough to witness incompatible quantum distributions for the Triangle Structure.
+This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as \cref{eq:ww_ineq} strong enough to witness incompatible quantum distributions for the Triangle structure.
 More universally, this result shows that the Inflation Technique is a promising tool for understanding quantum non-classical in more general causal structures.
 
-    In addition to \cref{eq:ww_ineq}, numerous independent inequalities were derived for the Triangle Structure that are violated by the Fritz distribution.
+    In addition to \cref{eq:ww_ineq}, numerous independent inequalities were derived for the Triangle structure that are violated by the Fritz distribution.
 The majority of these inequalities share most or all of the qualitative features of \cref{eq:ww_ineq}, and hence those inequalities are omitted from this manuscript.
@@
     The inequalities presented above (\cref{eq:ww_ineq,eq:web_inequality}) were curated to demonstrate the incompatibility of the Fritz distribution in particular.
-To reiterate, the Fritz distribution is incompatible with the Triangle Structure because it assigns a unique role to one of the variables, specifically $C$.
+To reiterate, the Fritz distribution is incompatible with the Triangle structure because it assigns a unique role to one of the variables, specifically $C$.
 The asymmetry within the Fritz distribution is reflected in the asymmetry of \cref{eq:ww_ineq,eq:web_inequality}.
-In order to discover new forms of non-classicality in the Triangle Structure, it is desirable to obtain measures of non-classicality (i.e.
+In order to discover new forms of non-classicality in the Triangle structure, it is desirable to obtain measures of non-classicality (i.e.
 inequalities) that do not admit this bias.
@@
 These inequalities are derived without making use of Bell's theorem and instead uses the Inflation Technique to approach non-classicality from a causal inference perspective.
-Additionally, the derivation of causal compatibility inequalities allows one prove incompatibility even when perfect correlations are absent.
+Additionally, the derivation of causal compatibility inequalities prove incompatibility even when perfect correlations are absent.
 
@@
     \label{sec:violations_noise}
-    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality.
-In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities.
-In order to compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ so $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
+    Causal compatibility inequalities, including those derived in \cref{sec:found_inequalities}, offer an avenue into studying quantum non-classicality.
+Ultimately, the motivation for finding these inequalities is binary: the first is to classify differing distributions by their compatibility with a given causal structure, and the second is to measure the degree in which a given distribution is non-classical.
+This approach has been well-studied in the Bell structure, where extremal non-classical correlations maximally violate Bell inequalities~\cite{PR_1995}.
+However, inequalities are just a singular example of numerous distinct measures of non-classicality~\cite[Section 5]{Vicente_2014}.
+Alternatives include measuring the non-local content, robustness to noise, or even the classical simulation cost of a given distribution.
+For previously studied causal structures, such as the Bell structure, there exists a uncertainty toward which measure of non-classicality is best.
+The inequalities derived in this report are likely \textit{not} the best measures of non-classicality simply because they have be curated toward the Fritz distribution.
+Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure to be found that admit quantum violations.
+In this section, two measures are used that make use of these compatibility inequalities: robustness to noise and direct numerical violation.
+
+    To compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ such that $I\br{\prob} < 0$ indicates violation of $I$ while $I\br{\prob} \leq 0$ indicates satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
 For the subsequent analysis, $4$ inequalities where chosen.
@@
     \label{sec:optimizations}
-    \todo[TC]{Determine if I should remove this paragraph or shorten it}
-    Causal compatibility inequalities act as a \textit{measure} of non-classicality.
-If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$.
-However, this statement is accompanied by a few caveats.
-First, it is possible (and frequently the case) for ${I\br{\prob[1]}} < I\br{\prob[2]}$ to hold for one inequality $I$ but have ${\ti I\br{\prob[2]}} < \ti I\br{\prob[1]}$ hold for another inequality $\ti I$.
-In this case, all one can claim is that $\prob[1]$ is more incompatible than $\prob[2]$ with respective to $I$ but the contrary is true with respect to $\ti I$.
-Second, not all inequalities $I$ are \textit{good} measures of non-classicality.
-In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality because the facets form a necessary and sufficient of constraints with all other inequalities following from positive mixtures.
-However, good measures of incompatibility are less understood in the Triangle structure where the space of classical correlations is non-convex.
-At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility simply because they have be curated toward the Fritz distribution.
-Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure.
-
-    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle Structure \cref{fig:triangle_structure} and thus expressed as follows:
+
+    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure (\cref{fig:triangle_structure}) and thus expressed as follows:
     \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
@@
 
-    \subsection{Rosset Variation}
-    \label{sec:rosset_variation}
-    \todo[TC]{This might take a page}
-
     \section{Conclusions}
@@
 In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states.
-As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.}.
-The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
+As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.} The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
 At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure.
@@
 By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled.
-This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle Structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings.
-Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible.\footnote{This insight was originally made by Miguel Navascués in private communications.} Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle Structure which have the fewest number of outcomes.
+This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings.
+Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible.\footnote{This insight was originally made by Miguel Navascués in private communications.} Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes.
+In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes, one corresponding to $A, B$ correlations and another corresponding to $A, B$ anti-correlations.\footnote{This variation was originally suggested by Denis Rosset in private communications.} These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and should be a focus for future research.
 
@@
 
-    \subsection{Exemplary Inflations of The Triangle Structure}
+    \subsection{Exemplary Inflations of The Triangle structure}
     \label{sec:exemplary_inflations_of_the_triangle structure}
 
-    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle Structure by constructing inflations of the Triangle Structure satisfying \cref{eq:inflation_defn}.
-Explicitly, for a given inflation $\graph'$ of the Triangle Structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal pre-injectable sets of $\graph'$, i.e.
+    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}.
+Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal pre-injectable sets of $\graph'$, i.e.
 $\mscenario = \PreInj[\graph]{\graph'}$.
@@
 those where $\forall \varphi \in \gp\br{\mscenario} :  \varphi\bs{I_{\mscenario}} = I_{\mscenario}$.
+To generate inequalities that exhibit certain symmetries using the methods described in \cref{sec:marginal_satisfiability}, it is sufficient to perform a change of basis on the incidence matrix $M$ for a given marginal scenario $\mscenario$.
 Through repeated action of $\varphi \in \gp$ on marginal outcomes $m \in \Events{\mscenario}$ and joint outcomes $j \in \Events{\jointvar}$, one can define \term{group orbits} of $\gp$ in $\Events{\mscenario}$ and $\Events{\jointvar}$; respectively $\Orb[\gp]{m} \defined \bc{\varphi\bs{m} \mid \varphi \in \gp}$, $\Orb[\gp]{j} \defined \bc{\varphi\bs{j} \mid \varphi \in \gp}$.
@@
 
-    % \section{Quantum Parameterization of Triangle Structure}
+    % \section{Quantum Parameterization of Triangle structure}
     % \label{sec:param_quantum_dist}

### 2017-05-31 documents/TriangleScenarioArXiv/ts.tex
removed all discussion of the local markov property

@@
 Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$.
-Specifically, the causal structure $\graph$ hypothesizes that each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$, then $n$ should be independent of all other variables, except its own descendants when conditioned over $\Pa[\graph]{n}$.
+Specifically, the causal structure $\graph$ hypothesizes that if each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$, then each $n$ should be conditionally independent of all other variables:
+    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:compatibility_as_factorization}\]
+    % , except its own descendants when conditioned over $\Pa[\graph]{n}$.
 This is known as the \term{local Markov property}:\footnote{Here $A \indep B \mid C$ denotes statistical independence between $A$ and $B$ conditional on $C$ where $A,B,C \subseteq \nodes$, i.e.
 for a given probability distribution $\prob[\nodes]$, $\prob[AB \mid C] = \prob[A \mid C]\prob[B \mid C]$.}
-    \[ n \indep \br{\nodes \setminus \De[\graph]{n}} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
-    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:local_markov_property}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}.
-Alternatively yet equivalently, the notion of compatibility can be interpreted as follows: a distribution $\prob[\nodes]$ is compatible with $\graph$ if $\prob[\nodes]$ can be consistently factorized into conditional probability distributions for each variable $n \in \nodes$ conditioned on its parents $\Pa[\graph]{n}$:
-    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:compatibility_as_factorization}\]
+    % \[ n \indep \br{\nodes \setminus \De[\graph]{n}} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
+    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:compatibility_as_factorization}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}.
 The conditional distributions in \cref{eq:compatibility_as_factorization} (i.e.
 $\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}.
-If a distribution $\prob[\nodes]$ violates \cref{eq:local_markov_property} or equivalently cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$.
+If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$.
 When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is trivially easy to verify whether or not $\prob[\nodes]$ is compatibility with $\graph$; \cref{sec:satisfaction_of_d_sep_relations} describes in detail how this is accomplished.
@@
     \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
-    Then the compatible marginal context $\prob[N']$ must be probabilistically separable $\prob[N'] = \prob[N_1']\prob[N_2']$ due to \cref{eq:local_markov_property}.
+    Then the compatible marginal context $\prob[N']$ must be probabilistically separable $\prob[N'] = \prob[N_1']\prob[N_2']$ due to \cref{eq:compatibility_as_factorization}.
 Since $N_1'$ and $N_2'$ are both injectable, the inflation lemma now applies and the original inequality can be deflated.

### 2017-06-01 documents/TriangleScenarioArXiv/ts.tex
Improved the discussion of d-seperation

@@
 If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$.
-When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is trivially easy to verify whether or not $\prob[\nodes]$ is compatibility with $\graph$; \cref{sec:satisfaction_of_d_sep_relations} describes in detail how this is accomplished.
-
-    A challenge is present when one is supplied with a partial observation, i.e.
+The compatibility of a distribution $\prob[\nodes]$ with a causal structure $\graph$ pursuant to \Cref{eq:compatibility_as_factorization} is equivalent to the requirement that $\prob[\nodes]$ obeys all of the conditional independence constraints implied by the \textit{d-separation relations} between variables/nodes in $\graph$~\cite{Pearl_2009}.
+When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is trivially easy to verify whether or not $\prob[\nodes]$ is compatible with $\graph$ by simply computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}.
+
+    A challenge is presented when one is supplied with a partial observation, i.e.
 a joint distribution $\prob[\nodes_{O}]$ where $\nodes_{O} \subset \nodes$ is some subset of variables referred to as the \term{observable nodes} $\nodes_O$.
-In such cases, \cref{eq:compatibility_as_factorization} can not be verified by direction calculation because it is certainly possible that the parents of some observable node are themselves unobservable $\Pa[\graph]{\nodes_{O}} \not \subseteq \nodes_{O}$.
-In such cases, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \prod_{n \in \nodes_{O}} \prob[n \mid \Pa[\graph]{n}]$.
-The unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$ representing hidden random variables that are hidden either by some fundamental process or cannot be measured due to other limitations.
-    \todo[TC]{Explain why this is difficult more.}
-    \todo[TC]{Figure out if I should include d-sep here}
-    \todo[TC]{Explain what this work and inflation accomplishes regarding this}
-
-    In practice however, checking causal parameters systemically is intractable, especially when the cardinality (number of outcomes) of the latent variables is unspecified.
-Instead, \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of simply Bell inequalities for two reasons.
+In such cases, $\prob[\nodes_{O}]$ does not induce a unique set of causal parameters for $\graph$ and \cref{eq:compatibility_as_factorization} can not be verified by direction calculation.
+Instead, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \prod_{n \in \nodes_{O}} \prob[n \mid \Pa[\graph]{n}]$.
+The complementary, unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$ representing hidden random variables that are hidden either by some fundamental process or cannot be measured due to other limitations.
+
+    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two naive approaches worth mentioning here.
+The first is to recognize that the conditional independence constraints implied by d-separation relations over the \textit{observable} variables form a family of necessary constraints for $\prob[\nodes_{O}]$.
+The failure to satisfy one of these observable independence relations immediately qualifies $\prob[\nodes_{O}]$ as incompatible with $\graph$.
+Often, the observable d-separation relations implied by a causal structure form an \textit{insufficient} set of constraints for compatible distributions.
+Such causal structures have been termed \textit{interesting}~\cite{Henson_2014}, and more involved classification techniques must be used~\cite{Inflation}.
+The principle focus of this paper is the Triangle structure and has been shown to be one of the smallest interesting causal structures~\cite{Henson_2014}.
+An alternative approach requires the cardinality (number of outcomes) of the latent variables to be fixed.
+In most realistic scenarios, the nature of the latent variables is completely unspecified.
+More powerful approaches find constraints for $\prob[\nodes]$ in the form of probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals which constraint the set of compatible probability distributions.
+We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of simply Bell inequalities for two reasons.
 Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure.
-Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.} are probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its induced marginals which constraint the set of compatible probability distributions.
-If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}.
+Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.} If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}.
 In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.
@@
     \end{equation*}
-    Analogously to the Wagon-Wheel inflation, these pre-injectable sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ and $201,326,592$ non-zero entires.
+    Analogously to the Wagon-Wheel inflation, these pre-injectable sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.
 

### 2017-06-01 documents/TriangleScenarioArXiv/ts.tex
removed appendix A1
added review section for Bell structure

@@
 Causal compatibility inequalities, such as Bell and Instrumental inequalities, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation.
-To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_scenario}.
+To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}.
 The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$.
@@
 
-    % A number of causal structures are depicted throughout this document (see \cref{fig:bell_scenario,fig:triangle_structure,fig:inflations}).
+    % A number of causal structures are depicted throughout this document (see \cref{fig:bell_structure,fig:triangle_structure,fig:inflations}).
 As an example, the Triangle structure has $3$ observable nodes and $3$ latent nodes,
@@
 Often, the observable d-separation relations implied by a causal structure form an \textit{insufficient} set of constraints for compatible distributions.
-Such causal structures have been termed \textit{interesting}~\cite{Henson_2014}, and more involved classification techniques must be used~\cite{Inflation}.
+Such causal structures, which include the Bell structure, have been termed \textit{interesting}~\cite{Henson_2014}, and more involved classification techniques must be used~\cite{Inflation}.
 The principle focus of this paper is the Triangle structure and has been shown to be one of the smallest interesting causal structures~\cite{Henson_2014}.
@@
     \label{sec:bell_structure}
-    \todo[TC]{Review of Bell structure, Tsirelson-box, CHSH inequality}
-
+    This section aims to define the Bell structure and summarize the main results associated with its non-classical character.
+The purpose of this section is to equip an unfamiliar reader with the pertinent background and also to establish a context for which to draw comparisons between the advancements made toward understanding non-classicality of the Bell structure and the analogous results obtained for Triangle structure in the remainder of this work.
+Readers familiar with the Bell structure (sometimes called Bell scenario/experiment) will experience little obstacles proceeding to \Cref{sec:triangle_structure}.
+
+    The Bell structure (\cref{fig:bell_structure}) refers to an iconic causal structure involving two distant observers which make local measurements $A, B$ determined by measurement settings $S_A, S_B$ on a shared latent resource $\la$~\cite{Brunner_2013}.
+The resulting observed correlations form a conditional probability distribution $\prob[AB|S_AS_B]$.
+Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, this distribution is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ such that there exists a distribution $\prob[AB|S_AS_B,\la]$ such that $\prob[AB|S_AS_B] = \sum_{\la} \prob[AB|S_AS_B,\la]$ and also satisfies the following implementation of \cref{eq:compatibility_as_factorization}:
+    \[ \prob[AB|S_AS_B,\la] = \prob[A|S_A,\la]\prob[B|S_B,\la] \]
+    Any observed distribution $\prob[AB|S_AS_B]$ which fails to be explained by the classical causal hypothesis of the Bell structure is appropriately termed non-classical.
+Often, distributions incompatible with the Bell structure are referred to as non-local because the Bell structure indicates that the latent resource is shared locally and measurements are made locally.
+In particular,~\citet{Bell_1964} demonstrated that there exists distributions that are non-classical yet are attainable via quantum resources and measurements.
+If one does not wish to accept fine-tuning arguments, one must accept that quantum correlations can be non-local as no variation to the latent nodes can explain the same correlations~\cite{Wood_2012}.\footnote{This is unlike the Triangle structure wherein a global yet latent common cause is always an acceptable explanation for any correlation and does require fine-tuning.
+Therefore, we never refer to non-classical correlations in Triangle Structure as non-local.} A distribution is accessible with quantum resources and measurements if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension and measurement operators $M_{A|S_A}, M_{B|S_B}$ conditional indexed by the measurement settings such that $\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}$.
+The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities such as the CHSH inequality (\cref{eq:CHSH_ineq_orig}) which constrain the correlations between binary variables $A$ and $B$ for classical distributions~\cite{CHSH_Original}.
     \[ \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 0} + \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 1} + \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 0} - \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 1} \leq 2 \eq \label{eq:CHSH_ineq_orig} \]
+    Non-trivial Bell inequalities such as the CHSH inequality are capable of distinguishing the non-classical nature of distributions beyond the constraints implied by observable d-separation relations; the inequalities presented in \cref{sec:found_inequalities} are also of this type.
+
+    Finally, must like any causal structure, Bell inequalities act as a measure of the non-classical character of a given distribution.
+In particular, the antecedent of \cref{eq:CHSH_ineq_orig} has a classical upper-bound of $2$ and it can be shown to have a quantum upper-bound of $2\sqrt{2}$~\cite{Cirelson_1980}.
+Furthermore, non-classical distributions that are also non-quantum such as the PR-box correlations are upper-bounded by $4$~\cite{PR_1995}.
+In \cref{sec:found_inequalities}, newly discovered and analogous inequalities for the Triangle structure are presented.
+Although their associated quantum and post-quantum upper-bounds are currently unknown, an attempt to numerical compute these is discussed in \cref{sec:optimizations}.
 
@@
 The shared hidden variable is labeled $\la$.}
-            \label{fig:bell_scenario}
+            \label{fig:bell_structure}
         \end{minipage}\hspace{0.04\textwidth}%
@@
     %And also, the given distribution
-    $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$:
+    $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}:
     \[ \prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \eq \label{eq:triangle_compatibility} \]
@@
         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational_fritz_bell}}
-        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{\p{A}},S_{\p{B}}$ are latent nodes unlike the Bell structure (\cref{fig:bell_scenario}).}
+        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{\p{A}},S_{\p{B}}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
         \label{fig:triangle_structure_with_fritz_bell_embedded}
@@
     As was originally noticed by \citet{Fritz_2012}, it is possible to construct quantum distributions incompatible with the Triangle structure by utilizing quantum distributions incompatible with the familiar Bell structure.
-To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} and contrast it with the Bell structure of \cref{fig:bell_scenario}.
+To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} and contrast it with the Bell structure of \cref{fig:bell_structure}.
 Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure.
@@
 If one writes the outcome labels $\bc{0,1,2,3}$ in binary $\bc{00,01,10,11}$, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by the outcome of $\p C$.
-Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits emulate the measurement settings $S_{\p A}$ and $S_{\p B}$ and the right-hand bits emulate a two-outcome measurement performed by $A, B$ as they would in~\cref{fig:bell_scenario}.
+Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits emulate the measurement settings $S_{\p A}$ and $S_{\p B}$ and the right-hand bits emulate a two-outcome measurement performed by $A, B$ as they would in~\cref{fig:bell_structure}.
 Specifically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.
@@
 
-    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}).
+    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_structure}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}).
 Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations.
@@
 
-    \subsection{Satisfaction of d-Separation Relations}
-    \label{sec:satisfaction_of_d_sep_relations}
-    \todo[TC]{Absorb the relevant components of the next section into this one}
-    \todo[TC]{Given a distribution and a causal structure, does the distribution satisfy the conditional d-Separation relations?}
+    % \subsection{Satisfaction of d-SSeparation Relations}
+    % \label{sec:satisfaction_of_d_sep_relations}
+    % \todo[TC]{Absorb the relevant components of the next section into this one}
+    % \todo[TC]{Given a distribution and a causal structure, does the distribution satisfy the conditional d-Separation relations?}
 
@@
     \label{sec:inflation_technique_main_summary}
-    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$.
+    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$.
 As a preliminary summary, the Inflation Technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
@@
     % \cref{eq:unique_causal_parameters,eq:inflated_causal_parameters,eq:unique_causal_parameters_inflated}
-    Together, ??
-form the \term{weak inflation lemma}: compatible joint distributions over $\nodes$ induce compatible joint distributions over $\nodes'$.
-Before generalizing to the inflation lemma, a careful observation needs to be made.
+    In essence, a compatible joint distribution over $\nodes$ can be \textit{inflated} to induce compatible joint distributions over $\nodes'$.
+Before generalizing this idea, a careful observation needs to be made.
 For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$, where $N \subset \nodes$, induces a compatible marginal distribution $\prob[N']$ over $N'$.
@@
     \end{align*}
-    Injectable sets are incredibly useful for causal compatibility because they allow one to extend the weak inflation lemma to \textit{the} inflation lemma:
-    \todo[TC]{How do I claim the inflation lemma without defining compatibility over a marginal model (instead of a distribution)}
+    Injectable sets are incredibly useful for causal compatibility because they permit one to inflate compatibility over a particular subset of \textit{marginal models}.
+A marginal model is compatible with a given causal structure $\graph$ if it admits a joint distribution (see \cref{sec:marginal_satisfiability}) that is compatible with $\graph$.
+
     \begin{lemma}
@@
 Fortunately, an inflated causal structure $\graph'$ possesses its own conditional independence relations which can be exploited to turn linear inequalities on $\graph'$ into polynomial inequalities on $\graph$.
-
-    Suppose that one were to obtain an inequality on $\graph'$ that contained probabilistic terms such as $\prob[N']$ where $N' \not \in \Inj[\graph]{\graph'}$.
+After obtaining an inequality for $\graph'$, each of its term is generically of the form $\prob[N']$ where $N'$ may not be injectable $N' \not \in \Inj[\graph]{\graph'}$.
 At this point, the Inflation lemma is not applicable because it requires probabilistic constraints to consist entirely of distributions $\prob[N']$ where $N'$ is injectable.
-If for example, $N' \not \in \Inj[\graph]{\graph'}$ could be partitioned into two injectable subsets $N_1' \in \Inj[\graph]{\graph'}$ and $N_2' \in \Inj[\graph]{\graph'}$ that where \term{ancestrally independent} in $\graph'$,
+If for example, $N' \not \in \Inj[\graph]{\graph'}$ could be partitioned into two injectable subsets $N_1' \in \Inj[\graph]{\graph'}$ and $N_2' \in \Inj[\graph]{\graph'}$ that where \term{ancestrally independent} in $\graph'$,\footnote{Ancestral independence is equivalent to d-separation conditioned on the empty set $\emptyset$~\cite{Pearl_2009}.}
     \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
@@
 
-    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that can are called the \term{pre-injectable sets}.
+    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{pre-injectable sets} of $\graph'$.
 A set $N' \subseteq \nodes'$ is a pre-injectable set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
 
-    A pre-injectable set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to graphical $d$-separation conditions~\cite{Pearl_2009},
+    A pre-injectable set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions~\cite{Pearl_2009}\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}.
+This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.},
     \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
@@
 Throughout the body of this work, we let $\PreInj[\graph]{\graph'}$ denote the set of all pre-injectable sets.
-Naturally, the pre-injectable sets will define a marginal scenario $\mscenario$ that are used to derive compatibility inequalities in \cref{sec:deriving_inequalities}\footnote{Analogously for a marginal scenario $\mscenario$, the pre-injectable sets $\PreInj[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
-Therefore, in practice, it is completely sufficient to focus on the maximal pre-injectable sets}.
+To derive inequalities for the inflated causal structure $\graph'$, the pre-injectable sets define a marginal scenario $\mscenario$\footnote{Analogously for a marginal scenario $\mscenario$, the pre-injectable sets $\PreInj[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
+Therefore, in practice, it is completely sufficient to focus on the maximal pre-injectable sets.} that are used to derive inequalities using methods discussed in \cref{sec:marginal_satisfiability}.
 

### 2017-06-10 documents/TriangleScenarioArXiv/ts.tex
Changed all of the inequalities to a canonical form where violation is a maximization above zero

@@
     \eq\label{eq:ww_ineq}
-    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \cdots \\
-    \cdots + P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \cdots \\
-    \cdots + P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \cdots \\
-    \cdots + P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \cdots \\
-    \cdots + P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \cdots \\
-    \cdots + P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \cdots \\
-    \cdots + P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \cdots \\
-    \cdots + P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \cdots \\
-    \cdots + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \cdots \\
-    \cdots + P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \cdots \\
-    \cdots + P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) - P_{ABC}(000)P_{C}(3) \geq 0
+    + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
+    - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
+    - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
+    - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
+    - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
+    - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
+    - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
+    - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
+    - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
+    - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
+    - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
     \end{gathered}
@@
 As a demonstration, the Fritz distribution violates \cref{eq:ww_ineq}.
-Notice the final term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $-1$.
-For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$.
+Notice the first term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $+1$.
+For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $0.0129\ldots \not \leq 0$.
 Consequently we conclude that the Fritz distribution is incompatible with the Triangle structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.
@@
 
-    It is possible to simplify \cref{eq:ww_ineq} identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$.
+    It is possible to simplify \cref{eq:ww_ineq} by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$.
 Upon doing so, one obtains the following,
     \begin{gather*}
-        P_{ABC}(303)P_{C}(0) + P_{ABC}(313)P_{C}(0) + P_{ABC}(302)P_{C}(1) + P_{AB}(02)P_{C}(2) + P_{AB}(03)P_{C}(2) + \cdots \\
-        \cdots + P_{AB}(20) + P_{AB}(30) + P_{C}(3)P_{C}(0) - P_{ABC}(000)P_{C}(3) - P_{ABC}(021)P_{C}(2) + \cdots \\
-        \cdots - P_{ABC}(202) - P_{ABC}(302) - P_{ABC}(233)P_{C}(0) - P_{AC}(33)P_{C}(0) \geq 0
+        + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
+        - P_{ABC}(303)P_{C}(0) - P_{ABC}(313)P_{C}(0) - P_{ABC}(302)P_{C}(1) - P_{AB}(02)P_{C}(2) - \\
+        - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
     \end{gather*}

### 2017-06-12 documents/TriangleScenarioArXiv/ts.tex
removed table of contents and added appropriate reference to Miguel Navascues' recent work

@@
     \maketitle
-    \tableofcontents
+    % \tableofcontents
     % \setlength{\parskip}{1em}
@@
 Upon doing so, one obtains the following,
-    \begin{gather*}
+    \begin{equation*}
+    \begin{gathered}
+    \eq\label{eq:ww_ineq_symplified}
         + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
@@
         - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
-    \end{gather*}
+    \end{gathered}
+    \end{equation*}
 
@@
 For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$.
-Furthermore, the existence of an inequality capable of witnessing Fritz distribution \textit{is guaranteed}, albeit there was \textit{no guarantee} that the Inflation Technique would be capable of producing such an inequality.
-In fact, \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
+Furthermore, the existence of an inequality capable of witnessing the non-classicality of the Fritz distribution is guaranteed and the Inflation Technique is capable of producing such an inequality~\cite{Navascues_2017}, albeit requiring a sufficiently complex inflation of the Triangle structure.
+In fact, \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and others were \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
 This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as \cref{eq:ww_ineq} strong enough to witness incompatible quantum distributions for the Triangle structure.

### 2017-06-12 documents/TriangleScenarioArXiv/ts.tex
Credited Miguel Navascues and Denis Rosset in the acknowledgements section

@@
 This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings.
-Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible.\footnote{This insight was originally made by Miguel Navascués in private communications.} Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes.
-In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes, one corresponding to $A, B$ correlations and another corresponding to $A, B$ anti-correlations.\footnote{This variation was originally suggested by Denis Rosset in private communications.} These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and should be a focus for future research.
-
-    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_structure}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}).
+Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible.
+Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes.
+In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations.
+These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and should be a focus for future research.
+
+    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_structure}) into the Triangle structure via the re-imagined version of the Triangle structure (\cref{fig:triangle_structure_with_fritz_bell_embedded}).
 Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations.
@@
 Research at Perimeter Institute is supported by the Government of Canada through the Department of Innovation, Science and Economic Development Canada and by the Province of Ontario through the Ministry of Research, Innovation and Science.
+The authors are grateful to Miguel Navascués for drawing our attention to the existence of distributions genuinely requiring quantum resources for all latent nodes in the Triangle structure.
+Moreover, the authors credit Denis Rosset for suggesting a Fritz distribution variant involving a reduced cardinality of outcomes.
     \end{acknowledgments}
@@
 $\mscenario = \PreInj[\graph]{\graph'}$.
-This section acts as a reference for the particular inflations of the Triangle scenario that are mentioned throughout this manuscript.
+This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript.
 Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their pre-injectable sets.

### 2017-06-12 documents/TriangleScenarioArXiv/ts.tex
Removed I_2 and added names to all inequalities that remained

@@
 
-    The first causal compatibility inequality is reported below:
+    The first causal compatibility inequality chosen for presentation is reported below:
     \begin{equation*}
@@
     \eq\label{eq:ww_ineq}
+    I\tsb{WagonWheel} : \\
     + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
@@
     \end{equation*}
+    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it.
+To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:exemplary_inflations_of_the_triangle structure}.
+
     By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure (i.e.
-factorizes according to \cref{eq:compatibility_as_factorization}) must satisfy \cref{eq:ww_ineq}.
-As a demonstration, the Fritz distribution violates \cref{eq:ww_ineq}.
-Notice the first term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $+1$.
-For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $0.0129\ldots \not \leq 0$.
+factorizes according to \cref{eq:triangle_compatibility}) must satisfy $I\tsb{WagonWheel}$.
+As a demonstration, the first term in \cref{eq:ww_ineq} for the Fritz distribution is $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ while all of the remaining terms sum to $\simeq 0.0136$.
+Therefore, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $0.0129\ldots \not \leq 0$.
 Consequently we conclude that the Fritz distribution is incompatible with the Triangle structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.
 
-    To reiterate, the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary} and more details can be found in \cref{sec:exemplary_inflations_of_the_triangle structure}.
-
-    It is possible to simplify \cref{eq:ww_ineq} by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$.
-Upon doing so, one obtains the following,
+    It is possible to simplify $I\tsb{WagonWheel}$ by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$.
+Upon doing so, one obtains an equivalent representation for $I\tsb{WagonWheel}$,
     \begin{equation*}
@@
     \eq\label{eq:ww_ineq_symplified}
+    I\tsb{WagonWheel} : \\
     + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
@@
 
-    In order to understand the importance of \cref{eq:ww_ineq}, there are a couple of important concepts to understand.
+    In order to understand the importance of $I\tsb{WagonWheel}$, there are a couple of important concepts to understand.
 First, the Fritz distribution was originally known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings $A_l, B_l$.
-The inequality of \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure.
-For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$.
+The inequality of $I\tsb{WagonWheel}$ represents a significant advancement in our understanding of non-classicality in the Triangle structure.
+For example, $I\tsb{WagonWheel}$ is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$.
 Furthermore, the existence of an inequality capable of witnessing the non-classicality of the Fritz distribution is guaranteed and the Inflation Technique is capable of producing such an inequality~\cite{Navascues_2017}, albeit requiring a sufficiently complex inflation of the Triangle structure.
-In fact, \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and others were \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
-This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as \cref{eq:ww_ineq} strong enough to witness incompatible quantum distributions for the Triangle structure.
+In fact, $I\tsb{WagonWheel}$ was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and others were \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
+This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as $I\tsb{WagonWheel}$ strong enough to witness incompatible quantum distributions for the Triangle structure.
 More universally, this result shows that the Inflation Technique is a promising tool for understanding quantum non-classical in more general causal structures.
 
-    In addition to \cref{eq:ww_ineq}, numerous independent inequalities were derived for the Triangle structure that are violated by the Fritz distribution.
-The majority of these inequalities share most or all of the qualitative features of \cref{eq:ww_ineq}, and hence those inequalities are omitted from this manuscript.
-Instead, we present \cref{eq:web_inequality}, another causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was produced using the \cref{fig:the_web_inflation} --- a considerably larger inflation than the Wagon-Wheel inflation.
+    In addition to $I\tsb{WagonWheel}$, numerous independent inequalities were derived for the Triangle structure that are violated by the Fritz distribution.
+The majority of these inequalities share most or all of the qualitative features of $I\tsb{WagonWheel}$, and hence those inequalities are omitted from this manuscript.
+Instead, we present $I\tsb{Web}$ (\cref{eq:web_inequality}), another causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was produced using the Web inflation (\cref{fig:the_web_inflation}) --- a considerably larger inflation than the Wagon-Wheel inflation.
 Note that in \cref{eq:web_inequality} $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
@@
     \label{eq:web_inequality}
-        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
+    \begin{gathered}
+        I\tsb{Web} : \\
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
+    \end{gathered}
     \end{equation}
 
-    The inequalities presented above (\cref{eq:ww_ineq,eq:web_inequality}) were curated to demonstrate the incompatibility of the Fritz distribution in particular.
+    The inequalities presented above, namely $I\tsb{WagonWheel}$ and $I\tsb{Web}$, were curated to demonstrate the incompatibility of the Fritz distribution in particular.
 To reiterate, the Fritz distribution is incompatible with the Triangle structure because it assigns a unique role to one of the variables, specifically $C$.
-The asymmetry within the Fritz distribution is reflected in the asymmetry of \cref{eq:ww_ineq,eq:web_inequality}.
-In order to discover new forms of non-classicality in the Triangle structure, it is desirable to obtain measures of non-classicality (i.e.
-inequalities) that do not admit this bias.
-In an effort to find a causal compatibility inequality qualitatively distinct from \cref{eq:ww_ineq,eq:web_inequality}, we developed a technique to derive inequalities with certain symmetry properties such as \cref{eq:symmetic_web_inequality} which is symmetric with respect to any permutation of the variables $A, B, C$.
+The asymmetry within the Fritz distribution is reflected in the asymmetry of $I\tsb{WagonWheel}$ and $I\tsb{Web}$.
+In order to discover new forms of non-classicality in the Triangle structure, it is desirable to obtain measures of non-classicality, such as inequalities, that do not admit this bias.
+In an effort to find a causal compatibility inequality qualitatively distinct from $I\tsb{WagonWheel}$ or $I\tsb{Web}$, we developed a technique to derive inequalities with certain symmetry properties such as \cref{eq:symmetic_web_inequality} which is symmetric with respect to any permutation of the variables $A, B, C$.
 These techniques are explained in \cref{sec:symmetric_inequalities}.
@@
         \label{eq:symmetic_web_inequality}
-        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
+    \begin{gathered}
+        I\tsb{SymmetricWeb} : \\
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
+    \end{gathered}
     \end{equation}
@@
     Most importantly, these causal compatibility inequalities are a positive resolution of Fritz's problem from \cref{sec:fritz_distribution}.
-These inequalities are derived without making use of Bell's theorem and instead uses the Inflation Technique to approach non-classicality from a causal inference perspective.
-Additionally, the derivation of causal compatibility inequalities prove incompatibility even when perfect correlations are absent.
+These inequalities are derived without making use of Bell's theorem and instead uses the Inflation Technique to approach non-classicality from a more universal causal inference perspective.
 
@@
 
-    To compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ such that $I\br{\prob} < 0$ indicates violation of $I$ while $I\br{\prob} \leq 0$ indicates satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
-For the subsequent analysis, $4$ inequalities where chosen.
-First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}.
-The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{eq:web_inequality} while $I_3$ is the symmetric inequality in \cref{eq:symmetic_web_inequality}.
-Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{eq:web_inequality}.
+    To compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ into the format of \cref{eq:ww_ineq,eq:web_inequality,eq:symmetic_web_inequality} where the linear combination of all terms is upper-bound by $0$.
+For each inequality $I$ and distribution $\prob$, $I\br{\prob}$ denotes the numerical value associated with this upper-bound.
+Correspondingly, $I\br{\prob} > 0$ indicates violation of $I$ while $I\br{\prob} \leq 0$ indicates satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
 
@@
 
-    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$.
-Since the uniform distribution $\s{U}$ is trivially compatible with the Triangle structure, the objective of this section is to determine how much uniform noise needs to be added to the Fritz distribution $\prob[\fritz]$ before it transitions from incompatible to compatible.
-We do this by defining an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ along with the \term{noisy variant} $\s{N}_{\vep}$ of the Fritz distribution,
+    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$, which is trivially compatible with the Triangle structure.
+The objective of this section is to quantify how much statistical noise can be added to the Fritz distribution $\prob[\fritz]$ before the reported inequalities fail to witness incompatibility.
+The associated quantifier used was an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ where $\s{N}_{\vep}$ denotes an \term{$\vep$-noisy Fritz distribution},
     \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
-    Therefore as $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$.
-For each inequality $I$ and distribution $\prob$, let $I\br{\prob}$ denote a scalar value representing the amount of violation seen by $\prob$.
-Our tests suggest that inequality $I_1$ (\cref{eq:web_inequality}) is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to at least a noise parameter of $\vep \simeq 0.085$.
+    As $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$.
+Our tests suggest that $I\tsb{Web}$ is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to a noise parameter of $\vep \simeq 0.085$.
 The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}.
-Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I_1$.
+Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I\tsb{Web}$; an exhaustive search has not been conducted.
 
@@
 In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
-Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states.
-Qubit states are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix.
+Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states which are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix.
 Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
-First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure.
+First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for generating incompatible quantum distributions in the Triangle structure.
 Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$.
@@
             \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
-            \caption{Probability distribution that maximizes violation of $I_1$ from \cref{eq:web_inequality} ($V_F \simeq 1.501$).}
+            \caption{Probability distribution that maximizes violation of $I\tsb{Web}$ ($V_F \simeq 1.501$).}
             \label{fig:maximum_violation_I_1}
@@
             \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
-            \caption{Probability distribution that maximizes violation of $I_3$ from \cref{eq:symmetic_web_inequality} ($V_F \simeq 2.61$).}
+            \caption{Probability distribution that maximizes violation of $I\tsb{SymmetricWeb}$ ($V_F \simeq 2.61$).}
             \label{fig:maximum_violation_I_3}
@@
     To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
-$V_F \defined \min_{P}\bc{I\br{P}}/I\br{P_F}$.
-The first inequality in consideration is $I_1$; the non-symmetric Web inflation inequality presented in \cref{eq:web_inequality}.
+$V_F \defined \max_{P}\bc{I\br{P}/I\br{P_F}}$.
+The first inequality in consideration is $I\tsb{Web}$.
 At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
@@
 As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure.
-Consequently, it seems that $I_1$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.
+Consequently, it seems that $I\tsb{Web}$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.
 
@@
 Above it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
-Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to inequality \textit{saturation} instead of inequality \textit{violation} which is achievable by the Fritz distribution $\prob[\fritz]$.
+Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to inequality \textit{saturation} instead of inequality \textit{violation}.
 Instead, it was observed that only parameters close enough to the \textit{Fritz parameters} (i.e.
@@
 
-    The second inequality in consideration is the \textit{symmetric} inequality $I_3$ (\cref{eq:symmetic_web_inequality}).
-This inequality was able to achieve a greater relative violation than $I_1$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
+    The second inequality in consideration is the \textit{symmetric} inequality $I\tsb{SymmetricWeb}$.
+This inequality was able to achieve a greater relative violation than $I\tsb{Web}$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
 Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution.
@@
 Since the inequality is symmetric with respect to the permutation of parties, one would naively expect that the maximum violating distribution be symmetric as well.
-If it were not, one could construct a distribution that violates $I_3$ more by symmetrizing $\prob[\fritz]$ by summing over all possible permutations and normalizing.
-The symmetrized Fritz distribution is plotted in \cref{fig:symmetrized_fritz}.
+If it were not, one could construct a distribution that violates $I\tsb{SymmetricWeb}$ further by symmetrizing $\prob[\fritz]$ (\cref{fig:symmetrized_fritz}) by normalizing over all possible permutations of $A,B,C$.
 This distribution is also non-classical with relative violation $V_F = 3$.
@@
 
-    Finally for both $I_0$ and $I_2$, the maximum relative violation happens to be $V_F = 1$ (up to numerical precision).
-This means that the Fritz distribution either represents a local minimum of the parameter space or is in fact \textit{the} maximally violating distribution.
-Without further investigations, it remains unclear if this behavior is related to the universality of the Fritz distribution or if its an artifact of the methods used to derive $I_0$ and $I_2$.
+    Finally, the maximum relative violation of $I\tsb{WagonWheel}$ was found to be $V_F = 1$ (up to numerical precision), indicating that the Fritz distribution either represents a local minimum of the parameter space or is in fact \textit{the} maximally violating distribution.
+Without further investigations, it remains unclear if this behavior is related to the universality of the Fritz distribution or if its an artifact of the methods used to derive $I\tsb{WagonWheel}$.
 

### 2017-06-12 documents/TriangleScenarioArXiv/ts.tex
pre-injectable -> ai-expressible

@@
 
-    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{pre-injectable sets} of $\graph'$.
-A set $N' \subseteq \nodes'$ is a pre-injectable set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
-
-    A pre-injectable set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions~\cite{Pearl_2009}\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}.
+    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{ai-expressible sets} of $\graph'$.
+A set $N' \subseteq \nodes'$ is a ai-expressible set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
+
+    A ai-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions~\cite{Pearl_2009}\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}.
 This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.},
     \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
-    Application of the inflation lemma to linear inequalities constraining pre-injectable distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
-Throughout the body of this work, we let $\PreInj[\graph]{\graph'}$ denote the set of all pre-injectable sets.
-To derive inequalities for the inflated causal structure $\graph'$, the pre-injectable sets define a marginal scenario $\mscenario$\footnote{Analogously for a marginal scenario $\mscenario$, the pre-injectable sets $\PreInj[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
-Therefore, in practice, it is completely sufficient to focus on the maximal pre-injectable sets.} that are used to derive inequalities using methods discussed in \cref{sec:marginal_satisfiability}.
+    Application of the inflation lemma to linear inequalities constraining ai-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
+Throughout the body of this work, we let $\AI[\graph]{\graph'}$ denote the set of all ai-expressible sets.
+To derive inequalities for the inflated causal structure $\graph'$, the ai-expressible sets define a marginal scenario $\mscenario$\footnote{Analogously for a marginal scenario $\mscenario$, the ai-expressible sets $\AI[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
+Therefore, in practice, it is completely sufficient to focus on the maximal ai-expressible sets.} that are used to derive inequalities using methods discussed in \cref{sec:marginal_satisfiability}.
 
@@
     \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}.
-Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal pre-injectable sets of $\graph'$, i.e.
-$\mscenario = \PreInj[\graph]{\graph'}$.
+Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal ai-expressible sets of $\graph'$, i.e.
+$\mscenario = \AI[\graph]{\graph'}$.
 This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript.
-Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their pre-injectable sets.
-An efficient algorithm for computing the injectable and pre-injectable sets of an inflation can be found in~\cite{Inflation}.
+Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their ai-expressible sets.
+An efficient algorithm for computing the injectable and ai-expressible sets of an inflation can be found in~\cite{Inflation}.
     \begin{center}
@@
 The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
-The maximal pre-injectable sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
-These maximal pre-injectable sets define the following marginal scenario where the joint variables $\jointvar$ are simply the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
-    \[ \mscenario = \PreInj[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
+The maximal ai-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
+These maximal ai-expressible sets define the following marginal scenario where the joint variables $\jointvar$ are simply the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
+    \[ \mscenario = \AI[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
     Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
@@
         \begin{gathered}
-            \textbf{Maximal Pre-injectable Sets} \\
+            \textbf{Maximal AI-Expressible Sets} \\
             \bc{A_2, B_1, C_3, C_1} \\
@@
     The remaining inequalities in \cref{sec:found_inequalities} were derived using the Web inflation of \cref{fig:the_web_inflation}.
-The maximal pre-injectable sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_web}.
+The maximal ai-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_web}.
     \begin{equation*}
@@
         \begin{gathered}
-            \textbf{Maximal Pre-injectable Sets} \\
+            \textbf{Maximal AI-Expressible Sets} \\
             \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
@@
     \end{equation*}
-    Analogously to the Wagon-Wheel inflation, these pre-injectable sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.
+    Analogously to the Wagon-Wheel inflation, these ai-expressible sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.
 
@@
     For the Triangle structure in particular, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
-For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\PreInj[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
+For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\AI[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
     \begin{equation*}
@@
     It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
-Moreover they stabilize the pre-injectable sets of \cref{eq:pre_injectable_triangle_structure_web}.
+Moreover they stabilize the ai-expressible sets of \cref{eq:pre_injectable_triangle_structure_web}.
 Importantly,
-    \[ \gp\br{\PreInj[\graph]{\graph'}} \sim \Perm{A,B,C} \]
+    \[ \gp\br{\AI[\graph]{\graph'}} \sim \Perm{A,B,C} \]
     To see this, $\varphi_1$ and $\varphi_4$ become the identity element in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.

### 2017-06-12 documents/TriangleScenarioArXiv/ts.tex
Removed the cut inflation

@@
     \begin{figure}
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_cut}}
-    \caption{The Cut inflation.}\label{fig:cut_inflation}
-    \end{subfigure}
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
+    \begin{subfigure}[b]{.30\linewidth}
+    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
     \caption{The Spiral inflation.}\label{fig:spiral_inflation}
     \end{subfigure}
-
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
+    \begin{subfigure}[b]{.30\linewidth}
+    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
     \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
     \end{subfigure}
-    \begin{subfigure}[b]{.45\linewidth}
-    \scalebox{1}{\input{../../figures/causal_structures/inflated_triangle_structure}}
+    \begin{subfigure}[b]{.30\linewidth}
+    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure}}
     \caption{The Web Inflation.}\label{fig:the_web_inflation}

### 2017-06-13 documents/TriangleScenarioArXiv/ts.tex
Added more discussion of preliminary research

@@
     Additionally, \citet{Fritz_2012} demonstrated that the Triangle structure is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell structure in that measurement setting variables are absent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we discuss in detail in \cref{sec:fritz_distribution}.
-Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classical in the Triangle structure.
+Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classicality in the Triangle structure~\cite{Fritz_2012}.
     % \comment[E]{Revisions processed up to here thusfar.}
@@
     Finally, \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}) --- a novel tool for solving causal inference problems.
-Using the Inflation Technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum non-accessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints.
+Using the Inflation Technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum-inaccessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints.
 Consequently, as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure than all others.
@@
 Most recently, \citet{Inflation} derive a family of polynomial, $2$-outcome, causal compatibility inequalities; $37$ non-trivial representatives are printed in~\cite{Inflation}.
-
-    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}.
-Unfortunately, none of these inequalities could be violated.
-These early results suggest, although do not prove, that quantum non-classical does not exist in the Triangle structure for \textit{two-outcome} measurements.
-Therefore, it is conjectured that all quantum non-classical distributions in the Triangle structure must utilize more than $2$ outcomes in at least one variable.
-Moreover we take these observations as motivation to explore incompatibility in Triangle structure for a larger cardinalities.
-
-    In conclusion, the Triangle structure is a causal structure whose non-classicality remains an open problem.
-The Triangle structure is a desirable case study because there is a quantum distribution that is known to be incompatible, but no previously known inequalities were able to witness its incompatibility.
-This failure represents a gap in our understanding of quantum non-classicality, where recent developments (namely the Inflation Technique) have made partial progress.
-This document expands on our understanding of non-classicality in the Triangle structure and also our understanding on how to find inequalities using the Inflation Technique for interesting causal structures in general.
+\Cref{sec:preliminary_research} outlines our initial attempts to utilize these inequalities to search for incompatible distributions that are also quantum-accessible.
+The subsequent failure of these approaches will motivate the remainder of this work.
+
+    In conclusion, the Triangle structure is a desirable case study because there exists a quantum distribution that is known to be incompatible, but no previously known inequalities were able to witness its incompatibility.
+This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.
 
@@
 
-    Understandably, Fritz's Problem is stated ambiguously as it is not yet entirely clear how to distinguish between non-classical distributions on differing causal structures.
+    Understandably, Fritz's Problem is stated ambiguously as it is not yet entirely clear how to rigorously compare the qualitative features of differing non-classical distributions on differing causal structures (such as the Bell and Triangle structures).
 The remainder of this paper focuses on our advancement toward solving Fritz's Problem.
-\Cref{sec:conclusions} proposes three refinements of Fritz's Problem which are to be labeled \ref{r:1},\ref{r:2} and \ref{r:3} respectively.
-Specifically, \ref{r:1} embodies the degree in which the results of \cref{sec:found_inequalities} solve Fritz's problem while \ref{r:2} and \ref{r:3} characterize interpretations of Fritz's Problem that remain partially solved.
-
-    \section{Triangle structure Inequalities}
+\Cref{sec:conclusions} concludes by outlining our resolution to Fritz's problem and mentioning areas for future research.
+
+    \section{Preliminary Research}
+    \label{sec:preliminary_research}
+
+    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}.
+Unfortunately, none of these inequalities could be violated.
+These early results suggest, although do not prove, that quantum non-classicality does not exist in the Triangle structure for \textit{two-outcome} measurements.
+Therefore, it is conjectured that all quantum non-classical distributions in the Triangle structure must utilize more than two outcomes in at least one variable.
+Pursuant to this conjecture, this work expands the search for quantum-accessible incompatibility in Triangle structure by increasing the cardinality of outcomes.
+
+    Moreover, the existence of the Fritz distribution (\cref{sec:fritz_distribution}) directly demonstrates that quantum-accessible incompatibility exists in the Triangle structure and indirectly suggests the existence of causal compatibility inequalities capable of witnessing the non-classicality of the Fritz distribution.
+The Inflation Technique has been shown to completely solve the classical causal inference problem~\cite{Navascues_2017} --- indicating that these undiscovered inequalities can be generated using sufficiently complex inflations.
+The 37 inequalities in~\cite{Inflation} were derived using the Spiral inflation (\cref{fig:spiral_inflation}) and their failure motivated us to consider larger inflations such as those in \cref{fig:wagon_wheel_inflation,fig:the_web_inflation}.
+
+    These incipient insights were sufficient for focusing the search for new inequalities to $4$-outcomes which are violated by the Fritz distribution.
+\Cref{sec:found_inequalities} expands on our understanding of non-classicality in the Triangle structure by reporting the discovery of these inequalities which admit quantum-accessible violations.
+As a by-product, this research supports illuminates the advantage in using the Inflation Technique to find inequalities for interesting causal structures in general.
+
+    \section{Triangle Structure Inequalities}
     \label{sec:found_inequalities}
@@
 As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}.
-Therefore we conclude that the space of quantum accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.
+Therefore we conclude that the space of quantum-accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.
 
@@
 
-    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum accessible distributions.
+    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions.
 This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) when applied to the Fritz distribution.

### 2017-06-13 documents/TriangleScenarioArXiv/ts.tex
Fixed up conclusion, removed refinement 3

@@
 \begin{document}
-    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure}
+    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
     \author{Thomas C. Fraser}
@@
     In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions.
-This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) when applied to the Fritz distribution.
-In the context of Fritz's Problem, our result corresponds to a resolution to the following refinement of Fritz's original Problem.
+This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) applied to the Fritz distribution.
+In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
     \begin{enumerate}[label=\textbf{R.\arabic*}]
@@
 In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation Technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure.
-Consequently, this work strongly indicates that the Inflation Technique has the potential to solve a assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
+Consequently, this work strongly indicates that the Inflation Technique has the potential to solve an assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
 Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations.
@@
 
-    In consideration of our resolution to \ref{r:1}, we additionally propose two more refinements to Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
+    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}.
+When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state.
+In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states.
+As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.} In consideration of our resolution to \ref{r:1}, we propose an alternative reinterpretation of Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
+
     \begin{enumerate}[label=\textbf{R.\arabic*}]
@@
         \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
-        \item \label{r:3} Find incompatible quantum distributions on the Triangle structure that satisfy all Bell structure inequalities under Fritz-type embeddings.
     \end{enumerate}
 
-    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}.
-When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state.
-In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states.
-As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.} The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
+    The question, as proposed by \ref{r:2}, is: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
 At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure.
@@
 In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations.
-These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and should be a focus for future research.
-
-    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_structure}) into the Triangle structure via the re-imagined version of the Triangle structure (\cref{fig:triangle_structure_with_fritz_bell_embedded}).
-Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations.
-Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure.
-Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility.
-Ultimately, it remains unclear whether or not a positive resolution to \ref{r:3} is even feasible.
+These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and is a recommended focus for future research.
+
+    Using the Inflation technique, it became possible to provide a stronger proof of non-classicality than proposed by Fritz~\cite{Fritz_2012}.
+In particular, noisy variants of the Fritz distribution are provably non-classical (\cref{sec:noise}) and there exist quantum distributions quantitatively distinct from the Fritz distribution which admit greater numerical violations (\cref{sec:optimizations}).
+Despite these advancements, the distributions obtained closely resemble the Fritz distribution indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure.
+Currently, it remains speculative about how to recognize whether or not a given distribution for the Triangle structure exhibits non-classical correlations that maintain distinct qualitatively advantages from a resource perspective.
+One possibility is to extend \cref{r:2} to include the necessity of entanglement measurements.
+Ultimately, given any said classifier, it remains unclear whether or not such distributions even exist.
 

### 2017-06-13 documents/TriangleScenarioArXiv/ts.tex
Changed R.1, R.2 to FP.A, FP.B respectively
Made significant changes to A2

@@
 In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
-    \begin{enumerate}[label=\textbf{R.\arabic*}]
+    \begin{enumerate}[label=\textbf{FP.\Alph*}]
         \setcounter{enumi}{0}
@@
 
-    \begin{enumerate}[label=\textbf{R.\arabic*}]
+    \begin{enumerate}[label=\textbf{FP.\Alph*}]
         \setcounter{enumi}{1}
@@
     \label{sec:inflation_technique_main_summary}
-    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$.
-As a preliminary summary, the Inflation Technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
-As a example, four inflations of the Triangle structure are depicted in \cref{fig:inflations}.
+    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if an observable probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$.
+As a precursor, the Inflation Technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
+As a example, a few inflations of the Triangle structure are depicted in \cref{fig:inflations}.
 Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}.
@@
     \begin{definition}
+        \label{def:inflation}
         An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
@@
     \end{definition}
-    Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is equivalent to its counterpart in $\graph$ up to copy-index.
-The motivation behind this definition is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible distribution $\prob[N]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
-To do this, first notice that for every distribution $\prob[N]$ compatible with $\graph$, there must exist a set of causal parameters $\{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes\}$ for $\graph$ such that $\prob[N] = \prod_{n \in N} \prob[n\mid \Pa[\graph]{n}]$.
-Since the inflation criteria (\cref{eq:inflation_defn}) requires that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$ one can create a set of \term{inflated causal parameters} by matching causal parameters according to respective copy-indices.
-    \[ \forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}] \eq \label{eq:inflated_causal_parameters} \]
-    Which in turn uniquely defines a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course, there exists compatible joint distributions on $\nodes'$ that can not be constructed in this manner.
-The claim is that all joint distributions that are constructed in this way are compatible.}.
-    \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \eq \label{eq:unique_causal_parameters_inflated}\]
-    % \cref{eq:unique_causal_parameters,eq:inflated_causal_parameters,eq:unique_causal_parameters_inflated}
-    In essence, a compatible joint distribution over $\nodes$ can be \textit{inflated} to induce compatible joint distributions over $\nodes'$.
-Before generalizing this idea, a careful observation needs to be made.
-For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$, where $N \subset \nodes$, induces a compatible marginal distribution $\prob[N']$ over $N'$.
-In fact, $N'$ must contain no duplicate nodes up to copy index and thus $\prob[N] = \prob[N']$.
-These subsets of nodes are so essential to the Inflation Technique they are assigned a special name: sets $N' \subseteq \nodes'$ as called the \term{injectable sets} of $\graph'$ and $N \subset \nodes$ the \term{images of the injectable sets} of $\graph$.
-    \begin{align*}
-        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
-        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'}
-    \end{align*}
-    Injectable sets are incredibly useful for causal compatibility because they permit one to inflate compatibility over a particular subset of \textit{marginal models}.
-A marginal model is compatible with a given causal structure $\graph$ if it admits a joint distribution (see \cref{sec:marginal_satisfiability}) that is compatible with $\graph$.
-
-    \begin{lemma}
-        \label[lemma]{lem:inflation}
-        \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-    \end{lemma}
-    Diagrammatically, \cref{lem:inflation} can be visualized as follows:
-
-    \begin{center}
-        \begin{tikzpicture}
-            \pgfmathsetmacro{\vs}{2.2};
-            \pgfmathsetmacro{\hs}{5.2};
-            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
-            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
-            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
-            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
-            \draw[very thick, ->] (pn) -- (cp);
-            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
-            \draw[very thick, ->] (cp_) -- (pn_);
-        \end{tikzpicture}
-    \end{center}
-
-    The inflation lemma is the most important result of the causal Inflation Technique.
-The contrapositive version of \cref{lem:inflation} is a powerful tool for deriving causal compatibility constraints.
-Any causal compatibility constraint, such as a causal compatibility inequality, that constrains injectable marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ can be \textit{deflated} into a valid compatibility constraint on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure by dropping all references to the copy-indices.
-Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
-Therefore, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
-
-    Heretofore, the Inflation Technique as stated by \cref{lem:inflation} does not facilitate the derivation of any non-trivial inequalities.
-The Inflation lemma simply casts causal inference problems on $\graph$ to causal inference problems on $\graph'$.
-Fortunately, an inflated causal structure $\graph'$ possesses its own conditional independence relations which can be exploited to turn linear inequalities on $\graph'$ into polynomial inequalities on $\graph$.
-After obtaining an inequality for $\graph'$, each of its term is generically of the form $\prob[N']$ where $N'$ may not be injectable $N' \not \in \Inj[\graph]{\graph'}$.
-At this point, the Inflation lemma is not applicable because it requires probabilistic constraints to consist entirely of distributions $\prob[N']$ where $N'$ is injectable.
-If for example, $N' \not \in \Inj[\graph]{\graph'}$ could be partitioned into two injectable subsets $N_1' \in \Inj[\graph]{\graph'}$ and $N_2' \in \Inj[\graph]{\graph'}$ that where \term{ancestrally independent} in $\graph'$,\footnote{Ancestral independence is equivalent to d-separation conditioned on the empty set $\emptyset$~\cite{Pearl_2009}.}
-    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
-    Then the compatible marginal context $\prob[N']$ must be probabilistically separable $\prob[N'] = \prob[N_1']\prob[N_2']$ due to \cref{eq:compatibility_as_factorization}.
-Since $N_1'$ and $N_2'$ are both injectable, the inflation lemma now applies and the original inequality can be deflated.
-
-    \begin{center}
-        \begin{tikzpicture}[scale=0.8]
-            \pgfmathsetmacro{\hs}{1.4};
-            \pgfmathsetmacro{\vs}{0.6};
-            \pgfmathsetmacro{\cross}{0.2};
-            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
-            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
-            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
-            \draw (2*\hs, 4*\vs + 0.7*\vs) node[]{$N_1' \cup N_2' = N$};
-            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
-            \draw (0, 0) node[](b){??};
-            \draw[thick, ] (a) -- (ab);
-            \draw[thick, ] (c) -- (cd);
-            \draw[thick, ] (a) -- (ac);
-            \draw[thick, ->] (ac) -- (c);
-            \draw[thick, ->] (ab) -- (b);
-            \draw[thick, ->] (cd) -- (d);
-            \draw[very thick, red]
-            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
-            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
-            ;
-        \end{tikzpicture}
-    \end{center}
-
-    Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{ai-expressible sets} of $\graph'$.
-A set $N' \subseteq \nodes'$ is a ai-expressible set if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
-
-    A ai-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions~\cite{Pearl_2009}\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}.
-This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.},
-    \[ \prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i] \]
-    Application of the inflation lemma to linear inequalities constraining ai-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
-Throughout the body of this work, we let $\AI[\graph]{\graph'}$ denote the set of all ai-expressible sets.
-To derive inequalities for the inflated causal structure $\graph'$, the ai-expressible sets define a marginal scenario $\mscenario$\footnote{Analogously for a marginal scenario $\mscenario$, the ai-expressible sets $\AI[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
-Therefore, in practice, it is completely sufficient to focus on the maximal ai-expressible sets.} that are used to derive inequalities using methods discussed in \cref{sec:marginal_satisfiability}.
-
-    \subsection{Exemplary Inflations of The Triangle structure}
-    \label{sec:exemplary_inflations_of_the_triangle structure}
-
-    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}.
-Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal ai-expressible sets of $\graph'$, i.e.
-$\mscenario = \AI[\graph]{\graph'}$.
-This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript.
-Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their ai-expressible sets.
-An efficient algorithm for computing the injectable and ai-expressible sets of an inflation can be found in~\cite{Inflation}.
     \begin{center}
@@
     \end{center}
+    \begin{center}
+    \begin{figure}
+    \begin{subfigure}[b]{.23\linewidth}
+    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
+    \caption{$\AnSub[\graph]{A}$}\label{fig:spiral_inflation_iminj1}
+    \end{subfigure}
+    \begin{subfigure}[b]{.23\linewidth}
+    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
+    \caption{$\AnSub[\graph']{A_1}$}\label{fig:spiral_inflation_inj1}
+    \end{subfigure}
+    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
+    \begin{subfigure}[b]{.23\linewidth}
+    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_2}}
+    \caption{$\AnSub[\graph]{A,C}$}\label{fig:spiral_inflation_iminj2}
+    \end{subfigure}
+    \begin{subfigure}[b]{.23\linewidth}
+    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
+    \caption{$\AnSub[\graph']{A_2, C_1}$}\label{fig:spiral_inflation_inj2}
+    \end{subfigure}
+    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$).}
+    \label{fig:injectablesets}
+    \end{figure}
+    \end{center}
+    Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is homomorphic to its counterpart in $\graph$ where the homomorphism is the removal of the copy-index.
+For example, the ancestral subgraph of $A$ in the Triangle structure (denoted $\AnSub[\graph]{A}$) is highlighted in \cref{fig:spiral_inflation_iminj1} and is clearly homomorphic to the ancestral subgraph of $A_1$ in the Spiral inflation (denoted $\AnSub[\graph]{A_1}$) depicted in \cref{fig:spiral_inflation_inj1}.
+Since this ancestral homomorphism exists for each node $n'$ of the Spiral inflation (\cref{fig:spiral_inflation}), it qualifies as a valid inflation of the Triangle structure (\cref{fig:triangle_structure}).
+
+    \begin{definition}
+        Given a causal structure $\graph$ and an inflation $\graph'$ of $\graph$, define the \term{injectable sets} in $\graph'$ and the \term{images of the injectable sets} in $\graph$, (respectively denoted $\Inj[\graph]{\graph'}$ and $\ImInj[\graph]{\graph'}$), as follows:
+        \begin{align*}
+            \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}} \\
+            \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}
+        \end{align*}
+    \end{definition}
+
+    As defined, the injectable sets of an inflation are also simple to comprehend.
+As an example, the set $\bc{A_2, C_1}$ of the Spiral inflation ($\graph'$) (\cref{fig:spiral_inflation}) is an injectable set of $\graph'$ because its ancestral subgraph $\AnSub[\graph']{A_2, C_1}$ (highlighted in \cref{fig:spiral_inflation_inj2}) is homomorphic (via copy-index removal) to the ancestral subgraph of $\bc{A, C}$ in the Triangle structure $(\graph)$ (\cref{fig:spiral_inflation_iminj2}).
+The injectable sets of an inflation are of \textit{principle importance} to the inflation technique.
+The Inflation Technique begins with joint distribution $\prob[\nodes_O]$ defined over the observable nodes of $\graph$ and the a priori assumption that it is compatible with $\graph$ as defined in \cref{sec:causal_compatibility}.
+For each injectable set $N' \subseteq \Inj[\graph]{\graph'}$ and image $N \subseteq \ImInj[\graph]{\graph'}$ consisting entirely of observable nodes ($N \subseteq \nodes_O$), there is a pair $\prob[N], \prob[N']$ of marginal distributions induced by $\prob[\nodes_O]$ where $\prob[N']$ assigns the same probability to all events of $\prob[N]$ whenever the events are equivalent under the removal of copy-indices.
+These pairs of distributions can be raveled to form a pair of marginal models defined over the injectable sets $\prob^{\Inj[\graph]{\graph'}} = \bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ and their images $\prob^{\ImInj[\graph]{\graph'}} = \bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$.
+
+    \begin{lemma}
+        \label[lemma]{lem:inflation}
+        \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\prob^{\ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\prob^{\Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+    \end{lemma}
+
+    \begin{proof}
+        Given that $\prob^{\ImInj[\graph]{\graph'}}$ is compatible with $\graph$, it admits a joint distribution $\prob[\nodes]$ that can be factorized into its causal parameters $\prob[\nodes] = \prod_{n \in \nodes} \prob[n\mid \Pa[\graph]{n}]$.
+Given \cref{eq:inflation_defn}, one can create a set of \textit{inflated} causal parameters by matching causal parameters according to respective copy-indices: $\forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}]$.
+This uniquely induces a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course, there exists compatible joint distributions on $\nodes'$ that can not be constructed in this manner.
+The claim is that all joint distributions that are constructed in this way are compatible.}: $\prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}]$.
+The proof is completed by demonstrating that the marginals of $\prob[\nodes']$ are members of the marginal model $\prob^{\Inj[\graph]{\graph'}}$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+Given $N' \in \Inj[\graph]{\graph'}$ and $N \sim N'$:
+        \[ \sum_{\nodes' \setminus N'} \prob[\nodes'] = \sum_{\nodes' \setminus N'} \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] = \prod_{n' \in N'} \prob[n'\mid \Pa[\graph]{n'}] = \prod_{n \in N} \prob[n\mid \Pa[\graph]{n}] = \prob[N] = \prob[N']  \]
+    \end{proof}
+
+    % The motivation behind \cref{def:inflation} is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible distribution $\prob[N]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
+To do this, first notice that for every distribution $\prob[N]$ compatible with $\graph$, there must exist a set of causal parameters $\{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes\}$ for $\graph$ such that $\prob[N] = \prod_{n \in N} \prob[n\mid \Pa[\graph]{n}]$.
+Since the inflation criteria (\cref{eq:inflation_defn}) requires that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$.
+    % \[ ss \eq \label{eq:inflated_causal_parameters} \]
+    % \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \eq \label{eq:unique_causal_parameters_inflated}\]
+
+    % % \cref{eq:unique_causal_parameters,eq:inflated_causal_parameters,eq:unique_causal_parameters_inflated}
+    % In essence, a compatible joint distribution over $\nodes$ can be \textit{inflated} to induce compatible joint distributions over $\nodes'$.
+Before generalizing this idea, a careful observation needs to be made.
+For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$, where $N \subset \nodes$, induces a compatible marginal distribution $\prob[N']$ over $N'$.
+In fact, $N'$ must contain no duplicate nodes up to copy-index and thus $\prob[N] = \prob[N']$.
+These subsets of nodes are so essential to the Inflation Technique they are assigned a special name:
+
+    % % Injectable sets are incredibly useful for causal compatibility because they permit one to inflate compatibility over a particular subset of \textit{marginal models}.
+A marginal model is compatible with a given causal structure $\graph$ if it admits a joint distribution (see \cref{sec:marginal_satisfiability}) that is compatible with $\graph$.
+
+    % % Diagrammatically, \cref{lem:inflation} can be visualized as follows:
+
+    % % \begin{center}
+    % %     \begin{tikzpicture}
+    % %         \pgfmathsetmacro{\vs}{2.2};
+    % %         \pgfmathsetmacro{\hs}{5.2};
+    % %         \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
+    % %         \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
+    % %         \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
+    % %         \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
+    % %         \draw[very thick, ->] (pn) -- (cp);
+    % %         \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
+    % %         \draw[very thick, ->] (cp_) -- (pn_);
+    % %     \end{tikzpicture}
+    % % \end{center}
+
+    % The inflation lemma is the most important result of the causal Inflation Technique.
+The contrapositive version of \cref{lem:inflation} is a powerful tool for deriving causal compatibility constraints.
+Any causal compatibility constraint, such as a causal compatibility inequality, that constrains injectable marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ can be \textit{deflated} into a valid compatibility constraint on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure by dropping all references to the copy-indices.
+Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
+Therefore, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
+
+    The contrapositive of the Inflation Lemma (\cref{lem:inflation}) casts the compatibility problem for $\prob^{\ImInj[\graph]{\graph'}}$ (which exhibits equivalent compatibility as $\prob[\nodes_O]$) into a compatibility problem for $\prob^{\Inj[\graph]{\graph'}}$ of any non-trivial inequalities.
+If $\prob^{\Inj[\graph]{\graph'}}$ is found to be incompatible with $\graph'$, then $\prob[\nodes_O]$ is subsequently incompatible with $\graph$.
+Fortunately, the inflated causal structure $\graph'$ possesses its own \textit{d-separation relations} which enforces conditional independence equality constraints on $\prob^{\Inj[\graph]{\graph'}}$.
+A useful subset of d-separation relations are those corresponding to unconditional d-separations, known as \term{ancestrally independent} sets~\cite{Pearl_2009}.
+Two sets $N_1', N_2'$ are ancestrally independent ($N_1' \ancestralindep N_2'$) if they have distinct ancestry in $\graph'$.
+    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
+    Ancestral independence implies an unconditional probabilistic independence --- if $N_1' \ancestralindep N_2'$ then $\prob[N_1' \cup N_2'] = \prob[N_1']\prob[N_2']$.
+If $N_1', N_2' \in \Inj[\graph]{\graph'}$, then the associated probabilistic constraint is an applicable constraint for $\prob^{\Inj[\graph]{\graph'}}$.
+This notion generalizes to more than two ancestrally independent sets.
+A set $N' \subseteq \nodes'$ is an \term{ai-expressible set} if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
+The analogous probabilistic constraint is: $\prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i]$~\cite{Pearl_2009}.\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}.
+This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.} Throughout this work, we let $\AI[\graph]{\graph'}$ denote the set of all ai-expressible sets.\footnote{Analogously to a marginal scenario $\mscenario$, the ai-expressible sets $\AI[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
+Therefore, in practice, it is completely sufficient to focus on the \textit{maximal} ai-expressible sets.}
+
+    Unlike $\prob^{\ImInj[\graph]{\graph'}}$, which is non-contextual by construction, $\prob^{\Inj[\graph]{\graph'}}$ contains overlapping marginals meaning its contextuality remains unknown and must be determined using any of the techniques discussed in~\cref{sec:marginal_satisfiability}.
+More importantly, the Inflation Technique introduces new constraints relating to the ai-expressible sets.
+In practice, the equality constraints implied by $\AI[\graph]{\graph'}$ permits one to construct a marginal model defined over the ai-expressible sets $\AI[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$.
+In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (see \cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$.
+
+      % that are used to derive inequalities using methods discussed in \cref{sec:marginal_satisfiability}.
+
+    % \begin{center}
+    %     \begin{tikzpicture}[scale=0.8]
+    %         \pgfmathsetmacro{\hs}{1.4};
+    %         \pgfmathsetmacro{\vs}{0.6};
+    %         \pgfmathsetmacro{\cross}{0.2};
+    %         \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
+    %         \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
+    %         \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
+    %         \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
+    %         \draw (2*\hs, 4*\vs + 0.7*\vs) node[]{$N_1' \cup N_2' = N$};
+    %         \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
+    %         \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
+    %         \draw (0, 0) node[](b){??};
+    %         \draw[thick, ] (a) -- (ab);
+    %         \draw[thick, ] (c) -- (cd);
+    %         \draw[thick, ] (a) -- (ac);
+    %         \draw[thick, ->] (ac) -- (c);
+    %         \draw[thick, ->] (ab) -- (b);
+    %         \draw[thick, ->] (cd) -- (d);
+    %         \draw[very thick, red]
+    %         (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
+    %         (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
+    %         ;
+    %     \end{tikzpicture}
+    % \end{center}
+
+    % Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{ai-expressible sets} of $\graph'$.
+
+    % A ai-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions
+    % \[  \]
+    % Application of the inflation lemma to linear inequalities constraining ai-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
+
+    \subsection{Exemplary Inflations of The Triangle structure}
+    \label{sec:exemplary_inflations_of_the_triangle structure}
+
+    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}.
+Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal ai-expressible sets of $\graph'$, i.e.
+$\mscenario = \AI[\graph]{\graph'}$.
+This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript.
+Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their ai-expressible sets.
+An efficient algorithm for computing the injectable and ai-expressible sets of an inflation can be found in~\cite{Inflation}.
 

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Pushing ShareLatex to GitHub

@@
     \end{center}
-    Verbally, for each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is homomorphic to its counterpart in $\graph$ where the homomorphism is the removal of the copy-index.
+    For each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is homomorphic to its counterpart in $\graph$ where the homomorphism is the removal of the copy-index.
 For example, the ancestral subgraph of $A$ in the Triangle structure (denoted $\AnSub[\graph]{A}$) is highlighted in \cref{fig:spiral_inflation_iminj1} and is clearly homomorphic to the ancestral subgraph of $A_1$ in the Spiral inflation (denoted $\AnSub[\graph]{A_1}$) depicted in \cref{fig:spiral_inflation_inj1}.
@@
     \bibliographystyle{apsrev4-1}
-    % \nocite{apsrev41Control}
+    \nocite{apsrev41Control}
     \bibliography{references}

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Changed order of figures in figure 10
Fritz's problem is not stated ambiguously

@@
 
-    Understandably, Fritz's Problem is stated ambiguously as it is not yet entirely clear how to rigorously compare the qualitative features of differing non-classical distributions on differing causal structures (such as the Bell and Triangle structures).
+    Fritz's problem is concerned with how to find and recognize non-classical quantum distributions specifically for the Triangle structure.
+In \cite{Fritz_2012}, Fritz proves the Fritz distribution is non-classical by \textit{recycling} Bell's theorem.
+Being limited by the requirement of perfect correlations and the reliant on Bell's theorem, Fritz's methods are problematic if one hopes to find new quantum resources for the Triangle structure.
 The remainder of this paper focuses on our advancement toward solving Fritz's Problem.
-\Cref{sec:conclusions} concludes by outlining our resolution to Fritz's problem and mentioning areas for future research.
+\Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem.
+Afterwards, \Cref{sec:found_inequalities} reports the discovery of new causal compatibility inequalities wish are capable of proving the non-classicality of Fritz's distribution.
+Finally, \Cref{sec:conclusions} concludes by outlining our resolution to Fritz's problem and mentioning areas for future research.
 
@@
     \begin{subfigure}[b]{.23\linewidth}
+    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
+    \caption{$\AnSub[\graph']{A_1}$}\label{fig:spiral_inflation_inj1}
+    \end{subfigure}
+    \begin{subfigure}[b]{.23\linewidth}
     \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
@@
     \end{subfigure}
+    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
-    \caption{$\AnSub[\graph']{A_1}$}\label{fig:spiral_inflation_inj1}
+    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
+    \caption{$\AnSub[\graph']{A_2, C_1}$}\label{fig:spiral_inflation_inj2}
     \end{subfigure}
-    % \par\bigskip % For vertical spacing https://tex.stackexchange.com/questions/120700/vertical-spacing-using-subcaption-package
     \begin{subfigure}[b]{.23\linewidth}
@@
     \caption{$\AnSub[\graph]{A,C}$}\label{fig:spiral_inflation_iminj2}
-    \end{subfigure}
-    \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
-    \caption{$\AnSub[\graph']{A_2, C_1}$}\label{fig:spiral_inflation_inj2}
     \end{subfigure}

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Improvments to academic writing style (no more usage of simple, easy, trivial, very, etc.)

@@
 3]{Fritz_2012},~\cite[Fig.
+4]{Weilenmann_2016},~\cite[Fig.
 1]{Inflation}, $\ldots$).
@@
 The compatibility of a distribution $\prob[\nodes]$ with a causal structure $\graph$ pursuant to \Cref{eq:compatibility_as_factorization} is equivalent to the requirement that $\prob[\nodes]$ obeys all of the conditional independence constraints implied by the \textit{d-separation relations} between variables/nodes in $\graph$~\cite{Pearl_2009}.
-When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is trivially easy to verify whether or not $\prob[\nodes]$ is compatible with $\graph$ by simply computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}.
+When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is possible to completely determine whether or not $\prob[\nodes]$ is compatible with $\graph$ by computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}.
 
@@
 More powerful approaches find constraints for $\prob[\nodes]$ in the form of probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals which constraint the set of compatible probability distributions.
-We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of simply Bell inequalities for two reasons.
+We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons.
 Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure.
@@
     \[ \ba{\p A_r \p B_r} = \prob[\p A_r \p B_r][00] + \prob[\p A_r \p B_r][11] - \prob[\p A_r \p B_r][01] - \prob[\p A_r \p B_r][10] \]
-    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the Triangle structure by performing a simple relabeling: $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}} \mapsto \p{A}_r, \p{B}_r, \p A_l, \p B_l$.
+    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the Triangle structure by performing a the following relabeling: $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}} \mapsto \p{A}_r, \p{B}_r, \p A_l, \p B_l$.
 As an example, the famous CHSH inequality~\cite{CHSH_Original} (\cref{eq:CHSH_ineq_orig}) constrains the correlation between the right-bits of $A$ and $B$,
@@
 Unfortunately, none of these inequalities could be violated.
+Furthermore, none of these inequalities were violated by any 2-outcome coarse-graining of the Fritz distribution.
 These early results suggest, although do not prove, that quantum non-classicality does not exist in the Triangle structure for \textit{two-outcome} measurements.
@@
 
-    Moreover, the existence of the Fritz distribution (\cref{sec:fritz_distribution}) directly demonstrates that quantum-accessible incompatibility exists in the Triangle structure and indirectly suggests the existence of causal compatibility inequalities capable of witnessing the non-classicality of the Fritz distribution.
+    Moreover, the existence of the Fritz distribution (\cref{sec:fritz_distribution}) directly demonstrates that quantum-accessible incompatibility exists in the Triangle structure and indirectly proves the existence of causal compatibility inequalities capable of witnessing the non-classicality of the Fritz distribution.
 The Inflation Technique has been shown to completely solve the classical causal inference problem~\cite{Navascues_2017} --- indicating that these undiscovered inequalities can be generated using sufficiently complex inflations.
@@
 
-    These incipient insights were sufficient for focusing the search for new inequalities to $4$-outcomes which are violated by the Fritz distribution.
-\Cref{sec:found_inequalities} expands on our understanding of non-classicality in the Triangle structure by reporting the discovery of these inequalities which admit quantum-accessible violations.
-As a by-product, this research supports illuminates the advantage in using the Inflation Technique to find inequalities for interesting causal structures in general.
+    These incipient insights were sufficient for focusing the search for new inequalities sensitive enough to be violated by the Fritz distribution.
+\Cref{sec:found_inequalities} reports the discovery of these inequalities which expand on our understanding of non-classicality in the Triangle structure.
+As a by-product, this research illuminates the advantage in using the Inflation Technique to find inequalities for interesting causal structures in general.
 
@@
     \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it.
-To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:exemplary_inflations_of_the_triangle structure}.
+To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:exemplary_inflations_of_the_triangle_structure}.
 
@@
 For previously studied causal structures, such as the Bell structure, there exists a uncertainty toward which measure of non-classicality is best.
-The inequalities derived in this report are likely \textit{not} the best measures of non-classicality simply because they have be curated toward the Fritz distribution.
+The inequalities derived in this report are likely \textit{not} the best measures of non-classicality because they have be curated toward the Fritz distribution.
 Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure to be found that admit quantum violations.
@@
     In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality.
-As was mentioned in \cref{sec:fritz_distribution}, this embedding required a very idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$.
+As was mentioned in \cref{sec:fritz_distribution}, this embedding required an idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$.
 From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}.
@@
 
-    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$, which is trivially compatible with the Triangle structure.
+    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$\footnote{The completely noisy observation is compatible with the Triangle structure}.
 The objective of this section is to quantify how much statistical noise can be added to the Fritz distribution $\prob[\fritz]$ before the reported inequalities fail to witness incompatibility.
@@
 As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure.
-Consequently, it seems that $I\tsb{Web}$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.
+Consequently, it seems that $I\tsb{Web}$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution closely.
 
@@
 At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure.
-Unfortunately, this is simply not the case.
+Unfortunately, this is not the case.
 By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled.
@@
 For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable.
-This will become apparent in \cref{sec:exemplary_inflations_of_the_triangle structure} when the Inflation Technique is applied to the Triangle structure, producing marginal models that are very large.
+This will become apparent in \cref{sec:exemplary_inflations_of_the_triangle_structure} when the Inflation Technique is applied to the Triangle structure, producing considerably large marginal models.
 Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
@@
 
-    As defined, the injectable sets of an inflation are also simple to comprehend.
-As an example, the set $\bc{A_2, C_1}$ of the Spiral inflation ($\graph'$) (\cref{fig:spiral_inflation}) is an injectable set of $\graph'$ because its ancestral subgraph $\AnSub[\graph']{A_2, C_1}$ (highlighted in \cref{fig:spiral_inflation_inj2}) is homomorphic (via copy-index removal) to the ancestral subgraph of $\bc{A, C}$ in the Triangle structure $(\graph)$ (\cref{fig:spiral_inflation_iminj2}).
+    As an example of an injectable set, the set $\bc{A_2, C_1}$ of the Spiral inflation ($\graph'$) (\cref{fig:spiral_inflation}) is an injectable set of $\graph'$ because its ancestral subgraph $\AnSub[\graph']{A_2, C_1}$ (highlighted in \cref{fig:spiral_inflation_inj2}) is homomorphic (via copy-index removal) to the ancestral subgraph of $\bc{A, C}$ in the Triangle structure $(\graph)$ (\cref{fig:spiral_inflation_iminj2}).
 The injectable sets of an inflation are of \textit{principle importance} to the inflation technique.
@@
 Fortunately, the inflated causal structure $\graph'$ possesses its own \textit{d-separation relations} which enforces conditional independence equality constraints on $\prob^{\Inj[\graph]{\graph'}}$.
-A useful subset of d-separation relations are those corresponding to unconditional d-separations, known as \term{ancestrally independent} sets~\cite{Pearl_2009}.
-Two sets $N_1', N_2'$ are ancestrally independent ($N_1' \ancestralindep N_2'$) if they have distinct ancestry in $\graph'$.
+A useful subset of d-separation relations are those corresponding to unconditional d-separations, known as \term{ancestrally separated} sets~\cite{Pearl_2009}.
+Two sets $N_1', N_2'$ are ancestrally separated ($N_1' \ancestralindep N_2'$) if they have distinct ancestry in $\graph'$.
     \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
@@
 If $N_1', N_2' \in \Inj[\graph]{\graph'}$, then the associated probabilistic constraint is an applicable constraint for $\prob^{\Inj[\graph]{\graph'}}$.
-This notion generalizes to more than two ancestrally independent sets.
-A set $N' \subseteq \nodes'$ is an \term{ai-expressible set} if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
+This notion generalizes to more than two ancestrally separated sets.
+A set $N' \subseteq \nodes'$ is an \term{as-expressible set} if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally separated: $\forall i, j : N_i' \ancestralindep N_j'$.
 The analogous probabilistic constraint is: $\prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i]$~\cite{Pearl_2009}.\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}.
-This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.} Throughout this work, we let $\AI[\graph]{\graph'}$ denote the set of all ai-expressible sets.\footnote{Analogously to a marginal scenario $\mscenario$, the ai-expressible sets $\AI[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
-Therefore, in practice, it is completely sufficient to focus on the \textit{maximal} ai-expressible sets.}
+This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.} Throughout this work, we let $\AnSepExpr[\graph]{\graph'}$ denote the set of all as-expressible sets.\footnote{Analogously to a marginal scenario $\mscenario$, the as-expressible sets $\AnSepExpr[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
+Therefore, in practice, it is completely sufficient to focus on the \textit{maximal} as-expressible sets.}
 
     Unlike $\prob^{\ImInj[\graph]{\graph'}}$, which is non-contextual by construction, $\prob^{\Inj[\graph]{\graph'}}$ contains overlapping marginals meaning its contextuality remains unknown and must be determined using any of the techniques discussed in~\cref{sec:marginal_satisfiability}.
-More importantly, the Inflation Technique introduces new constraints relating to the ai-expressible sets.
-In practice, the equality constraints implied by $\AI[\graph]{\graph'}$ permits one to construct a marginal model defined over the ai-expressible sets $\AI[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$.
+More importantly, the Inflation Technique introduces new constraints relating to the as-expressible sets.
+In practice, the equality constraints implied by $\AnSepExpr[\graph]{\graph'}$ permits one to construct a marginal model defined over the as-expressible sets $\AnSepExpr[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$.
 In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (see \cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$.
@@
 
-    % Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{ai-expressible sets} of $\graph'$.
-
-    % A ai-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions
+    % Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{as-expressible sets} of $\graph'$.
+
+    % A as-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions
     % \[  \]
-    % Application of the inflation lemma to linear inequalities constraining ai-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
+    % Application of the inflation lemma to linear inequalities constraining as-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
 
     \subsection{Exemplary Inflations of The Triangle structure}
-    \label{sec:exemplary_inflations_of_the_triangle structure}
+    \label{sec:exemplary_inflations_of_the_triangle_structure}
 
     \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}.
-Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal ai-expressible sets of $\graph'$, i.e.
-$\mscenario = \AI[\graph]{\graph'}$.
+Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal as-expressible sets of $\graph'$, i.e.
+$\mscenario = \AnSepExpr[\graph]{\graph'}$.
 This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript.
-Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their ai-expressible sets.
-An efficient algorithm for computing the injectable and ai-expressible sets of an inflation can be found in~\cite{Inflation}.
+Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their as-expressible sets.
+An efficient algorithm for computing the injectable and as-expressible sets of an inflation can be found in~\cite{Inflation}.
 
@@
 The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
-The maximal ai-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
-These maximal ai-expressible sets define the following marginal scenario where the joint variables $\jointvar$ are simply the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
-    \[ \mscenario = \AI[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
+The maximal as-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
+These maximal as-expressible sets define a marginal scenario where the joint variables $\jointvar$ are the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
+    \[ \mscenario = \AnSepExpr[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
     Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
@@
         \begin{gathered}
-            \textbf{Maximal AI-Expressible Sets} \\
+            \textbf{Maximal AS-Expressible Sets} \\
             \bc{A_2, B_1, C_3, C_1} \\
@@
         \begin{gathered}
-            \textbf{Ancestral Independences} \\
+            \textbf{Ancestral Separations} \\
             \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
@@
     \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
-    Which can be factored into the ancestrally independent injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
+    Which can be factored into the ancestrally separated injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
     \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
@@
     The remaining inequalities in \cref{sec:found_inequalities} were derived using the Web inflation of \cref{fig:the_web_inflation}.
-The maximal ai-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_web}.
+The maximal as-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_web}.
     \begin{equation*}
@@
         \begin{gathered}
-            \textbf{Maximal AI-Expressible Sets} \\
+            \textbf{Maximal AS-Expressible Sets} \\
             \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
@@
         \begin{gathered}
-            \textbf{Ancestral Independences} \\
+            \textbf{Ancestral Separations} \\
             \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
@@
     \end{equation*}
-    Analogously to the Wagon-Wheel inflation, these ai-expressible sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.
+    Analogously to the Wagon-Wheel inflation, these as-expressible sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.
 
@@
     The \term{variable permutation group} $\gp\br{\mscenario}$ for a marginal scenario $\mscenario$ is the joint permutation subgroup that stabilizes the marginal scenario, $\Phi\br{\mscenario} \defined \bc{\varphi \in \Perm{\jointvar} \mid \forall V \in \mscenario : \varphi\bs{V} \in \mscenario}$.
-    Obtaining the variable permutation group $\gp\br{\mscenario}$ is a simple application of a group stabilizer algorithm.
+    In general, the variable permutation group $\gp\br{\mscenario}$ can be obtained using group stabilizer algorithms.
 After obtaining $\gp\br{\mscenario}$, one can take known compatibility inequalities $I_{\mscenario}$ can create a whole family of inequalities $\bc{\varphi\bs{I_{\mscenario}} \mid \varphi \in \gp\br{\mscenario}}$ that are valid for the same marginal scenario $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}} = \varphi\bs{I}_{\mscenario}$.
 
-    Although very useful for reducing computational complexity~\cite{Bancal_2010}, we divert our attention to finding \textit{symmetric} inequalities, i.e.
+    Although useful for reducing computational complexity~\cite{Bancal_2010}, we divert our attention to finding \textit{symmetric} inequalities, i.e.
 those where $\forall \varphi \in \gp\br{\mscenario} :  \varphi\bs{I_{\mscenario}} = I_{\mscenario}$.
@@
 
-    For the Triangle structure in particular, the variable permutation group is simply the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
-For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\AI[\graph]{\graph'}}$ which is an order $48$ group with the following $4$ generators:
+    For the Triangle structure in particular, the variable permutation group is the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
+For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\AnSepExpr[\graph]{\graph'}}$ --- an order $48$ group with the following $4$ generators:
     \begin{equation*}
@@
     %  (0, 1, 2, 3, 5, 4, 7, 6, 10, 11, 8, 9))
-    It is easy to verify that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
-Moreover they stabilize the ai-expressible sets of \cref{eq:pre_injectable_triangle_structure_web}.
+    Notice that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
+Moreover they stabilize the as-expressible sets of \cref{eq:pre_injectable_triangle_structure_web}.
 Importantly,
-    \[ \gp\br{\AI[\graph]{\graph'}} \sim \Perm{A,B,C} \]
+    \[ \gp\br{\AnSepExpr[\graph]{\graph'}} \sim \Perm{A,B,C} \]
     To see this, $\varphi_1$ and $\varphi_4$ become the identity element in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Removed the word Understandably

@@
 Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$~\cite{Fritz_2012}.
-Understandably there are numerous ways that this can be accomplished, albeit we will focus on elucidating an exemplary method.
+There are numerous ways this can be accomplished, albeit we will focus on elucidating an exemplary method.
 
@@
     Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
-This marginal scenario $\mscenario$ then defines an incidence matrix $M$ capable of accommodating the Fritz distribution that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = 4^8 = 65,536$ columns.
-Understandably, this matrix is not reproduced here.
+This marginal scenario $\mscenario$ then defines an incidence matrix $M$ capable of accommodating the Fritz distribution that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = 4^8 = 65,536$ columns --- this matrix is not reproduced here.
 The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
@@
 Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
-The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to be asymmetric, then one can conclude the space of accessible distributions is non-convex.}.
+The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution.\footnote{If the extremal distribution happens to be asymmetric, then one can conclude the space of accessible distributions is non-convex.}
 

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Changed A2 again

@@
     \begin{figure}
-    \begin{center}
+    \begin{nscenter}
         \begin{minipage}[t]{.48\textwidth}
@@
         \end{minipage}
-    \end{center}
+    \end{nscenter}
     \end{figure}
@@
     \begin{figure}
-    \begin{center}
+    \begin{nscenter}
         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational_fritz_bell}}
@@
         \label{fig:triangle_structure_with_fritz_bell_embedded}
-    \end{center}
+    \end{nscenter}
     \end{figure}
@@
     \begin{figure}
-    \begin{center}
+    \begin{nscenter}
             \includegraphics[scale=0.6]{../../figures/distributions/fritz_dist_plotted_bits.pdf}
@@
             \label{fig:fritz_distribution_visualized}
-    \end{center}
+    \end{nscenter}
     \end{figure}
@@
     \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it.
-To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:exemplary_inflations_of_the_triangle_structure}.
+To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:deriving_inequalities_from_the_inflation_technique}.
 
@@
     % \begin{figure}
-    % \begin{center}
+    % \begin{nscenter}
     %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
@@
     %         \label{fig:uniform_distribution}
-    % \end{center}
+    % \end{nscenter}
     % \end{figure}
@@
     \begin{figure}
-    \begin{center}
+    \begin{nscenter}
             \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
@@
             \label{fig:noisy_fritz}
-    \end{center}
+    \end{nscenter}
     \end{figure}
@@
     % \begin{figure}
-    % \begin{center}
+    % \begin{nscenter}
     %         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
@@
     %         \label{fig:triangle_structure_quantum_model}
-    % \end{center}
+    % \end{nscenter}
     % \end{figure}
@@
     \begin{figure}
-    \begin{center}
+    \begin{nscenter}
             \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
@@
             \label{fig:maximum_violation_I_1}
-    \end{center}
+    \end{nscenter}
     \end{figure}
     \begin{figure}
-    \begin{center}
+    \begin{nscenter}
             \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
@@
             \label{fig:maximum_violation_I_3}
-    \end{center}
+    \end{nscenter}
     \end{figure}
     \begin{figure}
-    \begin{center}
+    \begin{nscenter}
             \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
@@
             \label{fig:symmetrized_fritz}
-    \end{center}
+    \end{nscenter}
     \end{figure}
@@
 For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable.
-This will become apparent in \cref{sec:exemplary_inflations_of_the_triangle_structure} when the Inflation Technique is applied to the Triangle structure, producing considerably large marginal models.
+This will become apparent in \cref{sec:deriving_inequalities_from_the_inflation_technique} when the Inflation Technique is applied to the Triangle structure, producing considerably large marginal models.
 Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
@@
     The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if an observable probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$.
-As a precursor, the Inflation Technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure.
-As a example, a few inflations of the Triangle structure are depicted in \cref{fig:inflations}.
+As a precursor, the Inflation Technique begins by \textit{augmenting} a causal structure $\graph$ with additional copies of its nodes, producing an \textit{inflated} causal structure $\graph'$ called an \term{inflation}, and then exposes how causal inference tasks on the inflation can be used to make inferences on the original causal structure.
+For reference, a few inflations of the Triangle structure are depicted in \cref{fig:inflations}.
 Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}.
@@
 All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'.
-A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
-    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
-    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index.
-In addition to the common graph-theoretic terminology and notation presented in \cref{sec:causal_compatibility}, we define two more concepts necessary to formally define an inflation of $\graph$.
-First, an \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$: $\Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to m} \mid n, m \in N}}$.
-An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$: $\AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}}$.
-
-    \begin{definition}
-        \label{def:inflation}
-        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
-        \[ \forall n' \in \nodes': \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \eq \label{eq:inflation_defn}\]
-    \end{definition}
-    \begin{center}
+A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$, i.e.
+$A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B'$.\footnote{Note that we preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X$ is equivalent to $Y$ upon removal of the copy-index.}
+
+    \begin{nscenter}
     \begin{figure}
@@
     \end{figure}
-    \end{center}
-    \begin{center}
+    \end{nscenter}
+
+    In addition to the common graph-theoretic terminology and notation presented in \cref{sec:causal_compatibility}, two related concepts need introductions.
+First, an \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$: $\Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to m} \mid n, m \in N}}$.
+An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$: $\AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}}$.
+
+    The Inflation Technique begins with distribution $\prob[N]$ defined over some observable nodes $N$ of $\graph$ and the a priori assumption that it is compatible with $\graph$ pursuant to the definitions provided in \cref{sec:causal_compatibility}.
+Regarding $\graph$ as a causal hypothesis, the observable correlation $\prob[N]$ can only be influenced by the ancestry of $N$ in $\graph$.
+Consequently, for any set of nodes $N'$ of an inflation $\graph'$ where the ancestral subgraph $\AnSub[\graph']{N'}$ happens to be homomorphic to the ancestral subgraph $\AnSub[\graph]{N}$, one can conclude that the distribution $\prob[N']$ (induced by $\prob[N]$\footnote{The inflated distribution $\prob[N']$ assigns the same probability to all events of $\prob[N]$ whenever the events are equivalent under the removal of copy-indices.}) is compatible with $\graph'$ using the same latent explanations for $\prob[N]$ in $\graph$.
+This observation is known as the \term{Inflation Lemma}~\cite[Lemma 3]{Inflation}.
+
+    To formalize the Inflation Lemma, we define the \term{injectable sets of $\graph'$}, denoted $\Inj[\graph]{\graph'}$, as all sets of nodes in $\graph'$ whose ancestral subgraphs are homomorphic (via copy-index removal) to an ancestral subgraph in $\graph$: $\Inj[\graph]{\graph'} \defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}$.
+Analogously defined are the \term{images of the injectable sets in $\graph$}: $\ImInj[\graph]{\graph'} \defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}$.
+
+    To illustrate these concepts, consider the Spiral inflation $\graph'$ depicted in \cref{fig:spiral_inflation}.
+The ancestral subgraph of $\bc{A_1}$ in the Spiral inflation (denoted $\AnSub[\graph']{\bc{A_1}}$) is highlighted in \cref{fig:spiral_inflation_inj1} and is clearly homomorphic to the ancestral subgraph of its image $\bc{A}$ in the Triangle structure ($\graph$) (\cref{fig:spiral_inflation_iminj1}).
+Additionally, the set $\bc{A_2, C_1}$ is an injectable set of $\graph'$ because $\AnSub[\graph']{\bc{A_2, C_1}}$ (highlighted in \cref{fig:spiral_inflation_inj2}) is homomorphic (via copy-index removal) to the $\AnSub[\graph]{\bc{A, C}}$ in the Triangle structure $(\graph)$ (\cref{fig:spiral_inflation_iminj2}).
+
+    \begin{nscenter}
     \begin{figure}
@@
     \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
-    \caption{$\AnSub[\graph']{A_1}$}\label{fig:spiral_inflation_inj1}
+    \caption{$\AnSub[\graph']{\bc{A_1}}$}\label{fig:spiral_inflation_inj1}
     \end{subfigure}
@@
     \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
-    \caption{$\AnSub[\graph]{A}$}\label{fig:spiral_inflation_iminj1}
+    \caption{$\AnSub[\graph]{\bc{A}}$}\label{fig:spiral_inflation_iminj1}
     \end{subfigure}
@@
     \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
-    \caption{$\AnSub[\graph']{A_2, C_1}$}\label{fig:spiral_inflation_inj2}
+    \caption{$\AnSub[\graph']{\bc{A_2, C_1}}$}\label{fig:spiral_inflation_inj2}
     \end{subfigure}
@@
     \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_2}}
-    \caption{$\AnSub[\graph]{A,C}$}\label{fig:spiral_inflation_iminj2}
+    \caption{$\AnSub[\graph]{\bc{A,C}}$}\label{fig:spiral_inflation_iminj2}
     \end{subfigure}
@@
     \end{figure}
-    \end{center}
-    For each inflated node $n'$, the ancestral sub-graph of $n'$ in $\graph'$ is homomorphic to its counterpart in $\graph$ where the homomorphism is the removal of the copy-index.
-For example, the ancestral subgraph of $A$ in the Triangle structure (denoted $\AnSub[\graph]{A}$) is highlighted in \cref{fig:spiral_inflation_iminj1} and is clearly homomorphic to the ancestral subgraph of $A_1$ in the Spiral inflation (denoted $\AnSub[\graph]{A_1}$) depicted in \cref{fig:spiral_inflation_inj1}.
-Since this ancestral homomorphism exists for each node $n'$ of the Spiral inflation (\cref{fig:spiral_inflation}), it qualifies as a valid inflation of the Triangle structure (\cref{fig:triangle_structure}).
-
-    \begin{definition}
-        Given a causal structure $\graph$ and an inflation $\graph'$ of $\graph$, define the \term{injectable sets} in $\graph'$ and the \term{images of the injectable sets} in $\graph$, (respectively denoted $\Inj[\graph]{\graph'}$ and $\ImInj[\graph]{\graph'}$), as follows:
-        \begin{align*}
-            \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}} \\
-            \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}
-        \end{align*}
-    \end{definition}
-
-    As an example of an injectable set, the set $\bc{A_2, C_1}$ of the Spiral inflation ($\graph'$) (\cref{fig:spiral_inflation}) is an injectable set of $\graph'$ because its ancestral subgraph $\AnSub[\graph']{A_2, C_1}$ (highlighted in \cref{fig:spiral_inflation_inj2}) is homomorphic (via copy-index removal) to the ancestral subgraph of $\bc{A, C}$ in the Triangle structure $(\graph)$ (\cref{fig:spiral_inflation_iminj2}).
-The injectable sets of an inflation are of \textit{principle importance} to the inflation technique.
-The Inflation Technique begins with joint distribution $\prob[\nodes_O]$ defined over the observable nodes of $\graph$ and the a priori assumption that it is compatible with $\graph$ as defined in \cref{sec:causal_compatibility}.
-For each injectable set $N' \subseteq \Inj[\graph]{\graph'}$ and image $N \subseteq \ImInj[\graph]{\graph'}$ consisting entirely of observable nodes ($N \subseteq \nodes_O$), there is a pair $\prob[N], \prob[N']$ of marginal distributions induced by $\prob[\nodes_O]$ where $\prob[N']$ assigns the same probability to all events of $\prob[N]$ whenever the events are equivalent under the removal of copy-indices.
-These pairs of distributions can be raveled to form a pair of marginal models defined over the injectable sets $\prob^{\Inj[\graph]{\graph'}} = \bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ and their images $\prob^{\ImInj[\graph]{\graph'}} = \bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$.
-
-    \begin{lemma}
-        \label[lemma]{lem:inflation}
-        \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\prob^{\ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\prob^{\Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-    \end{lemma}
-
-    \begin{proof}
-        Given that $\prob^{\ImInj[\graph]{\graph'}}$ is compatible with $\graph$, it admits a joint distribution $\prob[\nodes]$ that can be factorized into its causal parameters $\prob[\nodes] = \prod_{n \in \nodes} \prob[n\mid \Pa[\graph]{n}]$.
+    \end{nscenter}
+    % \begin{definition}
+    %     Given a causal structure $\graph$ and an inflation $\graph'$ of $\graph$, define the \term{injectable sets} in $\graph'$ and the \term{images of the injectable sets} in $\graph$, (respectively denoted $\Inj[\graph]{\graph'}$ and $\ImInj[\graph]{\graph'}$), as follows:
+    %     \begin{align*}
+    %         \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}} \\
+    %         \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}
+    %     \end{align*}
+    % \end{definition}
+
+    % \begin{lemma}
+    %     \label[lemma]{lem:inflation}
+    %     \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\prob^{\ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\prob^{\Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
+    % \end{lemma}
+
+    % \begin{proof}
+    %     Given that $\prob^{\ImInj[\graph]{\graph'}}$ is compatible with $\graph$, it admits a joint distribution $\prob[\nodes]$ that can be factorized into its causal parameters $\prob[\nodes] = \prod_{n \in \nodes} \prob[n\mid \Pa[\graph]{n}]$.
 Given \cref{eq:inflation_defn}, one can create a set of \textit{inflated} causal parameters by matching causal parameters according to respective copy-indices: $\forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}]$.
@@
 Given $N' \in \Inj[\graph]{\graph'}$ and $N \sim N'$:
-        \[ \sum_{\nodes' \setminus N'} \prob[\nodes'] = \sum_{\nodes' \setminus N'} \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] = \prod_{n' \in N'} \prob[n'\mid \Pa[\graph]{n'}] = \prod_{n \in N} \prob[n\mid \Pa[\graph]{n}] = \prob[N] = \prob[N']  \]
-    \end{proof}
+    %     \[ \sum_{\nodes' \setminus N'} \prob[\nodes'] = \sum_{\nodes' \setminus N'} \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] = \prod_{n' \in N'} \prob[n'\mid \Pa[\graph]{n'}] = \prod_{n \in N} \prob[n\mid \Pa[\graph]{n}] = \prob[N] = \prob[N']  \]
+    % \end{proof}
 
@@
 
-    % % \begin{center}
+    % % \begin{nscenter}
     % %     \begin{tikzpicture}
@@
     % %     \end{tikzpicture}
-    % % \end{center}
+    % % \end{nscenter}
 
@@
 
-    The contrapositive of the Inflation Lemma (\cref{lem:inflation}) casts the compatibility problem for $\prob^{\ImInj[\graph]{\graph'}}$ (which exhibits equivalent compatibility as $\prob[\nodes_O]$) into a compatibility problem for $\prob^{\Inj[\graph]{\graph'}}$ of any non-trivial inequalities.
-If $\prob^{\Inj[\graph]{\graph'}}$ is found to be incompatible with $\graph'$, then $\prob[\nodes_O]$ is subsequently incompatible with $\graph$.
+    The injectable sets of an inflation are of \textit{principle importance} to the Inflation Technique.
+Given a distribution $\prob[\nodes_{O}]$ defined over the observable nodes of $\graph$, one can compute a marginal model defined over the injectable sets $\prob^{\Inj[\graph]{\graph'}} = \bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ and their images $\prob^{\ImInj[\graph]{\graph'}} = \bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$.
+The contrapositive of the Inflation Lemma casts the compatibility problem for $\prob^{\ImInj[\graph]{\graph'}}$ (which exhibits equivalent compatibility as $\prob[\nodes_O]$) into a compatibility problem for $\prob^{\Inj[\graph]{\graph'}}$ of any non-trivial inequalities.
+If $\prob^{\Inj[\graph]{\graph'}}$ is found to be incompatible with $\graph'$, then $\prob^{\ImInj[\graph]{\graph}}$ (and also $\prob[\nodes_O]$) must be incompatible with $\graph$.
 Fortunately, the inflated causal structure $\graph'$ possesses its own \textit{d-separation relations} which enforces conditional independence equality constraints on $\prob^{\Inj[\graph]{\graph'}}$.
@@
 This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.} Throughout this work, we let $\AnSepExpr[\graph]{\graph'}$ denote the set of all as-expressible sets.\footnote{Analogously to a marginal scenario $\mscenario$, the as-expressible sets $\AnSepExpr[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
-Therefore, in practice, it is completely sufficient to focus on the \textit{maximal} as-expressible sets.}
+Therefore, in practice, it is completely sufficient to focus on the \textit{maximal} as-expressible sets.} Efficient algorithms for computing the injectable and as-expressible sets of an inflation can be found in~\cite{Inflation}.
+\Cref{tab:asexpr_triangle_structure_wagon_wheel,tab:asexpr_triangle_structure_web} tabulate the as-expressible sets and the associated ancestral separations for the Wagon-Wheel and Web inflations (respectively \cref{fig:wagon_wheel_inflation,fig:the_web_inflation}).
+
+    \begin{nscenter}
+        \begin{table}
+        \parbox{.45\linewidth}{
+            \centering
+            \begin{tabular}{|c|c|}
+                \hline
+                \multicolumn{2}{|c|}{Maximally AS-Expressible Sets} \\
+                \multicolumn{2}{|c|}{for the Wagon-Wheel Inflation} \\
+                \hline
+                $\AnSepExpr[\graph]{\graph'}$ & Ancestral Separations \\
+                \hline
+                $\bc{A_2, B_1, C_3, C_1}$ & $\bc{A_2, B_1, C_3} \ancestralindep \bc{C_1}$ \\
+                $\bc{A_1, B_1, C_4, C_2}$ & $\bc{A_1, B_1, C_4} \ancestralindep \bc{C_2}$ \\
+                $\bc{A_1, B_2, C_1, C_3}$ & $\bc{A_1, B_2, C_1} \ancestralindep \bc{C_3}$ \\
+                $\bc{A_2, B_2, C_2, C_4}$ & $\bc{A_2, B_2, C_2} \ancestralindep \bc{C_4}$ \\
+                \hline
+            \end{tabular}
+            \caption{The maximally as-expressible sets for the Wagon-Wheel Inflation.
+            \label{tab:asexpr_triangle_structure_wagon_wheel}}
+        }
+        \hfill
+        \parbox{.45\linewidth}{
+            \centering
+            \begin{tabular}{|c|c|}
+                \hline
+                \multicolumn{2}{|c|}{Maximally AS-Expressible Sets} \\
+                \multicolumn{2}{|c|}{for the Web Inflation} \\
+                \hline
+                $\AnSepExpr[\graph]{\graph'}$ & Ancestral Separations \\
+                \hline
+                $\bc{A_1, B_1, C_1, A_4, B_4, C_4}$ & $\bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4}$ \\
+                $\bc{A_1, B_2, C_3, A_4, B_3, C_2}$ & $\bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2}$ \\
+                $\bc{A_2, B_3, C_1, A_3, B_2, C_4}$ & $\bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4}$ \\
+                $\bc{A_2, B_4, C_3, A_3, B_1, C_2}$ & $\bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2}$ \\
+                $\bc{A_1, B_3, C_4}$ & $\bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4}$ \\
+                $\bc{A_1, B_4, C_2}$ & $\bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2}$ \\
+                $\bc{A_2, B_1, C_4}$ & $\bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4}$ \\
+                $\bc{A_2, B_2, C_2}$ & $\bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2}$ \\
+                $\bc{A_3, B_3, C_3}$ & $\bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3}$ \\
+                $\bc{A_3, B_4, C_1}$ & $\bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1}$ \\
+                $\bc{A_4, B_1, C_3}$ & $\bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3}$ \\
+                $\bc{A_4, B_2, C_1}$ & $\bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}$ \\
+                \hline
+            \end{tabular}
+            \caption{The maximally as-expressible sets for the Web Inflation.
+            \label{tab:asexpr_triangle_structure_web}}
+        }
+        \end{table}
+    \end{nscenter}
 
@@
 In practice, the equality constraints implied by $\AnSepExpr[\graph]{\graph'}$ permits one to construct a marginal model defined over the as-expressible sets $\AnSepExpr[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$.
-In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (see \cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$.
+In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (see \cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$ --- the latter of which is discussed in \cref{sec:deriving_inequalities_from_the_inflation_technique}.
 
@@
 
-    % \begin{center}
+    % \begin{nscenter}
     %     \begin{tikzpicture}[scale=0.8]
@@
     %     \end{tikzpicture}
-    % \end{center}
+    % \end{nscenter}
 
@@
 
-    \subsection{Exemplary Inflations of The Triangle structure}
-    \label{sec:exemplary_inflations_of_the_triangle_structure}
-
-    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}.
+    \subsection{Deriving Inequalities from the Inflation Technique}
+    \label{sec:deriving_inequalities_from_the_inflation_technique}
+
+    \Cref{sec:inflation_technique_main_summary} summarizes how the Inflation Technique~\cite{Inflation} can cast the compatibility problem into the marginal problem by leveraging inflations of the Triangle structure.
 Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal as-expressible sets of $\graph'$, i.e.
 $\mscenario = \AnSepExpr[\graph]{\graph'}$.
-This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript.
-Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their as-expressible sets.
-An efficient algorithm for computing the injectable and as-expressible sets of an inflation can be found in~\cite{Inflation}.
 
@@
 The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
-The maximal as-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_wagon_wheel}.
+The maximal as-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{tab:asexpr_triangle_structure_wagon_wheel}.
 These maximal as-expressible sets define a marginal scenario where the joint variables $\jointvar$ are the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
@@
 The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
-
-    \begin{equation*}
-        \eq \label{eq:pre_injectable_triangle_structure_wagon_wheel}
-        \begin{gathered}
-            \textbf{Maximal AS-Expressible Sets} \\
-            \bc{A_2, B_1, C_3, C_1} \\
-            \bc{A_1, B_1, C_4, C_2} \\
-            \bc{A_1, B_2, C_1, C_3} \\
-            \bc{A_2, B_2, C_2, C_4} \\
-        \end{gathered}
-        \qquad
-        \begin{gathered}
-            \textbf{Ancestral Separations} \\
-            \bc{A_2, B_1, C_3} \ancestralindep \bc{C_1} \\
-            \bc{A_1, B_1, C_4} \ancestralindep \bc{C_2} \\
-            \bc{A_1, B_2, C_1} \ancestralindep \bc{C_3} \\
-            \bc{A_2, B_2, C_2} \ancestralindep \bc{C_4} \\
-        \end{gathered}
-    \end{equation*}
 To construct the marginal distribution vector $\probvec^{\mscenario}$ for the Fritz distribution, one begins with $\probvec^{\mscenario}$ defined in a \textit{symbolic} form,
     \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
-    Which can be factored into the ancestrally separated injectable sets using \cref{eq:pre_injectable_triangle_structure_wagon_wheel},
+    Which can be factored into the ancestrally separated injectable sets using \cref{tab:asexpr_triangle_structure_wagon_wheel},
     \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
@@
     The remaining inequalities in \cref{sec:found_inequalities} were derived using the Web inflation of \cref{fig:the_web_inflation}.
-The maximal as-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_web}.
-    \begin{equation*}
-        \eq \label{eq:pre_injectable_triangle_structure_web}
-        \begin{gathered}
-            \textbf{Maximal AS-Expressible Sets} \\
-            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
-            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
-            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
-            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
-            \bc{A_1, B_3, C_4} \\
-            \bc{A_1, B_4, C_2} \\
-            \bc{A_2, B_1, C_4} \\
-            \bc{A_2, B_2, C_2} \\
-            \bc{A_3, B_3, C_3} \\
-            \bc{A_3, B_4, C_1} \\
-            \bc{A_4, B_1, C_3} \\
-            \bc{A_4, B_2, C_1}
-        \end{gathered}
-        \qquad
-        \begin{gathered}
-            \textbf{Ancestral Separations} \\
-            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
-            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
-            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
-            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
-            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
-            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
-            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
-            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
-            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
-            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
-            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
-            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
-        \end{gathered}
-    \end{equation*}
+The maximal as-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{tab:asexpr_triangle_structure_web}.
 Analogously to the Wagon-Wheel inflation, these as-expressible sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.
@@
 Therefore $\varphi$ has capacity to modify both the terms of the inequality as well as the set of marginal models it constrains $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
-Permutations $\varphi$ that modify the marginal scenario have no application within the framework of the Inflation Technique because \cref{lem:inflation} requires inflated inequality to constrain injectable sets.
+Permutations $\varphi$ that modify the marginal scenario have no application within the framework of the Inflation Technique (\cref{sec:inflation_technique_main_summary}) because the Inflation Lemma only holds when the inflated inequality constrains injectable sets.
 Therefore, the desired set of symmetries for our purposes is a subgroup of $\Perm{\jointvar}$ that takes $\mscenario$ to $\mscenario$.
@@
     Notice that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
-Moreover they stabilize the as-expressible sets of \cref{eq:pre_injectable_triangle_structure_web}.
+Moreover they stabilize the as-expressible sets of \cref{tab:asexpr_triangle_structure_web}.
 Importantly,

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Improved compatibility discussion

@@
 
-    \Cref{sec:inflation_technique} briefly summaries the Inflation Technique in the specific context of this work.
+    \Cref{sec:main_appendix} briefly summaries the Inflation Technique in the specific context of this work.
 Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}.
@@
 Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$.
-Specifically, the causal structure $\graph$ hypothesizes that if each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$, then each $n$ should be conditionally independent of all other variables:
+Specifically, the causal structure $\graph$ hypothesizes that if each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$.
+Therefore, if each variable is conditioned on its parentage, the probability distribution $\prob[\nodes]$ should factorize accordingly:
     \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:compatibility_as_factorization}\]
@@
 
-    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two naive approaches worth mentioning here.
+    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two common approaches worth mentioning here.
 The first is to recognize that the conditional independence constraints implied by d-separation relations over the \textit{observable} variables form a family of necessary constraints for $\prob[\nodes_{O}]$.
@@
 Often, the observable d-separation relations implied by a causal structure form an \textit{insufficient} set of constraints for compatible distributions.
-Such causal structures, which include the Bell structure, have been termed \textit{interesting}~\cite{Henson_2014}, and more involved classification techniques must be used~\cite{Inflation}.
-The principle focus of this paper is the Triangle structure and has been shown to be one of the smallest interesting causal structures~\cite{Henson_2014}.
+Such causal structures, which include the Bell structure, have been termed \textit{interesting}~\cite{Henson_2014}.
+For interesting causal structures, stronger techniques must be used~\cite{Inflation}.
+The primary causal structure of this paper is the Triangle structure --- one of the smallest interesting causal structures~\cite{Henson_2014}.
 An alternative approach requires the cardinality (number of outcomes) of the latent variables to be fixed.
@@
 Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure.
-Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.} If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}.
-In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.
+Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}.
+If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}.
+\Cref{sec:main_appendix} provides a brief discussion of existing techniques used to derive these inequalities.
 
@@
 
-    Finally, \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:inflation_technique}) --- a novel tool for solving causal inference problems.
+    Finally, \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:main_appendix}) --- a novel tool for solving causal inference problems.
 Using the Inflation Technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum-inaccessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints.
@@
 The methods used to derive these inequalities are largely based on the Inflation Technique~\cite{Inflation}.
-A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:inflation_technique} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.
+A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:main_appendix} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.
 
@@
     \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it.
-To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:deriving_inequalities_from_the_inflation_technique}.
+To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:main_appendix_main_summary,sec:deriving_inequalities_from_the_inflation_technique}.
 
@@
     In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions.
-This result was made possible through extensive use of the Inflation Technique (\cref{sec:inflation_technique}) applied to the Fritz distribution.
+This result was made possible through extensive use of the Inflation Technique (\cref{sec:main_appendix}) applied to the Fritz distribution.
 In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
@@
 Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes.
-In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations.
+In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:main_appendix}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations.
 These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and is a recommended focus for future research.
@@
     \section{Summary of Inflation Technique}
-    \label{sec:inflation_technique}
+    \label{sec:main_appendix}
 
@@
 This is accomplished by illustrating how the marginal problem can be expressed as a linear program in which the solution to the marginal problem is encoded in the feasibility or infeasibility of said linear program.
-This section is presented prior to \cref{sec:inflation_technique_main_summary} as the marginal problem becomes an integral component of the Inflation Technique in subsequently deriving the inequalities presented in \cref{sec:found_inequalities}.
+This section is presented prior to \cref{sec:main_appendix_main_summary} as the marginal problem becomes an integral component of the Inflation Technique in subsequently deriving the inequalities presented in \cref{sec:found_inequalities}.
 Moreover, the Marginal problem is presented here logically independent from the remainder of the manuscript both for procedural clarity and because the marginal problem has applications to numerous areas of mathematics including game theory~\cite{Vorobev_1962}, database theory, knowledge integration of expert system, and of course, quantum information theory~\cite{Fritz_2011}.
@@
     \label{sec:deriving_inequalities}
-    \label{sec:inflation_technique_main_summary}
+    \label{sec:main_appendix_main_summary}
     The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if an observable probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$.
@@
     Ancestral independence implies an unconditional probabilistic independence --- if $N_1' \ancestralindep N_2'$ then $\prob[N_1' \cup N_2'] = \prob[N_1']\prob[N_2']$.
-If $N_1', N_2' \in \Inj[\graph]{\graph'}$, then the associated probabilistic constraint is an applicable constraint for $\prob^{\Inj[\graph]{\graph'}}$.
+If $N_1', N_2' \in \Inj[\graph]{\graph'}$, then the associated probabilistic constraint is applicable to $\prob^{\Inj[\graph]{\graph'}}$.
 This notion generalizes to more than two ancestrally separated sets.
@@
 
-    \Cref{sec:inflation_technique_main_summary} summarizes how the Inflation Technique~\cite{Inflation} can cast the compatibility problem into the marginal problem by leveraging inflations of the Triangle structure.
+    \Cref{sec:main_appendix_main_summary} summarizes how the Inflation Technique~\cite{Inflation} can cast the compatibility problem into the marginal problem by leveraging inflations of the Triangle structure.
 Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal as-expressible sets of $\graph'$, i.e.
@@
 
-    \Cref{sec:inflation_technique_main_summary} detailed how to obtain causal compatibility inequalities for any causal structure by constructing a marginal problem (see \cref{sec:marginal_satisfiability}) and supplying an incompatible distribution to generate an infeasibility certificate.
+    \Cref{sec:main_appendix_main_summary} detailed how to obtain causal compatibility inequalities for any causal structure by constructing a marginal problem (see \cref{sec:marginal_satisfiability}) and supplying an incompatible distribution to generate an infeasibility certificate.
 In \cref{sec:found_inequalities}, a causal compatibility inequality symmetric under permutations of the variables $A,B,C$ was presented (see \cref{eq:symmetic_web_inequality}).
@@
 Therefore $\varphi$ has capacity to modify both the terms of the inequality as well as the set of marginal models it constrains $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
-Permutations $\varphi$ that modify the marginal scenario have no application within the framework of the Inflation Technique (\cref{sec:inflation_technique_main_summary}) because the Inflation Lemma only holds when the inflated inequality constrains injectable sets.
+Permutations $\varphi$ that modify the marginal scenario have no application within the framework of the Inflation Technique (\cref{sec:main_appendix_main_summary}) because the Inflation Lemma only holds when the inflated inequality constrains injectable sets.
 Therefore, the desired set of symmetries for our purposes is a subgroup of $\Perm{\jointvar}$ that takes $\mscenario$ to $\mscenario$.

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
naive -> might

@@
 However, this result is far more surprising.
-Since the inequality is symmetric with respect to the permutation of parties, one would naively expect that the maximum violating distribution be symmetric as well.
+Since the inequality is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well.
 If it were not, one could construct a distribution that violates $I\tsb{SymmetricWeb}$ further by symmetrizing $\prob[\fritz]$ (\cref{fig:symmetrized_fritz}) by normalizing over all possible permutations of $A,B,C$.

### 2017-09-08 documents/TriangleScenarioArXiv/ts.tex
substantial edits to tone, a few paragraphs removed.

@@
 Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion.
-In the context of two parties sharing a common resource, these non-classical correlations are also known as non-local correlations.
-Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion.
-Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?
+In scenarios where all parties share a common resource, these non-classical correlations are also known as non-local correlations.
+Any constraint satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion.
+Such criteria were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?
 Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary.
 Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation.
+This provides the first robust-to-noise witness of quantum correlations in the Triangle structure.
 We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
@@
 
-    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964}.
+    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964,Brunner_2013}.
 Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}.
@@
 The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}.
-Causal compatibility inequalities, such as Bell and Instrumental inequalities, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation.
+Causal compatibility inequalities, such as Bell and Instrumental inequalities \cite{pearl1995instrumental,bonet2001instrumental,evans2012graphical}, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation.
 To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}.
@@
 
-    The Triangle structure (\cref{fig:triangle_structure}) is a causal structure composed of $3$ parties labeled $A, B, C$ arranged in a triangular configuration while pair-wise sharing hidden/latent variables $X, Y, Z$.
+    The Triangle structure (\cref{fig:triangle_structure}) is a causal structure comprised of $3$ parties labeled $A, B, C$ arranged in a triangular configuration while pair-wise sharing hidden/latent variables $X, Y, Z$.
 It has been extensively studied previously (see~\cite[Fig.
@@
 This accomplishment was made possible through the combination of two previous developments.
-The first, an insight made by \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure.
-The second, a new framework for solving causal inference problems developed by Wolfe \emph{et al.}~\cite{Inflation} called \term{The Inflation Technique}.
-Ultimately, this work serves as a validation that the Inflation Technique is sensitive enough to offer new insights into quantum non-classicality.
+First, the insight of \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure.
+Second, the new framework for solving causal inference problems developed by Wolfe \emph{et al.}~\cite{Inflation} called \term{The Inflation Technique}.
+Ultimately, this work serves as a validation that the Inflation Technique is sensitive enough to offer new insights into quantum non-classicality \cite{Navascues_2017}.
 Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of non-classicality.
@@
 \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}.
-The Fritz distribution was proven to be non-classical without the use of inequalities --- this report fills in the desired missing inequalities.
-A sample of these inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetic_web_inequality}.
-Finally, \cref{sec:violations_noise} introduces a method for parameterizing the space of quantum-accessible distributions which we used to numerically optimize against our derived inequalities in search of stronger types of non-classicality.
+The Fritz distribution first was proven to be non-classical without the use of inequalities.
+Here we offer a direct proof using inequalities, with the advantage that our proof is robust to noise.
+A sample of such inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality}.
+In \cref{sec:violations_noise} we quantify the robustness to noise of the Fritz distribution, and we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to seek out new new flavors of of non-classicality in the Triangle structure.
 Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.
@@
 Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}.
-\Cref{sec:deriving_inequalities} demonstrates how the Inflation Technique was used to derive causal compatibility inequalities for the Triangle structure that are violated by quantum-accessible distributions.
+\Cref{sec:deriving_inequalities} demonstrates how the Inflation Technique was used to derive the causal compatibility inequalities for the Triangle structure which admit violation by quantum-accessible distributions.
 
@@
 
-    Henceforth, we will utilize a number of familiar notions from graph theory and denote them accordingly.
+    Henceforth, we will utilize a number of familial notions from graph theory and denote them accordingly.
 The \term{parents of a node} $n \in \nodes$ are all nodes which point directly into $n$, i.e.
@@
 
-    Now that the notion of a causal structure $\graph$ is defined along with some standard graph-theoretic notation, it is now possible to precisely define the notion of compatibility between $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$.
+    Let us now formalize the notion of compatibility between a causal structure $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$.
 Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$.
@@
 If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$.
-The compatibility of a distribution $\prob[\nodes]$ with a causal structure $\graph$ pursuant to \Cref{eq:compatibility_as_factorization} is equivalent to the requirement that $\prob[\nodes]$ obeys all of the conditional independence constraints implied by the \textit{d-separation relations} between variables/nodes in $\graph$~\cite{Pearl_2009}.
+    % The compatibility of a distribution $\prob[\nodes]$ with a causal structure $\graph$ pursuant to \cref{eq:compatibility_as_factorization} is equivalent to the requirement that $\prob[\nodes]$ obeys all of the conditional independence constraints implied by the \textit{d-separation relations} between variables/nodes in $\graph$~\cite{Pearl_2009}.
      When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is possible to completely determine whether or not $\prob[\nodes]$ is compatible with $\graph$ by computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}.
 
-    A challenge is presented when one is supplied with a partial observation, i.e.
+    A challenge, however, is presented when one is supplied with a partial observation, i.e.
 a joint distribution $\prob[\nodes_{O}]$ where $\nodes_{O} \subset \nodes$ is some subset of variables referred to as the \term{observable nodes} $\nodes_O$.
@@
 Instead, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \prod_{n \in \nodes_{O}} \prob[n \mid \Pa[\graph]{n}]$.
-The complementary, unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$ representing hidden random variables that are hidden either by some fundamental process or cannot be measured due to other limitations.
+The complementary, unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$, and should be understood as hidden random variables that are unknowable either by some fundamental process or cannot be measured due to other limitations.
 
     There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two common approaches worth mentioning here.
-The first is to recognize that the conditional independence constraints implied by d-separation relations over the \textit{observable} variables form a family of necessary constraints for $\prob[\nodes_{O}]$.
-The failure to satisfy one of these observable independence relations immediately qualifies $\prob[\nodes_{O}]$ as incompatible with $\graph$.
-Often, the observable d-separation relations implied by a causal structure form an \textit{insufficient} set of constraints for compatible distributions.
-Such causal structures, which include the Bell structure, have been termed \textit{interesting}~\cite{Henson_2014}.
-For interesting causal structures, stronger techniques must be used~\cite{Inflation}.
-The primary causal structure of this paper is the Triangle structure --- one of the smallest interesting causal structures~\cite{Henson_2014}.
-An alternative approach requires the cardinality (number of outcomes) of the latent variables to be fixed.
-In most realistic scenarios, the nature of the latent variables is completely unspecified.
-More powerful approaches find constraints for $\prob[\nodes]$ in the form of probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals which constraint the set of compatible probability distributions.
+The first is to recognize that many equality constraints are implied by the causal structure, including conditional independence relations and so-called Verma constraints among others; see Refs.
+\cite{evans2015margins,evans2017markov} for thorough treatments.
+The failure to satisfy an equality constraint immediately disqualifies $\prob[\nodes_{O}]$ from being compatible with $\graph$.
+Equality constraints are easily derived given a causal structure, and checking equality-constraints satisfaction is the minimalistic algorithm which powers the overwhelming majority of practical causal inference hypothesis testing in the fields of machine learning and artificial intelligence.
+In quantum theory, however, we require strong, more sensitive, causal inference techniques.
+This is because the equality constraints satisfied by classical correlations (compatible with some classical causal structure) are also all satisfied by quantum correlations (generated by the quantumified causal structure in which latent variables are replaced with shared entanglement) \cite{Henson_2014}.
+    Our focus, therefore, in on deriving \emph{inequality} constraints (over $\prob[\nodes_{O}]$ and its marginals) implied by a causal structure, which we term \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons.
+Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure.
+Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}.
+For some causal structures, the equality constraints associated with it are sufficient to perfectly characterize the distributions genuinely compatible with it; for others, however, inequality constraints are also important.
+Causal structures for which inequality constraints are relevant have been termed \textit{interesting}~\cite{Henson_2014}, and such structures include the Instrumental structure, the Bell scenario, and the Triangle scenario studied here, among infinitely many others.
+    Herein we use the Inflation Technique~\cite{Inflation} to find causal compatibility inequalities; \Cref{sec:main_appendix} discusses the Inflation Technique as applied in this work.
+
+     probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals.
 We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons.
@@
 Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}.
+\Cref{sec:main_appendix} provides a brief discussion of existing techniques used to derive these inequalities.
+
     If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}.
-\Cref{sec:main_appendix} provides a brief discussion of existing techniques used to derive these inequalities.
-
-    Unfortunately, a singular inequality cannot prove that a given distribution is \textit{compatible}, only \textit{incompatible}.
-Instead, a \textit{complete characterization} of compatibility would consist of a complete set of all valid causal compatibility inequalities; satisfaction of a complete set of inequalities does prove compatibility.
+Conversely, however, a singular inequality can only be used to prove that a given distribution is \textit{incompatible}; a single inequality cannot certify compatibility.
+A \textit{complete characterization} of compatibility consists of a complete set of all valid causal compatibility inequalities such that satisfaction of the entire set certifiescompatibility.
 Currently however, it is unknown how to obtain a complete characterization for any given causal structure, including the Triangle structure.
@@
 Henceforth, we will use these two terms interchangeably.
-From a resource standpoint, if the non-classicality of $\prob[\nodes_{O}]$ can be witnessed by an inequality $I$, but $\prob[\nodes_{O}]$ can be implemented using quantum states and measurements, then the causal compatibility inequality $I$ represents a physical task where quantum resources out-perform classical resources.
+From a resource standpoint, if the non-classicality of $\prob[\nodes_{O}]$ with $\graph$ can be witnessed by an inequality $I$, but nevertheless $\prob[\nodes_{O}]$ can be implemented using quantum states and measurements while otherwise respecting the causal relations of $\graph$, then the causal compatibility inequality $I$ represents a task or game where quantum resources out-perform classical resources relative to $\graph$.
 
@@
     \label{sec:bell_structure}
-    This section aims to define the Bell structure and summarize the main results associated with its non-classical character.
-The purpose of this section is to equip an unfamiliar reader with the pertinent background and also to establish a context for which to draw comparisons between the advancements made toward understanding non-classicality of the Bell structure and the analogous results obtained for Triangle structure in the remainder of this work.
-Readers familiar with the Bell structure (sometimes called Bell scenario/experiment) will experience little obstacles proceeding to \Cref{sec:triangle_structure}.
-
-    The Bell structure (\cref{fig:bell_structure}) refers to an iconic causal structure involving two distant observers which make local measurements $A, B$ determined by measurement settings $S_A, S_B$ on a shared latent resource $\la$~\cite{Brunner_2013}.
-The resulting observed correlations form a conditional probability distribution $\prob[AB|S_AS_B]$.
-Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, this distribution is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ such that there exists a distribution $\prob[AB|S_AS_B,\la]$ such that $\prob[AB|S_AS_B] = \sum_{\la} \prob[AB|S_AS_B,\la]$ and also satisfies the following implementation of \cref{eq:compatibility_as_factorization}:
-    \[ \prob[AB|S_AS_B,\la] = \prob[A|S_A,\la]\prob[B|S_B,\la] \]
-    Any observed distribution $\prob[AB|S_AS_B]$ which fails to be explained by the classical causal hypothesis of the Bell structure is appropriately termed non-classical.
-Often, distributions incompatible with the Bell structure are referred to as non-local because the Bell structure indicates that the latent resource is shared locally and measurements are made locally.
-In particular,~\citet{Bell_1964} demonstrated that there exists distributions that are non-classical yet are attainable via quantum resources and measurements.
-If one does not wish to accept fine-tuning arguments, one must accept that quantum correlations can be non-local as no variation to the latent nodes can explain the same correlations~\cite{Wood_2012}.\footnote{This is unlike the Triangle structure wherein a global yet latent common cause is always an acceptable explanation for any correlation and does require fine-tuning.
-Therefore, we never refer to non-classical correlations in Triangle Structure as non-local.} A distribution is accessible with quantum resources and measurements if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension and measurement operators $M_{A|S_A}, M_{B|S_B}$ conditional indexed by the measurement settings such that $\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}$.
-The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities such as the CHSH inequality (\cref{eq:CHSH_ineq_orig}) which constrain the correlations between binary variables $A$ and $B$ for classical distributions~\cite{CHSH_Original}.
-    \[ \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 0} + \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 1} + \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 0} - \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 1} \leq 2 \eq \label{eq:CHSH_ineq_orig} \]
-    Non-trivial Bell inequalities such as the CHSH inequality are capable of distinguishing the non-classical nature of distributions beyond the constraints implied by observable d-separation relations; the inequalities presented in \cref{sec:found_inequalities} are also of this type.
-
-    Finally, must like any causal structure, Bell inequalities act as a measure of the non-classical character of a given distribution.
+    This section aims to define the Bell causal structure and to review some of the traditional witnesses used to asses the classicality (or lack thereof) of distributions relative to it.
+The purpose of this section is to equip readers with the pertinent background and also to draw comparisons between the advancements made toward understanding non-classicality of the Bell structure versus analogous results obtained for Triangle structure later in this work.
+
+    The bipartite Bell structure (\cref{fig:bell_structure}) refers to an iconic causal structure involving two distant parties who observe the outcomes of local measurements as random variables $A (B)$ determined by their individual measurement settings $S_A (S_B)$, and where the parties are also presumed to be commonly informed by some shared latent resource $\la$~\cite{Brunner_2013}.
+The resulting observable correlations hence naturally form a conditional probability distribution $\prob[AB|S_AS_B]$.
+Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, this distribution is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that
+%    there exists a distribution $\prob[AB|S_AS_B,\la]$ such that $\prob[AB|S_AS_B] = \sum_{\la} \prob[AB|S_AS_B,\la]$ and also satisfies the following implementation of \cref{eq:compatibility_as_factorization}:
+\begin{align}\label{eq:bellcompat}
+ \prob \text{ is classically compatible with \cref{fig:bell_structure}} \quad\text{iff}\quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\,.
+\end{align}
+    Any observed distribution $\prob[AB|S_AS_B]$ which fails to be explained by the classical causal hypothesis of the Bell structure as defined by \cref{eq:bellcompat} is appropriately termed non-classical.
+Often, distributions incompatible with the Bell structure are referred to as non-local because the Bell structure markedly lacks causal influence from one party to another.
+In particular,~\citet{Bell_1964} demonstrated that there exists distributions that are non-classical yet are attainable via local measurements on a shared quantum resource.
+    %If one does not wish to accept fine-tuning arguments, one must accept that quantum correlations can be non-local as no variation to the latent nodes can explain the same correlations~\cite{Wood_2012}.\footnote{This is unlike the Triangle structure wherein a global yet latent common cause is always an acceptable explanation for any correlation and does require fine-tuning.
+Therefore, we never refer to non-classical correlations in Triangle Structure as non-local.}
+
+    Let us now contrast now the classical definition of compatibility with its quantum generalization.
+Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems.
+Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement operators $M_{A|S_A}, M_{B|S_B}$ with indices conditional upon the measurement settings, such that
+\begin{align}\label{eq:bellQcompat}
+\prob \text{ is a quantum distribution of \cref{fig:bell_structure}} \quad\text{iff}\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
+\end{align}
+     The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities (such as the CHSH inequality \cref{eq:CHSH_ineq_orig} reproduced below) which constrain the correlations between binary variables $A$ and $B$ for classical distributions~\cite{CHSH_Original}.
+    \[ \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 0} + \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 1} + \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 0} - \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
+    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the non-classical nature of distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type.
+Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.
+
+%    Finally, must like any causal structure, Bell inequalities act as a measure of the non-classical character of a given distribution.
 In particular, the antecedent of \cref{eq:CHSH_ineq_orig} has a classical upper-bound of $2$ and it can be shown to have a quantum upper-bound of $2\sqrt{2}$~\cite{Cirelson_1980}.
@@
     \end{figure}
+
     \section{Triangle structure}
@@
 
-    Discovering quantum non-classicality in any causal structure is desirable, so why, in particular, is it important to do so in the Triangle structure?
     As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
+%Here we lay out the task for discovering quantum non-classicality in the Triangle structure. 
 Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that
@@
     %And also, the given distribution
-    $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}:
-    \[ \prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \eq \label{eq:triangle_compatibility} \]
-
-    For certain causal structures, the conditional independence relations provided by $d$-separation relations are a sufficient characterization of compatibility.
-Recently, \citet{Henson_2014}, classified the Triangle structure as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the Triangle structure possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover, \citet{Inflation} concretely demonstrate that the space of classical distributions on the Triangle structure is non-convex, unlike the Bell structure.
-It can be argued that convexity of the Bell structure distributions is partially responsible for the wealth of knowledge that is known about the Bell structure.
-It is also reasonable to speculate that quantum non-classicality in the Triangle structure can be translated directly into a computational advantage for certain computational circuits~\cite{Terhal_2002}.
-Characterizing quantum non-classicality for interesting causal structures remains an unsolved problem, and the Triangle structure is a small, non-trivial case study.
-
-    Additionally, \citet{Fritz_2012} demonstrated that the Triangle structure is the \textit{smallest} correlation scenario\footnote{Correlation scenarios differ from the Bell structure in that measurement setting variables are absent in correlation scenarios.} in which their exists incompatible, quantum distributions by explicitly mentioning one which we discuss in detail in \cref{sec:fritz_distribution}.
-Fritz's proof of non-classicality does not involve compatibility inequalities, but instead mentions that inequalities would be helpful for characterizing non-classicality in the Triangle structure~\cite{Fritz_2012}.
-    % \comment[E]{Revisions processed up to here thusfar.}
-
-    Finally, \citet{Inflation} proposed the Inflation Technique (summarized in \cref{sec:main_appendix}) --- a novel tool for solving causal inference problems.
-Using the Inflation Technique, they were able to prove incompatibility between the Triangle structure and the $W$-type distribution; a quantum-inaccessible distribution whose incompatibility is not witness-able by \textit{any} entropic inequalities or any other known constraints.
-Consequently, as a an algorithmic framework, the Inflation Technique comes closer to characterizing non-classicality in the Triangle structure than all others.
-
-    It is worth noting that a number of causal compatibility inequalities for the Triangle structure have been derived in previous works.
-For example, \citet{Steudel_2010} derived an inequality for a series of causal structures with $n \in \N$ variables where at most $c \in \N$ share a common ancestor.
-The Triangle structure is a special case with $c = 2$, $n = 3$.
-Moreover, \citet{Henson_2014} derive a family of entropic inequalities constraining the set of compatible correlations.
-Most recently, \citet{Inflation} derive a family of polynomial, $2$-outcome, causal compatibility inequalities; $37$ non-trivial representatives are printed in~\cite{Inflation}.
-\Cref{sec:preliminary_research} outlines our initial attempts to utilize these inequalities to search for incompatible distributions that are also quantum-accessible.
-The subsequent failure of these approaches will motivate the remainder of this work.
-
-    In conclusion, the Triangle structure is a desirable case study because there exists a quantum distribution that is known to be incompatible, but no previously known inequalities were able to witness its incompatibility.
+    $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}, i.e.
+    \[ \prob \text{ is classically compatible with \cref{fig:triangle_structure}} \quad\text{iff}\quad\prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z]\,.
+\eq \label{eq:triangle_compatibility} \]
+    By contrast, the quantum distribution of the Triangle structure are defined with substantially greater freedom, namely
+     \[ \prob \text{ is a quantum distribution of \cref{fig:bell_structure}} \quad\text{iff}\quad\prob[ABC][abc] = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}}\,, \eq \label{eq:triangle_Qcompatibility} \]
+where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets, and $\netperm$ is a permutation matrix to align the states and measurements appropriately.
+    %For certain causal structures, the conditional independence relations provided by $d$-separation relations are a sufficient characterization of compatibility.
+Recently, \citet{Henson_2014}, classified the Triangle structure as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the Triangle structure possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover,
+    The Triangle structure serves as an excellent test case for furthering our understanding of quantum nonclassicality in network causal structures.
+It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
+     For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \citet{Fritz_2012,Inflation}, unlike for the Bell structure.
+The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
+     Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum nonclassicality.
+It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicallity are expected to correspond to novel information-theoretical quantum advantages.
+A fundamental limitation of Fritz's proof of non-classicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
+     Some inequality constraints for the Triangle structure have been derived in previous works.
+For example, \citet{Steudel_2010} derived an inequality distinguishing the distributions compatible with the Triangle structure from those compatible with structures in which all the observable variables share a common latent ancestor.
+\citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}.
+Recently, \citet{Inflation} derived a variety of new polynomial causal compatibility inequalities for the Triangle structure.
+The inequalities of Ref.
+\cite{Inflation} are especially sensitive, in that they expose a distribution which had previously evaded detection as incompatible with the Triangle scenario as assessed by all formerly known constraints.
+     Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by quantum distribution.
+That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts.
+In \Cref{sec:preliminary_research} we report on attempts to utilize these inequalities to search for incompatible distributions that are also quantum-accessible.
+The subsequent failure of these approaches effectively motivates the remainder of this work.
+In summary, the Triangle structure is a desirable case study because it is known to admit nonclassical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions.
 This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.
@@
 
-    As was originally noticed by \citet{Fritz_2012}, it is possible to construct quantum distributions incompatible with the Triangle structure by utilizing quantum distributions incompatible with the familiar Bell structure.
-To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} and contrast it with the Bell structure of \cref{fig:bell_structure}.
+    As first realized by \citet{Fritz_2012}, one may construct quantum distributions incompatible with the Triangle structure by recasting quantum distributions incompatible with the familiar Bell structure into a settings-free tripartite format.
+To explain, imagine rearranging the Triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} so that it morely closely resembles the Bell structure of \cref{fig:bell_structure}.
 Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure.
-The crucial distinction is that the measurement settings $S_{\p{A}}, S_{\p{B}}$ are \textit{observable variables} in the Bell structure but become \textit{latent variables} in the Triangle structure.
-In order to embed distributions that are incompatible with the Bell structure into the Triangle structure, the latent nodes $S_{\p{A}}, S_{\p{B}}$ need to be observable and independent of the shared latent node $\la$.
-This can be accomplished by having $C$ ``measure'' the measurement settings $S_{\p{A}}, S_{\p{B}}$ and announce them as an outcome.
+The crucial distinction is that $S_{\p{A}}, S_{\p{B}}$ are random variable representing the recorded measurement \emph{settings} in the Bell structure whereas those $S_{\p{A}}, S_{\p{B}}$ are \emph{latent} variables in in the Triangle structure, which get reported as \textit{auxiliary outcomes} for Alice and Bob.
+
+    The analysis of nonclassicality changes, however, when $S_{\p{A}}, S_{\p{B}}$ are not freely chosen by the observers but rather by a process outside of the individual party's control.
+Relaxing the assumption of measurement independence opens up a possible loophole, namely the possibility that the auxiliary outcomes $S_{\p{A}}, S_{\p{B}}$ of Alice and Bob might be manipulated via dependence on their shared latent variable $\lambda$.
+We close this loophole by having the third party in the Triangle structure, Charlie, \emph{also} report the latent variables $S_{\p{A}}, S_{\p{B}}$ as a multivariate outcome.
+In this manner, the perfect correlation of $C$'s record of $S_{\p{A}}, S_{\p{B}}$ with the records of $S_{\p{A}}$ reported by $A$ and of $S_{\p{B}}$ reported by $B$ testifies to the independence of $S_{\p{A}}, S_{\p{B}}$ from $\lambda$.
 Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$~\cite{Fritz_2012}.
-There are numerous ways this can be accomplished, albeit we will focus on elucidating an exemplary method.
-
-    The \term{Fritz distribution}, denoted $\prob[\fritz]$, is a quantum-accessible distribution incompatible with the Triangle structure~\cite{Fritz_2012}.
-In the Fritz distribution, each of the variables $A,B,C$ have $4$ possible outcomes.
+
+    The exemplifying quantum distribution corresponding to a recasting of a nonclassical Bell structure distribution into the Triangle structure is the \term{Fritz distribution}~\cite{Fritz_2012}.
+In the Fritz distribution, denoted $\prob[\fritz]$, each of the variables $A,B,C$ is taken to have $4$ possible outcomes $\bc{0,1,2,3}$.
+It is convenient to represent the outcomes using two binary digits, $\bc{00,01,10,11}$.
 Explicitly, $\prob[\fritz]$ can be written as:
@@
     Here the notation $\prob[\fritz][abc] = \prob[\p{ABC}][abc] = \prob[][\p A\mapsto a,\p B\mapsto b,\p C\mapsto c]$ is used as shorthand.
-The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:quantum_model_triangle}~\cite{Fritz_2012}.
-The Fritz distribution is best visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}.
+The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:triangle_Qcompatibility}.
+     The Fritz distribution may be visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}.
 From this diagram, it can be seen that each of $\p{C}$'s outcomes restricts the possible outcomes for $\p A,\p B$ into a $2 \times 2$ block.
-If one writes the outcome labels $\bc{0,1,2,3}$ in binary $\bc{00,01,10,11}$, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by the outcome of $\p C$.
-Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits emulate the measurement settings $S_{\p A}$ and $S_{\p B}$ and the right-hand bits emulate a two-outcome measurement performed by $A, B$ as they would in~\cref{fig:bell_structure}.
-Specifically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.
+When expressing the outcomes as pairs of binary digits, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by (i.e.
+perfectly correlated with) the outcome of $\p C$.
+Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits $\p A_l$ and $\p B_l$ emulate the measurement settings $S_{\p A}$ and $S_{\p B}$, whereas the right-hand bits $\p A_r$ and $\p B_r$ emulate the outcomes which would be obtained by $A$ and $B$ back in the Bell structure of \cref{fig:bell_structure}.
+Critically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.
     \begin{figure}
@@
     \[ \ba{\p A_r \p B_r} = \prob[\p A_r \p B_r][00] + \prob[\p A_r \p B_r][11] - \prob[\p A_r \p B_r][01] - \prob[\p A_r \p B_r][10] \]
-    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the Triangle structure by performing a the following relabeling: $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}} \mapsto \p{A}_r, \p{B}_r, \p A_l, \p B_l$.
-As an example, the famous CHSH inequality~\cite{CHSH_Original} (\cref{eq:CHSH_ineq_orig}) constrains the correlation between the right-bits of $A$ and $B$,
-    \[ \ba{\p A_r \p B_r|\p C = 00} + \ba{\p A_r \p B_r|\p C = 01} + \ba{\p A_r \p B_r|\p C = 10} - \ba{\p A_r \p B_r|\p C = 11} \leq 2 \eq \label{eq:CHSH_intriangle} \]
-    Every compatible distribution $\prob[ABC]$ for which $C$ is perfectly correlated $A_l,B_l$ must satisfy \cref{eq:CHSH_intriangle}.
-Substituting the \cref{eq:fritz_dist} into \cref{eq:CHSH_intriangle} yields the maximal violation~\cite{Cirelson_1980}: $3 \br{1/\sqrt{2}} - \br{-1/\sqrt{2}} = 2\sqrt{2} \not \leq 2$.
-Therefore, we conclude the Fritz distribution is incompatible with the Triangle structure.
+    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the Triangle structure by performing the surjective relabeling:
+\begin{align*}
+    \p{A}_r\leftarrow \p{A}\,,\quad
+     \p{B}_r\leftarrow \p{B}\,,\quad
+     \p A_l\leftarrow S_{\p{A}}\,,\quad
+     \p B_l\leftarrow S_{\p{B}}\,,\quad
+     \p C_l\leftarrow S_{\p{A}}\,,\quad
+     \p C_r\leftarrow S_{\p{B}}\,.
+\end{align*}
+     As an example, the famous CHSH inequality~\cite{CHSH_Original} per \cref{eq:CHSH_ineq_orig} is translated into a constraint on the correlation between the right-bits of $A$ and $B$,
+    \[ \ba{\p A_r \p B_r|\p C = 00} + \ba{\p A_r \p B_r|\p C = 01} + \ba{\p A_r \p B_r|\p C = 10} - \ba{\p A_r \p B_r|\p C = 11} \leq 2 \eq \label[ineq]{eq:CHSH_intriangle} \]
+    Every compatible distribution $\prob[ABC]$ \emph{for which $C$ is perfectly correlated with $A_l,B_l$} must satisfy \cref{eq:CHSH_intriangle}.
+Substituting $\prob[\fritz]$ into \cref{eq:CHSH_intriangle} yields the traditional maximal quantum violation~\cite{Cirelson_1980}: $3 \br{1/\sqrt{2}} - \br{-1/\sqrt{2}} = 2\sqrt{2} \not \leq 2$.
+%Therefore, we conclude the Fritz distribution is incompatible with the Triangle structure.
 Before continuing it is worth noting that \cref{eq:fritz_dist} is non-unique.
@@
 
-    It is important to understand the domain in which Fritz's proof of incompatibility is valid; the details of which can found in the original work~\cite{Fritz_2012}.
-Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequality for the Triangle structure if there exists perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$.
-As a result, the incompatibility proof employed by Fritz is not applicable to any distribution that significantly deviates from the Fritz distribution presented above.
-For example, if one combines \cref{eq:fritz_dist} with more and more uniform noise, at what point does the resultant distribution transition from incompatibility to compatibility?
+    It is important to understand the domain in which Fritz's proof of incompatibility is valid.
+%the details of which can found in the original work~\cite{Fritz_2012}.
+Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequality for the Triangle structure if there exists
+    The proof relies on the perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$.
+For example, if one combines \cref{eq:fritz_dist} with slight uniform noise, what can we say with confidence regarding if the resulting modified distribution is classical or not?
+At what point does the resultant distribution transition from incompatibility to compatibility?
 This question is partially answered in \cref{sec:noise}.
 
-    Upon reflection, the Fritz distribution can be considered \textit{manufactured}.
-The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of entanglement resources made accessible by quantum mechanics.
-Therefore, it is desirable to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure.
-Pursuant to this, \citet{Fritz_2012} presented the following problem~\cite[Problem 2.17]{Fritz_2012}:%TODO figure out best way to link to this problem
+    Plainly $\prob[\fritz]$ is a valid but \textit{manufactured} example.
+The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of nonclassical resources made accessible by quantum mechanics.
+The goal, therefore, is to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure \cite{Gisin_2017}.
+Recognizing this, \citet{Fritz_2012} presented the following problem~\cite[Problem 2.17]{Fritz_2012}:%TODO figure out best way to link to this problem
 
@@
 
-    Fritz's problem is concerned with how to find and recognize non-classical quantum distributions specifically for the Triangle structure.
-In \cite{Fritz_2012}, Fritz proves the Fritz distribution is non-classical by \textit{recycling} Bell's theorem.
-Being limited by the requirement of perfect correlations and the reliant on Bell's theorem, Fritz's methods are problematic if one hopes to find new quantum resources for the Triangle structure.
-The remainder of this paper focuses on our advancement toward solving Fritz's Problem.
-\Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem.
-Afterwards, \Cref{sec:found_inequalities} reports the discovery of new causal compatibility inequalities wish are capable of proving the non-classicality of Fritz's distribution.
-Finally, \Cref{sec:conclusions} concludes by outlining our resolution to Fritz's problem and mentioning areas for future research.
+    Fritz's problem is concerned with how to find and recognize nonclassical quantum distributions specifically for the Triangle structure.
+The original proof of nonclassicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations\cite{Fritz_2012}.
+Fritz's problem, as originally stated, does not require that the \emph{type} of non-classicality be novel to the Triangle structure; rather, only that the proof should avoid Bell's theorem.
+\Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem; \Cref{sec:found_inequalities} reports our eventual success, via the discovery of new causal compatibility inequalities.
+
+     Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly novel form of nonclassicality for the Triangle structure.
+Such a discovery would presumably lead to an understanding of new advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open.
+We attempt to make progress on this problem by leveraging the the new causal compatibility inequalities derived herein, but this effort was plagued by instabilities in our numerical optimization which we have not yet overcome.
+\Cref{sec:conclusions} discusses these challenges, suggesting concrete targets for future research.
+\Cref{sec:conclusions} also considers how to best contrast non-classicality across differing causal structures.
 
@@
 
-    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}.
-Unfortunately, none of these inequalities could be violated.
-Furthermore, none of these inequalities were violated by any 2-outcome coarse-graining of the Fritz distribution.
-These early results suggest, although do not prove, that quantum non-classicality does not exist in the Triangle structure for \textit{two-outcome} measurements.
-Therefore, it is conjectured that all quantum non-classical distributions in the Triangle structure must utilize more than two outcomes in at least one variable.
-Pursuant to this conjecture, this work expands the search for quantum-accessible incompatibility in Triangle structure by increasing the cardinality of outcomes.
-
-    Moreover, the existence of the Fritz distribution (\cref{sec:fritz_distribution}) directly demonstrates that quantum-accessible incompatibility exists in the Triangle structure and indirectly proves the existence of causal compatibility inequalities capable of witnessing the non-classicality of the Fritz distribution.
+    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the previously-published compatibility inequalities of Ref.~\cite{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014} (which had also been investigated numerically independently by \citet{Weilenmann_2016}).
+This preliminary investigation did not yield interesting solutions, as none of those inequalities were violated by any 2-outcome coarse-graining of the Fritz distribution.
+These early results suggest that there is no quantum-classical gap in the Triangle structure for \textit{two-outcome} measurements, i.e.
+\cref{eq:triangle_compatibility} and \cref{eq:triangle_Qcompatibility} define identical sets of binary-outcome tripartite distributions.
+
+     Operating under the assumptions that all quantum \emph{non}-classical distributions in the Triangle structure must utilize more than two outcomes in at least one variable, this work expands the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.
+
+%    Moreover, the existence of the Fritz distribution (\cref{sec:fritz_distribution}) directly demonstrates that quantum-accessible incompatibility exists in the Triangle structure and indirectly proves the existence of causal compatibility inequalities capable of witnessing the non-classicality of the Fritz distribution.
 The Inflation Technique has been shown to completely solve the classical causal inference problem~\cite{Navascues_2017} --- indicating that these undiscovered inequalities can be generated using sufficiently complex inflations.
@@
 
-    These incipient insights were sufficient for focusing the search for new inequalities sensitive enough to be violated by the Fritz distribution.
-\Cref{sec:found_inequalities} reports the discovery of these inequalities which expand on our understanding of non-classicality in the Triangle structure.
+%    These incipient insights were sufficient for focusing the search for new inequalities sensitive enough to be violated by the Fritz distribution. \
+%    Cref{sec:found_inequalities} reports the discovery of these inequalities which expand on our understanding of non-classicality in the Triangle structure.
 As a by-product, this research illuminates the advantage in using the Inflation Technique to find inequalities for interesting causal structures in general.
@@
 
-    \Cref{sec:causal_compatibility} defined causal compatibility inequalities while \cref{sec:fritz_distribution} recalled and discussed the Fritz distribution together with a brief summary of its incompatibility with the Triangle structure.
+    \Cref{sec:causal_compatibility} introduced the notion of causal compatibility inequalities, and \cref{sec:fritz_distribution} discussed the Fritz distribution ($\prob[\fritz]$) together with the initial inequality-free proof of its incompatibility with the Triangle structure.
 Heretofore, there were no known causal compatibility inequalities for the Triangle structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}.
 By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle structure that are violated by the Fritz distribution.
-A representative sample of these inequalities are presented here.
+A representative trio of these $\prob[\fritz]$-incompatability-witnessing inequalities are presented here: $I\tsb{WagonWheel}$ per \cref{eq:ww_ineq_symplified}, notable for its simplicity; $I\tsb{Web}$ per \cref{eq:web_inequality}, which best witnesses the non-clasicality of $\prob[\fritz]$ in the presence of noise; and $I\tsb{SymmetricWeb}$ per \cref{eq:symmetric_web_inequality}, which is symmetric with respect to all permutations of the three parties.
+
     The methods used to derive these inequalities are largely based on the Inflation Technique~\cite{Inflation}.
 A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:main_appendix} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.
-
+    We emphasize that each of these causal compatibility inequalities independently provides a positive resolution of Fritz's problem.
+The inequalities are derived without making use of Bell's theorem; rather, they follow from the Inflation Technique's broader perspective on non-classicality as a special case of causal inference.
+
+\subsection{The WagonWheel Inequality}
     The first causal compatibility inequality chosen for presentation is reported below:
@@
     \begin{gathered}
-    \eq\label{eq:ww_ineq}
+    \eq\label[ineq]{eq:ww_ineq}
     I\tsb{WagonWheel} : \\
@@
     \end{equation*}
-    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it.
+    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it.
 To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:main_appendix_main_summary,sec:deriving_inequalities_from_the_inflation_technique}.
-
-    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure (i.e.
-factorizes according to \cref{eq:triangle_compatibility}) must satisfy $I\tsb{WagonWheel}$.
-As a demonstration, the first term in \cref{eq:ww_ineq} for the Fritz distribution is $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ while all of the remaining terms sum to $\simeq 0.0136$.
-Therefore, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $0.0129\ldots \not \leq 0$.
-Consequently we conclude that the Fritz distribution is incompatible with the Triangle structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.
+Aside from increasing outcome cardinality, we are also forced to consider larger inflations than those analyzed in Ref.~\cite{Inflation}.
+This is because we found the smaller inflations considered there --- such as the Spiral inflation depicted in \cref{fig:spiral_inflation} --- were simply \textit{unable} to witness the incompatibility of the Fritz distribution, even when analyzed explicitly using four possible outcomes for every observable variable.
+
+    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure per \cref{eq:triangle_compatibility} must satisfy $I\tsb{WagonWheel}$.
+On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $0.0129 \not \leq 0$\footnote{To aid verification: the first term in \cref{eq:ww_ineq} for the Fritz distribution is $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ while all of the remaining terms sum to $\simeq 0.0136$.}.
+Consequently we affirm that the Fritz distribution is incompatible with the Triangle structure, a fact previously only demonstrated without inequalities.
 
@@
     \begin{gathered}
-    \eq\label{eq:ww_ineq_symplified}
+    \eq\label[ineq]{eq:ww_ineq_symplified}
     I\tsb{WagonWheel} : \\
@@
 
-    In order to understand the importance of $I\tsb{WagonWheel}$, there are a couple of important concepts to understand.
+%   In order to understand the importance of $I\tsb{WagonWheel}$, there are a couple of important concepts to understand.
 First, the Fritz distribution was originally known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings $A_l, B_l$.
@@
 
-    In addition to $I\tsb{WagonWheel}$, numerous independent inequalities were derived for the Triangle structure that are violated by the Fritz distribution.
-The majority of these inequalities share most or all of the qualitative features of $I\tsb{WagonWheel}$, and hence those inequalities are omitted from this manuscript.
-Instead, we present $I\tsb{Web}$ (\cref{eq:web_inequality}), another causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was produced using the Web inflation (\cref{fig:the_web_inflation}) --- a considerably larger inflation than the Wagon-Wheel inflation.
-Note that in \cref{eq:web_inequality} $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
-
-    \begin{equation}
-    \label{eq:web_inequality}
-    \begin{gathered}
-        I\tsb{Web} : \\
+    %    The majority of these inequalities share most or all of the qualitative features of $I\tsb{WagonWheel}$, and hence those inequalities are omitted from this manuscript.
+\subsection{The Web Inequality}
+\label{sec:noise}
+\label{sec:violations_noise}
+     We next present \cref{eq:web_inequality}, another causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution.
+The Web inflation shown in \cref{fig:the_web_inflation} was used to produce the eponymous $I\tsb{Web}$ per \cref{eq:web_inequality}.
+The Web inflation being considerably larger than the Wagon-Wheel inflation of \cref{fig:wagon_wheel_inflation}, it is computationally more demanding to work with, but the Web inflation is capable of yielding strictly stronger inequalities.
+For brevity, we employ the shorthand $\prob\br{abc}$ in lieu of $\prob[ABC]\br{abc}$ in presenting \cref{eq:web_inequality}.
+
+    \begin{gather}
+    \label[ineq]{eq:web_inequality}
+        I\tsb{Web} : \\\nonumber
         \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
-    \end{gathered}
-    \end{equation}
-
-    The inequalities presented above, namely $I\tsb{WagonWheel}$ and $I\tsb{Web}$, were curated to demonstrate the incompatibility of the Fritz distribution in particular.
-To reiterate, the Fritz distribution is incompatible with the Triangle structure because it assigns a unique role to one of the variables, specifically $C$.
-The asymmetry within the Fritz distribution is reflected in the asymmetry of $I\tsb{WagonWheel}$ and $I\tsb{Web}$.
-In order to discover new forms of non-classicality in the Triangle structure, it is desirable to obtain measures of non-classicality, such as inequalities, that do not admit this bias.
-In an effort to find a causal compatibility inequality qualitatively distinct from $I\tsb{WagonWheel}$ or $I\tsb{Web}$, we developed a technique to derive inequalities with certain symmetry properties such as \cref{eq:symmetic_web_inequality} which is symmetric with respect to any permutation of the variables $A, B, C$.
-These techniques are explained in \cref{sec:symmetric_inequalities}.
-Surprisingly, \cref{eq:symmetic_web_inequality} is also violated by the Fritz distribution.
-    \begin{equation}
-        \label{eq:symmetic_web_inequality}
-    \begin{gathered}
-        I\tsb{SymmetricWeb} : \\
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
-    \end{gathered}
-    \end{equation}
-    Note that $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for a sum the over permutations of $A,B,C$, i.e.
-$\bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033)$.
-
-    Most importantly, these causal compatibility inequalities are a positive resolution of Fritz's problem from \cref{sec:fritz_distribution}.
-These inequalities are derived without making use of Bell's theorem and instead uses the Inflation Technique to approach non-classicality from a more universal causal inference perspective.
-
-    \section{Numerical Optimizations \& Noisy Distributions}
-    \label{sec:violations_noise}
-    Causal compatibility inequalities, including those derived in \cref{sec:found_inequalities}, offer an avenue into studying quantum non-classicality.
-Ultimately, the motivation for finding these inequalities is binary: the first is to classify differing distributions by their compatibility with a given causal structure, and the second is to measure the degree in which a given distribution is non-classical.
-This approach has been well-studied in the Bell structure, where extremal non-classical correlations maximally violate Bell inequalities~\cite{PR_1995}.
-However, inequalities are just a singular example of numerous distinct measures of non-classicality~\cite[Section 5]{Vicente_2014}.
-Alternatives include measuring the non-local content, robustness to noise, or even the classical simulation cost of a given distribution.
-For previously studied causal structures, such as the Bell structure, there exists a uncertainty toward which measure of non-classicality is best.
-The inequalities derived in this report are likely \textit{not} the best measures of non-classicality because they have be curated toward the Fritz distribution.
-Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure to be found that admit quantum violations.
-In this section, two measures are used that make use of these compatibility inequalities: robustness to noise and direct numerical violation.
-
-    To compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ into the format of \cref{eq:ww_ineq,eq:web_inequality,eq:symmetic_web_inequality} where the linear combination of all terms is upper-bound by $0$.
-For each inequality $I$ and distribution $\prob$, $I\br{\prob}$ denotes the numerical value associated with this upper-bound.
-Correspondingly, $I\br{\prob} > 0$ indicates violation of $I$ while $I\br{\prob} \leq 0$ indicates satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
-
-    \subsection{Noisy Distributions}
-    \label{sec:noise}
+    \end{gather}
+
+% \subsection{Noisy Distributions}
+
     % \begin{figure}
@@
     % \end{figure}
-    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality.
-As was mentioned in \cref{sec:fritz_distribution}, this embedding required an idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$.
-From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}.
-It is possible to minimize noise by developing more accurate measurement channels but perfect correlations are too idealistic.
-Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.
-
-    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$\footnote{The completely noisy observation is compatible with the Triangle structure}.
-The objective of this section is to quantify how much statistical noise can be added to the Fritz distribution $\prob[\fritz]$ before the reported inequalities fail to witness incompatibility.
+As mentioned in \cref{sec:fritz_distribution}, this original proof of the non-classicality of $\prob[\fritz]$ required an idealistic condition to hold: perfect correlations of $C$ with $A_l, B_l$.
+It is impossible to use Fritz's original argument to confirm non-classicality from an experimental point of view, because every laboratory-achievable distribution is subject to some amount of \text{noise}.
+One can minimize noise.
+e.g.
+by developing high-accuracy measurement channels, but \emph{perfect} correlations are unattainable.
+Causal compatibility inequalities such as  $I\tsb{Web}$ permit there to be noise within a set of observations before the ability to certify non-classicality breaks down.
+
+Here we quantify how much statistical noise can be added to the Fritz distribution $\prob[\fritz]$ before $I\tsb{Web}$ fails to witness incompatibility; we define the \term{$\vep$-noisy Fritz distribution} as
+\begin{align}\begin{split}
+\s{N}_{\vep} &= \br{1 - \vep} \prob[\fritz] + \vep \s{U}_{ABC}\\
+&\text{where}\\
+\s{U}_{ABC}\br{abc} &\equiv \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}\,.
+\end{split}\end{align}
+%
+%The uniform-noise probability distribution is defined for three parties and four outcomes as $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} \equiv \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$\footnote{The completely noisy observation is compatible with the Triangle structure}.
+Here we quantify how much statistical noise can be added to the Fritz distribution $\prob[\fritz]$ before $I\tsb{Web}$ fails to witness incompatibility.
 The associated quantifier used was an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ where $\s{N}_{\vep}$ denotes an \term{$\vep$-noisy Fritz distribution},
-    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
-    As $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$.
-Our tests suggest that $I\tsb{Web}$ is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to a noise parameter of $\vep \simeq 0.085$.
-The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}.
+%    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
+%   
+As $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}_{ABC}$.
+We find that $I\tsb{Web}$ demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to a noise parameter of $\vep \simeq 0.085$; the associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}.
 Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I\tsb{Web}$; an exhaustive search has not been conducted.
@@
 
-    \subsection{Numerical Optimizations}
-    \label{sec:optimizations}
-
-    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure (\cref{fig:triangle_structure}) and thus expressed as follows:
+\subsection{The Symmetric Web Inequality}
+    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies --- seeking violations --- towards the desired end-goal of discovering new forms of non-classicality in the Triangle structure.
+Of course, if some inequality achieves its optimal quantum violation on a distribution qualitatively similar to $\prob[\fritz]$, then such an inequality is unlikely to lead us to discover non-classicality of a type different than $\prob[\fritz]$.
+Indeed, we will show that the previous pair of $I\tsb{WagonWheel}$ and $I\tsb{Web}$, which were both specifically curated to demonstrate the incompatibility of $\prob[\fritz]$, apparently achieve maximum quantum violation on distribution very similar to $\prob[\fritz]$ itself.
+    To avoid the chasing our own tail in the numerical optimization we require an objective function which is \emph{not} tailor-designed to witness $\prob[\fritz]$.
+Finding such an inequality proved extremely challenging: While we could generate thousands of inequalities using the Inflation Technique~\cite{Inflation}, it appeared than only a vanishingly-small fraction of those inequalities admitted quantum violation whatsoever.
+We therefore modified the Inflation Technique to give us an inequality which both witnesses the non-classicality of $\prob[\fritz]$ but which is also symmetric with respect to any permutation of the variables $A, B, C$, resulting in \cref{eq:symmetric_web_inequality}.
+The modification of the Inflation Techniques which forces symmetry is explained in \cref{sec:symmetric_inequalities}.
+As $\prob[\fritz]$ is strongly assymetric due to the special role of $C$, we can hope that a symmetric inequality (even one which does witness $\prob[\fritz]$) might achieve its \emph{optimal} quantum violation on a distribution qualitative distinct from $\prob[\fritz]$.
+The details of our numerical finding are discussed in \cref{sec:optimizations}.
+
+%    To reiterate, the Fritz distribution is incompatible with the Triangle structure because it assigns a unique role to one of the variables, specifically $C$.
+The asymmetry within the Fritz distribution is reflected in the asymmetry of $I\tsb{WagonWheel}$ and $I\tsb{Web}$.
+In order to discover new forms of non-classicality in the Triangle structure, it is desirable to obtain measures of non-classicality, such as inequalities, that do not admit this bias.
+In an effort to find a causal compatibility inequality qualitatively distinct from $I\tsb{WagonWheel}$ or $I\tsb{Web}$, we developed a technique to derive inequalities with certain symmetry properties such as \cref{eq:symmetric_web_inequality} which is symmetric with respect to any permutation of the variables $A, B, C$.
+These techniques are explained in \cref{sec:symmetric_inequalities}.
+Surprisingly, \cref{eq:symmetric_web_inequality} is also violated by the Fritz distribution.
+
+    \begin{gather}
+        \label[ineq]{eq:symmetric_web_inequality}
+        I\tsb{SymmetricWeb} : \\\nonumber
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
+    \end{gather}
+
+    Note that $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for a sum the over permutations of $A,B,C$, i.e.
+$\bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033)$.
+
+    \section{Numerical Optimization}\label{sec:optimizations}
+
+%    Causal compatibility inequalities, including those derived in \cref{sec:found_inequalities}, offer an avenue into studying quantum non-classicality.
+Ultimately, the motivation for finding these inequalities is binary: the first is to classify differing distributions by their compatibility with a given causal structure, and the second is to measure the degree in which a given distribution is non-classical.
+This approach has been well-studied in the Bell structure, where extremal non-classical correlations maximally violate Bell inequalities~\cite{PR_1995}.
+However, inequalities are just a singular example of numerous distinct measures of non-classicality~\cite[Section 5]{Vicente_2014}.
+Alternatives include measuring the non-local content, robustness to noise, or even the classical simulation cost of a given distribution.
+For previously studied causal structures, such as the Bell structure, there exists a uncertainty toward which measure of non-classicality is best.
+The inequalities derived in this report are likely \textit{not} the best measures of non-classicality because they have be curated toward the Fritz distribution.
+Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure to be found that admit quantum violations.
+In this section, two measures are used that make use of these compatibility inequalities: robustness to noise and direct numerical violation.
+
+%    To compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ into the format of \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality} where the linear combination of all terms is upper-bound by $0$.
+For each inequality $I$ and distribution $\prob$, $I\br{\prob}$ denotes the numerical value associated with this upper-bound.
+Correspondingly, $I\br{\prob} > 0$ indicates violation of $I$ while $I\br{\prob} \leq 0$ indicates satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
+
+    %\subsection{Numerical Optimizations}
+
+    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure [\cref{fig:triangle_structure}] and thus expressed as follows:
     \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
-    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately.
+    where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately.
 In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
 In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
-Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states which are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix.
+Motivated by the fact that the Fritz distribution [\cref{sec:fritz_distribution}] only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states which are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix.
 Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
@@
     % \end{figure}
-
-    % \subsection{Numerical Optimization Results}
+%    An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization.
+Above, it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
+Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to saturating $I\tsb{Web}$ instead of violating it.
+We observed that only parameters close enough to the \textit{Fritz parameters} (i.e.
+parameters that induce the Fritz distribution) were able to achieve violation of $I\tsb{Web}$.
+
+    Since the inequalities we seek to optimily violate are polynomial, and since the space of quantum-accessible distributions is non-convex, we employ a number of optimization methods consecutivey in an attempt to avoid pitfalls associated with local minima or ill-conditioned convergence.
+Specifically, the BFGS method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
+
+    Nevertheless, we strongly caution against misinterpreting the numerical optima present in \cref{sec:optima} as if our findings represent genuine global-maxima of violation.
+Evidence for the unreliability of our numerical methods is the following: when supplied with randomly sampled initial parameters, \emph{all} optimization methods consistently converged to \emph{saturating} the target inequalities, instead of violating it!
+This, even though we \emph{know} that all the inequalities we consider \emph{do} admit quantum violation, namely by  $\prob[\fritz]$.
+To achieve inequality violation, we found ourselves forced to seed the numerical method with initial  parameters such that the initial point of the optimization was close to  $\prob[\fritz]$.
+
+  The fact that the \emph{final} points of optimization as returned by our numerical methods are invariably also close to $\prob[\fritz]$ makes interpreting the results somewhat murky.
+Could it be that the inequality's global maximum is, in-fact, not far from $\prob[\fritz]$?
+Or is this a limitation of the ill-conditioned nature of the optimization?
+The phenomena is likely due to a combination of both effects.
+
+    %   Despite our varied efforts, it remains unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
+More likely, this phenomena is due to a combination of both effects.
+
+    \subsection{Numerical Optimization Results}\label{sec:optima}
 
@@
             \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
-            \caption{Probability distribution that maximizes violation of $I\tsb{Web}$ ($V_F \simeq 1.501$).}
+            \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{Web}$.
+Notice that this distribution has precisely the same possibilistic structure as the Fritz distribution, as might be expected, since $I\tsb{Web}$ was specifically generated to witness the non-classicality of $\prob[\fritz]$.}
             \label{fig:maximum_violation_I_1}
@@
             \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
-            \caption{Probability distribution that maximizes violation of $I\tsb{SymmetricWeb}$ ($V_F \simeq 2.61$).}
+            \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{SymmetricWeb}$.
+Notice that this distribution has precisely the same (assymetric!) possibilistic structure as the Fritz distribution, even though $I\tsb{SymmetricWeb}$ itself is symmetric with respect to permutations of the variables $A, B, C$.
+}
             \label{fig:maximum_violation_I_3}
@@
     \end{figure}
-    \begin{figure}
-    \begin{nscenter}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
-            \caption{Symmetrized version of the Fritz distribution ($V_F \simeq 3$).}
-            \label{fig:symmetrized_fritz}
-    \end{nscenter}
-    \end{figure}
-
-    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
+%    \begin{figure}
+%    \begin{nscenter}
+%            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
+%            \caption{An artificially-symmetrized version of the Fritz distribution, constructed by averaging the six permutations of $\prob[\fritz]$ over the variables $A, B, C$.
+While this construction significantly violates $I\tsb{SymmetricWeb}$, we have no reason to believe that this distribution should actually be achievable using quantum resources in the Triangle structure, so its role here is purely apophatic.}
+%            \label{fig:symmetrized_fritz}
+%    \end{nscenter}
+%    \end{figure}
+
+    %To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
 $V_F \defined \max_{P}\bc{I\br{P}/I\br{P_F}}$.
-The first inequality in consideration is $I\tsb{Web}$.
-At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$.
-Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution.
-In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure}, i.e.
-the same set of possible events.
-This result is not entirely unexpected.
-As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure.
-Consequently, it seems that $I\tsb{Web}$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution closely.
-
-    An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization.
-Above it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
-Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to inequality \textit{saturation} instead of inequality \textit{violation}.
-Instead, it was observed that only parameters close enough to the \textit{Fritz parameters} (i.e.
-any non-unique set of parameters that induce the Fritz distribution) were able to achieve violation.
-Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence.
-Specifically, the BFGS method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
-Despite our varied efforts, it remains unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
-More likely, this phenomena is due to a combination of both effects.
-
-    It is also worth reporting that the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:quantum_model_triangle} are restricted to maximally entangled states.
-This result resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} which demonstrates that entanglement and non-classicality are different resources.
+    Our best numerical optimization of $I\tsb{WagonWheel}$ was found to be the Fritz distribution itself, visualized in \cref{fig:fritz_distribution_visualized}.
+$\prob[\fritz]$ is therefore either a local minimum of the parameter space or is in fact \textit{the} maximally violating distribution of $I\tsb{WagonWheel}$; it remains unclear to us if this behavior is related to the global optimality of the Fritz distribution, or if it's an artifact of the methods used to derive $I\tsb{WagonWheel}$, though we suspect the former.
+
+    Our best numerical optimization of $I\tsb{Web}$ is visualized in\cref{fig:maximum_violation_I_1}.
+Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution; in fact \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share their \term{possibilistic structure}.
+A distribution's possibilistic structure is the unitization of its probabilities, i.e.
+the partitioning of events into disjoint subsets: one containing those events that occur with nonzero probability (possible), the other containing the zero-probability events (impossible).
+    That \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} have the same possibilistic structure is not entirely unexpected;  As was mentioned in \cref{sec:found_inequalities}, as $I\tsb{Web}$ was derived specifically to prove the incompatibility of the Fritz distribution with the Triangle structure.
+Consequently, it seems that $I\tsb{Web}$ best witnesses incompatibility of those distributions that closely resemble the $\prob[\fritz]$.
+It could be, however, that the sharing of possibilistic structure is an artifact of unreliable convergence, such that the true optimally-violating $I\tsb{Web}$ quantum distribution might have a different structure.
+
+    It is perhaps curious, however, that the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:quantum_model_triangle} are restricted to maximally entangled states.
+This distributions certainly violate $I\tsb{Web}$ more than $\prob[\fritz]$, even it is isn't the global maximum of $I\tsb{Web}$.
+This finding of more-violation with less-entanglement resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} demonstrating that entanglement and non-classicality are different resources.
 
@@
 
-    The second inequality in consideration is the \textit{symmetric} inequality $I\tsb{SymmetricWeb}$.
-This inequality was able to achieve a greater relative violation than $I\tsb{Web}$ as optimizations converged to a distribution (\cref{fig:maximum_violation_I_3}) with relative violation $V_F \simeq 2.61$.
-Just as before, the maximum violating distribution shares a possibilistic structure with the Fritz distribution.
-However, this result is far more surprising.
-Since the inequality is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well.
-If it were not, one could construct a distribution that violates $I\tsb{SymmetricWeb}$ further by symmetrizing $\prob[\fritz]$ (\cref{fig:symmetrized_fritz}) by normalizing over all possible permutations of $A,B,C$.
+   Our best numerical optimization of $I\tsb{SymmetricWeb}$ is visualized in \cref{fig:maximum_violation_I_3}.
+Counter-intuitively, this distribution --- which violates $I\tsb{SymmetricWeb}$ considerably better than $\prob[\fritz]$ --- \emph{still} shares its possibilistic structure with the Fritz distribution!
+Since $I\tsb{SymmetricWeb}$ is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well.
+Our numerical optimization, however, failed to find \emph{any} symmetric quantum distributions capable of violating $I\tsb{SymmetricWeb}$, not even violating it suboptimally than $\prob[\fritz]$.
+The \emph{only} violations of $I\tsb{SymmetricWeb}$ appear to be by assymetric distributions.
+
+%   If it were not, one could construct a distribution that violates $I\tsb{SymmetricWeb}$ further by symmetrizing $\prob[\fritz]$ (\cref{fig:symmetrized_fritz}) by normalizing over all possible permutations of $A,B,C$.
 This distribution is also non-classical with relative violation $V_F = 3$.
@@
 
-    Finally, the maximum relative violation of $I\tsb{WagonWheel}$ was found to be $V_F = 1$ (up to numerical precision), indicating that the Fritz distribution either represents a local minimum of the parameter space or is in fact \textit{the} maximally violating distribution.
-Without further investigations, it remains unclear if this behavior is related to the universality of the Fritz distribution or if its an artifact of the methods used to derive $I\tsb{WagonWheel}$.
-
     \section{Conclusions}
     \label{sec:conclusions}
-    In \cref{sec:triangle_structure}, we elucidated that compatibility in the Triangle structure has been an unsolved problem for nearly a decade.
-Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality.
+    In \cref{sec:triangle_structure}, we elucidated that establishing or rejecting compatibility with the Triangle structure has been a challenging problem for nearly a decade \cite{Steudel_2010,Branciard_2012,Henson_2014,Fritz_2012,Gisin_2017}.
+Though some causal compatibility inequalities were known, those inequalities did not appear useful for the purpose of witnessing quantum non-classicality.
+Recently,~\citet{Fritz_2012} gave the the first example of quantum non-classicality in the Triangle structure, relying on an inequality-free proof that is not robust to any amount of noise.
+
+ %   Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality.
 Afterwards,~\citet{Henson_2014} were able to to classify the Triangle structure as \textit{interesting} which partially explains why it remains an enigma.
@@
 
-    In \cref{sec:found_inequalities}, we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions.
-This result was made possible through extensive use of the Inflation Technique (\cref{sec:main_appendix}) applied to the Fritz distribution.
-In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
-    \begin{enumerate}[label=\textbf{FP.\Alph*}]
-        \setcounter{enumi}{0}
-        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
-    \end{enumerate}
-
-    Ultimately, this work accomplishes two important tasks.
+%        Using the Inflation technique, it became possible to provide a stronger proof of non-classicality than proposed by Fritz~\cite{Fritz_2012}.
+In particular, noisy variants of the Fritz distribution are provably non-classical (\cref{sec:noise}) and
+        In \cref{sec:found_inequalities} we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions.
+This result was made possible through the Inflation Technique \cref{sec:main_appendix} applied to the Fritz distribution.
+
+In \cref{sec:noise} we demonstrated that a causal compatibility inequalities is robust to noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's perfect-correlation example.
+In \cref{sec:optimizations} we found quantum distributions quantitatively distinct from the Fritz's recycled-Bell's-theorem example, such that these variant distribution more strongly violate certain causal compatibility inequalities.
+
+%In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
+%    \begin{enumerate}[label=\textbf{FP.\Alph*}]
+%        \setcounter{enumi}{0}
+%        \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
+%    \end{enumerate}
+
+%    Ultimately, this work accomplishes two important tasks.
 First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation Technique specifically for quantum causal inference problems.
@@
 Consequently, this work strongly indicates that the Inflation Technique has the potential to solve an assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
-Secondly, \cref{sec:noise} demonstrates that the derived causal compatibility inequalities are robust to varying degrees of noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's distribution (\cref{sec:fritz_distribution}) which relies on perfect (non-noisy) correlations.
-In conclusion \ref{r:1} has been positively solved through the derivation of the inequalities found in \cref{sec:found_inequalities}.
-
-    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}.
+Secondly,
+
+%    In spirit, however,Fritz's Problem is fundamentally concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}.
 When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state.
@@
 
-    \begin{enumerate}[label=\textbf{FP.\Alph*}]
-        \setcounter{enumi}{1}
-        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
-    \end{enumerate}
-
-    The question, as proposed by \ref{r:2}, is: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
+%    \begin{enumerate}[label=\textbf{FP.\Alph*}]
+%        \setcounter{enumi}{1}
+%        \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
+%    \end{enumerate}
+
+%    The question, as proposed by \ref{r:2}, is: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
 At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure.
@@
 
-    Using the Inflation technique, it became possible to provide a stronger proof of non-classicality than proposed by Fritz~\cite{Fritz_2012}.
-In particular, noisy variants of the Fritz distribution are provably non-classical (\cref{sec:noise}) and there exist quantum distributions quantitatively distinct from the Fritz distribution which admit greater numerical violations (\cref{sec:optimizations}).
-Despite these advancements, the distributions obtained closely resemble the Fritz distribution indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure.
-Currently, it remains speculative about how to recognize whether or not a given distribution for the Triangle structure exhibits non-classical correlations that maintain distinct qualitatively advantages from a resource perspective.
-One possibility is to extend \cref{r:2} to include the necessity of entanglement measurements.
+ Despite these advancements, the distributions we discovered hew closely to the Fritz distribution, indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure.
+Currently, it remains speculative about how to recognize whether-or-not a given distribution for the Triangle structure exhibits non-classical correlations of a fundamentally novel qualitative nature than Bell-type non-classicality.
+We imagine that advantages from a resource perspective might be critical to establish such a novelty signature.
+Perhaps another signature would be if the distribution can arise in the Triangle structure only through the use of of entangled measurements, such as perhaps the conjecture in Ref.
+\cite{Gisin_2017}.
 Ultimately, given any said classifier, it remains unclear whether or not such distributions even exist.
@@
 The authors are grateful to Miguel Navascués for drawing our attention to the existence of distributions genuinely requiring quantum resources for all latent nodes in the Triangle structure.
-Moreover, the authors credit Denis Rosset for suggesting a Fritz distribution variant involving a reduced cardinality of outcomes.
+Moreover, the authors are grateful to Denis Rosset for suggesting a Fritz distribution variant involving a reduced cardinality of outcomes.
     \end{acknowledgments}
@@
     \appendix
+    %\gdef\p@subsection{\thesection-}
 
@@
     \Cref{sec:main_appendix_main_summary} detailed how to obtain causal compatibility inequalities for any causal structure by constructing a marginal problem (see \cref{sec:marginal_satisfiability}) and supplying an incompatible distribution to generate an infeasibility certificate.
-In \cref{sec:found_inequalities}, a causal compatibility inequality symmetric under permutations of the variables $A,B,C$ was presented (see \cref{eq:symmetic_web_inequality}).
-This section aims to describe a general technique that can be used to derive inequalities exhibiting this symmetry.
+\cref{eq:symmetric_web_inequality} presented the causal compatibility inequality $I\tsb{SymmetricWeb}$ which is symmetric under permutations of the variables $A,B,C$.
+This section aims to describe a general technique that can be used to derive  $I\tsb{SymmetricWeb}$ and other inequalities also exhibiting this symmetry.
 In brief, this is accomplished by grouping marginal events $m \in \Events{\mscenario}$ of a marginal scenario $\mscenario$ into orbits under the action of variable permutations.
@@
     To clarify which symmetries we have in mind, first consider the marginal scenario $\mscenario = \bc{\bc{A, B, C}, \bc{C, D}, \bc{A, D}}$ where each variable in $\jointvar = \bc{A,B,C,D}$ has binary outcomes $\bc{0,1}$.
-Moreover, let $I_{\mscenario} \defined \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}$ be some inequality constraining the set of non-contextual marginal models $\prob^{\mscenario}$.
-Intuitively, the contextuality of a distribution $\prob[ABCD]$ should be \textit{independent} of the how one labels the variables in $\jointvar$.
-Suppose $\varphi \in \Perm{\jointvar}$\footnote{The permutation group $\Perm{S}$ over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} is a permutation of the variables $\jointvar$ such that $\varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$.
+${I_{\mscenario} \defined \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}}$ is an inequality constraining the set of non-contextual marginal models $\prob^{\mscenario}$.
+Now, the contextuality of a distribution $\prob[ABCD]$ should be \textit{invariant} under those permutations of the variable labels in $\jointvar$  which map the marginal scenario to itself; but not all variable relabellings preserve $\mscenario$.
+An example of a permutation which does \emph{not} preserve $\mscenario$ is the $\varphi \in \Perm{\jointvar}$\footnote{The permutation group $\Perm{S}$ over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} which acts like $\varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$.
+Then, the action of $\varphi$ on $I_{\mscenario}$ is
+%    Suppose $\varphi \in \Perm{\jointvar}$\footnote{The permutation group $\Perm{S}$ over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} is a permutation of the variables $\jointvar$ such that $\varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$.
 Intuitively $\varphi$ acts on $I_{\mscenario}$ in the following way,
@@
     \end{align*}
-    Following this example, it is always possible to permute the random variables in marginal scenario to produce new and valid inequalities.
+    which yields a vali-but-irrelevant inequality, as the resulting inequality no longer pertains to  $\mscenario$%.
 In general, permutations over $\jointvar$ can modify the marginal scenario $\varphi\bs{\mscenario} \defined \bc{\varphi\bs{V_1}, \ldots, \varphi\bs{V_k}} \neq \mscenario$; this was the case for the above example.
 Therefore $\varphi$ has capacity to modify both the terms of the inequality as well as the set of marginal models it constrains $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
+
     Permutations $\varphi$ that modify the marginal scenario have no application within the framework of the Inflation Technique (\cref{sec:main_appendix_main_summary}) because the Inflation Lemma only holds when the inflated inequality constrains injectable sets.
@@
 Using the symmetric incidence matrix and linear programing methods, an infeasibility certificate was found that is capable of witnessing the Fritz distribution.
-The corresponding deflated inequality is presented in \cref{sec:found_inequalities} as \cref{eq:symmetic_web_inequality}.
+The corresponding deflated inequality is presented in \cref{sec:found_inequalities} as \cref{eq:symmetric_web_inequality}.
 

### 2017-09-13 documents/TriangleScenarioArXiv/ts.tex
Made changes that were simply typos/easy fixes.

@@
 A sample of such inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality}.
-In \cref{sec:violations_noise} we quantify the robustness to noise of the Fritz distribution, and we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to seek out new new flavors of of non-classicality in the Triangle structure.
+In \cref{sec:violations_noise} we quantify the robustness to noise of the Fritz distribution, and we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to seek out new new flavors of non-classicality in the Triangle structure.
 Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.
@@
 
-    Henceforth, we will utilize a number of familial notions from graph theory and denote them accordingly.
+    Henceforth, we will utilize a number of familiar notions from graph theory and denote them accordingly.
 The \term{parents of a node} $n \in \nodes$ are all nodes which point directly into $n$, i.e.
@@
 For some causal structures, the equality constraints associated with it are sufficient to perfectly characterize the distributions genuinely compatible with it; for others, however, inequality constraints are also important.
-Causal structures for which inequality constraints are relevant have been termed \textit{interesting}~\cite{Henson_2014}, and such structures include the Instrumental structure, the Bell scenario, and the Triangle scenario studied here, among infinitely many others.
+Causal structures for which inequality constraints are relevant have been termed \textit{interesting}~\cite{Henson_2014}, and such structures include the Instrumental structure, the Bell structure, and the Triangle structure studied here, among infinitely many others.
     Herein we use the Inflation Technique~\cite{Inflation} to find causal compatibility inequalities; \Cref{sec:main_appendix} discusses the Inflation Technique as applied in this work.
 
-     probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals.
-We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons.
-Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure.
-Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.}.
-\Cref{sec:main_appendix} provides a brief discussion of existing techniques used to derive these inequalities.
-
-    If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}.
-Conversely, however, a singular inequality can only be used to prove that a given distribution is \textit{incompatible}; a single inequality cannot certify compatibility.
-A \textit{complete characterization} of compatibility consists of a complete set of all valid causal compatibility inequalities such that satisfaction of the entire set certifiescompatibility.
+    If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution is deemed \textit{incompatible}.
+Conversely, a singular inequality can only be used to prove that a given distribution is \textit{incompatible}; a single inequality cannot certify compatibility.
+A \textit{complete characterization} of compatibility consists of a complete set of all valid causal compatibility inequalities such that satisfaction of the entire set certifies compatibility.
 Currently however, it is unknown how to obtain a complete characterization for any given causal structure, including the Triangle structure.
@@
 The resulting observable correlations hence naturally form a conditional probability distribution $\prob[AB|S_AS_B]$.
-Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, this distribution is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that
+Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, this distribution is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that\footnote{Here the summation $\sum_{\la}$ is used to denote a statistical marginalization over the latent variable $\la$ with unspecified support.}
     %    there exists a distribution $\prob[AB|S_AS_B,\la]$ such that $\prob[AB|S_AS_B] = \sum_{\la} \prob[AB|S_AS_B,\la]$ and also satisfies the following implementation of \cref{eq:compatibility_as_factorization}:
     \begin{align}\label{eq:bellcompat}
- \prob \text{ is classically compatible with \cref{fig:bell_structure}} \quad\text{iff}\quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\,.
+     \prob \text{ is classically compatible with \cref{fig:bell_structure}} \quad\text{iff} \quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\,.
     \end{align}
+
     Any observed distribution $\prob[AB|S_AS_B]$ which fails to be explained by the classical causal hypothesis of the Bell structure as defined by \cref{eq:bellcompat} is appropriately termed non-classical.
@@
     The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities (such as the CHSH inequality \cref{eq:CHSH_ineq_orig} reproduced below) which constrain the correlations between binary variables $A$ and $B$ for classical distributions~\cite{CHSH_Original}.
-    \[ \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 0} + \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 1} + \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 0} - \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
+    \[ \ba{\p A\p B | S_{A} = 0, S_{B} = 0} + \ba{\p A\p B | S_{A} = 0, S_{B} = 1} + \ba{\p A\p B | S_{A} = 1, S_{B} = 0} - \ba{\p A\p B | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
     Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the non-classical nature of distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type.
@@
             \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
-            \caption{The Bell structure consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively.
-The shared hidden variable is labeled $\la$.}
+            \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared hidden variable is labeled $\la$.}
             \label{fig:bell_structure}
@@
     By contrast, the quantum distribution of the Triangle structure are defined with substantially greater freedom, namely
-     \[ \prob \text{ is a quantum distribution of \cref{fig:bell_structure}} \quad\text{iff}\quad\prob[ABC][abc] = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}}\,, \eq \label{eq:triangle_Qcompatibility} \]
-where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets, and $\netperm$ is a permutation matrix to align the states and measurements appropriately.
+    \[ \prob \text{ is a quantum distribution of \cref{fig:bell_structure}} \quad\text{iff}\quad\prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}}\,, \eq \label{eq:triangle_Qcompatibility} \]
+    where $\rho_{AB}, \rho_{BC}, \rho_{CA}$ are bipartite density matrices, $M_{A}, M_{B}, M_{C}$ are generic measurements sets, and $\netperm$ is a permutation matrix to align the states and measurements appropriately.
     %For certain causal structures, the conditional independence relations provided by $d$-separation relations are a sufficient characterization of compatibility.
 Recently, \citet{Henson_2014}, classified the Triangle structure as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the Triangle structure possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover,
-    The Triangle structure serves as an excellent test case for furthering our understanding of quantum nonclassicality in network causal structures.
+    The Triangle structure serves as an excellent test case for furthering our understanding of quantum non-classicality in network causal structures.
 It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
-     For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \citet{Fritz_2012,Inflation}, unlike for the Bell structure.
+    For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \cite{Fritz_2012,Inflation}, unlike for the Bell structure.
 The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
-     Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum nonclassicality.
+    Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality.
 It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicallity are expected to correspond to novel information-theoretical quantum advantages.
@@
 The inequalities of Ref.
-\cite{Inflation} are especially sensitive, in that they expose a distribution which had previously evaded detection as incompatible with the Triangle scenario as assessed by all formerly known constraints.
+\cite{Inflation} are especially sensitive, in that they expose a distribution which had previously evaded detection as incompatible with the Triangle structure as assessed by all formerly known constraints.
     Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by quantum distribution.
@@
         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational_fritz_bell}}
-        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{\p{A}},S_{\p{B}}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
+        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{A},S_{B}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
         \label{fig:triangle_structure_with_fritz_bell_embedded}
@@
 Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure.
-The crucial distinction is that $S_{\p{A}}, S_{\p{B}}$ are random variable representing the recorded measurement \emph{settings} in the Bell structure whereas those $S_{\p{A}}, S_{\p{B}}$ are \emph{latent} variables in in the Triangle structure, which get reported as \textit{auxiliary outcomes} for Alice and Bob.
-
-    The analysis of nonclassicality changes, however, when $S_{\p{A}}, S_{\p{B}}$ are not freely chosen by the observers but rather by a process outside of the individual party's control.
-Relaxing the assumption of measurement independence opens up a possible loophole, namely the possibility that the auxiliary outcomes $S_{\p{A}}, S_{\p{B}}$ of Alice and Bob might be manipulated via dependence on their shared latent variable $\lambda$.
-We close this loophole by having the third party in the Triangle structure, Charlie, \emph{also} report the latent variables $S_{\p{A}}, S_{\p{B}}$ as a multivariate outcome.
-In this manner, the perfect correlation of $C$'s record of $S_{\p{A}}, S_{\p{B}}$ with the records of $S_{\p{A}}$ reported by $A$ and of $S_{\p{B}}$ reported by $B$ testifies to the independence of $S_{\p{A}}, S_{\p{B}}$ from $\lambda$.
-Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$~\cite{Fritz_2012}.
+The crucial distinction is that $S_{A}, S_{B}$ are random variable representing the recorded measurement \emph{settings} in the Bell structure whereas those $S_{A}, S_{B}$ are \emph{latent} variables in in the Triangle structure, which get reported as \textit{auxiliary outcomes} for Alice and Bob.
+
+    The analysis of non-classicality changes, however, when $S_{A}, S_{B}$ are not freely chosen by the observers but rather by a process outside of the individual party's control.
+Relaxing the assumption of measurement independence opens up a possible loophole, namely the possibility that the auxiliary outcomes $S_{A}, S_{B}$ of Alice and Bob might be manipulated via dependence on their shared latent variable $\lambda$.
+We close this loophole by having the third party in the Triangle structure, Charlie, \emph{also} report the latent variables $S_{A}, S_{B}$ as a multivariate outcome.
+In this manner, the perfect correlation of $C$'s record of $S_{A}, S_{B}$ with the records of $S_{A}$ reported by $A$ and of $S_{B}$ reported by $B$ testifies to the independence of $S_{A}, S_{B}$ from $\lambda$.
+Consequently, any distribution over $A, B, S_{A}, S_{B}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{A}, S_{B}$~\cite{Fritz_2012}.
 
@@
     \end{align*}
-    Here the notation $\prob[\fritz][abc] = \prob[\p{ABC}][abc] = \prob[][\p A\mapsto a,\p B\mapsto b,\p C\mapsto c]$ is used as shorthand.
+    Here the notation $\prob[\fritz][abc] = \prob[ABC][abc] = \prob[][\p A\mapsto a,\p B\mapsto b,\p C\mapsto c]$ is used as shorthand.
 The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:triangle_Qcompatibility}.
     The Fritz distribution may be visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}.
-From this diagram, it can be seen that each of $\p{C}$'s outcomes restricts the possible outcomes for $\p A,\p B$ into a $2 \times 2$ block.
+From this diagram, it can be seen that each of $C$'s outcomes restricts the possible outcomes for $\p A,\p B$ into a $2 \times 2$ block.
 When expressing the outcomes as pairs of binary digits, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by (i.e.
@@
     \[ \ba{\p A_r \p B_r} = \prob[\p A_r \p B_r][00] + \prob[\p A_r \p B_r][11] - \prob[\p A_r \p B_r][01] - \prob[\p A_r \p B_r][10] \]
-    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the Triangle structure by performing the surjective relabeling:
+    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $A, B, S_{A}, S_{B}$ can be directly converted to an inequality for the Triangle structure by performing the surjective relabeling:
     \begin{align*}
-    \p{A}_r\leftarrow \p{A}\,,\quad
-     \p{B}_r\leftarrow \p{B}\,,\quad
-     \p A_l\leftarrow S_{\p{A}}\,,\quad
-     \p B_l\leftarrow S_{\p{B}}\,,\quad
-     \p C_l\leftarrow S_{\p{A}}\,,\quad
-     \p C_r\leftarrow S_{\p{B}}\,.
+        A_r\leftarrow A\,,\quad
+         B_r\leftarrow B\,,\quad
+         \p A_l\leftarrow S_{A}\,,\quad
+         \p B_l\leftarrow S_{B}\,,\quad
+         \p C_l\leftarrow S_{A}\,,\quad
+         \p C_r\leftarrow S_{B}\,.
     \end{align*}
@@
 The goal, therefore, is to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure \cite{Gisin_2017}.
-Recognizing this, \citet{Fritz_2012} presented the following problem~\cite[Problem 2.17]{Fritz_2012}:%TODO figure out best way to link to this problem
+Recognizing this, \citet{Fritz_2012} presented the following problem~\cite[Problem 2.17]{Fritz_2012}:
 
@@
     Fritz's problem is concerned with how to find and recognize nonclassical quantum distributions specifically for the Triangle structure.
-The original proof of nonclassicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations\cite{Fritz_2012}.
+The original proof of non-classicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations~\cite{Fritz_2012}.
 Fritz's problem, as originally stated, does not require that the \emph{type} of non-classicality be novel to the Triangle structure; rather, only that the proof should avoid Bell's theorem.
@@
 
-     Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly novel form of nonclassicality for the Triangle structure.
+    Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly novel form of non-classicality for the Triangle structure.
 Such a discovery would presumably lead to an understanding of new advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open.
@@
     % The majority of these inequalities share most or all of the qualitative features of $I\tsb{WagonWheel}$, and hence those inequalities are omitted from this manuscript.
+
     \subsection{The Web Inequality}
@@
     Here we quantify how much statistical noise can be added to the Fritz distribution $\prob[\fritz]$ before $I\tsb{Web}$ fails to witness incompatibility; we define the \term{$\vep$-noisy Fritz distribution} as
-\begin{align}\begin{split}
-\s{N}_{\vep} &= \br{1 - \vep} \prob[\fritz] + \vep \s{U}_{ABC}\\
-&\text{where}\\
-\s{U}_{ABC}\br{abc} &\equiv \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}\,.
-\end{split}\end{align}
+    \begin{align}
+        \begin{split}
+            \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U}_{ABC} \quad \text{where} \quad \s{U}_{ABC}\br{abc} \equiv \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}\,. \\
+        \end{split}
+    \end{align}
     %
@@
     % \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
-%   
-As $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}_{ABC}$.
+
+    As $\vep$ varies from $0$ to $1$, noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}_{ABC}$.
 We find that $I\tsb{Web}$ demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to a noise parameter of $\vep \simeq 0.085$; the associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}.
@@
     To avoid the chasing our own tail in the numerical optimization we require an objective function which is \emph{not} tailor-designed to witness $\prob[\fritz]$.
-Finding such an inequality proved extremely challenging: While we could generate thousands of inequalities using the Inflation Technique~\cite{Inflation}, it appeared than only a vanishingly-small fraction of those inequalities admitted quantum violation whatsoever.
+Finding such an inequality proved extremely challenging; while we could generate thousands of inequalities using the Inflation Technique~\cite{Inflation}, it appeared than only a vanishingly-small fraction of those inequalities admitted quantum violation whatsoever.
 We therefore modified the Inflation Technique to give us an inequality which both witnesses the non-classicality of $\prob[\fritz]$ but which is also symmetric with respect to any permutation of the variables $A, B, C$, resulting in \cref{eq:symmetric_web_inequality}.
@@
     In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure [\cref{fig:triangle_structure}] and thus expressed as follows:
-    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
-    where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately.
+    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \eq \label{eq:quantum_model_triangle}\]
+    where $\rho_{AB}, \rho_{BC}, \rho_{CA}$ are bipartite density matrices, $M_{A}, M_{B}, M_{C}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately.
 In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
 In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
-Motivated by the fact that the Fritz distribution [\cref{sec:fritz_distribution}] only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states which are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix.
+Motivated by the fact that the Fritz distribution [\cref{sec:fritz_distribution}] only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states which are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA}$ becomes an $n^6 \times n^6$ matrix.
 Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
-First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for generating incompatible quantum distributions in the Triangle structure.
+First,~\citet{Fritz_2012} demonstrates via the Fritz distribution that PVMs are sufficient for generating incompatible quantum distributions in the Triangle structure.
 Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$.
 Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
-    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]
+    \[ \prob[ABC]\br{abc} = \bramidket{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{A,a}m_{B,b}m_{C,c}} \eq \label{eq:quantum_model_triangle_pvms}\]
 
@@
 Analogously, $\exp\br{i P_n \lambda_{n,m}}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $\exp\br{iP_l \lambda_{l,l}}$ fixes the global phase of $\ket{l}$.
-Finally, although not explicitly mentioned in~\cite{Spengler_2010_Unitary}, it is possible to remove the reliance on the computationally expensive matrix exponential operations in \cref{eq:spengler_unitary}~\cite{Moler_2003}.
+Finally, although not explicitly mentioned in~\cite{Spengler_2010_Unitary}, it is possible to remove the reliance on the computationally expensive matrix exponential operations~\cite{Moler_2003} in \cref{eq:spengler_unitary} and replace them with elementary trigonomentric functions in the paramaters $\la_{m,n}$.
 
@@
 
-%In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
+    % In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
     % \begin{enumerate}[label=\textbf{FP.\Alph*}]
@@
     % \end{enumerate}
-
     % Ultimately, this work accomplishes two important tasks.
@@
 Colloquially, this problem is referred to as \term{the marginal problem}~\cite{Fritz_2011}.
-Additionally, this section aims to accomplish something further.
-If such as joint distribution $\prob[\jointvar]$ exists, how does one find it?
-Moreover, if a joint distribution does not exist, find an inequality that $\bc{\prob[V_1], \ldots, \prob[V_m]}$ fails which proves such a joint distribution does not exist.
+Additionally, this section aims to accomplish something further: If such as joint distribution $\prob[\jointvar]$ exists, how does one find it?
+If not, how does one find an inequality whose violation by $\bc{\prob[V_1], \ldots, \prob[V_m]}$ proves the non-existence of a joint distribution.
 This is accomplished by illustrating how the marginal problem can be expressed as a linear program in which the solution to the marginal problem is encoded in the feasibility or infeasibility of said linear program.
@@
 Strictly speaking, as defined by~\cite{Fritz_2011}, a marginal scenario forms an \textit{abstract simplicial complex} where it is required that all subsets of contexts are also contexts: $\forall V \in \mscenario, V' \subset V : V' \in \mscenario$.
-Throughout this section, we exclusively consider (without loss of generality) the \textit{maximal} marginal scenario; restricting our focus to the largest contexts in the marginal scenario.
+Throughout this section, we exclusively consider (without loss of generality) the \textit{maximal} marginal scenario; restricting our focus to the largest marginal contexts.
 Additionally, all marginal scenarios are taken to be \text{complete} in the sense that the marginal scenario covers the complete set of observable variables, i.e $\jointvar = \bigcup_{V \in \mscenario} V$.
@@
     } \eq \label{eq:example_incidence}\]
-    The incidence matrix needs to act (to the right) on a vector representing the joint probability $\prob[\jointvar]$ distribution and outputs a vector representing the marginal model $\prob^{\mscenario}$.
+    The incidence matrix acts (to the right) on a vector representing the joint probability $\prob[\jointvar]$ distribution and outputs a vector representing the marginal model $\prob^{\mscenario}$.
 The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector indexed by joint events $j \in \Events{\jointvar}$ whose entries are populated by the probabilities that $\prob[\jointvar]$ assigns to each joint event: $\probvec^{\jointvar}_j = \prob[\jointvar][j]$.
@@
 For bipartite qubit states, $\netperm$ is the $64\times64$ bit-wise matrix depicted in \cref{fig:perm_mtrx}.
-Upon examination of \cref{eq:quantum_model_triangle_pvms}, we consider $\netperm$ to be acting on the joint global state $\rho_{\p{AB}} \otimes \rho_{\p{BC}} \otimes \rho_{\p{CA}}$.
+Upon examination of \cref{eq:quantum_model_triangle_pvms}, we consider $\netperm$ to be acting on the joint global state $\rho_{{AB}} \otimes \rho_{{BC}} \otimes \rho_{{CA}}$.
 To illuminate its necessity, consider \cref{eq:quantum_model_triangle} in the absence of $\netperm$.
     % % \begin{align*}
-    % % \prob[\p{ABC}]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{\p{AB}} \otimes \rho_{\p{BC}} \otimes \rho_{\p{CA}}} \br{M^a_{\p{A}}\otimes M^b_{\p{B}} \otimes M^c_{\p{C}}}}\\
-    % % &= \Tr\bs{\br{\rho_{\p{AB}}M^a_{\p{A}}}\otimes\br{\rho_{\p{BC}}M^b_{\p{B}}}\otimes\br{\rho_{\p{CA}}M^c_{\p{C}}}}\\
-    % % &= \Tr\br{\rho_{\p{AB}}M^a_{\p{A}}}\Tr\br{\rho_{\p{BC}}M^b_{\p{B}}}\Tr\br{\rho_{\p{CA}}M^c_{\p{C}}}\\
-    % % &= \prob[\p{A}\mid \rho_{\p{AB}}]\br{a}\prob[\p{B}\mid \rho_{\p{BC}}]\br{b}\prob[\p{C}\mid \rho_{\p{CA}}]\br{c}
+    % % \prob[{ABC}]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{{AB}} \otimes \rho_{{BC}} \otimes \rho_{{CA}}} \br{M^a_{{A}}\otimes M^b_{{B}} \otimes M^c_{{C}}}}\\
+    % % &= \Tr\bs{\br{\rho_{{AB}}M^a_{{A}}}\otimes\br{\rho_{{BC}}M^b_{{B}}}\otimes\br{\rho_{{CA}}M^c_{{C}}}}\\
+    % % &= \Tr\br{\rho_{{AB}}M^a_{{A}}}\Tr\br{\rho_{{BC}}M^b_{{B}}}\Tr\br{\rho_{{CA}}M^c_{{C}}}\\
+    % % &= \prob[{A}\mid \rho_{{AB}}]\br{a}\prob[{B}\mid \rho_{{BC}}]\br{b}\prob[{C}\mid \rho_{{CA}}]\br{c}
     % % \end{align*}

### 2017-09-15 documents/TriangleScenarioArXiv/ts.tex
Final edits to the paper

@@
 Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion.
-In scenarios where all parties share a common resource, these non-classical correlations are also known as non-local correlations.
+In structures where all parties share a common resource, these non-classical correlations are also known as non-local correlations.
 Any constraint satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion.
@@
 More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood.
-Here we investigate one particular causal structure: the Triangle structure (\cref{fig:triangle_structure}).
+Here we investigate one particular correlation scenario named the Triangle structure (\cref{fig:triangle_structure}).
 
@@
 
-    \Cref{sec:main_appendix} briefly summaries the Inflation Technique in the specific context of this work.
-Although the summary presented here is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}.
+    \Cref{sec:inflation_technique_summary} briefly summaries the Inflation Technique in the specific context of this work.
+Although the summary presented in \Cref{sec:inflation_technique_summary} is designed to be self-standing, a much more pedagogical introduction is offered by the original work~\cite{Inflation}.
 \Cref{sec:deriving_inequalities} demonstrates how the Inflation Technique was used to derive the causal compatibility inequalities for the Triangle structure which admit violation by quantum-accessible distributions.
@@
 Causal structures for which inequality constraints are relevant have been termed \textit{interesting}~\cite{Henson_2014}, and such structures include the Instrumental structure, the Bell structure, and the Triangle structure studied here, among infinitely many others.
-    Herein we use the Inflation Technique~\cite{Inflation} to find causal compatibility inequalities; \Cref{sec:main_appendix} discusses the Inflation Technique as applied in this work.
+    Herein we use the Inflation Technique~\cite{Inflation} to find causal compatibility inequalities; \Cref{sec:inflation_technique_summary} discusses the Inflation Technique as applied in this work.
 
@@
 The resulting observable correlations hence naturally form a conditional probability distribution $\prob[AB|S_AS_B]$.
-Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, this distribution is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that\footnote{Here the summation $\sum_{\la}$ is used to denote a statistical marginalization over the latent variable $\la$ with unspecified support.}
+Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, $\prob[A|S_A,\la]$ is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that\footnote{Here the summation $\sum_{\la}$ is used to denote a statistical marginalization over the latent variable $\la$ with unspecified support.}
     %    there exists a distribution $\prob[AB|S_AS_B,\la]$ such that $\prob[AB|S_AS_B] = \sum_{\la} \prob[AB|S_AS_B,\la]$ and also satisfies the following implementation of \cref{eq:compatibility_as_factorization}:
     \begin{align}\label{eq:bellcompat}
-     \prob \text{ is classically compatible with \cref{fig:bell_structure}} \quad\text{iff} \quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\,.
+     \prob[AB|S_AS_B] \text{ is classically compatible with \cref{fig:bell_structure}} \quad\iff \quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\,.
     \end{align}
@@
 Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems.
-Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement operators $M_{A|S_A}, M_{B|S_B}$ with indices conditional upon the measurement settings, such that
+Concretely, a distribution is accessible with quantum resources and measurements for the quantumified Bell structure if and only if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension, as well as Hilbert-space-localized measurement sets $M_{A|S_A}, M_{B|S_B}$\footnote{Note that a measurement set $M_{A} = \bc{M_{A}^{1}, M_{A}^{2}, \ldots, M_{A}^{k}}$ services a shorthand notation in the following sense, $\prob[A] = \Tr\bs{\rho M_{A}} \implies \prob[A]\br{a} = \Tr\bs{\rho M_{A}^{a}}$.} with indices conditional upon the measurement settings, such that
     \begin{align}\label{eq:bellQcompat}
-    \prob \text{ is a quantum distribution of \cref{fig:bell_structure}} \quad\text{iff}\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
+    \prob[AB|S_AS_B] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}\,.
     \end{align}
-    The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities (such as the CHSH inequality \cref{eq:CHSH_ineq_orig} reproduced below) which constrain the correlations between binary variables $A$ and $B$ for classical distributions~\cite{CHSH_Original}.
-    \[ \ba{\p A\p B | S_{A} = 0, S_{B} = 0} + \ba{\p A\p B | S_{A} = 0, S_{B} = 1} + \ba{\p A\p B | S_{A} = 1, S_{B} = 0} - \ba{\p A\p B | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
-    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the non-classical nature of distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type.
+    The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions.
+A notable example is the CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original}.
+    \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
+    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the non-classical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type.
 Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.
@@
             \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
-            \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared hidden variable is labeled $\la$.}
+            \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
             \label{fig:bell_structure}
@@
             \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
-            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
+            \caption{The Triangle structure consisting of three observable variables $A,B,C$ and three latent variables $X, Y, Z$.}
             \label{fig:triangle_structure}
@@
     $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}, i.e.
-    \[ \prob \text{ is classically compatible with \cref{fig:triangle_structure}} \quad\text{iff}\quad\prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z]\,.
+    \[ \prob[ABC] \text{ is classically compatible with \cref{fig:triangle_structure}} \quad\iff\quad\prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z]\,.
 \eq \label{eq:triangle_compatibility} \]
-    By contrast, the quantum distribution of the Triangle structure are defined with substantially greater freedom, namely
-    \[ \prob \text{ is a quantum distribution of \cref{fig:bell_structure}} \quad\text{iff}\quad\prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}}\,, \eq \label{eq:triangle_Qcompatibility} \]
+    By contrast, the quantum realization of the Triangle structure are defined with substantially greater freedom, namely
+    \[ \prob[ABC] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}}\,, \eq \label{eq:triangle_Qcompatibility} \]
     where $\rho_{AB}, \rho_{BC}, \rho_{CA}$ are bipartite density matrices, $M_{A}, M_{B}, M_{C}$ are generic measurements sets, and $\netperm$ is a permutation matrix to align the states and measurements appropriately.
@@
     Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality.
-It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicallity are expected to correspond to novel information-theoretical quantum advantages.
+It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of non-classicallity are expected to correspond to novel information-theoretical quantum advantages.
 A fundamental limitation of Fritz's proof of non-classicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
@@
 \citet{Henson_2014} derived a family of entropic inequalities for the Triangle structure, which was the expanded somewhat by \citet{Weilenmann_2016}.
-Recently, \citet{Inflation} derived a variety of new polynomial causal compatibility inequalities for the Triangle structure.
-The inequalities of Ref.
-\cite{Inflation} are especially sensitive, in that they expose a distribution which had previously evaded detection as incompatible with the Triangle structure as assessed by all formerly known constraints.
-    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by quantum distribution.
+Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure.
+In particular, the inequalities of Ref.
+\cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is non-classical, it is also non-quantum.
+The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
+    Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution.
 That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts.
@@
 The subsequent failure of these approaches effectively motivates the remainder of this work.
-    In summary, the Triangle structure is a desirable case study because it is known to admit nonclassical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions.
+    In summary, the Triangle structure is a desirable case study because it is known to admit non-classical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions.
 This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.
@@
     As first realized by \citet{Fritz_2012}, one may construct quantum distributions incompatible with the Triangle structure by recasting quantum distributions incompatible with the familiar Bell structure into a settings-free tripartite format.
-To explain, imagine rearranging the Triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} so that it morely closely resembles the Bell structure of \cref{fig:bell_structure}.
+To explain, imagine rearranging the Triangle structure into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} so that it closely resembles the Bell structure (\cref{fig:bell_structure}).
 Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure.
@@
 
-    The exemplifying quantum distribution corresponding to a recasting of a nonclassical Bell structure distribution into the Triangle structure is the \term{Fritz distribution}~\cite{Fritz_2012}.
+    The exemplifying quantum distribution corresponding to a recasting of a non-classical Bell structure distribution into the Triangle structure is the \term{Fritz distribution}~\cite{Fritz_2012}.
 In the Fritz distribution, denoted $\prob[\fritz]$, each of the variables $A,B,C$ is taken to have $4$ possible outcomes $\bc{0,1,2,3}$.
@@
     \end{align*}
-    Here the notation $\prob[\fritz][abc] = \prob[ABC][abc] = \prob[][\p A\mapsto a,\p B\mapsto b,\p C\mapsto c]$ is used as shorthand.
+    Here the notation $\prob[\fritz][abc] = \prob[ABC][abc] = \prob[][A\mapsto a,B\mapsto b,C\mapsto c]$ is used as shorthand.
 The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:triangle_Qcompatibility}.
     The Fritz distribution may be visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}.
-From this diagram, it can be seen that each of $C$'s outcomes restricts the possible outcomes for $\p A,\p B$ into a $2 \times 2$ block.
-When expressing the outcomes as pairs of binary digits, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by (i.e.
-perfectly correlated with) the outcome of $\p C$.
-Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits $\p A_l$ and $\p B_l$ emulate the measurement settings $S_{\p A}$ and $S_{\p B}$, whereas the right-hand bits $\p A_r$ and $\p B_r$ emulate the outcomes which would be obtained by $A$ and $B$ back in the Bell structure of \cref{fig:bell_structure}.
-Critically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.
+From this diagram, it can be seen that each of $C$'s outcomes restricts the possible outcomes for $A,B$ into a $2 \times 2$ block.
+When expressing the outcomes as pairs of binary digits, it can be seen that the left-hand bits for $A$ and $B$ (respectively denoted $A_l$, $B_l$) are fixed by (i.e.
+perfectly correlated with) the outcome of $C$.
+Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded}, the left-hand bits $A_l$ and $B_l$ emulate the measurement settings $S_{A}$ and $S_{B}$, whereas the right-hand bits $A_r$ and $B_r$ emulate the outcomes which would be obtained by $A$ and $B$ back in the Bell structure (\cref{fig:bell_structure}).
+Critically, $C$'s bits are perfectly correlated with the left-bits of $A,B$; $C_l = A_l$ and $C_r = B_l$.
     \begin{figure}
@@
     \end{figure}
-    Consequently, it is possible to define the correlation $\ba{\p A_r \p B_r}$ between the right-hand bits of $\p A$ and $\p B$:
-    \[ \ba{\p A_r \p B_r} = \prob[\p A_r \p B_r][00] + \prob[\p A_r \p B_r][11] - \prob[\p A_r \p B_r][01] - \prob[\p A_r \p B_r][10] \]
+    Consequently, it is possible to define the correlation $\ba{A_r B_r}$ between the right-hand bits of $A$ and $B$:
+    \[ \ba{A_r B_r} = \prob[A_r B_r][00] + \prob[A_r B_r][11] - \prob[A_r B_r][01] - \prob[A_r B_r][10] \eq \label{eq:right_bit_correlations} \]
     Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $A, B, S_{A}, S_{B}$ can be directly converted to an inequality for the Triangle structure by performing the surjective relabeling:
@@
         B_r\leftarrow B\,,\quad
-         \p A_l\leftarrow S_{A}\,,\quad
-         \p B_l\leftarrow S_{B}\,,\quad
-         \p C_l\leftarrow S_{A}\,,\quad
-         \p C_r\leftarrow S_{B}\,.
+        A_l\leftarrow S_{A}\,,\quad
+        B_l\leftarrow S_{B}\,,\quad
+        C_l\leftarrow S_{A}\,,\quad
+        C_r\leftarrow S_{B}\,.
+        \eq \label{eq:fritz_relabelling}
     \end{align*}
-    As an example, the famous CHSH inequality~\cite{CHSH_Original} per \cref{eq:CHSH_ineq_orig} is translated into a constraint on the correlation between the right-bits of $A$ and $B$,
-    \[ \ba{\p A_r \p B_r|\p C = 00} + \ba{\p A_r \p B_r|\p C = 01} + \ba{\p A_r \p B_r|\p C = 10} - \ba{\p A_r \p B_r|\p C = 11} \leq 2 \eq \label[ineq]{eq:CHSH_intriangle} \]
+    As an example, the famous CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original} is translated into a constraint on the correlation between the right-bits of $A$ and $B$,
+    \[ \ba{A_r B_r|C = 00} + \ba{A_r B_r|C = 01} + \ba{A_r B_r|C = 10} - \ba{A_r B_r|C = 11} \leq 2 \eq \label[ineq]{eq:CHSH_intriangle} \]
     Every compatible distribution $\prob[ABC]$ \emph{for which $C$ is perfectly correlated with $A_l,B_l$} must satisfy \cref{eq:CHSH_intriangle}.
@@
 Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequality for the Triangle structure if there exists
-    The proof relies on the perfect correlation between $\p C$'s outcomes and the measurement pseudo-settings (left-bits) of $\p A$ and $\p B$.
+    The proof relies on the perfect correlation between $C$'s outcomes and the measurement pseudo-settings (left-bits) of $A$ and $B$.
 For example, if one combines \cref{eq:fritz_dist} with slight uniform noise, what can we say with confidence regarding if the resulting modified distribution is classical or not?
@@
 
-    Plainly $\prob[\fritz]$ is a valid but \textit{manufactured} example.
-The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of nonclassical resources made accessible by quantum mechanics.
+    Plainly, $\prob[\fritz]$ is a valid but \textit{manufactured} example.
+The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of non-classical resources made accessible by quantum mechanics.
 The goal, therefore, is to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure \cite{Gisin_2017}.
@@
 
-    Fritz's problem is concerned with how to find and recognize nonclassical quantum distributions specifically for the Triangle structure.
+    Fritz's problem is concerned with how to find and recognize non-classical quantum distributions specifically for the Triangle structure.
 The original proof of non-classicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations~\cite{Fritz_2012}.
@@
     The methods used to derive these inequalities are largely based on the Inflation Technique~\cite{Inflation}.
-A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:main_appendix} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.
+A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:inflation_technique_summary} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.
     We emphasize that each of these causal compatibility inequalities independently provides a positive resolution of Fritz's problem.
@@
     The first causal compatibility inequality chosen for presentation is reported below:
+    % \begin{equation*}
+    % \begin{gathered}
+    %     \eq\label[ineq]{eq:ww_ineq}
+    %     I\tsb{WagonWheel} : \\
+    %     + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
+    %     - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
+    %     - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
+    %     - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
+    %     - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
+    %     - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
+    %     - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
+    %     - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
+    %     - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
+    %     - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
+    %     - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
+    % \end{gathered}
+    % \end{equation*}
     \begin{equation*}
@@
         I\tsb{WagonWheel} : \\
-        + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
-        - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
-        - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
-        - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
-        - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
-        - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
-        - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
-        - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
-        - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
-        - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
-        - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
+        +P_{A_{l}B_{l}}(11) -P_{A_{l}B_{l}C_{l}C_{r}}(1111) +P_{A_{l}B_{l}}(00) P_{C_{l}C_{r}}(11) +P_{C_{l}C_{r}}(01) P_{C_{l}C_{r}}(10) \\
+        -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
+        -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
+        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
+        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
+        \leq 0
     \end{gathered}
@@
     \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it.
-To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:main_appendix_main_summary,sec:deriving_inequalities_from_the_inflation_technique}.
+To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}.
     Aside from increasing outcome cardinality, we are also forced to consider larger inflations than those analyzed in Ref.~\cite{Inflation}.
@@
     By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure per \cref{eq:triangle_compatibility} must satisfy $I\tsb{WagonWheel}$.
-On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $0.0129 \not \leq 0$\footnote{To aid verification: the first term in \cref{eq:ww_ineq} for the Fritz distribution is $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ while all of the remaining terms sum to $\simeq 0.0136$.}.
+On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $\f{1}{16} \not \leq 0$.
 Consequently we affirm that the Fritz distribution is incompatible with the Triangle structure, a fact previously only demonstrated without inequalities.
 
-    It is possible to simplify $I\tsb{WagonWheel}$ by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$.
+    % \footnote{To aid verification: the first term in \cref{eq:ww_ineq} for the Fritz distribution is $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ while all of the remaining terms sum to $\simeq 0.0136$.}
+
+    % It is possible to simplify $I\tsb{WagonWheel}$ by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$.
 Upon doing so, one obtains an equivalent representation for $I\tsb{WagonWheel}$,
-    \begin{equation*}
-    \begin{gathered}
-    \eq\label[ineq]{eq:ww_ineq_symplified}
-    I\tsb{WagonWheel} : \\
-    + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
-    - P_{ABC}(303)P_{C}(0) - P_{ABC}(313)P_{C}(0) - P_{ABC}(302)P_{C}(1) - P_{AB}(02)P_{C}(2) - \\
-    - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
-    \end{gathered}
-    \end{equation*}
+
+    % \begin{equation*}
+    % \begin{gathered}
+    % \eq\label[ineq]{eq:ww_ineq_symplified}
+    % I\tsb{WagonWheel} : \\
+    % + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
+    % - P_{ABC}(303)P_{C}(0) - P_{ABC}(313)P_{C}(0) - P_{ABC}(302)P_{C}(1) - P_{AB}(02)P_{C}(2) - \\
+    % - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
+    % \end{gathered}
+    % \end{equation*}
+
+    % \begin{equation*}
+    % \begin{gathered}
+    % \eq\label[ineq]{eq:ww_ineq_symplified}
+    % I\tsb{WagonWheel} : \\
+    % - P_{A_lB_lB_r}(100) \\
+    % - P_{C_lC_r}(11)P_{C_lC_r}(00) \\
+    % + P_{A_lB_lB_rC_lC_r}(10010) \\
+    % + P_{A_{l}A_{r}C_lC_r}(1111)P_{C_lC_r}(00)\\
+    % - P_{A_lA_rB_lB_rC_lC_r}(110011)P_{C_lC_r}(00) \\
+    % - P_{A_lA_rB_lB_rC_lC_r}(110010)P_{C_lC_r}(01) \\
+    % + P_{A_lA_rB_lB_rC_lC_r}(001001)P_{C_lC_r}(10) \\
+    % - P_{A_lA_rB_l}(001)P_{C_lC_r}(10) \\
+    % + P_{A_lA_rB_lB_rC_lC_r}(000000)P_{C_lC_r}(11) \\
+    % \leq 0
+    % \end{gathered}
+    % \end{equation*}
 
@@
 The Web inflation shown in \cref{fig:the_web_inflation} was used to produce the eponymous $I\tsb{Web}$ per \cref{eq:web_inequality}.
-The Web inflation being considerably larger than the Wagon-Wheel inflation of \cref{fig:wagon_wheel_inflation}, it is computationally more demanding to work with, but the Web inflation is capable of yielding strictly stronger inequalities.
+The Web inflation is considerably larger than the Wagon-Wheel inflation; it is computationally more demanding to work with, albeit capable of yielding strictly stronger inequalities.
 For brevity, we employ the shorthand $\prob\br{abc}$ in lieu of $\prob[ABC]\br{abc}$ in presenting \cref{eq:web_inequality}.
@@
         I\tsb{Web} : \\\nonumber
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone_halfed}
     \end{gather}
@@
         I\tsb{SymmetricWeb} : \\\nonumber
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone_halfed}
     \end{gather}
@@
 
-    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure [\cref{fig:triangle_structure}] and thus expressed as follows:
-    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \eq \label{eq:quantum_model_triangle}\]
-    where $\rho_{AB}, \rho_{BC}, \rho_{CA}$ are bipartite density matrices, $M_{A}, M_{B}, M_{C}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately.
+    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure (\cref{fig:triangle_structure}) and thus expressed in the form of \cref{eq:triangle_Qcompatibility}.
 In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
-In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
-Motivated by the fact that the Fritz distribution [\cref{sec:fritz_distribution}] only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states which are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA}$ becomes an $n^6 \times n^6$ matrix.
+In order to qualify the scope of \cref{eq:triangle_Qcompatibility} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification.
+Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states which are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA}$ becomes an $n^6 \times n^6$ matrix.
 Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons.
@@
 Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$.
-Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
+Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:triangle_Qcompatibility} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
     \[ \prob[ABC]\br{abc} = \bramidket{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{A,a}m_{B,b}m_{C,c}} \eq \label{eq:quantum_model_triangle_pvms}\]
@@
     % the a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}.
-Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:quantum_model_triangle} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$.
+Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:triangle_Qcompatibility} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$.
 The objective value is simply the degree of violation $f = I\br{\prob[ABC]}$ and used to make adjustments to $\la$ in order to achieve largest and larger violations.
@@
 
-    It is perhaps curious, however, that the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:quantum_model_triangle} are restricted to maximally entangled states.
+    It is perhaps curious, however, that the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:triangle_Qcompatibility} are restricted to maximally entangled states.
 This distributions certainly violate $I\tsb{Web}$ more than $\prob[\fritz]$, even it is isn't the global maximum of $I\tsb{Web}$.
@@
 This distribution is also non-classical with relative violation $V_F = 3$.
-As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:quantum_model_triangle}.
+As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:triangle_Qcompatibility}.
 Therefore we conclude that the space of quantum-accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.
@@
     In \cref{sec:found_inequalities} we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions.
-This result was made possible through the Inflation Technique \cref{sec:main_appendix} applied to the Fritz distribution.
+This result was made possible through the Inflation Technique \cref{sec:inflation_technique_summary} applied to the Fritz distribution.
 
@@
 Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes.
-In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:main_appendix}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations.
+In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique_summary}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations.
 These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and is a recommended focus for future research.
@@
 Research at Perimeter Institute is supported by the Government of Canada through the Department of Innovation, Science and Economic Development Canada and by the Province of Ontario through the Ministry of Research, Innovation and Science.
-The authors are grateful to Miguel Navascués for drawing our attention to the existence of distributions genuinely requiring quantum resources for all latent nodes in the Triangle structure.
-Moreover, the authors are grateful to Denis Rosset for suggesting a Fritz distribution variant involving a reduced cardinality of outcomes.
+The authors are grateful to Miguel Navascués and Denis Rosset for their insightful dicussions.
     \end{acknowledgments}
@@
     \appendix
-    %\gdef\p@subsection{\thesection-}
-
-    \section{Summary of Inflation Technique}
-    \label{sec:main_appendix}
-
-    % \subsection{Satisfaction of d-SSeparation Relations}
-    % \label{sec:satisfaction_of_d_sep_relations}
-    % \todo[TC]{Absorb the relevant components of the next section into this one}
-    % \todo[TC]{Given a distribution and a causal structure, does the distribution satisfy the conditional d-Separation relations?}
-
-    \subsection{Marginal Satisfiability and Inequalities}
+
+    \section{Marginal Satisfiability and Inequalities}
     \label{sec:marginal_satisfiability}
-    \label{sec:marginal_linear}\label{sec:linear_programs}
 
@@
 This is accomplished by illustrating how the marginal problem can be expressed as a linear program in which the solution to the marginal problem is encoded in the feasibility or infeasibility of said linear program.
-This section is presented prior to \cref{sec:main_appendix_main_summary} as the marginal problem becomes an integral component of the Inflation Technique in subsequently deriving the inequalities presented in \cref{sec:found_inequalities}.
+This section is presented prior to \cref{sec:inflation_technique_summary} as the marginal problem becomes an integral component of the Inflation Technique in subsequently deriving the inequalities presented in \cref{sec:found_inequalities}.
 Moreover, the Marginal problem is presented here logically independent from the remainder of the manuscript both for procedural clarity and because the marginal problem has applications to numerous areas of mathematics including game theory~\cite{Vorobev_1962}, database theory, knowledge integration of expert system, and of course, quantum information theory~\cite{Fritz_2011}.
@@
 By construction each marginal event $m \in \Events{\mscenario}$ is a restriction of some joint event $j \in \Events{\jointvar}$.
-    % \subsubsection{Linear Programs}
-    % \label{sec:linear_programs}
-
-    The marginalization operation (\cref{eq:def:marginal_problem}) of the marginal problem is a linear operator.
-This linear operator maps a joint probability distribution $\prob[\jointvar] : \Events{\jointvar} \to \bs{0,1}$ into a marginal model $\prob^{\mscenario} = \bc{\prob[V] : \Events{V} \to \bs{0,1} \mid V \in \mscenario}$.
+    % \subsection{Linear Programs}
+
+    The marginalization operation of the marginal problem is a \textit{linear} operation, mapping a joint probability distribution $\prob[\jointvar] : \Events{\jointvar} \to \bs{0,1}$ into a marginal model $\prob^{\mscenario} = \bc{\prob[V] : \Events{V} \to \bs{0,1} \mid V \in \mscenario}$.
 Since $\Events{\mscenario}$ and $\Events{\jointvar}$ are finite, the marginal problem can be represented as a $\abs{\Events{\mscenario}} \times \abs{\Events{\jointvar}}$ matrix.
@@
 This question is naturally framed as the \term{marginal linear program}:
-    \begin{alignat*}{2}
+    \begin{equation}
+    \begin{aligned}
         & \text{minimize:} \quad&& \emptyset \cdot x\\
@@
         & && M \cdot x = \probvec^{\mscenario}
-    \end{alignat*}
+    \end{aligned}
+    \end{equation}
     If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries).
@@
 Constructing the dual linear program is straightforward~\cite{Lahaie_2008}.
-    \begin{alignat*}{2}
+    \begin{equation}
+    \begin{aligned}
         & \text{minimize:} \quad&& y \cdot \probvec^{\mscenario}\\
         & \text{subject to:} && y \cdot M \succeq 0
-    \end{alignat*}
+    \end{aligned}
+    \end{equation}
 
@@
 For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable.
-This will become apparent in \cref{sec:deriving_inequalities_from_the_inflation_technique} when the Inflation Technique is applied to the Triangle structure, producing considerably large marginal models.
-Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
-    \subsection{Inflation Technique}
-    \label{sec:deriving_inequalities}
-    \label{sec:main_appendix_main_summary}
+This will become apparent in \cref{sec:deriving_inequalities} when the Inflation Technique is applied to the Triangle structure, producing considerably large marginal models.
+Luckily, the Fritz distribution allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
+
+    \section{Inflation Technique}
+    \label{sec:inflation_technique_summary}
     The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if an observable probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$.
@@
 Fortunately, the inflated causal structure $\graph'$ possesses its own \textit{d-separation relations} which enforces conditional independence equality constraints on $\prob^{\Inj[\graph]{\graph'}}$.
-A useful subset of d-separation relations are those corresponding to unconditional d-separations, known as \term{ancestrally separated} sets~\cite{Pearl_2009}.
-Two sets $N_1', N_2'$ are ancestrally separated ($N_1' \ancestralindep N_2'$) if they have distinct ancestry in $\graph'$.
-    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \]
+A useful subset of d-separation relations are those corresponding to unconditional d-separations, known as \term{ancestrally independent} sets~\cite{Pearl_2009}.
+Two sets $N_1', N_2'$ are ancestrally independent ($N_1' \ancestralindep N_2'$) if they have distinct ancestry in $\graph'$.
+    \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \eq \]
     Ancestral independence implies an unconditional probabilistic independence --- if $N_1' \ancestralindep N_2'$ then $\prob[N_1' \cup N_2'] = \prob[N_1']\prob[N_2']$.
 If $N_1', N_2' \in \Inj[\graph]{\graph'}$, then the associated probabilistic constraint is applicable to $\prob^{\Inj[\graph]{\graph'}}$.
-This notion generalizes to more than two ancestrally separated sets.
-A set $N' \subseteq \nodes'$ is an \term{as-expressible set} if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally separated: $\forall i, j : N_i' \ancestralindep N_j'$.
+This notion generalizes to more than two ancestrally independent sets.
+A set $N' \subseteq \nodes'$ is an \term{ai-expressible set} if it can be decomposed into the disjoint union of injectable sets $N' = \coprod_{i} N'_i \mid N'_i \in \Inj[\graph]{\graph'}$ and all pairs $N_i', N_j'$ are ancestrally independent: $\forall i, j : N_i' \ancestralindep N_j'$.
 The analogous probabilistic constraint is: $\prob[N'] = \prob[\coprod_i N'_i] = \prod_{i}\prob[N'_i]$~\cite{Pearl_2009}.\footnote{In~\cite{Inflation}, this concept is generalized into terms which can be factorized via d-separation conditions and the corresponding inflated sets are termed \textit{expressible sets}.
-This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.} Throughout this work, we let $\AnSepExpr[\graph]{\graph'}$ denote the set of all as-expressible sets.\footnote{Analogously to a marginal scenario $\mscenario$, the as-expressible sets $\AnSepExpr[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
-Therefore, in practice, it is completely sufficient to focus on the \textit{maximal} as-expressible sets.} Efficient algorithms for computing the injectable and as-expressible sets of an inflation can be found in~\cite{Inflation}.
-\Cref{tab:asexpr_triangle_structure_wagon_wheel,tab:asexpr_triangle_structure_web} tabulate the as-expressible sets and the associated ancestral separations for the Wagon-Wheel and Web inflations (respectively \cref{fig:wagon_wheel_inflation,fig:the_web_inflation}).
+This generalization was not required for this work in particular because the ancestral independence relations formed a generating set of d-separation conditions for all of the inflations considered in \cref{fig:inflations}.} Throughout this work, we let $\AIExpr[\graph]{\graph'}$ denote the set of all ai-expressible sets.\footnote{Analogously to a marginal scenario $\mscenario$, the ai-expressible sets $\AIExpr[\graph]{\graph'}$ form an \textit{abstract simplicial complex}.
+Therefore, in practice, it is completely sufficient to focus on the \textit{maximal} ai-expressible sets.} Efficient algorithms for computing the injectable and ai-expressible sets of an inflation can be found in~\cite{Inflation}.
+\Cref{tab:asexpr_triangle_structure_wagon_wheel,tab:asexpr_triangle_structure_web} tabulate the ai-expressible sets and the associated ancestral separations for the Wagon-Wheel and Web inflations (respectively \cref{fig:wagon_wheel_inflation,fig:the_web_inflation}).
 
@@
                 \hline
-                \multicolumn{2}{|c|}{Maximally AS-Expressible Sets} \\
+                \multicolumn{2}{|c|}{Maximally AI-Expressible Sets} \\
                 \multicolumn{2}{|c|}{for the Wagon-Wheel Inflation} \\
                 \hline
-                $\AnSepExpr[\graph]{\graph'}$ & Ancestral Separations \\
+                $\AIExpr[\graph]{\graph'}$ & Ancestral Separations \\
                 \hline
@@
             \end{tabular}
-            \caption{The maximally as-expressible sets for the Wagon-Wheel Inflation.
+            \caption{The maximally ai-expressible sets for the Wagon-Wheel Inflation.
             \label{tab:asexpr_triangle_structure_wagon_wheel}}
@@
                 \hline
-                \multicolumn{2}{|c|}{Maximally AS-Expressible Sets} \\
+                \multicolumn{2}{|c|}{Maximally AI-Expressible Sets} \\
                 \multicolumn{2}{|c|}{for the Web Inflation} \\
                 \hline
-                $\AnSepExpr[\graph]{\graph'}$ & Ancestral Separations \\
+                $\AIExpr[\graph]{\graph'}$ & Ancestral Separations \\
                 \hline
@@
             \end{tabular}
-            \caption{The maximally as-expressible sets for the Web Inflation.
+            \caption{The maximally ai-expressible sets for the Web Inflation.
             \label{tab:asexpr_triangle_structure_web}}
@@
     Unlike $\prob^{\ImInj[\graph]{\graph'}}$, which is non-contextual by construction, $\prob^{\Inj[\graph]{\graph'}}$ contains overlapping marginals meaning its contextuality remains unknown and must be determined using any of the techniques discussed in~\cref{sec:marginal_satisfiability}.
-More importantly, the Inflation Technique introduces new constraints relating to the as-expressible sets.
-In practice, the equality constraints implied by $\AnSepExpr[\graph]{\graph'}$ permits one to construct a marginal model defined over the as-expressible sets $\AnSepExpr[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$.
-In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (see \cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$ --- the latter of which is discussed in \cref{sec:deriving_inequalities_from_the_inflation_technique}.
+More importantly, the Inflation Technique introduces new constraints relating to the ai-expressible sets.
+In practice, the equality constraints implied by $\AIExpr[\graph]{\graph'}$ permits one to construct a marginal model defined over the ai-expressible sets $\AIExpr[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$.
+In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (\cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$ --- the latter of which is discussed in \cref{sec:deriving_inequalities}.
 
@@
 
-    % Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{as-expressible sets} of $\graph'$.
-
-    % A as-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions
+    % Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{ai-expressible sets} of $\graph'$.
+
+    % A ai-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions
     % \[  \]
-    % Application of the inflation lemma to linear inequalities constraining as-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
-
-    \subsection{Deriving Inequalities from the Inflation Technique}
-    \label{sec:deriving_inequalities_from_the_inflation_technique}
-
-    \Cref{sec:main_appendix_main_summary} summarizes how the Inflation Technique~\cite{Inflation} can cast the compatibility problem into the marginal problem by leveraging inflations of the Triangle structure.
-Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal as-expressible sets of $\graph'$, i.e.
-$\mscenario = \AnSepExpr[\graph]{\graph'}$.
-
-    The first inequality presented in \cref{sec:found_inequalities} was \cref{eq:ww_ineq}.
-\cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation in \cref{fig:wagon_wheel_inflation}.
+    % Application of the inflation lemma to linear inequalities constraining ai-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
+
+    \section{Deriving Inequalities from the Inflation Technique}
+    \label{sec:deriving_inequalities}
+
+    \Cref{sec:inflation_technique_summary} summarizes how the Inflation Technique~\cite{Inflation} can cast the compatibility problem into the marginal problem by leveraging inflations of the Triangle structure.
+Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (\cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal ai-expressible sets of $\graph'$, i.e.
+$\mscenario = \AIExpr[\graph]{\graph'}$.
+
+    Recall that the first inequality (\cref{eq:ww_ineq}) presented in \cref{sec:found_inequalities} was derived using the Wagon-Wheel inflation (\cref{fig:wagon_wheel_inflation}).
 The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel.
-The maximal as-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{tab:asexpr_triangle_structure_wagon_wheel}.
-These maximal as-expressible sets define a marginal scenario where the joint variables $\jointvar$ are the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
-    \[ \mscenario = \AnSepExpr[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
+The maximal ai-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{tab:asexpr_triangle_structure_wagon_wheel}.
+These maximal ai-expressible sets define a marginal scenario where the joint variables $\jointvar$ are the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
+    \[ \mscenario = \AIExpr[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
     Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
@@
     \[ {\probvec^{\mscenario}}^{\intercal} = \underbrace{\br{\prob[A_2B_1C_3C_1]\br{0000}, \ldots, \prob[A_1B_1C_4C_2]\br{3232}, \ldots, \prob[A_2B_2C_2C_4]\br{3333}}}_{1024 \text{ entries}} \eq \label{eq:marginal_vector_wagon_wheel} \]
-    Which can be factored into the ancestrally separated injectable sets using \cref{tab:asexpr_triangle_structure_wagon_wheel},
+    Which can be factored into the ancestrally independent injectable sets using \cref{tab:asexpr_triangle_structure_wagon_wheel},
     \[ {\probvec^{\mscenario}}^{\intercal} = \br{\prob[A_2B_1C_3]\br{000}\prob[C_1]\br{0}, \ldots, \prob[A_1B_1C_4]\br{323}\prob[C_2]\br{2}, \ldots, \prob[A_2B_2C_2]\br{333}\prob[C_4]\br{3}} \eq \label{eq:marginal_vector_wagon_wheel_factors}\]
@@
 For example, $\prob[ABC]\br{323}\prob[C]\br{2}$ is assigned the following numerical value:
-    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267  \]
+    \[ \prob[ABC]\br{323}\prob[C]\br{2} = \f{1}{32}\br{2 + \sqrt{2}} \cdot \f{1}{4} \simeq 0.0267 \eq \]
     The same is applied to all other entries of $\probvec^{\mscenario}$.
-Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained, corresponding precisely to \cref{eq:ww_ineq} using \cref{eq:marginal_vector_wagon_wheel_factors_dropped}.
+Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained, corresponding precisely to \cref{eq:ww_ineq} using \cref{eq:marginal_vector_wagon_wheel_factors_dropped} in bit-wise notation.
 
     The remaining inequalities in \cref{sec:found_inequalities} were derived using the Web inflation of \cref{fig:the_web_inflation}.
-The maximal as-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{tab:asexpr_triangle_structure_web}.
-Analogously to the Wagon-Wheel inflation, these as-expressible sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.
-
-    \subsection{Deriving Symmetric Causal Compatibility Inequalities}
+The maximal ai-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{tab:asexpr_triangle_structure_web}.
+Analogously to the Wagon-Wheel inflation, these ai-expressible sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.
+
+    \section{Deriving Symmetric Causal Compatibility Inequalities}
     \label{sec:symmetric_inequalities}
 
-    \Cref{sec:main_appendix_main_summary} detailed how to obtain causal compatibility inequalities for any causal structure by constructing a marginal problem (see \cref{sec:marginal_satisfiability}) and supplying an incompatible distribution to generate an infeasibility certificate.
+    \Cref{sec:inflation_technique_summary} detailed how to obtain causal compatibility inequalities for any causal structure by constructing a corresponding marginal problem (as defined in \cref{sec:marginal_satisfiability}) and supplying an incompatible distribution to generate an infeasibility certificate.
 \cref{eq:symmetric_web_inequality} presented the causal compatibility inequality $I\tsb{SymmetricWeb}$ which is symmetric under permutations of the variables $A,B,C$.
@@
 
-    Permutations $\varphi$ that modify the marginal scenario have no application within the framework of the Inflation Technique (\cref{sec:main_appendix_main_summary}) because the Inflation Lemma only holds when the inflated inequality constrains injectable sets.
+    Permutations $\varphi$ that modify the marginal scenario have no application within the framework of the Inflation Technique (\cref{sec:inflation_technique_summary}) because the Inflation Lemma only holds when the inflated inequality constrains injectable sets.
 Therefore, the desired set of symmetries for our purposes is a subgroup of $\Perm{\jointvar}$ that takes $\mscenario$ to $\mscenario$.
@@
 The entries of $M_{\gp}$ are integers and correspond to summing over the rows and columns of $M$ that belong to each orbit.
-    \[ \br{M_{\gp}}_{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M_{m',j'} \]
+    \[ \br{M_{\gp}}_{\Orb[\gp]{m}, \Orb[\gp]{j}} = \sum_{\substack{j' \in \Orb[\gp]{j} \\ m' \in \Orb[\gp]{m}}} M_{m',j'} \eq \]
     It is possible to analogously define a \term{symmetric joint distribution vector} $\probvec^{\jointvar}_{\Phi}$ indexed by $\Orb[\gp]{j}$, $\br{\probvec^{\jointvar}_{\Phi}}_{\Orb[\gp]{j}} = \sum_{j' \in \Orb[\gp]{j}} \probvec^{\jointvar}_{j'}$ and a \term{symmetric marginal distribution vector} $\probvec^{\mscenario}_{\Phi}$ indexed by $\Orb[\gp]{m}$, $\br{\probvec^{\mscenario}_{\Phi}}_{\Orb[\gp]{m}} = \sum_{m' \in \Orb[\gp]{m}} \probvec^{\mscenario}_{m'}$.
@@
     For the Triangle structure in particular, the variable permutation group is the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
-For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\AnSepExpr[\graph]{\graph'}}$ --- an order $48$ group with the following $4$ generators:
-    \begin{equation*}
+For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\AIExpr[\graph]{\graph'}}$ --- an order $48$ group with the following $4$ generators:
+    \begin{equation}
     \begin{aligned}[c]
@@
     \end{aligned}
-    \end{equation*}
+    \end{equation}
     % ((3, 2, 1, 0, 7, 6, 5, 4, 11, 10, 9, 8),
@@
     Notice that $\varphi_1, \varphi_2, \varphi_3, \varphi_4$ are all automorphisms of the web inflation.
-Moreover they stabilize the as-expressible sets of \cref{tab:asexpr_triangle_structure_web}.
+Moreover they stabilize the ai-expressible sets of \cref{tab:asexpr_triangle_structure_web}.
 Importantly,
-    \[ \gp\br{\AnSepExpr[\graph]{\graph'}} \sim \Perm{A,B,C} \]
+    \[ \gp\br{\AIExpr[\graph]{\graph'}} \sim \Perm{A,B,C} \eq \]
     To see this, $\varphi_1$ and $\varphi_4$ become the identity element in $\Perm{A,B,C}$ upon removal of the copy-index, leaving $\varphi_2$ to generate reflections and $\varphi_3$ to generate rotations.
@@
 Possessing a parameterization that maintains this physical interpretation is useful as it allows one to readily eliminate any degeneracies.
-For the purposes of quantum distributions such as \cref{eq:quantum_model_triangle}, it should be clear that any contributions to global phase are irrelevant.
+For the purposes of quantum distributions such as \cref{eq:triangle_Qcompatibility}, it should be clear that any contributions to global phase are irrelevant.
 The SSH parameterization becomes especially attractive because it readily permits one to drop the global phase terms by setting $\la_{l,l} = 0$ for all $l = 1, \ldots, d$.
@@
     % \label{sec:measurements}
-    % For each measurement set $M$ in \cref{eq:quantum_model_triangle}, we consider a $d$-element projective-valued measure (PVM) $M = \bc{M_1, \ldots, M_d}$ satisfying a number of familiar constraints:
+    % For each measurement set $M$ in \cref{eq:triangle_Qcompatibility}, we consider a $d$-element projective-valued measure (PVM) $M = \bc{M_1, \ldots, M_d}$ satisfying a number of familiar constraints:
     % \begin{gather*}
@@
 
-    % Each state $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ of \cref{eq:quantum_model_triangle} is modeled as a two-qubit density matrices acting on $\Hilb^2 \otimes \Hilb^2$.
+    % Each state $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ of \cref{eq:triangle_Qcompatibility} is modeled as a two-qubit density matrices acting on $\Hilb^2 \otimes \Hilb^2$.
 The space of all such states corresponds to the space of all $4\times 4$ positive semi-definite hermitian matrices with unitary trace.
@@
 Upon examination of \cref{eq:quantum_model_triangle_pvms}, we consider $\netperm$ to be acting on the joint global state $\rho_{{AB}} \otimes \rho_{{BC}} \otimes \rho_{{CA}}$.
-To illuminate its necessity, consider \cref{eq:quantum_model_triangle} in the absence of $\netperm$.
+To illuminate its necessity, consider \cref{eq:triangle_Qcompatibility} in the absence of $\netperm$.
     % % \begin{align*}

### 2017-09-19 documents/TriangleScenarioArXiv/ts.tex
typo

@@
     \author{Thomas C. Fraser}
-    \email{tcfraser@tcfraser.com}
+    \email{tfraser@perimeterinstitute.ca}
     \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
@@
 By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle structure that are violated by the Fritz distribution.
-A representative trio of these $\prob[\fritz]$-incompatability-witnessing inequalities are presented here: $I\tsb{WagonWheel}$ per \cref{eq:ww_ineq_symplified}, notable for its simplicity; $I\tsb{Web}$ per \cref{eq:web_inequality}, which best witnesses the non-clasicality of $\prob[\fritz]$ in the presence of noise; and $I\tsb{SymmetricWeb}$ per \cref{eq:symmetric_web_inequality}, which is symmetric with respect to all permutations of the three parties.
+A representative trio of these $\prob[\fritz]$-incompatability-witnessing inequalities are presented here: $I\tsb{WagonWheel}$ per \cref{eq:ww_ineq}, notable for its simplicity; $I\tsb{Web}$ per \cref{eq:web_inequality}, which best witnesses the non-clasicality of $\prob[\fritz]$ in the presence of noise; and $I\tsb{SymmetricWeb}$ per \cref{eq:symmetric_web_inequality}, which is symmetric with respect to all permutations of the three parties.
 

### 2017-09-19 documents/TriangleScenarioArXiv/figures/causal_structures/triangle_structure_injectable_highlight_2.tex
isolating final document for arxiv

\begin{tikzpicture}[scale=1]
    \begin{scope}[every node/.style=observed, fade]
        \node[unfade] (C) at (-2, 0) {$\p{C}$};
        \node         (B) at (2, 0) {$\p{B}$};
        \node[unfade] (A) at (0, {2*sqrt(3)}) {$\p{A}$};
    \end{scope}
    \begin{scope}[every node/.style=latent, fade]
        \node[unfade] (X) at (-1, {sqrt(3)}) {$\p{X}$};
        \node[unfade] (Y) at (1, {sqrt(3)}) {$\p{Y}$};
        \node[unfade] (Z) at (0, 0) {$\p{Z}$};
    \end{scope}
    \begin{scope}[every path/.style={draw=cause, thick}, fade]
        \path[postaction={on each segment={mid arrow}}]
        (Y) -- (B)
        (Z) -- (B)
        ;
        \path[postaction={on each segment={mid arrow}}, unfade]
        (X) -- (C)
        (Z) -- (C)
        ;
        \path[postaction={on each segment={mid arrow}}, unfade]
        (X) -- (A)
        (Y) -- (A)
        ;
    \end{scope}
\end{tikzpicture}

### 2017-09-19 documents/TriangleScenarioArXiv/ts.tex
isolating final document for arxiv

@@
 % === All of the Packages I use frequently ===
-\usepackage{../../packages/document_config}
-\usepackage{../../packages/shared}
-\usepackage{../../packages/misc_commands}
-
-\renewcommand{\Events}[1]{\mathcal{S}\br{#1}} % This notation is conflicting
+\usepackage{packages/document_config}
 
 % === Causal structure formatting for tikz ===
-\input{../../figures/causal_structures/formatting}
+\input{figures/causal_structures/formatting}
 
@@
             \centering
-            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
+            \scalebox{1.0}{\input{figures/causal_structures/bell_scenario}}
             \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
@@
             \centering
-            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
+            \scalebox{1.0}{\input{figures/causal_structures/triangle_structure}}
             \caption{The Triangle structure consisting of three observable variables $A,B,C$ and three latent variables $X, Y, Z$.}
@@
     \begin{nscenter}
-        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational_fritz_bell}}
+        \scalebox{1.0}{\input{figures/causal_structures/triangle_structure_operational_fritz_bell}}
         \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{A},S_{B}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
@@
     \begin{nscenter}
-            \includegraphics[scale=0.6]{../../figures/distributions/fritz_dist_plotted_bits.pdf}
+            \includegraphics[scale=0.6]{figures/distributions/fritz_dist_plotted_bits.pdf}
             \vspace{-0.2in}
@@
         I\tsb{Web} : \\\nonumber
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone_halfed}
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/no_symwitness_ineq_print_standalone_halfed}
     \end{gather}
@@
     % \begin{nscenter}
-    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
+    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/uniform_dist_plot.pdf}
     %         \vspace{-0.2in}
@@
     % \begin{subfigure}[b]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}}
+    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_2017.pdf}}
     % \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
@@
     % \begin{subfigure}[b]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}}
+    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_2017_lims.pdf}}
     % \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
@@
     \begin{nscenter}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/noise/noisy_yet_non_local_fritz.pdf}
             \vspace{-0.2in}
@@
         I\tsb{SymmetricWeb} : \\\nonumber
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone_halfed}
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/MosekCertFritzSym_ineq_standalone_halfed}
     \end{gather}
@@
     % \begin{nscenter}
-    %         \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational}}
+    %         \scalebox{1.0}{\input{figures/causal_structures/triangle_structure_operational}}
     %         \caption{The Triangle structure as modeled by quantum states and measurements.}
@@
     \begin{nscenter}
-        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
+        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
         \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{Web}$.
@@
     \begin{nscenter}
-        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
+        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
         \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{SymmetricWeb}$.
@@
     % \begin{nscenter}
-    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/symmetrized_fritz.pdf}
+    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/symmetrized_fritz.pdf}
     %         \caption{An artificially-symmetrized version of the Fritz distribution, constructed by averaging the six permutations of $\prob[\fritz]$ over the variables $A, B, C$.
@@
     % \begin{subfigure}[t]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
+    % {\centering\includegraphics[width=\linewidth]{figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
     % \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
@@
     % \begin{subfigure}[t]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
+    % {\centering\includegraphics[width=\linewidth]{figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
     % \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
@@
     \begin{subfigure}[b]{.30\linewidth}
-    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral}}
+    \scalebox{0.65}{\input{figures/causal_structures/inflated_triangle_structure_spiral}}
     \caption{The Spiral inflation.}\label{fig:spiral_inflation}
@@
     \begin{subfigure}[b]{.30\linewidth}
-    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
+    \scalebox{0.65}{\input{figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
     \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
@@
     \begin{subfigure}[b]{.30\linewidth}
-    \scalebox{0.65}{\input{../../figures/causal_structures/inflated_triangle_structure}}
+    \scalebox{0.65}{\input{figures/causal_structures/inflated_triangle_structure}}
     \caption{The Web Inflation.}\label{fig:the_web_inflation}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
+    \scalebox{0.8}{\input{figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
     \caption{$\AnSub[\graph']{\bc{A_1}}$}\label{fig:spiral_inflation_inj1}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_1}}
+    \scalebox{0.8}{\input{figures/causal_structures/triangle_structure_injectable_highlight_1}}
     \caption{$\AnSub[\graph]{\bc{A}}$}\label{fig:spiral_inflation_iminj1}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
+    \scalebox{0.8}{\input{figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
     \caption{$\AnSub[\graph']{\bc{A_2, C_1}}$}\label{fig:spiral_inflation_inj2}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\input{../../figures/causal_structures/triangle_structure_injectable_highlight_2}}
+    \scalebox{0.8}{\input{figures/causal_structures/triangle_structure_injectable_highlight_2}}
     \caption{$\AnSub[\graph]{\bc{A,C}}$}\label{fig:spiral_inflation_iminj2}
@@
     % %     \centering
-    % %     \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
+    % %     \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{figures/perm_mtrx.pdf}
     % %     \caption{The permutation matrix $\netperm$ acting on $\br{\Hilb^2}^{\otimes 6}$ for the Triangle structure. Black entries represents a value of $1$ and white represents $0$.}

### 2017-09-19 old/documents/BrazilSlides/Archive Versions/slides_for_rob.tex
reformat github repo

--- 2016-11-21 documents/BrazilSlides/slides.tex
@@
-\documentclass[
-    hyperref={bookmarks=false},% ,, linkcolor=blue, urlcolor=blue,, colorlinks=true, citecolor=MidnightBlue
-    xcolor={dvipsnames},
-]{beamer}
+\documentclass[]{beamer}
 
@@
 
-% \usepackage{pgfpages} % For viewing slides on the right
-\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
-\AtBeginNote{\scriptsize} % Make notes small
-% \setbeameroption{show notes} % Shows notes
-% \setbeameroption{show only notes} % Shows only notes
-% \setbeameroption{show notes on second screen}
-\usefonttheme[onlymath]{serif} % For serif font in math mode
-\usepackage[backend=biber, style=authoryear, doi=false,isbn=false,url=false, citestyle=authoryear-comp]{biblatex} %
-
-\setbeamertemplate{navigation symbols}{
-\insertslidenavigationsymbol%
-\insertframenavigationsymbol%
-\insertsubsectionnavigationsymbol%
-\insertsectionnavigationsymbol%
-\insertdocnavigationsymbol%
-\insertbackfindforwardnavigationsymbol%
-\hspace{1em}%
-\usebeamerfont{footline} \insertframenumber/\inserttotalframenumber%
-}
-
-\AtBeginSection[]{
-  \begin{frame}
-  \vfill
-  \centering
-  \begin{beamercolorbox}[sep=16pt,center]{title}
-    \usebeamerfont{title}\insertsectionhead\par%
-  \end{beamercolorbox}
-  \vfill
-  \end{frame}
-}
-
-\usepackage{silence}
-\WarningFilter{biblatex}{Patching footnotes failed}
-\renewcommand\mkbibacro[1]{{\footnotesize\MakeUppercase{#1}}} % http://tex.stackexchange.com/questions/203111/small-caps-font-warning-in-beamer-using-biblatex
-
-\usepackage{../../packages/shared}
-\usepackage{../../packages/misc_commands}
-\input{../../figures/causal_structures/formatting} % Causal structure formatting for tikz
-\renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}
-\renewcommand{\tcdot}{\cdot} % Tentative cdot, not sure if I want to keep dots
-\setbeamertemplate{bibliography item}{\insertbiblabel}
-\addbibresource{../references.bib}
-\AtBeginBibliography{\small}
-
-\newcommand{\probplotvalue}[1]{%
-    \definecolor{probvalcolor}{RGB}{#1}%
-    \definecolor{outlinecolor}{RGB}{127, 127, 127}%
-    \begin{tikzpicture}[baseline={([yshift=-.5ex]current bounding box.center)}]%
-        \pgfmathsetmacro{\size}{0.2};%
-        \draw[outlinecolor, fill=probvalcolor] (-\size,-\size) -- (-\size, +\size) -- (+\size, +\size) -- (+\size, -\size) -- cycle;%
-    \end{tikzpicture}%
-}%
-
-\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
-\author[Fraser]{T.C.~Fraser\inst{1,2}}
-\institute
-{
-    \inst{1}%
-    Perimeter Institute for Theoretical Physics\\
-    Ontario, Canada \\
-    \inst{2}%
-    University of Waterloo\\
-    Ontario, Canada \\
-}
-\date[QN 2016]{Quantum Networks Workshop, IIP, Nov. 2016}
-
 \begin{document}
-
-\begin{frame}
-    \titlepage
-    \note[item]{Thank International Institute for Physics (IIP) for support}
-    \note[item]{Thank Perimeter Institute for Theoretical Physics (PI) for support}
-\end{frame}
-
-\begin{frame}
-    \frametitle{The Triangle Scenario (TS)}
-    \begin{center}
-        \scalebox{1.5}{\input{../../figures/causal_structures/triangle_scenario}}
-    \end{center}
-    \note[item]{Research project's goal was to derive new causal compatibility inequalities that distinguish quantum correlations from classical correlations}
-    \note[item]{Triangle Scenario has be studied extensively before}
-    \note[item]{In~\cite{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}}
-    \note[item]{In~\cite{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)}
-    \note[item]{In~\cite{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility (there are none)}
-    \note[item]{Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective}
-\end{frame}
-
-\begin{frame}
-    \frametitle{This Talk}
-    \begin{enumerate}
-        \item Inflation technique provides polynomial inequalities
-        \item Inequalities witnessing non-local quantum correlations in the Triangle Scenario
-        \item Discuss search for new non-local quantum correlations
-    \end{enumerate}
-    \note[item]{This talk is going to have three components}
-    \note[item]{Demonstrating how something called the inflation technique allows one derive polynomial compatibility constraints for and causal structure}
-    \note[item]{Using the inflation technique to find inequalities that demonstrate non-local quantum distributions on the Triangle scenario}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Causal Compatibility}
-    \vfill
-    \begin{center}
-        Triangle Scenario
-    \end{center}
-    \[ \prob[ABC] = \int_{XYZ}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
-    \vfill
-    \begin{center}
-        \noindent\rule{8cm}{0.4pt}
-    \end{center}
-    \vfill
-    \begin{center}
-        General Setting
-    \end{center}
-    \begin{align*}
-    \mscenario &= \bc{V_1, \ldots, V_n} \\
-    \prob^{\mscenario} &= \bc{\prob[V_1], \ldots, \prob[V_n]}
-    \end{align*}
-    \[ \forall V \in \mscenario: \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \]
-    \[ \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
-    \vfill
-\end{frame}
-
-\section{Part 1: Inflation Technique}
-\begin{frame}
-    \frametitle{Demonstrating Inflation Technique}
-    \vfill
-    \begin{center}
-    \begin{columns}
-        \column{0.5\linewidth}%
-        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_1}}
-        \column{0.5\linewidth}%
-        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_1}}
-    \end{columns}
-    \end{center}
-    \only<1>{\[\forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n}\]}%
-    \only<2>{\[\AnSub[\graph]{A} \sim \AnSub[\graph']{A_1}\]}%
-    \only<3>{\[\AnSub[\graph]{C} \sim \AnSub[\graph']{C_2}\]}%
-\end{frame}
-
-\begin{frame}
-    \frametitle{Some Inflations of the Triangle Scenario}
-    \begin{center}
-    \begin{tabular}{cc}
-        %\hline
-        \scalebox{0.5}{\input{../../figures/causal_structures/triangle_scenario}}
-        &
-        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral}}
-        \\
-        %\hline
-        The Triangle Scenario
-        &
-        Spiral Inflation \\
-        %\hline
-        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
-        &
-        \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
-        \\
-        %\hline
-        Cut Inflation
-        &
-        Large Inflation \\
-        %\hline
-    \end{tabular}
-    \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{What are Injectable Sets?}
-    \begin{center}
-    \begin{columns}
-        \column{0.5\linewidth}%
-        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_2}}
-        \column{0.5\linewidth}%
-        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_2}}
-    \end{columns}
-    \end{center}
-    \only<1>{\[\AnSub[\graph]{A,C} \sim \AnSub[\graph']{A_2,C_1}\]}%
-    \only<2>{\[?? \not \sim \AnSub[\graph']{B_1,B_2}\]}%
-    \only<3>{\[?? \not \sim \AnSub[\graph']{B_2,C_2}\]}%
-\end{frame}
-
-\begin{frame}
-    \frametitle{Injectable Sets Defined}
-    \vfill
-    The \term{injectable sets in $\graph'$}:
-    \begin{align*}
-        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
-    \end{align*}
-    The \term{images of the injectable sets in $\graph$}:
-    \begin{align*}
-        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
-    \end{align*}
-    \vfill
-    \begin{center}
-        \textbf{What makes injectable sets useful?}
-    \end{center}
-    \vfill
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Lemma}
-    \begin{lemma}[Inflation Lemma]
-    Given $\graph$ and inflation $\graph$':
-    \begin{center}
-        \begin{tikzpicture}
-            \pgfmathsetmacro{\vs}{2.2};
-            \pgfmathsetmacro{\hs}{5.2};
-            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
-            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
-            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
-            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
-            \draw[very thick, ->] (pn) -- (cp);
-            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
-            \draw[very thick, ->] (cp_) -- (pn_);
-        \end{tikzpicture}
-    \end{center}
-    \end{lemma}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Perfect Correlation Is Incompatible}
-    \begin{columns}
-        \column{0.5\linewidth}
-        \begin{center}
-            \includegraphics[width=\linewidth]{../../figures/distributions/perfect_correlation_2_outcomes.pdf}
-        \end{center}
-        \column{0.5\linewidth}
-        \begin{align*}
-        \probplotvalue{0, 0, 0} &= \f12 \\
-        \prob[ABC][abc] &= \f{\bs{000} + \bs{111}}{2} \\
-        \prob[ABC][abc] &= \begin{cases}
-            \f12 & a = b = c \\
-            0 & \text{ otherwise }
-        \end{cases}
-        \end{align*}
-    \end{columns}
-    \begin{center}
-        Compatibility Inequality
-    \end{center}
-    \[ \prob[A][0]\prob[B][1] \leq \prob[BC][10] + \prob[AC][01] \]
-    \begin{center}
-        Witnesses Perfect Correlation
-    \end{center}
-    \[ \br{\f{1}{2}}^{2} \not\leq 0 + 0 \]
-\end{frame}
-\makeatletter
-\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
-  \hskip -\arraycolsep
-  \let\@ifnextchar\new@ifnextchar
-  \array{#1}}
-\makeatother
-\begin{frame}
-    \frametitle{Deriving Compatibility Inequalities}
-    \begin{center}
-        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut}}
-    \end{center}
-    \[ \mscenario = \bc{\bc{A_1, B_1}, \bc{B_1, C_1}, \bc{A_1, C_1}} \]
-    \[ \prob^{\mscenario} = \bc{\prob[A_1B_1], \prob[B_1C_1], \prob[A_1C_1]} \]
-    \[ \text{Compatibility requires:} \qquad \exists \prob[\jointvar] = \prob[A_1B_1C_1] \]
-    \[ \prob[A_1B_1] = {\sum}_{C_1} \prob[\jointvar] \qquad \prob[B_1C_1] = {\sum}_{A_1} \prob[\jointvar] \qquad \prob[A_1C_1] = {\sum}_{B_1} \prob[\jointvar]\]
-\end{frame}
-
-\begin{frame}[shrink=13]
-    \frametitle{Deriving Compatibility Inequalities Cont'd}
-    \[ \underbrace{\prob[A_1B_1] = {\sum}_{C_1} \prob[\jointvar] \qquad \prob[B_1C_1] = {\sum}_{A_1} \prob[\jointvar] \qquad \prob[A_1C_1] = {\sum}_{B_1} \prob[\jointvar]} \]
-    \[ \underbrace{\forall V \in \mscenario: \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] }\]
-    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}  \]
-    \[ \probvec^{\mscenario} =
-        \begin{pmatrix}
-            \prob[A_1B_1][00] \\
-            \prob[A_1B_1][01] \\
-            \prob[A_1B_1][10] \\
-            \prob[A_1B_1][11] \\
-            \hline
-            \prob[B_1C_1][00] \\
-            \prob[B_1C_1][01] \\
-            \prob[B_1C_1][10] \\
-            \prob[B_1C_1][11] \\
-            \hline
-            \prob[A_1C_1][00] \\
-            \prob[A_1C_1][01] \\
-            \prob[A_1C_1][10] \\
-            \prob[A_1C_1][11] \\
-        \end{pmatrix}
-        \qquad
-        \probvec^{\jointvar} =
-        \begin{pmatrix}
-            \prob[A_1B_1C_1][000] \\
-            \prob[A_1B_1C_1][001] \\
-            \prob[A_1B_1C_1][010] \\
-            \prob[A_1B_1C_1][011] \\
-            \prob[A_1B_1C_1][100] \\
-            \prob[A_1B_1C_1][101] \\
-            \prob[A_1B_1C_1][110] \\
-            \prob[A_1B_1C_1][111] \\
-        \end{pmatrix}
-    \]
-\end{frame}
-
-\begin{frame}[shrink=15]
-    \frametitle{Incidence Example}
-    \[ M = \kbordermatrix{
-        (A_1,B_1,C_1) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
-        (A_1=0, B_1=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
-        (A_1=0, B_1=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
-        (A_1=1, B_1=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
-        (A_1=1, B_1=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
-        (B_1=0, C_1=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
-        (B_1=0, C_1=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
-        (B_1=1, C_1=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
-        (B_1=1, C_1=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
-        (A_1=0, C_1=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
-        (A_1=0, C_1=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
-        (A_1=1, C_1=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
-        (A_1=1, C_1=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
-    } \]
-    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar}  \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Marginal Linear Program}
-    \begin{columns}[T]
-        \column{0.4\linewidth}%
-            \term{Marginal LP}:%
-            \begin{alignat*}{2}
-                & \text{minimize:} \quad&& \emptyset \tcdot x\\
-                & \text{subject to:} && \probvec^{\jointvar} \succeq 0 \\
-                & && M \tcdot \probvec^{\jointvar} = \probvec^{\mscenario} \\
-            \end{alignat*}%
-        \column{0.4\linewidth}%
-            \term{Dual Marginal LP}:%
-            \begin{alignat*}{2}
-                & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
-                & \text{subject to:} && y \tcdot M \succeq 0 \\
-            \end{alignat*}%
-    \end{columns}
-    \begin{itemize}
-        \item If $\probvec^{\jointvar}$ exists, then:
-        \[ y \tcdot M \tcdot \probvec^{\jointvar} = y \tcdot \probvec^{\mscenario} \geq 0  \]
-        \item If not, then $y$ is an \term{infeasibility certificate} which generates \term{infeasibility inequality}:
-        \[ y \tcdot \probvec^{\mscenario} \geq 0 \]
-        \item Most linear programing toolkits return certificates (\href[pdfnewwindow]{http://docs.mosek.com/8.0/pythonapi/optimizer-task-gety.html}{\textit{Mosek}}, \href[pdfnewwindow]{https://www.gurobi.com/documentation/6.5/refman/farkasdual.html}{\textit{Gurobi}}, \href[pdfnewwindow]{http://www-01.ibm.com/support/docview.wss?uid=swg21400058}{\textit{CPLEX}}, \href[pdfnewwindow]{http://cvxr.com/cvx/doc/basics.html\#dual-variables}{\textit{cvxr}}/\href[pdfnewwindow]{http://cvxopt.org/userguide/coneprog.html\#linear-cone-programs}{\textit{cvxopt}}.)
-    \end{itemize}
-    \note[item]{It is possible to derive non-contextuality inequalities from $M$ and a known incompatible distribution $\probvec^{\mscenario}$}
-    \note[item]{Note the null objective; the minimization objective is trivially always zero}
-    \note[item]{The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.}
-    \note[item]{If \textit{feasible}, then there exists a vector $x$ that is a valid joint distribution vector $\probvec^{\jointvar}$.}
-    \note[item]{Feasibility implies that $\probvec^{\jointvar} = x$.}
-    \note[item]{Infeasibility implies contextuality}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Deflating Inequalities}
-    \begin{columns}
-        \column{0.5\linewidth}
-            \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_cut_anim_1}}
-        \column{0.5\linewidth}
-            \vfill
-            \begin{center}
-            \[ \Inj[\graph]{\graph'} = \begin{Bmatrix}
-                \bc{A_1,C_1}\\ \bc{B_1,C_1}\\ \bc{A_1}\\ \bc{B_1}\\ \bc{C_1}
-            \end{Bmatrix} \]
-            \[ \bc{A_1, B_1} \not \in \Inj[\graph]{\graph'} \]
-            \end{center}
-            \vfill
-    \end{columns}
-    \[ \prob[A_1B_1][01] \leq \prob[B_1C_1][10] + \prob[A_1C_1][01] \]
-    \only<1>{\begin{center}\textbf{Can not deflate inequality!}\end{center}}
-    \only<2>{\begin{center}\textbf{However!}\end{center}}
-    \only<2>{\[ \AnSub[\graph']{A_1} \cap \AnSub[\graph']{B_1} = \emptyset \iff A_1 \ancestralindep B_1 \]}
-    \onslide<3->{\[ \prob[A_1][0]\prob[B_1][1] \leq \prob[B_1C_1][10] + \prob[A_1C_1][01] \]}
-    \onslide<4->{\[ \prob[A][0]\prob[B][1] \leq \prob[BC][10] + \prob[AC][01] \]}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Gives Polynomial Inequalities}
-    \begin{itemize}
-        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
-        \item \textbf{Linear inequality} for $\graph'$
-    \end{itemize}
-    \begin{center}
-        \begin{tikzpicture}[scale=0.8]
-            \pgfmathsetmacro{\hs}{1.8};
-            \pgfmathsetmacro{\vs}{1};
-            \pgfmathsetmacro{\cross}{0.3};
-            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
-            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
-            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
-            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
-            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
-            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
-            \draw (0, 0) node[](b){??};
-            \draw[thick, ] (a) -- (ab);
-            \draw[thick, ] (c) -- (cd);
-            \draw[thick, ] (a) -- (ac);
-            \draw[thick, ->] (ac) -- (c);
-            \draw[thick, ->] (ab) -- (b);
-            \draw[thick, ->] (cd) -- (d);
-            \draw[very thick, red]
-            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
-            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
-            ;
-        \end{tikzpicture}
-    \end{center}
-    \begin{itemize}
-        \item \textbf{Polynomial inequality} for $\graph$!
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Pre-injectable Sets}
-    A \term{pre-injectable set} $N'$ is:
-    \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
-    \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
-    Only need to consider \term{maximal pre-injectable sets} denoted $\PreInj[\graph]{\graph'}$
-\end{frame}
-
-\section{Quantum Non-locality From Inflation}
-
-\begin{frame}
-    \frametitle{Quantum Correlation}
-    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
-    \begin{center}
-        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_operational}}
-    \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Distribution}
-    \begin{center}
-        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_bits_brazil.pdf}
-    \end{center}
-    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Quantum Implementation of Fritz Distribution}
-    \begin{itemize}
-        \item States:
-    \end{itemize}
-    \begin{gather*}
-        \rho_{AB} = \ket{\Phi^+}\bra{\Phi^+} \quad \rho_{BC} = \rho_{CA} = \f{\ket{00}\bra{00} + \ket{11}\bra{11}}{2}
-    \end{gather*}
-    \[ \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
-    \begin{itemize}
-        \item Measurements:
-    \end{itemize}
-    \begin{gather*}
-        M_{A} = \bc{\ket{0\psi_{1}}\bra{0\psi_{1}}, \ket{0\psi_{5}}\bra{0\psi_{5}}, \ket{1\psi_{3}}\bra{1\psi_{3}}, \ket{1\psi_{7}}\bra{1\psi_{7}}} \\
-        M_{B} = \bc{\ket{0\psi_{6}}\bra{0\psi_{6}}, \ket{0\psi_{2}}\bra{0\psi_{2}}, \ket{1\psi_{0}}\bra{1\psi_{0}}, \ket{1\psi_{4}}\bra{1\psi_{4}}} \\
-        M_{C} = \bc{\ket{00}\bra{00}, \ket{10}\bra{10}, \ket{01}\bra{01}, \ket{11}\bra{11}}
-    \end{gather*}
-    \begin{itemize}
-        \item Shorthand: $\ket{\psi_n} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{in/4}\ket{1}}$
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Distribution Violating CHSH}
-    % \begin{gather*}
-    % \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
-    % \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
-    % \end{gather*}
-    \begin{itemize}
-        \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
-        \item Correlation between right bits
-    \end{itemize}
-    \[ \ba{A_rB_r} = \prob[A_rB_r][00] + \prob[A_rB_r][11] - \prob[A_rB_r][01] - \prob[A_rB_r][10] \]
-    \[ \ba{A_rB_r | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{A_rB_r | C = 3} = - \f{1}{\sqrt{2}} \]
-    \begin{itemize}
-        \item Gives CHSH violation
-    \end{itemize}
-    \begin{align*}
-    &\ba{A_rB_r|C=0} + \ba{A_rB_r|C=1} + \ba{A_rB_r|C=2} - \ba{A_rB_r|C=3} \\
-    &\quad = 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} \\
-    &\quad = 2\sqrt{2} \not \leq 2
-    \end{align*}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Notes on Fritz Distribution}
-    \begin{itemize}
-        \item Incompatibility proof contingent on perfect correlation between $C$ and pseudo-settings
-        \item Proof not robust to noise
-    \end{itemize}
-    \begin{problem}[2.17 in \cite{Fritz_2012}]
-        Find an example of non-classical quantum correlations in TS together with a proof of its non-classicality which does not hinge on Bell’s Theorem.
-    \end{problem}
-    \begin{itemize}
-        \item ``...would be helpful to have inequalities...''
-        % \item Possible to find inequalities violated by $\prob[F]$ using the Large inflation of the TS
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Large Inflation}
-    \begin{center}
-        \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
-    \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Large Inflation Pre-injectable Sets}
-    \begin{equation*}
-        \begin{gathered}
-            \textbf{Maximal Pre-injectable Sets} \\
-            \bc{A_1, B_1, C_1, A_4, B_4, C_4} \\
-            \bc{A_1, B_2, C_3, A_4, B_3, C_2} \\
-            \bc{A_2, B_3, C_1, A_3, B_2, C_4} \\
-            \bc{A_2, B_4, C_3, A_3, B_1, C_2} \\
-            \bc{A_1, B_3, C_4} \\
-            \bc{A_1, B_4, C_2} \\
-            \bc{A_2, B_1, C_4} \\
-            \bc{A_2, B_2, C_2} \\
-            \bc{A_3, B_3, C_3} \\
-            \bc{A_3, B_4, C_1} \\
-            \bc{A_4, B_1, C_3} \\
-            \bc{A_4, B_2, C_1}
-        \end{gathered}
-        \qquad
-        \begin{gathered}
-            \textbf{Ancestral Independences} \\
-            \bc{A_1, B_1, C_1} \ancestralindep \bc{A_4, B_4, C_4} \\
-            \bc{A_1, B_2, C_3} \ancestralindep \bc{A_4, B_3, C_2} \\
-            \bc{A_2, B_3, C_1} \ancestralindep \bc{A_3, B_2, C_4} \\
-            \bc{A_2, B_4, C_3} \ancestralindep \bc{A_3, B_1, C_2} \\
-            \bc{A_1} \ancestralindep \bc{B_3} \ancestralindep \bc{C_4} \\
-            \bc{A_1} \ancestralindep \bc{B_4} \ancestralindep \bc{C_2} \\
-            \bc{A_2} \ancestralindep \bc{B_1} \ancestralindep \bc{C_4} \\
-            \bc{A_2} \ancestralindep \bc{B_2} \ancestralindep \bc{C_2} \\
-            \bc{A_3} \ancestralindep \bc{B_3} \ancestralindep \bc{C_3} \\
-            \bc{A_3} \ancestralindep \bc{B_4} \ancestralindep \bc{C_1} \\
-            \bc{A_4} \ancestralindep \bc{B_1} \ancestralindep \bc{C_3} \\
-            \bc{A_4} \ancestralindep \bc{B_2} \ancestralindep \bc{C_1}
-        \end{gathered}
-    \end{equation*}
-\end{frame}
-
-% \begin{frame}
-%     \frametitle{Deriving Inequalities}
-%     \begin{itemize}
-%         \item Inflation facilitates turning linear, inflated inequalities into polynomial deflated ones
-%         \item \textbf{Question:} How to derive compatibility inequalities for $\graph'$?
-%         \item \textbf{Answer:} Use your favorite technique for deriving compatibility inequalities:
-%         \begin{itemize}
-%             \item Entropic inequalities
-%             \item Finite outcome inequalities
-%         \end{itemize}
-%         \item Here we solve the marginal problem for $\mscenario = \PreInj[\graph]{\graph'}$
-%         \item First some notation and formalism
-%     \end{itemize}
-% \end{frame}
-
-\begin{frame}
-    \frametitle{Large Inflation Incidence}
-    \begin{itemize}
-        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
-        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
-        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
-        \item Inequalities violated by Fritz distribution are inherently $4$-outcome
-        \item Incidence matrix $M$ is \textbf{very large} $\sim 2.25 \textsf{Gb}$
-        \begin{itemize}
-            \item $\# \text{Columns} = 4^{12} = 16,777,216$
-            \item $\# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896$
-            \item $\# \text{Non-zero Entries} = 201,326,592$
-        \end{itemize}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Certificate for Fritz Distribution}
-    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
-    \vfill
-    \textbf{Note:} $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
-\end{frame}
-
-\begin{frame}[shrink=64]
-    \frametitle{Certificate for Fritz Distribution (Full)}
-    \begin{center}
-        \input{../../figures/inequalities/nosymwitness_ineq_print}
-    \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Party Symmetric Inequality}
-    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print_pretty}
-    \vfill
-    \textbf{Note:} $\bs{\prob[][113]\prob[][330]}_3$ shorthand sum over permutations:
-    \[ \prob[][113]\prob[][330] + \prob[][131]\prob[][303] + \prob[][311]\prob[][033] \]
-\end{frame}
-
-\begin{frame}[shrink=60]
-    \frametitle{Party Symmetric Inequality (Full)}
-    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
-\end{frame}
-
-\section{Maximal Violations \& Noise}
-
-\begin{frame}
-    \frametitle{Numerical Optimization}
-    Minimize objective function $f\br{\la} \in \R$:
-    \begin{enumerate}
-        \item Real-valued parameters $\la = \br{\la_0, \ldots, \la_n}$
-        \item Quantum states/measurements $\rho_{AB}, \rho_{BC}, \rho_{CA}, M_{A}, M_{B}, M_{C}$
-    \[ \prob[ABC]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A,a}\otimes M_{B,b} \otimes M_{C,c}} \]
-        \item Distribution $\prob[ABC]$
-        \item Plug into inequality $I$ in homogeneous form $I\br{\prob[ABC]} \geq 0$
-        \item Output is objective value $I\br{\prob[ABC]}$
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Numerical Optimization Methods}
-    \begin{itemize}
-        \item Numerical minimization of $f\br{\la}$
-        \[ f(\la_{(k+1)}) = \la_{(k)} - \ga_{(k)} \del f(\la_{(k)})  \]
-        \item Non-convex, non-linear, smooth/continuous
-        \item Gradient Descent, BFGS Method, Nelder-Mead simplex method
-        \item Stochastic methods: simulated annealing, basin-hopping
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing Unitary Group}
-    \begin{itemize}
-        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} demonstrate a parameterization of $\s{U}\br{d}$ where the parameters are organized in a $d \times d$-matrix of real values $\la_{n,m}$
-        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n} RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}} \]
-        \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
-        \item Relative Phase Terms: $RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$
-        \item Rotation Terms: $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
-        \item Projection Operators: $P_l = \ket{l}\bra{l}$
-        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
-        \item Parameters $\la_{n,m} \in \bs{0, 2\pi}$
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing Unitary Group Cont'd}
-    \begin{itemize}
-        \item Each parameter $\la_{n,m}$ has physical interpretation
-        \item Degeneracies are easily eliminated such as global phase
-        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = \ident \]
-        \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
-        \item Computationally efficient
-        \begin{alignat*}{2}
-            GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
-            RP_{n,m} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
-            R_{m,n} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
-            & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\
-        \end{alignat*}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing States}
-    \begin{itemize}
-        \item Each latent resource $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ modeled as bipartite qubit state acting on $\Hilb^{d/2} \otimes \Hilb^{d/2}$
-        \item $d \times d$ positive semi-definite (PSD) hermitian matrices with unitary trace
-        \item \term{Cholesky Parametrization} allows one to write any hermitian PSD as $\rho = T^{\dagger} T$
-        \item For $d = 4$:
-        \[ T = \begin{bmatrix}\la_{1}&0&0&0\\\la_{2} + i \la_{3}&\la_{4}&0&0\\\la_{5} + i \la_{6}&\la_{7} + i \la_{8}&\la_{9}&0\\\la_{10} + i \la_{11}&\la_{12} + i \la_{13}&\la_{14} + i \la_{15}&\la_{16}\end{bmatrix} \]
-        \item $d^2$ real-valued parameters
-        \item Normalized $\rho = {T^{\dagger}T}/{\Tr\br{T^{\dagger} T}}$ adds degeneracy
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing States Cont'd}
-    \begin{itemize}
-        \item \term{SHH parameterization} \cite{Spengler_2010_Unitary} exploits spectral decomposition; for rank $k \leq d$ density matrix
-        \[ \rho = \sum_{i=1}^{k} p_i \ket{\psi_i} \bra{\psi_i} \qquad p_i \geq 0, \sum_i p_i = 1 \]
-        \item Orthonormal $k$-element sub-basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into computational basis $\bc{\ket{i}}$ by unitary $U \in \s{U}\br{d}$ such that $\ket{\psi_i} = U \ket{i}$
-        \item Freedom to choice $k$
-        \item Parameterize $\rho$ through $\bc{p_i}$ and $\ti{U}_{k}$
-        \[ \ti{U}_{k} = \prod_{m=1}^{k} \br{\prod_{n={m+1}}^{d} R_{m,n} RP_{n,m}} \]
-        \item real-value parameters $d^2 - \br{d-k}^2 - k$ for $\ti{U}_{k}$, $k-1$ for $\bc{p_i}$ (no degeneracy)
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing POVMs}
-    \begin{itemize}
-        \item Each party $\br{A, B, C}$ is assigned a \term{projective-operator valued measure (POVM)} $\br{M_A, M_B, M_C}$
-        \[ \forall \ket{\psi} \in \Hilb^d : \bra{\psi} M_\chi \ket{\psi} \geq 0 \quad M_\chi = M_\chi^{\dagger} \]
-        \item $n$-outcome measurement
-        \[ M_\chi = \bc{M_{\chi, 1}, \ldots, M_{\chi, n}} \quad \sum_{i=1}^{n} M_{\chi, i} = \ident \]
-        \item For $n = 2$ outcomes, a parameterization exists by constraining the eigenvalues of $M_{\chi, i}$; for $n > 2$ not aware of anything
-        \item Warrants consideration of \term{projective-valued measures (PVMs)}
-    \end{itemize}
-    \note<1>[item]{Naimark's Dilation Theorem}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Parameterizing PVMs}
-    \begin{itemize}
-        \item Each party $\br{A, B, C}$ is assigned $n$-outcome $\br{M_A, M_B, M_C}$ such that,
-        \[ M_{\chi,i}M_{\chi,j} = \de_{ij} M_{\chi, i} \quad M_{\chi, i} = \ket{m_{\chi,i}}\bra{m_{\chi,i}} \]
-        \item Inspired by \cite{Pal_2010}, parameterizing PVMs means parameterizing a $n$-element sub-basis $\bc{\ket{m_{\chi,i}}}$
-        \item Use unitary transformation again
-        \[ \bc{\ket{m_{\chi,1}}, \ldots, \ket{m_{\chi,n}}} = \bc{U \ket{1}, \ldots, U \ket{n}} \]
-        \item Global phase and remaining basis irrelevant: $\ti{U}_{n}$ requires $n(2d - n - 1)$ real-valued parameters\
-        \item PVMs are computationally more efficient
-    \end{itemize}
-    \[ \prob[ABC]\br{abc} = \bra{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}\ket{m_{A,a}m_{B,b}m_{C,c}} \]
-\end{frame}
-\begin{frame}
-    \frametitle{Max Entangled vs. Max Violating} % $\chi = -2$
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_fritz_seed.pdf}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Maximal Violation}
-    \includegraphics[width=\linewidth]{../../figures/distributions/plotted_dist_I_2_max_violation.pdf}
-    \[ \text{Relative Violation:} \qquad V_F = \f{\min_P\bc{I\br{P}}}{I\br{P_F}} \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Maximally Violating Distributions}
-    \begin{itemize}
-        \item Able to out-perform violation provided by Fritz distribution
-        \item Maximally-violating states are not maximally-entangled; similar to detection loop-hole example of \cite{Methot_2006}
-        \item Both symmetric and asymmetric inequalities exhibit same qualitative features
-        % \item Violation very sensitive to the initial parameters $\la_{(0)}$
-    \end{itemize}
-\end{frame}
-\begin{frame}
-    \frametitle{Uniform Noise}
-    \[ \s{U}_{\varepsilon}\br{P} = \br{1 - \varepsilon} P + \varepsilon \s{U} \]
-    \begin{center}
-        \includegraphics[width=\linewidth]{../../figures/distributions/uniform_dist_plot.pdf}
-    \end{center}
-    \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
-    % \begin{center}
-    %     \begin{tikzpicture}
-    %         \pgfmathsetmacro{\ts}{0.5}; % term spacing
-    %         \draw[] (0*\ts,0) node[]{$P_\varepsilon$};
-    %         \draw[] (1*\ts,0) node[]{$=$};
-    %         \draw[] (2*\ts,0) node[]{$(1-\varepsilon)P_{F}$};
-    %         \draw[] (3*\ts,0) node[]{$+$};
-    %         \draw[] (4*\ts,0) node[]{$\delta$};
-    %     \end{tikzpicture}
-    % \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Robust to Noise}
-    \begin{center}
-        \includegraphics[width=\linewidth]{../../figures/noise/four_rep_inequalities_uniform_noise.pdf}
-    \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Robust to Noise Zoomed}
-    \begin{center}
-        \includegraphics[width=\linewidth]{../../figures/noise/four_rep_inequalities_uniform_noise_zoomed.pdf}
-    \end{center}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Noisy Non-locality}
-    \begin{center}
-        \includegraphics[width=\linewidth]{../../figures/noise/noisy_yet_non_local_fritz.pdf}
-    \end{center}
-    \[ \probplotvalue{255, 255, 255} = 0.00133 \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Conclusions}
-    \begin{enumerate}
-        \item Inflation technique capable of producing polynomial inequalities with quantum/classical witnesses
-        \item Fritz witness-able by party-symmetric inequalities
-        \item Maximally violating distributions require non-maximally entangled states
-    \end{enumerate}
-\end{frame}
 
@@
 
-\begin{frame}[allowframebreaks]
-    \frametitle{References}
-    \printbibliography
-\end{frame}
-
-\section{Optional Slides}
-
-\begin{frame}
-    \frametitle{Notation [Optional]}
-    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
-    \begin{itemize}
-        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
-        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
-        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
-        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        % \item Marginal scenario forms a \textit{simplicial complex}
-        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
-        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
-        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
-        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
-    \end{itemize}
-    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
-    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
-    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
-    \note[item]{Marginal scenario refers to the those sets of random variables}
-    \note[item]{The complete set of random variables are the joint random variables}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Graph Theory [Optional]}
-    Let $n, m \in \nodes$ be nodes of the graph $\graph$.
-    \begin{itemize}
-        \item \term{parents of $n$}: $\Pa[\graph]{n} \defined \bc{m \mid m \to n}$
-        \item \term{children of $n$}: $\Ch[\graph]{n} \defined \bc{m \mid n \to m}$
-        \item \term{ancestry of $n$}: $\An[\graph]{n} \defined \bigcup_{i\in\mathbb{W}} \Pa[\graph][i]{n}$
-        \[ \Pa[\graph][0]{n} = n \qquad \Pa[\graph][i]{n} \defined \Pa[\graph]{\Pa[\graph][i-1]{n}} \]
-    \end{itemize}
-    Notation extends to sets of nodes $N \subseteq \nodes$,
-    \begin{itemize}
-        \item \term{parents of $N$}: $\Pa[\graph]{N} \defined \bigcup_{n\in N}\Pa[\graph]{n}$
-        \item \term{children of $N$}: $\Ch[\graph]{N} \defined \bigcup_{n\in N}\Ch[\graph]{n}$
-        \item \term{ancestry of $N$}: $\An[\graph]{N} \defined \bigcup_{n\in N}\An[\graph]{n}$
-    \end{itemize}
-    An \term{induced subgraph} of $\graph = \br{\nodes, \edges}$ due to $N \subseteq \nodes$
-    \[ \Sub[\graph]{N} = \br{N, \bc{e \in \edges \mid e \subseteq N}} \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Causal Compatibility [Optional]}
-    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
-    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
-    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
-    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
-    \begin{enumerate}
-        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
-        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
-    \end{enumerate}
-    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
-\end{frame}
-
-\begin{frame}
-    \frametitle{Deriving Inequalities [Optional]}
-    Two necessary components to compatibility:
-    \begin{enumerate}
-        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
-        \begin{itemize}
-            \item Is the marginal model contextual or non-contextual?
-            \item 3 distinct ways to tackle this problem
-            \begin{enumerate}
-                \item Convex hull, Polytope projection, Fourier-Motzkin
-                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
-                \item Linear Program Feasibility/Infeasibility
-            \end{enumerate}
-        \end{itemize}
-        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
-        \begin{itemize}
-            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
-            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
-        \end{itemize}
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Technique [Optional]}
-    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
-    \begin{definition}
-        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
-        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
-        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
-        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
-        And '$\sim$' is a \term{copy-index} equivalence relation
-        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
-    \end{definition}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Lemma [Optional]}
-    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
-    \begin{enumerate}
-        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
-        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
-        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
-        \item Construct \term{inflated causal parameters}
-        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
-        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
-        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
-    \end{enumerate}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Lemma Cont'd [Optional]}
-    \begin{itemize}
-        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
-        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
-    \end{itemize}
-    \begin{align*}
-        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}} \\
-        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
-    \end{align*}
-    \begin{itemize}
-        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
-        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Inflation Lemma Cont'd [Optional]}
-    \begin{lemma}
-        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-    \end{lemma}
-    \begin{corollary}
-        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
-    \end{corollary}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Pre-injectable Sets [Optional]}
-    \begin{itemize}
-        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
-        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
-        \item A \term{pre-injectable set} $N'$:
-        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
-        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
-        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Network Permutation Matrix [Optional]}
-    \begin{columns}
-        \column{0.6\linewidth}
-        \begin{itemize}
-            \item States and measurements in the Triangle Scenario are not aligned
-            \item Without $\netperm$, $\prob[ABC]$ would be separable
-            \item Required to align $B$'s measurement over $\Tr_{A,C}\br{\rho_{AB} \otimes \rho_{BC}}$
-            \item $\netperm$ is a $2^6 \times 2^6$ matrix
-            \item Shifts one qubit to the left
-        \end{itemize}
-        \column{0.4\linewidth}
-            \includegraphics[trim={1.0cm 1.2cm 1.0cm 1cm},clip,width=1.0\textwidth]{../../figures/perm_mtrx.pdf}
-    \end{columns}
-    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Outcomes and Events [Optional]}
-    \begin{definition}
-        Each variable $v$ has finite set of \term{outcomes} $O_v$. \\
-        Each set of variables $V$ has finite set of \term{events} $\Events{V}$:
-        \[ \Events{V} \defined \bc{s: V \to O_V \mid \forall v \in V, s\br{v} \in O_v} \]
-    \end{definition}
-    \begin{definition}
-        The set of events over the joint variables $\Events{\jointvar}$ are termed the \term{joint events}.
-    \end{definition}
-    \begin{definition}
-        The set of events over the marginal contexts are the \term{marginal events}
-        \[ \Events{\mscenario} \defined \coprod_{V \in \mscenario} \Events{V} \]
-    \end{definition}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Distribution Vectors [Optional]}
-    \begin{definition}
-        The \term{joint distribution vector} $\probvec^{\jointvar}$
-        \[ \probvec^{\jointvar}_j = \prob[\jointvar][j] \quad \forall j \in \Events{\jointvar}\]
-    \end{definition}
-    \begin{definition}
-        The \term{marginal distribution vector} $\probvec^{\mscenario}$
-        \[ \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \quad \forall m \in \Events{\mscenario}, \Dom{m} \in \mscenario\]
-    \end{definition}
-    Can now write complete marginal problem as matrix multiplication:
-    \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \iff \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \]
-\end{frame}
-
-\begin{frame}
-    \frametitle{Incidence Matrix [Optional]}
-    \begin{itemize}
-        \item \term{Incidence matrix} $M$ is a bit-wise matrix
-        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
-        \item Column-indexed by joint events $j \in \Events{\jointvar}$
-        \[ M_{m,j} = \begin{cases}
-            1 & m = j|_{\Dom{m}} \\
-            0 & \text{otherwise}
-        \end{cases} \]
-        \begin{gather*}
-        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
-        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
-        \end{gather*}
-
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Causal Symmetry [Optional]}
-    \begin{itemize}
-        \item Desirable to find compatibility inequality $I$ such that
-        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
-        \item Compatibility is independent of variable labels $I, \graph \to \varphi\bs{I}, \varphi\bs{\graph}$
-        \item Need $\varphi\bs{\graph} = \graph$ to find new $\varphi\bs{I}$
-    \end{itemize}
-    \begin{definition}
-        The \term{causal symmetry group} of causal structure $\graph$:
-        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
-        Strictly speaking, one needs to preserve observable nodes:
-        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
-    \end{definition}
-    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
-    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e.
-inequality) that is symmetric under exchange of parties}
-    \note<1>[item]{Surprisingly, it is possible to do so!}
-    \note<1>[item]{Here is how.}
-    \note<1>[item]{First, we will formally define the symmetry group in question}
-    \note<1>[item]{Causal symmetry group is the group of automorphisms on causal structure}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Causal Symmetry and Inflation [Optional]}
-    \begin{itemize}
-        \item Causal symmetry group for $\graph'$ is no good!
-        \item Not possible to deflate inequality if it's not in terms of injectable sets
-        \begin{definition}
-            The \term{restricted causal symmetry group} $\Phi$ of $\graph'$:
-            \[ \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
-        \end{definition}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Restricted Causal Symmetry of Large Inflation [Optional]}
-    \begin{itemize}
-        \item $\Phi$ for the large inflation is an order $48$ group with $4$ generators
-    \end{itemize}
-    \begin{equation*}
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_1 \\
-    A_1 &\to A_4 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_1 \\B_1 &\to B_4 \\B_2 &\to B_3 \\B_3 &\to B_2 \\B_4 &\to B_1 \\C_1 &\to C_4 \\C_2 &\to C_3 \\C_3 &\to C_2 \\C_4 &\to C_1
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_2 \\
-    A_1 &\to A_1 \\A_2 &\to A_3 \\A_3 &\to A_2 \\A_4 &\to A_4 \\B_1 &\to C_1 \\B_2 &\to C_3 \\B_3 &\to C_2 \\B_4 &\to C_4 \\C_1 &\to B_1 \\C_2 &\to B_3 \\C_3 &\to B_2 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_3 \\
-    A_1 &\to C_1 \\A_2 &\to C_2 \\A_3 &\to C_3 \\A_4 &\to C_4 \\B_1 &\to A_1 \\B_2 &\to A_2 \\B_3 &\to A_3 \\B_4 &\to A_4 \\C_1 &\to B_1 \\C_2 &\to B_2 \\C_3 &\to B_3 \\C_4 &\to B_4
-    \end{aligned}
-    \quad
-    \begin{aligned}[c]
-    &\hspace{1mm}\gep_4 \\
-    A_1 &\to A_1 \\A_2 &\to A_2 \\A_3 &\to A_3 \\A_4 &\to A_4 \\B_1 &\to B_2 \\B_2 &\to B_1 \\B_3 &\to B_4 \\B_4 &\to B_3 \\C_1 &\to C_3 \\C_2 &\to C_4 \\C_3 &\to C_1 \\C_4 &\to C_2
-    \end{aligned}
-    \end{equation*}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Symmetric Incidence [Optional]}
-    \begin{itemize}
-        \item Group orbits through repeated action of $\varphi \in \Phi$ on $m \in \Events{\mscenario}$ and $j \in \Events{\jointvar}$
-    \end{itemize}
-    \begin{align*}
-        \Phi\bs{m} &\defined \bc{\varphi\bs{m} \mid \varphi \in \Phi} \\
-        \Phi\bs{j} &\defined \bc{\varphi\bs{j} \mid \varphi \in \Phi}
-    \end{align*}
-    \begin{itemize}
-        \item Construct \term{symmetric incidence matrix} $\Phi\bs{M}$
-    \end{itemize}
-    \[ \Phi\bs{M}_{\Phi\bs{m}, \Phi\bs{j}} = \sum_{m' \in \Phi\bs{m}}\sum_{j' \in \Phi\bs{j}} M_{m',j'} \]
-    \[ \Phi\bs{M} = \La_{\Phi\bs{\Events{\mscenario}}}\tcdot M \tcdot \La_{\Phi\bs{\Events{\jointvar}}} \]
-    \begin{itemize}
-        \item $\Phi\bs{M}$ not a bit-wise matrix like $M$
-        \item For large inflation $M$ is $16,896 \times 16,777,216$
-        \item For large inflation $\Phi\bs{M}$ is $450 \times 358,120$ % 3566922 entries
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Symmetrized Fritz [Optional]}
-    \begin{center}
-        \includegraphics[width=\linewidth]{../../figures/distributions/symmetrized_fritz.pdf}
-    \end{center}
-    \begin{itemize}
-        \item More non-local yet not quantum-accessible
-        \item Quantum-accessible distributions form non-context set
-    \end{itemize}
-\end{frame}
-
-\section{Local Minima Concerns}
-
-\begin{frame}
-    \frametitle{Results [Optional]}
-    \begin{itemize}
-        \item Finding global minimum is tricky
-        \item Difficult to converge to violation
-        \item Noisy seed (Gaussian noise):
-        \[ \la_{(0)} = \la_{(F)} + \de \la \qquad \de \la_{i} \sim \s{N}\br{\mu = 0, \si^2 = (2\pi10^{\chi})^2} \]
-        \item Uniform seed:
-        \[ \la_{(0), i} \sim \s{U}\br{[0, 2\pi]} \]
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Local Minima [Optional]}
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Fritz Local Minima Zoomed [Optional]}
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Max Entangled vs. Max Violating (???) [Optional]}
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_random_seed.pdf}
-\end{frame}
-
-\begin{frame}
-    \frametitle{Max Entangled vs. Max Violating (???) [Optional]}
-    \includegraphics[width=\linewidth]{../../figures/optimizations/Max_Entanglement_vs_Max_Violation_random_seed_Zoomed.pdf}
-\end{frame}
-
 \end{document}

### 2017-09-19 old/documents/Notes/inequality_demo_temp.tex
reformat github repo

% === Revtex Declaration ===
\documentclass[aps, 10pt, english, twoside, pra, nofootinbib, tightenlines, longbibliography, superscriptaddress]{revtex4-1}

% === All of the Packages I use frequently ===
\usepackage{../../packages/document_config}
\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}

\begin{document}
    The current WagonWheel inequality we are using in the paper is the following:
    \begin{equation*}
    \begin{gathered}
        \eq
        I\tsb{WagonWheel} : \\
        + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
        - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
        - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
        - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
        - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
        - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
        - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
        - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
        - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
        - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
        - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}

    Which is currently simplified to:
    \begin{equation*}
    \begin{gathered}
    \eq
    I\tsb{WagonWheel} : \\
    + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
    - P_{ABC}(303)P_{C}(0) - P_{ABC}(313)P_{C}(0) - P_{ABC}(302)P_{C}(1) - P_{AB}(02)P_{C}(2) - \\
    - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}

    I went ahead and converted to the bit-notation and obtained the following:
    \begin{equation*}
    \begin{gathered}
    \eq
    I\tsb{WagonWheel} : \\
    - P_{A_lB_lB_r}(100) \\
    - P_{C_lC_r}(11)P_{C_lC_r}(00) \\
    + P_{A_lB_lB_rC_lC_r}(10010) \\
    + P_{A_{l}A_{r}C_lC_r}(1111)P_{C_lC_r}(00)\\
    - P_{A_lA_rB_lB_rC_lC_r}(110011)P_{C_lC_r}(00) \\
    - P_{A_lA_rB_lB_rC_lC_r}(110010)P_{C_lC_r}(01) \\
    + P_{A_lA_rB_lB_rC_lC_r}(001001)P_{C_lC_r}(10) \\
    - P_{A_lA_rB_l}(001)P_{C_lC_r}(10) \\
    + P_{A_lA_rB_lB_rC_lC_r}(000000)P_{C_lC_r}(11) \\
    \leq 0
    \end{gathered}
    \end{equation*}

    The following inequality is the one that Elie Wolfe found, and was proposed as a replacement for the paper due to its algebraic clarity.
    \begin{equation*}
    \begin{gathered}
        \eq
        I\tsb{WagonWheelAlternative} : \\
        -P_{A_{l}B_{l}}(10) \\
        +P_{A_{l}B_{l}C_{l}C_{r}}(1010) \\
        -P_{A_{l}B_{l}}(01) P_{C_{l}C_{r}}(10) \\
        -P_{C_{l}C_{r}}(00) P_{C_{l}C_{r}}(11) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) \\
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) \\
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        \leq 0
    \end{gathered}
    \end{equation*}

    There are some observations:
    \begin{itemize}
        \item $I\tsb{WagonWheel}$ in bit-notation is actually shorter than $I\tsb{WagonWheelAlternative}$
        \item The paper mentions the exact violation ($0.0129 \nleq 0$) of $I\tsb{WagonWheel}$, something I would have to calculate for $I\tsb{WagonWheelAlternative}$
    \end{itemize}

    Swapping the bits $C_{r}$ and $B_{l}$,

    \begin{equation*}
    \begin{gathered}
        \eq
        I\tsb{WagonWheelAlternativeProperSwap} : \\
        +P_{A_{l}B_{l}}(11) \\
        -P_{A_{l}B_{l}C_{l}C_{r}}(1111) \\
        +P_{A_{l}B_{l}}(00) P_{C_{l}C_{r}}(11) \\
        +P_{C_{l}C_{r}}(01) P_{C_{l}C_{r}}(10) \\
        -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) \\
        -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) \\
        -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        \leq 0
    \end{gathered}
    \end{equation*}

    The violation using $I\tsb{WagonWheelAlternativeProperSwap}$,

    \begin{align*}
        +P_{A_{l}B_{l}}(11) &= +\f{1}{4}\\
        -P_{A_{l}B_{l}C_{l}C_{r}}(1111) &= -\f{1}{4}\\
        +P_{A_{l}B_{l}}(00) P_{C_{l}C_{r}}(11) &= +\br{\f{1}{4}}^2 \\
        +P_{C_{l}C_{r}}(01) P_{C_{l}C_{r}}(10) &= +\br{\f{1}{4}}^2 \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) &= -\f{1}{4}\br{\f{1}{32}\br{2 - \sqrt{2}}} \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) &= -\f{1}{4}\br{\f{1}{32}\br{2 - \sqrt{2}}} \\
        -P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) &= -\f{1}{4}\br{\f{1}{32}\br{2 + \sqrt{2}}} \\
        -P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) &= -\f{1}{4}\br{\f{1}{32}\br{2 + \sqrt{2}}} \\
        -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) &= -\f{1}{4}\br{\f{1}{32}\br{2 + \sqrt{2}}} \\
        -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) &= -\f{1}{4}\br{\f{1}{32}\br{2 + \sqrt{2}}} \\
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) &= +\f{1}{4}\br{\f{1}{32}\br{2 + \sqrt{2}}} \\
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) &= +\f{1}{4}\br{\f{1}{32}\br{2 + \sqrt{2}}} \\
        0.0625 = \f{1}{16} \nleq 0
    \end{align*}

    If we restrict the domain of $I\tsb{WagonWheelAlternativeProperSwap}$ to only consider distributions where $C_{l} = A_{l}, C_{r} = B_{l}$ and $P_{C}$ is uniform, we obtain the following constraint,

    \begin{equation*}
    \begin{gathered}
        I\tsb{WagonWheelRestricted} : \\
        + \f{1}{2} - P_{A_{r}B_{r}C_{l}C_{r}}(0110) - P_{A_{r}B_{r}C_{l}C_{r}}(1010) - P_{A_{r}B_{r}C_{l}C_{r}}(0000) - P_{A_{r}B_{r}C_{l}C_{r}}(1100) \\
        - P_{A_{r}B_{r}C_{l}C_{r}}(0001) - P_{A_{r}B_{r}C_{l}C_{r}}(1101) + P_{A_{r}B_{r}C_{l}C_{r}}(0111) + P_{A_{r}B_{r}C_{l}C_{r}}(1011)  \leq 0
    \end{gathered}
    \end{equation*}

\end{document}

### 2017-09-19 old/figures/causal_structures/inflated_triangle_scenario_spiral_anim_2.tex
reformat github repo

--- 2016-11-19 figures/causal_structures/inflated_triangle_scenario_spiral_anim_2.tex
@@
     \begin{scope}[every node/.style=observed, onslide=<1->{fade}]
-        \node[onslide=<3>{unfade}] (C2) at ({-2 + 2*1/\ift}, {2*1/(\ift*sqrt(3))}) {$C_2$};
-        \node[onslide=<1>{unfade}] (C1) at ({-2 + 3*1/\ift}, {3*1/(\ift*sqrt(3))}) {$C_1$};
-        \node[onslide=<2>{unfade},onslide=<3>{unfade}] (B2) at ({2 - 2*1/\ift}, {2*1/(\ift*sqrt(3))}) {$B_2$};
-        \node[onslide=<2>{unfade}] (B1) at ({2 - 3*1/\ift}, {3*1/(\ift*sqrt(3))}) {$B_1$};
-        \node[onslide=<1>{unfade}] (A2) at (0, {2*sqrt(3) - 2*2/sqrt(3)*(1/\ift)}) {$A_2$};
-        \node[] (A1) at (0, {2*sqrt(3) - 3*2/sqrt(3)*(1/\ift)}) {$A_1$};
+        \node[onslide=<3>{unfade}] (C2) at ({-2 + 2*1/\ift}, {2*1/(\ift*sqrt(3))}) {$\p{C}_2$};
+        \node[onslide=<1>{unfade}] (C1) at ({-2 + 3*1/\ift}, {3*1/(\ift*sqrt(3))}) {$\p{C}_1$};
+        \node[onslide=<2>{unfade},onslide=<3>{unfade}] (B2) at ({2 - 2*1/\ift}, {2*1/(\ift*sqrt(3))}) {$\p{B}_2$};
+        \node[onslide=<2>{unfade}] (B1) at ({2 - 3*1/\ift}, {3*1/(\ift*sqrt(3))}) {$\p{B}_1$};
+        \node[onslide=<1>{unfade}] (A2) at (0, {2*sqrt(3) - 2*2/sqrt(3)*(1/\ift)}) {$\p{A}_2$};
+        \node[] (A1) at (0, {2*sqrt(3) - 3*2/sqrt(3)*(1/\ift)}) {$\p{A}_1$};
     \end{scope}
     \begin{scope}[every node/.style=latent, onslide=<1->{fade}]
-        \node[onslide=<3>{unfade}] (X2) at (-1, {sqrt(3)}) {$X_2$};
-        \node[onslide=<1>{unfade}] (X1) at ({-1 + 1/\ift}, {sqrt(3) - 1/(\ift*sqrt(3))}) {$X_1$};
-        \node[onslide=<1>{unfade}] (Y2) at (1, {sqrt(3)}) {$Y_2$};
-        \node[onslide=<2>{unfade}, onslide=<3>{unfade}] (Y1) at ({1 - 1/\ift}, {sqrt(3) - 1/(\ift*sqrt(3))}) {$Y_1$};
-        \node[onslide=<1>{unfade}, onslide=<2>{unfade}, onslide=<3>{unfade}] (Z1) at (0, 0.5) {$Z_1$};
-        \node[onslide=<2>{unfade}, onslide=<3>{unfade}] (Z2) at (0, 0) {$Z_2$};
+        \node[onslide=<3>{unfade}] (X2) at (-1, {sqrt(3)}) {$\p{X}_2$};
+        \node[onslide=<1>{unfade}] (X1) at ({-1 + 1/\ift}, {sqrt(3) - 1/(\ift*sqrt(3))}) {$\p{X}_1$};
+        \node[onslide=<1>{unfade}] (Y2) at (1, {sqrt(3)}) {$\p{Y}_2$};
+        \node[onslide=<2>{unfade}, onslide=<3>{unfade}] (Y1) at ({1 - 1/\ift}, {sqrt(3) - 1/(\ift*sqrt(3))}) {$\p{Y}_1$};
+        \node[onslide=<1>{unfade}, onslide=<2>{unfade}, onslide=<3>{unfade}] (Z1) at (0, 0.5) {$\p{Z}_1$};
+        \node[onslide=<2>{unfade}, onslide=<3>{unfade}] (Z2) at (0, 0) {$\p{Z}_2$};
     \end{scope}

### 2017-09-19 CCIAQVTS/CCIAQVTS.tex
more reformats

--- 2017-09-19 documents/TriangleScenarioArXiv/ts.tex
@@
             \centering
-            \scalebox{1.0}{\input{figures/causal_structures/bell_scenario}}
+            \scalebox{1.0}{\input{figures/causal_structures/bell_structure}}
             \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
@@
         I\tsb{Web} : \\\nonumber
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/no_symwitness_ineq_print_standalone_halfed}
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/web_ineq_standalone_halfed}
     \end{gather}
@@
     % \begin{subfigure}[b]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_2017.pdf}}
+    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise.pdf}}
     % \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
@@
     % \begin{subfigure}[b]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_2017_lims.pdf}}
+    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_lims.pdf}}
     % \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
@@
         I\tsb{SymmetricWeb} : \\\nonumber
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/MosekCertFritzSym_ineq_standalone_halfed}
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/sym_web_ineq_standalone_halfed}
     \end{gather}
@@
     \begin{nscenter}
-        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
+        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_1_max_violation.pdf}
         \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{Web}$.
@@
     \begin{nscenter}
-        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
+        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_3_max_violation.pdf}
         \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{SymmetricWeb}$.
@@
 
-    Our best numerical optimization of $I\tsb{Web}$ is visualized in\cref{fig:maximum_violation_I_1}.
+    Our best numerical optimization of $I\tsb{Web}$ is visualized in \cref{fig:maximum_violation_I_1}.
 Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution; in fact \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share their \term{possibilistic structure}.

### 2017-09-21 CCIAQVTS/CCIAQVTS.tex
updates for arxiv

@@
 
-% === All of the Packages I use frequently ===
-\usepackage{packages/document_config}
-
-% === Causal structure formatting for tikz ===
-\input{figures/causal_structures/formatting}
+% === Bibliography Style Options ===
+\bibliographystyle{apsrev4-1}
+\setlength{\bibsep}{3pt plus 3pt minus 2pt}
+
+% === Packages ===
+\usepackage{document_config}
 
@@
             \centering
-            \scalebox{1.0}{\input{figures/causal_structures/bell_structure}}
+            \scalebox{1.0}{\includegraphics{figures/causal_structures/bell_structure}}
             \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
@@
             \centering
-            \scalebox{1.0}{\input{figures/causal_structures/triangle_structure}}
+            \scalebox{1.0}{\includegraphics{figures/causal_structures/triangle_structure}}
             \caption{The Triangle structure consisting of three observable variables $A,B,C$ and three latent variables $X, Y, Z$.}
@@
     \begin{nscenter}
-        \scalebox{1.0}{\input{figures/causal_structures/triangle_structure_operational_fritz_bell}}
+        \scalebox{1.0}{\includegraphics{figures/causal_structures/triangle_structure_operational_fritz_bell}}
         \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{A},S_{B}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
@@
     % \begin{nscenter}
-    %         \scalebox{1.0}{\input{figures/causal_structures/triangle_structure_operational}}
+    %         \scalebox{1.0}{\includegraphics{figures/causal_structures/triangle_structure_operational}}
     %         \caption{The Triangle structure as modeled by quantum states and measurements.}
@@
             0 & \text{otherwise}
-        \end{cases} \]
+        \end{cases} \eq \label{eq:incidence_definition}\]
         The incidence matrix has $\abs{\Events{\jointvar}}$ columns, $\abs{\Events{\mscenario}} = \sum_{i} \abs{\Events{V_i}}$ rows and $k\abs{\Events{\jointvar}}$ non-zero entries.
@@
     \begin{subfigure}[b]{.30\linewidth}
-    \scalebox{0.65}{\input{figures/causal_structures/inflated_triangle_structure_spiral}}
+    \scalebox{0.65}{\includegraphics{figures/causal_structures/inflated_triangle_structure_spiral}}
     \caption{The Spiral inflation.}\label{fig:spiral_inflation}
@@
     \begin{subfigure}[b]{.30\linewidth}
-    \scalebox{0.65}{\input{figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
+    \scalebox{0.65}{\includegraphics{figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
     \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
@@
     \begin{subfigure}[b]{.30\linewidth}
-    \scalebox{0.65}{\input{figures/causal_structures/inflated_triangle_structure}}
+    \scalebox{0.65}{\includegraphics{figures/causal_structures/inflated_triangle_structure}}
     \caption{The Web Inflation.}\label{fig:the_web_inflation}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\input{figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
+    \scalebox{0.8}{\includegraphics{figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
     \caption{$\AnSub[\graph']{\bc{A_1}}$}\label{fig:spiral_inflation_inj1}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\input{figures/causal_structures/triangle_structure_injectable_highlight_1}}
+    \scalebox{0.8}{\includegraphics{figures/causal_structures/triangle_structure_injectable_highlight_1}}
     \caption{$\AnSub[\graph]{\bc{A}}$}\label{fig:spiral_inflation_iminj1}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\input{figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
+    \scalebox{0.8}{\includegraphics{figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
     \caption{$\AnSub[\graph']{\bc{A_2, C_1}}$}\label{fig:spiral_inflation_inj2}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\input{figures/causal_structures/triangle_structure_injectable_highlight_2}}
+    \scalebox{0.8}{\includegraphics{figures/causal_structures/triangle_structure_injectable_highlight_2}}
     \caption{$\AnSub[\graph]{\bc{A,C}}$}\label{fig:spiral_inflation_iminj2}
@@
 
-    \setlength{\bibsep}{3pt plus 3pt minus 2pt}
-    \bibliographystyle{apsrev4-1}
+    % \bibliographystyle{apsrev4-1}
     \nocite{apsrev41Control}

### 2017-12-22 CCIAQVTS/CCIAQVTS.tex
Fixed a number of typos and broken sentences.

@@
 First, the insight of \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure.
-Second, the new framework for solving causal inference problems developed by Wolfe \emph{et al.}~\cite{Inflation} called \term{The Inflation Technique}.
+Second, the new framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}.
 Ultimately, this work serves as a validation that the Inflation Technique is sensitive enough to offer new insights into quantum non-classicality \cite{Navascues_2017}.
@@
 
-    % A number of causal structures are depicted throughout this document (see \cref{fig:bell_structure,fig:triangle_structure,fig:inflations}).
-As an example, the Triangle structure has $3$ observable nodes and $3$ latent nodes,
-    % \[ \nodes_{O} = \bc{A, B, C} \qquad \nodes_{L} = \bc{X, Y, Z} \]
-    % along with $6$ edges indicating that the latent nodes $\bc{X, Y, Z}$ cause and influence the observed nodes $\bc{A, B, C}$.
-    % \[ \edges = \bc{\bc{X \to A}, \bc{Y \to A}, \bc{Y \to B}, \bc{Z \to B}, \bc{Z \to C}, \bc{X \to C}} \]
-
     Let us now formalize the notion of compatibility between a causal structure $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$.
@@
     \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:compatibility_as_factorization}\]
-    % , except its own descendants when conditioned over $\Pa[\graph]{n}$.
-This is known as the \term{local Markov property}:\footnote{Here $A \indep B \mid C$ denotes statistical independence between $A$ and $B$ conditional on $C$ where $A,B,C \subseteq \nodes$, i.e.
-for a given probability distribution $\prob[\nodes]$, $\prob[AB \mid C] = \prob[A \mid C]\prob[B \mid C]$.}
-    % \[ n \indep \br{\nodes \setminus \De[\graph]{n}} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
+
     If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:compatibility_as_factorization}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}.
@@
 If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$.
-    % The compatibility of a distribution $\prob[\nodes]$ with a causal structure $\graph$ pursuant to \cref{eq:compatibility_as_factorization} is equivalent to the requirement that $\prob[\nodes]$ obeys all of the conditional independence constraints implied by the \textit{d-separation relations} between variables/nodes in $\graph$~\cite{Pearl_2009}.
+
     When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is possible to completely determine whether or not $\prob[\nodes]$ is compatible with $\graph$ by computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}.
@@
 Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, $\prob[A|S_A,\la]$ is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that\footnote{Here the summation $\sum_{\la}$ is used to denote a statistical marginalization over the latent variable $\la$ with unspecified support.}
-    %    there exists a distribution $\prob[AB|S_AS_B,\la]$ such that $\prob[AB|S_AS_B] = \sum_{\la} \prob[AB|S_AS_B,\la]$ and also satisfies the following implementation of \cref{eq:compatibility_as_factorization}:
+
     \begin{align}\label{eq:bellcompat}
@@
 In particular,~\citet{Bell_1964} demonstrated that there exists distributions that are non-classical yet are attainable via local measurements on a shared quantum resource.
-    %If one does not wish to accept fine-tuning arguments, one must accept that quantum correlations can be non-local as no variation to the latent nodes can explain the same correlations~\cite{Wood_2012}.\footnote{This is unlike the Triangle structure wherein a global yet latent common cause is always an acceptable explanation for any correlation and does require fine-tuning.
-Therefore, we never refer to non-classical correlations in Triangle Structure as non-local.}
 
@@
 Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.
-
-    % Finally, must like any causal structure, Bell inequalities act as a measure of the non-classical character of a given distribution.
-In particular, the antecedent of \cref{eq:CHSH_ineq_orig} has a classical upper-bound of $2$ and it can be shown to have a quantum upper-bound of $2\sqrt{2}$~\cite{Cirelson_1980}.
-Furthermore, non-classical distributions that are also non-quantum such as the PR-box correlations are upper-bounded by $4$~\cite{PR_1995}.
-In \cref{sec:found_inequalities}, newly discovered and analogous inequalities for the Triangle structure are presented.
-Although their associated quantum and post-quantum upper-bounds are currently unknown, an attempt to numerical compute these is discussed in \cref{sec:optimizations}.
 
@@
     As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
-    %Here we lay out the task for discovering quantum non-classicality in the Triangle structure.
-    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that
-    %the joint distribution $\prob[\nodes] = \prob[ABCXYZ]$ is a product over the causal parameters,
-    %\[ \prob[ABCXYZ] = \prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
-    %And also, the given distribution
-    $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}, i.e.
+
+    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}, i.e.
     \[ \prob[ABC] \text{ is classically compatible with \cref{fig:triangle_structure}} \quad\iff\quad\prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z]\,.
@@
     where $\rho_{AB}, \rho_{BC}, \rho_{CA}$ are bipartite density matrices, $M_{A}, M_{B}, M_{C}$ are generic measurements sets, and $\netperm$ is a permutation matrix to align the states and measurements appropriately.
-    %For certain causal structures, the conditional independence relations provided by $d$-separation relations are a sufficient characterization of compatibility.
-Recently, \citet{Henson_2014}, classified the Triangle structure as an \textit{interesting} causal structure in the sense that conditional independence relations \textit{do not} provide a sufficient characterization of non-classicality.\footnote{Note that the Triangle structure possesses \textit{zero} conditional independence relations over the observable nodes $A, B, C$.} Moreover,
+
     The Triangle structure serves as an excellent test case for furthering our understanding of quantum non-classicality in network causal structures.
@@
     Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality.
-It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of non-classicallity are expected to correspond to novel information-theoretical quantum advantages.
+It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of non-classicality are expected to correspond to novel information-theoretical quantum advantages.
 A fundamental limitation of Fritz's proof of non-classicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
@@
 Substituting $\prob[\fritz]$ into \cref{eq:CHSH_intriangle} yields the traditional maximal quantum violation~\cite{Cirelson_1980}: $3 \br{1/\sqrt{2}} - \br{-1/\sqrt{2}} = 2\sqrt{2} \not \leq 2$.
-%Therefore, we conclude the Fritz distribution is incompatible with the Triangle structure.
-Before continuing it is worth noting that \cref{eq:fritz_dist} is non-unique.
-Nonetheless for concreteness, \cref{eq:fritz_dist} is taken as \textit{the} Fritz distribution throughout this manuscript.
-
-    It is important to understand the domain in which Fritz's proof of incompatibility is valid.
-%the details of which can found in the original work~\cite{Fritz_2012}.
-Specifically, \cref{eq:CHSH_intriangle} only acts as a valid causal compatibility inequality for the Triangle structure if there exists
-    The proof relies on the perfect correlation between $C$'s outcomes and the measurement pseudo-settings (left-bits) of $A$ and $B$.
+
+    It is important to understand the domain in which Fritz's proof of incompatibility is valid; its proof relies on the perfect correlation between $C$'s outcomes and the measurement pseudo-settings (left-bits) of $A$ and $B$.
 For example, if one combines \cref{eq:fritz_dist} with slight uniform noise, what can we say with confidence regarding if the resulting modified distribution is classical or not?
@@
 
-    % Moreover, the existence of the Fritz distribution (\cref{sec:fritz_distribution}) directly demonstrates that quantum-accessible incompatibility exists in the Triangle structure and indirectly proves the existence of causal compatibility inequalities capable of witnessing the non-classicality of the Fritz distribution.
-The Inflation Technique has been shown to completely solve the classical causal inference problem~\cite{Navascues_2017} --- indicating that these undiscovered inequalities can be generated using sufficiently complex inflations.
-The 37 inequalities in~\cite{Inflation} were derived using the Spiral inflation (\cref{fig:spiral_inflation}) and their failure motivated us to consider larger inflations such as those in \cref{fig:wagon_wheel_inflation,fig:the_web_inflation}.
-
-    % These incipient insights were sufficient for focusing the search for new inequalities sensitive enough to be violated by the Fritz distribution. \
-    % Cref{sec:found_inequalities} reports the discovery of these inequalities which expand on our understanding of non-classicality in the Triangle structure.
-As a by-product, this research illuminates the advantage in using the Inflation Technique to find inequalities for interesting causal structures in general.
-
     \section{Triangle Structure Inequalities}
@@
 By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle structure that are violated by the Fritz distribution.
-A representative trio of these $\prob[\fritz]$-incompatability-witnessing inequalities are presented here: $I\tsb{WagonWheel}$ per \cref{eq:ww_ineq}, notable for its simplicity; $I\tsb{Web}$ per \cref{eq:web_inequality}, which best witnesses the non-clasicality of $\prob[\fritz]$ in the presence of noise; and $I\tsb{SymmetricWeb}$ per \cref{eq:symmetric_web_inequality}, which is symmetric with respect to all permutations of the three parties.
+A representative trio of these $\prob[\fritz]$-incompatibility-witnessing inequalities are presented here: $I\tsb{WagonWheel}$ per \cref{eq:ww_ineq}, notable for its simplicity; $I\tsb{Web}$ per \cref{eq:web_inequality}, which best witnesses the non-classicality of $\prob[\fritz]$ in the presence of noise; and $I\tsb{SymmetricWeb}$ per \cref{eq:symmetric_web_inequality}, which is symmetric with respect to all permutations of the three parties.
 
@@
     The first causal compatibility inequality chosen for presentation is reported below:
-    % \begin{equation*}
-    % \begin{gathered}
-    %     \eq\label[ineq]{eq:ww_ineq}
-    %     I\tsb{WagonWheel} : \\
-    %     + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
-    %     - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
-    %     - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
-    %     - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
-    %     - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
-    %     - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
-    %     - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
-    %     - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
-    %     - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
-    %     - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
-    %     - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
-    % \end{gathered}
-    % \end{equation*}
     \begin{equation*}
@@
 
-    % \footnote{To aid verification: the first term in \cref{eq:ww_ineq} for the Fritz distribution is $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ while all of the remaining terms sum to $\simeq 0.0136$.}
-
-    % It is possible to simplify $I\tsb{WagonWheel}$ by identifying sets of terms such as $P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3)$ which can be simplified to $P_{ABC}(300)$ by recognizing that $P_{C}(0) + P_{C}(1) + P_{C}(2) + P_{C}(3) = 1$.
-Upon doing so, one obtains an equivalent representation for $I\tsb{WagonWheel}$,
-
-    % \begin{equation*}
-    % \begin{gathered}
-    % \eq\label[ineq]{eq:ww_ineq_symplified}
-    % I\tsb{WagonWheel} : \\
-    % + P_{ABC}(000)P_{C}(3) + P_{ABC}(021)P_{C}(2) + P_{ABC}(202) + P_{ABC}(302) + P_{ABC}(233)P_{C}(0) + P_{AC}(33)P_{C}(0) \\
-    % - P_{ABC}(303)P_{C}(0) - P_{ABC}(313)P_{C}(0) - P_{ABC}(302)P_{C}(1) - P_{AB}(02)P_{C}(2) - \\
-    % - P_{AB}(03)P_{C}(2) - P_{AB}(20) - P_{AB}(30) - P_{C}(3)P_{C}(0) \leq 0
-    % \end{gathered}
-    % \end{equation*}
-
-    % \begin{equation*}
-    % \begin{gathered}
-    % \eq\label[ineq]{eq:ww_ineq_symplified}
-    % I\tsb{WagonWheel} : \\
-    % - P_{A_lB_lB_r}(100) \\
-    % - P_{C_lC_r}(11)P_{C_lC_r}(00) \\
-    % + P_{A_lB_lB_rC_lC_r}(10010) \\
-    % + P_{A_{l}A_{r}C_lC_r}(1111)P_{C_lC_r}(00)\\
-    % - P_{A_lA_rB_lB_rC_lC_r}(110011)P_{C_lC_r}(00) \\
-    % - P_{A_lA_rB_lB_rC_lC_r}(110010)P_{C_lC_r}(01) \\
-    % + P_{A_lA_rB_lB_rC_lC_r}(001001)P_{C_lC_r}(10) \\
-    % - P_{A_lA_rB_l}(001)P_{C_lC_r}(10) \\
-    % + P_{A_lA_rB_lB_rC_lC_r}(000000)P_{C_lC_r}(11) \\
-    % \leq 0
-    % \end{gathered}
-    % \end{equation*}
-
-    % In order to understand the importance of $I\tsb{WagonWheel}$, there are a couple of important concepts to understand.
-First, the Fritz distribution was originally known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings $A_l, B_l$.
-The inequality of $I\tsb{WagonWheel}$ represents a significant advancement in our understanding of non-classicality in the Triangle structure.
-For example, $I\tsb{WagonWheel}$ is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$.
-Furthermore, the existence of an inequality capable of witnessing the non-classicality of the Fritz distribution is guaranteed and the Inflation Technique is capable of producing such an inequality~\cite{Navascues_2017}, albeit requiring a sufficiently complex inflation of the Triangle structure.
-In fact, $I\tsb{WagonWheel}$ was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and others were \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution.
-This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as $I\tsb{WagonWheel}$ strong enough to witness incompatible quantum distributions for the Triangle structure.
-More universally, this result shows that the Inflation Technique is a promising tool for understanding quantum non-classical in more general causal structures.
-
-    % The majority of these inequalities share most or all of the qualitative features of $I\tsb{WagonWheel}$, and hence those inequalities are omitted from this manuscript.
-
     \subsection{The Web Inequality}
@@
 
-    % \subsection{Noisy Distributions}
-
-    % \begin{figure}
-    % \begin{nscenter}
-    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/uniform_dist_plot.pdf}
-    %         \vspace{-0.2in}
-    %         \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
-    %         \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
-    %         \label{fig:uniform_distribution}
-    % \end{nscenter}
-    % \end{figure}
     As mentioned in \cref{sec:fritz_distribution}, this original proof of the non-classicality of $\prob[\fritz]$ required an idealistic condition to hold: perfect correlations of $C$ with $A_l, B_l$.
@@
     \end{align}
-    %
-    %The uniform-noise probability distribution is defined for three parties and four outcomes as $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} \equiv \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$\footnote{The completely noisy observation is compatible with the Triangle structure}.
-Here we quantify how much statistical noise can be added to the Fritz distribution $\prob[\fritz]$ before $I\tsb{Web}$ fails to witness incompatibility.
-The associated quantifier used was an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ where $\s{N}_{\vep}$ denotes an \term{$\vep$-noisy Fritz distribution},
-    % \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
 
@@
 Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I\tsb{Web}$; an exhaustive search has not been conducted.
-
-    % Given that $I_0, I_1, I_2, I_3$ are far from a representative inequalities and are likely not facets of any inflated marginal polytope, it is save to say that this is possible.
-
-    % \begin{figure}
-    % \begin{subfigure}[b]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise.pdf}}
-    % \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_lims.pdf}}
-    % \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
-    % \end{subfigure}
-    % \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
-    % \end{figure}
-
-    % The results of our experiments are plotted in \cref{fig:master_noise}.
-\Cref{fig:noise} illustrates that each curve $I\br{\s{N}_{\vep}\br{\prob[\fritz]}}$ as a function of $\vep$ is monotonically increasing as expected; the more noise added to the probability distribution, the more classical it becomes.
-\Cref{fig:noise_zoomed} is the same plot as \cref{fig:noise} zoomed onto the interval $\vep \in \bs{0, 0.12}$.
 
@@
 The modification of the Inflation Techniques which forces symmetry is explained in \cref{sec:symmetric_inequalities}.
-As $\prob[\fritz]$ is strongly assymetric due to the special role of $C$, we can hope that a symmetric inequality (even one which does witness $\prob[\fritz]$) might achieve its \emph{optimal} quantum violation on a distribution qualitative distinct from $\prob[\fritz]$.
+As $\prob[\fritz]$ is strongly asymmetric due to the special role of $C$, we can hope that a symmetric inequality (even one which does witness $\prob[\fritz]$) might achieve its \emph{optimal} quantum violation on a distribution qualitative distinct from $\prob[\fritz]$.
 The details of our numerical finding are discussed in \cref{sec:optimizations}.
-
-    % To reiterate, the Fritz distribution is incompatible with the Triangle structure because it assigns a unique role to one of the variables, specifically $C$.
-The asymmetry within the Fritz distribution is reflected in the asymmetry of $I\tsb{WagonWheel}$ and $I\tsb{Web}$.
-In order to discover new forms of non-classicality in the Triangle structure, it is desirable to obtain measures of non-classicality, such as inequalities, that do not admit this bias.
-In an effort to find a causal compatibility inequality qualitatively distinct from $I\tsb{WagonWheel}$ or $I\tsb{Web}$, we developed a technique to derive inequalities with certain symmetry properties such as \cref{eq:symmetric_web_inequality} which is symmetric with respect to any permutation of the variables $A, B, C$.
-These techniques are explained in \cref{sec:symmetric_inequalities}.
-Surprisingly, \cref{eq:symmetric_web_inequality} is also violated by the Fritz distribution.
 
@@
     \section{Numerical Optimization}\label{sec:optimizations}
-
-    % Causal compatibility inequalities, including those derived in \cref{sec:found_inequalities}, offer an avenue into studying quantum non-classicality.
-Ultimately, the motivation for finding these inequalities is binary: the first is to classify differing distributions by their compatibility with a given causal structure, and the second is to measure the degree in which a given distribution is non-classical.
-This approach has been well-studied in the Bell structure, where extremal non-classical correlations maximally violate Bell inequalities~\cite{PR_1995}.
-However, inequalities are just a singular example of numerous distinct measures of non-classicality~\cite[Section 5]{Vicente_2014}.
-Alternatives include measuring the non-local content, robustness to noise, or even the classical simulation cost of a given distribution.
-For previously studied causal structures, such as the Bell structure, there exists a uncertainty toward which measure of non-classicality is best.
-The inequalities derived in this report are likely \textit{not} the best measures of non-classicality because they have be curated toward the Fritz distribution.
-Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure to be found that admit quantum violations.
-In this section, two measures are used that make use of these compatibility inequalities: robustness to noise and direct numerical violation.
-
-    % To compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ into the format of \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality} where the linear combination of all terms is upper-bound by $0$.
-For each inequality $I$ and distribution $\prob$, $I\br{\prob}$ denotes the numerical value associated with this upper-bound.
-Correspondingly, $I\br{\prob} > 0$ indicates violation of $I$ while $I\br{\prob} \leq 0$ indicates satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality).
-
-    %\subsection{Numerical Optimizations}
 
@@
 Analogously, $\exp\br{i P_n \lambda_{n,m}}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $\exp\br{iP_l \lambda_{l,l}}$ fixes the global phase of $\ket{l}$.
-Finally, although not explicitly mentioned in~\cite{Spengler_2010_Unitary}, it is possible to remove the reliance on the computationally expensive matrix exponential operations~\cite{Moler_2003} in \cref{eq:spengler_unitary} and replace them with elementary trigonomentric functions in the paramaters $\la_{m,n}$.
+Finally, although not explicitly mentioned in~\cite{Spengler_2010_Unitary}, it is possible to remove the reliance on the computationally expensive matrix exponential operations~\cite{Moler_2003} in \cref{eq:spengler_unitary} and replace them with elementary trigonometric functions in the parameters $\la_{m,n}$.
 
@@
 
-    % \Cref{sec:param_quantum_dist} expounds on our parameterized of the space of quantum distributions that can be realized on the quantum Triangle structure (\cref{fig:triangle_structure_quantum_model}) pursuant to \cref{eq:quantum_model_triangle_pvms}.
-Specifically, each bipartite quantum resource is modeled $2$-qubit, $4\times 4$ density matrix and each measurement is modeled as a $4$-element projective-value measure.
-
-    % the a objective scalar function $f: \R^n \in \R$ using the following pipeline: To begin, a set of real-valued parameters $\la = \br{\la_0, \ldots, \la_n} \in \R^{n}$ are used to parameterize a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ in agreement with the quantum version of the Triangle structure in \cref{fig:triangle_structure_quantum_model}.
-Second, a $4$-outcome distribution $\prob[ABC]$ is obtained via \cref{eq:triangle_Qcompatibility} and supplanted into an inequality $I$ in homogeneous and canonical form $I\br{\prob[ABC]} \leq 0$.
-The objective value is simply the degree of violation $f = I\br{\prob[ABC]}$ and used to make adjustments to $\la$ in order to achieve largest and larger violations.
-
-    % \subsection{Parameterizing Quantum Distributions}
-    % \begin{figure}
-    % \begin{nscenter}
-    %         \scalebox{1.0}{\includegraphics{figures/causal_structures/triangle_structure_operational}}
-    %         \caption{The Triangle structure as modeled by quantum states and measurements.}
-    %         \label{fig:triangle_structure_quantum_model}
-    % \end{nscenter}
-    % \end{figure}
-    % An alternative explanation for qualitative similarities between \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} is related to the sensitively of the initial parameters to our optimization.
-Above, it was shown that our parameter space of choice was $2\pi$-periodic in all entries.
-Somewhat surprisingly, when supplied with randomly sampled initial parameters, all optimization methods consistently converged to saturating $I\tsb{Web}$ instead of violating it.
-We observed that only parameters close enough to the \textit{Fritz parameters} (i.e.
-parameters that induce the Fritz distribution) were able to achieve violation of $I\tsb{Web}$.
-
-    Since the inequalities we seek to optimily violate are polynomial, and since the space of quantum-accessible distributions is non-convex, we employ a number of optimization methods consecutivey in an attempt to avoid pitfalls associated with local minima or ill-conditioned convergence.
+    Since the inequalities we seek to optimally violate are polynomial, and since the space of quantum-accessible distributions is non-convex, we employ a number of optimization methods consecutively in an attempt to avoid pitfalls associated identifying local minima and ill-conditioned convergence.
 Specifically, the BFGS method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
@@
 The phenomena is likely due to a combination of both effects.
-
-    % Despite our varied efforts, it remains unclear whether or not our results share the same possibilistic structure as $\prob[\fritz]$ because of the inequality itself or the ill-conditioned nature of the optimization.
-More likely, this phenomena is due to a combination of both effects.
 
@@
         \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{SymmetricWeb}$.
-Notice that this distribution has precisely the same (assymetric!) possibilistic structure as the Fritz distribution, even though $I\tsb{SymmetricWeb}$ itself is symmetric with respect to permutations of the variables $A, B, C$.
+Notice that this distribution has precisely the same (asymmetric!) possibilistic structure as the Fritz distribution, even though $I\tsb{SymmetricWeb}$ itself is symmetric with respect to permutations of the variables $A, B, C$.
 }
@@
     \end{figure}
-    % \begin{figure}
-    % \begin{nscenter}
-    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/symmetrized_fritz.pdf}
-    %         \caption{An artificially-symmetrized version of the Fritz distribution, constructed by averaging the six permutations of $\prob[\fritz]$ over the variables $A, B, C$.
-While this construction significantly violates $I\tsb{SymmetricWeb}$, we have no reason to believe that this distribution should actually be achievable using quantum resources in the Triangle structure, so its role here is purely apophatic.}
-    %         \label{fig:symmetrized_fritz}
-    % \end{nscenter}
-    % \end{figure}
-
-    %To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e.
-$V_F \defined \max_{P}\bc{I\br{P}/I\br{P_F}}$.
+
     Our best numerical optimization of $I\tsb{WagonWheel}$ was found to be the Fritz distribution itself, visualized in \cref{fig:fritz_distribution_visualized}.
@@
 Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution; in fact \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share their \term{possibilistic structure}.
-A distribution's possibilistic structure is the unitization of its probabilities, i.e.
-the partitioning of events into disjoint subsets: one containing those events that occur with nonzero probability (possible), the other containing the zero-probability events (impossible).
+A distribution's possibilistic structure the partitioning of events into two disjoint subsets: one containing those events that occur with non-zero probability (possible), the other containing the zero probability events (impossible).
     That \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} have the same possibilistic structure is not entirely unexpected;  As was mentioned in \cref{sec:found_inequalities}, as $I\tsb{Web}$ was derived specifically to prove the incompatibility of the Fritz distribution with the Triangle structure.
@@
 
-    % The Gaussian perturbation was given zero mean $\mu = 0$ and variance $\si^2 = \br{2 \pi 10^{\chi}}^2$ where $\chi$ measures an order of magnitude standard deviation.
-For $I_1$, deviations of $\chi \gtrsim 1.3$ inhibited convergence to violation.
-This is depicted in \cref{fig:initial_conditions}.
-
-    % \begin{figure}
-    % \begin{subfigure}[t]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{figures/optimizations/Gaussian_Perturbation_Fritz_Color_Default.pdf}}
-    % \caption{For each iteration step $k$, the inequality target decreases.}\label{fig:initial_conditions_a}
-    % \end{subfigure}
-    % \begin{subfigure}[t]{.48\linewidth}
-    % {\centering\includegraphics[width=\linewidth]{figures/optimizations/Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}}
-    % \caption{\Cref{fig:noise} zoomed to show convergence is sensitive to initial conditions.}\label{fig:initial_conditions_b}
-    % \end{subfigure}
-    % \caption{Numerical optimizations aimed at violating causal compatibility inequalities are sensitive to initial conditions.}\label{fig:initial_conditions}
-    % \end{figure}
-
     Our best numerical optimization of $I\tsb{SymmetricWeb}$ is visualized in \cref{fig:maximum_violation_I_3}.
@@
 Since $I\tsb{SymmetricWeb}$ is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well.
-Our numerical optimization, however, failed to find \emph{any} symmetric quantum distributions capable of violating $I\tsb{SymmetricWeb}$, not even violating it suboptimally than $\prob[\fritz]$.
-The \emph{only} violations of $I\tsb{SymmetricWeb}$ appear to be by assymetric distributions.
-
-    % If it were not, one could construct a distribution that violates $I\tsb{SymmetricWeb}$ further by symmetrizing $\prob[\fritz]$ (\cref{fig:symmetrized_fritz}) by normalizing over all possible permutations of $A,B,C$.
-This distribution is also non-classical with relative violation $V_F = 3$.
-As it turns out, numerical optimizations suggest that the symmetrized Fritz distribution is \textit{not} quantum-accessible in the sense that is cannot be written as \cref{eq:triangle_Qcompatibility}.
-Therefore we conclude that the space of quantum-accessible correlations on the Triangle structure is non-convex; a reiteration of a result mentioned in~\citet{Inflation}.
+Our numerical optimization, however, failed to find \emph{any} symmetric quantum distributions capable of violating $I\tsb{SymmetricWeb}$, not even violating it sub-optimally than $\prob[\fritz]$.
+The \emph{only} violations of $I\tsb{SymmetricWeb}$ appear to be by asymmetric distributions.
 
@@
 
-    % Initially,~\citet{Branciard_2012} identified the Triangle structure as a challenging causal structure for studying non-classicality.
-Afterwards,~\citet{Henson_2014} were able to to classify the Triangle structure as \textit{interesting} which partially explains why it remains an enigma.
-Recently,~\citet{Fritz_2012} discovered the Fritz distribution as the first example of quantum non-classicality in the Triangle structure.
-In \cref{sec:fritz_distribution} the Fritz distribution was described in detail along with Fritz's Problem~\cite[Problem 2.17]{Fritz_2012}.
-Heretofore, researchers have been able to derive causal incompatibility inequalities~\cite{Inflation,Steudel_2010,Henson_2014} but unable to show that any are non-trivial in the context of quantum non-classicality.
-
-    % Using the Inflation technique, it became possible to provide a stronger proof of non-classicality than proposed by Fritz~\cite{Fritz_2012}.
-In particular, noisy variants of the Fritz distribution are provably non-classical (\cref{sec:noise}) and
     In \cref{sec:found_inequalities} we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions.
@@
 In \cref{sec:optimizations} we found quantum distributions quantitatively distinct from the Fritz's recycled-Bell's-theorem example, such that these variant distribution more strongly violate certain causal compatibility inequalities.
-
-    % In the context of Fritz's Problem, our result corresponds to a resolution to the following \textit{reinterpretation} of Fritz's original Problem:
-    % \begin{enumerate}[label=\textbf{FP.\Alph*}]
-    %     \setcounter{enumi}{0}
-    %     \item \label{r:1} Find proofs for causal incompatibility of quantum distributions on the Triangle structure that are \textit{not} reliant on perfect correlations.
-    % \end{enumerate}
-    % Ultimately, this work accomplishes two important tasks.
-First and foremost, the derivation of inequalities such as \cref{eq:ww_ineq} demonstrates the utility of the Inflation Technique specifically for quantum causal inference problems.
-The Inflation Technique was able to derive causal compatibility inequalities that admit quantum violations in the Triangle structure --- a task that no other existing techniques have succeeded at.
-In this sense, the results of \cref{sec:found_inequalities} showcase how the Inflation Technique is capable of generating new proofs of causal incompatibility specifically of quantum distributions for the Triangle structure.
-Consequently, this work strongly indicates that the Inflation Technique has the potential to solve an assortment of unsolved causal inference problems including those manifest in quantum foundations and quantum information theory.
-Secondly,
-
-    %    In spirit, however,Fritz's Problem is fundamentally concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}.
-When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state.
-In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states.
-As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.} In consideration of our resolution to \ref{r:1}, we propose an alternative reinterpretation of Fritz's Problem that are concerned more with the nature of the entanglement resource being exploited in a incompatible quantum distribution:
-
-    % \begin{enumerate}[label=\textbf{FP.\Alph*}]
-    %     \setcounter{enumi}{1}
-    %     \item \label{r:2} Find incompatible quantum distributions on the Triangle structure that require entanglement in more than one shared state.
-    % \end{enumerate}
-
-    % The question, as proposed by \ref{r:2}, is: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states?
-At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure.
-Unfortunately, this is not the case.
-By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled.
-This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings.
-Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible.
-Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes.
-In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique_summary}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations.
-These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and is a recommended focus for future research.
 
@@
 Research at Perimeter Institute is supported by the Government of Canada through the Department of Innovation, Science and Economic Development Canada and by the Province of Ontario through the Ministry of Research, Innovation and Science.
-The authors are grateful to Miguel Navascués and Denis Rosset for their insightful dicussions.
+The authors are grateful to Miguel Navascués and Denis Rosset for their insightful discussions.
     \end{acknowledgments}
@@
 By construction each marginal event $m \in \Events{\mscenario}$ is a restriction of some joint event $j \in \Events{\jointvar}$.
-    % \subsection{Linear Programs}
 
@@
     \end{nscenter}
-    % \begin{definition}
-    %     Given a causal structure $\graph$ and an inflation $\graph'$ of $\graph$, define the \term{injectable sets} in $\graph'$ and the \term{images of the injectable sets} in $\graph$, (respectively denoted $\Inj[\graph]{\graph'}$ and $\ImInj[\graph]{\graph'}$), as follows:
-    %     \begin{align*}
-    %         \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}} \\
-    %         \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph']{N'} \sim \AnSub[\graph]{N}}
-    %     \end{align*}
-    % \end{definition}
-
-    % \begin{lemma}
-    %     \label[lemma]{lem:inflation}
-    %     \term{The Inflation Lemma}~\cite[Lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$ and a marginal model $\prob^{\ImInj[\graph]{\graph'}}$ compatible with $\graph$ then all marginal models $\prob^{\Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-    % \end{lemma}
-
-    % \begin{proof}
-    %     Given that $\prob^{\ImInj[\graph]{\graph'}}$ is compatible with $\graph$, it admits a joint distribution $\prob[\nodes]$ that can be factorized into its causal parameters $\prob[\nodes] = \prod_{n \in \nodes} \prob[n\mid \Pa[\graph]{n}]$.
-Given \cref{eq:inflation_defn}, one can create a set of \textit{inflated} causal parameters by matching causal parameters according to respective copy-indices: $\forall n' \in \nodes' : \prob[n'\mid \Pa[\graph']{n'}] \defined \prob[n\mid \Pa[\graph]{n}]$.
-This uniquely induces a compatible joint distribution $\prob[\nodes']$ on $\graph'$\footnote{Of course, there exists compatible joint distributions on $\nodes'$ that can not be constructed in this manner.
-The claim is that all joint distributions that are constructed in this way are compatible.}: $\prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}]$.
-The proof is completed by demonstrating that the marginals of $\prob[\nodes']$ are members of the marginal model $\prob^{\Inj[\graph]{\graph'}}$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
-Given $N' \in \Inj[\graph]{\graph'}$ and $N \sim N'$:
-    %     \[ \sum_{\nodes' \setminus N'} \prob[\nodes'] = \sum_{\nodes' \setminus N'} \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] = \prod_{n' \in N'} \prob[n'\mid \Pa[\graph]{n'}] = \prod_{n \in N} \prob[n\mid \Pa[\graph]{n}] = \prob[N] = \prob[N']  \]
-    % \end{proof}
-
-    % The motivation behind \cref{def:inflation} is that if the ancestry of each node $n'$ in $\graph'$ plays the \textit{exact same} role as the ancestry of its source copy $n$ in $\graph$, then every compatible distribution $\prob[N]$ on $\graph$ can be used to \textit{create} compatible joint distributions on $\graph'$.
-To do this, first notice that for every distribution $\prob[N]$ compatible with $\graph$, there must exist a set of causal parameters $\{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes\}$ for $\graph$ such that $\prob[N] = \prod_{n \in N} \prob[n\mid \Pa[\graph]{n}]$.
-Since the inflation criteria (\cref{eq:inflation_defn}) requires that $\Pa[\graph']{n'} \sim \Pa[\graph]{n}$.
-    % \[ ss \eq \label{eq:inflated_causal_parameters} \]
-    % \[ \prob[\nodes'] = \prod_{n' \in \nodes'} \prob[n'\mid \Pa[\graph']{n'}] \eq \label{eq:unique_causal_parameters_inflated}\]
-
-    % % \cref{eq:unique_causal_parameters,eq:inflated_causal_parameters,eq:unique_causal_parameters_inflated}
-    % In essence, a compatible joint distribution over $\nodes$ can be \textit{inflated} to induce compatible joint distributions over $\nodes'$.
-Before generalizing this idea, a careful observation needs to be made.
-For any pair of subsets of nodes $N \subseteq \nodes$ and $N' \subseteq \nodes'$ that are equivalent up to copy-index $N \sim N'$, if $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$ then any compatible \textit{marginal} distribution $\prob[N]$, where $N \subset \nodes$, induces a compatible marginal distribution $\prob[N']$ over $N'$.
-In fact, $N'$ must contain no duplicate nodes up to copy-index and thus $\prob[N] = \prob[N']$.
-These subsets of nodes are so essential to the Inflation Technique they are assigned a special name:
-
-    % % Injectable sets are incredibly useful for causal compatibility because they permit one to inflate compatibility over a particular subset of \textit{marginal models}.
-A marginal model is compatible with a given causal structure $\graph$ if it admits a joint distribution (see \cref{sec:marginal_satisfiability}) that is compatible with $\graph$.
-
-    % % Diagrammatically, \cref{lem:inflation} can be visualized as follows:
-
-    % % \begin{nscenter}
-    % %     \begin{tikzpicture}
-    % %         \pgfmathsetmacro{\vs}{2.2};
-    % %         \pgfmathsetmacro{\hs}{5.2};
-    % %         \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
-    % %         \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
-    % %         \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
-    % %         \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
-    % %         \draw[very thick, ->] (pn) -- (cp);
-    % %         \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
-    % %         \draw[very thick, ->] (cp_) -- (pn_);
-    % %     \end{tikzpicture}
-    % % \end{nscenter}
-
-    % The inflation lemma is the most important result of the causal Inflation Technique.
-The contrapositive version of \cref{lem:inflation} is a powerful tool for deriving causal compatibility constraints.
-Any causal compatibility constraint, such as a causal compatibility inequality, that constrains injectable marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ can be \textit{deflated} into a valid compatibility constraint on marginal models $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ of the original causal structure by dropping all references to the copy-indices.
-Additionally, the inflation lemma holds when considering any subset of $\Inj[\graph]{\graph'}$ (analogously $\ImInj[\graph]{\graph'}$).
-Therefore, one only needs to consider injectable sets that are composed of \textit{observable nodes}.
 
@@
 
-    % that are used to derive inequalities using methods discussed in \cref{sec:marginal_satisfiability}.
-
-    % \begin{nscenter}
-    %     \begin{tikzpicture}[scale=0.8]
-    %         \pgfmathsetmacro{\hs}{1.4};
-    %         \pgfmathsetmacro{\vs}{0.6};
-    %         \pgfmathsetmacro{\cross}{0.2};
-    %         \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
-    %         \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
-    %         \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
-    %         \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
-    %         \draw (2*\hs, 4*\vs + 0.7*\vs) node[]{$N_1' \cup N_2' = N$};
-    %         \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
-    %         \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
-    %         \draw (0, 0) node[](b){??};
-    %         \draw[thick, ] (a) -- (ab);
-    %         \draw[thick, ] (c) -- (cd);
-    %         \draw[thick, ] (a) -- (ac);
-    %         \draw[thick, ->] (ac) -- (c);
-    %         \draw[thick, ->] (ab) -- (b);
-    %         \draw[thick, ->] (cd) -- (d);
-    %         \draw[very thick, red]
-    %         (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
-    %         (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
-    %         ;
-    %     \end{tikzpicture}
-    % \end{nscenter}
-
-    % Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{ai-expressible sets} of $\graph'$.
-
-    % A ai-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions
-    % \[  \]
-    % Application of the inflation lemma to linear inequalities constraining ai-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.
-
     \section{Deriving Inequalities from the Inflation Technique}
@@
 Now, the contextuality of a distribution $\prob[ABCD]$ should be \textit{invariant} under those permutations of the variable labels in $\jointvar$  which map the marginal scenario to itself; but not all variable relabellings preserve $\mscenario$.
-An example of a permutation which does \emph{not} preserve $\mscenario$ is the $\varphi \in \Perm{\jointvar}$\footnote{The permutation group $\Perm{S}$ over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} which acts like $\varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$.
-Then, the action of $\varphi$ on $I_{\mscenario}$ is
-    % Suppose $\varphi \in \Perm{\jointvar}$\footnote{The permutation group $\Perm{S}$ over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} is a permutation of the variables $\jointvar$ such that $\varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$.
-Intuitively $\varphi$ acts on $I_{\mscenario}$ in the following way,
+An example of a permutation $\varphi \in \Perm{\jointvar}$\footnote{The permutation group $\Perm{S}$ over a set $S$ is the set of all bijective maps $\varphi : S \to S$.} which does \emph{not} preserve $\mscenario$ is $\varphi\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$.
+The action of $\varphi$ on $I_{\mscenario}$ is
     \begin{align*}
@@
     \end{align*}
-    which yields a vali-but-irrelevant inequality, as the resulting inequality no longer pertains to  $\mscenario$%.
-In general, permutations over $\jointvar$ can modify the marginal scenario $\varphi\bs{\mscenario} \defined \bc{\varphi\bs{V_1}, \ldots, \varphi\bs{V_k}} \neq \mscenario$; this was the case for the above example.
+    which yields a valid albeit irrelevant inequality, as the resulting inequality no longer pertains to  $\mscenario$.
+%In general, permutations over $\jointvar$ can modify the marginal scenario $\varphi\bs{\mscenario} \defined \bc{\varphi\bs{V_1}, \ldots, \varphi\bs{V_k}} \neq \mscenario$; this was the case for the above example.
 Therefore $\varphi$ has capacity to modify both the terms of the inequality as well as the set of marginal models it constrains $\varphi\bs{I_{\mscenario}} = \varphi\bs{I}_{\varphi\bs{\mscenario}}$.
@@
 
-    % \section{Quantum Parameterization of Triangle structure}
-    % \label{sec:param_quantum_dist}
-    % \subsection{Unitary Group}
-    % \label{sec:unitary_group}
-    % To facilitate the parameterization of quantum states states and PVMs, a parameterization of the unitary group of dimension $d$ (denoted $\s{U}\br{d}$) by Spengler, Huber and Hiesmayr~\cite{Spengler_2010_Unitary} is introduced.
-Discussions of its application to states and measurements are deferred to \cref{sec:states} and \cref{sec:measurements} respectively.
-
-    % In Ref.~\cite{Spengler_2010_Unitary}, Spengler \textit{et al.} proved that all unitaries $U \in \s{U}\br{d}$ can be parameterized without degeneracy as follows:
-    % \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary_old} \]
-    % Where $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ form a $d \times d$ matrix of real-valued parameters with periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
-    % \[ \la = \begin{pmatrix}
-    %     \la_{1,1} & \cdots & \la_{1, d} \\
-    %     \vdots & \ddots & \vdots \\
-    %     \la_{d,1} & \cdots & \la_{d, d} \\
-    % \end{pmatrix} \]
-    % And where $P_l$ are one-dimensional projective operators,
-    % \[ P_l = \ket{l}\bra{l} \qquad 1 \leq l \leq d \eq \label{eq:projective_operator} \]
-    % and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices,
-    % \[ \sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m} \qquad 1 \leq m < n \leq d\]
-    % The SSH parameterization (\cref{eq:spengler_unitary}) is unique in that each of the real-valued parameters $\la_{n,m}$ has physical significance.
-For the sake of reference, let us label the matrix exponential terms in \cref{eq:spengler_unitary} in a manner that corresponds to their affect on an orthonormal basis $\bc{\ket{1}, \ldots, \ket{d}}$.
-    % \begin{align*}
-    % \begin{split}
-    %     GP_l &= \exp\br{iP_l \lambda_{l,l}} \\
-    %     RP_{n,m} &= \exp\br{i P_n \lambda_{n,m}} \\
-    %     R_{m,n} &= \exp\br{i \si_{m,n} \lambda_{m,n}}
-    % \end{split} \eq \label{eq:exp_terms}
-    % \end{align*}
-    % For example, $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$.
-Analogously, $RP_{n,m}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $GP_l$ fixes the global phase of $\ket{l}$.
-Possessing a parameterization that maintains this physical interpretation is useful as it allows one to readily eliminate any degeneracies.
-For the purposes of quantum distributions such as \cref{eq:triangle_Qcompatibility}, it should be clear that any contributions to global phase are irrelevant.
-The SSH parameterization becomes especially attractive because it readily permits one to drop the global phase terms by setting $\la_{l,l} = 0$ for all $l = 1, \ldots, d$.
-It is convenient to denote the set of all unitaries up to global phase considerations as $\ti {\s{U}}\br{d}$ and express $\ti {U} \in \ti {\s{U}}\br{d}$ using $d\br{d-1}$ real-valued parameters:
-    % \[ \ti U = \prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} RP_{n,m}R_{m,n}} \eq \label{eq:spengler_unitary_gp} \]
-    % Another attractive feature of the SSH parameterization not mentioned in~\cite{Spengler_2010_Unitary} is that \cref{eq:spengler_unitary}, and thus \cref{eq:spengler_unitary_gp}, can be implemented in a computationally efficient manner.
-This is discussed in \cref{sec:comp_spengler}.
-    % \subsection{Measurements}
-    % \label{sec:measurements}
-    % For each measurement set $M$ in \cref{eq:triangle_Qcompatibility}, we consider a $d$-element projective-valued measure (PVM) $M = \bc{M_1, \ldots, M_d}$ satisfying a number of familiar constraints:
-    % \begin{gather*}
-    % \forall \ket{\phi} \in \Hilb^d: \bra{\phi} M_i \ket{\phi} \geq 0 \qquad \sum_{i=1}^{d} M_i = \ident_{d} \\
-    % M_i = \ket{m_i}\bra{m_i} \qquad M_i M_j = \de_{ij} M_i
-    % \end{gather*}
-    % Therefore, parameterizing $M$ corresponds to parameterizing the set of all orthonormal basis $\bc{\ket{\psi_1}, \ldots, \ket{\psi_d}}$ of $\Hilb^d$.
-    % First note that any such basis can be transformed into the computational basis $\bc{\ket{1}, \ldots, \ket{d}}$ by a unitary denoted $U^{-1} \in \mathcal{U}\br{d}$.
-    % \[ \forall i : U^{-1} \ket{\psi_i} = \ket{i} \eq \label{eq:unitary_transform}\]
-    % With this observation, all that is required is to parameterize the set of all unitaries $U \in \mathcal{U}\br{d}$.
-Specifically, the projective property each $M_i \in M$ means that the global phase of $U$ is completely arbitrary; one only needs to consider parameterizing unitaries up to global phase using \cref{eq:spengler_unitary_gp}.
-    % \[ M = \bc{\ti U \ket{i} \bra{i} \ti U^{\dagger} \mid i \in \bc{1, \ldots, d}} \]
-    % For the purposes discussed in \cref{sec:param_quantum_dist}, only $d = 4$ outcome measurements are utilized and therefore requiring $4\br{4 - 1} = 12$ real-valued parameters.
-This method was inspired by the measurement seeding method for iterative optimization used by \citet{Pal_2010} .
-    % \subsection{States}
-    % \label{sec:states}
-
-    % Each state $\rho \in \br{\rho_{AB}, \rho_{BC}, \rho_{CA}}$ of \cref{eq:triangle_Qcompatibility} is modeled as a two-qubit density matrices acting on $\Hilb^2 \otimes \Hilb^2$.
-The space of all such states corresponds to the space of all $4\times 4$ positive semi-definite hermitian matrices with unitary trace.
-    % \[ \forall \ket{\phi} \in \Hilb^d: \bra{\phi} \rho \ket{\phi} \geq 0 \qquad \rho^{\dagger} = \rho \qquad \Tr\br{\rho} = 1 \eq \label{eq:density_matrix}\]
-    % Although is common to parameterize all such matrices using a Cholesky decomposition~\cite{Grasmair_2014}, we make use of the non-degenerate SHH parameterization~\cite{Spengler_2010_Unitary} and the spectral decomposition of $\rho$.
-Retaining full generality, consider full-rank density matrices:
-    % \[ \rho = \sum_{i=1}^{d} p_i \ket{\psi_i}\bra{\psi_i} \qquad \sum_{i=1}^{d} p_i = 1, p_i \geq 0 \eq \label{eq:param_density} \]
-    % Where $\bc{p_i}$ are the eigenvalues of $\rho$ and $\bc{\ket{\psi_i}}$ are its eigenstates.
-It is here that one recognizes the reapplication of \cref{eq:unitary_transform}: any orthonormal basis $\bc{\ket{\psi_i}}$ of $\Hilb^d$ can be transformed into a computational basis $\bc{\ket{i}}$ by a unitary transformation $U \in \mathcal{U}\br{d}$ such that $\ket{\psi_i} = U\ket{i}$.
-Analogous to the projective measurements considered in \cref{sec:measurements}, the global phase contributions are redundant.
-    % \[ \rho = \sum_{i=1}^{d} p_i \ti U\ket{i}\bra{i} \ti U^{\dagger} \]
-    % Parameterizing the eigenvalues requires $d - 1$ real-valued parameters due to the trace constraint of \cref{eq:density_matrix}.
-The eigenvalues are parameterized without degeneracy using a tuple of $d-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{d-1}}, \lambda_i \in \bs{0, 2 \pi}$ using hyper-spherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary}:
-    % \begin{align*}
-    % \eq \label{eq:convex_param}
-    % \begin{split}
-    %     p_n &= \prod_{i=1}^{n-1} \sin^2 \lambda_i \\
-    %     p_j &= \cos^2 \lambda_j \prod_{i=1}^{j-1} \sin^2 \lambda_i \quad \forall j \in 1, \ldots, n - 1
-    % \end{split}
-    % \end{align*}
-
-    % Furthermore due to the periodicity of the parameter space $\bc{\lambda}$, \cref{eq:convex_param} can be used for either constrained or unconstrained optimization problems.
-For continuity reasons, unconstrained optimizations are performed whenever possible.
-In conclusion, it is possible to parametrize all $d$-dimensional density matrices satisfying \cref{eq:density_matrix} using $d\br{d - 1} + d - 1 = d^2 -1$ real-valued parameters.
-
-    % Although non-degenerate, \cref{eq:convex_param} suffers from a lack of uniformity; a randomly sampled vector of parameters $\bc{\lambda}$ \textit{does not} translate to a randomly sampled set of eigenvalues $\bc{p_i}$.
-Another, albeit degenerate, parameterization of $\bc{p_i}$ involves beginning with $d$ real parameters $\lambda = \br{\lambda_1, \ldots, \lambda_d}$, then forcing normalization by dividing each parameter $\la_i$ by the their sum.\footnote{Strictly speaking, \cref{eq:uniform_param} \textit{also} suffers from non-uniformity; being biased toward eigenvalues that have similar values to each other.}.
-    % \[ p_j = \f{\abs{\lambda_j}}{\sum_{i=1}^{n} \abs{\lambda_i}} \quad \forall j \in 1, \ldots, n \eq \label{eq:uniform_param} \]
-    % For various optimization tasks sensitive to initial conditions outlined \cref{sec:optimizations}, the latter parameterization of \cref{eq:uniform_param} generally performed better than the former \cref{eq:convex_param}.
-    % % \subsection{Permutation Matrix}
-    % % \label{sec:perm_matrix}
-    % % \begin{figure}
-    % %     \centering
-    % %     \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{figures/perm_mtrx.pdf}
-    % %     \caption{The permutation matrix $\netperm$ acting on $\br{\Hilb^2}^{\otimes 6}$ for the Triangle structure. Black entries represents a value of $1$ and white represents $0$.}
-    % %     \label{fig:perm_mtrx}
-    % % \end{figure}
-    % % Finally, we introduce the a permutation matrix $\netperm$ for the Triangle structure.
-For bipartite qubit states, $\netperm$ is the $64\times64$ bit-wise matrix depicted in \cref{fig:perm_mtrx}.
-Upon examination of \cref{eq:quantum_model_triangle_pvms}, we consider $\netperm$ to be acting on the joint global state $\rho_{{AB}} \otimes \rho_{{BC}} \otimes \rho_{{CA}}$.
-To illuminate its necessity, consider \cref{eq:triangle_Qcompatibility} in the absence of $\netperm$.
-    % % \begin{align*}
-    % % \prob[{ABC}]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{{AB}} \otimes \rho_{{BC}} \otimes \rho_{{CA}}} \br{M^a_{{A}}\otimes M^b_{{B}} \otimes M^c_{{C}}}}\\
-    % % &= \Tr\bs{\br{\rho_{{AB}}M^a_{{A}}}\otimes\br{\rho_{{BC}}M^b_{{B}}}\otimes\br{\rho_{{CA}}M^c_{{C}}}}\\
-    % % &= \Tr\br{\rho_{{AB}}M^a_{{A}}}\Tr\br{\rho_{{BC}}M^b_{{B}}}\Tr\br{\rho_{{CA}}M^c_{{C}}}\\
-    % % &= \prob[{A}\mid \rho_{{AB}}]\br{a}\prob[{B}\mid \rho_{{BC}}]\br{b}\prob[{C}\mid \rho_{{CA}}]\br{c}
-    % % \end{align*}
-    % % On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$.
-This is analogously troubling for $B$ and $C$ as well.
-To resolve this issue, the permutation matrix $\netperm$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$.
-To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
-    % % \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
-    % % $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''.
-It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
-    % % \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
-    % \subsection{Computationally Efficient Parameterization of the Unitary Group}
-    % \label{sec:comp_spengler}
-
-    % If \cref{sec:unitary_group}, the SSH parameterization was introduced as a non-degenerate parameterization of the unitary group $\s{U}\br{d}$.
-As presented, the SSH parameterization suffers due to the presence of computationally expensive matrix exponential terms~\cite{Moler_2003}.
-Although not explicitly mentioned in~\cite{Spengler_2010_Unitary}, it is possible to remove the reliance on matrix exponential operations in \cref{eq:spengler_unitary} by utilizing the explicit form of the exponential terms in \cref{eq:exp_terms}.
-As a first step, recognize the defining property of the projective operators \cref{eq:projective_operator},
-    % \[ P_l^k = \br{\ket{l}\bra{l}}^k = \ket{l}\bra{l} = P_l \]
-    % This greatly simplifies the global phase terms $GP_l$,
-    % \[ GP_l = \exp\br{iP_l \lambda_{l,l}} = \sum_{k=0}^{\inf} \f{\br{iP_l \lambda_{l,l}}^k}{k!} = \ident + \sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}P_l^k = \ident + P_l \bs{\sum_{k=1}^{\inf} \f{\br{i \lambda_{l,l}}^k}{k!}} = \ident + P_l \br{e^{i \lambda_{l,l}} - 1} \eq \label{eq:unitary_GP} \]
-    % Analogously for the relative phase terms $RP_{n,m}$,
-    % \[ RP_{n,m} = \cdots = \ident + P_n \br{e^{i \lambda_{n,m}} - 1} \eq \label{eq:unitary_RP} \]
-    % Finally, the rotation terms $R_{m,n}$ can also be simplified by examining powers of $i \sigma_{n,m}$,
-    % \[ R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}} = \sum_{k=0}^{\inf} \f{\br{\ket{m}\bra{n} - \ket{n}\bra{m}}^k \lambda_{m,n}^k}{k!} \]
-    % One can verify that the following properties hold,
-    % \begin{align*}
-    %     \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^0 &= \ident \\
-    %     \forall k \in \N, k \neq 0 : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k} &= \br{-1}^k\br{\ket{m}\bra{m} + \ket{n}\bra{n}} \\
-    %     \forall k \in \N : \br{\ket{m}\bra{n} - \ket{n}\bra{m}}^{2k+1} &= \br{-1}^k\br{\ket{m}\bra{n} - \ket{n}\bra{m}}
-    % \end{align*}
-    % Revealing the simplified form of $R_{m,n}$,
-    % \[ R_{m,n} = \ident + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \sum_{j=1}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j}}{\br{2j}!} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sum_{j=0}^{\inf} \br{-1}^j\f{\lambda_{n,m}^{2j+1}}{\br{2j+1}!} \]
-    % \[ R_{m,n} = \ident + \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} + \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \eq \label{eq:unitary_R} \]
-    % By combining the optimizations of \cref{eq:unitary_GP,eq:unitary_RP,eq:unitary_R} together we arrive at an equivalent form for \cref{eq:spengler_unitary} that is computational more efficient.
-    % \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n}RP_{n,m}}} \cdot \bs{\prod_{l=1}^{d} GP_{l}}  \eq \label{eq:spengler_unitary_fast} \]
-
     % \bibliographystyle{apsrev4-1}

### 2017-12-22 CCIAQVTS/CCIAQVTS.tex
Reformatting everything in agreement with PRA and its upload webform and formatting, etc.

@@
             \centering
-            \scalebox{1.0}{\includegraphics{figures/causal_structures/bell_structure}}
+            \scalebox{1.0}{\includegraphics{figure_bell_structure.pdf}}
             \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
@@
             \centering
-            \scalebox{1.0}{\includegraphics{figures/causal_structures/triangle_structure}}
+            \scalebox{1.0}{\includegraphics{figure_triangle_structure.pdf}}
             \caption{The Triangle structure consisting of three observable variables $A,B,C$ and three latent variables $X, Y, Z$.}
@@
     \begin{nscenter}
-        \scalebox{1.0}{\includegraphics{figures/causal_structures/triangle_structure_operational_fritz_bell}}
+        \scalebox{1.0}{\includegraphics{figure_triangle_structure_operational_fritz_bell.pdf}}
         \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{A},S_{B}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
@@
     \begin{nscenter}
-            \includegraphics[scale=0.6]{figures/distributions/fritz_dist_plotted_bits.pdf}
+            \includegraphics[scale=0.6]{figure_fritz_dist_plotted_bits.pdf}
             \vspace{-0.2in}
@@
         I\tsb{Web} : \\\nonumber
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/web_ineq_standalone_halfed}
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{ineq_web_ineq_standalone_halfed.pdf}
     \end{gather}
@@
     \begin{nscenter}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/noise/noisy_yet_non_local_fritz.pdf}
+            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figure_noisy_yet_non_local_fritz.pdf}
             \vspace{-0.2in}
@@
         I\tsb{SymmetricWeb} : \\\nonumber
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/sym_web_ineq_standalone_halfed}
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{ineq_sym_web_ineq_standalone_halfed.pdf}
     \end{gather}
@@
     \begin{nscenter}
-        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_1_max_violation.pdf}
+        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figure_plotted_dist_I_1_max_violation.pdf}
         \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{Web}$.
@@
     \begin{nscenter}
-        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_3_max_violation.pdf}
+        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figure_plotted_dist_I_3_max_violation.pdf}
         \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{SymmetricWeb}$.
@@
     \begin{subfigure}[b]{.30\linewidth}
-    \scalebox{0.65}{\includegraphics{figures/causal_structures/inflated_triangle_structure_spiral}}
+    \scalebox{0.65}{\includegraphics{figure_inflated_triangle_structure_spiral.pdf}}
     \caption{The Spiral inflation.}\label{fig:spiral_inflation}
@@
     \begin{subfigure}[b]{.30\linewidth}
-    \scalebox{0.65}{\includegraphics{figures/causal_structures/inflated_triangle_structure_wagon_wheel}}
+    \scalebox{0.65}{\includegraphics{figure_inflated_triangle_structure_wagon_wheel.pdf}}
     \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
@@
     \begin{subfigure}[b]{.30\linewidth}
-    \scalebox{0.65}{\includegraphics{figures/causal_structures/inflated_triangle_structure}}
+    \scalebox{0.65}{\includegraphics{figure_inflated_triangle_structure.pdf}}
     \caption{The Web Inflation.}\label{fig:the_web_inflation}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\includegraphics{figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_1}}
+    \scalebox{0.8}{\includegraphics{figure_inflated_triangle_structure_spiral_injectable_highlight_1.pdf}}
     \caption{$\AnSub[\graph']{\bc{A_1}}$}\label{fig:spiral_inflation_inj1}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\includegraphics{figures/causal_structures/triangle_structure_injectable_highlight_1}}
+    \scalebox{0.8}{\includegraphics{figure_triangle_structure_injectable_highlight_1.pdf}}
     \caption{$\AnSub[\graph]{\bc{A}}$}\label{fig:spiral_inflation_iminj1}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\includegraphics{figures/causal_structures/inflated_triangle_structure_spiral_injectable_highlight_2}}
+    \scalebox{0.8}{\includegraphics{figure_inflated_triangle_structure_spiral_injectable_highlight_2.pdf}}
     \caption{$\AnSub[\graph']{\bc{A_2, C_1}}$}\label{fig:spiral_inflation_inj2}
@@
     \begin{subfigure}[b]{.23\linewidth}
-    \scalebox{0.8}{\includegraphics{figures/causal_structures/triangle_structure_injectable_highlight_2}}
+    \scalebox{0.8}{\includegraphics{figure_triangle_structure_injectable_highlight_2.pdf}}
     \caption{$\AnSub[\graph]{\bc{A,C}}$}\label{fig:spiral_inflation_iminj2}

### 2018-01-10 CCIAQVTS/CCIAQVTS.tex
Improved the flow a tiny bit

@@
 Throughout history, every aspect of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the non-classical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}.
-Motivated by past successes, a primal objective of modern quantum information theory is the discovery of new situations wherein quantum mechanics offers an advantage, and certification that the quantum advantage is genuine.
+Motivated by past successes, a primal objective of modern quantum information theory is to discover new situations wherein quantum mechanics offers an advantage, and certification that the quantum advantage is genuine.
 
@@
 Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}.
-The enumeration of Bell inequalities has since become a widespread systematic way of demonstration the \textit{non-classicality} of a given observation.
+The enumeration of Bell inequalities has since become a widespread systematic method for demonstrating the \textit{non-classicality} of a given observation.
 More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}.
@@
 A sample of such inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality}.
-In \cref{sec:violations_noise} we quantify the robustness to noise of the Fritz distribution, and we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to seek out new new flavors of non-classicality in the Triangle structure.
-Additionally, the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.
+In \cref{sec:violations_noise} the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.
+Additionally, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to seek out new flavors of non-classicality in the Triangle structure.
 \Cref{sec:conclusions} concludes with proposed avenues for further research.
@@
 In quantum theory, however, we require strong, more sensitive, causal inference techniques.
-This is because the equality constraints satisfied by classical correlations (compatible with some classical causal structure) are also all satisfied by quantum correlations (generated by the quantumified causal structure in which latent variables are replaced with shared entanglement) \cite{Henson_2014}.
+This is because the equality constraints satisfied by compatible classical correlations are also all satisfied by quantum correlations \cite{Henson_2014}.
     Our focus, therefore, in on deriving \emph{inequality} constraints (over $\prob[\nodes_{O}]$ and its marginals) implied by a causal structure, which we term \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons.
@@
 
-    The bipartite Bell structure (\cref{fig:bell_structure}) refers to an iconic causal structure involving two distant parties who observe the outcomes of local measurements as random variables $A (B)$ determined by their individual measurement settings $S_A (S_B)$, and where the parties are also presumed to be commonly informed by some shared latent resource $\la$~\cite{Brunner_2013}.
-The resulting observable correlations hence naturally form a conditional probability distribution $\prob[AB|S_AS_B]$.
-Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, $\prob[A|S_A,\la]$ is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that\footnote{Here the summation $\sum_{\la}$ is used to denote a statistical marginalization over the latent variable $\la$ with unspecified support.}
+    The bipartite Bell structure (\cref{fig:bell_structure}) refers to an iconic causal structure involving two distant parties who observe the outcomes of local measurements as random variables $A,B$ determined by their individual measurement settings $S_A,S_B$, and where the parties are also presumed to be commonly informed by some shared latent resource $\la$~\cite{Brunner_2013}.
+The observed correlations naturally form a conditional probability distribution $\prob[AB|S_AS_B]$.
+Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, $\prob[AB|S_AS_B]$ is compatible with \cref{fig:bell_structure} if and only if there exists some distribution $\prob[\la]$ and causal parameters $\prob[A|S_A,\la]$, $\prob[B|S_B,\la]$ such that\footnote{Here the summation $\sum_{\la}$ is used to denote a statistical marginalization over the latent variable $\la$ with unspecified support.}
 
     \begin{align}\label{eq:bellcompat}
-     \prob[AB|S_AS_B] \text{ is classically compatible with \cref{fig:bell_structure}} \quad\iff \quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\,.
+     \prob[AB|S_AS_B] \text{ is classically compatible with \cref{fig:bell_structure}} \quad\iff \quad \prob[AB|S_AS_B] = \sum_{\la} \prob[A|S_A,\la]\prob[B|S_B,\la]\prob[\la]\,.
     \end{align}
@@
 
-    Let us now contrast now the classical definition of compatibility with its quantum generalization.
+    Let us now contrast the classical definition of compatibility with its quantum generalization.
 Quantum correlation arise from a quantumified version of the causal structure, in which latent variables are replaced with quantum systems.
@@
 
-    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}, i.e.
+    Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum_{X,Y,Z}$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}, i.e.
     \[ \prob[ABC] \text{ is classically compatible with \cref{fig:triangle_structure}} \quad\iff\quad\prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z]\,.
@@
     \[ \prob[ABC] \text{ is a quantum realization of \cref{fig:bell_structure}} \quad\iff\quad\prob[ABC] = \Tr\bs{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm M_{A}\otimes M_{B} \otimes M_{C}}\,, \eq \label{eq:triangle_Qcompatibility} \]
-    where $\rho_{AB}, \rho_{BC}, \rho_{CA}$ are bipartite density matrices, $M_{A}, M_{B}, M_{C}$ are generic measurements sets, and $\netperm$ is a permutation matrix to align the states and measurements appropriately.
+    where $\rho_{AB}, \rho_{BC}, \rho_{CA}$ are bipartite density matrices, $M_{A}, M_{B}, M_{C}$ are generic measurements sets, and $\netperm$ is a permutation matrix to align the underlying tensor structure of the states and measurements appropriately.
 
@@
 Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure.
-In particular, the inequalities of Ref.
-\cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is non-classical, it is also non-quantum.
+In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is non-classical, it is also non-quantum.
 The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
@@
 That is to say, it was unknown if any inequality known for the Triangle structure might be useful for distinguishing quantum distributions from their classical counterparts.
-In \Cref{sec:preliminary_research} we report on attempts to utilize these inequalities to search for incompatible distributions that are also quantum-accessible.
+\Cref{sec:preliminary_research} reports our attempt to utilize these aforementioned inequalities to search for incompatible distributions that are also quantum-accessible.
 The subsequent failure of these approaches effectively motivates the remainder of this work.
@@
 
-    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the previously-published compatibility inequalities of Ref.~\cite{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014} (which had also been investigated numerically independently by \citet{Weilenmann_2016}).
+    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the previously-published compatibility inequalities of~\cite{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014} (which had also been investigated numerically independently by \citet{Weilenmann_2016}).
 This preliminary investigation did not yield interesting solutions, as none of those inequalities were violated by any 2-outcome coarse-graining of the Fritz distribution.
@@
 To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}.
-    Aside from increasing outcome cardinality, we are also forced to consider larger inflations than those analyzed in Ref.~\cite{Inflation}.
+    Aside from increasing outcome cardinality, we are also forced to consider larger inflations than those analyzed in~\cite{Inflation}.
 This is because we found the smaller inflations considered there --- such as the Spiral inflation depicted in \cref{fig:spiral_inflation} --- were simply \textit{unable} to witness the incompatibility of the Fritz distribution, even when analyzed explicitly using four possible outcomes for every observable variable.
@@
 Indeed, we will show that the previous pair of $I\tsb{WagonWheel}$ and $I\tsb{Web}$, which were both specifically curated to demonstrate the incompatibility of $\prob[\fritz]$, apparently achieve maximum quantum violation on distribution very similar to $\prob[\fritz]$ itself.
-    To avoid the chasing our own tail in the numerical optimization we require an objective function which is \emph{not} tailor-designed to witness $\prob[\fritz]$.
+
+    In order for the numerical optimization to avoid distributions similar to $\prob[\fritz]$ we require an objective function which is \emph{not} tailor-designed to witness $\prob[\fritz]$.
 Finding such an inequality proved extremely challenging; while we could generate thousands of inequalities using the Inflation Technique~\cite{Inflation}, it appeared than only a vanishingly-small fraction of those inequalities admitted quantum violation whatsoever.
@@
 
-    It is perhaps curious, however, that the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:triangle_Qcompatibility} are restricted to maximally entangled states.
-This distributions certainly violate $I\tsb{Web}$ more than $\prob[\fritz]$, even it is isn't the global maximum of $I\tsb{Web}$.
+    It is perhaps curious, however, that violation achieved by the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:triangle_Qcompatibility} are restricted to maximally entangled states.
 This finding of more-violation with less-entanglement resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} demonstrating that entanglement and non-classicality are different resources.
@@
 We imagine that advantages from a resource perspective might be critical to establish such a novelty signature.
-    Perhaps another signature would be if the distribution can arise in the Triangle structure only through the use of of entangled measurements, such as perhaps the conjecture in Ref.
-\cite{Gisin_2017}.
+    Perhaps another signature would be if the distribution can arise in the Triangle structure only through the use of of entangled measurements, such as perhaps the conjecture in \cite{Gisin_2017}.
 Ultimately, given any said classifier, it remains unclear whether or not such distributions even exist.

### 2018-01-10 CCIAQVTS/CCIAQVTS.tex
cover letter first draft complete

@@
 Throughout history, every aspect of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the non-classical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}.
-Motivated by past successes, a primal objective of modern quantum information theory is to discover new situations wherein quantum mechanics offers an advantage, and certification that the quantum advantage is genuine.
+Motivated by past successes, a primal objective of modern quantum information theory is to discover new situations wherein quantum mechanics offers an advantage, and to certify that the quantum advantage is genuine.
 

### 2018-01-10 documents/PRACoverLetter/PRACoverLetter.tex
cover letter first draft complete

\documentclass[12pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}
\usepackage{lmodern}
\begin{document}
\begin{letter}{Physical Review A (PRA)}
{\fontfamily{lmss}\selectfont
\opening{Dear Editorial Board and Journal Staff,}

We hereby submit our manuscript, "Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure".

% Paragraph 1: Why look for non-classical, quantum correlations?

A necessary ingredient of any manifestly quantum technology is the exploitation of some quantum phenomena which fails to be emulated by classical resources. Inherently, the advantage of quantum resources is their ability to violate correlation constraints satisfied by all classical correlations. A primal objective of quantum information theory and quantum foundations is to discover new and practical situations wherein quantum theory offers an advantage and to quantify that advantage via inequality constraints. Developing tools which solve this foundational problem in turn enhance out ability to assess the limitations and capabilities of quantum computational algorithms and quantum communication protocols.

% Paragraph 2: The Triangle Structure and the long-standing unsolved problem.

Arguably the most prominent scenario in which such inequality constraints have been derived is the Bell structure, for which the inequalities are known as Bell inequalities. The Bell structure consists of two distant parties each making measurements on their respective portions of a shared bipartite state. The focus of the present submission is to progress our understanding of analogous constraints for a superficially simple structure called the Triangle structure wherein three parties arrange themselves in a triangle and each make measurements on respective portions of three bipartite states. Despite numerous attempts by other authors, finding inequalities constraining classical correlations for the Triangle structure which admit violations by quantum resources as heretofore remained a long-standing open problem.

% Paragraph 3: Achievements of this submission.

This submission provides a resolution to this problem, by reporting the derivation of several polynomial inequalities for the Triangle structure which, importantly, are violated by quantum resources. Three qualitatively distinct inequalities are reported in the document for discussion. These inequalities constitute the first verification of genuine non-classical behaviour in the Triangle structure, promoting its exploitation for quantum technologies. Moreover, we demonstrate that these inequalities are suitable measures of non-classicality for experimental correlations as they are robust to a suitable degree of noise.

% Paragraph 4: Future outlook.

Perhaps of chief importance, new methods and tools where developed in pursuit of obtaining these results. In particular, these inequalities were derived using a novel technique for solving general causal inference problems known as the Inflation Technique. This submission demonstrates that the Inflation Technique has leading utility for studying and identifying genuine quantum correlations in more involved scenarios and consequently, in the discovery of new quantum resources.

In consideration of the aforementioned achievements and insights, we are confident this submission meets PRA's standards.

Sincerely,

Thomas C. Fraser and Elie Wolfe
}
\end{letter}

\end{document}

### 2018-01-10 documents/PRACoverLetter/PRACoverLetter.tex
Elie's modifications to the cover letter

@@
 
-We hereby submit our manuscript, "Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure".
+We hereby submit our manuscript, “Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure”.
 
-% Paragraph 1: Why look for non-classical, quantum correlations?
+A necessary ingredient of any manifestly quantum technology is the capitalization of some quantum phenomenon which cannot be emulated by classical resources.
+Consequently, a foundational objective of quantum information theory is the characterization of situations wherein quantum resources offer unique advantages.
+Our manuscript concerns the exceptionally paradigmatic ability of quantum theory to violate certain constraints which are satisfied by all classical correlations.
 
-A necessary ingredient of any manifestly quantum technology is the exploitation of some quantum phenomena which fails to be emulated by classical resources.
-Inherently, the advantage of quantum resources is their ability to violate correlation constraints satisfied by all classical correlations.
-A primal objective of quantum information theory and quantum foundations is to discover new and practical situations wherein quantum theory offers an advantage and to quantify that advantage via inequality constraints.
-Developing tools which solve this foundational problem in turn enhance out ability to assess the limitations and capabilities of quantum computational algorithms and quantum communication protocols.
+The dual practices of deriving classically-inviolable inequality constraints, and quantifying their violation by quantum resources, have proven enormously effective in the development of quantum computational algorithms and quantum communication protocols.
+The first situation studied in this manner consisted of two distant parties each making measurements on their respective portions of a shared bipartite state; the pertinent inequalities there being the famous Bell inequalities.
+This specific type of cataloging of quantumness – of which the violation of Bell inequalities is emblematic – has since been extended to other situations involving multiple parties, sharing multiple states in a variety of configurations.
 
-% Paragraph 2: The Triangle Structure and the long-standing unsolved problem.
+However, a particular configuration of state-sharing, technically-termed “cyclic”, has proven heretofore intractable.
+The simplest cyclic situation is the “Triangle” structure, wherein three parties each make measurements on respective portions of three bipartite states.
+Although a variety of classically-inviolable inequalities for the Triangle structure have been derived in the last few years, none of those initial inequalities could be shown to admit violation by quantum resources.
+Identifying a quantumly-violable yet classically-inviolable inequality for the Triangle structure has persisted as a longstanding and vexing open problem, despite numerous attempts by other authors.
 
-Arguably the most prominent scenario in which such inequality constraints have been derived is the Bell structure, for which the inequalities are known as Bell inequalities.
-The Bell structure consists of two distant parties each making measurements on their respective portions of a shared bipartite state.
-The focus of the present submission is to progress our understanding of analogous constraints for a superficially simple structure called the Triangle structure wherein three parties arrange themselves in a triangle and each make measurements on respective portions of three bipartite states.
-Despite numerous attempts by other authors, finding inequalities constraining classical correlations for the Triangle structure which admit violations by quantum resources as heretofore remained a long-standing open problem.
+Our submission provides resolution to this problem.
+We derive several classically-inviolable inequalities for the Triangle structure which are demonstrably violated by quantum resources.
+We discuss three qualitatively-distinct inequalities in particular.
+A consequence of our derivation is that – for the first time – it is now possible to robustly verify manifestly quantum behaviors in the Triangle structure.
+As such, our submission opens the door for the Triangle structure to be capitalized in quantum technologies.
 
-% Paragraph 3: Achievements of this submission.
+Moreover, the pursuit of our results also sheds informative light on lesser-known mathematical methods.
+For instance, in deriving our inequalities we utilized the so-called “Inflation Technique” for solving general causal inference problems.
+The Inflation Technique was developed for the explicit purpose of identifying manifestly quantum behaviors; our manuscript is the first practical validation that the technique is indeed capable of doing so.
 
-This submission provides a resolution to this problem, by reporting the derivation of several polynomial inequalities for the Triangle structure which, importantly, are violated by quantum resources.
-Three qualitatively distinct inequalities are reported in the document for discussion.
-These inequalities constitute the first verification of genuine non-classical behaviour in the Triangle structure, promoting its exploitation for quantum technologies.
-Moreover, we demonstrate that these inequalities are suitable measures of non-classicality for experimental correlations as they are robust to a suitable degree of noise.
-
-% Paragraph 4: Future outlook.
-
-Perhaps of chief importance, new methods and tools where developed in pursuit of obtaining these results.
-In particular, these inequalities were derived using a novel technique for solving general causal inference problems known as the Inflation Technique.
-This submission demonstrates that the Inflation Technique has leading utility for studying and identifying genuine quantum correlations in more involved scenarios and consequently, in the discovery of new quantum resources.
-
-In consideration of the aforementioned achievements and insights, we are confident this submission meets PRA's standards.
+In consideration of the aforementioned achievements and insights contributed by our manuscript, we are confident that this submission meets PRA’s high standards of substantiveness and significance.
+In preparing this submission for PRA, we have taken care to write the text in a deliberate style that is both clear and comprehensive.
 
 Sincerely,
-
 Thomas C. Fraser and Elie Wolfe

### 2018-03-06 documents/Referee Responses/refereeresponses.tex
Added first draft of referee responses.

% === Revtex Declaration ===
\documentclass[aps, 10pt, twoside, pra, tightenlines, superscriptaddress, notitlepage]{revtex4-1}

% === Bibliography Style Options ===
\bibliographystyle{apsrev4-1}
\setlength{\bibsep}{3pt plus 3pt minus 2pt}

% \usepackage{xcolor}
\usepackage{tabularx}
\usepackage{document_config}
\newcounter{refereecounter}
\newcounter{commentcounter}[refereecounter]
\newcommand{\getcommentlabel}{\underline{\textbf{\arabic{refereecounter}.\arabic{commentcounter}}}}
\newcommand{\refereecommentformat}[1]{\textcolor{darkgray}{#1}}

\newcommand{\refereeresponse}[2]{
    \stepcounter{commentcounter}
    \begin{tabularx}{\textwidth}{rl}
        \multicolumn{1}{m{0.8cm}}{\getcommentlabel}
        &
        \multicolumn{1}{p{0.92\textwidth}}{\refereecommentformat{#1}}
        \\
        &
        \multicolumn{1}{p{0.92\textwidth}}{#2}
        \\
    \end{tabularx}
}
\setlength{\parindent}{0pt}

\begin{document}
    \title{Causal compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure [Referee Responses]}
    \author{Thomas C. Fraser}
    \email{tfraser@perimeterinstitute.ca}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \maketitle

    \stepcounter{refereecounter}
    \section{Responses to First Referee}

    \refereeresponse{This work considers the derivation of tests for discriminating classical correlations from non-classical correlations in a three-party scenario in which causal influences are pairwise shared between all three players. Hence it is a "triangle scenario". The authors apply the recently developed inflation technique to derive several new inequalities satisfied by all classical correlations in the triangle scenario. Next, they numerically study the ability of quantum theory to violate them. A quantum distribution that doesn't have a classical model has previously known -- Fritz's distribution. This distribution has a central role for how the authors approach the problem. In particular they manage to derive inequalities, robust to a small amount of noise, that detect Fritz's distribution, and some `similar' quantum distributions.}{}

    \refereeresponse{This is a long and quite technical paper. Having read it, I understand that it is directed at a specialist audience knowledgeable on causal inference and/or network Bell inequalities. The comments that follow are made with this specialized audience in mind.}{}

    \refereeresponse{As the original work, presented in sections VI to VIII, is heavy based on numeric and the computer-implemented inflation technique, I have not considered it reasonable to try to check the correctness of any derivations or numerical claims. I simply trust the authors on this matter.}{}

    \refereeresponse{I think the paper is well-written. I had no troubles understanding the messages the authors presumably wished to convey. However, the paper is quite long. Therefore, I think it would benefit from a short and clear summary of what the main contribution of this paper is, and what the outlook is. This appears currently in the conclusions. However, I think it is worth outlining this much earlier in the paper, so that a reader knows what to expect from the long read. Practically, I am proposing that the part of the introduction in which the structure of the paper is presented, is expanded or supplemented.}{}

    \refereeresponse{In general I appreciate this type of thorough basic research on a poorly understood topic by, due to currently lack of deep understanding, non-rigorous methods. I think it provides useful hints and shows the potential usefulness of the inflation technique for future work in this direction. By now, I believe it is well-established that it is a difficult matter to study quantum correlations in the triangle scenario. Therefore consider this type of investigations relevant.}{}

    \refereeresponse{I consider this paper suitable for PRA, since many previous works on quantum networks have been published here and therefore the right audience will probably notice it. I recommend it for publication, given that my more detailed comments, appearing below, are taken into consideration before either being (partially) addressed or discarded with a good motivation.}{}

    \refereeresponse{Regarding section VI. What is previously known about the inequalities of [21] and and [19]? Has nobody studied or attempted to violate these before? If yes, what were the results? I would be a bit surprised if triangle inequalities were derived but attempted to be violated by some super-classical model. Basically, I think it would be good to put the numerics for these inequalities into a bit more of a context.}{}

    \refereeresponse{In addition, I am a bit puzzled by the following comment "These early results suggest that there is no quantum-classical gap in the Triangle structure for two-outcome measurements". Although I am personally prepared to believe this for various reasons, I do not see how the numerical study of the particular inequalities of [21] and [19] justifies it? Disregarding that (what I understand is) optimization from the interior of the quantum set, cannot prove the correctness (indeed only “suggest” the correctness) of such a statement, one would still need to know a thing or two about the properties of the inequalities considered. For example, the classical set is non-convex so there is no notion of a facet. Are the inequalities in [21] and [19] `optimal', so that the inability to violate them somehow indicates the lack of a quantum advantage for any inequality? If yes, what would it mean that an inequality in a non-convex setting is optimal? Furthermore, is it uniquely optimal, or can there be other unknown optimal inequalities where we could find a quantum violation? In summary, I wonder whether the claim is properly motivated.}{}

    \refereeresponse{Regarding the new inequalities. Do the authors have some intuition for what type of inflations leads to interesting inequalities? It is stated that larger inflations were needed, as compared to those of ref [21]. Is it the case that the larger the inflation, the stronger the inequality? Furthermore, as far as I understand, a given inflations leads to many possible inequalities. Is there natural way to identify the interesting inequalities, or must check them one by one to find the interesting results? Again, if the authors have developed further intuition for such practically relevant matters of how to best use inflation, it would be good to mention it in the main text.}{}

    \refereeresponse{Regarding genuine quantum triangle correlations. I fully agree with the authors that the Fritz distribution is manufactured to fit the triangle scenario based on the well-known CHSH violations. Indeed, this is not a genuine triangle correlation. This is sufficient to convince a reader that not all quantum violations of a triangle inequality are qualitatively interesting. However, an important issue would be to define what it means that a quantum triangle correlation is not based on Bell's theorem. The authors inherit this question from the work of Fritz. Although agreeing with the intuition, I think the intuition for this question is not yet sufficiently developed to be phrased as a meaningful question. Basically, what does it mean for a general probability distribution in the triangle not to be based on Bell's theorem?}{}

    \refereeresponse{The authors have derived a triangle inequality with a quantum violation that is not identical to the Fritz distribution. Nevertheless, they make the following comment (in the conclusions):}{}

    \refereeresponse{"Despite these advancements, the distributions we discovered hew closely to the Fritz distribution, indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure. Currently, it remains speculative about how to recognize whether-or-not a given distribution for the Triangle structure exhibits non-classical correlations of a fundamentally novel qualitative nature than Bell-type non-classicality."}{}

    \refereeresponse{The inability to address my above question (what does it mean for triangle correlations not to be based on Bell's theorem?) hinders the authors to make a clear conclusion about their not-identical-but-quite-similar-to-Fritz's distribution. I would consider this an important question since it is essential to how strong a conclusion can be drawn from one of the key result of the paper. I am mildly surprised that the authors did not make an effort to at least partially address this matter. Perhaps the question could (at least) be rigorously formulated, i.e., a reasonable definition could be provided for what it means for triangle correlations not to be based on Bell's theorem. However, without knowing how such a definition may look, I suspect that resolving the question will not be straightforward. Nevertheless, it may be worth it for the authors to draw some attention to this poorly defined but clearly relevant idea.}{}

    \stepcounter{refereecounter}
    \section{Responses to Second Referee}

    \refereeresponse{This paper reports on the use of the inflation technique to derive inequalities for the triangle causal structure that admit quantum violations. The triangle causal structure is a well-studied example and seems to be resistant to being solved elegantly. The authors make progress on this difficult problem, while still not getting to an elegant solution. However, the progress they make is interesting and qualitatively different to before, since the inequalities found are the first that are known to have quantum violations (there are many existing inequalities not known to have such violations).}{}

    \refereeresponse{I am happy to recommend this be accepted subject to minor changes.}{}

    \refereecommentformat{More detailed remarks/comments/questions:}

    \refereecommentformat{Introduction:}

    \refereeresponse{It is perhaps a bit strong to claim that *every* aspect of quantum phenomena that is non classical had led to practical exploitation for computation or communication. [note the typo "of"-\textgreater"or" shortly before [4]]}
    {Agreed. Typo corrected. Modified sentence: ``Throughout history, numerous quantum phenomena which fail to be emulated by classical physics have been identified as resources for solving computational or communicational problems.''}

    \refereeresponse{Sentence "This work is the first therefore...", should perhaps say "known" rather than "able"}
    {Corrected.}

    \refereeresponse{Related to the same paragraph, isn't is implied by [22] that such inequalities must exist in principle? Is one conclusion of the present paper that one doesn't have to go too far down the inflation chain to find one?}{}

    \refereecommentformat{Sec II:}

    \refereeresponse{Sentence "Specifically, the causal structure G hypothesizes..." has grammatical issues.}
    {Agreed. Modified sentence: ``A causal structure $\graph$ hypothesizes that each variable $n \in \nodes$ is only directly influenced by its parents $\Pa[\graph]{n}$.''.}

    \refereeresponse{Near the end of Sec II, "complete characterization for any causal structure": this remark clashed with a later remark on p5 that Bell's structure has a "complete classification of classicality".}{}

    \refereecommentformat{Sec III:}

    \refereeresponse{typo "asses"-\textgreater"assess"}
    {Corrected.}

    \refereeresponse{In (2) there is a P\_lambda missing after the sum.}
    {This is a typo in the ArXiv submission and has was corrected for our PRA submission.}

    \refereecommentformat{Sec V:}

    \refereeresponse{Perhaps change "We close this loophole..." to "This loophole is closed..." to make clear this is not a new idea here.}
    {Corrected: ``This loophole is closed by having...''.}

    \refereecommentformat{Sec VII A:}

    \refereeresponse{Last paragraph, maybe write P\_ABC as P\_\{A\_lA\_rB\_lB\_rC\_lC\_r\} or mention equivalence: if I understand correctly, the alphabet size must be 4 for each of A, B and C to use (11).}{}

    \refereeresponse{typo "distribution very similar to P\_F itself" -\textgreater "distributions"}
    {Corrected.}

    \refereeresponse{Do you have any insights as to why the particular inflations considered turn out to be useful? Do you have any insight as to which inflations are likely to be useful?}{}

    \refereeresponse{I'm not sure the figures of distributions are presented in the best way: given that (if I understand correctly) there are only 3 different values in Fig 5, for example, why not just state these individually (like is done for the white value) rather than give the scale of values.}{}

    \refereecommentformat{Sec VIII:}

    \refereeresponse{"..initial parameters such that the initial point of the optimization was close to P\_F.": can you say more about what "close" means? Were all parameters varied or only the nonzero parameters?}{}

    \refereeresponse{"...violating it suboptimally than P\_F.": reword}
    {Reworded sentence: ``To the contrary, out numerical optimization failed to find any symmetric quantum distributions capable of violating $I_{\text{SymmetricWeb}}$''.}

    \refereecommentformat{Conclusions:}

    \refereeresponse{Perhaps it is misleading to say that no noise is tolerated by Fritz's argument: his argument works for noisy entangled states (provided CHSH is still violated). Perhaps it is less obvious what happens when noise occurs elsewhere, but the other parts need only classical resources to realize in which case noise is less problematic. I would also imagine that even if it not literally robust as written that it could be made robust fairly easily.}{}

    \refereeresponse{grammar: "a causal compatibility inequalities"}
    {Corrected: ``...it was demonstrated that these causal compatibility inequalities are robust to noise...''.}

    \refereeresponse{"advantages from a resource perspective": it isn't clear to me what you are referring to, so please add some explanation or reword.}{}

    \refereeresponse{p14 typo: "which be solved"}
    {Corrected: ``...which can be solved efficiently...''.}

    % \nocite{apsrev41Control}
    % \bibliography{references}

\end{document}

### 2018-03-06 CCIAQVTS/CCIAQVTS.tex
Added first draft of referee responses.

@@
 In the realm of secure communication, quantum protocols --- a popular example being Quantum Key Distribution~\cite{Bennett_2014} --- are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill.
-Throughout history, every aspect of quantum phenomena which fails to be emulated by classical resources has led to a practical exploitation of the non-classical feature in order to solve a some computational of communicational problem~\cite{Neilsen_Chaung_2011}.
+Throughout history, numerous quantum phenomena which fail to be emulated by classical physics have been identified as resources for solving computational or communicational problems~\cite{Neilsen_Chaung_2011}.
 Motivated by past successes, a primal objective of modern quantum information theory is to discover new situations wherein quantum mechanics offers an advantage, and to certify that the quantum advantage is genuine.
@@
 
-    This work is the first, therefore, to find causal compatibility inequalities for the Triangle structure that are able to be violated by quantum-accessible distributions.
+    This work is the first, therefore, to find causal compatibility inequalities for the Triangle structure that are known to be violated by quantum-accessible distributions.
 This accomplishment was made possible through the combination of two previous developments.
@@
     Let us now formalize the notion of compatibility between a causal structure $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$.
-Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$.
-Specifically, the causal structure $\graph$ hypothesizes that if each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$.
+A causal structure $\graph$ hypothesizes that each variable $n \in \nodes$ is only directly influenced by its parents $\Pa[\graph]{n}$.
 Therefore, if each variable is conditioned on its parentage, the probability distribution $\prob[\nodes]$ should factorize accordingly:
@@
     \label{sec:bell_structure}
-    This section aims to define the Bell causal structure and to review some of the traditional witnesses used to asses the classicality (or lack thereof) of distributions relative to it.
+    This section aims to define the Bell causal structure and to review some of the traditional witnesses used to assess the classicality (or lack thereof) of distributions relative to it.
 The purpose of this section is to equip readers with the pertinent background and also to draw comparisons between the advancements made toward understanding non-classicality of the Bell structure versus analogous results obtained for Triangle structure later in this work.
@@
 Relaxing the assumption of measurement independence opens up a possible loophole, namely the possibility that the auxiliary outcomes $S_{A}, S_{B}$ of Alice and Bob might be manipulated via dependence on their shared latent variable $\lambda$.
-We close this loophole by having the third party in the Triangle structure, Charlie, \emph{also} report the latent variables $S_{A}, S_{B}$ as a multivariate outcome.
+This loophole is closed by having the third party in the Triangle structure, Charlie, \emph{also} report the latent variables $S_{A}, S_{B}$ as a multivariate outcome.
 In this manner, the perfect correlation of $C$'s record of $S_{A}, S_{B}$ with the records of $S_{A}$ reported by $A$ and of $S_{B}$ reported by $B$ testifies to the independence of $S_{A}, S_{B}$ from $\lambda$.
@@
 Of course, if some inequality achieves its optimal quantum violation on a distribution qualitatively similar to $\prob[\fritz]$, then such an inequality is unlikely to lead us to discover non-classicality of a type different than $\prob[\fritz]$.
-Indeed, we will show that the previous pair of $I\tsb{WagonWheel}$ and $I\tsb{Web}$, which were both specifically curated to demonstrate the incompatibility of $\prob[\fritz]$, apparently achieve maximum quantum violation on distribution very similar to $\prob[\fritz]$ itself.
+Indeed, we will show that the previous pair of $I\tsb{WagonWheel}$ and $I\tsb{Web}$, which were both specifically curated to demonstrate the incompatibility of $\prob[\fritz]$, apparently achieve maximum quantum violation on distributions very similar to $\prob[\fritz]$ itself.
 
@@
     Our best numerical optimization of $I\tsb{SymmetricWeb}$ is visualized in \cref{fig:maximum_violation_I_3}.
-Counter-intuitively, this distribution --- which violates $I\tsb{SymmetricWeb}$ considerably better than $\prob[\fritz]$ --- \emph{still} shares its possibilistic structure with the Fritz distribution!
-Since $I\tsb{SymmetricWeb}$ is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well.
-Our numerical optimization, however, failed to find \emph{any} symmetric quantum distributions capable of violating $I\tsb{SymmetricWeb}$, not even violating it sub-optimally than $\prob[\fritz]$.
-The \emph{only} violations of $I\tsb{SymmetricWeb}$ appear to be by asymmetric distributions.
+Counter-intuitively, the distribution in \cref{fig:maximum_violation_I_3} --- which achieves a greater violation of $I\tsb{SymmetricWeb}$ than $\prob[\fritz]$ --- shares its \textit{possibilistic} structure with the Fritz distribution!
+Additionally, since $I\tsb{SymmetricWeb}$ is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well.
+To the contrary, out numerical optimization failed to find \emph{any} symmetric quantum distributions capable of violating $I\tsb{SymmetricWeb}$.
 
@@
 
-    In \cref{sec:noise} we demonstrated that a causal compatibility inequalities is robust to noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's perfect-correlation example.
+    In \cref{sec:noise} it was demonstrated that these causal compatibility inequalities are robust to noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's perfect-correlation example.
 In \cref{sec:optimizations} we found quantum distributions quantitatively distinct from the Fritz's recycled-Bell's-theorem example, such that these variant distribution more strongly violate certain causal compatibility inequalities.
@@
     A marginal model $\prob^{\mscenario}$ is said to be \textit{contextual} if it \textit{does not} admit a joint distribution and \textit{non-contextual} otherwise.
-Notice that \cref{eq:def:marginal_problem} is inherently a linear system of constraints which be solved rather efficiently using linear programs.
+Notice that \cref{eq:def:marginal_problem} is inherently a linear system of constraints which can be solved efficiently using linear programs.
 In consideration of this, we will now endeavor to discuss how to cast the \cref{eq:def:marginal_problem} as a matrix multiplication equation so that it becomes possible to discuss existing methods for deriving constraints on the set of contextual marginal models.

### 2018-06-07 documents/Referee Responses/refereeresponses.tex
First completed draft of the referee responses

@@
 % === Revtex Declaration ===
-\documentclass[aps, 10pt, twoside, pra, tightenlines, superscriptaddress, notitlepage]{revtex4-1}
+\documentclass[]{article}
 
-% === Bibliography Style Options ===
-\bibliographystyle{apsrev4-1}
-\setlength{\bibsep}{3pt plus 3pt minus 2pt}
-
-% \usepackage{xcolor}
-\usepackage{tabularx}
 \usepackage{document_config}
@@
 \newcounter{commentcounter}[refereecounter]
-\newcommand{\getcommentlabel}{\underline{\textbf{\arabic{refereecounter}.\arabic{commentcounter}}}}
-\newcommand{\refereecommentformat}[1]{\textcolor{darkgray}{#1}}
+\newcommand{\getcommentlabel}{Comment \textbf{\arabic{refereecounter}.\arabic{commentcounter}}}
+\newcommand{\getresponselabel}{Response \textbf{\arabic{refereecounter}.\arabic{commentcounter}}}
+\usepackage[margin=0.5in]{geometry}
 
-\newcommand{\refereeresponse}[2]{
+\newcommand{\ccomment}[1]{
+    \vspace{1em}
     \stepcounter{commentcounter}
-    \begin{tabularx}{\textwidth}{rl}
-        \multicolumn{1}{m{0.8cm}}{\getcommentlabel}
-        &
-        \multicolumn{1}{p{0.92\textwidth}}{\refereecommentformat{#1}}
-        \\
-        &
-        \multicolumn{1}{p{0.92\textwidth}}{#2}
-        \\
-    \end{tabularx}
+    \getcommentlabel \\
+    \textcolor{darkgray}{\rule{\linewidth}{0.5pt}}
+    \color{gray}
+    #1
+    \color{black}
+}
+\newcommand{\response}[1]{
+    \vspace{1em}
+    \getresponselabel \\
+    \textcolor{darkgray}{\rule{\linewidth}{0.5pt}}
+    #1
 }
@@
 \begin{document}
-    \title{Causal compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure [Referee Responses]}
-    \author{Thomas C. Fraser}
-    \email{tfraser@perimeterinstitute.ca}
-    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
-    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
-    \author{Elie Wolfe}
-    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
-    % \email{ewolfe@perimeterinstitute.ca}
-    \date{\today}
-    \maketitle
+    \begin{center}
+        \textbf{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure} \\
+        \textbf{[Referee Responses]} \\
+        Thomas C. Fraser and Elie Wolfe \\
+        Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5 \\
+        University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1\\
+        June 7, 2018
+    \end{center}
 
@@
 
-    \refereeresponse{This work considers the derivation of tests for discriminating classical correlations from non-classical correlations in a three-party scenario in which causal influences are pairwise shared between all three players.
+    \ccomment{This work considers the derivation of tests for discriminating classical correlations from non-classical correlations in a three-party scenario in which causal influences are pairwise shared between all three players.
 Hence it is a "triangle scenario".
@@
 This distribution has a central role for how the authors approach the problem.
-In particular they manage to derive inequalities, robust to a small amount of noise, that detect Fritz's distribution, and some `similar' quantum distributions.}{}
+In particular they manage to derive inequalities, robust to a small amount of noise, that detect Fritz's distribution, and some `similar' quantum distributions.}
 
-    \refereeresponse{This is a long and quite technical paper.
+    \ccomment{This is a long and quite technical paper.
 Having read it, I understand that it is directed at a specialist audience knowledgeable on causal inference and/or network Bell inequalities.
-The comments that follow are made with this specialized audience in mind.}{}
+The comments that follow are made with this specialized audience in mind.}
 
-    \refereeresponse{As the original work, presented in sections VI to VIII, is heavy based on numeric and the computer-implemented inflation technique, I have not considered it reasonable to try to check the correctness of any derivations or numerical claims.
-I simply trust the authors on this matter.}{}
+    \ccomment{As the original work, presented in sections VI to VIII, is heavy based on numeric and the computer-implemented inflation technique, I have not considered it reasonable to try to check the correctness of any derivations or numerical claims.
+I simply trust the authors on this matter.}
 
-    \refereeresponse{I think the paper is well-written.
+    \ccomment{I think the paper is well-written.
 I had no troubles understanding the messages the authors presumably wished to convey.
@@
 However, I think it is worth outlining this much earlier in the paper, so that a reader knows what to expect from the long read.
-Practically, I am proposing that the part of the introduction in which the structure of the paper is presented, is expanded or supplemented.}{}
+Practically, I am proposing that the part of the introduction in which the structure of the paper is presented, is expanded or supplemented.}
 
-    \refereeresponse{In general I appreciate this type of thorough basic research on a poorly understood topic by, due to currently lack of deep understanding, non-rigorous methods.
+    \response{
+        Fantastic suggestion; we have updated and adjusted the introduction to make the contributions of this paper more clear to the reader in two ways.
+First, when summarizing the organization of the manuscript, we make it explicit that the first half is dedicated to a review of previous works, while the second half includes the contributions made by the research.
+Second, when delineating the precise contributions made by the second half of the paper, we provide an overview of the main purposes for deriving these inequalities and how we explored their utility.
+The language used now more closely mirrors that of the conclusions.
+Hopefully, readers familiar, at least, with the subject matter of Bell inequalities will be able to comprehend the nature of the advancements made by this work from the introduction alone.
+    }
+
+    \ccomment{In general I appreciate this type of thorough basic research on a poorly understood topic by, due to currently lack of deep understanding, non-rigorous methods.
 I think it provides useful hints and shows the potential usefulness of the inflation technique for future work in this direction.
 By now, I believe it is well-established that it is a difficult matter to study quantum correlations in the triangle scenario.
-Therefore consider this type of investigations relevant.}{}
+Therefore consider this type of investigations relevant.}
 
-    \refereeresponse{I consider this paper suitable for PRA, since many previous works on quantum networks have been published here and therefore the right audience will probably notice it.
-I recommend it for publication, given that my more detailed comments, appearing below, are taken into consideration before either being (partially) addressed or discarded with a good motivation.}{}
+    \ccomment{I consider this paper suitable for PRA, since many previous works on quantum networks have been published here and therefore the right audience will probably notice it.
+I recommend it for publication, given that my more detailed comments, appearing below, are taken into consideration before either being (partially) addressed or discarded with a good motivation.}
 
-    \refereeresponse{Regarding section VI.
+    \ccomment{Regarding section VI.
 What is previously known about the inequalities of [21] and and [19]?
@@
 I would be a bit surprised if triangle inequalities were derived but attempted to be violated by some super-classical model.
-Basically, I think it would be good to put the numerics for these inequalities into a bit more of a context.}{}
+Basically, I think it would be good to put the numerics for these inequalities into a bit more of a context.}
 
-    \refereeresponse{In addition, I am a bit puzzled by the following comment "These early results suggest that there is no quantum-classical gap in the Triangle structure for two-outcome measurements".
-Although I am personally prepared to believe this for various reasons, I do not see how the numerical study of the particular inequalities of [21] and [19] justifies it?
-Disregarding that (what I understand is) optimization from the interior of the quantum set, cannot prove the correctness (indeed only “suggest” the correctness) of such a statement, one would still need to know a thing or two about the properties of the inequalities considered.
+    \response{
+    An excellent comment, thank you. We have elected to add more historical context to Section VI. Specifically, the first paragraph now reads,
+
+    ``As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations (in search of violation) against the previously-published compatibility inequalities of Wolfe et al.
+[21], as well as against the entropic inequalities of Henson et al.
+[19].
+For historical context, the entropic inequalities of [19] have already been independently investigated for quantum incompatibility by Weilenmann and Colbeck [20] using a variety of computational methods.
+Unfortunately, these methods failed to identify quantum-accessible distributions capable of violating any of the entropic inequalities considered by [20].
+Additionally, the inequalities presented in [21] have not been previously investigated numerically.''
+
+    For even more context (excluded from Section VI for brevity), entropic inequality constraints for the Triangle structure first appeared in Fritz, Chaves [40], but a completed list of all Shannon-type entropic inequalities could not be computed due to the computational limitations of Fourier Motzkin.
+In Chaves, Luft, and Gross [17], these computational limitations were overcame using all conditional independence constraints to pre-process the Fourier Motzkin procedure and produced two new entropic inequalities.
+To the best of our knowledge, attempts to violate these inequalities using computational methods first appeared in [20].
+    }
+
+    \ccomment{In addition, I am a bit puzzled by the following comment "These early results suggest that there is no quantum-classical gap in the Triangle structure for two-outcome measurements".
+Although I am personally prepared to believe this for various reasons, I do not see how the numerical study of the particular inequalities of [21] and [19] justifies it?}
+
+    \response{
+    You are correct.
+Strictly speaking, the numerical failings are inconclusive.
+The purpose of the `conjecture' was to narratively motivate the shift to larger-outcome inequalities.
+The document reflects this change of perspective:
+
+    ``Unfortunately, these early results are inconclusive for two reasons.
+First, an exhaustive search would need to consider the possibility of larger Hilbert spaces for the shared quantum states.
+Second, there is little reason to suggest that the inequalities considered in [21] are complete; it is possible there are other constraints on two outcome distributions for the Triangle structure yet to be discovered.
+
+    Nonetheless, having seen no quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for \emph{non}-classical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.''
+    }
+
+    \ccomment{ Disregarding that (what I understand is) optimization from the interior of the quantum set, cannot prove the correctness (indeed only “suggest” the correctness) of such a statement, one would still need to know a thing or two about the properties of the inequalities considered.
 For example, the classical set is non-convex so there is no notion of a facet.
@@
 Furthermore, is it uniquely optimal, or can there be other unknown optimal inequalities where we could find a quantum violation?
-In summary, I wonder whether the claim is properly motivated.}{}
+In summary, I wonder whether the claim is properly motivated.}
 
-    \refereeresponse{Regarding the new inequalities.
+    \response{
+        Excellent question.
+Evidently, the notion of a facet breaks down when the set of classical correlations no longer forms a polytope.
+The Triangle structure is an instance of this breakdown.
+Nonetheless, new results due to Rosset, Wolfe (https://arxiv.org/abs/1709.00707) reveal that it is possible to generalize the notion of an 'optimal' inequality.
+
+        Explicitly, in 1709.00707, it was proven that the set of compatible classical distributions for any causal network (including the Triangle structure) forms a semi-algebraic set; meaning that there exists a \textit{finite} list of inequality and equality constraints that are necessary and sufficient for accessing compatibility.
+Therefore, an inequality belonging to this necessary and sufficient set may be considered as optimal.
+Geometrically, an inequality is considered `tight' if its intersection with the classical/compatible set is full-dimensional.
+
+        Determining whether or not any given inequality is optimal in this sense is still poorly understood and certainly worthy or further research.
+For the sake of brevity, we elected to include the following sentence to Section VI.
+
+        ``Second, there is little reason to suggest that the inequalities considered in [21] are complete; it is possible there are other constraints on two outcome distributions for the Triangle structure yet to be discovered.''
+    }
+
+    \ccomment{Regarding the new inequalities.
 Do the authors have some intuition for what type of inflations leads to interesting inequalities?
@@
 Is there natural way to identify the interesting inequalities, or must check them one by one to find the interesting results?
-Again, if the authors have developed further intuition for such practically relevant matters of how to best use inflation, it would be good to mention it in the main text.}{}
+Again, if the authors have developed further intuition for such practically relevant matters of how to best use inflation, it would be good to mention it in the main text.}
 
-    \refereeresponse{Regarding genuine quantum triangle correlations.
+    \response{
+        Excellent questions.
+Your intuition is correct, larger inflations lead to stronger inequalities.
+This is proven in [22] by demonstrating that the Inflation Technique is capable of completely solving the causal compatibility problem.
+Explicitly, if a distribution is incompatible with a causal structure, then there exists a sufficiently large inflation capable of generating an inequality which witnesses its incompatibility.
+Nonetheless, the inequalities derived in the paper came from relatively small inflations.
+Our revision of the paper now expands on this point,
+
+        ``The Inflation Technique is known to completely solve the causal compatibility problem through increasing orders of inflations [22].
+Consequently, the derivation of Ineqs.
+(13,15,12) is guaranteed by [22] for sufficiently large inflations.
+Nonetheless, the following inequalities were obtained using the relatively small inflations found in Fig.
+8.''
+
+        In a footnote,
+        ``Note that the adjectives large and small used to describe an inflation only become well-defined in the context of the hierarchy proposed in [22].
+For example, the Web Inflation in Fig.
+8c is second in the hierarchy of [22] whereas the Wagon-Wheel Inflation in Fig.
+8b is somewhere between the first and second order.''
+
+        Regarding the generation of many possible inequalities, you are correct.
+In the absence of a particular distribution, the Inflation Technique yields a plethora of inequalities, many of which are redundant (strictly speaking, this problematic feature is shared among many inequality-deriving techniques which use linear (or non-linear) quantifier elimination).
+If the objective is to identify which of the non-redundant inequalities admit quantum violations, the best method (for the moment) is to check them one by one.
+However, in this paper we used a method (explained in Appendix C) for deriving inequalities in the presence of a particular distribution, namely the Fritz distribution.
+This method only produces inequalities which by construction are violated by the Fritz distribution already; therefore we avoid having to distinguish the interesting inequalities from the uninteresting ones.
+As such, the task of eliminating uninteresting inequalities never naturally arises in this paper.
+Moreover, the original Inflation paper [21] addresses most of these concerns and comments in a more universal setting (i.e.
+for any causal structure, not just the Triangle structure), and consequently, we have found it best to omit the topic from this paper.
+    }
+
+    \ccomment{Regarding genuine quantum triangle correlations.
 I fully agree with the authors that the Fritz distribution is manufactured to fit the triangle scenario based on the well-known CHSH violations.
@@
 Although agreeing with the intuition, I think the intuition for this question is not yet sufficiently developed to be phrased as a meaningful question.
-Basically, what does it mean for a general probability distribution in the triangle not to be based on Bell's theorem?}{}
+Basically, what does it mean for a general probability distribution in the triangle not to be based on Bell's theorem?}
 
-    \refereeresponse{The authors have derived a triangle inequality with a quantum violation that is not identical to the Fritz distribution.
-Nevertheless, they make the following comment (in the conclusions):}{}
+    \response{
+        See our response to \textbf{1.14}.
+    }
 
-    \refereeresponse{"Despite these advancements, the distributions we discovered hew closely to the Fritz distribution, indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure.
-Currently, it remains speculative about how to recognize whether-or-not a given distribution for the Triangle structure exhibits non-classical correlations of a fundamentally novel qualitative nature than Bell-type non-classicality."}{}
+    \ccomment{The authors have derived a triangle inequality with a quantum violation that is not identical to the Fritz distribution.
+Nevertheless, they make the following comment (in the conclusions):}
 
-    \refereeresponse{The inability to address my above question (what does it mean for triangle correlations not to be based on Bell's theorem?) hinders the authors to make a clear conclusion about their not-identical-but-quite-similar-to-Fritz's distribution.
+    \ccomment{"Despite these advancements, the distributions we discovered hew closely to the Fritz distribution, indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure.
+Currently, it remains speculative about how to recognize whether-or-not a given distribution for the Triangle structure exhibits non-classical correlations of a fundamentally novel qualitative nature than Bell-type non-classicality."}
+
+    \ccomment{The inability to address my above question (what does it mean for triangle correlations not to be based on Bell's theorem?) hinders the authors to make a clear conclusion about their not-identical-but-quite-similar-to-Fritz's distribution.
 I would consider this an important question since it is essential to how strong a conclusion can be drawn from one of the key result of the paper.
@@
 However, without knowing how such a definition may look, I suspect that resolving the question will not be straightforward.
-Nevertheless, it may be worth it for the authors to draw some attention to this poorly defined but clearly relevant idea.}{}
+Nevertheless, it may be worth it for the authors to draw some attention to this poorly defined but clearly relevant idea.}
 
+    \response{
+        This comment \textbf{1.14} and the above comment \textbf{1.11} will be answered here.
+
+        Determining whether or not a given quantum correlation incompatible with the Triangle structure expresses genuine, novel forms of non-classicality is, at the moment, not yet a sufficiently developed decision problem as you mention.
+Moreover, we completely agree that is worth drawing attention to this clearly relevant idea.
+As such, we have included in the paper submission a new section that precedes the conclusion titled Revisiting Fritz's Problem.
+In this section, we consider a few avenues for formalizing this idea, and point out a deficiency for each.
+Ultimately, this additional section fails to rigorously reformulate Fritz's problem, but at least provides the reader with an understanding for the importance of doing so.
+    }
+
+    \clearpage
     \stepcounter{refereecounter}
@@
 
-    \refereeresponse{This paper reports on the use of the inflation technique to derive inequalities for the triangle causal structure that admit quantum violations.
+    \ccomment{This paper reports on the use of the inflation technique to derive inequalities for the triangle causal structure that admit quantum violations.
 The triangle causal structure is a well-studied example and seems to be resistant to being solved elegantly.
 The authors make progress on this difficult problem, while still not getting to an elegant solution.
-However, the progress they make is interesting and qualitatively different to before, since the inequalities found are the first that are known to have quantum violations (there are many existing inequalities not known to have such violations).}{}
+However, the progress they make is interesting and qualitatively different to before, since the inequalities found are the first that are known to have quantum violations (there are many existing inequalities not known to have such violations).}
 
-    \refereeresponse{I am happy to recommend this be accepted subject to minor changes.}{}
+    \ccomment{I am happy to recommend this be accepted subject to minor changes.}{}
 
-    \refereecommentformat{More detailed remarks/comments/questions:}
+    \ccomment{
+    More detailed remarks/comments/questions:
 
-    \refereecommentformat{Introduction:}
+    Introduction:
 
-    \refereeresponse{It is perhaps a bit strong to claim that *every* aspect of quantum phenomena that is non classical had led to practical exploitation for computation or communication.
-[note the typo "of"-\textgreater"or" shortly before [4]]}
-    {Agreed.
+    It is perhaps a bit strong to claim that *every* aspect of quantum phenomena that is non classical had led to practical exploitation for computation or communication.
+[note the typo "of"-\textgreater"or" shortly before [4]]
+    }
+
+    \response{Agreed.
 Typo corrected.
@@
 
-    \refereeresponse{Sentence "This work is the first therefore...", should perhaps say "known" rather than "able"}
-    {Corrected.}
+    \ccomment{Sentence "This work is the first therefore...", should perhaps say "known" rather than "able"}
 
-    \refereeresponse{Related to the same paragraph, isn't is implied by [22] that such inequalities must exist in principle?
-Is one conclusion of the present paper that one doesn't have to go too far down the inflation chain to find one?}{}
+    \response{Corrected.}
 
-    \refereecommentformat{Sec II:}
+    \ccomment{Related to the same paragraph, isn't is implied by [22] that such inequalities must exist in principle?
+Is one conclusion of the present paper that one doesn't have to go too far down the inflation chain to find one?}
 
-    \refereeresponse{Sentence "Specifically, the causal structure G hypothesizes..." has grammatical issues.}
-    {Agreed. Modified sentence: ``A causal structure $\graph$ hypothesizes that each variable $n \in \nodes$ is only directly influenced by its parents $\Pa[\graph]{n}$.''.}
+    \response{
+        Correct, [22] proves that some inequality will be found at some sufficiently high order in the inflation hierarchy.
+The inflations consider in this paper are all relatively low on the hierarchy.
+However, when one expects to find an inequality (if there is one) is still poorly understood.
+For example, in [28] there is a $4$-outcome distribution for the Triangle structure which is conjectured to be incompatible and yet it passes the second order inflation tests failed by the Fritz distribution.
+The following addition is made to Section V II:
 
-    \refereeresponse{Near the end of Sec II, "complete characterization for any causal structure": this remark clashed with a later remark on p5 that Bell's structure has a "complete classification of classicality".}{}
+        ``The Inflation Technique is known to completely solve the causal compatibility problem through increasing orders of inflations [22].
+Consequently, the derivation of Ineqs.
+(13,15,12) is guaranteed by [22] for sufficiently large inflations.
+Nonetheless, the following inequalities were obtained using the relatively small inflations found in Fig.
+8.
+This efficiency is not universally guaranteed; for comparison, we remark that unlike the Fritz distribution, the conjectured incompatibility of the 4-outcome distribution proposed by [28] is not confirmed by Inflation Technique at the same level.''
 
-    \refereecommentformat{Sec III:}
+        See also response \textbf{1.10}.
+    }
 
-    \refereeresponse{typo "asses"-\textgreater"assess"}
-    {Corrected.}
+    \ccomment{
+    Sec II:
 
-    \refereeresponse{In (2) there is a P\_lambda missing after the sum.}
-    {This is a typo in the ArXiv submission and has was corrected for our PRA submission.}
+    Sentence "Specifically, the causal structure G hypothesizes..." has grammatical issues.}
 
-    \refereecommentformat{Sec V:}
+    \response{Agreed. Modified sentence: ``A causal structure $\graph$ hypothesizes that each variable $n \in \nodes$ is only directly influenced by its parents $\Pa[\graph]{n}$.''.}
 
-    \refereeresponse{Perhaps change "We close this loophole..." to "This loophole is closed..." to make clear this is not a new idea here.}
-    {Corrected: ``This loophole is closed by having...''.}
+    \ccomment{Near the end of Sec II, "complete characterization for any causal structure": this remark clashed with a later remark on p5 that Bell's structure has a "complete classification of classicality".}
 
-    \refereecommentformat{Sec VII A:}
+    \response{Corrected: Currently however, it is unknown how to obtain a complete characterization for all causal structures, including the Triangle structure.}
 
-    \refereeresponse{Last paragraph, maybe write P\_ABC as P\_\{A\_lA\_rB\_lB\_rC\_lC\_r\} or mention equivalence: if I understand correctly, the alphabet size must be 4 for each of A, B and C to use (11).}{}
+    \ccomment{
+    Sec III:
 
-    \refereeresponse{typo "distribution very similar to P\_F itself" -\textgreater "distributions"}
-    {Corrected.}
+    typo "asses"-\textgreater"assess"}
 
-    \refereeresponse{Do you have any insights as to why the particular inflations considered turn out to be useful? Do you have any insight as to which inflations are likely to be useful?}{}
+    \response{Corrected.}
 
-    \refereeresponse{I'm not sure the figures of distributions are presented in the best way: given that (if I understand correctly) there are only 3 different values in Fig 5, for example, why not just state these individually (like is done for the white value) rather than give the scale of values.}{}
+    \ccomment{In (2) there is a P\_lambda missing after the sum.}
 
-    \refereecommentformat{Sec VIII:}
+    \response{This is a typo in the ArXiv submission and was corrected for our PRA submission.}
 
-    \refereeresponse{"..initial parameters such that the initial point of the optimization was close to P\_F.": can you say more about what "close" means?
-Were all parameters varied or only the nonzero parameters?}{}
+    \ccomment{
+    Sec V:
 
-    \refereeresponse{"...violating it suboptimally than P\_F.": reword}
-    {Reworded sentence: ``To the contrary, out numerical optimization failed to find any symmetric quantum distributions capable of violating $I_{\text{SymmetricWeb}}$''.}
+    Perhaps change "We close this loophole..." to "This loophole is closed..." to make clear this is not a new idea here.}
 
-    \refereecommentformat{Conclusions:}
+    \response{Corrected: ``This loophole is closed by having...''.}
 
-    \refereeresponse{Perhaps it is misleading to say that no noise is tolerated by Fritz's argument: his argument works for noisy entangled states (provided CHSH is still violated).
+    \ccomment{
+    Sec VII A:
+
+    Last paragraph, maybe write P\_ABC as P\_\{A\_lA\_rB\_lB\_rC\_lC\_r\} or mention equivalence: if I understand correctly, the alphabet size must be 4 for each of A, B and C to use (11).}
+
+    \response{
+        Apologies for the confusion, this equivalence has now been explicitly mentioned.
+Moreover, we believe that the ordering of statements in Section V made it very confusing for any reader to understand the two different, but isomorphic notations.
+As such, we have made slight modifications to Section V to make this correspondence clear for future readers.
+    }
+
+    \ccomment{typo "distribution very similar to P\_F itself" -\textgreater "distributions"}
+
+    \response{Corrected.}
+
+    \ccomment{Do you have any insights as to why the particular inflations considered turn out to be useful? Do you have any insight as to which inflations are likely to be useful?}
+
+    \response{
+        Initially, the particular inflations considered were chosen with the intuition that ``larger'' inflations might be capable of generating new inequalities.
+Moreover, inflations ``larger'' than the Web inflation became computationally demanding for investigations.
+Overtime, more intuitions and insight began to develop.
+For example, the Wagon-Wheel inflation is not an arbitrary choice.
+In the Bell structure, both Alice $A$ and Bob $B$ have two settings.
+Therefore, in order to capture this idea in an inflation of the triangle structure, we needed to construct two copies of Alice $A_1$, $A_2$, and Bob $B_1$, $B_2$, and consequently two copies of settings variables $X_{1}, X_{2}$ and $Y_{1}, Y_{2}$.
+As pointed out in Section V, the role of Charlie $C$ is to document and announce all distinct pairs of settings and therefore at least four $C$'s are ``needed''.
+These observations suggest the Wagon-Wheel inflation is worth considering.
+In this sense, we might have expected the Wagon-Wheel inflation to be useful.
+At the moment, we have yet to develop a systematic and universal understanding of these vague intuitions and insights.
+Therefore, we elected to omit these imprecise discussions from the paper and have differed these ideas for future research.
+
+        See also response \textbf{2.5}.
+    }
+
+    \ccomment{I'm not sure the figures of distributions are presented in the best way: given that (if I understand correctly) there are only 3 different values in Fig 5, for example, why not just state these individually (like is done for the white value) rather than give the scale of values.}
+
+    \response{ Great point. Figures 4 and 5 have been tweaked to simply state the three probability values. }
+
+    \ccomment{
+    Sec VIII:
+
+    "..initial parameters such that the initial point of the optimization was close to P\_F.": can you say more about what "close" means? Were all parameters varied or only the nonzero parameters?}
+
+    \response{
+        Here ``close'' means close with respect to a Euclidean norm in parameter space.
+These nearby points in parameter space were obtained by first constructing parameters which reproduce $P_{F}$ exactly.
+Then for each individual parameter $\lambda$ in this set, we sampled a perturbation $\de \lambda$ from a Gaussian distribution with standard deviation $\sigma = 2\pi 10^{\chi}$.
+Then we seeded the numerical optimization with $\lambda + \de \lambda$.
+If we let $\chi$ become too large (approximately $\chi > -1.5$), the numerical optimization would converge to parameters that generate saturating distributions.
+For $\chi$ sufficiently small, the optimization would converge to parameters that generate violating distributions.
+In this sense, all of the parameters were varied.
+Below is a plot illustrating this phenomena.
+        \begin{center}
+            \includegraphics[scale=0.4]{Gaussian_Perturbation_Fritz_Color_Default.pdf}
+            \includegraphics[scale=0.4]{Gaussian_Perturbation_Fritz_Color_Zoomed.pdf}
+        \end{center}
+    }
+
+    \ccomment{"...violating it suboptimally than P\_F.": reword}
+
+    \response{Reworded sentence: ``To the contrary, our numerical optimization failed to find any symmetric quantum distributions capable of violating $I_{\text{SymmetricWeb}}$''.}
+
+    \ccomment{
+    Conclusions:
+
+    Perhaps it is misleading to say that no noise is tolerated by Fritz's argument: his argument works for noisy entangled states (provided CHSH is still violated).
 Perhaps it is less obvious what happens when noise occurs elsewhere, but the other parts need only classical resources to realize in which case noise is less problematic.
-I would also imagine that even if it not literally robust as written that it could be made robust fairly easily.}{}
+I would also imagine that even if it not literally robust as written that it could be made robust fairly easily.}
 
-    \refereeresponse{grammar: "a causal compatibility inequalities"}
-    {Corrected: ``...it was demonstrated that these causal compatibility inequalities are robust to noise...''.}
+    \response{
+        You are correct in saying that if the entangled quantum state shared between $A$ and $B$ is subjected to noise, then provided that CHSH is still violated, Fritz's argument still holds.
+Crucially however, the argument requires \textit{perfect} correlation between $C$ and the left bits of $A$ and $B$.
+Therefore, introducing \textit{any} amount of noise to the classical resources which establish these perfect correlations prohibits one from applying Fritz's argument with absolute confidence.
+Nonetheless, we \textit{are} sympathetic to sharing your intuition as a means of a priori expecting that \textit{some} amount of noise is tolerable, but the important question is how much noise?
+The robustification of Fritz’s argument is precisely what this paper accomplishes using the Inflation Technique.
+It is our hope that further research will identify a more direct/simple route for performing these robustifications in general.
+    }
 
-    \refereeresponse{"advantages from a resource perspective": it isn't clear to me what you are referring to, so please add some explanation or reword.}{}
+    \ccomment{grammar: "a causal compatibility inequalities"}
 
-    \refereeresponse{p14 typo: "which be solved"}
-    {Corrected: ``...which can be solved efficiently...''.}
+    \response{Corrected: ``...it was demonstrated that these causal compatibility inequalities are robust to noise...''.}
+
+    \ccomment{"advantages from a resource perspective": it isn't clear to me what you are referring to, so please add some explanation or reword.}
+
+    \response{
+        Apologies for this confusion.
+An earlier draft had a more detailed explanation of what we mean by a ``resource perspective'' but subsequently omitted.
+As such, we have decided to remove this comment from the conclusion entirely.
+Remnants of these ideas have been re-introduced in the new section titled Revisiting Fritz’s Problem (see Response \textbf{1.14}).
+
+        Specifically, the original idea was as follows.
+In order to find new examples of novel quantum resource in the Triangle structure, perhaps one might need to require the three parties $A,B,C$ to perform some correlation game/task using the latent resources of the Triangle structure.
+In particular, one could ask what correlations are achievable using only a single quantum state, or two quantum states, or all three.
+Since Fritz distribution can be achieved with only a single quantum state, maybe distributions which need to exploit the quantum resources of all three exhibit a type of non-classicality distinct from the Fritz distribution.
+    }
+
+    \ccomment{p14 typo: "which be solved"}
+
+    \response{Corrected: ``...which can be solved efficiently...''.}
 

### 2018-06-07 CCIAQVTS/CCIAQVTS.tex
First completed draft of the referee responses

@@
 To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}.
-The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$.
+The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$.
 Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}.
@@
 Second, the new framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}.
-Ultimately, this work serves as a validation that the Inflation Technique is sensitive enough to offer new insights into quantum non-classicality \cite{Navascues_2017}.
+Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer new insights into quantum non-classicality \cite{Navascues_2017}.
 Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of non-classicality.
-The authors attempts to find such novel resources were met with only partial success, suggesting clear refinements for future exploration.
+The authors attempts to find such novel resources were met with only partial success, suggesting the need for both conceptual refinements and future exploration.
 
-    The manuscript is organized into the following sections: \Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used.
+    The first half of the manuscript, namely \Cref{sec:causal_compatibility,sec:bell_structure,sec:triangle_structure,sec:fritz_distribution}, is entirely a review of previous works.
+\Cref{sec:causal_compatibility} recalls important notions from causal inference theory and sets up the notation to be used.
 \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities.
@@
 \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}.
-The Fritz distribution first was proven to be non-classical without the use of inequalities.
-Here we offer a direct proof using inequalities, with the advantage that our proof is robust to noise.
+In the same work~\cite{Fritz_2012}, the Fritz distribution was proven to be non-classical without the use of inequalities.
+
+    The second half of the manuscript, namely \Cref{sec:preliminary_research,sec:found_inequalities,sec:optimizations,sec:fritz_problem_revisit}, presents the main contributions made by this research project.
+Specifically, in \cref{sec:found_inequalities} we improve upon the results of \citet{Fritz_2012} by offering a direct proof of the incompatibility of the Fritz distribution using inequalities generated by the Inflation Technique~\cite{Inflation}.
 A sample of such inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality}.
+Aside from confirming the utility of the Inflation Technique, this paper explores the importance of having derived these inequalities.
+First, an inequality-based proof has the advantage of being robust to experimental noise.
 In \cref{sec:violations_noise} the Fritz distribution is subjected to noise in order to measure the robustness of the derived inequalities.
-Additionally, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to seek out new flavors of non-classicality in the Triangle structure.
-\Cref{sec:conclusions} concludes with proposed avenues for further research.
+Second, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to find the maximum violations achievable by quantum theory.
+The culmination of these analyses naturally prompts a discussion, found in \Cref{sec:fritz_problem_revisit}, regarding the fundamental problem of recognizing and classifying novel non-classicality in the Triangle structure.
+\Cref{sec:conclusions} concludes.
 
@@
 A \textit{complete characterization} of compatibility consists of a complete set of all valid causal compatibility inequalities such that satisfaction of the entire set certifies compatibility.
-Currently however, it is unknown how to obtain a complete characterization for any given causal structure, including the Triangle structure.
+Currently however, it is unknown how to obtain a complete characterization for all causal structures, including the Triangle structure.
 
@@
 The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
-    Importantly, \citet{Fritz_2012} explicitly demonstrated of existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality.
+    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality.
 It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of non-classicality are expected to correspond to novel information-theoretical quantum advantages.
@@
 In the Fritz distribution, denoted $\prob[\fritz]$, each of the variables $A,B,C$ is taken to have $4$ possible outcomes $\bc{0,1,2,3}$.
-It is convenient to represent the outcomes using two binary digits, $\bc{00,01,10,11}$.
 Explicitly, $\prob[\fritz]$ can be written as:
@@
     \end{align*}
-    Here the notation $\prob[\fritz][abc] = \prob[ABC][abc] = \prob[][A\mapsto a,B\mapsto b,C\mapsto c]$ is used as shorthand.
+    In~\cref{eq:fritz_dist}, the notation $\prob[\fritz][abc] = \prob[][A\mapsto a,B\mapsto b,C\mapsto c]$ is used as shorthand.
 The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:triangle_Qcompatibility}.
-    The Fritz distribution may be visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}.
+When expressing the outcomes $\bc{0,1,2,3}$ as pairs of binary digits $\bc{00, 01, 10, 11}$, it can be seen that the left-hand bits for $A$ and $B$ (respectively denoted $A_l$, $B_l$) are fixed by the outcome of $C$.
+    \begin{align*}
+    \eq \label{eq:fritz_dist_bit_variant}
+    \begin{split}
+        \prob[\fritz][00,00,00] = \prob[\fritz][01,01,00] = \prob[\fritz][00,10,01] = \prob[\fritz][01,11,01] &= \f{1}{32}\br{2 + \sqrt{2}} \\
+        \prob[\fritz][10,00,10] = \prob[\fritz][11,01,10] = \prob[\fritz][10,11,11] = \prob[\fritz][11,10,11] &= \f{1}{32}\br{2 + \sqrt{2}} \\
+        \prob[\fritz][00,01,00] = \prob[\fritz][01,00,00] = \prob[\fritz][00,11,01] = \prob[\fritz][01,10,01] &= \f{1}{32}\br{2 - \sqrt{2}} \\
+        \prob[\fritz][10,01,10] = \prob[\fritz][11,00,10] = \prob[\fritz][10,10,11] = \prob[\fritz][11,11,11] &= \f{1}{32}\br{2 - \sqrt{2}}
+    \end{split}
+    \end{align*}
+    % = \prob[A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}][a_{l}a_{r}b_{l}b_{r}c_{l}c_{r}]
+    In~\cref{eq:fritz_dist_bit_variant}, the notation $\prob[\fritz][a_{l}a_{r},b_{l}b_{r},c_{l}c_{r}] = \prob[][A_{l}\mapsto a_{l},A_{r}\mapsto a_{r},B_{l}\mapsto b_{l},B_{r}\mapsto b_{r},C_{l}\mapsto c_{l},C_{r}\mapsto c_{r}]$ is used as shorthand.
+This observation can be difficult to verify using~\cref{eq:fritz_dist_bit_variant}, but becomes easier after organizing the possible outcomes into a $4 \times 4 \times 4$ grid as depicted in \cref{fig:fritz_distribution_visualized}.
 From this diagram, it can be seen that each of $C$'s outcomes restricts the possible outcomes for $A,B$ into a $2 \times 2$ block.
-When expressing the outcomes as pairs of binary digits, it can be seen that the left-hand bits for $A$ and $B$ (respectively denoted $A_l$, $B_l$) are fixed by (i.e.
-perfectly correlated with) the outcome of $C$.
-Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded}, the left-hand bits $A_l$ and $B_l$ emulate the measurement settings $S_{A}$ and $S_{B}$, whereas the right-hand bits $A_r$ and $B_r$ emulate the outcomes which would be obtained by $A$ and $B$ back in the Bell structure (\cref{fig:bell_structure}).
-Critically, $C$'s bits are perfectly correlated with the left-bits of $A,B$; $C_l = A_l$ and $C_r = B_l$.
+Effectively, $C$'s bits are perfectly correlated with the left-bits of $A,B$; $C_l = A_l$ and $C_r = B_l$.
     \begin{figure}
     \begin{nscenter}
-            \includegraphics[scale=0.6]{figure_fritz_dist_plotted_bits.pdf}
-            \vspace{-0.2in}
-            \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
+            \includegraphics[trim={0 2.2cm 0 0}, clip, scale=0.6]{figure_fritz_dist_plotted_bits.pdf}
+            % \vspace{-0.2in}
+            \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}} \qquad \probplotvalue{255, 255, 255} = 0\]
             \caption{The Fritz distribution visualized using a $4 \times 4 \times 4$ grid.
@@
     \end{figure}
-    Consequently, it is possible to define the correlation $\ba{A_r B_r}$ between the right-hand bits of $A$ and $B$:
-    \[ \ba{A_r B_r} = \prob[A_r B_r][00] + \prob[A_r B_r][11] - \prob[A_r B_r][01] - \prob[A_r B_r][10] \eq \label{eq:right_bit_correlations} \]
+    Therefore, pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded}, the left-hand bits $A_l$ and $B_l$ emulate the measurement settings $S_{A}$ and $S_{B}$, whereas the right-hand bits $A_r$ and $B_r$ emulate the outcomes which would be obtained by $A$ and $B$ back in the Bell structure (\cref{fig:bell_structure}).
 Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $A, B, S_{A}, S_{B}$ can be directly converted to an inequality for the Triangle structure by performing the surjective relabeling:
@@
     \end{align*}
-    As an example, the famous CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original} is translated into a constraint on the correlation between the right-bits of $A$ and $B$,
-    \[ \ba{A_r B_r|C = 00} + \ba{A_r B_r|C = 01} + \ba{A_r B_r|C = 10} - \ba{A_r B_r|C = 11} \leq 2 \eq \label[ineq]{eq:CHSH_intriangle} \]
-    Every compatible distribution $\prob[ABC]$ \emph{for which $C$ is perfectly correlated with $A_l,B_l$} must satisfy \cref{eq:CHSH_intriangle}.
+    As an example, the famous CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original} is translated into a constraint on the correlation between the right-bits of $A$ and $B$ under~\cref{eq:fritz_relabelling},
+    \[ C = C_{l}C_{r} = A_{l}B_{l} \Longrightarrow \ba{A_r B_r|C = 00} + \ba{A_r B_r|C = 01} + \ba{A_r B_r|C = 10} - \ba{A_r B_r|C = 11} \leq 2, \eq \label[ineq]{eq:CHSH_intriangle} \]
+    where the correlation $\ba{A_r B_r}$ between the right-hand bits of $A$ and $B$ is defined as,
+    \[ \ba{A_r B_r} = \prob[A_r B_r][00] + \prob[A_r B_r][11] - \prob[A_r B_r][01] - \prob[A_r B_r][10]. \eq \label{eq:right_bit_correlations} \]
+    Therefore, every compatible distribution $\prob[ABC]$ \emph{for which $C$ is perfectly correlated with $A_l,B_l$} must satisfy \cref{eq:CHSH_intriangle}.
 Substituting $\prob[\fritz]$ into \cref{eq:CHSH_intriangle} yields the traditional maximal quantum violation~\cite{Cirelson_1980}: $3 \br{1/\sqrt{2}} - \br{-1/\sqrt{2}} = 2\sqrt{2} \not \leq 2$.
@@
     It is important to understand the domain in which Fritz's proof of incompatibility is valid; its proof relies on the perfect correlation between $C$'s outcomes and the measurement pseudo-settings (left-bits) of $A$ and $B$.
-For example, if one combines \cref{eq:fritz_dist} with slight uniform noise, what can we say with confidence regarding if the resulting modified distribution is classical or not?
-At what point does the resultant distribution transition from incompatibility to compatibility?
+For example, if one combines \cref{eq:fritz_dist} with slight uniform noise, what can be said with confidence regarding if the resulting modified distribution is classical or not?
+At what point does the resulting distribution transition from incompatibility to compatibility?
 This question is partially answered in \cref{sec:noise}.
@@
 Such a discovery would presumably lead to an understanding of new advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open.
-We attempt to make progress on this problem by leveraging the the new causal compatibility inequalities derived herein, but this effort was plagued by instabilities in our numerical optimization which we have not yet overcome.
-\Cref{sec:conclusions} discusses these challenges, suggesting concrete targets for future research.
-\Cref{sec:conclusions} also considers how to best contrast non-classicality across differing causal structures.
+We attempt to make progress on this problem by leveraging the new causal compatibility inequalities derived herein, but \Cref{sec:optimizations} delineates that is effort was plagued by instabilities in our numerical optimization which we have not yet overcome.
+Consequently, \Cref{sec:fritz_problem_revisit} discusses potential avenues for rigorously reformulating Fritz's problem in order to best capture this desire for novel quantum non-classicality.
 
@@
 
-    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the previously-published compatibility inequalities of~\cite{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014} (which had also been investigated numerically independently by \citet{Weilenmann_2016}).
-This preliminary investigation did not yield interesting solutions, as none of those inequalities were violated by any 2-outcome coarse-graining of the Fritz distribution.
-These early results suggest that there is no quantum-classical gap in the Triangle structure for \textit{two-outcome} measurements, i.e.
-\cref{eq:triangle_compatibility} and \cref{eq:triangle_Qcompatibility} define identical sets of binary-outcome tripartite distributions.
+    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations (in search of violation) against the previously-published compatibility inequalities of~\citet{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014}.
+For historical context, the entropic inequalities of \cite{Henson_2014} have already been independently investigated for quantum incompatibility by \citet{Weilenmann_2016} using a variety of computational methods.
+Unfortunately, these methods failed to identify quantum-accessible distributions capable of violating any of the entropic inequalities considered by \cite{Weilenmann_2016}.
+Additionally, the inequalities presented in~\cite{Inflation} have not been previously investigated numerically.
 
-    Operating under the assumptions that all quantum \emph{non}-classical distributions in the Triangle structure must utilize more than two outcomes in at least one variable, this work expands the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.
+    Explicitly, we parameterized the subset of quantum distributions accessible by bipartite qubit density matrices and $2$-outcome POVM measurements\footnote{In \cref{sec:optimizations}, we discuss methods for conducting similar parameterizations of quantum states and measurements.}.
+This preliminary investigation did not yield interesting solutions, as none of the Triangle structure inequalities in~\cite{Inflation} or~\cite{Henson_2014} were violated\footnote{We also directly checked all 2-outcome coarse-grainings of the Fritz distribution against the inequalities in~\cite{Inflation,Henson_2014}, with no violation.}.
+Unfortunately, these early results are inconclusive for two reasons.
+First, an exhaustive search would need to consider the possibility of larger Hilbert spaces for the shared quantum states.
+Second, there is little reason to suggest that the inequalities considered in~\cite{Inflation} are complete; it is possible there are other constraints on two outcome distributions for the Triangle structure yet to be discovered.
+
+    Nonetheless, having seen no quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for \emph{non}-classical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.
 
@@
 
-    The methods used to derive these inequalities are largely based on the Inflation Technique~\cite{Inflation}.
-A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:inflation_technique_summary} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.
+    Readers which are unfamiliar with the Inflation Technique~\cite{Inflation}, and wish to understand in detail how the following inequalities are derived, are recommended to consult \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities} wherein they will find a succinct yet sufficient presentation of the requisites needed for this paper.
+To briefly summarize, \cref{sec:inflation_technique_summary} reviews the basics of the Inflation Technique and formally defines the notion of an \textit{inflation} of a causal structure.
+\Cref{sec:deriving_inequalities} demonstrates how to use the Inflation Technique and a given probability distribution, such as the Fritz distribution, to cast the causal compatibility problem as a particular kind of linear program known as a marginal problem, defined in \cref{sec:marginal_satisfiability}.
+
+    The Inflation Technique is known to completely solve the causal compatibility problem through increasing orders of inflations~\cite{Navascues_2017}.
+Consequently, the derivation of \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality} is guaranteed by~\cite{Navascues_2017} for sufficiently large inflations.
+Nonetheless, the following inequalities were obtained using the relatively small inflations found in \cref{fig:inflations}\footnote{Note that the adjectives \textit{large} and \textit{small} used to describe an inflation only become well-defined in the context of the hierarchy proposed in~\cite{Navascues_2017}.
+For example, the Web Inflation in \cref{fig:the_web_inflation} is second in the hierarchy of~\cite{Navascues_2017} whereas the Wagon-Wheel Inflation in \cref{fig:wagon_wheel_inflation} is somewhere between the first and second order.}.
+This efficiency is not universally guaranteed; for comparison, we remark that unlike the Fritz distribution, the conjectured incompatibility of the $4$-outcome distribution proposed by \cite{Gisin_2017} is \textit{not} confirmed by Inflation Technique at the same level.
+
     We emphasize that each of these causal compatibility inequalities independently provides a positive resolution of Fritz's problem.
 The inequalities are derived without making use of Bell's theorem; rather, they follow from the Inflation Technique's broader perspective on non-classicality as a special case of causal inference.
+Afterwards, Section~\ref{sec:fritz_problem_revisit} returns to the topic of Fritz's problem and the status of our resolution.
 
@@
     \end{equation*}
+
     \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it.
 To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}.
+Moreover, note that \Cref{eq:ww_ineq} is reported using the same two-bit notation discussed in~\cref{sec:fritz_distribution} such that $\prob[A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}][a_{l}a_{r}b_{l}b_{r}c_{l}c_{r}] = \prob[ABC][abc]$.
+
     Aside from increasing outcome cardinality, we are also forced to consider larger inflations than those analyzed in~\cite{Inflation}.
-This is because we found the smaller inflations considered there --- such as the Spiral inflation depicted in \cref{fig:spiral_inflation} --- were simply \textit{unable} to witness the incompatibility of the Fritz distribution, even when analyzed explicitly using four possible outcomes for every observable variable.
+This is because we found the smaller inflations considered there, such as the Spiral inflation depicted in \cref{fig:spiral_inflation}, were simply \textit{unable} to witness the incompatibility of the Fritz distribution, even when analyzed explicitly using four possible outcomes for every observable variable.
 
@@
     \begin{nscenter}
-            \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figure_noisy_yet_non_local_fritz.pdf}
-            \vspace{-0.2in}
-            \[ \probplotvalue{255, 255, 243} = 0.00133 \]
+            \includegraphics[scale=0.6,trim={0 2.2cm 0 0.4in},clip]{figure_noisy_yet_non_local_fritz.pdf}
+            % \vspace{-0.2in}
+            \[ \probplotvalue{253, 253, 84} = 0.018 \qquad \probplotvalue{11, 1, 0} = 0.099 \qquad \probplotvalue{255, 255, 243} = 0.0013 \]
             \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
@@
 
-    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure (\cref{fig:triangle_structure}) and thus expressed in the form of \cref{eq:triangle_Qcompatibility}.
+    In order to find quantum distributions that are more non-classical than the Fritz distribution, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure (\cref{fig:triangle_structure}) and thus expressed in the form of \cref{eq:triangle_Qcompatibility}.
 In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
@@
 This, even though we \emph{know} that all the inequalities we consider \emph{do} admit quantum violation, namely by  $\prob[\fritz]$.
-To achieve inequality violation, we found ourselves forced to seed the numerical method with initial  parameters such that the initial point of the optimization was close to  $\prob[\fritz]$.
-
-    The fact that the \emph{final} points of optimization as returned by our numerical methods are invariably also close to $\prob[\fritz]$ makes interpreting the results somewhat murky.
+To achieve inequality violation, we found ourselves forced to initialize the numerical optimizer with parameters that were nearby (in parameter space) to parameters which generate the Fritz distribution $\prob[\fritz]$.
+Upon doing so, it was observed that the numerical methods converged invariably to parameters which generated distributions similar to $\prob[\fritz]$ (see~\cref{fig:maximum_violation_I_1} for instance); consequently making interpreting the results somewhat murky.
 Could it be that the inequality's global maximum is, in-fact, not far from $\prob[\fritz]$?
@@
 Additionally, since $I\tsb{SymmetricWeb}$ is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well.
-To the contrary, out numerical optimization failed to find \emph{any} symmetric quantum distributions capable of violating $I\tsb{SymmetricWeb}$.
+To the contrary, our numerical optimization failed to find \emph{any} symmetric quantum distributions capable of violating $I\tsb{SymmetricWeb}$.
+
+    \section{Revisiting Fritz's Problem}
+    \label{sec:fritz_problem_revisit}
+
+    In~\cref{sec:fritz_distribution}, we defined the Fritz distribution and summarized the inequality-free proof of its     incompatibility with the Triangle structure due to~\cite{Fritz_2012}.
+In addition, \cref{sec:fritz_distribution} discusses Fritz's Problem as a quest to find quantum distributions incompatible with the Triangle structure that are also qualitatively distinct from those distributions which are incompatible with the Bell structure.
+In light of the perhaps unsatisfactory results of~\cref{sec:optimizations}, the purpose of this section is to revisit Fritz's problem and to attempt to rigorously formulate criterion for quantum non-classicality that is genuine to the Triangle structure.
+
+    When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a \textit{single} bipartite quantum state.
+Unlike the Bell structure in~\Cref{fig:bell_structure}, the observable nodes of the Triangle structure in~\Cref{fig:triangle_structure} have access to potentially \textit{three} different bipartite quantum states.
+As noted in~\cite{Fritz_2012}, the Fritz distribution can be implemented using only a \textit{single} entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at \textit{minimum}, one is necessary.} Therefore, it becomes reasonable to propose that any quantum non-classicality in the Triangle structure that \textit{requires} entanglement in \textit{at least two} shared states constitutes non-classicality distinct from Bell non-classicality.
+At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource unique to the Triangle structure.
+Unfortunately, this is not the case.
+By multiplying the cardinality of the outcomes for $A, B, C$ three-fold, it is possible to generate a distribution that is non-classical yet quantum and requires \textit{all three} of the shared resources to be entangled.
+This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings.
+Such a distribution would require entanglement in all three quantum states; under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible\footnote{This observation was original provided by Miguel Navascués.}.
+Consequently, demanding the necessity of entanglement in every shared state is insufficient for finding novel non-classicality.
+
+    In consideration of this particular construction, perhaps the correct assessment for novel non-classicality must incorporate a restriction on the the cardinality of the observed variables?
+Pursuant to this objective, we were able to prove the non-classicality of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations\footnote{An inequality-free proof of the incompatibility of this distribution, using arguments analogous those presented in~\cite{Fritz_2012}, can be found in~\cite{Weilenmann_2016}.
+Assessing the compatibility of this variant using the methods in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities} was first suggested to the authors by Denis Rosset.}.
+Nonetheless, such a distribution fails to deviate significantly from Bell non-classicality.
+
+    It is worth noting that there are quantum-accessible distributions which are conjectured, but not proven, to be incompatible with the Triangle structure.
+For instance, the distribution proposed in~\cite{Gisin_2017} required the use of entangled measurements, and thus if proven incompatible, might constitute a novel form of quantum non-classicality.
+Unfortunately, as was previously noted in~\cref{sec:found_inequalities}, the proposed distribution in~\cite{Gisin_2017} satisfies all inequalities generated by the inflations considered in~\cref{fig:inflations}.
+Presently, computational limitations prevent us from considering larger inflations than those in~\cref{fig:inflations}, although we remain optimistic.
+
+    In truth, properly defining the novelty of quantum correlations and also recognizing the resourcefulness of those correlations in the Triangle structure, or any other causal structure, is a deep and meaningful, albeit unsettled, problem.
+Ultimately, if a satisfactory classifier of novelty is constructed, it remains unclear whether or not novel distributions even exist.
 
@@
 Though some causal compatibility inequalities were known, those inequalities did not appear useful for the purpose of witnessing quantum non-classicality.
-Recently,~\citet{Fritz_2012} gave the the first example of quantum non-classicality in the Triangle structure, relying on an inequality-free proof that is not robust to any amount of noise.
+Recently,~\citet{Fritz_2012} gave the first example of quantum non-classicality in the Triangle structure, relying on an inequality-free proof that is not robust to any amount of noise.
 
     In \cref{sec:found_inequalities} we presented the first examples of causal compatibility inequalities capable of having quantum violations in the sense that they are violated by quantum-accessible distributions.
-This result was made possible through the Inflation Technique \cref{sec:inflation_technique_summary} applied to the Fritz distribution.
+This result was made possible through the Inflation Technique~\cite{Inflation} (\cref{sec:inflation_technique_summary}) applied to the Fritz distribution.
+Moreover, the inequalities in \cref{sec:found_inequalities} were derived using the inflations in \cref{fig:inflations}, each of which is low in the hierarchy proposed by~\cite{Navascues_2017}, thus revealing the relative efficiency of the Inflation Technique.
 
     In \cref{sec:noise} it was demonstrated that these causal compatibility inequalities are robust to noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's perfect-correlation example.
-In \cref{sec:optimizations} we found quantum distributions quantitatively distinct from the Fritz's recycled-Bell's-theorem example, such that these variant distribution more strongly violate certain causal compatibility inequalities.
+In \cref{sec:optimizations} we found quantum distributions \textit{quantitatively} distinct from the Fritz's recycled-Bell's-theorem example, such that these optimized distributions more strongly violate certain causal compatibility inequalities.
 
     Despite these advancements, the distributions we discovered hew closely to the Fritz distribution, indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure.
-Currently, it remains speculative about how to recognize whether-or-not a given distribution for the Triangle structure exhibits non-classical correlations of a fundamentally novel qualitative nature than Bell-type non-classicality.
-We imagine that advantages from a resource perspective might be critical to establish such a novelty signature.
-    Perhaps another signature would be if the distribution can arise in the Triangle structure only through the use of of entangled measurements, such as perhaps the conjecture in \cite{Gisin_2017}.
-Ultimately, given any said classifier, it remains unclear whether or not such distributions even exist.
+\Cref{sec:fritz_problem_revisit} discusses potential proposals certifying the genuineness of non-classicality in the Triangle structure.
+Presently, the existence, and subsequent suitable classification of fundamentally novel non-classicality remains speculative, and certainly warrants future research.
 

### 2018-07-19 documents/Referee Responses/refereeresponses.tex
updates for resubmission to pra

@@
 
+    To begin, we would like to thank both referees for their insightful comments and constructive criticisms.
+Evidently, the referees understood the subject matter and were diligent in crafting their helpful comments.
+Therefore, we must sincerely thank the referees for their time and appreciate their expertise.
+Below we have responded individually, where applicable, to the referees' comments.
+Our responses are in black text, and the referees' original comments are in gray text.
+Overall, there were zero comments we disagreed with and we believe that each comment has directly or indirectly led to an improvement of our original submission.
+
     \stepcounter{refereecounter}
@@
 The language used now more closely mirrors that of the conclusions.
-Hopefully, readers familiar, at least, with the subject matter of Bell inequalities will be able to comprehend the nature of the advancements made by this work from the introduction alone.
+Hopefully, readers familiar with at least the subject matter of Bell inequalities will be able to comprehend the nature of the advancements made by this work from the introduction alone.
     }
@@
     \response{
-    An excellent comment, thank you. We have elected to add more historical context to Section VI. Specifically, the first paragraph now reads,
+    We thank the referee for this excellent comment. We have elected to add more historical context to Section VI. Specifically, the first paragraph now reads,
 
@@
 
-    For even more context (excluded from Section VI for brevity), entropic inequality constraints for the Triangle structure first appeared in Fritz, Chaves [40], but a completed list of all Shannon-type entropic inequalities could not be computed due to the computational limitations of Fourier Motzkin.
-In Chaves, Luft, and Gross [17], these computational limitations were overcame using all conditional independence constraints to pre-process the Fourier Motzkin procedure and produced two new entropic inequalities.
+    For even more context (excluded from Section VI for brevity), entropic inequality constraints for the Triangle structure first appeared in Fritz, Chaves [40], but a completed list of all Shannon-type entropic inequalities was not computed in [40] due to the computational limitations of the Fourier Motzkin elimination procedure.
+In Chaves, Luft, and Gross [17], these computational limitations were overcame using all conditional independence constraints present in the Triangle structure to pre-process the Fourier Motzkin procedure and produced two new entropic inequalities.
 To the best of our knowledge, attempts to violate these inequalities using computational methods first appeared in [20].
@@
     \response{
-    You are correct.
+    The referee is correct.
 Strictly speaking, the numerical failings are inconclusive.
 The purpose of the `conjecture' was to narratively motivate the shift to larger-outcome inequalities.
-The document reflects this change of perspective:
+The document now reflects a more conservative perspective:
 
@@
 
-    Nonetheless, having seen no quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for \emph{non}-classical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.''
+    Nonetheless, having failed to observe a quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for \emph{non}-classical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.''
     }
@@
 The Triangle structure is an instance of this breakdown.
-Nonetheless, new results due to Rosset, Wolfe (https://arxiv.org/abs/1709.00707) reveal that it is possible to generalize the notion of an 'optimal' inequality.
+Geometrically, an inequality is considered `tight' if its intersection with the classical/compatible set is full-dimensional (i.e.
+the surface of intersection has dimension one less than the embedding dimension).
 
+        More formally, new results due to Rosset, Gisin, Wolfe (\url{https://arxiv.org/abs/1709.00707}) reveal that it is possible to generalize the notion of an 'optimal' inequality.
 Explicitly, in 1709.00707, it was proven that the set of compatible classical distributions for any causal network (including the Triangle structure) forms a semi-algebraic set; meaning that there exists a \textit{finite} list of inequality and equality constraints that are necessary and sufficient for accessing compatibility.
 Therefore, an inequality belonging to this necessary and sufficient set may be considered as optimal.
-Geometrically, an inequality is considered `tight' if its intersection with the classical/compatible set is full-dimensional.
 
@@
 
-        Regarding the generation of many possible inequalities, you are correct.
+        Regarding the generation of many possible inequalities, the referee is correct.
 In the absence of a particular distribution, the Inflation Technique yields a plethora of inequalities, many of which are redundant (strictly speaking, this problematic feature is shared among many inequality-deriving techniques which use linear (or non-linear) quantifier elimination).
@@
 
-        Determining whether or not a given quantum correlation incompatible with the Triangle structure expresses genuine, novel forms of non-classicality is, at the moment, not yet a sufficiently developed decision problem as you mention.
+        Determining whether or not a given quantum correlation incompatible with the Triangle structure expresses genuine, novel forms of non-classicality is, at the moment, not yet a sufficiently developed decision problem as the referee mentions.
 Moreover, we completely agree that is worth drawing attention to this clearly relevant idea.
-As such, we have included in the paper submission a new section that precedes the conclusion titled Revisiting Fritz's Problem.
+As such, we have included in the resubmission a new section that precedes the conclusion titled Revisiting Fritz's Problem.
 In this section, we consider a few avenues for formalizing this idea, and point out a deficiency for each.
@@
 For $\chi$ sufficiently small, the optimization would converge to parameters that generate violating distributions.
-In this sense, all of the parameters were varied.
-Below is a plot illustrating this phenomena.
+In this sense, all of the parameters were varied, not just the non-zero parameters.
+Below is a plot (left), and the same plot zoomed in (right), illustrating this phenomena.
         \begin{center}
@@
     \response{
-        You are correct in saying that if the entangled quantum state shared between $A$ and $B$ is subjected to noise, then provided that CHSH is still violated, Fritz's argument still holds.
+        The referee is correct in saying that if the entangled quantum state shared between $A$ and $B$ is subjected to noise, then provided that CHSH is still violated, Fritz's argument still holds.
 Crucially however, the argument requires \textit{perfect} correlation between $C$ and the left bits of $A$ and $B$.
 Therefore, introducing \textit{any} amount of noise to the classical resources which establish these perfect correlations prohibits one from applying Fritz's argument with absolute confidence.
-Nonetheless, we \textit{are} sympathetic to sharing your intuition as a means of a priori expecting that \textit{some} amount of noise is tolerable, but the important question is how much noise?
+Nonetheless, we \textit{are} sympathetic to sharing the referees intuition as a means of a priori expecting that \textit{some} amount of noise is tolerable, but the important question is how much noise?
 The robustification of Fritz’s argument is precisely what this paper accomplishes using the Inflation Technique.
@@
         Apologies for this confusion.
-An earlier draft had a more detailed explanation of what we mean by a ``resource perspective'' but subsequently omitted.
-As such, we have decided to remove this comment from the conclusion entirely.
+An earlier draft had a more detailed explanation of what we mean by a ``resource perspective'' but was subsequently omitted before our original submission.
+We have decided to remove this comment from the conclusion entirely.
 Remnants of these ideas have been re-introduced in the new section titled Revisiting Fritz’s Problem (see Response \textbf{1.14}).

### 2018-07-19 CCIAQVTS/CCIAQVTS.tex
updates for resubmission to pra

@@
 First, an exhaustive search would need to consider the possibility of larger Hilbert spaces for the shared quantum states.
-Second, there is little reason to suggest that the inequalities considered in~\cite{Inflation} are complete; it is possible there are other constraints on two outcome distributions for the Triangle structure yet to be discovered.
-
-    Nonetheless, having seen no quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for \emph{non}-classical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.
+Second, there it is known that the inequalities~\cite{Inflation} are incomplete; there exists other constraints on two outcome distributions for the Triangle structure yet to be discovered.
+
+    Nonetheless, having failed to observe a quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for \emph{non}-classical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.
 
@@
         I\tsb{Web} : \\\nonumber
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{ineq_web_ineq_standalone_halfed.pdf}
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\textwidth]{ineq_web_ineq_standalone_large.pdf}
     \end{gather}
@@
         I\tsb{SymmetricWeb} : \\\nonumber
-        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{ineq_sym_web_ineq_standalone_halfed.pdf}
+        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\textwidth]{ineq_sym_web_ineq_standalone_large.pdf}
     \end{gather}
 
-    Note that $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for a sum the over permutations of $A,B,C$, i.e.
+    Note that $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for a sum the over permutations of $A,B,C$, e.g.
 $\bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033)$.
@@
 Unfortunately, this is not the case.
-By multiplying the cardinality of the outcomes for $A, B, C$ three-fold, it is possible to generate a distribution that is non-classical yet quantum and requires \textit{all three} of the shared resources to be entangled.
+By increasing the cardinality of each variable $A, B, C$ to $4^{3} = 64$, it is possible to generate a distribution that is non-classical yet quantum and requires \textit{all three} of the shared resources to be entangled.
 This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings.
@@
     \scalebox{0.65}{\includegraphics{figure_inflated_triangle_structure_spiral.pdf}}
-    \caption{The Spiral inflation.}\label{fig:spiral_inflation}
+    \caption{}
+    \label{fig:spiral_inflation}
     \end{subfigure}
@@
     \scalebox{0.65}{\includegraphics{figure_inflated_triangle_structure_wagon_wheel.pdf}}
-    \caption{The Wagon-Wheel inflation.}\label{fig:wagon_wheel_inflation}
+    \caption{}
+    \label{fig:wagon_wheel_inflation}
     \end{subfigure}
@@
     \scalebox{0.65}{\includegraphics{figure_inflated_triangle_structure.pdf}}
-    \caption{The Web Inflation.}\label{fig:the_web_inflation}
+    \caption{}
+    \label{fig:the_web_inflation}
     \end{subfigure}
-    \caption{Some inflations of the Triangle structure.}
+    \caption{Some inflations of the Triangle structure: (a) the Spiral inflation, (b) the Wagon-Wheel inflation, and (c) the Web Inflation.}
     \label{fig:inflations}
@@
     \scalebox{0.8}{\includegraphics{figure_inflated_triangle_structure_spiral_injectable_highlight_1.pdf}}
-    \caption{$\AnSub[\graph']{\bc{A_1}}$}\label{fig:spiral_inflation_inj1}
+    \caption{}
+    \label{fig:spiral_inflation_inj1}
     \end{subfigure}
@@
     \scalebox{0.8}{\includegraphics{figure_triangle_structure_injectable_highlight_1.pdf}}
-    \caption{$\AnSub[\graph]{\bc{A}}$}\label{fig:spiral_inflation_iminj1}
+    \caption{}
+    \label{fig:spiral_inflation_iminj1}
     \end{subfigure}
@@
     \scalebox{0.8}{\includegraphics{figure_inflated_triangle_structure_spiral_injectable_highlight_2.pdf}}
-    \caption{$\AnSub[\graph']{\bc{A_2, C_1}}$}\label{fig:spiral_inflation_inj2}
+    \caption{}
+    \label{fig:spiral_inflation_inj2}
     \end{subfigure}
@@
     \scalebox{0.8}{\includegraphics{figure_triangle_structure_injectable_highlight_2.pdf}}
-    \caption{$\AnSub[\graph]{\bc{A,C}}$}\label{fig:spiral_inflation_iminj2}
+    \caption{}
+    \label{fig:spiral_inflation_iminj2}
     \end{subfigure}
-    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$).}
+    \caption{Some injectable sets $\Inj[\graph]{\graph'}$ of the Spiral inflation ($\graph'$) and their corresponding images $\ImInj[\graph]{\graph'}$ in the Triangle structure ($\graph$): (a) $\AnSub[\graph']{\bc{A_1}}$, (b) $\AnSub[\graph]{\bc{A}}$, (c) $\AnSub[\graph']{\bc{A_2, C_1}}$, and (d) $\AnSub[\graph]{\bc{A,C}}$.}
     \label{fig:injectablesets}

### 2018-08-01 CCIAQVTS/CCIAQVTS.tex
Made changes to the figures in order to have the figure files match their appearance in the document.

@@
 \begin{document}
-    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
+    \title{Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure}
     \author{Thomas C. Fraser}
@@
 Any constraint satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion.
-Such criteria were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?
+Such criteria were recently derived for the Triangle structure (E.
+Wolfe \textit{et al.}, \href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}) in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?
 Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary.
-Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation.
-This provides the first robust-to-noise witness of quantum correlations in the Triangle structure.
+Our main contribution in this work, however, is the derivation of causal compatibility inequalities for the Triangle structure which do admit quantum violation.
+This provides a robust-to-noise witness of quantum correlations in the Triangle structure.
 We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
@@
 If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$.
-
 When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is possible to completely determine whether or not $\prob[\nodes]$ is compatible with $\graph$ by computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}.
-
 A challenge, however, is presented when one is supplied with a partial observation, i.e.
@@
     \begin{nscenter}
-            \includegraphics[trim={0 2.2cm 0 0}, clip, scale=0.6]{figure_fritz_dist_plotted_bits.pdf}
-            % \vspace{-0.2in}
-            \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}} \qquad \probplotvalue{255, 255, 255} = 0\]
+            \includegraphics{figure_fritz_dist_plotted_bits.pdf}
             \caption{The Fritz distribution visualized using a $4 \times 4 \times 4$ grid.
@@
     \begin{nscenter}
-            \includegraphics[scale=0.6,trim={0 2.2cm 0 0.4in},clip]{figure_noisy_yet_non_local_fritz.pdf}
-            % \vspace{-0.2in}
-            \[ \probplotvalue{253, 253, 84} = 0.018 \qquad \probplotvalue{11, 1, 0} = 0.099 \qquad \probplotvalue{255, 255, 243} = 0.0013 \]
+            \includegraphics{figure_noisy_yet_non_local_fritz.pdf}
             \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
@@
 \Citet{Spengler_2010_Unitary} demonstrated that all $d\times d$ unitary matrices $U$ can be parameterized without degeneracy as follows:
-    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \cdot \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
+    \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \exp\br{i P_n \lambda_{n,m}}\exp\br{i \si_{m,n} \lambda_{m,n}}}} \times \bs{\prod_{l=1}^{d} \exp\br{iP_l \lambda_{l,l}}}  \eq \label{eq:spengler_unitary} \]
     Where the real valued parameters $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ have periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
@@
     \begin{nscenter}
-        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figure_plotted_dist_I_1_max_violation.pdf}
+        \includegraphics{figure_plotted_dist_I_1_max_violation.pdf}
         \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{Web}$.
@@
     \begin{nscenter}
-        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figure_plotted_dist_I_3_max_violation.pdf}
+        \includegraphics{figure_plotted_dist_I_3_max_violation.pdf}
         \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{SymmetricWeb}$.

### 2018-08-01 documents/Proof Response/proof_response.tex
Made changes to the figures in order to have the figure files match their appearance in the document.

\documentclass{article}
\usepackage{verbatim}
\newenvironment{metaverbatim}{\verbatim}{\endverbatim}

\usepackage[margin=1in]{geometry}

\begin{document}
    \begin{center}
        \textbf{Proof Corrections for AN11411} \\
        \textbf{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure} \\
        Thomas C. Fraser and Elie Wolfe \\
        Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5 \\
        University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1\\
        August 1, 2018
    \end{center}

    \textbf{Specific Questions and Comments to Address for This Paper:}
    \begin{enumerate}
        \item
        \item The authors agree completely with all associated modifications made to the article pursuant to the policy on claims of priority and novelty of contributions.
        \item
        \item The authors approve of all substitutions made regarding the use of slash between words throughout the document.
        \item Thank you for pointing out this one sentence paragraph. The proof matches exactly how the authors would/will correct this mistake.
        \item Noted and approved.
        \item Regarding figures 4, 5, 6 and 7, the incorrect figures were used in the proof. The discrepancy between the figure files and appearance in the submitted article were a result of using the a clipping/trimming option of \verb|\includegraphics| command of the \verb|graphicx| package in order to trim whitespace and superfluous figure titles. The usage of the this option is as follows:
        \begin{verbatim}\includegraphics[trim={<left> <lower> <right> <upper>},clip]{figure_example.pdf}\end{verbatim}
        Attached to this proof correction are ``corrected'' figure replacements for figures 4, 5, 6 and 7 which have the cropping already applied. As such, the figures should now appear correctly in the article and will match the figure files exactly. The figure files are respectively named:
        \begin{verbatim}
        figure_fritz_dist_plotted_bits.pdf
        figure_noisy_yet_non_local_fritz.pdf
        figure_plotted_dist_I_1_max_violation.pdf
        figure_plotted_dist_I_3_max_violation.pdf
        \end{verbatim}
        Regarding figures 4 and 5 only, the colored gradient legends have been removed and replaced with the explicit legends. In the original manuscript, these explicit legends were included adjacent to the figure as an equation. These legends are now a part of the attached figure files, as they should be.
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item
        \item[FQ.]
        \item[Q.]
    \end{enumerate}

\end{document}

### 2018-08-01 documents/Proof Response/proof_response.tex
Almost completed the proof response.

@@
 \usepackage{verbatim}
-\newenvironment{metaverbatim}{\verbatim}{\endverbatim}
+\makeatletter
+\newcommand{\verbatimfont}[1]{\renewcommand{\verbatim@font}{\ttfamily#1}}
+\makeatother
+\verbatimfont{\footnotesize}%
 
@@
     \begin{enumerate}
-        \item
+        \item TODO: Email E. Wolfe
         \item The authors agree completely with all associated modifications made to the article pursuant to the policy on claims of priority and novelty of contributions.
-        \item
+        \item The authors have checked the proof completely and have no corrections to make regarding the removal of italics or boldface.
         \item The authors approve of all substitutions made regarding the use of slash between words throughout the document.
@@
 These legends are now a part of the attached figure files, as they should be.
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
-        \item
+        \item The deletion of \verb|\cdot| and addition of \verb|\times| in equation (17) is appropriate.
+        \item Broyden-Fletcher-Goldfarb-Shanno is the correct ``de-initialism'' of BFGS.
+        \item Thanks for noticing that the original sentence was missing something.
+However, the use of ``include'' here would be inappropriate.
+Ultimately, our original definition was unnecessarily complicated and confusing.
+The authors recommend the following substitution: ``...in fact Fig.
+6 and Fig.
+4 share their possibilistic structure.
+A distribution's possibilistic structure is the subset of events which it assigns a non-zero probability.
+That Fig.
+6 and Fig.
+4 have the same...''
+        \item This reference is correct and its link is accurate.
+        \item The reference for [13] is correct in the proof. Updated publishing information for [13]:
+        \begin{verbatim}
+@inproceedings{evans2012graphical,
+  author={R. J. Evans},
+  booktitle={2012 IEEE International Workshop on Machine Learning for Signal Processing},
+  title={Graphical methods for inequality constraints in marginalized DAGs},
+  year={2012},
+  volume={},
+  number={},
+  pages={1-6},
+  doi={10.1109/MLSP.2012.6349796},
+  ISSN={2378-928X},
+  month={Sept},
+}
+        \end{verbatim}
+        \item Updated publishing information for [13]:
+        \begin{verbatim}
+@article{Steudel_2010,
+  title={Information-theoretic inference of common ancestors},
+  author={Steudel, Bastian and Ay, Nihat},
+  journal={Entropy},
+  volume={17},
+  number={4},
+  pages={2304--2327},
+  year={2015},
+  url={http://www.mdpi.com/1099-4300/17/4/2304/htm},
+  publisher={Multidisciplinary Digital Publishing Institute}
+}
+        \end{verbatim}
+        \item The reference for [20] is correct in the proof. Updated publishing information for [20]:
+        \begin{verbatim}
+@article{Weilenmann_2016,
+  title={Non-Shannon inequalities in the entropy vector approach to causal structures},
+  author={Weilenmann, Mirjam and Colbeck, Roger},
+  journal={Quantum},
+  volume={2},
+  pages={57},
+  year={2018},
+  url={https://quantum-journal.org/papers/q-2018-03-14-57/},
+  publisher={Verein zur F{\"o}rderung des Open Access Publizierens in den Quantenwissenschaften}
+}
+        \end{verbatim}
+        \item Publishing information for [21] is accurate and up-to-date.
+        \item Publishing information for [22] is accurate and up-to-date.
+        \item Updated publishing information for [23]:
+        \begin{verbatim}
+@article {evans2015margins,
+  author = {Evans, Robin J.},
+  title = {{Graphs for Margins of Bayesian Networks}},
+  journal = {Scandinavian J. Stat.},
+  volume = {43},
+  number = {3},
+  issn = {1467-9469},
+  url = {https://arxiv.org/abs/1408.1809},
+  doi.hide = {10.1111/sjos.12194},
+  pages = {625--648},
+  keywords = {causal model, directed acyclic graph, latent variable},
+  year = {2016},
+  note = {10.1111/sjos.12194},
+}
+        \end{verbatim}
+        \item Publishing information for [24] is accurate and up-to-date. Also appeared in Conference Proceedings in 2012:
+        \begin{verbatim}
+@inproceedings{richardson2012nested,
+  title={Nested Markov properties for acyclic directed mixed graphs},
+  author={Richardson, Thomas S and Robins, James M and Shpitser, Ilya},
+  booktitle={Proceedings of the Twenty-Eighth Conference on Uncertainty in Artificial Intelligence},
+  pages={13--13},
+  year={2012},
+  organization={AUAI Press}
+}
+        \end{verbatim}
+        \item Publishing information for [29] is accurate and up-to-date.
+        \item Publishing information for [31] is accurate and up-to-date.
+        \item Publishing information for [34] is accurate, accessed today and available at:
+        \begin{verbatim}
+https://wiki.math.ntnu.no/_media/ma2501/2014v/cholesky.pdf
+        \end{verbatim}
+        \item The reference for [47] is correct in the proof.
+        \item The reference for [48] is correct in the proof.
+        \item The reference link for [51] is no longer directed to the correct documentation page as version 6.5 is no longer supported. An updated link and reference for version 8.0 is:
+        \begin{verbatim}
+@Misc{Gurobi_2016,
+  author  = {{Gurobi Optimizer}},
+  title   = {{FarkasDual}},
+  year    = {2018},
+  url     = {https://www.gurobi.com/documentation/8.0/refman/farkasdual.html},
+  urldate = {2018-08-01},
+}
+        \end{verbatim}
+        \item The reference for [52] is correct in the proof.
+        \item The reference for [53] is correct in the proof.
+        \item The reference for [54] is correct in the proof.
         \item[FQ.]
         \item[Q.]
+        \begin{itemize}
+            \item The references for [6,15,24] are correct in the proof.
+            \item These private communications should be dated: November 2016 for [27] and August 2017 for both [41] and [42].
+            \item The reference for [59] is mostly correct; this technical report was ``published'' by the Cambridge University Engineering Dept.
+An access url is \verb|https://infoscience.epfl.ch/record/169768/|.
+        \end{itemize}
     \end{enumerate}
 
+    \textbf{Other Corrections to Address for This Paper:}
+    \begin{itemize}
+        \item The justification of items within Tables I and II are inconsistent.
+        \item In equation (C1), the addition of the \verb|\times| is incorrect. The pertinent portion of equation (C1) is intended to be a comma separated list.
+        \item Page 16 line 1097, there is a citation to [59] typo; the surrounding sentence should read ``A popular tool for linear quantifier elimination is Fourier-Motzkin elimination [21,55,58].'' with [59] omitted.
+        \item Page 1 line 50, should read ``...inequalities can be understood as consequences...''. Currently, the word ``be'' is missing.
+        \item Page 3 line 169, there is a math typo: the descendants of a node $\Delta[\mathcal{G}]n$ should be $\mathsf{De}_{\mathcal{G}}(n)$.
+Specifically, \verb|\mathsf{De}_{\mathcal{G}}(n)| produces the desired effect.
+        \item Page 3 line 198, there is a typo in an inline equation.
+The surrounding sentence should read: ``...existence or non-existence of a set of causal parameters for $\mathcal G$ such that $P_{\mathcal{N}_{O}} = \sum_{n \not \in \mathcal{N}_{O}} P_{\mathcal{N}}$ where $P_{\mathcal{N}}$ is again given by Eq.
+(1).
+The complementary...''.
+        \item Page 5 line 381, there is a small typo; ``variable'' should be ``variables''.
+The surrounding sentence should read: ``...crucial distinction is that $S_{A}$ and $S_{B}$ are random variables representing...''.
+        % \item Page 6 line 472, ``Section VI'' should be ``Sec. VI'' to be consistent with the remainder of the document.
+        \item Page 7 line 511, ``there'' should be omitted. ``Second, it is known that the inequalities...''.
+        \item In several locations, the proof correctly replaces the usage of ``Section'' with its shorthand ``Sec.''.
+Should this correction also be applied to usage of ``Appendix'', i.e.
+``Appendix'' becomes ``App.'' where applicable?
+    \end{itemize}
+
 \end{document}

### 2020-06-02 old/documents/Notes/inequality_demo_temp.tex
figuring out a problem with WagonWheel inequality

@@
 \begin{document}
+
+    \section{June 1, 2020:}
+    As of today, it appears that there is an error in the WagonWheel inequality that ended up in the final manuscript (i.e.
+$I\tsb{WagonWheelAlternativeProperSwap}$).
+Specifically, the uniform distribution over all six bits $A_l, A_r, B_l, B_r, C_l, C_r$, which is causally compatible with the Triangle network, actually violates $I\tsb{WagonWheelAlternativeProperSwap}$:
+    \[ I\tsb{WagonWheelAlternativeProperSwap}\left(\frac{1}{2^6}\right) = +\left(\frac{1}{2}\right)^2-\left(\frac{1}{2}\right)^4+\left(\frac{1}{2}\right)^4+\left(\frac{1}{2}\right)^4\cdots\]
+    \[\cdots-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8 = \frac{19}{64} \not \leq 0.\]
+    Therefore, $I\tsb{WagonWheelAlternativeProperSwap}$ is clearly an invalid inequality and a mistake was introduced somewhere.
+The actually inequality that Elie proposed was $I\tsb{WagonWheelAlternative}$.
+In order to make the inequality in the paper correspond to the Fritz distribution in the paper, wherein $C_lC_r = 11$ plays the distinguished role, I attempted to flip the bits for $C_r$ and $B_l$ and erroneously derived $I\tsb{WagonWheelAlternativeProperSwap}$.
+The \textit{correct} version would have been:
+    \begin{equation*}
+    \begin{gathered}
+        \eq
+        I\tsb{WagonWheelCorrectBitFlip} : \\
+        -P_{A_{l}B_{l}}(11) \\
+        +P_{A_{l}B_{l}C_{l}C_{r}}(1111) \\
+        -P_{A_{l}B_{l}}(00) P_{C_{l}C_{r}}(11) \\
+        -P_{C_{l}C_{r}}(01) P_{C_{l}C_{r}}(10) \\
+        +P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) \\
+        +P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
+        -P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) \\
+        -P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
+        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) \\
+        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
+        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) \\
+        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
+        \leq 0
+    \end{gathered}
+    \end{equation*}
+    This inequality when evaluated at the Fritz distribution ($P_F$) reads term by term:
+    \begin{equation*}
+    \begin{gathered}
+        \eq
+        I\tsb{WagonWheelCorrectFlip}(P_F) : \\
+        -\frac{1}{4}
+        +\frac{1}{4}
+        -\left(\frac{1}{4}\right)^2
+        -\left(\frac{1}{4}\right)^2\\
+        +\frac{1}{4}\left(\frac{1}{32}\left(2-\sqrt{2}\right)\right)
+        +\frac{1}{4}\left(\frac{1}{32}\left(2-\sqrt{2}\right)\right)
+        -\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right)
+        -\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right) \\
+        +\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right)
+        +\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right)
+        +\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right)
+        +\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right) \\
+        =-\frac{1}{16} \leq 0
+    \end{gathered}
+    \end{equation*}
+    Additionally, this inequality when evaluated at the uniform distribution reads term by term:
+    \[ I\tsb{WagonWheelCorrectFlip}\left(\frac{1}{2^6}\right) = -\left(\frac{1}{2}\right)^2+\left(\frac{1}{2}\right)^4-\left(\frac{1}{2}\right)^4-\left(\frac{1}{2}\right)^4\cdots\]
+    \[\cdots+\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8 = -\frac{19}{64} \leq 0\]
+    Upon closer inspection, $I\tsb{WagonWheelCorrectFlip}$ is identical to the inequality found in the paper, with the direction of inequality reverse (i.e. it was off by an overall minus sign).
+
+    Therefore, it appears that either 1) I have isolated the wrong variables to bit-flip in Elie's $I\tsb{WagonWheelAlternative}$, 2) $I\tsb{WagonWheelAlternative}$ was transcribed from Elie incorrectly, 3) $I\tsb{WagonWheelAlternative}$ is incapable of witnessing the Fritz distribution, or 4) $I\tsb{WagonWheelAlternative}$ is not a valid inequality in the first place.
+
+    I suspect the resolution is of type 2) because the Fritz distribution is all about the agreement or disagreement between $A_r$ and $B_r$ in four different $C_lC_r$ contexts, and $I\tsb{WagonWheelAlternative}$ seems to have $A_r = B_r$ in two contexts and $A_r \neq B_r$ in the other two contexts, which is unlike the form of the Fritz distribution.
+
+    \section{September 18, 2017:}
     The current WagonWheel inequality we are using in the paper is the following:

### 2020-06-02 CCIAQVTS/CCIAQVTS.tex

@@
     \begin{abstract}
-        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure.
-Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion.
-In structures where all parties share a common resource, these non-classical correlations are also known as non-local correlations.
-Any constraint satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion.
+        It has long been recognized that certain quantum correlations are incompatible with a particular assumption about classical causal structure.
+Given a causal structure of unknown classicality, the presence of such correlations certifies the nonclassical nature of the causal structure in a device-independent fashion.
+In structures where all parties share a common resource, these nonclassical correlations are also known as non-local correlations.
+Any constraint satisfied by all correlations which are classically compatible with a given causal structure defines a causal compatibility criterion.
 Such criteria were recently derived for the Triangle structure (E.
-Wolfe \textit{et al.}, \href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}) in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations?
-Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary.
+Wolfe \textit{et al.}, \href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}) in the form of polynomial inequalities, begging the question of whether any of those inequalities admit violation by quantum correlations.
+Numerical investigation suggests that they do not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary.
 Our main contribution in this work, however, is the derivation of causal compatibility inequalities for the Triangle structure which do admit quantum violation.
@@
     In recent decades, the technical utility of quantum mechanics has become abundantly clear.
-In the realm of computation, quantum algorithms --- such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016} --- scale exponentially better than their classical counterparts.
-In the realm of secure communication, quantum protocols --- a popular example being Quantum Key Distribution~\cite{Bennett_2014} --- are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill.
-Throughout history, numerous quantum phenomena which fail to be emulated by classical physics have been identified as resources for solving computational or communicational problems~\cite{Neilsen_Chaung_2011}.
+In the realm of computation, quantum algorithms, such as Shor's algorithm~\cite{Shor_1997} and numerous others~\cite{Jordan_2016}, scale exponentially better than their classical counterparts.
+In the realm of secure communication, quantum protocols, a popular example being quantum key distribution~\cite{Bennett_2014}, are able to provide privacy even against hypothetical adversaries with unlimited computational power, a desideratum which classical protocols are unable to fulfill.
+Throughout history, numerous quantum phenomena which fail to be emulated by classical physics have been identified as resources for solving computational or communication problems~\cite{Neilsen_Chaung_2011}.
 Motivated by past successes, a primal objective of modern quantum information theory is to discover new situations wherein quantum mechanics offers an advantage, and to certify that the quantum advantage is genuine.
@@
     From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964,Brunner_2013}.
-Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}.
-The enumeration of Bell inequalities has since become a widespread systematic method for demonstrating the \textit{non-classicality} of a given observation.
-More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}.
+Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous Einstein-Podolsky-Rosen paradox~\cite{EPR_Orig}.
+The enumeration of Bell inequalities has since become a widespread systematic method for demonstrating the nonclassicality of a given observation.
+More recently it has been appreciated that Bell inequalities can be understood as consequences of \term{causal inference}~\cite{Wood_2012}.
 Causal inference is concerned with classifying observations into those which can and cannot be explained by a hypothesized causal structure.
@@
 To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}.
-The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$.
-Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}.
+The fundamental Bell structure involves noncommunicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A$ and $B$) are presumed to be stochastic functions of the local choices of measurement settings ($S_A$ and $S_B$) and the shared resource $\la$.
+Quantum nonclassicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}.
 More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood.
@@
 
-    The Triangle structure (\cref{fig:triangle_structure}) is a causal structure comprised of $3$ parties labeled $A, B, C$ arranged in a triangular configuration while pair-wise sharing hidden/latent variables $X, Y, Z$.
-It has been extensively studied previously (see~\cite[Fig.
+    The Triangle structure (\cref{fig:triangle_structure}) is a causal structure comprised of three parties labeled $A, B,$ and $C$ arranged in a triangular configuration while pairwise sharing hidden (latent) variables $X, Y,$ and $Z$.
+It has been extensively studied previously (see, e.g.,~\cite[Fig.
 1]{Steudel_2010},~\cite[Fig.
@@
 3]{Fritz_2012},~\cite[Fig.
-4]{Weilenmann_2016},~\cite[Fig.
-1]{Inflation}, $\ldots$).
+4]{Weilenmann_2016}, and~\cite[Fig.
+1]{Inflation}).
 An overview of some milestone results is provided in \cref{sec:triangle_structure}.
@@
 Second, the new framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}.
-Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer new insights into quantum non-classicality \cite{Navascues_2017}.
-Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of non-classicality.
+Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer new insights into quantum nonclassicality \cite{Navascues_2017}.
+Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of nonclassicality.
 The authors attempts to find such novel resources were met with only partial success, suggesting the need for both conceptual refinements and future exploration.
@@
 \Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}.
-In the same work~\cite{Fritz_2012}, the Fritz distribution was proven to be non-classical without the use of inequalities.
+In the same work~\cite{Fritz_2012}, the Fritz distribution was proven to be nonclassical without the use of inequalities.
 
@@
 Second, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to find the maximum violations achievable by quantum theory.
-The culmination of these analyses naturally prompts a discussion, found in \Cref{sec:fritz_problem_revisit}, regarding the fundamental problem of recognizing and classifying novel non-classicality in the Triangle structure.
+The culmination of these analyses naturally prompts a discussion, found in \Cref{sec:fritz_problem_revisit}, regarding the fundamental problem of recognizing and classifying novel nonclassicality in the Triangle structure.
 \Cref{sec:conclusions} concludes.
@@
 In such cases, $\prob[\nodes_{O}]$ does not induce a unique set of causal parameters for $\graph$ and \cref{eq:compatibility_as_factorization} can not be verified by direction calculation.
-Instead, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \prod_{n \in \nodes_{O}} \prob[n \mid \Pa[\graph]{n}]$.
+Instead, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \sum_{n \not \in \nodes_{O}} \prob[\nodes]$ where $\prob[\nodes]$ is again given by \cref{eq:compatibility_as_factorization}.
 The complementary, unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$, and should be understood as hidden random variables that are unknowable either by some fundamental process or cannot be measured due to other limitations.
@@
 
-    From the perspective of identifying quantum non-classicality, a causal structure $\graph$ adopts the role of a classical hypothesis.
-Therefore, non-classicality becomes synonymous with incompatibility: if a distribution $\prob[\nodes_{O}]$ is incompatible, then it is non-classical.
+    From the perspective of identifying quantum nonclassicality, a causal structure $\graph$ adopts the role of a classical hypothesis.
+Therefore, nonclassicality becomes synonymous with incompatibility: if a distribution $\prob[\nodes_{O}]$ is incompatible, then it is nonclassical.
 Henceforth, we will use these two terms interchangeably.
-From a resource standpoint, if the non-classicality of $\prob[\nodes_{O}]$ with $\graph$ can be witnessed by an inequality $I$, but nevertheless $\prob[\nodes_{O}]$ can be implemented using quantum states and measurements while otherwise respecting the causal relations of $\graph$, then the causal compatibility inequality $I$ represents a task or game where quantum resources out-perform classical resources relative to $\graph$.
+From a resource standpoint, if the nonclassicality of $\prob[\nodes_{O}]$ with $\graph$ can be witnessed by an inequality $I$, but nevertheless $\prob[\nodes_{O}]$ can be implemented using quantum states and measurements while otherwise respecting the causal relations of $\graph$, then the causal compatibility inequality $I$ represents a task or game where quantum resources out-perform classical resources relative to $\graph$.
 
@@
     This section aims to define the Bell causal structure and to review some of the traditional witnesses used to assess the classicality (or lack thereof) of distributions relative to it.
-The purpose of this section is to equip readers with the pertinent background and also to draw comparisons between the advancements made toward understanding non-classicality of the Bell structure versus analogous results obtained for Triangle structure later in this work.
+The purpose of this section is to equip readers with the pertinent background and also to draw comparisons between the advancements made toward understanding nonclassicality of the Bell structure versus analogous results obtained for Triangle structure later in this work.
 
@@
 
-    Any observed distribution $\prob[AB|S_AS_B]$ which fails to be explained by the classical causal hypothesis of the Bell structure as defined by \cref{eq:bellcompat} is appropriately termed non-classical.
+    Any observed distribution $\prob[AB|S_AS_B]$ which fails to be explained by the classical causal hypothesis of the Bell structure as defined by \cref{eq:bellcompat} is appropriately termed nonclassical.
 Often, distributions incompatible with the Bell structure are referred to as non-local because the Bell structure markedly lacks causal influence from one party to another.
-In particular,~\citet{Bell_1964} demonstrated that there exists distributions that are non-classical yet are attainable via local measurements on a shared quantum resource.
+In particular,~\citet{Bell_1964} demonstrated that there exists distributions that are nonclassical yet are attainable via local measurements on a shared quantum resource.
 
@@
     \end{align}
-    The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions.
+    The nonclassicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions.
 A notable example is the CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original}.
     \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
-    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the non-classical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type.
+    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the nonclassical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type.
 Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.
@@
 
-    The Triangle structure serves as an excellent test case for furthering our understanding of quantum non-classicality in network causal structures.
+    The Triangle structure serves as an excellent test case for furthering our understanding of quantum nonclassicality in network causal structures.
 It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
@@
 The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
-    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum non-classicality.
-It seems reasonable to assume that quantum non-classicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of non-classicality are expected to correspond to novel information-theoretical quantum advantages.
-A fundamental limitation of Fritz's proof of non-classicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
+    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum nonclassicality.
+It seems reasonable to assume that quantum nonclassicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicality are expected to correspond to novel information-theoretical quantum advantages.
+A fundamental limitation of Fritz's proof of nonclassicality, however, is that it does not involve causal compatibility inequalities, and hence does not advance our repertoire of inequality constraints for the Triangle structure.
     Some inequality constraints for the Triangle structure have been derived in previous works.
@@
 Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure.
-In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is non-classical, it is also non-quantum.
+In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is nonclassical, it is also non-quantum.
 The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
@@
 The subsequent failure of these approaches effectively motivates the remainder of this work.
-    In summary, the Triangle structure is a desirable case study because it is known to admit non-classical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions.
-This failure represents a gap in our understanding of quantum non-classicality and prompts the discovery of \textit{new} inequalities.
+    In summary, the Triangle structure is a desirable case study because it is known to admit nonclassical distributions using quantum resources, but yet no inequality heretofore could separate its classical distributions from its quantum distributions.
+This failure represents a gap in our understanding of quantum nonclassicality and prompts the discovery of \textit{new} inequalities.
 
@@
 
-    The analysis of non-classicality changes, however, when $S_{A}, S_{B}$ are not freely chosen by the observers but rather by a process outside of the individual party's control.
+    The analysis of nonclassicality changes, however, when $S_{A}, S_{B}$ are not freely chosen by the observers but rather by a process outside of the individual party's control.
 Relaxing the assumption of measurement independence opens up a possible loophole, namely the possibility that the auxiliary outcomes $S_{A}, S_{B}$ of Alice and Bob might be manipulated via dependence on their shared latent variable $\lambda$.
@@
 
-    The exemplifying quantum distribution corresponding to a recasting of a non-classical Bell structure distribution into the Triangle structure is the \term{Fritz distribution}~\cite{Fritz_2012}.
+    The exemplifying quantum distribution corresponding to a recasting of a nonclassical Bell structure distribution into the Triangle structure is the \term{Fritz distribution}~\cite{Fritz_2012}.
 In the Fritz distribution, denoted $\prob[\fritz]$, each of the variables $A,B,C$ is taken to have $4$ possible outcomes $\bc{0,1,2,3}$.
@@
     Plainly, $\prob[\fritz]$ is a valid but \textit{manufactured} example.
-The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of non-classical resources made accessible by quantum mechanics.
+The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of nonclassical resources made accessible by quantum mechanics.
 The goal, therefore, is to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure \cite{Gisin_2017}.
@@
 
-    \term{Fritz's Problem}: Find an example of non-classical quantum correlations in the Triangle structure together with a proof of its non-classicality which does not hinge on Bell’s theorem.
-
-    Fritz's problem is concerned with how to find and recognize non-classical quantum distributions specifically for the Triangle structure.
-The original proof of non-classicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations~\cite{Fritz_2012}.
-Fritz's problem, as originally stated, does not require that the \emph{type} of non-classicality be novel to the Triangle structure; rather, only that the proof should avoid Bell's theorem.
+    \term{Fritz's Problem}: Find an example of nonclassical quantum correlations in the Triangle structure together with a proof of its nonclassicality which does not hinge on Bell’s theorem.
+
+    Fritz's problem is concerned with how to find and recognize nonclassical quantum distributions specifically for the Triangle structure.
+The original proof of nonclassicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations~\cite{Fritz_2012}.
+Fritz's problem, as originally stated, does not require that the \emph{type} of nonclassicality be novel to the Triangle structure; rather, only that the proof should avoid Bell's theorem.
 \Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem; \Cref{sec:found_inequalities} reports our eventual success, via the discovery of new causal compatibility inequalities.
 
-    Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly novel form of non-classicality for the Triangle structure.
+    Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly novel form of nonclassicality for the Triangle structure.
 Such a discovery would presumably lead to an understanding of new advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open.
 We attempt to make progress on this problem by leveraging the new causal compatibility inequalities derived herein, but \Cref{sec:optimizations} delineates that is effort was plagued by instabilities in our numerical optimization which we have not yet overcome.
-Consequently, \Cref{sec:fritz_problem_revisit} discusses potential avenues for rigorously reformulating Fritz's problem in order to best capture this desire for novel quantum non-classicality.
+Consequently, \Cref{sec:fritz_problem_revisit} discusses potential avenues for rigorously reformulating Fritz's problem in order to best capture this desire for novel quantum nonclassicality.
 
@@
 First, an exhaustive search would need to consider the possibility of larger Hilbert spaces for the shared quantum states.
-Second, there it is known that the inequalities~\cite{Inflation} are incomplete; there exists other constraints on two outcome distributions for the Triangle structure yet to be discovered.
+Second, it is known that the inequalities~\cite{Inflation} are incomplete; there exists other constraints on two outcome distributions for the Triangle structure yet to be discovered.
 
@@
     \Cref{sec:causal_compatibility} introduced the notion of causal compatibility inequalities, and \cref{sec:fritz_distribution} discussed the Fritz distribution ($\prob[\fritz]$) together with the initial inequality-free proof of its incompatibility with the Triangle structure.
-Heretofore, there were no known causal compatibility inequalities for the Triangle structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}.
+Heretofore, there were no known causal compatibility inequalities for the Triangle structure that were capable of witnessing the nonclassicality of any quantum distributions~\cite{Inflation}.
 By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle structure that are violated by the Fritz distribution.
-A representative trio of these $\prob[\fritz]$-incompatibility-witnessing inequalities are presented here: $I\tsb{WagonWheel}$ per \cref{eq:ww_ineq}, notable for its simplicity; $I\tsb{Web}$ per \cref{eq:web_inequality}, which best witnesses the non-classicality of $\prob[\fritz]$ in the presence of noise; and $I\tsb{SymmetricWeb}$ per \cref{eq:symmetric_web_inequality}, which is symmetric with respect to all permutations of the three parties.
+A representative trio of these $\prob[\fritz]$-incompatibility-witnessing inequalities are presented here: $I\tsb{WagonWheel}$ per \cref{eq:ww_ineq}, notable for its simplicity; $I\tsb{Web}$ per \cref{eq:web_inequality}, which best witnesses the nonclassicality of $\prob[\fritz]$ in the presence of noise; and $I\tsb{SymmetricWeb}$ per \cref{eq:symmetric_web_inequality}, which is symmetric with respect to all permutations of the three parties.
 
@@
     We emphasize that each of these causal compatibility inequalities independently provides a positive resolution of Fritz's problem.
-The inequalities are derived without making use of Bell's theorem; rather, they follow from the Inflation Technique's broader perspective on non-classicality as a special case of causal inference.
+The inequalities are derived without making use of Bell's theorem; rather, they follow from the Inflation Technique's broader perspective on nonclassicality as a special case of causal inference.
 Afterwards, Section~\ref{sec:fritz_problem_revisit} returns to the topic of Fritz's problem and the status of our resolution.
@@
 
-    As mentioned in \cref{sec:fritz_distribution}, this original proof of the non-classicality of $\prob[\fritz]$ required an idealistic condition to hold: perfect correlations of $C$ with $A_l, B_l$.
-It is impossible to use Fritz's original argument to confirm non-classicality from an experimental point of view, because every laboratory-achievable distribution is subject to some amount of \text{noise}.
+    As mentioned in \cref{sec:fritz_distribution}, this original proof of the nonclassicality of $\prob[\fritz]$ required an idealistic condition to hold: perfect correlations of $C$ with $A_l, B_l$.
+It is impossible to use Fritz's original argument to confirm nonclassicality from an experimental point of view, because every laboratory-achievable distribution is subject to some amount of \text{noise}.
 One can minimize noise.
@@
 by developing high-accuracy measurement channels, but \emph{perfect} correlations are unattainable.
-Causal compatibility inequalities such as  $I\tsb{Web}$ permit there to be noise within a set of observations before the ability to certify non-classicality breaks down.
+Causal compatibility inequalities such as  $I\tsb{Web}$ permit there to be noise within a set of observations before the ability to certify nonclassicality breaks down.
 
@@
             \includegraphics{figure_noisy_yet_non_local_fritz.pdf}
-            \caption{$\s{N}_{0.085}$: A noisy yet still non-classical variant of the Fritz distribution.}
+            \caption{$\s{N}_{0.085}$: A noisy yet still nonclassical variant of the Fritz distribution.}
             \label{fig:noisy_fritz}
@@
     \subsection{The Symmetric Web Inequality}
-    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies --- seeking violations --- towards the desired end-goal of discovering new forms of non-classicality in the Triangle structure.
-Of course, if some inequality achieves its optimal quantum violation on a distribution qualitatively similar to $\prob[\fritz]$, then such an inequality is unlikely to lead us to discover non-classicality of a type different than $\prob[\fritz]$.
+    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies --- seeking violations --- towards the desired end-goal of discovering new forms of nonclassicality in the Triangle structure.
+Of course, if some inequality achieves its optimal quantum violation on a distribution qualitatively similar to $\prob[\fritz]$, then such an inequality is unlikely to lead us to discover nonclassicality of a type different than $\prob[\fritz]$.
 Indeed, we will show that the previous pair of $I\tsb{WagonWheel}$ and $I\tsb{Web}$, which were both specifically curated to demonstrate the incompatibility of $\prob[\fritz]$, apparently achieve maximum quantum violation on distributions very similar to $\prob[\fritz]$ itself.
@@
 Finding such an inequality proved extremely challenging; while we could generate thousands of inequalities using the Inflation Technique~\cite{Inflation}, it appeared than only a vanishingly-small fraction of those inequalities admitted quantum violation whatsoever.
-We therefore modified the Inflation Technique to give us an inequality which both witnesses the non-classicality of $\prob[\fritz]$ but which is also symmetric with respect to any permutation of the variables $A, B, C$, resulting in \cref{eq:symmetric_web_inequality}.
+We therefore modified the Inflation Technique to give us an inequality which both witnesses the nonclassicality of $\prob[\fritz]$ but which is also symmetric with respect to any permutation of the variables $A, B, C$, resulting in \cref{eq:symmetric_web_inequality}.
 The modification of the Inflation Techniques which forces symmetry is explained in \cref{sec:symmetric_inequalities}.
@@
 
-    In order to find quantum distributions that are more non-classical than the Fritz distribution, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure (\cref{fig:triangle_structure}) and thus expressed in the form of \cref{eq:triangle_Qcompatibility}.
+    In order to find quantum distributions that are more nonclassical than the Fritz distribution, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure (\cref{fig:triangle_structure}) and thus expressed in the form of \cref{eq:triangle_Qcompatibility}.
 In order to parameterize all such distributions, we elect to parameterize the states and measurements separately.
@@
     Since the inequalities we seek to optimally violate are polynomial, and since the space of quantum-accessible distributions is non-convex, we employ a number of optimization methods consecutively in an attempt to avoid pitfalls associated identifying local minima and ill-conditioned convergence.
-Specifically, the BFGS method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
+Specifically, the Broyden-Fletcher-Goldfarb-Shanno method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
 
     Nevertheless, we strongly caution against misinterpreting the numerical optima present in \cref{sec:optima} as if our findings represent genuine global-maxima of violation.
-Evidence for the unreliability of our numerical methods is the following: when supplied with randomly sampled initial parameters, \emph{all} optimization methods consistently converged to \emph{saturating} the target inequalities, instead of violating it!
+Evidence for the unreliability of our numerical methods is the following: When supplied with randomly sampled initial parameters, \emph{all} optimization methods consistently converged to \emph{saturating} the target inequalities, instead of violating it!
 This, even though we \emph{know} that all the inequalities we consider \emph{do} admit quantum violation, namely by  $\prob[\fritz]$.
@@
         \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{Web}$.
-Notice that this distribution has precisely the same possibilistic structure as the Fritz distribution, as might be expected, since $I\tsb{Web}$ was specifically generated to witness the non-classicality of $\prob[\fritz]$.}
+Notice that this distribution has precisely the same possibilistic structure as the Fritz distribution, as might be expected, since $I\tsb{Web}$ was specifically generated to witness the nonclassicality of $\prob[\fritz]$.}
         \label{fig:maximum_violation_I_1}
@@
 Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution; in fact \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share their \term{possibilistic structure}.
-A distribution's possibilistic structure the partitioning of events into two disjoint subsets: one containing those events that occur with non-zero probability (possible), the other containing the zero probability events (impossible).
+A distribution's possibilistic structure is the subset of events which it assigns a non-zero probability.
 That \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} have the same possibilistic structure is not entirely unexpected;  As was mentioned in \cref{sec:found_inequalities}, as $I\tsb{Web}$ was derived specifically to prove the incompatibility of the Fritz distribution with the Triangle structure.
@@
     It is perhaps curious, however, that violation achieved by the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:triangle_Qcompatibility} are restricted to maximally entangled states.
-This finding of more-violation with less-entanglement resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} demonstrating that entanglement and non-classicality are different resources.
+This finding of more-violation with less-entanglement resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} demonstrating that entanglement and nonclassicality are different resources.
 
@@
 In addition, \cref{sec:fritz_distribution} discusses Fritz's Problem as a quest to find quantum distributions incompatible with the Triangle structure that are also qualitatively distinct from those distributions which are incompatible with the Bell structure.
-In light of the perhaps unsatisfactory results of~\cref{sec:optimizations}, the purpose of this section is to revisit Fritz's problem and to attempt to rigorously formulate criterion for quantum non-classicality that is genuine to the Triangle structure.
-
-    When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a \textit{single} bipartite quantum state.
+In light of the perhaps unsatisfactory results of~\cref{sec:optimizations}, the purpose of this section is to revisit Fritz's problem and to attempt to rigorously formulate criterion for quantum nonclassicality that is genuine to the Triangle structure.
+
+    When specifically concerned with entanglement resources, Bell structure nonclassicality exploits the entanglement of a \textit{single} bipartite quantum state.
 Unlike the Bell structure in~\Cref{fig:bell_structure}, the observable nodes of the Triangle structure in~\Cref{fig:triangle_structure} have access to potentially \textit{three} different bipartite quantum states.
-As noted in~\cite{Fritz_2012}, the Fritz distribution can be implemented using only a \textit{single} entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at \textit{minimum}, one is necessary.} Therefore, it becomes reasonable to propose that any quantum non-classicality in the Triangle structure that \textit{requires} entanglement in \textit{at least two} shared states constitutes non-classicality distinct from Bell non-classicality.
+As noted in~\cite{Fritz_2012}, the Fritz distribution can be implemented using only a \textit{single} entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at \textit{minimum}, one is necessary.} Therefore, it becomes reasonable to propose that any quantum nonclassicality in the Triangle structure that \textit{requires} entanglement in \textit{at least two} shared states constitutes nonclassicality distinct from Bell nonclassicality.
 At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource unique to the Triangle structure.
 Unfortunately, this is not the case.
-By increasing the cardinality of each variable $A, B, C$ to $4^{3} = 64$, it is possible to generate a distribution that is non-classical yet quantum and requires \textit{all three} of the shared resources to be entangled.
+By increasing the cardinality of each variable $A, B, C$ to $4^{3} = 64$, it is possible to generate a distribution that is nonclassical yet quantum and requires \textit{all three} of the shared resources to be entangled.
 This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings.
 Such a distribution would require entanglement in all three quantum states; under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible\footnote{This observation was original provided by Miguel Navascués.}.
-Consequently, demanding the necessity of entanglement in every shared state is insufficient for finding novel non-classicality.
-
-    In consideration of this particular construction, perhaps the correct assessment for novel non-classicality must incorporate a restriction on the the cardinality of the observed variables?
-Pursuant to this objective, we were able to prove the non-classicality of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations\footnote{An inequality-free proof of the incompatibility of this distribution, using arguments analogous those presented in~\cite{Fritz_2012}, can be found in~\cite{Weilenmann_2016}.
+Consequently, demanding the necessity of entanglement in every shared state is insufficient for finding novel nonclassicality.
+
+    In consideration of this particular construction, perhaps the correct assessment for novel nonclassicality must incorporate a restriction on the the cardinality of the observed variables?
+Pursuant to this objective, we were able to prove the nonclassicality of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations\footnote{An inequality-free proof of the incompatibility of this distribution, using arguments analogous those presented in~\cite{Fritz_2012}, can be found in~\cite{Weilenmann_2016}.
 Assessing the compatibility of this variant using the methods in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities} was first suggested to the authors by Denis Rosset.}.
-Nonetheless, such a distribution fails to deviate significantly from Bell non-classicality.
+Nonetheless, such a distribution fails to deviate significantly from Bell nonclassicality.
 
     It is worth noting that there are quantum-accessible distributions which are conjectured, but not proven, to be incompatible with the Triangle structure.
-For instance, the distribution proposed in~\cite{Gisin_2017} required the use of entangled measurements, and thus if proven incompatible, might constitute a novel form of quantum non-classicality.
+For instance, the distribution proposed in~\cite{Gisin_2017} required the use of entangled measurements, and thus if proven incompatible, might constitute a novel form of quantum nonclassicality.
 Unfortunately, as was previously noted in~\cref{sec:found_inequalities}, the proposed distribution in~\cite{Gisin_2017} satisfies all inequalities generated by the inflations considered in~\cref{fig:inflations}.
@@
     In \cref{sec:triangle_structure}, we elucidated that establishing or rejecting compatibility with the Triangle structure has been a challenging problem for nearly a decade \cite{Steudel_2010,Branciard_2012,Henson_2014,Fritz_2012,Gisin_2017}.
-Though some causal compatibility inequalities were known, those inequalities did not appear useful for the purpose of witnessing quantum non-classicality.
-Recently,~\citet{Fritz_2012} gave the first example of quantum non-classicality in the Triangle structure, relying on an inequality-free proof that is not robust to any amount of noise.
+Though some causal compatibility inequalities were known, those inequalities did not appear useful for the purpose of witnessing quantum nonclassicality.
+Recently,~\citet{Fritz_2012} gave the first example of quantum nonclassicality in the Triangle structure, relying on an inequality-free proof that is not robust to any amount of noise.
 
@@
 
-    Despite these advancements, the distributions we discovered hew closely to the Fritz distribution, indicating that their non-classical nature remains some recycled version of the non-classicality found in the Bell structure.
-\Cref{sec:fritz_problem_revisit} discusses potential proposals certifying the genuineness of non-classicality in the Triangle structure.
-Presently, the existence, and subsequent suitable classification of fundamentally novel non-classicality remains speculative, and certainly warrants future research.
+    Despite these advancements, the distributions we discovered hew closely to the Fritz distribution, indicating that their nonclassical nature remains some recycled version of the nonclassicality found in the Bell structure.
+\Cref{sec:fritz_problem_revisit} discusses potential proposals certifying the genuineness of nonclassicality in the Triangle structure.
+Presently, the existence, and subsequent suitable classification of fundamentally novel nonclassicality remains speculative, and certainly warrants future research.
 
@@
 From the perspective of a marginal polytope, convex hull algorithms or linear quantifier elimination can be used to compute a representation of the complete set of linear inequalities and completely solve the marginal problem.
-A popular tool for linear quantifier elimination is \term{Fourier-Motzkin elimination} \cite{Dantzig_1973,Inflation,Abramsky_2012,jones_2004}.
+A popular tool for linear quantifier elimination is \term{Fourier-Motzkin elimination} \cite{Dantzig_1973,Inflation,Abramsky_2012}.
 Applying the Fourier-Motzkin procedure to completely solve the marginal problem is discussed in more detail in \citet{Fritz_2011}.

### 2020-06-02 documents/Proof Response/proof_response.tex

@@
 
+    \textbf{Attached Files:}
+    \begin{itemize}
+        \item {\verb|references.bib|} is a complete references file for the entire manuscript.
+Specifically, entries that required updating have been updated pursuant to the individual updates summarized below.
+        \item Each of the four \verb|figure_*.pdf| files are explained in correction (7.) below:
+    \end{itemize}
+
     \textbf{Specific Questions and Comments to Address for This Paper:}
     \begin{enumerate}
-        \item TODO: Email E. Wolfe
+        \item Currently, the publishing information for this reference is up-to-date.
         \item The authors agree completely with all associated modifications made to the article pursuant to the policy on claims of priority and novelty of contributions.
@@
 The discrepancy between the figure files and appearance in the submitted article were a result of using the a clipping/trimming option of \verb|\includegraphics| command of the \verb|graphicx| package in order to trim whitespace and superfluous figure titles.
-The usage of the this option is as follows:
+The usage of this option is as follows:
         \begin{verbatim}\includegraphics[trim={<left> <lower> <right> <upper>},clip]{figure_example.pdf}\end{verbatim}
-        Attached to this proof correction are ``corrected'' figure replacements for figures 4, 5, 6 and 7 which have the cropping already applied.
+        Nonetheless, attached to this proof correction are ``corrected'' figure replacements for figures 4, 5, 6 and 7 which have the cropping already applied.
 As such, the figures should now appear correctly in the article and will match the figure files exactly.
@@
         \item The reference for [54] is correct in the proof.
-        \item[FQ.]
+        \item[FQ.] The funding information is both correct and complete.
         \item[Q.]
@@
             \item The references for [6,15,24] are correct in the proof.
-            \item These private communications should be dated: November 2016 for [27] and August 2017 for both [41] and [42].
+            \item The authors recommend that these private communications be dated: November 2016 for [27] and August 2017 for both [41] and [42].
             \item The reference for [59] is mostly correct; this technical report was ``published'' by the Cambridge University Engineering Dept.
@@
 
-    \textbf{Other Corrections to Address for This Paper:}
+    \textbf{Other Comments to Address for This Paper:}
     \begin{itemize}
+        \item The author's names and institution's names are all spelled correctly.
+        \item The removal of the word ``of'' from the paper title is noted by the authors and approved.
         \item The justification of items within Tables I and II are inconsistent.
         \item In equation (C1), the addition of the \verb|\times| is incorrect. The pertinent portion of equation (C1) is intended to be a comma separated list.
-        \item Page 16 line 1097, there is a citation to [59] typo; the surrounding sentence should read ``A popular tool for linear quantifier elimination is Fourier-Motzkin elimination [21,55,58].'' with [59] omitted.
+        \item Page 16 line 1097, there is an inappropriate citation to [59]; the surrounding sentence should read ``A popular tool for linear quantifier elimination is Fourier-Motzkin elimination [21,55,58].'' with [59] omitted.
         \item Page 1 line 50, should read ``...inequalities can be understood as consequences...''. Currently, the word ``be'' is missing.

### 2020-06-02 CCIAQVTS/CCIAQVTS.tex
non-local -> nonlocal

@@
 Given a causal structure of unknown classicality, the presence of such correlations certifies the nonclassical nature of the causal structure in a device-independent fashion.
-In structures where all parties share a common resource, these nonclassical correlations are also known as non-local correlations.
+In structures where all parties share a common resource, these nonclassical correlations are also known as nonlocal correlations.
 Any constraint satisfied by all correlations which are classically compatible with a given causal structure defines a causal compatibility criterion.
@@
     Any observed distribution $\prob[AB|S_AS_B]$ which fails to be explained by the classical causal hypothesis of the Bell structure as defined by \cref{eq:bellcompat} is appropriately termed nonclassical.
-Often, distributions incompatible with the Bell structure are referred to as non-local because the Bell structure markedly lacks causal influence from one party to another.
+Often, distributions incompatible with the Bell structure are referred to as nonlocal because the Bell structure markedly lacks causal influence from one party to another.
 In particular,~\citet{Bell_1964} demonstrated that there exists distributions that are nonclassical yet are attainable via local measurements on a shared quantum resource.
@@
     Plainly, $\prob[\fritz]$ is a valid but \textit{manufactured} example.
-The phenomenology associated with Bell non-locality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of nonclassical resources made accessible by quantum mechanics.
+The phenomenology associated with Bell nonlocality or Bell incompatibility are well understood; examining these distributions embedded in the Triangle structure offers no additional perspective onto the types of nonclassical resources made accessible by quantum mechanics.
 The goal, therefore, is to find incompatible quantum distributions that are qualitatively different than those previously considered for the Bell structure \cite{Gisin_2017}.

### 2020-06-02 CCIAQVTS/CCIAQVTS.tex
made some edits to punctuation to make arxiv more on parity with PRA

@@
 
-    This work is the first, therefore, to find causal compatibility inequalities for the Triangle structure that are known to be violated by quantum-accessible distributions.
-This accomplishment was made possible through the combination of two previous developments.
-First, the insight of \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure.
-Second, the new framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}.
-Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer new insights into quantum nonclassicality \cite{Navascues_2017}.
-Moreover, these new inequalities offer an avenue for recognizing previously unknown forms of nonclassicality.
-The authors attempts to find such novel resources were met with only partial success, suggesting the need for both conceptual refinements and future exploration.
+    This work finds causal compatibility inequalities for the Triangle structure that are known to be violated by quantum-accessible distributions.
+This accomplishment was made possible through the combination of two previous developments: first, the insight of \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure, and second, the framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}.
+Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer insights into quantum nonclassicality \cite{Navascues_2017}.
+Moreover, these inequalities offer an avenue for recognizing previously unknown forms of nonclassicality.
+The authors' attempts to find such novel resources were met with only partial success, suggesting the need for both conceptual refinements and future exploration.
 
@@
 \Cref{sec:bell_structure} offers a summary of the popular Bell structure and associated inequalities.
-\Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research; identifying its stark differences from the Bell structure and motivating why the Triangle structure is worth studying.
-\Cref{sec:fritz_distribution} defines and discusses a singularly-quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}.
+\Cref{sec:triangle_structure} discusses the Triangle structure and provides an overview of existing research, identifying its stark differences from the Bell structure and motivating why the Triangle structure is worth studying.
+\Cref{sec:fritz_distribution} defines and discusses a singularly quantum correlation first conceived of by \citet{Fritz_2012}, which we term the \term{Fritz distribution}.
 In the same work~\cite{Fritz_2012}, the Fritz distribution was proven to be nonclassical without the use of inequalities.
@@
 Specifically, in \cref{sec:found_inequalities} we improve upon the results of \citet{Fritz_2012} by offering a direct proof of the incompatibility of the Fritz distribution using inequalities generated by the Inflation Technique~\cite{Inflation}.
-A sample of such inequalities are presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality}.
+A sample of such inequalities is presented in \cref{sec:found_inequalities}, specifically \cref{eq:ww_ineq}, \cref{eq:web_inequality}, and \cref{eq:symmetric_web_inequality}.
 Aside from confirming the utility of the Inflation Technique, this paper explores the importance of having derived these inequalities.
@@
     The nonclassicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities which constrain the correlations between binary variables $A$ and $B$ for classically compatible distributions.
-A notable example is the CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original}.
+A notable example is the Clauser-Horne-Shimony-Holt (CHSH) inequality~\cite{CHSH_Original}.
     \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
@@
 The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
-    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so its known to possess quantum nonclassicality.
+    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so it is known to possess quantum nonclassicality.
 It seems reasonable to assume that quantum nonclassicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicality are expected to correspond to novel information-theoretical quantum advantages.
@@
 The original proof of nonclassicality essentially recycled Bell's theorem, and was limited by the requirement of perfect correlations~\cite{Fritz_2012}.
-Fritz's problem, as originally stated, does not require that the \emph{type} of nonclassicality be novel to the Triangle structure; rather, only that the proof should avoid Bell's theorem.
+Fritz's problem, as originally stated, does not require that the \emph{type} of nonclassicality be novel to the Triangle structure, rather, only that the proof should avoid Bell's theorem.
 \Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem; \Cref{sec:found_inequalities} reports our eventual success, via the discovery of new causal compatibility inequalities.
@@
 
-    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations (in search of violation) against the previously-published compatibility inequalities of~\citet{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014}.
+    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations (in search of violation) against the previously published compatibility inequalities of~\citet{Inflation}, as well as against the entropic inequalities of \citet{Henson_2014}.
 For historical context, the entropic inequalities of \cite{Henson_2014} have already been independently investigated for quantum incompatibility by \citet{Weilenmann_2016} using a variety of computational methods.
@@
     \subsection{The Symmetric Web Inequality}
-    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies --- seeking violations --- towards the desired end-goal of discovering new forms of nonclassicality in the Triangle structure.
+    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies, seeking violations, towards the desired end-goal of discovering new forms of nonclassicality in the Triangle structure.
 Of course, if some inequality achieves its optimal quantum violation on a distribution qualitatively similar to $\prob[\fritz]$, then such an inequality is unlikely to lead us to discover nonclassicality of a type different than $\prob[\fritz]$.
@@
     Our best numerical optimization of $I\tsb{SymmetricWeb}$ is visualized in \cref{fig:maximum_violation_I_3}.
-Counter-intuitively, the distribution in \cref{fig:maximum_violation_I_3} --- which achieves a greater violation of $I\tsb{SymmetricWeb}$ than $\prob[\fritz]$ --- shares its \textit{possibilistic} structure with the Fritz distribution!
+Counter-intuitively, the distribution in \cref{fig:maximum_violation_I_3}, which achieves a greater violation of $I\tsb{SymmetricWeb}$ than $\prob[\fritz]$, shares its \textit{possibilistic} structure with the Fritz distribution!
 Additionally, since $I\tsb{SymmetricWeb}$ is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well.
@@
     \[ N_1' \ancestralindep N_2' \iff \An[\graph']{N_1'} \cap \An[\graph']{N_2'}= \emptyset \eq \]
-    Ancestral independence implies an unconditional probabilistic independence --- if $N_1' \ancestralindep N_2'$ then $\prob[N_1' \cup N_2'] = \prob[N_1']\prob[N_2']$.
+    Ancestral independence implies an unconditional probabilistic independence: if $N_1' \ancestralindep N_2'$ then $\prob[N_1' \cup N_2'] = \prob[N_1']\prob[N_2']$.
 If $N_1', N_2' \in \Inj[\graph]{\graph'}$, then the associated probabilistic constraint is applicable to $\prob^{\Inj[\graph]{\graph'}}$.
@@
 In practice, the equality constraints implied by $\AIExpr[\graph]{\graph'}$ permits one to construct a marginal model defined over the ai-expressible sets $\AIExpr[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$.
-In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (\cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$ --- the latter of which is discussed in \cref{sec:deriving_inequalities}.
+In summary, the Inflation Technique partially transforms the compatibility problem into a marginal problem, wherein one can solve the marginal problem (\cref{sec:marginal_satisfiability}) to either determine the compatibility of an observable distribution $\prob[\nodes_O]$ with $\graph$ or derive compatibility inequalities for $\graph$, the latter of which is discussed in \cref{sec:deriving_inequalities}.
 
@@
     Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
-This marginal scenario $\mscenario$ then defines an incidence matrix $M$ capable of accommodating the Fritz distribution that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = 4^8 = 65,536$ columns --- this matrix is not reproduced here.
+This marginal scenario $\mscenario$ then defines an incidence matrix $M$ capable of accommodating the Fritz distribution that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = 4^8 = 65,536$ columns; this matrix is not reproduced here.
 The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
@@
     For the Triangle structure in particular, the variable permutation group is the set of permutations on $A, B, C$: $\Phi\br{\mscenario} = \Perm{A, B, C}$.
-For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\AIExpr[\graph]{\graph'}}$ --- an order $48$ group with the following $4$ generators:
+For the Web inflation (\cref{fig:the_web_inflation}), we have obtained $\gp\br{\AIExpr[\graph]{\graph'}}$, an order $48$ group with the following $4$ generators:
     \begin{equation}

### 2020-06-02 CCIAQVTS/CCIAQVTS.tex
changed the wagon wheel inequality to the correct one, and changed the violation amount to the correct one
added an Acknowledgement to Chaves for spotting the error with the Wagon-Wheel inequality

@@
         I\tsb{WagonWheel} : \\
-        +P_{A_{l}B_{l}}(11) -P_{A_{l}B_{l}C_{l}C_{r}}(1111) +P_{A_{l}B_{l}}(00) P_{C_{l}C_{r}}(11) +P_{C_{l}C_{r}}(01) P_{C_{l}C_{r}}(10) \\
-        -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
-        -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
-        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
-        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
+        -P_{A_{l}B_{l}}(10)
+        +P_{A_{l}B_{l}C_{l}C_{r}}(1010)
+        -P_{A_{l}B_{l}}(01) P_{C_{l}C_{r}}(10)
+        -P_{C_{l}C_{r}}(00) P_{C_{l}C_{r}}(11) \\
+        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110)
+        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
+        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111)
+        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
+        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001)
+        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
+        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000)
+        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
         \leq 0
@@
 
-    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it.
+    \Cref{eq:ww_ineq} is termed the Wagon-Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it.
 To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}.
@@
     By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure per \cref{eq:triangle_compatibility} must satisfy $I\tsb{WagonWheel}$.
-On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $\f{1}{16} \not \leq 0$.
+On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $\f{1}{16}(\sqrt{2} - 1) \not \leq 0$.
 Consequently we affirm that the Fritz distribution is incompatible with the Triangle structure, a fact previously only demonstrated without inequalities.
@@
 The authors are grateful to Miguel Navascués and Denis Rosset for their insightful discussions.
+The authors would like to thank Rafael Chaves for identifying an error with the Wagon-Wheel inequality found in earlier versions of this paper.
     \end{acknowledgments}

### 2020-07-14 CCIAQVTS/CCIAQVTS_errata.tex
finished the first draft of the errata

% === Revtex Declaration ===
\documentclass[aps, 10pt, english, twoside, pra, nofootinbib, tightenlines, longbibliography, superscriptaddress, notitlepage]{revtex4-1}

% === Bibliography Style Options ===
\bibliographystyle{apsrev4-1}
\setlength{\bibsep}{3pt plus 3pt minus 2pt}

% === Packages ===
\usepackage{document_config}

\begin{document}
    \title{Erratum: Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tfraser@perimeterinstitute.ca}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \maketitle
    % \tableofcontents
    % \setlength{\parskip}{1em}
    \section{The Wagon-Wheel Inequality}
    Our article claimed that inequality (12), reproduced here,
    \begin{equation*}
    \begin{gathered}
        \eq\label[ineq]{eq:ww_ineq_incorrect}
        I\tsb{WagonWheel} : \\
        +P_{A_{l}B_{l}}(11) -P_{A_{l}B_{l}C_{l}C_{r}}(1111) +P_{A_{l}B_{l}}(00) P_{C_{l}C_{r}}(11) +P_{C_{l}C_{r}}(01) P_{C_{l}C_{r}}(10) \\
        -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        \leq 0,
    \end{gathered}
    \end{equation*}
    is a valid causal compatibility inequality for the triangle structure. Additionally, we claimed that the distribution in equation (8), namely Fritz's distrubtion $P_{\text{F}}$, achieves a violation of the above inequality with a numerical value of $\frac{1}{16} \not\leq 0$. Both of these reported claims are false.

    One avenue for correcting the above inequality would be to simply reverse the direction of the inequality sign ($\leq \mapsto \geq$), or equivalently flip the sign of each of the coefficients. While the inequality resulting from such a correction would indeed be a valid causal compatibility inequality for the triangle structure, it has the undesirable feature of being \textit{satisfied} by the Fritz's distribution $P_{\text{F}}$ with a numerical value of $\frac{1}{16} \geq 0$.

    Therefore, it is our recommendation to replace the incorrect inequality above with the following inequality:
    \begin{equation*}
    \begin{gathered}
        \eq\label[ineq]{eq:ww_ineq_correct}
        I\tsb{WagonWheel} : \\
        -P_{A_{l}B_{l}}(10)
        +P_{A_{l}B_{l}C_{l}C_{r}}(1010)
        -P_{A_{l}B_{l}}(01) P_{C_{l}C_{r}}(10)
        -P_{C_{l}C_{r}}(00) P_{C_{l}C_{r}}(11) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110)
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111)
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001)
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000)
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        \leq 0.
    \end{gathered}
    \end{equation*}
    Note that inequality~(\ref{eq:ww_ineq_correct}) is related to inequality~(\ref{eq:ww_ineq_incorrect}) by (i) flipping the signs of every coefficient, and (ii) flipping the bit-values for both $B_r$ and $C_l$. This substitute inequality is indeed a valid causal compatibility inequality for the triangle structure and moreover is violated by the Fritz distribution with a numerical violation of $\f{1}{16}(\sqrt{2} - 1) \not \leq 0$.

    It is also worth noting that the qualitative features of the wagon-wheel inequality discussed in the ``Numerical optimization results'' section of the published article were actually obtained from our proposed substitute inequality~(\ref{eq:ww_ineq_correct}), not the incorrectly published inequality~(\ref{eq:ww_ineq_incorrect}), and therefore those comments do not require any alteration. Inequality~(\ref{eq:ww_ineq_incorrect}) was published in place of inequality~(\ref{eq:ww_ineq_correct}) due to an error made by the first author during the final drafting stages of the manuscript.

    \section{Figure 1}
    The diagram appearing in Figure 1 of our article is incorrectly a duplicate of the diagram appearing in Figure 3. Instead, Figure 1 should have been been the following:
    \begin{figure}
        \centering
        \scalebox{1.0}{\includegraphics{figure_bell_structure.pdf}}
        \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
        \label{fig:bell_structure}
    \end{figure}

    %\begin{align*}
    %\eq \label{eq:fritz_dist_bit_variant}
    %\begin{split}
    %    \prob[\fritz][00,00,00] = \prob[\fritz][01,01,00] = \prob[\fritz][00,10,01] = \prob[\fritz][01,11,01] &= \f{1}{32}\br{2 + \sqrt{2}} \\
    %    \prob[\fritz][10,00,10] = \prob[\fritz][11,01,10] = \prob[\fritz][10,11,11] = \prob[\fritz][11,10,11] &= \f{1}{32}\br{2 + \sqrt{2}} \\
    %    \prob[\fritz][00,01,00] = \prob[\fritz][01,00,00] = \prob[\fritz][00,11,01] = \prob[\fritz][01,10,01] &= \f{1}{32}\br{2 - \sqrt{2}} \\
    %    \prob[\fritz][10,01,10] = \prob[\fritz][11,00,10] = \prob[\fritz][10,10,11] = \prob[\fritz][11,11,11] &= \f{1}{32}\br{2 - \sqrt{2}}
    %\end{split}
    %\end{align*}

    \begin{acknowledgments}
        The authors would like to thank Rafael Chaves for identifying the error with the wagon-wheel inequality found in earlier versions of this paper.
    \end{acknowledgments}

    % \bibliographystyle{apsrev4-1}
    \nocite{apsrev41Control}
    \bibliography{references}

\end{document}

### 2020-07-14 CCIAQVTS/CCIAQVTS.tex
removed all non-PRA instances of 'new'

@@
 Fritz's problem, as originally stated, does not require that the \emph{type} of nonclassicality be novel to the Triangle structure, rather, only that the proof should avoid Bell's theorem.
-\Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem; \Cref{sec:found_inequalities} reports our eventual success, via the discovery of new causal compatibility inequalities.
+\Cref{sec:preliminary_research} delineates our initial, failed attempts at resolving Fritz's problem; \Cref{sec:found_inequalities} reports our eventual success, via the discovery of different causal compatibility inequalities.
 
     Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly novel form of nonclassicality for the Triangle structure.
-Such a discovery would presumably lead to an understanding of new advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open.
-We attempt to make progress on this problem by leveraging the new causal compatibility inequalities derived herein, but \Cref{sec:optimizations} delineates that is effort was plagued by instabilities in our numerical optimization which we have not yet overcome.
+Such a discovery would presumably lead to an understanding of different advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open.
+We attempt to make progress on this problem by leveraging the causal compatibility inequalities derived herein, but \Cref{sec:optimizations} delineates that is effort was plagued by instabilities in our numerical optimization which we have not yet overcome.
 Consequently, \Cref{sec:fritz_problem_revisit} discusses potential avenues for rigorously reformulating Fritz's problem in order to best capture this desire for novel quantum nonclassicality.
@@
     \subsection{The Symmetric Web Inequality}
-    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies, seeking violations, towards the desired end-goal of discovering new forms of nonclassicality in the Triangle structure.
+    In \cref{sec:optimizations} we will consider numerically optimizing our inequalities over quantum strategies, seeking violations, towards the desired end goal of discovering different forms of nonclassicality in the Triangle structure.
 Of course, if some inequality achieves its optimal quantum violation on a distribution qualitatively similar to $\prob[\fritz]$, then such an inequality is unlikely to lead us to discover nonclassicality of a type different than $\prob[\fritz]$.
@@
 As noted in~\cite{Fritz_2012}, the Fritz distribution can be implemented using only a \textit{single} entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at \textit{minimum}, one is necessary.} Therefore, it becomes reasonable to propose that any quantum nonclassicality in the Triangle structure that \textit{requires} entanglement in \textit{at least two} shared states constitutes nonclassicality distinct from Bell nonclassicality.
-At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource unique to the Triangle structure.
+At first, one might suspect that finding such distributions would affirmatively demonstrate a form of entanglement resource unique to the Triangle structure.
 Unfortunately, this is not the case.
@@
     Unlike $\prob^{\ImInj[\graph]{\graph'}}$, which is non-contextual by construction, $\prob^{\Inj[\graph]{\graph'}}$ contains overlapping marginals meaning its contextuality remains unknown and must be determined using any of the techniques discussed in~\cref{sec:marginal_satisfiability}.
-More importantly, the Inflation Technique introduces new constraints relating to the ai-expressible sets.
+More importantly, the Inflation Technique introduces constraints relating to the ai-expressible sets.
 In practice, the equality constraints implied by $\AIExpr[\graph]{\graph'}$ permits one to construct a marginal model defined over the ai-expressible sets $\AIExpr[\graph]{\graph'}$ resulting in greater resolution in classifying the compatibility of $\prob[\nodes_O]$.

### 2020-07-14 CCIAQVTS/CCIAQVTS.tex
removed all non-PRA instances of 'novel'

@@
 Second, we numerically optimize our derived inequalities over quantum-accessible distributions (using qubits) in an effort to find the maximum violations achievable by quantum theory.
-The culmination of these analyses naturally prompts a discussion, found in \Cref{sec:fritz_problem_revisit}, regarding the fundamental problem of recognizing and classifying novel nonclassicality in the Triangle structure.
+The culmination of these analyses naturally prompts a discussion, found in \Cref{sec:fritz_problem_revisit}, regarding the fundamental problem of recognizing and classifying nonclassicality in the Triangle structure.
 \Cref{sec:conclusions} concludes.
@@
 
-    Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly novel form of nonclassicality for the Triangle structure.
+    Though not explicit, we read in the spirit of Fritz's problem a desideratum for the discovery of a truly different form of nonclassicality for the Triangle structure.
 Such a discovery would presumably lead to an understanding of different advantages of quantum resources in network structures; this related problem has attracted attention and conjecture \cite{Gisin_2017}, but remains open.
@@
     It is worth noting that there are quantum-accessible distributions which are conjectured, but not proven, to be incompatible with the Triangle structure.
-For instance, the distribution proposed in~\cite{Gisin_2017} required the use of entangled measurements, and thus if proven incompatible, might constitute a novel form of quantum nonclassicality.
+For instance, the distribution proposed in~\cite{Gisin_2017} required the use of entangled measurements and thus if proven incompatible might constitute a different form of quantum nonclassicality.
 Unfortunately, as was previously noted in~\cref{sec:found_inequalities}, the proposed distribution in~\cite{Gisin_2017} satisfies all inequalities generated by the inflations considered in~\cref{fig:inflations}.

### 2020-07-14 CCIAQVTS/CCIAQVTS.tex
made the hyphens consistent whereever PRA was consistent (PRA inconsistent about quantum-accessible, non-existence, non-zero, etc.

@@
 Identifying causal compatibility inequalities for this configuration has been seen as particularly challenging~\cite{Branciard_2012}.
-Further identifying causal compatibility inequalities of such high resolution that such inequalities can be violated by quantum-accessible distributions has remained out-of-reach for the Triangle structure.
+Further identifying causal compatibility inequalities of such high resolution that such inequalities can be violated by quantum-accessible distributions has remained out of reach for the Triangle structure.
 
     This work finds causal compatibility inequalities for the Triangle structure that are known to be violated by quantum-accessible distributions.
-This accomplishment was made possible through the combination of two previous developments: first, the insight of \citet{Fritz_2012} regarding the ability to re-interpret the Bell structure as a portion of the Triangle structure, and second, the framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}.
+This accomplishment was made possible through the combination of two previous developments: first, the insight of \citet{Fritz_2012} regarding the ability to reinterpret the Bell structure as a portion of the Triangle structure, and second, the framework for solving causal inference problems developed by~\citet{Inflation} called \term{The Inflation Technique}.
 Ultimately, this work serves as a validation that the Inflation Technique is efficient and sensitive enough at low orders to offer insights into quantum nonclassicality \cite{Navascues_2017}.
@@
 In such cases, $\prob[\nodes_{O}]$ does not induce a unique set of causal parameters for $\graph$ and \cref{eq:compatibility_as_factorization} can not be verified by direction calculation.
-Instead, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or non-existence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \sum_{n \not \in \nodes_{O}} \prob[\nodes]$ where $\prob[\nodes]$ is again given by \cref{eq:compatibility_as_factorization}.
+Instead, compatibility between $\graph$ and $\prob[\nodes_{O}]$ depends on the existence or nonexistence of a set of causal parameters for $\graph$ such that $\prob[\nodes_{O}] = \sum_{n \not \in \nodes_{O}} \prob[\nodes]$ where $\prob[\nodes]$ is again given by \cref{eq:compatibility_as_factorization}.
 The complementary, unobservable nodes are termed \term{latent nodes} $\nodes_L = \nodes \setminus \nodes_{O}$, and should be understood as hidden random variables that are unknowable either by some fundamental process or cannot be measured due to other limitations.
@@
 The failure to satisfy an equality constraint immediately disqualifies $\prob[\nodes_{O}]$ from being compatible with $\graph$.
-Equality constraints are easily derived given a causal structure, and checking equality-constraints satisfaction is the minimalistic algorithm which powers the overwhelming majority of practical causal inference hypothesis testing in the fields of machine learning and artificial intelligence.
+Equality constraints are easily derived given a causal structure, and checking equality-constraint satisfaction is the minimalistic algorithm which powers the overwhelming majority of practical causal inference hypothesis testing in the fields of machine learning and artificial intelligence.
 In quantum theory, however, we require strong, more sensitive, causal inference techniques.
@@
 Henceforth, we will use these two terms interchangeably.
-From a resource standpoint, if the nonclassicality of $\prob[\nodes_{O}]$ with $\graph$ can be witnessed by an inequality $I$, but nevertheless $\prob[\nodes_{O}]$ can be implemented using quantum states and measurements while otherwise respecting the causal relations of $\graph$, then the causal compatibility inequality $I$ represents a task or game where quantum resources out-perform classical resources relative to $\graph$.
+From a resource standpoint, if the nonclassicality of $\prob[\nodes_{O}]$ with $\graph$ can be witnessed by an inequality $I$, but nevertheless $\prob[\nodes_{O}]$ can be implemented using quantum states and measurements while otherwise respecting the causal relations of $\graph$, then the causal compatibility inequality $I$ represents a task or game where quantum resources outperform classical resources relative to $\graph$.
 
@@
     \[ \ba{AB | S_{A} = 0, S_{B} = 0} + \ba{AB | S_{A} = 0, S_{B} = 1} + \ba{AB | S_{A} = 1, S_{B} = 0} - \ba{AB | S_{A} = 1, S_{B} = 1} \leq 2 \eq \label[ineq]{eq:CHSH_ineq_orig} \]
-    Non-trivial Bell inequalities such as the CHSH inequality are capable of witnessing the nonclassical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type.
+    Nontrivial Bell inequalities such as the CHSH inequality are capable of witnessing the nonclassical nature of quantum distributions; the inequalities presented in \cref{sec:found_inequalities} are also of this type.
 Equality constraints, as previously mentioned, never have that sort of high-resolution discernment sensitivity.
@@
 
-    As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$.
+    As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pairwise sharing latent variables $X, Y, Z$.
 
@@
 It maintains superficial simplicity (only three observable variables) while introducing many challenging features not found in the study of the Bell structure.
-    For example, the spaces of both classical and quantum distributions on the Triangle structure are non-convex \cite{Fritz_2012,Inflation}, unlike for the Bell structure.
+    For example, the spaces of both classical and quantum distributions on the Triangle structure are nonconvex \cite{Fritz_2012,Inflation}, unlike for the Bell structure.
 The convexity of the Bell structure's distributions is arguably responsible for the wealth of knowledge about it, including its complete characterization of classicality \cite{Brunner_2013}.
-    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible-but-quantum distribution for the Triangle structure, so it is known to possess quantum nonclassicality.
+    Importantly, \citet{Fritz_2012} explicitly demonstrated the existence of (at least) one incompatible but quantum distribution for the Triangle structure, so it is known to possess quantum nonclassicality.
 It seems reasonable to assume that quantum nonclassicality in the Triangle structure should be translatable into a computational advantage for certain computational circuits~\cite{Terhal_2002}; novel instances of nonclassicality are expected to correspond to novel information-theoretical quantum advantages.
@@
 Recently, \citet{Inflation} derived a variety of new, especially sensitive, polynomial causal compatibility inequalities for the Triangle structure.
-In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is nonclassical, it is also non-quantum.
-The non-quantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
+In particular, the inequalities of \cite{Inflation} expose a previously unclassified (as assessed by all formerly known constraints) distribution called the $w$-distribution\footnote{Although the $w$-distribution is nonclassical, it is also nonquantum.
+The nonquantum nature of the $w$-distribution has been demonstrated by Miguel Navascués and Elie Wolfe in private correspondence.} as incompatible with the Triangle structures.
     Remarkably, \emph{none} of the existing causal compatibility inequalities for the Triangle structure were known to admit violation by any quantum distribution.
@@
         \scalebox{1.0}{\includegraphics{figure_triangle_structure_operational_fritz_bell.pdf}}
-        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{A},S_{B}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
+        \caption{The Triangle structure reimagined to mimic the Bell structure. The measurement settings $S_{A},S_{B}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
         \label{fig:triangle_structure_with_fritz_bell_embedded}
@@
 From this diagram, it can be seen that each of $C$'s outcomes restricts the possible outcomes for $A,B$ into a $2 \times 2$ block.
-Effectively, $C$'s bits are perfectly correlated with the left-bits of $A,B$; $C_l = A_l$ and $C_r = B_l$.
+Effectively, $C$'s bits are perfectly correlated with the left-hand bits of $A,B$; $C_l = A_l$ and $C_r = B_l$.
     \begin{figure}
@@
             \caption{The Fritz distribution visualized using a $4 \times 4 \times 4$ grid.
-The $4$ outcomes of $A,B,C$ are written in binary as a doublet of bits to illustrate that certain bits act as measurement pseudo-settings.}
+The $4$ outcomes of $A,B,C$ are written in binary as a doublet of bits to illustrate that certain bits act as measurement pseudosettings.}
             \label{fig:fritz_distribution_visualized}
@@
     \end{align*}
-    As an example, the famous CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original} is translated into a constraint on the correlation between the right-bits of $A$ and $B$ under~\cref{eq:fritz_relabelling},
+    As an example, the famous CHSH inequality (\cref{eq:CHSH_ineq_orig})~\cite{CHSH_Original} is translated into a constraint on the correlation between the right-hand bits of $A$ and $B$ under~\cref{eq:fritz_relabelling},
     \[ C = C_{l}C_{r} = A_{l}B_{l} \Longrightarrow \ba{A_r B_r|C = 00} + \ba{A_r B_r|C = 01} + \ba{A_r B_r|C = 10} - \ba{A_r B_r|C = 11} \leq 2, \eq \label[ineq]{eq:CHSH_intriangle} \]
@@
 
-    It is important to understand the domain in which Fritz's proof of incompatibility is valid; its proof relies on the perfect correlation between $C$'s outcomes and the measurement pseudo-settings (left-bits) of $A$ and $B$.
+    It is important to understand the domain in which Fritz's proof of incompatibility is valid; its proof relies on the perfect correlation between $C$'s outcomes and the measurement pseudosettings (left-hand bits) of $A$ and $B$.
 For example, if one combines \cref{eq:fritz_dist} with slight uniform noise, what can be said with confidence regarding if the resulting modified distribution is classical or not?
@@
 
-    Explicitly, we parameterized the subset of quantum distributions accessible by bipartite qubit density matrices and $2$-outcome POVM measurements\footnote{In \cref{sec:optimizations}, we discuss methods for conducting similar parameterizations of quantum states and measurements.}.
-This preliminary investigation did not yield interesting solutions, as none of the Triangle structure inequalities in~\cite{Inflation} or~\cite{Henson_2014} were violated\footnote{We also directly checked all 2-outcome coarse-grainings of the Fritz distribution against the inequalities in~\cite{Inflation,Henson_2014}, with no violation.}.
+    Explicitly, we parameterized the subset of quantum distributions accessible by bipartite qubit density matrices and two-outcome POVM measurements\footnote{In \cref{sec:optimizations}, we discuss methods for conducting similar parameterizations of quantum states and measurements.}.
+This preliminary investigation did not yield interesting solutions, as none of the Triangle structure inequalities in~\cite{Inflation} or~\cite{Henson_2014} were violated\footnote{We also directly checked all two-outcome coarse grainings of the Fritz distribution against the inequalities in~\cite{Inflation,Henson_2014}, with no violation.}.
 Unfortunately, these early results are inconclusive for two reasons.
@@
 
-    Nonetheless, having failed to observe a quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for \emph{non}-classical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.
+    Nonetheless, having failed to observe a quantum-classical gap in the Triangle structure for \textit{binary-outcome} measurements, a continued search for nonclassical distributions in the Triangle structure must expand the gamut of inequalities to optimize against to include inequalities referencing strictly more than two outcomes.
 
@@
 Consequently, the derivation of \cref{eq:ww_ineq,eq:web_inequality,eq:symmetric_web_inequality} is guaranteed by~\cite{Navascues_2017} for sufficiently large inflations.
-Nonetheless, the following inequalities were obtained using the relatively small inflations found in \cref{fig:inflations}\footnote{Note that the adjectives \textit{large} and \textit{small} used to describe an inflation only become well-defined in the context of the hierarchy proposed in~\cite{Navascues_2017}.
+Nonetheless, the following inequalities were obtained using the relatively small inflations found in \cref{fig:inflations}\footnote{Note that the adjectives \textit{large} and \textit{small} used to describe an inflation only become well defined in the context of the hierarchy proposed in~\cite{Navascues_2017}.
 For example, the Web Inflation in \cref{fig:the_web_inflation} is second in the hierarchy of~\cite{Navascues_2017} whereas the Wagon-Wheel Inflation in \cref{fig:wagon_wheel_inflation} is somewhere between the first and second order.}.
-This efficiency is not universally guaranteed; for comparison, we remark that unlike the Fritz distribution, the conjectured incompatibility of the $4$-outcome distribution proposed by \cite{Gisin_2017} is \textit{not} confirmed by Inflation Technique at the same level.
+This efficiency is not universally guaranteed; for comparison, we remark that unlike the Fritz distribution, the conjectured incompatibility of the four-outcome distribution proposed by \cite{Gisin_2017} is \textit{not} confirmed by Inflation Technique at the same level.
 
@@
 
-    \Cref{eq:ww_ineq} is termed the Wagon-Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it.
+    \Cref{eq:ww_ineq} is termed the Wagon-Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it.
 To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}.
@@
 
-    In order for the numerical optimization to avoid distributions similar to $\prob[\fritz]$ we require an objective function which is \emph{not} tailor-designed to witness $\prob[\fritz]$.
-Finding such an inequality proved extremely challenging; while we could generate thousands of inequalities using the Inflation Technique~\cite{Inflation}, it appeared than only a vanishingly-small fraction of those inequalities admitted quantum violation whatsoever.
+    In order for the numerical optimization to avoid distributions similar to $\prob[\fritz]$ we require an objective function which is \emph{not} tailor designed to witness $\prob[\fritz]$.
+Finding such an inequality proved extremely challenging; while we could generate thousands of inequalities using the Inflation Technique~\cite{Inflation}, it appeared than only a vanishingly small fraction of those inequalities admitted quantum violation whatsoever.
 We therefore modified the Inflation Technique to give us an inequality which both witnesses the nonclassicality of $\prob[\fritz]$ but which is also symmetric with respect to any permutation of the variables $A, B, C$, resulting in \cref{eq:symmetric_web_inequality}.
@@
 Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$.
-Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:triangle_Qcompatibility} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
+Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:triangle_Qcompatibility} to be rewritten as \cref{eq:quantum_model_triangle_pvms}.
     \[ \prob[ABC]\br{abc} = \bramidket{m_{A,a}m_{B,b}m_{C,c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{A,a}m_{B,b}m_{C,c}} \eq \label{eq:quantum_model_triangle_pvms}\]
@@
     Where the real valued parameters $\la = \bc{\la_{n,m} \mid n,m \in 1, \ldots, d}$ have periodicities $\la_{m,n} \in \bs{0, \f{\pi}{2}}$ for $m < n$ and $\la_{m,n} \in \bs{0, 2 \pi}$ for $m \geq n$.
-Moreover, $P_l$ are one-dimensional projective operators $P_l = \ket{l}\bra{l}$ and the $\si_{m,n}$ are generalized anti-symmetric $\si$-matrices $\sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m}$ where $1 \leq m < n \leq d$.
+Moreover, $P_l$ are one-dimensional projective operators $P_l = \ket{l}\bra{l}$ and the $\si_{m,n}$ are generalized antisymmetric $\si$-matrices $\sigma_{m,n} = -i \ket{m}\bra{n} +i \ket{n}\bra{m}$ where $1 \leq m < n \leq d$.
 This parameterization has the useful feature that each of the real-valued parameters $\la_{n,m}$ a direct and intuitive physical affect on each element of a computational basis $\bc{\ket{1}, \ldots, \ket{d}}$.
-Explicitly, $\exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the sub-space spanned by $\ket{m}$ and $\ket{n}$ for $m < n$.
+Explicitly, $\exp\br{i \si_{m,n} \lambda_{m,n}}$ applies a rotation to the subspace spanned by $\ket{m}$ and $\ket{n}$ for $m < n$.
 Analogously, $\exp\br{i P_n \lambda_{n,m}}$ generates the relative phase between $\ket{m}$ and $\ket{n}$ for $m > n$ and $\exp\br{iP_l \lambda_{l,l}}$ fixes the global phase of $\ket{l}$.
@@
 
-    Since the inequalities we seek to optimally violate are polynomial, and since the space of quantum-accessible distributions is non-convex, we employ a number of optimization methods consecutively in an attempt to avoid pitfalls associated identifying local minima and ill-conditioned convergence.
-Specifically, the Broyden-Fletcher-Goldfarb-Shanno method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.
-
-    Nevertheless, we strongly caution against misinterpreting the numerical optima present in \cref{sec:optima} as if our findings represent genuine global-maxima of violation.
+    Since the inequalities we seek to optimally violate are polynomial, and since the space of quantum-accessible distributions is nonconvex, we employ a number of optimization methods consecutively in an attempt to avoid pitfalls associated identifying local minima and ill-conditioned convergence.
+Specifically, the Broyden-Fletcher-Goldfarb-Shanno method~\cite[p.142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p.238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient-descent-based methods.
+
+    Nevertheless, we strongly caution against misinterpreting the numerical optima present in \cref{sec:optima} as if our findings represent genuine global maxima of violation.
 Evidence for the unreliability of our numerical methods is the following: When supplied with randomly sampled initial parameters, \emph{all} optimization methods consistently converged to \emph{saturating} the target inequalities, instead of violating it!
@@
 Upon doing so, it was observed that the numerical methods converged invariably to parameters which generated distributions similar to $\prob[\fritz]$ (see~\cref{fig:maximum_violation_I_1} for instance); consequently making interpreting the results somewhat murky.
-Could it be that the inequality's global maximum is, in-fact, not far from $\prob[\fritz]$?
+Could it be that the inequality's global maximum is in fact not far from $\prob[\fritz]$?
 Or is this a limitation of the ill-conditioned nature of the optimization?
@@
 Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution; in fact \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share their \term{possibilistic structure}.
-A distribution's possibilistic structure is the subset of events which it assigns a non-zero probability.
+A distribution's possibilistic structure is the subset of events which it assigns a nonzero probability.
 That \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} have the same possibilistic structure is not entirely unexpected;  As was mentioned in \cref{sec:found_inequalities}, as $I\tsb{Web}$ was derived specifically to prove the incompatibility of the Fritz distribution with the Triangle structure.
 Consequently, it seems that $I\tsb{Web}$ best witnesses incompatibility of those distributions that closely resemble the $\prob[\fritz]$.
-It could be, however, that the sharing of possibilistic structure is an artifact of unreliable convergence, such that the true optimally-violating $I\tsb{Web}$ quantum distribution might have a different structure.
+It could be, however, that the sharing of possibilistic structure is an artifact of unreliable convergence, such that the true optimally violating $I\tsb{Web}$ quantum distribution might have a different structure.
 
     It is perhaps curious, however, that violation achieved by the distribution in \cref{fig:maximum_violation_I_1} is not accessible when the bipartite states in \cref{eq:triangle_Qcompatibility} are restricted to maximally entangled states.
-This finding of more-violation with less-entanglement resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} demonstrating that entanglement and nonclassicality are different resources.
+This finding of more violation with less entanglement resembles a feature of quantum mechanics originally presented by~\citet{Methot_2006} demonstrating that entanglement and nonclassicality are different resources.
 
     Our best numerical optimization of $I\tsb{SymmetricWeb}$ is visualized in \cref{fig:maximum_violation_I_3}.
-Counter-intuitively, the distribution in \cref{fig:maximum_violation_I_3}, which achieves a greater violation of $I\tsb{SymmetricWeb}$ than $\prob[\fritz]$, shares its \textit{possibilistic} structure with the Fritz distribution!
+Counterintuitively, the distribution in \cref{fig:maximum_violation_I_3}, which achieves a greater violation of $I\tsb{SymmetricWeb}$ than $\prob[\fritz]$, shares its \textit{possibilistic} structure with the Fritz distribution!
 Additionally, since $I\tsb{SymmetricWeb}$ is symmetric with respect to the permutation of parties, one might expect that the maximum violating distribution be symmetric as well.
@@
 By increasing the cardinality of each variable $A, B, C$ to $4^{3} = 64$, it is possible to generate a distribution that is nonclassical yet quantum and requires \textit{all three} of the shared resources to be entangled.
-This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings.
+This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudosettings.
 Such a distribution would require entanglement in all three quantum states; under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible\footnote{This observation was original provided by Miguel Navascués.}.
@@
     In consideration of this particular construction, perhaps the correct assessment for novel nonclassicality must incorporate a restriction on the the cardinality of the observed variables?
-Pursuant to this objective, we were able to prove the nonclassicality of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations\footnote{An inequality-free proof of the incompatibility of this distribution, using arguments analogous those presented in~\cite{Fritz_2012}, can be found in~\cite{Weilenmann_2016}.
+Pursuant to this objective, we were able to prove the nonclassicality of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anticorrelations\footnote{An inequality-free proof of the incompatibility of this distribution, using arguments analogous those presented in~\cite{Fritz_2012}, can be found in~\cite{Weilenmann_2016}.
 Assessing the compatibility of this variant using the methods in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities} was first suggested to the authors by Denis Rosset.}.
@@
     In \cref{sec:noise} it was demonstrated that these causal compatibility inequalities are robust to noise, directly revealing a critical departure from Fritz's original proof of the incompatibility of the Fritz's perfect-correlation example.
-In \cref{sec:optimizations} we found quantum distributions \textit{quantitatively} distinct from the Fritz's recycled-Bell's-theorem example, such that these optimized distributions more strongly violate certain causal compatibility inequalities.
+In \cref{sec:optimizations} we found quantum distributions \textit{quantitatively} distinct from the Fritz's recycled Bell theorem example, such that these optimized distributions more strongly violate certain causal compatibility inequalities.
 
@@
 Additionally, this section aims to accomplish something further: If such as joint distribution $\prob[\jointvar]$ exists, how does one find it?
-If not, how does one find an inequality whose violation by $\bc{\prob[V_1], \ldots, \prob[V_m]}$ proves the non-existence of a joint distribution.
+If not, how does one find an inequality whose violation by $\bc{\prob[V_1], \ldots, \prob[V_m]}$ proves the nonexistence of a joint distribution.
 This is accomplished by illustrating how the marginal problem can be expressed as a linear program in which the solution to the marginal problem is encoded in the feasibility or infeasibility of said linear program.
@@
     \[ \forall V \in \mscenario : \prob[V] = \sum_{\jointvar \setminus V} \prob[\jointvar] \eq \label{eq:def:marginal_problem}\]
-    A marginal model $\prob^{\mscenario}$ is said to be \textit{contextual} if it \textit{does not} admit a joint distribution and \textit{non-contextual} otherwise.
+    A marginal model $\prob^{\mscenario}$ is said to be \textit{contextual} if it \textit{does not} admit a joint distribution and noncontextual otherwise.
 Notice that \cref{eq:def:marginal_problem} is inherently a linear system of constraints which can be solved efficiently using linear programs.
@@
     To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$.
-We also define the set of all \term{events over $v$}, denoted $\Events{v}$,\footnote{In the language of sheaf-theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
+We also define the set of all \term{events over $v$}, denoted $\Events{v}$,\footnote{In the language of sheaf theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
 Evidently, $\Events{v}$ and $O_v$ have a one-to-one correspondence and this distinction can be confounding.
@@
         \label{def:incidence_matrix}
-        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} events $j \in \Events{\jointvar}$ and the rows are events by \textit{marginal} events $m \in \Events{\mscenario}$.
+        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bitwise matrix where the columns are indexed by \textit{joint} events $j \in \Events{\jointvar}$ and the rows are events by \textit{marginal} events $m \in \Events{\mscenario}$.
 The entries of $M$ are populated whenever a marginal event $m$ is a restriction of the joint event $j$.
@@
         \end{cases} \eq \label{eq:incidence_definition}\]
-        The incidence matrix has $\abs{\Events{\jointvar}}$ columns, $\abs{\Events{\mscenario}} = \sum_{i} \abs{\Events{V_i}}$ rows and $k\abs{\Events{\jointvar}}$ non-zero entries.
+        The incidence matrix has $\abs{\Events{\jointvar}}$ columns, $\abs{\Events{\mscenario}} = \sum_{i} \abs{\Events{V_i}}$ rows and $k\abs{\Events{\jointvar}}$ nonzero entries.
     \end{definition}
@@
 Therefore the \textit{sign} of the dual objective $d \defined \min \br{y \cdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality; if $d < 0$ then $y \cdot \probvec^{\mscenario} \geq 0$ is violated and therefore $\probvec^{\mscenario}$ is contextual.
-Likewise if $d \geq 0$ (satisfying $y \cdot \probvec^{\mscenario}$), then $\probvec^{\mscenario}$ is non-contextual.\footnote{Actually, if $d \geq 0$ then it is exactly $d = 0$ due to the existence of the trivial $y = \emptyset$.
+Likewise if $d \geq 0$ (satisfying $y \cdot \probvec^{\mscenario}$), then $\probvec^{\mscenario}$ is noncontextual.\footnote{Actually, if $d \geq 0$ then it is exactly $d = 0$ due to the existence of the trivial $y = \emptyset$.
 This observation is an instance of the \textit{Complementary Slackness Property} of~\cite{Bradley_1977}.
@@
 Most linear program software packages such as Mosek~\cite{Mosek_2016}, Gurobi~\cite{Gurobi_2016}, CPLEX~\cite{Cplex_2016} and CVX/CVX OPT~\cite{CVX_2016,CVX_Opt_2016} are capable of producing infeasibility certificates.
-Furthermore, for every $y$ satisfying $y \cdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of non-contextual marginal models.
+Furthermore, for every $y$ satisfying $y \cdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of noncontextual marginal models.
 If $y$ is an infeasibility certificate, then $y \cdot \probvec^{\mscenario} \geq 0$ is satisfied by all contextual marginal models.
 
-    The marginal problem can sometimes take on a more general variant that does not begin with a specific marginal model~\cite{Abramsky_2012,Mansfield_2012,Fritz_2011}: \textit{Given a marginal scenario $\mscenario$, what is the set of all non-contextual marginal models?} \citet{Pitowsky_1991} demonstrates that the set of non-contextual marginal models forms a \textit{convex} polytope called the \term{marginal polytope}.
+    The marginal problem can sometimes take on a more general variant that does not begin with a specific marginal model~\cite{Abramsky_2012,Mansfield_2012,Fritz_2011}: \textit{Given a marginal scenario $\mscenario$, what is the set of all noncontextual marginal models?} \citet{Pitowsky_1991} demonstrates that the set of noncontextual marginal models forms a \textit{convex} polytope called the \term{marginal polytope}.
 The extremal rays of a marginal polytope directly correspond to the columns of $M$ which further correspond to \textit{deterministic} joint distributions $\probvec^{\jointvar}$.
 Since all joint distributions $\probvec^{\jointvar}$ are probability distributions, their entries must sum to unity $\sum_{j \in \Events{\jointvar}} \probvec^{\jointvar}_j = 1$.
-This normalization defines the convexity of the polytope; all non-contextual marginal models are convex mixtures of the deterministic marginal models pursuant to \cref{eq:incidence_matrix_use}.
+This normalization defines the convexity of the polytope; all noncontextual marginal models are convex mixtures of the deterministic marginal models pursuant to \cref{eq:incidence_matrix_use}.
 The marginal polytope is a beneficial tool for understanding contextuality.
@@
 Given a distribution $\prob[\nodes_{O}]$ defined over the observable nodes of $\graph$, one can compute a marginal model defined over the injectable sets $\prob^{\Inj[\graph]{\graph'}} = \bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ and their images $\prob^{\ImInj[\graph]{\graph'}} = \bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$.
-The contrapositive of the Inflation Lemma casts the compatibility problem for $\prob^{\ImInj[\graph]{\graph'}}$ (which exhibits equivalent compatibility as $\prob[\nodes_O]$) into a compatibility problem for $\prob^{\Inj[\graph]{\graph'}}$ of any non-trivial inequalities.
+The contrapositive of the Inflation Lemma casts the compatibility problem for $\prob^{\ImInj[\graph]{\graph'}}$ (which exhibits equivalent compatibility as $\prob[\nodes_O]$) into a compatibility problem for $\prob^{\Inj[\graph]{\graph'}}$ of any nontrivial inequalities.
 If $\prob^{\Inj[\graph]{\graph'}}$ is found to be incompatible with $\graph'$, then $\prob^{\ImInj[\graph]{\graph}}$ (and also $\prob[\nodes_O]$) must be incompatible with $\graph$.
@@
 
-    Unlike $\prob^{\ImInj[\graph]{\graph'}}$, which is non-contextual by construction, $\prob^{\Inj[\graph]{\graph'}}$ contains overlapping marginals meaning its contextuality remains unknown and must be determined using any of the techniques discussed in~\cref{sec:marginal_satisfiability}.
+    Unlike $\prob^{\ImInj[\graph]{\graph'}}$, which is noncontextual by construction, $\prob^{\Inj[\graph]{\graph'}}$ contains overlapping marginals meaning its contextuality remains unknown and must be determined using any of the techniques discussed in~\cref{sec:marginal_satisfiability}.
 More importantly, the Inflation Technique introduces constraints relating to the ai-expressible sets.
@@
     \[ \mscenario = \AIExpr[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
-    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well.
+    Given that the Fritz distribution is defined over four-outcome variables, the variables in the marginal scenario are assigned four-outcomes as well.
 This marginal scenario $\mscenario$ then defines an incidence matrix $M$ capable of accommodating the Fritz distribution that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = 4^8 = 65,536$ columns; this matrix is not reproduced here.
-The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.
+The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear quantifier elimination intractable.
 To construct the marginal distribution vector $\probvec^{\mscenario}$ for the Fritz distribution, one begins with $\probvec^{\mscenario}$ defined in a \textit{symbolic} form,
@@
     The same is applied to all other entries of $\probvec^{\mscenario}$.
-Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained, corresponding precisely to \cref{eq:ww_ineq} using \cref{eq:marginal_vector_wagon_wheel_factors_dropped} in bit-wise notation.
+Finally, this numerical version of $\probvec^{\mscenario}$ and $M$ are subjected to linear programing software and an infeasibility certificate $y$ was obtained, corresponding precisely to \cref{eq:ww_ineq} using \cref{eq:marginal_vector_wagon_wheel_factors_dropped} in bitwise notation.
 
@@
 The maximal ai-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{tab:asexpr_triangle_structure_web}.
-Analogously to the Wagon-Wheel inflation, these ai-expressible sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ non-zero entires.
+Analogously to the Wagon-Wheel inflation, these ai-expressible sets form a marginal scenario $\mscenario$ which defines an incidence matrix $M$ that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{6} + 8 \cdot 4^3 = 16,896$ rows, $\abs{\Events{\jointvar}} = 4^{12} = 16,777,216$ columns and $201,326,592$ nonzero entires.
 
@@
 First, \citet{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:marginal_satisfiability}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope.
-They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that non-trivial inequalities can be recovered from facets of a symmetric polytope.
+They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that nontrivial inequalities can be recovered from facets of a symmetric polytope.
 Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not.
-The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution.\footnote{If the extremal distribution happens to be asymmetric, then one can conclude the space of accessible distributions is non-convex.}
+The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution.\footnote{If the extremal distribution happens to be asymmetric, then one can conclude the space of accessible distributions is nonconvex.}
 
     To clarify which symmetries we have in mind, first consider the marginal scenario $\mscenario = \bc{\bc{A, B, C}, \bc{C, D}, \bc{A, D}}$ where each variable in $\jointvar = \bc{A,B,C,D}$ has binary outcomes $\bc{0,1}$.
-${I_{\mscenario} \defined \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}}$ is an inequality constraining the set of non-contextual marginal models $\prob^{\mscenario}$.
+${I_{\mscenario} \defined \bc{\prob[ABC][010] \leq \prob[CD][00] + \prob[AD][01]}}$ is an inequality constraining the set of noncontextual marginal models $\prob^{\mscenario}$.
 Now, the contextuality of a distribution $\prob[ABCD]$ should be \textit{invariant} under those permutations of the variable labels in $\jointvar$  which map the marginal scenario to itself; but not all variable relabellings preserve $\mscenario$.

### 2020-07-14 CCIAQVTS/CCIAQVTS_errata.tex
final edits to the errata

@@
     One avenue for correcting the above inequality would be to simply reverse the direction of the inequality sign ($\leq \mapsto \geq$), or equivalently flip the sign of each of the coefficients.
-While the inequality resulting from such a correction would indeed be a valid causal compatibility inequality for the triangle structure, it has the undesirable feature of being \textit{satisfied} by the Fritz's distribution $P_{\text{F}}$ with a numerical value of $\frac{1}{16} \geq 0$.
+While the inequality resulting from such a correction would indeed be a valid causal compatibility inequality for the triangle structure, it has the undesirable feature of being \textit{satisfied} by Fritz's distribution $P_{\text{F}}$ with a numerical value of $\frac{1}{16} \geq 0$.
 
@@
 
-    It is also worth noting that the qualitative features of the wagon-wheel inequality discussed in the ``Numerical optimization results'' section of the published article were actually obtained from our proposed substitute inequality~(\ref{eq:ww_ineq_correct}), not the incorrectly published inequality~(\ref{eq:ww_ineq_incorrect}), and therefore those comments do not require any alteration.
+    It is also worth noting that the qualitative features of the wagon-wheel inequality discussed in the ``Numerical optimization results'' section of the published article were actually determined using, and thus pertain to, our proposed substitute inequality~(\ref{eq:ww_ineq_correct}), not the incorrectly published inequality~(\ref{eq:ww_ineq_incorrect}).
+Consequently, those comments do not require any alteration.
 Inequality~(\ref{eq:ww_ineq_incorrect}) was published in place of inequality~(\ref{eq:ww_ineq_correct}) due to an error made by the first author during the final drafting stages of the manuscript.
@@
     % \bibliographystyle{apsrev4-1}
-    \nocite{apsrev41Control}
-    \bibliography{references}
+    %\nocite{apsrev41Control}
+    %\bibliography{references}
 

### 2020-08-07 CCIAQVTS/CCIAQVTS_errata.tex
minor changes to errata
minor edits to the errata to match the published version of the errata

@@
 \documentclass[aps, 10pt, english, twoside, pra, nofootinbib, tightenlines, longbibliography, superscriptaddress, notitlepage]{revtex4-1}
-
-% === Bibliography Style Options ===
-\bibliographystyle{apsrev4-1}
-\setlength{\bibsep}{3pt plus 3pt minus 2pt}
 
@@
     % \setlength{\parskip}{1em}
-    \section{The Wagon-Wheel Inequality}
+    %\section{The Wagon-Wheel Inequality}
     Our article claimed that inequality (12), reproduced here,
@@
     is a valid causal compatibility inequality for the triangle structure.
-Additionally, we claimed that the distribution in equation (8), namely Fritz's distrubtion $P_{\text{F}}$, achieves a violation of the above inequality with a numerical value of $\frac{1}{16} \not\leq 0$.
+Additionally, we claimed that the distribution in Eq.
+(8), namely, Fritz's distrubtion $P_{\text{F}}$, achieves a violation of the above inequality with a numerical value of $\frac{1}{16} \not\leq 0$.
 Both of these reported claims are false.
 
-    One avenue for correcting the above inequality would be to simply reverse the direction of the inequality sign ($\leq \mapsto \geq$), or equivalently flip the sign of each of the coefficients.
-While the inequality resulting from such a correction would indeed be a valid causal compatibility inequality for the triangle structure, it has the undesirable feature of being \textit{satisfied} by Fritz's distribution $P_{\text{F}}$ with a numerical value of $\frac{1}{16} \geq 0$.
+    One avenue for correcting the above inequality would be to simply reverse the direction of the inequality sign ($\leq \mapsto \geq$), or, equivalently, flip the sign of each of the coefficients.
+Although the inequality resulting from such a correction would, indeed, be a valid causal compatibility inequality for the triangle structure, it has the undesirable feature of being \textit{satisfied} by Fritz's distribution $P_{\text{F}}$ with a numerical value of $\frac{1}{16} \geq 0$.
 
@@
     \end{equation*}
-    Note that inequality~(\ref{eq:ww_ineq_correct}) is related to inequality~(\ref{eq:ww_ineq_incorrect}) by (i) flipping the signs of every coefficient, and (ii) flipping the bit-values for both $B_r$ and $C_l$.
-This substitute inequality is indeed a valid causal compatibility inequality for the triangle structure and moreover is violated by the Fritz distribution with a numerical violation of $\f{1}{16}(\sqrt{2} - 1) \not \leq 0$.
+    Note that inequality~(\ref{eq:ww_ineq_correct}) is related to inequality~(\ref{eq:ww_ineq_incorrect}) by (i) flipping the signs of every coefficient, and (ii) flipping the bit values for both $B_r$ and $C_l$.
+This substitute inequality is, indeed, a valid causal compatibility inequality for the triangle structure and, moreover, is violated by the Fritz distribution with a numerical violation of $\f{1}{16}(\sqrt{2} - 1) \not \leq 0$.
 
-    It is also worth noting that the qualitative features of the wagon-wheel inequality discussed in the ``Numerical optimization results'' section of the published article were actually determined using, and thus pertain to, our proposed substitute inequality~(\ref{eq:ww_ineq_correct}), not the incorrectly published inequality~(\ref{eq:ww_ineq_incorrect}).
+    It is also worth noting that the qualitative features of the wagon-wheel inequality discussed in the ``Numerical optimization results'' section of the published article were actually determined using, and, thus, pertain to, our proposed substitute inequality~(\ref{eq:ww_ineq_correct}), not the incorrectly published inequality~(\ref{eq:ww_ineq_incorrect}).
 Consequently, those comments do not require any alteration.
-Inequality~(\ref{eq:ww_ineq_incorrect}) was published in place of inequality~(\ref{eq:ww_ineq_correct}) due to an error made by the first author during the final drafting stages of the manuscript.
+Inequality~(\ref{eq:ww_ineq_incorrect}) was published in place of inequality~(\ref{eq:ww_ineq_correct}) due to an error made by the first author during the final drafting stages of the paper.
 
-    \section{Figure 1}
-    The diagram appearing in Figure 1 of our article is incorrectly a duplicate of the diagram appearing in Figure 3. Instead, Figure 1 should have been been the following:
+    %\section{Figure 1}
+    The diagram appearing in Fig. 1 of our article is incorrectly a duplicate of the diagram appearing in Fig. 3. Instead, Fig. 1 should have been been the following:
     \begin{figure}
@@
 
-    \begin{acknowledgments}
-        The authors would like to thank Rafael Chaves for identifying the error with the wagon-wheel inequality found in earlier versions of this paper.
-    \end{acknowledgments}
+    %\begin{acknowledgments}
+        The authors would like to thank R. Chaves for identifying the error with the wagon-wheel inequality found in earlier versions of this paper.
+    %\end{acknowledgments}
 

### 2020-08-07 CCIAQVTS/CCIAQVTS.tex
added links to the published errata in footnotes marking locations of the errors

@@
     \subsection{The WagonWheel Inequality}
-    The first causal compatibility inequality chosen for presentation is reported below:
+    The first causal compatibility inequality chosen for presentation is reported below:\footnote{\label{foot:error}In earlier versions of this paper, including the version published in Physical Review A (found here: \url{https://journals.aps.org/pra/abstract/10.1103/PhysRevA.98.022113}) and the initial arXiv submission, \Cref{eq:ww_ineq} was incorrectly presented.
+A detailed errata can be found here: \url{https://journals.aps.org/pra/abstract/10.1103/PhysRevA.102.029901}.}
+
     \begin{equation*}
@@
     By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure per \cref{eq:triangle_compatibility} must satisfy $I\tsb{WagonWheel}$.
-On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $\f{1}{16}(\sqrt{2} - 1) \not \leq 0$.
+On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $\f{1}{16}(\sqrt{2} - 1) \not \leq 0$\footnote{As a result of the error mentioned in Footnote~\ref{foot:error}, earlier versions of this paper erroneously reported a numerical violation of $\f{1}{16} \not \leq 0$.
+}.
 Consequently we affirm that the Fritz distribution is incompatible with the Triangle structure, a fact previously only demonstrated without inequalities.
